### 2015-06-19 stacky_write_up/spin_cring.tex
added spin_cring custom command divider

%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass{amsart}

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{subfiles}
\usepackage{mathpazo}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}

\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
\def\listtodoname{List of Todos}
\def\listoftodos{\@starttoc{tdo}\listtodoname}

%\addtolength{\oddsidemargin}{-.5 in}
	%\addtolength{\evensidemargin}{-.4 in}
	%\addtolength{\textwidth}{1 in}
%
	%\addtolength{\topmargin}{0 in}
	%\addtolength{\textheight}{0 in}

\RequirePackage{color}
\definecolor{myred}{rgb}{0.75,0,0}
\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{myblue}{rgb}{0,0,0.65}

\usepackage{hyperref}
  \hypersetup{colorlinks=true,citecolor=blue}

\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%%%%%%%%%%%%%%

\theoremstyle{plain}
  \newtheorem{thm}{Theorem}[section]
  \newtheorem{prop}[thm]{Proposition}
  \newtheorem{lem}[thm]{Lemma}
  \newtheorem{cor}[thm]{Corollary}
	\newtheorem{claim}[thm]{Claim}
	\newtheorem{question}[thm]{Question}

\theoremstyle{definition}
  \newtheorem{defn}[thm]{Definition}
  \newtheorem{example}[thm]{Example}
  \newtheorem{exer}[thm]{Exercise}
  \newtheorem{ctexample}[thm]{Counterexample}
  \newtheorem{convention}[thm]{Convention}
	\newtheorem{conjecture}[thm]{Conjecture}

\theoremstyle{remark}
	\newtheorem{rem}[thm]{Remark}
  \newtheorem{note}[thm]{Notation}
  \newtheorem*{note*}{Notation}
  \newtheorem{case}{Case}

\numberwithin{equation}{section}

%%%%%%%%%%%%%%%%%%%%%%%%% custom commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\nc{\newcommand}
\nc\on{\operatorname}
\nc\renc{\renewcommand}
\newcommand\ssec{\subsection*}
\newcommand\sssec{\subsubsection*}
\newcommand\bO{{\mathbf O}}
\newcommand\CC{{\mathcal C}}
\newcommand\BN{{\mathbb N}}
\newcommand\BC{{\mathbb C}}
\newcommand\BF{{\mathbb F}}
\newcommand\BR{{\mathbb R}}
\newcommand\BQ{{\mathbb Q}}
\newcommand\BP{{\mathbb P}}
\newcommand\BBZ{{\mathbb Z}}
\newcommand\uR{\underline{R}}
\newcommand\uZ{\underline{\BBZ}}
\newcommand\CF{{\mathcal F}}
\newcommand\uCF{\underline{{\mathcal F}}}
\newcommand\BZ{{\mathbb Z}}
\newcommand\BA{{\mathbb A}}
\newcommand\fa{{\mathfrak a}}
\newcommand\fp{{\mathfrak p}}
\newcommand\fq{{\mathfrak q}}
\newcommand\fm{{\mathfrak m}}
\newcommand\so{{\mathscr O}}
\newcommand\sg{{\mathscr G}}

\newcommand\scm{{\mathscr M}}
\newcommand\scn{{\mathscr N}}
\newcommand\scf{{\mathscr F}}
\newcommand\scg{{\mathscr G}}
\newcommand\sco{{\mathscr O}}
\newcommand\sch{{\mathscr H}}
\newcommand\scl{{\mathscr L}}
\newcommand\sci{{\mathscr I}}

\newcommand{\id}{\mathrm{id}}
\newcommand\im{\text{im }}
\newcommand\coker{\text{coker}}
\newcommand \spec{\text{Spec }}
\newcommand \proj{\text{Proj }}
\newcommand \rspec{\textit{Spec }}
\newcommand \rproj{\textit{Proj }}
\newcommand{\gal}{\mathrm{Gal}}

\newcommand \trdeg{\text{tr. deg }}
\newcommand \codim{\text{codim}}
\newcommand \rk{\text{rk }}
\newcommand \di{\text{div }}
\newcommand \depth{\text{depth }}

%%%%%%%%%%%%%%%%%%% spin cring custom commands %%%%%%%%%%%%%%%%%%%%%%

\newcommand \subhalf[1]{\frac{e_{#1} - 1}{2e_{#1}}}
\newcommand \sx{\mathscr X}
\newcommand{\se}[1]{\section*{Problem #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Spin canonical divisors of log stacky curves}

\author{Aaron Landesman}
\address[Aaron Landesman]{Department of Mathematics, Harvard University}
\email{aaronlandesman@college.harvard.edu}

\author{Peter Ruhm}
\address[Peter Ruhm]{Department of Mathematics, Stanford University}
\email{pruhm@stanford.edu}

\author{Robin Zhang}
\address[Robin Zhang]{Department of Mathematics, Stanford University}
\email{robinz16@stanford.edu}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
  Arithmetic geometry group at the Emory University Number Theory
	REU.
\end{abstract}

\maketitle

\section{Introduction}
This is our project.
Example, O'Dorney's paper \cite{dorney:canonical}.
We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{i}$.

\subsection{Main Results}
These are our results.

\section{Background}
Here are some definitions.
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.

\section{Genus zero}

\subsection{Effective}
Let us consider $\delta \geq 2$.

\subsection{Noneffective}
Now let us consider $\delta = 0$.
Overview, we do this, this, then this.

Here we do induction on adding points.

Then we raise coefficients.

Cases to induct on are here.

These are exceptional cases.

\section{Genus positive}
We haven't done this.

\section{Acknowledgements}
We are grateful to VZB.

\nocite{*}
\bibliography{bibliography}{}
\bibliographystyle{plain}

\end{document}

### 2015-06-19 stacky_write_up/spin_cring.tex
admissability at only one element

@@
 \newcommand\sg{{\mathscr G}}
+\newcommand \sx{\mathscr X}
 
@@
 \newcommand \depth{\text{depth }}
-
-%%%%%%%%%%%%%%%%%%% spin cring custom commands %%%%%%%%%%%%%%%%%%%%%%
+\DeclareMathOperator{\ord}{ord}
 
 \newcommand \subhalf[1]{\frac{e_{#1} - 1}{2e_{#1}}}
-\newcommand \sx{\mathscr X}
 \newcommand{\se}[1]{\section*{Problem #1}}
@@
 These are our results.
+\begin{thm}
+\label{thm:g_0_generators_relations}
+Let $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+\todo{Rewrite this to be more precise}
+\end{thm}
+\begin{proof}
+
+\end{proof}
 
@@
 
-\section{Genus zero}
-
-\subsection{Effective}
+\section{Effective Genus Zero Spin Divisors}
+\label{sec:g_0_effective}
 Let us consider $\delta \geq 2$.
 
-\subsection{Noneffective}
-Now let us consider $\delta = 0$.
-Overview, we do this, this, then this.
+\section{Non-effective Genus Zero Spin Divisors}
+\label{sec:g_0_non_effective}
 
-Here we do induction on adding points.
+In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+This is proven in Subsection ~\ref{ssec:g_0_conclusion}.
+The proof is a rather involved induction.
+In Subsections ~\ref{ssec:ram_pts}, ~\ref{ssec:ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction.
+Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.
 
-Then we raise coefficients.
+\ssec{Saturation}
+\label{ssec:g_0_saturation}
 
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points}
+\label{ssec:g_0_ram_pts}
+
+\begin{lem}
+\label{sat_three_induction}
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf i$.
+There are generators $y_3,y_4,y_5$ of $R_{D+D'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
+\todo{Include the order}
+Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively.
+\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
+\begin{align*}
+	in_\prec(I) = in_\prec(I')k[x,y_3,\ldots, y_e,z_4,z_5] + \\
+	\langle y_i y_j \mid 1 \leq i < j-3 \leq e \rangle +\\
+	\langle y_i x_j \mid i > 3 \rangle +\\
+	\langle z_i y_j \mid j > 3 \rangle  +\\
+	\langle z_i x_j \mid 4 \leq i \leq 5\rangle + \\
+	\langle z_iz_k \mid 4 \leq i \leq j \leq 5 \rangle 
+\end{align*}
+
+\end{lem}
+\begin{proof}
+We can see the following is a $k$ basis for $R$ over $R'$:
+\begin{align*}
+	\langle y_i^ay_{i+2}^b \mid a \geq 0,b\geq 0, 3 \leq i \leq e-2\rangle +\\
+	\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b \geq 0(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle +\\
+	\langle y_3^az_4,y_3^bz_5 \mid a \geq 0, b \geq 0 \rangle\\
+\end{align*}
+Note that this is precisely the monomials which are not divisible by those in the claimed initial ideal.
+By the trick of projecting to the pole order by degree 2-dim lattice, we see this is a $k$ basis.
+We also see that $z_i,y_j$ are generators.
+\todo{Note that $z_5$ is chosen specially, and is not generic}
+
+It only remains to show the initial ideal is as claimed. Note that once we show this, we will automatically obtain minimality, using the regrading to degree 1 trick.
+
+To show this is the initial ideal, it suffices to exhibit such relations with the claimed leading terms in the initial ideal.
+Indeed, we will now give only leading order terms.
+We have relations starting with
+\begin{align*}
+	y_iy_j - y_{i-1}y_{j+1} + \cdots &\mid i < j-1 \\
+	y_ix_4 - y_{i-2}y_3x_3 + \cdots & \mid i > 3\\
+	y_ix_5 - y_{i-2}y_3x_4 + \cdots & \mid i > 3\\
+	y_ix_3-y_3^3y_{i-6} + \cdots &\mid i > 7\\
+	y_7x_3-y_3^2 z_4 + \cdots \\
+	y_5x_3 - y_3z_5 + \cdots \\
+	z_4^2 - y_3 z_5 + \cdots \\
+	z_4z_5 - y_3^2x_3 + \cdots \\
+ 	z_5^2 - y_3^2 x_4 + \cdots \\
+ 	z_4 y_i - y_3^2 y_{i-2} + \cdots &\mid i > 3 \\
+ 	z_5 y_i - y_3y_{i-2}z_4 + \cdots &\mid i > 3 \\
+ 	z_i x_j - y_3 z_{i+j-3} + \cdots &\mid i+j \leq 8 \\
+ 	z_i x_j - y_3x_3x_{i+j-6} + \cdots &\mid i+j > 8
+\end{align*}
+\end{proof}
+\todo{Something is a little fishy with this order, it seems something like: first grade by degree, then try to decrease the highest y, if you cant, try to decrease the highest z, possibly replace $z_5$ by $z_5+Cy_5$ to generic element?}
+
+\ssec{Inductive theorem: Increasing the Ramification Orders}
+\label{ssec:g_0_ram_orders}
+In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}. Under fairly general conditions, this theorem will show that if
+
+\begin{defn}
+\label{defn:admissible}
+A pair $(\sx',e_i')$, with point $P$ corresponding to $e-2$ is admissible if
+\begin{enumerate}
+	\item There is an element $y_{e-2} \in R'$ so that $R'$ admits a presentation $(k[x] \otimes k[y_{e-2}])/I'$ with $\deg y_{e-2} = e-2$ and $-ord_P(y_{e-2}) = \frac{e-3}{2}$.
+\item For all $z \neq y_{e-2}$ generators of $R'$ we have
+\begin{align*}
+	\frac{- ord_P(z)}{\deg z} < \frac{e-3}{2(e-2)}
+\end{align*}
+\item We have
+\begin{align*}
+	\deg \lfloor e K_{\sx'} \rfloor \geq 0
+\end{align*}
+\end{enumerate}
+\end{defn}
+
+\begin{lem}
+\label{lem:admissible_inequality}
+Condition 2 of Definition ~\ref{defn:admissible} implies the stronger condition that
+\begin{align*}
+	-ord(z) \leq \deg(z) \frac{e-3}{2(e-2)}-\frac{1}{e-2}
+\end{align*}
+\end{lem}
+
+\begin{thm}
+\label{thm:ramification_order_induction}
+Suppose $(\sx',J)$ is admissible with a generator $y_{e-2} \in R'$ as in condition 1 of Definition ~\ref{defn:admissible}. Then the following are true:
+\begin{enumerate}
+	\item There exists $y_e \in H^0(\sx, e(K_\sx))$ so that 
+	\begin{align*}
+	-ord_P(y_e) = \frac{e-1}{2}
+\end{align*}
+\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
+\item Equip $k[y]$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
+\begin{align*}
+	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_{e-2} \rangle 
+\end{align*}
+	as $z$ ranges over generators of $R$.
+	\item Suppose $in_\prec(I')$ is minimally generated by quadratics and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$.
+\todo{prove this still}
+	\item $(\sx,e)$ is admissible.
+\end{enumerate}
+\end{thm}
+\begin{proof}
+
+\end{proof}
+
+\ssec{Base Cases}
+\label{ssec:g_0_base}
 Cases to induct on are here.
 
+\ssec{Exceptional Cases}
+\label{ssec:g_0_exceptional}
 These are exceptional cases.
+
+\ssec{Conclusion}
+\label{ssec:g_0_conclusion}
 

### 2015-06-19 stacky_write_up/spin_cring.tex
merged at beginning
fixed g 0 reference

@@
 \nc\renc{\renewcommand}
-\newcommand\ssec{\subsection*}
-\newcommand\sssec{\subsubsection*}
+\newcommand\ssec{\subsection}
+\newcommand\sssec{\subsubsection}
 \newcommand\bO{{\mathbf O}}
@@
 The proof is a rather involved induction.
-In Subsections ~\ref{ssec:ram_pts}, ~\ref{ssec:ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction.
+In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction.
 Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.

### 2015-06-19 stacky_write_up/spin_cring.tex
minor edits
remove extraneous header
add spaces

--- 2015-06-19 stacky_write_up/spin_cring.tex
@@
 
+%%%%%%%%%%%%%%%%%%% spin cring custom commands %%%%%%%%%%%%%%%%%%%%%%
+
 \newcommand \subhalf[1]{\frac{e_{#1} - 1}{2e_{#1}}}
@@
 
-In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r ;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 This is proven in Subsection ~\ref{ssec:g_0_conclusion}.

### 2015-06-19 stacky_write_up/spin_cring.tex

--- 2015-06-19 stacky_write_up/spin_cring.tex
@@
 
-In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 This is proven in Subsection ~\ref{ssec:g_0_conclusion}.

### 2015-06-19 stacky_write_up/spin_cring.tex
adding macro

--- 2015-06-19 stacky_write_up/spin_cring.tex
@@
 \DeclareMathOperator{\ord}{ord}
+\newcommand \halfcan{L}
 
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 \todo{Rewrite this to be more precise}
@@
 
-In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+In this section, we will prove that if $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 This is proven in Subsection ~\ref{ssec:g_0_conclusion}.
@@
 \label{sat_three_induction}
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf i$.
-There are generators $y_3,y_4,y_5$ of $R_{D+D'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $\halfcan = \subhalf i$.
+There are generators $y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
 \todo{Include the order}

### 2015-06-19 stacky_write_up/spin_cring.tex

@@
 
-In this section, we will prove that if $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+In this section, we will prove that if $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 This is proven in Subsection ~\ref{ssec:g_0_conclusion}.

### 2015-06-19 stacky_write_up/spin_cring.tex
clean code, break lines, and add VZB to bib

@@
 This is our project.
-Example, O'Dorney's paper \cite{dorney:canonical}.
+Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
+and O'Dorney's paper \cite{dorney:canonical}.
 We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{i}$.
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
-\todo{Rewrite this to be more precise}
+Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature
+$\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is
+generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with
+relations in degree at most $2e$, so long as $\sigma$ does not lie
+in a finite list of exceptions. \todo{Rewrite this to be more
+precise}
 \end{thm}
@@
 
-In this section, we will prove that if $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
-This is proven in Subsection ~\ref{ssec:g_0_conclusion}.
-The proof is a rather involved induction.
-In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction.
-Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.
+In this section, we will prove that if $(\sx,\halfcan)$ is a spin
+curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)
+$, then $R(\sx,\halfcan)$ is generated in degree at most $e =
+\max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so
+long as $\sigma$ does not lie in a finite list of exceptions. This
+is proven in Subsection ~\ref{ssec:g_0_conclusion}. The proof is a
+rather involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
+~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
+Subsection ~\ref{ssec:g_0_base} we check the base cases of the
+induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
+list out the exceptional cases.
 
@@
 \label{sat_three_induction}
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $\halfcan = \subhalf i$.
-There are generators $y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
-\todo{Include the order}
-Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively.
-\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
+rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(
+\halfcan')) = 3.$ Let $\halfcan = \subhalf i$. There are generators
+$y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$
+ lies in degree $i$ and has a pole of order $1$. \todo{Include the
+order}
+
+Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 
+respectively. \todo{Make sure to state some requirement on the 
+ordering of the $x_i$, analogously to 8.4.1, but I don't see why 
+this is important.} Then, letting $x_j$ range over all $x$ variables
 \begin{align*}
@@
 \end{align*}
+\end{lem}
 
-\end{lem}
 \begin{proof}
@@
 	\langle y_i^ay_{i+2}^b \mid a \geq 0,b\geq 0, 3 \leq i \leq e-2\rangle +\\
-	\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b \geq 0(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle +\\
+	\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0,
+					b \geq 0(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle +\\
 	\langle y_3^az_4,y_3^bz_5 \mid a \geq 0, b \geq 0 \rangle\\
 \end{align*}
-Note that this is precisely the monomials which are not divisible by those in the claimed initial ideal.
-By the trick of projecting to the pole order by degree 2-dim lattice, we see this is a $k$ basis.
-We also see that $z_i,y_j$ are generators.
-\todo{Note that $z_5$ is chosen specially, and is not generic}
 
-It only remains to show the initial ideal is as claimed. Note that once we show this, we will automatically obtain minimality, using the regrading to degree 1 trick.
+\noindent
+Note that this is precisely the monomials which are not divisible
+by those in the claimed initial ideal. By the trick of projecting
+to the pole order by degree 2-dim lattice, we see this is a $k$
+basis. We also see that $z_i,y_j$ are generators. \todo{Note that
+$z_5$ is chosen specially, and is not generic}
 
-To show this is the initial ideal, it suffices to exhibit such relations with the claimed leading terms in the initial ideal.
-Indeed, we will now give only leading order terms.
-We have relations starting with
+It only remains to show the initial ideal is as claimed. Note that
+once we show this, we will automatically obtain minimality, using
+the regrading to degree 1 trick.
+
+To show this is the initial ideal, it suffices to exhibit such
+relations with the claimed leading terms in the initial ideal.
+Indeed, we will now give only leading order terms. We have
+relations starting with
 \begin{align*}
@@
 \end{proof}
-\todo{Something is a little fishy with this order, it seems something like: first grade by degree, then try to decrease the highest y, if you cant, try to decrease the highest z, possibly replace $z_5$ by $z_5+Cy_5$ to generic element?}
+
+\todo{Something is a little fishy with this order, it seems 
+something like: first grade by degree, then try to decrease the 
+highest y, if you cant, try to decrease the highest z, possibly 
+replace $z_5$ by $z_5+Cy_5$ to generic element?}
 
@@
 \label{ssec:g_0_ram_orders}
-In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}. Under fairly general conditions, this theorem will show that if
+In this section, we aim to prove the inductive theorem, Theorem
+~\ref{thm:ramification_order_induction}. Under fairly general
+conditions, this theorem will show that if
 
@@
 \label{defn:admissible}
-A pair $(\sx',e_i')$, with point $P$ corresponding to $e-2$ is admissible if
+A pair $(\sx',e_i')$, with point $P$ corresponding to $e-2$ is
+admissible if
 \begin{enumerate}
-	\item There is an element $y_{e-2} \in R'$ so that $R'$ admits a presentation $(k[x] \otimes k[y_{e-2}])/I'$ with $\deg y_{e-2} = e-2$ and $-ord_P(y_{e-2}) = \frac{e-3}{2}$.
+	\item There is an element $y_{e-2} \in R'$ so that $R'$ admits a
+				presentation $(k[x] \otimes k[y_{e-2}])/I'$ with $\deg y_{e-2} = e-2$
+				and $-ord_P(y_{e-2}) = \frac{e-3}{2}$.
 \item For all $z \neq y_{e-2}$ generators of $R'$ we have
@@
 \label{lem:admissible_inequality}
-Condition 2 of Definition ~\ref{defn:admissible} implies the stronger condition that
+Condition 2 of Definition ~\ref{defn:admissible} implies the
+stronger condition that
 \begin{align*}
@@
 \label{thm:ramification_order_induction}
-Suppose $(\sx',J)$ is admissible with a generator $y_{e-2} \in R'$ as in condition 1 of Definition ~\ref{defn:admissible}. Then the following are true:
+Suppose $(\sx',J)$ is admissible with a generator $y_{e-2} \in R'$
+as in condition 1 of Definition ~\ref{defn:admissible}. Then the
+following are true:
+
 \begin{enumerate}
@@
 \end{align*}
-\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
-\item Equip $k[y]$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
+
+\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$
+			over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
+\item Equip $k[y]$ and $k[x]$ with any graded monomial order and
+			$k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$
+			Then,
 			\begin{align*}
-	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_{e-2} \rangle 
+					in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_
+					{e-2} \rangle 
 			\end{align*}
 			as $z$ ranges over generators of $R$.
-	\item Suppose $in_\prec(I')$ is minimally generated by quadratics and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$.
-\todo{prove this still}
+\item Suppose $in_\prec(I')$ is minimally generated by quadratics 
+				and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set 
+				of minimal generators for $I'$ together with any set of relations 
+				as in the previous part \todo{reference previous part as part c} 
+				minimally generate $I$. \todo{prove this still}
 \item $(\sx,e)$ is admissible.
@@
 \end{thm}
+
 \begin{proof}

### 2015-06-19 stacky_write_up/spin_cring.tex
fix overtabbing
adding macro

--- 2015-06-19 stacky_write_up/spin_cring.tex
@@
 \label{sec:g_0_effective}
-Let us consider $\delta \geq 2$.
+Suppose $\delta=\deg(\halfcan)>0$.  Then we can explicitly write out $D=K_\sx+\Delta=K_X+\sum \subhalf{i}$   Let us consider $\delta \geq 2$.
 
@@
 Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively.
-\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
+\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, l oetting $x_j$ range over all $x$ variables
 \begin{align*}

### 2015-06-19 stacky_write_up/spin_cring.tex
paste saturation list, add temporary table of cts

--- 2015-06-19 stacky_write_up/spin_cring.tex
@@
 
+\tableofcontents
+
 \section{Introduction}
@@
 \label{ssec:g_0_saturation}
+
+Here we compute saturation numbers. That is, given a list of
+ramification orders, with $g = 0,\delta = 0$ understood, we have
+the following saturations of the canonical divisor, as defined in
+7.2 of Voight and Zureick-Brown \cite{vzb:stacky}
+\begin{enumerate}
+	\item $(3,3,3)$ exceptional, we know it it is $k[x]$ in degree 3.
+	\item $(3,3,5) \mapsto 18.$ (gen in 3, 10, 15; min relations in 30)
+	\item $(3,3,7) \mapsto 12.$ (gen in 3, 7, 12; min relation in 24) 
+	\item $(3,3,9) \mapsto 12.$ (gen in 3, 7, 9; min relation in 21)
+	\item $(3,3,k) \mapsto 9$ for $k > 9$. (gen in 3, 7, ..., $k$; 
+min relation in 14 up to $2(k-1)$)
+	\item $(3,5,5) \mapsto 8.$ (gen in degree 3, 5, 10; min relation 
+in 20)
+	\item $(5,5,5)\mapsto 8$ (gen in degree 3, 5, 5; min relation in 
+15)
+	\item $(a,b,c)\mapsto 5$ if $a,b,c$ is not listed above. (
+generation in 3,5,7.) ($(a,b,c) = (3,5,7)$ generated in degree 3,5,7
+, some relation in degree 30, might be more).
+	\item $(3,3,3,3) \mapsto 6$ (monoid generation in degree 3,4) (
+the actual ring is also generated in degree 4 with 1 relation in 
+degree 12).
+	\item If $(e_1,\ldots, e_r)$ is not listed above it has 
+saturation $3$. (generation in 3,4,5.)
+\end{enumerate}
+\todo{make table and put proof}
 
@@
 \item Equip $k[y]$ and $k[x]$ with any graded monomial order and
-			$k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$
+		$k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I$.
 		Then,

### 2015-06-19 stacky_write_up/spin_cring.tex
added third admissible condition

--- 2015-06-19 stacky_write_up/spin_cring.tex
@@
 \DeclareMathOperator{\ord}{ord}
-\newcommand \halfcan{L}
-
-%%%%%%%%%%%%%%%%%%% spin cring custom commands %%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+Let $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 \todo{Rewrite this to be more precise}
@@
 \label{sec:g_0_effective}
-Suppose $\delta=\deg(\halfcan)>0$.  Then we can explicitly write out $D=K_\sx+\Delta=K_X+\sum \subhalf{i}$   Let us consider $\delta \geq 2$.
+Let us consider $\delta \geq 2$.
 
@@
 
-In this section, we will prove that if $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;0)$, then $R(\sx,\halfcan)$ is generated in degree at most $e = \max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
 This is proven in Subsection ~\ref{ssec:g_0_conclusion}.
@@
 \label{sat_three_induction}
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $\halfcan = \subhalf i$.
-There are generators $y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  log stacky curves $R \subset R'$ be the corresponding inclusion of canonical rings.
+Let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf i$.
+There are generators $y_3,y_4,y_5$ of $R_{D+D'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
 \todo{Include the order}
 Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively.
-\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, l oetting $x_j$ range over all $x$ variables
+\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
 \begin{align*}
@@
 \label{ssec:g_0_ram_orders}
-In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}. Under fairly general conditions, this theorem will show that if
+In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}.
+Under fairly general conditions, this theorem will allow us to show that if Theorem ~\ref{thm:ramification_order_induction} holds for a curve with signature $(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
 
@@
 \label{defn:admissible}
-A pair $(\sx',e_i')$, with point $P$ corresponding to $e-2$ is admissible if
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves, ramified over $Q_1,\ldots, Q_r$ and let $J \subset \{1,
+\ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
+$$
+\chi_J(i) = \begin{cases}
+	1, &\text{ if }i \in J\\
+	0, &\text{ otherwise. } 
+\end{cases}$$
+Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$, {\bf admissible} if the following three conditions hold.
 \begin{enumerate}
-	\item There is an element $y_{e-2} \in R'$ so that $R'$ admits a presentation $(k[x] \otimes k[y_{e-2}])/I'$ with $\deg y_{e-2} = e-2$ and $-ord_P(y_{e-2}) = \frac{e-3}{2}$.
-\item For all $z \neq y_{e-2}$ generators of $R'$ we have
+	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} \in R'$ so that $R'$ admits a presentation
 \begin{align*}
-	\frac{- ord_P(z)}{\deg z} < \frac{e-3}{2(e-2)}
+	R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
 \end{align*}
-\item We have
+so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
+\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a generator of $R'$ we have
 \begin{align*}
-	\deg \lfloor e K_{\sx'} \rfloor \geq 0
+	\frac{- ord_{Q_i}(z)}{\deg z} < \frac{e_i'-1}{2(e_i')}.
+\end{align*}
+\item[(Ad-iii)] For all $i \in J$ we have
+\begin{align*}
+	\deg \lfloor e K_{\sx'} \rfloor \geq \eta(i)
+\end{align*}
+where
+\begin{align*}
+	\eta(i) = \#\{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
 \end{align*}

### 2015-06-20 stacky_write_up/spin_cring.tex
writing up proof of longer induction

@@
 \label{defn:admissible}
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves, ramified over $Q_1,\ldots, Q_r$ and let $J \subset \{1,
+Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin curves, both ramified over ramified at $Q_1,\ldots, Q_r$.
+Suppose there is a birational map $\sx \rightarrow \sx'$, and let $J \subset \{1,
 \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
@@
 \begin{align*}
-	\deg \lfloor e K_{\sx'} \rfloor \geq \eta(i)
+	\deg \lfloor e_i L \rfloor \geq \# S(i)
 \end{align*}
@@
 \begin{align*}
-	\eta(i) = \#\{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+	\eta(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
 \end{align*}
@@
 \label{lem:admissible_inequality}
-Condition 2 of Definition ~\ref{defn:admissible} implies the stronger condition that
+Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the stronger condition that
 \begin{align*}
-	-ord(z) \leq \deg(z) \frac{e-3}{2(e-2)}-\frac{1}{e-2}
+	-\ord_{Q_i}(z) \leq \deg(z) \frac{e_i'-1}{2e_i'}-\frac{1}{e_i'}
 \end{align*}
 \end{lem}
+\begin{proof}
+We know by (Ad-ii) that
+\begin{align*}
+	-\ord_{Q_i}(z) < \deg(z) \frac{e_i'-1}{2e_i'}
+\end{align*}
+If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $e_i'-1$ is even.
+Therefore, since $-\ord_{Q_i}(z)$ is an integer, we must have
+\begin{align*}
+	-\ord_{Q_i}(z) \leq \deg(z) \frac{e_i'-1}{2e_i'} - \frac{1}{\beta} \leq \deg(z) \frac{e_i'-1}{2e_i'} - \frac{1}{e_i'}.
+\end{align*}
+\end{proof}
 
@@
 \label{thm:ramification_order_induction}
-Suppose $(\sx',J)$ is admissible with a generator $y_{e-2} \in R'$ as in condition 1 of Definition ~\ref{defn:admissible}. Then the following are true:
+Suppose $(\sx',L')$ is a tame separably rooted log stacky spin curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
+Then the following are true:
 \begin{enumerate}
-	\item There exists $y_e \in H^0(\sx, e(K_\sx))$ so that 
+	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in H^0(\sx, e_i(K_\sx))$ so that
 	\begin{align*}
-	-ord_P(y_e) = \frac{e-1}{2}
+	-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
 \end{align*}
-\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
-\item Equip $k[y]$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
+and
 \begin{align*}
-	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_{e-2} \rangle 
+	\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \frac{e_j'-1}{2e_j'}-\frac{1}{\deg(y_{i,e_i'})e_j'}
 \end{align*}
-	as $z$ ranges over generators of $R$.
-	\item Suppose $in_\prec(I')$ is minimally generated by quadratics and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$.
-\todo{prove this still}
-	\item $(\sx,e)$ is admissible.
+for all $j \in J$ with $j \neq i$.
+\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally generate $R$ over $R'$.
+\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
+\begin{align*}
+	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq y_{i,e_i},y_{i,e_i'} \rangle 
+\end{align*}
+	as $z$ ranges over all generators of $R$.
+	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by quadratics and that for all $i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$.
+	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
 \end{enumerate}
@@
 \begin{proof}
+Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in question. Define
+\begin{align*}
+	S(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+\end{align*}
 

### 2015-06-20 stacky_write_up/spin_cring.tex
proving b

@@
 
-\newcommand \subhalf[1]{\frac{e_{#1} - 1}{2e_{#1}}}
+\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
 \newcommand{\se}[1]{\section*{Problem #1}}
@@
 Example, O'Dorney's paper \cite{dorney:canonical}.
-We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{i}$.
+We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.
 
@@
 Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  log stacky curves $R \subset R'$ be the corresponding inclusion of canonical rings.
-Let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf i$.
+Let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf {e_i}$.
 There are generators $y_3,y_4,y_5$ of $R_{D+D'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
@@
 \begin{align*}
-	\frac{- ord_{Q_i}(z)}{\deg z} < \frac{e_i'-1}{2(e_i')}.
+	\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \frac{e_i'-1}{2e_i'}-\frac{1}{e_i'}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_i}(z) < \deg(z) \frac{e_i'-1}{2e_i'}
+	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \frac{e_i'-1}{2e_i'} - \frac{1}{\beta} \leq \deg(z) \frac{e_i'-1}{2e_i'} - \frac{1}{e_i'}.
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq \deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
 \end{align*}
@@
 \begin{align*}
-	\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \frac{e_j'-1}{2e_j'}-\frac{1}{\deg(y_{i,e_i'})e_j'}
+	\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-\frac{1}{\deg(y_{i,e_i'})e_j'}
 \end{align*}
@@
 \begin{proof}
-Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in question. Define
+Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in question, with coarse spaces $X = X'$. Define
 \begin{align*}
 	S(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+\end{align*}
+Define
+\begin{align*}
+	E_i = \sum_{j \in S(i)}^{}Q_j
+\end{align*}
+Note that
+\begin{align*}
+	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
+\end{align*}
+and so we obtain an inclusion
+\begin{align*}
+	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset H^0(\sx,e_iL).
+\end{align*}
+The assumption (Ad-iii) implies
+\begin{align*}
+	\deg \left( e_i L' - E_i \right) \geq 0
+\end{align*}
+implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by Riemann Roch, and so a general element
+\begin{align*}
+	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
+\end{align*}
+satisfies
+\begin{align*}
+	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 = \frac{e_i - 1}{2}
+\end{align*}
+Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
+
+We next show $y_{i,e_i}$ also satisfies the second part of the claim of $(a),$ by considering seperately the cases of whether $j \in S(i),$ and $j \notin S(i)$.
+
+If $j \in S(i)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)$,
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i \subhalf{e_j'} - \frac{1}{e_j'}.
+\end{align*}
+
+If instead $j \notin S(i)$, then since $e_j' \nmid e_i$, we know $e_i\subhalf{e_j'} \notin \BZ$, so
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor \leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
+\end{align*}
+completing the proof of (a).
+
+Next, define $R_0 = R'$ and inductively define 
+$$
+R_i = \begin{cases}
+	R_{i-1} &\text{ if }i \notin J\\
+	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
+\end{cases}$$
+To prove (b), it suffices to show that elements of the form $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly indpendent, and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-vector space.
+These elements do not lie in $R_{i-1}$ because their order of pole at $Q_i$ is bigger than the order of any element in $R_{i-1}$, and are linearly independent amongst themselves because of injectivity of the linear map
+\begin{align*}
+	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) \begin{pmatrix}
+	e_i' & \subhalf{e_i'} \\
+	e_i	 & \subhalf{e_i}
+\end{pmatrix} 
 \end{align*}

### 2015-06-20 stacky_write_up/spin_cring.tex
finished part b

@@
 	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) \begin{pmatrix}
-	e_i' & \subhalf{e_i'} \\
-	e_i	 & \subhalf{e_i}
+	e_i-2 & \frac{e_i-3}{2} \\
+	e_i	 & \frac{e_i-1}{2}
 \end{pmatrix} 
+\end{align*}
+The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the integer lattice points in the cone generated by the vectors $\left(e_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2} \right)$ is saturated, as the corresponding determinant is
+\begin{align*}
+	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
+\end{align*}
+completing part (b).
+
+To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for all $j \in J$ we have
+\begin{align*}
+	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
 \end{align*}

### 2015-06-20 stacky_write_up/spin_cring.tex
finished proof of complicated induction

@@
 \begin{lem}
+\label{lem:minimal_quadratic}
+
+\end{lem}
+\begin{proof}
+
+\end{proof}
+
+\begin{lem}
 \label{sat_three_induction}
@@
 \end{align*}
-\item[(Ad-iii)] For all $i \in J$ we have
+\item[(Ad-iii)] For all $i \in J$ we have for all $d \geq 0$,
 \begin{align*}
-	\deg \lfloor e_i L \rfloor \geq \# S(i)
+	\deg \lfloor e_i L \rfloor \geq \# S(i,d)
 \end{align*}
@@
 \begin{align*}
-	\eta(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+	S(i,d) = \{j \in J : j \neq i \text{ and }e_j'+2d \mid e_i+2d\}
 \end{align*}
@@
 	as $z$ ranges over all generators of $R$.
-	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by quadratics and that for all $i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in the previous part \todo{reference previous part as part c} minimally generate $I$.
+	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by products of two monomials and that for all $i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in part (c) minimally generate $I$.
 	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
@@
 \begin{align*}
-	S(i) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
 \end{align*}
@@
 \begin{align*}
-	E_i = \sum_{j \in S(i)}^{}Q_j
+	E_i = \sum_{j \in S(i,0)}^{}Q_j
 \end{align*}
@@
 
-We next show $y_{i,e_i}$ also satisfies the second part of the claim of $(a),$ by considering seperately the cases of whether $j \in S(i),$ and $j \notin S(i)$.
+We next show $y_{i,e_i}$ also satisfies the second part of the claim of $(a),$ by considering seperately the cases of whether $j \in S(i,0),$ and $j \notin S(i,0)$.
 
-If $j \in S(i)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)$,
+If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)$,
 \begin{align*}
@@
 
-If instead $j \notin S(i)$, then since $e_j' \nmid e_i$, we know $e_i\subhalf{e_j'} \notin \BZ$, so
+If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know $e_i\subhalf{e_j'} \notin \BZ$, so
 \begin{align*}
@@
 \end{align*}
+We now check this in three cases, depending on whether $j \notin \{i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
 
+\vskip.1in
+\noindent
+{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
+
+Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'}+ \deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
+\end{align*}
+
+\vskip.1in
+\noindent
+{\sf Case 2: $j =i.$}
+
+By part (a), condition (Ad-ii), and Lemma ~\ref{lem:admissible_inequality} we have
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq \frac{e_i-1}{2} + \deg z \left( \subhalf{e_i'} \right) -\frac{1}{e_i'}
+	& = \frac{e_i-1}{2}-\frac{1}{e_i'}+\left( \subhalf{e_i'} \right)\\
+	&= \frac{e_i(e_i-3)}{2(e_i-2)}+\left( \subhalf{e_i'} \right)\\
+	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
+\end{align*}
+
+\vskip.1in
+\noindent
+{\sf Case 3: $j \in S(i,0).$}
+In this case, we similarly obtain
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq  e_i \subhalf{e_j'} +\deg z \subhalf{e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'},
+\end{align*}
+completing part (c).
+
+Next, note that the minimal generators of $I'$ together with the new generators of $I$ given in (c) have independent initial terms by construction, and therefore are minimal by Lemma ~\ref{lem:minimal_quadratic}.
+
+Finally, to check (e), we will first show that $(\sx,J)$ is admissible.
+We know (Ad-i) is satisfied by part (b), taking the $y_{i,e_i}$ as the generators in degree $e_i$.
+Next, (Ad-ii) is strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
+Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by definition.
+This is where we use that (Ad-iii) holds for $d > 0$ and not just for $d = 0$.
+
+Finally, if $(\sx,J)$ then so is $(\sx,W)$ for any $W \subset J$, since each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$ if they hold for $J$.
 \end{proof}

### 2015-06-20 stacky_write_up/spin_cring.tex
wrote second inductive lemma

@@
 
-\begin{lem}
-\label{sat_three_induction}
+\begin{prop}
+\label{prop:sat_three_induction}
 Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  log stacky curves $R \subset R'$ be the corresponding inclusion of canonical rings.
-Let $R_{D'} = R' = k[x]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \subhalf {e_i}$.
-There are generators $y_3,y_4,y_5$ of $R_{D+D'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$.
-\todo{Include the order}
-Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively.
-\todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
+Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{3}P$.
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
 	\begin{align*}
-	in_\prec(I) = in_\prec(I')k[x,y_3,\ldots, y_e,z_4,z_5] + \\
-	\langle y_i y_j \mid 1 \leq i < j-3 \leq e \rangle +\\
-	\langle y_i x_j \mid i > 3 \rangle +\\
-	\langle z_i y_j \mid j > 3 \rangle  +\\
-	\langle z_i x_j \mid 4 \leq i \leq 5\rangle + \\
-	\langle z_iz_k \mid 4 \leq i \leq j \leq 5 \rangle 
+	J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+	&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+	&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
 \end{align*}
+Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with leading terms as in (b) minimally generate $I$.
+\end{enumerate}
+\end{prop}
+\begin{proof}
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord_P(y_i) = 1$ by Riemann Roch.
+\todo{Understand why/whether we need to cite lemma 5.4.7.} To complete the proof of (a) we only need show these elements generate $R$ over $R'$.
+We can first see that the following is a $k$ basis for $R$ over $R'$:
+\begin{align}
+\label{eqn:add_one_generator}
+\begin{split}
+	&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b \geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+	&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+\end{split}
+\end{align}
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch.
+So, it suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor,$ elements of degree $d$ in the claimed basis of ~\ref{eqn:add_one_generator}.
+Indeed, letting $a = \lfloor \frac{d}{3} \rfloor $ and $b = d \bmod 3$, we have that the elements
+\begin{align*}
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{3+b}
+\end{align*}
+are precisely $a$ elements, which are all independent as they have distinct pole orders at $P$. This completes part (a).
 
-\end{lem}
-\begin{proof}
-We can see the following is a $k$ basis for $R$ over $R'$:
+To show part (b), note that the generators in ~\ref{eqn:add_one_generator} are precisely a set of monomials which generate $k[x,y]/J$ over $k$.
+So, to show $J = in_\prec(I)$, it suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+This follows, since there exist constants $A_{i,j} \in k$ for $4 \leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and elements $w_{i,j} \in R'$ so that the following linear combinations of elements lie in $R'$.
+
 \begin{align*}
-	\langle y_i^ay_{i+2}^b \mid a \geq 0,b\geq 0, 3 \leq i \leq e-2\rangle +\\
-	\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b \geq 0(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle +\\
-	\langle y_3^az_4,y_3^bz_5 \mid a \geq 0, b \geq 0 \rangle\\
+y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+y_4^2 &+ B_1 y_3 y_5 \\
+y_4y_5 &+ B_2 y_3^2 x_3 \\
+y_5^2 &+ B_3 y_3^2 x_4
 \end{align*}
-Note that this is precisely the monomials which are not divisible by those in the claimed initial ideal.
-By the trick of projecting to the pole order by degree 2-dim lattice, we see this is a $k$ basis.
-We also see that $z_i,y_j$ are generators.
-\todo{Note that $z_5$ is chosen specially, and is not generic}
+Of course, the initial terms of these elements are precisely the generators of $J$, completing (b).
 
-It only remains to show the initial ideal is as claimed. Note that once we show this, we will automatically obtain minimality, using the regrading to degree 1 trick.
-
-To show this is the initial ideal, it suffices to exhibit such relations with the claimed leading terms in the initial ideal.
-Indeed, we will now give only leading order terms.
-We have relations starting with
-\begin{align*}
-	y_iy_j - y_{i-1}y_{j+1} + \cdots &\mid i < j-1 \\
-	y_ix_4 - y_{i-2}y_3x_3 + \cdots & \mid i > 3\\
-	y_ix_5 - y_{i-2}y_3x_4 + \cdots & \mid i > 3\\
-	y_ix_3-y_3^3y_{i-6} + \cdots &\mid i > 7\\
-	y_7x_3-y_3^2 z_4 + \cdots \\
-	y_5x_3 - y_3z_5 + \cdots \\
-	z_4^2 - y_3 z_5 + \cdots \\
-	z_4z_5 - y_3^2x_3 + \cdots \\
- 	z_5^2 - y_3^2 x_4 + \cdots \\
- 	z_4 y_i - y_3^2 y_{i-2} + \cdots &\mid i > 3 \\
- 	z_5 y_i - y_3y_{i-2}z_4 + \cdots &\mid i > 3 \\
- 	z_i x_j - y_3 z_{i+j-3} + \cdots &\mid i+j \leq 8 \\
- 	z_i x_j - y_3x_3x_{i+j-6} + \cdots &\mid i+j > 8
-\end{align*}
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
 \end{proof}

### 2015-06-20 stacky_write_up/spin_cring.tex
finished genus 0 induction

@@
 \section{Introduction}
+\todo{Edit this stuff}
 This is our project.
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
-\todo{Rewrite this to be more precise}
+Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the canonical ring 
+\begin{align*}
+	R(\sx,L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
+\end{align*}
+is generated as a $k$-algebra by elements of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
+\todo{Include reference to the table with this list of exceptions.}
 \end{thm}
@@
 \section{Background}
+\todo{edit this}
 Here are some definitions.
@@
 \label{lem:minimal_quadratic}
-
+Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily generated in degree 1, is equipped with a monomial ordering $\prec.$ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded rings with kernel $I,$ such that $I$ is generated by elements $f_1,\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$ is of the form $x_k$.
+Then, the elements $f_i$ determine minimal generators for $I$.
 \end{lem}
 \begin{proof}
-
+Regrade the ring $k[x_1,\ldots, x_n]$ so that all $x_i$ lie in degree 1.
+Then, $\phi:k[x_1,\ldots, x_n]\rightarrow B$ determines a map of rings, no longer necessarily graded.
+Consider the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$.
+By assumption, the kernel $I$ is generated by elements whose initial terms have degree 2 and are all distinct.
+Therefore, $\dim_k (k[x_1,\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of generators for $I$ must have at least $j$ elements.
+Since $f_1,\ldots, f_j$ is such a set, it is minimal.
 \end{proof}

### 2015-06-20 stacky_write_up/spin_cring.tex
major code cleaning
* added linebreaks between theorems/props/lemmata and proofs
* broke long lines
* addressed bad boxes and warnings
* added table of contents (temporary)
* added years to bib entries

@@
 
+%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%%%%%%%%%%%%%%%
+
 \newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
@@
 
+\tableofcontents
+
 \maketitle
@@
 This is our project.
-Example, O'Dorney's paper \cite{dorney:canonical}.
+Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
+and O'Dorney's paper \cite{dorney:canonical}.
 We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the canonical ring 
+Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so
+that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the
+canonical ring
+
 \begin{align*}
@@
 \end{align*}
-is generated as a $k$-algebra by elements of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
-\todo{Include reference to the table with this list of exceptions.}
+
+\noindent
+is generated as a $k$-algebra by elements of degree at most $e = 
+\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so 
+long as $\sigma$ does not lie in a finite list of exceptions. \todo{
+Include reference to the table with this list of exceptions.}
 \end{thm}
@@
 
-In this section, we will prove that if $(\sx,L)$ is a spin curve, so that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,L)$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does not lie in a finite list of exceptions.
-This is proven in Subsection ~\ref{ssec:g_0_conclusion}.
-The proof is a rather involved induction.
-In Subsections ~\ref{ssec:g_0_ram_pts}, ~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in Subsection ~\ref{ssec:g_0_base} we check the base cases of the induction.
-Finally, in Subsection ~\ref{ssec:g_0_exceptional} we list out the exceptional cases.
+In this section, we will prove that if $(\sx , L)$ is a spin curve,
+so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
+$R(\sx , L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
+e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does
+not lie in a finite list of exceptions. This is proven in
+Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
+involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
+~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
+Subsection ~\ref{ssec:g_0_base} we check the base cases of the
+induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
+list out the exceptional cases.
 
@@
 \label{lem:minimal_quadratic}
-Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily generated in degree 1, is equipped with a monomial ordering $\prec.$ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded rings with kernel $I,$ such that $I$ is generated by elements $f_1,\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$ is of the form $x_k$.
-Then, the elements $f_i$ determine minimal generators for $I$.
+Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
+generated in degree 1, is equipped with a monomial ordering $\prec$.
+ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
+rings with kernel $I,$ such that $I$ is generated by elements $f_1,
+\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
+is of the form $x_k$. Then, the elements $f_i$ determine minimal
+generators for $I$.
 \end{lem}
+
 \begin{proof}
-Regrade the ring $k[x_1,\ldots, x_n]$ so that all $x_i$ lie in degree 1.
-Then, $\phi:k[x_1,\ldots, x_n]\rightarrow B$ determines a map of rings, no longer necessarily graded.
-Consider the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$.
-By assumption, the kernel $I$ is generated by elements whose initial terms have degree 2 and are all distinct.
-Therefore, $\dim_k (k[x_1,\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of generators for $I$ must have at least $j$ elements.
-Since $f_1,\ldots, f_j$ is such a set, it is minimal.
+Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
+degree 1. Then,
+\[
+	\phi : k[x_1, \ldots, x_n] \rightarrow B
+\]
+
+\noindent
+determines a map of rings, no longer necessarily graded. Consider
+the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$. By
+assumption, the kernel $I$ is generated by elements whose initial
+terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
+\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
+generators for $I$ must have at least $j$ elements. Since $f_1,
+\ldots, f_j$ is such a set, it is minimal.
 \end{proof}
@@
 \label{prop:sat_three_induction}
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  log stacky curves $R \subset R'$ be the corresponding inclusion of canonical rings.
-Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{3}P$.
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
+rooted  log stacky curves $R \subset R'$ be the corresponding
+inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4
+,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
+3}P$.
+
 \begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec 
+		y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
+		order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
 		\begin{align*}
@@
 			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with leading terms as in (b) minimally generate $I$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
 \end{enumerate}
 \end{prop}
+
 \begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord_P(y_i) = 1$ by Riemann Roch.
-\todo{Understand why/whether we need to cite lemma 5.4.7.} To complete the proof of (a) we only need show these elements generate $R$ over $R'$.
-We can first see that the following is a $k$ basis for $R$ over $R'$:
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.} To complete the proof of (a) we only need 
+show these elements generate $R$ over $R'$. We can first see that 
+the following is a $k$ basis for $R$ over $R'$:
+
 \begin{align}
@@
 	\begin{split}
-	&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b \geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
 		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
@@
 \end{align}
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch.
-So, it suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor,$ elements of degree $d$ in the claimed basis of ~\ref{eqn:add_one_generator}.
-Indeed, letting $a = \lfloor \frac{d}{3} \rfloor $ and $b = d \bmod 3$, we have that the elements
-\begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{3+b}
-\end{align*}
-are precisely $a$ elements, which are all independent as they have distinct pole orders at $P$. This completes part (a).
 
-To show part (b), note that the generators in ~\ref{eqn:add_one_generator} are precisely a set of monomials which generate $k[x,y]/J$ over $k$.
-So, to show $J = in_\prec(I)$, it suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-This follows, since there exist constants $A_{i,j} \in k$ for $4 \leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and elements $w_{i,j} \in R'$ so that the following linear combinations of elements lie in $R'$.
+\noindent
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+,$ elements of degree $d$ in the claimed basis of
+~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+\rfloor $ and $b = d \bmod 3$, we have that the elements
 
 \begin{align*}
-y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+3+b}
+\end{align*}
+
+\noindent
+are precisely $a$ elements, which are all independent as they have
+distinct pole orders at $P$. This completes part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:add_one_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_{i,j} \in k$ for $4
+\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
 	y_4^2 &+ B_1 y_3 y_5 \\
@@
 \end{align*}
-Of course, the initial terms of these elements are precisely the generators of $J$, completing (b).
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
 
@@
 \end{proof}
-\todo{Something is a little fishy with this order, it seems something like: first grade by degree, then try to decrease the highest y, if you cant, try to decrease the highest z, possibly replace $z_5$ by $z_5+Cy_5$ to generic element?}
+
+\todo{Something is a little fishy with this order, it seems
+something like: first grade by degree, then try to decrease the
+highest y, if you cant, try to decrease the highest z, possibly
+replace $z_5$ by $z_5+Cy_5$ to generic element?}
 
@@
 \label{ssec:g_0_ram_orders}
-In this section, we aim to prove the inductive theorem, Theorem ~\ref{thm:ramification_order_induction}.
-Under fairly general conditions, this theorem will allow us to show that if Theorem ~\ref{thm:ramification_order_induction} holds for a curve with signature $(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
+In this section, we aim to prove the inductive theorem, Theorem
+~\ref{thm:ramification_order_induction}. Under fairly general
+conditions, this theorem will allow us to show that if Theorem ~\ref
+{thm:ramification_order_induction} holds for a curve with signature
+$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
+signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
 
@@
 \label{defn:admissible}
-Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin curves, both ramified over ramified at $Q_1,\ldots, Q_r$.
-Suppose there is a birational map $\sx \rightarrow \sx'$, and let $J \subset \{1,
-\ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
-$$
-\chi_J(i) = \begin{cases}
+Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin
+curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
+there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
+\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
+
+$$\chi_J(i) = \begin{cases}
 	1, &\text{ if }i \in J\\
@@
 \end{cases}$$
-Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$, {\bf admissible} if the following three conditions hold.
+
+Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
+{\bf admissible} if the following three conditions hold.
+
 \begin{enumerate}
-	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} \in R'$ so that $R'$ admits a presentation
+	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
+		\in R'$ so that $R'$ admits a presentation
 		\begin{align*}
@@
 		\end{align*}
-so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
-\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a generator of $R'$ we have
+		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
+		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
+	\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a 
+		generator of $R'$ we have
 		\begin{align*}
@@
 \label{lem:admissible_inequality}
-Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the stronger condition that
+Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
+stronger condition that
+
 \begin{align*}
@@
 \end{lem}
+
 \begin{proof}
 We know by (Ad-ii) that
+
 \begin{align*}
@@
 \end{align*}
-If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $e_i'-1$ is even.
-Therefore, since $-\ord_{Q_i}(z)$ is an integer, we must have
+
+\noindent
+If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
+as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
+e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
+we must have
+
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq \deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
+	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
 \end{align*}
@@
 \label{thm:ramification_order_induction}
-Suppose $(\sx',L')$ is a tame separably rooted log stacky spin curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
-Then the following are true:
+Suppose $(\sx',L')$ is a tame separably rooted log stacky spin
+curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
+as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
+following are true:
 \begin{enumerate}
-	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in H^0(\sx, e_i(K_\sx))$ so that
+	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
+		H^0(\sx, e_i(K_\sx))$ so that
 		\begin{align*}
@@
 		\begin{align*}
-	\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-\frac{1}{\deg(y_{i,e_i'})e_j'}
+			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
+			\frac{1}{\deg(y_{i,e_i'})e_j'}
 		\end{align*}
 		for all $j \in J$ with $j \neq i$.
-\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0, b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally generate $R$ over $R'$.
-\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$ Then,
+	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
+		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
+		generate $R$ over $R'$.
+	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
+		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
+		block order. Let $R = k[y,x]/I.$ Then,
 		\begin{align*}
-	in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq y_{i,e_i},y_{i,e_i'} \rangle 
+			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
+			y_{i,e_i},y_{i,e_i'} \rangle
 		\end{align*}
 		as $z$ ranges over all generators of $R$.
-	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by products of two monomials and that for all $i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$ Then any set of minimal generators for $I'$ together with any set of relations as in part (c) minimally generate $I$.
+	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
+		products of two monomials and that for all $i \in J$, we have $e_i >
+		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
+		generators for $I'$ together with any set of relations as in part (c)
+		minimally generate $I$.
 	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
@@
 \end{thm}
+
 \begin{proof}
-Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in question, with coarse spaces $X = X'$. Define
+Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in 
+question, with coarse spaces $X = X'$. Define
+
 \begin{align*}
@@
 \end{align*}
+
+\noindent
 Define
@@
 \end{align*}
+
+\noindent
 Note that
@@
 \end{align*}
+
+\noindent
 and so we obtain an inclusion
 \begin{align*}
-	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset H^0(\sx,e_iL).
+	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
+H^0(\sx,e_iL).
 \end{align*}
+
+\noindent
 The assumption (Ad-iii) implies
@@
 \end{align*}
-implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by Riemann Roch, and so a general element
+
+\noindent
+implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
+Riemann Roch, and so a general element
 \begin{align*}
@@
 \end{align*}
+
+\noindent
 satisfies
 \begin{align*}
-	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 = \frac{e_i - 1}{2}
+	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
+	\frac{e_i - 1}{2}
 \end{align*}
+
+\noindent
 Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
 
-We next show $y_{i,e_i}$ also satisfies the second part of the claim of $(a),$ by considering seperately the cases of whether $j \in S(i,0),$ and $j \notin S(i,0)$.
+We next show $y_{i,e_i}$ also satisfies the second part of the
+claim of $(a),$ by considering separately the cases of whether $j
+\in S(i,0),$ and $j \notin S(i,0)$.
 
-If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)$,
+If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
+(\sx',e_iL'-E_i + Q_i)$,
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i \subhalf{e_j'} - \frac{1}{e_j'}.
+	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
+	\subhalf{e_j'} - \frac{1}{e_j'}.
 \end{align*}
 
-If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know $e_i\subhalf{e_j'} \notin \BZ$, so
+If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
+$e_i\subhalf{e_j'} \notin \BZ$, so
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor \leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
+	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
 \end{align*}
+
+\noindent
 completing the proof of (a).
@@
 Next, define $R_0 = R'$ and inductively define 
-$$
-R_i = \begin{cases}
+$$R_i = \begin{cases}
 	R_{i-1} &\text{ if }i \notin J\\
@@
 \end{cases}$$
-To prove (b), it suffices to show that elements of the form $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly indpendent, and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-vector space.
-These elements do not lie in $R_{i-1}$ because their order of pole at $Q_i$ is bigger than the order of any element in $R_{i-1}$, and are linearly independent amongst themselves because of injectivity of the linear map
+
+\noindent
+To prove (b), it suffices to show that elements of the form $y_{i,e_
+i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
+and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
+vector space. These elements do not lie in $R_{i-1}$ because their
+order of pole at $Q_i$ is bigger than the order of any element in $R
+_{i-1}$, and are linearly independent amongst themselves because of
+injectivity of the linear map
+
 \begin{align*}
-	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) \begin{pmatrix}
+	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
+	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
+	\begin{pmatrix}
 		e_i-2 & \frac{e_i-3}{2} \\
@@
 \end{align*}
-The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the integer lattice points in the cone generated by the vectors $\left(e_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2} \right)$ is saturated, as the corresponding determinant is
+
+\noindent
+The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
+b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
+integer lattice points in the cone generated by the vectors $\left(e
+_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
+\right)$ is saturated, as the corresponding determinant is
 \begin{align*}
@@
 
-To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for all $j \in J$ we have
+To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
+i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
+all $j \in J$ we have
 \begin{align*}
@@
 \end{align*}
-We now check this in three cases, depending on whether $j \notin \{i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
+
+\noindent
+We now check this in three cases, depending on whether $j \notin \{
+i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
 
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'}+ \deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
+	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
 \end{align*}
@@
 
-By part (a), condition (Ad-ii), and Lemma ~\ref{lem:admissible_inequality} we have
+By part (a), condition (Ad-ii), and Lemma
+~\ref{lem:admissible_inequality} we have
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq \frac{e_i-1}{2} + \deg z \left( \subhalf{e_i'} \right) -\frac{1}{e_i'}
-	& = \frac{e_i-1}{2}-\frac{1}{e_i'}+\left( \subhalf{e_i'} \right)\\
-	&= \frac{e_i(e_i-3)}{2(e_i-2)}+\left( \subhalf{e_i'} \right)\\
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
+	&\leq \frac{e_i-1}{2} + \deg z \left( \subhalf{e_i'} \right) -\frac{1}{e_i'} \\
+	& = \frac{e_i-1}{2}-\frac{1}{e_i'}+\left( \subhalf{e_i'} \right) \\
+	&= \frac{e_i(e_i-3)}{2(e_i-2)}+\left( \subhalf{e_i'} \right) \\
 	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq  e_i \subhalf{e_j'} +\deg z \subhalf{e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'},
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq  e_i \subhalf{e_j'} +
+	\deg z \subhalf{e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}
 \end{align*}
@@
 
-Next, note that the minimal generators of $I'$ together with the new generators of $I$ given in (c) have independent initial terms by construction, and therefore are minimal by Lemma ~\ref{lem:minimal_quadratic}.
+Next, note that the minimal generators of $I'$ together with the
+new generators of $I$ given in (c) have independent initial terms
+by construction, and therefore are minimal by Lemma
+~\ref{lem:minimal_quadratic}.
 
-Finally, to check (e), we will first show that $(\sx,J)$ is admissible.
-We know (Ad-i) is satisfied by part (b), taking the $y_{i,e_i}$ as the generators in degree $e_i$.
-Next, (Ad-ii) is strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
-Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by definition.
-This is where we use that (Ad-iii) holds for $d > 0$ and not just for $d = 0$.
+Finally, to check (e), we will first show that $(\sx,J)$ is
+admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
+i,e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
+strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
+Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
+definition. This is where we use that (Ad-iii) holds for $d > 0$
+and not just for $d = 0$.
 
-Finally, if $(\sx,J)$ then so is $(\sx,W)$ for any $W \subset J$, since each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$ if they hold for $J$.
+Finally, if $(\sx,J)$ then so is $(\sx,W)$ for any $W \subset J$,
+since each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for
+$W$ if they hold for $J$.
 \end{proof}

### 2015-06-20 stacky_write_up/spin_cring.tex
order todos

@@
 determines a map of rings, no longer necessarily graded. Consider
-the grlex monomial ordering $<$ on $k[x_1,\ldots, x_n]$. By
+the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
+\todo{This ordering isn't quite right. 
+We need to preserve the ordering on quadratic terms}
+By
 assumption, the kernel $I$ is generated by elements whose initial
@@
 rooted  log stacky curves $R \subset R'$ be the corresponding
-inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3,x_4
-,x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
+inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
 3}P$.
@@
 	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec 
-		y_4 \prec y_5$ and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
+		y_4 \prec y_5$ 
+		\todo{This order isn't quite right, we need $y_4^2 < y_5y_3$.}
+		and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
 		order so that $R = k[y_3,y_4,y_5,x]/I$. Let,

### 2015-06-20 stacky_write_up/spin_cring.tex
editing section 3
added delta to spin curves

@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so
-that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the
+Let $(\sx,\Delta, L)$ be a tame log spin curve over a perfect field $k$, so
+that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;\delta)$. Then the
 canonical ring
@@
 \begin{align*}
-	R(\sx,L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
+	R(\sx, \Delta, L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
 \end{align*}
@@
 
-In this section, we will prove that if $(\sx , L)$ is a spin curve,
+In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
 so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
-$R(\sx , L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
+$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
 e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does
@@
 \label{defn:admissible}
-Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin
+Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
+separably rooted log stacky spin
 curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
@@
 \label{thm:ramification_order_induction}
-Suppose $(\sx',L')$ is a tame separably rooted log stacky spin
+Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
 curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
@@
 \begin{proof}
-Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in 
-question, with coarse spaces $X = X'$. Define
+Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
+question, with coarse spaces $X = X'$. 
+\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
+Define
 

### 2015-06-20 stacky_write_up/spin_cring.tex
editing section 3

--- 2015-06-20 stacky_write_up/spin_cring.tex
@@
 \newcommand{\se}[1]{\section*{Problem #1}}
+\newcommand \halfcan{L}
 
@@
 \label{sec:g_0_effective}
-Let us consider $\delta \geq 2$.
+In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ when $\Delta$ is a non-zero effective divisor.
+Using this, we can reduce to looking at effective stacky divisors.
+Then, applying a result for general effective $\mathbf{Q}$ divisors, we deduce that $R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with relations generated up to degree $2e$ with initial terms quadratic in the generators.
+We also demonstrate that these bounds are tight up to \todo{insert how tight they are}.
+
+Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+\Delta\sim -2\infty+\Delta$ is a divisor of $X$ (i.e. with possibly negative integer coefficients). 
+ Since $\Delta$ is non-zero effective, $\deg(D)\ge -1$.  
+ Noting that the coefficient of any point $P$ occurring in a stacky divisor of $\sx$ must have coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$s appearing in the characteristic of $(\sx,\Delta)$).
+Since all $e_i$s are odd, $2$ cannot appear in a denominator of the coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$ must be a $X$-divisor.  
+Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  
+Thus $\halfcan$ is linearly equivalent to an effective $X$ divisor plus $\sum \subhalf{i}P_i$.  
+We have now reduced to the case of $\halfcan$ linearly equivalent to an effective divisor.
+The result in this specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum \frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
+
+To prove thisUsing induction, we can prove prove that $\halfcan$ is generated up to degrees $e$ with relations up to degree $2e$.  O'Dorney \todo{Insert reference} proves
 

### 2015-06-20 stacky_write_up/spin_cring.tex
editing section 3

@@
 
-%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%
+%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% custom commands %%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%% custom commands %%%%%%%%%%
+%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%
+%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{sec:g_0_effective}
-In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ when $\Delta$ is a non-zero effective divisor.
-Using this, we can reduce to looking at effective stacky divisors.
-Then, applying a result for general effective $\mathbf{Q}$ divisors, we deduce that $R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with relations generated up to degree $2e$ with initial terms quadratic in the generators.
-We also demonstrate that these bounds are tight up to \todo{insert how tight they are}.
+In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ when $\Delta$ is a non-
+zero effective divisor.  Using this, we can reduce to looking at effective stacky divisors.  
+Then, applying a result for general effective $\mathbf{Q}$ divisors, we deduce that 
+$R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with relations generated up to 
+degree $2e$ with initial terms quadratic in the generators.  We also demonstrate that these 
+bounds are tight up to \todo{insert how tight they are}.
 
-Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+\Delta\sim -2\infty+\Delta$ is a divisor of $X$ (i.e. with possibly negative integer coefficients). 
+Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+\Delta\sim -2\infty+
+\Delta$ is a divisor of $X$ (i.e. with possibly negative integer coefficients). 
  Since $\Delta$ is non-zero effective, $\deg(D)\ge -1$.  
- Noting that the coefficient of any point $P$ occurring in a stacky divisor of $\sx$ must have coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$s appearing in the characteristic of $(\sx,\Delta)$).
-Since all $e_i$s are odd, $2$ cannot appear in a denominator of the coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$ must be a $X$-divisor.  
+ Noting that the coefficient of any point $P$ occurring in a stacky divisor of $\sx$ must have 
+coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$s appearing in the 
+characteristic of $(\sx,\Delta)$).  
+Since all $e_i$s are odd, $2$ cannot appear in a denominator of the coefficient of a point 
+$P$ in $\halfcan$, meaning that $\frac{D}{2}$ must be a $X$-divisor.  
 Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  
@@
 We have now reduced to the case of $\halfcan$ linearly equivalent to an effective divisor.  
-The result in this specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum \frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
+The result in this specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum 
+\frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
 
-To prove thisUsing induction, we can prove prove that $\halfcan$ is generated up to degrees $e$ with relations up to degree $2e$.  O'Dorney \todo{Insert reference} proves
+To prove thisUsing induction, we can prove prove that $\halfcan$ is generated up to 
+degrees $e$ with relations up to degree $2e$.  O'Dorney \todo{Insert reference} proves
 

### 2015-06-20 stacky_write_up/spin_cring.tex
fix spacing, move table of contents before title

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%% custom commands %%%%%%%%%%
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%% custom commands %%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%
-%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\maketitle
+
 \tableofcontents
-
-\maketitle
 
@@
 \label{sec:g_0_effective}
-In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ when $\Delta$ is a non-
-zero effective divisor.  Using this, we can reduce to looking at effective stacky divisors.  
-Then, applying a result for general effective $\mathbf{Q}$ divisors, we deduce that 
-$R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with relations generated up to 
-degree $2e$ with initial terms quadratic in the generators.  We also demonstrate that these 
-bounds are tight up to \todo{insert how tight they are}.
+In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
+when $\Delta$ is a non- zero effective divisor.  Using this, we can 
+reduce to looking at effective stacky divisors.  Then, applying a 
+result for general effective $\mathbf{Q}$ divisors, we deduce that $
+R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
+relations generated up to degree $2e$ with initial terms quadratic 
+in the generators.  We also demonstrate that these bounds are tight 
+up to \todo{insert how tight they are}.
 
-Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+\Delta\sim -2\infty+
-\Delta$ is a divisor of $X$ (i.e. with possibly negative integer coefficients). 
- Since $\Delta$ is non-zero effective, $\deg(D)\ge -1$.  
- Noting that the coefficient of any point $P$ occurring in a stacky divisor of $\sx$ must have 
-coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$s appearing in the 
-characteristic of $(\sx,\Delta)$).  
-Since all $e_i$s are odd, $2$ cannot appear in a denominator of the coefficient of a point 
-$P$ in $\halfcan$, meaning that $\frac{D}{2}$ must be a $X$-divisor.  
-Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  
-Thus $\halfcan$ is linearly equivalent to an effective $X$ divisor plus $\sum \subhalf{i}P_i$.  
-We have now reduced to the case of $\halfcan$ linearly equivalent to an effective divisor.  
-The result in this specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum 
+Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+
+\Delta\sim -2\infty+ \Delta$ is a divisor of $X$ (i.e. with 
+possibly negative integer coefficients).  Since $\Delta$ is non-
+zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
+any point $P$ occurring in a stacky divisor of $\sx$ must have 
+coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+s appearing in the characteristic of $(\sx,\Delta)$).
+
+Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
+coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
+ must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
+\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
+is linearly equivalent to an effective $X$ divisor plus $\sum 
+\subhalf{i}P_i$.  We have now reduced to the case of $\halfcan$ 
+linearly equivalent to an effective divisor.  The result in this 
+specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum
 \frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
 
-To prove thisUsing induction, we can prove prove that $\halfcan$ is generated up to 
-degrees $e$ with relations up to degree $2e$.  O'Dorney \todo{Insert reference} proves
+To prove thisUsing induction, we can prove prove that $\halfcan$ is 
+generated up to degrees $e$ with relations up to degree $2e$.  
+O'Dorney \todo{Insert reference} proves
 

### 2015-06-20 stacky_write_up/spin_cring.tex
not editing section 3
O'Dorney's base case in section 3

@@
 
-%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%
-%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%
+%%%%%%%%%%%%%%%
 
@@
 linearly equivalent to an effective divisor.  The result in this 
-specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum
+specific case in fact generalizes to any $\mathbf{Q}$-divisor: $D=\sum
 \frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
 
-To prove thisUsing induction, we can prove prove that $\halfcan$ is 
-generated up to degrees $e$ with relations up to degree $2e$.  
-O'Dorney \todo{Insert reference} proves
+We will sketch a proof by induction.
+O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$.
+He finds generators in degrees up to $\beta$ and relations that are all quadratic in the generators (and thus lying in degrees at most $2\beta$).
+We can ind
 

### 2015-06-21 stacky_write_up/spin_cring.tex
minor AD-ii wording edit
half of theorem in section 3

@@
 \newcommand \halfcan{L}
+\newcommand \Supp{\text{Supp}}
+\newcommand \initial{\text{in}}
 
@@
 
-We will sketch a proof by induction.
-O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$.
-He finds generators in degrees up to $\beta$ and relations that are all quadratic in the generators (and thus lying in degrees at most $2\beta$).
-We can ind
+We will prove this by induction using methods analogous to ones of VZB\todo{add reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$:
+\begin{lem}\label{lem:O'Dorney_1_point}
+Let 
+\[
+	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
+\] 
+be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}$.
+Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ lies in degree $d_i$ with pole of degree $c_i$ at $P$.
+\end{lem}
+\begin{proof}
+See O'Dorney \todo{provide reference}.
+\end{proof}
+
+The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
+
+\begin{lem}\label{lem:deg_1_saturation_induction}
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.
+Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.
+Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that
+\begin{equation}\label{lem:deg_1_saturation_induction_dimension_condition}
+h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:d\ge \frac{\beta}{\alpha}.
+\end{equation}
+Let 
+\[
+	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+\]
+be the nonnegative best lower approximation.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
+\[
+	\initial_\prec(I')=\initial_\prec(I) k[u,x_1,...,x_m,y_1,...,y_n]+\langle y_ix_j: 1\le i\le n, 1\le j\le m\rangle+\langle y_iy_j: 1\le i\le j\le n-1\rangle.
+\]
+\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
+\end{itemize}
+\end{lem}
+\begin{proof}
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
+These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.
+
+Begin by focusing on the $d^{th}$ component of $R_{D'}$: $(R_{D'})_d=H^0(X,\lfloor D+\frac{\alpha}{\beta}P\rfloor)$.
+By our hypothesis (equation \ref{lem:deg_1_saturation_induction_dimension_condition}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{\alpha}{\beta}\rfloor>0$,
+\[
+	h^0(X,d(D+\frac{\alpha}{\beta}))=h^0(X,dD)+\deg(d\frac{\alpha}{\beta})
+\]
+so in $H^0(X,\lfloor dD'\rfloor)$ we can find elements with pole order $i$ at $P$ for any $i\in 0,...,\lfloor d\frac{\alpha}{\beta}\rfloor$.
+We can use a method similar to O'Dorney to construct the $y_i$s as desired:
+
+Let $0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}$ be the nonnegative best lower approximation of $\frac{\alpha}{\beta}$.
+Note that elements of $H^0(X,dD')$ have pole of orders ranging from 0 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor=c_i$ at $P$.
+For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction, so any product of $\prod z_i$ of elements of degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i}$, so we have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.
+Thus, the elements of $R_{d_i}
+
+ in fact a generic element in the respective degree will suffice.\todo{add proof of this; is the generic statement correct?}  Following O'Dorney's argument correctly gives that these along with $u$ (in degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{\alpha}{\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{D'})_d$ with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace consisting of elements only with nonzero pole at $P$.
+Therefore, by pole considerations $y_1,...,y_n$ generate $(R_{D'})_d$ over $(R_{D})_d$, \todo{the word generate here is a little imprecise} so $u,x_1,...,x_m,y_1,...,y_n$ generate $R_{D'}$.
+
+\end{proof}
 

### 2015-06-21 stacky_write_up/spin_cring.tex
more proof of section 3 main theorem

@@
 
-We will prove this by induction using methods analogous to ones of VZB\todo{add reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$:
+We will prove this by induction using methods analogous to ones of VZB\todo{add 
+reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D
+\sim \frac{\alpha}{\beta} P$:
 \begin{lem}\label{lem:O'Dorney_1_point}
@@
 \] 
-be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}$.
-Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ lies in degree $d_i$ with pole of degree $c_i$ at $P$.
+be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}
+$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ 
+lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
 \end{lem}
@@
 
-The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
+The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
+8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
 
 \begin{lem}\label{lem:deg_1_saturation_induction}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.
-Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.
-Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney
+\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so 
+$R_D$ has a generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by 
+$u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau
+$.  Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in 
+\mathbf{N}$ such that 
 \begin{equation}\label{lem:deg_1_saturation_induction_dimension_condition}
-h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:d\ge \frac{\beta}{\alpha}.
+h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD\rfloor)+\lfloor d\frac{\alpha}
+{\beta}\rfloor \forall d\in \mathbf{N}:d\ge \frac{\beta}{\alpha}.
 \end{equation}
@@
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
 \[
-	\initial_\prec(I')=\initial_\prec(I) k[u,x_1,...,x_m,y_1,...,y_n]+\langle y_ix_j: 1\le i\le n, 1\le j\le m\rangle+\langle y_iy_j: 1\le i\le j\le n-1\rangle.
+	\initial_\prec(I')=\initial_\prec(I) k[u,x_1,...,x_m,y_1,...,y_n]+\langle y_ix_j: 1\le i\le n, 1\le 
+j\le m\rangle+\langle y_iy_j: 1\le i\le j\le n-1\rangle.
 \]
@@
 \begin{proof}
-Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.  These can be chosen 
+generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if 
+it turns out to be unnecessary}.
 
-Begin by focusing on the $d^{th}$ component of $R_{D'}$: $(R_{D'})_d=H^0(X,\lfloor D+\frac{\alpha}{\beta}P\rfloor)$.
-By our hypothesis (equation \ref{lem:deg_1_saturation_induction_dimension_condition}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{\alpha}{\beta}\rfloor>0$,
+Begin by focusing on the $d^{th}$ component of $R_{D'}$: $(R_{D'})_d=H^0(X,\lfloor D+
+\frac{\alpha}{\beta}P\rfloor)$.  By our hypothesis (equation 
+\ref{lem:deg_1_saturation_induction_dimension_condition}), for any $d\in\mathbf{N}$ such 
+that $\lfloor d\frac{\alpha}{\beta}\rfloor>0$,
 \[
@@
 \]
-so in $H^0(X,\lfloor dD'\rfloor)$ we can find elements with pole order $i$ at $P$ for any $i\in 0,...,\lfloor d\frac{\alpha}{\beta}\rfloor$.
-We can use a method similar to O'Dorney to construct the $y_i$s as desired:
+so in $H^0(X,\lfloor dD'\rfloor)$ we can find elements with pole order $i$ at $P$ for any $i\in 
+0,...,\lfloor d\frac{\alpha}{\beta}\rfloor$.  We can use a method similar to O'Dorney to 
+construct the $y_i$s as desired:
 
-Let $0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}$ be the nonnegative best lower approximation of $\frac{\alpha}{\beta}$.
-Note that elements of $H^0(X,dD')$ have pole of orders ranging from 0 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor=c_i$ at $P$.
-For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction, so any product of $\prod z_i$ of elements of degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i}$, so we have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.
-Thus, the elements of $R_{d_i}
+Let $0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}$ be the nonnegative best 
+lower approximation of $\frac{\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have 
+pole of orders ranging from 0 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor=c_i$ at $P$.  A set of 
+these one for each pole degree 1 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor$ are linearly 
+independent from each other and $(R_D)_d$, so by degree considerations, they span $
+(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
 
- in fact a generic element in the respective degree will suffice.\todo{add proof of this; is the generic statement correct?}  Following O'Dorney's argument correctly gives that these along with $u$ (in degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{\alpha}{\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{D'})_d$ with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace consisting of elements only with nonzero pole at $P$.
-Therefore, by pole considerations $y_1,...,y_n$ generate $(R_{D'})_d$ over $(R_{D})_d$, \todo{the word generate here is a little imprecise} so $u,x_1,...,x_m,y_1,...,y_n$ generate $R_{D'}$.
+For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction, so any product of $\prod z_i$ 
+of elements of degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i}
+$, so we have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{\sum -\ord( z_i)}
+{\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.  Thus, elements of $(R_{D'})d_i$ with pole order 
+$c_i$ at $P$ are not generated by lower degrees; generically choose some $y_i
+\in(R_{D'})_{d_i}$ to have maximal pole order (note that if $d_i=1$ then $-\ord_P(y_i)=
+\max(c_j:d_j=1)$ and if more than one $d_i$ is 1, we must also choose them generically so 
+they generate $(R_{D'})_1$).
+
+Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}}\le \frac{\alpha}{\beta}$ with $c>0$ is not a 
+best lower approximation.  Then choose best lower approximation $\frac{c_i}{d_i}$ such that 
+$c_i\le c$ is maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From this we can 
+deduce that $c_i+(d-d_i)\lfloor \frac{\alpha}{\beta}\rfloor\ge c$.  Therefore, we can produce 
+an element in $(R_{D'})_d$ with pole degree $c$ at $P$ by either $y_iu^b$ or $y_jy_iu^b$ 
+where $d_j=1$ and if $d_i=1$ as well then $c_i=1$.  Thus, for a general $d$ (not 
+necessarily less than $\beta$), if $\frac{c}{d}\le \frac{\alpha}{\beta}$ is not a best lower 
+approximation than we can construct an element in degree $d$ with pole degree $c$ by 
+either $y_n^a y_iu^b$ or $y_n^a y_j y_iu^b$ with the latter satisfying the same conditions.  
+We notice that elements of this form are all linearly independent in $R_{D'}$.  Thus, they 
+form a $k$-basis for $R_{D'}$ over $R_D$.  Thus $u,x_1,...,x_m,y_1,...,y_n$ generate 
+$R_{D'}$.
+
+\todo{finish proof of relations, which follows easily using VZB's method; peter will do this tomorrow (sunday)}
 
 \end{proof}
+
+\todo{lot's of corollaries; peter can do this tomorrow}
 
@@
 		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
-	\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a 
-		generator of $R'$ we have
+	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
+		of $R'$ satisfies
 		\begin{align*}

### 2015-06-21 stacky_write_up/spin_cring.tex
minor edits to admissibilty, fix Peter's code

--- 2015-06-20 stacky_write_up/spin_cring.tex
@@
 
-We will sketch a proof by induction.
-O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$.
-He finds generators in degrees up to $\beta$ and relations that are all quadratic in the generators (and thus lying in degrees at most $2\beta$).
-We can ind
+We will prove this by induction using methods analogous to ones of VZB\todo{add reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$:
+\begin{lem}\label{lem:O'Dorney_1_point}
+Let 
+\[
+	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
+\] 
+be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}$.
+Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ lies in degree $d_i$ with pole of degree $c_i$ at $P$.
+\end{lem}
+\begin{proof}
+See O'Dorney \todo{provide reference}.
+\end{proof}
+
+The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
+
+\begin{lem}
+\label{lem:deg1_sat_ind}
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.
+Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.
+Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that
+\begin{equation}
+\label{eqn:deg1_sat_ind_dim}
+	h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD
+	\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:
+	d\ge \frac{\beta}{\alpha}.
+\end{equation}
+Let 
+\[
+	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+\]
+be the non-negative best lower approximation.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
+\begin{align*}
+	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
+										 &+ \langle y_i y_j: 1 \le i \le j \le n-1 \rangle.
+\end{align*}
+\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
+\end{itemize}
+\end{lem}
+
+\begin{proof}
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
+These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.
+
+Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
+{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$.  By our
+hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{
+\alpha}{\beta}\rfloor>0$,
+
+\[
+	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
+\]
+
+\noindent
+so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
+order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
+\beta} \rfloor \}$. We can use a method similar to O'Dorney to
+construct the $y_i$'s as desired: \todo{cite where}
+
+Let $0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+\beta}$ be the non-negative best lower approximation of $\frac{
+\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
+orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
+c_i $ at $P$.  For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
+by construction, so any product of $\prod z_i$ of elements of
+degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)} <
+\frac{c_i}{d _i}$, so we have the pole order of this product is $
+\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_
+i\frac{c_i}{d_i} = c_i $. Thus, the elements of $R_{d_i}$
+
+In fact, a generic element in the respective degree will suffice.
+\todo{add proof of this; is the generic statement correct?}
+Following the argument given by O'Dorney \todo{cite, give specific
+theorem number} correctly gives that these along with $u$ (in
+degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{ \alpha}{
+\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{ D'})_d$
+with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace
+consisting of elements only with nonzero pole at $P$. Therefore, by
+pole considerations $y_1,...,y_n$ generate $(R_{D'})_d $ over $(R_{D
+})_d$, \todo{the word generate here is a little imprecise} so $u,x_1
+,...,x_m,y_1,...,y_n$ generate $R_{D'}$.
+
+\end{proof}
 
@@
 		\end{align*}
-	\item[(Ad-iii)] For all $i \in J$ we have for all $d \geq 0$,
+	\item[(Ad-iii)] For all $i \in J$ we have
 		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq \# S(i,d)
+			\deg \lfloor e_i L \rfloor \geq \# S(i)
 		\end{align*}
@@
 		\begin{align*}
-			S(i,d) = \{j \in J : j \neq i \text{ and }e_j'+2d \mid e_i+2d\}
+			S(i) := \{j \in J : j \neq i \text{ and } e_j'+2d \mid e_i -
+			e_j' \text{ for some } d \geq 0\}
 		\end{align*}
@@
 
+\begin{lem}
+\label{lem:admissible_subset}
+If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
+then $(\sx', W)$ is also admissible.
+\end{lem}
+
+\begin{proof}
+Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
+if they hold for $J$.
+\end{proof}
+
 \begin{thm}
@@
 Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
-curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
-as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
-following are true:
+curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
+R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
+Then the following are true:
 \begin{enumerate}
@@
 		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
-			y_{i,e_i},y_{i,e_i'} \rangle
+			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
+			\neq y_{i,e_i},y_{i,e_i'} \rangle
 		\end{align*}
@@
 	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
-		products of two monomials and that for all $i \in J$, we have $e_i >
-		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
-		generators for $I'$ together with any set of relations as in part (c)
-		minimally generate $I$.
+		products of two monomials and that for all $i \in J$, we have $e
+		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
+		minimal generators for $I'$ together with any set of relations as in 
+		part (c) minimally generate $I$.
 	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
@@
 
-Finally, if $(\sx,J)$ then so is $(\sx,W)$ for any $W \subset J$,
-since each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for
-$W$ if they hold for $J$.
+Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
+$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
 \end{proof}

### 2015-06-21 stacky_write_up/spin_cring.tex

@@
 
-The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
+The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
+8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
 
@@
 \label{lem:deg1_sat_ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.
-Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.
-Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
+defined by O'Dorney \todo{reference this-Section 1 of Evan's paper})
+satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
+generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\delta$ with relations generated 
+in degree at most $\tau $.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
+that
+
 \begin{equation}
 \label{eqn:deg1_sat_ind_dim}
-	h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD
-	\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:
-	d\ge \frac{\beta}{\alpha}.
+	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
+	N} : d \ge \frac{\beta}{\alpha}.
 \end{equation}
@@
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+
 \begin{align*}
@@
 \end{align*}
+
 \todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
@@
 Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.
+These can be chosen generically to not have a zero at $P$ \todo{
+check that we can actually do this, or eliminate if it turns out to
+be unnecessary}.
 
 Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
-{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$.  By our
-hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{
-\alpha}{\beta}\rfloor>0$,
+{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
+our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
+\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
 
@@
 orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
+c_i $ at $P$. A set of these one for each pole degree 1 to $\lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
+each other and $(R_D)_d$, so by degree considerations, they span
+$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
+
+For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
 by construction, so any product of $\prod z_i$ of elements of
@@
 
-In fact, a generic element in the respective degree will suffice.
-\todo{add proof of this; is the generic statement correct?}
-Following the argument given by O'Dorney \todo{cite, give specific
-theorem number} correctly gives that these along with $u$ (in
-degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{ \alpha}{
-\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{ D'})_d$
-with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace
-consisting of elements only with nonzero pole at $P$. Therefore, by
-pole considerations $y_1,...,y_n$ generate $(R_{D'})_d $ over $(R_{D
-})_d$, \todo{the word generate here is a little imprecise} so $u,x_1
-,...,x_m,y_1,...,y_n$ generate $R_{D'}$.
+For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction,
+so any product of $\prod z_i$ of elements of degrees less than $d_i$
+ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i} $, so we
+have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{
+\sum -\ord( z_i)} {\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.
+Thus, elements of $(R_{D'})d_i$ with pole order $c_i$ at $P$ are
+not generated by lower degrees; generically choose some $y_i \in(R_{
+D'})_{d_i}$ to have maximal pole order (note that if $d_i=1$ then $-
+\ord_P(y_i)= \max(c_j:d_j=1)$ and if more than one $d_i$ is 1, we
+must also choose them generically so they generate $(R_{D'})_1$).
+
+Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}}\le \frac{\alpha}{
+\beta}$ with $c>0$ is not a best lower approximation.  Then choose
+best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
+maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
+this we can deduce that $c_i+(d-d_i)\lfloor \frac{\alpha}{\beta}
+\rfloor\ge c$.  Therefore, we can produce an element in $(R_{D'})_d$
+ with pole degree $c$ at $P$ by either $y_i u^b$ or $y_j y_i u^b$
+where $d_j=1$ and if $d_i=1$ as well then $c_i=1$. Thus, for a
+general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+\frac{\alpha}{\beta}$ is not a best lower approximation than we can
+construct an element in degree $d$ with pole degree $c$ by either $y
+_n^a y_i u^b$ or $y_n^a y_j y_iu^b$ with the latter satisfying the
+same conditions.  We notice that elements of this form are all
+linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
+$R_{D'}$ over $R_D$.  Thus $u,x_1,...,x_m,y_1,...,y_n$ generate
+$R_{D'}$.
+
+\todo{finish proof of relations, which follows easily using VZB's
+method; peter will do this tomorrow (sunday)}
 
 \end{proof}
+
+\todo{lots of corollaries; peter can do this tomorrow}
 

### 2015-06-21 stacky_write_up/spin_cring.tex
add base cases, exception cases, concl, saturation
* also added tables
* also shortened label names
* added subscript to S(i)

@@
 \usepackage{color}
+\usepackage{longtable}
 
@@
 
-\usepackage{hyperref}
-  \hypersetup{colorlinks=true,citecolor=blue}
+%\usepackage{hyperref}
+  %\hypersetup{colorlinks=true,citecolor=blue}
 
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx,\Delta, L)$ be a tame log spin curve over a perfect field $k$, so
-that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;\delta)$. Then the
+Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
+that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
 canonical ring
@@
 \begin{align*}
-	R(\sx, \Delta, L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
+	R(\sx, \Delta, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
 \end{align*}
@@
 \end{thm}
-\begin{proof}
-
-\end{proof}
 
@@
 $R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
-e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does
-not lie in a finite list of exceptions. This is proven in
+e_r)$ with relations generated in degree at most $2e$, so long as $\sigma$
+does not lie in a finite list of exceptions. This is proven in
 Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
@@
 \label{ssec:g_0_saturation}
+Here we compute saturation numbers. That is, given a list of
+ramification orders, with $g = 0,\delta = 0$ understood, we have
+the following saturations of the canonical divisor, as defined in 7.
+2 of VZB \cite{vzb:stacky}. Exceptional cases are listed first
+and generic cases follow.
+
+\todo{prove}
+
+\begin{longtable}
+	{| c | c |}
+	\hline
+	Signature & Saturation \\
+	\hline
+	\hline
+
+	$(0; 3, 3, 3; 0)$ & $\infty$ \\	\hline
+
+	$(0; 3, 3, 5; 0)$ & $18$ \\	\hline
+
+	$(0; 3, 3, 7; 0)$ & $12$ \\	\hline
+
+	$(0; 3, 3, 9; 0)$ & $12$ \\	\hline
+
+	$(0; 3, 5, 5; 0)$ & $8$ \\	\hline
+
+	$(0; 5, 5, 5; 0)$ & $8$ \\	\hline
+
+	$(0; 3, 3, 3, 3; 0)$ & $6$ \\	\hline
+
+	\hline
+
+	$(0; 3, 3, k; 0)$ & $9$ \\	\hline
+
+	$(0; a, b, c; 0)$ & $5$ \\	\hline
+
+	$(0; e_1, \ldots, e_r; 0)$ & $3$ \\	\hline
+\end{longtable}
+
+\begin{center}
+\textbf{Table (I)}: Genus 0 saturation
+\end{center}
 
@@
 
-\ssec{Inductive theorem: Increasing the Ramification Orders}
+\ssec{Inductive Theorem: Increasing the Ramification Orders}
 \label{ssec:g_0_ram_orders}
 In this section, we aim to prove the inductive theorem, Theorem
-~\ref{thm:ramification_order_induction}. Under fairly general
+~\ref{thm:ram_order_ind}. Under fairly general
 conditions, this theorem will allow us to show that if Theorem ~\ref
-{thm:ramification_order_induction} holds for a curve with signature
+{thm:ram_order_ind} holds for a curve with signature
 $(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
@@
 		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq \# S(i)
+			\deg \lfloor e_i L \rfloor \geq \# S_{\sigma, J}(i)
 		\end{align*}
@@
 		\begin{align*}
-			S(i) := \{j \in J : j \neq i \text{ and } e_j'+2d \mid e_i -
-			e_j' \text{ for some } d \geq 0\}
+			S_{\sigma, J}(i) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i - e_j' \text{ for some } d \geq 0\}
 		\end{align*}
@@
 \begin{thm}
-\label{thm:ramification_order_induction}
+\label{thm:ram_order_ind}
 Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
@@
 \label{ssec:g_0_base}
-Cases to induct on are here.
+Now we have an inductive statement on the number of ramified
+points in Proposition ~\ref{prop:sat_three_induction} and
+an inductive statement on ramification orders in Theorem
+~\ref{thm:ram_order_ind}. After verifying that explicit pairs
+$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
+particular choices of $J$ are admissible, the application of the
+two inductive statements demonstrate that the spin canonical ring
+$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
+\ldots, e_r)$ with relations generated in degree at most $2e$ for
+$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
+of a finite set of exceptional cases.
+
+\begin{lem}
+\label{lem:g_0_admissible_cases}
+Let $(\sx', \Delta, L')$ be a tame log spin curve over a perfect field $k$,
+so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$.
+Then $R(\sx', \Delta, L')$ is generated as a $k$-algebra by elements of
+degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at
+most $2e$ and $(\sx', J)$ is admissible for the following cases:
+
+\begin{enumerate}
+	\item[(a)] $\sigma = (0; 3, 3, 11; 0), J = \{3\}$
+	\item[(b)] $\sigma = (0; 3, 5, 9; 0), J = \{2, 3\}$
+	\item[(c)] $\sigma = (0; 5, 5, 7; 0), J = \{1, 2, 3\}$
+	\item[(d)] $\sigma = (0; 3, 3, 3, 5; 0), J = \{1, 2, 3, 4\}$
+	\item[(e)] $\sigma = (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+For each case, computations using a combination of Riemann-Roch and
+comparing pole orders at each ramification point $P_i$ gives the
+generator and relation degrees. Note that (Ad-i) always holds.
+In each case we can also pick a set of generators such that
+(Ad-ii) holds. \todo{justification for these}
+
+The following table demonstrates that $R(\sx', \Delta, L')$ is
+generated as a $k$-algebra by elements of degree at most $e$
+with relations in degree at most $2e$ for each case.
+
+\begin{longtable}
+	{| c || c | c | c |}
+	\hline
+	Case & Generator Degrees & Minimal Relation Degrees & $e$\\
+	\hline
+	\hline
+
+	(a) & \{3, 7, 9, 11\} & \{14, 18\} & 11\\	\hline
+
+	(b) & \{3, 5, 7, 9\} & \{12, 14\}	& 9\\ \hline
+
+	(c) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
+
+	(d) & \{3, 3, 4, 5\} & \{8,	9\} & 5\\ \hline
+
+	(e) & \{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
+\end{longtable}
+
+\begin{center}
+\textbf{Table (II)}: Genus 0 noneffective base cases
+\end{center}
+
+Furthermore, each case satisfies (Ad-iii) as demonstrated below.
+
+\begin{enumerate}
+	\item[(a)] $(\deg \lfloor e_3 \rfloor, \# S_{(\sigma, J)}(3)) = (1, 0)$
+
+	\item[(b)] $(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (1, 0)$ \\
+		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
+
+	\item[(c)] $(\deg \lfloor e_1 \rfloor, \#S_{(\sigma, J)}(1)) = (2, 1)$ \\
+		$(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (2, 1)$ \\
+		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
+
+	\item[(d)] $(\deg \lfloor e_i \rfloor, \#S_{(\sigma, J)}(i)) = (3, 1)$
+		for $i \neq 4$ \\
+		$(\deg \lfloor e_4 \rfloor, \#S_{(\sigma, J)}(4))	= (2, 0)$.
+
+	\item[(e)] $(\deg \lfloor e_i \rfloor, \#S_{(\sigma, J)}(1)) = (5, 0)$
+		for all $i \in J$.
+\end{enumerate}
+
+Finally, each case also satisfies the property that $in_\prec(I')$ is
+minimally generated by products of two monomials and that for all
+$i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$
+\todo{prove}
+\end{proof}
+
+Now we can induct on cases (a)-(e) of \ref{lem:g_0_admissible_cases}
+to obtain bounds on the minimal generator and relation degrees for
+canonical rings of curves in the genus 0 case.
+
+Using the results of Proposition ~\ref{prop:sat_three_induction}
+and Theorem ~\ref{thm:ram_order_ind}, we can inductively raise
+the ramification orders and number of ramified points in all of the
+cases in Lemma ~\ref{lem:g_0_admissible_cases} to obtain the following
+result.
+
+\begin{cor}
+\label{cor:g_0_gen_rel_base_cases}
+Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
+that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$. Then the
+canonical ring
+
+\[
+	R(\sx, 0, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+\]
+
+\noindent
+is generated as a $k$-algebra by elements of degree at most $e := 
+\max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so 
+long as $\sigma \notin S$ where
+
+\begin{align*}
+	S &:= \{(0; 3, 3, k; 0) : 3 \leq k \leq 9 \text{ odd}\} \\
+		&\cup \{(0; 3, b, c; 0) : 5 \leq b \leq c \leq 7\} \\
+		&\cup \{(0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
+\end{align*}
+
+\noindent
+is a finite set.
+\end{cor}
+
+\begin{proof}
+A process of induction raising the ramification orders of
+the ramified points of the spin curves corresponding to Lemma
+~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
+~\ref{thm:ram_order_ind} will demonstrate the desired generator and
+relation degree results for curves with three ramified points.
+Similarly, this induction process on Lemma
+~\ref{lem:g_0_admissible_cases} case (d) will give the desired
+result for curves with four ramified points excluding signature
+$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
+number of ramified points via Proposition
+~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
+case (e) combined with the induction process on ramification orders
+will yield the result for curves with at least five ramified points.
+\todo{Detailed description of how the inductive lemmata yield e and 2e}
+\end{proof}
 
@@
 \label{ssec:g_0_exceptional}
-These are exceptional cases.
+Here we present the explicit generators and relations of the remaining
+cases given by signatures in the finite set
+
+\begin{align*}
+	S &:= \{(0; 3, 3, k; 0) : 3 \leq k \leq 9 \text{ odd}\} \\
+		&\cup \{(0; 3, b, c; 0) : 5 \leq b \leq c \leq 7\} \\
+		&\cup \{(0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
+\end{align*}
+
+\noindent
+and in particular describe the only exceptions to the $e$ and $2e$
+bounds on the generator degree and relation degree, respectively,
+in the genus 0 case.
+
+\begin{longtable}
+	{| c || c | c | c |}
+	\hline
+	Signature & Generator Degrees & Minimal Relation Degrees & $e$ \\
+	\hline
+	\hline
+
+	$(0; 3, 3, 3; 0)$ & $\{3\}$ & $\emptyset$ & $3$ \\	\hline
+
+	$(0; 3, 3, 5; 0)$ & $\{3, 10, 15\}$ & $\{30\}$ & $5$ \\	\hline
+
+	$(0; 3, 3, 7; 0)$ & $\{3, 7, 12\}$ & $\{24\}$ & $7$ \\	\hline
+
+	$(0; 3, 3, 9; 0)$ & $\{3, 7, 9\}$ & $\{21\}$ & $9$ \\	\hline
+
+	$(0; 3, 5, 5; 0)$ & $\{3, 5, 10\}$ & $\{20\}$ & $5$ \\	\hline
+
+	$(0; 3, 5, 7; 0)$ & $\{3, 5, 7\}$ & $\{17\}$ & $7$ \\	\hline
+
+	$(0; 5, 5, 5; 0)$ & $\{3, 5, 5\}$ & $\{15\}$ & $5$ \\	\hline
+
+	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $3$ \\	\hline
+
+	\hline
+
+	$(0; 3, 7, 7; 0)$ & $\{3, 5, 7, 7\}$ & $\{10, 14\}$ & $7$ \\	\hline
+\end{longtable}
+
+\begin{center}
+\textbf{Table (III)}: Genus 0 exceptional cases
+\end{center}
+
+\begin{rem}
+These cases, apart from $(0; 3, 7, 7; 0)$, give all of the
+exceptions to the $e$ and $2e$ bounds on the generator and relation
+degree. Notice that each of these exceptional cases, apart from
+$(0; 3, 5, 7; 0)$, corresponds to a signature with non-generic
+saturation (i.e. saturation not equal to 3, 5, or 9 as seen
+in the table in Subsection ~\ref{ssec:g_0_saturation}). Exceptional
+saturation can be viewed as ``forcing'' generators (and thus
+relations) in higher degrees than in the generic case.
+\end{rem}
 
@@
 \label{ssec:g_0_conclusion}
+
+\begin{thm}
+\label{thm:g_0_generators_relations_rep}
+Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
+that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
+canonical ring
+
+\begin{align*}
+	R(\sx, \Delta, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+\end{align*}
+
+\noindent
+is generated as a $k$-algebra by elements of degree at most $e = 
+\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so 
+long as $\sigma$ does not lie in a finite list of exceptions. \todo{
+Include reference to the table with this list of exceptions.}
+\end{thm}
 

### 2015-06-21 stacky_write_up/spin_cring.tex
A few todos added to section 4; in particular suggests generalization to arbitrary genus

--- 2015-06-21 stacky_write_up/spin_cring.tex
@@
 
-The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
+The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
+8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
 
-\begin{lem}
-\label{lem:deg1_sat_ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.
-Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.
-Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that
-\begin{equation}
-\label{eqn:deg1_sat_ind_dim}
-	h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD
-	\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:
-	d\ge \frac{\beta}{\alpha}.
+\begin{lem}\label{lem:deg_1_saturation_induction}
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney
+\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so 
+$R_D$ has a generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by 
+$u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau
+$.  Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in 
+\mathbf{N}$ such that 
+\begin{equation}\label{lem:deg_1_saturation_induction_dimension_condition}
+h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD\rfloor)+\lfloor d\frac{\alpha}
+{\beta}\rfloor \forall d\in \mathbf{N}:d\ge \frac{\beta}{\alpha}.
 \end{equation}
@@
 \]
-be the non-negative best lower approximation.
+be the nonnegative best lower approximation.
 Then 
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: 1 \le i \le j \le n-1 \rangle.
-\end{align*}
+\[
+	\initial_\prec(I')=\initial_\prec(I) k[u,x_1,...,x_m,y_1,...,y_n]+\langle y_ix_j: 1\le i\le n, 1\le 
+j\le m\rangle+\langle y_iy_j: 1\le i\le j\le n-1\rangle.
+\]
 \todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
@@
 \end{lem}
+\begin{proof}
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.  These can be chosen 
+generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if 
+it turns out to be unnecessary}.
 
-\begin{proof}
-Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.
+Begin by focusing on the $d^{th}$ component of $R_{D'}$: $(R_{D'})_d=H^0(X,\lfloor D+
+\frac{\alpha}{\beta}P\rfloor)$.  By our hypothesis (equation 
+\ref{lem:deg_1_saturation_induction_dimension_condition}), for any $d\in\mathbf{N}$ such 
+that $\lfloor d\frac{\alpha}{\beta}\rfloor>0$,
+\[
+	h^0(X,d(D+\frac{\alpha}{\beta}))=h^0(X,dD)+\deg(d\frac{\alpha}{\beta})
+\]
+so in $H^0(X,\lfloor dD'\rfloor)$ we can find elements with pole order $i$ at $P$ for any $i\in 
+0,...,\lfloor d\frac{\alpha}{\beta}\rfloor$.  We can use a method similar to O'Dorney to 
+construct the $y_i$s as desired:
 
-Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
-{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$.  By our
-hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{
-\alpha}{\beta}\rfloor>0$,
+Let $0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}$ be the nonnegative best 
+lower approximation of $\frac{\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have 
+pole of orders ranging from 0 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor=c_i$ at $P$.  A set of 
+these one for each pole degree 1 to $\lfloor d_i\frac{\alpha}{\beta}\rfloor$ are linearly 
+independent from each other and $(R_D)_d$, so by degree considerations, they span $
+(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
 
-\[
-	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
-\]
+For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction, so any product of $\prod z_i$ 
+of elements of degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i}
+$, so we have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{\sum -\ord( z_i)}
+{\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.  Thus, elements of $(R_{D'})d_i$ with pole order 
+$c_i$ at $P$ are not generated by lower degrees; generically choose some $y_i
+\in(R_{D'})_{d_i}$ to have maximal pole order (note that if $d_i=1$ then $-\ord_P(y_i)=
+\max(c_j:d_j=1)$ and if more than one $d_i$ is 1, we must also choose them generically so 
+they generate $(R_{D'})_1$).
 
-\noindent
-so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
-order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We can use a method similar to O'Dorney to
-construct the $y_i$'s as desired: \todo{cite where}
+Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}}\le \frac{\alpha}{\beta}$ with $c>0$ is not a 
+best lower approximation.  Then choose best lower approximation $\frac{c_i}{d_i}$ such that 
+$c_i\le c$ is maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From this we can 
+deduce that $c_i+(d-d_i)\lfloor \frac{\alpha}{\beta}\rfloor\ge c$.  Therefore, we can produce 
+an element in $(R_{D'})_d$ with pole degree $c$ at $P$ by either $y_iu^b$ or $y_jy_iu^b$ 
+where $d_j=1$ and if $d_i=1$ as well then $c_i=1$.  Thus, for a general $d$ (not 
+necessarily less than $\beta$), if $\frac{c}{d}\le \frac{\alpha}{\beta}$ is not a best lower 
+approximation than we can construct an element in degree $d$ with pole degree $c$ by 
+either $y_n^a y_iu^b$ or $y_n^a y_j y_iu^b$ with the latter satisfying the same conditions.  
+We notice that elements of this form are all linearly independent in $R_{D'}$.  Thus, they 
+form a $k$-basis for $R_{D'}$ over $R_D$.  Thus $u,x_1,...,x_m,y_1,...,y_n$ generate 
+$R_{D'}$.
 
-Let $0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-\beta}$ be the non-negative best lower approximation of $\frac{
-\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
-orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
-by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)} <
-\frac{c_i}{d _i}$, so we have the pole order of this product is $
-\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_
-i\frac{c_i}{d_i} = c_i $. Thus, the elements of $R_{d_i}$
-
-In fact, a generic element in the respective degree will suffice.
-\todo{add proof of this; is the generic statement correct?}
-Following the argument given by O'Dorney \todo{cite, give specific
-theorem number} correctly gives that these along with $u$ (in
-degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{ \alpha}{
-\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{ D'})_d$
-with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace
-consisting of elements only with nonzero pole at $P$. Therefore, by
-pole considerations $y_1,...,y_n$ generate $(R_{D'})_d $ over $(R_{D
-})_d$, \todo{the word generate here is a little imprecise} so $u,x_1
-,...,x_m,y_1,...,y_n$ generate $R_{D'}$.
+\todo{finish proof of relations, which follows easily using VZB's method; peter will do this tomorrow (sunday)}
 
@@
 
+\todo{lot's of corollaries; peter can do this tomorrow}
+
 \section{Non-effective Genus Zero Spin Divisors}
 \label{sec:g_0_non_effective}
+
+\todo{Peter: throughout this section I will provide a few notes of how we can generalize this to arbitrary genus with the appropriate conditions}
 
@@
 Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
-rooted  log stacky curves $R \subset R'$ be the corresponding
+rooted log stacky curves $R \subset R'$
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$)}
+be the corresponding
 inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3, x_4
 , x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
-3}P$.
+3}P$\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
 
@@
 \end{align}
+\todo{You need to say explicitly somewhere that $x_i$ lies in degree $i$; also for the higher genus case, we should replace $x_3, x_4, x_5$ with $x_2, x_3$ and everything should work the same.}
 
@@
 Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
-{\bf admissible} if the following three conditions hold.
+{\bf admissible} if the following three conditions hold.  \todo{Peter: We should make the definition of admissibility be a condition for the triple: $(\sx',\sx,J)$.}
 
@@
 		\end{align*}
-	\item[(Ad-iii)] For all $i \in J$ we have
+	\item[(Ad-iii)] For all $i \in J$ we have for all $d \geq 0$,
 		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq \# S(i)
+			\deg \lfloor e_i L \rfloor \geq \# S(i,d)
 		\end{align*}
@@
 		\begin{align*}
-			S(i) := \{j \in J : j \neq i \text{ and } e_j'+2d \mid e_i -
-			e_j' \text{ for some } d \geq 0\}
+			S(i,d) = \{j \in J : j \neq i \text{ and }e_j'+2d \mid e_i+2d\}
 		\end{align*}
@@
 
-\begin{lem}
-\label{lem:admissible_subset}
-If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
-then $(\sx', W)$ is also admissible.
-\end{lem}
-
-\begin{proof}
-Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
-if they hold for $J$.
-\end{proof}
-
 \begin{thm}
 \label{thm:ramification_order_induction}
-Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
-curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
-R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
-Then the following are true:
+Suppose $(\sx', 0, L')$\todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
+curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
+as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
+following are true:
 \begin{enumerate}
@@
 		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
-			\neq y_{i,e_i},y_{i,e_i'} \rangle
+			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
+			y_{i,e_i},y_{i,e_i'} \rangle
 		\end{align*}
@@
 	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
-		products of two monomials and that for all $i \in J$, we have $e
-		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
-		minimal generators for $I'$ together with any set of relations as in 
-		part (c) minimally generate $I$.
+		products of two monomials and that for all $i \in J$, we have $e_i >
+		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
+		generators for $I'$ together with any set of relations as in part (c)
+		minimally generate $I$.
 	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
@@
 H^0(\sx,e_iL).
-\end{align*}
+\end{align*}\todo{Peter: should be $Q_i$?}
 
@@
 implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch, and so a general element
+Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
 \begin{align*}
@@
 
-Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
-$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
+Finally, if $(\sx,J)$ then so is $(\sx,W)$ for any $W \subset J$,
+since each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for
+$W$ if they hold for $J$.
 \end{proof}

### 2015-06-21 stacky_write_up/spin_cring.tex

--- 2015-06-21 stacky_write_up/spin_cring.tex
@@
 
+\todo{Peter: throughout this section I will provide a few notes of how we can generalize this to arbitrary genus with the appropriate conditions}
+
 In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
@@
 \begin{thm}
+
 \label{thm:ram_order_ind}
-Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
+Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
 curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in

### 2015-06-21 stacky_write_up/spin_cring.tex
edited generaliztion to higher genus

--- 2015-06-21 stacky_write_up/spin_cring.tex
@@
 Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
-defined by O'Dorney \todo{reference this-Section 1 of Evan's paper})
+defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
 satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
-generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by $
+generator $u$ in degree 1; let $u$ \todo{Was there supposed to be something else in this sentence?}.  Suppose $D$ is generated by $
 u, x_1, \ldots, x_m$ in degree at most $\delta$ with relations generated 
@@
 \ssec{Saturation}
-\label{ssec:g_0_saturation}
+\label{ssec:g_0_saturation} \todo{Define saturation}
 Here we compute saturation numbers. That is, given a list of
@@
 
-\todo{Something is a little fishy with this order, it seems
-something like: first grade by degree, then try to decrease the
-highest y, if you cant, try to decrease the highest z, possibly
-replace $z_5$ by $z_5+Cy_5$ to generic element?}
-
 \ssec{Inductive Theorem: Increasing the Ramification Orders}
@@
 		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq \# S_{\sigma, J}(i)
-		\end{align*}
+			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+		\end{align*}
+		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
 		where
 		\begin{align*}
-			S_{\sigma, J}(i) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i - e_j' \text{ for some } d \geq 0\}
+			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i + 2d\}
 		\end{align*}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
-			\frac{1}{\deg(y_{i,e_i'})e_j'}
+			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
+			\frac{1}{\deg(y_{i,e_i})e_j'}
 		\end{align*}
@@
 \begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 0
+	\deg \left( e_i L' - E_i \right) \geq 2g-1
 \end{align*}
@@
 	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
-	&\leq \frac{e_i-1}{2} + \deg z \left( \subhalf{e_i'} \right) -\frac{1}{e_i'} \\
-	& = \frac{e_i-1}{2}-\frac{1}{e_i'}+\left( \subhalf{e_i'} \right) \\
-	&= \frac{e_i(e_i-3)}{2(e_i-2)}+\left( \subhalf{e_i'} \right) \\
+	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
+	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
+	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
 	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
@@
 {\sf Case 3: $j \in S(i,0).$}
-In this case, we similarly obtain
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq  e_i \subhalf{e_j'} +
-	\deg z \subhalf{e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}
+
+In this case, we may first assume $z \neq y_{j,e_j}$, 
+as this is covered by case 2, with $i$ and $j$ reversed. 
+Hence, 
+\begin{align*}
+	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
+\end{align*}
+implying
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
+	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
+	= \deg (y_{i,e_i}z) \subhalf{e_j'},
 \end{align*}

### 2015-06-21 stacky_write_up/spin_cring.tex
added inductive lemma for genus > 0

@@
 
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points}
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
 \label{ssec:g_0_ram_pts}
@@
 \label{prop:sat_three_induction}
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably
-rooted log stacky curves $R \subset R'$
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$)}
-be the corresponding
-inclusion of canonical rings. Let $R_{D'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $D = \frac{1}{
-3}P$\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Make explicit assumptions on genus.}
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
+Actually, the map isn't ramified at $P$, it's just defined away from $P$.
+I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
+3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies 
+\begin{align*}
+	\ord_{x_3}(f) < \ord_{x_3}(g) \implies f \prec g.
+\end{align*}
+Then, the following statements hold.
+
+\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
 \todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
@@
 		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3,y_4,y_5]$ with $grlex$ so that $y_3 \prec 
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_3 \prec 
 		y_4 \prec y_5$
-		\todo{This order isn't quite right, we need $y_4^2 < y_5y_3$.}
-		and equip the ring $k[y_3,y_4,y_5,x]$ with the block 
-		order so that $R = k[y_3,y_4,y_5,x]/I$. Let,
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
+		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
 		\begin{align*}
@@
 \end{align}
-\todo{You need to say explicitly somewhere that $x_i$ lies in degree $i$; also for the higher genus case, we should replace $x_3, x_4, x_5$ with $x_2, x_3$ and everything should work the same.}
 
@@
 \section{Genus positive}
-We haven't done this.
+
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
+
+\begin{prop}
+\label{prop:sat_two_induction}
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be log stacky spin curves.
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature $\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
+, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
+3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$ Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
+\end{align*}
+Then, the following statements hold.
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_3 \prec 
+		y_4$
+		and equip the ring $k[y_3, y_4, x]$ with the block 
+		order so that $R = k[y_3, y_4, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x, y_3, y_4] \\
+			&+\langle y_4 x_j \mid 3 \leq j \leq m \rangle \\
+			&+\langle y_4^2.\rangle
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
+_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.}
+
+In a fashion analogous to the proof of Proposition 
+~\ref{prop:sat_three_induction}, we see 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:sat_two_add_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\rangle \\
+		&+\langle y_3^ay_4 \mid a \geq 0 \rangle,
+	\end{split}
+\end{align}
+
+\noindent completing part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B y_3^2 x_2 \\
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
 

### 2015-06-21 stacky_write_up/spin_cring.tex
more proof added to lemma 3.2

--- 2015-06-21 stacky_write_up/spin_cring.tex
@@
 Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
-defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
+defined by O'Dorney \todo{reference this-Section 1 of Evan's paper})
 satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
-generator $u$ in degree 1; let $u$ \todo{Was there supposed to be something else in this sentence?}.  Suppose $D$ is generated by $
+generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by $
 u, x_1, \ldots, x_m$ in degree at most $\delta$ with relations generated 
@@
 
-Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}}\le \frac{\alpha}{
+Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}} \le \frac{\alpha}{
 \beta}$ with $c>0$ is not a best lower approximation.  Then choose
@@
 \rfloor\ge c$.  Therefore, we can produce an element in $(R_{D'})_d$
- with pole degree $c$ at $P$ by either $y_i u^b$ or $y_j y_i u^b$
-where $d_j=1$ and if $d_i=1$ as well then $c_i=1$. Thus, for a
+ with pole degree $c$ at $P$ by either $y_i u^b$ or $z y_i u^b$ with $i>\lfloor \frac{\alpha}{\beta} \rfloor$, or $zu^b$
+for some $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1}$.  Thus, for a
 general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
@@
 construct an element in degree $d$ with pole degree $c$ by either $y
-_n^a y_i u^b$ or $y_n^a y_j y_iu^b$ with the latter satisfying the
+_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
 same conditions.  We notice that elements of this form are all
 linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$.  Thus $u,x_1,...,x_m,y_1,...,y_n$ generate
+$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
 $R_{D'}$.
 
-\todo{finish proof of relations, which follows easily using VZB's
-method; peter will do this tomorrow (sunday)}
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ corresponds to the best lower approximation $\frac{c_j}{d_j}$.
+Recall from the previous paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at $P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if $d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.
+Specifically, we can successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.
+For convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.
+In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the expression still makes sense; in such cases we will always choose $a_l=0$ so this choice is irrelevant, and only makes writing out cases more convenient.
+Therefore, we can write
+\[
+	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
+\]
+giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at the beginning}
+
+Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so $y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i u^0$).
+Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j+1} > c_j$.
+Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either $c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.
+Since $\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i+c_j$ we must have $d_h<d_i+d_j$.
+Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h + 1 \le d_i + d_j$.
+That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find (where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and $y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.
+From here we can follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P$ to find
+\[
+	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}u^{b_l}\in R_D
+\]
+implying a relation with initial term $y_i y_j$.
+
+Finally, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j+1}=1$ (i.e.
+$c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).
+If $i>1$ and then $y_{j+1}y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following the same method as the previous two paragraphs we find
+\[
+	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
+\]
+Similarly if $i=1$, then we get the same result using
+\[
+	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
+\]
+In both cases we deduce that $y_iy_j$ is an initial term of some relation.
+
+Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor \frac{\alpha}{\beta}\rfloor$.
+If $\beta=1$, then there are no relations with initial term a power of $y_i$ and we are immediately done.
+Otherwise, assuming $\beta\ne 1$, we note that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$.
+\todo{reference to Evan's paper where he proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the $d_{i+1}+1$ degree with pole order $c_{i+1}+1$.
+Following a similar technique to the previous paragraphs we find
+\[
+	(y_{i})^{c+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}
+\]
+
+Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial terms described in the previous paragraphs.
+We show that $J$ is in fact all of the initial ideal.
+Suppose $f$ is a non-constant monomial that does not lie within $J$.
+Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$.
+Then there is some $y_i|f$.
+Since $f\not\in j$, we cannot have some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.
+Furthermore, if $y_l|f$ for $l<i$, then we must have $d_l=1$.
+If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$, or else.
+We observe, that such elements are precisely
 
@@
 \ssec{Saturation}
-\label{ssec:g_0_saturation} \todo{Define saturation}
+\label{ssec:g_0_saturation}
 Here we compute saturation numbers. That is, given a list of
@@
 
+\todo{Something is a little fishy with this order, it seems
+something like: first grade by degree, then try to decrease the
+highest y, if you cant, try to decrease the highest z, possibly
+replace $z_5$ by $z_5+Cy_5$ to generic element?}
+
 \ssec{Inductive Theorem: Increasing the Ramification Orders}
@@
 		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
-		\end{align*}
-		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
+			\deg \lfloor e_i L \rfloor \geq \# S_{\sigma, J}(i)
+		\end{align*}
 		where
 		\begin{align*}
-			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i + 2d\}
+			S_{\sigma, J}(i) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i - e_j' \text{ for some } d \geq 0\}
 		\end{align*}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
-			\frac{1}{\deg(y_{i,e_i})e_j'}
+			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
+			\frac{1}{\deg(y_{i,e_i'})e_j'}
 		\end{align*}
@@
 \begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g-1
+	\deg \left( e_i L' - E_i \right) \geq 0
 \end{align*}
@@
 	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
-	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
+	&\leq \frac{e_i-1}{2} + \deg z \left( \subhalf{e_i'} \right) -\frac{1}{e_i'} \\
+	& = \frac{e_i-1}{2}-\frac{1}{e_i'}+\left( \subhalf{e_i'} \right) \\
+	&= \frac{e_i(e_i-3)}{2(e_i-2)}+\left( \subhalf{e_i'} \right) \\
 	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
@@
 {\sf Case 3: $j \in S(i,0).$}
-
-In this case, we may first assume $z \neq y_{j,e_j}$, 
-as this is covered by case 2, with $i$ and $j$ reversed. 
-Hence, 
-\begin{align*}
-	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
-\end{align*}
-implying
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
-	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
-	= \deg (y_{i,e_i}z) \subhalf{e_j'},
+In this case, we similarly obtain
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) &\leq  e_i \subhalf{e_j'} +
+	\deg z \subhalf{e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}
 \end{align*}

### 2015-06-21 stacky_write_up/spin_cring.tex
reintroduce e_i - e_j', index base cases
added more proof to section 3 main lemma

@@
 \newcommand \initial{\text{in}}
+\newcommand \gin{\text{gin}}
 
@@
 degree $d_i$ and has a pole at $P$ of degree $c_i$
+
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
@@
 										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: 1 \le i \le j \le n-1 \rangle.
-\end{align*}
-
-\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
+										 &+ \langle (y_i)^{\deg(y_{i+1})}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
 \end{itemize}
@@
 
-Let $0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-\beta}$ be the non-negative best lower approximation of $\frac{
+Let 
+\[
+	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+\beta}
+\] 
+be the non-negative best lower approximation of $\frac{
 \alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
@@
 by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)} <
-\frac{c_i}{d _i}$, so we have the pole order of this product is $
-\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_
-i\frac{c_i}{d_i} = c_i $. Thus, the elements of $R_{d_i}$
-
-For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction,
-so any product of $\prod z_i$ of elements of degrees less than $d_i$
- must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i} $, so we
-have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{
-\sum -\ord( z_i)} {\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.
-Thus, elements of $(R_{D'})d_i$ with pole order $c_i$ at $P$ are
-not generated by lower degrees; generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order (note that if $d_i=1$ then $-
-\ord_P(y_i)= \max(c_j:d_j=1)$ and if more than one $d_i$ is 1, we
+degrees less than $d_i$ must have 
+\[
+	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
+\]
+so we have the pole order of $\prod z_i$ is 
+\[
+	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
+\] 
+Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
+lower degrees.  
+Generically choose some $y_i \in(R_{
+D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
+\[
+	-\ord_P(y_i)= \max(c_j:d_j=1)
+\]
+and if more than one $d_i$ is 1, we
 must also choose them generically so they generate $(R_{D'})_1$).
 
-Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}} \le \frac{\alpha}{
-\beta}$ with $c>0$ is not a best lower approximation.  Then choose
+Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
+\beta}$ not a best lower approximation.  Then choose
 best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
 maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
-this we can deduce that $c_i+(d-d_i)\lfloor \frac{\alpha}{\beta}
-\rfloor\ge c$.  Therefore, we can produce an element in $(R_{D'})_d$
- with pole degree $c$ at $P$ by either $y_i u^b$ or $z y_i u^b$ with $i>\lfloor \frac{\alpha}{\beta} \rfloor$, or $zu^b$
-for some $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1}$.  Thus, for a
-general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+this we can deduce that 
+\[
+	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
+\]  
+Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
+has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
+\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
+where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+\rfloor + 1}$.  
+Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
 \frac{\alpha}{\beta}$ is not a best lower approximation than we can
@@
 
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ corresponds to the best lower approximation $\frac{c_j}{d_j}$.
-Recall from the previous paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at $P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if $d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.
-Specifically, we can successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.
-For convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.
-In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the expression still makes sense; in such cases we will always choose $a_l=0$ so this choice is irrelevant, and only makes writing out cases more convenient.
-Therefore, we can write
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
+corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
+paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
+$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
+$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
+successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
+\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
+\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
+convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
+with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
+is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
+expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
+is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
 \[
@@
 \]
-giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at the beginning}
-
-Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so $y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i u^0$).
-Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j+1} > c_j$.
-Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either $c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.
-Since $\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i+c_j$ we must have $d_h<d_i+d_j$.
-Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h + 1 \le d_i + d_j$.
-That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find (where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and $y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.
-From here we can follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P$ to find
-\[
-	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}u^{b_l}\in R_D
+giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
+the beginning}
+
+Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
+$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
+u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
++c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
++1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
+$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
+$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
+larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
++c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
+d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
+(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
+$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
+follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
+$ to find
+\[
+	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
+u^{b_l}\in R_D
 \]
@@
 
-Finally, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j+1}=1$ (i.e.
-$c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).
-If $i>1$ and then $y_{j+1}y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following the same method as the previous two paragraphs we find
+Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
++1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
+y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
+the same method as the previous two paragraphs we find
 \[
@@
 
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor \frac{\alpha}{\beta}\rfloor$.
-If $\beta=1$, then there are no relations with initial term a power of $y_i$ and we are immediately done.
-Otherwise, assuming $\beta\ne 1$, we note that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$.
-\todo{reference to Evan's paper where he proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the $d_{i+1}+1$ degree with pole order $c_{i+1}+1$.
-Following a similar technique to the previous paragraphs we find
-\[
-	(y_{i})^{c+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}
-\]
-
-Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial terms described in the previous paragraphs.
-We show that $J$ is in fact all of the initial ideal.
-Suppose $f$ is a non-constant monomial that does not lie within $J$.
-Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$.
-Then there is some $y_i|f$.
-Since $f\not\in j$, we cannot have some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.
-Furthermore, if $y_l|f$ for $l<i$, then we must have $d_l=1$.
-If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$, or else.
-We observe, that such elements are precisely
-
+Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
+\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
+power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
+that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
+proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
+$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
+previous paragraphs we find
+\[
+	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
+\]
+Similarly if $i=1$ then
+\[
+	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
+\]
+In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
+
+Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
+terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
+x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
+non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
+$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
+some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
+$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
+relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
+{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
+\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
+elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
+u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
+y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
+we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
+generic, this is in fact the generic initial ideal.
 \end{proof}
 
-\todo{lots of corollaries; peter can do this tomorrow}
+This yields some immediate corollaries:
+
+\begin{cor}
+
+\end{cor}
 

### 2015-06-21 stacky_write_up/spin_cring.tex
added missing L's in base cases
adding corollaries to section 3

@@
 
-Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+
-\Delta\sim -2\infty+ \Delta$ is a divisor of $X$ (i.e. with 
-possibly negative integer coefficients).  Since $\Delta$ is non-
-zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
-any point $P$ occurring in a stacky divisor of $\sx$ must have 
-coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
-s appearing in the characteristic of $(\sx,\Delta)$).
-
-Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
-coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
- must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
-\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
-is linearly equivalent to an effective $X$ divisor plus $\sum 
-\subhalf{i}P_i$.  We have now reduced to the case of $\halfcan$ 
-linearly equivalent to an effective divisor.  The result in this 
-specific case in fact generalizes to any $\mathbf{Q}$-divisor: $D=\sum
-\frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
-
 We will prove this by induction using methods analogous to ones of VZB\todo{add 
@@
 										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1})}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
 \end{align*}
@@
 \item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
 \end{itemize}
@@
 generic, this is in fact the generic initial ideal.
+
+\todo{Extend Lemma \ref{lem:minimal:quadratic} to commutative diagrams to show minimality}
 \end{proof}
 
+\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
+Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\delta,\beta)$ with relations generated in degree at most $\max(\tau,\delta+\beta,2\beta)$
+\end{rem}
+
 This yields some immediate corollaries:
 
+\begin{cor}\label{cor:effective_Q_divisor_can_ring}
+If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
+\end{cor}
+
+\begin{proof}
+We can prove this by induction.  As a base case, let $D\sim 0$.  Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
+Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i=1}^{r+1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
+By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
+Since $D$ is effective, the condition of equation \ref{eqn:deg1_sat_ind_dim} is met, so by remark \ref{rem:deg1_sat_ind_gen_rel_degrees} of lemma \ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
+\end{proof}
+
+\begin{cor}\label{cor:genus_0_posiive_delta}
+Let $\halfcan$ be a stacky log spin canonical divisor of signature $(0,e_1,...,e_n,\delta)$ with $\delta>0$.  Then 
+\end{cor}
+\begin{proof}
+Since $\halfcan$ is a half canonical divisor, 
+\[
+	2\halfcan=D+\sum \subhalf{i}P_i
+\] 
+where 
+\[
+	D\sim K_X+\Delta\sim -2\infty+ \Delta
+\] is a divisor of $X$ (i.e. with 
+possibly negative integer coefficients).  Since $\Delta$ is non-
+zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
+any point $P$ occurring in a stacky divisor of $\sx$ must have 
+coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+s appearing in the characteristic of $(\sx,\Delta)$).
+
+Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
+coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
+ must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
+\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
+is linearly equivalent to an effective $X$ divisor plus $\sum 
+\subhalf{i}P_i$.  We have thus shown $\halfcan$ is linearly equivalent to an effective divisor.  Thus, by \ref{cor:effective_Q_divisor_can_ring} the desired result follows.
+\end{proof}
+
 \begin{cor}
-
+Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
 \end{cor}
+\begin{proof}
+For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
+\end{proof}
+
+\todo{Add higher genus corollaries once we figure out what we want to say there}
 
@@
 	\hline
+	\hline
 
@@
 			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i + 2d\}
+			\mid e_i - e_j'\}
 		\end{align*}
@@
 \begin{enumerate}
-	\item[(a)] $\sigma = (0; 3, 3, 11; 0), J = \{3\}$
-	\item[(b)] $\sigma = (0; 3, 5, 9; 0), J = \{2, 3\}$
-	\item[(c)] $\sigma = (0; 5, 5, 7; 0), J = \{1, 2, 3\}$
-	\item[(d)] $\sigma = (0; 3, 3, 3, 5; 0), J = \{1, 2, 3, 4\}$
-	\item[(e)] $\sigma = (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$
+	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
+	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{2, 3\}$
+	\item[(c)] $\sigma_3 = (0; 5, 5, 7; 0), J_3 = \{1, 2, 3\}$
+	\item[(d)] $\sigma_4 = (0; 3, 3, 3, 5; 0), J_4 = \{1, 2, 3, 4\}$
+	\item[(e)] $\sigma_5 = (0; 3, 3, 3, 3, 3; 0), J_5 = \{1, 2, 3, 4, 5\}$
 \end{enumerate}
@@
 \begin{enumerate}
-	\item[(a)] $(\deg \lfloor e_3 \rfloor, \# S_{(\sigma, J)}(3)) = (1, 0)$
-
-	\item[(b)] $(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (1, 0)$ \\
-		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
-
-	\item[(c)] $(\deg \lfloor e_1 \rfloor, \#S_{(\sigma, J)}(1)) = (2, 1)$ \\
-		$(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (2, 1)$ \\
-		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
-
-	\item[(d)] $(\deg \lfloor e_i \rfloor, \#S_{(\sigma, J)}(i)) = (3, 1)$
-		for $i \neq 4$ \\
-		$(\deg \lfloor e_4 \rfloor, \#S_{(\sigma, J)}(4))	= (2, 0)$.
-
-	\item[(e)] $(\deg \lfloor e_i \rfloor, \#S_{(\sigma, J)}(1)) = (5, 0)$
-		for all $i \in J$.
+	\item[(a)] $(\deg \lfloor e_3 \rfloor, \max_{d \geq 0} \# S_{(
+		\sigma_1, J_1)}(3)) = (1, 0)$
+
+	\item[(b)] $(\deg \lfloor e_2 \rfloor, \max_{d \geq 0} \#S_{(
+		\sigma_2, J_2)}(2)) = (1, 0)$ \\
+		$(\deg \lfloor e_3 \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
+		= (1, 0)$
+
+	\item[(c)] $(\deg \lfloor e_1 \rfloor, \max_{d \geq 0}
+		\#S_{(\sigma_3, J_3)}(1)) = (2, 1)$ \\
+		$(\deg \lfloor e_2 \rfloor, \max_{d \geq 0}
+		\#S_{(\sigma_3, J_3)}(2)) = (2, 1)$ \\
+		$(\deg \lfloor e_3 \rfloor, \max_{d \geq 0}
+		\#S_{(\sigma_3, J_3)}(3)) = (1, 0)$
+
+	\item[(d)] $(\deg \lfloor e_i \rfloor, \max_{d \geq 0}
+		\#S_{(\sigma_4, J_4)}(i)) = (3, 1)$	for $i \neq 4$ \\
+		$(\deg \lfloor e_4 \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
+		= (2, 0)$.
+
+	\item[(e)] $(\deg \lfloor e_i \rfloor, \max_{d \geq 0}
+		\#S_{(\sigma_5, J_5)}(1)) = (5, 0)$	for all $i \in J$.
 \end{enumerate}

### 2015-06-21 stacky_write_up/spin_cring.tex
Moved lemma from section 4 to section 3 and made it more general

@@
 \usepackage{tikz}
+\usepackage{tikz-cd}
 \usetikzlibrary{matrix,arrows,decorations.pathmorphing}
@@
 
-We will prove this by induction using methods analogous to ones of VZB\todo{add 
-reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D
-\sim \frac{\alpha}{\beta} P$:
-\begin{lem}\label{lem:O'Dorney_1_point}
-Let 
-\[
-	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
-\] 
-be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}
-$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ 
-lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
+First we prove a nice result about minimal generation of ideals of relations:
+
+\begin{lem}
+\label{lem:minimal_quadratic}
+Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
+generated in degree 1 that are equipped with monomial ordering $\prec$.
+ Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
+rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
+\[
+	\begin{tikzcd}
+	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	\end{tikzcd}
+\]
+Further suppose that $I'$ is generated over $I$ by elements $f_1,
+\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
+is of the form $y_i$.  Then, the elements $f_i$ determine minimal
+generators for $I'$ over $I$.
 \end{lem}
+
 \begin{proof}
-See O'Dorney \todo{provide reference}.
+Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
+degree 1. Then,
+\[
+	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
+\]
+\[
+	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
+\]
+
+\noindent
+determines map of rings, no longer necessarily graded. 
+By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
+\[
+	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
+\]
+so
+\[
+	\dim_k (I'/I)_2=j.
+\]
+This implies any set of
+generators for $I$ must have at least $j$ elements. Since $f_1,
+\ldots, f_j$ is such a set, it is minimal.
 \end{proof}
-
-The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
-8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
+\begin{rem}\label{rem:minimal_quadratic_trivial_case}
+It will be useful to use lemma \ref{lem:minimal_quadratic} in the case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$ are $k$-minimal generators for $I'$ (over the trivial base vector space).
+\end{rem}
+
+We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
+reference} and O'Dorney\todo{reference}.
 
@@
 
-\todo{Extend Lemma \ref{lem:minimal:quadratic} to commutative diagrams to show minimality}
+In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
+\todo{What about $\frac{\alpha}{beta}>1$?}
 \end{proof}
@@
 \label{ssec:g_0_ram_pts}
-
-\begin{lem}
-\label{lem:minimal_quadratic}
-Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
-generated in degree 1, is equipped with a monomial ordering $\prec$.
- Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
-rings with kernel $I,$ such that $I$ is generated by elements $f_1,
-\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
-is of the form $x_k$. Then, the elements $f_i$ determine minimal
-generators for $I$.
-\end{lem}
-
-\begin{proof}
-Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
-degree 1. Then,
-\[
-	\phi : k[x_1, \ldots, x_n] \rightarrow B
-\]
-
-\noindent
-determines a map of rings, no longer necessarily graded. Consider
-the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
-\todo{This ordering isn't quite right. 
-We need to preserve the ordering on quadratic terms}
-By
-assumption, the kernel $I$ is generated by elements whose initial
-terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
-\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
-generators for $I$ must have at least $j$ elements. Since $f_1,
-\ldots, f_j$ is such a set, it is minimal.
-\end{proof}
 
@@
 \begin{enumerate}
-	\item[(a)] $(\deg \lfloor e_3 \rfloor, \max_{d \geq 0} \# S_{(
+	\item[(a)] $(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \# S_{(
 		\sigma_1, J_1)}(3)) = (1, 0)$
 
-	\item[(b)] $(\deg \lfloor e_2 \rfloor, \max_{d \geq 0} \#S_{(
+	\item[(b)] $(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0} \#S_{(
 		\sigma_2, J_2)}(2)) = (1, 0)$ \\
-		$(\deg \lfloor e_3 \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
+		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
 		= (1, 0)$
 
-	\item[(c)] $(\deg \lfloor e_1 \rfloor, \max_{d \geq 0}
+	\item[(c)] $(\deg \lfloor e_1 L \rfloor, \max_{d \geq 0}
 		\#S_{(\sigma_3, J_3)}(1)) = (2, 1)$ \\
-		$(\deg \lfloor e_2 \rfloor, \max_{d \geq 0}
+		$(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0}
 		\#S_{(\sigma_3, J_3)}(2)) = (2, 1)$ \\
-		$(\deg \lfloor e_3 \rfloor, \max_{d \geq 0}
+		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0}
 		\#S_{(\sigma_3, J_3)}(3)) = (1, 0)$
 
-	\item[(d)] $(\deg \lfloor e_i \rfloor, \max_{d \geq 0}
+	\item[(d)] $(\deg \lfloor e_i  L \rfloor, \max_{d \geq 0}
 		\#S_{(\sigma_4, J_4)}(i)) = (3, 1)$	for $i \neq 4$ \\
-		$(\deg \lfloor e_4 \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
+		$(\deg \lfloor e_4 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
 		= (2, 0)$.
 
-	\item[(e)] $(\deg \lfloor e_i \rfloor, \max_{d \geq 0}
+	\item[(e)] $(\deg \lfloor e_i L \rfloor, \max_{d \geq 0}
 		\#S_{(\sigma_5, J_5)}(1)) = (5, 0)$	for all $i \in J$.

### 2015-06-21 stacky_write_up/spin_cring.tex
redo tables with new base cases

@@
 so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$.
-Then $R(\sx', \Delta, L')$ is generated as a $k$-algebra by elements of
-degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at
-most $2e$ and $(\sx', J)$ is admissible for the following cases:
+Then $R' := R(\sx', \Delta, L')$ is generated as a $k$-algebra by elements
+of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree
+at most $2e$ and $(\sx', J)$ is admissible for the following cases:
 
@@
 	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
-	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{2, 3\}$
-	\item[(c)] $\sigma_3 = (0; 5, 5, 7; 0), J_3 = \{1, 2, 3\}$
-	\item[(d)] $\sigma_4 = (0; 3, 3, 3, 5; 0), J_4 = \{1, 2, 3, 4\}$
-	\item[(e)] $\sigma_5 = (0; 3, 3, 3, 3, 3; 0), J_5 = \{1, 2, 3, 4, 5\}$
+	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
+	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
+	\item[(d)] $\sigma_4 = (0; 5, 7, 7; 0), J_4 = \{2, 3\}$
+	\item[(e)] $\sigma_5 = (0; 7, 7, 7; 0), J_5 = \{1, 2, 3\}$
+	\item[(f)] $\sigma_6 = (0; 3, 3, 3, 5; 0), J_6 = \{4\}$
+	\item[(g)] $\sigma_7 = (0; 3, 3, 5, 5; 0), J_7 = \{3, 4\}$
+	\item[(h)] $\sigma_8 = (0; 3, 5, 5, 5; 0), J_8 = \{2, 3, 4\}$
+	\item[(i)] $\sigma_9 = (0; 5, 5, 5, 5; 0), J_9 = \{1, 2, 3, 4\}$
+	\item[(j)] $\sigma_{10} = (0; 3, 3, 3, 3, 3; 0), J_{10} = \{1, 2, 3, 4, 5\}$
 \end{enumerate}
@@
 comparing pole orders at each ramification point $P_i$ gives the
-generator and relation degrees. Note that (Ad-i) always holds.
+generator and relation degrees.
+
+The following table demonstrates that $R(\sx', \Delta, L')$ is
+generated as a $k$-algebra by elements of degree at most $e$
+with relations in degree at most $2e$ for each case. Also note
+that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
+and any generator $z$ of $R'$.
+
+\begin{longtable}
+	{| c || c | c | c |}
+	\hline
+	Case & Generator Degrees & Minimal Relation Degrees & $e$\\
+	\hline
+	\hline
+
+	(a) & \{3, 7, 9, 11\} & \{14, 18\} & 11\\	\hline
+
+	(b) & \{3, 5, 7, 9\} & \{12, 14\}	& 9\\ \hline
+
+	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
+
+	(d) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline
+
+	(e) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline
+
+	(f) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline
+
+	(g) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline
+
+	(h) & \{3, 3, 4, 5, 5, 5\} &
+	\{8, 8, 8, 9, 9, 9, 10, 10, 10\} & 5\\ \hline
+
+	(i) & \{3, 3, 4, 5, 5, 5, 5\} &
+	\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\} & 5\\ \hline
+
+	(j) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
+\end{longtable}
+
+\begin{center}
+\textbf{Table (II)}: Genus 0 noneffective base cases generator/relations
+\end{center}
+
+Note that (Ad-i) always holds.
 In each case we can also pick a set of generators such that
@@
 
-The following table demonstrates that $R(\sx', \Delta, L')$ is
-generated as a $k$-algebra by elements of degree at most $e$
-with relations in degree at most $2e$ for each case.
+Furthermore, each case satisfies (Ad-iii) as demonstrated below.
+Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
+for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i L
+\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$ are
+independent of the choice of $i$.
 
 \begin{longtable}
-	{| c || c | c | c |}
-	\hline
-	Case & Generator Degrees & Minimal Relation Degrees & $e$\\
-	\hline
-	\hline
-
-	(a) & \{3, 7, 9, 11\} & \{14, 18\} & 11\\	\hline
-
-	(b) & \{3, 5, 7, 9\} & \{12, 14\}	& 9\\ \hline
-
-	(c) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
-
-	(d) & \{3, 3, 4, 5\} & \{8,	9\} & 5\\ \hline
-
-	(e) & \{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
+	{| c | c || c | c | c |}
+	\hline
+	$\sigma$ & $J$ &  $i$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
+	\hline
+	\hline
+
+	$(0; 3, 3, 11; 0)$ & $\{3\}$ & $\forall i \in J$ & 1 & 0\\	\hline
+
+	$(0; 3, 7, 7; 0)$ & $\{3\}$ & $\forall i \in J$ & 2 & 0\\ \hline
+
+	$(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $\forall i \in J$ & 2 & 0\\ \hline
+
+	$(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $\forall i \in J$ & 3 & 0\\ \hline
+
+	$(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $\forall i \in J$ & 2 & 0\\ \hline
+
+	$(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $\forall i \in J$ & 3 & 0\\ \hline
+
+	$(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $\forall i \in J$ & 4 & 0\\ \hline
+
+	$(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $\forall i \in J$ & 5 & 0\\ \hline
+
+	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $\forall i \in J$ & 5 & 0\\ \hline
 \end{longtable}
@@
 \begin{center}
-\textbf{Table (II)}: Genus 0 noneffective base cases
+\textbf{Table (III)}: Genus 0 noneffective base cases (Ad-iii)
 \end{center}
 
-Furthermore, each case satisfies (Ad-iii) as demonstrated below.
-
-\begin{enumerate}
-	\item[(a)] $(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \# S_{(
-		\sigma_1, J_1)}(3)) = (1, 0)$
-
-	\item[(b)] $(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0} \#S_{(
-		\sigma_2, J_2)}(2)) = (1, 0)$ \\
-		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
-		= (1, 0)$
-
-	\item[(c)] $(\deg \lfloor e_1 L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_3, J_3)}(1)) = (2, 1)$ \\
-		$(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_3, J_3)}(2)) = (2, 1)$ \\
-		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_3, J_3)}(3)) = (1, 0)$
-
-	\item[(d)] $(\deg \lfloor e_i  L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_4, J_4)}(i)) = (3, 1)$	for $i \neq 4$ \\
-		$(\deg \lfloor e_4 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
-		= (2, 0)$.
-
-	\item[(e)] $(\deg \lfloor e_i L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_5, J_5)}(1)) = (5, 0)$	for all $i \in J$.
-\end{enumerate}
+Thus, we have admissibility of $(\sx', J)$ in each of these cases.
 
 Finally, each case also satisfies the property that $in_\prec(I')$ is
-minimally generated by products of two monomials and that for all
-$i \in J$, we have $e_i > \deg z$ for any generator $z$ of $R'.$
+minimally generated by products of two monomials.
 \todo{prove}
@@
 \begin{center}
-\textbf{Table (III)}: Genus 0 exceptional cases
+\textbf{Table (IV)}: Genus 0 exceptional cases
 \end{center}

### 2015-06-21 stacky_write_up/spin_cring.tex
add additional hypotheses to base case lemma

@@
 \begin{thm}
-
 \label{thm:ram_order_ind}
@@
 \end{enumerate}
+
+\noindent
+Furthermore, $R'$ satisfies the hypothesis of Theorem ~\ref
+{thm:ram_order_ind}(d), which asserts that for all $i \in J$, $e_i >
+\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
+(as defined in Theorem ~\ref{thm:ram_order_ind}(c)) then
+$in_\prec(I')$ is minimally generated by products of two monomials.
 \end{lem}
@@
 for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i L
-\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$ are
+\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ are
 independent of the choice of $i$.

### 2015-06-22 stacky_write_up/spin_cring.tex
changed g to h

--- 2015-06-21 stacky_write_up/spin_cring.tex
@@
 \usepackage{tikz}
-\usepackage{tikz-cd}
 \usetikzlibrary{matrix,arrows,decorations.pathmorphing}
@@
 \newcommand \initial{\text{in}}
-\newcommand \gin{\text{gin}}
 
@@
 
-First we prove a nice result about minimal generation of ideals of relations:
-
-\begin{lem}
-\label{lem:minimal_quadratic}
-Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-generated in degree 1 that are equipped with monomial ordering $\prec$.
- Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
+Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+
+\Delta\sim -2\infty+ \Delta$ is a divisor of $X$ (i.e. with 
+possibly negative integer coefficients).  Since $\Delta$ is non-
+zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
+any point $P$ occurring in a stacky divisor of $\sx$ must have 
+coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+s appearing in the characteristic of $(\sx,\Delta)$).
+
+Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
+coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
+ must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
+\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
+is linearly equivalent to an effective $X$ divisor plus $\sum 
+\subhalf{i}P_i$.  We have now reduced to the case of $\halfcan$ 
+linearly equivalent to an effective divisor.  The result in this 
+specific case in fact generalizes to any $\mathbf{Q}$-divisor: $D=\sum
+\frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.
+
+We will prove this by induction using methods analogous to ones of VZB\todo{add 
+reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D
+\sim \frac{\alpha}{\beta} P$:
+\begin{lem}\label{lem:O'Dorney_1_point}
+Let 
 \[
-	\begin{tikzcd}
-	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	\end{tikzcd}
+	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
 \] 
-Further suppose that $I'$ is generated over $I$ by elements $f_1,
-\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
-is of the form $y_i$.  Then, the elements $f_i$ determine minimal
-generators for $I'$ over $I$.
+be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}
+$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ 
+lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
 \end{lem}
-
 \begin{proof}
-Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-degree 1. Then,
-\[
-	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-\]
-\[
-	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-\]
-
-\noindent
-determines map of rings, no longer necessarily graded. 
-By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
-\[
-	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-\]
-so
-\[
-	\dim_k (I'/I)_2=j.
-\]
-This implies any set of
-generators for $I$ must have at least $j$ elements. Since $f_1,
-\ldots, f_j$ is such a set, it is minimal.
+See O'Dorney \todo{provide reference}.
 \end{proof}
-\begin{rem}\label{rem:minimal_quadratic_trivial_case}
-It will be useful to use lemma \ref{lem:minimal_quadratic} in the case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$ are $k$-minimal generators for $I'$ (over the trivial base vector space).
-\end{rem}
-
-We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
-reference} and O'Dorney\todo{reference}.
+
+The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
+8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.
 
@@
 degree $d_i$ and has a pole at $P$ of degree $c_i$
-
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
@@
 										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
-										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
-\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
+										 &+ \langle y_i y_j: 1 \le i \le j \le n-1 \rangle.
+\end{align*}
+
+\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
 \end{itemize}
@@
 
-Let 
-\[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-\beta}
-\] 
-be the non-negative best lower approximation of $\frac{
+Let $0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+\beta}$ be the non-negative best lower approximation of $\frac{
 \alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
@@
 by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have 
-\[
-	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
-\]
-so we have the pole order of $\prod z_i$ is 
-\[
-	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
-\] 
-Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees.  
-Generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
-\[
-	-\ord_P(y_i)= \max(c_j:d_j=1)
-\]
-and if more than one $d_i$ is 1, we
+degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)} <
+\frac{c_i}{d _i}$, so we have the pole order of this product is $
+\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_
+i\frac{c_i}{d_i} = c_i $. Thus, the elements of $R_{d_i}$
+
+For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction,
+so any product of $\prod z_i$ of elements of degrees less than $d_i$
+ must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i} $, so we
+have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{
+\sum -\ord( z_i)} {\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.
+Thus, elements of $(R_{D'})d_i$ with pole order $c_i$ at $P$ are
+not generated by lower degrees; generically choose some $y_i \in(R_{
+D'})_{d_i}$ to have maximal pole order (note that if $d_i=1$ then $-
+\ord_P(y_i)= \max(c_j:d_j=1)$ and if more than one $d_i$ is 1, we
 must also choose them generically so they generate $(R_{D'})_1$).
 
-Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ not a best lower approximation.  Then choose
+Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}}\le \frac{\alpha}{
+\beta}$ with $c>0$ is not a best lower approximation.  Then choose
 best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
 maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
-this we can deduce that 
-\[
-	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
-\]  
-Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
-has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
-\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
-where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
-\rfloor + 1}$.  
-Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+this we can deduce that $c_i+(d-d_i)\lfloor \frac{\alpha}{\beta}
+\rfloor\ge c$.  Therefore, we can produce an element in $(R_{D'})_d$
+ with pole degree $c$ at $P$ by either $y_i u^b$ or $y_j y_i u^b$
+where $d_j=1$ and if $d_i=1$ as well then $c_i=1$. Thus, for a
+general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
 \frac{\alpha}{\beta}$ is not a best lower approximation than we can
 construct an element in degree $d$ with pole degree $c$ by either $y
-_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
+_n^a y_i u^b$ or $y_n^a y_j y_iu^b$ with the latter satisfying the
 same conditions.  We notice that elements of this form are all
 linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
+$R_{D'}$ over $R_D$.  Thus $u,x_1,...,x_m,y_1,...,y_n$ generate
 $R_{D'}$.
 
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
-corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
-paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
-$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
-$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
-successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
-convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
-expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
-is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
-\[
-	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-\]
-giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
-the beginning}
-
-Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
-$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
-u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
-+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
-+1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
-$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
-$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
-larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
-+c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
-d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
-(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
-$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
-follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
-$ to find
-\[
-	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-u^{b_l}\in R_D
-\]
-implying a relation with initial term $y_i y_j$.
-
-Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
-+1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
-y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
-the same method as the previous two paragraphs we find
-\[
-	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-\]
-Similarly if $i=1$, then we get the same result using
-\[
-	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
-\]
-In both cases we deduce that $y_iy_j$ is an initial term of some relation.
-
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
-\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
-power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
-that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
-proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
-$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
-previous paragraphs we find
-\[
-	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-\]
-Similarly if $i=1$ then
-\[
-	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
-\]
-In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
-
-Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
-terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
-x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
-non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
-$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
-some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
-$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
-relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
-{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
-\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
-elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
-u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
-y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
-we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
-generic, this is in fact the generic initial ideal.
-
-In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
-\todo{What about $\frac{\alpha}{beta}>1$?}
+\todo{finish proof of relations, which follows easily using VZB's
+method; peter will do this tomorrow (sunday)}
+
 \end{proof}
 
-\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
-Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\delta,\beta)$ with relations generated in degree at most $\max(\tau,\delta+\beta,2\beta)$
-\end{rem}
-
-This yields some immediate corollaries:
-
-\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
-\end{cor}
-
-\begin{proof}
-We can prove this by induction.  As a base case, let $D\sim 0$.  Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
-Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i=1}^{r+1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
-By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
-Since $D$ is effective, the condition of equation \ref{eqn:deg1_sat_ind_dim} is met, so by remark \ref{rem:deg1_sat_ind_gen_rel_degrees} of lemma \ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
-\end{proof}
-
-\begin{cor}\label{cor:genus_0_posiive_delta}
-Let $\halfcan$ be a stacky log spin canonical divisor of signature $(0,e_1,...,e_n,\delta)$ with $\delta>0$.  Then 
-\end{cor}
-\begin{proof}
-Since $\halfcan$ is a half canonical divisor, 
-\[
-	2\halfcan=D+\sum \subhalf{i}P_i
-\] 
-where 
-\[
-	D\sim K_X+\Delta\sim -2\infty+ \Delta
-\] is a divisor of $X$ (i.e. with 
-possibly negative integer coefficients).  Since $\Delta$ is non-
-zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
-any point $P$ occurring in a stacky divisor of $\sx$ must have 
-coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
-s appearing in the characteristic of $(\sx,\Delta)$).
-
-Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
-coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
- must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
-\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
-is linearly equivalent to an effective $X$ divisor plus $\sum 
-\subhalf{i}P_i$.  We have thus shown $\halfcan$ is linearly equivalent to an effective divisor.  Thus, by \ref{cor:effective_Q_divisor_can_ring} the desired result follows.
-\end{proof}
-
-\begin{cor}
-Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
-\end{cor}
-\begin{proof}
-For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
-\end{proof}
-
-\todo{Add higher genus corollaries once we figure out what we want to say there}
+\todo{lots of corollaries; peter can do this tomorrow}
 
@@
 	\hline
-	\hline
 
@@
 \label{ssec:g_0_ram_pts}
+
+\begin{lem}
+\label{lem:minimal_quadratic}
+Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
+generated in degree 1, is equipped with a monomial ordering $\prec$.
+ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
+rings with kernel $I,$ such that $I$ is generated by elements $f_1,
+\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
+is of the form $x_k$. Then, the elements $f_i$ determine minimal
+generators for $I$.
+\end{lem}
+
+\begin{proof}
+Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
+degree 1. Then,
+\[
+	\phi : k[x_1, \ldots, x_n] \rightarrow B
+\]
+
+\noindent
+determines a map of rings, no longer necessarily graded. Consider
+the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
+\todo{This ordering isn't quite right. 
+We need to preserve the ordering on quadratic terms}
+By
+assumption, the kernel $I$ is generated by elements whose initial
+terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
+\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
+generators for $I$ must have at least $j$ elements. Since $f_1,
+\ldots, f_j$ is such a set, it is minimal.
+\end{proof}
 
@@
 \begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(g) \implies f \prec g.
+	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
 \end{align*}
@@
 			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i - e_j'\}
+			\mid e_i + 2d\}
 		\end{align*}
@@
 \begin{enumerate}
-	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
-	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{2, 3\}$
-	\item[(c)] $\sigma_3 = (0; 5, 5, 7; 0), J_3 = \{1, 2, 3\}$
-	\item[(d)] $\sigma_4 = (0; 3, 3, 3, 5; 0), J_4 = \{1, 2, 3, 4\}$
-	\item[(e)] $\sigma_5 = (0; 3, 3, 3, 3, 3; 0), J_5 = \{1, 2, 3, 4, 5\}$
+	\item[(a)] $\sigma = (0; 3, 3, 11; 0), J = \{3\}$
+	\item[(b)] $\sigma = (0; 3, 5, 9; 0), J = \{2, 3\}$
+	\item[(c)] $\sigma = (0; 5, 5, 7; 0), J = \{1, 2, 3\}$
+	\item[(d)] $\sigma = (0; 3, 3, 3, 5; 0), J = \{1, 2, 3, 4\}$
+	\item[(e)] $\sigma = (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$
 \end{enumerate}
@@
 \begin{enumerate}
-	\item[(a)] $(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \# S_{(
-		\sigma_1, J_1)}(3)) = (1, 0)$
-
-	\item[(b)] $(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0} \#S_{(
-		\sigma_2, J_2)}(2)) = (1, 0)$ \\
-		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
-		= (1, 0)$
-
-	\item[(c)] $(\deg \lfloor e_1 L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_3, J_3)}(1)) = (2, 1)$ \\
-		$(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_3, J_3)}(2)) = (2, 1)$ \\
-		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_3, J_3)}(3)) = (1, 0)$
-
-	\item[(d)] $(\deg \lfloor e_i  L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_4, J_4)}(i)) = (3, 1)$	for $i \neq 4$ \\
-		$(\deg \lfloor e_4 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
-		= (2, 0)$.
-
-	\item[(e)] $(\deg \lfloor e_i L \rfloor, \max_{d \geq 0}
-		\#S_{(\sigma_5, J_5)}(1)) = (5, 0)$	for all $i \in J$.
+	\item[(a)] $(\deg \lfloor e_3 \rfloor, \# S_{(\sigma, J)}(3)) = (1, 0)$
+
+	\item[(b)] $(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (1, 0)$ \\
+		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
+
+	\item[(c)] $(\deg \lfloor e_1 \rfloor, \#S_{(\sigma, J)}(1)) = (2, 1)$ \\
+		$(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (2, 1)$ \\
+		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
+
+	\item[(d)] $(\deg \lfloor e_i \rfloor, \#S_{(\sigma, J)}(i)) = (3, 1)$
+		for $i \neq 4$ \\
+		$(\deg \lfloor e_4 \rfloor, \#S_{(\sigma, J)}(4))	= (2, 0)$.
+
+	\item[(e)] $(\deg \lfloor e_i \rfloor, \#S_{(\sigma, J)}(1)) = (5, 0)$
+		for all $i \in J$.
 \end{enumerate}

### 2015-06-22 stacky_write_up/spin_cring.tex
add missing base case 3, 5, 7; added neves to bib
minimal quadratic generators

--- 2015-06-21 stacky_write_up/spin_cring.tex
@@
 
+\todo{Include one of the following, if the first one, include a remark for quotient}
 \begin{lem}
 \label{lem:minimal_quadratic}
+Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
+generated in degree 1, is equipped with a monomial ordering $\prec$.
+ Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
+rings with kernel $I,$ such that $I$ is generated by elements $f_1,
+\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
+is of the form $x_k$. Then, the elements $f_i$ determine minimal
+generators for $I$.
+\end{lem}
+\begin{proof}
+Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
+degree 1. Then,
+\[
+	\phi : k[x_1, \ldots, x_n] \rightarrow B
+\]
+\noindent
+determines a map of rings, no longer necessarily graded. Consider
+the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
+\todo{This ordering isn't quite right. 
+We need to preserve the ordering on quadratic terms}
+By
+assumption, the kernel $I$ is generated by elements whose initial
+terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
+\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
+generators for $I$ must have at least $j$ elements. Since $f_1,
+\ldots, f_j$ is such a set, it is minimal.
+\end{proof}
+
+\iffalse
+\begin{lem}
+\label{lem:minimal_quadratic_2}
 Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
@@
 \end{proof}
+\fi
+
 \begin{rem}\label{rem:minimal_quadratic_trivial_case}
@@
 Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be log stacky spin curves. 
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature $\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
+$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
 Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
 , x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
-3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$ Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
 \begin{align*}

### 2015-06-22 stacky_write_up/spin_cring.tex
produced outline, reordered paper with filler intro

@@
 This is our project.
+Modular Forms.
+
 Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
 and O'Dorney's paper \cite{dorney:canonical}.
+
 We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.
@@
 \section{Background}
+Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
 \todo{edit this}
+
+\subsection{Definitions}
 Here are some definitions.
-Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
-
-\section{Effective Genus Zero Spin Divisors}
-\label{sec:g_0_effective}
-In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
-when $\Delta$ is a non- zero effective divisor.  Using this, we can 
-reduce to looking at effective stacky divisors.  Then, applying a 
-result for general effective $\mathbf{Q}$ divisors, we deduce that $
-R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
-relations generated up to degree $2e$ with initial terms quadratic 
-in the generators.  We also demonstrate that these bounds are tight 
-up to \todo{insert how tight they are}.
-
+
+\begin{defn}
+\textbf{Saturations} of the canonical divisor, as defined in 7.
+2 of VZB \cite{vzb:stacky}.
+\end{defn}
+
+\section{General Lemmata}
+First we present the general inductive lemmata that will be applied
+for all genera.
+
+\ssec{General: quadratic initial ideal minimal relations}
 First we prove a nice result about minimal generation of ideals of relations:
@@
 
-\iffalse
+%
+%\begin{lem}
+%\label{lem:minimal_quadratic_2}
+%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
+%generated in degree 1 that are equipped with monomial ordering $\prec$.
+ %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
+%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
+%\[
+	%\begin{tikzcd}
+	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	%\end{tikzcd}
+%\]
+%Further suppose that $I'$ is generated over $I$ by elements $f_1,
+%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
+%is of the form $y_i$.  Then, the elements $f_i$ determine minimal
+%generators for $I'$ over $I$.
+%\end{lem}
+%
+%\begin{proof}
+%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
+%degree 1. Then,
+%\[
+	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
+%\]
+%\[
+	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
+%\]
+%
+%
+%\noindent
+%determines map of rings, no longer necessarily graded. 
+%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
+%\[
+	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
+%\]
+%so
+%\[
+	%\dim_k (I'/I)_2=j.
+%\]
+%This implies any set of
+%generators for $I$ must have at least $j$ elements. Since $f_1,
+%\ldots, f_j$ is such a set, it is minimal.
+%\end{proof}
+%
+
+\begin{rem}\label{rem:minimal_quadratic_trivial_case}
+It will be useful to use lemma \ref{lem:minimal_quadratic} in the
+case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
+are $k$-minimal generators for $I'$ (over the trivial base vector
+space).  
+\end{rem}
+
+TRANSITION
+\todo{transition!}
+
+\ssec{Inductive Theorem: Increasing the Ramification Orders}
+\label{ssec:g_0_ram_orders}
+In this section, we aim to prove the inductive theorem, Theorem
+~\ref{thm:ram_order_ind}. Under fairly general
+conditions, this theorem will allow us to show that if Theorem ~\ref
+{thm:ram_order_ind} holds for a curve with signature
+$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
+signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
+
+\begin{defn}
+\label{defn:admissible}
+Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
+separably rooted log stacky spin
+curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
+there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
+\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
+
+$$\chi_J(i) = \begin{cases}
+	1, &\text{ if }i \in J\\
+	0, &\text{ otherwise. } 
+\end{cases}$$
+
+Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
+{\bf admissible} if the following three conditions hold.  \todo{Peter: We should make the definition of admissibility be a condition for the triple: $(\sx',\sx,J)$.}
+
+\begin{enumerate}
+	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
+		\in R'$ so that $R'$ admits a presentation
+		\begin{align*}
+			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
+		\end{align*}
+		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
+		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
+	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
+		of $R'$ satisfies
+		\begin{align*}
+			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[(Ad-iii)] For all $i \in J$ we have
+		\begin{align*}
+			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+		\end{align*}
+		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
+		where
+		\begin{align*}
+			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i - e_j'\}
+		\end{align*}
+\end{enumerate}
+\end{defn}
+
 \begin{lem}
-\label{lem:minimal_quadratic_2}
-Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-generated in degree 1 that are equipped with monomial ordering $\prec$.
- Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
-\[
-	\begin{tikzcd}
-	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	\end{tikzcd}
-\]
-Further suppose that $I'$ is generated over $I$ by elements $f_1,
-\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
-is of the form $y_i$.  Then, the elements $f_i$ determine minimal
-generators for $I'$ over $I$.
+\label{lem:admissible_inequality}
+Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
+stronger condition that
+
+\begin{align*}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
+\end{align*}
 \end{lem}
@@
 \begin{proof}
-Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-degree 1. Then,
-\[
-	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-\]
-\[
-	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-\]
-
-\noindent
-determines map of rings, no longer necessarily graded. 
-By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
-\[
-	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-\]
-so
-\[
-	\dim_k (I'/I)_2=j.
-\]
-This implies any set of
-generators for $I$ must have at least $j$ elements. Since $f_1,
-\ldots, f_j$ is such a set, it is minimal.
+We know by (Ad-ii) that
+
+\begin{align*}
+	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
+\end{align*}
+
+\noindent
+If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
+as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
+e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
+we must have
+
+\begin{align*}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
+	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
+\end{align*}
 \end{proof}
-\fi
-
-\begin{rem}\label{rem:minimal_quadratic_trivial_case}
-It will be useful to use lemma \ref{lem:minimal_quadratic} in the case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$ are $k$-minimal generators for $I'$ (over the trivial base vector space).
-\end{rem}
+
+\begin{lem}
+\label{lem:admissible_subset}
+If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
+then $(\sx', W)$ is also admissible.
+\end{lem}
+
+\begin{proof}
+Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
+if they hold for $J$.
+\end{proof}
+
+\begin{thm}
+\label{thm:ram_order_ind}
+Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
+curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
+R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
+Then the following are true:
+\begin{enumerate}
+	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
+		H^0(\sx, e_i(K_\sx))$ so that
+		\begin{align*}
+			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
+		\end{align*}
+		and
+		\begin{align*}
+			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
+			\frac{1}{\deg(y_{i,e_i})e_j'}
+		\end{align*}
+		for all $j \in J$ with $j \neq i$.
+	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
+		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
+		generate $R$ over $R'$.
+	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
+		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
+		block order. Let $R = k[y,x]/I.$ Then,
+		\begin{align*}
+			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
+			\neq y_{i,e_i},y_{i,e_i'} \rangle
+		\end{align*}
+		as $z$ ranges over all generators of $R$.
+	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
+		products of two monomials and that for all $i \in J$, we have $e
+		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
+		minimal generators for $I'$ together with any set of relations as in 
+		part (c) minimally generate $I$.
+	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
+\end{enumerate}
+\end{thm}
+
+\begin{proof}
+Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
+question, with coarse spaces $X = X'$. 
+\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
+Define
+
+\begin{align*}
+	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+\end{align*}
+
+\noindent
+Define
+\begin{align*}
+	E_i = \sum_{j \in S(i,0)}^{}Q_j
+\end{align*}
+
+\noindent
+Note that
+\begin{align*}
+	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
+\end{align*}
+
+\noindent
+and so we obtain an inclusion
+\begin{align*}
+	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
+H^0(\sx,e_iL).
+\end{align*}\todo{Peter: should be $Q_i$?}
+
+\noindent
+The assumption (Ad-iii) implies
+\begin{align*}
+	\deg \left( e_i L' - E_i \right) \geq 2g-1
+\end{align*}
+
+\noindent
+implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
+Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
+\begin{align*}
+	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
+\end{align*}
+
+\noindent
+satisfies
+\begin{align*}
+	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
+	\frac{e_i - 1}{2}
+\end{align*}
+
+\noindent
+Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
+
+We next show $y_{i,e_i}$ also satisfies the second part of the
+claim of $(a),$ by considering separately the cases of whether $j
+\in S(i,0),$ and $j \notin S(i,0)$.
+
+If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
+(\sx',e_iL'-E_i + Q_i)$,
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
+	\subhalf{e_j'} - \frac{1}{e_j'}.
+\end{align*}
+
+If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
+$e_i\subhalf{e_j'} \notin \BZ$, so
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
+\end{align*}
+
+\noindent
+completing the proof of (a).
+
+Next, define $R_0 = R'$ and inductively define 
+$$R_i = \begin{cases}
+	R_{i-1} &\text{ if }i \notin J\\
+	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
+\end{cases}$$
+
+\noindent
+To prove (b), it suffices to show that elements of the form $y_{i,e_
+i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
+and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
+vector space. These elements do not lie in $R_{i-1}$ because their
+order of pole at $Q_i$ is bigger than the order of any element in $R
+_{i-1}$, and are linearly independent amongst themselves because of
+injectivity of the linear map
+
+\begin{align*}
+	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
+	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
+	\begin{pmatrix}
+		e_i-2 & \frac{e_i-3}{2} \\
+		e_i	 & \frac{e_i-1}{2}
+	\end{pmatrix} 
+\end{align*}
+
+\noindent
+The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
+b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
+integer lattice points in the cone generated by the vectors $\left(e
+_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
+\right)$ is saturated, as the corresponding determinant is
+\begin{align*}
+	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
+\end{align*}
+completing part (b).
+
+To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
+i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
+all $j \in J$ we have
+\begin{align*}
+	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
+\end{align*}
+
+\noindent
+We now check this in three cases, depending on whether $j \notin \{
+i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
+
+\vskip.1in
+\noindent
+{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
+
+Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
+	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
+\end{align*}
+
+\vskip.1in
+\noindent
+{\sf Case 2: $j =i.$}
+
+By part (a), condition (Ad-ii), and Lemma
+~\ref{lem:admissible_inequality} we have
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
+	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
+	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
+	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
+	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
+\end{align*}
+
+\vskip.1in
+\noindent
+{\sf Case 3: $j \in S(i,0).$}
+
+In this case, we may first assume $z \neq y_{j,e_j}$, 
+as this is covered by case 2, with $i$ and $j$ reversed. 
+Hence, 
+\begin{align*}
+	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
+\end{align*}
+implying
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
+	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
+	= \deg (y_{i,e_i}z) \subhalf{e_j'},
+\end{align*}
+completing part (c).
+
+Next, note that the minimal generators of $I'$ together with the
+new generators of $I$ given in (c) have independent initial terms
+by construction, and therefore are minimal by Lemma
+~\ref{lem:minimal_quadratic}.
+
+Finally, to check (e), we will first show that $(\sx,J)$ is
+admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
+i,e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
+strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
+Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
+definition. This is where we use that (Ad-iii) holds for $d > 0$
+and not just for $d = 0$.
+
+Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
+$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
+\end{proof}
+
+\section{Genus one}
+We now consider the case when the genus is positive. The genus zero
+case is the most complicated and reserve that for Section ~\ref{sec:g_0_effective}
+and Section ~\ref{sec:g_0_non_effective}. We begin with the genus one case.
+
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
+We prove an inductive theorem on adding 2-sat here.
+\todo{description}
+
+\begin{prop}
+\label{prop:sat_two_induction}
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be log stacky spin curves. 
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
+$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
+, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
+3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
+\end{align*}
+Then, the following statements hold.
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_3 \prec 
+		y_4$
+		and equip the ring $k[y_3, y_4, x]$ with the block 
+		order so that $R = k[y_3, y_4, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x, y_3, y_4] \\
+			&+\langle y_4 x_j \mid 3 \leq j \leq m \rangle \\
+			&+\langle y_4^2.\rangle
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
+_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.}
+
+In a fashion analogous to the proof of Proposition 
+~\ref{prop:sat_three_induction}, we see 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:sat_two_add_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\rangle \\
+		&+\langle y_3^ay_4 \mid a \geq 0 \rangle,
+	\end{split}
+\end{align}
+
+\noindent completing part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B y_3^2 x_2 \\
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
+\section{High genus}
+Aaron will write amazing things here.
+
+\section{Genus Zero Effective}
+\label{sec:g_0_effective}
+Now we consider the genus zero case.
+\todo{write intro}
+
+In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
+when $\Delta$ is a non- zero effective divisor.  Using this, we can 
+reduce to looking at effective stacky divisors.  Then, applying a 
+result for general effective $\mathbf{Q}$ divisors, we deduce that $
+R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
+relations generated up to degree $2e$ with initial terms quadratic 
+in the generators.  We also demonstrate that these bounds are tight 
+up to \todo{insert how tight they are}.
+
+We have Lemma ~\ref{lem:minimal_quadratic}.
+\todo{fill in hole here}
 
@@
 
-\section{Non-effective Genus Zero Spin Divisors}
+\section{Genus Zero Non-effective}
 \label{sec:g_0_non_effective}
@@
 does not lie in a finite list of exceptions. This is proven in
-Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
+Subsection ~\ref{ssec:g_0_noneff_induction}. The proof is a rather
 involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
@@
 
-\ssec{Inductive Theorem: Increasing the Ramification Orders}
-\label{ssec:g_0_ram_orders}
-In this section, we aim to prove the inductive theorem, Theorem
-~\ref{thm:ram_order_ind}. Under fairly general
-conditions, this theorem will allow us to show that if Theorem ~\ref
-{thm:ram_order_ind} holds for a curve with signature
-$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
-signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
-
-\begin{defn}
-\label{defn:admissible}
-Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
-separably rooted log stacky spin
-curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
-there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
-\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
-
-$$\chi_J(i) = \begin{cases}
-	1, &\text{ if }i \in J\\
-	0, &\text{ otherwise. } 
-\end{cases}$$
-
-Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
-{\bf admissible} if the following three conditions hold.  \todo{Peter: We should make the definition of admissibility be a condition for the triple: $(\sx',\sx,J)$.}
-
-\begin{enumerate}
-	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
-		\in R'$ so that $R'$ admits a presentation
-		\begin{align*}
-			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
-		\end{align*}
-		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
-		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
-	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
-		of $R'$ satisfies
-		\begin{align*}
-			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[(Ad-iii)] For all $i \in J$ we have
-		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
-		\end{align*}
-		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
-		where
-		\begin{align*}
-			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i - e_j'\}
-		\end{align*}
-\end{enumerate}
-\end{defn}
-
-\begin{lem}
-\label{lem:admissible_inequality}
-Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
-stronger condition that
-
-\begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
-\end{align*}
-\end{lem}
-
-\begin{proof}
-We know by (Ad-ii) that
-
-\begin{align*}
-	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
-\end{align*}
-
-\noindent
-If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
-as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
-we must have
-
-\begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
-	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
-\end{align*}
-\end{proof}
-
-\begin{lem}
-\label{lem:admissible_subset}
-If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
-then $(\sx', W)$ is also admissible.
-\end{lem}
-
-\begin{proof}
-Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
-if they hold for $J$.
-\end{proof}
-
-\begin{thm}
-\label{thm:ram_order_ind}
-Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
-curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
-R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
-Then the following are true:
-\begin{enumerate}
-	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
-		H^0(\sx, e_i(K_\sx))$ so that
-		\begin{align*}
-			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
-		\end{align*}
-		and
-		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
-			\frac{1}{\deg(y_{i,e_i})e_j'}
-		\end{align*}
-		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
-		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
-		generate $R$ over $R'$.
-	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
-		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
-		block order. Let $R = k[y,x]/I.$ Then,
-		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
-			\neq y_{i,e_i},y_{i,e_i'} \rangle
-		\end{align*}
-		as $z$ ranges over all generators of $R$.
-	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
-		products of two monomials and that for all $i \in J$, we have $e
-		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
-		minimal generators for $I'$ together with any set of relations as in 
-		part (c) minimally generate $I$.
-	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
-\end{enumerate}
-\end{thm}
-
-\begin{proof}
-Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
-question, with coarse spaces $X = X'$. 
-\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
-Define
-
-\begin{align*}
-	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
-\end{align*}
-
-\noindent
-Define
-\begin{align*}
-	E_i = \sum_{j \in S(i,0)}^{}Q_j
-\end{align*}
-
-\noindent
-Note that
-\begin{align*}
-	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
-\end{align*}
-
-\noindent
-and so we obtain an inclusion
-\begin{align*}
-	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
-H^0(\sx,e_iL).
-\end{align*}\todo{Peter: should be $Q_i$?}
-
-\noindent
-The assumption (Ad-iii) implies
-\begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g-1
-\end{align*}
-
-\noindent
-implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
-\begin{align*}
-	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
-\end{align*}
-
-\noindent
-satisfies
-\begin{align*}
-	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
-	\frac{e_i - 1}{2}
-\end{align*}
-
-\noindent
-Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
-
-We next show $y_{i,e_i}$ also satisfies the second part of the
-claim of $(a),$ by considering separately the cases of whether $j
-\in S(i,0),$ and $j \notin S(i,0)$.
-
-If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
-(\sx',e_iL'-E_i + Q_i)$,
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
-	\subhalf{e_j'} - \frac{1}{e_j'}.
-\end{align*}
-
-If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
-$e_i\subhalf{e_j'} \notin \BZ$, so
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
-	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
-\end{align*}
-
-\noindent
-completing the proof of (a).
-
-Next, define $R_0 = R'$ and inductively define 
-$$R_i = \begin{cases}
-	R_{i-1} &\text{ if }i \notin J\\
-	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
-\end{cases}$$
-
-\noindent
-To prove (b), it suffices to show that elements of the form $y_{i,e_
-i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
-and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
-vector space. These elements do not lie in $R_{i-1}$ because their
-order of pole at $Q_i$ is bigger than the order of any element in $R
-_{i-1}$, and are linearly independent amongst themselves because of
-injectivity of the linear map
-
-\begin{align*}
-	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
-	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
-	\begin{pmatrix}
-		e_i-2 & \frac{e_i-3}{2} \\
-		e_i	 & \frac{e_i-1}{2}
-	\end{pmatrix} 
-\end{align*}
-
-\noindent
-The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
-b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
-integer lattice points in the cone generated by the vectors $\left(e
-_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
-\right)$ is saturated, as the corresponding determinant is
-\begin{align*}
-	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
-\end{align*}
-completing part (b).
-
-To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
-i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
-all $j \in J$ we have
-\begin{align*}
-	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
-\end{align*}
-
-\noindent
-We now check this in three cases, depending on whether $j \notin \{
-i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
-
-\vskip.1in
-\noindent
-{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
-
-Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
-	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 2: $j =i.$}
-
-By part (a), condition (Ad-ii), and Lemma
-~\ref{lem:admissible_inequality} we have
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
-	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 3: $j \in S(i,0).$}
-
-In this case, we may first assume $z \neq y_{j,e_j}$, 
-as this is covered by case 2, with $i$ and $j$ reversed. 
-Hence, 
-\begin{align*}
-	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
-\end{align*}
-implying
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
-	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
-	= \deg (y_{i,e_i}z) \subhalf{e_j'},
-\end{align*}
-completing part (c).
-
-Next, note that the minimal generators of $I'$ together with the
-new generators of $I$ given in (c) have independent initial terms
-by construction, and therefore are minimal by Lemma
-~\ref{lem:minimal_quadratic}.
-
-Finally, to check (e), we will first show that $(\sx,J)$ is
-admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
-i,e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
-strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
-Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
-definition. This is where we use that (Ad-iii) holds for $d > 0$
-and not just for $d = 0$.
-
-Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
-$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
-\end{proof}
+Here we describe induction of raising degrees from Theorem ~\ref{thm:ram_order_ind}
+\todo{fill out}
 
@@
 	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
-	\item[(d)] $\sigma_4 = (0; 5, 7, 7; 0), J_4 = \{2, 3\}$
-	\item[(e)] $\sigma_5 = (0; 7, 7, 7; 0), J_5 = \{1, 2, 3\}$
-	\item[(f)] $\sigma_6 = (0; 3, 3, 3, 5; 0), J_6 = \{4\}$
-	\item[(g)] $\sigma_7 = (0; 3, 3, 5, 5; 0), J_7 = \{3, 4\}$
-	\item[(h)] $\sigma_8 = (0; 3, 5, 5, 5; 0), J_8 = \{2, 3, 4\}$
-	\item[(i)] $\sigma_9 = (0; 5, 5, 5, 5; 0), J_9 = \{1, 2, 3, 4\}$
-	\item[(j)] $\sigma_{10} = (0; 3, 3, 3, 3, 3; 0), J_{10} = \{1, 2, 3, 4, 5\}$
+	\item[(d)] $\sigma_4 = (0; 5, 5, 7; 0), J_4 = \{3\}$
+	\item[(e)] $\sigma_5 = (0; 5, 7, 7; 0), J_5 = \{2, 3\}$
+	\item[(f)] $\sigma_6 = (0; 7, 7, 7; 0), J_6 = \{1, 2, 3\}$
+	\item[(g)] $\sigma_7 = (0; 3, 3, 3, 5; 0), J_7 = \{4\}$
+	\item[(h)] $\sigma_8 = (0; 3, 3, 5, 5; 0), J_8 = \{3, 4\}$
+	\item[(i)] $\sigma_9 = (0; 3, 5, 5, 5; 0), J_9 = \{2, 3, 4\}$
+	\item[(j)] $\sigma_{10} = (0; 5, 5, 5, 5; 0), J_{10} = \{1, 2, 3, 4\}$
+	\item[(k)] $\sigma_{11} = (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$
 \end{enumerate}
@@
 
-	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
-
-	(d) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline
-
-	(e) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline
-
-	(f) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline
-
-	(g) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline
-
-	(h) & \{3, 3, 4, 5, 5, 5\} &
+	(c) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
+
+	(d) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
+
+	(e) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline
+
+	(f) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline
+
+	(g) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline
+
+	(h) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline
+
+	(i) & \{3, 3, 4, 5, 5, 5\} &
 	\{8, 8, 8, 9, 9, 9, 10, 10, 10\} & 5\\ \hline
 
-	(i) & \{3, 3, 4, 5, 5, 5, 5\} &
+	(j) & \{3, 3, 4, 5, 5, 5, 5\} &
 	\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\} & 5\\ \hline
 
-	(j) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
+	(k) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
 \end{longtable}
@@
 \begin{longtable}
-	{| c | c || c | c | c |}
-	\hline
-	$\sigma$ & $J$ &  $i$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
-	\hline
-	\hline
-
-	$(0; 3, 3, 11; 0)$ & $\{3\}$ & $\forall i \in J$ & 1 & 0\\	\hline
-
-	$(0; 3, 7, 7; 0)$ & $\{3\}$ & $\forall i \in J$ & 2 & 0\\ \hline
-
-	$(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $\forall i \in J$ & 2 & 0\\ \hline
-
-	$(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $\forall i \in J$ & 3 & 0\\ \hline
-
-	$(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $\forall i \in J$ & 2 & 0\\ \hline
-
-	$(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $\forall i \in J$ & 3 & 0\\ \hline
-
-	$(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $\forall i \in J$ & 4 & 0\\ \hline
-
-	$(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $\forall i \in J$ & 5 & 0\\ \hline
-
-	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $\forall i \in J$ & 5 & 0\\ \hline
+	{| c | c | c || c | c |}
+	\hline
+	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
+	\hline
+	\hline
+
+	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0\\	\hline
+
+	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0\\ \hline
+
+	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0\\ \hline
+
+	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0\\ \hline
+
+	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0\\ \hline
+
+	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0\\ \hline
+
+	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0\\ \hline
+
+	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0\\ \hline
+
+	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0\\ \hline
+
+	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0\\ \hline
+
+	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0\\ \hline
 \end{longtable}
@@
 
-\ssec{Conclusion}
-\label{ssec:g_0_conclusion}
+\ssec{Application of induction}
+\label{ssec:g_0_noneff_induction}
+Now we can combine this.
 
@@
 
-\section{Genus positive}
-
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
-
-\begin{prop}
-\label{prop:sat_two_induction}
-Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be log stacky spin curves. 
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
-$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
-Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
-, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
-3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
-Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
-\end{align*}
-Then, the following statements hold.
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_3 \prec 
-		y_4$
-		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order so that $R = k[y_3, y_4, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 3 \leq j \leq m \rangle \\
-			&+\langle y_4^2.\rangle
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.}
-
-In a fashion analogous to the proof of Proposition 
-~\ref{prop:sat_three_induction}, we see 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:sat_two_add_generator}
-	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\rangle \\
-		&+\langle y_3^ay_4 \mid a \geq 0 \rangle,
-	\end{split}
-\end{align}
-
-\noindent completing part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B y_3^2 x_2 \\
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
 \section{Acknowledgements}
-We are grateful to VZB.
+We are grateful to David Zureick-Brown for introducing us to this
+field of study, providing incredibly helpful guidance, and being an
+excellent project mentor. We also thank Ken Ono and the Emory University
+Number Theory REU for arranging our project and providing a great
+environment for mathematical learning and collaboration. Finally, we
+gratefully acknowledge that our research was financially supported by
+NSF Grant \_\_\_\_\_ via the Emory University Number Theory REU. We deeply
+appreciate all of the support that has made our work possible.
 

### 2015-06-22 stacky_write_up/spin_cring.tex
nsf grant award number, st-donat in bib

@@
 gratefully acknowledge that our research was financially supported by
-NSF Grant \_\_\_\_\_ via the Emory University Number Theory REU. We deeply
-appreciate all of the support that has made our work possible.
+NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
+We deeply appreciate all of the support that has made our work possible.
 

### 2015-06-22 stacky_write_up/spin_cring.tex
added subsections
modify def admissible, reword base cases

@@
 
-Let $R'$ be the canonical ring associated to $\sx'$. Say $(\sx',J)$,
-{\bf admissible} if the following three conditions hold.  \todo{Peter: We should make the definition of admissibility be a condition for the triple: $(\sx',\sx,J)$.}
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
+to be {\bf admissible} if the $R'$ admits a presentation
+
+\begin{align*}
+	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
+\end{align*}
+
+\noindent
+with $y_{i,e_i'} \in R'$ for each $i \in J$ such that the following
+three conditions hold.
+
+\todo{Peter: We should make the definition of admissibility be a 
+condition for the triple: $(\sx',\sx,J)$.}
 
 \begin{enumerate}
-	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
-		\in R'$ so that $R'$ admits a presentation
-		\begin{align*}
-			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
-		\end{align*}
-		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
+	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
 		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
@@
 
+\ssec{Genus 1 base cases}
+
+\ssec{Main Theorem for Genus 1}
+
 \section{High genus}
-Aaron will write amazing things here.
+
+\ssec{Inductive Theorem: Adding points for high genus}
+
+\ssec{Bounds on Generators and Relations in high genus}
+
+\ssec{Main theorem for high genus}
 
@@
 
+\begin{example}
+Here we demonstrate, in detail, that case (b) ($\sigma_2 =
+(0; 3, 5, 9; 0), J_2 = \{3\}$) satisfies the conditions.
+\end{example}
+
 \begin{proof}
-For each case, computations using a combination of Riemann-Roch and
-comparing pole orders at each ramification point $P_i$ gives the
-generator and relation degrees.
+For these cases, we can always find a presentation satisfying (Ad-i).
+Furthermore, we can verify that these base cases satisfy the
+remaining conditions using computations of Riemann-Roch and pole
+orders similar to those in the given example.
 
@@
 
-Note that (Ad-i) always holds.
-In each case we can also pick a set of generators such that
-(Ad-ii) holds. \todo{justification for these}
-
 Furthermore, each case satisfies (Ad-iii) as demonstrated below.
@@
 
-Thus, we have admissibility of $(\sx', J)$ in each of these cases.
-
-Finally, each case also satisfies the property that $in_\prec(I')$ is
-minimally generated by products of two monomials.
-\todo{prove}
+All that remains to be shown is that these cases satisfy
+(Ad-ii) and that $in_\prec(I')$ is minimally generated by
+products of two monomials. The procedure for verifying these
+are similar to those for the given example. Below, we
+give a table for the explicit generators and initial ideals.
+\todo{make table}
 \end{proof}
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 We are grateful to David Zureick-Brown for introducing us to this

### 2015-06-22 stacky_write_up/spin_cring.tex
swap rows in coln
fixed grlex order in noneffective genus 0

--- 2015-06-22 stacky_write_up/spin_cring.tex
@@
 the following saturations of the canonical divisor, as defined in 7.
-2 of VZB \cite{vzb:stacky}. Exceptional cases are listed first
+2 of Voight and Zureick-Brown \cite{vzb:stacky}. Exceptional cases are listed first
 and generic cases follow.
@@
 		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_3 \prec 
-		y_4 \prec y_5$
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
 		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 

### 2015-06-22 stacky_write_up/spin_cring.tex

--- 2015-06-22 stacky_write_up/spin_cring.tex
@@
 
-	(c) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
-
-	(d) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
+	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
+
+	(d) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
 

### 2015-06-22 stacky_write_up/spin_cring.tex
added genus 2 generator and relation bounds

@@
 \DeclareMathOperator{\ord}{ord}
+\DeclareMathOperator{\sym}{Sym}
 
@@
 
+\begin{lem}
+\label{lem:semicanonical_generation}\todo{include that this was as shown in Neves, with degree 6 omitted}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, for $n \geq 5$, the map
+\begin{align*}
+	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
+\end{align*}
+is surjective.
+In particular, $R_L$ is generated in degree at most $6$.
+\end{lem}
+\begin{proof}
+Therefore, to show there are no new generators in degree at least $7$, it suffices to show that for $n \geq 5$, the map
+\begin{align*}
+	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
+\end{align*}
+is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
+Since $K$ is basepoint free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
+Then, by the basepoint free pencil trick, we obtain an exact sequence
+$$\begin{tikzcd}
+0 \ar r & H^0((n-2)L) \ar r & V \otimes H^0(nL) \ar{r}{f} & H^0((n+2)L)
+\end{tikzcd}$$
+We wish to show $f$ is surjective.
+Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption that $n \geq 5$.
+Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n-1)(g-1)$, again using Riemann--Roch.
+Therefore, $$\dim \im f = 2 \cdot (n-1)(g-1) -(n-3)(g-1) = (n+1)(g-1) = \dim H^0((n+2)L),$$
+again using Riemann-Roch, implying $f$ is surjective.
+\end{proof}
+
+\begin{prop}
+\label{prop:genus_2_generation_5}
+Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
+Then, $R_L$ is generated in degree at most $5$.
+\end{prop}
+\begin{proof}
+By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
+Let $P_1,\ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
+Recall that all spin divisors on $X$ can be written as 
+$$L = P_1 + \sum_{i=2}^{6} \epsilon_i (P_1 - P_i),$$ 
+with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
+Note that $H^0(X,K)$ is spanned by rational functions $u,x$ with $\di u|_{2L} = 2L, \di x|_{2L} = 2L - 2P_1.$ Therefore, the image of the multiplication map 
+\begin{align*}
+	Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
+\end{align*}
+is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2,x^3$, 
+which have $\di u^3|_{2L} = 2L, \di u^2x|_{2L} = 2L - 2P_1,\di ux^2|_{2L} = 2L-4P_1, \di x^3|_{2L} = 2L - 6P_1.$ 
+Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
+it suffices to produce one more independent function in the image of the multiplication map.
+There are now two cases, depending on whether $H^0(X,L) = 0$.
+First, suppose $H^0(X,L) = 0$.
+Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
+Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
+we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = 2P_1 + L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
+with $\di g|_{2P_1 + L} = L,$ since $H^0(X,L) = 0.$ Therefore, there must 
+exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = L + P_1$.
+Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
+order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
+Second, we deal with the case that $H^0(X,L) \neq 0$. 
+Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$. 
+In this case, $L$ is linearly equivalent to an effective divisor, so we may assume $L = P_1$. 
+Then, taking the function $y \in H^0(X,5P_1),$ to be that with $\di_\infty y = 5P_1,$ 
+corresponding to the hyperelliptic involution, and $u \in H^0(X,P_1)$ 
+corresponding to the rational function 1, we see that $y \cdot v \in H^0
+(X,6P_1)$ determines an element with a pole of odd order at $P_1$, which is 
+therefore independent from the image of $\sym^3 H^0(X,K)$. Hence, we again 
+obtain there are no new generators in degree 6.
+\end{proof}
+
+\begin{lem}
+\label{lem:generation_5}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, $R_L$ is generated in degree at most $5$.
+\end{lem}
+\begin{proof}
+If $g = 2$ then the claim follows from 
+Proposition ~\ref{prop:genus_2_generation_5}.
+However, if $g > 2$, then by \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective, so again there are no new generators in degree 6.
+\end{proof}
+
+\todo{This should be $k[x_1,\ldots, x_n]$ instead of $\sym H^0$.}
+\begin{lem}
+\label{lem:reducing_degree}
+Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$.
+Choose generators $x_1,\ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1,\ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and $J_{L,d} = \sum_{j = 1}^{d-1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ Let for any $f \in k[x_1, \ldots, x_n]$ with $\deg f \geq 12,$ there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+\end{lem}
+\begin{proof}
+Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
+By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i=1}^{n}a_ix_i$ with $a_i \in k[x_1,\ldots, x_n]_{d-\deg x_i}$.
+We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i- 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
+Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$. By Lemma ~\ref{lem:semicanonical_generation},
+\begin{align*}
+	V \otimes H^0((\deg f-\deg x_i-2)L) \rightarrow H^0((\deg f-\deg x_i)L)
+\end{align*}
+is surjective, since $\deg f - \deg a_i - 2 \geq 12 - 5 - 2 = 5$.
+In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
+Chosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+
+Finally, we may then take $g = \sum_{i}^{}g_ix_i,h = \sum_{i}^{}h_ix_i,$ so that 
+\begin{align*}
+	f \equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \equiv s_1 g + s_2 h \bmod J_{L,d}.
+\end{align*}
+\end{proof}
+
+\begin{thm}
+\label{}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
+\end{thm}
+\begin{proof}
+Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
+Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
+$$\begin{tikzcd}
+V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
+\end{tikzcd}$$
+we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
+So, using the refined version of the basepoint free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
+Therefore,
+\begin{align*}
+	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
+\end{align*}
+\end{proof}
+
 \ssec{Main theorem for high genus}

### 2015-06-22 stacky_write_up/spin_cring.tex
add example

@@
 Here we demonstrate, in detail, that case (b) ($\sigma_2 =
-(0; 3, 5, 9; 0), J_2 = \{3\}$) satisfies the conditions.
+(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
+We have that $K_{\sx'} \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
+P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
+We exhibit a (minimal) presentation for $R'$.
+
+Notice that $\deg \lfloor d K_{\sx'} = -d + \lfloor \frac{d}{3}
+\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
+
+By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
+and Zureick-Brown \cite{vzb:stacky}),
+
+\[
+	H^0 (\sx', \lfloor 21 K_{\sx'} \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 21) K_{\sx'} \rfloor) \twoheadrightarrow = H^0 (\sx', \lfloor
+	d K_{\sx'} \rfloor)
+\]
+
+\noindent
+is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
+\geq 0$. Also, $\sigma_2$ has saturation $s = 5$ as noted in
+Subsection ~\ref{ssec:g_0_saturation}. Thus, $R'$ is generated up to
+degree $21 + (s - 1) = 24$.
+
+For $d = 0, 1, 2, \ldots$ we have
+
+\[
+	dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+\]
+
+\noindent
+so $R'$ must have some generators $x_{1, 3}, x_{1, 5}, x_{1, 7},
+x_{1, 7}$. Let $(-ord_{P_1}(x_j), -ord_{P_2}(x_j), -ord_{P_3}(x_j))$
+represent the pole orders of $x_i$ at each point. Then these generators
+must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
+respectively.
+
 \end{example}

### 2015-06-22 stacky_write_up/spin_cring.tex
Lemma to add points in higher genus

--- 2015-06-22 stacky_write_up/spin_cring.tex
@@
 \label{prop:sat_two_induction}
-Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be log stacky spin curves. 
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
 Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
@@
 		_3,y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_3 \prec 
-		y_4$
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
+		y_3$
 		and equip the ring $k[y_3, y_4, x]$ with the block 
@@
 			J &= gin_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 3 \leq j \leq m \rangle \\
+			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
 			&+\langle y_4^2.\rangle
@@
 	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\rangle \\
-		&+\langle y_3^ay_4 \mid a \geq 0 \rangle,
+		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \\
+		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
 	\end{split}
@@
 \begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
 	y_4^2 &+ B y_3^2 x_2 \\
@@
 \ssec{Inductive Theorem: Adding points for high genus}
+
+\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
+Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
+curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
+\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
+\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
+$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
+x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
+\begin{enumerate}
+\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
+(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
+independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
+\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
+x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
+Then
+\begin{align*}
+			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_2^2\rangle.
+		\end{align*}
+\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
+leading terms as above minimally generate $I$.
+\end{enumerate}
+
+\end{lem}
+\begin{proof}
+Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
+Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
+\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
+all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
+$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
+choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
+dimension counting, we see that 
+\[
+	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
+\]
+\[
+	\langle y_1^a y_2: a\ge 0\rangle
+\]
+form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).
+
+To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
+\prec(I)$.  Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$.  For $j\ge 2$, we 
+can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
+\[
+	y_2x_j-A_jy_3w_j
+\]
+has no pole at $P$ at thus lies in $R_{\halfcan'}$.  Similarly, we can choose $B$ and $C$ 
+such that
+\[y^2_4+By_1^2x_2+Cy_1x_3\]
+has no pole at $P$, so it lies in $R_{\halfcan'}$.  These give us relations with initial terms 
+as desired, concluding part (b).
+
+Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
+
+\end{proof}
+
+\begin{lem}\label{lem:adding_points_saturation_2_to_1_no_log}
+Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
+with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
+\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
+Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
+$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
+Then
+\begin{enumerate}
+\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
+(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
+independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
+\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
+x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
+Then
+\begin{align*}
+			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_3^2
+		\end{align*}
+\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
+leading terms as above minimally generate $I$.
+\end{enumerate}
+\end{lem}
+\begin{proof}
+The proof follows similarly to that of lemma 
+\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
+\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
+generator in degree 3 rather than degree 2.  
+\end{proof}
 
@@
 the following saturations of the canonical divisor, as defined in 7.
-2 of Voight and Zureick-Brown \cite{vzb:stacky}. Exceptional cases are listed first
+2 of VZB \cite{vzb:stacky}. Exceptional cases are listed first
 and generic cases follow.
@@
 		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_3 \prec 
+		y_4 \prec y_5$
 		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
@@
 
-	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
-
-	(d) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
+	(c) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
+
+	(d) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
 
@@
 	\hline
-	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
+	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$\\
 	\hline
@@
 
+\section{Further Research}
+\begin{itemize}
+\item More on fractional modular forms
+\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
+\end{itemize}
+
 \section{Acknowledgments}

### 2015-06-22 stacky_write_up/spin_cring.tex
add halfcan to ex, check gens and rels in ex

@@
 \begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
+Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
 Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
@@
 \label{lem:g_0_admissible_cases}
-Let $(\sx', \Delta, L')$ be a tame log spin curve over a perfect field $k$,
+Let $(\sx', \Delta, \halfcan')$ be a tame log spin curve over a perfect field $k$,
 so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$.
-Then $R' := R(\sx', \Delta, L')$ is generated as a $k$-algebra by elements
+Then $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k$-algebra by elements
 of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree
@@
 (0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
-We have that $K_{\sx'} \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
+We have that $\halfcan \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
 P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
@@
 and Zureick-Brown \cite{vzb:stacky}),
-
-\[
-	H^0 (\sx', \lfloor 21 K_{\sx'} \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) K_{\sx'} \rfloor) \twoheadrightarrow = H^0 (\sx', \lfloor
-	d K_{\sx'} \rfloor)
+\[
+	H^0 (\sx', \lfloor 21 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 21) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan \rfloor)
 \]
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Also, $\sigma_2$ has saturation $s = 5$ as noted in
-Subsection ~\ref{ssec:g_0_saturation}. Thus, $R'$ is generated up to
-degree $21 + (s - 1) = 24$.
+\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
+Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
+when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24).
 
 For $d = 0, 1, 2, \ldots$ we have
-
-\[
-	dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{1, 3}, x_{1, 5}, x_{1, 7},
-x_{1, 7}$. Let $(-ord_{P_1}(x_j), -ord_{P_2}(x_j), -ord_{P_3}(x_j))$
-represent the pole orders of $x_i$ at each point. Then these generators
-must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
-respectively.
+\[
+	\dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+\]
+
+\noindent
+so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
+x_{7, 2}$.
+
+To show that these generate all of $R'$, we need to show that all
+$H^0 (\sx', d \halfcan)$ are generated by lower degrees for $d = 6$
+and $7 < d \leq 24$. Note that we can again use Max Noether's theorem
+(taking saturation into account) to see that
+
+\begin{align*}
+	&H^0 (\sx', \lfloor 3 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 3) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
+	&H^0 (\sx', \lfloor 7 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 7) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
+	\text{ (mod } 7)
+\end{align*}
+
+\noindent
+are surjective. This reduces the problem to checking generation
+in the degrees of the exceptions $d \in \{8, 12, 21\}$.
+Checking the remaining cases via pole degrees shows that
+these degrees are also generated in lower degrees,
+so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
+
+%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
+%represent the pole orders of $x_i$ at each point. Then these generators
+%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
+%respectively.
+
+Furthermore, we can directly see that the relations are given
+in degrees $10$ and $14$. In particular, we have a relation
+of the form
+\[
+	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0
+\]
+
+\noindent
+in degree $10$ and a relation of the form
+\[
+	a_1 x_{3, 1}^3 x_{5, 1} + a_2 x_{7, 1}^2 + a_3 x_{7, 1} x_{7, 2} + a_4 x_{7, 2}^2 = 0
+\]
+
+\noindent
+in degree $14$.
+
+Therefore, the canonical ring $R'$ has presentation $R' =
+k[x_{7, 1}, x_{7, 2}, x{5, 1}, x_{3, 1}] / I$ with
+initial ideal
+\[
+	in_\prec(I) = < x_{7, 1} x_{3, 1}, x_{7, 1}^2 >
+\]
+
+\noindent
+generated by quadratics under grevlex with $x_{i, j} \prec x_{k, l}$
+if $i > j$ or $i = j$ and $j < l$. These quadratics must also 
+determine minimal generators for $I$ by Lemma
+~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to degree
+$e = 7$ with relations up to degree $2e = 14$, as desired.
+
+Now we check admissibility.
 

### 2015-06-23 stacky_write_up/spin_cring.tex
additions to corollaries of induction when saturated at 1

--- 2015-06-22 stacky_write_up/spin_cring.tex
@@
 \begin{cor}\label{cor:genus_0_posiive_delta}
-Let $\halfcan$ be a stacky log spin canonical divisor of signature $(0,e_1,...,e_n,\delta)$ with $\delta>0$.  Then 
+Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.
+Then $\halfcan$ is effective so we can inductively apply lemma \ref{lem:deg1_sat_ind}.
 \end{cor}
@@
 \[
-	2\halfcan=D+\sum \subhalf{i}P_i
+	2\halfcan=D+\sum \subhalf{e_i}P_i
 \] 

### 2015-06-23 stacky_write_up/spin_cring.tex
added genus 1 base cases loosely

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 \label{prop:sat_two_induction}
-Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be log stacky spin curves. 
 Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
@@
 		_3,y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
-		y_3$
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_3 \prec 
+		y_4$
 		and equip the ring $k[y_3, y_4, x]$ with the block 
@@
 			J &= gin_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_4 x_j \mid 3 \leq j \leq m \rangle \\
 			&+\langle y_4^2.\rangle
@@
 	\begin{split}
-		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \\
-		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
+		&\langle y_3^ax_3^b x_4^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\rangle \\
+		&+\langle y_3^ay_4 \mid a \geq 0 \rangle,
 	\end{split}
@@
 \begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 3 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
 	y_4^2 &+ B y_3^2 x_2 \\
@@
 
+Let $\sx$ be a tame, seperably rooted stacky curve of genus 1.
+Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$.
+In this section, will compute the canonical ring $R_L$ in the cases that
+\begin{enumerate}
+	\item $L = 0$
+	\item $L = P-Q$
+	\item $L = P - Q + \frac{1}{3}R$
+	\item $L = P - Q + \sum_{i=1}^{n}\frac{1}{3}R_i$
+\end{enumerate}
+In addition to being illustrative examples, these will serve as the base cases of induction, in order to compute generators and relations for an arbitrary genus 1, stacky log half canonical divisor.
+In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.
+
+\begin{example}
+\label{eg:g_1_triv}
+In the case $L = 0,$ we see immediately that $R_L \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+\label{eg:g_1_half_can}
+In the case $L=P - Q.$ Then, we have $R_{(2k+1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
+\end{example}
+
+\begin{example}
+\label{eg:g_1_deg_third}
+Let $L = P - Q + \frac{1}{3}R$.
+Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$.
+For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
+We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q + 2R.$
+\end{example}
+
+\begin{example}
+Let $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
+Here, we claim $R_L \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k$, and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
+\todo{Explain why this forms a system of generators and relations, and also state more clearly what $y_i$ are.}
+\end{example}
+
+\begin{example}
+\label{}
+Let $L = P - Q + \frac{e-1}{2e}R_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+Furthermore, $\deg u = 2, \deg y_i = i$.
+\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
+\end{example}
+
 \ssec{Main Theorem for Genus 1}
@@
 
-\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
-Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
-curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
-\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
-\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
-$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
-x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
-\begin{enumerate}
-\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
-(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
-independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
-x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
-Then
-\begin{align*}
-			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_2^2\rangle.
-		\end{align*}
-\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-leading terms as above minimally generate $I$.
-\end{enumerate}
-
-\end{lem}
-\begin{proof}
-Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
-Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
-\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
-all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
-$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
-choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
-dimension counting, we see that 
-\[
-	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
-\]
-\[
-	\langle y_1^a y_2: a\ge 0\rangle
-\]
-form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).
-
-To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
-\prec(I)$.  Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$.  For $j\ge 2$, we 
-can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
-\[
-	y_2x_j-A_jy_3w_j
-\]
-has no pole at $P$ at thus lies in $R_{\halfcan'}$.  Similarly, we can choose $B$ and $C$ 
-such that
-\[y^2_4+By_1^2x_2+Cy_1x_3\]
-has no pole at $P$, so it lies in $R_{\halfcan'}$.  These give us relations with initial terms 
-as desired, concluding part (b).
-
-Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
-
-\end{proof}
-
-\begin{lem}\label{lem:adding_points_saturation_2_to_1_no_log}
-Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
-with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
-\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
-Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
-$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
-Then
-\begin{enumerate}
-\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
-(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
-independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
-x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
-Then
-\begin{align*}
-			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_3^2
-		\end{align*}
-\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-leading terms as above minimally generate $I$.
-\end{enumerate}
-\end{lem}
-\begin{proof}
-The proof follows similarly to that of lemma 
-\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
-\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
-generator in degree 3 rather than degree 2.  
-\end{proof}
-
 \ssec{Bounds on Generators and Relations in high genus}
 
+\todo{make sure to switch poles and zeros where appropriate}
 \begin{lem}
@@
 \begin{cor}\label{cor:genus_0_posiive_delta}
-Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.
-Then $\halfcan$ is effective so we can inductively apply lemma \ref{lem:deg1_sat_ind}.
+Let $\halfcan$ be a stacky log spin canonical divisor of signature $(0,e_1,...,e_n,\delta)$ with $\delta>0$.  Then 
 \end{cor}
@@
 \[
-	2\halfcan=D+\sum \subhalf{e_i}P_i
+	2\halfcan=D+\sum \subhalf{i}P_i
 \] 
@@
 Here we demonstrate, in detail, that case (b) ($\sigma_2 =
-(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
-We have that $K_{\sx'} \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
-P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
-We exhibit a (minimal) presentation for $R'$.
-
-Notice that $\deg \lfloor d K_{\sx'} = -d + \lfloor \frac{d}{3}
-\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
-
-By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
-and Zureick-Brown \cite{vzb:stacky}),
-
-\[
-	H^0 (\sx', \lfloor 21 K_{\sx'} \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) K_{\sx'} \rfloor) \twoheadrightarrow = H^0 (\sx', \lfloor
-	d K_{\sx'} \rfloor)
-\]
-
-\noindent
-is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Also, $\sigma_2$ has saturation $s = 5$ as noted in
-Subsection ~\ref{ssec:g_0_saturation}. Thus, $R'$ is generated up to
-degree $21 + (s - 1) = 24$.
-
-For $d = 0, 1, 2, \ldots$ we have
-
-\[
-	dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{1, 3}, x_{1, 5}, x_{1, 7},
-x_{1, 7}$. Let $(-ord_{P_1}(x_j), -ord_{P_2}(x_j), -ord_{P_3}(x_j))$
-represent the pole orders of $x_i$ at each point. Then these generators
-must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
-respectively.
-
+(0; 3, 5, 9; 0), J_2 = \{3\}$) satisfies the conditions.
 \end{example}
@@
 	\hline
-	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$\\
+	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i))$\\
 	\hline
@@
 
-\section{Further Research}
-\begin{itemize}
-\item More on fractional modular forms
-\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
-\end{itemize}
-
 \section{Acknowledgments}

### 2015-06-23 stacky_write_up/spin_cring.tex

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 
+\todo{make sure to switch poles and zeros where appropriate}
 \begin{lem}

### 2015-06-23 stacky_write_up/spin_cring.tex
sharpness of relation bounds

@@
 	\item $L = P - Q + \frac{1}{3}R$
-	\item $L = P - Q + \sum_{i=1}^{n}\frac{1}{3}R_i$
+	\item $L = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
+	\item $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
 \end{enumerate}
@@
 \begin{example}
-Let $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
-Here, we claim $R_L \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k$, and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
-\todo{Explain why this forms a system of generators and relations, and also state more clearly what $y_i$ are.}
-\end{example}
-
-\begin{example}
 \label{}
@@
 Furthermore, $\deg u = 2, \deg y_i = i$.
-\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
+\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.} \todo{Check admissibility}
+\end{example}
+
+\begin{example}
+Let $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
+Here, we claim $R_L \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k$, and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
+\todo{Explain why this forms a system of generators and relations, and also state more clearly what $y_i$ are.} \todo{check admissibility}
 \end{example}
@@
 
-\todo{make sure to switch poles and zeros where appropriate}
 \begin{lem}
-\label{lem:semicanonical_generation}\todo{include that this was as shown in Neves, with degree 6 omitted}
+\label{lem:semicanonical_generation} \cite{neves:halfcan}[Proposition III.4]
 Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, for $n \geq 5$, the map
@@
 \end{lem}
+\iffalse
 \begin{proof}
@@
 \end{proof}
+\fi
+
+\begin{rem}
+In \cite{neves:halfcan}[Proposition III.4], Neves claims to prove that $R_L$ is generated in degree at most 5.
+However, when the proof is carefully examined, it only shows generation in degree at most 6.
+For this reason, we only state Lemma ~\ref{lem:semicanonical_generation} as generation in degree at most 6.
+We next proceed to show this can be reduced to generation in degree 5.
+The trickiest case is genus 2, which we address next.
+\end{rem}
 
@@
 with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
-Note that $H^0(X,K)$ is spanned by rational functions $u,x$ with $\di u|_{2L} = 2L, \di x|_{2L} = 2L - 2P_1.$ Therefore, the image of the multiplication map 
+Note that $H^0(X,K)$ is spanned by rational functions $u,x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
 \begin{align*}
@@
 is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2,x^3$, 
-which have $\di u^3|_{2L} = 2L, \di u^2x|_{2L} = 2L - 2P_1,\di ux^2|_{2L} = 2L-4P_1, \di x^3|_{2L} = 2L - 6P_1.$ 
+which have $\di u^3|_{2L} = -2L, \di u^2x|_{2L} = -2L + 2P_1,\di ux^2|_{2L} = -2L+4P_1, \di x^3|_{2L} = -2L + 6P_1.$ 
 Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
@@
 There are now two cases, depending on whether $H^0(X,L) = 0$.
-First, suppose $H^0(X,L) = 0$.
+
+First, we deal with the case that $H^0(X,L) \neq 0$. 
+Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
+Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed.
+In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
+
+Second, suppose $H^0(X,L) = 0$.
 Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
 Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = 2P_1 + L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
-with $\di g|_{2P_1 + L} = L,$ since $H^0(X,L) = 0.$ Therefore, there must 
-exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = L + P_1$.
+we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
+with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
+exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
 Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
 order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
-Second, we deal with the case that $H^0(X,L) \neq 0$. 
-Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$. 
-In this case, $L$ is linearly equivalent to an effective divisor, so we may assume $L = P_1$. 
-Then, taking the function $y \in H^0(X,5P_1),$ to be that with $\di_\infty y = 5P_1,$ 
-corresponding to the hyperelliptic involution, and $u \in H^0(X,P_1)$ 
-corresponding to the rational function 1, we see that $y \cdot v \in H^0
-(X,6P_1)$ determines an element with a pole of odd order at $P_1$, which is 
-therefore independent from the image of $\sym^3 H^0(X,K)$. Hence, we again 
-obtain there are no new generators in degree 6.
 \end{proof}
@@
 \begin{align*}
-	f \equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \equiv s_1 g + s_2 h \bmod J_{L,d}.
+	f &\equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \\
+	&\equiv s_1 g + s_2 h \bmod J_{L,d}.
 \end{align*}
@@
 
-\begin{thm}
-\label{}
+\begin{prop}
+\label{prop:relations_generation}
 Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
-\end{thm}
+\end{prop}
 \begin{proof}
@@
 \end{proof}
+
+\begin{rem}
+\label{rem:relations_generation_ten}
+In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
+Therefore, the bound from Proposition ~\ref{prop:relations_generation}, that $I_L$ is generated in degree at most 11 is close to sharp.
+\end{rem}
 
@@
 	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
+	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
+\todo{Possibly think more about this}
 \end{itemize}

### 2015-06-23 stacky_write_up/spin_cring.tex
admissibility in g0 example, add pic, g0 saturation

@@
 \begin{defn}
+\label{defn:sat}
 \textbf{Saturations} of the canonical divisor, as defined in 7.
@@
 \ssec{Saturation}
-\label{ssec:g_0_saturation} \todo{Define saturation}
-Here we compute saturation numbers. That is, given a list of
-ramification orders, with $g = 0,\delta = 0$ understood, we have
-the following saturations of the canonical divisor, as defined in 7.
-2 of Voight and Zureick-Brown \cite{vzb:stacky}. Exceptional cases are listed first
-and generic cases follow.
-
-\todo{prove}
+\label{ssec:g_0_saturation}
+First, we present the saturations $s$ of the canonical divisor for
+all cases where $g = 0, \delta = 0$ as defined in Definition
+~\ref{defn:sat}. The saturation can be computed via the application
+of Riemann-Roch on degrees up to $s$. Exceptional cases are listed
+first and generic cases follow.
 
@@
 \begin{example}
+\label{ex:base-377}
 Here we demonstrate, in detail, that case (b) ($\sigma_2 =
 (0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
-We have that $\halfcan \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
+We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
 P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
@@
 \[
-	H^0 (\sx', \lfloor 21 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan \rfloor)
+	H^0 (\sx', \lfloor 21 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor)
 \]
@@
 To show that these generate all of $R'$, we need to show that all
-$H^0 (\sx', d \halfcan)$ are generated by lower degrees for $d = 6$
+$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
 and $7 < d \leq 24$. Note that we can again use Max Noether's theorem
@@
 \begin{align*}
-	&H^0 (\sx', \lfloor 3 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 3) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
-	&H^0 (\sx', \lfloor 7 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 7) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
+	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
+	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
 	\text{ (mod } 7)
@@
 $e = 7$ with relations up to degree $2e = 14$, as desired.
-
-Now we check admissibility.
-
+We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
+since $e_i = 9 > e$ for all $i \in J$.
+
+\todo{show only relations}
+
+Admissibility is the remaining condition to check. WLOG, we can
+let $x_{7, 1}$ correspond to the generator with maximal pole order
+at $P_2$ and $x_{7, 2}$ correspond to the generator with maximal
+pole order at $P_3$. Use the presentation given above with $y
+_{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$. We see that
+it immediately satisfies (Ad-i) of Definition ~\ref{defn:admissible}.
+It also satisfies (Ad-ii) because $y_{i, e_i'}$ is the only generator
+lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$ in the
+$(\deg z, -ord_{P_i}(z))$ lattice and the other generators
+must lie below the line as seen below:
+
+\begin{center}
+\includegraphics{pics/spin-377-pic-pics.pdf}
+\end{center}
+
+Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
+$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
+0$. Thus, $S_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
+Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
+\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
+\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and $\sigma_2, J_2$ is
+admissible.
 \end{example}
@@
 \begin{proof}
-For these cases, we can always find a presentation satisfying (Ad-i).
-Furthermore, we can verify that these base cases satisfy the
-remaining conditions using computations of Riemann-Roch and pole
-orders similar to those in the given example.
+For the remaining cases, we can use a similar method to the one
+used in Example ~\ref{ex:base-377} to find a presentation the
+desired conditions.
 
@@
 All that remains to be shown is that these cases satisfy
-(Ad-ii) and that $in_\prec(I')$ is minimally generated by
+(Ad-i) and (Ad-ii) and that $in_\prec(I')$ is minimally generated by
 products of two monomials. The procedure for verifying these
@@
 give a table for the explicit generators and initial ideals.
-\todo{make table}
+\todo{make table, move this before (Ad-iii)?}
 \end{proof}

### 2015-06-23 stacky_write_up/spin_cring.tex
minor edits

@@
 \label{ex:base-377}
-Here we demonstrate, in detail, that case (b) ($\sigma_2 =
+Here we demonstrate, in detail, that case (b) with ($\sigma_2 =
 (0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
-We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
-P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
+We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 +
+\frac{3}{7} P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
 We exhibit a (minimal) presentation for $R'$.
@@
 	\hline
-	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ & $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$\\
+	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
+	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
 	\hline
@@
 
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0\\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0\\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0\\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0\\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0\\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0\\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0\\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0\\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0\\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0\\ \hline
-
-	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0\\ \hline
+	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0 \\	\hline
+
+	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0 \\ \hline
+
+	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0 \\ \hline
+
+	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0 \\ \hline
+
+	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0 \\ \hline
+
+	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0 \\ \hline
+
+	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0 \\ \hline
+
+	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0 \\ \hline
+
+	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0 \\ \hline
+
+	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0 \\ \hline
+
+	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0 \\ \hline
 \end{longtable}

### 2015-06-23 stacky_write_up/spin_cring.tex
adding lemma for effective divisors adding a point with no new generator in degree 1

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q + 2R.$
+We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{Peter: Why don't we have something in degree 4?}
 \end{example}
@@
 satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
-generator $u$ in degree 1; let $u$ \todo{Was there supposed to be something else in this sentence?}.  Suppose $D$ is generated by $
-u, x_1, \ldots, x_m$ in degree at most $\delta$ with relations generated 
-in degree at most $\tau $.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+generator $u$ in degree 1.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
 for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
@@
 \begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
-Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\delta,\beta)$ with relations generated in degree at most $\max(\tau,\delta+\beta,2\beta)$
+Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
 \end{rem}
@@
 
-\todo{Add higher genus corollaries once we figure out what we want to say there}
+\todo{Move this lemma:}
+\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
+Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
+Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
+generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\tau $.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
+
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
+										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
+\end{itemize}
+\end{lem}
 

### 2015-06-23 stacky_write_up/spin_cring.tex
More saturation 1 lemmata

@@
 Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $
-u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\tau $.
+generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.
 Then 
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$
-
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
@@
 	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
-										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
-\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
+										 &+ \langle y_i x_j \rangle \\
+										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
+\end{align*}
+\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
 \end{itemize}
 \end{lem}
+\begin{proof}
+Similar to all the other lemmas\todo{combine sections?}
+\end{proof}
+
+\begin{lem}\label{lem:add_point_effective_divisor_deg_1_but_not_deg_2_generators}
+Let $2\halfcan=K_X$ of a non-stacky curve $X$ such that $h^0(X, \halfcan) > 0$.  Then for any point $P$, 
+\[
+	H^0(X, \halfcan+P)=H^0(X,\halfcan).
+\]
+\end{lem}
+\begin{proof}
+\todo{add proof}
+\end{proof}
 
@@
 \todo{Possibly think more about this}
+	\item Generic Initial ideal (and other genericness properties?)
 \end{itemize}

### 2015-06-23 stacky_write_up/spin_cring.tex
minor changes to genus 0 base cases

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 
-\ssec{Genus 1 base cases}
-
+\ssec{Genus 1 Base Cases}
+
+In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
+We aim to inductively construct presentations by increasing the values
+
+\begin{enumerate}
+	\item $\halfcan' = 0$
+	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
+\end{enumerate}
+
+\begin{example}
+\label{eg:g_1_triv}
+In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+Let $\sx$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
+
+Here, we claim $R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k.$
+
+ and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
+
+\todo{check admissibility}
+\end{example}
+
+\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
 Let $\sx$ be a tame, seperably rooted stacky curve of genus 1.
 Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$.
-In this section, will compute the canonical ring $R_L$ in the cases that
+In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that
 \begin{enumerate}
-	\item $L = 0$
-	\item $L = P-Q$
-	\item $L = P - Q + \frac{1}{3}R$
-	\item $L = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
-	\item $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
+	\item $\halfcan' = P-Q$
+	\item $\halfcan' = 0$
+	\item $\halfcan' = P-Q$
+	\item $\halfcan' = P - Q + \frac{1}{3}R$
+	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
+	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
 \end{enumerate}
@@
 In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.
-
-\begin{example}
-\label{eg:g_1_triv}
-In the case $L = 0,$ we see immediately that $R_L \cong k[x]$ with $x$ a generator in degree 1.
-\end{example}
 

### 2015-06-23 stacky_write_up/spin_cring.tex
finish base/exception cases, add larger pic

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 \usepackage{longtable}
+\usepackage{float}
 
@@
 Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.
+generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\tau $.
 Then 
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
+
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
@@
 	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j \rangle \\
-										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
-\end{align*}
-\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
+										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
+										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
 \end{itemize}
 \end{lem}
-\begin{proof}
-Similar to all the other lemmas\todo{combine sections?}
-\end{proof}
-
-\begin{lem}\label{lem:add_point_effective_divisor_deg_1_but_not_deg_2_generators}
-Let $2\halfcan=K_X$ of a non-stacky curve $X$ such that $h^0(X, \halfcan) > 0$.  Then for any point $P$, 
-\[
-	H^0(X, \halfcan+P)=H^0(X,\halfcan).
-\]
-\end{lem}
-\begin{proof}
-\todo{add proof}
-\end{proof}
 
@@
 
+Let $I$ be the ideal generated by these relations in
+$k[x_{7, 1}, x_{7, 2}, x{5, 1}, x_{3, 1}]$. Under grlex with
+$x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$,
+the initial ideal of $I$ is
+\[
+	in_\prec(I) = < x_{5, 1}^2, x_{7, 1}^2 >
+\]
+
+To demonstrate that these two relations generate all 
+relations, we show that $\dim (R')_d = \dim
+(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d$ for all degrees
+$d \geq 0$. In particular,
+
+\begin{align*}
+	\dim (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
+	\dim (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
+	&= \dim (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / < x_{5, 1}^2,
+	x_{7, 1}^2 >
+\end{align*}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim (R')_d = \dim (k[x_{3, 1},
+x_{5, 1}, x_{7, 1}, x_{7, 2}] / < x_{5, 1}^2,	x_{7, 1}^2 >$ can
+be checked by looking at the $k$-basis at each degree $d$.
+
 Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 1}, x_{7, 2}, x{5, 1}, x_{3, 1}] / I$ with
-initial ideal
-\[
-	in_\prec(I) = < x_{7, 1} x_{3, 1}, x_{7, 1}^2 >
-\]
-
-\noindent
-generated by quadratics under grevlex with $x_{i, j} \prec x_{k, l}$
-if $i > j$ or $i = j$ and $j < l$. These quadratics must also 
-determine minimal generators for $I$ by Lemma
-~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to degree
-$e = 7$ with relations up to degree $2e = 14$, as desired.
+k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
+initial ideal $in_\prec(I)$ generated by quadratics under grlex
+with $x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$.
+These quadratics must also determine minimal generators for $I$ by
+Lemma ~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to
+degree $e = 7$ with relations up to degree $2e = 14$, as desired.
 We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
@@
 
-\todo{show only relations}
-
-Admissibility is the remaining condition to check. WLOG, we can
-let $x_{7, 1}$ correspond to the generator with maximal pole order
+Admissibility is the remaining condition to check. We can assume
+that $x_{7, 1}$ corresponds to the generator with maximal pole order
 at $P_2$ and $x_{7, 2}$ correspond to the generator with maximal
-pole order at $P_3$. Use the presentation given above with $y
-_{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$. We see that
-it immediately satisfies (Ad-i) of Definition ~\ref{defn:admissible}.
-It also satisfies (Ad-ii) because $y_{i, e_i'}$ is the only generator
-lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$ in the
-$(\deg z, -ord_{P_i}(z))$ lattice and the other generators
-must lie below the line as seen below:
-
-\begin{center}
-\includegraphics{pics/spin-377-pic-pics.pdf}
-\end{center}
+pole order at $P_3$ (relabel otherwise). Use the presentation given
+above with $y _{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
+We see that it immediately satisfies (Ad-i) of Definition
+~\ref{defn:admissible}. We may also choose pole orders of the generators
+such that $y_{i, e_i'}$ is the only generator lying on the line
+$-ord_{P_i}(z) = \deg z \frac{3d}{7}$ in the $(\deg z, -ord_{P_i}(z))$
+ lattice and with the other generators lying below the line as seen
+in Figure ~\ref{fig:377} (e.g. the pole orders $(-ord_{P_1}(z)$,
+$-ord_{P_2}(z)$, $-ord_{P_3}(z))$ may be chosen to be $(1, 1, 1)$,
+$(1, 2, 2)$, $(2, 3, 2)$, and $(2, 2, 3)$ for $x_{3, 1}, x_{5, 1},
+x_{7, 1}, x_{7, 2}$ respectively).
+
+\begin{figure}[H]
+\label{fig:377}
+\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\end{figure}
 
@@
 \halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and $\sigma_2, J_2$ is
-admissible.
+\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
+$\sigma_2, J_2$ is admissible.
 \end{example}
@@
 
-Furthermore, each case satisfies (Ad-iii) as demonstrated below.
+We can also always find a presentation for these cases such that
+they satisfy (Ad-i) and (Ad-ii) and that $in_\prec(I')$ is
+minimally generated by products of two monomials. The procedure for
+verifying these are similar to those for the given example.
+
+Furthermore, each case always satisfies (Ad-iii) as demonstrated below.
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
@@
 
-All that remains to be shown is that these cases satisfy
-(Ad-i) and (Ad-ii) and that $in_\prec(I')$ is minimally generated by
-products of two monomials. The procedure for verifying these
-are similar to those for the given example. Below, we
-give a table for the explicit generators and initial ideals.
-\todo{make table, move this before (Ad-iii)?}
+Thus, all of the cases are admissible and satisfy the additional
+desired conditions.
 \end{proof}
@@
 	S &:= \{(0; 3, 3, k; 0) : 3 \leq k \leq 9 \text{ odd}\} \\
-		&\cup \{(0; 3, b, c; 0) : 5 \leq b \leq c \leq 7\} \\
-		&\cup \{(0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
+		&\cup \{(0; 3, 5, 5; 0) ,(0; 3, 5, 7; 0), (0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
 \end{align*}
@@
 	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $3$ \\	\hline
-
-	\hline
-	\hline
-
-	$(0; 3, 7, 7; 0)$ & $\{3, 5, 7, 7\}$ & $\{10, 14\}$ & $7$ \\	\hline
 \end{longtable}
@@
 \begin{rem}
-These cases, apart from $(0; 3, 7, 7; 0)$, give all of the
-exceptions to the $e$ and $2e$ bounds on the generator and relation
-degree. Notice that each of these exceptional cases, apart from
-$(0; 3, 5, 7; 0)$, corresponds to a signature with non-generic
-saturation (i.e. saturation not equal to 3, 5, or 9 as seen
-in the table in Subsection ~\ref{ssec:g_0_saturation}). Exceptional
-saturation can be viewed as ``forcing'' generators (and thus
-relations) in higher degrees than in the generic case.
+These cases give all of the exceptions to the $e$ and $2e$ bounds on
+the generator and relation degree. Notice that each of these
+exceptional cases, apart from $(0; 3, 5, 7; 0)$, corresponds to a
+signature with non-generic saturation (i.e. saturation not equal to
+3, 5, or 9 as seen in the table in Subsection
+~\ref{ssec:g_0_saturation}). Exceptional saturation can be viewed as
+``forcing'' generators (and thus relations) in higher degrees than
+in the generic case.
 \end{rem}
@@
 Now we can combine this.
+\todo{write this section}
 
@@
 \todo{Possibly think more about this}
-	\item Generic Initial ideal (and other genericness properties?)
 \end{itemize}

### 2015-06-23 stacky_write_up/spin_cring.tex
major restructure; much to fix and transition

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Background}
@@
 
-\section{General Lemmata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive Lemmata %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inductive Lemmata}
 First we present the general inductive lemmata that will be applied
 for all genera.
+\todo{intro}
 
@@
 \end{proof}
+
+\begin{rem}
+Fact about quotient.
+\end{rem}
 
@@
 
-\begin{rem}\label{rem:minimal_quadratic_trivial_case}
+\begin{rem}
+\label{rem:minimal_quadratic_trivial_case}
 It will be useful to use lemma \ref{lem:minimal_quadratic} in the
@@
 
-TRANSITION
+Transition words.
 \todo{transition!}
 
-\ssec{Inductive Theorem: Increasing the Ramification Orders}
-\label{ssec:g_0_ram_orders}
-In this section, we aim to prove the inductive theorem, Theorem
-~\ref{thm:ram_order_ind}. Under fairly general
-conditions, this theorem will allow us to show that if Theorem ~\ref
-{thm:ram_order_ind} holds for a curve with signature
-$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
-signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
-
-\begin{defn}
-\label{defn:admissible}
-Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
-separably rooted log stacky spin
-curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
-there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
-\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
-
-$$\chi_J(i) = \begin{cases}
-	1, &\text{ if }i \in J\\
-	0, &\text{ otherwise. } 
-\end{cases}$$
-
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
-to be {\bf admissible} if the $R'$ admits a presentation
-
-\begin{align*}
-	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
-\end{align*}
-
-\noindent
-with $y_{i,e_i'} \in R'$ for each $i \in J$ such that the following
-three conditions hold.
-
-\todo{Peter: We should make the definition of admissibility be a 
-condition for the triple: $(\sx',\sx,J)$.}
-
-\begin{enumerate}
-	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
-		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
-	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
-		of $R'$ satisfies
-		\begin{align*}
-			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[(Ad-iii)] For all $i \in J$ we have
-		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
-		\end{align*}
-		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
-		where
-		\begin{align*}
-			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i - e_j'\}
-		\end{align*}
-\end{enumerate}
-\end{defn}
-
-\begin{lem}
-\label{lem:admissible_inequality}
-Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
-stronger condition that
-
-\begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
-\end{align*}
-\end{lem}
-
-\begin{proof}
-We know by (Ad-ii) that
-
-\begin{align*}
-	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
-\end{align*}
-
-\noindent
-If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
-as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
-we must have
-
-\begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
-	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
-\end{align*}
-\end{proof}
-
-\begin{lem}
-\label{lem:admissible_subset}
-If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
-then $(\sx', W)$ is also admissible.
-\end{lem}
-
-\begin{proof}
-Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
-if they hold for $J$.
-\end{proof}
-
-\begin{thm}
-\label{thm:ram_order_ind}
-Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
-curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
-R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
-Then the following are true:
-\begin{enumerate}
-	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
-		H^0(\sx, e_i(K_\sx))$ so that
-		\begin{align*}
-			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
-		\end{align*}
-		and
-		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
-			\frac{1}{\deg(y_{i,e_i})e_j'}
-		\end{align*}
-		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
-		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
-		generate $R$ over $R'$.
-	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
-		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
-		block order. Let $R = k[y,x]/I.$ Then,
-		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
-			\neq y_{i,e_i},y_{i,e_i'} \rangle
-		\end{align*}
-		as $z$ ranges over all generators of $R$.
-	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
-		products of two monomials and that for all $i \in J$, we have $e
-		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
-		minimal generators for $I'$ together with any set of relations as in 
-		part (c) minimally generate $I$.
-	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
-\end{enumerate}
-\end{thm}
-
-\begin{proof}
-Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
-question, with coarse spaces $X = X'$. 
-\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
-Define
-
-\begin{align*}
-	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
-\end{align*}
-
-\noindent
-Define
-\begin{align*}
-	E_i = \sum_{j \in S(i,0)}^{}Q_j
-\end{align*}
-
-\noindent
-Note that
-\begin{align*}
-	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
-\end{align*}
-
-\noindent
-and so we obtain an inclusion
-\begin{align*}
-	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
-H^0(\sx,e_iL).
-\end{align*}\todo{Peter: should be $Q_i$?}
-
-\noindent
-The assumption (Ad-iii) implies
-\begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g-1
-\end{align*}
-
-\noindent
-implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
-\begin{align*}
-	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
-\end{align*}
-
-\noindent
-satisfies
-\begin{align*}
-	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
-	\frac{e_i - 1}{2}
-\end{align*}
-
-\noindent
-Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
-
-We next show $y_{i,e_i}$ also satisfies the second part of the
-claim of $(a),$ by considering separately the cases of whether $j
-\in S(i,0),$ and $j \notin S(i,0)$.
-
-If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
-(\sx',e_iL'-E_i + Q_i)$,
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
-	\subhalf{e_j'} - \frac{1}{e_j'}.
-\end{align*}
-
-If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
-$e_i\subhalf{e_j'} \notin \BZ$, so
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
-	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
-\end{align*}
-
-\noindent
-completing the proof of (a).
-
-Next, define $R_0 = R'$ and inductively define 
-$$R_i = \begin{cases}
-	R_{i-1} &\text{ if }i \notin J\\
-	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
-\end{cases}$$
-
-\noindent
-To prove (b), it suffices to show that elements of the form $y_{i,e_
-i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
-and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
-vector space. These elements do not lie in $R_{i-1}$ because their
-order of pole at $Q_i$ is bigger than the order of any element in $R
-_{i-1}$, and are linearly independent amongst themselves because of
-injectivity of the linear map
-
-\begin{align*}
-	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
-	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
-	\begin{pmatrix}
-		e_i-2 & \frac{e_i-3}{2} \\
-		e_i	 & \frac{e_i-1}{2}
-	\end{pmatrix} 
-\end{align*}
-
-\noindent
-The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
-b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
-integer lattice points in the cone generated by the vectors $\left(e
-_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
-\right)$ is saturated, as the corresponding determinant is
-\begin{align*}
-	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
-\end{align*}
-completing part (b).
-
-To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
-i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
-all $j \in J$ we have
-\begin{align*}
-	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
-\end{align*}
-
-\noindent
-We now check this in three cases, depending on whether $j \notin \{
-i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
-
-\vskip.1in
-\noindent
-{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
-
-Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
-	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 2: $j =i.$}
-
-By part (a), condition (Ad-ii), and Lemma
-~\ref{lem:admissible_inequality} we have
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
-	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 3: $j \in S(i,0).$}
-
-In this case, we may first assume $z \neq y_{j,e_j}$, 
-as this is covered by case 2, with $i$ and $j$ reversed. 
-Hence, 
-\begin{align*}
-	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
-\end{align*}
-implying
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
-	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
-	= \deg (y_{i,e_i}z) \subhalf{e_j'},
-\end{align*}
-completing part (c).
-
-Next, note that the minimal generators of $I'$ together with the
-new generators of $I$ given in (c) have independent initial terms
-by construction, and therefore are minimal by Lemma
-~\ref{lem:minimal_quadratic}.
-
-Finally, to check (e), we will first show that $(\sx,J)$ is
-admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
-i,e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
-strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
-Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
-definition. This is where we use that (Ad-iii) holds for $d > 0$
-and not just for $d = 0$.
-
-Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
-$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
-\end{proof}
-
-\section{Genus one}
-We now consider the case when the genus is positive. The genus zero
-case is the most complicated and reserve that for Section ~\ref{sec:g_0_effective}
-and Section ~\ref{sec:g_0_non_effective}. We begin with the genus one case.
-
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
-We prove an inductive theorem on adding 2-sat here.
-\todo{description}
-
-\begin{prop}
-\label{prop:sat_two_induction}
-Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
-$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
-Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
-, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
-3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
-Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
-\end{align*}
-Then, the following statements hold.
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
-		y_3$
-		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order so that $R = k[y_3, y_4, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_4^2.\rangle
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.}
-
-In a fashion analogous to the proof of Proposition 
-~\ref{prop:sat_three_induction}, we see 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:sat_two_add_generator}
-	\begin{split}
-		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \\
-		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
-	\end{split}
-\end{align}
-
-\noindent completing part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B y_3^2 x_2 \\
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
-\ssec{Genus 1 Base Cases}
-
-In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values
-
-\begin{enumerate}
-	\item $\halfcan' = 0$
-	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
-\end{enumerate}
-
-\begin{example}
-\label{eg:g_1_triv}
-In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
-\end{example}
-
-\begin{example}
-Let $\sx$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
-
-Here, we claim $R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k.$
-
- and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
-
-\todo{check admissibility}
-\end{example}
-
-\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
-Let $\sx$ be a tame, seperably rooted stacky curve of genus 1.
-Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$.
-In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that
-\begin{enumerate}
-	\item $\halfcan' = P-Q$
-	\item $\halfcan' = 0$
-	\item $\halfcan' = P-Q$
-	\item $\halfcan' = P - Q + \frac{1}{3}R$
-	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
-	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
-\end{enumerate}
-In addition to being illustrative examples, these will serve as the base cases of induction, in order to compute generators and relations for an arbitrary genus 1, stacky log half canonical divisor.
-In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.
-
-\begin{example}
-\label{eg:g_1_half_can}
-In the case $L=P - Q.$ Then, we have $R_{(2k+1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
-\end{example}
-
-\begin{example}
-\label{eg:g_1_deg_third}
-Let $L = P - Q + \frac{1}{3}R$.
-Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$.
-For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{Peter: Why don't we have something in degree 4?}
-\end{example}
-
-\begin{example}
-\label{}
-Let $L = P - Q + \frac{e-1}{2e}R_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
-Furthermore, $\deg u = 2, \deg y_i = i$.
-\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.} \todo{Check admissibility}
-\end{example}
-
-\begin{example}
-Let $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
-Here, we claim $R_L \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k$, and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
-\todo{Explain why this forms a system of generators and relations, and also state more clearly what $y_i$ are.} \todo{check admissibility}
-\end{example}
-
-\ssec{Main Theorem for Genus 1}
-
-\section{High genus}
+\ssec{Inductive Lemmata: Adding Points}
+\label{ssec:add_pts}
+In this section, we prove various inductive statements about
+generators and relations with respect to adding points.
 
@@
 \end{enumerate}
-
 \end{lem}
+
 \begin{proof}
@@
 
-\begin{lem}\label{lem:adding_points_saturation_2_to_1_no_log}
+\begin{lem}
+\label{lem:adding_points_saturation_2_to_1_no_log}
 Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
@@
 
-\ssec{Bounds on Generators and Relations in high genus}
-
-\begin{lem}
-\label{lem:semicanonical_generation} \cite{neves:halfcan}[Proposition III.4]
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, for $n \geq 5$, the map
-\begin{align*}
-	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective.
-In particular, $R_L$ is generated in degree at most $6$.
-\end{lem}
-\iffalse
-\begin{proof}
-Therefore, to show there are no new generators in degree at least $7$, it suffices to show that for $n \geq 5$, the map
-\begin{align*}
-	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
-Since $K$ is basepoint free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
-Then, by the basepoint free pencil trick, we obtain an exact sequence
-$$\begin{tikzcd}
-0 \ar r & H^0((n-2)L) \ar r & V \otimes H^0(nL) \ar{r}{f} & H^0((n+2)L)
-\end{tikzcd}$$
-We wish to show $f$ is surjective.
-Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption that $n \geq 5$.
-Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n-1)(g-1)$, again using Riemann--Roch.
-Therefore, $$\dim \im f = 2 \cdot (n-1)(g-1) -(n-3)(g-1) = (n+1)(g-1) = \dim H^0((n+2)L),$$
-again using Riemann-Roch, implying $f$ is surjective.
-\end{proof}
-\fi
-
-\begin{rem}
-In \cite{neves:halfcan}[Proposition III.4], Neves claims to prove that $R_L$ is generated in degree at most 5.
-However, when the proof is carefully examined, it only shows generation in degree at most 6.
-For this reason, we only state Lemma ~\ref{lem:semicanonical_generation} as generation in degree at most 6.
-We next proceed to show this can be reduced to generation in degree 5.
-The trickiest case is genus 2, which we address next.
-\end{rem}
+Transition to genus one.
+\todo{transition!}
+
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
+We prove an inductive theorem on adding 2-sat here.
+\todo{description}
 
 \begin{prop}
-\label{prop:genus_2_generation_5}
-Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
-Then, $R_L$ is generated in degree at most $5$.
+\label{prop:sat_two_induction}
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
+$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
+, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
+3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
+\end{align*}
+Then, the following statements hold.
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
+		y_3$
+		and equip the ring $k[y_3, y_4, x]$ with the block 
+		order so that $R = k[y_3, y_4, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x, y_3, y_4] \\
+			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_4^2.\rangle
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
 \end{prop}
-\begin{proof}
-By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
-Let $P_1,\ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
-Recall that all spin divisors on $X$ can be written as 
-$$L = P_1 + \sum_{i=2}^{6} \epsilon_i (P_1 - P_i),$$ 
-with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
-Note that $H^0(X,K)$ is spanned by rational functions $u,x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
-\begin{align*}
-	Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
-\end{align*}
-is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2,x^3$, 
-which have $\di u^3|_{2L} = -2L, \di u^2x|_{2L} = -2L + 2P_1,\di ux^2|_{2L} = -2L+4P_1, \di x^3|_{2L} = -2L + 6P_1.$ 
-Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
-it suffices to produce one more independent function in the image of the multiplication map.
-There are now two cases, depending on whether $H^0(X,L) = 0$.
-
-First, we deal with the case that $H^0(X,L) \neq 0$. 
-Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
-Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed.
-In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
-
-Second, suppose $H^0(X,L) = 0$.
-Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
-Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
-with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
-exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
-Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
-order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
-\end{proof}
-
-\begin{lem}
-\label{lem:generation_5}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, $R_L$ is generated in degree at most $5$.
-\end{lem}
-\begin{proof}
-If $g = 2$ then the claim follows from 
-Proposition ~\ref{prop:genus_2_generation_5}.
-However, if $g > 2$, then by \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective, so again there are no new generators in degree 6.
-\end{proof}
-
-\todo{This should be $k[x_1,\ldots, x_n]$ instead of $\sym H^0$.}
-\begin{lem}
-\label{lem:reducing_degree}
-Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$.
-Choose generators $x_1,\ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1,\ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and $J_{L,d} = \sum_{j = 1}^{d-1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ Let for any $f \in k[x_1, \ldots, x_n]$ with $\deg f \geq 12,$ there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
-\end{lem}
-\begin{proof}
-Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
-By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i=1}^{n}a_ix_i$ with $a_i \in k[x_1,\ldots, x_n]_{d-\deg x_i}$.
-We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i- 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
-Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$. By Lemma ~\ref{lem:semicanonical_generation},
-\begin{align*}
-	V \otimes H^0((\deg f-\deg x_i-2)L) \rightarrow H^0((\deg f-\deg x_i)L)
-\end{align*}
-is surjective, since $\deg f - \deg a_i - 2 \geq 12 - 5 - 2 = 5$.
-In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Chosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
-
-Finally, we may then take $g = \sum_{i}^{}g_ix_i,h = \sum_{i}^{}h_ix_i,$ so that 
-\begin{align*}
-	f &\equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \\
-	&\equiv s_1 g + s_2 h \bmod J_{L,d}.
-\end{align*}
-\end{proof}
-
-\begin{prop}
-\label{prop:relations_generation}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
-\end{prop}
-\begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
-Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
-$$\begin{tikzcd}
-V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
-\end{tikzcd}$$
-we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
-So, using the refined version of the basepoint free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
-Therefore,
-\begin{align*}
-	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
-\end{align*}
-\end{proof}
-
-\begin{rem}
-\label{rem:relations_generation_ten}
-In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relations_generation}, that $I_L$ is generated in degree at most 11 is close to sharp.
-\end{rem}
-
-\ssec{Main theorem for high genus}
-
-\section{Genus Zero Effective}
-\label{sec:g_0_effective}
-Now we consider the genus zero case.
-\todo{write intro}
-
-In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
-when $\Delta$ is a non- zero effective divisor.  Using this, we can 
-reduce to looking at effective stacky divisors.  Then, applying a 
-result for general effective $\mathbf{Q}$ divisors, we deduce that $
-R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
-relations generated up to degree $2e$ with initial terms quadratic 
-in the generators.  We also demonstrate that these bounds are tight 
-up to \todo{insert how tight they are}.
-
-We have Lemma ~\ref{lem:minimal_quadratic}.
-\todo{fill in hole here}
+
+\begin{proof}
+The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
+_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.}
+
+In a fashion analogous to the proof of Proposition 
+~\ref{prop:sat_three_induction}, we see 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:sat_two_add_generator}
+	\begin{split}
+		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \\
+		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
+	\end{split}
+\end{align}
+
+\noindent completing part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B y_3^2 x_2 \\
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
+Transition words.
+\todo{transition!}
 
@@
 
+\todo{do these corollaries fit here?}
+
 \begin{cor}\label{cor:genus_0_posiive_delta}
@@
 \end{proof}
+
+Transition words.
+\todo{transition!}
+
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
+\label{ssec:g_0_ram_pts}
+
+\begin{prop}
+\label{prop:sat_three_induction}
+\todo{Make explicit assumptions on genus.}
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
+Actually, the map isn't ramified at $P$, it's just defined away from $P$.
+I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
+3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
+\end{align*}
+Then, the following statements hold.
+
+\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
+
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
+		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.} To complete the proof of (a) we only need 
+show these elements generate $R$ over $R'$. We can first see that 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:add_one_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+	\end{split}
+\end{align}
+
+\noindent
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+,$ elements of degree $d$ in the claimed basis of
+~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+\rfloor $ and $b = d \bmod 3$, we have that the elements
+
+\begin{align*}
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+3+b}
+\end{align*}
+
+\noindent
+are precisely $a$ elements, which are all independent as they have
+distinct pole orders at $P$. This completes part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:add_one_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_{i,j} \in k$ for $4
+\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B_1 y_3 y_5 \\
+	y_4y_5 &+ B_2 y_3^2 x_3 \\
+	y_5^2 &+ B_3 y_3^2 x_4
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
+Transition words.
+\todo{transition!}
+
+\ssec{Inductive Lemma: Raising Ramification Orders}
+\label{ssec:ram_orders}
+In this section, we aim to prove the inductive theorem, Theorem
+~\ref{thm:ram_order_ind}. Under fairly general
+conditions, this theorem will allow us to show that if Theorem ~\ref
+{thm:ram_order_ind} holds for a curve with signature
+$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
+signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
+
+\begin{defn}
+\label{defn:admissible}
+Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
+separably rooted log stacky spin
+curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
+there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
+\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
+
+$$\chi_J(i) = \begin{cases}
+	1, &\text{ if }i \in J\\
+	0, &\text{ otherwise. } 
+\end{cases}$$
+
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
+to be {\bf admissible} if the $R'$ admits a presentation
+
+\begin{align*}
+	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
+\end{align*}
+
+\noindent
+with $y_{i,e_i'} \in R'$ for each $i \in J$ such that the following
+three conditions hold.
+
+\todo{Peter: We should make the definition of admissibility be a 
+condition for the triple: $(\sx',\sx,J)$.}
+
+\begin{enumerate}
+	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
+		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
+	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
+		of $R'$ satisfies
+		\begin{align*}
+			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[(Ad-iii)] For all $i \in J$ we have
+		\begin{align*}
+			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+		\end{align*}
+		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
+		where
+		\begin{align*}
+			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i - e_j'\}
+		\end{align*}
+\end{enumerate}
+\end{defn}
+
+\begin{lem}
+\label{lem:admissible_inequality}
+Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
+stronger condition that
+
+\begin{align*}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
+\end{align*}
+\end{lem}
+
+\begin{proof}
+We know by (Ad-ii) that
+
+\begin{align*}
+	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
+\end{align*}
+
+\noindent
+If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
+as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
+e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
+we must have
+
+\begin{align*}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
+	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
+\end{align*}
+\end{proof}
+
+\begin{lem}
+\label{lem:admissible_subset}
+If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
+then $(\sx', W)$ is also admissible.
+\end{lem}
+
+\begin{proof}
+Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
+if they hold for $J$.
+\end{proof}
+
+\begin{thm}
+\label{thm:ram_order_ind}
+Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
+curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
+R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
+Then the following are true:
+\begin{enumerate}
+	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
+		H^0(\sx, e_i(K_\sx))$ so that
+		\begin{align*}
+			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
+		\end{align*}
+		and
+		\begin{align*}
+			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
+			\frac{1}{\deg(y_{i,e_i})e_j'}
+		\end{align*}
+		for all $j \in J$ with $j \neq i$.
+	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
+		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
+		generate $R$ over $R'$.
+	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
+		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
+		block order. Let $R = k[y,x]/I.$ Then,
+		\begin{align*}
+			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
+			\neq y_{i,e_i},y_{i,e_i'} \rangle
+		\end{align*}
+		as $z$ ranges over all generators of $R$.
+	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
+		products of two monomials and that for all $i \in J$, we have $e
+		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
+		minimal generators for $I'$ together with any set of relations as in 
+		part (c) minimally generate $I$.
+	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
+\end{enumerate}
+\end{thm}
+
+\begin{proof}
+Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
+question, with coarse spaces $X = X'$. 
+\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
+Define
+
+\begin{align*}
+	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+\end{align*}
+
+\noindent
+Define
+\begin{align*}
+	E_i = \sum_{j \in S(i,0)}^{}Q_j
+\end{align*}
+
+\noindent
+Note that
+\begin{align*}
+	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
+\end{align*}
+
+\noindent
+and so we obtain an inclusion
+\begin{align*}
+	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
+H^0(\sx,e_iL).
+\end{align*}\todo{Peter: should be $Q_i$?}
+
+\noindent
+The assumption (Ad-iii) implies
+\begin{align*}
+	\deg \left( e_i L' - E_i \right) \geq 2g-1
+\end{align*}
+
+\noindent
+implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
+Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
+\begin{align*}
+	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
+\end{align*}
+
+\noindent
+satisfies
+\begin{align*}
+	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
+	\frac{e_i - 1}{2}
+\end{align*}
+
+\noindent
+Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
+
+We next show $y_{i,e_i}$ also satisfies the second part of the
+claim of $(a),$ by considering separately the cases of whether $j
+\in S(i,0),$ and $j \notin S(i,0)$.
+
+If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
+(\sx',e_iL'-E_i + Q_i)$,
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
+	\subhalf{e_j'} - \frac{1}{e_j'}.
+\end{align*}
+
+If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
+$e_i\subhalf{e_j'} \notin \BZ$, so
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
+\end{align*}
+
+\noindent
+completing the proof of (a).
+
+Next, define $R_0 = R'$ and inductively define 
+$$R_i = \begin{cases}
+	R_{i-1} &\text{ if }i \notin J\\
+	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
+\end{cases}$$
+
+\noindent
+To prove (b), it suffices to show that elements of the form $y_{i,e_
+i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
+and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
+vector space. These elements do not lie in $R_{i-1}$ because their
+order of pole at $Q_i$ is bigger than the order of any element in $R
+_{i-1}$, and are linearly independent amongst themselves because of
+injectivity of the linear map
+
+\begin{align*}
+	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
+	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
+	\begin{pmatrix}
+		e_i-2 & \frac{e_i-3}{2} \\
+		e_i	 & \frac{e_i-1}{2}
+	\end{pmatrix} 
+\end{align*}
+
+\noindent
+The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
+b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
+integer lattice points in the cone generated by the vectors $\left(e
+_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
+\right)$ is saturated, as the corresponding determinant is
+\begin{align*}
+	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
+\end{align*}
+completing part (b).
+
+To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
+i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
+all $j \in J$ we have
+\begin{align*}
+	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
+\end{align*}
+
+\noindent
+We now check this in three cases, depending on whether $j \notin \{
+i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
+
+\vskip.1in
+\noindent
+{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
+
+Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
+	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
+\end{align*}
+
+\vskip.1in
+\noindent
+{\sf Case 2: $j =i.$}
+
+By part (a), condition (Ad-ii), and Lemma
+~\ref{lem:admissible_inequality} we have
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
+	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
+	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
+	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
+	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
+\end{align*}
+
+\vskip.1in
+\noindent
+{\sf Case 3: $j \in S(i,0).$}
+
+In this case, we may first assume $z \neq y_{j,e_j}$, 
+as this is covered by case 2, with $i$ and $j$ reversed. 
+Hence, 
+\begin{align*}
+	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
+\end{align*}
+implying
+\begin{align*}
+	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
+	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
+	= \deg (y_{i,e_i}z) \subhalf{e_j'},
+\end{align*}
+completing part (c).
+
+Next, note that the minimal generators of $I'$ together with the
+new generators of $I$ given in (c) have independent initial terms
+by construction, and therefore are minimal by Lemma
+~\ref{lem:minimal_quadratic}.
+
+Finally, to check (e), we will first show that $(\sx,J)$ is
+admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
+i,e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
+strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
+Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
+definition. This is where we use that (Ad-iii) holds for $d > 0$
+and not just for $d = 0$.
+
+Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
+$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% High genus %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{High genus}
+
+\ssec{Bounds on Generators and Relations in high genus}
+
+\begin{lem}
+\label{lem:semicanonical_generation} \cite{neves:halfcan}[Proposition III.4]
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, for $n \geq 5$, the map
+\begin{align*}
+	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
+\end{align*}
+is surjective.
+In particular, $R_L$ is generated in degree at most $6$.
+\end{lem}
+\iffalse
+\begin{proof}
+Therefore, to show there are no new generators in degree at least $7$, it suffices to show that for $n \geq 5$, the map
+\begin{align*}
+	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
+\end{align*}
+is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
+Since $K$ is basepoint free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
+Then, by the basepoint free pencil trick, we obtain an exact sequence
+$$\begin{tikzcd}
+0 \ar r & H^0((n-2)L) \ar r & V \otimes H^0(nL) \ar{r}{f} & H^0((n+2)L)
+\end{tikzcd}$$
+We wish to show $f$ is surjective.
+Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption that $n \geq 5$.
+Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n-1)(g-1)$, again using Riemann--Roch.
+Therefore, $$\dim \im f = 2 \cdot (n-1)(g-1) -(n-3)(g-1) = (n+1)(g-1) = \dim H^0((n+2)L),$$
+again using Riemann-Roch, implying $f$ is surjective.
+\end{proof}
+\fi
+
+\begin{rem}
+In \cite{neves:halfcan}[Proposition III.4], Neves claims to prove that $R_L$ is generated in degree at most 5.
+However, when the proof is carefully examined, it only shows generation in degree at most 6.
+For this reason, we only state Lemma ~\ref{lem:semicanonical_generation} as generation in degree at most 6.
+We next proceed to show this can be reduced to generation in degree 5.
+The trickiest case is genus 2, which we address next.
+\end{rem}
+
+\begin{prop}
+\label{prop:genus_2_generation_5}
+Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
+Then, $R_L$ is generated in degree at most $5$.
+\end{prop}
+\begin{proof}
+By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
+Let $P_1,\ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
+Recall that all spin divisors on $X$ can be written as 
+$$L = P_1 + \sum_{i=2}^{6} \epsilon_i (P_1 - P_i),$$ 
+with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
+Note that $H^0(X,K)$ is spanned by rational functions $u,x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
+\begin{align*}
+	Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
+\end{align*}
+is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2,x^3$, 
+which have $\di u^3|_{2L} = -2L, \di u^2x|_{2L} = -2L + 2P_1,\di ux^2|_{2L} = -2L+4P_1, \di x^3|_{2L} = -2L + 6P_1.$ 
+Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
+it suffices to produce one more independent function in the image of the multiplication map.
+There are now two cases, depending on whether $H^0(X,L) = 0$.
+
+First, we deal with the case that $H^0(X,L) \neq 0$. 
+Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
+Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed.
+In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
+
+Second, suppose $H^0(X,L) = 0$.
+Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
+Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
+we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
+with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
+exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
+Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
+order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
+\end{proof}
+
+\begin{lem}
+\label{lem:generation_5}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, $R_L$ is generated in degree at most $5$.
+\end{lem}
+\begin{proof}
+If $g = 2$ then the claim follows from 
+Proposition ~\ref{prop:genus_2_generation_5}.
+However, if $g > 2$, then by \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective, so again there are no new generators in degree 6.
+\end{proof}
+
+\todo{This should be $k[x_1,\ldots, x_n]$ instead of $\sym H^0$.}
+\begin{lem}
+\label{lem:reducing_degree}
+Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$.
+Choose generators $x_1,\ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1,\ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and $J_{L,d} = \sum_{j = 1}^{d-1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ Let for any $f \in k[x_1, \ldots, x_n]$ with $\deg f \geq 12,$ there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+\end{lem}
+\begin{proof}
+Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
+By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i=1}^{n}a_ix_i$ with $a_i \in k[x_1,\ldots, x_n]_{d-\deg x_i}$.
+We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i- 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
+Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$. By Lemma ~\ref{lem:semicanonical_generation},
+\begin{align*}
+	V \otimes H^0((\deg f-\deg x_i-2)L) \rightarrow H^0((\deg f-\deg x_i)L)
+\end{align*}
+is surjective, since $\deg f - \deg a_i - 2 \geq 12 - 5 - 2 = 5$.
+In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
+Chosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+
+Finally, we may then take $g = \sum_{i}^{}g_ix_i,h = \sum_{i}^{}h_ix_i,$ so that 
+\begin{align*}
+	f &\equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \\
+	&\equiv s_1 g + s_2 h \bmod J_{L,d}.
+\end{align*}
+\end{proof}
+
+\begin{prop}
+\label{prop:relations_generation}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
+\end{prop}
+\begin{proof}
+Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
+Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
+$$\begin{tikzcd}
+V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
+\end{tikzcd}$$
+we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
+So, using the refined version of the basepoint free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
+Therefore,
+\begin{align*}
+	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
+\end{align*}
+\end{proof}
+
+\begin{rem}
+\label{rem:relations_generation_ten}
+In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
+Therefore, the bound from Proposition ~\ref{prop:relations_generation}, that $I_L$ is generated in degree at most 11 is close to sharp.
+\end{rem}
+
+\ssec{Main theorem for high genus}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus one %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Genus one}
+We now consider the case when the genus is positive. The genus zero
+case is the most complicated and reserve that for Section ~\ref{sec:g_0_effective}
+and Section ~\ref{sec:g_0_non_effective}. We begin with the genus one case.
+
+\ssec{Genus 1 Base Cases}
+
+In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
+We aim to inductively construct presentations by increasing the values
+
+\begin{enumerate}
+	\item $\halfcan' = 0$
+	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
+\end{enumerate}
+
+\begin{example}
+\label{eg:g_1_triv}
+In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+Let $\sx$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
+
+Here, we claim $R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k.$
+
+ and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
+
+\todo{check admissibility}
+\end{example}
+
+\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
+Let $\sx$ be a tame, seperably rooted stacky curve of genus 1.
+Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$.
+In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that
+\begin{enumerate}
+	\item $\halfcan' = P-Q$
+	\item $\halfcan' = 0$
+	\item $\halfcan' = P-Q$
+	\item $\halfcan' = P - Q + \frac{1}{3}R$
+	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
+	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
+\end{enumerate}
+In addition to being illustrative examples, these will serve as the base cases of induction, in order to compute generators and relations for an arbitrary genus 1, stacky log half canonical divisor.
+In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.
+
+\begin{example}
+\label{eg:g_1_half_can}
+In the case $L=P - Q.$ Then, we have $R_{(2k+1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
+\end{example}
+
+\begin{example}
+\label{eg:g_1_deg_third}
+Let $L = P - Q + \frac{1}{3}R$.
+Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$.
+For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
+We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{Peter: Why don't we have something in degree 4?}
+\end{example}
+
+\begin{example}
+\label{}
+Let $L = P - Q + \frac{e-1}{2e}R_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+Furthermore, $\deg u = 2, \deg y_i = i$.
+\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.} \todo{Check admissibility}
+\end{example}
+
+\begin{example}
+Let $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
+Here, we claim $R_L \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k$, and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
+\todo{Explain why this forms a system of generators and relations, and also state more clearly what $y_i$ are.} \todo{check admissibility}
+\end{example}
+
+\ssec{Main Theorem for Genus 1}
+Words.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus zero %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Genus Zero Effective}
+\label{sec:g_0_effective}
+Now we consider the genus zero case.
+\todo{write intro}
+
+In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
+when $\Delta$ is a non- zero effective divisor.  Using this, we can 
+reduce to looking at effective stacky divisors.  Then, applying a 
+result for general effective $\mathbf{Q}$ divisors, we deduce that $
+R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
+relations generated up to degree $2e$ with initial terms quadratic 
+in the generators.  We also demonstrate that these bounds are tight 
+up to \todo{insert how tight they are}.
+
+We have Lemma ~\ref{lem:minimal_quadratic}.
+\todo{fill in hole here, with adding points too}
 
@@
 
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
-\label{ssec:g_0_ram_pts}
-
-\begin{prop}
-\label{prop:sat_three_induction}
-\todo{Make explicit assumptions on genus.}
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
-Actually, the map isn't ramified at $P$, it's just defined away from $P$.
-I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
-3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-Then, the following statements hold.
-
-\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
-\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
-		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
-			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
-_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.} To complete the proof of (a) we only need 
-show these elements generate $R$ over $R'$. We can first see that 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
-	\end{split}
-\end{align}
-
-\noindent
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
-_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-,$ elements of degree $d$ in the claimed basis of
-~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-\rfloor $ and $b = d \bmod 3$, we have that the elements
-
-\begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
-3+b}
-\end{align*}
-
-\noindent
-are precisely $a$ elements, which are all independent as they have
-distinct pole orders at $P$. This completes part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_{i,j} \in k$ for $4
-\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B_1 y_3 y_5 \\
-	y_4y_5 &+ B_2 y_3^2 x_3 \\
-	y_5^2 &+ B_3 y_3^2 x_4
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
+\todo{transition}
 Here we describe induction of raising degrees from Theorem ~\ref{thm:ram_order_ind}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Acknowledgments}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \nocite{*}

### 2015-06-23 stacky_write_up/spin_cring.tex
reorganized some lemmas and sections

@@
 %
-
-\begin{rem}
-\label{rem:minimal_quadratic_trivial_case}
-It will be useful to use lemma \ref{lem:minimal_quadratic} in the
-case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
-are $k$-minimal generators for $I'$ (over the trivial base vector
-space).  
-\end{rem}
+%
+%\begin{rem}
+%\label{rem:minimal_quadratic_trivial_case}
+%It will be useful to use lemma \ref{lem:minimal_quadratic} in the
+%case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
+%are $k$-minimal generators for $I'$ (over the trivial base vector
+%space).  
+%\end{rem}
 
@@
 \ssec{Inductive Theorem: Adding points for high genus}
+
+\begin{lem}
+\label{lem:deg1_sat_ind}
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
+defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
+satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
+generator $u$ in degree 1.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
+that
+
+\begin{equation}
+\label{eqn:deg1_sat_ind_dim}
+	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
+	N} : d \ge \frac{\beta}{\alpha}.
+\end{equation}
+Let 
+\[
+	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+\]
+be the non-negative best lower approximation.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
+
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
+										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
+\end{itemize}
+\end{lem}
+
+\begin{proof}
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
+These can be chosen generically to not have a zero at $P$ \todo{
+check that we can actually do this, or eliminate if it turns out to
+be unnecessary}.
+
+Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
+{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
+our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
+\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+
+\[
+	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
+\]
+
+\noindent
+so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
+order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
+\beta} \rfloor \}$. We can use a method similar to O'Dorney to
+construct the $y_i$'s as desired: \todo{cite where}
+
+Let 
+\[
+	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+\beta}
+\] 
+be the non-negative best lower approximation of $\frac{
+\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
+orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
+c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
+each other and $(R_D)_d$, so by degree considerations, they span
+$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
+
+For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
+by construction, so any product of $\prod z_i$ of elements of
+degrees less than $d_i$ must have 
+\[
+	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
+\]
+so we have the pole order of $\prod z_i$ is 
+\[
+	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
+\] 
+Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
+lower degrees.  
+Generically choose some $y_i \in(R_{
+D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
+\[
+	-\ord_P(y_i)= \max(c_j:d_j=1)
+\]
+and if more than one $d_i$ is 1, we
+must also choose them generically so they generate $(R_{D'})_1$).
+
+Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
+\beta}$ not a best lower approximation.  Then choose
+best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
+maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
+this we can deduce that 
+\[
+	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
+\]  
+Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
+has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
+\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
+where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+\rfloor + 1}$.  
+Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+\frac{\alpha}{\beta}$ is not a best lower approximation than we can
+construct an element in degree $d$ with pole degree $c$ by either $y
+_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
+same conditions.  We notice that elements of this form are all
+linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
+$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
+$R_{D'}$.
+
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
+corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
+paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
+$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
+$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
+successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
+\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
+\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
+convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
+with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
+is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
+expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
+is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
+\[
+	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
+\]
+giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
+the beginning}
+
+Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
+$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
+u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
++c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
++1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
+$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
+$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
+larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
++c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
+d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
+(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
+$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
+follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
+$ to find
+\[
+	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
+u^{b_l}\in R_D
+\]
+implying a relation with initial term $y_i y_j$.
+
+Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
++1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
+y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
+the same method as the previous two paragraphs we find
+\[
+	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
+\]
+Similarly if $i=1$, then we get the same result using
+\[
+	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
+\]
+In both cases we deduce that $y_iy_j$ is an initial term of some relation.
+
+Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
+\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
+power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
+that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
+proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
+$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
+previous paragraphs we find
+\[
+	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
+\]
+Similarly if $i=1$ then
+\[
+	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
+\]
+In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
+
+Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
+terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
+x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
+non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
+$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
+some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
+$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
+relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
+{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
+\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
+elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
+u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
+y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
+we see that $J'$ is the initial ideal of $I'$.
+
+In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
+\todo{What about $\frac{\alpha}{\beta}>1$?}
+\end{proof}
 
@@
 
+\begin{lem}
+\label{lem:sat_three_induction}
+\todo{Make explicit assumptions on genus.}
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
+Actually, the map isn't ramified at $P$, it's just defined away from $P$.
+I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
+3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
+\end{align*}
+Then, the following statements hold.
+
+\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
+
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
+		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.} To complete the proof of (a) we only need 
+show these elements generate $R$ over $R'$. We can first see that 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:add_one_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+	\end{split}
+\end{align}
+
+\noindent
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+,$ elements of degree $d$ in the claimed basis of
+~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+\rfloor $ and $b = d \bmod 3$, we have that the elements
+
+\begin{align*}
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+3+b}
+\end{align*}
+
+\noindent
+are precisely $a$ elements, which are all independent as they have
+distinct pole orders at $P$. This completes part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:add_one_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_{i,j} \in k$ for $4
+\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B_1 y_3 y_5 \\
+	y_4y_5 &+ B_2 y_3^2 x_3 \\
+	y_5^2 &+ B_3 y_3^2 x_4
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
 Transition to genus one.
@@
 
+\todo{Move this lemma:}
+\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
+Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
+Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
+generator $u$ in degree 1 and $R_{\halfcan'}$ has no new generators in degree 1.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 &+ \langle y_i x_j \rangle \\
+										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
+\end{align*}
+\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
+\end{itemize}
+\end{lem}
+\begin{proof}
+Similar to all the other lemmas\todo{combine sections?}
+\end{proof}
+
 Transition words.
@@
 reference} and O'Dorney\todo{reference}.
-
-\begin{lem}
-\label{lem:deg1_sat_ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
-defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
-generator $u$ in degree 1.  Suppose $D$ is generated by $
-u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
-that
-
-\begin{equation}
-\label{eqn:deg1_sat_ind_dim}
-	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
-	N} : d \ge \frac{\beta}{\alpha}.
-\end{equation}
-Let 
-\[
-	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
-\]
-be the non-negative best lower approximation.
-Then 
-\begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$
-
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
-										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
-\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
-\end{itemize}
-\end{lem}
-
-\begin{proof}
-Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{
-check that we can actually do this, or eliminate if it turns out to
-be unnecessary}.
-
-Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
-{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
-our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
-\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
-
-\[
-	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
-\]
-
-\noindent
-so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
-order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We can use a method similar to O'Dorney to
-construct the $y_i$'s as desired: \todo{cite where}
-
-Let 
-\[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-\beta}
-\] 
-be the non-negative best lower approximation of $\frac{
-\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
-orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
-each other and $(R_D)_d$, so by degree considerations, they span
-$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
-
-For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
-by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have 
-\[
-	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
-\]
-so we have the pole order of $\prod z_i$ is 
-\[
-	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
-\] 
-Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees.  
-Generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
-\[
-	-\ord_P(y_i)= \max(c_j:d_j=1)
-\]
-and if more than one $d_i$ is 1, we
-must also choose them generically so they generate $(R_{D'})_1$).
-
-Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ not a best lower approximation.  Then choose
-best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
-maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
-this we can deduce that 
-\[
-	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
-\]  
-Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
-has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
-\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
-where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
-\rfloor + 1}$.  
-Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
-\frac{\alpha}{\beta}$ is not a best lower approximation than we can
-construct an element in degree $d$ with pole degree $c$ by either $y
-_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-same conditions.  We notice that elements of this form are all
-linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
-$R_{D'}$.
-
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
-corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
-paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
-$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
-$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
-successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
-convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
-expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
-is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
-\[
-	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-\]
-giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
-the beginning}
-
-Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
-$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
-u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
-+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
-+1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
-$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
-$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
-larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
-+c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
-d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
-(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
-$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
-follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
-$ to find
-\[
-	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-u^{b_l}\in R_D
-\]
-implying a relation with initial term $y_i y_j$.
-
-Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
-+1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
-y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
-the same method as the previous two paragraphs we find
-\[
-	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-\]
-Similarly if $i=1$, then we get the same result using
-\[
-	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
-\]
-In both cases we deduce that $y_iy_j$ is an initial term of some relation.
-
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
-\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
-power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
-that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
-proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
-$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
-previous paragraphs we find
-\[
-	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-\]
-Similarly if $i=1$ then
-\[
-	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
-\]
-In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
-
-Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
-terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
-x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
-non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
-$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
-some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
-$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
-relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
-{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
-\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
-elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
-u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
-y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
-we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
-generic, this is in fact the generic initial ideal.
-
-In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
-\todo{What about $\frac{\alpha}{beta}>1$?}
-\end{proof}
 
@@
 
-\todo{Move this lemma:}
-\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
-Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
-Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.
-Then 
-\begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j \rangle \\
-										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
-\end{align*}
-\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
-\end{itemize}
-\end{lem}
-\begin{proof}
-Similar to all the other lemmas\todo{combine sections?}
-\end{proof}
-
 Transition words.
@@
 \label{ssec:g_0_ram_pts}
-
-\begin{prop}
-\label{prop:sat_three_induction}
-\todo{Make explicit assumptions on genus.}
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
-Actually, the map isn't ramified at $P$, it's just defined away from $P$.
-I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
-3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-Then, the following statements hold.
-
-\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
-\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
-		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
-			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
-_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.} To complete the proof of (a) we only need 
-show these elements generate $R$ over $R'$. We can first see that 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
-	\end{split}
-\end{align}
-
-\noindent
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
-_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-,$ elements of degree $d$ in the claimed basis of
-~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-\rfloor $ and $b = d \bmod 3$, we have that the elements
-
-\begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
-3+b}
-\end{align*}
-
-\noindent
-are precisely $a$ elements, which are all independent as they have
-distinct pole orders at $P$. This completes part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_{i,j} \in k$ for $4
-\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B_1 y_3 y_5 \\
-	y_4y_5 &+ B_2 y_3^2 x_3 \\
-	y_5^2 &+ B_3 y_3^2 x_4
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
 
@@
 
-\section{Genus Zero Effective}
-\label{sec:g_0_effective}
+\section{Genus Zero}
+\label{sec:g_0}
+
 Now we consider the genus zero case.
 \todo{write intro}
+
+\ssec{Genus Zero Effective}
 
@@
 
-\section{Genus Zero Non-effective}
+\ssec{Genus Zero Non-effective}
 \label{sec:g_0_non_effective}

### 2015-06-23 stacky_write_up/spin_cring.tex

@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}
 
@@
 \begin{example}
-\label{eg:g_1_triv}
+\label{eg:base-1-0}
 In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
@@
 \begin{example}
-Let $\sx$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
+\label{eg:base-1-33}
+Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
+$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$$
+and that $(\sx',\{3,3\})$ is admissible.
+
 Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$.
+Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$.
 Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
 
-Here, we claim $R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k.$
-
- and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
-
-\todo{check admissibility}
+Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
+$R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic, and analogous to that completed in Example ~\ref{ex:base-377}.
+
+We next check $(\sx',\{3,3\})$ is admissible.
+We clearly have two generators $x_3,y_3$ in degree 3 with a pole of order $\frac{3-1}{2}$ by construction.
+Hence, (Ad-i) holds.
+We next check (Ad-ii) for the point $R_1$, as the case of $R_2$ is symmetric.
+Here, by construction
+$$
+\frac{-\ord_{R_1}(z)}{\ord(z)} = \begin{cases}
+	0 &\text{ if }z \in \{u,y_3\}\\
+	\frac{1}{4} &\text{ if }z = y_4
+\end{cases}.$$
+Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
+Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 -1 + 0$.
 \end{example}
+
+\ssec{Genus 1 Exceptional Cases}
 

### 2015-06-23 stacky_write_up/spin_cring.tex
merged

@@
 %
-%
-%\begin{rem}
-%\label{rem:minimal_quadratic_trivial_case}
-%It will be useful to use lemma \ref{lem:minimal_quadratic} in the
-%case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
-%are $k$-minimal generators for $I'$ (over the trivial base vector
-%space).  
-%\end{rem}
+
+\begin{rem}
+\label{rem:minimal_quadratic_trivial_case}
+It will be useful to use lemma \ref{lem:minimal_quadratic} in the
+case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
+are $k$-minimal generators for $I'$ (over the trivial base vector
+space).  
+\end{rem}
 
@@
 \ssec{Inductive Theorem: Adding points for high genus}
-
-\begin{lem}
-\label{lem:deg1_sat_ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
-defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
-generator $u$ in degree 1.  Suppose $D$ is generated by $
-u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
-that
-
-\begin{equation}
-\label{eqn:deg1_sat_ind_dim}
-	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
-	N} : d \ge \frac{\beta}{\alpha}.
-\end{equation}
-Let 
-\[
-	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
-\]
-be the non-negative best lower approximation.
-Then 
-\begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$
-
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
-										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
-\end{itemize}
-\end{lem}
-
-\begin{proof}
-Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{
-check that we can actually do this, or eliminate if it turns out to
-be unnecessary}.
-
-Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
-{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
-our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
-\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
-
-\[
-	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
-\]
-
-\noindent
-so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
-order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We can use a method similar to O'Dorney to
-construct the $y_i$'s as desired: \todo{cite where}
-
-Let 
-\[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-\beta}
-\] 
-be the non-negative best lower approximation of $\frac{
-\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
-orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
-each other and $(R_D)_d$, so by degree considerations, they span
-$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
-
-For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
-by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have 
-\[
-	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
-\]
-so we have the pole order of $\prod z_i$ is 
-\[
-	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
-\] 
-Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees.  
-Generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
-\[
-	-\ord_P(y_i)= \max(c_j:d_j=1)
-\]
-and if more than one $d_i$ is 1, we
-must also choose them generically so they generate $(R_{D'})_1$).
-
-Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ not a best lower approximation.  Then choose
-best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
-maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
-this we can deduce that 
-\[
-	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
-\]  
-Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
-has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
-\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
-where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
-\rfloor + 1}$.  
-Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
-\frac{\alpha}{\beta}$ is not a best lower approximation than we can
-construct an element in degree $d$ with pole degree $c$ by either $y
-_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-same conditions.  We notice that elements of this form are all
-linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
-$R_{D'}$.
-
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
-corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
-paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
-$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
-$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
-successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
-convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
-expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
-is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
-\[
-	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-\]
-giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
-the beginning}
-
-Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
-$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
-u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
-+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
-+1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
-$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
-$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
-larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
-+c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
-d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
-(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
-$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
-follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
-$ to find
-\[
-	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-u^{b_l}\in R_D
-\]
-implying a relation with initial term $y_i y_j$.
-
-Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
-+1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
-y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
-the same method as the previous two paragraphs we find
-\[
-	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-\]
-Similarly if $i=1$, then we get the same result using
-\[
-	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
-\]
-In both cases we deduce that $y_iy_j$ is an initial term of some relation.
-
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
-\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
-power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
-that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
-proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
-$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
-previous paragraphs we find
-\[
-	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-\]
-Similarly if $i=1$ then
-\[
-	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
-\]
-In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
-
-Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
-terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
-x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
-non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
-$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
-some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
-$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
-relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
-{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
-\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
-elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
-u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
-y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
-we see that $J'$ is the initial ideal of $I'$.
-
-In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
-\todo{What about $\frac{\alpha}{\beta}>1$?}
-\end{proof}
 
@@
 
-\begin{lem}
-\label{lem:sat_three_induction}
-\todo{Make explicit assumptions on genus.}
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
-Actually, the map isn't ramified at $P$, it's just defined away from $P$.
-I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
-3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-Then, the following statements hold.
-
-\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
-\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
-		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
-			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
-_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.} To complete the proof of (a) we only need 
-show these elements generate $R$ over $R'$. We can first see that 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
-	\end{split}
-\end{align}
-
-\noindent
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
-_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-,$ elements of degree $d$ in the claimed basis of
-~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-\rfloor $ and $b = d \bmod 3$, we have that the elements
-
-\begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
-3+b}
-\end{align*}
-
-\noindent
-are precisely $a$ elements, which are all independent as they have
-distinct pole orders at $P$. This completes part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_{i,j} \in k$ for $4
-\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B_1 y_3 y_5 \\
-	y_4y_5 &+ B_2 y_3^2 x_3 \\
-	y_5^2 &+ B_3 y_3^2 x_4
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
 Transition to genus one.
@@
 
-\todo{Move this lemma:}
-\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
-Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
-Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-generator $u$ in degree 1 and $R_{\halfcan'}$ has no new generators in degree 1.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.
+Transition words.
+\todo{transition!}
+
+We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
+reference} and O'Dorney\todo{reference}.
+
+\begin{lem}
+\label{lem:deg1_sat_ind}
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
+defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
+satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
+generator $u$ in degree 1.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
+that
+
+\begin{equation}
+\label{eqn:deg1_sat_ind_dim}
+	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
+	N} : d \ge \frac{\beta}{\alpha}.
+\end{equation}
+Let 
+\[
+	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+\]
+be the non-negative best lower approximation.
 Then 
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
+
 \item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
@@
 	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j \rangle \\
-										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
-\end{align*}
-\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
+										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
+										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
 \end{itemize}
 \end{lem}
-\begin{proof}
-Similar to all the other lemmas\todo{combine sections?}
-\end{proof}
-
-Transition words.
-\todo{transition!}
-
-We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
-reference} and O'Dorney\todo{reference}.
+
+\begin{proof}
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
+These can be chosen generically to not have a zero at $P$ \todo{
+check that we can actually do this, or eliminate if it turns out to
+be unnecessary}.
+
+Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
+{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
+our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
+\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+
+\[
+	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
+\]
+
+\noindent
+so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
+order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
+\beta} \rfloor \}$. We can use a method similar to O'Dorney to
+construct the $y_i$'s as desired: \todo{cite where}
+
+Let 
+\[
+	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+\beta}
+\] 
+be the non-negative best lower approximation of $\frac{
+\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
+orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
+c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
+each other and $(R_D)_d$, so by degree considerations, they span
+$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
+
+For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
+by construction, so any product of $\prod z_i$ of elements of
+degrees less than $d_i$ must have 
+\[
+	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
+\]
+so we have the pole order of $\prod z_i$ is 
+\[
+	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
+\] 
+Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
+lower degrees.  
+Generically choose some $y_i \in(R_{
+D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
+\[
+	-\ord_P(y_i)= \max(c_j:d_j=1)
+\]
+and if more than one $d_i$ is 1, we
+must also choose them generically so they generate $(R_{D'})_1$).
+
+Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
+\beta}$ not a best lower approximation.  Then choose
+best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
+maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
+this we can deduce that 
+\[
+	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
+\]  
+Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
+has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
+\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
+where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+\rfloor + 1}$.  
+Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+\frac{\alpha}{\beta}$ is not a best lower approximation than we can
+construct an element in degree $d$ with pole degree $c$ by either $y
+_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
+same conditions.  We notice that elements of this form are all
+linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
+$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
+$R_{D'}$.
+
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
+corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
+paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
+$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
+$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
+successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
+\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
+\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
+convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
+with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
+is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
+expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
+is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
+\[
+	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
+\]
+giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
+the beginning}
+
+Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
+$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
+u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
++c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
++1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
+$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
+$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
+larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
++c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
+d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
+(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
+$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
+follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
+$ to find
+\[
+	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
+u^{b_l}\in R_D
+\]
+implying a relation with initial term $y_i y_j$.
+
+Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
++1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
+y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
+the same method as the previous two paragraphs we find
+\[
+	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
+\]
+Similarly if $i=1$, then we get the same result using
+\[
+	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
+\]
+In both cases we deduce that $y_iy_j$ is an initial term of some relation.
+
+Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
+\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
+power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
+that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
+proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
+$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
+previous paragraphs we find
+\[
+	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
+\]
+Similarly if $i=1$ then
+\[
+	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
+\]
+In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
+
+Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
+terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
+x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
+non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
+$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
+some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
+$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
+relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
+{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
+\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
+elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
+u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
+y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
+we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
+generic, this is in fact the generic initial ideal.
+
+In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
+\todo{What about $\frac{\alpha}{beta}>1$?}
+\end{proof}
 
@@
 
+\todo{Move this lemma:}
+\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
+Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
+Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
+generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 &+ \langle y_i x_j \rangle \\
+										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
+\end{align*}
+\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
+\end{itemize}
+\end{lem}
+\begin{proof}
+Similar to all the other lemmas\todo{combine sections?}
+\end{proof}
+
 Transition words.
@@
 \label{ssec:g_0_ram_pts}
+
+\begin{prop}
+\label{prop:sat_three_induction}
+\todo{Make explicit assumptions on genus.}
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
+Actually, the map isn't ramified at $P$, it's just defined away from $P$.
+I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
+3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
+\end{align*}
+Then, the following statements hold.
+
+\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
+
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
+		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.} To complete the proof of (a) we only need 
+show these elements generate $R$ over $R'$. We can first see that 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:add_one_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+	\end{split}
+\end{align}
+
+\noindent
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+,$ elements of degree $d$ in the claimed basis of
+~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+\rfloor $ and $b = d \bmod 3$, we have that the elements
+
+\begin{align*}
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+3+b}
+\end{align*}
+
+\noindent
+are precisely $a$ elements, which are all independent as they have
+distinct pole orders at $P$. This completes part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:add_one_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_{i,j} \in k$ for $4
+\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B_1 y_3 y_5 \\
+	y_4y_5 &+ B_2 y_3^2 x_3 \\
+	y_5^2 &+ B_3 y_3^2 x_4
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
 
@@
 
-\section{Genus Zero}
-\label{sec:g_0}
-
+\section{Genus Zero Effective}
+\label{sec:g_0_effective}
 Now we consider the genus zero case.
 \todo{write intro}
-
-\ssec{Genus Zero Effective}
 
@@
 
-\ssec{Genus Zero Non-effective}
+\section{Genus Zero Non-effective}
 \label{sec:g_0_non_effective}

### 2015-06-23 stacky_write_up/spin_cring.tex
adding transitions to section 3

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 for all genera.
-\todo{intro}
-
-\ssec{General: quadratic initial ideal minimal relations}
-First we prove a nice result about minimal generation of ideals of relations:
-
+We offer various inductive lemmata that will allow us to add fractional point $\frac{\alpha}{\beta}P$ to a $\mathbf{Q}$ divisor $D$ of $X$ and describe the new generators and relations of $R_{D+p}$ not in $R_D$.
+Next, we provide a method specific to the case of stacky canonical divisors with no log component, which under certain conditions allows us to transfer information about the generators and relations of the half canonical ring of a stacky curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$ where each $e_i\in \{e_i', e_i'+2\}$.
+
+However, before we can answer these general lemmata, it is useful to prove a nice result about minimal generation of ideals of relations:
 \todo{Include one of the following, if the first one, include a remark for quotient}
@@
 
-Transition words.
-\todo{transition!}
+With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
 
@@
 \label{ssec:add_pts}
-In this section, we prove various inductive statements about
-generators and relations with respect to adding points.
-
-\ssec{Inductive Theorem: Adding points for high genus}
+In this section, we prove various inductive statements under the following setup:
+Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
+Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).
+The proofs of these lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
 
@@
 
-Transition to genus one.
-\todo{transition!}
-
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
-We prove an inductive theorem on adding 2-sat here.
-\todo{description}
-
-\begin{prop}
-\label{prop:sat_two_induction}
+\begin{lem}
+\label{lem:sat_two_induction}
 Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
@@
 \end{enumerate}
-\end{prop}
+\end{lem}
 
@@
 \end{proof}
-
-Transition words.
-\todo{transition!}
-
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
-\label{ssec:g_0_ram_pts}
 

### 2015-06-24 stacky_write_up/spin_cring.tex
edits to genus 1, cleaning up base cases

--- 2015-06-23 stacky_write_up/spin_cring.tex
@@
 \section{High genus}
+\label{sec:g_high}
+We now consider the case when the genus is at least 2.
+In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$.
+In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Sections ~\ref{sec:g_1} and ~\ref{sec:g_0_effective} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
+The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved.
+We begin with the case that $g \geq 2$.
 
@@
 \ssec{Main theorem for high genus}
+\label{ssec:main_g_high}
 
@@
 \section{Genus one}
-We now consider the case when the genus is positive. The genus zero
-case is the most complicated and reserve that for Section ~\ref{sec:g_0_effective}
-and Section ~\ref{sec:g_0_non_effective}. We begin with the genus one case.
+\label{sec:g_1}
+
+In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}.
 
 \ssec{Genus 1 Base Cases}
-
-In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}
+\label{ssec:g_1_base}
+
+We first analyze the following two examples, which will be crucial base cases for our inductive approach, completed in Subsection ~\ref{ssec:main_g_1}.
 
@@
 \end{enumerate}
+\todo{make table}
 
@@
 Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$.
-In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that
+In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that $\sigma = (1;-;0),\sigma = (1;e;0)$.
+That is, we will consider the cases.
 \begin{enumerate}
 	\item $\halfcan' = P-Q$
-	\item $\halfcan' = 0$
-	\item $\halfcan' = P-Q$
 	\item $\halfcan' = P - Q + \frac{1}{3}R$
-	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 3, e \equiv 1 \bmod 2$ 
-	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3$
+	\item $\halfcan' = P - Q + \frac{1}{5}R$
+	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 5, e \equiv 1 \bmod 2$ 
 \end{enumerate}
-In addition to being illustrative examples, these will serve as the base cases of induction, in order to compute generators and relations for an arbitrary genus 1, stacky log half canonical divisor.
-In each of the following examples, we will give explicit generators and relations, and in case $(3)$ and $(4)$ we check the corresponding signature is admissible.
+\todo{make table}
 
 \begin{example}
-\label{eg:g_1_half_can}
+\label{eg:exceptional-1-0}
 In the case $L=P - Q.$ Then, we have $R_{(2k+1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
@@
 \begin{example}
-\label{eg:g_1_deg_third}
+\label{eg:exceptional-1-3}
 Let $L = P - Q + \frac{1}{3}R$.
@@
 \begin{example}
-\label{}
+\label{eg:exception-1-5}
+Let $L = P - Q + \frac{2}{5}R_1.$ Here, we 
+\todo{say what the variables are}
+$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2),$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+Furthermore, $\deg u = 2, \deg y_i = i$.
+\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
+\todo{Check admissibility}
+\end{example}
+
+\begin{example}
+\label{eg:exception-1-e}
 Let $L = P - Q + \frac{e-1}{2e}R_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
 Furthermore, $\deg u = 2, \deg y_i = i$.
-\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.} \todo{Check admissibility}
+\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
 \end{example}
 
-\begin{example}
-Let $L = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$.
-Here, we claim $R_L \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k$, and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.
-\todo{Explain why this forms a system of generators and relations, and also state more clearly what $y_i$ are.} \todo{check admissibility}
-\end{example}
-
 \ssec{Main Theorem for Genus 1}
-Words.
+\label{ssec:main_g_1}
 

### 2015-06-24 stacky_write_up/spin_cring.tex
delete duplicate chunk, minor reference fixes

@@
 \subsection{Main Results}
+\begin{enumerate}
+	\item Petri's Theorem
+	\item Modular Forms
+	\item Stacky Relations
+	\item Statement of Results
+	\item Outline of paper
+\end{enumerate}
+
 These are our results.
@@
 \label{thm:g_0_generators_relations}
-Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
+Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
 that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
@@
 \begin{align*}
-	R(\sx, \Delta, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
 \end{align*}
@@
 is generated as a $k$-algebra by elements of degree at most $e = 
-\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so 
-long as $\sigma$ does not lie in a finite list of exceptions. \todo{
-Include reference to the table with this list of exceptions.}
+\max(5,e_1,\ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx, \Delta, \halfcan)$ has relations in degree at most $\max(11,e_1,\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta, \halfcan)$ has relations in degree at most $\max(10,e_1,\ldots, e_r),$ so
+long as $\sigma$ does not lie in a finite list of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional} for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
 \end{thm}
+
+Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations.
+In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations.
+While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$.
+In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].
 
@@
 In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$.
-In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Sections ~\ref{sec:g_1} and ~\ref{sec:g_0_effective} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
+In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Subsection ~\ref{ssec:g_0_effective} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
 The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved.
@@
 \end{enumerate}
-\todo{make table}
 
@@
 Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic, and analogous to that completed in Example ~\ref{ex:base-377}.
+$R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
+The details are omitted as it is analogous to Example ~\ref{ex:base-377}.
 
@@
 \todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
-Let $\sx$ be a tame, seperably rooted stacky curve of genus 1.
-Let $P,Q$ are distinct hyperelliptic fixed points, and $R_1,\ldots, R_n$ be points on $\sx$.
-In this section, will compute the canonical ring $R_{\halfcan'}$ in the cases that $\sigma = (1;-;0),\sigma = (1;e;0)$.
-That is, we will consider the cases.
-\begin{enumerate}
-	\item $\halfcan' = P-Q$
-	\item $\halfcan' = P - Q + \frac{1}{3}R$
-	\item $\halfcan' = P - Q + \frac{1}{5}R$
-	\item $\halfcan' = P - Q + \frac{e-1}{2e}R, e > 5, e \equiv 1 \bmod 2$ 
-\end{enumerate}
-\todo{make table}
-
+Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R$ be a point on $\sx$.
+
+\todo{cite genus 1 final theorem here, to explain what these cases are exceptional to}
+\begin{longtable}	{| c || c | c | c |}
+	\hline
+	L' & Generator Degrees & Degrees of Minimal Relations \\
+	\hline
+	\hline
+	$(1;-; 0)$ & $\{2\}$ & $\emptyset$ \\	\hline
+
+	$(1; 3; 0)$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
+
+	$(1; 5; 0)$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10,\ldots, e+2, e+3, e+5,e+7,\ldots, 2e-4\}$ \\	\hline
+\end{longtable}
+
+\begin{center}
+\label{table:g-1-exceptional}
+\textbf{Table (IV)}: Genus 1 exceptional cases, where $L' = P-Q + \frac{e-1}{2e}R$, with $P \neq Q$.
+\end{center}
+\iffalse
+\begin{rem}
+\label{rem:g-1-exceptional-e}
+Note that for $e > 5$ generators and relations for $L = P -Q + \frac{e-1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P-Q + \frac{(e-2)-1}{2(e-2)}R$ using 
+Theorem ~\ref{thm:ram_order_ind}.
+\end{rem}
+\fi
+
+We now elaborate on the computation of the results in 
+Table ~\ref{table:g-1-exceptional}. In the following example we will explain the case $\sigma = (1;5;0)$ as the other cases are even easier.
+
+\iffalse
 \begin{example}
@@
 For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{Peter: Why don't we have something in degree 4?}
-\end{example}
-
-\begin{example}
-\label{eg:exception-1-5}
-Let $L = P - Q + \frac{2}{5}R_1.$ Here, we 
-\todo{say what the variables are}
-$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2),$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
-Furthermore, $\deg u = 2, \deg y_i = i$.
-\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
-\todo{Check admissibility}
+We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
 \end{example}
@@
 \end{example}
+\fi
+
+\begin{example}
+\label{eg:exception-1-5}
+Let $L = P - Q + \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$.
+Let $u \in (R_L)_1$ be any nonzero element.
+We obtain $\di u|_R = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1$ let $y_3 \in (R_L)_3$ be any nonzero element.
+We obtain $\di y_3|_R = - R,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$.
+Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_R = -R$.
+Then, we claim there is some $\alpha \in k$ so that
+$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+It is analogous to Example ~\ref{ex:base-377}, and is omittied.
+\end{example}
 
@@
 
-\section{Genus Zero Effective}
-\label{sec:g_0_effective}
+\section{Genus Zero}
+\label{sec:g_0}
 Now we consider the genus zero case.
 \todo{write intro}
+
+\ssec{Genus Zero Effective}
+\label{ssec:g_0_effective}
 
@@
 
-\section{Genus Zero Non-effective}
-\label{sec:g_0_non_effective}
+\ssec{Genus Zero Non-effective}
+\label{ssec:g_0_non_effective}
 
@@
 involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
-~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
+~\ref{ssec:g_0_ram_orders} \todo{fix} we prove inductive theorems, and in
 Subsection ~\ref{ssec:g_0_base} we check the base cases of the
@@
 and any generator $z$ of $R'$.
-
 \begin{longtable}
@@
 	\hline
-	Case & Generator Degrees & Minimal Relation Degrees & $e$\\
+	Case & Generator Degrees & Degrees of Minimal Relations & $e$\\
 	\hline
@@
 	\hline
-	Signature & Generator Degrees & Minimal Relation Degrees & $e$ \\
+	Signature & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
@@
 \begin{center}
+\label{table:g-0-exceptional}
 \textbf{Table (IV)}: Genus 0 exceptional cases
@@
 
+\todo{Aaron: Use thmrestate instead of rewriting the Theorem}
 \begin{thm}

### 2015-06-24 stacky_write_up/spin_cring.tex
shift/reword g=0 and g=1 theorems

@@
 \begin{thm}
-\label{thm:g_0_generators_relations}
+\label{thm:general_generators_relations}
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5,e_1,\ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx, \Delta, \halfcan)$ has relations in degree at most $\max(11,e_1,\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta, \halfcan)$ has relations in degree at most $\max(10,e_1,\ldots, e_r),$ so
-long as $\sigma$ does not lie in a finite list of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional} for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
+\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx,
+\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
+\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta
+, \halfcan)$ has relations in degree at most $\max(10, e_1, \ldots,
+e_r),$ so long as $\sigma$ does not lie in a finite list of
+exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
+for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
+for signatures with $g = 0$.
 \end{thm}
@@
 
+\begin{thm}
+\label{thm:g_1_generators_relations}
+Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
+so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
+If $g = 1$, then the canonical ring
+
+\begin{align*}
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+\end{align*}
+
+\noindent
+is generated as a $k$-algebra by elements of degree at most $e =
+\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
+(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
+finite list of exceptional cases, as listed in Table
+~\ref{table:g-1-exceptional}.
+\end{thm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus zero %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{Aaron: Use thmrestate instead of rewriting the Theorem}
 \begin{thm}
-\label{thm:g_0_generators_relations_rep}
-Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
-that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
-canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+\label{thm:g_0_generators_relations}
+Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
+so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
+If $g = 0$, then the canonical ring
+
+\begin{align*}
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
 \end{align*}
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$, so 
-long as $\sigma$ does not lie in a finite list of exceptions. \todo{
-Include reference to the table with this list of exceptions.}
+\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
+(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
+finite list of exceptional cases, as listed in Table
+~\ref{table:g-0-exceptional}.
 \end{thm}

### 2015-06-24 stacky_write_up/spin_cring.tex
major g = 0 revisions, minor typo fixes elsewhere

@@
 
-\begin{cor}\label{cor:genus_0_posiive_delta}
+\begin{cor}\label{cor:genus_0_positive_delta}
 Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.
@@
 $(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
-signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.
+signature $(0;e_1, \ldots, e_r; 0)$ with $e_i' - e_i \in \{0,2\}$.
 
@@
 there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
-\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where
+\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
 
@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx,0,L)$ as well} is a tame separably rooted log stacky spin
+Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx, 0, L)$ as well} is a tame separably rooted log stacky spin
 curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
+	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
 		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
@@
 \label{ssec:g_0_non_effective}
-
-\todo{Peter: throughout this section I will provide a few notes of how we can generalize this to arbitrary genus with the appropriate conditions}
-
 In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
@@
 \label{lem:g_0_admissible_cases}
-Let $(\sx', \Delta, \halfcan')$ be a tame log spin curve over a perfect field $k$,
-so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$.
-Then $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k$-algebra by elements
-of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree
-at most $2e$ and $(\sx', J)$ is admissible for the following cases:
+Let $(\sx', \Delta, \halfcan')$ be a tame log spin curve over a
+perfect field $k$, so that $\sx$ has signature $\sigma = (0; e_1,
+\ldots, e_r; 0)$. Then $R' := R(\sx', \Delta, \halfcan')$ has a
+presentation
+
+is
+generated as a $k$-algebra by elements of degree at most $e = \max(5
+,e_1,\ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
+', J)$ is admissible for the following cases:
 
@@
 
-Using the results of Proposition ~\ref{prop:sat_three_induction}
-and Theorem ~\ref{thm:ram_order_ind}, we can inductively raise
-the ramification orders and number of ramified points in all of the
-cases in Lemma ~\ref{lem:g_0_admissible_cases} to obtain the following
-result.
-
-\begin{cor}
-\label{cor:g_0_gen_rel_base_cases}
-Let $(\sx, \Delta, L)$ be a tame log spin curve over a perfect field $k$, so
-that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$. Then the
-canonical ring
-
-\[
-	R(\sx, 0, L) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
-\]
-
-\noindent
-is generated as a $k$-algebra by elements of degree at most $e := 
-\max(5, e_1, \ldots, e_r)$ with relations in degree at most $2e$, so 
-long as $\sigma \notin S$ where
-
-\begin{align*}
-	S &:= \{(0; 3, 3, k; 0) : 3 \leq k \leq 9 \text{ odd}\} \\
-		&\cup \{(0; 3, 5, 5; 0) ,(0; 3, 5, 7; 0), (0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
-\end{align*}
-
-\noindent
-is a finite set.
-\end{cor}
-
-\begin{proof}
-A process of induction raising the ramification orders of
-the ramified points of the spin curves corresponding to Lemma
-~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
-~\ref{thm:ram_order_ind} will demonstrate the desired generator and
-relation degree results for curves with three ramified points.
-Similarly, this induction process on Lemma
-~\ref{lem:g_0_admissible_cases} case (d) will give the desired
-result for curves with four ramified points excluding signature
-$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
-number of ramified points via Proposition
-~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
-case (e) combined with the induction process on ramification orders
-will yield the result for curves with at least five ramified points.
-\todo{Detailed description of how the inductive lemmata yield e and 2e}
-\end{proof}
+Through the application of two processes of induction, by adding 
+points via Proposition ~\ref{prop:sat_three_induction} and by raising
+ramification orders via Theorem ~\ref{thm:ram_order_ind},
+we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
+log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
+signature $\sigma$ covered by this induction process.
+In particular, this induction process covers all signatures $\sigma
+= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
+for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
+\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
+Before we prove the main theorem, we describe the cases not be
+covered by induction.
 
@@
 \label{ssec:g_0_exceptional}
+First, we describe the cases that would not be covered by induction.
 Here we present the explicit generators and relations of the remaining
@@
 
+\begin{proof}
+
+%By Lemma ~\ref{lem:g_0_admissible_cases}, we know that for
+%any tame log spin curves $(\sx', \Delta, \halfcan')$ over a perfect
+%field $k$ with signature $\sigma'$ and set $J$ such that $(\sigma',
+%J)$ is one of the listed base cases, $(\sigma', J)$ is admissible.
+%Furthermore, $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k
+%$- algebra by elements of degree at most $e = \max(5, e_1, \ldots, e
+%_r)$ with relations in degree at most $2e$. It also admits a
+%presentation
+%
+%\begin{align*}
+	%R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
+%\end{align*}
+%
+%\noindent
+%given by admissibility satisfying the statements that for all $i \in 
+%J$, $e_i > \deg z$ for any generator $z$ of $R'$ and that $in_\prec
+%(I')$ is minimally generated by products of two monomials under
+%some ordering.
+%
+%Then we can apply two processes of induction, by adding points via
+%Proposition ~\ref{prop:sat_three_induction} and by raising
+%ramification orders via Theorem ~\ref{thm:ram_order_ind},
+%to obtain the desired result for any tame log spin curve $(\sx,
+%\Delta, L)$ over a perfect field $k$ with signature $\sigma$
+%covered by this induction process.
+%
+%
+%
+%A process of induction raising the ramification orders of
+%the ramified points of the spin curves corresponding to Lemma
+%~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
+%~\ref{thm:ram_order_ind} will demonstrate the desired generator and
+%relation degree results for curves with three ramified points.
+%Similarly, this induction process on Lemma
+%~\ref{lem:g_0_admissible_cases} case (d) will give the desired
+%result for curves with four ramified points excluding signature
+%$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
+%number of ramified points via Proposition
+%~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
+%case (e) combined with the induction process on ramification orders
+%will yield the result for curves with at least five ramified points.
+\end{proof}
+
 \section{Further Research}

### 2015-06-24 stacky_write_up/spin_cring.tex

@@
 \section{Introduction}
-\todo{Edit this stuff}
-This is our project.
-Modular Forms.
 
@@
 
-These are our results.
 \begin{thm}
@@
 \end{thm}
-
+\todo{Say that this follows immediately from the three theorems for the special cases.}
 Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations.

### 2015-06-24 stacky_write_up/spin_cring.tex
edit hypothesis theorem

@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx, 0, L)$ as well} is a tame separably rooted log stacky spin
-curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
-R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
-Then the following are true:
+Suppose $(\sx', 0, \halfcan')$ is a tame separably rooted log
+stacky spin curve with coarse space $X'$ and signature
+$(g; e_1', \ldots, e_r'; \delta)$ and $(\sx', J)$ is
+admissible with generators $x_j, y_{i,e_i'} \in R' = R_{L'}$ with
+$i \in J$ as in Definition ~\ref{defn:admissible}. Let $(\sx, 0,
+\halfcan)$ be another tame separable rooted log stacky spin curve
+with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
+\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
+$e_j = e_j'$ for $j \notin J$. Then the following are true:
 \begin{enumerate}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
+			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{
+e_j'}-
 			\frac{1}{\deg(y_{i,e_i})e_j'}
@@
 		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
-		minimal generators for $I'$ together with any set of relations as in 
+		minimal generators for $I'$ together with any set of relations 
+as in 
 		part (c) minimally generate $I$.
@@
 does not lie in a finite list of exceptions. This is proven in
-Subsection ~\ref{ssec:g_0_noneff_induction}. The proof is a rather
+Subsection ~\ref{ssec:g_0_main}. The proof is a rather
 involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
@@
 
-\ssec{Application of induction}
-\label{ssec:g_0_noneff_induction}
+\ssec{Main Theorem for Genus Zero}
+\label{ssec:g_0_main}
 Now we can combine this.

### 2015-06-24 stacky_write_up/spin_cring.tex
editing log divisor genus 2

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 \begin{lem}
-\label{lem:semicanonical_generation} \cite{neves:halfcan}[Proposition III.4]
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, for $n \geq 5$, the map
+\label{lem:semicanonical_generation}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$. Then, the map
 \begin{align*}
@@
 \end{align*}
-is surjective.
-In particular, $R_L$ is generated in degree at most $6$.
+is surjective if $n \geq 5$ or if ($n = 5$ and $\Delta > 0$).
+In particular, $R_L$ is generated in degree at most $6$ if $\Delta = 0$ and in degree at most $5$ if $\Delta > 0$.
 \end{lem}
-\iffalse
 \begin{proof}
-Therefore, to show there are no new generators in degree at least $7$, it suffices to show that for $n \geq 5$, the map
+Therefore, to show there are no new generators in degree at least $7$, it suffices to show that if $n \geq 5$ or if ($n = 5$ and $\Delta > 0$), the map
 \begin{align*}
@@
 We wish to show $f$ is surjective.
-Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption that $n \geq 5$.
+Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$).
 Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n-1)(g-1)$, again using Riemann--Roch.
@@
 \end{proof}
-\fi
 
 \begin{rem}
+\todo{This remark isn't quite right, we're changing the proof}
+\cite{neves:halfcan}[Proposition III.4]
 In \cite{neves:halfcan}[Proposition III.4], Neves claims to prove that $R_L$ is generated in degree at most 5.

### 2015-06-24 stacky_write_up/spin_cring.tex
editing subsection structure of section 3

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 
-Transition to genus one.
-\todo{transition!}
-
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
 We prove an inductive theorem on adding 2-sat here.
-\todo{description}
 
@@
 \end{proof}
-
-Transition words.
-\todo{transition!}
 
@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', 0, \halfcan')$ is a tame separably rooted log
-stacky spin curve with coarse space $X'$ and signature
-$(g; e_1', \ldots, e_r'; \delta)$ and $(\sx', J)$ is
-admissible with generators $x_j, y_{i,e_i'} \in R' = R_{L'}$ with
-$i \in J$ as in Definition ~\ref{defn:admissible}. Let $(\sx, 0,
-\halfcan)$ be another tame separable rooted log stacky spin curve
-with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
-\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
-$e_j = e_j'$ for $j \notin J$. Then the following are true:
+Suppose $(\sx', 0, L')$ \todo{Peter: You should also instantiate $(\sx, 0, L)$ as well} is a tame separably rooted log stacky spin
+curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
+R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
+Then the following are true:
 \begin{enumerate}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{
-e_j'}-
+			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{e_j'}-
 			\frac{1}{\deg(y_{i,e_i})e_j'}
@@
 		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
-		minimal generators for $I'$ together with any set of relations 
-as in 
+		minimal generators for $I'$ together with any set of relations as in 
 		part (c) minimally generate $I$.
@@
 does not lie in a finite list of exceptions. This is proven in
-Subsection ~\ref{ssec:g_0_main}. The proof is a rather
+Subsection ~\ref{ssec:g_0_noneff_induction}. The proof is a rather
 involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
@@
 
-\ssec{Main Theorem for Genus Zero}
-\label{ssec:g_0_main}
+\ssec{Application of induction}
+\label{ssec:g_0_noneff_induction}
 Now we can combine this.

### 2015-06-24 stacky_write_up/spin_cring.tex
edited genus bigger than 2 case

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 	\item Stacky Relations
-	\item Statement of Results
-	\item Outline of paper
 \end{enumerate}
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ then $R(\sx,
-\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
-\ldots, e_r).$ If the genus $g = 0$ or $g = 1,$ then $R(\sx, \Delta
-, \halfcan)$ has relations in degree at most $\max(10, e_1, \ldots,
-e_r),$ so long as $\sigma$ does not lie in a finite list of
+\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
+$R(\sx,\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
+\ldots, e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has relations in degree at most
+$\max(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a finite list of
 exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
@@
 
+The remainder of the paper will be primarily devoted to proving Theorem ~\ref{thm:general_generators_relations}.
+The idea of the proof will be to induct on the order and number of elliptic points.
+To this end, we first review important background in Section ~\ref{sec:background}.
+Then, in Section ~\ref{sec:induction}, we develop various inductive tools.
+In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively.
+Finally, in Section ~\ref{further-questions}, we pose several questions for future research.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Background}
+\label{sec:background}
 Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
@@
 \section{Inductive Lemmata}
+\label{sec:induction}
 First we present the general inductive lemmata that will be applied
@@
 We wish to show $f$ is surjective.
-Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$).
+Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
 Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n-1)(g-1)$, again using Riemann--Roch.
@@
 \label{lem:generation_5}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K$. Then, $R_L$ is generated in degree at most $5$.
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
 \end{lem}
 \begin{proof}
-If $g = 2$ then the claim follows from 
+If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
 Proposition ~\ref{prop:genus_2_generation_5}.
-However, if $g > 2$, then by \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective, so again there are no new generators in degree 6.
+Finally, if $g > 2$, then by \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective, so again there are no new generators in degree 6.
 \end{proof}
@@
 \label{lem:reducing_degree}
-Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$.
+Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$.
 Choose generators $x_1,\ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1,\ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and $J_{L,d} = \sum_{j = 1}^{d-1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ Let for any $f \in k[x_1, \ldots, x_n]$ with $\deg f \geq 12,$ there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and let $J_{L,d} = \sum_{j = 1}^{d-1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ For any $f \in k[x_1, \ldots, x_n]$ such that
+$$
+\deg f \geq \begin{cases}
+	12 &\text{ if }\Delta = 0\\
+	11 &\text{ if }\Delta > 0
+\end{cases}$$
+there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
 \end{lem}
@@
 \end{align*}
-is surjective, since $\deg f - \deg a_i - 2 \geq 12 - 5 - 2 = 5$.
+is surjective, since
+$$
+\deg f- \deg a_i-2 \geq \begin{cases}
+	5 &\text{ if }\Delta = 0\\
+	4 &\text{ if }\Delta > 0.
+\end{cases}$$
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
@@
 \label{prop:relations_generation}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K + \Delta$. Then $I_L$ is generated in degree at most $11$ if $\Delta = 0$ and degree at most $10$ if $\Delta > 0$.
 \end{prop}
@@
 \section{Further Research}
+\label{sec:further-questions}
 \begin{itemize}

### 2015-06-24 stacky_write_up/spin_cring.tex
some of proof g=0 main thm, minor edits

@@
 exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
-for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
+for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
 for signatures with $g = 0$.
@@
 I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
 3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
@@
 		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
 	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
@@
 \begin{center}
-\label{table:g-0-exceptional}
+\label{table:g_0_exceptional}
 \textbf{Table (IV)}: Genus 0 exceptional cases
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
-(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
-finite list of exceptional cases, as listed in Table
-~\ref{table:g-0-exceptional}.
+\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
+so long as $\sigma$ does not lie in a finite list of exceptional
+cases, as listed in Table ~\ref{table:g_0_exceptional}.
 \end{thm}
@@
 \begin{proof}
+If $\sx$ has no ramification points, then we have the classical
+case which is done in Chapter 4 of Voight and Zureick-Brown
+\cite{vzb:stacky}.
+
+Now let us consider the case when $\delta \geq 2$. In this case,
+$\halfcan$ is an effective divisor.
+
+Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
+If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
+exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
+5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
+~\ref{lem:g_0_admissible_cases}. In other words, one of the base
+cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
+satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
+$e_i = e_i'$ otherwise. If $r > 5$, then we can use Proposition
+~\ref{prop:sat_three_induction} to add ramified points with
+ramification order $3$ to case (k) of Lemma
+~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
+= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$, since the
+saturation in this case is equal to $3$.
+
+We know that each base case satisfies all of the hypotheses of
+Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
+R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
+to degree $e' := \max (5, e_1', \ldots, e_r')$ with relations
+generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
+It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
+R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
+e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
+(d) that the relations are generated up to degree $2e$.
 

### 2015-06-24 stacky_write_up/spin_cring.tex
remove remark from section 3

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 
-Transition words.
-\todo{transition!}
-
-\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
-\label{ssec:g_0_ram_pts}
-
 \begin{prop}

### 2015-06-24 stacky_write_up/spin_cring.tex
wrote most of g=0 main theorem pf

@@
 Now let us consider the case when $\delta \geq 2$. In this case,
-$\halfcan$ is an effective divisor.
+$\halfcan$ is an effective divisor. \todo{need to do this case}
 
 Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
-If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
-exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
-5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
-~\ref{lem:g_0_admissible_cases}. In other words, one of the base
-cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
-satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
-$e_i = e_i'$ otherwise. If $r > 5$, then we can use Proposition
+Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
+and not one of the exceptional cases in Table
+~\ref{table:g_0_exceptional}.
+
+If $r > 5$, then we can use Proposition
 ~\ref{prop:sat_three_induction} to add ramified points with
@@
 ~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
-= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$, since the
-saturation in this case is equal to $3$.
-
-We know that each base case satisfies all of the hypotheses of
+= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. Since
+this case satisfies all of the conditions by Lemma \todo{need this case
+to satisfy conditions for adding points}, the
+immediate consequence of parts (a) and (c) of Proposition
+~\ref{prop:sat_three_induction} is that any $R(\sx', \Delta,
+\halfcan')$ corresponding to signatures $\sigma'$ with ramification
+orders all equal to $3$ is generated up to degree $e := \max(5, e_1',
+\ldots, e_r')$ with relations generated up to degree $2e$.
+Furthermore, Proposition ~\ref{prop:sat_three_induction}(d)
+implies that these cases satisfy all of the hypotheses of Theorem
+~\ref{thm:ram_order_ind}.
+
+So if $r > 5$, then $\sigma$ ``lies above'' the case $\sigma', J$
+where $\sigma'$ has $r$ many ramification points all of order $3$
+and $J = \{1, \ldots, r\}$. If $r \leq 5$, then $\sigma$ ``lies
+above'' one of the base cases of Lemma ~\ref{lem:g_0_admissible_cases}.
+In either case, there is a $(\sigma', J)$ with $\sigma' = (0; e_1',
+\ldots, e_r'; 0)$ satisfying the property that for all $i \in J$,
+$e_i \geq e_i'$ and $e_i = e_i'$ otherwise where $(\sigma', J)$
+is either a base case from Lemma ~\ref{lem:g_0_admissible_cases}
+or the case from $r > 5$.
+
+All such base cases satisfy all of the hypotheses of
 Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
 R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
-to degree $e' := \max (5, e_1', \ldots, e_r')$ with relations
+to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
 generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.

### 2015-06-24 stacky_write_up/spin_cring.tex
delete unnecessary lemmas in section 3

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 
+\begin{lem}
+\label{lem:deg1_sat_ind}
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
+defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
+satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
+generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $\alpha,\beta \in \mathbf{N}$ such
+that
+\begin{equation}
+\label{eqn:deg1_sat_ind_dim}
+	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
+	N} : d \ge \frac{\beta}{\alpha}.
+\end{equation}
+Let 
+\[
+	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+\]
+be the non-negative best lower approximation.
+Then 
+\begin{itemize}
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+degree $d_i$ and has a pole at $P$ of degree $c_i$
+
+\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
+										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
+\end{itemize}
+\end{lem}
+
+\begin{proof}
+Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
+These can be chosen generically to not have a zero at $P$ \todo{
+check that we can actually do this, or eliminate if it turns out to
+be unnecessary}.
+
+Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
+{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
+our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
+\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+
+\[
+	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
+\]
+
+\noindent
+so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
+order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
+\beta} \rfloor \}$. We can use a method similar to O'Dorney to
+construct the $y_i$'s as desired: \todo{cite where}
+
+Let 
+\[
+	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+\beta}
+\] 
+be the non-negative best lower approximation of $\frac{
+\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
+orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
+c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
+each other and $(R_D)_d$, so by degree considerations, they span
+$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
+
+For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
+by construction, so any product of $\prod z_i$ of elements of
+degrees less than $d_i$ must have 
+\[
+	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
+\]
+so we have the pole order of $\prod z_i$ is 
+\[
+	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
+\] 
+Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
+lower degrees.  
+Generically choose some $y_i \in(R_{
+D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
+\[
+	-\ord_P(y_i)= \max(c_j:d_j=1)
+\]
+and if more than one $d_i$ is 1, we
+must also choose them generically so they generate $(R_{D'})_1$).
+
+Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
+\beta}$ not a best lower approximation.  Then choose
+best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
+maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
+this we can deduce that 
+\[
+	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
+\]  
+Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
+has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
+\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
+where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+\rfloor + 1}$.  
+Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+\frac{\alpha}{\beta}$ is not a best lower approximation than we can
+construct an element in degree $d$ with pole degree $c$ by either $y
+_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
+same conditions.  We notice that elements of this form are all
+linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
+$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
+$R_{D'}$.
+
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
+corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
+paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
+$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
+$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
+successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
+\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
+\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
+convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
+with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
+is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
+expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
+is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
+\[
+	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
+\]
+giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
+the beginning}
+
+Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
+$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
+u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
++c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
++1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
+$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
+$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
+larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
++c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
+d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
+(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
+$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
+follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
+$ to find
+\[
+	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
+u^{b_l}\in R_D
+\]
+implying a relation with initial term $y_i y_j$.
+
+Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
++1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
+y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
+the same method as the previous two paragraphs we find
+\[
+	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
+\]
+Similarly if $i=1$, then we get the same result using
+\[
+	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
+\]
+In both cases we deduce that $y_iy_j$ is an initial term of some relation.
+
+Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
+\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
+power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
+that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
+proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
+$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
+previous paragraphs we find
+\[
+	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
+\]
+Similarly if $i=1$ then
+\[
+	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
+\]
+In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
+
+Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
+terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
+x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
+non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
+$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
+some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
+$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
+relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
+{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
+\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
+elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
+u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
+y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
+we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
+generic, this is in fact the generic initial ideal.
+
+In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
+\todo{What about $\frac{\alpha}{beta}>1$?}
+\end{proof}
+
+\begin{lem}
+\label{lem:sat_two_induction}
+Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
+, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$.
+Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
+\end{align*}
+Then, the following statements hold.
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
+		y_3$
+		and equip the ring $k[y_3, y_4, x]$ with the block 
+		order so that $R = k[y_3, y_4, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x, y_3, y_4] \\
+			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_4^2.\rangle
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
+_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.}
+
+In a fashion analogous to the proof of Lemma 
+~\ref{lem:sat_three_induction}, we see 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:sat_two_add_generator}
+	\begin{split}
+		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \\
+		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
+	\end{split}
+\end{align}
+
+\noindent completing part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B y_3^2 x_2 \\
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
+\begin{lem}
+\label{lem:sat_two_induction}
+\todo{Make explicit assumptions on genus.}
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
+Actually, the map isn't ramified at $P$, it's just defined away from $P$.
+I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
+3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
+\end{align*}
+Then, the following statements hold.
+
+\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
+
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
+		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.} To complete the proof of (a) we only need 
+show these elements generate $R$ over $R'$. We can first see that 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:add_one_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+	\end{split}
+\end{align}
+
+\noindent
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+,$ elements of degree $d$ in the claimed basis of
+~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+\rfloor $ and $b = d \bmod 3$, we have that the elements
+
+\begin{align*}
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+3+b}
+\end{align*}
+
+\noindent
+are precisely $a$ elements, which are all independent as they have
+distinct pole orders at $P$. This completes part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:add_one_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_{i,j} \in k$ for $4
+\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B_1 y_3 y_5 \\
+	y_4y_5 &+ B_2 y_3^2 x_3 \\
+	y_5^2 &+ B_3 y_3^2 x_4
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
+\iffalse{
 \begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
@@
 
-\begin{prop}
-\label{prop:sat_two_induction}
-Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
-Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
-$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
-Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
-, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
-3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
-Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
-\end{align*}
-Then, the following statements hold.
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
-		y_3$
-		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order so that $R = k[y_3, y_4, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_4^2.\rangle
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.}
-
-In a fashion analogous to the proof of Proposition 
-~\ref{prop:sat_three_induction}, we see 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:sat_two_add_generator}
-	\begin{split}
-		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \\
-		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
-	\end{split}
-\end{align}
-
-\noindent completing part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B y_3^2 x_2 \\
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
 We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
 reference} and O'Dorney\todo{reference}.
-
-\begin{lem}
-\label{lem:deg1_sat_ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
-defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
-generator $u$ in degree 1.  Suppose $D$ is generated by $
-u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
-that
-
-\begin{equation}
-\label{eqn:deg1_sat_ind_dim}
-	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
-	N} : d \ge \frac{\beta}{\alpha}.
-\end{equation}
-Let 
-\[
-	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
-\]
-be the non-negative best lower approximation.
-Then 
-\begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$
-
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
-										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
-\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
-\end{itemize}
-\end{lem}
-
-\begin{proof}
-Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{
-check that we can actually do this, or eliminate if it turns out to
-be unnecessary}.
-
-Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
-{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
-our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
-\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
-
-\[
-	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
-\]
-
-\noindent
-so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
-order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We can use a method similar to O'Dorney to
-construct the $y_i$'s as desired: \todo{cite where}
-
-Let 
-\[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-\beta}
-\] 
-be the non-negative best lower approximation of $\frac{
-\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
-orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
-each other and $(R_D)_d$, so by degree considerations, they span
-$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
-
-For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
-by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have 
-\[
-	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
-\]
-so we have the pole order of $\prod z_i$ is 
-\[
-	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
-\] 
-Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees.  
-Generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
-\[
-	-\ord_P(y_i)= \max(c_j:d_j=1)
-\]
-and if more than one $d_i$ is 1, we
-must also choose them generically so they generate $(R_{D'})_1$).
-
-Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ not a best lower approximation.  Then choose
-best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
-maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
-this we can deduce that 
-\[
-	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
-\]  
-Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
-has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
-\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
-where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
-\rfloor + 1}$.  
-Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
-\frac{\alpha}{\beta}$ is not a best lower approximation than we can
-construct an element in degree $d$ with pole degree $c$ by either $y
-_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-same conditions.  We notice that elements of this form are all
-linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
-$R_{D'}$.
-
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
-corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
-paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
-$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
-$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
-successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
-convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
-expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
-is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
-\[
-	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-\]
-giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
-the beginning}
-
-Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
-$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
-u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
-+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
-+1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
-$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
-$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
-larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
-+c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
-d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
-(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
-$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
-follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
-$ to find
-\[
-	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-u^{b_l}\in R_D
-\]
-implying a relation with initial term $y_i y_j$.
-
-Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
-+1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
-y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
-the same method as the previous two paragraphs we find
-\[
-	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-\]
-Similarly if $i=1$, then we get the same result using
-\[
-	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
-\]
-In both cases we deduce that $y_iy_j$ is an initial term of some relation.
-
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
-\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
-power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
-that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
-proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
-$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
-previous paragraphs we find
-\[
-	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-\]
-Similarly if $i=1$ then
-\[
-	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
-\]
-In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
-
-Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
-terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
-x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
-non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
-$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
-some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
-$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
-relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
-{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
-\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
-elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
-u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
-y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
-we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
-generic, this is in fact the generic initial ideal.
-
-In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
-\todo{What about $\frac{\alpha}{beta}>1$?}
-\end{proof}
 
@@
 
-\begin{prop}
-\label{prop:sat_three_induction}
-\todo{Make explicit assumptions on genus.}
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
-Actually, the map isn't ramified at $P$, it's just defined away from $P$.
-I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
-3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-Then, the following statements hold.
-
-\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
-\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
-		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
-			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
-_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.} To complete the proof of (a) we only need 
-show these elements generate $R$ over $R'$. We can first see that 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
-	\end{split}
-\end{align}
-
-\noindent
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
-_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-,$ elements of degree $d$ in the claimed basis of
-~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-\rfloor $ and $b = d \bmod 3$, we have that the elements
-
-\begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
-3+b}
-\end{align*}
-
-\noindent
-are precisely $a$ elements, which are all independent as they have
-distinct pole orders at $P$. This completes part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_{i,j} \in k$ for $4
-\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B_1 y_3 y_5 \\
-	y_4y_5 &+ B_2 y_3^2 x_3 \\
-	y_5^2 &+ B_3 y_3^2 x_4
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
+}
+\fi
 
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.
 
@@
 Now we have an inductive statement on the number of ramified
-points in Proposition ~\ref{prop:sat_three_induction} and
+points in Lemma ~\ref{lem:sat_three_induction} and
 an inductive statement on ramification orders in Theorem
@@
 Through the application of two processes of induction, by adding 
-points via Proposition ~\ref{prop:sat_three_induction} and by raising
+points via Lemma ~\ref{lem:sat_three_induction} and by raising
 ramification orders via Theorem ~\ref{thm:ram_order_ind},
@@
 satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
-$e_i = e_i'$ otherwise. If $r > 5$, then we can use Proposition
-~\ref{prop:sat_three_induction} to add ramified points with
+$e_i = e_i'$ otherwise. If $r > 5$, then we can use Lemma
+~\ref{lem:sat_three_induction} to add ramified points with
 ramification order $3$ to case (k) of Lemma
@@
 %Then we can apply two processes of induction, by adding points via
-%Proposition ~\ref{prop:sat_three_induction} and by raising
+%Lemma ~\ref{lem:sat_two_induction} and by raising
 %ramification orders via Theorem ~\ref{thm:ram_order_ind},
@@
 %$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
-%number of ramified points via Proposition
-%~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
+%number of ramified points via Lemma
+%~\ref{lem:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
 %case (e) combined with the induction process on ramification orders

### 2015-06-24 stacky_write_up/spin_cring.tex

@@
 Now let us consider the case when $\delta \geq 2$. In this case,
-$\halfcan$ is an effective divisor.
+$\halfcan$ is an effective divisor. \todo{need to do this case}
 

### 2015-06-24 stacky_write_up/spin_cring.tex
minor fixes from Peter's merge

@@
 \begin{proof}
-For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
+For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
 \end{proof}
@@
 Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
-If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
-exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
-5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
-~\ref{lem:g_0_admissible_cases}. In other words, one of the base
-cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
-satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
-$e_i = e_i'$ otherwise. If $r > 5$, then we can use Lemma
+Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
+and not one of the exceptional cases in Table
+~\ref{table:g_0_exceptional}.
+
+If $r > 5$, then we can use Lemma
 ~\ref{lem:sat_three_induction} to add ramified points with
@@
 to satisfy conditions for adding points}, the
-immediate consequence of parts (a) and (c) of Proposition
-~\ref{prop:sat_three_induction} is that any $R(\sx', \Delta,
+immediate consequence of parts (a) and (c) of Lemma
+~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
 \halfcan')$ corresponding to signatures $\sigma'$ with ramification
@@
 \ldots, e_r')$ with relations generated up to degree $2e$.
-Furthermore, Proposition ~\ref{prop:sat_three_induction}(d)
+Furthermore, Lemma ~\ref{lem:sat_three_induction}(d)
 implies that these cases satisfy all of the hypotheses of Theorem

### 2015-06-24 stacky_write_up/spin_cring.tex
finish g=0 proof (mostly)

@@
 
-Now we can induct on cases (a)-(e) of \ref{lem:g_0_admissible_cases}
+Now we can induct on cases (a)-(k) of \ref{lem:g_0_admissible_cases}
 to obtain bounds on the minimal generator and relation degrees for
@@
 ~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
-= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. Since
-this case satisfies all of the conditions by Lemma \todo{need this case
-to satisfy conditions for adding points}, the
+= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
+clearly satisfies the conditions of Lemma
+~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
+{ssec:g_0_saturation} that saturation is 3 here), and the
 immediate consequence of parts (a) and (c) of Lemma
@@
 \halfcan')$ corresponding to signatures $\sigma'$ with ramification
-orders all equal to $3$ is generated up to degree $e := \max(5, e_1',
-\ldots, e_r')$ with relations generated up to degree $2e$.
-Furthermore, Lemma ~\ref{lem:sat_three_induction}(d)
-implies that these cases satisfy all of the hypotheses of Theorem
+orders all equal to $3$ for any $r > 5$ is generated up to
+degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
+up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
+implies that these cases satisfy all of the conditions of Theorem
 ~\ref{thm:ram_order_ind}.
 
-So if $r > 5$, then $\sigma$ ``lies above'' the case $\sigma', J$
+So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
 where $\sigma'$ has $r$ many ramification points all of order $3$
-and $J = \{1, \ldots, r\}$. If $r \leq 5$, then $\sigma$ ``lies
-above'' one of the base cases of Lemma ~\ref{lem:g_0_admissible_cases}.
-In either case, there is a $(\sigma', J)$ with $\sigma' = (0; e_1',
-\ldots, e_r'; 0)$ satisfying the property that for all $i \in J$,
-$e_i \geq e_i'$ and $e_i = e_i'$ otherwise where $(\sigma', J)$
-is either a base case from Lemma ~\ref{lem:g_0_admissible_cases}
-or the case from $r > 5$.
+and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
+all of the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+If $r \leq 5$, then $\sigma$ ``lies above'' one of the base cases
+of Lemma ~\ref{lem:g_0_admissible_cases}, all of which satisfy
+the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.
+
+So for any $r > 0$, there is a $(\sigma', J)$, either from
+Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
+the $r > 5$ case with ramification orders all $3$, with $\sigma' =
+(0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
+\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
 

### 2015-06-24 stacky_write_up/spin_cring.tex
edited section 3 lemmas

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 \begin{lem}
-\label{lem:sat_two_induction}
+\label{lem:sat-two-induction-high-genus}
 Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
@@
 , x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$.
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$).
 Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
-Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and choose an ordering on $k[x_2, \ldots, x_m]$ satisfies
 \begin{align*}
@@
 		\begin{align*}
-			J &= gin_\prec(I')k[x, y_3, y_4] \\
+			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4] \\
 			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
@@
 		\end{align*}
-			Then, $gin_\prec(I) = J$.
 	\item[(c)] Any set of minimal generators for $I'$ together with 
@@
 \begin{lem}
-\label{lem:sat_two_induction}
+\label{lem:sat-two-induction-genus-0}
 \todo{Make explicit assumptions on genus.}
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
-Actually, the map isn't ramified at $P$, it's just defined away from $P$.
-I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
-3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+Suppose $L'$ is a log half-canonical divisor of $\sx$ with course space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_{\halfcan'} = k[x_3, x_4
+, x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac{1}{
+3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
 \begin{align*}
@@
 Then, the following statements hold.
-
-\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
-\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
 
@@
 \begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+First, note that since we are in genus 0, we can choose the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
 _P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
@@
 \end{defn}
+
+\begin{lem}\label{lem:n-3s-admissible}
+\todo{lemma and proof}
+\end{lem}
 

### 2015-06-24 stacky_write_up/spin_cring.tex
edited introduction

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 \begin{enumerate}
-	\item Petri's Theorem
 	\item Modular Forms
-	\item Stacky Relations
+	\todo{Reference independence of base field}
 \end{enumerate}
+
+Let $X$ be a smooth algebraic curve over $k$ of genus $g$.
+It is well known that the sheaf $\Omega_X,$ with associated divisor $K_X$ determines the {\bf canonical map} $\pi:X \rightarrow \BP_k^{g-1}.$ Then, the {\bf canonical ring}, is defined as
+\begin{align*}
+	R(X,K_X) = \bigoplus_{n \geq 0} H^0(X,nK_X),
+\end{align*}
+with multiplication structure corresponding to tensor product of sections.
+Since $\Omega_X$ is ample, $X \cong \proj R$.
+Petri's theorem gives generators and relations for $R(X,K_X),$ see for example, \cite{saint-donat:proj}[Theorem, p.
+157], showing that in most cases $R(X,K_X)$ is generated in degree 1 with relations in degree 2.
+This has the pleasant geometric consequence that all such canonically embedded curves are scheme theoretically cut out by quadratic equations.
+
+In Voight and Zureick-Brown, \cite{vzb:stacky} examine a much more general setting, generalizing Petri's theorem in many directions.
+A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
+Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
+Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf ramification order} $e_i$ at $P_i$.
+Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$.
+A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
+The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
+\begin{align*}
+	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
+\end{align*}
+The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:
 
@@
 exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
-for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
+for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
 for signatures with $g = 0$.
@@
 
+\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
+Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
+curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
+\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
+\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
+$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
+x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
+\begin{enumerate}
+\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
+(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
+independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
+\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
+x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
+Then
+\begin{align*}
+			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_2^2\rangle.
+		\end{align*}
+\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
+leading terms as above minimally generate $I$.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
+Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
+\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
+all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
+$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
+choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
+dimension counting, we see that 
+\[
+	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
+\]
+\[
+	\langle y_1^a y_2: a\ge 0\rangle
+\]
+form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).
+
+To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
+\prec(I)$.  Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$.  For $j\ge 2$, we 
+can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
+\[
+	y_2x_j-A_jy_3w_j
+\]
+has no pole at $P$ at thus lies in $R_{\halfcan'}$.  Similarly, we can choose $B$ and $C$ 
+such that
+\[y^2_4+By_1^2x_2+Cy_1x_3\]
+has no pole at $P$, so it lies in $R_{\halfcan'}$.  These give us relations with initial terms 
+as desired, concluding part (b).
+
+Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
+
+\end{proof}
+
+\begin{lem}
+\label{lem:adding_points_saturation_2_to_1_no_log}
+Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
+with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
+\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
+Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
+$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
+Then
+\begin{enumerate}
+\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
+(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
+independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
+\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
+x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
+Then
+\begin{align*}
+			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_3^2
+		\end{align*}
+\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
+leading terms as above minimally generate $I$.
+\end{enumerate}
+\end{lem}
+\begin{proof}
+The proof follows similarly to that of lemma 
+\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
+\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
+generator in degree 3 rather than degree 2.  
+\end{proof}
+
+Transition to genus one.
+\todo{transition!}
+
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 2-Saturated Divisor}
+We prove an inductive theorem on adding 2-sat here.
+\todo{description}
+
+\begin{prop}
+\label{prop:sat_two_induction}
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
+Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
+$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
+, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
+3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
+\end{align*}
+Then, the following statements hold.
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
+		y_3$
+		and equip the ring $k[y_3, y_4, x]$ with the block 
+		order so that $R = k[y_3, y_4, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x, y_3, y_4] \\
+			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
+			&+\langle y_4^2.\rangle
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
+_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.}
+
+In a fashion analogous to the proof of Proposition 
+~\ref{prop:sat_three_induction}, we see 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:sat_two_add_generator}
+	\begin{split}
+		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \\
+		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
+	\end{split}
+\end{align}
+
+\noindent completing part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B y_3^2 x_2 \\
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
+
+Transition words.
+\todo{transition!}
+
+We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
+reference} and O'Dorney\todo{reference}.
+
 \begin{lem}
@@
 defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
-generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
+generator $u$ in degree 1.  Suppose $D$ is generated by $
+u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
 in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbf{N}$ such
+for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
 that
+
 \begin{equation}
@@
 In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
-%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
 \item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
@@
 
-\begin{lem}
-\label{lem:sat_two_induction}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
-Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
-, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$.
-Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
-Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
-\end{align*}
-Then, the following statements hold.
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
-		y_3$
-		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order so that $R = k[y_3, y_4, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_4^2.\rangle
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.}
-
-In a fashion analogous to the proof of Lemma 
-~\ref{lem:sat_three_induction}, we see 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:sat_two_add_generator}
-	\begin{split}
-		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \\
-		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
-	\end{split}
-\end{align}
-
-\noindent completing part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B y_3^2 x_2 \\
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
-\begin{lem}
-\label{lem:sat_two_induction}
-\todo{Make explicit assumptions on genus.}
-\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
-Actually, the map isn't ramified at $P$, it's just defined away from $P$.
-I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
-, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
-3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-Then, the following statements hold.
-
-\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
-\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
-		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
-		\begin{align*}
-			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
-			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
-		\end{align*}
-			Then, $gin_\prec(I) = J$.
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
-_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.} To complete the proof of (a) we only need 
-show these elements generate $R$ over $R'$. We can first see that 
-the following is a $k$ basis for $R$ over $R'$:
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
-	\end{split}
-\end{align}
-
-\noindent
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
-_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-,$ elements of degree $d$ in the claimed basis of
-~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-\rfloor $ and $b = d \bmod 3$, we have that the elements
-
-\begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
-3+b}
-\end{align*}
-
-\noindent
-are precisely $a$ elements, which are all independent as they have
-distinct pole orders at $P$. This completes part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_{i,j} \in k$ for $4
-\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B_1 y_3 y_5 \\
-	y_4y_5 &+ B_2 y_3^2 x_3 \\
-	y_5^2 &+ B_3 y_3^2 x_4
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
-\iffalse{
-\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
-Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
-curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
-\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
-\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
-$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
-x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
-\begin{enumerate}
-\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
-(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
-independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
-x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
-Then
-\begin{align*}
-			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_2^2\rangle.
-		\end{align*}
-\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-leading terms as above minimally generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
-Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
-\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
-all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
-$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
-choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
-dimension counting, we see that 
-\[
-	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
-\]
-\[
-	\langle y_1^a y_2: a\ge 0\rangle
-\]
-form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).
-
-To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
-\prec(I)$.  Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$.  For $j\ge 2$, we 
-can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
-\[
-	y_2x_j-A_jy_3w_j
-\]
-has no pole at $P$ at thus lies in $R_{\halfcan'}$.  Similarly, we can choose $B$ and $C$ 
-such that
-\[y^2_4+By_1^2x_2+Cy_1x_3\]
-has no pole at $P$, so it lies in $R_{\halfcan'}$.  These give us relations with initial terms 
-as desired, concluding part (b).
-
-Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
-
-\end{proof}
-
-\begin{lem}
-\label{lem:adding_points_saturation_2_to_1_no_log}
-Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
-with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
-\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
-Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
-$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
-Then
-\begin{enumerate}
-\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
-(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
-independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
-x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
-Then
-\begin{align*}
-			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_3^2
-		\end{align*}
-\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-leading terms as above minimally generate $I$.
-\end{enumerate}
-\end{lem}
-\begin{proof}
-The proof follows similarly to that of lemma 
-\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
-\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
-generator in degree 3 rather than degree 2.  
-\end{proof}
-
-We prove an inductive theorem on adding 2-sat here.
-
-We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
-reference} and O'Dorney\todo{reference}.
-
 \begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
@@
 \begin{proof}
-For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
+For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
 \end{proof}
@@
 
-}
-\fi
+Transition words.
+\todo{transition!}
+
+\ssec{Inductive Theorem: Increasing the Number of Ramified Points for a 3-saturated divisor}
+\label{ssec:g_0_ram_pts}
+
+\begin{prop}
+\label{prop:sat_three_induction}
+\todo{Make explicit assumptions on genus.}
+\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction.
+Actually, the map isn't ramified at $P$, it's just defined away from $P$.
+I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
+, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
+3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+\begin{align*}
+	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
+\end{align*}
+Then, the following statements hold.
+
+\todo{Peter: Do you mean to have $D=\frac{1}{3}P+D'$ or is it correct as written?}.
+\todo{Peter: We can generalize to arbitrary genus with the condition $\deg(D)>2g-2$ meaning $h^0(X,K-D)=0$ so Riemann-Roch gives us everything we wanted from $\mathbb{P}^1$.}
+
+\begin{enumerate}
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		_3,y_4,$ and$ y_5$ minimally generate $R$ over $R'$.
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
+		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
+		\begin{align*}
+			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
+		\end{align*}
+			Then, $gin_\prec(I) = J$.
+	\item[(c)] Any set of minimal generators for $I'$ together with 
+		any set of relations with leading terms as in (b) minimally 
+		generate $I$.
+\end{enumerate}
+\end{prop}
+
+\begin{proof}
+First, the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
+_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.} To complete the proof of (a) we only need 
+show these elements generate $R$ over $R'$. We can first see that 
+the following is a $k$ basis for $R$ over $R'$:
+
+\begin{align}
+\label{eqn:add_one_generator}
+	\begin{split}
+		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
+		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+	\end{split}
+\end{align}
+
+\noindent
+To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+,$ elements of degree $d$ in the claimed basis of
+~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+\rfloor $ and $b = d \bmod 3$, we have that the elements
+
+\begin{align*}
+	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+3+b}
+\end{align*}
+
+\noindent
+are precisely $a$ elements, which are all independent as they have
+distinct pole orders at $P$. This completes part (a).
+
+To show part (b), note that the generators in
+~\ref{eqn:add_one_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_{i,j} \in k$ for $4
+\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B_1 y_3 y_5 \\
+	y_4y_5 &+ B_2 y_3^2 x_3 \\
+	y_5^2 &+ B_3 y_3^2 x_4
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
+
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+\end{proof}
 
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}.
 
@@
 Now we have an inductive statement on the number of ramified
-points in Lemma ~\ref{lem:sat_three_induction} and
+points in Proposition ~\ref{prop:sat_three_induction} and
 an inductive statement on ramification orders in Theorem
@@
 
-Now we can induct on cases (a)-(k) of \ref{lem:g_0_admissible_cases}
+Now we can induct on cases (a)-(e) of \ref{lem:g_0_admissible_cases}
 to obtain bounds on the minimal generator and relation degrees for
@@
 Through the application of two processes of induction, by adding 
-points via Lemma ~\ref{lem:sat_three_induction} and by raising
+points via Proposition ~\ref{prop:sat_three_induction} and by raising
 ramification orders via Theorem ~\ref{thm:ram_order_ind},
@@
 \begin{center}
-\label{table:g_0_exceptional}
+\label{table:g-0-exceptional}
 \textbf{Table (IV)}: Genus 0 exceptional cases
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
-so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as listed in Table ~\ref{table:g_0_exceptional}.
+\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
+(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
+finite list of exceptional cases, as listed in Table
+~\ref{table:g-0-exceptional}.
 \end{thm}
@@
 \begin{proof}
-If $\sx$ has no ramification points, then we have the classical
-case which is done in Chapter 4 of Voight and Zureick-Brown
-\cite{vzb:stacky}.
-
-Now let us consider the case when $\delta \geq 2$. In this case,
-$\halfcan$ is an effective divisor. \todo{need to do this case}
-
-Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
-Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
-and not one of the exceptional cases in Table
-~\ref{table:g_0_exceptional}.
-
-If $r > 5$, then we can use Lemma
-~\ref{lem:sat_three_induction} to add ramified points with
-ramification order $3$ to case (k) of Lemma
-~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
-= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
-clearly satisfies the conditions of Lemma
-~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
-{ssec:g_0_saturation} that saturation is 3 here), and the
-immediate consequence of parts (a) and (c) of Lemma
-~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
-\halfcan')$ corresponding to signatures $\sigma'$ with ramification
-orders all equal to $3$ for any $r > 5$ is generated up to
-degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
-up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
-implies that these cases satisfy all of the conditions of Theorem
-~\ref{thm:ram_order_ind}.
-
-So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
-where $\sigma'$ has $r$ many ramification points all of order $3$
-and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
-all of the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
-If $r \leq 5$, then $\sigma$ ``lies above'' one of the base cases
-of Lemma ~\ref{lem:g_0_admissible_cases}, all of which satisfy
-the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.
-
-So for any $r > 0$, there is a $(\sigma', J)$, either from
-Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
-the $r > 5$ case with ramification orders all $3$, with $\sigma' =
-(0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
-\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
-
-All such base cases satisfy all of the hypotheses of
-Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
-R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
-to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
-generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
-It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
-R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
-e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
-(d) that the relations are generated up to degree $2e$.
 
@@
 %Then we can apply two processes of induction, by adding points via
-%Lemma ~\ref{lem:sat_two_induction} and by raising
+%Proposition ~\ref{prop:sat_three_induction} and by raising
 %ramification orders via Theorem ~\ref{thm:ram_order_ind},
@@
 %$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
-%number of ramified points via Lemma
-%~\ref{lem:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
+%number of ramified points via Proposition
+%~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
 %case (e) combined with the induction process on ramification orders

### 2015-06-24 stacky_write_up/spin_cring.tex
minor changes section 3
replace all ram pt -> stacky pt, ram ord -> stab ord

@@
 Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
-Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf ramification order} $e_i$ at $P_i$.
+Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$.
 Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$.
@@
 		\begin{align*}
-			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
+			\initial_\prec(I) &= \initial_\prec(I)k[x,y_3,y_4,y_5] \\
 			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
@@
 
-\ssec{Inductive Lemma: Raising Ramification Orders}
+\ssec{Inductive Lemma: Raising stabilizer orders}
 \label{ssec:ram_orders}
@@
 points in Lemma ~\ref{lem:sat_three_induction} and
-an inductive statement on ramification orders in Theorem
+an inductive statement on stabilizer orders in Theorem
 ~\ref{thm:ram_order_ind}. After verifying that explicit pairs
@@
 points via Lemma ~\ref{lem:sat_three_induction} and by raising
-ramification orders via Theorem ~\ref{thm:ram_order_ind},
+stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
 we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
@@
 \begin{proof}
-If $\sx$ has no ramification points, then we have the classical
+If $\sx$ has no stacky points, then we have the classical
 case which is done in Chapter 4 of Voight and Zureick-Brown
@@
 ~\ref{lem:sat_three_induction} to add ramified points with
-ramification order $3$ to case (k) of Lemma
+stabilizer order $3$ to case (k) of Lemma
 ~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
@@
 So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
-where $\sigma'$ has $r$ many ramification points all of order $3$
+where $\sigma'$ has $r$ many stacky points all of order $3$
 and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
@@
 Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
-the $r > 5$ case with ramification orders all $3$, with $\sigma' =
+the $r > 5$ case with stabilizer orders all $3$, with $\sigma' =
 (0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
@@
 %Lemma ~\ref{lem:sat_two_induction} and by raising
-%ramification orders via Theorem ~\ref{thm:ram_order_ind},
+%stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
 %to obtain the desired result for any tame log spin curve $(\sx,
@@
 %
-%A process of induction raising the ramification orders of
+%A process of induction raising the stabilizer orders of
 %the ramified points of the spin curves corresponding to Lemma
@@
 %~\ref{lem:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
-%case (e) combined with the induction process on ramification orders
+%case (e) combined with the induction process on stabilizer orders
 %will yield the result for curves with at least five ramified points.

### 2015-06-24 stacky_write_up/spin_cring.tex
minor citation fixes

@@
 While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$.
-In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].
+In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite[Section III.4]{neves:halfcan}.
 
@@
 \label{defn:sat}
-\textbf{Saturations} of the canonical divisor, as defined in 7.
-2 of VZB \cite{vzb:stacky}.
+\textbf{Saturations} of the canonical divisor, as defined in Voight
+and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
 \end{defn}

### 2015-06-24 stacky_write_up/spin_cring.tex
preliminary introduction

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 \newcommand\sssec{\subsubsection}
+\newcommand\bh{{\mathbb H}}
 \newcommand\bO{{\mathbf O}}
@@
 
-Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
-and O'Dorney's paper \cite{dorney:canonical}.
-
-We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.
-
-\subsection{Main Results}
-\begin{enumerate}
-	\item Modular Forms
-	\todo{Reference independence of base field}
-\end{enumerate}
+Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e.
+a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations.
+We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$.
+For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$.
+It may well be that $\Gamma \backslash \bh$ is not comapact.
+Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$.
+We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$.
+In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
+
+In order to answer this question, we translate the seemingly analytic question into the algebraic category, using a generalization of the GAGA principle.
+That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of categories between orbifold curves and log stacky curves over $\BC$.
+Hence, for the remainder of the paper, we will work in the algebraic category.
 
@@
 
-In Voight and Zureick-Brown, \cite{vzb:stacky} examine a much more general setting, generalizing Petri's theorem in many directions.
+Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
 A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
@@
 \label{sec:background}
+\todo{Reference independence of base field}
 Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.

### 2015-06-24 stacky_write_up/spin_cring.tex
include delta>0 in g=0 pf

@@
 \label{sec:g_0}
-Now we consider the genus zero case.
-\todo{write intro}
-
-\ssec{Genus Zero Effective}
-\label{ssec:g_0_effective}
-
-In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ 
-when $\Delta$ is a non- zero effective divisor.  Using this, we can 
-reduce to looking at effective stacky divisors.  Then, applying a 
-result for general effective $\mathbf{Q}$ divisors, we deduce that $
-R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with 
-relations generated up to degree $2e$ with initial terms quadratic 
-in the generators.  We also demonstrate that these bounds are tight 
-up to \todo{insert how tight they are}.
-
-We have Lemma ~\ref{lem:minimal_quadratic}.
-\todo{fill in hole here, with adding points too}
-
-\begin{lem}\label{lem:add_point_effective_divisor_deg_1_but_not_deg_2_generators}
-Let $2\halfcan=K_X$ of a non-stacky curve $X$ such that $h^0(X, \halfcan) > 0$.  Then for any point $P$, 
-\[
-	H^0(X, \halfcan+P)=H^0(X,\halfcan).
-\]
-\end{lem}
-\begin{proof}
-\todo{add proof}
-\end{proof}
-
-\ssec{Genus Zero Non-effective}
-\label{ssec:g_0_non_effective}
-In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
-so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
-$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
-e_r)$ with relations generated in degree at most $2e$, so long as $\sigma$
-does not lie in a finite list of exceptions. This is proven in
-Subsection ~\ref{ssec:g_0_main}. The proof is a rather
-involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
-~\ref{ssec:g_0_ram_orders} \todo{fix} we prove inductive theorems, and in
-Subsection ~\ref{ssec:g_0_base} we check the base cases of the
-induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
-list out the exceptional cases.
+We will prove that if $(\sx , 0, \halfcan)$ is a spin curve, so
+that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
+then $R(\sx , \Delta, L)$ is generated in degree at most $e := \max(
+5, e_1, \ldots, e_r)$ with relations generated in degree at most $2e
+$, so long as $\sigma$ does not lie in a finite list of exceptions.
+
+There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
+ (note that $\delta$ must be odd or zero because $\halfcan \in \text
+{ Div } \sx$). In the first case, $\deg \lfloor \halfcan \rfloor
+\geq 0$ so the result directly follows from Lemma
+~\ref{rem:deg1_sat_ind}. When $\delta = 0$, this is not necessarily
+true so the proof is a rather involved induction using Lemma
+~\ref{lem:sat_three_ induction} and Theorem ~\ref{thm:ram_order_ind}.
+The remainder of this section is dedicated to characterizing the
+saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
+base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
+cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
+before proving the main theorem in full for all $\delta$ in
+Subsection ~\ref{ssec:g_0_ main}.
 
@@
 If $\sx$ has no stacky points, then we have the classical
-case which is done in Chapter 4 of Voight and Zureick-Brown
-\cite{vzb:stacky}.
-
-Now let us consider the case when $\delta \geq 2$. In this case,
-$\halfcan$ is an effective divisor. \todo{need to do this case}
+case which is done in Voight and Zureick-Brown ~\cite[Section 4.2]
+{vzb:stacky}.
+
+Now let us consider the case when $\delta \geq 2$. In any such case,
+$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
+of Lemma ~\ref{rem:deg1_sat_ind} are satisfied. Thus, we can apply
+the lemma inductively on the classical case with no stacky points
+to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
+with relations generated up to degree $2e$.
 

### 2015-06-24 stacky_write_up/spin_cring.tex
minor citation fixes

@@
 We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$.
-In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
+In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[Chapters 7-9]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
 
@@
 A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
-Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
+Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
 Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$.
-Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$.
+Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$.
 A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.

### 2015-06-24 stacky_write_up/spin_cring.tex
Changes to proofs of section 3 lemmas

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 \newcommand\sssec{\subsubsection}
-\newcommand\bh{{\mathbb H}}
 \newcommand\bO{{\mathbf O}}
@@
 
-Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e.
-a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations.
-We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$.
-For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$.
-It may well be that $\Gamma \backslash \bh$ is not comapact.
-Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$.
-We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$.
-In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
-
-In order to answer this question, we translate the seemingly analytic question into the algebraic category, using a generalization of the GAGA principle.
-That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of categories between orbifold curves and log stacky curves over $\BC$.
-Hence, for the remainder of the paper, we will work in the algebraic category.
+Example, stuff from Voight and Zureick-Brown \cite{vzb:stacky}
+and O'Dorney's paper \cite{dorney:canonical}.
+
+We consider divisors of the form $D = \sum_{i = 1}^{r} \subhalf{e_i}$.
+
+\subsection{Main Results}
+\begin{enumerate}
+	\item Modular Forms
+	\todo{Reference independence of base field}
+\end{enumerate}
 
@@
 
-Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
+In Voight and Zureick-Brown, \cite{vzb:stacky} examine a much more general setting, generalizing Petri's theorem in many directions.
 A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
@@
 While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$.
-In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite[Section III.4]{neves:halfcan}.
+In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite{neves:halfcan}[Section III.4].
 
@@
 \label{sec:background}
-\todo{Reference independence of base field}
 Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
@@
 \label{defn:sat}
-\textbf{Saturations} of the canonical divisor, as defined in Voight
-and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
+\textbf{Saturations} of the canonical divisor, as defined in 7.
+2 of VZB \cite{vzb:stacky}.
 \end{defn}
@@
 
+\todo{definition and basic properties of best lower approximations}
+
 \begin{lem}
@@
 defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
-generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbf{N}$ such
-that
+satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.
+Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbf{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
+$u, x_1, \ldots, _m$ all with $\ord_P=0$ and such that $\deg(u)=1$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$, where all $x_i$s also satisfy $\ord_P(u)(x_i)$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $\alpha,\beta \in \mathbf{N}$ such that
 \begin{equation}
@@
 	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbf{
 	N} : d \ge \frac{\beta}{\alpha}.
@@
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$).  
-Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
-Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and choose an ordering on $k[x_2, \ldots, x_m]$ satisfies
+Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)=0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
+Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
 \begin{align*}
@@
 Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.}
+_P(y_i) = 1$ by Riemann-Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need to cite lemma 5.4.7.}
 
@@
 
-To show part (b), note that the generators in
-~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B y_3^2 x_2 \\
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
+For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$.  If it is nonpositive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$.  Otherwise, 
+we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j-A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation.  
+Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
+In both cases we induce a relation, with initial term described in the lemma's statement.
+Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
 

### 2015-06-24 stacky_write_up/spin_cring.tex
ref fixes

@@
 Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
-A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
+A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
 Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
@@
 In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively.
-Finally, in Section ~\ref{further-questions}, we pose several questions for future research.
+Finally, in Section ~\ref{sec:further-questions}, we pose several questions for future research.
 
@@
 (d) that the relations are generated up to degree $2e$.
-
-%By Lemma ~\ref{lem:g_0_admissible_cases}, we know that for
-%any tame log spin curves $(\sx', \Delta, \halfcan')$ over a perfect
-%field $k$ with signature $\sigma'$ and set $J$ such that $(\sigma',
-%J)$ is one of the listed base cases, $(\sigma', J)$ is admissible.
-%Furthermore, $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k
-%$- algebra by elements of degree at most $e = \max(5, e_1, \ldots, e
-%_r)$ with relations in degree at most $2e$. It also admits a
-%presentation
-%
-%\begin{align*}
-	%R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
-%\end{align*}
-%
-%\noindent
-%given by admissibility satisfying the statements that for all $i \in 
-%J$, $e_i > \deg z$ for any generator $z$ of $R'$ and that $in_\prec
-%(I')$ is minimally generated by products of two monomials under
-%some ordering.
-%
-%Then we can apply two processes of induction, by adding points via
-%Lemma ~\ref{lem:sat_two_induction} and by raising
-%stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
-%to obtain the desired result for any tame log spin curve $(\sx,
-%\Delta, L)$ over a perfect field $k$ with signature $\sigma$
-%covered by this induction process.
-%
-%
-%
-%A process of induction raising the stabilizer orders of
-%the ramified points of the spin curves corresponding to Lemma
-%~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
-%~\ref{thm:ram_order_ind} will demonstrate the desired generator and
-%relation degree results for curves with three ramified points.
-%Similarly, this induction process on Lemma
-%~\ref{lem:g_0_admissible_cases} case (d) will give the desired
-%result for curves with four ramified points excluding signature
-%$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
-%number of ramified points via Lemma
-%~\ref{lem:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
-%case (e) combined with the induction process on stabilizer orders
-%will yield the result for curves with at least five ramified points.
 \end{proof}

### 2015-06-24 stacky_write_up/spin_cring.tex
sat-three-induction fix

@@
 \begin{lem}
-\label{lem:sat-two-induction-genus-0}
+\label{lem:sat-three-induction-g-0}
 \todo{Make explicit assumptions on genus.}
@@
 Now we have an inductive statement on the number of ramified
-points in Lemma ~\ref{lem:sat_three_induction} and
+points in Lemma ~\ref{lem:sat-three-induction-g-0} and
 an inductive statement on stabilizer orders in Theorem
@@
 Through the application of two processes of induction, by adding 
-points via Lemma ~\ref{lem:sat_three_induction} and by raising
+points via Lemma ~\ref{sat-three-induction-g-0} and by raising
 stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
@@
 If $r > 5$, then we can use Lemma
-~\ref{lem:sat_three_induction} to add ramified points with
+~\ref{sat-three-induction-g-0} to add ramified points with
 stabilizer order $3$ to case (k) of Lemma
@@
 clearly satisfies the conditions of Lemma
-~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
+~\ref{sat-three-induction-g-0} (recall from Subsection ~\ref
 {ssec:g_0_saturation} that saturation is 3 here), and the
 immediate consequence of parts (a) and (c) of Lemma
-~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
+~\ref{sat-three-induction-g-0} is that any $R(\sx', \Delta,
 \halfcan')$ corresponding to signatures $\sigma'$ with ramification

### 2015-06-24 stacky_write_up/spin_cring.tex
fixed all bad references

@@
 \begin{lem}
-\label{lem:deg1_sat_ind}
+\label{lem:deg1-sat-ind}
 Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
@@
 In a fashion analogous to the proof of Lemma 
-~\ref{lem:sat_three_induction}, we see 
+~\ref{lem:sat-three-induction-g-0}, we see 
 the following is a $k$ basis for $R$ over $R'$:
@@
 \iffalse{
-\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
+\begin{lem}
+\label{lem:adding_points_saturation_2_to_1_with_log}
 Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
@@
 In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$.
-In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Subsection ~\ref{ssec:g_0_effective} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
+In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
 The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved.
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
 
@@
 \geq 0$ so the result directly follows from Lemma
-~\ref{rem:deg1_sat_ind}. When $\delta = 0$, this is not necessarily
+~\ref{lem:deg1-sat-ind}. When $\delta = 0$, this is not necessarily
 true so the proof is a rather involved induction using Lemma
-~\ref{lem:sat_three_ induction} and Theorem ~\ref{thm:ram_order_ind}.
+~\ref{lem:sat-three-induction-g-0} and Theorem ~\ref{thm:ram_order_ind}.
 The remainder of this section is dedicated to characterizing the
-saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
-base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
+saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
+base cases (Subsection ~\ref{ssec:g_0_base}), and exceptional
 cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
 before proving the main theorem in full for all $\delta$ in
-Subsection ~\ref{ssec:g_0_ main}.
+Subsection ~\ref{ssec:g_0_main}.
 
@@
 Through the application of two processes of induction, by adding 
-points via Lemma ~\ref{sat-three-induction-g-0} and by raising
+points via Lemma ~\ref{lem:sat-three-induction-g-0} and by raising
 stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
@@
 $\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
-of Lemma ~\ref{rem:deg1_sat_ind} are satisfied. Thus, we can apply
+of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
 the lemma inductively on the classical case with no stacky points
@@
 If $r > 5$, then we can use Lemma
-~\ref{sat-three-induction-g-0} to add ramified points with
+~\ref{lem:sat-three-induction-g-0} to add ramified points with
 stabilizer order $3$ to case (k) of Lemma
@@
 clearly satisfies the conditions of Lemma
-~\ref{sat-three-induction-g-0} (recall from Subsection ~\ref
+~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
 {ssec:g_0_saturation} that saturation is 3 here), and the
 immediate consequence of parts (a) and (c) of Lemma
-~\ref{sat-three-induction-g-0} is that any $R(\sx', \Delta,
+~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
 \halfcan')$ corresponding to signatures $\sigma'$ with ramification
@@
 to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
-generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
+generated up to degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}.
 It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
@@
 	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
-	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
+	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relations_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
 \todo{Possibly think more about this}

### 2015-06-24 stacky_write_up/spin_cring.tex
edit proof to 3.4
document-wide style edits

@@
 \end{align*}
+
+\noindent
 with multiplication structure corresponding to tensor product of sections.
@@
 \begin{align*}
-	R(X,\Delta,L) = \oplus_{n=0}^\infty H^0(X,nL)
-\end{align*}
+	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
+\end{align*}
+
+\noindent
 The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
 \end{align*}
@@
 \]
+
+\noindent
 be the non-negative best lower approximation of $\frac{
@@
 \]
+
+\noindent
 so we have the pole order of $\prod z_i$ is 
@@
 \]
+
+\noindent
 Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
@@
 \]
+
+\noindent
 and if more than one $d_i$ is 1, we
@@
 \]
+
+\noindent
 Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
@@
 \rfloor + 1}$.
+
 Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
@@
 \]
+
+\noindent
 giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
@@
 \]
+
+\noindent
 implying a relation with initial term $y_i y_j$.
@@
 \]
+
+\noindent
 Similarly if $i=1$, then we get the same result using
@@
 \]
+
+\noindent
 In both cases we deduce that $y_iy_j$ is an initial term of some relation.
@@
 \]
+
+\noindent
 Similarly if $i=1$ then
@@
 \]
+
+\noindent
 In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
@@
 Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+
 Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
 , x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$).  
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
+
 Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)=0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
@@
 \end{align*}
+
+\noindent
 Then, the following statements hold.
+
 \begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ minimally generate $R$ over $R'$.
+	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
+		\{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements
+		$y_3,y_4,$ minimally generate $R$ over $R'$.
 	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
@@
 
-\noindent completing part (a).
-
-For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$.  If it is nonpositive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$.  Otherwise, 
+\noindent
+completing part (a).
+
+For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$.  If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$.  Otherwise, 
 we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j-A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation.  
@@
 
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
 \end{proof}
@@
 \todo{Make explicit assumptions on genus.}
-Suppose $L'$ is a log half-canonical divisor of $\sx$ with course space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_{\halfcan'} = k[x_3, x_4
-, x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac{1}{
-3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
+Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
+space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_
+{\halfcan'} = k[x_3, x_4 , x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac
+{1}{3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
+the ordering on $k[x]$ satisfies
 \begin{align*}
@@
 \end{align*}
+
+\noindent
 Then, the following statements hold.
@@
 \begin{proof}
-First, note that since we are in genus 0, we can choose the elements $y_3,y_4,$ and $y_5$ are general and have $-\ord
-_P(y_i) = 1$ by Riemann Roch. \todo{Understand why/whether we need 
-to cite lemma 5.4.7.} To complete the proof of (a) we only need 
-show these elements generate $R$ over $R'$. We can first see that 
-the following is a $k$ basis for $R$ over $R'$:
+First, note that since we are in genus 0, we can choose the
+elements $y_3,y_4,$ and $y_5$ are general and have $-\ord _P(y_i) =
+1$ by Riemann Roch. \todo{Understand why/whether we need to cite 
+lemma 5.4.7.} To complete the proof of (a) we only need show these
+elements generate $R$ over $R'$. We can first see that the
+following is a $k$ basis for $R$ over $R'$:
 
@@
 
-\iffalse{
-\begin{lem}
-\label{lem:adding_points_saturation_2_to_1_with_log}
-Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
-curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
-\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
-\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
-$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
-x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
-\begin{enumerate}
-\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
-(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
-independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
-x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
-Then
-\begin{align*}
-			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_2^2\rangle.
-		\end{align*}
-\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-leading terms as above minimally generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
-Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
-\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
-all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
-$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
-choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
-dimension counting, we see that 
-\[
-	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
-\]
-\[
-	\langle y_1^a y_2: a\ge 0\rangle
-\]
-form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).
-
-To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
-\prec(I)$.  Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$.  For $j\ge 2$, we 
-can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
-\[
-	y_2x_j-A_jy_3w_j
-\]
-has no pole at $P$ at thus lies in $R_{\halfcan'}$.  Similarly, we can choose $B$ and $C$ 
-such that
-\[y^2_4+By_1^2x_2+Cy_1x_3\]
-has no pole at $P$, so it lies in $R_{\halfcan'}$.  These give us relations with initial terms 
-as desired, concluding part (b).
-
-Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
-
-\end{proof}
-
-\begin{lem}
-\label{lem:adding_points_saturation_2_to_1_no_log}
-Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
-with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
-\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
-Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
-$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
-Then
-\begin{enumerate}
-\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
-(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
-independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
-x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
-Then
-\begin{align*}
-			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_3^2
-		\end{align*}
-\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-leading terms as above minimally generate $I$.
-\end{enumerate}
-\end{lem}
-\begin{proof}
-The proof follows similarly to that of lemma 
-\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
-\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
-generator in degree 3 rather than degree 2.  
-\end{proof}
-
-We prove an inductive theorem on adding 2-sat here.
-
-We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
-reference} and O'Dorney\todo{reference}.
-
-\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
-Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
-\end{rem}
-
-This yields some immediate corollaries:
-
-\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
-\end{cor}
-
-\begin{proof}
-We can prove this by induction.  As a base case, let $D\sim 0$.  Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
-Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i=1}^{r+1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
+%\begin{lem}
+%\label{lem:adding_points_saturation_2_to_1_with_log}
+%Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
+%curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
+%\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
+%\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
+%$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
+%x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. Then
+%
+%\begin{enumerate}
+%\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
+%(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
+%independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
+%\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
+%x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
+%Then
+%\begin{align*}
+			%in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			%&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
+			%&+\langle y_2^2\rangle.
+		%\end{align*}
+%\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
+%leading terms as above minimally generate $I$.
+%\end{enumerate}
+%\end{lem}
+%
+%\begin{proof}
+%Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
+%Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
+%\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
+%all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
+%$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
+%choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
+%dimension counting, we see that 
+%\[
+	%\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
+%\]
+%\[
+	%\langle y_1^a y_2: a\ge 0\rangle
+%\]
+%form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).
+%
+%To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
+%\prec(I)$.  Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$.  For $j\ge 2$, we 
+%can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
+%\[
+	%y_2x_j-A_jy_3w_j
+%\]
+%has no pole at $P$ at thus lies in $R_{\halfcan'}$.  Similarly, we can choose $B$ and $C$ 
+%such that
+%\[y^2_4+By_1^2x_2+Cy_1x_3\]
+%has no pole at $P$, so it lies in $R_{\halfcan'}$.  These give us relations with initial terms 
+%as desired, concluding part (b).
+%
+%Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
+%
+%\end{proof}
+%
+%\begin{lem}
+%\label{lem:adding_points_saturation_2_to_1_no_log}
+%Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
+%with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
+%\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
+%Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
+%$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
+%Then
+%\begin{enumerate}
+%\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
+%(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
+%independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
+%\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
+%x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
+%Then
+%\begin{align*}
+			%in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			%&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
+			%&+\langle y_3^2
+		%\end{align*}
+%\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
+%leading terms as above minimally generate $I$.
+%\end{enumerate}
+%\end{lem}
+%\begin{proof}
+%The proof follows similarly to that of lemma 
+%\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
+%\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
+%generator in degree 3 rather than degree 2.  
+%\end{proof}
+%
+%We prove an inductive theorem on adding 2-sat here.
+%
+%
+%We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
+%reference} and O'Dorney\todo{reference}.
+%
+%\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
+%Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
+%\end{rem}
+%
+%This yields some immediate corollaries:
+%
+%\begin{cor}\label{cor:effective_Q_divisor_can_ring}
+%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
+%\end{cor}
+%
+%\begin{proof}
+%We can prove this by induction.  As a base case, let $D\sim 0$.  Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
+%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i=1}^{r+1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
 By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
 Since $D$ is effective, the condition of equation \ref{eqn:deg1_sat_ind_dim} is met, so by remark \ref{rem:deg1_sat_ind_gen_rel_degrees} of lemma \ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
-\end{proof}
-
-\todo{do these corollaries fit here?}
-
-\begin{cor}\label{cor:genus_0_positive_delta}
-Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.
+%\end{proof}
+%
+%\todo{do these corollaries fit here?}
+%
+%\begin{cor}\label{cor:genus_0_positive_delta}
+%Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.
 Then $\halfcan$ is effective so we can inductively apply lemma \ref{lem:deg1_sat_ind}.
-\end{cor}
-\begin{proof}
-Since $\halfcan$ is a half canonical divisor, 
-\[
-	2\halfcan=D+\sum \subhalf{e_i}P_i
-\] 
-where 
-\[
-	D\sim K_X+\Delta\sim -2\infty+ \Delta
-\] is a divisor of $X$ (i.e. with 
-possibly negative integer coefficients).  Since $\Delta$ is non-
-zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
-any point $P$ occurring in a stacky divisor of $\sx$ must have 
-coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
-s appearing in the characteristic of $(\sx,\Delta)$).
-
-Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
-coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
- must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
-\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
-is linearly equivalent to an effective $X$ divisor plus $\sum 
-\subhalf{i}P_i$.  We have thus shown $\halfcan$ is linearly equivalent to an effective divisor.  Thus, by \ref{cor:effective_Q_divisor_can_ring} the desired result follows.
-\end{proof}
-
-\begin{cor}
-Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
-\end{cor}
-\begin{proof}
-For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
-\end{proof}
-
-\todo{Move this lemma:}
-\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
-Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
-Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$.
-Then 
-\begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j \rangle \\
-										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
-\end{align*}
-\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
-\end{itemize}
-\end{lem}
-\begin{proof}
-Similar to all the other lemmas\todo{combine sections?}
-\end{proof}
-
-}
-\fi
+%\end{cor}
+%\begin{proof}
+%Since $\halfcan$ is a half canonical divisor, 
+%\[
+	%2\halfcan=D+\sum \subhalf{e_i}P_i
+%\] 
+%where 
+%\[
+	%D\sim K_X+\Delta\sim -2\infty+ \Delta
+%\] is a divisor of $X$ (i.e. with 
+%possibly negative integer coefficients).  Since $\Delta$ is non-
+%zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
+%any point $P$ occurring in a stacky divisor of $\sx$ must have 
+%coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+%s appearing in the characteristic of $(\sx,\Delta)$).
+ %
+%Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
+%coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
+ %must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
+%\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
+%is linearly equivalent to an effective $X$ divisor plus $\sum 
+%\subhalf{i}P_i$.  We have thus shown $\halfcan$ is linearly equivalent to an effective divisor.  Thus, by \ref{cor:effective_Q_divisor_can_ring} the desired result follows.
+%\end{proof}
+%
+%\begin{cor}
+%Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
+%\end{cor}
+%\begin{proof}
+%For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
+%\end{proof}
+%
+%\todo{Move this lemma:}
+%\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
+%Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
+%Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
+%generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+%in degree at most $\bar{\tau}$.
+%Then 
+%\begin{itemize}
+%\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
+%\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
+%
+%\begin{align*}
+	%\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+										 %&+ \langle y_i x_j \rangle \\
+										 %&+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
+%\end{align*}
+%\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
+%\end{itemize}
+%\end{lem}
+%\begin{proof}
+%Similar to all the other lemmas\todo{combine sections?}
+%\end{proof}
 
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i,e_i})}{\deg (y_{i,e_i})} \leq \subhalf{
-e_j'}-
-			\frac{1}{\deg(y_{i,e_i})e_j'}
+			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq \subhalf{
+			e_j'} - \frac{1}{\deg(y_{i,e_i})e_j'}
 		\end{align*}
@@
 is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
-Since $K$ is basepoint free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
-Then, by the basepoint free pencil trick, we obtain an exact sequence
+Since $K$ is basepoint-free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
+Then, by the basepoint-free pencil trick, we obtain an exact sequence
 $$\begin{tikzcd}
@@
 \end{tikzcd}$$
+
 We wish to show $f$ is surjective.
@@
 \todo{This remark isn't quite right, we're changing the proof}
-\cite{neves:halfcan}[Proposition III.4]
-In \cite{neves:halfcan}[Proposition III.4], Neves claims to prove that $R_L$ is generated in degree at most 5.
+In \cite[Proposition III.4]{neves:halfcan}, Neves claims to prove that $R_L$ is generated in degree at most 5.
 However, when the proof is carefully examined, it only shows generation in degree at most 6.
@@
 
-\section{Genus one}
+\section{Genus One}
 \label{sec:g_1}
@@
 
-\ssec{Genus 1 Base Cases}
+\ssec{Genus One Base Cases}
 \label{ssec:g_1_base}
@@
 
-\ssec{Genus 1 Exceptional Cases}
+\ssec{Genus One Exceptional Cases}
 
@@
 
-\ssec{Main Theorem for Genus 1}
+\ssec{Main Theorem for Genus One}
 \label{ssec:main_g_1}

### 2015-06-24 stacky_write_up/spin_cring.tex
add n 3s lemma
oops pushed non-compilable tex

@@
 \begin{lem}\label{lem:n-3s-admissible}
-\todo{lemma and proof}
+Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.
+Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
 \end{lem}
+\begin{proof}\todo{proof}
+
+\end{proof}
 

### 2015-06-24 stacky_write_up/spin_cring.tex
added list for background

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$.
-In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[Chapters 7-9]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
+In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
 
@@
 Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
-A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
-Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
+A divisor $\Delta \in \d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
+Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite{vzb:stacky}[Section 5.2] so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
 Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$.
-Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$.
+Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$.
 A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
@@
 In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively.
-Finally, in Section ~\ref{sec:further-questions}, we pose several questions for future research.
+Finally, in Section ~\ref{further-questions}, we pose several questions for future research.
 
@@
 Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
-\todo{edit this}
+Include the following:
+\begin{enumerate}
+	\item Note that this result is independence of base field
+	\item background on grobner bases
+	\item Notation $h^0 = \dim H^0$.
+	\item Why we have these fractions $\frac{e_i-1}{2e_i}$ and why $e_i$ must be odd.
+\end{enumerate}
 
@@
 
-\todo{definition and basic properties of best lower approximations}
-
 \begin{lem}
-\label{lem:deg1-sat-ind}
+\label{lem:deg1_sat_ind}
 Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
 defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbf{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
-$u, x_1, \ldots, _m$ all with $\ord_P=0$ and such that $\deg(u)=1$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$, where all $x_i$s also satisfy $\ord_P(u)(x_i)$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbf{N}$ such that
+satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
+generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
+in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $\alpha,\beta \in \mathbf{N}$ such
+that
 \begin{equation}
@@
 	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbf{
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
 	N} : d \ge \frac{\beta}{\alpha}.
@@
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$).
-Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)=0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
-Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
+Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
+Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and choose an ordering on $k[x_2, \ldots, x_m]$ satisfies
 \begin{align*}
@@
 Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann-Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need to cite lemma 5.4.7.}
+_P(y_i) = 1$ by Riemann Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need 
+to cite lemma 5.4.7.}
 
 In a fashion analogous to the proof of Lemma 
-~\ref{lem:sat-three-induction-g-0}, we see 
+~\ref{lem:sat_three_induction}, we see 
 the following is a $k$ basis for $R$ over $R'$:
@@
 
-For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$.  If it is nonpositive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$.  Otherwise, 
-we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j-A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation.  
-Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
-In both cases we induce a relation, with initial term described in the lemma's statement.
-Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
+To show part (b), note that the generators in
+~\ref{eqn:sat_two_add_generator} are precisely a set of monomials which
+generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+
+This follows, since there exist constants $A_j \in k$ for $3 \leq j \leq m,$ and a constnant $B \in k$ and
+elements $w_{i,j} \in R'$ so that the following linear combinations
+of elements lie in $R'$.
+
+\begin{align*}
+	y_4x_j &- A_j y_3 w_j & \text{ so that } 2 \leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B y_3^2 x_2 \\
+\end{align*}
+
+\noindent
+Of course, the initial terms of these elements are precisely the
+generators of $J$, completing (b).
 
@@
 \begin{lem}
-\label{lem:sat-three-induction-g-0}
+\label{lem:sat-two-induction-genus-0}
 \todo{Make explicit assumptions on genus.}
@@
 \iffalse{
-\begin{lem}
-\label{lem:adding_points_saturation_2_to_1_with_log}
+\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
 Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
@@
 In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$.
-In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
+In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Subsection ~\ref{ssec:g_0_effective} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
 The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved.
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.
 
@@
 \geq 0$ so the result directly follows from Lemma
-~\ref{lem:deg1-sat-ind}. When $\delta = 0$, this is not necessarily
+~\ref{rem:deg1_sat_ind}. When $\delta = 0$, this is not necessarily
 true so the proof is a rather involved induction using Lemma
-~\ref{lem:sat-three-induction-g-0} and Theorem ~\ref{thm:ram_order_ind}.
+~\ref{lem:sat_three_ induction} and Theorem ~\ref{thm:ram_order_ind}.
 The remainder of this section is dedicated to characterizing the
-saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
-base cases (Subsection ~\ref{ssec:g_0_base}), and exceptional
+saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
+base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
 cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
 before proving the main theorem in full for all $\delta$ in
-Subsection ~\ref{ssec:g_0_main}.
+Subsection ~\ref{ssec:g_0_ main}.
 
@@
 Now we have an inductive statement on the number of ramified
-points in Lemma ~\ref{lem:sat-three-induction-g-0} and
+points in Lemma ~\ref{lem:sat_three_induction} and
 an inductive statement on stabilizer orders in Theorem
@@
 Through the application of two processes of induction, by adding 
-points via Lemma ~\ref{lem:sat-three-induction-g-0} and by raising
+points via Lemma ~\ref{lem:sat_three_induction} and by raising
 stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
@@
 $\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
-of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
+of Lemma ~\ref{rem:deg1_sat_ind} are satisfied. Thus, we can apply
 the lemma inductively on the classical case with no stacky points
@@
 If $r > 5$, then we can use Lemma
-~\ref{lem:sat-three-induction-g-0} to add ramified points with
+~\ref{lem:sat_three_induction} to add ramified points with
 stabilizer order $3$ to case (k) of Lemma
@@
 clearly satisfies the conditions of Lemma
-~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
+~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
 {ssec:g_0_saturation} that saturation is 3 here), and the
 immediate consequence of parts (a) and (c) of Lemma
-~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
+~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
 \halfcan')$ corresponding to signatures $\sigma'$ with ramification
@@
 to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
-generated up to degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}.
+generated up to degree $2e'$ by Lemma ~\ref{g_0_admissible_cases}.
 It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
@@
 (d) that the relations are generated up to degree $2e$.
+
+%By Lemma ~\ref{lem:g_0_admissible_cases}, we know that for
+%any tame log spin curves $(\sx', \Delta, \halfcan')$ over a perfect
+%field $k$ with signature $\sigma'$ and set $J$ such that $(\sigma',
+%J)$ is one of the listed base cases, $(\sigma', J)$ is admissible.
+%Furthermore, $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k
+%$- algebra by elements of degree at most $e = \max(5, e_1, \ldots, e
+%_r)$ with relations in degree at most $2e$. It also admits a
+%presentation
+%
+%\begin{align*}
+	%R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
+%\end{align*}
+%
+%\noindent
+%given by admissibility satisfying the statements that for all $i \in 
+%J$, $e_i > \deg z$ for any generator $z$ of $R'$ and that $in_\prec
+%(I')$ is minimally generated by products of two monomials under
+%some ordering.
+%
+%Then we can apply two processes of induction, by adding points via
+%Lemma ~\ref{lem:sat_two_induction} and by raising
+%stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
+%to obtain the desired result for any tame log spin curve $(\sx,
+%\Delta, L)$ over a perfect field $k$ with signature $\sigma$
+%covered by this induction process.
+%
+%
+%
+%A process of induction raising the stabilizer orders of
+%the ramified points of the spin curves corresponding to Lemma
+%~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
+%~\ref{thm:ram_order_ind} will demonstrate the desired generator and
+%relation degree results for curves with three ramified points.
+%Similarly, this induction process on Lemma
+%~\ref{lem:g_0_admissible_cases} case (d) will give the desired
+%result for curves with four ramified points excluding signature
+%$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
+%number of ramified points via Lemma
+%~\ref{lem:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
+%case (e) combined with the induction process on stabilizer orders
+%will yield the result for curves with at least five ramified points.
 \end{proof}
@@
 	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
-	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relations_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
+	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
 \todo{Possibly think more about this}

### 2015-06-24 stacky_write_up/spin_cring.tex
fixed genus 1 base cases to include canonical divisor as half canonical divisor

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 
+\begin{longtable}	{| c || c | c | c |}
+	\hline
+	L' & Generator Degrees & Degrees of Minimal Relations \\
+	\hline
+	\hline
+	$0$ & $\{1\}$ & $\emptyset$ \\	\hline
+
+	$P-Q + \frac{2}{5}R_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+	$\frac{3}{7}R_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
+
+	$P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline
+
+%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10,\ldots, e+2, e+3, e+5,e+7,\ldots, 2e-4\}$ \\	\hline
+\end{longtable}
 \begin{enumerate}
 	\item $\halfcan' = 0$
-	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
+	\item $\halfcan' = P - Q + \frac{2}{5}R_1.$
+	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2.$
+	\item $\halfcan' = \frac{3}{7}R_1.$
 \end{enumerate}
+\todo{Is it ok that two genus 1 base cases are also exceptional, in terms of their relation degree?}
 
@@
 Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$$
+$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(x_3 y_3- \alpha uy_4,y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
 and that $(\sx',\{3,3\})$ is admissible.
@@
 
+\begin{example}
+\label{eg:exception-1-5}
+Let $L' = \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$.
+Let $u \in (R_L)_1$ be any nonzero element.
+We obtain $\di u|_{R_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
+We obtain $\di y_3|_{R_1} = - R_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$.
+Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{R_1} = -R_1$.
+Then, we claim there is some $\alpha \in k$ so that
+$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+It is analogous to Example ~\ref{ex:base-377}, and is omittied.
+
+Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
+
+Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Theorem ~\ref{thm:ram_order_ind}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}R_1$ is not exceptional because $12 < 2 \cdot 7$.
+\end{example}
+
+\iffalse
+The base case of $L' = \frac{3}{7}R_1$ has $R_L \cong k[u,y_5,y_7]/(y_5)^3 - uy_7^2.$ 
+\fi
+
+The base case of $L' = \frac{3}{7}R_1$ can be similarly computed. Note this is yet another exceptional case.
+
 \ssec{Genus One Exceptional Cases}
@@
 	\hline
-	$(1;-; 0)$ & $\{2\}$ & $\emptyset$ \\	\hline
-
-	$(1; 3; 0)$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
-
-	$(1; 5; 0)$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+	$P-Q$ & $\{2\}$ & $\emptyset$ \\	\hline
+
+	$P-Q + \frac{1}{3}R_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
+
+	$P-Q + \frac{2}{5}R_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+	$\frac{1}{3}R_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline
+
+	$\frac{2}{5}R_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline
+
+	$\frac{3}{7}R_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
 
@@
 We now elaborate on the computation of the results in 
-Table ~\ref{table:g-1-exceptional}. In the following example we will explain the case $\sigma = (1;5;0)$ as the other cases are even easier.
+Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
+$L' = P-Q + \frac{1}{5}R_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
 
@@
 \fi
-
-\begin{example}
-\label{eg:exception-1-5}
-Let $L = P - Q + \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$.
-Let $u \in (R_L)_1$ be any nonzero element.
-We obtain $\di u|_R = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1$ let $y_3 \in (R_L)_3$ be any nonzero element.
-We obtain $\di y_3|_R = - R,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$.
-Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_R = -R$.
-Then, we claim there is some $\alpha \in k$ so that
-$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
-The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
-It is analogous to Example ~\ref{ex:base-377}, and is omittied.
-\end{example}
 

### 2015-06-25 stacky_write_up/spin_cring.tex
replace symbols with words in deg1_sat_ind
added genus 1 proof

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
-Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \div X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
+Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
 Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$.
@@
 \max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
-$R(\sx,\Delta, \halfcan)$ has relations in degree at most $\max(11, e_1,
-\ldots, e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has relations in degree at most
-$\max(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a finite list of
+$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
+\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
+$\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
 exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).
@@
 \label{lem:deg1-sat-ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
+Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
 defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
 satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbf{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
-$u, x_1, \ldots, _m$ all with $\ord_P=0$ and such that $\deg(u)=1$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-in degree at most $\bar{\tau}$, where all $x_i$s also satisfy $\ord_P(u)(x_i)$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbf{N}$ such that
+Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
+$u, x_1, \ldots, x_m$ all with $\ord_P(u) =0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)=1$.
+Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
+in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
+for some $\alpha,\beta \in \mathbb{N}$ such that
 \begin{equation}
@@
 	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbf{
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbb{
 	N} : d \ge \frac{\beta}{\alpha}.
 \end{equation}
+\label{eqn:deg1-sat-ind}
 Let 
@@
 our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
-\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
 
@@
 %\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
+%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbb{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
 %\end{cor}
@@
 %any point $P$ occurring in a stacky divisor of $\sx$ must have 
-%coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+%coefficient lying in $\mathbb{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
 %s appearing in the characteristic of $(\sx,\Delta)$).
@@
 to be {\bf admissible} if the $R'$ admits a presentation
-
+\todo{We should incorporate dependence on $L$ into the definition of admissible.}
 \begin{align*}
@@
 Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
+\todo{Aaron: Is this actually true? Shouldn't we say that if $(\sx',\{e_1,...,e_{r-1}\})$ is admissible then so is $(\sx,\{e_1,...,e_r\})$?}
 \end{lem}
@@
 Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-we have that there exists a rational function $f$ with $\div f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
+we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
 with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_ordeP_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
 
@@
 
-\begin{enumerate}
-	\item $\halfcan' = 0$
-	\item $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_3.$
-\end{enumerate}
+\begin{longtable}	{| c || c | c | c |}
+	\hline
+	L' & Generator Degrees & Degrees of Minimal Relations \\
+	\hline
+	\hline
+	$0$ & $\{1\}$ & $\emptyset$ \\	\hline
+
+	$P-Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
+
+	$P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline
+	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline
+
+%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10,\ldots, e+2, e+3, e+5,e+7,\ldots, 2e-4\}$ \\	\hline
+\end{longtable}
 
@@
 \label{eg:base-1-33}
-Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$$
+Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(x_3 y_3- \alpha uy_4,y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
 and that $(\sx',\{3,3\})$ is admissible.
@@
 Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
 
@@
 Hence, (Ad-i) holds.
-We next check (Ad-ii) for the point $R_1$, as the case of $R_2$ is symmetric.
+We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric.
 Here, by construction
 $$
-\frac{-\ord_{R_1}(z)}{\ord(z)} = \begin{cases}
+\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
 	0 &\text{ if }z \in \{u,y_3\}\\
@@
 
+\begin{example}
+\label{eg:exception-1-5}
+Let $L' = \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$.
+Let $u \in (P_L)_1$ be any nonzero element.
+We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
+We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$.
+Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$.
+Then, we claim there is some $\alpha \in k$ so that
+$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $P_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+It is analogous to Example ~\ref{ex:base-377}, and is omittied.
+
+Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
+
+Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Theorem ~\ref{thm:ram_order_ind}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
+\end{example}
+
+\iffalse
+The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u,y_5,y_7]/(y_5)^3 - uy_7^2.$ 
+\fi
+
+The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed. Note this is yet another exceptional case.
+
 \ssec{Genus One Exceptional Cases}
-
+\label{ssec:g-1-exceptional}
 \todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
@@
 	\hline
-	$(1;-; 0)$ & $\{2\}$ & $\emptyset$ \\	\hline
-
-	$(1; 3; 0)$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
-
-	$(1; 5; 0)$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+	$P-Q$ & $\{2\}$ & $\emptyset$ \\	\hline
+
+	$P-Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
+
+	$P-Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+	$\frac{1}{3}P_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline
+
+	$\frac{2}{5}P_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline
+
+	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
 
@@
 We now elaborate on the computation of the results in 
-Table ~\ref{table:g-1-exceptional}. In the following example we will explain the case $\sigma = (1;5;0)$ as the other cases are even easier.
+Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
+$L' = P-Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
 
@@
 \label{eg:exception-1-e}
-Let $L = P - Q + \frac{e-1}{2e}R_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+Let $L = P - Q + \frac{e-1}{2e}P_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
 Furthermore, $\deg u = 2, \deg y_i = i$.
@@
 
-\begin{example}
-\label{eg:exception-1-5}
-Let $L = P - Q + \frac{2}{5}R_1$ be a half canonical divisor on a stacky curve $\sx$.
-Let $u \in (R_L)_1$ be any nonzero element.
-We obtain $\di u|_R = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (R_L)_1 = 1$ let $y_3 \in (R_L)_3$ be any nonzero element.
-We obtain $\di y_3|_R = - R,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$.
-Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_R = -R$.
-Then, we claim there is some $\alpha \in k$ so that
-$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
-The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $R$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
-It is analogous to Example ~\ref{ex:base-377}, and is omittied.
-\end{example}
-
 \ssec{Main Theorem for Genus One}
@@
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
-so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
+so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
 If $g = 1$, then the canonical ring
-
 \begin{align*}
@@
 \noindent
-is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $\max
-(10, e_1, \ldots, e_r),$ so long as $\sigma$ does not lie in a
+is generated as a $k$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has minimal relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
 finite list of exceptional cases, as listed in Table
@@
 \end{thm}
+
+\begin{proof}
+
+\vskip.1in
+\noindent
+{\sf Case 1: $\Delta > 0$}
+
+If $\Delta > 0$, we must have $\Delta \geq 2$.
+In this case, let $L_X \in \di X$ be so that $2L_X \sim K_X + \Delta$.
+We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor, so without loss of generality, we may assume $L$ is an effective divisor.
+We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
+\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it}
+
+We first now show the theorem holds for $L_X$ by induction.
+Assume it holds for $L' \in \di X$, with $L'$ effective.
+We will show it holds for $L' + P$.
+There are two cases, depending on whether $P$ is a basepoint of $L'$.
+
+First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:deg1-sat-ind}.
+In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $ with $\ord_P(u) = 0$, as $P$ is not a basepoint of $L'$.
+Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:deg1-sat-ind}, the theorem holds for $L= L'+P$.
+
+Second, if $P$ is a basepoint of $L'$, then the hypotheses of Lemma ~\ref{lem:sat-two-induction-high-genus} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$.
+Therefore, by Lemma ~\ref{lem:sat-two-induction-high-genus}, the theorem holds for $L = L'+P$.
+This shows the theorem holds for $L_X$.
+
+To complete the case that $\Delta > 0$, we only need show the theorem holds for $L$, assuming it holds for $L_X$.
+By induction, it suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i,$ with $e_i$ odd.
+Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by emma ~\ref{lem:deg1-sat-ind}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-two-induction-high-genus}.
+
+\vskip.1in
+\noindent
+{\sf Case 2: $\Delta = 0$}
+
+Since $\Delta = 0$, we may write $L = L_X + \sum_{i=1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P-Q$ for $P$ and $Q$ two distinct hyperelliptic fixed points.
+
+\vskip.1in
+\noindent
+{\sf Case 2a: $L_X = P-Q, P \neq Q$}
+
+Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
+
+First, we deal with the case $\sx$ has at least 1 stacky point.
+By Example ~\ref{eg:exception-1-5}, if $L' = P-Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P-Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
+Therefore, the Theorem holds for $L' = P-Q + \frac{3}{7}P_2$.
+Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P-Q + \frac{e-1}{2e}P_1$.
+
+\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together?}
+Second, we deal with the case that $\sx$ has at least two stacky points.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base-1-33}, it follows that $(\sx', \{3,3\})$ is admissible and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\frac{1}{3}P_i,$ the pair $(\sx',\{3,\ldots, 3\})$ is admissible.
+Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$.
+Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1,\ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible.
+Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1,\ldots, e_1\},$ with $\# J' = r-1$.
+Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2,\ldots, e_2\}$ so that $\# J_2 = r-1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i=2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible.
+Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P-Q + \sum_{i=1}^{r}\subhalf {e_i}P_i$, as desired.
+
+\vskip.1in
+\noindent
+{\sf Case 2b: $L_X = 0$}
+
+This case is completely analogous to 2a.
+\end{proof}
+
+\begin{rem}
+In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g_1_generators_relations}, proof of Theorem ~\ref{thm:g_1_generators_relations} yields an explicit procedure for computing those minimal generators and relations.
+That, is one can start with the generators and relations for the base cases, and then inductively add in generators and relations, according to the inductive theorems.
+\end{rem}
 
@@
 {vzb:stacky}.
+\todo{This confused me because while they do technically prove this, they only prove it for the canonical divisor, not the log canonical divisor.
+It would be clearer to write that in this case, we can assume $L = n \cdot \infty$ with $n \in \BZ$, which is covered in 4.2, with $L$ replaced by $K$.}
 
@@
 ~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
-{ssec:g_0_saturation} that saturation is 3 here), and the
+{ssec:g_0_saturation} that saturation is 3 here \todo{Write this out more precisely, it should be something like $sat(Eff(\sigma)) = 3$}), and the
 immediate consequence of parts (a) and (c) of Lemma
@@
 
-So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
+So if $r > 5$, then $\sigma$ ``lies above'' \todo{Aaron: what does this mean} the case $(\sigma', J)$
 where $\sigma'$ has $r$ many stacky points all of order $3$

### 2015-06-25 stacky_write_up/spin_cring.tex
part of proof to lemma 3.7

--- 2015-06-24 stacky_write_up/spin_cring.tex
@@
 \begin{rem}
-Fact about quotient.
+In particular, in the case of
+\[
+	\begin{tikzcd}
+	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	\end{tikzcd}
+\]
+inducing
+\[
+	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
+\]
+\todo{how do we make this proof?}
 \end{rem}
@@
 
-\todo{Peter: We should make the definition of admissibility be a 
-condition for the triple: $(\sx',\sx,J)$.}
-
+\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number.
+What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
 \begin{enumerate}
@@
 \begin{lem}\label{lem:n-3s-admissible}
-Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.
-Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
+Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
+Suppose $3\le r\in \mathbf{N}$ so that all stacky curves $\sx'$ with $r-1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ admissible in $L'$.
+Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i=3$) is admissible viewed in $L$.
 \end{lem}
 \begin{proof}\todo{proof}
-
+To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r-1$ stacky points $S=\{Q_1, \ldots, Q_{j-1}, Q_{j+1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
+Furthermore, since $S$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}=0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+
+ follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
+\begin{itemize}
+\item When $g>0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
+\item When $g=0$, since $L'$ has a nontrivial admissible subset within $\{e_1,\ldots, e_{r-1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+\end{itemize}
 \end{proof}

### 2015-06-25 stacky_write_up/spin_cring.tex
switching todos

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \; \forall d \in \mathbb{
-	N} : d \ge \frac{\beta}{\alpha}.
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
+	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
 \end{equation}
@@
 We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
-\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it}
+\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it. }
 
@@
 
-\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together?}
+\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together?
+Better yet, this should probably be a corollary somewhere, since we have to use this implicitly in all three genus cases.}
 Second, we deal with the case that $\sx$ has at least two stacky points.

### 2015-06-25 stacky_write_up/spin_cring.tex

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 \begin{lem}\label{lem:n-3s-admissible}
-Let $(\sx', L', \Delta), (\sx, L,\Delta)$ be log stacky curve with log half-canonical divisors $L'$ and $L$ with signatures $(g; e_1, \ldots, e_{r-1}; \delta)$ and $(g; e_1, \ldots, e_r; \delta)$ with all $e_i=3$ and $L=L'+\frac{1}{3}P$ for some point $P$.
-Then if $\{e_1,...,e_{r-1}\}$ in has any nontrivial admissible subset, then any subset of $\{e_1,...,e_r\}$ is admissible.
-\todo{Aaron: Is this actually true? Shouldn't we say that if $(\sx',\{e_1,...,e_{r-1}\})$ is admissible then so is $(\sx,\{e_1,...,e_r\})$?}
+Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
+Suppose $3\le r\in \mathbf{N}$ so that all stacky curves $\sx'$ with $r-1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r-1}\}$ admissible in $L'$.
+Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i=3$) is admissible viewed in $L$.
 \end{lem}
-\begin{proof}\todo{proof}
-
+\begin{proof}
+To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r-1$ stacky points $S=\{Q_1, \ldots, Q_{j-1}, Q_{j+1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
+Furthermore, since $S$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}=0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+
+ follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
+\begin{itemize}
+\item When $g>0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
+\item When $g=0$, since $L'$ has a nontrivial admissible subset within $\{e_1,\ldots, e_{r-1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+\end{itemize}
 \end{proof}

### 2015-06-25 stacky_write_up/spin_cring.tex
MAJOR code cleaning of intro, inductive lem

@@
 \section{Introduction}
-
-Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e.
-a discrete subgroup of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by fractional linear transformations.
-We can then consider the orbifold $\Gamma \backslash \bh$ over $\BC$.
-For example, in the case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a Riemann Surface over $\BC$.
-It may well be that $\Gamma \backslash \bh$ is not comapact.
-Defining $\Delta$ as the divisor of cusps associated to $\Gamma$, we can form a space $\Gamma \backslash \bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with associated {\bf divisor of cusps} $\Delta$.
-We can now consider the {\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$.
-In this paper, for general $\Gamma$, we sharply bound the degree of the generators and relations for $M(\Gamma).$ This was already answered in \cite[Chapters 7-9]{vzb:stacky} in the case that $M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is, when $\Gamma$ has no odd weight modular forms, and we extend this to all Fuchsian subgroups $\Gamma$.
-
-In order to answer this question, we translate the seemingly analytic question into the algebraic category, using a generalization of the GAGA principle.
-That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of categories between orbifold curves and log stacky curves over $\BC$.
-Hence, for the remainder of the paper, we will work in the algebraic category.
-
-Let $X$ be a smooth algebraic curve over $k$ of genus $g$.
-It is well known that the sheaf $\Omega_X,$ with associated divisor $K_X$ determines the {\bf canonical map} $\pi:X \rightarrow \BP_k^{g-1}.$ Then, the {\bf canonical ring}, is defined as
+Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup
+of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by
+fractional linear transformations. We can then consider the
+orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the
+case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a
+Riemann Surface over $\BC$. It may well be that $\Gamma \backslash
+\bh$ is not compact. Defining $\Delta$ as the divisor of cusps
+associated to $\Gamma$, we can form a space $\Gamma \backslash
+\bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with
+associated {\bf divisor of cusps} $\Delta$.
+
+We can now consider the
+{\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In
+this paper, for general $\Gamma$, we sharply bound the degree of
+the generators and relations for $M(\Gamma).$ This was already
+answered in \cite[Chapters 7-9]{vzb:stacky} in the case that
+$M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is,
+when $\Gamma$ has no odd weight modular forms, and we extend this
+to all Fuchsian subgroups $\Gamma$. In order to answer this
+question, we translate the seemingly analytic question into the
+algebraic category, using a generalization of the GAGA principle.
+That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an
+equivalence of categories between orbifold curves and log stacky
+curves over $\BC$. Hence, for the remainder of the paper, we will
+work in the algebraic category. Let $X$ be a smooth algebraic
+curve over $k$ of genus $g$. It is well known that the sheaf $\Omega
+_X,$ with associated divisor $K_X$ determines the {\bf canonical map
+} $\pi:X \rightarrow \BP_k^{g - 1}.$ Then, the {\bf canonical ring},
+is defined as
 \begin{align*}
@@
 \noindent
-with multiplication structure corresponding to tensor product of sections.
-Since $\Omega_X$ is ample, $X \cong \proj R$.
-Petri's theorem gives generators and relations for $R(X,K_X),$ see for example, \cite{saint-donat:proj}[Theorem, p.
-157], showing that in most cases $R(X,K_X)$ is generated in degree 1 with relations in degree 2.
-This has the pleasant geometric consequence that all such canonically embedded curves are scheme theoretically cut out by quadratic equations.
-
-Folloing Voight and Zureick-Brown, \cite{vzb:stacky}, we examine a much more general setting, generalizing Petri's theorem in many directions.
-A divisor $\Delta \in d X$ is a {\bf log divisor} if $\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct.
-Let $(\sx,\Delta)$ denote a tame seperably rooted stacky curve over a field $k$ so that $X$ is the coarse space of $\sx$, as defined in \cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i=1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$.
-Let $K_\sx = K_X + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i.$ In this case, we say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$.
-Call $\halfcan \in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$, be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx + \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$.
-A {\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$ and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
-The central object of study in this paper is the {\bf log spin canonical ring} of $(X,\Delta,L)$ is
+with multiplication structure corresponding to tensor product of
+sections. Since $\Omega_X$ is ample, $X \cong \proj R$. Petri's
+theorem gives generators and relations for $R(X,K_X),$ see for
+example, \cite{saint-donat:proj}[Theorem, p. 157], showing that in
+most cases $R(X,K_X)$ is generated in degree 1 with relations in
+degree 2. This has the pleasant geometric consequence that all such
+canonically embedded curves are scheme theoretically cut out by
+quadratic equations.
+
+Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
+much more general setting, generalizing Petri's theorem in many
+directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
+$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
+$(\sx,\Delta)$ denote a tame separably rooted curve over a
+field $k$ so that $X$ is the coarse space of $\sx$, as defined in
+\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
+= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
+\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
+say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
+\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$,
+be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx +
+\Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
+say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log
+spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
+and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
+The central object of study in this paper is the {\bf log spin
+canonical ring} of $(X,\Delta,L)$ is
 \begin{align*}
@@
 \noindent
-The main theorem of this paper is the following bound on the degree of generators and relations of arbitrary log spin canonical rings:
+The main theorem of this paper is the following bound on the degree
+of generators and relations of arbitrary log spin canonical rings:
 
@@
 $\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
-exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
+exceptional cases, as listed in Table ~\ref{table:g - 1-exceptional}
 for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
@@
 \end{thm}
+
 \todo{Say that this follows immediately from the three theorems for the special cases.}
-Note that in the course of the proof of Theorem ~\ref{thm:g_0_generators_relations} we will not merely obtain bounds on the degrees of the generators and relations.
-In fact, if the genus $g = 0$ or $g = 1$, the proof yields an explicit system of generators and the initial ideal of relations.
-While in the genus $g \geq 2$ case, the proof does not always yield an explicit system of generators and relations, if the halfcanonical divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',0,X)$ a log spin curve, and a system of generators and relations for $\halfcan'$ is known, then our proof provides an inductive procedure for determining the generators and initial ideal of relations for $\halfcan$.
-In fact, such a system of generators and relations are known for $\halfcan'$ in many cases, as detailed in Neves ~\cite[Section III.4]{neves:halfcan}.
-
-The remainder of the paper will be primarily devoted to proving Theorem ~\ref{thm:general_generators_relations}.
-The idea of the proof will be to induct on the order and number of elliptic points.
-To this end, we first review important background in Section ~\ref{sec:background}.
-Then, in Section ~\ref{sec:induction}, we develop various inductive tools.
-In Sections ~\ref{sec:g_high}, ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem \ref{thm:general_generators_relations} in the cases that the genus $g \geq 2, g = 1$ and $g = 0$ respectively.
-Finally, in Section ~\ref{sec:further-questions}, we pose several questions for future research.
+
+Note that in the course of the proof of Theorem
+~\ref{thm:g_0_generators_relations} we will not merely obtain
+bounds on the degrees of the generators and relations. In fact, if
+the genus $g = 0$ or $g = 1$, the proof yields an explicit system
+of generators and the initial ideal of relations. While in the
+genus $g \geq 2$ case, the proof does not always yield an explicit
+system of generators and relations, if the halfcanonical divisor
+$\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',
+0, X)$ a log spin curve, and a system of generators and relations for
+$ \halfcan'$ is known, then our proof provides an inductive
+procedure for determining the generators and initial ideal of
+relations for $ \halfcan$. In fact, such a system of generators and
+relations are known for $\halfcan'$ in many cases, as detailed in
+Neves ~\cite[ Section III.4]{neves:halfcan}.
+
+The remainder of the paper will be primarily devoted to proving
+Theorem ~\ref{thm:general_generators_relations}. The idea of the
+proof will be to induct on the order and number of elliptic points.
+To this end, we first review important background in Section
+~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we
+develop various inductive tools. In Sections ~\ref{sec:g_high},
+~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem
+~\ref{thm:general_generators_relations} in the cases that the genus
+$g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section
+~\ref{sec:further-questions}, we pose several questions for future
+research.
 
@@
 	\item Notation $h^0 = \dim H^0$.
-	\item Why we have these fractions $\frac{e_i-1}{2e_i}$ and why $e_i$ must be odd.
+	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
 \end{enumerate}
@@
 \label{sec:induction}
-First we present the general inductive lemmata that will be applied
-for all genera.
-We offer various inductive lemmata that will allow us to add fractional point $\frac{\alpha}{\beta}P$ to a $\mathbf{Q}$ divisor $D$ of $X$ and describe the new generators and relations of $R_{D+p}$ not in $R_D$.
-Next, we provide a method specific to the case of stacky canonical divisors with no log component, which under certain conditions allows us to transfer information about the generators and relations of the half canonical ring of a stacky curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$ where each $e_i\in \{e_i', e_i'+2\}$.
-
-However, before we can answer these general lemmata, it is useful to prove a nice result about minimal generation of ideals of relations:
-\todo{Include one of the following, if the first one, include a remark for quotient}
+First we present the general inductive Lemmata that will be applied
+for all genera. We offer various inductive Lemmata that will allow
+us to add fractional point $\frac{\alpha}{\beta}P$ to a $\BQ$
+ divisor $D$ of $X$ and describe the new generators and relations
+of $R_{D+p}$ not in $R_D$. Next, we provide a method specific to
+the case of stacky canonical divisors with no log component, which
+under certain conditions allows us to transfer information about
+the generators and relations of the half canonical ring of a stacky
+curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a
+stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$
+where each $e_i\in \{e_i', e_i' + 2\}$.
+
+However, before we can answer these general Lemmata, it is useful
+to prove a nice result about minimal generation of ideals of
+relations.
+
+\todo{Include one of the following, if the first one, include a 
+remark for quotient}
 \begin{lem}
 \label{lem:minimal_quadratic}
-Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
+Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
 generated in degree 1, is equipped with a monomial ordering $\prec$.
- Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
+ Let $\phi:k[x_1, \ldots, x_n] \rightarrow B$ be a map of graded
 rings with kernel $I,$ such that $I$ is generated by elements $f_1,
-\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
+\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
 is of the form $x_k$. Then, the elements $f_i$ determine minimal
@@
 determines a map of rings, no longer necessarily graded. Consider
-the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
+the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
 \todo{This ordering isn't quite right. 
@@
 terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
-\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
+\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
 generators for $I$ must have at least $j$ elements. Since $f_1,
@@
 	\begin{tikzcd}
-	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
+		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
 		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
@@
 %Further suppose that $I'$ is generated over $I$ by elements $f_1,
-%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
+%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
 %is of the form $y_i$. Then, the elements $f_i$ determine minimal
@@
 %\label{rem:minimal_quadratic_trivial_case}
-%It will be useful to use lemma \ref{lem:minimal_quadratic} in the
-%case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
+%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
+%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
 %are $k$-minimal generators for $I'$ (over the trivial base vector
@@
 Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).
-The proofs of these lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
+The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
 
@@
 Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
-$u, x_1, \ldots, x_m$ all with $\ord_P(u) =0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)=1$.
+$u, x_1, \ldots, x_m$ all with $\ord_P(u) = 0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)= 1$.
 Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
@@
 \[
-	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+	0<\frac{c_1}{d_1}<\ldots<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
 \]
@@
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
+\item $R_{D'}$ is generated over $R_D$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
 degree $d_i$ and has a pole at $P$ of degree $c_i$
@@
 										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
+										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n- 1 \\
 										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
+										 &+ \langle (y_i)^{\deg(y_{i + 1} + 1)}: 1\le i =\lfloor \frac{\alpha}{\beta} \rfloor
+\end{align*}
+
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
 %\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
+\item A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
+	and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
+	\frac{\alpha}{\beta} \rfloor} + 1}$ as shown above minimally
+generates $I'$.
 \end{itemize}
@@
 \begin{proof}
-Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.
+Observe that $u_D, x_1, \ldots, x_m$ each of which has no pole at $P$.
 These can be chosen generically to not have a zero at $P$ \todo{
@@
 be the non-negative best lower approximation of $\frac{
-\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
+\alpha}{\beta}$. Note that elements of $H^0(X, dD')$ have pole of
 orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
@@
 Generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
+D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i = 1$ then 
 \[
-	-\ord_P(y_i)= \max(c_j:d_j=1)
+	-\ord_P(y_i)= \max(c_j:d_j = 1)
 \]
@@
 best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
-maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
+maximal; since $c<c_{i + 1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$. From
 this we can deduce that 
 \[
-	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
+	c_i +(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
 \]
@@
 \lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
-where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+where $d_j = 1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
 \rfloor + 1}$.
@@
 linearly independent in $R_{D'}$. Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
+$R_{D'}$ over $R_D$. Thus $u, x_1, \ldots, x_m, y_1, \ldots, y_n$ generate
 $R_{D'}$.
@@
 paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
-$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
-$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
+$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l= 1$ and if 
+$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
 successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
@@
 is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
-expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
+expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
 is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
@@
 \noindent
-giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
+giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
 the beginning}
 
-Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
-$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
-u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
-+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
-+1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
-$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
-$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
-larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
-+c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
-d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
-(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
-$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
-follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
-$ to find
+Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
+< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
+basis element of the form described above: $y_n^0 y_j y_i u^0$). 
+Choose the maximal $l$ such that $c_h \le c_i + c_j$; since $1 < d_i
+\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
+so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
+Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
+$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
+= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
+best lower approximation of $\frac{\alpha}{\beta}$ with denominator
+larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
+know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
+Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
+1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
+h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
+appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
+$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
+follow a similar technique as in the previous paragraph to cancel
+out poles of $y_i y_j$ at $P $ to find
 \[
-	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
+	y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
 	u^{b_l}\in R_D
@@
 
-Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
-+1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
-y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
-the same method as the previous two paragraphs we find
+Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
+$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
+\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
+{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
+with the same pole order; following the same method as the previous
+two paragraphs we find
 \[
-	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
+	y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
 \]
@@
 \noindent
-Similarly if $i=1$, then we get the same result using
+Similarly if $i = 1$, then we get the same result using
 \[
-	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
+	y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
 \]
@@
 \noindent
-In both cases we deduce that $y_iy_j$ is an initial term of some relation.
-
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
-\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
-power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
-that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
-proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
-$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
-previous paragraphs we find
+In both cases we deduce that $y_i y_j$ is an initial term of some relation.
+
+Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
+1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
+then there are no relations with initial term a power of $y_i$
+and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
+note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
+{reference to Evan's paper where he proves this} Therefore, if $i >
+ 1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
+in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
+Following a similar technique to the previous paragraphs we find
 \[
-	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
+	(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
 \]
@@
 \noindent
-Similarly if $i=1$ then
+Similarly if $i = 1$ then
 \[
-	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
+	(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
 \]
@@
 \noindent
-In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.
-
-Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
-terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
-x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
-non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
-$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
-some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
-$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
-relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
-{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
-\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
-elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
-u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
-y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
-we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
-generic, this is in fact the generic initial ideal.
-
-In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
-\todo{What about $\frac{\alpha}{beta}>1$?}
+In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation.
+
+Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
+generated by the initial terms described in the previous paragraphs
+together with $\gin_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
+
+We show that $J$ is in fact all of the initial ideal. Suppose
+$f$ is a non-constant monomial that does not lie within $J$.
+Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
+there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
+some $x_j \mid f$ or else we would have $y_i x_j \mid f$
+contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
+i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
+element of a relation and divides $f$. If $d_i = 1$ as well, then
+we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
+$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
+\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
+f$. We observe that the remaining elements are precisely those of
+the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
+which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
+, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
+Therefore, by dimension counting (in each degree), we see that $J'$
+is the initial ideal of $I'$. Furthermore, since our choice of $y_i
+$'s was generic, this is in fact the generic initial ideal.
+
+In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
+~\ref{lem:minimal_quadratic} immediately tells us that the Grobner
+basis defined above is minimal.
+\todo{What about $\frac{\alpha}{\beta} > 1$?}
 \end{proof}
@@
 \label{lem:sat-two-induction-high-genus}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
 
 Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
-, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
+, x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
 
-Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)=0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
+Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
 Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
@@
 		\{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements
-		$y_3,y_4,$ minimally generate $R$ over $R'$.
+		$y_3, y_4,$ minimally generate $R$ over $R'$.
 	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
@@
 \begin{proof}
-The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g-1$ and $\deg 4L > 2g-1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-If $g = 1$, we assume $\deg 3L \geq 2 > 2g-1$, so we also have $\deg 4L \geq 2 > 2g -1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g - 1$ and $\deg 4L > 2g - 1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+If $g = 1$, we assume $\deg 3L \geq 2 > 2g - 1$, so we also have $\deg 4L \geq 2 > 2g - 1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
 Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann-Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need to cite lemma 5.4.7.}
+_P(y_i) = 1$ by Riemann-Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need to cite Lemma 5.4.7.}
 
@@
 For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
-we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j-A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation.  
+we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
 Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
-In both cases we induce a relation, with initial term described in the lemma's statement.
+In both cases we induce a relation, with initial term described in the Lemma's statement.
 Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
@@
 Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
-space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_
-{\halfcan'} = k[x_3, x_4 , x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac
+space $X$ of genus 0 such that $'sat(Eff(\halfcan')) = 3$ with $R_
+{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
 {1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
@@
 \begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
+	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
 		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
-		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
+		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
 	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
@@
 		\begin{align*}
-			\initial_\prec(I) &= \initial_\prec(I)k[x,y_3,y_4,y_5] \\
-			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
+			\initial_\prec(I) &= \initial_\prec(I) k[x, y_3, y_4, y_5] \\
+			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
+			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5.\rangle 
 		\end{align*}
@@
 First, note that since we are in genus 0, we can choose the
-elements $y_3,y_4,$ and $y_5$ are general and have $-\ord _P(y_i) =
+elements $y_3, y_4,$ and $y_5$ are general and have $- \ord_P(y_i) =
 1$ by Riemann Roch. \todo{Understand why/whether we need to cite 
-lemma 5.4.7.} To complete the proof of (a) we only need show these
+Lemma 5.4.7.} To complete the proof of (a) we only need show these
 elements generate $R$ over $R'$. We can first see that the
@@
 		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4,y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+		&+\langle y_3^ay_4, y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
 	\end{split}
@@
 \begin{align*}
-	x_3^{a-1}x_{3+b},y_3x_3^{a-2}x_{3+b},\ldots, y_3^ax_{3+b},y_3^ay_{
+	x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
 3+b}
@@
 ~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x,y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+generate $k[x, y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
 suffices to show that all generators of $J$ lie in $in_\prec(I)$.
@@
 \begin{align*}
-	y_ix_j &- A_{i,j} y_{i-1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	y_i x_j &- A_{i,j} y_{i - 1}w_j & \text{ so that } 4 \leq i \leq 5,3
 	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
@@
 %\label{lem:adding_points_saturation_2_to_1_with_log}
-%Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
+%Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be log spin log stacky spin 
 %curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
@@
 %\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures. Suppose 
-%$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
+%$'sat(Eff(\halfcan))= 1$ and $'sat(Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 
 %x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. Then
@@
 %\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
-%(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
+%(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)> 0$ and $\{y_1^2, y_2\}$ is linearly 
 %independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-%\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
+%\item[(b)] Equip $k[y_1, y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
 %x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$. 
@@
 %\begin{proof}
-%Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
+%Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)= 1$. 
 %Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
-%\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
-%all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
+%\ord_P(y_1)= 1$. Furthermore, since $\delta> 0$, we use Riemann-Roch to deduce that for 
+%all $d> 1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
 %$-vector space over $(R_{\halfcan'})_d$. In particular, this means we can generically 
@@
 %
-%To show part (b), we note that the monomials in the basis above generate $k[x,y]/\initial_
+%To show part (b), we note that the monomials in the basis above generate $k[x, y]/\initial_
 %\prec(I)$. Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$. For $j\ge 2$, we 
-%can choose $w_j$ in degree $\deg(x_j)+1$ and $A_j\in k$ such that
+%can choose $w_j$ in degree $\deg(x_j) + 1$ and $A_j\in k$ such that
 %\[
-	%y_2x_j-A_jy_3w_j
+	%y_2x_j -A_jy_3w_j
 %\]
@@
 %
-%Finally, (c) follows immediately from Lemma \ref{lem:minimal_quadratic}.
+%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
 %
@@
 %\label{lem:adding_points_saturation_2_to_1_no_log}
-%Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
+%Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be log spin log stacky spin curves 
 %with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$. Let $(g; e_1, \ldots, e_
 %\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures. 
-%Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
+%Suppose $'sat(Eff(\halfcan))= 1$ and $'sat(Eff(\halfcan'))=2$. Further suppose 
 %$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. 
@@
 %\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
-%(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
+%(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)> 1$ and $\{y_1^3, y_2\}$ is linearly 
 %independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-%\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
+%\item[(b)] Equip $k[y_1, y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
 %x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$. 
@@
 %\begin{proof}
-%The proof follows similarly to that of lemma 
+%The proof follows similarly to that of Lemma 
 %\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
@@
 %
-%We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
+%We will now prove a Lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
 %reference} and O'Dorney\todo{reference}.
@@
 %\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
-%Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
+%Notice that in Lemma ~\ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
 %\end{rem}
@@
 %We can prove this by induction. As a base case, let $D\sim 0$. Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
-%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i=1}^{r+1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
+%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i = 1}^{r+ 1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
 By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
-Since $D$ is effective, the condition of equation \ref{eqn:deg1_sat_ind_dim} is met, so by remark \ref{rem:deg1_sat_ind_gen_rel_degrees} of lemma \ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
+Since $D$ is effective, the condition of equation ~\ref{eqn:deg1_sat_ind_dim} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
 %\end{proof}
@@
 %\begin{cor}\label{cor:genus_0_positive_delta}
-%Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.
-Then $\halfcan$ is effective so we can inductively apply lemma \ref{lem:deg1_sat_ind}.
+%Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1, \ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)> 0$.
+Then $\halfcan$ is effective so we can inductively apply Lemma ~\ref{lem:deg1_sat_ind}.
 %\end{cor}
@@
 %possibly negative integer coefficients). Since $\Delta$ is non-
-%zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
+%zero effective, $\deg(D)\ge - 1$.  Noting that the coefficient of 
 %any point $P$ occurring in a stacky divisor of $\sx$ must have 
@@
  %
-%Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
+%Since all $e_i$'s are odd, $2$ cannot appear in a denominator of the 
 %coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
@@
 %is linearly equivalent to an effective $X$ divisor plus $\sum 
-%\subhalf{i}P_i$.  We have thus shown $\halfcan$ is linearly equivalent to an effective divisor.  Thus, by \ref{cor:effective_Q_divisor_can_ring} the desired result follows.
+%\subhalf{i}P_i$. We have thus shown $\halfcan$ is linearly equivalent to an effective divisor. Thus, by ~\ref{cor:effective_Q_divisor_can_ring} the desired result follows.
 %\end{proof}
@@
 %\begin{proof}
-%For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
+%For a similar reason as in corollary ~\ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta= 0$), so by corollary ~\ref{cor:effective_Q_divisor_can_ring} we get the desired result.
 %\end{proof}
 %
-%\todo{Move this lemma:}
+%\todo{Move this Lemma:}
 %\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
@@
 %\begin{proof}
-%Similar to all the other lemmas\todo{combine sections?}
+%Similar to all the other Lemmas\todo{combine sections?}
 %\end{proof}
@@
 {thm:ram_order_ind} holds for a curve with signature
-$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
-signature $(0;e_1, \ldots, e_r; 0)$ with $e_i' - e_i \in \{0,2\}$.
+$(0;e_1', \ldots, e_r';0)$ then it also holds for a curve with
+signature $(0; e_1, \ldots, e_r; 0)$ with $e_i' - e_i \in \{0 , 2\}$.
 
@@
 separably rooted log stacky spin
-curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
+curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
 there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
@@
 \begin{align*}
-	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
-\end{align*}
-
-\noindent
-with $y_{i,e_i'} \in R'$ for each $i \in J$ such that the following
+	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
+\end{align*}
+
+\noindent
+with $y_{i, e_i'} \in R'$ for each $i \in J$ such that the following
 three conditions hold.
@@
 	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
-		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
-	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
+		Q_i}(y_{i, e_i'}) = \frac{e_i'- 1}{2}$.
+	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i, e_i'}$
 		of $R'$ satisfies
@@
 \begin{lem}\label{lem:n-3s-admissible}
-Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
-Suppose $3\le r\in \mathbf{N}$ so that all stacky curves $\sx'$ with $r-1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r-1}\}$ admissible in $L'$.
-Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i=3$) is admissible viewed in $L$.
+Fi x a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
+Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$.
+Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
 \end{lem}
 \begin{proof}
-To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r-1$ stacky points $S=\{Q_1, \ldots, Q_{j-1}, Q_{j+1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
-Furthermore, since $S$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}=0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}= 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
 
@@
 \begin{itemize}
-\item When $g>0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-\item When $g=0$, since $L'$ has a nontrivial admissible subset within $\{e_1,\ldots, e_{r-1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
+\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 \end{itemize}
@@
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}-\frac{1}{e_i'}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
 \end{align*}
@@
 \noindent
-If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'-1}{2e_i'}$ 
+If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'- 1}{2e_i'}$ 
 as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'-1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
+e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
 we must have
@@
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'}- \frac{1}{\beta} \leq 
-	\deg(z) \subhalf{e_i'}- \frac{1}{e_i'}.
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
+	\deg(z) \subhalf{e_i'} - \frac{1}{e_i'}.
 \end{align*}
@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', 0, \halfcan')$ is a tame separably rooted log
-stacky spin curve with coarse space $X'$ and signature
-$(g; e_1', \ldots, e_r'; \delta)$ and $(\sx', J)$ is
-admissible with generators $x_j, y_{i,e_i'} \in R' = R_{L'}$ with
-$i \in J$ as in Definition ~\ref{defn:admissible}. Let $(\sx, 0,
-\halfcan)$ be another tame separable rooted log stacky spin curve
+Suppose $(\sx', 0, \halfcan')$ is a log spin curve with coarse
+space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and
+$(\sx', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
+R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
+$(\sx, 0, \halfcan)$ be another log spin curve
 with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
@@
 \begin{enumerate}
-	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
+	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
 		H^0(\sx, e_i(K_\sx))$ so that
 		\begin{align*}
-			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
+			-ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
 		\end{align*}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq \subhalf{
-			e_j'} - \frac{1}{\deg(y_{i,e_i})e_j'}
+			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
+\subhalf{
+			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
 		\end{align*}
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
-		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
+	\item[(b)] The elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
+0,
+		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
 		generate $R$ over $R'$.
-	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
-		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
-		block order. Let $R = k[y,x]/I.$ Then,
-		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
-			\neq y_{i,e_i},y_{i,e_i'} \rangle
+	\item[(c)] Equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
+		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
+		block order. Let $R = k[y, x]/I.$ Then,
+		\begin{align*}
+			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
+			\neq y_{i, e_i}, y_{i, e_i'} \rangle
 		\end{align*}
@@
 \begin{align*}
-	H^0(\sx',e_iL'-E_i + Q_j) \rightarrow H^0(\sx,e_iL - E_i) \subset 
-H^0(\sx,e_iL).
+	H^0(\sx', e_iL'-E_i + Q_j) \rightarrow H^0(\sx, e_iL - E_i) \subset 
+H^0(\sx, e_iL).
 \end{align*}\todo{Peter: should be $Q_i$?}
@@
 \begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g-1
-\end{align*}
-
-\noindent
-implying that $H^0(\sx',e_iL'-E_i + Q_i)$ is base point free by 
+	\deg \left( e_i L' - E_i \right) \geq 2g - 1
+\end{align*}
+
+\noindent
+implying that $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
 Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
 \begin{align*}
-	y_{i,e_i} \in H^0(\sx',e_iL'-E_i + Q_i)
+	y_{i, e_i} \in H^0(\sx', e_iL'-E_i + Q_i)
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_i}(y_{i,e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor +1 =
+	-\ord_{Q_i}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
 	\frac{e_i - 1}{2}
@@
 \noindent
-Therefore, $y_{i,e_i}$ satisfies the first part of the claim of $(a)$.
-
-We next show $y_{i,e_i}$ also satisfies the second part of the
+Therefore, $y_{i, e_i}$ satisfies the first part of the claim of $(a)$.
+
+We next show $y_{i, e_i}$ also satisfies the second part of the
 claim of $(a),$ by considering separately the cases of whether $j
@@
 
-If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i,e_i} \in H^0
-(\sx',e_iL'-E_i + Q_i)$,
-\begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
+If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i, e_i} \in H^0
+(\sx', e_iL'-E_i + Q_i)$,
+\begin{align*}
+	-\ord_{Q_j}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
 	\subhalf{e_j'} - \frac{1}{e_j'}.
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+	-\ord_{Q_j}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
 	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
@@
 $$R_i = \begin{cases}
-	R_{i-1} &\text{ if }i \notin J\\
-	R_{i-1}[y_{i,e_i}] &\text{ otherwise.} 
+	R_{i - 1} &\text{ if }i \notin J\\
+	R_{i - 1}[y_{i, e_i}] &\text{ otherwise.} 
 \end{cases}$$
@@
 \noindent
-To prove (b), it suffices to show that elements of the form $y_{i,e_
-i'}^ay_{i,e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
-and that these elements together with $R_{i-1}$ span $R_i$ as a $k$-
-vector space. These elements do not lie in $R_{i-1}$ because their
+To prove (b), it suffices to show that elements of the form $y_{i, e_
+i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
+and that these elements together with $R_{i - 1}$ span $R_i$ as a $k$-
+vector space. These elements do not lie in $R_{i - 1}$ because their
 order of pole at $Q_i$ is bigger than the order of any element in $R
-_{i-1}$, and are linearly independent amongst themselves because of
+_{i - 1}$, and are linearly independent amongst themselves because of
 injectivity of the linear map
@@
 \begin{align*}
-	(a,b) \mapsto \left( \deg\left(y_{i,e_i'}^ay_{i,e_i}^b\right),-
-	\ord_{Q_i}\left( y_{i,e_i'}^ay_{i,e_i}^b \right)  \right) = (a,b) 
+	(a,b) \mapsto \left( \deg\left(y_{i, e_i'}^ay_{i, e_i}^b\right),-
+	\ord_{Q_i}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
 	\begin{pmatrix}
-		e_i-2 & \frac{e_i-3}{2} \\
-		e_i	 & \frac{e_i-1}{2}
+		e_i -2 & \frac{e_i -3}{2} \\
+		e_i	 & \frac{e_i - 1}{2}
 	\end{pmatrix} 
@@
 \noindent
-The fact the the elements $y_{i,e_i'}^ay_{i,e_i}^b$ with $a \geq 0,
-b > 0$ span $R_i$ over $R{i-1}$ follows from the fact that the
+The fact the the elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 0,
+b > 0$ span $R_i$ over $R{i - 1}$ follows from the fact that the
 integer lattice points in the cone generated by the vectors $\left(e
-_i-2, \frac{e_i-3}{2} \right)$ and $\left(e_i, \frac{e_i-1}{2}
+_i -2, \frac{e_i -3}{2} \right)$ and $\left(e_i, \frac{e_i - 1}{2}
 \right)$ is saturated, as the corresponding determinant is
 \begin{align*}
-	(e_i-2) \frac{e_i-1}{2} - e_i \frac{e_i-3}{2} = 1,
+	(e_i -2) \frac{e_i - 1}{2} - e_i \frac{e_i -3}{2} = 1,
 \end{align*}
@@
 
-To show (c), we wish to show $y_{i,e_i}z \in R'$ for $z \neq y_{i,e_
-i},y_{i,e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
+To show (c), we wish to show $y_{i, e_i}z \in R'$ for $z \neq y_{i, e_
+i}, y_{i, e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
 all $j \in J$ we have
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
-	\deg z \subhalf {e_j'} = \deg (y_{i,e_i}z) \subhalf{e_j'}. 
+	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
+	\deg z \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z)
-	&\leq \frac{e_j-1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j-1}{2}-\frac{1}{e_j'}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j-3)}{2(e_j-2)}+\deg z \left( \subhalf{e_j'} \right) \\
-	&= \deg (y_{i,e_i}z) \subhalf{e_j'}.
+	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z)
+	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
+	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg z \left( \subhalf{e_j'} \right) \\
+	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg z \left( \subhalf{e_j'} \right) \\
+	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
 \end{align*}
@@
 
-In this case, we may first assume $z \neq y_{j,e_j}$, 
+In this case, we may first assume $z \neq y_{j, e_j}$, 
 as this is covered by case 2, with $i$ and $j$ reversed. 
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i,e_i})-\ord_{Q_j}(z) 
+	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z) 
 	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
-	= \deg (y_{i,e_i}z) \subhalf{e_j'},
+	= \deg (y_{i, e_i}z) \subhalf{e_j'},
 \end{align*}
@@
 admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
-i,e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
+i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
 strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
@@
 \end{align*}
-is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
+is surjective. Indeed, let $'s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
 Since $K$ is basepoint-free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
@@
 We wish to show $f$ is surjective.
-Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g-1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
-Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n-1)(g-1)$, again using Riemann--Roch.
-Therefore, $$\dim \im f = 2 \cdot (n-1)(g-1) -(n-3)(g-1) = (n+1)(g-1) = \dim H^0((n+2)L),$$
+Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
+Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
+Therefore, $$\dim \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim H^0((n+2)L),$$
 again using Riemann-Roch, implying $f$ is surjective.
@@
 By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
-Let $P_1,\ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
+Let $P_1, \ldots, P_6$ be the si x hyperelliptic fi xed points of $X$. 
 Recall that all spin divisors on $X$ can be written as 
-$$L = P_1 + \sum_{i=2}^{6} \epsilon_i (P_1 - P_i),$$ 
+$$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
 with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
-Note that $H^0(X,K)$ is spanned by rational functions $u,x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
+Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
 \begin{align*}
@@
 \end{align*}
-is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2,x^3$, 
+is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
 which have $\di u^3|_{2L} = -2L, \di u^2x|_{2L} = -2L + 2P_1,\di ux^2|_{2L} = -2L+4P_1, \di x^3|_{2L} = -2L + 6P_1.$ 
@@
 Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
-Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed.
+Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fi xed.
 In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
@@
 
-\todo{This should be $k[x_1,\ldots, x_n]$ instead of $\sym H^0$.}
+\todo{This should be $k[x_1, \ldots, x_n]$ instead of $\sym H^0$.}
 \begin{lem}
@@
 Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$.
-Choose generators $x_1,\ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1,\ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and let $J_{L,d} = \sum_{j = 1}^{d-1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ For any $f \in k[x_1, \ldots, x_n]$ such that
+Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and let $J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ For any $f \in k[x_1, \ldots, x_n]$ such that
 $$
@@
 \end{cases}$$
-there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+there exist $'s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $'s_1g + s_2h = f \bmod J_{L,d}.$
 \end{lem}
 \begin{proof}
-Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
-By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i=1}^{n}a_ix_i$ with $a_i \in k[x_1,\ldots, x_n]_{d-\deg x_i}$.
-We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i- 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
+Choose $'s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
+By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
+We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
 Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$. By Lemma ~\ref{lem:semicanonical_generation},
 \begin{align*}
-	V \otimes H^0((\deg f-\deg x_i-2)L) \rightarrow H^0((\deg f-\deg x_i)L)
+	V \otimes H^0((\deg f-\deg x_i -2)L) \rightarrow H^0((\deg f-\deg x_i)L)
 \end{align*}
@@
 $$
-\deg f- \deg a_i-2 \geq \begin{cases}
+\deg f- \deg a_i -2 \geq \begin{cases}
 	5 &\text{ if }\Delta = 0\\
@@
 
-Finally, we may then take $g = \sum_{i}^{}g_ix_i,h = \sum_{i}^{}h_ix_i,$ so that 
+Finally, we may then take $g = \sum_{i}^{}g_i x_i,h = \sum_{i}^{}h_i x_i,$ so that 
 \begin{align*}
@@
 \begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
+Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $'s_1g+s_2h \in I_{L,d}'$. 
 Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
@@
 we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
-So, using the refined version of the basepoint free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
+So, using the refined version of the basepoint-free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
 Therefore,
@@
 
-In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_ordeP_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
+In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fi xed under the hyperelliptic involution.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
 
@@
 
-	$P-Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
 
@@
 
-%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10,\ldots, e+2, e+3, e+5,e+7,\ldots, 2e-4\}$ \\	\hline
+%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
 \end{longtable}
@@
 \begin{example}
-\label{eg:base-1-0}
+\label{eg:base- 1-0}
 In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
@@
 \begin{example}
-\label{eg:base-1-33}
+\label{eg:base- 1-33}
 Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(x_3 y_3- \alpha uy_4,y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
+$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
 and that $(\sx',\{3,3\})$ is admissible.
@@
 Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
 
 Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
+$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
 The details are omitted as it is analogous to Example ~\ref{ex:base-377}.
@@
 We next check $(\sx',\{3,3\})$ is admissible.
-We clearly have two generators $x_3,y_3$ in degree 3 with a pole of order $\frac{3-1}{2}$ by construction.
+We clearly have two generators $x_3, y_3$ in degree 3 with a pole of order $\frac{3- 1}{2}$ by construction.
 Hence, (Ad-i) holds.
@@
 \frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u,y_3\}\\
+	0 &\text{ if }z \in \{u, y_3\}\\
 	\frac{1}{4} &\text{ if }z = y_4
@@
 Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
-Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 -1 + 0$.
+Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
 \end{example}
@@
 \begin{example}
-\label{eg:exception-1-5}
+\label{eg:exception- 1-5}
 Let $L' = \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$.
@@
 We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
-We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx,P-Q) \cong 0$ as $P \neq Q$.
+We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$.
 Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$.
 Then, we claim there is some $\alpha \in k$ so that
-$R_L \cong k[u,y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
 The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $P_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
@@
 
-Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
+Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base- 1-33}.
 
@@
 \iffalse
-The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u,y_5,y_7]/(y_5)^3 - uy_7^2.$ 
+The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u, y_5, y_7]/(y_5)^3 - uy_7^2.$ 
 \fi
@@
 \ssec{Genus One Exceptional Cases}
-\label{ssec:g-1-exceptional}
+\label{ssec:g - 1-exceptional}
 \todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
-Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R$ be a point on $\sx$.
+Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fi xed points, and $R$ be a point on $\sx$.
 
@@
 	\hline
-	$P-Q$ & $\{2\}$ & $\emptyset$ \\	\hline
-
-	$P-Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
-
-	$P-Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline
+
+	$P - Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
+
+	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
 
@@
 \begin{center}
-\label{table:g-1-exceptional}
-\textbf{Table (IV)}: Genus 1 exceptional cases, where $L' = P-Q + \frac{e-1}{2e}R$, with $P \neq Q$.
+\label{table:g - 1-exceptional}
+\textbf{Table (IV)}: Genus 1 exceptional cases, where $L' = P - Q + \frac{e- 1}{2e}R$, with $P \neq Q$.
 \end{center}
@@
 \begin{rem}
-\label{rem:g-1-exceptional-e}
-Note that for $e > 5$ generators and relations for $L = P -Q + \frac{e-1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P-Q + \frac{(e-2)-1}{2(e-2)}R$ using 
+\label{rem:g - 1-exceptional-e}
+Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
 Theorem ~\ref{thm:ram_order_ind}.
@@
 We now elaborate on the computation of the results in 
-Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
-$L' = P-Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
+Table ~\ref{table:g - 1-exceptional}. We have already explained the case of 
+$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception- 1-5}. The other cases are similar.
 
@@
 \begin{example}
-\label{eg:exceptional-1-0}
-In the case $L=P - Q.$ Then, we have $R_{(2k+1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
+\label{eg:exceptional- 1-0}
+In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
 \end{example}
@@
 \begin{example}
-\label{eg:exceptional-1-3}
+\label{eg:exceptional- 1-3}
 Let $L = P - Q + \frac{1}{3}R$.
@@
 For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-We find that $R_L \cong k[u,x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
+We find that $R_L \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
 \end{example}
@@
 \begin{example}
-\label{eg:exception-1-e}
-Let $L = P - Q + \frac{e-1}{2e}P_1.$ Here, we claim $R_L \cong k[u,y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3,\ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+\label{eg:exception- 1-e}
+Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
 Furthermore, $\deg u = 2, \deg y_i = i$.
@@
 finite list of exceptional cases, as listed in Table
-~\ref{table:g-1-exceptional}.
+~\ref{table:g - 1-exceptional}.
 \end{thm}
@@
 We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor, so without loss of generality, we may assume $L$ is an effective divisor.
-We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
-\todo{fix this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it. }
+We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base- 1-0}.
+\todo{fi x this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it. }
 
@@
 
-Since $\Delta = 0$, we may write $L = L_X + \sum_{i=1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P-Q$ for $P$ and $Q$ two distinct hyperelliptic fixed points.
+Since $\Delta = 0$, we may write $L = L_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fi xed points.
 
@@
 \noindent
-{\sf Case 2a: $L_X = P-Q, P \neq Q$}
-
-Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
+{\sf Case 2a: $L_X = P - Q, P \neq Q$}
+
+Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g - 1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
 
 First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P-Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
-While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P-Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
-Therefore, the Theorem holds for $L' = P-Q + \frac{3}{7}P_2$.
-Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P-Q + \frac{e-1}{2e}P_1$.
+By Example ~\ref{eg:exception- 1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
+Therefore, the Theorem holds for $L' = P - Q + \frac{3}{7}P_2$.
+Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P - Q + \frac{e- 1}{2e}P_1$.
 
@@
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base-1-33}, it follows that $(\sx', \{3,3\})$ is admissible and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
-Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\frac{1}{3}P_i,$ the pair $(\sx',\{3,\ldots, 3\})$ is admissible.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that $(\sx', \{3,3\})$ is admissible and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i,$ the pair $(\sx',\{3, \ldots, 3\})$ is admissible.
 Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$.
-Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1,\ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i=1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible.
-Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1,\ldots, e_1\},$ with $\# J' = r-1$.
-Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2,\ldots, e_2\}$ so that $\# J_2 = r-1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i=2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible.
-Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P-Q + \sum_{i=1}^{r}\subhalf {e_i}P_i$, as desired.
+Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1, \ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible.
+Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1, \ldots, e_1\},$ with $\# J' = r- 1$.
+Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2, \ldots, e_2\}$ so that $\# J_2 = r- 1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i =2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible.
+Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
 
@@
 \label{ssec:g_0_saturation}
-First, we present the saturations $s$ of the canonical divisor for
+First, we present the saturations $'s$ of the canonical divisor for
 all cases where $g = 0, \delta = 0$ as defined in Definition
 ~\ref{defn:sat}. The saturation can be computed via the application
-of Riemann-Roch on degrees up to $s$. Exceptional cases are listed
+of Riemann-Roch on degrees up to $'s$. Exceptional cases are listed
 first and generic cases follow.
@@
 \label{lem:g_0_admissible_cases}
-Let $(\sx', \Delta, \halfcan')$ be a tame log spin curve over a
+Let $(\sx', \Delta, \halfcan')$ be a log spin curve over a
 perfect field $k$, so that $\sx$ has signature $\sigma = (0; e_1,
@@
 generated as a $k$-algebra by elements of degree at most $e = \max(5
-,e_1,\ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
+, e_1, \ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
 ', J)$ is admissible for the following cases:
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
+\geq 0$. Since $\sigma_2$ has saturation $'s = 5$, as noted in
 Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
@@
 $i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $S_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
+0$. Thus, $'s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
 Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
@@
 
-Now we can induct on cases (a)-(k) of \ref{lem:g_0_admissible_cases}
+Now we can induct on cases (a)-(k) of ~\ref{lem:g_0_admissible_cases}
 to obtain bounds on the minimal generator and relation degrees for
@@
 stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
-we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
+we obtain Theorem ~\ref{thm:g_0_generators_relations} for any
 log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
@@
 of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
-the lemma inductively on the classical case with no stacky points
+the Lemma inductively on the classical case with no stacky points
 to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
@@
 ~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
-{ssec:g_0_saturation} that saturation is 3 here \todo{Write this out more precisely, it should be something like $sat(Eff(\sigma)) = 3$}), and the
+{ssec:g_0_saturation} that saturation is 3 here \todo{Write this out more precisely, it should be something like $'sat(Eff(\sigma)) = 3$}), and the
 immediate consequence of parts (a) and (c) of Lemma

### 2015-06-25 stacky_write_up/spin_cring.tex
add transitions to section 3

@@
 of $R_{D+p}$ not in $R_D$. Next, we provide a method specific to
-the case of stacky canonical divisors with no log component, which
+the case of stacky canonical divisors, which
 under certain conditions allows us to transfer information about
@@
 curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a
-stacky curve $\sx$ with signature $(g; e_1', \ldots, e_\tau'; 0)$
+stacky curve $\sx$ with signature $(g; e_1, \ldots, e_\tau; 0)$
 where each $e_i\in \{e_i', e_i' + 2\}$.
@@
 Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
-Let $\halfcan=\halfcan'+P$ for some $P$ not in the support of $\halfcan$.\todo{do we always assume this?}  Then we will explicitly describe elements that minimally generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).
+Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
+Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).
 The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
 
-\todo{definition and basic properties of best lower approximations}
+First, let's introduce some notation from O'Dorney.   \todo{cite O'downey}
+\begin{defn}\label{den:lower-approximation}
+If $\frac{\alpha}{\beta}\in \mathbf{Q}$ (for $\alpha\in \mathbf{Z}, \beta\in \mathbf{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
+\[
+	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
+\]
+\end{defn}
+\todo{add a picture of lattice}
+
+O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\mathbf{P}^1$ consisting of at most 2 points in its support, showing that it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
+He further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
+
+The following lemma provides an inductive method to extend O'Dorney's result on $\mathbf{P}^1$ to divisors $D=\sum_i \frac{\alpha_i}{\beta_i}P_i$ consisting of arbitrarily many points satisfying $H^0(X,\lfloor D\rfloor)>0$, showing that they are generated in degrees at most $e=\max(\beta_i)$ with relations generated in degrees at most $2e$.
+Furthermore, given some constraints on $H^0(X, \lfloor dD\rfloor)$ for various values of $d$, we can apply the same Riemann-Roch arguments from $\mathbf{P}^1$ in arbitrary genus, allowing a similar inductive result in arbitrary genus $e=\max(\beta_i)$.
+To do this, we extend an inductive result by Voight and Zurich-Brown on stacky canonical rings to arbitrary $\mathbf{Q}$-divisors.
+\todo{cite theorem 8.3.1}
 
@@
 \label{lem:deg1-sat-ind}
-Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $D$ (as
-defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
-satisfying $h^0(X, \lfloor{D}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $dD$ for all $d\in \mathbb{N}^+$ meaning that $R_D$ has generically chosen generators (in the appropriate respective degrees)
-$u, x_1, \ldots, x_m$ all with $\ord_P(u) = 0$ \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)= 1$.
-Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated
-in degree at most $\bar{\tau}$, where all $x_i$ also satisfy $\ord_P(u)(x_i)$. \todo{Aaron: What does $\ord_P(u)(x_i)$ mean?}  Suppose $D' = D + \frac{\alpha}{\beta} P$
+Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $\halfcan'$
+satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
+$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_D$.
+Suppose $u, x_1, \ldots, x_m$ generate $R_D$ in degree at most $\bar{d}$ with relations generated
+in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
 for some $\alpha,\beta \in \mathbb{N}$ such that
@@
 \]
-be the non-negative best lower approximation.
+be the positive best lower approximations of $\frac{\alpha}{\beta}$.
 Then 
@@
 \begin{proof}
-Observe that $u_D, x_1, \ldots, x_m$ each of which has no pole at $P$.
-These can be chosen generically to not have a zero at $P$ \todo{
-check that we can actually do this, or eliminate if it turns out to
-be unnecessary}.
-
-Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
+Inside of $(R_
 {D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
@@
 \end{proof}
+
+\begin{rem}\label{rem:sat-1-gen-lem-generic}
+The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (so there is not more than one $d_i=1$).
+When $\frac{\alpha}{\beta}$, the choice of generators in degrees above 1 is generic, and we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$.
+\end{rem}
 

### 2015-06-25 stacky_write_up/spin_cring.tex
remove redundancy from admiss def
edited genus 1 induction

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', 0, \halfcan')$ is a log spin curve with coarse
+Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
 space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and
@@
 R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
-$(\sx, 0, \halfcan)$ be another log spin curve
+$(\sx, \Delta, \halfcan)$ be another log spin curve
 with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
@@
 
-Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
+Finally, if $(\sx , J)$ is admissible then so is $(\sx,W)$ for any
 $W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
+\end{proof}
+
+\begin{cor}
+\label{cor:raise-stacky-order}
+Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ with $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
+so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}.
+Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of ramified points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
+$$
+e_i \begin{cases}
+	= e_i' &\text{ if }i \notin J\\
+	\leq e_i' &\text{ if } i \in J
+\end{cases}$$
+then Theorem ~\ref{thm:general_generators_relations} holds for $(\sx,\Delta,L)$
+\end{cor}
+\begin{proof}
+For $t \leq i \leq r$.
+Let $(\sx_i,\Delta, L_i)$ be the log stacky spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
+$J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
+
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, L_i, J_i)$ is admissible.
+
+Since $(*_0)$ holds by assumption, by induction on $i$, it suffices to show that if $(*_i)$ holds then so does $(*_{i+1}).$ 
+Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, L_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
+Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
 \end{proof}
@@
 \begin{prop}
-\label{prop:relations_generation}
+\label{prop:relation_11}
 Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K + \Delta$. Then $I_L$ is generated in degree at most $11$ if $\Delta = 0$ and degree at most $10$ if $\Delta > 0$.
@@
 In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relations_generation}, that $I_L$ is generated in degree at most 11 is close to sharp.
+Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 is close to sharp.
 \end{rem}
@@
 \label{ssec:main_g_high}
+
+\begin{thm}
+\label{thm:general_generators_relations}
+Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
+that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
+canonical ring
+
+\begin{align*}
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
+\end{align*}
+
+\noindent
+is generated as a $k$-algebra by elements of degree at most $e =
+\max(5, e_1, \ldots, e_r).$ If $\Delta = 0$ then 
+$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
+\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
+$\max(10, 2e_1, \ldots, 2e_r).$
+\end{thm}
+
+\begin{proof}
+By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, we are done in the case that there are no stacky points. 
+\end{proof}
 
@@
 
-\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together?
-Better yet, this should probably be a corollary somewhere, since we have to use this implicitly in all three genus cases.}
 Second, we deal with the case that $\sx$ has at least two stacky points.
@@
 Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$.
-Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1, \ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible.
-Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1, \ldots, e_1\},$ with $\# J' = r- 1$.
-Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2, \ldots, e_2\}$ so that $\# J_2 = r- 1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i =2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible.
-Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
+Then, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
 
@@
 	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
-	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relations_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
+	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
 \todo{Possibly think more about this}

### 2015-06-25 stacky_write_up/spin_cring.tex

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 \begin{enumerate}
-	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
-		Q_i}(y_{i, e_i'}) = \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i, e_i'}$
+	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
+		= \frac{e_i'- 1}{2}$.
+	\item[(Ad-ii)] Any generator $z \neq y_{i, e_i'}$
 		of $R'$ satisfies
@@
 		\end{align*}
-	\item[(Ad-iii)] For all $i \in J$ we have
+	\item[(Ad-iii)] The minimality condition
 		\begin{align*}

### 2015-06-25 stacky_write_up/spin_cring.tex
added g > 1 induction

@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 Then 
-\begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
+\begin{enumerate}
+\item[(a)] $R_{D'}$ is generated over $R_D$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
 degree $d_i$ and has a pole at $P$ of degree $c_i$
 
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
+\item[(b)] If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
 
@@
 %\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
-\item A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
+\item[(c)] A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
 	and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
@@
 generates $I'$.
-\end{itemize}
+\end{enumerate}
 \end{lem}
@@
 \label{lem:sat-two-induction-high-genus}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
+Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
 
@@
 \label{defn:admissible}
-Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
-separably rooted log stacky spin
+Let $(\sx', 0, L'),(\sx, 0, L)$ be log spin
 curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
@@
 \begin{proof}
-Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
+Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
 question, with coarse spaces $X = X'$. 
-\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
+\todo{possibly generalize these to arbitrary log  $\Delta \neq 0$ spin curves}
 Define
@@
 For $t \leq i \leq r$.
-Let $(\sx_i,\Delta, L_i)$ be the log stacky spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
+Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
 $J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
@@
 \begin{proof}
-By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, we are done in the case that there are no stacky points. 
+Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
+By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta, \halfcan_X)$.
+Next, consider a divisor of the form $\halfcan' = \halfcan_X + \frac{1}{3}P_i$.
+Then, the theorem holds for $(\sx,\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus} if $P_i$ is a basepoint of $\halfcan'$ or by Lemma ~\ref{deg1-sat-ind} if $P_i$ is not a basepoint of $L'$.
+Note, in the case $P$ is a not basepoint of $\halfcan'$, Equation ~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d \geq 3$.
+
+In this case, we claim $(\sx',L',\{1\})$ is admissible.
+Indeed, (Ad-i) holds by part (a) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, (Ad-ii) holds by part (b) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by Lemma ~\ref{lem:n-3s-admissible}, Any triple of the form $(\sx',L',\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
+Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for all log spin curves $(\sx, L, J).$
 \end{proof}
@@
 
-We next check $(\sx',\{3,3\})$ is admissible.
+We next check $(\sx',\{1,2\})$ is admissible.
 We clearly have two generators $x_3, y_3$ in degree 3 with a pole of order $\frac{3- 1}{2}$ by construction.

### 2015-06-25 stacky_write_up/spin_cring.tex
editing section 3 lemmas

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
-$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor D|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_D$.
-Suppose $u, x_1, \ldots, x_m$ generate $R_D$ in degree at most $\bar{d}$ with relations generated
-in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
+$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
+Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\bar{d}$ with relations generated
+in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
 for some $\alpha,\beta \in \mathbb{N}$ such that
@@
 \label{eqn:deg1_sat_ind_dim}
-	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
+	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
 	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
@@
 \[
-	0<\frac{c_1}{d_1}<\ldots<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
+	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
 \]
@@
 \begin{itemize}
-\item $R_{D'}$ is generated over $R_D$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
+\item $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
 degree $d_i$ and has a pole at $P$ of degree $c_i$
 
-\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+\item If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
 										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
@@
 In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
-%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
 \item A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
-	and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
-	\frac{\alpha}{\beta} \rfloor} + 1}$ as shown above minimally
+	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
+	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
 generates $I'$.
@@
 \begin{proof}
-Inside of $(R_
-{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$. By
+By
 our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
@@
 \[
-	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
+	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \deg(d\frac{\alpha}{\beta})
 \]
@@
 \noindent
-so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
+so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
 order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We can use a method similar to O'Dorney to
-construct the $y_i$'s as desired: \todo{cite where}
+\beta} \rfloor \}$. We will use O'Dorney's method of best lower approximations to
+construct the $y_i$'s as desired. \todo{cite where}
 
@@
 be the non-negative best lower approximation of $\frac{
-\alpha}{\beta}$. Note that elements of $H^0(X, dD')$ have pole of
+\alpha}{\beta}$ as described in the lemma's statement.  Note that elements of $H^0(X, d\halfcan)$ have pole of
 orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$. A set of these one for each pole degree 1 to $\lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
-each other and $(R_D)_d$, so by degree considerations, they span
-$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.
+c_i $ at $P$.  Moreover, a set $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
+$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.
 
@@
 \[
-	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
+	\sum -\ord(z_i) < c_i .
 \]
@@
 \noindent
-Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
+Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
 lower degrees. 
-Generically choose some $y_i \in(R_{
-D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i = 1$ then 
-\[
-	-\ord_P(y_i)= \max(c_j:d_j = 1)
-\]
-
-\noindent
-and if more than one $d_i$ is 1, we
-must also choose them generically so they generate $(R_{D'})_1$).
+Choose some $y_i \in(R_{
+\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.
 
@@
 \noindent
-Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
-has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
-\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
-where $d_j = 1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+Therefore, we can generate an element of $(R_{\halfcan})_d$ as a product of lower degrees that 
+has pole degree $c$ at $P$ by either $y_i u^b$, $y_i z u^b$, or $zu^b$ satisfying $i>
+\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$, 
+with $d_j = 1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
 \rfloor + 1}$.
@@
 _n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-same conditions. We notice that elements of this form are all
-linearly independent in $R_{D'}$. Thus, they form a $k$-basis for
-$R_{D'}$ over $R_D$. Thus $u, x_1, \ldots, x_m, y_1, \ldots, y_n$ generate
-$R_{D'}$.
+same conditions.
+This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.
+In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.
 
@@
 with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
+is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
 expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
@@
 
-Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
+Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
 generated by the initial terms described in the previous paragraphs
-together with $\gin_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
+together with $\initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
 
@@
 , x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
-Therefore, by dimension counting (in each degree), we see that $J'$
-is the initial ideal of $I'$. Furthermore, since our choice of $y_i
-$'s was generic, this is in fact the generic initial ideal.
+Therefore, by dimension counting (in each degree), we see that $J$
+is the initial ideal of $I$. 
+%Furthermore, since our choice of $y_i
+%$'s was generic, this is in fact the generic initial ideal.
 
@@
 \begin{enumerate}
-	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
-		= \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] Any generator $z \neq y_{i, e_i'}$
+	\item[(Ad-i)] For all $i \in J$, $\deg y_{e_i'} = e_i'$ and $-ord_{
+		Q_i}(y_{i, e_i'}) = \frac{e_i'- 1}{2}$.
+	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i, e_i'}$
 		of $R'$ satisfies
@@
 		\end{align*}
-	\item[(Ad-iii)] The minimality condition
+	\item[(Ad-iii)] For all $i \in J$ we have
 		\begin{align*}
@@
 \begin{lem}\label{lem:n-3s-admissible}
-Fi x a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
+Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
 Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$.
@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
+Suppose $(\sx', 0, \halfcan')$ is a log spin curve with coarse
 space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and
@@
 R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
-$(\sx, \Delta, \halfcan)$ be another log spin curve
+$(\sx, 0, \halfcan)$ be another log spin curve
 with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
@@
 
-Finally, if $(\sx , J)$ is admissible then so is $(\sx,W)$ for any
+Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
 $W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
-\end{proof}
-
-\begin{cor}
-\label{cor:raise-stacky-order}
-Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ with $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
-so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}.
-Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of ramified points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
-$$
-e_i \begin{cases}
-	= e_i' &\text{ if }i \notin J\\
-	\leq e_i' &\text{ if } i \in J
-\end{cases}$$
-then Theorem ~\ref{thm:general_generators_relations} holds for $(\sx,\Delta,L)$
-\end{cor}
-\begin{proof}
-For $t \leq i \leq r$.
-Let $(\sx_i,\Delta, L_i)$ be the log stacky spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
-$J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
-
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, L_i, J_i)$ is admissible.
-
-Since $(*_0)$ holds by assumption, by induction on $i$, it suffices to show that if $(*_i)$ holds then so does $(*_{i+1}).$ 
-Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, L_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
-Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
 \end{proof}
@@
 \begin{prop}
-\label{prop:relation_11}
+\label{prop:relations_generation}
 Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K + \Delta$. Then $I_L$ is generated in degree at most $11$ if $\Delta = 0$ and degree at most $10$ if $\Delta > 0$.
@@
 In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 is close to sharp.
+Therefore, the bound from Proposition ~\ref{prop:relations_generation}, that $I_L$ is generated in degree at most 11 is close to sharp.
 \end{rem}
@@
 \label{ssec:main_g_high}
-
-\begin{thm}
-\label{thm:general_generators_relations}
-Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
-that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
-canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
-\end{align*}
-
-\noindent
-is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r).$ If $\Delta = 0$ then 
-$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
-\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
-$\max(10, 2e_1, \ldots, 2e_r).$
-\end{thm}
-
-\begin{proof}
-By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, we are done in the case that there are no stacky points. 
-\end{proof}
 
@@
 
+\todo{Aaron: It becomes a bit tedious for this proof to alternatingly cite ~\ref{lem:admissible_subset} and ~\ref{thm:ram_order_ind} is there a reason these were separated/can we merge the back together?
+Better yet, this should probably be a corollary somewhere, since we have to use this implicitly in all three genus cases.}
 Second, we deal with the case that $\sx$ has at least two stacky points.
@@
 Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$.
-Then, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
+Applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_1-3}{2}$ times, and letting $J_1 = \{e_1, \ldots, e_1\}$ so that $\# J_1 = r$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\subhalf{e_1}P_i,$ and that $(\sx',J_1)$ is admissible.
+Hence, by Lemma ~\ref{lem:admissible_subset}, it follows that $(\sx',J')$ is admissible, with $J' \subset \{e_1, \ldots, e_1\},$ with $\# J' = r- 1$.
+Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_2-e_1}{2}$ times, and letting $J_2 = \{e_2, \ldots, e_2\}$ so that $\# J_2 = r- 1$, we obtain that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \subhalf{e_1}P_1 + \sum_{i =2}^{r}\subhalf{e_2}P_i,$ and that $(\sx',J_1)$ is admissible.
+Continuing to altenatively apply Lemma ~\ref{lem:admissible_subset} and Theorem ~\ref{thm:ram_order_ind}, we eventually obtain the theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
 
@@
 	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
-	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
+	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relations_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
 \todo{Possibly think more about this}

### 2015-06-25 stacky_write_up/spin_cring.tex

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 Then
-\begin{enumerate}
-\item[(a)] $R_{D'}$ is generated over $R_D$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
+
+\begin{itemize}
+\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
 degree $d_i$ and has a pole at $P$ of degree $c_i$
 
-\item[(b)] If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then
-
-\begin{align*}
-	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+\item[(b)] If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
+
+\begin{align*}
+	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
 										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
@@
 In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
-%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
+%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
 \item[(c)] A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
-	and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
-	\frac{\alpha}{\beta} \rfloor} + 1}$ as shown above minimally
+	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
+	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
 generates $I'$.

### 2015-06-25 stacky_write_up/spin_cring.tex
compile error fixed
fix bad refs, add gitignore to beamer folder

@@
 
-\begin{itemize}
+\begin{enumerate}
 \item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
@@
 \begin{thm}
-\label{thm:general_generators_relations}
+\label{thm:high_generators_relations}
 Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
@@
 Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
-By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta, \halfcan_X)$.
-Next, consider a divisor of the form $\halfcan' = \halfcan_X + \frac{1}{3}P_i$.
-Then, the theorem holds for $(\sx,\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus} if $P_i$ is a basepoint of $\halfcan'$ or by Lemma ~\ref{deg1-sat-ind} if $P_i$ is not a basepoint of $L'$.
-Note, in the case $P$ is a not basepoint of $\halfcan'$, Equation ~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d \geq 3$.
-
-In this case, we claim $(\sx',L',\{1\})$ is admissible.
-Indeed, (Ad-i) holds by part (a) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, (Ad-ii) holds by part (b) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by Lemma ~\ref{lem:n-3s-admissible}, Any triple of the form $(\sx',L',\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
-Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for all log spin curves $(\sx, L, J).$
+By Lemma ~\ref{lem:generation_5} and Proposition
+~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
+\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
+\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
+\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus}
+ if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
+~\ref{lem:deg1-sat-ind} if $P_i $ is not a basepoint of $L'$. Note,
+in the case $P$  is a not basepoint of $\halfcan'$, Equation
+~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
+\geq 3$.
+
+In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-
+i) holds by part (a) of Lemmas
+~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
+(Ad-ii) holds by part (b) of Lemmas
+~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
+and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by
+Lemma ~\ref{lem:n-3s-admissible} , Any triple of the form $(\sx', L',
+\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
+Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
+holds for all log spin curves $(\sx, L, J)$. 
 \end{proof}

### 2015-06-25 stacky_write_up/spin_cring.tex
modify Ad-ii to include 3s

@@
 		= \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] Any generator $z \neq y_{i, e_i'}$
-		of $R'$ satisfies
+	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
+		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
 		\begin{align*}
@@
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
-strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
+strictly monotonic in the $e_i$ and hence also holds for $(\sx,J)$.
 Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
@@
 
-Finally, if $(\sx , J)$ is admissible then so is $(\sx,W)$ for any
+Finally, if $(\sx , J)$ is admissible then so is $(\sx, W)$ for any
 $W \subset J$ by Lemma ~\ref{lem:admissible_subset}.

### 2015-06-25 stacky_write_up/spin_cring.tex
minor raising degree theorem wording edits

@@
 claim of $(a),$ by considering separately the cases of whether $j
-\in S(i,0),$ and $j \notin S(i,0)$.
+\in S(i, 0),$ and $j \notin S(i,0)$.
 
@@
 
-To show (c), we wish to show $y_{i, e_i}z \in R'$ for $z \neq y_{i, e_
-i}, y_{i, e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
-all $j \in J$ we have
+To show (c), we wish to show that $f := y_{i, e_i}z \in R'$ for $z
+\neq y_{i, e_i} \text{ or } y_{i, e_i'}$. Note that $f \in R$ lies
+in $R'$ if and only if for all $j \in J$ we have
 \begin{align*}
@@
 We now check this in three cases, depending on whether $j \notin \{
-i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
+i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
 

### 2015-06-25 stacky_write_up/spin_cring.tex
added part for n 3s in raising order lemma

@@
 
-To show (c), we wish to show that $f := y_{i, e_i}z \in R'$ for $z
-\neq y_{i, e_i} \text{ or } y_{i, e_i'}$. Note that $f \in R$ lies
-in $R'$ if and only if for all $j \in J$ we have
+To show (c), we wish to show, for all generators $z$ of $R'$
+such that $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$, that
+$f := y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
+only if for all $j \in J$ we have
 \begin{align*}
@@
 
-By part (a), condition (Ad-ii), and Lemma
+For the case when $e_j' = 3$ for all $j \in \{1, \ldots, r\}$,
+we know that
+
+Otherwise by part (a), condition (Ad-ii), and Lemma
 ~\ref{lem:admissible_inequality} we have

### 2015-06-25 stacky_write_up/spin_cring.tex
modify g0 main proof, minor other style edits

@@
 
-The following lemma provides an inductive method to extend O'Dorney's result on $\mathbf{P}^1$ to divisors $D=\sum_i \frac{\alpha_i}{\beta_i}P_i$ consisting of arbitrarily many points satisfying $H^0(X,\lfloor D\rfloor)>0$, showing that they are generated in degrees at most $e=\max(\beta_i)$ with relations generated in degrees at most $2e$.
-Furthermore, given some constraints on $H^0(X, \lfloor dD\rfloor)$ for various values of $d$, we can apply the same Riemann-Roch arguments from $\mathbf{P}^1$ in arbitrary genus, allowing a similar inductive result in arbitrary genus $e=\max(\beta_i)$.
-To do this, we extend an inductive result by Voight and Zurich-Brown on stacky canonical rings to arbitrary $\mathbf{Q}$-divisors.
-\todo{cite theorem 8.3.1}
+The following lemma provides an inductive method to extend
+O'Dorney's result on $\BP^1$ to divisors $D = \sum_i \frac{\alpha_i
+}{\beta_i} P_i$ consisting of arbitrarily many points satisfying $H^
+0(X, \lfloor D \rfloor) > 0$, showing that they are generated in
+degrees at most $e = \max(\beta_i)$ with relations generated in
+degrees at most $2e$.  Furthermore, given some constraints on $H^0(
+X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
+same Riemann-Roch arguments from $\BP^1$ in arbitrary genus,
+allowing a similar inductive result in arbitrary genus $e = \max(
+\beta_i)$. To do this, we extend an inductive result by Voight and
+Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
+divisors. \todo{cite theorem 8.3.1}
 
@@
 Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
-In both cases we induce a relation, with initial term described in the Lemma's statement.
+In both cases we induce a relation, with initial term described in the lemma's statement.
 Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
@@
 \label{ssec:g_0_saturation}
-First, we present the saturations $'s$ of the canonical divisor for
+First, we present the saturations $s$ of the canonical divisor for
 all cases where $g = 0, \delta = 0$ as defined in Definition
 ~\ref{defn:sat}. The saturation can be computed via the application
-of Riemann-Roch on degrees up to $'s$. Exceptional cases are listed
+of Riemann-Roch on degrees up to $s$. Exceptional cases are listed
 first and generic cases follow.
@@
 \begin{proof}
-If $\sx$ has no stacky points, then we have the classical
-case which is done in Voight and Zureick-Brown ~\cite[Section 4.2]
-{vzb:stacky}.
-\todo{This confused me because while they do technically prove this, they only prove it for the canonical divisor, not the log canonical divisor.
-It would be clearer to write that in this case, we can assume $L = n \cdot \infty$ with $n \in \BZ$, which is covered in 4.2, with $L$ replaced by $K$.}
+If $\sx$ has no stacky points, then we can assume that $L \sim
+n \cdot \infty$ with $n \in \BZ$. This is the classical
+case which is done, with $L$ replaced by $K$, by Voight and
+Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.
 
@@
 of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
-the Lemma inductively on the classical case with no stacky points
+the lemma inductively on the classical case with no stacky points
 to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
@@
 ~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
-{ssec:g_0_saturation} that saturation is 3 here \todo{Write this out more precisely, it should be something like $'sat(Eff(\sigma)) = 3$}), and the
+{ssec:g_0_saturation} that $sat(Eff(\sigma_{11})) = 3$), and the
 immediate consequence of parts (a) and (c) of Lemma
@@
 degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
-up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
-implies that these cases satisfy all of the conditions of Theorem
-~\ref{thm:ram_order_ind}.
-
-So if $r > 5$, then $\sigma$ ``lies above'' \todo{Aaron: what does this mean} the case $(\sigma', J)$
+up to degree $2e$. Furthermore, these cases satisfy all of the
+conditions of Theorem ~\ref{thm:ram_order_ind}.
+
+So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
 where $\sigma'$ has $r$ many stacky points all of order $3$
-and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
-all of the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
-If $r \leq 5$, then $\sigma$ ``lies above'' one of the base cases
-of Lemma ~\ref{lem:g_0_admissible_cases}, all of which satisfy
-the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.
+and $J = \{1, \ldots, r\}$ in the sense that for all $i
+\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
+If $r \leq 5$, then $\sigma$ similarly ``lies above'' one of the
+base cases of Lemma ~\ref{lem:g_0_admissible_cases}, all of which
+satisfy the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.
 

### 2015-06-25 stacky_write_up/spin_cring.tex
lemma 3.1 stuff

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 remark for quotient}
+\iffalse{
 \begin{lem}
@@
 generated in degree 1, is equipped with a monomial ordering $\prec$.
- Let $\phi:k[x_1, \ldots, x_n] \rightarrow B$ be a map of graded
-rings with kernel $I,$ such that $I$ is generated by elements $f_1,
+ Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
+rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
 \ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
@@
 \end{rem}
-
-%
-%\begin{lem}
-%\label{lem:minimal_quadratic_2}
-%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-%generated in degree 1 that are equipped with monomial ordering $\prec$.
- %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
-%\[
-	%\begin{tikzcd}
-	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	%\end{tikzcd}
-%\]
-%Further suppose that $I'$ is generated over $I$ by elements $f_1,
-%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
-%is of the form $y_i$. Then, the elements $f_i$ determine minimal
-%generators for $I'$ over $I$.
-%\end{lem}
-%
-%\begin{proof}
-%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-%degree 1. Then,
-%\[
-	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-%\]
-%\[
-	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-%\]
-%
-%
-%\noindent
-%determines map of rings, no longer necessarily graded. 
-%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
-%\[
-	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-%\]
-%so
-%\[
-	%\dim_k (I'/I)_2=j.
-%\]
-%This implies any set of
-%generators for $I$ must have at least $j$ elements. Since $f_1,
-%\ldots, f_j$ is such a set, it is minimal.
-%\end{proof}
-%
-%
-%\begin{rem}
-%\label{rem:minimal_quadratic_trivial_case}
-%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
-%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
-%are $k$-minimal generators for $I'$ (over the trivial base vector
-%space). 
-%\end{rem}
+}\fi
+
+\begin{lem}
+\label{lem:minimal_quadratic_2}
+Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
+generated in degree 1 that are equipped with monomial ordering $\prec$.
+Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
+rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
+\[
+	\begin{tikzcd}
+	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	\end{tikzcd}
+\]
+Further suppose that $I'$ is generated over $I$ by elements $f_1,
+\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
+is of the form $y_i$. Then, the elements $f_i$ determine minimal
+generators for $I'$ over $I$.
+\end{lem}
+
+\begin{proof}
+Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
+degree 1. Then,
+\[
+	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
+\]
+\[
+	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
+\]
+
+\noindent
+determines map of rings, no longer necessarily graded. 
+By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
+\[
+	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
+\]
+so
+\[
+	\dim_k (I'/I)_2=j.
+\]
+This implies any set of
+generators for $I$ must have at least $j$ elements. Since $f_1,
+\ldots, f_j$ is such a set, it is minimal.
+\end{proof}
+
+\begin{rem}
+\label{rem:minimal_quadratic_trivial_case}
+It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
+case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
+are $k$-minimal generators for $I'$ (over the trivial base vector
+space). 
+\end{rem}
 
@@
 
+Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$.
+
+\begin{lem}\label{lem:relations_from_generators_induction} 
+Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
+Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
+Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.
+Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.
+Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then
+\begin{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
+Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Grobner Basis with an initial term for each element of $T$.
+\end{lem}
 \begin{proof}
+
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
 By
@@
 
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
-corresponds to the best lower approximation $\frac{c_j}{d_j}$. Recall from the previous 
-paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
-$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l= 1$ and if 
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.
+Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if
 $d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
@@
 		= \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
-		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
+	\item[(Ad-ii)] Any generator $z \neq y_{i, e_i'}$
+		of $R'$ satisfies
 		\begin{align*}
@@
 claim of $(a),$ by considering separately the cases of whether $j
-\in S(i, 0),$ and $j \notin S(i,0)$.
+\in S(i,0),$ and $j \notin S(i,0)$.
 
@@
 
-To show (c), we wish to show that $f := y_{i, e_i}z \in R'$ for $z
-\neq y_{i, e_i} \text{ or } y_{i, e_i'}$. Note that $f \in R$ lies
-in $R'$ if and only if for all $j \in J$ we have
+To show (c), we wish to show $y_{i, e_i}z \in R'$ for $z \neq y_{i, e_
+i}, y_{i, e_i'}$. Note that $f\in R$ lies in $R'$ if and only if for
+all $j \in J$ we have
 \begin{align*}
@@
 We now check this in three cases, depending on whether $j \notin \{
-i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
+i \} \cup S(i,0),j = i,$ or $j \in S(i,0)$.
 
@@
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
-strictly monotonic in the $e_i$ and hence also holds for $(\sx,J)$.
+strictly monotonic in the $e_i$, and hence also holds for $(\sx,J)$.
 Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
@@
 
-Finally, if $(\sx , J)$ is admissible then so is $(\sx, W)$ for any
+Finally, if $(\sx , J)$ is admissible then so is $(\sx,W)$ for any
 $W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
@@
 \begin{thm}
-\label{thm:high_generators_relations}
+\label{thm:general_generators_relations}
 Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
@@
 Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
-By Lemma ~\ref{lem:generation_5} and Proposition
-~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
-\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
-\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
-\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus}
- if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
-~\ref{lem:deg1-sat-ind} if $P_i $ is not a basepoint of $L'$. Note,
-in the case $P$  is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
-\geq 3$.
-
-In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-
-i) holds by part (a) of Lemmas
-~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
-(Ad-ii) holds by part (b) of Lemmas
-~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
-and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by
-Lemma ~\ref{lem:n-3s-admissible} , Any triple of the form $(\sx', L',
-\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
-Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
-holds for all log spin curves $(\sx, L, J)$. 
+By Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta, \halfcan_X)$.
+Next, consider a divisor of the form $\halfcan' = \halfcan_X + \frac{1}{3}P_i$.
+Then, the theorem holds for $(\sx,\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus} if $P_i$ is a basepoint of $\halfcan'$ or by Lemma ~\ref{deg1-sat-ind} if $P_i$ is not a basepoint of $L'$.
+Note, in the case $P$ is a not basepoint of $\halfcan'$, Equation ~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d \geq 3$.
+
+In this case, we claim $(\sx',L',\{1\})$ is admissible.
+Indeed, (Ad-i) holds by part (a) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, (Ad-ii) holds by part (b) of Lemmas ~\ref{lem:sat-two-induction-high-genus} and ~\ref{deg1-sat-ind}, and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by Lemma ~\ref{lem:n-3s-admissible}, Any triple of the form $(\sx',L',\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
+Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for all log spin curves $(\sx, L, J).$
 \end{proof}
@@
 	\item Generic Initial ideal (and other genericness properties?)
+	\item Complete minimal generation
 \end{itemize}

### 2015-06-25 stacky_write_up/spin_cring.tex
fixed some spaced-out refs, accent grobner

@@
 $\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
-exceptional cases, as listed in Table ~\ref{table:g - 1-exceptional}
+exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
 for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
@@
 procedure for determining the generators and initial ideal of
-relations for $ \halfcan$. In fact, such a system of generators and
+relations for $\halfcan$. In fact, such a system of generators and
 relations are known for $\halfcan'$ in many cases, as detailed in
@@
 	\item Note that this result is independence of base field
-	\item background on grobner bases
+	\item background on Gr\"{o}bner bases
 	\item Notation $h^0 = \dim H^0$.
@@
 determines map of rings, no longer necessarily graded. 
-By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
+By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Gr\"{o}bner basis,
 \[
@@
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
-Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Grobner Basis).
+Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
 The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
@@
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
-\item[(c)] A Grobner basis with the initial terms $y_i x_j$, $y_i y_j$,
+\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
 	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
@@
 \end{align*}
-Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Grobner Basis with an initial term for each element of $T$.
+Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Gr\"{o}bner Basis with an initial term for each element of $T$.
 \end{lem}
@@
 In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
-~\ref{lem:minimal_quadratic} immediately tells us that the Grobner
+~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
 basis defined above is minimal.
@@
 %\end{align*}
-%\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
+%\item A Gr\"{o}bner basis with initial terms described above minimally generates $I'$ over $I$.
 %\end{itemize}
@@
 \ssec{Genus One Exceptional Cases}
-\label{ssec:g - 1-exceptional}
+\label{ssec:g-1-exceptional}
 \todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
@@
 \begin{center}
-\label{table:g - 1-exceptional}
+\label{table:g-1-exceptional}
 \textbf{Table (IV)}: Genus 1 exceptional cases, where $L' = P - Q + \frac{e- 1}{2e}R$, with $P \neq Q$.
@@
 \begin{rem}
-\label{rem:g - 1-exceptional-e}
+\label{rem:g-1-exceptional-e}
 Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
@@
 We now elaborate on the computation of the results in 
-Table ~\ref{table:g - 1-exceptional}. We have already explained the case of 
+Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
 $L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception- 1-5}. The other cases are similar.
@@
 \begin{example}
-\label{eg:exceptional- 1-0}
+\label{eg:exceptional-1-0}
 In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
@@
 finite list of exceptional cases, as listed in Table
-~\ref{table:g - 1-exceptional}.
+~\ref{table:g-1-exceptional}.
 \end{thm}
@@
 
-Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g - 1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
+Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
 

### 2015-06-25 stacky_write_up/spin_cring.tex
some intro changes (parts -> background), ref fix

@@
 Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup
-of $PSL_2(\BR)$ acting on the {\bf upper half plane} $\bh$ by
-fractional linear transformations. We can then consider the
-orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the
-case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a
-Riemann Surface over $\BC$. It may well be that $\Gamma \backslash
-\bh$ is not compact. Defining $\Delta$ as the divisor of cusps
-associated to $\Gamma$, we can form a space $\Gamma \backslash
-\bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with
-associated {\bf divisor of cusps} $\Delta$.
-
-We can now consider the
-{\bf ring of modular forms} $M(\Gamma) = \oplus_k M_k(\Gamma)$. In
-this paper, for general $\Gamma$, we sharply bound the degree of
-the generators and relations for $M(\Gamma).$ This was already
-answered in \cite[Chapters 7-9]{vzb:stacky} in the case that
-$M(\Gamma)$ has $M_{2k}(\Gamma) = 0$ for all $k \in \BZ$, that is,
-when $\Gamma$ has no odd weight modular forms, and we extend this
-to all Fuchsian subgroups $\Gamma$. In order to answer this
-question, we translate the seemingly analytic question into the
-algebraic category, using a generalization of the GAGA principle.
-That is, by \cite[Proposition 6.1.5]{vzb:stacky}, there is an
-equivalence of categories between orbifold curves and log stacky
-curves over $\BC$. Hence, for the remainder of the paper, we will
-work in the algebraic category. Let $X$ be a smooth algebraic
-curve over $k$ of genus $g$. It is well known that the sheaf $\Omega
-_X,$ with associated divisor $K_X$ determines the {\bf canonical map
-} $\pi:X \rightarrow \BP_k^{g - 1}.$ Then, the {\bf canonical ring},
-is defined as
+of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
+linear transformations. We consider the {\bf ring of modular forms}
+$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, for general
+$\Gamma$, we sharply bound the degree of the generators and
+relations for $M(\Gamma).$ The case where $M(\Gamma)$ has $M_{2k + 1
+}(\Gamma) = 0$ for all $k \in \BZ$, i.e. when $\Gamma$ has no odd
+weight modular forms, is answered in Voight and Zureick-Brown
+\cite[Chapters 7-9]{vzb:stacky}. This work extends this result to
+all Fuchsian subgroups $\Gamma$. In order to answer this question,
+we translate the seemingly analytic question into the algebraic
+category, using a generalization of the GAGA principle. By
+\cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
+categories between orbifold curves and log stacky curves over $\BC$
+. Hence, for the remainder of the paper, we will work in the
+algebraic category.
+
+Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is
+well known that the sheaf $\Omega _X,$ with associated divisor $K_X$
+ determines the {\bf canonical map } $\pi:X \rightarrow \BP_k^{g - 1}$.
+Then, the {\bf canonical ring} is defined to be
 \begin{align*}
@@
 sections. Since $\Omega_X$ is ample, $X \cong \proj R$. Petri's
-theorem gives generators and relations for $R(X,K_X),$ see for
-example, \cite{saint-donat:proj}[Theorem, p. 157], showing that in
-most cases $R(X,K_X)$ is generated in degree 1 with relations in
-degree 2. This has the pleasant geometric consequence that all such
-canonically embedded curves are scheme theoretically cut out by
-quadratic equations.
+theorem gives generators and relations for $R(X, K_X)$ showing that
+in most cases $R(X, K_X)$ is generated in degree 1 with relations
+in degree 2 (see \cite[p. 157]{saint-donat:proj}). This has the
+pleasant geometric consequence that all such canonically embedded
+curves are scheme theoretically cut out by quadratic equations
 
@@
 \Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
-say $\sx$ has signature $(g; e_1, \ldots, e_r;\delta)$. A {\bf log
-spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
+say $\sx$ has \textbf{signature} $(g; e_1, \ldots, e_r;\delta)$. A
+{\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
 and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$ then 
-$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
-\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
-$\max(10, 2e_1, \ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list of
-exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
-for signatures with $g = 1$ and Table ~\ref{table:g_0_exceptional}
+\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0
+$ then $R(\sx,\Delta, \halfcan)$ has relations generated in degrees
+up to $\max(11, 2e_1, \ldots, 2e_r)$. Otherwise, $R(\sx, \Delta,
+\halfcan)$ has relations generated in degrees up to $\max(10, 2e_1,
+\ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list
+of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
+for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
 for signatures with $g = 0$.
@@
 
+\subsection{Junk}
+This is stuff that has been moved out of the introduction to possibly
+be retooled for this section.
+
+We can then consider the
+orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the
+case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a
+Riemann Surface over $\BC$. It may well be that $\Gamma \backslash
+\bh$ is not compact. Defining $\Delta$ as the divisor of cusps
+associated to $\Gamma$, we can form a space $\Gamma \backslash
+\bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with
+associated {\bf divisor of cusps} $\Delta$.
+
 \subsection{Definitions}
@@
  divisor $D$ of $X$ and describe the new generators and relations
-of $R_{D+p}$ not in $R_D$. Next, we provide a method specific to
+of $R_{D + P}$ not in $R_D$. Next, we provide a method specific to
 the case of stacky canonical divisors, which
@@
 remark for quotient}
-\iffalse{
+
+%\begin{lem}
+%\label{lem:minimal_quadratic}
+%Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
+%generated in degree 1, is equipped with a monomial ordering $\prec$.
+ %Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
+%rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
+%\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
+%is of the form $x_k$. Then, the elements $f_i$ determine minimal
+%generators for $I$.
+%\end{lem}
+%\begin{proof}
+%Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
+%degree 1. Then,
+%\[
+	%\phi : k[x_1, \ldots, x_n] \rightarrow B
+%\]
+%\noindent
+%determines a map of rings, no longer necessarily graded. Consider
+%the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
+%\todo{This ordering isn't quite right. 
+%We need to preserve the ordering on quadratic terms}
+%By
+%assumption, the kernel $I$ is generated by elements whose initial
+%terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
+%\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
+%generators for $I$ must have at least $j$ elements. Since $f_1,
+%\ldots, f_j$ is such a set, it is minimal.
+%\end{proof}
+%
+%\begin{rem}
+%In particular, in the case of
+%\[
+	%\begin{tikzcd}
+		%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
+		%\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
+		%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	%\end{tikzcd}
+%\]
+%inducing
+%\[
+	%I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
+%\]
+%\todo{how do we make this proof?}
+%\end{rem}
+
 \begin{lem}
 \label{lem:minimal_quadratic}
-Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
-generated in degree 1, is equipped with a monomial ordering $\prec$.
- Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
-rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
-\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
-is of the form $x_k$. Then, the elements $f_i$ determine minimal
-generators for $I$.
-\end{lem}
-\begin{proof}
-Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
-degree 1. Then,
-\[
-	\phi : k[x_1, \ldots, x_n] \rightarrow B
-\]
-\noindent
-determines a map of rings, no longer necessarily graded. Consider
-the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
-\todo{This ordering isn't quite right. 
-We need to preserve the ordering on quadratic terms}
-By
-assumption, the kernel $I$ is generated by elements whose initial
-terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
-\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
-generators for $I$ must have at least $j$ elements. Since $f_1,
-\ldots, f_j$ is such a set, it is minimal.
-\end{proof}
-
-\begin{rem}
-In particular, in the case of
-\[
-	\begin{tikzcd}
-		I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
-		\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
-		I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	\end{tikzcd}
-\]
-inducing
-\[
-	I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
-\]
-\todo{how do we make this proof?}
-\end{rem}
-}\fi
-
-\begin{lem}
-\label{lem:minimal_quadratic_2}
 Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
@@
 base cases (Subsection ~\ref{ssec:g_0_base}), and exceptional
-cases (Subsection ~\ref{ssec:g_0_exceptional}) when $\delta = 0$
+cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
 before proving the main theorem in full for all $\delta$ in
@@
 \ssec{Exceptional Cases}
-\label{ssec:g_0_exceptional}
+\label{ssec:g-0-exceptional}
 First, we describe the cases that would not be covered by induction.
@@
 so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as listed in Table ~\ref{table:g_0_exceptional}.
+cases, as listed in Table ~\ref{table:g-0-exceptional}.
 \end{thm}
@@
 and not one of the exceptional cases in Table
-~\ref{table:g_0_exceptional}.
+~\ref{table:g-0-exceptional}.
 

### 2015-06-25 stacky_write_up/spin_cring.tex
lemma 3.1 issues

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 \begin{lem}
-\label{lem:minimal_quadratic_2}
+\label{lem:minimal_quadratic}
 Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily

### 2015-06-25 stacky_write_up/spin_cring.tex

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 \newcommand \gin{\text{gin}}
+\newcommand \Eff{\text{Eff}}
+\newcommand \sat{\text{sat}}
 
@@
 \subsection{Definitions}
+We reserve the notation $\halfcan$ for the halfcanonical divisor
+where $\halfcan \sim $.
+
 Here are some definitions.
+
+We define the notion of the saturation of a divisor, taken from
+Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
+
+\begin{defn}
+Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
+is the monoid
+\[
+	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}
+\]
+\end{defn}
 
@@
 \label{defn:sat}
-\textbf{Saturations} of the canonical divisor, as defined in Voight
-and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
+The \textbf{saturation} for a monoid $M \subseteq \BZ_{\geq 0}$,
+denoted $\sat(M)$, is the smallest integer $s$ such that $M
+\supseteq \BZ_{\geq s}$, if such an integer exists.
 \end{defn}
+
+\begin{rem}
+For our purposes, it is useful to call the saturation of the
+effective monoid of a divisor $D$ as the saturation $s$ of the
+divisor $D$ on $\sx$. In this case, the saturation $s$ of a divisor
+$D$ on $\sx$ (i.e. $\sat(\Eff(D))$) is the smallest positive $s \in
+\BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d \geq s$.
+\end{rem}
 
@@
 Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
-space $X$ of genus 0 such that $'sat(Eff(\halfcan')) = 3$ with $R_
+space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ with $R_
 {\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
@@
 %\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures. Suppose 
-%$'sat(Eff(\halfcan))= 1$ and $'sat(Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 
+%$\sat(\Eff(\halfcan))= 1$ and $\sat(\Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 
 %x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. Then
@@
 %\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures. 
-%Suppose $'sat(Eff(\halfcan))= 1$ and $'sat(Eff(\halfcan'))=2$. Further suppose 
+%Suppose $'\sat(\Eff(\halfcan))= 1$ and $'\sat(\Eff(\halfcan'))=2$. Further suppose 
 %$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. 
@@
 ~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
-{ssec:g_0_saturation} that $sat(Eff(\sigma_{11})) = 3$), and the
+{ssec:g_0_saturation} that $\sat(\Eff(\sigma_{11})) = 3$), and the
 immediate consequence of parts (a) and (c) of Lemma

### 2015-06-25 stacky_write_up/spin_cring.tex
added rational section order

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 remark for quotient}
-\iffalse{
 \begin{lem}
@@
 generated in degree 1, is equipped with a monomial ordering $\prec$.
- Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
-rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
+ Let $\phi:k[x_1, \ldots, x_n] \rightarrow B$ be a map of graded
+rings with kernel $I,$ such that $I$ is generated by elements $f_1,
 \ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
@@
 \end{rem}
-}\fi
-
-\begin{lem}
-\label{lem:minimal_quadratic}
-Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-generated in degree 1 that are equipped with monomial ordering $\prec$.
-Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
-\[
-	\begin{tikzcd}
-	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	\end{tikzcd}
-\]
-Further suppose that $I'$ is generated over $I$ by elements $f_1,
-\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
-is of the form $y_i$. Then, the elements $f_i$ determine minimal
-generators for $I'$ over $I$.
-\end{lem}
-
-\begin{proof}
-Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-degree 1. Then,
-\[
-	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-\]
-\[
-	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-\]
-
-\noindent
-determines map of rings, no longer necessarily graded. 
-By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
-\[
-	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-\]
-so
-\[
-	\dim_k (I'/I)_2=j.
-\]
-This implies any set of
-generators for $I$ must have at least $j$ elements. Since $f_1,
-\ldots, f_j$ is such a set, it is minimal.
-\end{proof}
-
-\begin{rem}
-\label{rem:minimal_quadratic_trivial_case}
-It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
-case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
-are $k$-minimal generators for $I'$ (over the trivial base vector
-space). 
-\end{rem}
+
+%
+%\begin{lem}
+%\label{lem:minimal_quadratic_2}
+%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
+%generated in degree 1 that are equipped with monomial ordering $\prec$.
+ %Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
+%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
+%\[
+	%\begin{tikzcd}
+	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	%\end{tikzcd}
+%\]
+%Further suppose that $I'$ is generated over $I$ by elements $f_1,
+%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
+%is of the form $y_i$. Then, the elements $f_i$ determine minimal
+%generators for $I'$ over $I$.
+%\end{lem}
+%
+%\begin{proof}
+%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
+%degree 1. Then,
+%\[
+	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
+%\]
+%\[
+	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
+%\]
+%
+%
+%\noindent
+%determines map of rings, no longer necessarily graded. 
+%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Grobner basis,
+%\[
+	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
+%\]
+%so
+%\[
+	%\dim_k (I'/I)_2=j.
+%\]
+%This implies any set of
+%generators for $I$ must have at least $j$ elements. Since $f_1,
+%\ldots, f_j$ is such a set, it is minimal.
+%\end{proof}
+%
+%
+%\begin{rem}
+%\label{rem:minimal_quadratic_trivial_case}
+%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
+%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
+%are $k$-minimal generators for $I'$ (over the trivial base vector
+%space). 
+%\end{rem}
 
@@
 
-Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$.
-
-\begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
-Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
-Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.
-Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.
-Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
-Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Grobner Basis with an initial term for each element of $T$.
-\end{lem}
 \begin{proof}
-
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
 By
@@
 degrees less than $d_i$ must have
+\todo{Aaron: at what point is the following order taken at?}
 \[
@@
 
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.
-Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if
+Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
+corresponds to the best lower approximation $\frac{c_j}{d_j}$. Recall from the previous 
+paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
+$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l= 1$ and if 
 $d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
@@
 \begin{defn}
+\label{}
+If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
+
+\begin{defn}
 \label{defn:admissible}
-Let $(\sx', 0, L'),(\sx, 0, L)$ be log spin
+Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
 curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
@@
 \begin{enumerate}
-	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
+	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}(y_{i, e_i'})
 		= \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
-		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
-		\begin{align*}
-			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
+	\item[(Ad-ii)] If every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
+		\begin{align*}
+			\frac{-\ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
 		\end{align*}
@@
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
-Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}= 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
 
@@
 Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
-space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and
-$(\sx', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
+space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either $e_1' = \cdots = e_r' = 3$ or $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
 R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
@@
 		\begin{align*}
-			-ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
+			-\ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
 		\end{align*}
@@
 \begin{proof}
+We will only prove this in the harder case $(\sx, L', J)$ is admissible, as the case $e_1 = \cdots = e_r = 3$ is similar.
+
 Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
@@
 	\item Generic Initial ideal (and other genericness properties?)
-	\item Complete minimal generation
 \end{itemize}

### 2015-06-25 stacky_write_up/spin_cring.tex
changing order to rational section

@@
 \lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$, 
-with $d_j = 1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
+with $d_j = 1 =d_{{\lfloor \frac{a}{b} \rfloor}}$ and $b<d_{\lfloor \frac{\alpha}{\beta} 
 \rfloor + 1}$.
@@
 \begin{enumerate}
-	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}(y_{i, e_i'})
+	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}
+^{\halfcan_X'}(y_{i, e_i'})
 		= \frac{e_i'- 1}{2}$.
@@
 		\begin{align*}
-			\frac{-\ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
+			\frac{-\ord_{Q_i}
+^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
 		\end{align*}
@@
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
-Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
+^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
 
@@
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
+	-\ord_{Q_i}
+^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
+	-\ord_{Q_i}
+^{\halfcan_X'}(z) < \deg(z) \subhalf{e_i'}
 \end{align*}
@@
 as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
+e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}
+^{\halfcan_X'}(z)$ is an integer, 
 we must have
@@
 \begin{align*}
-	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
+	-\ord_{Q_i}
+^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
 	\deg(z) \subhalf{e_i'} - \frac{1}{e_i'}.
@@
 		\begin{align*}
-			-\ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
+			-\ord_{Q_i}
+^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
 		\end{align*}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
+			\frac{-\ord_{Q_j}
+^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
 \subhalf{
@@
 \begin{align*}
-	-\ord_{Q_i}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
+	-\ord_{Q_i}
+^{\halfcan_X'}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
 	\frac{e_i - 1}{2}
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
+	-\ord_{Q_j}
+^{\halfcan_X'}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
 	\subhalf{e_j'} - \frac{1}{e_j'}.
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+	-\ord_{Q_j}
+^{\halfcan_X'}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
 	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
@@
 	(a,b) \mapsto \left( \deg\left(y_{i, e_i'}^ay_{i, e_i}^b\right),-
-	\ord_{Q_i}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
+	\ord_{Q_i}
+^{\halfcan_X'}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
 	\begin{pmatrix}
@@
 such that $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$, that
-$f := y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
+$y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
 only if for all $j \in J$ we have
-\begin{align*}
-	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
-\end{align*}
-
-\noindent
-We now check this in three cases, depending on whether $j \notin \{
+\begin{align}
+\label{eqn:order-degree}
+	-\ord_{Q_j}
+^{\halfcan_X'}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
+\end{align}
+
+\noindent
+We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in three cases, depending on whether $j \notin \{
 i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
@@
 
-Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
-\begin{align*}
-	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
+Here, $-\ord_{Q_j}
+^{\halfcan_X'}(L) = -\ord_{Q_j}
+^{\halfcan_X'}(L'),$ so
+\begin{align*}
+	-\ord_{Q_j}
+^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
+^{\halfcan_X'}(z) \leq e_i \subhalf {e_j'} +
 	\deg z \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z)
+	-\ord_{Q_j}
+^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
+^{\halfcan_X'}(z)
 	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
@@
 \begin{align*}
-	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
+	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'}
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z) 
+	-\ord_{Q_j}^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}^{\halfcan_X'}(z) 
 	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 

### 2015-06-25 stacky_write_up/spin_cring.tex
revisions to end of intro, g0 r<3 case, minor fixes

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\todo{Say that this follows immediately from the three theorems for the special cases.}
-
-Note that in the course of the proof of Theorem
-~\ref{thm:g_0_generators_relations} we will not merely obtain
-bounds on the degrees of the generators and relations. In fact, if
-the genus $g = 0$ or $g = 1$, the proof yields an explicit system
-of generators and the initial ideal of relations. While in the
-genus $g \geq 2$ case, the proof does not always yield an explicit
-system of generators and relations, if the halfcanonical divisor
-$\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',
-0, X)$ a log spin curve, and a system of generators and relations for
-$ \halfcan'$ is known, then our proof provides an inductive
-procedure for determining the generators and initial ideal of
-relations for $\halfcan$. In fact, such a system of generators and
-relations are known for $\halfcan'$ in many cases, as detailed in
-Neves ~\cite[ Section III.4]{neves:halfcan}.
+This theorem is proven in three different genus cases, each of
+which use similar inductive processes. The high genus case is
+proven in Theorem ~\ref{thm:high_generators_relations}. In Theorem
+~\ref{thm:g_1_generators_relations} and Theorem
+~\ref{thm:g_0_generators_relations}, we also give the respective
+genus one and genus zero results after using a similar induction
+process while dealing with more complicated base cases and
+exceptional cases.
+
+\begin{rem}
+The proofs of the main theorems in the low genus cases not only
+obtain bounds on the degrees of the generators and relations, but
+also yield explicit systems of generators and the initial ideal of
+relations. Furthermore, our proof of the high genus case also
+provides an inductive procedure for determining the generators and
+initial ideal of relations for $\halfcan'$ when the halfcanonical
+divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with
+$(\halfcan', 0, X)$ a log spin curve. In fact, such a system of
+generators and relations are known for $\halfcan'$ in many cases,
+as detailed in Neves ~\cite[ Section III.4]{neves:halfcan}.
+\end{rem}
 
@@
 Theorem ~\ref{thm:general_generators_relations}. The idea of the
-proof will be to induct on the order and number of elliptic points.
-To this end, we first review important background in Section
-~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we
-develop various inductive tools. In Sections ~\ref{sec:g_high},
+proof will be to induct on the order and number of hyperelliptic-
+fixed points. To this end, we first review important background in
+Section ~\ref{sec:background}. Then, we develop various inductive
+tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
 ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem
-~\ref{thm:general_generators_relations} in the cases that the genus
-$g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section
+~\ref{thm:general_generators_relations} in the high genus, genus
+one, and genus zero cases respectively. Finally, in Section
 ~\ref{sec:further-questions}, we pose several questions for future
@@
 
-\section{High genus}
+\section{High Genus}
 \label{sec:g_high}
@@
 
-\ssec{Bounds on Generators and Relations in high genus}
+\ssec{Bounds on Generators and Relations in High Genus}
 
@@
 
-\ssec{Main theorem for high genus}
+\ssec{Main Theorem for High Genus}
 \label{ssec:main_g_high}
@@
 \begin{example}
-\label{eg:exception- 1-5}
+\label{eg:exception-1-5}
 Let $L' = \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$.
@@
 Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
-$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception- 1-5}. The other cases are similar.
+$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
 
@@
 \begin{example}
-\label{eg:exception- 1-e}
+\label{eg:exception-1-e}
 Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
@@
 First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception- 1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
 While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
@@
 and not one of the exceptional cases in Table
-~\ref{table:g-0-exceptional}.
+~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
+\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
+trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
+only consider when $r \geq 3$.
 

### 2015-06-25 stacky_write_up/spin_cring.tex
include corollary to theorem for g0 main theorem

@@
 
-All such base cases satisfy all of the hypotheses of
-Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
-R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
-to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
-generated up to degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}.
-It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
-R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
-e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
-(d) that the relations are generated up to degree $2e$.
+All such base cases satisfy all of the hypotheses of Theorem
+~\ref{thm:ram_order_ind} and their corresponding $R' := R(\sx',
+\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
+$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
+degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
+from induction using Theorem ~\ref{thm:ram_order_ind}(b) and
+Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
+\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
+It also follows from induction on Theorem ~\ref{thm:ram_order_ind}(c)
+and ~\ref{cor:raise-stacky-order} that the relations are generated
+up to degree $2e$.
  \end{proof}

### 2015-06-25 stacky_write_up/spin_cring.tex
minor intro edit

@@
 say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
-\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$,
-be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx +
-\Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
-say $\sx$ has \textbf{signature} $(g; e_1, \ldots, e_r;\delta)$. A
-{\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
+\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$ if
+$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\delta := \deg \Delta,$ then we
+say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$. A
+{\bf log spin curve} is a triple $(X, \Delta, \halfcan)$ where $(X,\Delta)$
 and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
@@
 We reserve the notation $\halfcan$ for the halfcanonical divisor
-where $\halfcan \sim $.
+where $2\halfcan \sim K_\sx + \Delta$.
 

### 2015-06-25 stacky_write_up/spin_cring.tex
lemma 3.3

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 \newcommand\sssec{\subsubsection}
-\newcommand\bh{{\mathbb H}}
+\newcommand\bh{{\mathbf H}}
 \newcommand\bO{{\mathbf O}}
 \newcommand\CC{{\mathcal C}}
-\newcommand\BN{{\mathbb N}}
-\newcommand\BC{{\mathbb C}}
-\newcommand\BF{{\mathbb F}}
-\newcommand\BR{{\mathbb R}}
-\newcommand\BQ{{\mathbb Q}}
-\newcommand\BP{{\mathbb P}}
-\newcommand\BBZ{{\mathbb Z}}
+\newcommand\BN{{\mathbf N}}
+\newcommand\BC{{\mathbf C}}
+\newcommand\BF{{\mathbf F}}
+\newcommand\BR{{\mathbf R}}
+\newcommand\BQ{{\mathbf Q}}
+\newcommand\BP{{\mathbf P}}
+\newcommand\BBZ{{\mathbf Z}}
 \newcommand\uR{\underline{R}}
@@
 \newcommand\uCF{\underline{{\mathcal F}}}
-\newcommand\BZ{{\mathbb Z}}
-\newcommand\BA{{\mathbb A}}
+\newcommand\BZ{{\mathbf Z}}
+\newcommand\BA{{\mathbf A}}
 \newcommand\fa{{\mathfrak a}}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-This theorem is proven in three different genus cases, each of
-which use similar inductive processes. The high genus case is
-proven in Theorem ~\ref{thm:high_generators_relations}. In Theorem
-~\ref{thm:g_1_generators_relations} and Theorem
-~\ref{thm:g_0_generators_relations}, we also give the respective
-genus one and genus zero results after using a similar induction
-process while dealing with more complicated base cases and
-exceptional cases.
-
-\begin{rem}
-The proofs of the main theorems in the low genus cases not only
-obtain bounds on the degrees of the generators and relations, but
-also yield explicit systems of generators and the initial ideal of
-relations. Furthermore, our proof of the high genus case also
-provides an inductive procedure for determining the generators and
-initial ideal of relations for $\halfcan'$ when the halfcanonical
-divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with
-$(\halfcan', 0, X)$ a log spin curve. In fact, such a system of
-generators and relations are known for $\halfcan'$ in many cases,
-as detailed in Neves ~\cite[ Section III.4]{neves:halfcan}.
-\end{rem}
+\todo{Say that this follows immediately from the three theorems for the special cases.}
+
+Note that in the course of the proof of Theorem
+~\ref{thm:g_0_generators_relations} we will not merely obtain
+bounds on the degrees of the generators and relations. In fact, if
+the genus $g = 0$ or $g = 1$, the proof yields an explicit system
+of generators and the initial ideal of relations. While in the
+genus $g \geq 2$ case, the proof does not always yield an explicit
+system of generators and relations, if the halfcanonical divisor
+$\halfcan$ can be written as $\halfcan' + \Lambda$ with $(\halfcan',
+0, X)$ a log spin curve, and a system of generators and relations for
+$ \halfcan'$ is known, then our proof provides an inductive
+procedure for determining the generators and initial ideal of
+relations for $\halfcan$. In fact, such a system of generators and
+relations are known for $\halfcan'$ in many cases, as detailed in
+Neves ~\cite[ Section III.4]{neves:halfcan}.
 
@@
 Theorem ~\ref{thm:general_generators_relations}. The idea of the
-proof will be to induct on the order and number of hyperelliptic-
-fixed points. To this end, we first review important background in
-Section ~\ref{sec:background}. Then, we develop various inductive
-tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
+proof will be to induct on the order and number of elliptic points.
+To this end, we first review important background in Section
+~\ref{sec:background}. Then, in Section ~\ref{sec:induction}, we
+develop various inductive tools. In Sections ~\ref{sec:g_high},
 ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem
-~\ref{thm:general_generators_relations} in the high genus, genus
-one, and genus zero cases respectively. Finally, in Section
+~\ref{thm:general_generators_relations} in the cases that the genus
+$g \geq 2, g = 1$ and $g = 0$ respectively. Finally, in Section
 ~\ref{sec:further-questions}, we pose several questions for future
@@
 
+\iffalse{
 However, before we can answer these general Lemmata, it is useful
@@
 %\end{rem}
-
 \begin{lem}
@@
 \end{rem}
-
 With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
+}\fi
 
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 \label{lem:deg1-sat-ind}
-Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $\halfcan'$
+Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $\halfcan'$
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbf{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
 $u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
@@
 in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbb{N}$ such that
+for some $\alpha,\beta \in \mathbf{N}$ such that
 \begin{equation}
@@
 	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbf{
 	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
@@
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
-\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
-	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
-	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
-generates $I'$.
+%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
+%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
+%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
+%generates $I'$.
 \end{enumerate}
@@
 Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
-Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
-Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.
-Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.
-Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then
+Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose there is a $k$-basis $S$ for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
+Let $I$ and $I'$ be the ideals of relations of $R_{\halfcan'}$ and $R_{\halfcan}$, for the given generating sets.  
+Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $I' k[x_1, \ldots, x_m, y_1, \ldots, y_n]$.
+Moreover, suppose there is some ordering $\prec$ such that if $T\prec S\prec k[x_1, \ldots, x_n]$ (that is, all elements of $T$ precede elements of $S$ which proceed monomials only in the $x_i$s).
+, then
 \begin{align*}
@@
 \end{align*}
-Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Gr\"{o}bner Basis with an initial term for each element of $T$.
 \end{lem}
 \begin{proof}
-
+Suppose monomial $f\in T$ has a pole order $a$ at $P$.
+Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
+This demonstrates that
+\begin{align*}
+	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
+Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
+\begin{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
 \end{proof}
@@
 our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
-\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
 
@@
 degrees less than $d_i$ must have 
-\todo{Aaron: at what point is the following order taken at?}
 \[
@@
 \lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$, 
-with $d_j = 1 =d_{{\lfloor \frac{a}{b} \rfloor}}$ and $b<d_{\lfloor \frac{\alpha}{\beta} 
+with $d_j = 1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
 \rfloor + 1}$.
@@
 %\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbb{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
+%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
 %\end{cor}
@@
 %any point $P$ occurring in a stacky divisor of $\sx$ must have 
-%coefficient lying in $\mathbb{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+%coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
 %s appearing in the characteristic of $(\sx,\Delta)$).
@@
 \begin{defn}
-\label{}
-If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
-
-\begin{defn}
 \label{defn:admissible}
-Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
+Let $(\sx', 0, L'),(\sx, 0, L)$ be log spin
 curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
@@
 \begin{enumerate}
-	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i'})
+	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-ord_{Q_i}(y_{i, e_i'})
 		= \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] If every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}
-^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
+	\item[(Ad-ii)] Either $e_j' = 3$ for all $j \in \{1, \ldots, r\}$
+		or any generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
+		\begin{align*}
+			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
 		\end{align*}
@@
 
+\iffalse{
 \begin{lem}\label{lem:n-3s-admissible}
@@
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
-Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
-^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}(y_i)}= 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
 
@@
 \end{proof}
+}\fi
 
@@
 \begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) < \deg(z) \subhalf{e_i'}
+	-\ord_{Q_i}(z) < \deg(z) \subhalf{e_i'}
 \end{align*}
@@
 as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}
-^{\halfcan_X'}(z)$ is an integer, 
+e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}(z)$ is an integer, 
 we must have
@@
 \begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
+	-\ord_{Q_i}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
 	\deg(z) \subhalf{e_i'} - \frac{1}{e_i'}.
@@
 Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
-space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either $e_1' = \cdots = e_r' = 3$ or $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
+space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and
+$(\sx', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
 R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
@@
 		\begin{align*}
-			-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
+			-ord_{Q_i}(y_{i, e_i}) = \frac{e_i - 1}{2}
 		\end{align*}
@@
 		\begin{align*}
-			\frac{-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
+			\frac{-\ord_{Q_j}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
 \subhalf{
@@
 \begin{proof}
-We will only prove this in the harder case $(\sx, L', J)$ is admissible, as the case $e_1 = \cdots = e_r = 3$ is similar.
-
 Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
@@
 \begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
+	-\ord_{Q_i}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
 	\frac{e_i - 1}{2}
@@
 \begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
+	-\ord_{Q_j}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
 	\subhalf{e_j'} - \frac{1}{e_j'}.
@@
 \begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+	-\ord_{Q_j}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
 	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
@@
 	(a,b) \mapsto \left( \deg\left(y_{i, e_i'}^ay_{i, e_i}^b\right),-
-	\ord_{Q_i}
-^{\halfcan_X'}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
+	\ord_{Q_i}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
 	\begin{pmatrix}
@@
 such that $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$, that
-$y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
+$f := y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
 only if for all $j \in J$ we have
-\begin{align}
-\label{eqn:order-degree}
-	-\ord_{Q_j}
-^{\halfcan_X'}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
-\end{align}
-
-\noindent
-We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in three cases, depending on whether $j \notin \{
+\begin{align*}
+	-\ord_{Q_j}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
+\end{align*}
+
+\noindent
+We now check this in three cases, depending on whether $j \notin \{
 i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
@@
 
-Here, $-\ord_{Q_j}
-^{\halfcan_X'}(L) = -\ord_{Q_j}
-^{\halfcan_X'}(L'),$ so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
-^{\halfcan_X'}(z) \leq e_i \subhalf {e_j'} +
+Here, $-\ord_{Q_j}(L) = -\ord_{Q_j}(L'),$ so
+\begin{align*}
+	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z) \leq e_i \subhalf {e_j'} +
 	\deg z \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
@@
 \begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
-^{\halfcan_X'}(z)
+	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z)
 	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
@@
 \begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'}
+	-\ord_{Q_j}(z) \leq \deg z \subhalf{e_j'}
 \end{align*}
@@
 \begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}^{\halfcan_X'}(z) 
+	-\ord_{Q_j}(y_{i, e_i})-\ord_{Q_j}(z) 
 	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
@@
 
-\section{High Genus}
+\section{High genus}
 \label{sec:g_high}
@@
 
-\ssec{Bounds on Generators and Relations in High Genus}
+\ssec{Bounds on Generators and Relations in high genus}
 
@@
 
-\ssec{Main Theorem for High Genus}
+\ssec{Main theorem for high genus}
 \label{ssec:main_g_high}
@@
 Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
-$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
+$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception- 1-5}. The other cases are similar.
 
@@
 \begin{example}
-\label{eg:exception-1-e}
+\label{eg:exception- 1-e}
 Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
@@
 First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+By Example ~\ref{eg:exception- 1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
 While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
@@
 and not one of the exceptional cases in Table
-~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
-\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
-trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
-only consider when $r \geq 3$.
+~\ref{table:g-0-exceptional}.
 

### 2015-06-25 stacky_write_up/spin_cring.tex
reinstate mathbb, iffalse -> %

@@
 \newcommand\sssec{\subsubsection}
-\newcommand\bh{{\mathbf H}}
+\newcommand\bh{{\mathbb H}}
 \newcommand\bO{{\mathbf O}}
 \newcommand\CC{{\mathcal C}}
-\newcommand\BN{{\mathbf N}}
-\newcommand\BC{{\mathbf C}}
-\newcommand\BF{{\mathbf F}}
-\newcommand\BR{{\mathbf R}}
-\newcommand\BQ{{\mathbf Q}}
-\newcommand\BP{{\mathbf P}}
-\newcommand\BBZ{{\mathbf Z}}
+\newcommand\BN{{\mathbb N}}
+\newcommand\BC{{\mathbb C}}
+\newcommand\BF{{\mathbb F}}
+\newcommand\BR{{\mathbb R}}
+\newcommand\BQ{{\mathbb Q}}
+\newcommand\BP{{\mathbb P}}
+\newcommand\BBZ{{\mathbb Z}}
 \newcommand\uR{\underline{R}}
@@
 \newcommand\uCF{\underline{{\mathcal F}}}
-\newcommand\BZ{{\mathbf Z}}
-\newcommand\BA{{\mathbf A}}
+\newcommand\BZ{{\mathbb Z}}
+\newcommand\BA{{\mathbb A}}
 \newcommand\fa{{\mathfrak a}}
@@
 
-\iffalse{
-However, before we can answer these general Lemmata, it is useful
-to prove a nice result about minimal generation of ideals of
-relations.
-
-\todo{Include one of the following, if the first one, include a 
-remark for quotient}
+%However, before we can answer these general Lemmata, it is useful
+%to prove a nice result about minimal generation of ideals of
+%relations.
+%
+%\todo{Include one of the following, if the first one, include a 
+%remark for quotient}
 
@@
 %\end{rem}
-\begin{lem}
-\label{lem:minimal_quadratic}
-Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-generated in degree 1 that are equipped with monomial ordering $\prec$.
-Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
-\[
-	\begin{tikzcd}
-	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	\end{tikzcd}
-\]
-Further suppose that $I'$ is generated over $I$ by elements $f_1,
-\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
-is of the form $y_i$. Then, the elements $f_i$ determine minimal
-generators for $I'$ over $I$.
-\end{lem}
-
-\begin{proof}
-Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-degree 1. Then,
-\[
-	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-\]
-\[
-	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-\]
-
-\noindent
-determines map of rings, no longer necessarily graded. 
-By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Gr\"{o}bner basis,
-\[
-	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-\]
-so
-\[
-	\dim_k (I'/I)_2=j.
-\]
-This implies any set of
-generators for $I$ must have at least $j$ elements. Since $f_1,
-\ldots, f_j$ is such a set, it is minimal.
-\end{proof}
-
-\begin{rem}
-\label{rem:minimal_quadratic_trivial_case}
-It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
-case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
-are $k$-minimal generators for $I'$ (over the trivial base vector
-space). 
-\end{rem}
-With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
-}\fi
+%\begin{lem}
+%\label{lem:minimal_quadratic}
+%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
+%generated in degree 1 that are equipped with monomial ordering $\prec$.
+%Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
+%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
+%\[
+	%\begin{tikzcd}
+	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
+	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
+	%\end{tikzcd}
+%\]
+%Further suppose that $I'$ is generated over $I$ by elements $f_1,
+%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
+%is of the form $y_i$. Then, the elements $f_i$ determine minimal
+%generators for $I'$ over $I$.
+%\end{lem}
+%
+%\begin{proof}
+%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
+%degree 1. Then,
+%\[
+	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
+%\]
+%\[
+	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
+%\]
+%
+%
+%\noindent
+%determines map of rings, no longer necessarily graded. 
+%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Gr\"{o}bner basis,
+%\[
+	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
+%\]
+%so
+%\[
+	%\dim_k (I'/I)_2=j.
+%\]
+%This implies any set of
+%generators for $I$ must have at least $j$ elements. Since $f_1,
+%\ldots, f_j$ is such a set, it is minimal.
+%\end{proof}
+%
+%\begin{rem}
+%\label{rem:minimal_quadratic_trivial_case}
+%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
+%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
+%are $k$-minimal generators for $I'$ (over the trivial base vector
+%space). 
+%\end{rem}
+%With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
 
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \mathbf{Q}$ (for $\alpha\in \mathbf{Z}, \beta\in \mathbf{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha\in \mathbf{Z}, \beta\in \mathbf{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
@@
 \label{lem:deg1-sat-ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $\halfcan'$
+Let $X$ be a genus $g$ curve with a $\BQ$-divisor $\halfcan'$
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
@@
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
+Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
 Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose there is a $k$-basis $S$ for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
@@
 %\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
+%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\BQ$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
 %\end{cor}
@@
 
-\iffalse{
-\begin{lem}\label{lem:n-3s-admissible}
-Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
+%\begin{lem}\label{lem:n-3s-admissible}
+%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
 Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$.
 Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
-\end{lem}
-\begin{proof}
-To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+%\end{lem}
+%\begin{proof}
+%To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
 Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
-^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
-
- follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
-\begin{itemize}
-\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
-\end{itemize}
-\end{proof}
-}\fi
+%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+%
+ %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
+%\begin{itemize}
+%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
+%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\end{itemize}
+%\end{proof}
 
@@
 
-\iffalse
-The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u, y_5, y_7]/(y_5)^3 - uy_7^2.$ 
-\fi
+%The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u, y_5, y_7]/(y_5)^3 - uy_7^2.$
 
@@
 \end{center}
-\iffalse
-\begin{rem}
-\label{rem:g-1-exceptional-e}
-Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
-Theorem ~\ref{thm:ram_order_ind}.
-\end{rem}
-\fi
+
+%\begin{rem}
+%\label{rem:g-1-exceptional-e}
+%Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
+%Theorem ~\ref{thm:ram_order_ind}.
+%\end{rem}
 
@@
 
-\iffalse
-\begin{example}
-\label{eg:exceptional-1-0}
-In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
-\end{example}
-
-\begin{example}
-\label{eg:exceptional- 1-3}
-Let $L = P - Q + \frac{1}{3}R$.
+%\begin{example}
+%\label{eg:exceptional-1-0}
+%In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
+%\end{example}
+%
+%\begin{example}
+%\label{eg:exceptional- 1-3}
+%Let $L = P - Q + \frac{1}{3}R$.
 Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$.
 For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-We find that $R_L \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
-\end{example}
-
-\begin{example}
-\label{eg:exception-1-e}
-Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
-Furthermore, $\deg u = 2, \deg y_i = i$.
-\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
-\end{example}
-\fi
+%We find that $R_L \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
+%\end{example}
+%
+%
+%\begin{example}
+%\label{eg:exception-1-e}
+%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+%Furthermore, $\deg u = 2, \deg y_i = i$.
+%\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
+%\end{example}
 

### 2015-06-25 stacky_write_up/spin_cring.tex
remove minimal_quadratic refs

@@
 
-In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
-~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
-basis defined above is minimal.
-\todo{What about $\frac{\alpha}{\beta} > 1$?}
+%In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
+%~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
+%basis defined above is minimal.
+%\todo{What about $\frac{\alpha}{\beta} > 1$?}
 \end{proof}
@@
 		\end{align*}
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
-		generate $I$.
+	%\item[(c)] Any set of minimal generators for $I'$ together with 
+		%any set of relations with leading terms as in (b) minimally 
+		%generate $I$.
 \end{enumerate}
@@
 
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
+%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
 \end{proof}
@@
 
-Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
+%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
 \end{proof}
@@
 
-Next, note that the minimal generators of $I'$ together with the
-new generators of $I$ given in (c) have independent initial terms
-by construction, and therefore are minimal by Lemma
-~\ref{lem:minimal_quadratic}.
-
-Finally, to check (e), we will first show that $(\sx,J)$ is
+%Next, note that the minimal generators of $I'$ together with the
+%new generators of $I$ given in (c) have independent initial terms
+%by construction, and therefore are minimal by Lemma
+%~\ref{lem:minimal_quadratic}.
+
+Finally, to check (e), we will first show that $(\sx, J)$ is
 admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
-strictly monotonic in the $e_i$ and hence also holds for $(\sx,J)$.
-Finally, if (Ad-iii) holds for $e$ then it holds for $e+2$ by
+strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
+Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
 definition. This is where we use that (Ad-iii) holds for $d > 0$
@@
 with $x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$.
-These quadratics must also determine minimal generators for $I$ by
-Lemma ~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to
+%These quadratics must also determine minimal generators for $I$ by
+%Lemma ~\ref{lem:minimal_quadratic}.
+Thus, $R'$ is generated up to
 degree $e = 7$ with relations up to degree $2e = 14$, as desired.

### 2015-06-25 stacky_write_up/spin_cring.tex
editing order ram

--- 2015-06-25 stacky_write_up/spin_cring.tex
@@
 say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
-\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$ if
-$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\delta := \deg \Delta,$ then we
-say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$. A
-{\bf log spin curve} is a triple $(X, \Delta, \halfcan)$ where $(X,\Delta)$
+\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$,
+be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx +
+\Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
+say $\sx$ has \textbf{signature} $(g; e_1, \ldots, e_r;\delta)$. A
+{\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
 and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
@@
 We reserve the notation $\halfcan$ for the halfcanonical divisor
-where $2\halfcan \sim K_\sx + \Delta$.
+where $\halfcan \sim $.
 
@@
 
-\iffalse{
 However, before we can answer these general Lemmata, it is useful
@@
 %\end{rem}
+
 \begin{lem}
@@
 \end{rem}
+
 With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
-}\fi
 
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 \label{lem:deg1-sat-ind}
-Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $\halfcan'$
+Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $\halfcan'$
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbf{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
 $u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
@@
 in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbf{N}$ such that
+for some $\alpha,\beta \in \mathbb{N}$ such that
 \begin{equation}
@@
 	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbf{
+	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
 	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
@@
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
-%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
-%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
-%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
-%generates $I'$.
+\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
+	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
+	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
+generates $I'$.
 \end{enumerate}
@@
 Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
-Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose there is a $k$-basis $S$ for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
-Let $I$ and $I'$ be the ideals of relations of $R_{\halfcan'}$ and $R_{\halfcan}$, for the given generating sets.  
-Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $I' k[x_1, \ldots, x_m, y_1, \ldots, y_n]$.
-Moreover, suppose there is some ordering $\prec$ such that if $T\prec S\prec k[x_1, \ldots, x_n]$ (that is, all elements of $T$ precede elements of $S$ which proceed monomials only in the $x_i$s).
-, then
+Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
+Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.
+Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.
+Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then
 \begin{align*}
@@
 \end{align*}
+Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Gr\"{o}bner Basis with an initial term for each element of $T$.
 \end{lem}
 \begin{proof}
-Suppose monomial $f\in T$ has a pole order $a$ at $P$.
-Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
-This demonstrates that
-\begin{align*}
-	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
-Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
+
 \end{proof}
@@
 
-\iffalse{
 \begin{lem}\label{lem:n-3s-admissible}
@@
 \end{proof}
-}\fi
 
@@
 
+\begin{rem}
+\label{rem:three-cases}
+For the purposes of our induction, we will often be adding in a single 
+stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
+curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
+\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases:
+\begin{enumerate}
+	\item $g = 0, \delta = 0, $ and $r \geq 5$
+	\item $g = 1, \delta = 0,$ and $ r \geq 2$
+	\item $g \geq 2, \delta$ arbitrary, and $r \geq 1$.
+\end{enumerate}
+\end{rem}
+
 \begin{thm}
@@
 Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
-space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either $e_1' = \cdots = e_r' = 3$ or $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
-R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
+space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either 
+\begin{enumerate}
+	\item  $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
+	\item or $e_1' = \cdots = e_r' = 3$ and $r \geq 2$ or $g \geq 2$, and let $y_{1, 3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
+\end{enumerate}
+Let
 $(\sx, \Delta, \halfcan)$ be another log spin curve
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
+	\item[(b1)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
 0,
@@
 		generate $R$ over $R'$.
-	\item[(c)] Equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
+	\item[(b2)] If $(\sx',\halfcan',J)$ is not admissible, but $\{e_1,\ldots, e_n\} = \{3\},$ the elements $y_{i, e_i}$ minimally
+		generate $R$ over $R'$.
+	\item[(c1)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
 		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
@@
 		as $z$ ranges over all generators of $R$.
+	\item[(c2)]  If $(\sx',\halfcan',J)$ is not admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
+		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
+		block order. Let $R = k[y, x]/I.$ Then,
+		\begin{align*}
+			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
+			\neq y_{i, e_i}, y_{i, e_i'} \rangle
+		\end{align*}
+		as $z$ ranges over all generators of $R$.
+
 	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
@@
 
-All such base cases satisfy all of the hypotheses of Theorem
-~\ref{thm:ram_order_ind} and their corresponding $R' := R(\sx',
-\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
-$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
-degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
-from induction using Theorem ~\ref{thm:ram_order_ind}(b) and
-Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
-\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
-It also follows from induction on Theorem ~\ref{thm:ram_order_ind}(c)
-and ~\ref{cor:raise-stacky-order} that the relations are generated
-up to degree $2e$.
+All such base cases satisfy all of the hypotheses of
+Theorem ~\ref{thm:ram_order_ind} and their corresponding $R' :=
+R(\sx', \Delta, \halfcan')$ are generated, as $k$-algebras, up
+to degree $e' := \max(5, e_1', \ldots, e_r')$ with relations
+generated up to degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}.
+It follows from Theorem ~\ref{thm:ram_order_ind}(b) that $R :=
+R(\sx, \Delta, \halfcan)$ is generated up to degree $e := \max(5,
+e_1, \ldots, e_r)$. It follows from Theorem ~\ref{thm:ram_order_ind}
+(d) that the relations are generated up to degree $2e$.
 \end{proof}

### 2015-06-25 stacky_write_up/spin_cring.tex
jellin 3 induction

@@
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
-Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
+Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
 The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
@@
 
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
+In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally \todo{Aaron: Should the word minimally be removed here?} generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
@@
 		\end{align*}
-	\item[(c)] Any set of minimal generators for $I'$ together with 
-		any set of relations with leading terms as in (b) minimally 
+	\item[(c)] Any set of generators for $I'$ together with 
+		any set of relations with leading terms as in (b) 
 		generate $I$.
@@
 \begin{enumerate}
-	\item[(Ad-i)] $\deg y_{e_i'} = e_i'$ and $-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i'})
-		= \frac{e_i'- 1}{2}$.
-	\item[(Ad-ii)] If every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
+	\item[(Ad-i)] First, 
+	\begin{align*}
+	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
+		= \frac{e_i'- 1}{2}.
+	\end{align*}
+		\item[(Ad-ii)] Second, every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
 		\begin{align*}
@@
 		\end{align*}
-	\item[(Ad-iii)] The minimality condition
+	\item[(Ad-iii)] Third, we have
 		\begin{align*}
@@
 		\end{align*}
-		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
 		where
@@
 %\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (Ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 %\end{itemize}
@@
 \label{thm:ram_order_ind}
-Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
-space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either 
+Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
+space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$ and either 
 \begin{enumerate}
 	\item  $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
-	\item or $e_1' = \cdots = e_r' = 3$ and $r \geq 2$ or $g \geq 2$, and let $y_{1, 3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
+	\item or $\sigma$ is one of the signatures described in Remark ~\ref{rem:three-cases}, with $y_{1, 3} = y_{2,3} = \ldots, y_{r,3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
 \end{enumerate}
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b1)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
+	\item[(b)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
 0,
@@
 		generate $R$ over $R'$.
-	\item[(b2)] If $(\sx',\halfcan',J)$ is not admissible, but $\{e_1,\ldots, e_n\} = \{3\},$ the elements $y_{i, e_i}$ minimally
-		generate $R$ over $R'$.
-	\item[(c1)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
+	\item[(c)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
 		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
@@
 		as $z$ ranges over all generators of $R$.
-	\item[(c2)]  If $(\sx',\halfcan',J)$ is not admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
-		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
-		block order. Let $R = k[y, x]/I.$ Then,
-		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
-			\neq y_{i, e_i}, y_{i, e_i'} \rangle
-		\end{align*}
-		as $z$ ranges over all generators of $R$.
-
-	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
-		products of two monomials and that for all $i \in J$, we have $e
-		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
-		minimal generators for $I'$ together with any set of relations 
-as in 
-		part (c) minimally generate $I$.
-	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
+	\item[(d)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
 \end{enumerate}
@@
 \begin{proof}
-We will only prove this in the harder case $(\sx, L', J)$ is admissible, as the case $e_1 = \cdots = e_r = 3$ is similar.
-
-Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log spin curves in 
+We will only prove this in the case (1), that $(\sx', L', J)$ is admissible, as the case (2) that $\sigma$ is as in Remark ~\ref{rem:three-cases} is completely analogous.
+
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be the two log spin curves in 
 question, with coarse spaces $X = X'$.
-\todo{possibly generalize these to arbitrary log  $\Delta \neq 0$ spin curves}
 Define
@@
 \begin{align*}
-	H^0(\sx', e_iL'-E_i + Q_j) \rightarrow H^0(\sx, e_iL - E_i) \subset 
+	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subset 
 H^0(\sx, e_iL).
-\end{align*}\todo{Peter: should be $Q_i$?}
+\end{align*}
 
@@
 
-Next, define $R_0 = R'$ and inductively define 
+Next, define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
 $$R_i = \begin{cases}
@@
 
-Finally, to check (e), we will first show that $(\sx, J)$ is
+Finally, to check (d), we will first show that $(\sx, J)$ is
 admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
@@
 \label{cor:raise-stacky-order}
-Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ with $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
+Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three cases}.
+Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
 so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}.

### 2015-06-25 stacky_write_up/spin_cring.tex
removed minimality and changed admissibility notation to a tripple from a pair

@@
 
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',J)$
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
 to be {\bf admissible} if the $R'$ admits a presentation
-\todo{We should incorporate dependence on $L$ into the definition of admissible.}
 \begin{align*}
@@
 \label{lem:admissible_subset}
-If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
-then $(\sx', W)$ is also admissible.
+If $(\sx',\Delta,L')$ is a log spin curve, $(\sx',L', J)$ is admissible and $W \subset J$ is any subset,
+then $(\sx', L', W)$ is also admissible.
 \end{lem}
@@
 \begin{enumerate}
-	\item  $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
+	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
 	\item or $\sigma$ is one of the signatures described in Remark ~\ref{rem:three-cases}, with $y_{1, 3} = y_{2,3} = \ldots, y_{r,3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
@@
 		as $z$ ranges over all generators of $R$.
-	\item[(d)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
+	\item[(d)] The triple $(\sx, \halfcan', J)$ is admissible.
 \end{enumerate}
@@
 \begin{proof}
-We will only prove this in the case (1), that $(\sx', L', J)$ is admissible, as the case (2) that $\sigma$ is as in Remark ~\ref{rem:three-cases} is completely analogous.
+We will only prove this in the case (1), that $(\sx', \halfcan', J)$ is admissible, as the case (2) that $\sigma$ is as in Remark ~\ref{rem:three-cases} is completely analogous.
 
@@
 
-Finally, to check (d), we will first show that $(\sx, J)$ is
-admissible. We know (Ad-i) is satisfied by part (b), taking the $y_{
+Finally, we check (d), by checking $(Ad-i),(Ad-ii)$ and $(Ad-iii)$ are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
@@
 and not just for $d = 0$.
-
-Finally, if $(\sx , J)$ is admissible then so is $(\sx, W)$ for any
-$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
 \end{proof}
@@
 For $t \leq i \leq r$.
-Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g;e_1, \ldots e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
+Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g; e_1, \ldots.
+e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
 $J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
 
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, L_i, J_i)$ is admissible.
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
 
 Since $(*_0)$ holds by assumption, by induction on $i$, it suffices to show that if $(*_i)$ holds then so does $(*_{i+1}).$ 
-Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, L_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
+Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
 Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
@@
 
-In this case, we claim $(\sx',L',\{1\})$ is admissible. Indeed, (Ad-
-i) holds by part (a) of Lemmas
+In this case, we claim the theorem holds for $(\sx',\Delta, L')$. Indeed, the bound on the generators holds by part (a) of Lemmas
 ~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
-(Ad-ii) holds by part (b) of Lemmas
-~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
-and (Ad-iii) holds as $5\deg L \geq 5(g-1)> 2g-1.$ Therefore, by
-Lemma ~\ref{lem:n-3s-admissible} , Any triple of the form $(\sx', L',
-\{1,\ldots, r\})$ is admissible, with $e_1 = \cdots = e_r = 3$.
-Hence, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
+and the bound on the relations holds by part (b) of Lemmas
+~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind}.
+Therefore, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
 holds for all log spin curves $(\sx, L, J)$. 
@@
 $$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx',\{3,3\})$ is admissible.
+and that $(\sx', \halfcan',\{1,2\})$ is admissible.
 
@@
 
-We next check $(\sx',\{1,2\})$ is admissible.
+We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
 We clearly have two generators $x_3, y_3$ in degree 3 with a pole of order $\frac{3- 1}{2}$ by construction.
@@
 
-Note that $L'$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base- 1-33}.
+Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base- 1-33}.
 
@@
 \noindent
-is generated as a $k$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has minimal relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
+is generated as a $k$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
 finite list of exceptional cases, as listed in Table
@@
 First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
 While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
@@
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that $(\sx', \{3,3\})$ is admissible and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
-Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i,$ the pair $(\sx',\{3, \ldots, 3\})$ is admissible.
-Assume for convenience that $e_1 \leq e_2 \leq \cdots \leq e_r$.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i,$ the pair $(\sx', \halfcan', \{1, \ldots, r\})$.
+Assume for convenience  $e_1 \leq e_2 \leq \cdots \leq e_r$.
 Then, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
@@
 perfect field $k$, so that $\sx$ has signature $\sigma = (0; e_1,
-\ldots, e_r; 0)$. Then $R' := R(\sx', \Delta, \halfcan')$ has a
-presentation
-
-is
-generated as a $k$-algebra by elements of degree at most $e = \max(5
+\ldots, e_r; 0)$. Then, $R' := R(\sx', \Delta, \halfcan')$ has a
+presentation generated as a $k$-algebra by elements of degree at most $e = \max(5
 , e_1, \ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
-', J)$ is admissible for the following cases:
+', \halfcan', J)$ is admissible for the following cases:
 
@@
 they satisfy (Ad-i) and (Ad-ii) and that $in_\prec(I')$ is
-minimally generated by products of two monomials. The procedure for
+generated by products of two monomials. The procedure for
 verifying these are similar to those for the given example.

### 2015-06-26 stacky_write_up/spin_cring.tex
changed ramified to stacky and other edits

@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} subgroup, i.e. a discrete subgroup
+Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
 of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
@@
 $\Gamma$, we sharply bound the degree of the generators and
-relations for $M(\Gamma).$ The case where $M(\Gamma)$ has $M_{2k + 1
-}(\Gamma) = 0$ for all $k \in \BZ$, i.e. when $\Gamma$ has no odd
-weight modular forms, is answered in Voight and Zureick-Brown
-\cite[Chapters 7-9]{vzb:stacky}. This work extends this result to
-all Fuchsian subgroups $\Gamma$. In order to answer this question,
-we translate the seemingly analytic question into the algebraic
+relations for $M(\Gamma).$ In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
+\cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$.
+In order to answer this question, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
 category, using a generalization of the GAGA principle. By
@@
 	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
+	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
 \end{enumerate}
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
-Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
+Then we will explicitly describe elements that minimally generate \todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
 The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
 
-First, let's introduce some notation from O'Dorney.   \todo{cite O'downey}
+First, let's introduce some notation from O'Dorney.  \cite{dorney:canonical}
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha\in \mathbf{Z}, \beta\in \mathbf{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha\in \mathbb{Z}, \beta\in \mathbb{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
@@
 
-O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\mathbf{P}^1$ consisting of at most 2 points in its support, showing that it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
+In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\mathbb{P}^1$ consisting of at most 2 points in its support, showing that it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
 He further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
@@
 The following lemma provides an inductive method to extend
-O'Dorney's result on $\BP^1$ to divisors $D = \sum_i \frac{\alpha_i
+O'Dorney's result \todo{Aaron: Which result?
+If anything, wouldn't this be a strengthening of his bounds from Theorem 8, instead of an extension?
+I guess it is an extension in that it generalizes to higher genus?
+Cite the theorem number you are talking about} on $\BP^1$ to divisors $D = \sum_i \frac{\alpha_i
 }{\beta_i} P_i$ consisting of arbitrarily many points satisfying $H^
-0(X, \lfloor D \rfloor) > 0$, showing that they are generated in
+0(X, \lfloor D \rfloor) > 0$, showing that they \todo{What are generated?} are generated in
 degrees at most $e = \max(\beta_i)$ with relations generated in
@@
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbf{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
-$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
+$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0$ for all $x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
 Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\bar{d}$ with relations generated
 in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbf{N}$ such that
+for some $\alpha,\beta \in \mathbb{N}$ such that
 \begin{equation}
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, both ramified over ramified at $Q_1, \ldots, Q_r$. Suppose
+curves, with the same stacky points $Q_1, \ldots, Q_r$. Suppose
 there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
@@
 %Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
-Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$.
+Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$.
 Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
@@
 so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}.
-Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of ramified points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
+Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
 $$
@@
 \label{sec:g_0}
-We will prove that if $(\sx , 0, \halfcan)$ is a spin curve, so
+We will prove that if $(\sx , \Delta, \halfcan)$ is a log spin curve and
 that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
@@
 5, e_1, \ldots, e_r)$ with relations generated in degree at most $2e
-$, so long as $\sigma$ does not lie in a finite list of exceptions.
+$, so long as $\sigma$ does not lie in the finite list given in Table ~\ref{table:g-0-exceptional}.
 
 There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
- (note that $\delta$ must be odd or zero because $\halfcan \in \text
-{ Div } \sx$). In the first case, $\deg \lfloor \halfcan \rfloor
+ (note that $\delta$ must be even because $\halfcan_X \in \di X$ with $2\halfcan_X \sim K_X +\Delta$, where $\deg K_X$ is even) \todo{make a remark about this somewhere in the begining and reference it}.
+In the first case, $\deg \lfloor \halfcan \rfloor
 \geq 0$ so the result directly follows from Lemma
-~\ref{lem:deg1-sat-ind}. When $\delta = 0$, this is not necessarily
-true so the proof is a rather involved induction using Lemma
+~\ref{lem:deg1-sat-ind}. When $\delta = 0$, the proof is a rather involved induction using Lemma
 ~\ref{lem:sat-three-induction-g-0} and Theorem ~\ref{thm:ram_order_ind}.
@@
 \label{ssec:g_0_saturation}
-First, we present the saturations $s$ of the canonical divisor for
+First, we present the saturations of the canonical divisor for
 all cases where $g = 0, \delta = 0$ as defined in Definition
 ~\ref{defn:sat}. The saturation can be computed via the application
-of Riemann-Roch on degrees up to $s$. Exceptional cases are listed
+of Riemann-Roch on degrees up to the saturation. Exceptional cases are listed
 first and generic cases follow.
@@
 \label{ssec:g_0_base}
-Now we have an inductive statement on the number of ramified
+Now we have an inductive statement on the number of stacky
 points in Lemma ~\ref{lem:sat-three-induction-g-0} and
@@
 If $r > 5$, then we can use Lemma
-~\ref{lem:sat-three-induction-g-0} to add ramified points with
+~\ref{lem:sat-three-induction-g-0} to add stacky points with
 stabilizer order $3$ to case (k) of Lemma

### 2015-06-26 stacky_write_up/spin_cring.tex
comments on g0

@@
 	\item background on Gr\"{o}bner bases
-	\item Notation $h^0 = \dim H^0$.
+	\item Notation $h^0 = \dim_k H^0$.
 	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
@@
 I guess it is an extension in that it generalizes to higher genus?
-Cite the theorem number you are talking about} on $\BP^1$ to divisors $D = \sum_i \frac{\alpha_i
+Cite the theorem number you are talking about} on $\BP^1_k$ to divisors $D = \sum_i \frac{\alpha_i
 }{\beta_i} P_i$ consisting of arbitrarily many points satisfying $H^
@@
 X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-same Riemann-Roch arguments from $\BP^1$ in arbitrary genus,
+same Riemann-Roch arguments from $\BP^1_k$ in arbitrary genus,
 allowing a similar inductive result in arbitrary genus $e = \max(
@@
 Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$.
+\todo{Would it make sense to put this lemma before the previous theorem, instead of after the statement?}
 
@@
 
-For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
+For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$ \todo{Where do the $z_i$ live? How many $z_i$ are there, what indexing sets are the product and sums taken over?}
 by construction, so any product of $\prod z_i$ of elements of
@@
 \noindent
-To see these generate $R'$ over $R$, note that $\dim R'_d - \dim_k R
+To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
 _d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
@@
 In this section, we aim to prove the inductive theorem, Theorem
-~\ref{thm:ram_order_ind}. Under fairly general
+~\ref{lem:raise-stacky-order}. Under fairly general
 conditions, this theorem will allow us to show that if Theorem ~\ref
-{thm:ram_order_ind} holds for a curve with signature
+{lem:raise-stacky-order} holds for a curve with signature
 $(0;e_1', \ldots, e_r';0)$ then it also holds for a curve with
@@
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
-Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
+Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
 %^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
@@
 
-\begin{thm}
-\label{thm:ram_order_ind}
+\begin{lem}
+\label{lem:raise-stacky-order}
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
@@
 \end{enumerate}
-\end{thm}
+\end{lem}
 
@@
 Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
-so that $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations}.
+so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:general_generators_relations}.
 Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
@@
 
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Theorem ~\ref{thm:ram_order_ind} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
 
@@
 Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
-Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
+Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
 \end{proof}
@@
 \end{align*}
-is surjective. Indeed, let $'s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
+is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
 Since $K$ is basepoint-free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
@@
 We wish to show $f$ is surjective.
-Note that $\dim \ker f = \dim H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
-Additionally, $\dim V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
-Therefore, $$\dim \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim H^0((n+2)L),$$
+Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
+Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
+Therefore, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L),$$
 again using Riemann-Roch, implying $f$ is surjective.
@@
 First, we deal with the case that $H^0(X,L) \neq 0$. 
-Then, since $X \not \cong \BP^1,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
+Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
 Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fi xed.
@@
 \end{cases}$$
-there exist $'s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $'s_1g + s_2h = f \bmod J_{L,d}.$
+there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
 \end{lem}
 \begin{proof}
-Choose $'s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
+Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
 By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
@@
 \begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $'s_1g+s_2h \in I_{L,d}'$. 
+Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
 Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fi xed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
 
@@
 
-Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Theorem ~\ref{thm:ram_order_ind}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
+Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
 \end{example}
@@
 %Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
-%Theorem ~\ref{thm:ram_order_ind}.
+%Lemma ~\ref{lem:raise-stacky-order}.
 %\end{rem}
@@
 %\label{eg:exception-1-e}
-%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Theorem ~\ref{thm:ram_order_ind} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Lemma ~\ref{lem:raise-stacky-order} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
 %Furthermore, $\deg u = 2, \deg y_i = i$.
@@
 First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
-While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Theorem ~\ref{thm:ram_order_ind}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
+By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
+While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
 Therefore, the Theorem holds for $L' = P - Q + \frac{3}{7}P_2$.
-Then, applying Theorem ~\ref{thm:ram_order_ind} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P - Q + \frac{e- 1}{2e}P_1$.
+Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P - Q + \frac{e- 1}{2e}P_1$.
 
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
 Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i,$ the pair $(\sx', \halfcan', \{1, \ldots, r\})$.
@@
 We will prove that if $(\sx , \Delta, \halfcan)$ is a log spin curve and
-that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
+$\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
 then $R(\sx , \Delta, L)$ is generated in degree at most $e := \max(
@@
 There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
- (note that $\delta$ must be even because $\halfcan_X \in \di X$ with $2\halfcan_X \sim K_X +\Delta$, where $\deg K_X$ is even) \todo{make a remark about this somewhere in the begining and reference it}.
-In the first case, $\deg \lfloor \halfcan \rfloor
+ (note that $\delta$ must be even because $\halfcan_X \in \di X$ with $2\halfcan_X \sim K_X +\Delta$, where $\deg K_X$ is even).
+\todo{make a remark about this somewhere in the begining and reference it} In the first case, $\deg \lfloor \halfcan \rfloor
 \geq 0$ so the result directly follows from Lemma
 ~\ref{lem:deg1-sat-ind}. When $\delta = 0$, the proof is a rather involved induction using Lemma
-~\ref{lem:sat-three-induction-g-0} and Theorem ~\ref{thm:ram_order_ind}.
+~\ref{lem:sat-three-induction-g-0} and Lemma ~\ref{lem:raise-stacky-order}.
 The remainder of this section is dedicated to characterizing the
@@
 
+\begin{rem}
+Since all points are linearly equivalent on $\BP^1_k$, we may assume without loss of generality that $L_X = n \infty$ for some $n \in \BN$ and $K_X = -2 \infty.$ We will use this convention throughout this section.
+\end{rem}
+
 \ssec{Saturation}
@@
 First, we present the saturations of the canonical divisor for
-all cases where $g = 0, \delta = 0$ as defined in Definition
-~\ref{defn:sat}. The saturation can be computed via the application
-of Riemann-Roch on degrees up to the saturation. Exceptional cases are listed
+all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
+~\ref{defn:sat}. The saturation can be computed via applications
+of Riemann-Roch. Exceptional cases are listed
 first and generic cases follow.
@@
 \begin{center}
-\textbf{Table (I)}: Genus 0 saturation
+\textbf{Table (I)}: Genus 0 saturation \todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
 \end{center}
@@
 \todo{transition}
-Here we describe induction of raising degrees from Theorem ~\ref{thm:ram_order_ind}
+Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}
 \todo{fill out}
@@
 an inductive statement on stabilizer orders in Theorem
-~\ref{thm:ram_order_ind}. After verifying that explicit pairs
-$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
-particular choices of $J$ are admissible, the application of the
-two inductive statements demonstrate that the spin canonical ring
+~\ref{lem:raise-stacky-order}. After verifying that explicit triples
+$(\sx, L, J)$ of stacky curves $\sx$ with particular signatures and
+particular choices of $J$ are admissible, we will use Lemmas ~\ref{lem:raise-stacky-order}, and ~\ref{lem:sat-three-induction-g-0} imply that the spin canonical ring
 $R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
@@
 $\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
-of a finite set of exceptional cases.
+of the list of exceptional cases in Table ~\ref{table:g-0-exceptional}.
 
@@
 \label{lem:g_0_admissible_cases}
-Let $(\sx', \Delta, \halfcan')$ be a log spin curve over a
-perfect field $k$, so that $\sx$ has signature $\sigma = (0; e_1,
+Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$ has signature $\sigma = (0; e_1,
 \ldots, e_r; 0)$. Then, $R' := R(\sx', \Delta, \halfcan')$ has a
@@
 , e_1, \ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
-', \halfcan', J)$ is admissible for the following cases:
+', \halfcan', J) =(\sx
+', -\infty + \sum_{i=1}^{r}\subhalf{e_i}P_i, J)$ is admissible for the following cases:
 
@@
 \end{enumerate}
-
-\noindent
-Furthermore, $R'$ satisfies the hypothesis of Theorem ~\ref
-{thm:ram_order_ind}(d), which asserts that for all $i \in J$, $e_i >
+\iffalse
+\noindent
+Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
+{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
 \deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
-(as defined in Theorem ~\ref{thm:ram_order_ind}(c)) then
+(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
 $in_\prec(I')$ is minimally generated by products of two monomials.
+\fi
 \end{lem}
+
+Before proving Lemma ~\ref{lem:g_0_admissible_cases} in general, we check the lemma holds for case (b).
 
@@
 Here we demonstrate, in detail, that case (b) with ($\sigma_2 =
-(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
-We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
+(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
+\frac{3}{7} P_2 + \frac{3}{7} P_3, J_2 = \{3, 4\},$) with distinct points $P_i \neq \infty$,
+satisfies the conditions of Lemma ~\ref{lem:g_0_admissible_cases}.
 We exhibit a (minimal) presentation for $R'$.
 
-Notice that $\deg \lfloor d K_{\sx'} = -d + \lfloor \frac{d}{3}
+Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
 \rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
 
-By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
-and Zureick-Brown \cite{vzb:stacky}),
+By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
 \[
-	H^0 (\sx', \lfloor 21 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
 	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma_2$ has saturation $'s = 5$, as noted in
+\geq 0$. Since $\sigma_2$ has saturation $s = 5$, \todo{Why is there a 's here instead of just s?} as noted in
 Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
-when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24).
+when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24). \todo{Aaron: Isn't $s + 21 = 26$? Shouldn't it be generated up to degree 25, potentially?}
 
@@
 \[
-	\dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
 \]
@@
 so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$.
+x_{7, 2}$ with $x_{i,j} = H^0(\sx',iK_{\sx'})$.
 
@@
 $H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 24$. Note that we can again use Max Noether's theorem
+and $7 < d \leq 24$. \todo{Should this be 25?} Note that we can again use Max Noether's theorem
 (taking saturation into account) to see that
@@
 Furthermore, we can directly see that the relations are given
-in degrees $10$ and $14$. In particular, we have a relation
-of the form
+in degrees $10$ and $14$. In particular, we have relations
+\begin{align*}
+	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} &= 0 & \text{ in degree $10$ and } \\
+	b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 &= 0 & \text{ in degree $14.$ }
+\end{align*}
+
+Let $I$ be the ideal generated by these relations in
+$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
+$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$), the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$.
+We can definitely make this hold if we set up the variables in the right way, but I'm not sure if it's always true.}
 \[
-	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0
+	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
 \]
 
-\noindent
-in degree $10$ and a relation of the form
-\[
-	a_1 x_{3, 1}^3 x_{5, 1} + a_2 x_{7, 1}^2 + a_3 x_{7, 1} x_{7, 2} + a_4 x_{7, 2}^2 = 0
-\]
-
-\noindent
-in degree $14$.
-
-Let $I$ be the ideal generated by these relations in
-$k[x_{7, 1}, x_{7, 2}, x{5, 1}, x_{3, 1}]$. Under grlex with
-$x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$,
-the initial ideal of $I$ is
-\[
-	in_\prec(I) = < x_{5, 1}^2, x_{7, 1}^2 >
-\]
-
 To demonstrate that these two relations generate all 
-relations, we show that $\dim (R')_d = \dim
-(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d$ for all degrees
+relations, we show that $\dim_k (R')_d = \dim_k
+(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / in_\prec(I))_d$ for all degrees
 $d \geq 0$. In particular,
@@
 \begin{align*}
-	\dim (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
-	\dim (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
-	&= \dim (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / < x_{5, 1}^2,
-	x_{7, 1}^2 >
-\end{align*}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim (R')_d = \dim (k[x_{3, 1},
-x_{5, 1}, x_{7, 1}, x_{7, 2}] / < x_{5, 1}^2,	x_{7, 1}^2 >$ can
+	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
+	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,
+	x_{7, 1}^2 \rangle
+\end{align*}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{3, 1},
+x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,	x_{7, 1}^2 \rangle$ can
 be checked by looking at the $k$-basis at each degree $d$.
@@
 initial ideal $in_\prec(I)$ generated by quadratics under grlex
-with $x_{i, j} \prec x_{k, l}$ if $i > j$ or $i = j$ and $j < l$.
+with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$
 %These quadratics must also determine minimal generators for $I$ by
@@
 Thus, $R'$ is generated up to
-degree $e = 7$ with relations up to degree $2e = 14$, as desired.
+degree $e = 7$ with relations up to degree $2e = 14$, as desired.s
+\iffalse
 We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
 since $e_i = 9 > e$ for all $i \in J$.
-
-Admissibility is the remaining condition to check. We can assume
+\fi
+
+Admissibility is the remaining condition to check. By relabelling the variables if necessary, we can assume
 that $x_{7, 1}$ corresponds to the generator with maximal pole order
 at $P_2$ and $x_{7, 2}$ correspond to the generator with maximal
-pole order at $P_3$ (relabel otherwise). Use the presentation given
+pole order at $P_3$.
+\todo{There is actually a small problem here, which needs to be fixed earlier.
+I think in order to satisfy admissibility, you will actually have to choose $x_{7,i}$ from the beginning to satisfy these constraints, as this will not generically be true.
+Just make sure to put these constraints on the poles when you define $x_{7,i}$} Use the presentation given
 above with $y _{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
@@
 $-ord_{P_2}(z)$, $-ord_{P_3}(z))$ may be chosen to be $(1, 1, 1)$,
-$(1, 2, 2)$, $(2, 3, 2)$, and $(2, 2, 3)$ for $x_{3, 1}, x_{5, 1},
+$(1, 2, 2)$, $(2, 3, 2)$, and $(2, 2, 3)$ for $z = x_{3, 1}, x_{5, 1},
 x_{7, 1}, x_{7, 2}$ respectively).
@@
 $i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $'s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
+0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
 Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
@@
 
-\begin{proof}
+\begin{proof}[Proof of Lemma ~\ref{lem:g_0_admissible_cases}]
 For the remaining cases, we can use a similar method to the one
@@
 
-The following table demonstrates that $R(\sx', \Delta, L')$ is
+The following table demonstrates that $R(\sx', 0, L')$ is
 generated as a $k$-algebra by elements of degree at most $e$
@@
 	\hline
-	Case & Generator Degrees & Degrees of Minimal Relations & $e$\\
+	Case & Generator Degrees & Degrees of Relations & $e$\\
 	\hline
@@
 
-Now we can induct on cases (a)-(k) of ~\ref{lem:g_0_admissible_cases}
+Now we can induct on cases (a)-(k) of Lemma ~\ref{lem:g_0_admissible_cases}
 to obtain bounds on the minimal generator and relation degrees for
-canonical rings of curves in the genus 0 case.
-
-Through the application of two processes of induction, by adding 
-points via Lemma ~\ref{lem:sat-three-induction-g-0} and by raising
-stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
+canonical rings of genus 0 curves. This process will be carried out in Subsection ~\ref{ssec:g-0-main}.
+
+\iffalse
+Through the application of two inductively adding 
+points via Lemma ~\ref{lem:sat-three-induction-g-0} and inductively raising
+stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
 we obtain Theorem ~\ref{thm:g_0_generators_relations} for any
@@
 covered by induction.
+\fi
 
@@
 \label{ssec:g-0-exceptional}
-First, we describe the cases that would not be covered by induction.
-Here we present the explicit generators and relations of the remaining
+In this subsection, we describe the cases that would not be covered by induction.
+We present the explicit generators and relations for the remaining
 cases given by signatures in the finite set
@@
 \noindent
-and in particular describe the only exceptions to the $e$ and $2e$
-bounds on the generator degree and relation degree, respectively,
-in the genus 0 case.
+and in particular describe the only exceptions to Theorem ~\ref{thm:main}
+in the case $g = 0$.
 
@@
 	\hline
-	Signature & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	Signature & Generator Degrees & Degrees of Relations & $e$ \\
 	\hline
@@
 exceptional cases, apart from $(0; 3, 5, 7; 0)$, corresponds to a
-signature with non-generic saturation (i.e. saturation not equal to
-3, 5, or 9 as seen in the table in Subsection
-~\ref{ssec:g_0_saturation}). Exceptional saturation can be viewed as
-``forcing'' generators (and thus relations) in higher degrees than
-in the generic case.
+signature with saturation not equal to
+3, 5, or 9. as seen in the table in Subsection
+~\ref{ssec:g_0_saturation}. Heuristically, these exceptional saturations can be viewed as
+``forcing'' generators (and thus relations) to lie in higher degrees than
+expected.
 \end{rem}
@@
 so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
-If $g = 0$, then the canonical ring
+Then, the canonical ring
 
@@
 \max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
-so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as listed in Table ~\ref{table:g-0-exceptional}.
+so long as $\sigma$ does not lie in the finite list of exceptional
+cases listed in Table ~\ref{table:g-0-exceptional}.
 \end{thm}
@@
 
-Now let us consider the case when $\delta \geq 2$. In any such case,
+First, let us consider the case when $\delta \geq 2$. In any such case,
 $\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
 of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
-the lemma inductively on the classical case with no stacky points
+the Lemma ~\ref{lem:deg1-sat-ind} inductively on the classical case with no stacky points
 to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
@@
 
-Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
+It only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
 Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
-and not one of the exceptional cases in Table
+so that $\sigma \neq \sigma_i$ where $\sigma_i$ is one of the exceptional cases in Table
 ~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
@@
 trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
-only consider when $r \geq 3$.
+only consider the cases with $r \geq 3$.
 
@@
 up to degree $2e$. Furthermore, these cases satisfy all of the
-conditions of Theorem ~\ref{thm:ram_order_ind}.
+conditions of Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 base cases of Lemma ~\ref{lem:g_0_admissible_cases}, all of which
-satisfy the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.
+satisfy the hypotheses of Lemma ~\ref{lem:raise-stacky-order} as well. \todo{Aaron: I think we replace the above paragraph with an application of Corollary ~\ref{cor:raise-stacky-order}.}
 
@@
 All such base cases satisfy all of the hypotheses of Theorem
-~\ref{thm:ram_order_ind} and their corresponding $R' := R(\sx',
+~\ref{lem:raise-stacky-order} and their corresponding $R' := R(\sx',
 \Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
@@
 degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
-from induction using Theorem ~\ref{thm:ram_order_ind}(b) and
+from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
 Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
 \halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
-It also follows from induction on Theorem ~\ref{thm:ram_order_ind}(c)
+It also follows from induction on Lemma ~\ref{lem:raise-stacky-order}(c)
 and ~\ref{cor:raise-stacky-order} that the relations are generated
-up to degree $2e$.
+up to degree $2e$. \todo{What does it mean to induct on the statements of two lemmas? Clarify this please.}
  \end{proof}

### 2015-06-26 stacky_write_up/spin_cring.tex
genus 2 hypothesis for petri
changed sat lemma names

@@
 with multiplication structure corresponding to tensor product of
-sections. Since $\Omega_X$ is ample, $X \cong \proj R$. Petri's
+sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. Petri's
 theorem gives generators and relations for $R(X, K_X)$ showing that
@@
 \begin{lem}
-\label{lem:deg1-sat-ind}
+\label{lem:sat-1}
 Let $X$ be a genus $g$ curve with a $\BQ$-divisor $\halfcan'$
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
+\begin{proof}[Proof of Lemma \ref{lem:sat-1}]
 By
@@
 \begin{lem}
-\label{lem:sat-two-induction-high-genus}
+\label{lem:sat-2}
 Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
@@
 In a fashion analogous to the proof of Lemma 
-~\ref{lem:sat-three-induction-g-0}, we see 
+~\ref{lem:sat-3}, we see 
 the following is a $k$ basis for $R$ over $R'$:
@@
 \begin{lem}
-\label{lem:sat-three-induction-g-0}
+\label{lem:sat-3}
 \todo{Make explicit assumptions on genus.}
@@
 \halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
-\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-two-induction-high-genus}
+\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-2}
  if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
-~\ref{lem:deg1-sat-ind} if $P_i $ is not a basepoint of $L'$. Note,
+~\ref{lem:sat-1} if $P_i $ is not a basepoint of $L'$. Note,
 in the case $P$  is a not basepoint of $\halfcan'$, Equation
@@
 In this case, we claim the theorem holds for $(\sx',\Delta, L')$. Indeed, the bound on the generators holds by part (a) of Lemmas
-~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind},
+~\ref{lem:sat-2} and ~\ref{lem:sat-1},
 and the bound on the relations holds by part (b) of Lemmas
-~\ref{lem:sat-two-induction-high-genus} and ~\ref{lem:deg1-sat-ind}.
+~\ref{lem:sat-2} and ~\ref{lem:sat-1}.
 Therefore, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
@@
 In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fi xed under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:deg1-sat-ind} and Lemma ~\ref{lem:sat-two-induction-high-genus}.
+We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.
 
@@
 We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base- 1-0}.
-\todo{fi x this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:deg1-sat-ind} accommodates it. }
+\todo{fi x this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:sat-1} accommodates it. }
 
@@
 
-First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:deg1-sat-ind}.
+First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1}.
 In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $ with $\ord_P(u) = 0$, as $P$ is not a basepoint of $L'$.
-Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:deg1-sat-ind}, the theorem holds for $L= L'+P$.
-
-Second, if $P$ is a basepoint of $L'$, then the hypotheses of Lemma ~\ref{lem:sat-two-induction-high-genus} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$.
-Therefore, by Lemma ~\ref{lem:sat-two-induction-high-genus}, the theorem holds for $L = L'+P$.
+Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $L= L'+P$.
+
+Second, if $P$ is a basepoint of $L'$, then the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$.
+Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L = L'+P$.
 This shows the theorem holds for $L_X$.
@@
 By induction, it suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i,$ with $e_i$ odd.
-Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by emma ~\ref{lem:deg1-sat-ind}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-two-induction-high-genus}.
+Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by emma ~\ref{lem:sat-1}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
 
@@
 \geq 0$ so the result directly follows from Lemma
-~\ref{lem:deg1-sat-ind}. When $\delta = 0$, the proof is a rather involved induction using Lemma
-~\ref{lem:sat-three-induction-g-0} and Lemma ~\ref{lem:raise-stacky-order}.
+~\ref{lem:sat-1}. When $\delta = 0$, the proof is a rather involved induction using Lemma
+~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}.
 The remainder of this section is dedicated to characterizing the
@@
 Now we have an inductive statement on the number of stacky
-points in Lemma ~\ref{lem:sat-three-induction-g-0} and
+points in Lemma ~\ref{lem:sat-3} and
 an inductive statement on stabilizer orders in Theorem
@@
 $(\sx, L, J)$ of stacky curves $\sx$ with particular signatures and
-particular choices of $J$ are admissible, we will use Lemmas ~\ref{lem:raise-stacky-order}, and ~\ref{lem:sat-three-induction-g-0} imply that the spin canonical ring
+particular choices of $J$ are admissible, we will use Lemmas ~\ref{lem:raise-stacky-order}, and ~\ref{lem:sat-3} imply that the spin canonical ring
 $R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
@@
 Through the application of two inductively adding 
-points via Lemma ~\ref{lem:sat-three-induction-g-0} and inductively raising
+points via Lemma ~\ref{lem:sat-3} and inductively raising
 stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
@@
 $\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
-of Lemma ~\ref{lem:deg1-sat-ind} are satisfied. Thus, we can apply
-the Lemma ~\ref{lem:deg1-sat-ind} inductively on the classical case with no stacky points
+of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can apply
+the Lemma ~\ref{lem:sat-1} inductively on the classical case with no stacky points
 to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
@@
 If $r > 5$, then we can use Lemma
-~\ref{lem:sat-three-induction-g-0} to add stacky points with
+~\ref{lem:sat-3} to add stacky points with
 stabilizer order $3$ to case (k) of Lemma
@@
 clearly satisfies the conditions of Lemma
-~\ref{lem:sat-three-induction-g-0} (recall from Subsection ~\ref
+~\ref{lem:sat-3} (recall from Subsection ~\ref
 {ssec:g_0_saturation} that $\sat(\Eff(\sigma_{11})) = 3$), and the
 immediate consequence of parts (a) and (c) of Lemma
-~\ref{lem:sat-three-induction-g-0} is that any $R(\sx', \Delta,
+~\ref{lem:sat-3} is that any $R(\sx', \Delta,
 \halfcan')$ corresponding to signatures $\sigma'$ with ramification

### 2015-06-26 stacky_write_up/spin_cring.tex
fixed bad refs and some typos

@@
 \begin{thm}
-\label{thm:general_generators_relations}
+\label{thm:main}
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
@@
 provides an inductive procedure for determining the generators and
-initial ideal of relations for $\halfcan'$ when the halfcanonical
+initial ideal of relations for $\halfcan'$ when the half-canonical
 divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with
@@
 The remainder of the paper will be primarily devoted to proving
-Theorem ~\ref{thm:general_generators_relations}. The idea of the
+Theorem ~\ref{thm:main}. The idea of the
 proof will be to induct on the order and number of hyperelliptic-
@@
 ~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem
-~\ref{thm:general_generators_relations} in the high genus, genus
+~\ref{thm:main} in the high genus, genus
 one, and genus zero cases respectively. Finally, in Section
@@
 \subsection{Definitions}
-We reserve the notation $\halfcan$ for the halfcanonical divisor
+We reserve the notation $\halfcan$ for the half-canonical divisor
 where $2\halfcan \sim K_\sx + \Delta$.
@@
 \label{cor:raise-stacky-order}
-Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three cases}.
+Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}.
 Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
-so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:general_generators_relations}.
+so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}.
 Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
@@
 \end{cases}$$
-then Theorem ~\ref{thm:general_generators_relations} holds for $(\sx,\Delta,L)$
+then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$
 \end{cor}
@@
 
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:general_generators_relations} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
 
@@
 By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
-Let $P_1, \ldots, P_6$ be the si x hyperelliptic fi xed points of $X$. 
+Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
 Recall that all spin divisors on $X$ can be written as 
@@
 If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Therefore, applying Lemma ~\ref{lem:n-3s-admissible} $r-2$ times, we see that for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i,$ the pair $(\sx', \halfcan', \{1, \ldots, r\})$.
-Assume for convenience  $e_1 \leq e_2 \leq \cdots \leq e_r$.
+Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Assume for convenience  $e_1 \leq e_2 \leq \cdots \leq e_r$.
 Then, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
@@
 before proving the main theorem in full for all $\delta$ in
-Subsection ~\ref{ssec:g_0_main}.
+Subsection ~\ref{ssec:g-0-main}.
 
@@
 \ssec{Main Theorem for Genus Zero}
-\label{ssec:g_0_main}
+\label{ssec:g-0-main}
 Now we can combine this.

### 2015-06-26 stacky_write_up/spin_cring.tex
rephrased lemma 3.3

--- 2015-06-26 stacky_write_up/spin_cring.tex
@@
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.
-Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose there is a $k$-basis $S$ for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.
-Let $I$ and $I'$ be the ideals of relations of $R_{\halfcan'}$ and $R_{\halfcan}$, for the given generating sets.  
-Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $I' k[x_1, \ldots, x_m, y_1, \ldots, y_n]$.
-Moreover, suppose there is some ordering $\prec$ such that if $T\prec S\prec k[x_1, \ldots, x_n]$ (that is, all elements of $T$ precede elements of $S$ which proceed monomials only in the $x_i$s).
-, then
+Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
+Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such
+\begin{enumerate}
+\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
+\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
+\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
+\begin{align*}
+	& S \\
+	\cup \; &\langle T\rangle \\
+	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+\end{align*}
+\end{enumerate}
+Then 
 \begin{align*}

### 2015-06-26 stacky_write_up/spin_cring.tex
edited some typos

@@
 Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
-Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fi xed.
+Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed .
 In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
@@
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Chosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+Choosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
 
@@
 
-In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fi xed under the hyperelliptic involution.
+In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
 We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.
@@
 The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $P_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
-It is analogous to Example ~\ref{ex:base-377}, and is omittied.
+It is analogous to Example ~\ref{ex:base-377}, and is omitted.
 
@@
 \todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
-Let $\sx$ be a tame, seperably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fi xed points, and $R$ be a point on $\sx$.
+Let $\sx$ be a tame, separably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R$ be a point on $\sx$.
 
@@
 We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base- 1-0}.
-\todo{fi x this to accomodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:sat-1} accommodates it. }
+\todo{fix this to accommodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:sat-1} accommodates it. }
 
@@
 By induction, it suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i,$ with $e_i$ odd.
-Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by emma ~\ref{lem:sat-1}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
+Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
 
@@
 
-Since $\Delta = 0$, we may write $L = L_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fi xed points.
+Since $\Delta = 0$, we may write $L = L_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
 
@@
  (note that $\delta$ must be even because $\halfcan_X \in \di X$ with $2\halfcan_X \sim K_X +\Delta$, where $\deg K_X$ is even).
-\todo{make a remark about this somewhere in the begining and reference it} In the first case, $\deg \lfloor \halfcan \rfloor
+\todo{make a remark about this somewhere in the beginning and reference it} In the first case, $\deg \lfloor \halfcan \rfloor
 \geq 0$ so the result directly follows from Lemma
@@
 $H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 24$. \todo{Should this be 25?} Note that we can again use Max Noether's theorem
+and $7 < d \leq 24$. \todo{Should this be 25?} Note that we can again use Max No ether's theorem
 (taking saturation into account) to see that
@@
 \begin{center}
-\textbf{Table (II)}: Genus 0 noneffective base cases generator/relations
+\textbf{Table (II)}: Genus 0 non-effective base cases generator/relations
 \end{center}
@@
 \begin{center}
-\textbf{Table (III)}: Genus 0 noneffective base cases (Ad-iii)
+\textbf{Table (III)}: Genus 0 non-effective base cases (Ad-iii)
 \end{center}

### 2015-06-26 stacky_write_up/spin_cring.tex
editing raise stacky order

@@
 which use similar inductive processes. The high genus case is
-proven in Theorem ~\ref{thm:high_generators_relations}. In Theorem
-~\ref{thm:g_1_generators_relations} and Theorem
-~\ref{thm:g_0_generators_relations}, we also give the respective
+proven in Theorem ~\ref{thm:g-high-main}. In Theorem
+~\ref{thm:g-1-main} and Theorem
+~\ref{thm:g-0-main}, we also give the respective
 genus one and genus zero results after using a similar induction
@@
 \begin{enumerate}
+	\item Notation for Coarse space
+	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
 	\item Note that this result is independence of base field
@@
 
-Transition words.
 \todo{transition!}
 
-\ssec{Inductive Lemma: Raising stabilizer orders}
+\ssec{Raising Stabilizer Orders}
 \label{ssec:ram_orders}
-In this section, we aim to prove the inductive theorem, Theorem
-~\ref{lem:raise-stacky-order}. Under fairly general
-conditions, this theorem will allow us to show that if Theorem ~\ref
-{lem:raise-stacky-order} holds for a curve with signature
-$(0;e_1', \ldots, e_r';0)$ then it also holds for a curve with
-signature $(0; e_1, \ldots, e_r; 0)$ with $e_i' - e_i \in \{0 , 2\}$.
+In this subsection, we aim to prove Lemma
+~\ref{lem:raise-stacky-order}, whose proof is almost identical to that of \cite[Theorem 8.5.7]{vzb:stacky}. In many cases, Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem 
+~\ref{thm:main}, holds for a curve with signature
+$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta),$ with $e_{k+1}' = \cdots = e_r',$ then Theorem ~\ref{thm:main} also holds for a curve with
+signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta).$ In order to state Lemma
+~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
+
+One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and \cite[Definition 8.5.1]{vzb:stacky} is that in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ However, we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $L_X$ is not necessarily basepoint-free.
+Therefore, we will have to work with orders of zeros of poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
+Hence, we introduce the following notation.
 
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same stacky points $Q_1, \ldots, Q_r$. Suppose
-there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
+curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
 \{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
@@
 \end{defn}
+
+\begin{rem}
+Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+\end{rem}
 
@@
 
+The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}
+
 \begin{lem}
@@
 \label{rem:three-cases}
-For the purposes of our induction, we will often be adding in a single 
+For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
 stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
 curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
-\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases:
+\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
 \begin{enumerate}
-	\item $g = 0, \delta = 0, $ and $r \geq 5$
-	\item $g = 1, \delta = 0,$ and $ r \geq 2$
-	\item $g \geq 2, \delta$ arbitrary, and $r \geq 1$.
+	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
+	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
+	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
 \end{enumerate}
@@
 \ssec{Main Theorem for High Genus}
-\label{ssec:main_g_high}
+\label{ssec:g-high-main}
 
 \begin{thm}
-\label{thm:high_generators_relations}
+\label{thm:g-high-main}
 Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
@@
 \begin{thm}
-\label{thm:g_1_generators_relations}
+\label{thm:g-1-main}
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
@@
 \begin{rem}
-In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g_1_generators_relations}, proof of Theorem ~\ref{thm:g_1_generators_relations} yields an explicit procedure for computing those minimal generators and relations.
+In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
 That, is one can start with the generators and relations for the base cases, and then inductively add in generators and relations, according to the inductive theorems.
@@
 stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
-we obtain Theorem ~\ref{thm:g_0_generators_relations} for any
+we obtain Theorem ~\ref{thm:g-0-main} for any
 log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
@@
 \begin{thm}
-\label{thm:g_0_generators_relations}
+\label{thm:g-0-main}
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,

### 2015-06-26 stacky_write_up/spin_cring.tex
more edits to increasing ramification order

@@
 	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
+	\item Notation for grobner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
 \end{enumerate}
@@
 
+We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an analog of Lemma ~\ref[Theorem 8.5.7]{vzb:stacky}
+
 \begin{lem}
@@
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$ and either 
+space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta).$ Further, assume either 
 \begin{enumerate}
-	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
-	\item or $\sigma$ is one of the signatures described in Remark ~\ref{rem:three-cases}, with $y_{1, 3} = y_{2,3} = \ldots, y_{r,3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
+	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_1,\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' = R_{L'}$ for all $i \in J,$ as in Definition ~\ref{defn:admissible} or
+	\item $\sigma$ is one of the signatures described in cases (1), (2) and (3) of Remark ~\ref{rem:three-cases} and $y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of $\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ for $1 \leq  i \leq r$.
 \end{enumerate}
@@
 $(\sx, \Delta, \halfcan)$ be another log spin curve
-with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
+with coarse space $X$, so that $X \cong X'$ and signature $(g; e_1, \ldots, e_r;
 \delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
+	\item[(b)] The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
 0,
@@
 		generate $R$ over $R'$.
-	\item[(c)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
-		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
-		block order. Let $R = k[y, x]/I.$ Then,
-		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
+	\item[(c)] Endow $k[y] := k[y_{i, e_i}]_{i \in J}$ and $k[x]:=k[x_1,\ldots, x_m]$ with graded monomial orders and give $k[y, x] = k[y] \otimes k[x]$ block order, as defined in \cite[Definition 8.1.1]{vzb:stacky}.
+\todo{Possibly reference definition in this paper instead.} Let $R = k[y, x]/I.$ Then,
+		\begin{align*}
+			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z : z 
 			\neq y_{i, e_i}, y_{i, e_i'} \rangle
@@
 \begin{proof}
-We will only prove this in the case (1), that $(\sx', \halfcan', J)$ is admissible, as the case (2) that $\sigma$ is as in Remark ~\ref{rem:three-cases} is completely analogous.
-
-Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be the two log spin curves in 
-question, with coarse spaces $X = X'$.
+We will only prove this in the case (1), in which $(\sx', \halfcan', J)$ is admissible, as the case (2), in which $\sigma$ is as in Remark ~\ref{rem:three-cases}, is completely analogous.
+
+{\bf Part (a):} 
+Recall from Definition ~\ref{defn:admissible} that
+
+\begin{align*}
+	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i-e_j'\} = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}.
+\end{align*}
+
+\noindent
 Define
-
-\begin{align*}
-	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
-\end{align*}
-
-\noindent
-Define
-\begin{align*}
-	E_i = \sum_{j \in S(i,0)}^{}Q_j
+\begin{align*}
+	E_i = \sum_{j \in S(i,0)}^{}Q_j.
 \end{align*}
@@
 \begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g - 1
-\end{align*}
-
-\noindent
-implying that $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
+	\deg \left( e_i L' - E_i \right) \geq 2g - 1,
+\end{align*}
+
+\noindent
+and so $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
+Riemann Roch.
+Hence, a general element
 \begin{align*}
@@
 	-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
+^{\halfcan_X'}(y_{i, e_i}) = \left\lfloor e_i \subhalf {e_i'} \right\rfloor + 1 =
 	\frac{e_i - 1}{2}
@@
 We next show $y_{i, e_i}$ also satisfies the second part of the
-claim of $(a),$ by considering separately the cases of whether $j
+claim of $(a),$ by considering separately the cases in which $j
 \in S(i, 0),$ and $j \notin S(i,0)$.
 
-If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i, e_i} \in H^0
+If $j \in S(i,0)$, since $E_i \geq Q_j$ and $y_{i, e_i} \in H^0
 (\sx', e_iL'-E_i + Q_i)$,
@@
 	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
+^{\halfcan_X'}(y_{i, e_i}) \leq \left\lfloor  e_i\subhalf{e_j'} \right\rfloor 
 	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
@@
 
-Next, define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
+{\bf Part (b):}
+Define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
 $$R_i = \begin{cases}
 	R_{i - 1} &\text{ if }i \notin J\\
-	R_{i - 1}[y_{i, e_i}] &\text{ otherwise.} 
+	R_{i - 1}[y_{i, e_i}] &\text{ if }i \in J. 
 \end{cases}$$
@@
 and that these elements together with $R_{i - 1}$ span $R_i$ as a $k$-
-vector space. These elements do not lie in $R_{i - 1}$ because their
-order of pole at $Q_i$ is bigger than the order of any element in $R
-_{i - 1}$, and are linearly independent amongst themselves because of
+vector space. These elements do not lie in $R_{i - 1}$ because when viewed as a rational section of $\sco(L_X')$, their order of pole at $Q_i$ is bigger than the order of any element in $R
+_{i - 1}$. Additionally, these elements are linearly independent amongst themselves because of
 injectivity of the linear map
@@
 The fact the the elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 0,
-b > 0$ span $R_i$ over $R{i - 1}$ follows from the fact that the
+b > 0$ span $R_i$ over $R_{i - 1}$ follows from the fact that the
 integer lattice points in the cone generated by the vectors $\left(e
@@
 
-To show (c), we wish to show, for all generators $z$ of $R'$
-such that $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$, that
-$y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
+{\bf Part (c):}
+To show (c), we wish to show that $y_{i, e_i}z \in R'$ for all generators $z$ of $R'$
+with $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$. Note that $f \in R$ further satisfies $f \in R'$ if and
 only if for all $j \in J$ we have
@@
 \noindent
-We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in three cases, depending on whether $j \notin \{
+We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases that $j \notin \{
 i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
@@
 {\sf Case 2: $j =i.$}
-
-For the case when $e_j' = 3$ for all $j \in \{1, \ldots, r\}$,
-we know that
-
-Otherwise by part (a), condition (Ad-ii), and Lemma
+By part (a), condition (Ad-ii), and Lemma
 ~\ref{lem:admissible_inequality} we have
@@
 
-Finally, we check (d), by checking $(Ad-i),(Ad-ii)$ and $(Ad-iii)$ are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
+{\bf Part (d):}
+To check (d), we show $(Ad-i),(Ad-ii)$ and $(Ad-iii)$ are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is

### 2015-06-27 stacky_write_up/spin_cring.tex
editing beginning of genus 2 case

@@
 
-Here, $-\ord_{Q_j}
-^{\halfcan_X'}(L) = -\ord_{Q_j}
-^{\halfcan_X'}(L'),$ so
+Here, $L|_{Q_j} = L'|_{Q_j},$ so
 \begin{align*}
@@
 \begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'}
+	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'},
 \end{align*}
@@
 {\bf Part (d):}
-To check (d), we show $(Ad-i),(Ad-ii)$ and $(Ad-iii)$ are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
+To check (d), we show (Ad-i),(Ad-ii), and (Ad-iii) are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
@@
 Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}.
-Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
+Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
 so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}.
@@
 \end{cases}$$
-then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$
+then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L).$
 \end{cor}
 \begin{proof}
-For $t \leq i \leq r$.
-Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g; e_1, \ldots.
-e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
-$J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
-
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
+For $t \leq i \leq r$, let $(\sx_i,\Delta, L_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx',\Delta,L),$ and having signature $(g; e_1, \ldots.
+e_{i-1}, e_i, e_i, \ldots, e_i; \delta).$ Let
+$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
+
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is admissible.
 
@@
 Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
-Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
+Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2},$ times, for the fixed set $J_{i+1},$ we see $(*_{i+1})$ holds.
 \end{proof}
@@
 In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
-The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved.
-We begin with the case that $g \geq 2$.
+The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.
 
 \ssec{Bounds on Generators and Relations in High Genus}
+
+The main result of this subsection is that for a log spin curve (with no stacky points) $(X,\Delta,L)$, the half-canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
+The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relations_11}.
+In fact, it is fairly immediate from Riemann--Roch and the basepoint-free pencil trick that $R_L$ is generated in degree at most $6$, as is demonstrated in the following
+Lemma ~\ref{lem:semicanonical_generation}.
+However, to reduce the bound from 5 to 6 in the case $g =2$, we will have to work a little in Proposition ~\ref{prop:genus_2_generation_5}.
+The following proof of Lemma ~\ref{lem:semicanonical_generation} is due to Neves \cite[Proposition III.4]{neves:halfcan}, although he omits the fairly tricky genus 2 case.
+We produce the proof here for completeness.
 

### 2015-06-27 stacky_write_up/spin_cring.tex
more edits to genus 2

@@
 	\item Notation for grobner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
+	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non stacky) curves.
 \end{enumerate}
+
+\begin{rem}
+\label{rem:delta-not-1}
+Suppose $(\sx,\Delta,L)$ is a log spin curve.
+Note that $\deg \lfloor L \rfloor$ is even.
+because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K \rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
+In particular, we shall often use $\deg \Delta \neq 1$.
+\end{rem}
 
@@
 
-The main result of this subsection is that for a log spin curve (with no stacky points) $(X,\Delta,L)$, the half-canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
-The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relations_11}.
+The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the half-canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
+The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relation_11}.
 In fact, it is fairly immediate from Riemann--Roch and the basepoint-free pencil trick that $R_L$ is generated in degree at most $6$, as is demonstrated in the following
-Lemma ~\ref{lem:semicanonical_generation}.
-However, to reduce the bound from 5 to 6 in the case $g =2$, we will have to work a little in Proposition ~\ref{prop:genus_2_generation_5}.
-The following proof of Lemma ~\ref{lem:semicanonical_generation} is due to Neves \cite[Proposition III.4]{neves:halfcan}, although he omits the fairly tricky genus 2 case.
+Lemma ~\ref{lem:semicanonical_generation}. However, to reduce the bound from 5 to 6 in the case $g =2$, we will have to work a little in Proposition ~\ref{prop:genus_2_generation_5}.
+
+\begin{rem}
+The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}, although he omits the fairly tricky genus 2 case.
 We produce the proof here for completeness.
+\end{rem}
 
@@
 \label{lem:semicanonical_generation}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$. Then, the map
-\begin{align*}
-	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective if $n \geq 5$ or if ($n = 5$ and $\Delta > 0$).
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$.
+Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$ is basepoint free.
+Then, the map
+\begin{align*}
+	V \otimes H^0(nL) \rightarrow H^0((n+2)L)
+\end{align*}
+is surjective if $n \geq 5$ and if {\rm(}$n = 4$ and $\Delta > 0${\rm)}.
 In particular, $R_L$ is generated in degree at most $6$ if $\Delta = 0$ and in degree at most $5$ if $\Delta > 0$.
@@
 \begin{proof}
-Therefore, to show there are no new generators in degree at least $7$, it suffices to show that if $n \geq 5$ or if ($n = 5$ and $\Delta > 0$), the map
+To show there are no new generators in degree at least $7$ if $\Delta = 0$ and in degree at least $6$ if $\Delta > 0$, it suffices to show that if $n \geq 5$ or if ($n = 4$ and $\Delta > 0$), the map
 \begin{align*}
@@
 \end{align*}
-is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
-Since $K$ is basepoint-free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
-Then, by the basepoint-free pencil trick, we obtain an exact sequence
+is surjective.
+Indeed, since $V= ks_1 \oplus k s_2 \subset H^0(K)$ is basepoint free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
 $$\begin{tikzcd}
@@
 We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
+Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 5$ or ($n = 4$ and $\Delta > 0$).
+Note that here we are implicitly using the Remark ~\ref{rem:delta-not-1}
 Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
@@
 \end{proof}
-
-\begin{rem}
-\todo{This remark isn't quite right, we're changing the proof}
-In \cite[Proposition III.4]{neves:halfcan}, Neves claims to prove that $R_L$ is generated in degree at most 5.
-However, when the proof is carefully examined, it only shows generation in degree at most 6.
-For this reason, we only state Lemma ~\ref{lem:semicanonical_generation} as generation in degree at most 6.
-We next proceed to show this can be reduced to generation in degree 5.
-The trickiest case is genus 2, which we address next.
-\end{rem}
 
@@
 
-There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
- (note that $\delta$ must be even because $\halfcan_X \in \di X$ with $2\halfcan_X \sim K_X +\Delta$, where $\deg K_X$ is even).
-\todo{make a remark about this somewhere in the beginning and reference it} In the first case, $\deg \lfloor \halfcan \rfloor
+There are two main cases: when $\delta \geq 2$ and when $\delta = 0$, where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}. In the first case, $\deg \lfloor \halfcan \rfloor
 \geq 0$ so the result directly follows from Lemma

### 2015-06-27 stacky_write_up/spin_cring.tex
address some g0 todos, minor edits elsewhere

@@
 	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
-	\item Notation for grobner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
-	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non stacky) curves.
+	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
+	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
 \end{enumerate}
@@
 In particular, we shall often use $\deg \Delta \neq 1$.
+\todo{This seems to actually be proving that $\deg \Delta$ is even}
 \end{rem}
@@
 effective monoid of a divisor $D$ as the saturation $s$ of the
-divisor $D$ on $\sx$. In this case, the saturation $s$ of a divisor
-$D$ on $\sx$ (i.e. $\sat(\Eff(D))$) is the smallest positive $s \in
-\BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d \geq s$.
+divisor $D$ on $\sx$. In this case, the saturation $s :=
+\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
+$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
+\geq s$.
 \end{rem}
@@
 Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}
-\todo{fill out}
 
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma_2$ has saturation $s = 5$, \todo{Why is there a 's here instead of just s?} as noted in
+\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
 Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
-when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24). \todo{Aaron: Isn't $s + 21 = 26$? Shouldn't it be generated up to degree 25, potentially?}
+when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
 
@@
 $H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 24$. \todo{Should this be 25?} Note that we can again use Max No ether's theorem
+and $7 < d \leq 25$. Note that we can again use Max No ether's theorem
 (taking saturation into account) to see that
@@
 \begin{align*}
-	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} &= 0 & \text{ in degree $10$ and } \\
-	b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 &= 0 & \text{ in degree $14.$ }
+	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0 &\text{ in degree $10$} \\
+	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
 \end{align*}
@@
 Now we can combine this.
-\todo{write this section}
 

### 2015-06-27 stacky_write_up/spin_cring.tex
fix delta-not-1 typo
finished g=2 base

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 5$ or ($n = 4$ and $\Delta > 0$).
-Note that here we are implicitly using the Remark ~\ref{rem:delta-not-1}
+Note that here we are implicitly using the Remark ~\ref{rem:delta-not-1}.
 Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
 Therefore, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L),$$
-again using Riemann-Roch, implying $f$ is surjective.
+again using Riemann-Roch. Ergo, $f$ is surjective.
 \end{proof}
@@
 \begin{proof}
-By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
+By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_L$ has no minimal generators in degree 6.
 Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
-Recall that all spin divisors on $X$ can be written as 
+Recall that all linear equivalence classes of spin divisors on $X$ have a representative of the form
 $$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
-with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
-Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
+with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
+\todo{cite this somewhere, maybe ask david for a place to cite?
+We can cite http://www.math.harvard.edu/~ctm/home/text/class/harvard/213b/14/html/home/course/course.pdf, for example, from complex analysis course notes!}
+Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
+Therefore, the image of the multiplication map
 \begin{align*}
@@
 is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
-which have $\di u^3|_{2L} = -2L, \di u^2x|_{2L} = -2L + 2P_1,\di ux^2|_{2L} = -2L+4P_1, \di x^3|_{2L} = -2L + 6P_1.$ 
+which have 
+\begin{align*}
+	\di u^3|_{2L} &= -2L \\
+	\di u^2x|_{2L} &= -2L + 2P_1 \\
+	\di ux^2|_{2L} &= -2L+4P_1, \\
+	\di x^3|_{2L} &= -2L + 6P_1.
+\end{align*}
+
+\noindent
 Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
@@
 Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
-Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed .
+Hence, we know $L$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
 In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
@@
 
-\todo{This should be $k[x_1, \ldots, x_n]$ instead of $\sym H^0$.}
 \begin{lem}
@@
 Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and let $J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ For any $f \in k[x_1, \ldots, x_n]$ such that
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ let
+$$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j},$$
+and let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subset H^0(X,2L)$ is basepoint free.
+For any $f \in k[x_1, \ldots, x_n]$ such that
 $$
@@
 \end{cases}$$
-there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+there exist $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
 \end{lem}
 \begin{proof}
-Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
+Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subset H^0(X,2L)$.
 By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
 We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
-Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$. By Lemma ~\ref{lem:semicanonical_generation},
+By Lemma ~\ref{lem:semicanonical_generation},
 \begin{align*}
@@
 	5 &\text{ if }\Delta = 0\\
-	4 &\text{ if }\Delta > 0.
+	4 &\text{ if }\Delta > 0,
 \end{cases}$$
+by the assumption on $\deg f$.
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Choosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
 
@@
 \begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
-Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
+Suppose $f \in I_L$ with 
+$$
+\deg f \geq \begin{cases}
+	12 &\text{ if }\Delta = 0\\
+	11 &\text{ if }\Delta > 0.
+\end{cases}$$
+To complete the proof, it suffices to show $f \in I_{L,d}'$.
+By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subset H^0(K)$ is basepoint free.
+Consider the map
 $$\begin{tikzcd}
@@
 we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
-So, using the refined version of the basepoint-free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
-Therefore,
-\begin{align*}
-	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
+So, by the explicit isomorphism given in the proof of the basepoint-free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
+Hence,
+\begin{align*}
+	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
 \end{align*}
@@
 In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 is close to sharp.
+Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0$ is close to sharp.
 \end{rem}

### 2015-06-27 stacky_write_up/spin_cring.tex

@@
 \label{rem:delta-not-1}
-Suppose $(\sx,\Delta,L)$ is a log spin curve.
-Note that $\deg \lfloor L \rfloor$ is even.
-because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K \rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
+Suppose $(\sx,\Delta,L)$ is a log spin curve. Note that $\deg \Delta
+$ is even. because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K
+\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
 In particular, we shall often use $\deg \Delta \neq 1$.

### 2015-06-27 stacky_write_up/spin_cring.tex
sim edit
some typographical & alignment fixes

@@
 \label{eqn:sat_two_add_generator}
-	\begin{split}
-		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \\
-		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
-	\end{split}
+		\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
 \end{align}
@@
 \begin{align*}
-	y_i x_j &- A_{i,j} y_{i - 1}w_j & \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
-	y_4^2 &+ B_1 y_3 y_5 \\
-	y_4y_5 &+ B_2 y_3^2 x_3 \\
-	y_5^2 &+ B_3 y_3^2 x_4
+	&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
+	&y_4^2 + B_1 y_3 y_5 \\
+	&y_4 y_5 + B_2 y_3^2 x_3 \\
+	&y_5^2 + B_3 y_3^2 x_4
 \end{align*}
@@
 Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
-$$
-e_i \begin{cases}
-	= e_i' &\text{ if }i \notin J\\
-	\leq e_i' &\text{ if } i \in J
-\end{cases}$$
-then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L).$
+\begin{align*}
+	e_i	= e_i' \text{ if }i \notin J \\
+	& e_i \leq e_i' &\text{ if } i \in J
+\end{align*}
+
+\noindent
+then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$.
 \end{cor}
@@
 \begin{proof}
-Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
+Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X \sim 2 K_X + \Delta$.
 By Lemma ~\ref{lem:generation_5} and Proposition
@@
 $H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 25$. Note that we can again use Max No ether's theorem
+and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
 (taking saturation into account) to see that
@@
 from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
-Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
+Corollary ~\ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
 \halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.

### 2015-06-27 stacky_write_up/spin_cring.tex
edited genus 1 and intro

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 \cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$.
-In order to answer this question, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
+In order to find generators and relations for $M(\Gamma)$, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
 category, using a generalization of the GAGA principle. By
@@
 Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is
-well known that the sheaf $\Omega _X,$ with associated divisor $K_X$
+well known that the canonical sheaf $\Omega _X,$ with associated canonical divisor $K_X$
  determines the {\bf canonical map } $\pi:X \rightarrow \BP_k^{g - 1}$.
@@
 with multiplication structure corresponding to tensor product of
-sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. Petri's
+sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
 theorem gives generators and relations for $R(X, K_X)$ showing that
 in most cases $R(X, K_X)$ is generated in degree 1 with relations
-in degree 2 (see \cite[p. 157]{saint-donat:proj}). This has the
+in degree 2, as shown in \cite[p. 157]{saint-donat:proj}. This has the
 pleasant geometric consequence that all such canonically embedded
-curves are scheme theoretically cut out by quadratic equations
-
-Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
-much more general setting, generalizing Petri's theorem in many
-directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
-$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
-$(\sx,\Delta)$ denote a tame separably rooted curve over a
+curves are scheme theoretically cut out by quadratic equations.
+
+Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many
+directions. A divisor $\Delta \in \di X$ is a {\bf log divisor} if
+$\Delta = \sum_{i=1}^{n}P_i \in \di X,$ with $P_i$ distinct points of $X$. Let
+$\sx$ denote a tame separably rooted curve over a
 field $k$ so that $X$ is the coarse space of $\sx$, as defined in
-\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
-= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
+\cite[Section 5.2]{vzb:stacky}, with $\di \sx = \di X \oplus \left(\bigoplus_{i
+= 1}^r \langle \frac{1}{e_i}P_i \rangle \right),$ so that $e_i \in \BZ$. Let $K_
 \sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
 say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
-\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$ if
-$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\delta := \deg \Delta,$ then we
+\in \di \sx$ a {\bf log half-canonical divisor}, also known as a theta-characteristic, on the {\bf log stacky curve} $(\sx,\Delta)$ if
+$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\deg \Delta =\delta,$ then we
 say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$. A
-{\bf log spin curve} is a triple $(X, \Delta, \halfcan)$ where $(X,\Delta)$
-and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
+{\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $(\sx,\Delta)$
+is a log stacky curve and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
 The central object of study in this paper is the {\bf log spin
@@
 \begin{align*}
-	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
+	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
 \end{align*}
@@
 This theorem is proven in three different genus cases, each of
-which use similar inductive processes. The high genus case is
+which use similar inductive processes. The genus $g \geq 2$ case is
 proven in Theorem ~\ref{thm:g-high-main}. In Theorem
@@
 provides an inductive procedure for determining the generators and
-initial ideal of relations for $\halfcan'$ when the half-canonical
-divisor $\halfcan$ can be written as $\halfcan' + \Lambda$ with
-$(\halfcan', 0, X)$ a log spin curve. In fact, such a system of
-generators and relations are known for $\halfcan'$ in many cases,
+initial ideal of relations for the half-canonical divisor $\halfcan$ can be written as $\halfcan = \halfcan' + \Lambda$ with
+$(\halfcan', \Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact, such a system of
+generators and relations are known for $\halfcan'$ in many interesting low genus cases,
 as detailed in Neves ~\cite[ Section III.4]{neves:halfcan}.
@@
 Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct on the order and number of hyperelliptic-
-fixed points. To this end, we first review important background in
+proof will be to induct on the order and number of stacky points. To this end, we first review important background in
 Section ~\ref{sec:background}. Then, we develop various inductive
 tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
-~\ref{sec:g_1} and ~\ref{sec:g_0}, we prove Theorem
+~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
 ~\ref{thm:main} in the high genus, genus
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e.}
 
@@
 \begin{enumerate}
+	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
+	\item While the remainder paper could be writen using stack-theoretic terms, as is done in \cite{vzb:stacky}, we shall adopt the simpler language of $\BQ$ divisors, thinking of $\sx$ as the underlying scheme $X$ with fractional points.
+	\item Include explicit definitions for what we are assuming about a curve, i.e.
+smooth, projective, etc.
+Also, possibly discuss the relations to stacks, either here in or in the introduction.
+Make sure to make clear the assumption that we will work over an algebraically closed field through tensoring up.
 	\item Notation for Coarse space
@@
 
+We are finally ready to prove our main theorem ~\ref{thm:main} in the case $g \geq 2$.
+The idea of the proof is to use Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11} to complete the base case when $L = L_X$ and then apply Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:raise-stacky-order} to complete the induction step.
+
 \begin{thm}
 \label{thm:g-high-main}
-Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
+Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ be a log spin curve so
 that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r).$ If $\Delta = 0$ then 
+\max(5, e_1, \ldots, e_r).$ If $\Delta = 0,$ then 
 $R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
@@
 \begin{proof}
-Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
+As the base case, let $\halfcan_X \in \di X$ satisfy $2\halfcan_X \sim 2 K_X + \Delta$.
+
 By Lemma ~\ref{lem:generation_5} and Proposition
@@
 \halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
-\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx,
+\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx',
 \Delta, \halfcan')$ by Lemma ~\ref{lem:sat-2}
@@
 in the case $P$  is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann Roch, and the fact that $d
-\geq 3$.
-
-In this case, we claim the theorem holds for $(\sx',\Delta, L')$. Indeed, the bound on the generators holds by part (a) of Lemmas
+~\ref{eqn:deg1-sat-ind} holds by Riemann Roch since $\frac{\beta}{\alpha} = \frac{3}{1}=3$.
+In this case, we claim the theorem holds for $(\sx',\Delta, L')$.
+Indeed, the bound on the generators holds by part (a) of Lemmas
 ~\ref{lem:sat-2} and ~\ref{lem:sat-1},
@@
 ~\ref{lem:sat-2} and ~\ref{lem:sat-1}.
-Therefore, by Corollary ~\ref{cor:raise-stacky-order}, this theorem 
+
+Applying this argument $r-1$ additional times, we obtain that the Theorem holds for $(\sx', \Delta, \halfcan')$ where $\sx'$ has signature $(g;3,\ldots, 3;\delta)$ with $g \geq 2$.
+Therefore, by Corollary
+~\ref{cor:raise-stacky-order}, this theorem 
 holds for all log spin curves $(\sx, L, J)$. 
@@
 
-In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
+In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
+Unlike the $g \geq 2$ case, here we obtain explicit generators and relations for any log spin curve $(\sx, \Delta, L)$ with $g = 1$.
+
+The inductive strategy we will adopt to prove Theorem ~\ref{thm:main} is similar to that of the genus $g \geq 2$ case.
+In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
 We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.
@@
 
+	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
+
+	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline
+
 	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
 
-	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
-
 	$P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline
-	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline
 
@@
 \end{longtable}
+\begin{center}
+\label{table:g-1-base}
+Genus 1 base cases
+\end{center}
 
 \begin{example}
-\label{eg:base- 1-0}
+\label{eg:base-1-0}
 In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
@@
 \begin{example}
-\label{eg:base- 1-33}
+\label{eg:base-1-33}
 Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
@@
 
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$.
-Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
+Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are both one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
 
@@
 We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
-We clearly have two generators $x_3, y_3$ in degree 3 with a pole of order $\frac{3- 1}{2}$ by construction.
+We clearly have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
 Hence, (Ad-i) holds.
@@
 Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
-Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
 \end{example}
@@
 \label{eg:exception-1-5}
-Let $L' = \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$.
+Let $L' = P - Q + \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$.
 Let $u \in (P_L)_1$ be any nonzero element.
-We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
+We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
 We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$.
@@
 $R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
-The proof of this can be gotten by first using Riemann--Roch and counting the pole order at $P_1$ considerations to check the above relation exists, and that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
-It is analogous to Example ~\ref{ex:base-377}, and is omitted.
-
-Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base- 1-33}.
-
-Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 caries over, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
+
+In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
+One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+The verification is analogous to Example ~\ref{ex:base-377} and is omitted.
+
+Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
+
+Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 also determines a relation in the canonical ring for $L = P - Q + \frac{3}{7}$, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
 \end{example}
@@
 
-The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed. Note this is yet another exceptional case.
+The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
+Note that just like $L' = P - Q + \frac{2}{5}P_1$ is an exceptional case, as noted at the end of Example ~\ref{eg:exception-1-5}, $L' = \frac{3}{7}P_1$ is yet another exceptional case.
 
@@
 \label{ssec:g-1-exceptional}
-\todo{remove stuff about tame and separably rooted, change to $\BQ$ divisor.}
-Let $\sx$ be a tame, separably rooted stacky curve of genus 1. Let $P,Q$ are distinct hyperelliptic fixed points, and $R$ be a point on $\sx$.
-
-\todo{cite genus 1 final theorem here, to explain what these cases are exceptional to}
+Let $\sx$ be a stacky curve, with Let $P,Q$ distinct hyperelliptic fixed points on $X$.
+The following table provides a list of all cases which are not generated in degrees $e=\max(5,e_1,\ldots, e_r)$ with relations in degrees $2e$, as described in Theorem ~\ref{thm:g-1-main}.
+
 \begin{longtable}	{| c || c | c | c |}
@@
 \end{longtable}
-
+\todo{Possibly add an autoincrement counter to deal with table numbering}
 \begin{center}
 \label{table:g-1-exceptional}
-\textbf{Table (IV)}: Genus 1 exceptional cases, where $L' = P - Q + \frac{e- 1}{2e}R$, with $P \neq Q$.
+Genus 1 exceptional cases
 \end{center}
@@
 
-We now elaborate on the computation of the results in 
-Table ~\ref{table:g-1-exceptional}. We have already explained the case of 
+We have already checked the case of 
 $L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
@@
 
+We now have all the tools necessary to prove our main theorem, ~\ref{thm:main} in the case $g = 1$.
+
 \begin{thm}
 \label{thm:g-1-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
-so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
+Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
 If $g = 1$, then the canonical ring
@@
 
-If $\Delta > 0$, we must have $\Delta \geq 2$.
-In this case, let $L_X \in \di X$ be so that $2L_X \sim K_X + \Delta$.
-We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor, so without loss of generality, we may assume $L$ is an effective divisor.
-We know the theorem holds for $L' = 0$ by Example ~\ref{eg:base- 1-0}.
-\todo{fix this to accommodate the possibility that $P \in supp(L')$, this has already been done suppose ~\ref{lem:sat-1} accommodates it. }
+If $\Delta > 0$, we must have $\Delta \geq 2$, by Remark ~\ref{rem:delta-not-1}.
+In this case, let $L_X \in \di X$ satisfy $2L_X \sim K_X + \Delta$.
+We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor.
+Thus, without loss of generality, we may assume $L$ is an effective divisor.
 
 We first now show the theorem holds for $L_X$ by induction.
+Since $L$ is effective, we may induct on the degree of the divisor.
+The base case is easy: the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
 Assume it holds for $L' \in \di X$, with $L'$ effective.
-We will show it holds for $L' + P$.
+We will show it holds for $L' + P,$ verifying the inductive step.
 There are two cases, depending on whether $P$ is a basepoint of $L'$.
 
-First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1}.
-In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $ with $\ord_P(u) = 0$, as $P$ is not a basepoint of $L'$.
+First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
+In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $, as $P$ is not a basepoint of $L'$.
 Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $L= L'+P$.
@@
 
-Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points
+Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points.
 
 First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-While $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, while the previous relation lies in degree $12$, which is less than $2 \cdot 7 = 14$.
+By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12.
+Furthermore, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
+Observe that $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$.
+However, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, and the relation in degree $12$ coming from $R_{L'}$, lies in a degree less than $2 \cdot 7 = 14$.
 Therefore, the Theorem holds for $L' = P - Q + \frac{3}{7}P_2$.
@@
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base- 1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Assume for convenience  $e_1 \leq e_2 \leq \cdots \leq e_r$.
-Then, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base-1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
+Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
 
@@
 
-This case is completely analogous to 2a.
+This case is analogous to 2a.
 \end{proof}
@@
 \begin{center}
-\textbf{Table (I)}: Genus 0 saturation \todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
+Genus 0 saturation \todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
 \end{center}
@@
 \begin{center}
-\textbf{Table (II)}: Genus 0 non-effective base cases generator/relations
+Genus 0 non-effective base cases generator/relations
 \end{center}
@@
 \begin{center}
-\textbf{Table (III)}: Genus 0 non-effective base cases (Ad-iii)
+Genus 0 non-effective base cases (Ad-iii)
 \end{center}
@@
 we obtain Theorem ~\ref{thm:g-0-main} for any
-log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
+log spin curve $(\sx, \Delta, L)$ with
 signature $\sigma$ covered by this induction process.
@@
 \label{table:g-0-exceptional}
-\textbf{Table (IV)}: Genus 0 exceptional cases
+Genus 0 exceptional cases
 \end{center}
@@
 \label{thm:g-0-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
+Let $(\sx, \Delta, \halfcan)$ log spin curve,
 so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.

### 2015-06-27 stacky_write_up/spin_cring.tex
Fixed section 3 lemma

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 which use similar inductive processes. The high genus case is
-proven in Theorem ~\ref{thm:g-high-main}. In Theorem
-~\ref{thm:g-1-main} and Theorem
-~\ref{thm:g-0-main}, we also give the respective
+proven in Theorem ~\ref{thm:high_generators_relations}. In Theorem
+~\ref{thm:g_1_generators_relations} and Theorem
+~\ref{thm:g_0_generators_relations}, we also give the respective
 genus one and genus zero results after using a similar induction
@@
 \begin{enumerate}
-	\item Notation for Coarse space
-	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
 	\item Note that this result is independence of base field
@@
 	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
-	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
-	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
 \end{enumerate}
-
-\begin{rem}
-\label{rem:delta-not-1}
-Suppose $(\sx,\Delta,L)$ is a log spin curve. Note that $\deg \Delta
-$ is even. because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K
-\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
-In particular, we shall often use $\deg \Delta \neq 1$.
-\end{rem}
 
@@
 effective monoid of a divisor $D$ as the saturation $s$ of the
-divisor $D$ on $\sx$. In this case, the saturation $s :=
-\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
-$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
-\geq s$.
+divisor $D$ on $\sx$. In this case, the saturation $s$ of a divisor
+$D$ on $\sx$ (i.e. $\sat(\Eff(D))$) is the smallest positive $s \in
+\BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d \geq s$.
 \end{rem}
@@
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
-Then we will explicitly describe elements that minimally generate \todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
-The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.
+Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
 
@@
 
-The following lemma provides an inductive method to extend
-O'Dorney's result \todo{Aaron: Which result?
-If anything, wouldn't this be a strengthening of his bounds from Theorem 8, instead of an extension?
-I guess it is an extension in that it generalizes to higher genus?
-Cite the theorem number you are talking about} on $\BP^1_k$ to divisors $D = \sum_i \frac{\alpha_i
-}{\beta_i} P_i$ consisting of arbitrarily many points satisfying $H^
-0(X, \lfloor D \rfloor) > 0$, showing that they \todo{What are generated?} are generated in
+In Lemma \ref{lem:sat-1} we provide an inductive method to strengthen
+O'Dorney's result \todo{cite theorem 8} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
+}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
+0(X, \lfloor D \rfloor) > 0$; our result implies that $R_D$ is generated in
 degrees at most $e = \max(\beta_i)$ with relations generated in
-degrees at most $2e$.  Furthermore, given some constraints on $H^0(
+degrees at most $2e$.  Furthermore, given additional constraints on $H^0(
 X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-same Riemann-Roch arguments from $\BP^1_k$ in arbitrary genus,
-allowing a similar inductive result in arbitrary genus $e = \max(
-\beta_i)$. To do this, we extend an inductive result by Voight and
+same Riemann-Roch arguments in arbitrary genus. 
+To do this, we extend an inductive result by Voight and
 Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
 divisors. \todo{cite theorem 8.3.1}
+
+First, however, we give a criteria to determine if a set of monomials generates the initial ideal of relations, and define notation for a type of monomial ordering.
+
+\begin{lem}\label{lem:relations_from_generators_induction} 
+Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
+Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such
+\begin{enumerate}
+\item[(\ref{lem:relations_from_generators_induction}.1)]  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
+\item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
+\item[(\ref{lem:relations_from_generators_induction}.3)] All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
+\begin{align*}
+	& S \\
+	\cup \; &\langle T\rangle \\
+	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+\end{align*}
+\end{enumerate}
+Then 
+\begin{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
+\end{lem}
+\begin{proof}
+Suppose monomial $f\in T$ has a pole order $a$ at $P$.
+Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
+This demonstrates that
+\begin{align*}
+	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
+Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
+\begin{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
+\end{proof}
+
+As suggested by the previous lemma, we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
+\begin{defn}
+We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff one of the following holds
+\begin{enumerate}
+\item $\deg(f) < \deg(g)$
+\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$
+\item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative.  
+\end{enumerate}
+\end{defn}
+We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is}
+We now offer a lemma that allows us to inductively add $\mathbb{Q}$-points to a divisor and describe the new generators and relations.
 
@@
 $u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0$ for all $x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
-Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\bar{d}$ with relations generated
-in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
+Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\sigma$ with relations generated
+in degree at most $\tau$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
 for some $\alpha,\beta \in \mathbb{N}$ such that
@@
 \item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$
-
-\item[(b)] If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
+degree $d_i$ and has a pole at $P$ of degree $c_i$, when viewed as sections of $\so_{\halfcan'}$
+
+\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
+\[
+	\ord_u(f) < \ord_u(g) \implies f\prec g
+\]
+and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with a block order.
+If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
 
@@
 	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
-										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n- 1 \\
-										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
-										 &+ \langle (y_i)^{\deg(y_{i + 1} + 1)}: 1\le i =\lfloor \frac{\alpha}{\beta} \rfloor
-\end{align*}
-
-In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally \todo{Aaron: Should the word minimally be removed here?} generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
+										 &+ \langle U_i: 1 \le i \le n-1 \rangle\\
+										 &+ \langle V \rangle\\
+\end{align*}
+where 
+$V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_i^{a_i}$ with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ such that
+$\sum_{j=1}^i a_j c_j \ge c_{j+1}$
+and there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ such that with all $b_j\le a_j$ and 
+$\sum_{j=1}^i b_jc_j\ge c_{j+1})\}$.  \\
+
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with relations $I$ generated over $I'$ by relations in degree is generated $\max(2\beta, \beta + \sigma)$ (where $\sigma=\max(\deg(x_i))$).
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
@@
 \end{lem}
-
-Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$.
-\todo{Would it make sense to put this lemma before the previous theorem, instead of after the statement?}
-
-\begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
-Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such
-\begin{enumerate}
-\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
-\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
-\begin{align*}
-	& S \\
-	\cup \; &\langle T\rangle \\
-	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
-\end{align*}
-\end{enumerate}
-Then 
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
-\end{lem}
 \begin{proof}
-Suppose monomial $f\in T$ has a pole order $a$ at $P$.
-Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
-This demonstrates that
-\begin{align*}
-	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
-Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:sat-1}]
 By
@@
 \noindent
-be the non-negative best lower approximation of $\frac{
+be the positive best lower approximation of $\frac{
 \alpha}{\beta}$ as described in the lemma's statement.  Note that elements of $H^0(X, d\halfcan)$ have pole of
@@
 
-For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$ \todo{Where do the $z_i$ live? How many $z_i$ are there, what indexing sets are the product and sums taken over?}
-by construction, so any product of $\prod z_i$ of elements of
-degrees less than $d_i$ must have
-\todo{Aaron: at what point is the following order taken at?}
+For any $j < i \in \mathbf{N}$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$, so for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ for all $z_j$, $\prod_{j=1}^n z_j$ must satisfy
 \[
-	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
+	\frac{-\ord_P(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
 \]
@@
 \noindent
-so we have the pole order of $\prod z_i$ is 
+so we have the pole order of $\prod_{j=1}^n z_j$ is 
 \[
-	\sum -\ord(z_i) < c_i .
+	\sum -\ord(z_j) < c_i .
 \]
@@
 Choose some $y_i \in(R_{
-\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.
-
-Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ not a best lower approximation. Then choose
-best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
-maximal; since $c<c_{i + 1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$. From
-this we can deduce that 
+\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ and if $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
+
+Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
+\beta}$ is not a best lower approximation. Then choose
+best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
+%  The argument goes $c_i d \ge c d_i$
+% implies c_i \frac{d}{d_i} \ge c
+% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
+% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
+% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
+% \implies the equation below:
 \[
-	c_i +(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
+	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
 \]
 
-\noindent
-Therefore, we can generate an element of $(R_{\halfcan})_d$ as a product of lower degrees that 
-has pole degree $c$ at $P$ by either $y_i u^b$, $y_i z u^b$, or $zu^b$ satisfying $i>
-\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$, 
-with $d_j = 1 =d_{{\lfloor \frac{a}{b} \rfloor}}$ and $b<d_{\lfloor \frac{\alpha}{\beta} 
-\rfloor + 1}$.
-
+This suggests how we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
+\[
+	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
+\]
+and for $i \in \mathbf{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
+\[
+	S_i = y_j S_{i-j}.
+\]
+Then define 
+\[
+	S = \cup_{i=1}^{\infty} S_i.
+\]
+A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).
+
+Furthermore, if we define $U_i$ and $V$ as in the lemma's statement and
+\[
+	T = (\bigcup_{i=1}^{n-1} U_i) \cup V,
+\]
+then we observe that $S$ and $T$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, so we immediately prove part (b) of this lemma.
+
+\iffalse{
 Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
@@
 is the initial ideal of $I$. 
+}\fi
+
 %Furthermore, since our choice of $y_i
@@
 
+\begin{rem}\label{rem:quad-gen}
+If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbf{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
+\end{rem}
+
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
@@
 
+\todo{Something about fractional weight modular forms?}
+
 \begin{lem}
 \label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
-
-Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
+Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, \halfcan_X)$ with signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively with $g > 0,$ and, if $g = 1$ then $\deg 3\halfcan' \geq 2$.
+Let $R_{L'} = k[x]/I'= k[x_2, x_3
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-
 Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
@@
 \label{eqn:sat_two_add_generator}
-		\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
+	\begin{split}
+		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \\
+		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
+	\end{split}
 \end{align}
@@
 \todo{Make explicit assumptions on genus.}
-Suppose $L'$ is a log half-canonical divisor of $\sx$ with course
+Suppose $L'$ is a log half-canonical divisor of $\sx'$ with course
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ with $R_
@@
 \begin{align*}
-	&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
-	&y_4^2 + B_1 y_3 y_5 \\
-	&y_4 y_5 + B_2 y_3^2 x_3 \\
-	&y_5^2 + B_3 y_3^2 x_4
+	y_i x_j &- A_{i,j} y_{i - 1}w_j & \text{ so that } 4 \leq i \leq 5,3
+	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1\\
+	y_4^2 &+ B_1 y_3 y_5 \\
+	y_4y_5 &+ B_2 y_3^2 x_3 \\
+	y_5^2 &+ B_3 y_3^2 x_4
 \end{align*}
@@
 
+Transition words.
 \todo{transition!}
 
-\ssec{Raising Stabilizer Orders}
+\ssec{Inductive Lemma: Raising stabilizer orders}
 \label{ssec:ram_orders}
-In this subsection, we aim to prove Lemma
-~\ref{lem:raise-stacky-order}, whose proof is almost identical to that of \cite[Theorem 8.5.7]{vzb:stacky}. In many cases, Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem 
-~\ref{thm:main}, holds for a curve with signature
-$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta),$ with $e_{k+1}' = \cdots = e_r',$ then Theorem ~\ref{thm:main} also holds for a curve with
-signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta).$ In order to state Lemma
-~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
-
-One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and \cite[Definition 8.5.1]{vzb:stacky} is that in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ However, we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $L_X$ is not necessarily basepoint-free.
-Therefore, we will have to work with orders of zeros of poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
-Hence, we introduce the following notation.
+In this section, we aim to prove the inductive theorem, Theorem
+~\ref{lem:raise-stacky-order}. Under fairly general
+conditions, this theorem will allow us to show that if Theorem ~\ref
+{lem:raise-stacky-order} holds for a curve with signature
+$(0;e_1', \ldots, e_r';0)$ then it also holds for a curve with
+signature $(0; e_1, \ldots, e_r; 0)$ with $e_i' - e_i \in \{0 , 2\}$.
 
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
+curves, with the same stacky points $Q_1, \ldots, Q_r$. Suppose
+there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
 \{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
@@
 \end{defn}
-
-\begin{rem}
-Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
-\end{rem}
 
@@
 
-The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}
-
 \begin{lem}
@@
 \label{rem:three-cases}
-For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
+For the purposes of our induction, we will often be adding in a single 
 stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
 curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
-\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
+\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases:
 \begin{enumerate}
-	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
-	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
-	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
+	\item $g = 0, \delta = 0, $ and $r \geq 5$
+	\item $g = 1, \delta = 0,$ and $ r \geq 2$
+	\item $g \geq 2, \delta$ arbitrary, and $r \geq 1$.
 \end{enumerate}
 \end{rem}
-
-We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an analog of Lemma ~\ref[Theorem 8.5.7]{vzb:stacky}
 
@@
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta).$ Further, assume either 
+space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$ and either 
 \begin{enumerate}
-	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_1,\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' = R_{L'}$ for all $i \in J,$ as in Definition ~\ref{defn:admissible} or
-	\item $\sigma$ is one of the signatures described in cases (1), (2) and (3) of Remark ~\ref{rem:three-cases} and $y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of $\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ for $1 \leq  i \leq r$.
+	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
+	\item or $\sigma$ is one of the signatures described in Remark ~\ref{rem:three-cases}, with $y_{1, 3} = y_{2,3} = \ldots, y_{r,3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
 \end{enumerate}
@@
 $(\sx, \Delta, \halfcan)$ be another log spin curve
-with coarse space $X$, so that $X \cong X'$ and signature $(g; e_1, \ldots, e_r;
+with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
 \delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
+	\item[(b)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
 0,
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y] := k[y_{i, e_i}]_{i \in J}$ and $k[x]:=k[x_1,\ldots, x_m]$ with graded monomial orders and give $k[y, x] = k[y] \otimes k[x]$ block order, as defined in \cite[Definition 8.1.1]{vzb:stacky}.
-\todo{Possibly reference definition in this paper instead.} Let $R = k[y, x]/I.$ Then,
-		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z : z 
+	\item[(c)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
+		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
+		block order. Let $R = k[y, x]/I.$ Then,
+		\begin{align*}
+			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
 			\neq y_{i, e_i}, y_{i, e_i'} \rangle
@@
 \begin{proof}
-We will only prove this in the case (1), in which $(\sx', \halfcan', J)$ is admissible, as the case (2), in which $\sigma$ is as in Remark ~\ref{rem:three-cases}, is completely analogous.
-
-{\bf Part (a):} 
-Recall from Definition ~\ref{defn:admissible} that
-
-\begin{align*}
-	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i-e_j'\} = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}.
-\end{align*}
-
-\noindent
+We will only prove this in the case (1), that $(\sx', \halfcan', J)$ is admissible, as the case (2) that $\sigma$ is as in Remark ~\ref{rem:three-cases} is completely analogous.
+
+Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be the two log spin curves in 
+question, with coarse spaces $X = X'$.
 Define
-\begin{align*}
-	E_i = \sum_{j \in S(i,0)}^{}Q_j.
+
+\begin{align*}
+	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}
+\end{align*}
+
+\noindent
+Define
+\begin{align*}
+	E_i = \sum_{j \in S(i,0)}^{}Q_j
 \end{align*}
@@
 \begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g - 1,
-\end{align*}
-
-\noindent
-and so $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch.
-Hence, a general element
+	\deg \left( e_i L' - E_i \right) \geq 2g - 1
+\end{align*}
+
+\noindent
+implying that $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
+Riemann Roch \todo{Peter: Or more for higher genus, by our hypothesis}, and so a general element
 \begin{align*}
@@
 	-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \left\lfloor e_i \subhalf {e_i'} \right\rfloor + 1 =
+^{\halfcan_X'}(y_{i, e_i}) = \lfloor e_i \subhalf {e_i'} \rfloor + 1 =
 	\frac{e_i - 1}{2}
@@
 We next show $y_{i, e_i}$ also satisfies the second part of the
-claim of $(a),$ by considering separately the cases in which $j
+claim of $(a),$ by considering separately the cases of whether $j
 \in S(i, 0),$ and $j \notin S(i,0)$.
 
-If $j \in S(i,0)$, since $E_i \geq Q_j$ and $y_{i, e_i} \in H^0
+If $j \in S(i,0)$ then, since $E_i \geq Q_j$, and $y_{i, e_i} \in H^0
 (\sx', e_iL'-E_i + Q_i)$,
@@
 	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq \left\lfloor  e_i\subhalf{e_j'} \right\rfloor 
+^{\halfcan_X'}(y_{i, e_i}) \leq \lfloor  e_i\subhalf{e_j'} \rfloor 
 	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
@@
 
-{\bf Part (b):}
-Define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
+Next, define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
 $$R_i = \begin{cases}
 	R_{i - 1} &\text{ if }i \notin J\\
-	R_{i - 1}[y_{i, e_i}] &\text{ if }i \in J. 
+	R_{i - 1}[y_{i, e_i}] &\text{ otherwise.} 
 \end{cases}$$
@@
 and that these elements together with $R_{i - 1}$ span $R_i$ as a $k$-
-vector space. These elements do not lie in $R_{i - 1}$ because when viewed as a rational section of $\sco(L_X')$, their order of pole at $Q_i$ is bigger than the order of any element in $R
-_{i - 1}$. Additionally, these elements are linearly independent amongst themselves because of
+vector space. These elements do not lie in $R_{i - 1}$ because their
+order of pole at $Q_i$ is bigger than the order of any element in $R
+_{i - 1}$, and are linearly independent amongst themselves because of
 injectivity of the linear map
@@
 The fact the the elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 0,
-b > 0$ span $R_i$ over $R_{i - 1}$ follows from the fact that the
+b > 0$ span $R_i$ over $R{i - 1}$ follows from the fact that the
 integer lattice points in the cone generated by the vectors $\left(e
@@
 
-{\bf Part (c):}
-To show (c), we wish to show that $y_{i, e_i}z \in R'$ for all generators $z$ of $R'$
-with $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$. Note that $f \in R$ further satisfies $f \in R'$ if and
+To show (c), we wish to show, for all generators $z$ of $R'$
+such that $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$, that
+$y_{i, e_i}z \in R'$. Note that $f \in R$ lies in $R'$ if and
 only if for all $j \in J$ we have
@@
 \noindent
-We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases that $j \notin \{
+We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in three cases, depending on whether $j \notin \{
 i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
@@
 
-Here, $L|_{Q_j} = L'|_{Q_j},$ so
+Here, $-\ord_{Q_j}
+^{\halfcan_X'}(L) = -\ord_{Q_j}
+^{\halfcan_X'}(L'),$ so
 \begin{align*}
@@
 {\sf Case 2: $j =i.$}
-By part (a), condition (Ad-ii), and Lemma
+
+For the case when $e_j' = 3$ for all $j \in \{1, \ldots, r\}$,
+we know that
+
+Otherwise by part (a), condition (Ad-ii), and Lemma
 ~\ref{lem:admissible_inequality} we have
@@
 \begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'},
+	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'}
 \end{align*}
@@
 
-{\bf Part (d):}
-To check (d), we show (Ad-i),(Ad-ii), and (Ad-iii) are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
+Finally, we check (d), by checking $(Ad-i),(Ad-ii)$ and $(Ad-iii)$ are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
 i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
@@
 Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}.
-Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
+Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$
 so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}.
 Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
-\begin{align*}
-	e_i	= e_i' \text{ if }i \notin J \\
-	& e_i \leq e_i' &\text{ if } i \in J
-\end{align*}
-
-\noindent
-then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$.
+$$
+e_i \begin{cases}
+	= e_i' &\text{ if }i \notin J\\
+	\leq e_i' &\text{ if } i \in J
+\end{cases}$$
+then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$
 \end{cor}
 \begin{proof}
-For $t \leq i \leq r$, let $(\sx_i,\Delta, L_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx',\Delta,L),$ and having signature $(g; e_1, \ldots.
-e_{i-1}, e_i, e_i, \ldots, e_i; \delta).$ Let
-$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
-
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is admissible.
+For $t \leq i \leq r$.
+Let $(\sx_i,\Delta, L_i)$ be the log spin curve with the same coarse space as $L'$ and with the same stacky points as $(\sx',\Delta,L),$ having signature $(g; e_1, \ldots.
+e_{i-1}, e_i, e_i, \ldots, e_i;\delta),$ and let
+$J_i = \{i,\ldots, r\}.$ Note that $(\sx_k,L_k,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
+
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main} and $(\sx_i, \halfcan_i, J_i)$ is admissible.
 
@@
 Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
-Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2},$ times, for the fixed set $J_{i+1},$ we see $(*_{i+1})$ holds.
+Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2}$ times, we see $(*_{i+1})$ holds.
 \end{proof}
@@
 In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
-The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.
+The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved.
+We begin with the case that $g \geq 2$.
 
 \ssec{Bounds on Generators and Relations in High Genus}
-
-The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the half-canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
-The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relation_11}.
-In fact, it is fairly immediate from Riemann--Roch and the basepoint-free pencil trick that $R_L$ is generated in degree at most $6$, as is demonstrated in the following
-Lemma ~\ref{lem:semicanonical_generation}. However, to reduce the bound from 5 to 6 in the case $g =2$, we will have to work a little in Proposition ~\ref{prop:genus_2_generation_5}.
-
-\begin{rem}
-The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}, although he omits the fairly tricky genus 2 case.
-We produce the proof here for completeness.
-\end{rem}
 
@@
 \label{lem:semicanonical_generation}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$.
-Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$ is basepoint free.
-Then, the map
-\begin{align*}
-	V \otimes H^0(nL) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective if $n \geq 5$ and if {\rm(}$n = 4$ and $\Delta > 0${\rm)}.
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$. Then, the map
+\begin{align*}
+	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
+\end{align*}
+is surjective if $n \geq 5$ or if ($n = 5$ and $\Delta > 0$).
 In particular, $R_L$ is generated in degree at most $6$ if $\Delta = 0$ and in degree at most $5$ if $\Delta > 0$.
@@
 \begin{proof}
-To show there are no new generators in degree at least $7$ if $\Delta = 0$ and in degree at least $6$ if $\Delta > 0$, it suffices to show that if $n \geq 5$ or if ($n = 4$ and $\Delta > 0$), the map
+Therefore, to show there are no new generators in degree at least $7$, it suffices to show that if $n \geq 5$ or if ($n = 5$ and $\Delta > 0$), the map
 \begin{align*}
@@
 \end{align*}
-is surjective.
-Indeed, since $V= ks_1 \oplus k s_2 \subset H^0(K)$ is basepoint free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
+is surjective. Indeed, let $s_1,s_2 \in H^0(2L) \cong H^0(K)$ be two independent sections. 
+Since $K$ is basepoint-free, so is the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$. 
+Then, by the basepoint-free pencil trick, we obtain an exact sequence
 $$\begin{tikzcd}
@@
 We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 5$ or ($n = 4$ and $\Delta > 0$).
-Note that here we are implicitly using the Remark ~\ref{rem:delta-not-1}.
+Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption if $n \geq 5$ or ($n = 5$ and $\Delta > 0$), as in the case $\Delta > 0$ we have $\deg \Delta \geq 2$.
 Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
 Therefore, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L),$$
-again using Riemann-Roch. Ergo, $f$ is surjective.
+again using Riemann-Roch, implying $f$ is surjective.
 \end{proof}
+
+\begin{rem}
+\todo{This remark isn't quite right, we're changing the proof}
+In \cite[Proposition III.4]{neves:halfcan}, Neves claims to prove that $R_L$ is generated in degree at most 5.
+However, when the proof is carefully examined, it only shows generation in degree at most 6.
+For this reason, we only state Lemma ~\ref{lem:semicanonical_generation} as generation in degree at most 6.
+We next proceed to show this can be reduced to generation in degree 5.
+The trickiest case is genus 2, which we address next.
+\end{rem}
 
@@
 \begin{proof}
-By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_L$ has no minimal generators in degree 6.
+By Lemma ~\ref{lem:semicanonical_generation} it suffices to show there are no new generators in degree 6.
 Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
-Recall that all linear equivalence classes of spin divisors on $X$ have a representative of the form
+Recall that all spin divisors on $X$ can be written as 
 $$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
-with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
-\todo{cite this somewhere, maybe ask david for a place to cite?
-We can cite http://www.math.harvard.edu/~ctm/home/text/class/harvard/213b/14/html/home/course/course.pdf, for example, from complex analysis course notes!}
-Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
-Therefore, the image of the multiplication map
+with $\epsilon_i \in \{0,1\},$ and some $i \in \{2, 3, 4, 5, 6\}$ for which $\epsilon_i = 0$. \todo{cite this somewhere, maybe ask david for a place to cite?}
+Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1.$ Therefore, the image of the multiplication map 
 \begin{align*}
@@
 is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
-which have 
-\begin{align*}
-	\di u^3|_{2L} &= -2L \\
-	\di u^2x|_{2L} &= -2L + 2P_1 \\
-	\di ux^2|_{2L} &= -2L+4P_1, \\
-	\di x^3|_{2L} &= -2L + 6P_1.
-\end{align*}
-
-\noindent
+which have $\di u^3|_{2L} = -2L, \di u^2x|_{2L} = -2L + 2P_1,\di ux^2|_{2L} = -2L+4P_1, \di x^3|_{2L} = -2L + 6P_1.$ 
 Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
@@
 Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
-Hence, we know $L$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
+Hence, we know $L$ is effective, so we must have $L = P$ where $P$ is hyperelliptic fixed .
 In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
@@
 
+\todo{This should be $k[x_1, \ldots, x_n]$ instead of $\sym H^0$.}
 \begin{lem}
@@
 Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ let
-$$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j},$$
-and let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subset H^0(X,2L)$ is basepoint free.
-For any $f \in k[x_1, \ldots, x_n]$ such that
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and let $J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$ For any $f \in k[x_1, \ldots, x_n]$ such that
 $$
@@
 \end{cases}$$
-there exist $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+there exist $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ and $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
 \end{lem}
 \begin{proof}
-Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subset H^0(X,2L)$.
+Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ are independent elements.
 By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
 We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
-By Lemma ~\ref{lem:semicanonical_generation},
+Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$. By Lemma ~\ref{lem:semicanonical_generation},
 \begin{align*}
@@
 	5 &\text{ if }\Delta = 0\\
-	4 &\text{ if }\Delta > 0,
+	4 &\text{ if }\Delta > 0.
 \end{cases}$$
-by the assumption on $\deg f$.
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+Choosing $g_i,h_i$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
 
@@
 \begin{proof}
-Suppose $f \in I_L$ with 
-$$
-\deg f \geq \begin{cases}
-	12 &\text{ if }\Delta = 0\\
-	11 &\text{ if }\Delta > 0.
-\end{cases}$$
-To complete the proof, it suffices to show $f \in I_{L,d}'$.
-By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subset H^0(K)$ is basepoint free.
-Consider the map
+Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
+Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
 $$\begin{tikzcd}
@@
 we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
-So, by the explicit isomorphism given in the proof of the basepoint-free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
-Hence,
-\begin{align*}
-	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
+So, using the refined version of the basepoint-free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
+Therefore,
+\begin{align*}
+	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
 \end{align*}
@@
 In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0$ is close to sharp.
+Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 is close to sharp.
 \end{rem}
@@
 \ssec{Main Theorem for High Genus}
-\label{ssec:g-high-main}
+\label{ssec:main_g_high}
 
 \begin{thm}
-\label{thm:g-high-main}
+\label{thm:high_generators_relations}
 Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
@@
 \begin{proof}
-Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X \sim 2 K_X + \Delta$.
+Let $\halfcan_X \in \di X$ satisfy $2\halfcan_X + 2 K_X + \Delta$.
 By Lemma ~\ref{lem:generation_5} and Proposition
@@
 \begin{thm}
-\label{thm:g-1-main}
+\label{thm:g_1_generators_relations}
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
@@
 \begin{rem}
-In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
+In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g_1_generators_relations}, proof of Theorem ~\ref{thm:g_1_generators_relations} yields an explicit procedure for computing those minimal generators and relations.
 That, is one can start with the generators and relations for the base cases, and then inductively add in generators and relations, according to the inductive theorems.
@@
 
-There are two main cases: when $\delta \geq 2$ and when $\delta = 0$, where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}. In the first case, $\deg \lfloor \halfcan \rfloor
+There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
+ (note that $\delta$ must be even because $\halfcan_X \in \di X$ with $2\halfcan_X \sim K_X +\Delta$, where $\deg K_X$ is even).
+\todo{make a remark about this somewhere in the beginning and reference it} In the first case, $\deg \lfloor \halfcan \rfloor
 \geq 0$ so the result directly follows from Lemma
@@
 Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}
+\todo{fill out}
 
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
+\geq 0$. Since $\sigma_2$ has saturation $s = 5$, \todo{Why is there a 's here instead of just s?} as noted in
 Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
-when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
+when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24). \todo{Aaron: Isn't $s + 21 = 26$? Shouldn't it be generated up to degree 25, potentially?}
 
@@
 $H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
+and $7 < d \leq 24$. \todo{Should this be 25?} Note that we can again use Max No ether's theorem
 (taking saturation into account) to see that
@@
 \begin{align*}
-	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
+	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} &= 0 & \text{ in degree $10$ and } \\
+	b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 &= 0 & \text{ in degree $14.$ }
 \end{align*}
@@
 $k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
-$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$), the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$.
+$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$.
 We can definitely make this hold if we set up the variables in the right way, but I'm not sure if it's always true.}
@@
 stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
-we obtain Theorem ~\ref{thm:g-0-main} for any
+we obtain Theorem ~\ref{thm:g_0_generators_relations} for any
 log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
@@
 Now we can combine this.
+\todo{write this section}
 
 \begin{thm}
-\label{thm:g-0-main}
+\label{thm:g_0_generators_relations}
 Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
@@
 from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
-Corollary ~\ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
+Corollary ~ \ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
 \halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.

### 2015-06-27 stacky_write_up/spin_cring.tex
section 3 adding points theorems ammended

@@
 \]
-then we observe that $S$ and $T$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, so we immediately prove part (b) of this lemma.
+then we observe that $S$ and $T$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, so parts (b) and (c) of the lemma follow immediately
 
@@
 			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_4^2.\rangle
+			&+\langle y_4^2 \rangle.
 		\end{align*}
@@
 \begin{proof}
-The assumptions on $g,\sigma$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g - 1$ and $\deg 4L > 2g - 1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+The assumptions on $g$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g - 1$ and $\deg 4L > 2g - 1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
 If $g = 1$, we assume $\deg 3L \geq 2 > 2g - 1$, so we also have $\deg 4L \geq 2 > 2g - 1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
 Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann-Roch, and the assumptions on $\sigma$. \todo{Understand why/whether we need to cite Lemma 5.4.7.}
+_P(y_i) = 1$ by Riemann-Roch. \todo{Understand why/whether we need to cite Lemma 5.4.7.}
 
@@
 \label{eqn:sat_two_add_generator}
-		\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
+	S =	& \; \{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
+		\geq 0, \epsilon \in \{0, 1\}\} \\
+	\cup	& \; \{ y_3^ay_4 \mid a \geq 0 \}
 \end{align}
@@
 
+Letting
+\begin{align*}
+	T =   &\; \{ y_4 x_j \mid 2 \leq j \leq m \} \\
+	\cup &\; \{ y_4^2 \}
+\end{align*}
+part (b) follows immediately from lemma \ref{lem:relations_from_generators_induction}
+
+\iffalse{
 For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
@@
 Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
-
 %Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
+}\fi
 \end{proof}
@@
 Suppose $L'$ is a log half-canonical divisor of $\sx'$ with course
-space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ with $R_
+space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
 {\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
@@
 			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5.\rangle 
-		\end{align*}
-	\item[(c)] Any set of generators for $I'$ together with 
-		any set of relations with leading terms as in (b) 
-		generate $I$.
+			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5\rangle.
+		\end{align*}
+	%\item[(c)] Any set of generators for $I'$ together with 
+	%	any set of relations with leading terms as in (b) 
+	%	generate $I$.
 \end{enumerate}
@@
 \begin{proof}
-First, note that since we are in genus 0, we can choose the
-elements $y_3, y_4,$ and $y_5$ are general and have $- \ord_P(y_i) =
-1$ by Riemann Roch. \todo{Understand why/whether we need to cite 
-Lemma 5.4.7.} To complete the proof of (a) we only need show these
-elements generate $R$ over $R'$. We can first see that the
-following is a $k$ basis for $R$ over $R'$:
+Since we are genus 0, general
+elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P(y_i) =
+1$. \todo{Understand why/whether we need to cite 
+Lemma 5.4.7.}  We see by pole order considerations that
 
@@
 	\begin{split}
-		&\langle y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \rangle \\
-		&+\langle y_3^ay_4, y_3^by_5 \mid a \geq 0, b \geq 0 \rangle
+	S=	&\{ y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
+		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \} \\
+	\cup \;&\{y_3^ay_4, y_3^by_5 \mid a \geq 0, b \geq 0 \}
 	\end{split}
@@
 
-\noindent
+\noindent forms a $k$ basis for $R$ over $R'$, which concludes part (a) of the proof.
+
+Letting
+\begin{align*}
+	T = & \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\} \\
+	   + & \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
+\end{align*}
+we see that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, immediately implying part (b) of this proof.
+
+\iffalse{
 To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
@@
 generators of $J$, completing (b).
+}\fi
 

### 2015-06-27 stacky_write_up/spin_cring.tex
comment on background todo, change font, cite fix

@@
 \usepackage{subfiles}
-\usepackage{mathpazo}
+%\usepackage{mathpazo} not a huge fan
 \usepackage{euler}
@@
 
-\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e.}
+\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e. Robin: Aren't the base cases suitable examples?}
 
@@
 
-We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an analog of Lemma ~\ref[Theorem 8.5.7]{vzb:stacky}
+We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
+analog of ~\cite[Theorem 8.5.7]{vzb:stacky}
 

### 2015-06-27 stacky_write_up/spin_cring.tex
improved intro, added some comments

@@
 Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many
-directions. A divisor $\Delta \in \di X$ is a {\bf log divisor} if
-$\Delta = \sum_{i=1}^{n}P_i \in \di X,$ with $P_i$ distinct points of $X$. Let
-$\sx$ denote a tame separably rooted curve over a
-field $k$ so that $X$ is the coarse space of $\sx$, as defined in
-\cite[Section 5.2]{vzb:stacky}, with $\di \sx = \di X \oplus \left(\bigoplus_{i
-= 1}^r \langle \frac{1}{e_i}P_i \rangle \right),$ so that $e_i \in \BZ$. Let $K_
-\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
-say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
-\in \di \sx$ a {\bf log half-canonical divisor}, also known as a theta-characteristic, on the {\bf log stacky curve} $(\sx,\Delta)$ if
-$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\deg \Delta =\delta,$ then we
-say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$. A
-{\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $(\sx,\Delta)$
-is a log stacky curve and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
+directions. 
+If $X$ is a curve, then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
+$$\di \sx = \di X \oplus \left(\bigoplus_{i
+= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
+As is done in \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points.
+A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
 The central object of study in this paper is the {\bf log spin
-canonical ring} of $(X,\Delta,L)$ is
+canonical ring} of $(\sx,\Delta,L)$ is
 \begin{align*}
@@
 
-\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e. Robin: Aren't the base cases suitable examples?}
+\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e.
+Robin: Aren't the base cases suitable examples?
+Aaron: Those don't show it for general e, do they?
+I don't think we really need an example, just a remark somewhere that one cannot really hope to do better than e, 2e somewhere.}
 
@@
 \begin{enumerate}
+	\item Possibly include some of the following notation, it it isn't dealt with well in the background.
+
+ A divisor $\Delta \in \di X$ is a {\bf log divisor} if
+$\Delta = \sum_{i=1}^{n}P_i \in \di X,$ with $P_i$ distinct points of $X$. \todo{Do we want to assume they are distinct?} Let
+$\sx$ denote a tame separably rooted curve over a
+field $k$ so that $X$ is the coarse space of $\sx$, as defined in
+\cite[Section 5.2]{vzb:stacky}, with $\di \sx = \di X \oplus \left(\bigoplus_{i
+= 1}^r \langle \frac{1}{e_i}P_i \rangle \right),$ so that $e_i \in \BZ$. Let $K_
+\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
+say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
+\in \di \sx$ a {\bf log half-canonical divisor}, also known as a theta-characteristic, on the {\bf log stacky curve} $(\sx,\Delta)$ if
+$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\deg \Delta =\delta,$ then we
+say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
+
 	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
@@
 In Lemma \ref{lem:sat-1} we provide an inductive method to strengthen
-O'Dorney's result \todo{cite theorem 8} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
+O'Dorney's result \todo{cite theorem 8, Aaron: If you want to cite Theorem 8, just do \cite[Theorem 8]{dorney:canonical}} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
 }{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
@@
 \end{defn}
-We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is}
+We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is, Aaron: I suggest not to use the phrase ``leave as an exercise'' in a paper}
 We now offer a lemma that allows us to inductively add $\mathbb{Q}$-points to a divisor and describe the new generators and relations.
@@
 \todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number.
-What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$}
+What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$.
+Aaron: By all means, please suggest better notation and we can discuss it.
+However, I think your particular concern is well answered because we include the further subscript $i$.
+That is, $y_{1,e_1} \neq y_{2,e_2}$ even if $e_1 = e_2=5$, because $y_{1,5}$ and $y_{2,5}$ are different variables.
+Another thing to note here is that $e_i' = e_i + 2,$ so that the two will never be equal.
+Does this assuage your concern?
+Also, Further, when I read David's paper, he used this notation, and I was never confused by this notation.}
 \begin{enumerate}

### 2015-06-27 stacky_write_up/spin_cring.tex
minor edits to intro to section 3

@@
 \begin{enumerate}
+	\item Include explanation of Kodaira spencer, and use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic geometry.
 	\item Possibly include some of the following notation, it it isn't dealt with well in the background.
@@
 \label{sec:induction}
-First we present the general inductive Lemmata that will be applied
-for all genera. We offer various inductive Lemmata that will allow
-us to add fractional point $\frac{\alpha}{\beta}P$ to a $\BQ$
- divisor $D$ of $X$ and describe the new generators and relations
-of $R_{D + P}$ not in $R_D$. Next, we provide a method specific to
-the case of stacky canonical divisors, which
-under certain conditions allows us to transfer information about
-the generators and relations of the half canonical ring of a stacky
-curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a
-stacky curve $\sx$ with signature $(g; e_1, \ldots, e_\tau; 0)$
-where each $e_i\in \{e_i', e_i' + 2\}$.
+First we present several lemmata which play a crucial role in the inductive step of the proof of the main theorem, Theorem ~\ref{thm:main}.
+In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$.
+While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-orders}
 
@@
 \ssec{Inductive Lemmata: Adding Points}
-\label{ssec:add_pts}
+\label{ssec:add-points}
 In this section, we prove various inductive statements under the following setup:
@@
 \ssec{Raising Stabilizer Orders}
-\label{ssec:ram_orders}
+\label{ssec:raise-orders}
 In this subsection, we aim to prove Lemma
@@
 \end{proof}
+
+\begin{rem}
+\label{rem:raise-fractional-order}
+It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-orders} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical.
+In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
+\end{rem}
 

### 2015-06-27 stacky_write_up/spin_cring.tex
comments on first page of inductive section

@@
 In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$.
-While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-orders}
+While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}
 
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
 Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
-
-First, let's introduce some notation from O'Dorney.  \cite{dorney:canonical}
+\todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph?
+Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
+
+First, we introduce some notation from O'Dorney.  \cite{dorney:canonical}
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha\in \mathbb{Z}, \beta\in \mathbb{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha, \beta \in \mathbb{Z}, \beta> 0$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
@@
 \]
+\todo{This Moreover statement shouldn't really be part of the definition.}
 \end{defn}
@@
 
-In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\mathbb{P}^1$ consisting of at most 2 points in its support, showing that it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
-He further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
+In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical?
+I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
+Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
+\todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
+\todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper.
+Can you state this more precisely, or possibly just remove it.}
 
@@
 }{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
-0(X, \lfloor D \rfloor) > 0$; our result implies that $R_D$ is generated in
+0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
 degrees at most $e = \max(\beta_i)$ with relations generated in
-degrees at most $2e$.  Furthermore, given additional constraints on $H^0(
+degrees at most $2e$.
+\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
+If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
 X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-same Riemann-Roch arguments in arbitrary genus. 
-To do this, we extend an inductive result by Voight and
+same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
+To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
 Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
-divisors. \todo{cite theorem 8.3.1}
+divisors. \todo{cite theorem 8.3.1} \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
 
 First, however, we give a criteria to determine if a set of monomials generates the initial ideal of relations, and define notation for a type of monomial ordering.
+\todo{Perhaps say which parts of the proofs of which future lemmas it will be used in?}
+
+\todo{Somehow, I feel like most of this page can be cut, it seems to mostly vaguely describe what we are doing, and takes up a lot of space.}
 
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
+Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such

### 2015-06-27 stacky_write_up/spin_cring.tex
more comments on section 3

@@
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
+Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m,$
+and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
+$R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively \todo{Usually respectively is applied when two things are said at the same time, this doesn't seem to fit the usual gramattical pattern}.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
 \begin{enumerate}
-\item[(\ref{lem:relations_from_generators_induction}.1)]  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
+\item[(\ref{lem:relations_from_generators_induction}.1)] \todo{It would probably be clearer to just call these conditions 1,2,3 instead of 3.2.1...}  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
 \item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
@@
 \begin{align*}
-	& S \\
-	\cup \; &\langle T\rangle \\
-	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+	S	\cup \; \langle T\rangle \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
 \end{align*}
 \end{enumerate}
-Then 
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
+Then,
+\begin{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+	+ \langle T \rangle.
 \end{align*}
@@
 \begin{proof}
-Suppose monomial $f\in T$ has a pole order $a$ at $P$.
-Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
+Suppose a monomial $f\in T$ has a pole order $a$ at $P$.
+Then, since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f = (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
 This demonstrates that
 \begin{align*}
-	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
+	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
+\end{align*}
+\todo{Aaron: I don't understand why this holds}
 Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
 \begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
-		     & + \langle T \rangle.
-\end{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
+\end{align*}
+\todo{Aaron: Why can't the initial term lie in S?}
+\todo{It might be helpful to say where you use conditions 1 2 and 3.}
 \end{proof}
 
-As suggested by the previous lemma, we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
+As suggested by the previous lemma, \todo{Reference the lemma, instead of using previous, since things might get moved around} we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
+\todo{Again, reference this}
 \begin{defn}
-We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff one of the following holds
+We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff \todo{It's better not to use abbreviations like iff in papers.
+Also, usually in definitions, one uses if in place of iff.} one of the following holds
 \begin{enumerate}
 \item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$
+\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$ \todo{Order at which point, in this line and the next}
 \item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative.
+\todo{I do not understand what this means, maximal under what ordering?
+Also, }
 \end{enumerate}

### 2015-06-27 stacky_write_up/spin_cring.tex
comments to page 3 of induction section

@@
 \todo{I do not understand what this means, maximal under what ordering?
-Also, }
+Also, what expression are you talking about?}
 \end{enumerate}
 \end{defn}
-We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is, Aaron: I suggest not to use the phrase ``leave as an exercise'' in a paper}
-We now offer a lemma that allows us to inductively add $\mathbb{Q}$-points to a divisor and describe the new generators and relations.
+We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is, Aaron: I suggest not to use the phrase ``leave as an exercise'' in a paper.}
+We now offer \todo{Maybe state instead of offer?} a lemma that allows us to inductively add $\mathbb{Q}$-points \todo{$\BQ$ points usually refers to maps to $\spec \BQ$.
+Maybe we can just say a rational multiple of a poitn?} to a divisor and describe the new generators and relations.
+
+\begin{defn}
+\label{}
+If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
 
@@
 \label{lem:sat-1}
-Let $X$ be a genus $g$ curve with a $\BQ$-divisor $\halfcan'$
+Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
-$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0$ for all $x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.
-Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\sigma$ with relations generated
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generators (in the necessary degrees \todo{What does this mean?})
+$u, x_1, \ldots, x_m$ with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\sigma$ with relations generated
 in degree at most $\tau$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
@@
 	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
-	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
+	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
 	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
@@
 be the positive best lower approximations of $\frac{\alpha}{\beta}$.
-Then
+Then,
 
@@
 \item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$, when viewed as sections of $\so_{\halfcan'}$
+degree $d_i$ and has a pole at $P$ of degree $c_i$, when viewed as sections of $\so_{\halfcan'}$ \todo{Clearer to say $\deg (y_i) = d_i,\ord_P^{L'} = c_i.$}
 
@@
 \]
-and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with a block order.
+and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with a block order \todo{it should be called block order, instead of ``a block order''}.
 If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
@@
 \begin{align*}
-	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 &+ \langle U_i: 1 \le i \le n-1 \rangle\\
-										 &+ \langle V \rangle\\
+	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
+										 + \langle U_i: 1 \le i \le n-1 \rangle
+										 + \langle V \rangle\\
 \end{align*}
@@
 $V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
- and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_i^{a_i}$ with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ such that
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_i^{a_i}$ \todo{should this be $y_j^{a_j}$ instead of $y_i^{a_i}$?} with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ \todo{this conflation of $j$ and $i$ is confusing me, is $j$ ranging over all indices from $1$ to $i$?} such that
 $\sum_{j=1}^i a_j c_j \ge c_{j+1}$
 and there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ such that with all $b_j\le a_j$ and 
-$\sum_{j=1}^i b_jc_j\ge c_{j+1})\}$.  \\
-
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with relations $I$ generated over $I'$ by relations in degree is generated $\max(2\beta, \beta + \sigma)$ (where $\sigma=\max(\deg(x_i))$).
+$\sum_{j=1}^i b_jc_j\ge c_{j+1})\}$. \todo{what is this close bracket closing?}  \\
+
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with relations $I$ generated over $I'$ by relations in degree is generated $\max(2\beta, \beta + \sigma)$ {\rm(}where $\sigma=\max(\deg(x_i))$ \todo{include what indexing set this $i$ is over ($ i = 1,\ldots, m$).}{\rm)}.
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
@@
 By
-our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
+Equation ~\ref{eqn:deg1_sat_ind_dim}, for any $d
 \in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
@@
 \noindent
-so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
+\todo{why is there no floor in the above equation, as in ~\ref{eqn:deg1_sat_ind_dim}} so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
 order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
 \beta} \rfloor \}$. We will use O'Dorney's method of best lower approximations to
-construct the $y_i$'s as desired. \todo{cite where}
+construct the $y_i$'s as desired. \todo{cite where} \todo{What do we desire about the $y_i$?}
 
@@
 \noindent
-be the positive best lower approximation of $\frac{
-\alpha}{\beta}$ as described in the lemma's statement.  Note that elements of $H^0(X, d\halfcan)$ have pole of
+be the positive best lower approximations of $\frac{
+\alpha}{\beta}$ as described in this lemma's statement. Note that elements of $H^0(X, d\halfcan)$ have poles of
 orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
@@
 For any $j < i \in \mathbf{N}$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$, so for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ for all $z_j$, $\prod_{j=1}^n z_j$ must satisfy
+\todo{In the next equations, are we viewing these as rational functions on the structure sheaf or on $L'$, what point is the order of $z_j$ taken with respect to?}
 \[
-	\frac{-\ord_P(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
+	\frac{-\ord_P(z_i)}{\deg(z_i)} < \frac{c_i}{d_i},
 \]
@@
 \noindent
-so we have the pole order of $\prod_{j=1}^n z_j$ is 
+so we have the pole order of $\prod_{j=1}^n z_j$ is \todo{what is the following sum taken over?}
 \[
@@
 Therefore, we will have to work with orders of zeros of poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
-Hence, we introduce the following notation.
-
-\begin{defn}
-\label{}
-If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
 

### 2015-06-27 stacky_write_up/spin_cring.tex
ref fix, iffalse -> %, minor g1 table fix

@@
 In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$.
-While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}
+While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-order} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-order} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}
 
@@
 
-\iffalse{
-Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
-\frac{\alpha}{\beta}$ is not a best lower approximation than we can
-construct an element in degree $d$ with pole degree $c$ by either $y
-_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-same conditions.
+%Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
+%\frac{\alpha}{\beta}$ is not a best lower approximation than we can
+%construct an element in degree $d$ with pole degree $c$ by either $y
+%_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
+%same conditions.
 This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.
 In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.
-
-Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.
+%
+%Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.
 Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if
-$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
-successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
-convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
-expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
-is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
-\[
-	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-\]
-
-\noindent
-giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
-the beginning}
-
-Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
-< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
-basis element of the form described above: $y_n^0 y_j y_i u^0$). 
-Choose the maximal $l$ such that $c_h \le c_i + c_j$; since $1 < d_i
-\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
-so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
-Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
-$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
-= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
-best lower approximation of $\frac{\alpha}{\beta}$ with denominator
-larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
-know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
-Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
-1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
-h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
-appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
-$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
-follow a similar technique as in the previous paragraph to cancel
-out poles of $y_i y_j$ at $P $ to find
-\[
-	y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-	u^{b_l}\in R_D
-\]
-
-\noindent
-implying a relation with initial term $y_i y_j$.
-
-Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
-$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
-\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
-{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
-with the same pole order; following the same method as the previous
-two paragraphs we find
-\[
-	y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-\]
-
-\noindent
-Similarly if $i = 1$, then we get the same result using
-\[
-	y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
-\]
-
-\noindent
-In both cases we deduce that $y_i y_j$ is an initial term of some relation.
-
-Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
-1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
-then there are no relations with initial term a power of $y_i$
-and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
-note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
-{reference to Evan's paper where he proves this} Therefore, if $i >
- 1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
-in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
-Following a similar technique to the previous paragraphs we find
-\[
-	(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-\]
-
-\noindent
-Similarly if $i = 1$ then
-\[
-	(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
-\]
-
-\noindent
-In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation.
-
-Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
-generated by the initial terms described in the previous paragraphs
-together with $\initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
-
-We show that $J$ is in fact all of the initial ideal. Suppose
-$f$ is a non-constant monomial that does not lie within $J$.
-Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
-there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
-some $x_j \mid f$ or else we would have $y_i x_j \mid f$
-contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
-i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
-element of a relation and divides $f$. If $d_i = 1$ as well, then
-we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
-$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
-\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
-f$. We observe that the remaining elements are precisely those of
-the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
-which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
-, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
-Therefore, by dimension counting (in each degree), we see that $J$
-is the initial ideal of $I$. 
-}\fi
+%$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
+%successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
+%\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
+%\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
+%convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
+%with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
+%is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
+%expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
+%is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
+%\[
+	%x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
+%\]
+%
+%\noindent
+%giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
+%the beginning}
+%
+%Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
+%< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
+%basis element of the form described above: $y_n^0 y_j y_i u^0$). 
+%Choose the maximal $l$ such that $c_h \le c_i + c_j$; since $1 < d_i
+%\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
+%so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
+%Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
+%$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
+%= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
+%best lower approximation of $\frac{\alpha}{\beta}$ with denominator
+%larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
+%know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
+%Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
+%1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
+%h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
+%appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
+%$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
+%follow a similar technique as in the previous paragraph to cancel
+%out poles of $y_i y_j$ at $P $ to find
+%\[
+	%y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
+	%u^{b_l}\in R_D
+%\]
+%
+%\noindent
+%implying a relation with initial term $y_i y_j$. 
+%
+%Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
+%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
+%\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
+%{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
+%with the same pole order; following the same method as the previous
+%two paragraphs we find
+%\[
+	%y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
+%\]
+%
+%\noindent
+%Similarly if $i = 1$, then we get the same result using
+%\[
+	%y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
+%\]
+%
+%\noindent
+%In both cases we deduce that $y_i y_j$ is an initial term of some relation.
+%
+%
+%Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
+%1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
+%then there are no relations with initial term a power of $y_i$
+%and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
+%note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
+%{reference to Evan's paper where he proves this} Therefore, if $i >
+ %1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
+%in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
+%Following a similar technique to the previous paragraphs we find
+%\[
+	%(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
+%\]
+%
+%\noindent
+%Similarly if $i = 1$ then
+%\[
+	%(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
+%\]
+%
+%\noindent
+%In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation. 
+%
+%Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
+%generated by the initial terms described in the previous paragraphs
+%together with $\initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
+%
+%We show that $J$ is in fact all of the initial ideal. Suppose
+%$f$ is a non-constant monomial that does not lie within $J$.
+%Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
+%there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
+%some $x_j \mid f$ or else we would have $y_i x_j \mid f$
+%contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
+%i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
+%element of a relation and divides $f$. If $d_i = 1$ as well, then
+%we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
+%$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
+%\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
+%f$. We observe that the remaining elements are precisely those of
+%the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
+%which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
+%, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
+%Therefore, by dimension counting (in each degree), we see that $J$
+%is the initial ideal of $I$.
 
@@
 
-\iffalse{
-For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
-we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
-Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
+%For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
+%we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
+%Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
 In both cases we induce a relation, with initial term described in the lemma's statement.
@@
 %Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
-}\fi
+
 \end{proof}
@@
 
-\iffalse{
-To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
-_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-,$ elements of degree $d$ in the claimed basis of
-~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-\rfloor $ and $b = d \bmod 3$, we have that the elements
-
-\begin{align*}
-	x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
-3+b}
-\end{align*}
-
-\noindent
-are precisely $a$ elements, which are all independent as they have
-distinct pole orders at $P$. This completes part (a).
-
-To show part (b), note that the generators in
-~\ref{eqn:add_one_generator} are precisely a set of monomials which
-generate $k[x, y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-suffices to show that all generators of $J$ lie in $in_\prec(I)$.
-
-This follows, since there exist constants $A_{i,j} \in k$ for $4
-\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-elements $w_{i,j} \in R'$ so that the following linear combinations
-of elements lie in $R'$.
-
-\begin{align*}
-	&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
-	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
-	&y_4^2 + B_1 y_3 y_5 \\
-	&y_4 y_5 + B_2 y_3^2 x_3 \\
-	&y_5^2 + B_3 y_3^2 x_4
-\end{align*}
-
-\noindent
-Of course, the initial terms of these elements are precisely the
-generators of $J$, completing (b).
-}\fi
+%To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
+%_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
+%suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
+%,$ elements of degree $d$ in the claimed basis of
+%~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
+%\rfloor $ and $b = d \bmod 3$, we have that the elements
+%
+%\begin{align*}
+	%x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
+%3+b}
+%\end{align*}
+%
+%\noindent
+%are precisely $a$ elements, which are all independent as they have
+%distinct pole orders at $P$. This completes part (a).
+%
+%To show part (b), note that the generators in
+%~\ref{eqn:add_one_generator} are precisely a set of monomials which
+%generate $k[x, y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
+%suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+%
+%This follows, since there exist constants $A_{i,j} \in k$ for $4
+%\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
+%elements $w_{i,j} \in R'$ so that the following linear combinations
+%of elements lie in $R'$.
+%
+%\begin{align*}
+	%&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
+	%\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
+	%&y_4^2 + B_1 y_3 y_5 \\
+	%&y_4 y_5 + B_2 y_3^2 x_3 \\
+	%&y_5^2 + B_3 y_3^2 x_4
+%\end{align*}
+%
+%\noindent
+%Of course, the initial terms of these elements are precisely the
+%generators of $J$, completing (b).
 
@@
 \label{rem:raise-fractional-order}
-It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-orders} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical.
+It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-order} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical.
 In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
@@
 
-\begin{longtable}	{| c || c | c | c |}
+\begin{longtable}	{| c || c | c |}
 	\hline
@@
 \end{longtable}
+
 \begin{center}
@@
 \todo{Possibly add an autoincrement counter to deal with table numbering}
+
 \begin{center}
@@
 \end{enumerate}
-\iffalse
-\noindent
-Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
-{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
-\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
-(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
-$in_\prec(I')$ is minimally generated by products of two monomials.
-\fi
+
+%\noindent
+%Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
+%{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
+%\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
+%(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
+%$in_\prec(I')$ is minimally generated by products of two monomials.
+
 \end{lem}
@@
 degree $e = 7$ with relations up to degree $2e = 14$, as desired.s
-\iffalse
-We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
-since $e_i = 9 > e$ for all $i \in J$.
-\fi
+
+%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
+%since $e_i = 9 > e$ for all $i \in J$.
 
@@
 
-\iffalse
-Through the application of two inductively adding 
-points via Lemma ~\ref{lem:sat-3} and inductively raising
-stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
-we obtain Theorem ~\ref{thm:g-0-main} for any
-log spin curve $(\sx, \Delta, L)$ with
-signature $\sigma$ covered by this induction process.
-In particular, this induction process covers all signatures $\sigma
-= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
-for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
-\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
-Before we prove the main theorem, we describe the cases not be
-covered by induction.
-\fi
+%Through the application of two inductively adding 
+%points via Lemma ~\ref{lem:sat-3} and inductively raising
+%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
+%we obtain Theorem ~\ref{thm:g-0-main} for any
+%log spin curve $(\sx, \Delta, L)$ with
+%signature $\sigma$ covered by this induction process.
+%In particular, this induction process covers all signatures $\sigma
+%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
+%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
+%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
+%Before we prove the main theorem, we describe the cases not be
+%covered by induction.
 

### 2015-06-27 stacky_write_up/spin_cring.tex
section 3 transitions

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$.
-While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}
+While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:sat-2} and ~\ref{lem:sat-3} are more specific to half-canonical divisors.
 
@@
 In this section, we prove various inductive statements under the following setup:
-Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
 Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
-\todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph?
-Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-
-First, we introduce some notation from O'Dorney.  \cite{dorney:canonical}
+
+First, let's introduce some notation from O'Dorney.  \cite{dorney:canonical}
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha, \beta \in \mathbb{Z}, \beta> 0$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha\in \mathbb{Z}, \beta\in \mathbb{N}$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
@@
 \]
-\todo{This Moreover statement shouldn't really be part of the definition.}
 \end{defn}
@@
 
-In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical?
-I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
-Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
-\todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
-\todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper.
-Can you state this more precisely, or possibly just remove it.}
-
-In Lemma \ref{lem:sat-1} we provide an inductive method to strengthen
-O'Dorney's result \todo{cite theorem 8, Aaron: If you want to cite Theorem 8, just do \cite[Theorem 8]{dorney:canonical}} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
+In ~\cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\mathbb{P}^1$ consisting of at most 2 points in its support, showing that it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
+He further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
+
+In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
+O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
 }{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
-0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
+0(X, \lfloor D \rfloor) > 0$; our result implies that $R_D$ is generated in
 degrees at most $e = \max(\beta_i)$ with relations generated in
-degrees at most $2e$.
-\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
-If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
+degrees at most $2e$.  Furthermore, given additional constraints on $H^0(
 X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
-To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
-Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
-divisors. \todo{cite theorem 8.3.1} \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
+same Riemann-Roch arguments in arbitrary genus. 
+To do this, we extend an inductive result by Voight and
+Zureick-Brown ~\cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
+divisors.
 
 First, however, we give a criteria to determine if a set of monomials generates the initial ideal of relations, and define notation for a type of monomial ordering.
-\todo{Perhaps say which parts of the proofs of which future lemmas it will be used in?}
-
-\todo{Somehow, I feel like most of this page can be cut, it seems to mostly vaguely describe what we are doing, and takes up a lot of space.}
 
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m,$
-and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively \todo{Usually respectively is applied when two things are said at the same time, this doesn't seem to fit the usual gramattical pattern}.
+Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such
 \begin{enumerate}
-\item[(\ref{lem:relations_from_generators_induction}.1)] \todo{It would probably be clearer to just call these conditions 1,2,3 instead of 3.2.1...}  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
+\item[(\ref{lem:relations_from_generators_induction}.1)]  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
 \item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
@@
 \begin{align*}
-	S	\cup \; \langle T\rangle \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+	& S \\
+	\cup \; &\langle T\rangle \\
+	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
 \end{align*}
 \end{enumerate}
-Then,
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
-	+ \langle T \rangle.
+Then 
+\begin{align*}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
 \end{align*}
@@
 \begin{proof}
-Suppose a monomial $f\in T$ has a pole order $a$ at $P$.
-Then, since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f = (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
+Suppose monomial $f\in T$ has a pole order $a$ at $P$.
+Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
 This demonstrates that
 \begin{align*}
-	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
-\end{align*}
-\todo{Aaron: I don't understand why this holds}
+	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
 Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
 \begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
-\end{align*}
-\todo{Aaron: Why can't the initial term lie in S?}
-\todo{It might be helpful to say where you use conditions 1 2 and 3.}
+	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
+		     & + \langle T \rangle.
+\end{align*}
 \end{proof}
 
-As suggested by the previous lemma, \todo{Reference the lemma, instead of using previous, since things might get moved around} we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
-\todo{Again, reference this}
+As suggested by the previous lemma, we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
 \begin{defn}
-We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff \todo{It's better not to use abbreviations like iff in papers.
-Also, usually in definitions, one uses if in place of iff.} one of the following holds
+We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff one of the following holds
 \begin{enumerate}
 \item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$ \todo{Order at which point, in this line and the next}
+\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$
 \item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative.  
-\todo{I do not understand what this means, maximal under what ordering?
-Also, }
 \end{enumerate}
@@
 
+Lemma \ref{lem:sat-1} leads to the the following corollaries.
+\todo{do we want this here?}
+\begin{cor}\label{cor-gen-0-with-log}
+If $(\sx, \halfcan, \Delta)$ is a stacky curve with signature $(g; e_1, \ldots, e_n; \delta)$ with $g=0$ and $\delta>0$, then $R_\halfcan$ is generated in degree at most $e=\max(e_i)$ with relations generated in degree at most $2e$.
+\end{cor}
+\begin{proof}
+By remark \ref{rem:delta-not-1}, $\delta\ge 2$ so $\halfcan$ is linearly equivalent to an effective divisor.  Thus, we can recursively apply Lemma \ref{lem:sat-1} to prove the corollary.
+\end{proof}
+
 \todo{Something about fractional weight modular forms?}
+\iffalse{
+\begin{cor}
+Let $R_\halfcan$ be the fractional weight canonical ring associated to a fractional $\frac{2\alpha}{\beta}$-weight cusp forms with $\frac{\alpha}{\beta}$ in reduced form and $\beta\ge 3$, with signature $(g; e_1, \ldots, e_n; \delta)$ where $g=0$.
+Then $R_\halfcan$ is generated in degrees at most $e = \max(e_i)$ with relations generated in degrees at most $2e$.
+\end{cor}
+\begin{proof}
+Let $K$ be the log canonical divisor of the curve $(\sx, \Delta)$ associated to the $\frac{2\alpha}{\beta}$ weight cusp forms.
+We see that $\frac{\beta}{\alpha}\halfcan_\sx\sim K_\sx$, so the floors of each
+
+Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.
+Thus, since $\beta\ge 3$, $\deg(K_\sx)\ge 0$.
+Thus $\deg(
+\end{proof}
+}\fi
+
+We now restrict our attention to log canonical rings of stacky curves.
+The previous lemma deals with most relevant induction cases when inducting from a half-canonical ring saturated at one.
+We complement it with the following two lemmas that allow us to induct under certain conditions when the half-canonical ring is saturated at two and three.
 
@@
 
-\todo{transition!}
+One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only these three cases (Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}) are needed for the remainder of this paper.
+Instead we turn now to inductive methods to incrementally increase the $e_i$s.
+Combined with the previous lemma on adding points, these will provide all the necessary inductive tools.
 

### 2015-06-27 stacky_write_up/spin_cring.tex
more edits to induction

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  Moreover, a set $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
+c_i $ at $P$.  Moreover, a set $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ \todo{how is this a set?} elements in $(R_{D})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
 d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
@@
 
-For any $j < i \in \mathbf{N}$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$, so for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ for all $z_j$, $\prod_{j=1}^n z_j$ must satisfy
+For any $j, i \in \mathbb{N}$, with $i < j$, we have $\frac{c_i}{d_i} > \frac{c_j}{d_j}$.
+So, for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ \todo{are the $i$ and $j$ mismatched?} for all $z_j$, \todo{It might be clearer to say for all $j \in \{1,\ldots, ?\},$ since the subscript is really want is changing, or instead for all $j$ with $1 \leq j \leq ?$ } $\prod_{j=1}^n z_j$ must satisfy \todo{It seems like each $z_j$ must satisfy this, instead of the product satisfying this}
 \todo{In the next equations, are we viewing these as rational functions on the structure sheaf or on $L'$, what point is the order of $z_j$ taken with respect to?}

### 2015-06-27 stacky_write_up/spin_cring.tex
fix previous merge conflict

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 \label{sec:induction}
-First we present several lemmata which play a crucial role in the inductive step of the proof of the main theorem, Theorem ~\ref{thm:main}.
-In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$.
-While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-order} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-order} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}
+First we present several lemmata which play a crucial role in the
+inductive step of the proof of the main theorem, Theorem
+~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove
+Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
+which describe the generators and relations of $R_{D + \frac{\alpha
+}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di
+X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in
+Subsection ~\ref{ssec:raise-orders}, we prove Lemma
+~\ref{lem:raise-stacky-order}, which the generators and relations 
+of the log spin canonical ring curve with signature $(g; e_1', 
+\ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a 
+curve with a certain subset of the $e_ i'$ incremented by $2$. 
+While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
+context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
+half-canonical divisors, although even Lemma
+~\ref{lem:raise-stacky-order} has certain generalizations, as noted
+in Remark ~\ref{rem:raise-fractional-order}
 
@@
 
-In Lemma \ref{lem:sat-1} we provide an inductive method to strengthen
-O'Dorney's result \todo{cite theorem 8, Aaron: If you want to cite Theorem 8, just do \cite[Theorem 8]{dorney:canonical}} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
+In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
+O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
 }{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
@@
 To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
-Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
-divisors. \todo{cite theorem 8.3.1} \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
+Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
+divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
 
@@
 
+\todo{label/ref of long tables doesn't work!}
+
 \begin{example}
@@
 \todo{Possibly add an autoincrement counter to deal with table numbering}
+\todo{label/ref of long tables doesn't work!}
 

### 2015-06-27 stacky_write_up/spin_cring.tex
fix all longtable numbering/labeling

@@
 \begin{longtable}	{| c || c | c |}
+	\caption{Genus 1 Base Cases}
+	\label{table:g-1-base}
+
+	\tabularnewline
+
 	\hline
@@
 \end{longtable}
-
-\begin{center}
-\label{table:g-1-base}
-Genus 1 base cases
-\end{center}
-
-\todo{label/ref of long tables doesn't work!}
 
@@
 \begin{longtable}	{| c || c | c |}
+	\caption{Genus 1 Exceptional Cases}
+	\label{table:g-1-exceptional}
+
+	\tabularnewline
+
 	\hline
@@
 \end{longtable}
-\todo{Possibly add an autoincrement counter to deal with table numbering}
-\todo{label/ref of long tables doesn't work!}
-
-\begin{center}
-\label{table:g-1-exceptional}
-Genus 1 exceptional cases
-\end{center}
 
@@
 	{| c | c |}
+	\caption{Genus 0 Saturation}
+	\label{table:g-0-sat}
+
+	\tabularnewline
+
 	\hline
@@
 
-\begin{center}
-Genus 0 saturation \todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
-\end{center}
+\todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
 
@@
 	{| c || c | c | c |}
+	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
+	\label{table:g-0-base-cases}
+
+	\tabularnewline
+
 	\hline
@@
 \end{longtable}
-
-\begin{center}
-Genus 0 non-effective base cases generator/relations
-\end{center}
 
@@
 	{| c | c | c || c | c |}
+	\caption{Genus 0 Non-Effective Base Cases (Ad-iii)}
+	\label{table:g-0-base-cases-admissibility}
+
+	\tabularnewline
+
 	\hline
@@
 \end{longtable}
-
-\begin{center}
-Genus 0 non-effective base cases (Ad-iii)
-\end{center}
 
@@
 	{| c || c | c | c |}
+	\caption{Genus 0 Exceptional Cases}
+	\label{table:g-0-exceptional}
+
+	\tabularnewline
+
 	\hline
@@
 \end{longtable}
-
-\begin{center}
-\label{table:g-0-exceptional}
-Genus 0 exceptional cases
-\end{center}
 

### 2015-06-27 stacky_write_up/spin_cring.tex

@@
 \]
-and for $i \in \mathbf{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
+and for $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
 \[
@@
 \begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbf{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
+If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
 \end{rem}

### 2015-06-27 stacky_write_up/spin_cring.tex
moved O'Dorney mention from section3 to intro

@@
 research.
+
+\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
+In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical?
+I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
+Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
+\todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
+\todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper.
+Can you state this more precisely, or possibly just remove it.}
+
+In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
+O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
+}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
+0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
+degrees at most $e = \max(\beta_i)$ with relations generated in
+degrees at most $2e$.
+\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
+If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
+X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
+same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
+To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
+Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
+divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
 
@@
 
-In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical?
-I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
-Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
-\todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
-\todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper.
-Can you state this more precisely, or possibly just remove it.}
-
-In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
-O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
-}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
-0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
-degrees at most $e = \max(\beta_i)$ with relations generated in
-degrees at most $2e$.
-\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
-If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
-X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
-To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
-Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
-divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
+Previously discussed O'Dorney's result and our improvement when restricting to effective. Moved to Intro.
+\todo{new transition}
 

### 2015-06-28 stacky_write_up/spin_cring.tex
add coln to g0 sat table, change ref to table

@@
 \begin{longtable}
-	{| c | c |}
+	{| c | c || c |}
 	\caption{Genus 0 Saturation}
@@
 	\hline
-	Signature & Saturation \\
+	Signature & Note & Saturation \\
 	\hline
@@
 
-	$(0; 3, 3, 3; 0)$ & $\infty$ \\	\hline
-
-	$(0; 3, 3, 5; 0)$ & $18$ \\	\hline
-
-	$(0; 3, 3, 7; 0)$ & $12$ \\	\hline
-
-	$(0; 3, 3, 9; 0)$ & $12$ \\	\hline
-
-	$(0; 3, 5, 5; 0)$ & $8$ \\	\hline
-
-	$(0; 5, 5, 5; 0)$ & $8$ \\	\hline
-
-	$(0; 3, 3, 3, 3; 0)$ & $6$ \\	\hline
+	$(0; 3, 3, 3; 0)$ & & $\infty$ \\	\hline
+
+	$(0; 3, 3, 5; 0)$ & & $18$ \\	\hline
+
+	$(0; 3, 3, 7; 0)$ & & $12$ \\	\hline
+
+	$(0; 3, 3, 9; 0)$ & & $12$ \\	\hline
+
+	$(0; 3, 5, 5; 0)$ & & $8$ \\	\hline
+
+	$(0; 5, 5, 5; 0)$ & & $8$ \\	\hline
+
+	$(0; 3, 3, 3, 3; 0)$ & & $6$ \\	\hline
 
@@
 
-	$(0; 3, 3, k; 0)$ & $9$ \\	\hline
-
-	$(0; a, b, c; 0)$ & $5$ \\	\hline
-
-	$(0; e_1, \ldots, e_r; 0)$ & $3$ \\	\hline
+	$(0; 3, 3, k; 0)$ & $k > 9$ & $9$ \\	\hline
+
+	$(0; a, b, c; 0)$ & not listed above & $5$ \\	\hline
+
+	$(0; e_1, \ldots, e_r; 0)$ & not listed above & $3$ \\	\hline
 \end{longtable}
-
-\todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
 
@@
 \geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
-Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
+Table ~\ref{table:g-0-sat}, then this map is surjective
 when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
@@
 
+\todo{induct on cases?}
+
 %Through the application of two inductively adding 
@@
 signature with saturation not equal to
-3, 5, or 9. as seen in the table in Subsection
-~\ref{ssec:g_0_saturation}. Heuristically, these exceptional saturations can be viewed as
-``forcing'' generators (and thus relations) to lie in higher degrees than
-expected.
+3, 5, or 9. as seen in Table ~\ref{table:g-0-sat}. Heuristically,
+these exceptional saturations can be viewed as ``forcing'' generators
+(and thus relations) to lie in higher degrees than expected.
 \end{rem}
@@
 clearly satisfies the conditions of Lemma
-~\ref{lem:sat-3} (recall from Subsection ~\ref
-{ssec:g_0_saturation} that $\sat(\Eff(\sigma_{11})) = 3$), and the
+~\ref{lem:sat-3} (recall from Table ~\ref
+{table:g-0-sat} that $\sat(\Eff(\sigma_{11})) = 3$), and the
 immediate consequence of parts (a) and (c) of Lemma

### 2015-06-28 stacky_write_up/spin_cring.tex
reorder g0 slightly

@@
 
+Now, we check admissibility. By relabelling the
+variables if necessary, we can assume that $x_{7, 1}$ corresponds
+to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
+correspond to the generator with maximal pole order at $P_3$. Use
+the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
+$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
+(Ad-i) of Definition ~\ref{defn:admissible}. We may also choose
+pole orders of the generators such that $y_{i, e_i'}$ is the only
+generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
+in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
+generators lying below the line as seen in Figure ~\ref{fig:377}
+(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
+(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
+and $(2, 2, 3)$ for $z = x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}$
+respectively).
+
+\begin{figure}[H]
+\label{fig:377}
+\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\end{figure}
+
+Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
+$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
+0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
+Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
+\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
+\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
+$\sigma_2, J_2$ is admissible.
+
 %Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
@@
 
-Furthermore, we can directly see that the relations are given
-in degrees $10$ and $14$. In particular, we have relations
-\begin{align*}
-	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
+We can directly see that the relations are given in degrees $10$
+and $14$. In particular, we have relations
+\begin{align*}
+	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 
+0 &\text{ in degree $10$} \\
+	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} 
++ b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
 \end{align*}
@@
 initial ideal $in_\prec(I)$ generated by quadratics under grlex
-with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$
+with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$.
 %These quadratics must also determine minimal generators for $I$ by
 %Lemma ~\ref{lem:minimal_quadratic}.
-Thus, $R'$ is generated up to
-degree $e = 7$ with relations up to degree $2e = 14$, as desired.s
+Thus, $R'$ is generated up to degree $e = 7$ with relations up to
+degree $2e = 14$, as desired.
 
@@
 %since $e_i = 9 > e$ for all $i \in J$.
-
-Admissibility is the remaining condition to check. By relabelling the variables if necessary, we can assume
-that $x_{7, 1}$ corresponds to the generator with maximal pole order
-at $P_2$ and $x_{7, 2}$ correspond to the generator with maximal
-pole order at $P_3$.
-\todo{There is actually a small problem here, which needs to be fixed earlier.
-I think in order to satisfy admissibility, you will actually have to choose $x_{7,i}$ from the beginning to satisfy these constraints, as this will not generically be true.
-Just make sure to put these constraints on the poles when you define $x_{7,i}$} Use the presentation given
-above with $y _{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
-We see that it immediately satisfies (Ad-i) of Definition
-~\ref{defn:admissible}. We may also choose pole orders of the generators
-such that $y_{i, e_i'}$ is the only generator lying on the line
-$-ord_{P_i}(z) = \deg z \frac{3d}{7}$ in the $(\deg z, -ord_{P_i}(z))$
- lattice and with the other generators lying below the line as seen
-in Figure ~\ref{fig:377} (e.g. the pole orders $(-ord_{P_1}(z)$,
-$-ord_{P_2}(z)$, $-ord_{P_3}(z))$ may be chosen to be $(1, 1, 1)$,
-$(1, 2, 2)$, $(2, 3, 2)$, and $(2, 2, 3)$ for $z = x_{3, 1}, x_{5, 1},
-x_{7, 1}, x_{7, 2}$ respectively).
-
-\begin{figure}[H]
-\label{fig:377}
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
-\end{figure}
-
-Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
-$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
-Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
-$\sigma_2, J_2$ is admissible.
 \end{example}

### 2015-06-28 stacky_write_up/spin_cring.tex
Making edits to section 3

--- 2015-06-27 stacky_write_up/spin_cring.tex
@@
 \label{ssec:add-points}
-In this section, we prove various inductive statements under the following setup:
-Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+%In this section, we prove various inductive statements under the following setup:
+%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 
-First, we introduce some notation from O'Dorney.  \cite{dorney:canonical}
+Before proving three inductive lemmas, we introduce some notation from O'Dorney \cite{dorney:canonical}. 
 \begin{defn}\label{den:lower-approximation}
 If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha, \beta \in \mathbb{Z}, \beta> 0$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+\end{defn}
 Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
@@
 \]
-\todo{This Moreover statement shouldn't really be part of the definition.}
-\end{defn}
-\todo{add a picture of lattice}
+Refer to figure \ref{fig:s14/5-lattice} for an example of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
+
+\begin{figure}[H]\label{fig:s14/5-lattice}
+\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+\caption{This figure shows the positive best lower approximations shown as $*$ and other lattice points shown in $o$ of $\frac{14}{5}$.
+Note that they minimally generate lattice in $\mathbb{N}\times \mathbb{N}$ not above $5y=14x$.}
+\end{figure}
 
@@
 
-First, however, we give a criteria to determine if a set of monomials generates the initial ideal of relations, and define notation for a type of monomial ordering.
+Before proving three inductive lemmas, we give a criteria to determine if a set of monomials generates the initial ideal of relations.
 \todo{Perhaps say which parts of the proofs of which future lemmas it will be used in?}
 
-\todo{Somehow, I feel like most of this page can be cut, it seems to mostly vaguely describe what we are doing, and takes up a lot of space.}
-
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m,$
+Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$
 and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively \todo{Usually respectively is applied when two things are said at the same time, this doesn't seem to fit the usual gramattical pattern}.
+$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
 \begin{enumerate}
-\item[(\ref{lem:relations_from_generators_induction}.1)] \todo{It would probably be clearer to just call these conditions 1,2,3 instead of 3.2.1...}  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
-\item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item[(\ref{lem:relations_from_generators_induction}.3)] All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
+\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
+\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
+\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
 \begin{align*}
@@
 \begin{proof}
-Suppose a monomial $f\in T$ has a pole order $a$ at $P$.
-Then, since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f = (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.
+First, notice that $I'\subseteq I$ so 
+\[
+	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
+\]
+
+Now, suppose a monomial $f\in T$ has a pole order $a$ at $P$.
+Then, since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
 This demonstrates that
 \begin{align*}
-	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
-\end{align*}
-\todo{Aaron: I don't understand why this holds}
-Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
+	\initial(I) & \supseteq \langle T \rangle.
+\end{align*}
+
+Finally, suppose $f\in S$.
+Note that by (2) any polynomial $G$ in $x_1,\ldots, x_m, y_1, \ldots, y_n$ with initial term in $S$ cannot have a term in $T$.
+Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), any such polynomial does not map to an element of $R_{\halfcan'}$ (since it has a non-zero constant factor with $f$).
+Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
+Therefore,
+\[
+	\initial(I)\subseteq R_\halfcan-S.
+\]
+
+Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ by (3),
 \begin{align*}
@@
 \end{align*}
-\todo{Aaron: Why can't the initial term lie in S?}
-\todo{It might be helpful to say where you use conditions 1 2 and 3.}
 \end{proof}
 
-As suggested by the previous lemma, \todo{Reference the lemma, instead of using previous, since things might get moved around} we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
+As suggested by the the previous lemma, \todo{Reference the lemma, instead of using previous, since things might get moved around} we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
 \todo{Again, reference this}
 \begin{defn}
-We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff \todo{It's better not to use abbreviations like iff in papers.
-Also, usually in definitions, one uses if in place of iff.} one of the following holds
+We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ if one of the following holds
 \begin{enumerate}
 \item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$ \todo{Order at which point, in this line and the next}
-\item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative.
-\todo{I do not understand what this means, maximal under what ordering?
-Also, what expression are you talking about?}
+\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_O(g)$
+\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, $q_i-r_i$ is negative.
+\todo{I do not understand what this means, maximal under what ordering?}
 \end{enumerate}
 \end{defn}
-We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is, Aaron: I suggest not to use the phrase ``leave as an exercise'' in a paper.}
-We now offer \todo{Maybe state instead of offer?} a lemma that allows us to inductively add $\mathbb{Q}$-points \todo{$\BQ$ points usually refers to maps to $\spec \BQ$.
+One can easily verify that these satisfy the conditions of an ordering.  
+We now state a lemma that allows us to inductively add $\mathbb{Q}$-points \todo{$\BQ$ points usually refers to maps to $\spec \BQ$.
 Maybe we can just say a rational multiple of a poitn?} to a divisor and describe the new generators and relations.
@@
 Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
-satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generators (in the necessary degrees \todo{What does this mean?})
+satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generators
 $u, x_1, \ldots, x_m$ with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\sigma$ with relations generated
@@
 \begin{enumerate}
-\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
-degree $d_i$ and has a pole at $P$ of degree $c_i$, when viewed as sections of $\so_{\halfcan'}$ \todo{Clearer to say $\deg (y_i) = d_i,\ord_P^{L'} = c_i.$}
+\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such thaty $\deg(y_i)=d_i$ and $-\ord_P(y_i)=c_i$ when viewed as sections of $\so_{\halfcan'}$.
 
@@
 \]
-and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with a block order \todo{it should be called block order, instead of ``a block order''}.
+and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order \todo{it should be called block order, instead of ``a block order''}.
 If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
@@
 $V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
- and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_i^{a_i}$ \todo{should this be $y_j^{a_j}$ instead of $y_i^{a_i}$?} with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ \todo{this conflation of $j$ and $i$ is confusing me, is $j$ ranging over all indices from $1$ to $i$?} such that
-$\sum_{j=1}^i a_j c_j \ge c_{j+1}$
-and there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ such that with all $b_j\le a_j$ and 
-$\sum_{j=1}^i b_jc_j\ge c_{j+1})\}$. \todo{what is this close bracket closing?}  \\
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ such that
+\begin{enumerate}
+	\item $\sum_{j=1}^i a_j c_j \ge c_{i+1}$\\
+	\item there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ such that with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1})$ \\
+	\item there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
+\end{enumerate}
 
@@
 order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We will use O'Dorney's method of best lower approximations to
-construct the $y_i$'s as desired. \todo{cite where} \todo{What do we desire about the $y_i$?}
+\beta} \rfloor \}$. We will use positive best lower approximations to
+construct the generators $\{y_i\}$ as described in the lemma's statement.
 

### 2015-06-28 stacky_write_up/spin_cring.tex

@@
 canonical rings of genus 0 curves. This process will be carried out in Subsection ~\ref{ssec:g-0-main}.
+
+\todo{induct on cases?}
 

### 2015-06-28 stacky_write_up/spin_cring.tex
add ind lem pic, div -> Div, modify sat table

@@
 \newcommand \rk{\text{rk }}
-\newcommand \di{\text{div }}
+\newcommand \di{\text{Div }}
 \newcommand \depth{\text{depth }}
@@
 	\hline
-	Signature & Note & Saturation \\
+	Signature & Condition & Saturation \\
 	\hline
@@
 (z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
-and $(2, 2, 3)$ for $z = x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}$
-respectively).
+and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
+$x_{7, 2}$ respectively).
 

### 2015-06-28 stacky_write_up/spin_cring.tex
fix g0 example with a_1, b_1 nonzero

@@
 
+\noindent
+and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
+have that
+\[
+	a_2 x_{3, 1} x_{7, 1} = a_3 x_{3, 1} x_{7, 2}
+\]
+
+\noindent
+However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
+$x_{3, 1} x_{7, 2}$ has pole orders $(3, 3, 4)$ so their
+coefficients must be zero for this equality to hold. We have a
+similar pole-order consideration in forcing $b_1$ to be nonzero.
+
 Let $I$ be the ideal generated by these relations in
 $k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
-$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial ideal of $I$ is \todo{This will only be the case if $a_1,b_1 \neq 0$.
-We can definitely make this hold if we set up the variables in the right way, but I'm not sure if it's always true.}
+$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial
+ideal of $I$ is
 \[
@@
 \]
+
+\noindent
+since $a_1$ and $b_1$ are nonzero.
 
@@
 
-Now we can induct on cases (a)-(k) of Lemma ~\ref{lem:g_0_admissible_cases}
-to obtain bounds on the minimal generator and relation degrees for
-canonical rings of genus 0 curves. This process will be carried out in Subsection ~\ref{ssec:g-0-main}.
+Now we can induct on cases (a)-(k) of Lemma
+~\ref{lem:g_0_admissible_cases} to obtain bounds on the minimal
+generator and relation degrees for canonical rings of genus 0
+curves. This process will be carried out in Subsection
+~\ref{ssec:g-0-main}.
 

### 2015-06-28 stacky_write_up/spin_cring.tex
edits to section 3

--- 2015-06-28 stacky_write_up/spin_cring.tex
@@
 \begin{defn}
-We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ if one of the following holds
+We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{graded Prevlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
 \begin{enumerate}
 \item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_O(g)$
-\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, $q_i-r_i$ is negative.
-\todo{I do not understand what this means, maximal under what ordering?}
+\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
+\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
 \end{enumerate}
@@
 One can easily verify that these satisfy the conditions of an ordering.  
-We now state a lemma that allows us to inductively add $\mathbb{Q}$-points \todo{$\BQ$ points usually refers to maps to $\spec \BQ$.
-Maybe we can just say a rational multiple of a poitn?} to a divisor and describe the new generators and relations.
+We now state a lemma that allows us to inductively add rational multiples of a point to a divisor and describe the new generators and relations.
 
@@
 \]
-and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order \todo{it should be called block order, instead of ``a block order''}.
+and equip $k[y_1, \ldots, y_n]$ with graded Prevlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order \todo{it should be called block order, instead of ``a block order''}.
 If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then

### 2015-06-28 stacky_write_up/spin_cring.tex
???

@@
 \begin{defn}
-We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{graded Prevlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
+We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{graded P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
 \begin{enumerate}
@@
 \]
-and equip $k[y_1, \ldots, y_n]$ with graded Prevlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order \todo{it should be called block order, instead of ``a block order''}.
+and equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order \todo{it should be called block order, instead of ``a block order''}.
 If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then

### 2015-06-28 stacky_write_up/spin_cring.tex
edited picture

@@
 \includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows the positive best lower approximations shown as $*$ and other lattice points shown in $o$ of $\frac{14}{5}$.
+\caption{$d_i$ vs.
+$c_i$.
+This figure shows the positive best lower approximations shown as $*$ and other lattice points shown in $o$ of $\frac{14}{5}$.
 Note that they minimally generate lattice in $\mathbb{N}\times \mathbb{N}$ not above $5y=14x$.}

### 2015-06-28 stacky_write_up/spin_cring.tex
section 3 stuff
small line break changes and got pic to compile
section 3 edits

@@
 \label{sec:induction}
-First we present several lemmata which play a crucial role in the
-inductive step of the proof of the main theorem, Theorem
-~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove
-Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
+First we present several lemmata which provide the
+inductive steps in the proof of the main theorem, Theorem
+~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
+%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
 which describe the generators and relations of $R_{D + \frac{\alpha
-}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di
-X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in
-Subsection ~\ref{ssec:raise-orders}, we prove Lemma
-~\ref{lem:raise-stacky-order}, which the generators and relations 
-of the log spin canonical ring curve with signature $(g; e_1', 
-\ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a 
-curve with a certain subset of the $e_ i'$ incremented by $2$. 
-While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
-context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
-half-canonical divisors, although even Lemma
-~\ref{lem:raise-stacky-order} has certain generalizations, as noted
-in Remark ~\ref{rem:raise-fractional-order}
+}{\beta}P},$ given those in $R_D,$ 
+where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
+$D \in \di
+X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ 
+In
+Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
+\ldots, e_\tau'; 0)$ to that of a
+curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. 
+%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
+%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
+%half-canonical divisors, although even Lemma
+%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
+%in Remark ~\ref{rem:raise-fractional-order}
 
@@
 
-\ssec{Inductive Lemmata: Adding Points}
+\ssec{Adding Points}
 \label{ssec:add-points}
@@
 
-Before proving three inductive lemmas, we introduce some notation from O'Dorney \cite{dorney:canonical}. 
-\begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$ (for $\alpha, \beta \in \mathbb{Z}, \beta> 0$ written in reduced form), then a \begin{bf}{best lower approximation}\end{bf} to $\frac{\alpha}{\beta}$ is a a fraction $\frac{c}{d}$ (written in reduced form with $d>0$) such that there is no $\frac{c'}{d'}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
-\end{defn}
-Moreover, the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
-\[
-	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
-\]
-Refer to figure \ref{fig:s14/5-lattice} for an example of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
-
-\begin{figure}[H]\label{fig:s14/5-lattice}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{$d_i$ vs.
-$c_i$.
-This figure shows the positive best lower approximations shown as $*$ and other lattice points shown in $o$ of $\frac{14}{5}$.
-Note that they minimally generate lattice in $\mathbb{N}\times \mathbb{N}$ not above $5y=14x$.}
-\end{figure}
-
-Previously discussed O'Dorney's result and our improvement when restricting to effective. Moved to Intro.
-\todo{new transition}
-
-Before proving three inductive lemmas, we give a criteria to determine if a set of monomials generates the initial ideal of relations.
+Before proving three inductive lemmas, we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
 \todo{Perhaps say which parts of the proofs of which future lemmas it will be used in?}
@@
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$
-and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
+Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
+and $R_{\halfcan}$ minimally generated by $y_1, \ldots, y_n$ over 
 $R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
-Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
+Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
 \begin{enumerate}
@@
 
-Now, suppose a monomial $f\in T$ has a pole order $a$ at $P$.
-Then, since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
+Now, let $f\in T$.
+Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
 This demonstrates that
@@
 
-Finally, suppose $f\in S$.
+Next, suppose $f\in S$.
 Note that by (2) any polynomial $G$ in $x_1,\ldots, x_m, y_1, \ldots, y_n$ with initial term in $S$ cannot have a term in $T$.
@@
 
-As suggested by the the previous lemma, \todo{Reference the lemma, instead of using previous, since things might get moved around} we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
-\todo{Again, reference this}
+To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
+The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
 \begin{defn}
-We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, \todo{attached to $x_i$ doesn't really sound like the correct terminology to me} the graded $P$ reverse lexicographic order {\bf{graded P-revlex}} \todo{This name seems a bit funny looking to me} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
+Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated $x_1, \ldots x_m$.
+Then we have a map $\phi: k[z_1, \ldots z_m]\to R_\halfcan$ given by $z_i\mapsto x_i$.
+If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows:
+If $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
 \begin{enumerate}
@@
 \end{defn}
-One can easily verify that these satisfy the conditions of an ordering.  
-We now state a lemma that allows us to inductively add rational multiples of a point to a divisor and describe the new generators and relations.
-
-\begin{defn}
+\noindent One can easily verify that these satisfy the conditions of an ordering.
+
+Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
+
+\begin{defn}\label{den:lower-approximation}
+If $\frac{\alpha}{\beta}\in \BQ$ (written in reduced form with $\alpha \in \mathbb{Z}, \beta> \mathbb{N}$), then $\frac{c}{d}$ (written in reduced form) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there is no $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+\end{defn}
+Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
+\[
+	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
+\]
+Refer to figure \ref{fig:s14/5-lattice} for an example of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
+
+\begin{figure}[H]\label{fig:s14/5-lattice}
+\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+\caption{This figure illustrates each non-negative best lower approximation of $\frac{14}{5}$ with a ``$\bullet$'' and each other lattice point below $5y=14x$ with a ``$\circ$''.
+Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}
+\end{figure}
+
+\begin{defn}\todo{move to background}
 \label{}
@@
 
+We can now prove our first adding-points lemma.
+
 \begin{lem}
@@
 Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
-satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generators
-$u, x_1, \ldots, x_m$ with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\sigma$ with relations generated
-in degree at most $\tau$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
+satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$ meaning that $R_{\halfcan'}$ has generators
+$u, x_1, \ldots, x_m$ in degree at most $\sigma$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
+Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
 for some $\alpha,\beta \in \mathbb{N}$ such that
@@
 	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
-	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
+	N} \text{ such that } d \ge \frac{\beta}{\alpha},
 \end{equation}
-\label{eqn:deg1-sat-ind}
-Let 
+and let
 \[
@@
 \begin{enumerate}
-\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such thaty $\deg(y_i)=d_i$ and $-\ord_P(y_i)=c_i$ when viewed as sections of $\so_{\halfcan'}$.
+\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $\deg(y_i)=d_i$ and $-\ord_P^{L'}(y_i)=c_i$.
 
@@
 \[
-	\ord_u(f) < \ord_u(g) \implies f\prec g
+	\ord_u(f) < \ord_u(g) \implies f\prec g.
 \]
-and equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order \todo{it should be called block order, instead of ``a block order''}.
-If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then
+Equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order.  
+If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
 
@@
 \begin{enumerate}
-	\item $\sum_{j=1}^i a_j c_j \ge c_{i+1}$\\
-	\item there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ such that with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1})$ \\
-	\item there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
+	\item[(1)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$\\
+	\item[(2)] there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1})$ \\
+	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
 \end{enumerate}
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with relations $I$ generated over $I'$ by relations in degree is generated $\max(2\beta, \beta + \sigma)$ {\rm(}where $\sigma=\max(\deg(x_i))$ \todo{include what indexing set this $i$ is over ($ i = 1,\ldots, m$).}{\rm)}.
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
@@
 \[
-	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \deg(d\frac{\alpha}{\beta})
+	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + d\frac{\alpha}{\beta}
 \]
@@
 orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  Moreover, a set $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ \todo{how is this a set?} elements in $(R_{D})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
+c_i $ at $P$.  Moreover, a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with pole orders $1, \ldots, \lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus form a $k$-basis for
 $(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.
@@
 We now restrict our attention to log canonical rings of stacky curves.
-The previous lemma deals with most relevant induction cases when inducting from a half-canonical ring saturated at one.
-We complement it with the following two lemmas that allow us to induct under certain conditions when the half-canonical ring is saturated at two and three.
+The previous lemma accounts for the relevant induction cases when the half-canonical ring is already saturated in 1.
+We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the half-canonical ring is saturated at degrees two and three.
 
@@
 		\begin{align*}
-			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4] \\
-			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
-			&+\langle y_4^2 \rangle.
+			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
 		\end{align*}
@@
 	S =	& \; \{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \\
-	\cup	& \; \{ y_3^ay_4 \mid a \geq 0 \}
+		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
 \end{align}
@@
 \begin{align*}
-	T =   &\; \{ y_4 x_j \mid 2 \leq j \leq m \} \\
-	\cup &\; \{ y_4^2 \}
+	T =   &\; \{ y_4 x_j \mid 2 \leq j \leq m \}\cup \{ y_4^2 \}
 \end{align*}
@@
 \begin{align*}
-	T = & \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\} \\
-	   + & \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
+	T = & \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\}+ \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
 \end{align*}
@@
 Instead we turn now to inductive methods to incrementally increase the $e_i$s.
-Combined with the previous lemma on adding points, these will provide all the necessary inductive tools.
+Combined with the previous lemmata on adding points, these will provide all the necessary inductive tools for the remainder of the paper.
 

### 2015-06-28 stacky_write_up/spin_cring.tex
played around with order of proof of generation g>2 lemma, feel free to tell me to switch it back if you dont like it

@@
 The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relation_11}.
-In fact, it is fairly immediate from Riemann--Roch and the basepoint-free pencil trick that $R_L$ is generated in degree at most $6$, as is demonstrated in the following
-Lemma ~\ref{lem:semicanonical_generation}. However, to reduce the bound from 5 to 6 in the case $g =2$, we will have to work a little in Proposition ~\ref{prop:genus_2_generation_5}.
-
-\begin{rem}
-The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}, although he omits the fairly tricky genus 2 case.
-We produce the proof here for completeness.
-\end{rem}
+
+The proofs of these results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}, although ~\cite[Proposition III.4]{neves:halfcan} has a key ommission, as noted in Remark ~\ref{rem:neves-omission}
+
+\begin{lem}
+\label{lem:generation_5}
+Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
+\end{lem}
+
+The strategy of the proof of Lemma ~\ref{lem:generation_5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_L$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
+When $g > 3$, it is easy to reduce the bound from 5 to 6.
+The trickiest case is to show $R_L$ is generated in degree 5 when $g = 2$, which is done in Lemma ~\ref{lem:genus-2-generation-5}.
+After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation_5}.
 
@@
 \end{lem}
-\begin{proof}
+
+\begin{rem}
+\label{rem:neves-omission}
+The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}.
+However, Neves states that this proof also proves Lemma ~\ref{lem:generation_5}, while it crucially omits the case of genus 2 curves.
+We produce the proof here for completeness.
+\end{rem}
+
+\begin{proof}[Proof of Lemma ~\ref{lem:semicanonical_generation}]
 To show there are no new generators in degree at least $7$ if $\Delta = 0$ and in degree at least $6$ if $\Delta > 0$, it suffices to show that if $n \geq 5$ or if ($n = 4$ and $\Delta > 0$), the map
@@
 
-\begin{prop}
-\label{prop:genus_2_generation_5}
+\begin{lem}
+\label{lem:genus-2-generation-5}
 Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
 Then, $R_L$ is generated in degree at most $5$.
-\end{prop}
+\end{lem}
 \begin{proof}
@@
 
-\begin{lem}
-\label{lem:generation_5}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
-\end{lem}
-\begin{proof}
+We are now equipped to prove Lemma ~\ref{lem:generation_5}, completing the desired bound on the degree of the generators.
+
+\begin{proof}[Proof of Lemma ~\ref{lem:generation_5}]
 If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
-Proposition ~\ref{prop:genus_2_generation_5}.
-Finally, if $g > 2$, then by \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective, so again there are no new generators in degree 6.
+Lemma ~\ref{lem:genus-2-generation-5}.
+Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$.
+By \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
+Hence, $R_L$ is generated in degree at most 5.
 \end{proof}
+
+The next step is to bound the degrees of the relations of $R_L$.
+This is done in Proposition ~\ref{prop:relation_11}.
+The idea of the proof of Proposition ~\ref{prop:relation_11} is to use the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
+We now fix notation for this ideal generated by lower degrees relations.
+
+\begin{defn}
+\label{defn:lower-ideal}
+Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$.
+Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
+Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and define
+$$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$$
+\end{defn}
 
@@
 Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ let
-$$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j},$$
-and let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subset H^0(X,2L)$ is basepoint free.
+Let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subset H^0(X,2L)$ is basepoint free.
 For any $f \in k[x_1, \ldots, x_n]$ such that
@@
 \begin{proof}
-Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subset H^0(X,2L)$.
+% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subset H^0(X,2L)$.
 By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
@@
 \end{align*}
-is surjective, since
+is surjective, since the restriction on $\deg f$ guarantees
 $$
 \deg f- \deg a_i -2 \geq \begin{cases}
-	5 &\text{ if }\Delta = 0\\
-	4 &\text{ if }\Delta > 0,
+	5 &\text{ if }\Delta = 0,\\
+	4 &\text{ if }\Delta > 0.
 \end{cases}$$
-by the assumption on $\deg f$.
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i = s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i \equiv s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
 
@@
 In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0$ is close to sharp.
+Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to sharp.
 \end{rem}

### 2015-06-28 stacky_write_up/spin_cring.tex
address all g0 todos, rewrite g0 transitions, table

@@
 \todo{Make explicit assumptions on genus.}
-Suppose $L'$ is a log half-canonical divisor of $\sx'$ with course
+Suppose $L'$ is a log half-canonical divisor of $\sx'$ with coarse
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
@@
 all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
-~\ref{defn:sat}. The saturation can be computed via applications
-of Riemann-Roch. Exceptional cases are listed
-first and generic cases follow.
+~\ref{defn:sat}. The saturations can be computed using Riemann-Roch.
+By classifying the saturations of all signatures, we can determine
+the base cases on which we can apply inductive lemmata from
+Section ~\ref{sec:induction}. Exceptional cases are listed first
+and generic cases follow.
 
@@
 
-\todo{transition}
-Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}
-
 \ssec{Base Cases}
 \label{ssec:g_0_base}
-Now we have an inductive statement on the number of stacky
-points in Lemma ~\ref{lem:sat-3} and
-an inductive statement on stabilizer orders in Theorem
-~\ref{lem:raise-stacky-order}. After verifying that explicit triples
-$(\sx, L, J)$ of stacky curves $\sx$ with particular signatures and
-particular choices of $J$ are admissible, we will use Lemmas ~\ref{lem:raise-stacky-order}, and ~\ref{lem:sat-3} imply that the spin canonical ring
-$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
-\ldots, e_r)$ with relations generated in degree at most $2e$ for
-$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
-of the list of exceptional cases in Table ~\ref{table:g-0-exceptional}.
+In order to apply Lemma ~\ref{lem:sat-3} and Lemma
+~\ref{lem:raise-stacky-order} when $\delta = 0$,
+we need to determine appropriate base cases that will
+cover all but finitely many signatures by induction.
+Here we provide such base cases and demonstrate that
+they satisfy all of the necessary conditions of
+Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
+(e.g. admissibility). We also show that that the associated spin
+canonical rings are generated in degree at most $e := \max(5, e_1,
+\ldots, e_r)$ with relations generated in degree at most $2e$.
 
 \begin{lem}
-\label{lem:g_0_admissible_cases}
+\label{lem:g-0-admissible-cases}
 Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$ has signature $\sigma = (0; e_1,
@@
 
-\begin{enumerate}
-	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
-	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
-	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
-	\item[(d)] $\sigma_4 = (0; 5, 5, 7; 0), J_4 = \{3\}$
-	\item[(e)] $\sigma_5 = (0; 5, 7, 7; 0), J_5 = \{2, 3\}$
-	\item[(f)] $\sigma_6 = (0; 7, 7, 7; 0), J_6 = \{1, 2, 3\}$
-	\item[(g)] $\sigma_7 = (0; 3, 3, 3, 5; 0), J_7 = \{4\}$
-	\item[(h)] $\sigma_8 = (0; 3, 3, 5, 5; 0), J_8 = \{3, 4\}$
-	\item[(i)] $\sigma_9 = (0; 3, 5, 5, 5; 0), J_9 = \{2, 3, 4\}$
-	\item[(j)] $\sigma_{10} = (0; 5, 5, 5, 5; 0), J_{10} = \{1, 2, 3, 4\}$
-	\item[(k)] $\sigma_{11} = (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$
-\end{enumerate}
+\begin{longtable}
+	{| c || c | c | c |}
+	\caption{Genus 0 Base Cases}
+	\label{table:g-0-base-cases}
+
+	\tabularnewline
+
+	\hline
+	Case & Signature $\sigma$ & $J$ & $e$\\
+	\hline
+	\hline
+
+	(a) & (0; 3, 3, 11; 0) & \{3\} & 11\\	\hline
+
+	(b) & (0; 3, 5, 9; 0) & \{3\}	& 9\\ \hline
+
+	(c) & (0; 3, 7, 7; 0) & \{2, 3\}	& 7\\ \hline
+
+	(d) & (0; 5, 5, 7; 0) & \{3\}	& 7\\ \hline
+
+	(e) & (0; 5, 7, 7; 0) & \{2, 3\}	& 7\\ \hline
+
+	(f) & (0; 7, 7, 7; 0) & \{1, 2, 3\}	& 7\\ \hline
+
+	(g) & (0; 3, 3, 3, 5; 0) & \{4\} & 5\\ \hline
+
+	(h) & (0; 3, 3, 5, 5; 0) & \{3, 4\} & 5\\ \hline
+
+	(i) & (0; 3, 5, 5, 5; 0) & \{2, 3, 4\} & 5\\ \hline
+
+	(j) & (0; 5, 5, 5, 5; 0) & \{1, 2, 3, 4\} & 5\\ \hline
+
+	(k) &	(0; 3, 3, 3, 3, 3; 0) & \{1, 2, 3, 4, 5\} & 5\\ \hline
+\end{longtable}
 
@@
 
-Before proving Lemma ~\ref{lem:g_0_admissible_cases} in general, we check the lemma holds for case (b).
+Before proving Lemma ~\ref{lem:g-0-admissible-cases} in general, we check the lemma holds for case (b).
 
@@
 \label{ex:base-377}
-Here we demonstrate, in detail, that case (b) with ($\sigma_2 =
+Here we demonstrate, in detail, that case (b) with ($\sigma =
 (0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3, J_2 = \{3, 4\},$) with distinct points $P_i \neq \infty$,
-satisfies the conditions of Lemma ~\ref{lem:g_0_admissible_cases}.
+\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
+satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
 We exhibit a (minimal) presentation for $R'$.
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
+\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
 Table ~\ref{table:g-0-sat}, then this map is surjective
@@
 Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
-$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $s_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
+$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
+0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
 Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
@@
 \frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
-$\sigma_2, J_2$ is admissible.
+$\sigma, J$ is admissible.
 
@@
 
-\begin{proof}[Proof of Lemma ~\ref{lem:g_0_admissible_cases}]
+\begin{proof}[Proof of Lemma ~\ref{lem:g-0-admissible-cases}]
 For the remaining cases, we can use a similar method to the one
@@
 	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
-	\label{table:g-0-base-cases}
+	\label{table:g-0-base-cases-degrees}
 
@@
 
-Now we can induct on cases (a)-(k) of Lemma
-~\ref{lem:g_0_admissible_cases} to obtain bounds on the minimal
-generator and relation degrees for canonical rings of genus 0
-curves. This process will be carried out in Subsection
+Now we can use Lemma ~\ref{lem:sat-3}, Lemma
+~\ref{lem:raise-stacky-order}, and Corollary
+~\ref{cor:raise-stacky-order} inductively on the cases of Table
+~\ref{table:g-0-base-cases} to obtain the desired bounds on the
+generator and relation degrees for log spin canonical rings of
+genus 0 curves. This process will be carried out in Subsection
 ~\ref{ssec:g-0-main}.
-
-\todo{induct on cases?}
 
@@
 Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
-so that $\sigma \neq \sigma_i$ where $\sigma_i$ is one of the exceptional cases in Table
+so that $\sigma$ is not one of the exceptional cases in Table
 ~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
@@
 ~\ref{lem:sat-3} to add stacky points with
-stabilizer order $3$ to case (k) of Lemma
-~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
-= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
+stabilizer order $3$ to case (k) of Table
+~\ref{table:g-0-base-cases}, which corresponds to $\sigma
+= (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$. This case
 clearly satisfies the conditions of Lemma
 ~\ref{lem:sat-3} (recall from Table ~\ref
-{table:g-0-sat} that $\sat(\Eff(\sigma_{11})) = 3$), and the
+{table:g-0-sat} that $\sat(\Eff(\sigma)) = 3$), and the
 immediate consequence of parts (a) and (c) of Lemma
@@
 orders all equal to $3$ for any $r > 5$ is generated up to
-degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
-up to degree $2e$. Furthermore, these cases satisfy all of the
-conditions of Lemma ~\ref{lem:raise-stacky-order}.
-
-So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
-where $\sigma'$ has $r$ many stacky points all of order $3$
-and $J = \{1, \ldots, r\}$ in the sense that for all $i
-\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
-If $r \leq 5$, then $\sigma$ similarly ``lies above'' one of the
-base cases of Lemma ~\ref{lem:g_0_admissible_cases}, all of which
-satisfy the hypotheses of Lemma ~\ref{lem:raise-stacky-order} as well. \todo{Aaron: I think we replace the above paragraph with an application of Corollary ~\ref{cor:raise-stacky-order}.}
-
-So for any $r > 0$, there is a $(\sigma', J)$, either from
-Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
-the $r > 5$ case with stabilizer orders all $3$, with $\sigma' =
-(0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
-\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
-
-All such base cases satisfy all of the hypotheses of Theorem
-~\ref{lem:raise-stacky-order} and their corresponding $R' := R(\sx',
-\Delta, \halfcan')$ are generated, as $k$-algebras, up to degree
-$e' := \max(5, e_1', \ldots, e_r')$ with relations generated up to
-degree $2e'$ by Lemma ~\ref{lem:g_0_admissible_cases}. It follows
-from induction using Lemma ~\ref{lem:raise-stacky-order}(b) and
-Corollary ~\ref{cor:raise-stacky-order} that $R := R(\sx, \Delta,
-\halfcan)$ is generated up to degree $e := \max(5, e_1, \ldots, e_r)$.
-It also follows from induction on Lemma ~\ref{lem:raise-stacky-order}(c)
-and ~\ref{cor:raise-stacky-order} that the relations are generated
-up to degree $2e$. \todo{What does it mean to induct on the statements of two lemmas? Clarify this please.}
+degree $e' := \max(5, e_1', \ldots, e_r')$ with relations generated
+up to degree $2e'$. Furthermore, these cases satisfy all of the
+conditions of Lemma ~\ref{lem:raise-stacky-order}. Now we can
+apply Corollary ~\ref{cor:raise-stacky-order} to deduce that
+$R(\sx, \delta, \halfcan)$ is generated up to degree $e :=
+\max(5, e_1, \ldots, e_r)$ with relations generated up to degree
+$2e$.
+
+If $r \leq 5$ and $\sigma$ is not one of the exceptional cases,
+then we may similarly apply Lemma ~\ref{g-0-admissible-cases} and
+Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
+from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
+\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
+\ldots, e_r)$ with relations generated up to degree $2e$.
  \end{proof}

### 2015-06-28 stacky_write_up/spin_cring.tex
merged

--- 2015-06-28 stacky_write_up/spin_cring.tex
@@
 \noindent
-\todo{why is there no floor in the above equation, as in ~\ref{eqn:deg1_sat_ind_dim}} so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
+so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
 order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{

### 2015-06-28 stacky_write_up/spin_cring.tex
...???

--- 2015-06-28 stacky_write_up/spin_cring.tex
@@
 	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
+	\item \begin{defn}
+\label{}
+If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
 \end{enumerate}
@@
 
-\begin{defn}\todo{move to background}
-\label{}
-If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
-
 We can now prove our first adding-points lemma.
@@
 \[
-	\sum -\ord(z_j) < c_i .
+	\sum_{j=1}^n -\ord(z_j) < c_i .
 \]

### 2015-06-28 stacky_write_up/spin_cring.tex
minor cite changes

@@
 in most cases $R(X, K_X)$ is generated in degree 1 with relations
-in degree 2, as shown in \cite[p. 157]{saint-donat:proj}. This has the
+in degree 2, as shown in Saint-Donat\cite[p. 157]{saint-donat:proj}. This has the
 pleasant geometric consequence that all such canonically embedded
@@
 = 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
-As is done in \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points.
+As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points.
 A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
@@
 Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$.
-By \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
+By Voight and Zurieck-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
 Hence, $R_L$ is generated in degree at most 5.

### 2015-06-28 stacky_write_up/spin_cring.tex
delete clearly

@@
 We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
-We clearly have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
+We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
 Hence, (Ad-i) holds.
@@
 = (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$. This case
-clearly satisfies the conditions of Lemma
+satisfies the conditions of Lemma
 ~\ref{lem:sat-3} (recall from Table ~\ref

### 2015-06-28 stacky_write_up/spin_cring.tex
lemmata -> lemmas

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive Lemmata %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inductive Lemmata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive lemmas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inductive lemmas}
 \label{sec:induction}
-First we present several lemmata which provide the
+First we present several lemmas which provide the
 inductive steps in the proof of the main theorem, Theorem
@@
 
-%However, before we can answer these general Lemmata, it is useful
+%However, before we can answer these general lemmas, it is useful
 %to prove a nice result about minimal generation of ideals of
@@
 Instead we turn now to inductive methods to incrementally increase the $e_i$s.
-Combined with the previous lemmata on adding points, these will provide all the necessary inductive tools for the remainder of the paper.
+Combined with the previous lemmas on adding points, these will provide all the necessary inductive tools for the remainder of the paper.
 
@@
 By classifying the saturations of all signatures, we can determine
-the base cases on which we can apply inductive lemmata from
+the base cases on which we can apply inductive lemmas from
 Section ~\ref{sec:induction}. Exceptional cases are listed first

### 2015-06-29 stacky_write_up/spin_cring.tex
capital section names
added further questions

@@
 \label{thm:main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
+Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere?} so
 that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
@@
 \begin{rem}
+\label{rem:explicit-generators}
 The proofs of the main theorems in the low genus cases not only
@@
 We now restrict our attention to log canonical rings of stacky curves.
-The previous lemma accounts for the relevant induction cases when the half-canonical ring is already saturated in 1.
-We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the half-canonical ring is saturated at degrees two and three.
+The previous lemma accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.
+We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.
 
@@
 
-The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the half-canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
+The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
 The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relation_11}.
@@
 \label{sec:further-questions}
-\begin{itemize}
-	\item More on fractional modular forms
-	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
-	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_11} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})?
-\todo{Possibly think more about this}
-	\item Generic Initial ideal (and other genericness properties?)
-	\item Complete minimal generation
-\end{itemize}
+
+This paper leaves open many directions for further research.
+
+\begin{enumerate}
+	\item In the case $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of a log spin canonical ring $R_L$.
+Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with half canonical divisor $L = P$ has spin canonical ring $R_L$ with relations in degree 10.
+This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$.
+In particlar, we make the following conjecture.
+\begin{conjecture}
+\label{conj:relations-10}
+If $X$ is a curve of genus $g \geq 2$ and $L \in \di X$ with $2L \sim K,$ the ideal of relations in $R_L$ is generated in degree at most $10$.
+More precisely, if $x_1,\ldots, x_n$ is a minimal set of generators for $R_L$ and $\phi:k[y_1,\ldots, y_n] \rightarrow R_L, y_i \mapsto x_i,$ then $I_L := \ker \phi$, is generated in degree at most 10.
+\end{conjecture}
+Note that in the case $\dim L \geq 2$ and $L$ is basepoint-free, by Neves ~\cite[Proposition III.12]{neves:halfcan}, $I_L$ is generated in degree at most 8.
+Additionally, if Conjecture ~\ref{conj:relations-10} were true, by Theorem ~\ref{thm:main} we would immediately obtain the following corollary, providing a more concise statement than that of Theorem ~\ref{thm:main}.
+\begin{cor}
+\label{}
+Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring.
+Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.
+\end{cor}
+	\item Another direction for further research is to extend the results of this paper to fractional modular forms, just as this paper extends the results of Voight and Zureick-Brown \cite{vzb:stacky} from even weight modular forms to odd weight modular forms.
+In particular, we pose the following question:
+\begin{question}
+\label{ques:fractional-weight}
+If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ where $K$ is the canonical divisor of $\sx$, can one bound the degrees of generators and relations of $R_D$?
+\end{question}
+Note that that the above question is answered affirmatively in the case that $\sx$ has signature $(0;e_1,\ldots, e_r;\delta)$ in \todo{Aren't we supposed to mention fractional weight modular forms after an early inductive lemma?
+Can we include this as a remark somewhere?} \todo{Include reference to the fractional weight modular forms remark, in this remark, we should probably reference \cite[Remark 10.2.3]{vzb:stacky}}.
+In fact, we show that if $D \in \di \sx$ so that $nD = K$ for some $n \geq 2$, then $R_D$ is generated in degree at most $e=\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$.
+Additionally, Lemma ~\ref{lem:raise-stacky-order} naturally extends to the setting fractional weight modular forms, as noted in Remark ~\ref{rem:raise-fractional-order}.
+	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense.
+The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner.
+In particular, Lemma ~\ref{lem:raise-order-stacky} constructs generators with non-maximal pole orders at certain points, making the relations non-generic.
+\begin{question}
+\label{}
+If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$, does there exist a function $\sigma \mapsto d(\sigma)$ so that the generic initial ideal {\rm(} with some specified ordering{\rm)} is generated in degree at most $d(\sigma)$?
+Can one write down the generic initial ideal explicitly?
+\end{question}
+	\item As noted in Remark ~\ref{rem:explicit-generators}, the proof of Theorem ~\ref{thm:main} given in this paper gives an explicit procedure for computing the generators and relations of $R_L$ when the genus of $\sx$ is $0$ or $1$.
+\begin{question}
+\label{}
+Can one give an algorithm for explicitly computing the generators and relations for an arbitrary genus $g \geq 2$ curve?
+\end{question}
+Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a half canonical divisor of $X$.
+In this case our proof of Theorem ~\ref{thm:main} yields an algorithm for determining the generators of $L$.
+This raises the following Petri-like question:
+\begin{question}
+\label{ques:half-canonical-petri}
+Given a {\rm(}non-stacky {\rm)} curve $X$ and a half canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$?
+If so, can one give the generic ideal of $R_L$ or the generic initial ideal of $R_L$, as defined in Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}?
+\end{question}
+In particular, if Question ~\ref{ques:half-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
+	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
+	\item While Theorem ~\ref{thm:main} gives a minimal set of generators for the log spin canonical ring $R_L,$ the set of relations is not minimal.
+In many of the $g = 0$ and $g=1$ cases, it is not too difficult to see that our inductive procedure also yields a minimal set of relations for $R_L$.
+One might investigate whether the generators and relations given by the inductive proof of Theorem ~\ref{thm:main} are always minimal.
+	\end{enumerate}
 

### 2015-06-29 stacky_write_up/spin_cring.tex
edits to section 3 first two lemmas

@@
 If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
+	\item Define $(R_\halfcan)_d$ to refer to the $d^{th}$ component.
 \end{defn}
@@
 
-\section{Inductive lemmas}
+\section{Inductive Lemmas}
 \label{sec:induction}
 First we present several lemmas which provide the
-inductive steps in the proof of the main theorem, Theorem
+inductive steps in the proof of the main theorem: Theorem
 ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
 %Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
-which describe the generators and relations of $R_{D + \frac{\alpha
-}{\beta}P},$ given those in $R_D,$ 
-where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
-$D \in \di
-X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ.$ 
+which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
+}{\beta}P}$ from those of $R_{\halfcan'}$, where
+%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
+$\halfcan \in \di
+X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
 In
@@
 curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$.
+\todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.
+There are too many clauses...}
 %While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
@@
 
-Before proving three inductive lemmas, we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
-\todo{Perhaps say which parts of the proofs of which future lemmas it will be used in?}
+Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e.
+$\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
+This will be used in the subsequent three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}
 
@@
 Now, let $f\in T$.
-Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
+Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
 This demonstrates that
@@
 Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), any such polynomial does not map to an element of $R_{\halfcan'}$ (since it has a non-zero constant factor with $f$).
-Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
+\todo{Peter: Is this abuse of notation okay?} Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
 Therefore,
@@
 \begin{defn}
-Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated $x_1, \ldots x_m$.
-Then we have a map $\phi: k[z_1, \ldots z_m]\to R_\halfcan$ given by $z_i\mapsto x_i$.
-If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows:
-If $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, then $f\prec g$ if one of the following holds:
+Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.
+Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$.
+\todo{Do we need to instantiate the $z_i$.
+If so, what is the best way to do so.
+Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows:
+If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
 \begin{enumerate}
@@
 \end{defn}
-\noindent One can easily verify that these satisfy the conditions of an ordering.
+\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.
 
 Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
+\todo{Peter: This sentence is very ugly.
+On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.
+How should we state it better?
+Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}
 
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$ (written in reduced form with $\alpha \in \mathbb{Z}, \beta> \mathbb{N}$), then $\frac{c}{d}$ (written in reduced form) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there is no $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c\in \mathbb{Z}, d\in \mathbb{N}$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 \end{defn}
@@
 
+\todo{Peter: Do we want this as an [H] figure; this seems a little non-standard and can create problems with display.  Nonetheless, I copied this format to match the figure in a later section}
 \begin{figure}[H]\label{fig:s14/5-lattice}
 \includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure illustrates each non-negative best lower approximation of $\frac{14}{5}$ with a ``$\bullet$'' and each other lattice point below $5y=14x$ with a ``$\circ$''.
+\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}$ with a ``$\bullet$'' and each other lattice point below $5y=14x$ with a ``$\circ$''.
 Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}
@@
 Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
-satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$ meaning that $R_{\halfcan'}$ has generators
-$u, x_1, \ldots, x_m$ in degree at most $\sigma$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
+satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
@@
 $V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
- and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ such that
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}^{\ge 0}$ such that
 \begin{enumerate}
@@
 \[
-	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + d\frac{\alpha}{\beta}
+	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor
 \]
@@
 order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We will use positive best lower approximations to
+\beta} \rfloor \}$. We will the use positive best lower approximations to
 construct the generators $\{y_i\}$ as described in the lemma's statement.
@@
 be the positive best lower approximations of $\frac{
-\alpha}{\beta}$ as described in this lemma's statement. Note that elements of $H^0(X, d\halfcan)$ have poles of
-orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
-c_i $ at $P$.  Moreover, a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with pole orders $1, \ldots, \lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus form a $k$-basis for
+\alpha}{\beta}$ as described in this lemma's statement. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
 $(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.
 
-For any $j, i \in \mathbb{N}$, with $i < j$, we have $\frac{c_i}{d_i} > \frac{c_j}{d_j}$.
-So, for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ \todo{are the $i$ and $j$ mismatched?} for all $z_j$, \todo{It might be clearer to say for all $j \in \{1,\ldots, ?\},$ since the subscript is really want is changing, or instead for all $j$ with $1 \leq j \leq ?$ } $\prod_{j=1}^n z_j$ must satisfy \todo{It seems like each $z_j$ must satisfy this, instead of the product satisfying this}
-\todo{In the next equations, are we viewing these as rational functions on the structure sheaf or on $L'$, what point is the order of $z_j$ taken with respect to?}
+%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
+Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Let $z_1, \ldots, z_r \in R_\halfcan$ with $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.  Then for each $z_j$,
 \[
-	\frac{-\ord_P(z_i)}{\deg(z_i)} < \frac{c_i}{d_i},
+	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
 \]
@@
 \noindent
-so we have the pole order of $\prod_{j=1}^n z_j$ is \todo{what is the following sum taken over?}
+so
 \[
-	\sum_{j=1}^n -\ord(z_j) < c_i .
+	-\ord^{\halfcan'}_P(\prod_{j=1}^n z_j) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
 \]
@@
 Choose some $y_i \in(R_{
-\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ and if $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
+\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
 
 Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ is not a best lower approximation. Then choose
+\beta}$ is not a best lower approximation. Then choose a
 best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
@@
 
-This suggests how we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
+Using this fact, we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
 \[

### 2015-06-29 stacky_write_up/spin_cring.tex
section 3 edits; dare I say the section is now readable?

@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
+Let $\Gamma$ be a {\bf Fuchsian} group, \todo{Peter: comma or colon here?} i.e. a discrete subgroup
 of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
 linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, for general
-$\Gamma$, we sharply bound the degree of the generators and
-relations for $M(\Gamma).$ In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
+$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, we sharply bound the degree of the generators and
+relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?
+I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}.
+In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
 \cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$.
@@
 \begin{align*}
-	S	\cup \; \langle T\rangle \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+	S \; \cup\; \langle T\rangle \; \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
 \end{align*}
@@
 
-Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ by (3),
+Finally, note that
+\[
+	\initial(I) \cap k[x_1, \ldots, x_m] = \initial(I').
+\]
+
+Therefore, since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ by (3),\todo{Peter: A little bit awkwardly phrased with way too many commas}
 \begin{align*}
@@
 \]
-Equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with block order.  
+Equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.
 If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
@@
 \item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.
+\todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.
+On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.
+Maybe in a remark after the lemma?}
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
@@
 % \implies the equation below:
-\[
+\begin{equation}\label{eqn:c-from-lower-terms}
 	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
-\]
-
-Using this fact, we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
+\end{equation}
+
+Using this fact, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
 \[
@@
 \]
-A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).
-
-Furthermore, if we define $U_i$ and $V$ as in the lemma's statement and
+Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor$, so by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).
+
+Define $U_i$ and $V$ as in the lemma's statement and define
 \[
-	T = (\bigcup_{i=1}^{n-1} U_i) \cup V,
+	T = (\bigcup_{i=1}^{n-1} U_i) \cup V.
 \]
-then we observe that $S$ and $T$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, so parts (b) and (c) of the lemma follow immediately
+
+We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.
+We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).
+Our choice of order on monomials in $k[y_1, \ldots, y_n]$ and block order on those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\prec S\prec k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).
+Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
+Further suppose $f\not\in \langle V \rangle$; then for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
+Therefore, $f\in k[u, y_1, \ldots, y_n]$.
+We note that $S\cup S_0$ generate $k[u,y_1, \ldots, y_n]$ as a $k$-algebra (since each of $u, y_1, \ldots, y_n$ is contained in either $S$ or $S_0$).
+Furthermore, if $f\not\in k[u, x_1, \ldots, x_m]$ then $f\in k[y_1, \ldots, y_n]$ which is generated by $S$ as a $k$-algebra.
+That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+\[
+	k[u, x_1, \ldots, x_m] \cup V \cup k[y_1, \ldots, y_n].
+\]
+Suppose $f=a^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{N}$ for all $j$.
+For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.
+Then if $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$, but for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
+We see that this latter statement is equivalent to $\prod_{j=1}^r {y_j}^{a_j}\in U_r$.
+Thus, since $S$ generates $k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial not in $S$, every monomial in $k[y_1, \ldots, y_n]$ is contained in $S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle$.
+Therefore, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+\[
+	k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \subseteq S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
+\]
+This gives us condition \ref{lem:relations_from_generators_induction}(3).
+Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we get (b) of this lemma.
+\todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.
+On the other hand, it is somewhat important.
+Should it be included?}
+
+Finally, (c) of this lemma follows immediately by looking at the constructions of parts (a) and (b).
 
@@
 \label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, \halfcan_X)$ with signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively with $g > 0,$ and, if $g = 1$ then $\deg 3\halfcan' \geq 2$.
-Let $R_{L'} = k[x]/I'= k[x_2, x_3
+Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, \halfcan_X)$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
+Suppose $g > 0,$ and, if $g = 1$ then $\deg 3\halfcan' \geq 2$ (note that this implies $\sat(Eff(L'))\le 2$).
+Let $R_{L'} = k[x_2, x_3
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
+Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
 Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
@@
 	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
-		\{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements
+		\{3, 4\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements
 		$y_3, y_4,$ minimally generate $R$ over $R'$.
@@
 		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order so that $R = k[y_3, y_4, x]/I$. Let,
+		order with $y_3, y_4$ preceding $x_2, \ldots, x_m$.  Then
 		\begin{align*}
@@
 If $g = 1$, we assume $\deg 3L \geq 2 > 2g - 1$, so we also have $\deg 4L \geq 2 > 2g - 1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord
-_P(y_i) = 1$ by Riemann-Roch. \todo{Understand why/whether we need to cite Lemma 5.4.7.}
-
-In a fashion analogous to the proof of Lemma 
-~\ref{lem:sat-3}, we see 
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch.
+\todo{Understand why/whether we need to cite Lemma 5.4.7.}
+
+A quick computation checks that
 the following is a $k$ basis for $R$ over $R'$:
@@
 \end{align*}
-part (b) follows immediately from lemma \ref{lem:relations_from_generators_induction}
+a similar (but much easier) computation to that of lemma $\ref{lem:sat-1}$ determines that $S$, $T$, and $\prec$ meet the conditions of Lemma \ref{lem:relations_from_generators_induction}, whose result then immediately implies part (b).
 
@@
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
-{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Let $L = L' + \frac
+{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$; since we are in genus 0, we can choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i$. Let $L = L' + \frac
 {1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
-the ordering on $k[x]$ satisfies
+the ordering on $k[x_3, \ldots, x_m]$ satisfies
 \begin{align*}
@@
 	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
+		4,5\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements $y
 		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
@@
 		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
-		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $y_3, y_4, y_5$ precede $x_3, \ldots, x_m$.  Then,
 		\begin{align*}
@@
 \begin{proof}
-Since we are genus 0, general
-elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P(y_i) =
+Since we are in genus 0, general
+elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P^{\halfcan'}(y_i) =
 1$. \todo{Understand why/whether we need to cite 
-Lemma 5.4.7.}  We see by pole order considerations that
+Lemma 5.4.7.  Peter: What does this mean?}  We see by pole order considerations that
 
@@
 
-Letting
-\begin{align*}
-	T = & \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\}+ \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
-\end{align*}
-we see that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, immediately implying part (b) of this proof.
+Setting
+\[
+	T = \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\}+ \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
+\]
+we can argue similarly to Lemma $\ref{lem:sat-1}$ that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, immediately implying part (b) of this proof.
 
@@
 \end{proof}
+
+\todo{Add conclusion to section}
 

### 2015-06-29 stacky_write_up/spin_cring.tex
fix bad refs/labels

@@
 	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
-	\item \begin{defn}
-\label{}
+	\item
+
+	\begin{defn}
+	\label{def:order-sup}
 	If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
@@
 \begin{equation}
-\label{eqn:deg1_sat_ind_dim}
+\label{eqn:deg1-sat-ind}
 	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
@@
 By
-Equation ~\ref{eqn:deg1_sat_ind_dim}, for any $d
+Equation ~\ref{eqn:deg1-sat-ind}, for any $d
 \in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
@@
 By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
-Since $D$ is effective, the condition of equation ~\ref{eqn:deg1_sat_ind_dim} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
+Since $D$ is effective, the condition of equation ~\ref{eqn:deg1-sat-ind} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
 %\end{proof}
@@
 If $r \leq 5$ and $\sigma$ is not one of the exceptional cases,
-then we may similarly apply Lemma ~\ref{g-0-admissible-cases} and
+then we may similarly apply Lemma ~\ref{lem:g-0-admissible-cases} and
 Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
@@
 \begin{cor}
-\label{}
+\label{cor:main-refined}
 Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring.
+Suppose Conjecture ~\ref{conj:relations-10}.
 Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.
@@
 The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner.
-In particular, Lemma ~\ref{lem:raise-order-stacky} constructs generators with non-maximal pole orders at certain points, making the relations non-generic.
+In particular, Lemma ~\ref{lem:raise-stacky-order} constructs generators with non-maximal pole orders at certain points, making the relations non-generic.
 \begin{question}
-\label{}
+\label{ques:generic-initial}
 If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$, does there exist a function $\sigma \mapsto d(\sigma)$ so that the generic initial ideal {\rm(} with some specified ordering{\rm)} is generated in degree at most $d(\sigma)$?
@@
 \begin{question}
-\label{}
+\label{ques:algorithm}
 Can one give an algorithm for explicitly computing the generators and relations for an arbitrary genus $g \geq 2$ curve?

### 2015-06-29 stacky_write_up/spin_cring.tex
write background, a few items/?s remain

@@
 in most cases $R(X, K_X)$ is generated in degree 1 with relations
-in degree 2, as shown in Saint-Donat\cite[p. 157]{saint-donat:proj}. This has the
+in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]{saint-donat:proj}). This has the
 pleasant geometric consequence that all such canonically embedded
@@
 directions. 
-If $X$ is a curve, then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
+If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve?
+shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if
 $$\di \sx = \di X \oplus \left(\bigoplus_{i
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e.
@@
 \label{sec:background}
-Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
-Include the following:
+Here we denote various definitions and useful notation that will be
+used throughout the paper. Many of the conventions come from existing
+literature. In particular, we use much of the notation from Voight
+and Zureick-Brown. Here, we briefly present the definitions
+and notation we use.
+
+A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
+geometrically-connected Deligne-Mumford stack of dimension $1$ over
+$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
+its stabilizers are coprime to char $k$. Throughout this paper,
+stacky curves will be assumed to be tame and $k$ will always be
+algebraically closed. The language of stacks will be omitted in
+this paper, as it is sufficient to view stacky curves and related
+objects $\sx$ as a scheme whose associated divisor group allows for
+a finite number of \textbf{stacky points} which may be viewed
+heuristically as ``fractional points''. See Voight and
+Zureick-Brown for more thorough treatment of these definitions
+\cite[Chapter 5]{vzb:stacky}.
+
+If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
+then we use $e_1,\ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
+of the stabilizer groups of the points with non-trivial
+stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
+In order to study objects associated with stacky curves, it is often
+useful to consider them in the context of ordinary schemes.
+
+\begin{defn}
+Let $\sx$ be a stacky curve over $k$ with stacky points $P_1, \ldots,
+P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
+Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
+genus $g$. Then $X$ is the \textbf{coarse space} associated to $\sx$
+if
+
+\[
+	\di \sx = \di X \oplus \left(\bigoplus_{i
+	= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X
+\]
+\end{defn}
+
+We can equip stacky curves with a divisor $\Delta$ that is a 
+sum of distinct points each with trivial stabilizer. A divisor
+$\Delta$ of this form is called a \textbf{log divisor}. We use
+$\delta := \deg \Delta$ to refer to the degree of the log divisor.
+If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
+\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
+
+\todo{canonical divisor?}
+The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
+and the study of their canonical rings is the main focus of
+the work by Voight and Zureick-Brown \cite{vzb:stacky}.
+For this paper, we consider \textbf{log spin curves} which are
+triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
+and a divisor $\halfcan$ which satisfies the property that
+$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
+is called a \textbf{half-canonical divisor} on $(\sx, \Delta)$
+and are sometimes referred to as theta-characteristics in other
+literature. We also use $\halfcan_X$ to refer to the half-canonical
+divisor associated with the coarse space $X$ of $\sx$, where
+$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
+Now we can define the analogy to canonical rings for
+log spin curves.
+
+\begin{defn}
+The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
+\[
+	R(\sx, \Delta, L) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
+\]
+\end{defn}
+\todo{what about floors?}
+
+\noindent
+When the log spin curve is fixed, we usually use $R$ to represent
+$R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D) :=
+H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
+
+\todo{do this part}
+Part on Kodaira-Spencer \cite{kodaira:complex-manifolds}.
+Use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic 
+geometry.
+
 \begin{enumerate}
-	\item Include explanation of Kodaira spencer, and use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic geometry.
-	\item Possibly include some of the following notation, it it isn't dealt with well in the background.
-
- A divisor $\Delta \in \di X$ is a {\bf log divisor} if
-$\Delta = \sum_{i=1}^{n}P_i \in \di X,$ with $P_i$ distinct points of $X$. \todo{Do we want to assume they are distinct?} Let
-$\sx$ denote a tame separably rooted curve over a
-field $k$ so that $X$ is the coarse space of $\sx$, as defined in
-\cite[Section 5.2]{vzb:stacky}, with $\di \sx = \di X \oplus \left(\bigoplus_{i
-= 1}^r \langle \frac{1}{e_i}P_i \rangle \right),$ so that $e_i \in \BZ$. Let $K_
-\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
-say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
-\in \di \sx$ a {\bf log half-canonical divisor}, also known as a theta-characteristic, on the {\bf log stacky curve} $(\sx,\Delta)$ if
-$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\deg \Delta =\delta,$ then we
-say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
-
-	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
-	\item While the remainder paper could be writen using stack-theoretic terms, as is done in \cite{vzb:stacky}, we shall adopt the simpler language of $\BQ$ divisors, thinking of $\sx$ as the underlying scheme $X$ with fractional points.
-	\item Include explicit definitions for what we are assuming about a curve, i.e.
-smooth, projective, etc.
-Also, possibly discuss the relations to stacks, either here in or in the introduction.
-Make sure to make clear the assumption that we will work over an algebraically closed field through tensoring up.
-	\item Notation for Coarse space
-	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
 	\item Note that this result is independence of base field
 	\item background on Gr\"{o}bner bases
-	\item Notation $h^0 = \dim_k H^0$.
 	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
-	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
 	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
-	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
 	\item
@@
 In particular, we shall often use $\deg \Delta \neq 1$.
+\end{rem}
+
+We define the notion of the saturation of a divisor, taken from
+Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
+
+\begin{defn}
+Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
+is the monoid
+\[
+	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}
+\]
+\end{defn}
+
+\begin{defn}
+\label{defn:sat}
+The \textbf{saturation} for a monoid $M \subseteq \BZ_{\geq 0}$,
+denoted $\sat(M)$, is the smallest integer $s$ such that $M
+\supseteq \BZ_{\geq s}$, if such an integer exists.
+\end{defn}
+
+\begin{rem}
+For our purposes, it is useful to call the saturation of the
+effective monoid of a divisor $D$ as the saturation $s$ of the
+divisor $D$ on $\sx$. In this case, the saturation $s :=
+\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
+$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
+\geq s$.
 \end{rem}
@@
 associated {\bf divisor of cusps} $\Delta$.
-
-\subsection{Definitions}
-We reserve the notation $\halfcan$ for the half-canonical divisor
-where $2\halfcan \sim K_\sx + \Delta$.
-
-Here are some definitions.
-
-We define the notion of the saturation of a divisor, taken from
-Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
-
-\begin{defn}
-Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
-is the monoid
-\[
-	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}
-\]
-\end{defn}
-
-\begin{defn}
-\label{defn:sat}
-The \textbf{saturation} for a monoid $M \subseteq \BZ_{\geq 0}$,
-denoted $\sat(M)$, is the smallest integer $s$ such that $M
-\supseteq \BZ_{\geq s}$, if such an integer exists.
-\end{defn}
-
-\begin{rem}
-For our purposes, it is useful to call the saturation of the
-effective monoid of a divisor $D$ as the saturation $s$ of the
-divisor $D$ on $\sx$. In this case, the saturation $s :=
-\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
-$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
-\geq s$.
-\end{rem}
 

### 2015-06-29 stacky_write_up/spin_cring.tex
skeleton abstract, remove table of contents

@@
 \begin{abstract}
-  Arithmetic geometry group at the Emory University Number Theory
-	REU.
+  Generalizing the classical theorems of Max Noether and Karl 
+	Petri, we describe generators and relations for the spin canonical
+	ring of a stacky curve equipped with an arbitrary log divisor. As
+	an application, we bound the generation degrees and relation
+	degrees for graded rings of modular forms of arbitrary integral
+	weight arising from finite-area quotients of the upper half-
+	plane by Fuchsian groups.
 \end{abstract}
@@
 \maketitle
-
-\tableofcontents
 

### 2015-06-29 stacky_write_up/spin_cring.tex
todos added (section 1)

@@
 
+\maketitle
+
 \begin{abstract}
@@
 
-\maketitle
+\todo{Peter: I don't like the first thing our reader will read to be a dependent clause}
 
@@
 relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?
-I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}.
+I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}  \todo{Peter: also, its not clear to me that this should be said right here.
+I think we may want to say a bit more about what's already known instead of going directly to what we have done}.
 In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
@@
 
-Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many
+\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
+Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.
+We mostly generalize in one direction}
 directions. 
@@
 \beta} \rfloor \}$. We will the use positive best lower approximations to
-construct the generators $\{y_i\}$ as described in the lemma's statement.
+construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
 
@@
 be the positive best lower approximations of $\frac{
-\alpha}{\beta}$ as described in this lemma's statement. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
+\alpha}{\beta}$. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
+d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by a dimension count form a $k$-basis for
 $(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.
@@
 %For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
-Choose a positive best lower approximation $\frac{c_i}{d_i}$.  Let $z_1, \ldots, z_r \in R_\halfcan$ with $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.  Then for each $z_j$,
+Choose a positive best lower approximation $\frac{c_i}{d_i}$.
+Let $z_1, \ldots, z_r \in R_\halfcan$ with $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
+Then for each $z_j$,
 \[
@@
 Choose some $y_i \in(R_{
-\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
-
-Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
-\beta}$ is not a best lower approximation. Then choose a
+\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
+
+Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} < \frac{\alpha}{
+\beta}$ is not a best lower approximation.  Choose a
 best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
@@
 \]
-and for $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
+and for each $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i$ (note that this always exists since $1=c_1\le i$), define
 \[
@@
 \]
+Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$.
 Then define 
@@
 \]
+Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.
+
 Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor$, so by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).
@@
 Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
-Further suppose $f\not\in \langle V \rangle$; then for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
+Further suppose $f\not\in \langle V \rangle$, so for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
 Therefore, $f\in k[u, y_1, \ldots, y_n]$.
-We note that $S\cup S_0$ generate $k[u,y_1, \ldots, y_n]$ as a $k$-algebra (since each of $u, y_1, \ldots, y_n$ is contained in either $S$ or $S_0$).
-Furthermore, if $f\not\in k[u, x_1, \ldots, x_m]$ then $f\in k[y_1, \ldots, y_n]$ which is generated by $S$ as a $k$-algebra.
+We note that $S$ generate $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
 That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \[
-	k[u, x_1, \ldots, x_m] \cup V \cup k[y_1, \ldots, y_n].
+	k[u, x_1, \ldots, x_m] \cup V \cup \{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]. 
 \]
-Suppose $f=a^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{N}$ for all $j$.
+\todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
+We see that we can write $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.
 For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.
-Then if $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$, but for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
-We see that this latter statement is equivalent to $\prod_{j=1}^r {y_j}^{a_j}\in U_r$.
-Thus, since $S$ generates $k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial not in $S$, every monomial in $k[y_1, \ldots, y_n]$ is contained in $S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle$.
-Therefore, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\[
-	k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \subseteq S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
-\]
+If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
+We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_r$.
+Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+\begin{align*}
+				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \\
+	\subseteq \; 	& S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
+\end{align*}
 This gives us condition \ref{lem:relations_from_generators_induction}(3).
@@
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (so there is not more than one $d_i=1$).
-When $\frac{\alpha}{\beta}$, the choice of generators in degrees above 1 is generic, and we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$.
+The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
+When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
 \end{rem}
@@
 \todo{Something about fractional weight modular forms?}
-\iffalse{
+
 \begin{cor}
@@
 
-Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.
+Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor$ so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.
 Thus, since $\beta\ge 3$, $\deg(K_\sx)\ge 0$.
-Thus $\deg(
+Thus $\deg($
 \end{proof}
-}\fi
 

### 2015-06-29 stacky_write_up/spin_cring.tex
sco(L)^... to \lfloor dL \rfloor, more bkgnd items

@@
 \begin{align*}
-	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
+	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d L \rfloor)
 \end{align*}
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
 \end{align*}
@@
 
-\todo{canonical divisor?}
 The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
@@
 literature. We also use $\halfcan_X$ to refer to the half-canonical
-divisor associated with the coarse space $X$ of $\sx$, where
+divisor associated with the coarse space $X$ of $\sx$, i.e.
 $\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
@@
 \[
-	R(\sx, \Delta, L) = \bigoplus_{d \geq 0} H^0(\sx, \sco(L)^{\otimes d})
+	R(\sx, \Delta, L) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
 \]
@@
 \noindent
-When the log spin curve is fixed, we usually use $R$ to represent
-$R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D) :=
-H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
+When the log spin curve is fixed, we usually use $R$ or $R_L$ to
+represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
+:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
 
@@
 	\item background on Gr\"{o}bner bases
-	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
 	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
-	\item
+\end{enumerate}
+
+Define $(R)_d$ to refer to the $d^{th}$ component
 
@@
 \label{def:order-sup}
-	If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
-	\item Define $(R_\halfcan)_d$ to refer to the $d^{th}$ component.
+If $z$ is a rational section of $\sco(D)$ denote the order of
+zero of $z$ at $P$ by $\ord_P^D(z)$.
 \end{defn}
-\end{enumerate}
+
+\begin{rem}
+\label{rem:odd-denom}
+Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
+\[
+	L = \sum_{i = 1}^{r} \frac{e_i - 1}{2e_i} P_i + \sum_{i = 1}^{s} a_i P_i
+\]
+
+\noindent
+where $a_i \in \BZ$ and $e_i$ are odd.
+\todo{give reason}
+\end{rem}
 
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \lfloor d L \rfloor)
 \end{align*}

### 2015-06-29 stacky_write_up/spin_cring.tex
minor intro edits

@@
 \begin{align*}
-	R(X,K_X) = \bigoplus_{n \geq 0} H^0(X,nK_X),
+	R(X,K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
 \end{align*}
@@
 
+The main theorem of this paper provides the following application
+to modular forms when combined with a result from Voight and
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}.
+
+\begin{cor}
+\label{cor:main-mod-forms}
+There exists a log half-canonical divisor $\halfcan$ on $\sx$ such
+that we have a graded isomorphism of $\BC$-algebras
+\[
+	\bigoplus_{k = 0}^{\infty} M_k(\Gamma) \cong R(\sx (\Gamma), 
+\Delta, \halfcan)
+\]
+
+\noindent
+Let $\sigma = (g; e_1, \ldots, e_r; \delta)$ be the signature
+of $\sx$. Then $\bigoplus_{k = 0}^{\infty} M_k(\Gamma)$ is
+generated as a $\BC$-algebra by elements of degree at most $e = \max
+(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
+then $R(\sx,\Delta, \halfcan)$ has relations generated in degrees
+up to $\max(11, 2e_1, \ldots, 2e_r)$. Otherwise, $R(\sx, \Delta,
+\halfcan)$ has relations generated in degrees up to $\max(10, 2e_1,
+\ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list
+of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
+for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
+for signatures with $g = 0$.
+\end{cor}
+
 The remainder of the paper will be primarily devoted to proving
 Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct on the order and number of stacky points. To this end, we first review important background in
+proof will be to induct on the stabilizer order of and number of stacky points. To this end, we first review important background in
 Section ~\ref{sec:background}. Then, we develop various inductive
@@
 \todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
-In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical?
-I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
-Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
+In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a divisor $D = \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
+Of course, this is minor, and it's fine to keep it this way.} with at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
 \todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.

### 2015-06-29 stacky_write_up/spin_cring.tex
remove fractional weight corollary

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 
+\todo{State for even weight modular forms attributed to VZB.}
 \begin{thm}
@@
 
+\iffalse{
 Lemma \ref{lem:sat-1} leads to the the following corollaries.
@@
 \end{proof}
-
-\todo{Something about fractional weight modular forms?}
-
-\begin{cor}
-Let $R_\halfcan$ be the fractional weight canonical ring associated to a fractional $\frac{2\alpha}{\beta}$-weight cusp forms with $\frac{\alpha}{\beta}$ in reduced form and $\beta\ge 3$, with signature $(g; e_1, \ldots, e_n; \delta)$ where $g=0$.
-Then $R_\halfcan$ is generated in degrees at most $e = \max(e_i)$ with relations generated in degrees at most $2e$.
-\end{cor}
-\begin{proof}
-Let $K$ be the log canonical divisor of the curve $(\sx, \Delta)$ associated to the $\frac{2\alpha}{\beta}$ weight cusp forms.
-We see that $\frac{\beta}{\alpha}\halfcan_\sx\sim K_\sx$, so the floors of each
-
-Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor$ so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.
-Thus, since $\beta\ge 3$, $\deg(K_\sx)\ge 0$.
-Thus $\deg($
-\end{proof}
+}\fi
 

### 2015-06-29 stacky_write_up/spin_cring.tex
editing previous lemma

@@
 %context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
-%half-canonical divisors, although even Lemma
-%~\ref{lem:raise-stacky-order} has certain generalizations, as noted
-%in Remark ~\ref{rem:raise-fractional-order}
+%half-canonical divisors.
 
@@
 \end{rem}
-
-\iffalse{
-Lemma \ref{lem:sat-1} leads to the the following corollaries.
-\todo{do we want this here?}
-\begin{cor}\label{cor-gen-0-with-log}
-If $(\sx, \halfcan, \Delta)$ is a stacky curve with signature $(g; e_1, \ldots, e_n; \delta)$ with $g=0$ and $\delta>0$, then $R_\halfcan$ is generated in degree at most $e=\max(e_i)$ with relations generated in degree at most $2e$.
-\end{cor}
-\begin{proof}
-By remark \ref{rem:delta-not-1}, $\delta\ge 2$ so $\halfcan$ is linearly equivalent to an effective divisor.  Thus, we can recursively apply Lemma \ref{lem:sat-1} to prove the corollary.
-\end{proof}
-}\fi
 

### 2015-06-29 stacky_write_up/spin_cring.tex
address o'dorney in intro, other intro edits

@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, \todo{Peter: comma or colon here?} i.e. a discrete subgroup
+Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
 of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
@@
 The central object of study in this paper is the {\bf log spin
-canonical ring} of $(\sx,\Delta,L)$ is
-\begin{align*}
-	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d L \rfloor)
-\end{align*}
-
-\noindent
-The main theorem of this paper is the following bound on the degree
-of generators and relations of arbitrary log spin canonical rings:
+canonical ring} of $(\sx, \Delta, \halfcan)$ is
+\begin{align*}
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
+\end{align*}
+
+\noindent
+\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
+In particular, we would like to bound the degrees in which the
+graded ring and its relations are generated. The work by O'Dorney
+shows that the canonical ring of any $\BQ$-divisor $D =
+\frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of
+$\BP_k^1$ with $\# \Supp(D) \leq 2$ is generated in degrees up
+to $e := \max(\beta_1, \beta_2)$ with relations generated in
+degrees up to $2e$ \cite[Section 4]{dorney:canonical}. Furthermore,
+O'Dorney gives a larger bound when the support of $D$ is allowed to
+have arbitrarily many points in terms of least-common-multiples.
+Voight and Zureick-Brown also bounded the generator and relation
+degrees of log spin canonical rings of $(\sx, \Delta, \halfcan)$,
+in the case that genus is positive and $\halfcan$ is effective,
+by $3e$ and $6e$ for $e := \max(e_1, \ldots, e_r)$.
+
+The goal of this paper is to provide a stricter bound on the
+generator and relation degrees of log spin canonical rings
+for all genera. Note that O'Dorney's bounds are asymptotically
+strict for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
+to the log spin curve case allows for lower bounds.
+The main theorem of this paper is the following improved bound on
+the degree of generators and relations of log spin canonical rings:
+
+%uses best lower approximations to provide a minimal presentation for the canonical ring of an arbitrary $\BQ$-divisor $D = \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ with $\# \Supp(D) \leq 2$ and shows that it is generated in degree $e := \max(\beta_1, \beta_2)$ with relations generated in degrees at most $2e$ \cite[Section 4]{dorney:canonical}.
+For arbitrarily many points, O'Dorney also provides much larger bounds \cite[Section 5]{dorney:canonical}.
+While
+%
+%In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
+%O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i = 1}^n \frac{\alpha_i
+%}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
+%0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
+%degrees at most $e = \max(\beta_i)$ with relations generated in
+%degrees at most $2e$.
+\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
+If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
+%X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
+%same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
+%To do this, we extend a result by Voight and
+%Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
+%divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
 
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d \halfcan \rfloor)
 \end{align*}
@@
 provides an inductive procedure for determining the generators and
-initial ideal of relations for the half-canonical divisor $\halfcan$ can be written as $\halfcan = \halfcan' + \Lambda$ with
-$(\halfcan', \Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact, such a system of
-generators and relations are known for $\halfcan'$ in many interesting low genus cases,
-as detailed in Neves ~\cite[ Section III.4]{neves:halfcan}.
+initial ideal of relations for the half-canonical divisor $\halfcan$
+ can be written as $\halfcan = \halfcan' + \Lambda$ with $(\halfcan
+', \Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact,
+such a system of generators and relations are known for $\halfcan'$
+in many interesting low genus cases, as detailed in Neves
+~\cite[Section III.4]{neves:halfcan}.
 \end{rem}
@@
 
-\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
-In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a divisor $D = \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise.
-Of course, this is minor, and it's fine to keep it this way.} with at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$.
-\todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points.
-\todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper.
-Can you state this more precisely, or possibly just remove it.}
-
-In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
-O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
-}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
-0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
-degrees at most $e = \max(\beta_i)$ with relations generated in
-degrees at most $2e$.
-\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
-If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
-X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
-To do this, we extend an inductive result \todo{Is ``inductive result'' a phrase? Can we just remove the word ``inductive'' every time it appears?} by Voight and
-Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
-divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e.
@@
 \todo{do this part}
-Part on Kodaira-Spencer \cite{kodaira:complex-manifolds}.
+Part on Kodaira--Spencer \cite{kodaira:complex-manifolds}.
 Use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic 

### 2015-06-29 stacky_write_up/spin_cring.tex
subsequent removed

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 First we present several lemmas which provide the
-inductive steps in the proof of the main theorem: Theorem
+inductive steps for the proof of the main theorem: Theorem
 ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
@@
 $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
-This will be used in the subsequent three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}
+This will be used in three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}
 
@@
 To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
-The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
+The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
 \begin{defn}
@@
 
-Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
+Before stating the Lemma \ref{lem:sat-1}, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
 \todo{Peter: This sentence is very ugly.

### 2015-06-29 stacky_write_up/spin_cring.tex
previous removed from paper

@@
 
-To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
+To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
 The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
@@
 \begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
+If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i P_i}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
 \end{rem}
@@
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
+The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
 When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
@@
 We now restrict our attention to log canonical rings of stacky curves.
-The previous lemma accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.
+Lemma \ref{lem:sat-1} accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.
 We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.
@@
 Instead we turn now to inductive methods to incrementally increase the $e_i$s.
-Combined with the previous lemmas on adding points, these will provide all the necessary inductive tools for the remainder of the paper.
+Combined with the adding points lemmas, these will provide all the necessary inductive tools for the remainder of the paper.
 

### 2015-06-29 stacky_write_up/spin_cring.tex
main corollary revision, minor typographical things

@@
 \newcommand\sssec{\subsubsection}
-\newcommand\bh{{\mathbb H}}
+\newcommand\BH{{\mathbb H}}
 \newcommand\bO{{\mathbf O}}
@@
 Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
-of $PSL_2(\BR)$ acting on the upper half plane $\bh$ by fractional
+of $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
 linear transformations. We consider the {\bf ring of modular forms}
@@
 
-\noindent
-\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
 In particular, we would like to bound the degrees in which the
@@
 the degree of generators and relations of log spin canonical rings:
-
-%uses best lower approximations to provide a minimal presentation for the canonical ring of an arbitrary $\BQ$-divisor $D = \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ with $\# \Supp(D) \leq 2$ and shows that it is generated in degree $e := \max(\beta_1, \beta_2)$ with relations generated in degrees at most $2e$ \cite[Section 4]{dorney:canonical}.
-For arbitrarily many points, O'Dorney also provides much larger bounds \cite[Section 5]{dorney:canonical}.
-While
-%
-%In Lemma ~\ref{lem:sat-1} we provide an inductive method to strengthen
-%O'Dorney's result \cite[Theorem 8]{dorney:canonical} on $\BP^1_k$ to divisors $D = \sum_{i = 1}^n \frac{\alpha_i
-%}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
-%0(X, \lfloor D \rfloor) > 0$. Our result implies that $R_D$ is generated in
-%degrees at most $e = \max(\beta_i)$ with relations generated in
-%degrees at most $2e$.
-\todo{Are you sure you're not assuming $\frac{\alpha}{\beta}$ is effective?
-If not, doesn't what you say contradict Evan's example showing that his bounds of about lcm are asymptotically sharp?} Furthermore, given additional constraints on $H^0(
-%X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
-%same Riemann-Roch \todo{same as what? Maybe just say we can generalize his results to arbitrary genus?} arguments in arbitrary genus. 
-%To do this, we extend a result by Voight and
-%Zureick-Brown \cite[Theorem 8.3.1]{vzb:stacky} on stacky canonical rings to arbitrary $\BQ$-
-%divisors. \todo{Again, I don't think it can be arbitrary, and what are the $\BQ$ divisors on?}
 
@@
 \label{cor:main-mod-forms}
-There exists a log half-canonical divisor $\halfcan$ on $\sx$ such
-that we have a graded isomorphism of $\BC$-algebras
-\[
-	\bigoplus_{k = 0}^{\infty} M_k(\Gamma) \cong R(\sx (\Gamma), 
-\Delta, \halfcan)
-\]
-
-\noindent
-Let $\sigma = (g; e_1, \ldots, e_r; \delta)$ be the signature
-of $\sx$. Then $\bigoplus_{k = 0}^{\infty} M_k(\Gamma)$ is
+Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
+associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
+\ldots, e_r; \delta)$. Then the ring of modular forms
+$M(\Gamma) := \bigoplus_{k = 0}^{\infty} M_k(\Gamma)$ is
 generated as a $\BC$-algebra by elements of degree at most $e = \max
  (5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
-then $R(\sx,\Delta, \halfcan)$ has relations generated in degrees
-up to $\max(11, 2e_1, \ldots, 2e_r)$. Otherwise, $R(\sx, \Delta,
-\halfcan)$ has relations generated in degrees up to $\max(10, 2e_1,
-\ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list
-of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
-for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
-for signatures with $g = 0$.
+then $M(\Gamma)$ has relations generated in degrees up to $\max(11,
+2e_1, \ldots, 2e_r)$. Otherwise, $M(\Gamma)$ has relations
+generated in degrees up to $\max(10, 2e_1, \ldots, 2e_r)$, so long
+as $\sigma$ does not lie in a finite list of exceptional cases, as
+listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
+= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
+0$.
 \end{cor}
@@
 \begin{defn}
+If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
+with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
+\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
+\lfloor \alpha_i \rfloor P_i$.
+
 The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
 \[
-	R(\sx, \Delta, L) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d \halfcan \rfloor)
 \]
 \end{defn}
-\todo{what about floors?}
 
@@
 We can then consider the
-orbifold $\Gamma \backslash \bh$ over $\BC$. For example, in the
-case $\Gamma$ acts freely on $\bh$, $\Gamma \backslash \bh$ is a
+orbifold $\Gamma \backslash \BH$ over $\BC$. For example, in the
+case $\Gamma$ acts freely on $\BH$, $\Gamma \backslash \BH$ is a
 Riemann Surface over $\BC$. It may well be that $\Gamma \backslash
-\bh$ is not compact. Defining $\Delta$ as the divisor of cusps
+\BH$ is not compact. Defining $\Delta$ as the divisor of cusps
 associated to $\Gamma$, we can form a space $\Gamma \backslash
-\bh^*$ which is a compactification of $\Gamma \backslash \bh,$ with
+\BH^*$ which is a compactification of $\Gamma \backslash \BH,$ with
 associated {\bf divisor of cusps} $\Delta$.

### 2015-06-29 stacky_write_up/spin_cring.tex
g0 base case ordering switch

@@
 Part on Kodaira--Spencer \cite{kodaira:complex-manifolds}.
-Use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic 
-geometry.
 
@@
 \begin{align*}
-	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 
+	&a_1 x_{3, 1} x_{7, 2} + a_2 x_{3, 1} x_{7, 1} + a_3 x_{5, 1}^2 = 
 	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} 
-	+ b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
+	&b_1 x_{7, 2}^2 + b_2 x_{7, 1} x_{7, 2} + b_3 x_{7, 1}^2
+	+ b_4 x_{3, 1}^3 x_{5, 1} = 0  &\text{ in degree $14$}
 \end{align*}
@@
 \[
-	a_2 x_{3, 1} x_{7, 1} = a_3 x_{3, 1} x_{7, 2}
+	a_2 x_{3, 1} x_{7, 1} = -a_3 x_{5, 1}^2
 \]
@@
 However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
-$x_{3, 1} x_{7, 2}$ has pole orders $(3, 3, 4)$ so their
+$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
 coefficients must be zero for this equality to hold. We have a
-similar pole-order consideration in forcing $b_1$ to be nonzero.
+similar pole order consideration in forcing $b_1$ to be nonzero.
 
@@
 $k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
-$x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$, the initial
+$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
 ideal of $I$ is
 \[
-	in_\prec(I) = \langle x_{5, 1}^2, x_{7, 1}^2 \rangle
+	in_\prec(I) = \langle x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
 \]

### 2015-06-29 stacky_write_up/spin_cring.tex
fixing some monomial orderings to reflect new understanding of initial ideals

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 \item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
+\item $T\succ S\succ k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ succeed all monomials in $S$ which succeed all monomials in $k[x_1, \ldots, x_n]$)
 \item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
@@
 If so, what is the best way to do so.
-Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows:
+Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows:
 If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
@@
 \item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
-\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
+\item $\deg(f) = \deg(g)$ and $-\ord_P(f) < -\ord_P(g)$
+\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i > r_i$ for the largest $i$ such that $q_i\ne r_i$
 \end{enumerate}
 \end{defn}
-\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.
+\noindent One can easily verify graded $P$-lex these satisfy the conditions of an ordering.
 
@@
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
@@
 \]
-Equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.
+Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.
 If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
@@
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$.
 \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.
@@
 We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).
-Our choice of order on monomials in $k[y_1, \ldots, y_n]$ and block order on those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\prec S\prec k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).
+Our choice of order for monomials in $k[y_1, \ldots, y_n]$ and block order for those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).
+
 Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
-Further suppose $f\not\in \langle V \rangle$, so for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
+Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
 Therefore, $f\in k[u, y_1, \ldots, y_n]$.
-We note that $S$ generate $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
+We note that $S$ generates $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
 That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
@@
 \todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
-We see that we can write $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.
+Thus, we see that if $f\in k[u, y_1, \ldots, y_n]$, then $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{Z}_{\ge 0}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.
 For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.
 If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
-We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_r$.
-Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_h$.
+Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 This gives us condition \ref{lem:relations_from_generators_induction}(3).
-Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we get (b) of this lemma.
+Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we prove (b) of this lemma.
 \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.
@@
 		$y_3, y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
-		y_3$
+	\item[(b)] Equip $k[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
+		y_4$
 		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order with $y_3, y_4$ preceding $x_2, \ldots, x_m$.  Then
+		order with $x_2, \ldots, x_m$ preceding $y_3, y_4$.  Then
 		\begin{align*}
@@
 		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
-		y_4 \prec y_3$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $y_3, y_4, y_5$ precede $x_3, \ldots, x_m$.  Then,
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grevlex$ so that $y_3 \prec 
+		y_4 \prec y_5$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $x_3, \ldots, x_m$ precede $y_3, y_4, y_5$.  Then,
 		\begin{align*}

### 2015-06-29 stacky_write_up/spin_cring.tex
add monomial order ssec, minor bg edit, add to bib

@@
 generated as a $\BC$-algebra by elements of degree at most $e = \max
- (5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
+ (5$, $e_1$, $\ldots$, $e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
 then $M(\Gamma)$ has relations generated in degrees up to $\max(11,
@@
 used throughout the paper. Many of the conventions come from existing
-literature. In particular, we use much of the notation from Voight
-and Zureick-Brown. Here, we briefly present the definitions
-and notation we use.
-
+literature. For basic references on the statements and definitions
+used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
+Saint-Donat \cite{saint-donat:proj}, the book of Arbarello--
+Cornalba--Griffiths--Harris \cite[Section III.2]
+{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
+Chapter 5]{vzb:stacky}.
+
+\ssec{Stacky Curves and Log Spin Canonical Rings}
+\label{ssec:stacky-background}
 A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
@@
 
-\begin{enumerate}
-	\item Note that this result is independence of base field
-	\item background on Gr\"{o}bner bases
-	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
-\end{enumerate}
-
-Define $(R)_d$ to refer to the $d^{th}$ component
+\todo{Note that this result is independence of base field}
+
+If $R$ is a graded ring, then $(R)_d$ refers to the $d^{th}$ degree
+component of $R$.
 
@@
 \end{rem}
+
+\ssec{Monomial Ordering}
+\label{ssec:monomial-order}
+Here we give a brief overview of the monomial orderings
+that we use. For further reference on monomial orderings,
+initial ideals, and Gr\"{o}bner bases, see Eisenbud
+\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--Shea
+\cite[Chapter 2]{cls:ideals-varieties-algorithms}.
+
+We equip the polynomial ring $k[x]_{\vec{a}}$ with the (weighted graded) reverse lexicographic order \defiindex{grevlex} $\prec$: if 
+\[ x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}} \]
+and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m}} \succ x^{\vec{n}}$ if and only if either
+\begin{equation}
+\vec{a}\cdot\vec{m} = \sum_{d,i} dm_{d,i}  > \vec{a} \cdot \vec{n}
+\end{equation}
+or
+\begin{equation} \label{eqn:grevlexdef}
+\text{$\vec{a}\cdot\vec{m} = \vec{a} \cdot \vec{n}$ and the last (right-most) nonzero entry in $\vec{m}-\vec{n}$ is negative.}
+\end{equation}
+It is important to note that in \eqref{eqn:grevlexdef}, the ordering of the variables matters: it corresponds to a choice of writing the exponents of a monomial as a vector.
+A common choice for us will be
+\begin{equation} \label{eqn:xdOrder}
+ x_{1,1}^{m_{1,1}} \cdots x_{D,a_D}^{m_{D,a_D}} \leftrightarrow (m_{D,1},\dots,m_{D,a_D},\ldots,m_{1,1},\dots,m_{1,a_1}) 
+ \end{equation}
+in which case we have $x_{2,1} \succ x_{1,2}^2$
+and $x_{5,1} \succ x_{1,6}^2 x_{3,2}$, etc.
+We indicate this ordering in the presentation of the ring, e.g.~for the above we would write
+\[ k[x]_{\vec{a}}= k[x_{1,1},\dots,x_{1,a_1},\dots,x_{D,1},\dots,x_{D,a_D}]. \]
+In this way, our relations write generators in larger degree in terms of those in smaller degree (``later generators in terms of earlier generators''), which gives the most natural-looking canonical rings to our eyes.
+
+For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\init_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\init_{\prec}(0)=0$.
+Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.
+We define the \textbf{initial ideal} $\init_{\prec}(I)$ to be the ideal generated by $\{\init_{\prec}(f) : f \in I\}$.
+A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that
+\[ \langle \init_{\prec}(f_1),\dots,\init_{\prec}(f_n) \rangle = \init_{\prec}(I). \]
+
+A Gr\"obner basis for $I$ \emph{a priori} depends on a choice of basis for the ambient graded polynomial ring; we now see what happens for a general choice of basis.
+
+background on Gr\"{o}bner bases
+Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
 

### 2015-06-29 stacky_write_up/spin_cring.tex
added fractional weight references

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 First we present several lemmas which provide the
-inductive steps for the proof of the main theorem: Theorem
+inductive steps in the proof of the main theorem: Theorem
 ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
@@
 $\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
-This will be used in three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}
+This will be used in the subsequent three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}
 
@@
 \item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T\succ S\succ k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ succeed all monomials in $S$ which succeed all monomials in $k[x_1, \ldots, x_n]$)
+\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
 \item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
@@
 
-To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
-The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
+To apply the previous lemma, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
+The following definition provides the necessary ordering for the subsequent lemma (Lemma \ref{lem:sat-1}).
 \begin{defn}
@@
 If so, what is the best way to do so.
-Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows:
+Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ reverse lexicographic order {\bf{graded P-revlex}} on $k[z_1, \ldots, z_m]$ as follows:
 If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
@@
 \item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord_P(f) < -\ord_P(g)$
-\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i > r_i$ for the largest $i$ such that $q_i\ne r_i$
+\item $\deg(f) = \deg(g)$ and $-\ord_P(f) > -\ord_P(g)$
+\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i<r_i$ for the largest $i$ such that $q_i\ne r_i$
 \end{enumerate}
 \end{defn}
-\noindent One can easily verify graded $P$-lex these satisfy the conditions of an ordering.
-
-Before stating the Lemma \ref{lem:sat-1}, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
+\noindent One can easily verify graded $P$-reflex these satisfy the conditions of an ordering.
+
+Before stating the subsequent lemma, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
 \todo{Peter: This sentence is very ugly.
@@
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
@@
 \]
-Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.
+Equip $k[y_1, \ldots, y_n]$ with graded P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.
 If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
@@
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$.
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.
 \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.
@@
 We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).
-Our choice of order for monomials in $k[y_1, \ldots, y_n]$ and block order for those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).
-
+Our choice of order on monomials in $k[y_1, \ldots, y_n]$ and block order on those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\prec S\prec k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).
 Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
-Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
+Further suppose $f\not\in \langle V \rangle$, so for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
 Therefore, $f\in k[u, y_1, \ldots, y_n]$.
-We note that $S$ generates $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
+We note that $S$ generate $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
 That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
@@
 \todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
-Thus, we see that if $f\in k[u, y_1, \ldots, y_n]$, then $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{Z}_{\ge 0}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.
+We see that we can write $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{J}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.
 For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.
 If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
-We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_h$.
-Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_r$.
+Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U-i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 This gives us condition \ref{lem:relations_from_generators_induction}(3).
-Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we prove (b) of this lemma.
+Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we get (b) of this lemma.
 \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.
@@
 \begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i P_i}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
+If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
 \end{rem}
@@
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
+The generators in the previous lemma are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
 When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
@@
 We now restrict our attention to log canonical rings of stacky curves.
-Lemma \ref{lem:sat-1} accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.
+The previous lemma accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.
 We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.
@@
 		$y_3, y_4,$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
-		y_4$
+	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
+		y_3$
 		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order with $x_2, \ldots, x_m$ preceding $y_3, y_4$.  Then
+		order with $y_3, y_4$ preceding $x_2, \ldots, x_m$.  Then
 		\begin{align*}
@@
 		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grevlex$ so that $y_3 \prec 
-		y_4 \prec y_5$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $x_3, \ldots, x_m$ precede $y_3, y_4, y_5$.  Then,
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
+		y_4 \prec y_3$
+		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $y_3, y_4, y_5$ precede $x_3, \ldots, x_m$.  Then,
 		\begin{align*}
@@
 %\end{proof}
-%
-%\begin{cor}
-%Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
-%\end{cor}
-%\begin{proof}
-%For a similar reason as in corollary ~\ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta= 0$), so by corollary ~\ref{cor:effective_Q_divisor_can_ring} we get the desired result.
-%\end{proof}
-%
+
 %\todo{Move this Lemma:}
@@
 Instead we turn now to inductive methods to incrementally increase the $e_i$s.
-Combined with the adding points lemmas, these will provide all the necessary inductive tools for the remainder of the paper.
+Combined with the previous lemmas on adding points, these will provide all the necessary inductive tools for the remainder of the paper.
 
@@
 \end{proof}
-
-\begin{rem}
-\label{rem:raise-fractional-order}
-It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-order} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical.
-In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
-\end{rem}
 
@@
 \end{cor}
-	\item Another direction for further research is to extend the results of this paper to fractional modular forms, just as this paper extends the results of Voight and Zureick-Brown \cite{vzb:stacky} from even weight modular forms to odd weight modular forms.
-In particular, we pose the following question:
+	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms.
+As defined in Adler and Ramanan, immediately following \cite[Corollary 24.5]{adler:moduli}, a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$.
+Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$.
+Fractional modular forms also make an apperance in Milnor \cite[$\mathsection$ 6]{milnor:fractional-weight}.
+In this work, Milnor shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3^{e_3} = 0$.
+
+Having motivated the importance of fractional weight modular forms, we pose the following question:
+
 \begin{question}
@@
 \end{question}
-Note that that the above question is answered affirmatively in the case that $\sx$ has signature $(0;e_1,\ldots, e_r;\delta)$ in \todo{Aren't we supposed to mention fractional weight modular forms after an early inductive lemma?
-Can we include this as a remark somewhere?} \todo{Include reference to the fractional weight modular forms remark, in this remark, we should probably reference \cite[Remark 10.2.3]{vzb:stacky}}.
-In fact, we show that if $D \in \di \sx$ so that $nD = K$ for some $n \geq 2$, then $R_D$ is generated in degree at most $e=\max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e$.
-Additionally, Lemma ~\ref{lem:raise-stacky-order} naturally extends to the setting fractional weight modular forms, as noted in Remark ~\ref{rem:raise-fractional-order}.
+Note that that the above question is answered affirmatively in the case that $\sx$ has genus $0$ and $D$ is effective, as follows by inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature $(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most $2e$.
+Additionally, it may be possible to modify the proof of Lemma ~\ref{lem:raise-stacky-order} to extend to the setting of fractional weight modular forms.
+Given suitable generalizations of these lemmas, one may be able to approach the problem of finding generators and relations for fractional weight modular forms using techniques similar to those in this paper.
 	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense.

### 2015-06-29 stacky_write_up/spin_cring.tex
fix noncompilation of vzb copied stuff

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 \label{ssec:monomial-order}
-Here we give a brief overview of the monomial orderings
+Here we give a brief overview of the three monomial orderings
 that we use. For further reference on monomial orderings,
@@
 
-We equip the polynomial ring $k[x]_{\vec{a}}$ with the (weighted graded) reverse lexicographic order \defiindex{grevlex} $\prec$: if 
-\[ x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}} \]
-and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m}} \succ x^{\vec{n}}$ if and only if either
+\begin{defn}
+We equip the polynomial ring $k[x_1, \ldots, x_n]$ with the
+(weighted graded) reverse lexicographic order \textbf{grevlex}
+$\prec$: if 
+\[
+	x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}}
+\]
+
+\noindent
+and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m
+}} \succ x^{\vec{n}}$ if and only if either
 \begin{equation}
@@
 
-For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\init_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\init_{\prec}(0)=0$.
+For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.
 Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.
-We define the \textbf{initial ideal} $\init_{\prec}(I)$ to be the ideal generated by $\{\init_{\prec}(f) : f \in I\}$.
+We define the \textbf{initial ideal} $\initial_{\prec}(I)$ to be the ideal generated by $\{\initial_{\prec}(f) : f \in I\}$.
 A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that
-\[ \langle \init_{\prec}(f_1),\dots,\init_{\prec}(f_n) \rangle = \init_{\prec}(I). \]
-
-A Gr\"obner basis for $I$ \emph{a priori} depends on a choice of basis for the ambient graded polynomial ring; we now see what happens for a general choice of basis.
+\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]
+
+\begin{rem}
+A Gr\"obner basis for $I$ \emph{a priori} depends on a choice of basis for the ambient graded polynomial ring.
+\end{rem}
+
+We also introduce a term ordering that is well-suited for inductive arguments: the \emph{block} term order.  
+In our inductive arguments, we will often have the following setup: an inclusion $R \supset R'$ of canonical rings such that $R'$ is generated by elements $x_{i,d}$ and $R$ is generated over $R$ by elements $y_j$.
+It is natural, therefore, to consider term orders which treat these sets of variables separately.
+More formally, we make the following definition.
+
+Let $k[x]_{\vec{a}}$ and $k[y]_{\vec{b}}$ be weighted polynomial rings with term orders $\prec_x$ and $\prec_y$, respectively, and consider $k[y,x]_{\vec{b},\vec{a}} = k[y]_{\vec{b}} \otimes_k k[x]_{\vec{a}}$ the common weighted polynomial ring in these two sets of variables $y,x$.
+
+\begin{defn}
+The \textbf{(graded) block} (or \textbf{elimination}) term ordering on $k[y,x]_{\vec{b},\vec{a}}$ is defined as follows: we declare
+  \[ y^{\vec{m}}x^{\vec{n}}  \succ y^{\vec{m}'}x^{\vec{n}'}\]  
+  if and only if
+  \begin{enumerate}
+  \item[(i)] $\deg y^{\vec{m}} x^{\vec{n}}  > \deg y^{\vec{m}'} x^{\vec{n}'} $, or
+  \item[(ii)] $\deg y^{\vec{m}}x^{\vec{n}} = \deg y^{\vec{m}'} x^{\vec{n}'} $ and 
+    \begin{enumerate}
+    \item $y^{\vec{m}}\succ_y y^{\vec{m}'}$ or
+    \item $y^{\vec{m}} =  y^{\vec{m}'}$ and $x^{\vec{n}} \succ_x x^{\vec{n}'}$.
+    \end{enumerate}
+  \end{enumerate}
+\end{defn}
+
+The block ordering is indeed a term order: the displayed inequalities directly give that any two monomials are comparable, and the inequalities are visibly stable under multiplication by a monomial.
+One can similarly define an \textbf{iterated (graded) block} term ordering for any finite number of weighted polynomial rings.
+
+The block ordering is the most suitable ordering for the structure of $R$ as an $R'$-algebra
 

### 2015-06-29 stacky_write_up/spin_cring.tex
added extra end defn
section 3 edits???

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 generated as a $\BC$-algebra by elements of degree at most $e = \max
- (5$, $e_1$, $\ldots$, $e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
+ (5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
 then $M(\Gamma)$ has relations generated in degrees up to $\max(11,
@@
 used throughout the paper. Many of the conventions come from existing
-literature. For basic references on the statements and definitions
-used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
-Saint-Donat \cite{saint-donat:proj}, the book of Arbarello--
-Cornalba--Griffiths--Harris \cite[Section III.2]
-{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
-Chapter 5]{vzb:stacky}.
-
-\ssec{Stacky Curves and Log Spin Canonical Rings}
-\label{ssec:stacky-background}
+literature. In particular, we use much of the notation from Voight
+and Zureick-Brown. Here, we briefly present the definitions
+and notation we use.
+
 A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
@@
 
-\todo{Note that this result is independence of base field}
-
-If $R$ is a graded ring, then $(R)_d$ refers to the $d^{th}$ degree
-component of $R$.
+\begin{enumerate}
+	\item Note that this result is independence of base field
+	\item background on Gr\"{o}bner bases
+	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
+\end{enumerate}
+
+Define $(R)_d$ to refer to the $d^{th}$ component
 
@@
 \end{rem}
-
-\ssec{Monomial Ordering}
-\label{ssec:monomial-order}
-Here we give a brief overview of the three monomial orderings
-that we use. For further reference on monomial orderings,
-initial ideals, and Gr\"{o}bner bases, see Eisenbud
-\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--Shea
-\cite[Chapter 2]{cls:ideals-varieties-algorithms}.
-
-\begin{defn}
-We equip the polynomial ring $k[x_1, \ldots, x_n]$ with the
-(weighted graded) reverse lexicographic order \textbf{grevlex}
-$\prec$: if 
-\[
-	x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}}
-\]
-
-\noindent
-and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m
-}} \succ x^{\vec{n}}$ if and only if either
-\begin{equation}
-\vec{a}\cdot\vec{m} = \sum_{d,i} dm_{d,i}  > \vec{a} \cdot \vec{n}
-\end{equation}
-or
-\begin{equation} \label{eqn:grevlexdef}
-\text{$\vec{a}\cdot\vec{m} = \vec{a} \cdot \vec{n}$ and the last (right-most) nonzero entry in $\vec{m}-\vec{n}$ is negative.}
-\end{equation}
-It is important to note that in \eqref{eqn:grevlexdef}, the ordering of the variables matters: it corresponds to a choice of writing the exponents of a monomial as a vector.
-A common choice for us will be
-\begin{equation} \label{eqn:xdOrder}
- x_{1,1}^{m_{1,1}} \cdots x_{D,a_D}^{m_{D,a_D}} \leftrightarrow (m_{D,1},\dots,m_{D,a_D},\ldots,m_{1,1},\dots,m_{1,a_1}) 
- \end{equation}
-in which case we have $x_{2,1} \succ x_{1,2}^2$
-and $x_{5,1} \succ x_{1,6}^2 x_{3,2}$, etc.
-We indicate this ordering in the presentation of the ring, e.g.~for the above we would write
-\[ k[x]_{\vec{a}}= k[x_{1,1},\dots,x_{1,a_1},\dots,x_{D,1},\dots,x_{D,a_D}]. \]
-In this way, our relations write generators in larger degree in terms of those in smaller degree (``later generators in terms of earlier generators''), which gives the most natural-looking canonical rings to our eyes.
-
-For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.
-Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.
-We define the \textbf{initial ideal} $\initial_{\prec}(I)$ to be the ideal generated by $\{\initial_{\prec}(f) : f \in I\}$.
-A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that
-\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]
-
-\begin{rem}
-A Gr\"obner basis for $I$ \emph{a priori} depends on a choice of basis for the ambient graded polynomial ring.
-\end{rem}
-
-We also introduce a term ordering that is well-suited for inductive arguments: the \emph{block} term order.  
-In our inductive arguments, we will often have the following setup: an inclusion $R \supset R'$ of canonical rings such that $R'$ is generated by elements $x_{i,d}$ and $R$ is generated over $R$ by elements $y_j$.
-It is natural, therefore, to consider term orders which treat these sets of variables separately.
-More formally, we make the following definition.
-
-Let $k[x]_{\vec{a}}$ and $k[y]_{\vec{b}}$ be weighted polynomial rings with term orders $\prec_x$ and $\prec_y$, respectively, and consider $k[y,x]_{\vec{b},\vec{a}} = k[y]_{\vec{b}} \otimes_k k[x]_{\vec{a}}$ the common weighted polynomial ring in these two sets of variables $y,x$.
-
-\begin{defn}
-The \textbf{(graded) block} (or \textbf{elimination}) term ordering on $k[y,x]_{\vec{b},\vec{a}}$ is defined as follows: we declare
-  \[ y^{\vec{m}}x^{\vec{n}}  \succ y^{\vec{m}'}x^{\vec{n}'}\]  
-  if and only if
-  \begin{enumerate}
-  \item[(i)] $\deg y^{\vec{m}} x^{\vec{n}}  > \deg y^{\vec{m}'} x^{\vec{n}'} $, or
-  \item[(ii)] $\deg y^{\vec{m}}x^{\vec{n}} = \deg y^{\vec{m}'} x^{\vec{n}'} $ and 
-    \begin{enumerate}
-    \item $y^{\vec{m}}\succ_y y^{\vec{m}'}$ or
-    \item $y^{\vec{m}} =  y^{\vec{m}'}$ and $x^{\vec{n}} \succ_x x^{\vec{n}'}$.
-    \end{enumerate}
-  \end{enumerate}
-\end{defn}
-
-The block ordering is indeed a term order: the displayed inequalities directly give that any two monomials are comparable, and the inequalities are visibly stable under multiplication by a monomial.
-One can similarly define an \textbf{iterated (graded) block} term ordering for any finite number of weighted polynomial rings.
-
-The block ordering is the most suitable ordering for the structure of $R$ as an $R'$-algebra
-
-background on Gr\"{o}bner bases
-Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
 
@@
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$.
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$).
 \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.
@@
 \label{ssec:raise-orders}
-In this subsection, we aim to prove Lemma
-~\ref{lem:raise-stacky-order}, whose proof is almost identical to that of \cite[Theorem 8.5.7]{vzb:stacky}. In many cases, Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem 
+In this subsection, we present Lemma
+~\ref{lem:raise-stacky-order}, whose proof is almost identical to one of Voight and Zureick-Brown \cite[Theorem 8.5.7]{vzb:stacky}.
+Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem
 ~\ref{thm:main}, holds for a curve with signature
-$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta),$ with $e_{k+1}' = \cdots = e_r',$ then Theorem ~\ref{thm:main} also holds for a curve with
-signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta).$ In order to state Lemma
-~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
-
-One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and \cite[Definition 8.5.1]{vzb:stacky} is that in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ However, we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $L_X$ is not necessarily basepoint-free.
-Therefore, we will have to work with orders of zeros of poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
+$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k+1}' = \cdots = e_r'$ satisfying certain admissibility (cf.
+Definition ~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for a curve with
+signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta)$. 
+%In order to state Lemma
+%~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in %Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
+
+One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
+%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
+we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.
+We circumvent this issue by working with orders of zeros and poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
 

### 2015-06-29 stacky_write_up/spin_cring.tex

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 In this way, our relations write generators in larger degree in terms of those in smaller degree (``later generators in terms of earlier generators''), which gives the most natural-looking canonical rings to our eyes.
+\end{defn}
 

### 2015-06-29 stacky_write_up/spin_cring.tex
Edits to section 3 (3.9-3.13)

@@
 we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.
-We circumvent this issue by working with orders of zeros and poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
+We circumvent this issue by working with the orders of zeros and poles relative to the divisor we are inducting from, rather than relative to the structure sheaf.\todo{Peter: This last sentence is kind of awkward.
+I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner...
+I hope...}
 
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
+curves, with the same course space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
 \{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
@@
 Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
-to be {\bf admissible} if the $R'$ admits a presentation
+to be {\bf admissible} if $R'$ admits a presentation
 \begin{align*}
@@
 \noindent
-with $y_{i, e_i'} \in R'$ for each $i \in J$ such that the following
-three conditions hold.
-
-\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number.
-What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$.
-Aaron: By all means, please suggest better notation and we can discuss it.
-However, I think your particular concern is well answered because we include the further subscript $i$.
-That is, $y_{1,e_1} \neq y_{2,e_2}$ even if $e_1 = e_2=5$, because $y_{1,5}$ and $y_{2,5}$ are different variables.
-Another thing to note here is that $e_i' = e_i + 2,$ so that the two will never be equal.
-Does this assuage your concern?
-Also, Further, when I read David's paper, he used this notation, and I was never confused by this notation.}
+with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
+three conditions hold:
 \begin{enumerate}
@@
 	\end{align*}
-		\item[(Ad-ii)] Second, every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
+		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
 		\begin{align*}
@@
 \end{rem}
+\todo{Peter: I'm not sure how useful this remark is.
+After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.
+The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
 
@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}
+Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}.
+\todo{Peter: In general, I'm not sure how important it is for us to draw all the analogs between your definition and proofs and those of VZB.
+As long as we make not in the section's introduction that they are similar, we might leave it out of the remaining transitions and remarks.}
 
@@
 Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
-stronger condition that
+stronger condition \todo{Peter: How is it a stronger condition if it implied by that of (Ad-ii).
+If $a\implies b$ then $b$ is by definition a weaker condition right?
+I agree that the latter condition is somehow better, but it seems inaccurate to call it stronger.
+I may be being over picky here...} that
 
@@
 \label{rem:three-cases}
-For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
+For our inductive arguments in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
 stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
 curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
-\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
+\delta)$, and our base cases include signatures $\sigma$ characterized by one of the following:
 \begin{enumerate}
@@
 We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
-analog of ~\cite[Theorem 8.5.7]{vzb:stacky}
+analog of ~\cite[Theorem 8.5.7]{vzb:stacky}.
 

### 2015-06-29 stacky_write_up/spin_cring.tex
section 1 edits

@@
 If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve?
-shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if
-$$\di \sx = \di X \oplus \left(\bigoplus_{i
-= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
-As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points.
-A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
+shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if
+\[
+	\di \sx = \di X \oplus \left(\bigoplus_{i
+	= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
+\]\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?}
+As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points.
+\todo{I don't know if this is a good statement to make.
+We aren't really viewing $\sx$ as a scheme.
+Rather we're are determining information about its canonical rings through knowledge of scheme data.}  A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
 The central object of study in this paper is the {\bf log spin
@@
 In particular, we would like to bound the degrees in which the
-graded ring and its relations are generated. The work by O'Dorney
+graded ring and its relations are generated.  O'Dorney
 shows that the canonical ring of any $\BQ$-divisor $D =
 \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of
-$\BP_k^1$ with $\# \Supp(D) \leq 2$ is generated in degrees up
+$\BP_k^1$ (i.e. $\# \Supp(D) \leq 2$) is generated in degrees up
 to $e := \max(\beta_1, \beta_2)$ with relations generated in
-degrees up to $2e$ \cite[Section 4]{dorney:canonical}. Furthermore,
-O'Dorney gives a larger bound when the support of $D$ is allowed to
-have arbitrarily many points in terms of least-common-multiples.
+degrees up to $2e$ \cite[Theorem 6]{dorney:canonical}. Furthermore,
+O'Dorney gives a larger bound in terms of least common multiples of the denominators when the support of $D$ is allowed to
+have arbitrarily many points.
 Voight and Zureick-Brown also bounded the generator and relation

### 2015-06-29 stacky_write_up/spin_cring.tex
write monomial ordering ssec of bg

@@
 
+First, we give a definition of the graded degree of a monomial
+in a graded polynomial ring.
+
 \begin{defn}
-We equip the polynomial ring $k[x_1, \ldots, x_n]$ with the
-(weighted graded) reverse lexicographic order \textbf{grevlex}
-$\prec$: if 
+\label{defn:monomial-degree}
+Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
+ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
+k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
+we define
+
 \[
-	x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}}
+	\deg \alpha := \sum_{i = 1}^{n} d f_i
 \]
-
-\noindent
-and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m
-}} \succ x^{\vec{n}}$ if and only if either
+\end{defn}
+
+Now define the (graded) lexicographic order \textbf{grlex}
+$\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
+x_{d_n, n}]$ to be the monomial ordering such that:
+
+\begin{defn}
+\label{defn:grlex}
+If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
 \begin{equation}
-\vec{a}\cdot\vec{m} = \sum_{d,i} dm_{d,i}  > \vec{a} \cdot \vec{n}
+	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
 \end{equation}
-or
-\begin{equation} \label{eqn:grevlexdef}
-\text{$\vec{a}\cdot\vec{m} = \vec{a} \cdot \vec{n}$ and the last (right-most) nonzero entry in $\vec{m}-\vec{n}$ is negative.}
+or $\alpha$ is larger using the lexicographical ordering event of equal
+degrees:
+
+\begin{equation}
+\label{eqn:grlex-tie}
+	\deg \alpha = \deg \beta \text{ and }
+	\alpha \succ_{\text{lex}} \beta
 \end{equation}
-It is important to note that in \eqref{eqn:grevlexdef}, the ordering of the variables matters: it corresponds to a choice of writing the exponents of a monomial as a vector.
-A common choice for us will be
-\begin{equation} \label{eqn:xdOrder}
- x_{1,1}^{m_{1,1}} \cdots x_{D,a_D}^{m_{D,a_D}} \leftrightarrow (m_{D,1},\dots,m_{D,a_D},\ldots,m_{1,1},\dots,m_{1,a_1}) 
+\end{defn}
+
+We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
+with the (weighted graded) reverse lexicographic order
+\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
+
+\begin{defn}
+\label{defn:grevlex}
+If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
+
+\begin{equation}
+	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
 \end{equation}
-in which case we have $x_{2,1} \succ x_{1,2}^2$
-and $x_{5,1} \succ x_{1,6}^2 x_{3,2}$, etc.
-We indicate this ordering in the presentation of the ring, e.g.~for the above we would write
-\[ k[x]_{\vec{a}}= k[x_{1,1},\dots,x_{1,a_1},\dots,x_{D,1},\dots,x_{D,a_D}]. \]
-In this way, our relations write generators in larger degree in terms of those in smaller degree (``later generators in terms of earlier generators''), which gives the most natural-looking canonical rings to our eyes.
+or $\alpha$ has a smaller right-most entry in the event of equal
+degrees:
+
+\begin{equation}
+\label{eqn:grevlex-tie}
+	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
+the	largest } i \text{ such that } f_i \neq f_i'
+\end{equation}
 \end{defn}
 
+\begin{rem}
+Note that the ordering of the variables matters in both
+Equation ~\ref{eqn:grlex-tie} and Equation ~\ref{eqn:grevlex-tie}.
+\end{rem}
+
+Our inductive arguments in Section ~\ref{sec:induction} will
+usually have an inclusion $R \supset R'$ of log spin canonical
+rings such that $R'$ is generated by elements $x_{d_i, i}$ and $R$
+is generated over $R'$ by elements $y_j$. In these cases, it is
+natural to consider term orders which treat these sets of variables
+separately. We now present the \textbf{block term order} introduced
+by Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
+
+\begin{defn}
+\label{defn:block-order}
+Let $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and $k[y_{c_1, 1}, \ldots,
+y_{c_m, m}]$ be weighted polynomial rings with existing term
+orders $\prec_x$ and $\prec_y$, respectively. Let $\alpha :=
+\prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ $\prod_{j = 1}^{m} y_{c_j, j}
+^{h_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}
+\prod_{j = 1}^{m} y_{c_j, j}^{h_i'}$ be monomials in $k[x_{d_1, 1},
+\ldots, x_{d_n, n}] \otimes$ $k[y_{d_1', 1}, \ldots, y_{d_m', m}]$.
+Let $\alpha_x := \prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ be the
+part of $\alpha$ in $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and
+likewise with $\alpha_y$, $\beta_x$, and $\beta_y$.
+
+In the \textbf{(graded) block} (or \textbf{elimination}) term
+ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
+\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
+  \begin{enumerate}
+  \item[(i)] $\deg \alpha  > \deg \beta$ or
+  \item[(ii)] $\deg \alpha = \deg \beta$ and 
+    \begin{enumerate}
+    \item $\alpha_y \succ_y \beta_y$ or
+    \item $\alpha_y =  \beta_y$ and $\alpha_x \succ_x \beta_x$
+    \end{enumerate}
+  \end{enumerate}
+\end{defn}
+
+\todo{write below part}
 For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.
@@
 \end{rem}
-
-We also introduce a term ordering that is well-suited for inductive arguments: the \emph{block} term order.  
-In our inductive arguments, we will often have the following setup: an inclusion $R \supset R'$ of canonical rings such that $R'$ is generated by elements $x_{i,d}$ and $R$ is generated over $R$ by elements $y_j$.
-It is natural, therefore, to consider term orders which treat these sets of variables separately.
-More formally, we make the following definition.
-
-Let $k[x]_{\vec{a}}$ and $k[y]_{\vec{b}}$ be weighted polynomial rings with term orders $\prec_x$ and $\prec_y$, respectively, and consider $k[y,x]_{\vec{b},\vec{a}} = k[y]_{\vec{b}} \otimes_k k[x]_{\vec{a}}$ the common weighted polynomial ring in these two sets of variables $y,x$.
-
-\begin{defn}
-The \textbf{(graded) block} (or \textbf{elimination}) term ordering on $k[y,x]_{\vec{b},\vec{a}}$ is defined as follows: we declare
-  \[ y^{\vec{m}}x^{\vec{n}}  \succ y^{\vec{m}'}x^{\vec{n}'}\]  
-  if and only if
-  \begin{enumerate}
-  \item[(i)] $\deg y^{\vec{m}} x^{\vec{n}}  > \deg y^{\vec{m}'} x^{\vec{n}'} $, or
-  \item[(ii)] $\deg y^{\vec{m}}x^{\vec{n}} = \deg y^{\vec{m}'} x^{\vec{n}'} $ and 
-    \begin{enumerate}
-    \item $y^{\vec{m}}\succ_y y^{\vec{m}'}$ or
-    \item $y^{\vec{m}} =  y^{\vec{m}'}$ and $x^{\vec{n}} \succ_x x^{\vec{n}'}$.
-    \end{enumerate}
-  \end{enumerate}
-\end{defn}
-
-The block ordering is indeed a term order: the displayed inequalities directly give that any two monomials are comparable, and the inequalities are visibly stable under multiplication by a monomial.
-One can similarly define an \textbf{iterated (graded) block} term ordering for any finite number of weighted polynomial rings.
-
-The block ordering is the most suitable ordering for the structure of $R$ as an $R'$-algebra
-
-background on Gr\"{o}bner bases
-Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
 
@@
 Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and define
+Let $I_{L, d}$ be the $d$th graded piece of $I_L$ and define
 $$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$$
@@
 so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i,j} = H^0(\sx',iK_{\sx'})$.
+x_{7, 2}$ with $x_{i,j} \in H^0(\sx', i K_{\sx'})$.
 
@@
 relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / in_\prec(I))_d$ for all degrees
-$d \geq 0$. In particular,
+(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / in_\prec(I))_d$ for 
+all degrees $d \geq 0$. In particular,
 

### 2015-06-29 stacky_write_up/spin_cring.tex
small edits on 3.1

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 \newcommand{\se}[1]{\section*{Problem #1}}
-\newcommand \halfcan{L}
-\newcommand \Supp{\text{Supp}}
-\newcommand \initial{\text{in}}
-\newcommand \gin{\text{gin}}
-\newcommand \Eff{\text{Eff}}
-\newcommand \sat{\text{sat}}
+\newcommand{\halfcan}{L}
+\DeclareMathOperator{\Supp}{Supp}
+\DeclareMathOperator{\initial}{in}
+\DeclareMathOperator{\gin}{gin}
+\DeclareMathOperator{\Eff}{Eff}
+\DeclareMathOperator{\sat}{sat}
 
@@
 \todo{Peter: I don't like the first thing our reader will read to be a dependent clause}
+\todo{Comprehensive change: make sure $\subset$ and $\subseteq$ notation is standardized throughout paper}
 
@@
 %where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
-$\halfcan \in \di
+$\halfcan' \in \di
 X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
@@
 Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-
-Before proving three lemmas that allow us to inductively add points to the support of a divisor (i.e.
-$\halfcan\to \halfcan + \frac{\alpha}{\beta}P$), we give a criteria to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
-This will be used in three lemmas of this section to show, in each case, that a chosen homogeneous ideal is in fact the ideal of relations.\todo{Peter:This last sentence is a little redundant}
+\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial_\succ(I)$. We can even build this in to the macro possibly? }
+Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
+This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
 
@@
 Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
-and $R_{\halfcan}$ minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
+and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
+$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
@@
 \item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T\succ S\succ k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ succeed all monomials in $S$ which succeed all monomials in $k[x_1, \ldots, x_n]$)
+\item $T\succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
 \item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
@@
 Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
-This demonstrates that
-\begin{align*}
-	\initial(I) & \supseteq \langle T \rangle.
-\end{align*}
-
-Next, suppose $f\in S$.
-Note that by (2) any polynomial $G$ in $x_1,\ldots, x_m, y_1, \ldots, y_n$ with initial term in $S$ cannot have a term in $T$.
-Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), any such polynomial does not map to an element of $R_{\halfcan'}$ (since it has a non-zero constant factor with $f$).
-\todo{Peter: Is this abuse of notation okay?} Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
+This demonstrates that $\initial(I) \supseteq T$, and hence
+\[
+	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
+\]
+
+To complete the proof, it suffices to show the reverse inclusion holds.
+By (2), any polynomial $G\in k[x_1,\ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
+Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
 Therefore,
@@
 \]
-
+\todo{Aaron: There is a small abuse of notation here: S is a set of monomials whereas $I$ is an ideal.
+Don't we really want to make clear that $S$ is a $k$ vector space?
+Alternatively, perhaps you want to talk about the monomials in $\initial(I)$ instead of all of the ideal}
 Finally, note that
@@
 
-Therefore, since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ by (3),\todo{Peter: A little bit awkwardly phrased with way too many commas}
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
+By (3), every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
+\begin{align*}
+	\initial(I) & \subseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
 \end{align*}
@@
 we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to the divisor we are inducting from, rather than relative to the structure sheaf.\todo{Peter: This last sentence is kind of awkward.
-I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner...
-I hope...}
+We circumvent this issue by working with orders of zeros and poles relative to the divisor we are inducting from, instead of relative to the structure sheaf.
 
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same course space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
+curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
 \{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
@@
 Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
-to be {\bf admissible} if $R'$ admits a presentation
+to be {\bf admissible} if the $R'$ admits a presentation
 \begin{align*}
@@
 \noindent
-with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
-three conditions hold:
+with $y_{i, e_i'} \in R'$ for each $i \in J$ such that the following
+three conditions hold.
+
+\todo{Peter:I'm still kind of unhappy with the notation $y_{e_i'}$ because it is treating $e_i'$ like a formal object rather than a number.
+What I mean is if $e_1'=e_2'$ that a reader might reasonably interpret $y_{e_1'}$ the same as $y_{e_2'}$.
+Aaron: By all means, please suggest better notation and we can discuss it.
+However, I think your particular concern is well answered because we include the further subscript $i$.
+That is, $y_{1,e_1} \neq y_{2,e_2}$ even if $e_1 = e_2=5$, because $y_{1,5}$ and $y_{2,5}$ are different variables.
+Another thing to note here is that $e_i' = e_i + 2,$ so that the two will never be equal.
+Does this assuage your concern?
+Also, Further, when I read David's paper, he used this notation, and I was never confused by this notation.}
 \begin{enumerate}
@@
 	\end{align*}
-		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
+		\item[(Ad-ii)] Second, every generator $z \neq y_{i, e_i'}$	of $R'$ satisfies
 		\begin{align*}
@@
 \end{rem}
-\todo{Peter: I'm not sure how useful this remark is.
-After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.
-The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
 
@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}.
-\todo{Peter: In general, I'm not sure how important it is for us to draw all the analogs between your definition and proofs and those of VZB.
-As long as we make not in the section's introduction that they are similar, we might leave it out of the remaining transitions and remarks.}
+Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}
 
@@
 Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
-stronger condition \todo{Peter: How is it a stronger condition if it implied by that of (Ad-ii).
-If $a\implies b$ then $b$ is by definition a weaker condition right?
-I agree that the latter condition is somehow better, but it seems inaccurate to call it stronger.
-I may be being over picky here...} that
+stronger condition that
 
@@
 \label{rem:three-cases}
-For our inductive arguments in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
+For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
 stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
 curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
-\delta)$, and our base cases include signatures $\sigma$ characterized by one of the following:
+\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
 \begin{enumerate}
@@
 We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
-analog of ~\cite[Theorem 8.5.7]{vzb:stacky}.
+analog of ~\cite[Theorem 8.5.7]{vzb:stacky}
 

### 2015-06-30 stacky_write_up/spin_cring.tex
edited section 3.1 except the monster lemma

--- 2015-06-29 stacky_write_up/spin_cring.tex
@@
 \newcommand \rk{\text{rk }}
-\newcommand \di{\text{Div }}
+\DeclareMathOperator\di{Div}
 \newcommand \depth{\text{depth }}
@@
 \]
-\todo{Aaron: There is a small abuse of notation here: S is a set of monomials whereas $I$ is an ideal.
-Don't we really want to make clear that $S$ is a $k$ vector space?
-Alternatively, perhaps you want to talk about the monomials in $\initial(I)$ instead of all of the ideal}
+\todo{Aaron: This is correct, but it might be clearer to say there are no monomials in $I$ with initial term in $S$. }
 Finally, note that
@@
 
-To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.  \todo{Reference the lemma, instead of using previous, since things might get moved around}
+To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.
+\todo{Reference the lemma, instead of using previous, since things might get moved around.
+Aaron: Great, thanks!}
 The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
 \begin{defn}
+\label{defn:graded-p-lex}
 Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.
-Then we have a map $\phi$ from the polynomial ring $k[z_1, \ldots z_m]$ to $R_\halfcan$ given by $z_i\mapsto x_i$.
+Then we have a map $\phi: k[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
 \todo{Do we need to instantiate the $z_i$.
 If so, what is the best way to do so.
-Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows:
-If $f=\prod_{i=1}^m {z_i}^{q_i}\ne g=\prod_{i=1}^m {z_i}^{r_i}$, then $f\prec g$ if one of the following holds:
+Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.
+Aaron: No, what you say is great!}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows.
+If $f=\prod_{i=1}^m {z_i}^{q_i}$ and $g=\prod_{i=1}^m {z_i}^{r_i}$ with $f \neq g,$ then $f\prec g$ if one of the following holds:
 \begin{enumerate}
@@
 \end{defn}
-\noindent One can easily verify graded $P$-lex these satisfy the conditions of an ordering.
-
-Before stating the Lemma \ref{lem:sat-1}, which improves O'Dorney's bounds on generators and relations over $\mathbb{P}^1$ \cite[Theorem 8]{dorney:canonical} in the case of effective divisors, we first introduce some of his notation \cite{dorney:canonical}.
+
+\todo{Perhaps note that this ordering is independent of whether we take the order relative to a line bundle}
+\noindent One can easily verify graded $P$-lex is a monomial ordering in the sense defined in Cox--Little--Shea \cite[Chapter 2, $\mathsection$ 2, Definition 1]{cls:ideals-varieties-algorithms}.
+
+We area almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective divisor.
+While in O'Dorney \cite[Theorem 8]{dorney:canonical} gives a bound for the degree of generation of arbitrary $D \in \di \BP^1$, we obtain a much tighter bound in the case $D$ is effective.
+Furthermore, Lemma ~\ref{lem:sat-1} also applies to curves of genus $g > 0$.
+Before stating Lemma ~\ref{lem:sat-1}, we recall some notation from O'Dorney \cite{dorney:canonical}.
+
 \todo{Peter: This sentence is very ugly.
@@
 How should we state it better?
-Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.}
+Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.
+Aaron: Do you like it any better now?}
 
@@
 \end{defn}
-Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a sequence
+Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a finite sequence
 \[
@@
 \]
-Refer to figure \ref{fig:s14/5-lattice} for an example of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
-
-\todo{Peter: Do we want this as an [H] figure; this seems a little non-standard and can create problems with display.  Nonetheless, I copied this format to match the figure in a later section}
+Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
+
+\todo{Peter: Do we want this as an [H] figure; this seems a little non-standard and can create problems with display.
+Nonetheless, I copied this format to match the figure in a later section.
+Aaron: I'm fine with not making it an [H]}
 \begin{figure}[H]\label{fig:s14/5-lattice}
 \includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}$ with a ``$\bullet$'' and each other lattice point below $5y=14x$ with a ``$\circ$''.
+\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each $\circ$ denotes a lattice point below $5y=14x$ which is not a best lower approximation.
 Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}
@@
 
-We can now prove our first adding-points lemma.
+We can now prove our first lemma for adding points.
 
@@
 for some $\alpha,\beta \in \mathbb{N}$ such that
-\begin{equation}
+\begin{align}
 \label{eqn:deg1-sat-ind}
-	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
-	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
-	N} \text{ such that } d \ge \frac{\beta}{\alpha},
-\end{equation}
-and let
+	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X,\lfloor d\halfcan'
+	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
+	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
+\end{align}
+Let
 \[
@@
 \[
-	\ord_u(f) < \ord_u(g) \implies f\prec g.
+	\ord_u(f) < \ord_u(h) \implies f\prec h.
 \]
-Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order on $y_1, \ldots, y_n$ precedence over that on $u, x_1, \ldots, x_m$.
-If $I'$ and $I$ are the ideal of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
+Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order giving $y_1, \ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.
+If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
 
@@
 										 + \langle U_i: 1 \le i \le n-1 \rangle
-										 + \langle V \rangle\\
+										 + \langle V \rangle,\\
 \end{align*}
@@
 $V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
- and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}^{\ge 0}$ such that
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}_{\ge 0}$ such that
 \begin{enumerate}
-	\item[(1)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$\\
-	\item[(2)] there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1})$ \\
+	\item[(1)] $\sum_{j=1}^i a_j c_j \ge c_{i+1},$\\
+	\item[(2)] there does not exist $(b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1},$ \\
 	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
@@
 On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.
-Maybe in a remark after the lemma?}
+Maybe in a remark after the lemma?
+Aaron: I like including it in the lemma.
+I think it's really the most important point of this, so it's fine to include it here.
+It's also ok to just include this as a statement after parts a and b, if we don't particularly care about referencing part c.}
 %\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
@@
 \begin{proof}
+{\bf Part (a):}
 By
@@
 \[
-	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
+	S_0 = \{u^l : l\in \mathbb{Z}_{\ge 0}\}
 \]
@@
 
+{\bf Part (b):}
 Define $U_i$ and $V$ as in the lemma's statement and define
@@
 
+{\bf Part (c):}
 Finally, (c) of this lemma follows immediately by looking at the constructions of parts (a) and (b).
@@
 \begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i P_i}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
+If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i}$ for some odd $e_i\in \mathbb{N}_{\geq 3}$, then $T,$ as defined in the beginning of the proof of (b) in Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
 \end{rem}
@@
 We now restrict our attention to log canonical rings of stacky curves.
-Lemma \ref{lem:sat-1} accounts for the relevant induction cases when the spin canonical ring is already saturated in 1.
-We complement it with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated at degrees two and three.
+Lemma \ref{lem:sat-1} accounts for many of the induction cases when the spin canonical ring is saturated in degree 1, as defined in Definition ~\ref{defn:sat}.
+We complement Lemma ~\ref{lem:sat-1} with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated in degree two or three.
 
@@
 \label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, \halfcan_X)$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
-Suppose $g > 0,$ and, if $g = 1$ then $\deg 3\halfcan' \geq 2$ (note that this implies $\sat(Eff(L'))\le 2$).
-Let $R_{L'} = k[x_2, x_3
+Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ \todo{The notation i was using for these throughout the paper was $\halfcan$ and $\halfcan'$ without the $\sx$ subscripts.
+We should make one of them consistent with the other.} be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
+Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, $\sat(Eff(L'))\le 2$.
+\todo{Why is it automatic that the saturation is 2?
+Maybe you can explain this in the proof in a sentence.}
+Furthermore, let $R_{L'} = k[x_2, x_3
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch).
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$). \todo{Ask David, is it useful to include this parenthetical?}
+Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch \todo{Probably include this in a remark below the proof}).
 Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
 \begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
+	\ord_{x_2}(f) < \ord_{x_2}(h) \implies f \prec h.
 \end{align*}
@@
 		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order with $x_2, \ldots, x_m$ preceding $y_3, y_4$.  Then
+		order with $y_3, y_4$ preceeding $x_2, \ldots, x_m$. Then,
 		\begin{align*}
@@
 \begin{proof}
-The assumptions on $g$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g - 1$ and $\deg 4L > 2g - 1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+First, we shall show the assumptions on $g$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g - 1$ \todo{If $g = 2$ then we in fact have $\deg 3L = 3g-3 = 2g - 1.$ Is this a big problem?
+It's almost base point free, except if the point you take out yields the canonical divisor, after removing it.} and $\deg 4L > 2g - 1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
 If $g = 1$, we assume $\deg 3L \geq 2 > 2g - 1$, so we also have $\deg 4L \geq 2 > 2g - 1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch.
-\todo{Understand why/whether we need to cite Lemma 5.4.7.}
+
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a). \todo{Ask David, Understand why/whether we need to cite Lemma 5.4.7.}
 
 A quick computation checks that
-the following is a $k$ basis for $R$ over $R'$:
+the following set $S$ is a $k$ basis for $R$ over $R'$:
 
@@
 \end{align*}
-a similar (but much easier) computation to that of lemma $\ref{lem:sat-1}$ determines that $S$, $T$, and $\prec$ meet the conditions of Lemma \ref{lem:relations_from_generators_induction}, whose result then immediately implies part (b).
+a similar (but much easier) computation to that of lemma $\ref{lem:sat-1}$ determines that $S$, $T$, and $\prec,$ using the ordering defined in (b), meet the conditions of 
+Lemma \ref{lem:relations_from_generators_induction}. 
+Hence, by Lemma \ref{lem:relations_from_generators_induction}, part (b) holds.
 
@@
 \label{lem:sat-3}
-\todo{Make explicit assumptions on genus.}
 Suppose $L'$ is a log half-canonical divisor of $\sx'$ with coarse
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
-{\halfcan'} = k[x_3, x_4 , x_5, \ldots, x_m]/I'$; since we are in genus 0, we can choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i$. Let $L = L' + \frac
+{\halfcan'} \cong k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
 {1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
@@
 		y_4 \prec y_5$
-		and equip the ring $k[y_3, y_4, y_5, x]$ with the block order so that $x_3, \ldots, x_m$ precede $y_3, y_4, y_5$.  Then,
-		\begin{align*}
-			\initial_\prec(I) &= \initial_\prec(I) k[x, y_3, y_4, y_5] \\
+		and equip the ring $k[y_3, y_4, y_5, x_3, \ldots, x_m]$ with the block order so that $y_3, y_4, y_5$ dominate $x_3, \ldots, x_m$ \todo{Aaron: I used the word dominate, is this ok?}.  Then,
+		\begin{align*}
+			\initial_\prec(I) &= \initial_\prec(I) k[y_3, y_4, y_5, x_3, \ldots, x_m] \\
 			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
@@
 \begin{proof}
-Since we are in genus 0, general
+Since $X$ has genus 0, general
 elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P^{\halfcan'}(y_i) =
@@
 \[
-	T = \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\}+ \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
+	T = \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\} \cup \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
 \]
-we can argue similarly to Lemma $\ref{lem:sat-1}$ that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, immediately implying part (b) of this proof.
+we can argue similarly to Lemma $\ref{lem:sat-1}$ that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, concluding part (b).
 
@@
 
-One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only these three cases (Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}) are needed for the remainder of this paper.
-Instead we turn now to inductive methods to incrementally increase the $e_i$s.
-Combined with the adding points lemmas, these will provide all the necessary inductive tools for the remainder of the paper.
+One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only the cases of Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} are needed for the remainder of this paper.
+We next turn to an inductive method to increment the $e_i$'s.
 
@@
 
-It only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
+By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
 Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$

### 2015-06-30 stacky_write_up/spin_cring.tex
edited part a of monster lemma

@@
 \[
-	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor
+	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor.
 \]
@@
 \noindent
-so in $H^0 (X, \lfloor d\halfcan \rfloor)$ we can find elements with pole
-order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
+So, \todo{Aaron: Presumably this is Riemann Roch, but you should explain why, as I don't see it immediately.} there exist rational sections $t_i$ of $\sco(\lfloor d\halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
+for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
 \beta} \rfloor \}$. We will the use positive best lower approximations to
@@
 be the positive best lower approximations of $\frac{
-\alpha}{\beta}$. Note that a set of $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{\halfcan})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
-d_i \frac{\alpha}{\beta} \rfloor$ (viewed as sections of $\so_{L'}$) are linearly independent over $(R_{\halfcan'})_d$, and thus by a dimension count form a $k$-basis for
+\alpha}{\beta}$.
+Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
+Hence, by a dimension count, these sections form a $k$-basis for
 $(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.
@@
 Choose a positive best lower approximation $\frac{c_i}{d_i}$.
-Let $z_1, \ldots, z_r \in R_\halfcan$ with $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
-Then for each $z_j$,
+Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
+Then for each $j$, \todo{Aaron: I don't see why either of the next 2 claims hold, but maybe I'm being silly.}
 \[
@@
 \[
-	-\ord^{\halfcan'}_P(\prod_{j=1}^n z_j) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
+	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
 \]
@@
 Choose some $y_i \in(R_{
-\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
-
-Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} < \frac{\alpha}{
-\beta}$ is not a best lower approximation.  Choose a
-best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
+\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
+Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
+\todo{This sentence on genericness seems like it does not belong in the proof.}
+
+Choose $c,d\in \mathbb{N}$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
+\beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
+best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.
+This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so \todo{Why does the next equation follow from this inequality?}\todo{Aaron: Is it true that $c_1 \leq \cdots \leq c_n$?
+I think it is true and that it is implicitly being used here and later.
+Perhaps this needs to be said, or perhaps it doesn't, I'm not sure.}
 %  The argument goes $c_i d \ge c d_i$
@@
 \begin{equation}\label{eqn:c-from-lower-terms}
-	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
+	c_i +\left\lfloor (d-d_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
 \end{equation}
 
-Using this fact, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
+Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
 \[
@@
 \]
-and for each $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i$ (note that this always exists since $1=c_1\le i$), define
+and for each $i \in \mathbb{N}$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
 \[
@@
 Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$.
+\todo{Perhaps it's worth reminding the reader here that $y_i$ are as in the statement of (a) and have order $-c_i$.}
 Then define 
@@
 
-Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor$, so by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).
+Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
+\todo{Maybe we should make reference these generating the desired lattice, as described in Evan's paper?
+I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
 

### 2015-06-30 stacky_write_up/spin_cring.tex
edits finished for monster theorem

@@
 	\item[(2)] there does not exist $(b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1},$ \\
-	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$
+	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$.
 \end{enumerate}
@@
 \[
-	T = (\bigcup_{i=1}^{n-1} U_i) \cup V.
+	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
 \]
@@
 We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.
-We have already shown $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving us condition \ref{lem:relations_from_generators_induction}(1).
-Our choice of order for monomials in $k[y_1, \ldots, y_n]$ and block order for those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$ giving us condition \ref{lem:relations_from_generators_induction}(2).
-
-Now, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
-Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j\not |f$ so $x_i\not|f$.
+In part (a), we have shown $S$ \todo{What is $S$.
+I presume it is the complement, but can you spell it out?} forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ implying condition (1) of Lemma ~\ref{lem:relations_from_generators_induction} holds.
+Our choice of order for monomials in $k[y_1, \ldots, y_n]$ and block order for those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, implying that condition (2) of Lemma \ref{lem:relations_from_generators_induction} holds.
+
+It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}.
+To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
+Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$.
+Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.
 Therefore, $f\in k[u, y_1, \ldots, y_n]$.
-We note that $S$ generates $y_j (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
+We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
 That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \[
-	k[u, x_1, \ldots, x_m] \cup V \cup \{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]. 
+	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
 \]
-\todo{is $\{y_1, \ldots, y_n\} k[u, y_1, \ldots, y_n]$ appropriate notation to mean all possible products between some $y_j\in \{y_1, \ldots, y_n\}$ and some element in $k[u, y_1, \ldots, y_n]$?}
-Thus, we see that if $f\in k[u, y_1, \ldots, y_n]$, then $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{Z}_{\ge 0}$, and $a_j\in \mathbb{Z}_{\ge 0}$ for all $j$ with $a_l> 0$.
+Thus, we see that if $f\in k[u, y_1, \ldots, y_n]$, then $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{Z}_{\ge 0}$, so that $a_l > 0$ and $a_j\in \mathbb{Z}_{\ge 0}$ for $1 \leq j \leq l$.
 For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.
-If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...}, and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
-We see that this latter case when $y_if\not\in S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_h$.
-Thus, since $S$ generates $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\begin{align*}
-				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \langle \bigcup_{i=1}^{n-1} U_i \rangle \\
+\todo{Is there a reason why you don't just take the product up to $n$ and let $l$ be the highest number so that $a_l \neq 0$?
+This seems simpler to me}
+If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...
+Aaron: Indeed, why not just omit the subscript?},
+and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
+We see that this latter case when $y_i f \notin S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_h$.
+\todo{Aaron: Why to we see this?
+Presumably this is using conditions 1,2,3 but it would be helpful for you to spell out which.
+Also, what are the latter and former cases?
+I don't see the casework anywhere}
+Thus, since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+\begin{align*}
+				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
 	\subseteq \; 	& S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
 \end{align*}
-This gives us condition \ref{lem:relations_from_generators_induction}(3).
-Thus, the conditions of Lemma \ref{lem:relations_from_generators_induction} are met, and by applying its conclusion we prove (b) of this lemma.
+This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
+Lemma ~\ref{lem:relations_from_generators_induction} are met.
+Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).
 \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.

### 2015-06-30 stacky_write_up/spin_cring.tex
Wierd former commit: changes before editing 3.1 seemed to delete some of robin and my changes; I added them back.

@@
 If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve?
-shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if
-$$\di \sx = \di X \oplus \left(\bigoplus_{i
-= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
-As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points.
-A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
+shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if
+\[
+\di \sx = \di X \oplus \left(\bigoplus_{i
+= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
+\]
+\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?}
+As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points.
+\todo{I don't know if this is a good statement to make.
+We aren't really viewing $\sx$ as a scheme.
+Rather we're are determining information about its canonical rings through knowledge of scheme data.}  A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
 The central object of study in this paper is the {\bf log spin
@@
 In particular, we would like to bound the degrees in which the
-graded ring and its relations are generated. The work by O'Dorney
+graded ring and its relations are generated.  O'Dorney
 shows that the canonical ring of any $\BQ$-divisor $D =
 \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of
-$\BP_k^1$ with $\# \Supp(D) \leq 2$ is generated in degrees up
+$\BP_k^1$ is generated in degrees up
 to $e := \max(\beta_1, \beta_2)$ with relations generated in
-degrees up to $2e$ \cite[Section 4]{dorney:canonical}. Furthermore,
-O'Dorney gives a larger bound when the support of $D$ is allowed to
-have arbitrarily many points in terms of least-common-multiples.
+degrees up to $2e$ \cite[Theorem 6]{dorney:canonical}. Furthermore,
+O'Dorney gives a larger bound in terms of least common multiples of the denominators when the support of $D$ is allowed to
+have arbitrarily many points.
 Voight and Zureick-Brown also bounded the generator and relation
@@
 
+First, we give a definition of the graded degree of a monomial
+in a graded polynomial ring.
+
  \begin{defn}
-We equip the polynomial ring $k[x_1, \ldots, x_n]$ with the
-(weighted graded) reverse lexicographic order \textbf{grevlex}
-$\prec$: if 
+\label{defn:monomial-degree}
+Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
+ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
+k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
+we define
 \[
-	x^{\vec{m}} = \prod_{d,i} x_{d,i}^{m_{d,i}}
+	\deg \alpha := \sum_{i = 1}^{n} d f_i
 \]
-
-\noindent
-and $x^{\vec{n}}$ are monomials in $k[x]_{\vec{a}}$, then $x^{\vec{m
-}} \succ x^{\vec{n}}$ if and only if either
+\end{defn}
+
+Now define the (graded) lexicographic order \textbf{grlex}
+$\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
+x_{d_n, n}]$ to be the monomial ordering such that:
+
+\begin{defn}
+\label{defn:grlex}
+If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
 \begin{equation}
-\vec{a}\cdot\vec{m} = \sum_{d,i} dm_{d,i}  > \vec{a} \cdot \vec{n}
+\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
 \end{equation}
-or
-\begin{equation} \label{eqn:grevlexdef}
-\text{$\vec{a}\cdot\vec{m} = \vec{a} \cdot \vec{n}$ and the last (right-most) nonzero entry in $\vec{m}-\vec{n}$ is negative.}
+or $\alpha$ is larger using the lexicographical ordering event of equal
+degrees:
+
+\begin{equation}
+\label{eqn:grlex-tie}
+	\deg \alpha = \deg \beta \text{ and }
+	\alpha \succ_{\text{lex}} \beta
 \end{equation}
-It is important to note that in \eqref{eqn:grevlexdef}, the ordering of the variables matters: it corresponds to a choice of writing the exponents of a monomial as a vector.
-A common choice for us will be
-\begin{equation} \label{eqn:xdOrder}
- x_{1,1}^{m_{1,1}} \cdots x_{D,a_D}^{m_{D,a_D}} \leftrightarrow (m_{D,1},\dots,m_{D,a_D},\ldots,m_{1,1},\dots,m_{1,a_1}) 
+\end{defn}
+
+We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
+-with the (weighted graded) reverse lexicographic order
+-\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
+-
+-\begin{defn}
+-\label{defn:grevlex}
+-If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+-monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+-\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
+-
+-\begin{equation}
+-	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
+-\end{equation}
+-or $\alpha$ has a smaller right-most entry in the event of equal
+-degrees:
+-
+-\begin{equation}
+-\label{eqn:grevlex-tie}
+-	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
+-the	largest } i \text{ such that } f_i \neq f_i'
+-\end{equation}
+-\end{defn}
+
+We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
+with the (weighted graded) reverse lexicographic order
+\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
+
+\begin{defn}
+\label{defn:grevlex}
+If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
+
+\begin{equation}
+	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
 \end{equation}
-in which case we have $x_{2,1} \succ x_{1,2}^2$
-and $x_{5,1} \succ x_{1,6}^2 x_{3,2}$, etc.
-We indicate this ordering in the presentation of the ring, e.g.~for the above we would write
-\[ k[x]_{\vec{a}}= k[x_{1,1},\dots,x_{1,a_1},\dots,x_{D,1},\dots,x_{D,a_D}]. \]
-In this way, our relations write generators in larger degree in terms of those in smaller degree (``later generators in terms of earlier generators''), which gives the most natural-looking canonical rings to our eyes.
+or $\alpha$ has a smaller right-most entry in the event of equal
+degrees:
+
+\begin{equation}
+\label{eqn:grevlex-tie}
+	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
+the	largest } i \text{ such that } f_i \neq f_i'
+\end{equation}
 \end{defn}
 
+\begin{rem}
+Note that the ordering of the variables matters in both
+Equation ~\ref{eqn:grlex-tie} and Equation ~\ref{eqn:grevlex-tie}.
+\end{rem}
+
+Our inductive arguments in Section ~\ref{sec:induction} will
+usually have an inclusion $R \supset R'$ of log spin canonical
+rings such that $R'$ is generated by elements $x_{d_i, i}$ and $R$
+is generated over $R'$ by elements $y_j$. In these cases, it is
+natural to consider term orders which treat these sets of variables
+separately. We now present the \textbf{block term order} introduced
+by Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
+
+\begin{defn}
+\label{defn:block-order}
+Let $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and $k[y_{c_1, 1}, \ldots,
+y_{c_m, m}]$ be weighted polynomial rings with existing term
+orders $\prec_x$ and $\prec_y$, respectively. Let $\alpha :=
+\prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ $\prod_{j = 1}^{m} y_{c_j, j}
+^{h_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}
+\prod_{j = 1}^{m} y_{c_j, j}^{h_i'}$ be monomials in $k[x_{d_1, 1},
+\ldots, x_{d_n, n}] \otimes$ $k[y_{d_1', 1}, \ldots, y_{d_m', m}]$.
+Let $\alpha_x := \prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ be the
+part of $\alpha$ in $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and
+likewise with $\alpha_y$, $\beta_x$, and $\beta_y$.
+
+In the \textbf{(graded) block} (or \textbf{elimination}) term
+ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
+\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
+  \begin{enumerate}
+  \item[(i)] $\deg \alpha  > \deg \beta$ or
+  \item[(ii)] $\deg \alpha = \deg \beta$ and 
+    \begin{enumerate}
+    \item $\alpha_y \succ_y \beta_y$ or
+    \item $\alpha_y =  \beta_y$ and $\alpha_x \succ_x \beta_x$
+    \end{enumerate}
+  \end{enumerate}
+\end{defn}
+
+\todo{write below part}
 For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.
@@
 A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that
-\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]
++\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]
 
@@
 Hence, by a dimension count, these sections form a $k$-basis for
-$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.
+$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}
 
@@
 Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
-Then for each $j$, \todo{Aaron: I don't see why either of the next 2 claims hold, but maybe I'm being silly.}
+Observe that $\frac{c_i}{d_i}$ is a best lower approximation for $\frac{\alpha}{\beta}$ and $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
+Hence, for each $j$,
 \[
@@
 \]
-
-\noindent
-so
+so the mediant inequality tells us
+\[
+	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{d_i}.
+\]
+Multiplying through by $d_i$ gives
 \[
@@
 	S = \cup_{i=1}^{\infty} S_i.  
-\]
+\]\todo{make equation and reference}
 Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.
@@
 \todo{Maybe we should make reference these generating the desired lattice, as described in Evan's paper?
-I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
+I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a) \todo{why follows from 3.1}.
 
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
+curves, with the same course space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
 \{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
 
-$$\chi_J(i) = \begin{cases}
+\[
+\chi_J(i) = \begin{cases}
 	1, &\text{ if }i \in J\\
 	0, &\text{ otherwise. } 
-\end{cases}$$
+\end{cases}
+\]
 
 Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
-to be {\bf admissible} if the $R'$ admits a presentation
+to be {\bf admissible} if $R'$ admits a presentation
 \begin{align*}
@@
 \label{rem:three-cases}
-For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
+For our inductive arguments in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
 stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
 curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
-\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
+\delta)$, and our base cases include signatures $\sigma$ characterized by one of the following: cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
 \begin{enumerate}
@@
 Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L,d}$ be the $d$th graded piece of $I_L$ and define
-$$J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.$$
+Let $I_{L, d}$ be the $d$th graded piece of $I_L$ and define
+\[
+	J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.
+\]
 \end{defn}

### 2015-06-30 stacky_write_up/spin_cring.tex
maketitle change
fixed slight errors in peter adding back my ssec

@@
 
-\maketitle
-
 \begin{abstract}
@@
 \end{abstract}
+
+\maketitle
 
@@
 \succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
+
 \begin{equation}
@@
 \end{defn}
-
-We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
--with the (weighted graded) reverse lexicographic order
--\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
--
--\begin{defn}
--\label{defn:grevlex}
--If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
--^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
--monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
--\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
--
--\begin{equation}
--	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
--\end{equation}
--or $\alpha$ has a smaller right-most entry in the event of equal
--degrees:
--
--\begin{equation}
--\label{eqn:grevlex-tie}
--	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
--the	largest } i \text{ such that } f_i \neq f_i'
--\end{equation}
--\end{defn}
 
@@
 so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i,j} \in H^0(\sx', i K_{\sx'})$.
+x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
beamer skeleton, correct kodaira-spencer bib entry

@@
 
-\todo{Peter: I think we need something about odd weight modular forms before going right into stacks.}  
-Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many \todo{Peter: not clear to me that ``many'' is a good word to use here.
-We mostly generalize in one direction}
+\todo{Peter: I think we need something about odd weight modular 
+forms before going right into stacks.}
+Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
+Petri's theorem in many \todo{Peter: not clear to me that ``many'' 
+is a good word to use here.  We mostly generalize in one direction}
 directions.
-If $X$ is a curve, \todo{why do you start with a curve and then move to a stacky curve?
-shouldn't it be the opposite order?} then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if
+
+If $X$ is a curve, \todo{why do you start with a curve and then
+move to a stacky curve? shouldn't it be the opposite order?} then
+we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
+and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
+\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
+\geq 2}$ if 
 \[
-\di \sx = \di X \oplus \left(\bigoplus_{i
-= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
+	\di \sx = \di X \oplus \left(\bigoplus_{i = 1}^r \left\langle 
+	\frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
 \]
@@
 \todo{do this part}
-Part on Kodaira--Spencer \cite{kodaira:complex-manifolds}.
+Part on Kodaira--Spencer \cite{kodaira-spencer:deformations}.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
responded to peters section 3 comments

@@
 %in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
-we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $H^0(X, L_X)$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to the divisor we are inducting from, rather than relative to the structure sheaf.\todo{Peter: This last sentence is kind of awkward.
+	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections.
+We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.\todo{Peter: This last sentence is kind of awkward.
 I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner...
-I hope...}
+I hope...
+Aaron: I changed it.
+Is it better now?}
 
@@
 
+\iffalse
 \begin{rem}
@@
 The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
+\fi
 
@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}.
-\todo{Peter: In general, I'm not sure how important it is for us to draw all the analogs between your definition and proofs and those of VZB.
-As long as we make not in the section's introduction that they are similar, we might leave it out of the remaining transitions and remarks.}
 
@@
 \label{lem:admissible_inequality}
-Condition (Ad-ii) of Definition ~\ref{defn:admissible} implies the
-stronger condition \todo{Peter: How is it a stronger condition if it implied by that of (Ad-ii).
-If $a\implies b$ then $b$ is by definition a weaker condition right?
-I agree that the latter condition is somehow better, but it seems inaccurate to call it stronger.
-I may be being over picky here...} that
+The inequality (Ad-ii) of Definition ~\ref{defn:admissible} implies the
+tighter inequality that
 
@@
 \end{rem}
-
-We next come to Lemma ~\ref{lem:raise-stacky-order}, which is an
-analog of ~\cite[Theorem 8.5.7]{vzb:stacky}.
 
@@
 
-\todo{Add conclusion to section}
+\todo{Add conclusion to section. Aaron: Should we have conclusions?}
 

### 2015-06-30 stacky_write_up/spin_cring.tex
minor edits to section 3.2 todos, and others

@@
 \]
-\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?}
+\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?
+Aaron: I agree what is written isn't actually correct, maybe we should say the free direct sum over points not in the $P_i$, together with the fractional points.
+It's not a localization because we don't want to invert $P_i$.}
 As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points.
@@
 \label{defn:block-order}
+\todo{Aaron: Doesn't \cite{vzb:stacky} put the $y_i$ before the $x_i$? Shouldn't we match this convention (here and anywhere we use this in the paper later?}
 Let $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and $k[y_{c_1, 1}, \ldots,
@@
 		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order with $y_3, y_4$ preceeding $x_2, \ldots, x_m$. Then,
+		order with $y_3, y_4$ preceeding $x_2, \ldots, x_m$.
+\todo{In here and throughout the section, we should just enforce the convention that the $y_i$ come before the $x_j$, and then we won't have to say which preceed which.} Then,
 		\begin{align*}
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y] := k[y_{i, e_i}]_{i \in J}$ and $k[x]:=k[x_1,\ldots, x_m]$ with graded monomial orders and give $k[y, x] = k[y] \otimes k[x]$ block order, as defined in \cite[Definition 8.1.1]{vzb:stacky}.
-\todo{Possibly reference definition in this paper instead.} Let $R = k[y, x]/I.$ Then,
+	\item[(c)] Endow $k[y] := k[y_{i, e_i}]_{i \in J}$ and $k[x]:=k[x_1,\ldots, x_m]$ with graded monomial orders and give $k[y, x] = k[y] \otimes k[x]$ block order. Let $R = k[y, x]/I.$ Then,
 		\begin{align*}

### 2015-06-30 stacky_write_up/spin_cring.tex
add some todos,slight shifting, g0 index fix

@@
 
+\todo{combine below two paragraphs with the corresponding
+near-duplicate part from the background}
 If $X$ is a curve, \todo{why do you start with a curve and then
@@
 degrees up to $2e$ \cite[Theorem 6]{dorney:canonical}. Furthermore,
-O'Dorney gives a larger bound in terms of least common multiples of the denominators when the support of $D$ is allowed to
+O'Dorney gives a larger bound in terms of least common multiples of
+the denominators when the support of $D$ is allowed to
 have arbitrarily many points.
@@
 for all genera. Note that O'Dorney's bounds are asymptotically
-strict for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
+tight for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
 to the log spin curve case allows for lower bounds.
@@
 \label{ssec:stacky-background}
+\todo{combine the below chunk with the near-duplicate section
+in the introduction}
 A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
@@
 Zureick-Brown for more thorough treatment of these definitions
-\cite[Chapter 5]{vzb:stacky}.
+\cite[Chapter 5]{vzb:stacky}. \todo{again, not quite viewing as a scheme}
 
@@
 := H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
+If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^{th}$
+degree component of $R$.
 
@@
 \todo{Note that this result is independence of base field}
-
-If $R$ is a graded ring, then $(R)_d$ refers to the $d^{th}$ degree
-component of $R$.
 
@@
 
-\iffalse
-\begin{rem}
-Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
-\end{rem}
-\todo{Peter: I'm not sure how useful this remark is.
+%\begin{rem}
+%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+%\end{rem}
+%\todo{Peter: I'm not sure how useful this remark is.
 After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.
 The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
-\fi
 
@@
 	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,
-	x_{7, 1}^2 \rangle
+	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle
+	x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
 \end{align*}

### 2015-06-30 stacky_write_up/spin_cring.tex
add main thm to beamer, add kodaira-spencer

@@
 that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
-canonical ring
+log spin canonical ring
 
@@
 to modular forms when combined with a result from Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}.
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} which itself
+follows from the classical work of Kodaira--Spencer
+\cite{kodaira-spencer:deformations}.
 
@@
 degree component of $R$.
-
-\todo{do this part}
-Part on Kodaira--Spencer \cite{kodaira-spencer:deformations}.
 
@@
 \end{lem}
+
 \begin{proof}

### 2015-06-30 stacky_write_up/spin_cring.tex
Theorem 3.5 edits

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \DeclareMathOperator{\Supp}{Supp}
-\DeclareMathOperator{\initial}{in}
+\DeclareMathOperator{\initial}{in_\prec}
 \DeclareMathOperator{\gin}{gin}
@@
 \todo{write below part}
-For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial_{\prec}(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial_{\prec}(0)=0$.
+For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial(0)=0$.
 Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.
-We define the \textbf{initial ideal} $\initial_{\prec}(I)$ to be the ideal generated by $\{\initial_{\prec}(f) : f \in I\}$.
+We define the \textbf{initial ideal} $\initial(I)$ to be the ideal generated by $\{\initial(f) : f \in I\}$.
 A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that
-+\[ \langle \initial_{\prec}(f_1),\dots,\initial_{\prec}(f_n) \rangle = \initial_{\prec}(I). \]
++\[ \langle \initial(f_1),\dots,\initial(f_n) \rangle = \initial(I). \]
 
@@
 %rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
-%\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
+%\ldots, f_j$, where $\initial(f_i) = x_i x_j,$ and no term of $f_i$
 %is of the form $x_k$. Then, the elements $f_i$ determine minimal
@@
 %Further suppose that $I'$ is generated over $I$ by elements $f_1,
-%\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
+%\ldots, f_j$ as a $k$-vector space, where $\initial(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
 %is of the form $y_i$. Then, the elements $f_i$ determine minimal
@@
 Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial_\succ(I)$. We can even build this in to the macro possibly? }
+\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
 Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
@@
 \begin{align*}
-	S \; \cup\; \langle T\rangle \; \cup \; \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
+	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
 \end{align*}
@@
 
-By (3), every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
+By (3), every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
 \begin{align*}
@@
 To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.
-\todo{Reference the lemma, instead of using previous, since things might get moved around.
-Aaron: Great, thanks!}
 The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
@@
 
-\todo{Perhaps note that this ordering is independent of whether we take the order relative to a line bundle}
+\begin{rem}\label{rem:graded-P-lex-independent-of-line-bundle}
+Observe that Definition \ref{defn:graded-p-lex} remains the same if we replace $-\ord_P$ with $-\ord_P^{L'}$ for any divisor $L'$ of $X$.
+\end{rem}
+
 \noindent One can easily verify graded $P$-lex is a monomial ordering in the sense defined in Cox--Little--Shea \cite[Chapter 2, $\mathsection$ 2, Definition 1]{cls:ideals-varieties-algorithms}.
 
-We area almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective divisor.
-While in O'Dorney \cite[Theorem 8]{dorney:canonical} gives a bound for the degree of generation of arbitrary $D \in \di \BP^1$, we obtain a much tighter bound in the case $D$ is effective.
-Furthermore, Lemma ~\ref{lem:sat-1} also applies to curves of genus $g > 0$.
+We area almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
+\mathbb{Q}$-divisor.
+Whereas O'Dorney considers arbitrary $\mathbb{Q}$ divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
+Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$.
 Before stating Lemma ~\ref{lem:sat-1}, we recall some notation from O'Dorney \cite{dorney:canonical}.
-
-\todo{Peter: This sentence is very ugly.
-On the other hand, I feel we need to say something about O'Dorney before the following definition, or else it is completely unmotivated.
-How should we state it better?
-Also note that in its current form this sentence neglects that we also extend the result to higher genus; it was too difficult to have this in though.
-Aaron: Do you like it any better now?}
 
@@
 Aaron: I'm fine with not making it an [H]}
-\begin{figure}[H]\label{fig:s14/5-lattice}
+\begin{figure}\label{fig:s14/5-lattice}
 \includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
@@
 	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
-	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
+	N}.
 \end{align}
@@
 \begin{align*}
-	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
+	\initial(I) &= \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
 										 + \langle U_i: 1 \le i \le n-1 \rangle
@@
 \begin{enumerate}
-	\item[(1)] $\sum_{j=1}^i a_j c_j \ge c_{i+1},$\\
-	\item[(2)] there does not exist $(b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1},$ \\
-	\item[(3)] there does not exist $h<i$ such that $\sum_{j=1}^h y_j^{a_j}\ge c_{h+1}$.
+	\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1},$\\
+	\item[(**)] there does not exist $(b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1},$ \\
+	\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r+1}$.
 \end{enumerate}
@@
 \item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$).
-\todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.
-On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.
-Maybe in a remark after the lemma?
-Aaron: I like including it in the lemma.
-I think it's really the most important point of this, so it's fine to include it here.
-It's also ok to just include this as a statement after parts a and b, if we don't particularly care about referencing part c.}
-%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
-%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
-%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
-%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
-%generates $I'$.
 \end{enumerate}
@@
 \alpha}{\beta}$. 
-Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
+%Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
 Hence, by a dimension count, these sections form a $k$-basis for
-$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}
-
+%$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}
 %For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
@@
 Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
-Observe that $\frac{c_i}{d_i}$ is a best lower approximation for $\frac{\alpha}{\beta}$ and $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
+Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
 Hence, for each $j$,
@@
 \halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-Note that this choice is generic if $d_i>1$ or $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.
-\todo{This sentence on genericness seems like it does not belong in the proof.}
-
-Choose $c,d\in \mathbb{N}$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
+
+Suppose $c,d\in \mathbb{N}$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
 \beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.
-This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so \todo{Why does the next equation follow from this inequality?}\todo{Aaron: Is it true that $c_1 \leq \cdots \leq c_n$?
-I think it is true and that it is implicitly being used here and later.
-Perhaps this needs to be said, or perhaps it doesn't, I'm not sure.}
+best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so 
 %  The argument goes $c_i d \ge c d_i$
@@
 % \implies the equation below:
+\[
+	\frac{c-c_i}{d-d_i}\le \frac{\alpha}{\beta}
+\]
+which implies
 \begin{equation}\label{eqn:c-from-lower-terms}
@@
 \]
-Observe that this recursive definition ensures that $S_i$ contains only elements $z\in R_\halfcan$ satisfying $-\ord^{\halfcan'}_P(z)=i$.
-\todo{Perhaps it's worth reminding the reader here that $y_i$ are as in the statement of (a) and have order $-c_i$.}
+Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
+\[
+	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
+\]
 Then define 
-\[
+\begin{equation}\label{eqn:sat-1-defining-S}
 	S = \cup_{i=1}^{\infty} S_i.  
-\]\todo{make equation and reference}
+\end{equation}
 Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.
 
-Applying Equation \ref{eqn:c-from-lower-terms}, we see that $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
-\todo{Maybe we should make reference these generating the desired lattice, as described in Evan's paper?
-I think this is basically a rehashing of Evan's 1-point case?} Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a) \todo{why follows from 3.1}.
+By equation \label{eqn:deg1-sat-ind} for $d\in \mathbb{N}$,
+\[
+	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
+		\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor,
+\] 
+so $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
+Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
 
 {\bf Part (b):}
-Define $U_i$ and $V$ as in the lemma's statement and define
+Let $S$ be as above in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
 \[
@@
 We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.
-In part (a), we have shown $S$ \todo{What is $S$.
-I presume it is the complement, but can you spell it out?} forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ implying condition (1) of Lemma ~\ref{lem:relations_from_generators_induction} holds.
-Our choice of order for monomials in $k[y_1, \ldots, y_n]$ and block order for those in $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, implying that condition (2) of Lemma \ref{lem:relations_from_generators_induction} holds.
+In part (a), we showed that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving condition (1) of Lemma ~\ref{lem:relations_from_generators_induction}.
+Our choice of monomial order in $k[y_1, \ldots, y_n]$ and block order for $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
 
@@
 \]
-Thus, we see that if $f\in k[u, y_1, \ldots, y_n]$, then $f=u^b \prod_{j=1}^l {y_j}^{a_j}\in S$ for some $1\le l\le n$, $b\in \mathbb{Z}_{\ge 0}$, so that $a_l > 0$ and $a_j\in \mathbb{Z}_{\ge 0}$ for $1 \leq j \leq l$.
-For $j\in \mathbb{N}$ with $l < j\le n$, assign $a_j=0$.
-\todo{Is there a reason why you don't just take the product up to $n$ and let $l$ be the highest number so that $a_l \neq 0$?
-This seems simpler to me}
-If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{a_j}\not\in S_{\sum_{j=1}^h c_j a_j}$ \todo{Peter: terrible subscripts...
-Aaron: Indeed, why not just omit the subscript?},
-and for all $r<h$, we have $\prod_{j=1}^r {y_j}^{a_j}\in S_{\sum_{j=1}^r c_ja_j}$.
-We see that this latter case when $y_i f \notin S$ is equivalent to $\prod_{j=1}^h {y_j}^{a_j}\in U_h$.
-\todo{Aaron: Why to we see this?
-Presumably this is using conditions 1,2,3 but it would be helpful for you to spell out which.
-Also, what are the latter and former cases?
-I don't see the casework anywhere}
+Notice that $S$ generates the ideal $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$; let $l$ be maximal such that $a_l\ne 0$.
+If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
+and for all $r<h$ $\prod_{j=1}^r {y_j}^{b_j}\in S$, where $b_j=a_j$ when $j\ne i$ and $b_i=a_i+1$.
+Choose $(\gamma_1, \ldots, \gamma_n)$ minimal (that is, so that we cannot decrease any $\gamma_j$ and have the following still satisfied) such that each $\gamma_j\le b_j$ and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$; our recursive definition of $S$ implies that for each $1\le r< h$, we still have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
+
+We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
+Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above immediately gives (**).
+Since for each $r<h$, $\prod_{j=1}^r y_{j}^{a_j}\in S$, we get condition (***).
+Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
+
 Thus, since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
@@
 				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
-	\subseteq \; 	& S \cup \langle T\rangle \cup \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
+	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
 \end{align*}
@@
 %generated by the initial terms described in the previous paragraphs
-%together with $\initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
+%together with $\initial(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
 %
@@
 		\begin{align*}
-			\initial_\prec(I) &= \initial_\prec(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
+			\initial(I) &= \initial(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
 		\end{align*}
@@
 		\begin{align*}
-			\initial_\prec(I) &= \initial_\prec(I) k[y_3, y_4, y_5, x_3, \ldots, x_m] \\
+			\initial(I) &= \initial(I) k[y_3, y_4, y_5, x_3, \ldots, x_m] \\
 			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
@@
 %~\ref{eqn:add_one_generator} are precisely a set of monomials which
-%generate $k[x, y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
-%suffices to show that all generators of $J$ lie in $in_\prec(I)$.
+%generate $k[x, y]/J$ over $k$. So, to show $J = \initial(I)$, it
+%suffices to show that all generators of $J$ lie in $\initial(I)$.
 %
@@
 %\begin{align*}
-			%in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			%\initial(I) &= \initial(I')k[x_2, \ldots, x_m, y_1, y_2] \\
 			%&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
@@
 %To show part (b), we note that the monomials in the basis above generate $k[x, y]/\initial_
-%\prec(I)$. Thus, it is sufficient to show that $J\subseteq \initial_\prec(I)$. For $j\ge 2$, we 
+%\prec(I)$. Thus, it is sufficient to show that $J\subseteq \initial(I)$. For $j\ge 2$, we 
 %can choose $w_j$ in degree $\deg(x_j) + 1$ and $A_j\in k$ such that
@@
 %\begin{align*}
-			%in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
+			%\initial(I) &= \initial(I')k[x_2, \ldots, x_m, y_1, y_2] \\
 			%&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
@@
 %\begin{align*}
-	%\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
+	%\initial(I') &= \initial(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
 										 %&+ \langle y_i x_j \rangle \\
@@
 		\begin{align*}
-			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z : z 
+			\initial(I) = \initial(I')k[x, y] + \langle y_{i, e_i}z : z 
 			\neq y_{i, e_i}, y_{i, e_i'} \rangle
@@
 %(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
-%$in_\prec(I')$ is minimally generated by products of two monomials.
+%$\initial(I')$ is minimally generated by products of two monomials.
 
@@
 \[
-	in_\prec(I) = \langle x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
+	\initial(I) = \langle x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
 \]
@@
 relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / in_\prec(I))_d$ for 
+(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \initial(I))_d$ for 
 all degrees $d \geq 0$. In particular,
@@
 	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
-	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
+	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ \initial(I))_d \\
 	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,
@@
 k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
-initial ideal $in_\prec(I)$ generated by quadratics under grlex
+initial ideal $\initial(I)$ generated by quadratics under grlex
 with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$.
@@
 We can also always find a presentation for these cases such that
-they satisfy (Ad-i) and (Ad-ii) and that $in_\prec(I')$ is
+they satisfy (Ad-i) and (Ad-ii) and that $\initial(I')$ is
 generated by products of two monomials. The procedure for

### 2015-06-30 stacky_write_up/spin_cring.tex
david's comments

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 
-\todo{combine below two paragraphs with the corresponding
-near-duplicate part from the background}
 If $X$ is a curve, \todo{why do you start with a curve and then
@@
 degrees up to $2e$ \cite[Theorem 6]{dorney:canonical}. Furthermore,
-O'Dorney gives a larger bound in terms of least common multiples of
-the denominators when the support of $D$ is allowed to
+O'Dorney gives a larger bound in terms of least common multiples of the denominators when the support of $D$ is allowed to
 have arbitrarily many points.
@@
 for all genera. Note that O'Dorney's bounds are asymptotically
-tight for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
+strict for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
 to the log spin curve case allows for lower bounds.
@@
 \label{thm:main}
-Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere?} so
+Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use seperable stacky points} so
 that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
@@
 \label{ssec:stacky-background}
-\todo{combine the below chunk with the near-duplicate section
-in the introduction}
 A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
@@
 Zureick-Brown for more thorough treatment of these definitions
-\cite[Chapter 5]{vzb:stacky}. \todo{again, not quite viewing as a scheme}
+\cite[Chapter 5]{vzb:stacky}.
 
@@
 := H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
-If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^{th}$
-degree component of $R$.
 
@@
 \todo{Note that this result is independence of base field}
+
+If $R$ is a graded ring, then $(R)_d$ refers to the $d^{th}$ degree
+component of $R$.
 
@@
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$). \todo{Ask David, is it useful to include this parenthetical?}
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$). \todo{Ask David, is it useful to include this parenthetical? yes}
 Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch \todo{Probably include this in a remark below the proof}).
@@
 
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a). \todo{Ask David, Understand why/whether we need to cite Lemma 5.4.7.}
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a).
+\todo{Ask David, Understand why/whether we need to cite Lemma 5.4.7.
+we don't just say it at the beginning}
 
@@
 
-%\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
-%\end{rem}
-%\todo{Peter: I'm not sure how useful this remark is.
+\iffalse
+\begin{rem}
+Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+\end{rem}
+\todo{Peter: I'm not sure how useful this remark is.
 After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.
 The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
+\fi
 
@@
 \todo{cite this somewhere, maybe ask david for a place to cite?
-We can cite http://www.math.harvard.edu/~ctm/home/text/class/harvard/213b/14/html/home/course/course.pdf, for example, from complex analysis course notes!}
+We can cite http://www.math.harvard.edu/~ctm/home/text/class/harvard/213b/14/html/home/course/course.pdf, for example, from complex analysis course notes!
+Don't use coarse notes}
 Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
@@
 	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle
-	x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
+	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,
+	x_{7, 1}^2 \rangle
 \end{align*}

### 2015-06-30 stacky_write_up/spin_cring.tex

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
-categories between orbifold curves and log stacky curves over $\BC$
-. Hence, for the remainder of the paper, we will work in the
-algebraic category.
+categories between orbifold curves and log stacky curves over $\BC$.
+Hence, for the remainder of the paper, we will work in the
+algebraic category. \todo{mention that we will use the language
+of Weil divisors?}
 
@@
 \label{thm:main}
-Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere?} so
+Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use seperable stacky points} so
 that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
-canonical ring
+log spin canonical ring
 
@@
 \end{thm}
+
+\begin{rem}
+In fact, the theorem only needs to assume that the stacky curve
+is separably rooted, i.e. the residue field at each stacky point
+is separable.
+\end{rem}
 
@@
 stacky curves will be assumed to be tame and $k$ will always be
-algebraically closed. The language of stacks will be omitted in
+algebraically closed. We also assume that the stacky curves are
+separably rooted, i.e. the residue field of each stacky points
+is separable. The language of stacks will be omitted in
 this paper, as it is sufficient to view stacky curves and related
@@
 Zureick-Brown for more thorough treatment of these definitions
-\cite[Chapter 5]{vzb:stacky}.
+\cite[Chapter 5]{vzb:stacky}. \todo{again, not quite viewing as a
+scheme}
 
@@
 \begin{defn}
-If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
+If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
 with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
@@
 \lfloor \alpha_i \rfloor P_i$.
+\todo{cite lemma 5.4.7 from VZB maybe?}
 
@@
 := H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
-
-\todo{do this part}
-Part on Kodaira--Spencer \cite{kodaira-spencer:deformations}.
+If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^{th}$
+degree component of $R$.
 
 \todo{Note that this result is independence of base field}
-
-If $R$ is a graded ring, then $(R)_d$ refers to the $d^{th}$ degree
-component of $R$.
 
@@
 \subsection{Junk}
+\todo{add this back into the intro}
 This is stuff that has been moved out of the introduction to possibly
@@
 Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same course space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
+curves, with the same coarse space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
 \{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
@@
 	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
-	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ \initial(I))_d \\
-	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,
-	x_{7, 1}^2 \rangle
+	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle
+	x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
 \end{align*}

### 2015-06-30 stacky_write_up/spin_cring.tex
bib fix, minor ref/label fix, Shea -> O'Shea

@@
 initial ideals, and Gr\"{o}bner bases, see Eisenbud
-\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--Shea
+\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--O'Shea
 \cite[Chapter 2]{cls:ideals-varieties-algorithms}.
@@
 
-\noindent One can easily verify graded $P$-lex is a monomial ordering in the sense defined in Cox--Little--Shea \cite[Chapter 2, $\mathsection$ 2, Definition 1]{cls:ideals-varieties-algorithms}.
+\noindent One can easily verify graded $P$-lex is a monomial ordering in the sense defined in Cox--Little--O'Shea \cite[Chapter 2, $\mathsection$ 2, Definition 1]{cls:ideals-varieties-algorithms}.
 
@@
 
-By equation \label{eqn:deg1-sat-ind} for $d\in \mathbb{N}$,
+By equation \ref{eqn:deg1-sat-ind} for $d\in \mathbb{N}$,
 \[

### 2015-06-30 stacky_write_up/spin_cring.tex
combine block ordering items, todo on saint-donat

@@
 in most cases $R(X, K_X)$ is generated in degree 1 with relations
-in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]{saint-donat:proj}). This has the
-pleasant geometric consequence that all such canonically embedded
-curves are scheme theoretically cut out by quadratic equations.
+in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]
+{saint-donat:proj}). This has the pleasant geometric consequence \todo{maybe use a different ref}
+that all such canonically embedded curves are scheme theoretically 
+cut out by quadratic equations.
 
@@
 \label{thm:main}
-Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use seperable stacky points} so
+Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use separable stacky points} so
 that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
@@
 	\item[(i)] $\deg \alpha  > \deg \beta$ or
-  \item[(ii)] $\deg \alpha = \deg \beta$ and 
-    \begin{enumerate}
-    \item $\alpha_y \succ_y \beta_y$ or
-    \item $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$
-    \end{enumerate}
+  \item[(ii)] $\deg \alpha = \deg \beta$ and $\alpha_y \succ_y \beta_y$ or
+	\item[(iii)] $\deg \alpha = \deg \beta$ and $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$
   \end{enumerate}

### 2015-06-30 stacky_write_up/spin_cring.tex
removed todos

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.\todo{Peter: This last sentence is kind of awkward.
-I changed ``instead of relative to the structure sheaf'' to ``rather than relative to the structure sheaf,'' but it can still be made to sound cleaner...
-I hope...
-Aaron: I changed it.
-Is it better now?}
+We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
 
@@
 \end{proof}
-
-\todo{Add conclusion to section. Aaron: Should we have conclusions?}
 

### 2015-06-30 stacky_write_up/spin_cring.tex
subseteq

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 	\di \sx = \di X \oplus \left(\bigoplus_{i = 1}^r \left\langle 
-	\frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.
+	\frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X.
 \]
@@
 	\di \sx = \di X \oplus \left(\bigoplus_{i
-	= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X
+	= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X
 \]
@@
 Our inductive arguments in Section ~\ref{sec:induction} will
-usually have an inclusion $R \supset R'$ of log spin canonical
+usually have an inclusion $R \supseteq R'$ of log spin canonical
 rings such that $R'$ is generated by elements $x_{d_i, i}$ and $R$
@@
 We define the \textbf{initial ideal} $\initial(I)$ to be the ideal generated by $\{\initial(f) : f \in I\}$.
-A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subset I$ such that
+A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subseteq I$ such that
 +\[ \langle \initial(f_1),\dots,\initial(f_n) \rangle = \initial(I). \]
@@
 \label{lem:admissible_subset}
-If $(\sx',\Delta,L')$ is a log spin curve, $(\sx',L', J)$ is admissible and $W \subset J$ is any subset,
+If $(\sx',\Delta,L')$ is a log spin curve, $(\sx',L', J)$ is admissible and $W \subseteq J$ is any subset,
 then $(\sx', L', W)$ is also admissible.
@@
 \begin{align*}
-	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subset 
+	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subseteq 
 H^0(\sx, e_iL).
@@
 Since $(*_0)$ holds by assumption, by induction on $i$, it suffices to show that if $(*_i)$ holds then so does $(*_{i+1}).$ 
-Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subset J_i$.
+Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subseteq J_i$.
 Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2},$ times, for the fixed set $J_{i+1},$ we see $(*_{i+1})$ holds.
@@
 Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$.
-Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subset H^0(K)$ is basepoint free.
+Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint free.
 Then, the map
@@
 is surjective.
-Indeed, since $V= ks_1 \oplus k s_2 \subset H^0(K)$ is basepoint free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
+Indeed, since $V= ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
 $$\begin{tikzcd}
@@
 Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subset H^0(X,2L)$ is basepoint free.
+Let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subseteq H^0(X,2L)$ is basepoint free.
 For any $f \in k[x_1, \ldots, x_n]$ such that
@@
 \begin{proof}
-% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subset H^0(X,2L)$.
+% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
 By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
@@
 To complete the proof, it suffices to show $f \in I_{L,d}'$.
-By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subset H^0(K)$ is basepoint free.
+By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subseteq H^0(K)$ is basepoint free.
 Consider the map

### 2015-06-30 stacky_write_up/spin_cring.tex
changed div ex notation
flip order of monomials in block order def & g0 ex

@@
 \[
-	\di \sx = \di X \oplus \left(\bigoplus_{i = 1}^r \left\langle 
+	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle P  \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left\langle 
 	\frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X.
@@
 \[
-	\di \sx = \di X \oplus \left(\bigoplus_{i
-	= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X
+	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle P  \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left\langle 
+	\frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X.
 \]
@@
 \begin{equation}
-	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
+	\deg \alpha := \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' =: \deg \beta
 \end{equation}
@@
 \label{defn:block-order}
-\todo{Aaron: Doesn't \cite{vzb:stacky} put the $y_i$ before the $x_i$? Shouldn't we match this convention (here and anywhere we use this in the paper later?}
-Let $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and $k[y_{c_1, 1}, \ldots,
-y_{c_m, m}]$ be weighted polynomial rings with existing term
-orders $\prec_x$ and $\prec_y$, respectively. Let $\alpha :=
-\prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ $\prod_{j = 1}^{m} y_{c_j, j}
-^{h_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}
-\prod_{j = 1}^{m} y_{c_j, j}^{h_i'}$ be monomials in $k[x_{d_1, 1},
-\ldots, x_{d_n, n}] \otimes$ $k[y_{d_1', 1}, \ldots, y_{d_m', m}]$.
-Let $\alpha_x := \prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ be the
-part of $\alpha$ in $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and
-likewise with $\alpha_y$, $\beta_x$, and $\beta_y$.
+Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
+x_{d_n, n}]$ be weighted polynomial rings with existing term
+orders $\prec_y$ and $\prec_x$, respectively. Let $\alpha :=
+\prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ $\prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{c_j, j}^{h_i'}
+\prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ be monomials in $k[y_{d_1', 1},
+\ldots, y_{d_m', m}] \otimes$ $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$.
+Let $\alpha_y := \prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ be the
+part of $\alpha$ in $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and
+likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
 
 In the \textbf{(graded) block} (or \textbf{elimination}) term
-ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
-\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
+ordering on $k[y_{d_1', 1}, \ldots, y_{d_m', m}] \otimes k[x_{d_1, 1},
+\ldots, x_{d_n, n}]$, we define $\alpha \succ \beta$ if
   \begin{enumerate}
@@
 \begin{align*}
-	&a_1 x_{3, 1} x_{7, 2} + a_2 x_{3, 1} x_{7, 1} + a_3 x_{5, 1}^2 = 
+	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
 	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 2}^2 + b_2 x_{7, 1} x_{7, 2} + b_3 x_{7, 1}^2
-	+ b_4 x_{3, 1}^3 x_{5, 1} = 0  &\text{ in degree $14$}
+	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
+	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
 \end{align*}
@@
 \[
-	a_2 x_{3, 1} x_{7, 1} = -a_3 x_{5, 1}^2
-\]
-
-\noindent
-However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
+	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
+\]
+
+\noindent
+However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
 $x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
@@
 Let $I$ be the ideal generated by these relations in
-$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
+$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
 $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
@@
 \[
-	\initial(I) = \langle x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
+	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
 \]
@@
 relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \initial(I))_d$ for 
+(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
 all degrees $d \geq 0$. In particular,
@@
 \begin{align*}
-	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
-	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle
-	x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
-\end{align*}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{3, 1},
-x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,	x_{7, 1}^2 \rangle$ can
-be checked by looking at the $k$-basis at each degree $d$.
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
+	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
+\end{align*}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
+x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
+\rangle$ can be checked by looking at the $k$-basis at each degree
+$d$.
 
 Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
+k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
 initial ideal $\initial(I)$ generated by quadratics under grlex
-with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$.
+with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
 %These quadratics must also determine minimal generators for $I$ by
@@
 This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$.
-In particlar, we make the following conjecture.
+In particular, we make the following conjecture.
 \begin{conjecture}

### 2015-06-30 stacky_write_up/spin_cring.tex
write defns for initial ideal, grobner basis

@@
 
-\todo{write below part}
-For a homogeneous polynomial $f \in k[x]_{\vec{a}}$, we define the \textbf{initial term} $\initial(f)$ to be the monomial in the support of $f$ that is largest with respect to $\prec$, and we define $\initial(0)=0$.
-Let $I \subseteq k[x]_{\vec{a}}$ be a homogeneous ideal.
-We define the \textbf{initial ideal} $\initial(I)$ to be the ideal generated by $\{\initial(f) : f \in I\}$.
-A \textbf{Gr\"obner basis} (also called a \textbf{standard basis}) for $I$ is a set $\{f_1,\dots,f_n\} \subseteq I$ such that
-+\[ \langle \initial(f_1),\dots,\initial(f_n) \rangle = \initial(I). \]
-
-\begin{rem}
-A Gr\"obner basis for $I$ \emph{a priori} depends on a choice of basis for the ambient graded polynomial ring.
-\end{rem}
+Now we give brief definitions of initial terms and Gr\"{o}bner
+bases. These will be used in the proofs of the inductive lemmas
+in Section ~\ref{sec:induction} and in the proof of Theorem
+~\ref{thm:main}.
+
+\begin{defn}
+\label{defn:initial-term}
+Let $f \in k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a homogeneous
+polynomial. The \textbf{initial term} $\initial(f)$ of $f$
+is the largest monomial in the support of $f$ with respect to
+the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
+\end{defn}
+
+Given a homogeneous ideal $I \subseteq k[x_{d_1, 1}$, $\ldots$,
+$x_{d_n, n}]$, we can now define the \textbf{initial ideal}
+$\initial(I)$ of $I$.
+
+\begin{defn}
+\label{defn:initial-ideal}
+Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
+$x_{d_n, n}]$. Then the initial ideal $\initial(I)$ of $I$ is
+the ideal generated by the initial terms of homogeneous polynomials
+in $I$:
+\[
+	\initial(I) := \langle \initial(f) \rangle_{f \in I}
+\]
+\end{defn}
+
+Furthermore, we will use Gr\"{o}bner bases, which are bases
+for these initial ideals and have many useful properties.
+
+\begin{defn}
+\label{defn:grobner-basis}
+Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
+$x_{d_n, n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
+\textbf{standard basis} for $I$, is a set of elements in $I$
+such that their initial terms form a basis for the initial
+ideal of $I$.
+\end{defn}
 

### 2015-06-30 stacky_write_up/spin_cring.tex
reintroduce orbifolds to intro, previous work

@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup
-of $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
+Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
+$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
 linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. In this paper, we sharply bound the degree of the generators and
-relations for $M(\Gamma)$, for general $\Gamma$ \todo{Peter: Why do you say general gamma?
-I think you should either add "general fuchsian groups gamma" or just take out that clause, since you just defined what gamma is.}  \todo{Peter: also, its not clear to me that this should be said right here.
-I think we may want to say a bit more about what's already known instead of going directly to what we have done}.
-In the special that $\Gamma$ has no odd weight modular forms, Voight and Zureick-Brown
-\cite[Chapters 7-9]{vzb:stacky} give similar bounds, and we extend their work to all Fuchsian groups $\Gamma$.
-In order to find generators and relations for $M(\Gamma)$, we translate the seemingly analytic question of understanding the ring of modular forms into the algebraic
-category, using a generalization of the GAGA principle. By
-\cite[Proposition 6.1.5]{vzb:stacky}, there is an equivalence of
-categories between orbifold curves and log stacky curves over $\BC$.
-Hence, for the remainder of the paper, we will work in the
-algebraic category. \todo{mention that we will use the language
-of Weil divisors?}
+$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. Often, it is useful to
+bound the degree of the generators and relations for $M(\Gamma)$
+for general Fuchsian groups $\Gamma$. In the special case that $\Gamma$
+has no odd weight modular forms, Voight and Zureick-Brown
+\cite[Chapters 7-9]{vzb:stacky} give nice bounds.
+This work extends their work to all Fuchsian groups $\Gamma$.
+
+We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
+For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
+\backslash \BH$ is a Riemann Surface over $\BC$. It may well be
+that $\Gamma \backslash \BH$ is not compact, but we can form a
+space $\Gamma \backslash \BH^*$ which is a compactification of
+$\Gamma \backslash \BH,$ with associated divisor of cusps $\Delta$.
+In order to find generators and relations for $M(\Gamma)$, we
+translate the seemingly analytic question of understanding the ring
+of modular forms into the algebraic category, using a
+generalization of the GAGA principle. By \cite[Proposition 6.1.5]
+{vzb:stacky}, there is an equivalence of categories between orbifold
+curves and log stacky curves over $\BC$. Hence, for the remainder
+of the paper, we will work in the algebraic category.
+\todo{mention that we will use the language of Weil divisors?}
 
@@
 \[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle P  \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left\langle 
-	\frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X.
+	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
+	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
+	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
 \]
@@
 In particular, we would like to bound the degrees in which the
-graded ring and its relations are generated.  O'Dorney
-shows that the canonical ring of any $\BQ$-divisor $D =
-\frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of
-$\BP_k^1$ is generated in degrees up
-to $e := \max(\beta_1, \beta_2)$ with relations generated in
-degrees up to $2e$ \cite[Theorem 6]{dorney:canonical}. Furthermore,
-O'Dorney gives a larger bound in terms of least common multiples of
-the denominators when the support of $D$ is allowed to
-have arbitrarily many points.
-Voight and Zureick-Brown also bounded the generator and relation
-degrees of log spin canonical rings of $(\sx, \Delta, \halfcan)$,
-in the case that genus is positive and $\halfcan$ is effective,
-by $3e$ and $6e$ for $e := \max(e_1, \ldots, e_r)$.
-
-The goal of this paper is to provide a stricter bound on the
-generator and relation degrees of log spin canonical rings
-for all genera. Note that O'Dorney's bounds are asymptotically
-tight for arbitrary $\BQ$-divisors on $\BP^1$, but restricting
-to the log spin curve case allows for lower bounds.
-The main theorem of this paper is the following improved bound on
-the degree of generators and relations of log spin canonical rings:
+log spin canonical ring and its relations are generated. Let
+$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
+e_r; \delta)$. The application of O'Dorney's work to log spin
+canonical rings gives a large bound for the genus zero case in
+terms of least common multiples of the $e_i$'s \cite[Chapter 5]
+{dorney:canonical}. Voight and Zureick-Brown bounded the 
+generator degrees by $3e$ and the relation degrees by $6e$ when
+$\halfcan$ is effective \cite[Corollary 10.4.6]{vzb:stacky}.
+
+These bounds, particularly those derived from O'Dorney's work
+in the genus zero case, are far from tight and do not collectively
+cover all cases in all genera. The main theorem of this paper
+gives significantly tighter bounds across all cases in all
+genera on the generator and relation degrees of log spin canonical
+rings.
 
@@
 \label{thm:main}
-Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use separable stacky points} so
-that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
-log spin canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d \halfcan \rfloor)
-\end{align*}
-
-\noindent
-is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0
-$ then $R(\sx,\Delta, \halfcan)$ has relations generated in degrees
-up to $\max(11, 2e_1, \ldots, 2e_r)$. Otherwise, $R(\sx, \Delta,
-\halfcan)$ has relations generated in degrees up to $\max(10, 2e_1,
-\ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list
-of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
-for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
-for signatures with $g = 0$.
+Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
+field $k$, so that $\sx$ has signature $\sigma = (0; e_1, \ldots,
+e_r; \delta)$.
+
+Then the log spin canonical ring is generated as a $k$-algebra by 
+elements of degree at most $e = \max(5, e_1, \ldots, e_r).$ If the 
+genus $g \geq 2,$ and $\Delta = 0$ then $R(\sx,\Delta, \halfcan)$
+has relations generated in degrees up to $\max(11, 2e_1, \ldots,
+2e_r)$. Otherwise, $R(\sx, \Delta, \halfcan)$ has relations
+generated in degrees up to $\max(10, 2e_1, \ldots, 2e_r),$ so long
+as $\sigma$ does not lie in a finite list of exceptional cases, as
+listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
+= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
+0$.
 \end{thm}
@@
 \end{defn}
-
-\subsection{Junk}
-\todo{add this back into the intro}
-This is stuff that has been moved out of the introduction to possibly
-be retooled for this section.
-
-We can then consider the
-orbifold $\Gamma \backslash \BH$ over $\BC$. For example, in the
-case $\Gamma$ acts freely on $\BH$, $\Gamma \backslash \BH$ is a
-Riemann Surface over $\BC$. It may well be that $\Gamma \backslash
-\BH$ is not compact. Defining $\Delta$ as the divisor of cusps
-associated to $\Gamma$, we can form a space $\Gamma \backslash
-\BH^*$ which is a compactification of $\Gamma \backslash \BH,$ with
-associated {\bf divisor of cusps} $\Delta$.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
edits to theorem 3.14

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle P  \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left\langle 
+	\di \sx = \di X \oplus \left(\bigoplus_{i = 1}^r \left\langle 
 	\frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X.
@@
 \[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle P  \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left\langle 
-	\frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X.
+	\di \sx = \di X \oplus \left(\bigoplus_{i
+	= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subseteq \BQ \otimes \di X
 \]
@@
 \begin{equation}
-	\deg \alpha := \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' =: \deg \beta
+	\deg \alpha := \sum_{i = 1}^{n} d f_i  > \sum_{i = 1}^{n} d f_i' =: \deg \beta
 \end{equation}
@@
 usually have an inclusion $R \supseteq R'$ of log spin canonical
-rings such that $R'$ is generated by elements $x_{d_i, i}$ and $R$
-is generated over $R'$ by elements $y_j$. In these cases, it is
+rings such that $R_\halfcan$ is generated by elements $x_{d_i, i}$ and $R$
+is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
 natural to consider term orders which treat these sets of variables
@@
 \label{defn:block-order}
-Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
-x_{d_n, n}]$ be weighted polynomial rings with existing term
-orders $\prec_y$ and $\prec_x$, respectively. Let $\alpha :=
-\prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ $\prod_{i = 1}^{n} x_{d_i, i}
-^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{c_j, j}^{h_i'}
-\prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ be monomials in $k[y_{d_1', 1},
-\ldots, y_{d_m', m}] \otimes$ $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$.
-Let $\alpha_y := \prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ be the
-part of $\alpha$ in $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and
-likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
+\todo{Aaron: Doesn't \cite{vzb:stacky} put the $y_i$ before the $x_i$? Shouldn't we match this convention (here and anywhere we use this in the paper later)?}
+Let $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and $k[y_{c_1, 1}, \ldots,
+y_{c_m, m}]$ be weighted polynomial rings with existing term
+orders $\prec_x$ and $\prec_y$, respectively. Let $\alpha :=
+\prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ $\prod_{j = 1}^{m} y_{c_j, j}
+^{h_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}
+\prod_{j = 1}^{m} y_{c_j, j}^{h_i'}$ be monomials in $k[x_{d_1, 1},
+\ldots, x_{d_n, n}] \otimes$ $k[y_{d_1', 1}, \ldots, y_{d_m', m}]$.
+Let $\alpha_x := \prod_{i = 1}^{n} x_{d_i, i}^{f_i}$ be the
+part of $\alpha$ in $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ and
+likewise with $\alpha_y$, $\beta_x$, and $\beta_y$.
 
 In the \textbf{(graded) block} (or \textbf{elimination}) term
-ordering on $k[y_{d_1', 1}, \ldots, y_{d_m', m}] \otimes k[x_{d_1, 1},
-\ldots, x_{d_n, n}]$, we define $\alpha \succ \beta$ if
+ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
+\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
   \begin{enumerate}
@@
 
-\ssec{Adding Points}
+\ssec{Adding Points}  \todo{Peter: Note to self: replace $H^0(X, \lfloor L\rfloor)$ with $H^0(\sx, L)$.}
 \label{ssec:add-points}
@@
 
-Thus, since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 		\{3, 4\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements
-		$y_3, y_4,$ minimally generate $R$ over $R'$.
+		$y_3, y_4,$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
 	\item[(b)] Equip $k[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
@@
 A quick computation checks that
-the following set $S$ is a $k$ basis for $R$ over $R'$:
+the following set $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$:
 
@@
 		4,5\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements $y
-		_3, y_4,$ and $y_5$ minimally generate $R$ over $R'$.
+		_3, y_4,$ and $y_5$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
 	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grevlex$ so that $y_3 \prec 
@@
 
-\noindent forms a $k$ basis for $R$ over $R'$, which concludes part (a) of the proof.
+\noindent forms a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$, which concludes part (a) of the proof.
 
@@
 \label{defn:admissible}
-Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
-curves, with the same coarse space $X$ and stacky points $Q_1, \ldots, Q_r$. Let $J \subset
-\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where
+Let $(\sx', \Delta, L')$ be a log spin
+curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
+\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
 
@@
 		\begin{align*}
-			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d), 0
 		\end{align*}
@@
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta).$ Further, assume either 
+space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$.  Define $R':= R_{L'}$.  Further, assume either 
 \begin{enumerate}
-	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_1,\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' = R_{L'}$ for all $i \in J,$ as in Definition ~\ref{defn:admissible} or
+	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_1,\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J,$ as in Definition ~\ref{defn:admissible} or
 	\item $\sigma$ is one of the signatures described in cases (1), (2) and (3) of Remark ~\ref{rem:three-cases} and $y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of $\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ for $1 \leq  i \leq r$.
@@
 \delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
-$e_j = e_j'$ for $j \notin J$. Then the following are true:
+$e_j = e_j'$ for $j \notin J$. Define $R := R_L$.  Then the following are true:
 \begin{enumerate}
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)] The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
-0,
-		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
+	\item[(b)] 
+	%The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
+%0,
+%		b > 0$ span $R$ over $R'$ and
+		A choice of elements $y_{1, e_1}, \ldots, y_{r, e_r}$ as in part (a) minimally
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y] := k[y_{i, e_i}]_{i \in J}$ and $k[x]:=k[x_1,\ldots, x_m]$ with graded monomial orders and give $k[y, x] = k[y] \otimes k[x]$ block order. Let $R = k[y, x]/I.$ Then,
+	\item[(c)] Endow $k[y_{1, e_1}, \ldots, y_{r, e_r}]$ and $ k[x_1,\ldots, x_m, y_{1, e_1'}, \ldots, y_{r, e_r'}]$ with graded monomial orders and give 
+\begin{align*}
+		& k[x_1, \ldots, x_m, y_{1, e_1'}, \ldots, y_{r, e_r'}, y_{1, e_r}, \ldots, y_{r,e_r}] \\
+	= \;	& k[y_{1,e_1}, \ldots, y_{r, e_r}] \otimes k[x_1, \ldots, x_m, y_{1, e_1'}, \ldots, y_{r, e_r'}]
+\end{align*}
+ block order. Let $R = k[y, x]/I.$ Then,
 		\begin{align*}
 			\initial(I) = \initial(I')k[x, y] + \langle y_{i, e_i}z : z 
-			\neq y_{i, e_i}, y_{i, e_i'} \rangle
+			\not\in \{y_{i, e_i}, y_{i, e_i'}\} \rangle
 		\end{align*}
@@
 \begin{proof}
-We will only prove this in the case (1), in which $(\sx', \halfcan', J)$ is admissible, as the case (2), in which $\sigma$ is as in Remark ~\ref{rem:three-cases}, is completely analogous.
+We will only prove this in case (1), since case (2), is completely analogous.  \todo{Peter: Note to self: come back after reading proof to see if I actually buy this statement.}
 
 {\bf Part (a):} 
-Recall from Definition ~\ref{defn:admissible} that
+By Definition ~\ref{defn:admissible}, for all $i\in J$
 
@@
 \noindent
-Note that
-\begin{align*}
-	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor 
-\end{align*}
-
-\noindent
-and so we obtain an inclusion
-\begin{align*}
-	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subseteq 
-H^0(\sx, e_iL).
-\end{align*}
-
-\noindent
 The assumption (Ad-iii) implies
 \begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq 2g - 1,
+	\deg \left( e_i L' - E_i \right) \geq \max(2g - 1,0),
 \end{align*}
@@
 ^{\halfcan_X'}(y_{i, e_i}) = \left\lfloor e_i \subhalf {e_i'} \right\rfloor + 1 =
-	\frac{e_i - 1}{2}
-\end{align*}
-
-\noindent
-Therefore, $y_{i, e_i}$ satisfies the first part of the claim of $(a)$.
+	\frac{e_i - 1}{2}.
+\end{align*}
+
+Noting that
+\begin{align*}
+	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor,
+\end{align*}
+
+\noindent
+we obtain an inclusion
+\begin{align*}
+	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subseteq 
+H^0(\sx, e_iL).
+\end{align*}
+
+\noindent
+meaning that $y_{i,e_i}\in H^0(\sx,e_iL)$ satisfies the first part of claim (a).
 
@@
 \begin{align*}
-	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
+	&a_1 x_{3, 1} x_{7, 2} + a_2 x_{3, 1} x_{7, 1} + a_3 x_{5, 1}^2 = 
 	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
-	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
+	&b_1 x_{7, 2}^2 + b_2 x_{7, 1} x_{7, 2} + b_3 x_{7, 1}^2
+	+ b_4 x_{3, 1}^3 x_{5, 1} = 0  &\text{ in degree $14$}
 \end{align*}
@@
 \[
-	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
-\]
-
-\noindent
-However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
+	a_2 x_{3, 1} x_{7, 1} = -a_3 x_{5, 1}^2
+\]
+
+\noindent
+However, $x_{3, 1} x_{7, 1}$ has pole orders $(3, 4, 3)$ and
 $x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
@@
 Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
+$k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}]$. Under grlex with
 $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
@@
 \[
-	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
+	\initial(I) = \langle x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
 \]
@@
 relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
+(k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \initial(I))_d$ for 
 all degrees $d \geq 0$. In particular,
@@
 \begin{align*}
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
-\end{align*}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
-\rangle$ can be checked by looking at the $k$-basis at each degree
-$d$.
+	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / I)_d &=
+	\dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}]	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{3, 1}, x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle
+	x_{3, 1} x_{7, 2}, x_{7, 2}^2 \rangle
+\end{align*}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{3, 1},
+x_{5, 1}, x_{7, 1}, x_{7, 2}] / \langle x_{5, 1}^2,	x_{7, 1}^2 \rangle$ can
+be checked by looking at the $k$-basis at each degree $d$.
 
 Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
+k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
 initial ideal $\initial(I)$ generated by quadratics under grlex
-with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
+with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$.
 %These quadratics must also determine minimal generators for $I$ by
@@
 This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$.
-In particular, we make the following conjecture.
+In particlar, we make the following conjecture.
 \begin{conjecture}

### 2015-06-30 stacky_write_up/spin_cring.tex

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \label{defn:block-order}
+
 Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,

### 2015-06-30 stacky_write_up/spin_cring.tex
define H^0(\sx, D), move def with floors

@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
 \end{align*}
@@
 elements of degree at most $e = \max(5, e_1, \ldots, e_r).$ If the 
-genus $g \geq 2,$ and $\Delta = 0$ then $R(\sx,\Delta, \halfcan)$
+genus $g \geq 2,$ and $\Delta = 0$ then $R(\sx, \Delta, \halfcan)$
 has relations generated in degrees up to $\max(11, 2e_1, \ldots,
@@
 $\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
-Now we can define the analogy to canonical rings for
-log spin curves.
+Furthermore, we use the following analogous notation:
 
@@
 \todo{cite lemma 5.4.7 from VZB maybe?}
-
+\end{defn}
+
+\begin{defn}
+Let $\sx$ be a stacky curve with coarse space $X$.
+If $D \in \di \sx$ is a Weil divisor, then we define
+
+\[
+	H^0(\sx, D) := H^0(X, \lfloor D \rfloor)
+\]
+\end{defn}
+
+\begin{defn}
 The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
 \[
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d \halfcan \rfloor)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
 \]

### 2015-06-30 stacky_write_up/spin_cring.tex
moved around some notation defs in bg

@@
 $\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
-Furthermore, we use the following analogous notation:
+Furthermore, we use the following analogous notations:
 
@@
 
+\begin{rem}
+\label{rem:odd-denom}
+Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
+\[
+	\halfcan = \sum_{i = 1}^{r} \frac{e_i - 1}{2e_i} P_i + \sum_{i = 1}^{s} a_i P_i
+\]
+
+\noindent
+where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
+that $\halfcan \in \di \sx$ by Kodaira--Spencer
+\cite{kodaira-spencer:deformations}. If $e_i$ were even,
+then $\frac{e_i - 1}{2e_i}$ would be in reduced form and
+the denominator would be too large for $\halfcan$ to be
+in $\di \sx$.
+\todo{refine above}
+\end{rem}
+
+\begin{rem}
+\label{rem:delta-not-1}
+Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta
+$ is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
+\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
+In particular, we shall often use $\deg \Delta \neq 1$.
+\end{rem}
+
 \begin{defn}
@@
 \end{defn}
-
-\begin{rem}
-\label{rem:odd-denom}
-Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
-\[
-	L = \sum_{i = 1}^{r} \frac{e_i - 1}{2e_i} P_i + \sum_{i = 1}^{s} a_i P_i
-\]
-
-\noindent
-where $a_i \in \BZ$ and $e_i$ are odd.
-\todo{give reason}
-\end{rem}
-
-\begin{rem}
-\label{rem:delta-not-1}
-Suppose $(\sx,\Delta,L)$ is a log spin curve. Note that $\deg \Delta
-$ is even. because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K
-\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
-In particular, we shall often use $\deg \Delta \neq 1$.
-\end{rem}
+\todo{where to put above?}
 

### 2015-06-30 stacky_write_up/spin_cring.tex
delete some intro todos, minor rewording

@@
 \]
-\todo{Peter: Would it be better to say $Div(\sx)=(Div(X))[\frac{1}{e_i}P_i]_{1\le i\le r}$ or something like that?
-Aaron: I agree what is written isn't actually correct, maybe we should say the free direct sum over points not in the $P_i$, together with the fractional points.
-It's not a localization because we don't want to invert $P_i$.}
-As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky curves may be formalized as stacks, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of stacky points.
-\todo{I don't know if this is a good statement to make.
-We aren't really viewing $\sx$ as a scheme.
-Rather we're are determining information about its canonical rings through knowledge of scheme data.}  A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
+
+As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky
+curves may be formalized as stacks, but for the purposes of this
+paper, it suffices to view $\sx$ as a scheme whose associated
+divisor group allows a finite number of stacky points.
+\todo{I don't know if this is a good statement to make.  We aren't
+really viewing $\sx$ as a scheme.  Rather we're are determining 
+information about its canonical rings through knowledge of scheme 
+data.}
+
+A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
+$\Delta \in \di X$ is an effective divisor and $2\halfcan = K _X +
+\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
 The central object of study in this paper is the {\bf log spin
@@
 terms of least common multiples of the $e_i$'s \cite[Chapter 5]
-{dorney:canonical}. Voight and Zureick-Brown bounded the 
-generator degrees by $3e$ and the relation degrees by $6e$ when
-$\halfcan$ is effective \cite[Corollary 10.4.6]{vzb:stacky}.
+{dorney:canonical}. In their treatment of log spin canonical
+rings, Voight and Zureick-Brown bounded generator degrees by $3e$
+and relation degrees by $6e$ when $\halfcan$ is effective
+\cite[Corollary 10.4.6]{vzb:stacky}.
 
@@
 Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
-field $k$, so that $\sx$ has signature $\sigma = (0; e_1, \ldots,
+field $k$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
 e_r; \delta)$.
@@
 := H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
-If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^{th}$
+If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
 degree component of $R$.
@@
 \[
-	\halfcan = \sum_{i = 1}^{r} \frac{e_i - 1}{2e_i} P_i + \sum_{i = 1}^{s} a_i P_i
+	\halfcan = \sum_{i = 1}^{r} \subhalf{e_i} P_i + \sum_{i = 1}^{s} a_i P_i
 \]

### 2015-06-30 stacky_write_up/spin_cring.tex
admissibility theorem edits

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx,\lfloor d \halfcan \rfloor)
 \end{align*}
@@
 elements of degree at most $e = \max(5, e_1, \ldots, e_r).$ If the 
-genus $g \geq 2,$ and $\Delta = 0$ then $R(\sx, \Delta, \halfcan)$
+genus $g \geq 2,$ and $\Delta = 0$ then $R(\sx,\Delta, \halfcan)$
 has relations generated in degrees up to $\max(11, 2e_1, \ldots,
@@
 $\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
-Furthermore, we use the following analogous notation:
+Now we can define the analogy to canonical rings for
+log spin curves.
 
@@
 \todo{cite lemma 5.4.7 from VZB maybe?}
-\end{defn}
-
-\begin{defn}
-Let $\sx$ be a stacky curve with coarse space $X$.
-If $D \in \di \sx$ is a Weil divisor, then we define
-
-\[
-	H^0(\sx, D) := H^0(X, \lfloor D \rfloor)
-\]
-\end{defn}
-
-\begin{defn}
+
 The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
 \[
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d \halfcan \rfloor)
 \]
@@
 
-If $j \in S(i,0)$, since $E_i \geq Q_j$ and $y_{i, e_i} \in H^0
-(\sx', e_iL'-E_i + Q_i)$,
+If $j \in S(i,0)$, then $E_i \geq Q_j$ gives $y_{i, e_i} \in H^0
+(\sx', e_iL'-E_i + Q_i)$ an extra vanishing condition at $Q_j$, so
 \begin{align*}
@@
 
-If instead $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
+If instead $j\ne i$ and $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
 $e_i\subhalf{e_j'} \notin \BZ$, so

### 2015-06-30 stacky_write_up/spin_cring.tex
rewrite intro stacky defns, also view -> treat

@@
 
-\todo{Peter: I think we need something about odd weight modular 
-forms before going right into stacks.}
 Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
-Petri's theorem in many \todo{Peter: not clear to me that ``many'' 
-is a good word to use here.  We mostly generalize in one direction}
-directions.
-
-\todo{combine below two paragraphs with the corresponding
-near-duplicate part from the background}
-If $X$ is a curve, \todo{why do you start with a curve and then
-move to a stacky curve? shouldn't it be the opposite order?} then
-we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
-and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
-\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
-\geq 2}$ if 
+Petri's theorem in the direction of stacky curves equipped with
+log divisors. For a stacky curve $\sx$ with coarse space $X$ and
+stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
+with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$,
+
 \[
@@
 	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
-\]
-
+	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
+\]
+
+Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
+where $\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
+\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$.
+
+The central object of study in this paper is the {\bf log spin
+canonical ring} of $(\sx, \Delta, \halfcan)$ is
+\begin{align*}
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
+\end{align*}
+
+\noindent
+A brief overview of stacky curves, log divisors, and log spin
+canonical rings and references are given in Subsection
+~\ref{ssec:stacky-background}.
+
+%If $X$ is a curve, \todo{why do you start with a curve and then
+%move to a stacky curve? shouldn't it be the opposite order?} then
+%we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
+%and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
+%\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
+%\geq 2}$ if 
+%\[
+	%\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
+	%P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
+	%\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
+%\]
+
+\begin{rem}
+\label{rem:stack-formalism}
 As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky
 curves may be formalized as stacks, but for the purposes of this
-paper, it suffices to view $\sx$ as a scheme whose associated
+paper, it suffices to treat $\sx$ as a scheme whose associated
 divisor group allows a finite number of stacky points.
-\todo{I don't know if this is a good statement to make.  We aren't
-really viewing $\sx$ as a scheme.  Rather we're are determining 
-information about its canonical rings through knowledge of scheme 
-data.}
-
-A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
-$\Delta \in \di X$ is an effective divisor and $2\halfcan = K _X +
-\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
-The central object of study in this paper is the {\bf log spin
-canonical ring} of $(\sx, \Delta, \halfcan)$ is
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
-\end{align*}
+\end{rem}
+
+%A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
+%$\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
+%\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
+%The central object of study in this paper is the {\bf log spin
+%canonical ring} of $(\sx, \Delta, \halfcan)$ is
+%\begin{align*}
+	%R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
+%\end{align*}
 
@@
 
-\todo{State for even weight modular forms attributed to VZB.}
 \begin{thm}
@@
 \begin{rem}
+\label{rem:separably-rooted}
 In fact, the theorem only needs to assume that the stacky curve
@@
 $k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
-its stabilizers are coprime to char $k$. Throughout this paper,
-stacky curves will be assumed to be tame and $k$ will always be
-algebraically closed. We also assume that the stacky curves are
-separably rooted, i.e. the residue field of each stacky points
-is separable. The language of stacks will be omitted in
-this paper, as it is sufficient to view stacky curves and related
-objects $\sx$ as a scheme whose associated divisor group allows for
-a finite number of \textbf{stacky points} which may be viewed
-heuristically as ``fractional points''. See Voight and
+its stabilizers are coprime to char $k$.
+
+Throughout this paper, stacky curves will be assumed to be tame and
+$k$ will always be algebraically closed. We also assume that the
+stacky curves are separably rooted, i.e. the residue field of each
+stacky points is separable. As noted in Remark
+~\ref{rem:stack-formalism}, the language of stacks will be omitted
+in this paper, as it is sufficient to treat stacky curves and
+related objects $\sx$ as a scheme whose associated divisor group
+allows for a finite number of \textbf{stacky points} which may be
+viewed heuristically as ``fractional points''. See Voight and
 Zureick-Brown for more thorough treatment of these definitions
-\cite[Chapter 5]{vzb:stacky}. \todo{again, not quite viewing as a
-scheme}
+\cite[Chapter 5]{vzb:stacky}.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
admissibility theorem edits

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 To prove (b), it suffices to show that elements of the form $y_{i, e_
-i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ are linearly independent,
-and that these elements together with $R_{i - 1}$ span $R_i$ as a $k$-
-vector space. These elements do not lie in $R_{i - 1}$ because when viewed as a rational section of $\sco(L_X')$, their order of pole at $Q_i$ is bigger than the order of any element in $R
-_{i - 1}$. Additionally, these elements are linearly independent amongst themselves because of
+i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $k$-basis for $R_{i}$ over $R_{i-1}$.
+These elements do not lie in $R_{i - 1}$ because pole orders at $Q_i$ are bigger than that of any element of $R_{i - 1}$.
+Additionally, these elements are linearly independent amongst themselves because of
 injectivity of the linear map
@@
 		e_i	 & \frac{e_i - 1}{2}
-	\end{pmatrix} 
+	\end{pmatrix}.
 \end{align*}

### 2015-06-30 stacky_write_up/spin_cring.tex
join two sparse-looking paragraphs
rem that \Delta can be any effective, label defns

@@
 where $\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
-\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$.
-
-The central object of study in this paper is the {\bf log spin
-canonical ring} of $(\sx, \Delta, \halfcan)$ is
+\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
+study in this paper is the {\bf log spin canonical ring} of $(\sx,
+\Delta, \halfcan)$ is
 \begin{align*}
@@
 \begin{rem}
-\label{rem:separably-rooted}
+\label{rem:main-weaker-assumptions}
 In fact, the theorem only needs to assume that the stacky curve
 is separably rooted, i.e. the residue field at each stacky point
-is separable.
+is separable. Furthermore, the proof works even when letting
+$\Delta$ be any effective divisor rather than just a log divisor.
 \end{rem}
@@
 initial ideal of relations for the half-canonical divisor $\halfcan$
- can be written as $\halfcan = \halfcan' + \Lambda$ with $(\halfcan
-', \Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact,
+can be written as $\halfcan = \halfcan' + \Lambda$ with $(\halfcan',
+\Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact,
 such a system of generators and relations are known for $\halfcan'$
@@
 If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
-then we use $e_1,\ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
+then we use $e_1, \ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
 of the stabilizer groups of the points with non-trivial
@@
 \begin{defn}
+\label{defn:coarse-space}
 Let $\sx$ be a stacky curve over $k$ with stacky points $P_1, \ldots,
@@
 \begin{defn}
+\label{defn:divisor-floor}
 If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
@@
 \begin{defn}
+\label{defn:h0-stacky}
 Let $\sx$ be a stacky curve with coarse space $X$.
@@
 \begin{defn}
+\label{defn:log-spin-canonical-ring}
 The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is

### 2015-06-30 stacky_write_up/spin_cring.tex
revision to remark on explicit gens/rels, add "."s

@@
 	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
+	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
 \]
@@
 Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
-where $\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
+where $\Delta \in \di X$ is a log divisor and $2\halfcan \sim K_X +
 \Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan).
 \end{align*}
@@
 relations. Furthermore, our proof of the high genus case also
-provides an inductive procedure for determining the generators and
-initial ideal of relations for the half-canonical divisor $\halfcan$
-can be written as $\halfcan = \halfcan' + \Lambda$ with $(\halfcan',
-\Delta, \sx)$ when $\Lambda \in \di \sx$ effective. In fact,
-such a system of generators and relations are known for $\halfcan'$
-in many interesting low genus cases, as detailed in Neves
-~\cite[Section III.4]{neves:halfcan}.
+provides an inductive procedure for explicitly determining the 
+generators and initial ideal of relations for log spin canonical
+rings. Many explicit systems of generators and relations are
+detailed in interesting low genus examples by Neves
+\cite[Section III.4]{neves:halfcan}.
 \end{rem}
@@
 \[
-	H^0(\sx, D) := H^0(X, \lfloor D \rfloor)
+	H^0(\sx, D) := H^0(X, \lfloor D \rfloor).
 \]
@@
 \[
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan).
 \]
@@
 \label{rem:delta-not-1}
-Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta
-$ is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
+Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta$
+is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
 \rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
@@
 \[
-	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}
+	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}.
 \]
@@
 \[
-	\deg \alpha := \sum_{i = 1}^{n} d f_i
+	\deg \alpha := \sum_{i = 1}^{n} d f_i.
 \]
@@
 	\deg \alpha = \deg \beta \text{ and }
-	\alpha \succ_{\text{lex}} \beta
+	\alpha \succ_{\text{lex}} \beta.
 \end{equation}
@@
 	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
-the	largest } i \text{ such that } f_i \neq f_i'
+	the	largest } i \text{ such that } f_i \neq f_i'.
 \end{equation}
@@
   \item[(ii)] $\deg \alpha = \deg \beta$ and $\alpha_y \succ_y \beta_y$ or
-	\item[(iii)] $\deg \alpha = \deg \beta$ and $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$
+	\item[(iii)] $\deg \alpha = \deg \beta$ and $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$.
   \end{enumerate}

### 2015-06-30 stacky_write_up/spin_cring.tex
admissibility theorem edits

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y_{1, e_1}, \ldots, y_{r, e_r}]$ and $ k[x_1,\ldots, x_m, y_{1, e_1'}, \ldots, y_{r, e_r'}]$ with graded monomial orders and give 
-\begin{align*}
-		& k[x_1, \ldots, x_m, y_{1, e_1'}, \ldots, y_{r, e_r'}, y_{1, e_r}, \ldots, y_{r,e_r}] \\
-	= \;	& k[y_{1,e_1}, \ldots, y_{r, e_r}] \otimes k[x_1, \ldots, x_m, y_{1, e_1'}, \ldots, y_{r, e_r'}]
-\end{align*}
+	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1,\ldots, x_m\{y_{i, e_i'}:{i\in J}\}$ with graded monomial orders and give 
+$k[y_{i, e_i}]_{i\in J} \otimes \left(k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i\in J}\right)$
  block order. Let $R = k[y, x]/I.$ Then,
 		\begin{align*}
-			\initial(I) = \initial(I')k[x, y] + \langle y_{i, e_i}z : z 
-			\not\in \{y_{i, e_i}, y_{i, e_i'}\} \rangle
+			\initial(I) = \initial(I')k[x, y] + \langle y_{i, e_i}z : i\in J, z\in (\{x_1, \ldots, x_m, y_{1, e_1'}, \ldots y_{r},e_\{y_{i, e_i}, y_{i, e_i'}\} \rangle
 		\end{align*}
@@
 i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $k$-basis for $R_{i}$ over $R_{i-1}$.
-These elements do not lie in $R_{i - 1}$ because pole orders at $Q_i$ are bigger than that of any element of $R_{i - 1}$.
+These elements do not lie in $R_{i - 1}$ because the pole order of $y_{i, e_i'}^ay_{i,e_i}^b$ at $Q_i$ is larger than that of any element in the $d^{th}$ component of $R_{i - 1}$.
 Additionally, these elements are linearly independent amongst themselves because of
@@
 \noindent
-The fact the the elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 0,
-b > 0$ span $R_i$ over $R_{i - 1}$ follows from the fact that the
+Furthermore, $\{y_{i, e_i'}^a y_{i, e_i}^b:a \geq 0,
+b > 0\}$ span $R_i$ over $R_{i - 1}$, because the set of
 integer lattice points in the cone generated by the vectors $\left(e
 _i -2, \frac{e_i -3}{2} \right)$ and $\left(e_i, \frac{e_i - 1}{2}
-\right)$ is saturated, as the corresponding determinant is
-\begin{align*}
-	(e_i -2) \frac{e_i - 1}{2} - e_i \frac{e_i -3}{2} = 1,
-\end{align*}
-completing part (b).
+\right)$ is saturated, because the corresponding determinant is
+\begin{align*}
+	(e_i -2) \frac{e_i - 1}{2} - e_i \frac{e_i -3}{2} = 1.
+\end{align*}
+This completes part (b).
 

### 2015-06-30 stacky_write_up/spin_cring.tex
half(-)canonical -> spin canonical

@@
 $2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
-is called a \textbf{half-canonical divisor} on $(\sx, \Delta)$
+is called a \textbf{spin canonical divisor} on $(\sx, \Delta)$
 and are sometimes referred to as theta-characteristics in other
-literature. We also use $\halfcan_X$ to refer to the half-canonical
-divisor associated with the coarse space $X$ of $\sx$, i.e.
+literature. We also use $\halfcan_X$ to refer to the spin canonical
+divisor (also known as the half-canonical divisor or semi-canonical
+divisor) associated with the coarse space $X$ of $\sx$, i.e.
 $\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
@@
 In
-Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
+Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log spin canonical ring of a curve with signature $(g; e_1', 
 \ldots, e_\tau'; 0)$ to that of a
@@
 %context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
-%half-canonical divisors.
+%spin canonical divisors.
 
@@
 %In this section, we prove various inductive statements under the following setup:
-%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 \label{lem:sat-3}
-Suppose $L'$ is a log half-canonical divisor of $\sx'$ with coarse
+Suppose $L'$ is a log spin canonical divisor of $\sx'$ with coarse
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
@@
 %\begin{proof}
-%Since $\halfcan$ is a half canonical divisor, 
+%Since $\halfcan$ is a spin canonical divisor, 
 %\[
@@
 We now consider the case when the genus is at least 2.
-In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$.
+In this case, we are able to bound the degrees and relations of the spin canonical ring $R_L$.
 In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
@@
 \label{rem:relations_generation_ten}
-In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10.
-Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to sharp.
+In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$
+ is a spin canonical divisor on a genus 2 curve, then $R_L$ has a
+relation in degree 10. Therefore, the bound from Proposition
+~\ref{prop:relation_11}, that $I_L$ is generated in degree at most
+11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
+sharp.
 \end{rem}
@@
 The inductive strategy we will adopt to prove Theorem ~\ref{thm:main} is similar to that of the genus $g \geq 2$ case.
-In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
+In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
 We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.
@@
 \label{eg:exception-1-5}
-Let $L' = P - Q + \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$.
+Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$.
 Let $u \in (P_L)_1$ be any nonzero element.
@@
 	\item In the case $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of a log spin canonical ring $R_L$.
-Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with half canonical divisor $L = P$ has spin canonical ring $R_L$ with relations in degree 10.
+Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with spin canonical divisor $L = P$ has spin canonical ring $R_L$ with relations in degree 10.
 This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$.
@@
 \end{question}
-Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a half canonical divisor of $X$.
+Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor of $X$.
 In this case our proof of Theorem ~\ref{thm:main} yields an algorithm for determining the generators of $L$.
@@
 \begin{question}
-\label{ques:half-canonical-petri}
-Given a {\rm(}non-stacky {\rm)} curve $X$ and a half canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$?
+\label{ques:spin-canonical-petri}
+Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$?
 If so, can one give the generic ideal of $R_L$ or the generic initial ideal of $R_L$, as defined in Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}?
 \end{question}
-In particular, if Question ~\ref{ques:half-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
+In particular, if Question ~\ref{ques:spin-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
 	\todo{This last one doesn't seem particularly interesting. Should we remove it?}

### 2015-06-30 stacky_write_up/spin_cring.tex
admissibility theorem edits

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1,\ldots, x_m\{y_{i, e_i'}:{i\in J}\}$ with graded monomial orders and give 
-$k[y_{i, e_i}]_{i\in J} \otimes \left(k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i\in J}\right)$
- block order. Let $R = k[y, x]/I.$ Then,
-		\begin{align*}
-			\initial(I) = \initial(I')k[x, y] + \langle y_{i, e_i}z : i\in J, z\in (\{x_1, \ldots, x_m, y_{1, e_1'}, \ldots y_{r},e_\{y_{i, e_i}, y_{i, e_i'}\} \rangle
-		\end{align*}
-		as $z$ ranges over all generators of $R$.
+	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1,\ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
+$k[y_{i, e_i}]_{i\in J} \otimes k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
+ block order.  Let $I$ be the kernel of $k[x_1, \ldots, x_m, y_{i, e_i'}, y_{i, e_i}]_{i\in J} \to R$.
+  Then,
+		\begin{align*}
+			\initial(I) \;	&= \; \initial(I')k[x, y] \\
+					&+ \; \langle y_{j, e_j}x_i  : 1\le i \le m, j\in J\rangle \\
+					&+ \; \langle y_{j, e_j}y_{i, e_i'}: i,j\in J, i\ne j\rangle \\
+					&+ \; \langle y_{j,e_j}y_{i,e_i}: i,j\in J, i\ne j\rangle.
+		\end{align*}
 	\item[(d)] The triple $(\sx, \halfcan', J)$ is admissible.
@@
 	-\ord_{Q_j}
-^{\halfcan_X'}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
+^{\halfcan_X'}(f) \leq \deg (f) \left( \subhalf {e_j'} \right).
 \end{align}
@@
 \noindent
-We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases that $j \notin \{
-i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
+We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases: 
+%$j \notin \{i \} \cup S(i, 0)$, $j = i,$ and $j \in S(i, 0)$.
 
@@
 ^{\halfcan_X'}(z) \leq e_i \subhalf {e_j'} +
-	\deg z \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
+	\deg (z) \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
 \end{align*}
@@
 {\sf Case 2: $j =i.$}
+
 By part (a), condition (Ad-ii), and Lemma
@@
 ^{\halfcan_X'}(z)
-	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg z \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg z \left( \subhalf{e_j'} \right) \\
+	&\leq \frac{e_j - 1}{2} + \deg (z) \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
+	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg (z) \left( \subhalf{e_j'} \right) \\
+	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg (z) \left( \subhalf{e_j'} \right) \\
 	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.

### 2015-06-30 stacky_write_up/spin_cring.tex
Div X tensor Q -> Q tensor Div X

@@
 \todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
-Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.
+Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
 This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
@@
 \begin{lem}\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan, \halfcan' \in \di X \otimes \BQ$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
+Suppose $\halfcan, \halfcan' \in \BQ \otimes \di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
 and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
@@
 \label{lem:sat-1}
-Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
+Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.

### 2015-06-30 stacky_write_up/spin_cring.tex
mid moving examples

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 research.
+\todo{Add examples section.}
 
@@
 $2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
-is called a \textbf{spin canonical divisor} on $(\sx, \Delta)$
-and are sometimes referred to as theta-characteristics in other
-literature. We also use $\halfcan_X$ to refer to the spin canonical
-divisor (also known as the half-canonical divisor or semi-canonical
-divisor) associated with the coarse space $X$ of $\sx$, i.e.
+is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. We also use $\halfcan_X$ to refer to the spin canonical
+divisor (also known as the half-canonical divisor, semi-canonical
+divisor, or theta-characteristics) associated with the coarse space $X$ of $\sx$, i.e.
 $\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
@@
 \end{defn}
+
+\ssec{Admissibility}
+
+In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin-canonical divisors.
+
+One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
+%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
+	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections.
+We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
+
+\begin{defn}
+\label{defn:admissible}
+Let $(\sx', \Delta, L')$ be a log spin
+curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
+\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
+
+\[
+\chi_J(i) = \begin{cases}
+	1, &\text{ if }i \in J\\
+	0, &\text{ otherwise. } 
+\end{cases}
+\]
+
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
+to be {\bf admissible} if $R'$ admits a presentation
+\begin{align*}
+	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
+\end{align*}
+
+\noindent
+with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
+three conditions hold:
+\begin{enumerate}
+	\item[(Ad-i)] First, 
+	\begin{align*}
+	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
+		= \frac{e_i'- 1}{2}.
+	\end{align*}
+		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
+		\begin{align*}
+			\frac{-\ord_{Q_i}
+^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[(Ad-iii)] Third, we have
+		\begin{align*}
+			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+		\end{align*}
+		where
+		\begin{align*}
+			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i - e_j'\}.
+		\end{align*}
+\end{enumerate}
+\end{defn}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Examples %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Examples}
+\label{sec:examples}
+
+\begin{example}
+\label{eg:base-1-0}
+In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+\label{eg:base-1-33}
+Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
+and that $(\sx', \halfcan',\{1,2\})$ is admissible.
+
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
+Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are both one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
+
+Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
+$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
+The details are omitted as it is analogous to Example ~\ref{ex:base-377}.
+
+We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
+We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
+Hence, (Ad-i) holds.
+We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric.
+Here, by construction
+$$
+\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
+	0 &\text{ if }z \in \{u, y_3\}\\
+	\frac{1}{4} &\text{ if }z = y_4
+\end{cases}.$$
+Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
+Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+\end{example}
+
+\begin{example}
+\label{eg:exception-1-5}
+Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$.
+Let $u \in (P_L)_1$ be any nonzero element.
+We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
+We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$.
+Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$.
+Then, we claim there is some $\alpha \in k$ so that
+$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+
+In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
+One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+The verification is analogous to Example ~\ref{ex:base-377} and is omitted.
+
+Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
+
+Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 also determines a relation in the canonical ring for $L = P - Q + \frac{3}{7}$, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
+\end{example}
 
@@
 %~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in %Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
-
-One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
-%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
-	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
-
-\begin{defn}
-\label{defn:admissible}
-Let $(\sx', \Delta, L')$ be a log spin
-curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
-\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
-
-\[
-\chi_J(i) = \begin{cases}
-	1, &\text{ if }i \in J\\
-	0, &\text{ otherwise. } 
-\end{cases}
-\]
-
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
-to be {\bf admissible} if $R'$ admits a presentation
-\begin{align*}
-	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
-\end{align*}
-
-\noindent
-with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
-three conditions hold:
-\begin{enumerate}
-	\item[(Ad-i)] First, 
-	\begin{align*}
-	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
-		= \frac{e_i'- 1}{2}.
-	\end{align*}
-		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}
-^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[(Ad-iii)] Third, we have
-		\begin{align*}
-			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d), 0
-		\end{align*}
-		where
-		\begin{align*}
-			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i - e_j'\}
-		\end{align*}
-\end{enumerate}
-\end{defn}
+d
 
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1,\ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
-$k[y_{i, e_i}]_{i\in J} \otimes k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
- block order.  Let $I$ be the kernel of $k[x_1, \ldots, x_m, y_{i, e_i'}, y_{i, e_i}]_{i\in J} \to R$.
-  Then,
-		\begin{align*}
-			\initial(I) \;	&= \; \initial(I')k[x, y] \\
-					&+ \; \langle y_{j, e_j}x_i  : 1\le i \le m, j\in J\rangle \\
-					&+ \; \langle y_{j, e_j}y_{i, e_i'}: i,j\in J, i\ne j\rangle \\
-					&+ \; \langle y_{j,e_j}y_{i,e_i}: i,j\in J, i\ne j\rangle.
-		\end{align*}
+	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1,\ldots, x_m\{y_{i, e_i'}:{i\in J}\}$ with graded monomial orders and give 
+$k[y_{i, e_i}]_{i\in J} \otimes \left(k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i\in J}\right)$
+ block order. Let $R = k[y, x]/I.$ Then,
+		\begin{align*}
+			\initial(I) = \initial(I')k[x, y] + \langle y_{i, e_i}z : i\in J, z\in (\{x_1, \ldots, x_m, y_{1, e_1'}, \ldots y_{r},e_\{y_{i, e_i}, y_{i, e_i'}\} \rangle
+		\end{align*}
+		as $z$ ranges over all generators of $R$.
 	\item[(d)] The triple $(\sx, \halfcan', J)$ is admissible.
@@
 	-\ord_{Q_j}
-^{\halfcan_X'}(f) \leq \deg (f) \left( \subhalf {e_j'} \right).
+^{\halfcan_X'}(f) \leq \deg f \left( \subhalf {e_j'} \right) 
 \end{align}
@@
 \noindent
-We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases: 
-%$j \notin \{i \} \cup S(i, 0)$, $j = i,$ and $j \in S(i, 0)$.
+We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases that $j \notin \{
+i \} \cup S(i, 0), j = i,$ or $j \in S(i, 0)$.
 
@@
 ^{\halfcan_X'}(z) \leq e_i \subhalf {e_j'} +
-	\deg (z) \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
+	\deg z \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
 \end{align*}
@@
 {\sf Case 2: $j =i.$}
-
 By part (a), condition (Ad-ii), and Lemma
@@
 ^{\halfcan_X'}(z)
-	&\leq \frac{e_j - 1}{2} + \deg (z) \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg (z) \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg (z) \left( \subhalf{e_j'} \right) \\
+	&\leq \frac{e_j - 1}{2} + \deg z \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
+	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg z \left( \subhalf{e_j'} \right) \\
+	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg z \left( \subhalf{e_j'} \right) \\
 	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
@@
 $y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-(Ad-i) of Definition ~\ref{defn:admissible}. We may also choose
+(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
@@
 Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
+\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
 \frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
-$\sigma, J$ is admissible.
+$(\sigma, \sx', J)$ is admissible.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
pushed new examples section

@@
 In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+\label{ex:base-377}
+Here we demonstrate, in detail, that case (b) with ($\sigma =
+(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
+\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
+satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
+We exhibit a (minimal) presentation for $R'$.
+
+Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
+\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
+
+By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
+\[
+	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor)
+\]
+
+\noindent
+is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
+\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
+Table ~\ref{table:g-0-sat}, then this map is surjective
+when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
+
+For $d = 0, 1, 2, \ldots$ we have
+\[
+	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+\]
+
+\noindent
+so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
+x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
+
+To show that these generate all of $R'$, we need to show that all
+$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
+and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
+(taking saturation into account) to see that
+
+\begin{align*}
+	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
+	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
+	\text{ (mod } 7)
+\end{align*}
+
+\noindent
+are surjective. This reduces the problem to checking generation
+in the degrees of the exceptions $d \in \{8, 12, 21\}$.
+Checking the remaining cases via pole degrees shows that
+these degrees are also generated in lower degrees,
+so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
+
+Now, we check admissibility. By relabelling the
+variables if necessary, we can assume that $x_{7, 1}$ corresponds
+to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
+correspond to the generator with maximal pole order at $P_3$. Use
+the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
+$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
+(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
+pole orders of the generators such that $y_{i, e_i'}$ is the only
+generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
+in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
+generators lying below the line as seen in Figure ~\ref{fig:377}
+(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
+(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
+and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
+$x_{7, 2}$ respectively).
+
+\begin{figure}[H]
+\label{fig:377}
+\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\end{figure}
+
+Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
+$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
+0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
+Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
+\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
+\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
+$(\sigma, \sx', J)$ is admissible.
+
+%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
+%represent the pole orders of $x_i$ at each point. Then these generators
+%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
+%respectively.
+
+We can directly see that the relations are given in degrees $10$
+and $14$. In particular, we have relations
+\begin{align*}
+	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
+	0 &\text{ in degree $10$} \\
+	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
+	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
+\end{align*}
+
+\noindent
+and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
+have that
+\[
+	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
+\]
+
+\noindent
+However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
+$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
+coefficients must be zero for this equality to hold. We have a
+similar pole order consideration in forcing $b_1$ to be nonzero.
+
+Let $I$ be the ideal generated by these relations in
+$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
+$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
+ideal of $I$ is
+\[
+	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
+\]
+
+\noindent
+since $a_1$ and $b_1$ are nonzero.
+
+To demonstrate that these two relations generate all 
+relations, we show that $\dim_k (R')_d = \dim_k
+(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
+all degrees $d \geq 0$. In particular,
+
+\begin{align*}
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
+	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
+\end{align*}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
+x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
+\rangle$ can be checked by looking at the $k$-basis at each degree
+$d$.
+
+Therefore, the canonical ring $R'$ has presentation $R' =
+k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
+initial ideal $\initial(I)$ generated by quadratics under grlex
+with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
+%These quadratics must also determine minimal generators for $I$ by
+%Lemma ~\ref{lem:minimal_quadratic}.
+Thus, $R'$ is generated up to degree $e = 7$ with relations up to
+degree $2e = 14$, as desired.
+
+%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
+%since $e_i = 9 > e$ for all $i \in J$.
 \end{example}
@@
 \label{ssec:g_1_base}
-
-We first analyze the following two examples, which will be crucial base cases for our inductive approach, completed in Subsection ~\ref{ssec:main_g_1}.
+In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g=1$.
 
@@
 
-\begin{example}
-\label{eg:base-1-0}
-In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
-\end{example}
-
-\begin{example}
-\label{eg:base-1-33}
-Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx', \halfcan',\{1,2\})$ is admissible.
-
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
-Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are both one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
-
-Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
-The details are omitted as it is analogous to Example ~\ref{ex:base-377}.
-
-We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
-We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, (Ad-i) holds.
-We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric.
-Here, by construction
-$$
-\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4
-\end{cases}.$$
-Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
-Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
-\end{example}
-
-\begin{example}
-\label{eg:exception-1-5}
-Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$.
-Let $u \in (P_L)_1$ be any nonzero element.
-We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
-We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$.
-Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$.
-Then, we claim there is some $\alpha \in k$ so that
-$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
-
-In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
-The verification is analogous to Example ~\ref{ex:base-377} and is omitted.
-
-Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
-
-Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 also determines a relation in the canonical ring for $L = P - Q + \frac{3}{7}$, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
-\end{example}
-
-%The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u, y_5, y_7]/(y_5)^3 - uy_7^2.$
+The cases that $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
 
 The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
-Note that just like $L' = P - Q + \frac{2}{5}P_1$ is an exceptional case, as noted at the end of Example ~\ref{eg:exception-1-5}, $L' = \frac{3}{7}P_1$ is yet another exceptional case.
+Note that in addition to $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ being base cases, they are also exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}.
 
@@
 
-Before proving Lemma ~\ref{lem:g-0-admissible-cases} in general, we check the lemma holds for case (b).
-
-\begin{example}
-\label{ex:base-377}
-Here we demonstrate, in detail, that case (b) with ($\sigma =
-(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
-satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
-We exhibit a (minimal) presentation for $R'$.
-
-Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
-\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
-
-By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
-\[
-	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor)
-\]
-
-\noindent
-is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
-Table ~\ref{table:g-0-sat}, then this map is surjective
-when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
-
-For $d = 0, 1, 2, \ldots$ we have
-\[
-	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
-
-To show that these generate all of $R'$, we need to show that all
-$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
-(taking saturation into account) to see that
-
-\begin{align*}
-	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
-	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
-	\text{ (mod } 7)
-\end{align*}
-
-\noindent
-are surjective. This reduces the problem to checking generation
-in the degrees of the exceptions $d \in \{8, 12, 21\}$.
-Checking the remaining cases via pole degrees shows that
-these degrees are also generated in lower degrees,
-so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
-
-Now, we check admissibility. By relabelling the
-variables if necessary, we can assume that $x_{7, 1}$ corresponds
-to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
-correspond to the generator with maximal pole order at $P_3$. Use
-the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
-$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
-pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
-in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
-generators lying below the line as seen in Figure ~\ref{fig:377}
-(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
-(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
-and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
-$x_{7, 2}$ respectively).
-
-\begin{figure}[H]
-\label{fig:377}
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
-\end{figure}
-
-Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
-$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
-Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
-$(\sigma, \sx', J)$ is admissible.
-
-%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
-%represent the pole orders of $x_i$ at each point. Then these generators
-%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
-%respectively.
-
-We can directly see that the relations are given in degrees $10$
-and $14$. In particular, we have relations
-\begin{align*}
-	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
-	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
-	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
-\end{align*}
-
-\noindent
-and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
-have that
-\[
-	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
-\]
-
-\noindent
-However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
-$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
-coefficients must be zero for this equality to hold. We have a
-similar pole order consideration in forcing $b_1$ to be nonzero.
-
-Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
-$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
-ideal of $I$ is
-\[
-	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
-\]
-
-\noindent
-since $a_1$ and $b_1$ are nonzero.
-
-To demonstrate that these two relations generate all 
-relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
-all degrees $d \geq 0$. In particular,
-
-\begin{align*}
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
-\end{align*}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
-\rangle$ can be checked by looking at the $k$-basis at each degree
-$d$.
-
-Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
-initial ideal $\initial(I)$ generated by quadratics under grlex
-with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
-%These quadratics must also determine minimal generators for $I$ by
-%Lemma ~\ref{lem:minimal_quadratic}.
-Thus, $R'$ is generated up to degree $e = 7$ with relations up to
-degree $2e = 14$, as desired.
-
-%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
-%since $e_i = 9 > e$ for all $i \in J$.
-\end{example}
+Note that Example ~\ref{eg:base-377}, precisely proves case (b) of Lemma ~\ref{lem:g-0-admissible-cases}.
 

### 2015-06-30 stacky_write_up/spin_cring.tex

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \end{defn}
+
+\ssec{Admissibility}
+
+In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin-canonical divisors.
+
+One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
+%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
+	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections.
+We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
+
+\begin{defn}
+\label{defn:admissible}
+Let $(\sx', \Delta, L')$ be a log spin
+curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
+\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
+
+\[
+\chi_J(i) = \begin{cases}
+	1, &\text{ if }i \in J\\
+	0, &\text{ otherwise. } 
+\end{cases}
+\]
+
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
+to be {\bf admissible} if $R'$ admits a presentation
+\begin{align*}
+	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
+\end{align*}
+
+\noindent
+with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
+three conditions hold:
+\begin{enumerate}
+	\item[(Ad-i)] First, 
+	\begin{align*}
+	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
+		= \frac{e_i'- 1}{2}.
+	\end{align*}
+		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
+		\begin{align*}
+			\frac{-\ord_{Q_i}
+^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[(Ad-iii)] Third, we have
+		\begin{align*}
+			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+		\end{align*}
+		where
+		\begin{align*}
+			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			\mid e_i - e_j'\}.
+		\end{align*}
+\end{enumerate}
+\end{defn}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%% Examples %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Examples}
+\label{sec:examples}
+
+\begin{example}
+\label{eg:base-1-0}
+In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+\label{ex:base-377}
+Here we demonstrate, in detail, that case (b) with ($\sigma =
+(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
+\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
+satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
+We exhibit a (minimal) presentation for $R'$.
+
+Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
+\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
+
+By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
+\[
+	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor)
+\]
+
+\noindent
+is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
+\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
+Table ~\ref{table:g-0-sat}, then this map is surjective
+when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
+
+For $d = 0, 1, 2, \ldots$ we have
+\[
+	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+\]
+
+\noindent
+so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
+x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
+
+To show that these generate all of $R'$, we need to show that all
+$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
+and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
+(taking saturation into account) to see that
+
+\begin{align*}
+	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
+	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
+	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
+	\text{ (mod } 7)
+\end{align*}
+
+\noindent
+are surjective. This reduces the problem to checking generation
+in the degrees of the exceptions $d \in \{8, 12, 21\}$.
+Checking the remaining cases via pole degrees shows that
+these degrees are also generated in lower degrees,
+so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
+
+Now, we check admissibility. By relabelling the
+variables if necessary, we can assume that $x_{7, 1}$ corresponds
+to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
+correspond to the generator with maximal pole order at $P_3$. Use
+the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
+$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
+(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
+pole orders of the generators such that $y_{i, e_i'}$ is the only
+generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
+in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
+generators lying below the line as seen in Figure ~\ref{fig:377}
+(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
+(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
+and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
+$x_{7, 2}$ respectively).
+
+\begin{figure}[H]
+\label{fig:377}
+\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\end{figure}
+
+Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
+$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
+0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
+Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
+\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
+\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
+$(\sigma, \sx', J)$ is admissible.
+
+%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
+%represent the pole orders of $x_i$ at each point. Then these generators
+%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
+%respectively.
+
+We can directly see that the relations are given in degrees $10$
+and $14$. In particular, we have relations
+\begin{align*}
+	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
+	0 &\text{ in degree $10$} \\
+	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
+	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
+\end{align*}
+
+\noindent
+and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
+have that
+\[
+	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
+\]
+
+\noindent
+However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
+$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
+coefficients must be zero for this equality to hold. We have a
+similar pole order consideration in forcing $b_1$ to be nonzero.
+
+Let $I$ be the ideal generated by these relations in
+$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
+$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
+ideal of $I$ is
+\[
+	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
+\]
+
+\noindent
+since $a_1$ and $b_1$ are nonzero.
+
+To demonstrate that these two relations generate all 
+relations, we show that $\dim_k (R')_d = \dim_k
+(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
+all degrees $d \geq 0$. In particular,
+
+\begin{align*}
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
+	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
+\end{align*}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
+x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
+\rangle$ can be checked by looking at the $k$-basis at each degree
+$d$.
+
+Therefore, the canonical ring $R'$ has presentation $R' =
+k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
+initial ideal $\initial(I)$ generated by quadratics under grlex
+with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
+%These quadratics must also determine minimal generators for $I$ by
+%Lemma ~\ref{lem:minimal_quadratic}.
+Thus, $R'$ is generated up to degree $e = 7$ with relations up to
+degree $2e = 14$, as desired.
+
+%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
+%since $e_i = 9 > e$ for all $i \in J$.
+\end{example}
+
+\begin{example}
+\label{eg:base-1-33}
+Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
+and that $(\sx', \halfcan',\{1,2\})$ is admissible.
+
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
+Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are both one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
+
+Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
+$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
+The details are omitted as it is analogous to Example ~\ref{ex:base-377}.
+
+We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
+We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
+Hence, (Ad-i) holds.
+We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric.
+Here, by construction
+$$
+\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
+	0 &\text{ if }z \in \{u, y_3\}\\
+	\frac{1}{4} &\text{ if }z = y_4
+\end{cases}.$$
+Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
+Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+\end{example}
+
+\begin{example}
+\label{eg:exception-1-5}
+Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$.
+Let $u \in (P_L)_1$ be any nonzero element.
+We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
+We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$.
+Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$.
+Then, we claim there is some $\alpha \in k$ so that
+$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+
+In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
+One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+The verification is analogous to Example ~\ref{ex:base-377} and is omitted.
+
+Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
+
+Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 also determines a relation in the canonical ring for $L = P - Q + \frac{3}{7}$, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
+\end{example}
 
@@
 
-Before proving Lemma ~\ref{lem:g-0-admissible-cases} in general, we check the lemma holds for case (b).
-
-\begin{example}
-\label{ex:base-377}
-Here we demonstrate, in detail, that case (b) with ($\sigma =
-(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
-satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
-We exhibit a (minimal) presentation for $R'$.
-
-Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
-\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
-
-By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
-\[
-	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor)
-\]
-
-\noindent
-is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
-Table ~\ref{table:g-0-sat}, then this map is surjective
-when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
-
-For $d = 0, 1, 2, \ldots$ we have
-\[
-	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
-
-To show that these generate all of $R'$, we need to show that all
-$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
-(taking saturation into account) to see that
-
-\begin{align*}
-	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
-	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
-	\text{ (mod } 7)
-\end{align*}
-
-\noindent
-are surjective. This reduces the problem to checking generation
-in the degrees of the exceptions $d \in \{8, 12, 21\}$.
-Checking the remaining cases via pole degrees shows that
-these degrees are also generated in lower degrees,
-so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
-
-Now, we check admissibility. By relabelling the
-variables if necessary, we can assume that $x_{7, 1}$ corresponds
-to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
-correspond to the generator with maximal pole order at $P_3$. Use
-the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
-$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-(Ad-i) of Definition ~\ref{defn:admissible}. We may also choose
-pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
-in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
-generators lying below the line as seen in Figure ~\ref{fig:377}
-(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
-(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
-and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
-$x_{7, 2}$ respectively).
-
-\begin{figure}[H]
-\label{fig:377}
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
-\end{figure}
-
-Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
-$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
-Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
-$\sigma, J$ is admissible.
-
-%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
-%represent the pole orders of $x_i$ at each point. Then these generators
-%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
-%respectively.
-
-We can directly see that the relations are given in degrees $10$
-and $14$. In particular, we have relations
-\begin{align*}
-	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
-	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
-	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
-\end{align*}
-
-\noindent
-and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
-have that
-\[
-	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
-\]
-
-\noindent
-However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
-$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
-coefficients must be zero for this equality to hold. We have a
-similar pole order consideration in forcing $b_1$ to be nonzero.
-
-Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
-$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
-ideal of $I$ is
-\[
-	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
-\]
-
-\noindent
-since $a_1$ and $b_1$ are nonzero.
-
-To demonstrate that these two relations generate all 
-relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
-all degrees $d \geq 0$. In particular,
-
-\begin{align*}
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
-\end{align*}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
-\rangle$ can be checked by looking at the $k$-basis at each degree
-$d$.
-
-Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
-initial ideal $\initial(I)$ generated by quadratics under grlex
-with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
-%These quadratics must also determine minimal generators for $I$ by
-%Lemma ~\ref{lem:minimal_quadratic}.
-Thus, $R'$ is generated up to degree $e = 7$ with relations up to
-degree $2e = 14$, as desired.
-
-%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
-%since $e_i = 9 > e$ for all $i \in J$.
-\end{example}
+Note that Example ~\ref{eg:base-377}, precisely proves case (b) of Lemma ~\ref{lem:g-0-admissible-cases}.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
add some edits/todos in Further Research

@@
 In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$
+\todo{specify that this is a single point}
 is a spin canonical divisor on a genus 2 curve, then $R_L$ has a
@@
 In particular, we make the following conjecture.
+\todo{specify that $L = P$ means it is a single point}
 \begin{conjecture}
@@
 \end{conjecture}
-Note that in the case $\dim L \geq 2$ and $L$ is basepoint-free, by Neves ~\cite[Proposition III.12]{neves:halfcan}, $I_L$ is generated in degree at most 8.
+Note that in the case that $\dim L \geq 2$ and $L$ is basepoint-free, the ideal $I_L$ is generated in degree at most 8 by Neves ~\cite[Proposition III.12]{neves:halfcan}.
 Additionally, if Conjecture ~\ref{conj:relations-10} were true, by Theorem ~\ref{thm:main} we would immediately obtain the following corollary, providing a more concise statement than that of Theorem ~\ref{thm:main}.
@@
 Suppose Conjecture ~\ref{conj:relations-10}.
-Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.
+Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions given by Table ~\ref{table:g-1-exceptional} and Table ~\ref{table:g-0-exceptional}
 \end{cor}
 	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms.
-As defined in Adler and Ramanan, immediately following \cite[Corollary 24.5]{adler:moduli}, a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$.
+As defined in Adler and Ramanan (in the passage immediately following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$.
 Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$.

### 2015-06-30 stacky_write_up/spin_cring.tex
genus zero base case transition rewrite for example

@@
 %~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in %Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
-d
 
@@
 
-There are two main cases: when $\delta \geq 2$ and when $\delta = 0$, where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}. In the first case, $\deg \lfloor \halfcan \rfloor
-\geq 0$ so the result directly follows from Lemma
-~\ref{lem:sat-1}. When $\delta = 0$, the proof is a rather involved induction using Lemma
-~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}.
-The remainder of this section is dedicated to characterizing the
-saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
-base cases (Subsection ~\ref{ssec:g_0_base}), and exceptional
+There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
+, where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}
+. In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
+result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
+0$, the proof is a rather involved induction using Lemma
+~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
+remainder of this section is dedicated to characterizing the
+saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
+base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
 cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
@@
 \begin{rem}
-Since all points are linearly equivalent on $\BP^1_k$, we may assume without loss of generality that $L_X = n \infty$ for some $n \in \BN$ and $K_X = -2 \infty.$ We will use this convention throughout this section.
+Since all points are linearly equivalent on $\BP^1_k$, we may
+assume without loss of generality that $L_X = n \infty$ for some $n
+\in \BN$ and $K_X = -2 \infty$. We will use this convention
+throughout this section.
 \end{rem}
@@
 \label{lem:g-0-admissible-cases}
-Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$ has signature $\sigma = (0; e_1,
-\ldots, e_r; 0)$. Then, $R' := R(\sx', \Delta, \halfcan')$ has a
-presentation generated as a $k$-algebra by elements of degree at most $e = \max(5
-, e_1, \ldots, e_r)$ with relations in degree at most $2e$ and $(\sx
-', \halfcan', J) =(\sx
-', -\infty + \sum_{i=1}^{r}\subhalf{e_i}P_i, J)$ is admissible for the following cases:
+Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$
+has signature $\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R(
+\sx', \Delta, \halfcan')$ has a presentation generated as a $k$-
+algebra by elements of degree at most $e = \max(5 , e_1, \ldots, e_r
+)$ with relations in degree at most $2e$ and $(\sx ', \halfcan', J)
+= (\sx ', -\infty + \sum_{i = 1}^{r} \subhalf{e_i} P_i, J)$ is
+admissible for the following cases:
 
@@
 %$\initial(I')$ is minimally generated by products of two monomials.
-
 \end{lem}
 
-Note that Example ~\ref{eg:base-377}, precisely proves case (b) of Lemma ~\ref{lem:g-0-admissible-cases}.
-
-\begin{proof}[Proof of Lemma ~\ref{lem:g-0-admissible-cases}]
-For the remaining cases, we can use a similar method to the one
-used in Example ~\ref{ex:base-377} to find a presentation the
-desired conditions.
+\begin{proof}
+Recall that Case (b) is proven in Example ~\ref{ex:base-377}. For
+the remaining cases, we can use a similar method to find a
+presentation satisfying the desired conditions.
 
@@
 they satisfy (Ad-i) and (Ad-ii) and that $\initial(I')$ is
-generated by products of two monomials. The procedure for
-verifying these are similar to those for the given example.
+generated by products of two monomials. Again, the procedure for
+verifying these are similar to that given in Example
+~\ref{ex:base-377}.
 

### 2015-06-30 stacky_write_up/spin_cring.tex
edited examples a bit

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \label{eg:base-1-0}
-In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+Let $(\sx',0,\halfcan')$ be a log stacky curve of genus $g = 1$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 \label{ex:base-377}
-Here we demonstrate, in detail, that case (b) with ($\sigma =
-(0; 3, 7, 7; 0), \halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3, J = \{3, 4\},$) with distinct points $P_i \neq \infty$,
-satisfies the conditions of Lemma ~\ref{lem:g-0-admissible-cases}.
-We exhibit a (minimal) presentation for $R'$.
+Let $(\sx,0,\halfcan')$ be a log spin curve with signature $\sigma =
+(0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
+\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are distinct points.
+In this example, we will exhibit a minimal presentation for $R' = R(\sx,0,\halfcan')$ and show the triple $(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
 
@@
 and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
-\[
+\begin{align}
+\label{eqn:noether-377}
 	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
@@
 	d \halfcan' \rfloor)
-\]
+\end{align}
 
@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. Since $\sigma$ has saturation $s = 5$, as noted in
-Table ~\ref{table:g-0-sat}, then this map is surjective
+\geq 0$. It is fairly easy to see using Riemann--Roch that $\sat(\Eff(\sigma)) = 5.$
+Then the map in ~\eqref{eqn:noether-377} is surjective
 when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
@@
 \begin{figure}[H]
-\label{fig:377}
 \includegraphics{pics/spin-377-pic-pics.pdf} \\
 \caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\label{fig:377}
 \end{figure}
@@
 \label{eg:base-1-33}
-Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+Let $(\sx',0 ,\halfcan')$ be a log spin curve of genus $1$ so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
 $$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
@@
 \label{eg:exception-1-5}
-Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$.
-Let $u \in (P_L)_1$ be any nonzero element.
+Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P - Q + \frac{2}{5}P_1.$ Let $u \in (P_L)_1$ be any nonzero element.
 We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
@@
 Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
-
-Finally, note that this particular case is also exceptional, because there is a relation in degree $12 > 2 \cdot 5$, but once $e' = 5$ is incremented to $e = e'+2 = 7,$ using Lemma ~\ref{lem:raise-stacky-order}, this relation in degree 12 also determines a relation in the canonical ring for $L = P - Q + \frac{3}{7}$, and so the case $L' = P - Q + \frac{3}{7}P_1$ is not exceptional because $12 < 2 \cdot 7$.
 \end{example}

### 2015-06-30 stacky_write_up/spin_cring.tex
theta-characteristics -> theta characteristic

@@
 $2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
-is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. We also use $\halfcan_X$ to refer to the spin canonical
-divisor (also known as the half-canonical divisor, semi-canonical
-divisor, or theta-characteristics) associated with the coarse space $X$ of $\sx$, i.e.
-$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
-Furthermore, we use the following analogous notations:
+is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
+We also use $\halfcan_X$ to refer to the spin canonical divisor
+(also known as the half-canonical divisor, semi-canonical divisor, 
+or a theta characteristic in other literature) associated with the
+coarse space $X$ of $  \sx$, i.e. $\halfcan_X$ is a divisor such
+that $2\halfcan \sim K_X$. Furthermore, we use the following
+analogous notations:
 

### 2015-06-30 stacky_write_up/spin_cring.tex
finished preliminary examples section

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 
-In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin-canonical divisors.
+In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin canonical divisors.
 
@@
 
+In this section, we compute several examples of computing presentations for spin canonical rings.
+In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}.
+In addition to demonstrating the algorithmic procedure for computing presetations, these examples will also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
+
 \begin{example}
 \label{eg:base-1-0}
-Let $(\sx',0,\halfcan')$ be a log stacky curve of genus $g = 1$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+Let $(\sx',0,L')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 Then, we claim there is some $\alpha \in k$ so that
-$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$
+
+$$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$$
 

### 2015-06-30 stacky_write_up/spin_cring.tex
new abstract, add Weil divisor to rem, add to bib

@@
 \begin{abstract}
-  Generalizing the classical theorems of Max Noether and Karl 
-	Petri, we describe generators and relations for the spin canonical
-	ring of a stacky curve equipped with an arbitrary log divisor. As
-	an application, we bound the generation degrees and relation
-	degrees for graded rings of modular forms of arbitrary integral
-	weight arising from finite-area quotients of the upper half-
-	plane by Fuchsian groups.
+  The study of rings of modular forms arising from finite-area
+	quotients of the upper-half plane by Fuchsian groups may be
+	translated to the study of canonical rings by the classical
+	results of Kodaira--Spencer. In particular, this work describes
+	generators and relations of spin canonical rings of a stacky
+	curve equipped with an arbitrary log (or effective)	divisor in a
+	generalization of the classical theorems of Max Noether	and Karl
+	Petri. As an application, these results strongly bound the
+	generator and relation degrees for the aforementioned rings
+	of modular forms of arbitrary integral weight with some insight
+	into rings of modular forms of fractional weight.
 \end{abstract}
@@
 \maketitle
-
-\todo{Peter: I don't like the first thing our reader will read to be a dependent clause}
-\todo{Comprehensive change: make sure $\subset$ and $\subseteq$ notation is standardized throughout paper}
 
@@
 of the paper, we will work in the algebraic category.
-\todo{mention that we will use the language of Weil divisors?}
 
@@
 \label{rem:stack-formalism}
-As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky
-curves may be formalized as stacks, but for the purposes of this
-paper, it suffices to treat $\sx$ as a scheme whose associated
-divisor group allows a finite number of stacky points.
+Stacky curves may be formalized in the language of stacks (e.g. as
+done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
+Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
+Behrend and Noohi \cite{behrend-noohi:uniformization}), but for the
+purposes of this paper, it suffices to treat $\sx$ as a scheme
+whose associated divisor group allows a finite number of stacky
+points. The remainder of the paper will primarily use the language
+of Weil divisors.
 \end{rem}

### 2015-07-01 stacky_write_up/spin_cring.tex
trying to find reference

--- 2015-06-30 stacky_write_up/spin_cring.tex
@@
 \label{rem:relations_generation_ten}
-In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$
-\todo{specify that this is a single point}
-is a spin canonical divisor on a genus 2 curve, then $R_L$ has a
+Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_L$ has a
 relation in degree 10. Therefore, the bound from Proposition
@@
 \begin{enumerate}
-	\item In the case $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of a log spin canonical ring $R_L$.
-Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with spin canonical divisor $L = P$ has spin canonical ring $R_L$ with relations in degree 10.
+	\item In the case that $(\sx,\Delta, \halfcan')$ is log spin curve of genus $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of the log spin canonical ring $R_L$.
+Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with spin canonical divisor $L = P,$ for $P$ a closed point of $X,$  $R_L$ with relations in degree 10.
 This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$.

### 2015-07-01 stacky_write_up/spin_cring.tex
acknowledged neves
some minor todos removed

@@
 research.
-\todo{Add examples section.}
 
@@
 \lfloor \alpha_i \rfloor P_i$.
-\todo{cite lemma 5.4.7 from VZB maybe?}
 \end{defn}
@@
 Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a).
-\todo{Ask David, Understand why/whether we need to cite Lemma 5.4.7.
-we don't just say it at the beginning}
 
@@
 elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P^{\halfcan'}(y_i) =
-1$. \todo{Understand why/whether we need to cite 
-Lemma 5.4.7.  Peter: What does this mean?}  We see by pole order considerations that
+1$. We see by pole order considerations that
 
@@
 Number Theory REU for arranging our project and providing a great
-environment for mathematical learning and collaboration. Finally, we
+environment for mathematical learning and collaboration.
+We thank Jorge Sentieiro Neves help pointing out Reid's bound on the maximal degrees of minimal generators and relations of spin canonical rings.
+Finally, we
 gratefully acknowledge that our research was financially supported by

### 2015-07-01 stacky_write_up/spin_cring.tex
more edits to admissibility lemma

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+\todo{Peter: be clear what $z$ is}
 
@@
 \end{align}
+\todo{Peter: I understand why this should be true, although its not clear to me that there it easily follows.  Maybe we should explain it a little as to not confuse the reader.}
 
@@
 
+\todo{Peter: be clear with this that we aren't checking $y_{i,e_i}z\in R'$ for various cases, but rather are checking that equation 4.6 is met in various cases, giving $y_{i,e_i}z\in R'$ for a specific fixed $i$.
+}
 \vskip.1in
@@
 \begin{align*}
-	e_i	= e_i' \text{ if }i \notin J \\
-	& e_i \leq e_i' &\text{ if } i \in J
+	& e_i	= e_i' &\text{ if }i \notin J \\
+	& e_i \ge e_i' &\text{ if } i \in J
 \end{align*}
@@
 e_{i-1}, e_i, e_i, \ldots, e_i; \delta).$ Let
-$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, J)$.
+$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, \{r\})$.
 

### 2015-07-01 stacky_write_up/spin_cring.tex
merged
update main thm, further ref, add reid to bib

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 Then the log spin canonical ring is generated as a $k$-algebra by 
-elements of degree at most $e = \max(5, e_1, \ldots, e_r).$ If the 
-genus $g \geq 2,$ and $\Delta = 0$ then $R(\sx, \Delta, \halfcan)$
-has relations generated in degrees up to $\max(11, 2e_1, \ldots,
-2e_r)$. Otherwise, $R(\sx, \Delta, \halfcan)$ has relations
-generated in degrees up to $\max(10, 2e_1, \ldots, 2e_r),$ so long
-as $\sigma$ does not lie in a finite list of exceptional cases, as
-listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
-= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
-0$.
+elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
+relations generated in degrees up to $\max(10, 2e_1, \ldots, 2e_r)$
+so long as $\sigma$ does not lie in a finite list of exceptional
+cases, as listed in Table ~\ref{table:g-1-exceptional} for
+signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
+signatures with $g = 0$.
 \end{thm}
@@
 
-\begin{lem}\label{lem:relations_from_generators_induction} 
+\begin{lem}
+\label{lem:relations_from_generators_induction} 
 Suppose $\halfcan, \halfcan' \in \BQ \otimes \di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
@@
 \ssec{Bounds on Generators and Relations in High Genus}
-
-The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $11$ if $\Delta = 0$ and at most $10$ if $\Delta > 0$.
+The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
 The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relation_11}.
@@
 The proofs of these results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}, although ~\cite[Proposition III.4]{neves:halfcan} has a key ommission, as noted in Remark ~\ref{rem:neves-omission}
+
+Reid \cite{reid:infinitesimal}
+\todo{update section to use Reid's paper}
 
@@
 \begin{lem}
-\label{lem:reducing_degree}
+\label{lem:reducing-degree}
 Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$.
@@
 To complete the proof, it suffices to show $f \in I_{L,d}'$.
-By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subseteq H^0(K)$ is basepoint free.
+By Lemma ~\ref{lem:reducing-degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subseteq H^0(K)$ is basepoint free.
 Consider the map
@@
 
-We are finally ready to prove our main theorem ~\ref{thm:main} in the case $g \geq 2$.
+We are ready to prove our main theorem ~\ref{thm:main} in the case $g \geq 2$.
 The idea of the proof is to use Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11} to complete the base case when $L = L_X$ and then apply Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:raise-stacky-order} to complete the induction step.
@@
 that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
-canonical ring
+log spin canonical ring
 
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r).$ If $\Delta = 0,$ then 
+\max(5, e_1, \ldots, e_r)$. If $\Delta = 0,$ then 
 $R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
@@
 \end{thm}
+
+%is generated as a $k$-algebra by elements of degree at most $e =
+%\max(5, e_1, \ldots, e_r)$ with relations in degree up to $2e$.
+%
+%Furthermore, there are even stronger bounds for the following
+%exceptional cases (X, :
 
@@
 Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
-If $g = 1$, then the canonical ring
+If $g = 1$, then the log spin canonical ring
 \begin{align*}
@@
 so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
-Then, the canonical ring
+Then, the log spin canonical ring
 
@@
 \begin{enumerate}
-	\item In the case that $(\sx,\Delta, \halfcan')$ is log spin curve of genus $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of the log spin canonical ring $R_L$.
-Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with spin canonical divisor $L = P,$ for $P$ a closed point of $X,$  $R_L$ with relations in degree 10.
-This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$.
-In particular, we make the following conjecture.
-\todo{specify that $L = P$ means it is a single point}
-\begin{conjecture}
-\label{conj:relations-10}
-If $X$ is a curve of genus $g \geq 2$ and $L \in \di X$ with $2L \sim K,$ the ideal of relations in $R_L$ is generated in degree at most $10$.
-More precisely, if $x_1,\ldots, x_n$ is a minimal set of generators for $R_L$ and $\phi:k[y_1,\ldots, y_n] \rightarrow R_L, y_i \mapsto x_i,$ then $I_L := \ker \phi$, is generated in degree at most 10.
-\end{conjecture}
-Note that in the case that $\dim L \geq 2$ and $L$ is basepoint-free, the ideal $I_L$ is generated in degree at most 8 by Neves ~\cite[Proposition III.12]{neves:halfcan}.
-Additionally, if Conjecture ~\ref{conj:relations-10} were true, by Theorem ~\ref{thm:main} we would immediately obtain the following corollary, providing a more concise statement than that of Theorem ~\ref{thm:main}.
-\begin{cor}
-\label{cor:main-refined}
-Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring.
-Suppose Conjecture ~\ref{conj:relations-10}.
-Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions given by Table ~\ref{table:g-1-exceptional} and Table ~\ref{table:g-0-exceptional}
-\end{cor}
 	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms.
@@
 Number Theory REU for arranging our project and providing a great
-environment for mathematical learning and collaboration.
-We thank Jorge Sentieiro Neves help pointing out Reid's bound on the maximal degrees of minimal generators and relations of spin canonical rings.
-Finally, we
-gratefully acknowledge that our research was financially supported by
-NSF Grant Award Number 1250467 via the Emory University Number Theory REU.
-We deeply appreciate all of the support that has made our work possible.
+environment for mathematical learning and collaboration. We thank
+Jorge Sentieiro Neves help pointing out Reid's bound on the maximal
+degrees of minimal generators and relations of spin canonical rings
+in high genera. Finally, we gratefully acknowledge that our
+research was financially supported by NSF Grant Award Number 1250467
+via the Emory University Number Theory REU. We deeply appreciate
+all of the support that has made our work possible
 

### 2015-07-01 stacky_write_up/spin_cring.tex
edited genus 2 to reflect reid

@@
 \ssec{Bounds on Generators and Relations in High Genus}
+\todo{Make edits that you want to further incorporate Reid's paper}
+
 The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
-The generation bound is shown in Lemma ~\ref{lem:generation_5} and the relations bound is shown in Lemma ~\ref{prop:relation_11}.
-
-The proofs of these results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}, although ~\cite[Proposition III.4]{neves:halfcan} has a key ommission, as noted in Remark ~\ref{rem:neves-omission}
-
-Reid \cite{reid:infinitesimal}
-\todo{update section to use Reid's paper}
-
+The case that $\Delta = 0$ was completed in Reid \todo{cite Ried article}.
+The generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
+We summarize the result in Corollary ~\ref{cor:g-2-presentation-bound}
+
+The proofs of these results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}, but slightly generalized as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
+
+\iffalse
 \begin{lem}
-\label{lem:generation_5}
+\label{lem:generation-5}
 Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
@@
 
-The strategy of the proof of Lemma ~\ref{lem:generation_5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_L$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
+The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_L$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
 When $g > 3$, it is easy to reduce the bound from 5 to 6.
 The trickiest case is to show $R_L$ is generated in degree 5 when $g = 2$, which is done in Lemma ~\ref{lem:genus-2-generation-5}.
-After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation_5}.
+After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation-5}.
+\fi
 
 \begin{lem}
-\label{lem:semicanonical_generation}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K + \Delta$.
-Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint free.
+\label{lem:generation-5}
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$ and $\Delta > 0.$ Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint free.
 Then, the map
@@
 \end{align*}
-is surjective if $n \geq 5$ and if {\rm(}$n = 4$ and $\Delta > 0${\rm)}.
-In particular, $R_L$ is generated in degree at most $6$ if $\Delta = 0$ and in degree at most $5$ if $\Delta > 0$.
+is surjective if $n \geq 5.$ In particular, $R_L$ is generated in degree at most $5.$
 \end{lem}
 
+\iffalse
 \begin{rem}
@@
 The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}.
-However, Neves states that this proof also proves Lemma ~\ref{lem:generation_5}, while it crucially omits the case of genus 2 curves.
+However, Neves states that this proof also proves Lemma ~\ref{lem:generation-5}, while it crucially omits the case of genus 2 curves.
 We produce the proof here for completeness.
 \end{rem}
-
-\begin{proof}[Proof of Lemma ~\ref{lem:semicanonical_generation}]
+\fi
+
+\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
 To show there are no new generators in degree at least $7$ if $\Delta = 0$ and in degree at least $6$ if $\Delta > 0$, it suffices to show that if $n \geq 5$ or if ($n = 4$ and $\Delta > 0$), the map
@@
 
+\iffalse
 \begin{lem}
@@
 \end{proof}
-
-We are now equipped to prove Lemma ~\ref{lem:generation_5}, completing the desired bound on the degree of the generators.
-
-\begin{proof}[Proof of Lemma ~\ref{lem:generation_5}]
+\fi
+
+\iffalse
+We are now equipped to prove Lemma ~\ref{lem:generation-5}, completing the desired bound on the degree of the generators.
+
+\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
 If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
@@
 \end{proof}
+\fi
 
 The next step is to bound the degrees of the relations of $R_L$.
-This is done in Proposition ~\ref{prop:relation_11}.
-The idea of the proof of Proposition ~\ref{prop:relation_11} is to use the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
+This is done in Proposition ~\ref{prop:relation-10}.
+The idea of the proof of Proposition ~\ref{prop:relation-10} is to use the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
 We now fix notation for this ideal generated by lower degrees relations.
@@
 \label{defn:lower-ideal}
-Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$.
-Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
 Let $I_{L, d}$ be the $d$th graded piece of $I_L$ and define
@@
 \label{lem:reducing-degree}
-Suppose $X$ is a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K+\Delta$.
-Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
+Let $(X, \Delta, L)$ be a log spin curve of genus $g \geq 2,$ so that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
 Let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subseteq H^0(X,2L)$ is basepoint free.
-For any $f \in k[x_1, \ldots, x_n]$ such that
-$$
-\deg f \geq \begin{cases}
-	12 &\text{ if }\Delta = 0\\
-	11 &\text{ if }\Delta > 0
-\end{cases}$$
+For any $f \in k[x_1, \ldots, x_n]$ such that $\deg f \leq 11,$
 there exist $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
@@
 % Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
-By Lemma ~\ref{lem:generation_5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
+By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
 We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
-By Lemma ~\ref{lem:semicanonical_generation},
+By Lemma ~\ref{lem:generation-5},
 \begin{align*}
@@
 \end{align*}
-is surjective, since the restriction on $\deg f$ guarantees
-$$
-\deg f- \deg a_i -2 \geq \begin{cases}
-	5 &\text{ if }\Delta = 0,\\
-	4 &\text{ if }\Delta > 0.
-\end{cases}$$
+is surjective, and $\deg f \leq 11$ guarantees
+$\deg f- \deg a_i -2 \geq 4.$
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
@@
 \begin{prop}
-\label{prop:relation_11}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K + \Delta$. Then $I_L$ is generated in degree at most $11$ if $\Delta = 0$ and degree at most $10$ if $\Delta > 0$.
+\label{prop:relation-10}
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$ and $\Delta > 0.$ Then $I_L$ is generated in degree at most degree at most $10.$
 \end{prop}
 \begin{proof}
-Suppose $f \in I_L$ with 
-$$
-\deg f \geq \begin{cases}
-	12 &\text{ if }\Delta = 0\\
-	11 &\text{ if }\Delta > 0.
-\end{cases}$$
+Suppose $f \in I_L$ with $\deg f \geq 11$.
 To complete the proof, it suffices to show $f \in I_{L,d}'$.
@@
 relation in degree 10. Therefore, the bound from Proposition
-~\ref{prop:relation_11}, that $I_L$ is generated in degree at most
+~\ref{prop:relation-10}, that $I_L$ is generated in degree at most
 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
@@
 \end{rem}
+\fi
+
+We now concisely summarize what we have shown.
+
+\begin{cor}
+\label{cor:g-2-presentation-bound}
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$. Then $X$ has minimal generators in degree at most 5 and minimal relations in degree at most 10.
+\end{cor}
+\begin{proof}
+If $\Delta =0$, the result is immediate from Reid \todo{cite Reid}.
+Otherwise, if $\Delta > 0$, the bound on the degrees of minimal generators follows from Lemma ~\ref{lem:generation-5}, while the bound on the degrees of minimal relations follows from Proposition ~\ref{prop:relation-10}.
+\end{proof}
 
@@
 We are ready to prove our main theorem ~\ref{thm:main} in the case $g \geq 2$.
-The idea of the proof is to use Lemma ~\ref{lem:generation_5} and Proposition ~\ref{prop:relation_11} to complete the base case when $L = L_X$ and then apply Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:raise-stacky-order} to complete the induction step.
+The idea of the proof is to use Lemma ~\ref{lem:generation-5} and Proposition ~\ref{prop:relation-10} to complete the base case when $L = L_X$ and then apply Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:raise-stacky-order} to complete the induction step.
 
@@
 is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r)$. If $\Delta = 0,$ then 
-$R(\sx,\Delta, \halfcan)$ has minimal relations in degree at most $\max(11, 2e_1,
-\ldots, 2e_r).$ Otherwise, $R(\sx, \Delta, \halfcan)$ has minimal relations in degree at most
-$\max(10, 2e_1, \ldots, 2e_r).$
+\max(5, e_1, \ldots, e_r)$ with minimal relations in degree at most $2e$.
 \end{thm}
@@
 
-By Lemma ~\ref{lem:generation_5} and Proposition
-~\ref{prop:relation_11}, the theorem holds for $(\sx, \Delta,
+By Corollary ~\ref{cor:g-2-presentation-bound}, the theorem holds for $(\sx, \Delta,
 \halfcan_X)$. Next, consider a divisor of the form $\halfcan' =

### 2015-07-01 stacky_write_up/spin_cring.tex
edited revised genus 2

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 The case that $\Delta = 0$ was completed in Reid \todo{cite Ried article}.
-The generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-We summarize the result in Corollary ~\ref{cor:g-2-presentation-bound}
-
-The proofs of these results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}, but slightly generalized as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
+For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
+Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ and so $H^0(X, 2L)$ is basepoint free by Riemann-Roch.
+We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
+
+The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
+However, the statements are different, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
 
@@
 \end{align*}
-is surjective if $n \geq 5.$ In particular, $R_L$ is generated in degree at most $5.$
+is surjective if $n \geq 4.$ In particular, $R_L$ is generated in degree at most $5.$
 \end{lem}
@@
 \begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
-To show there are no new generators in degree at least $7$ if $\Delta = 0$ and in degree at least $6$ if $\Delta > 0$, it suffices to show that if $n \geq 5$ or if ($n = 4$ and $\Delta > 0$), the map
+To show there are no new generators in degree at least $6$, it suffices to show that if $n \geq 4$, the map
 \begin{align*}
@@
 We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 5$ or ($n = 4$ and $\Delta > 0$).
-Note that here we are implicitly using the Remark ~\ref{rem:delta-not-1}.
+Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 4.$
 Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
-Therefore, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L),$$
-again using Riemann-Roch. Ergo, $f$ is surjective.
+By rank-nullity, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L).$$
+Ergo, $f$ is surjective.
 \end{proof}
@@
 
-The next step is to bound the degrees of the relations of $R_L$.
+The next step is to bound the degrees of the relations of $R_L$ when $\Delta > 0$.
 This is done in Proposition ~\ref{prop:relation-10}.
@@
 
-Finally, we may then take $g = \sum_{i}^{}g_i x_i,h = \sum_{i}^{}h_i x_i,$ so that 
+Finally, we may then take $g = \sum_{i}^{}g_i x_i, \: h = \sum_{i}^{}h_i x_i,$ so that 
 \begin{align*}
@@
 we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
-So, by the explicit isomorphism given in the proof of the basepoint-free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
+So, by the explicit isomorphism given in the proof of the basepoint-free pencil trick, as shown in the proof of \cite[Lemma 2.6]{saint-donat:proj}, there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
 Hence,

### 2015-07-01 stacky_write_up/spin_cring.tex
comments on abstract

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 \maketitle
+
+\todo{Peter ``the study of'' is used twice in the first sentence.  Can we find a way to replace one of them?}
+
+\todo{Peter: I don't like the use of ``In particular, this work..."  Can we say something like ``This paper ..."}
+
+\todo{Peter: I don't understand the purpose of the parenthetical ``(or effective).''  What is it trying to say?}
+
+\todo{Peter: I don't like the use of the word ``strongly'' in the third sentence; these sort of adjectives are ambiguous and subjective, and don't add any real content to the statement}
+
+\todo{Peter: Get rid of comment about fractional weight modular forms.  This does not appear anywhere except in further questions, and does not deserve a spot in the abstract.}
 

### 2015-07-01 stacky_write_up/spin_cring.tex
address abstract todos

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 	quotients of the upper-half plane by Fuchsian groups may be
-	translated to the study of canonical rings by the classical
-	results of Kodaira--Spencer. In particular, this work describes
+	translated to (log spin) canonical rings by the classical
+	results of Kodaira--Spencer. This work describes
 	generators and relations of spin canonical rings of a stacky
-	curve equipped with an arbitrary log (or effective)	divisor in a
+	curve equipped with an arbitrary log	divisor in a
 	generalization of the classical theorems of Max Noether	and Karl
-	Petri. As an application, these results strongly bound the
+	Petri. As an application, these results tightly bound the
 	generator and relation degrees for the aforementioned rings
-	of modular forms of arbitrary integral weight with some insight
-	into rings of modular forms of fractional weight.
+	of modular forms of arbitrary integral weight.
 \end{abstract}

### 2015-07-01 stacky_write_up/spin_cring.tex
cite Reid, fi->%, bpt free->bpt-free, ackn. edits

@@
 Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is
-well known that the canonical sheaf $\Omega _X,$ with associated canonical divisor $K_X$
- determines the {\bf canonical map } $\pi:X \rightarrow \BP_k^{g - 1}$.
-Then, the {\bf canonical ring} is defined to be
+well known that the canonical sheaf $\Omega _X,$ with associated
+canonical divisor $K_X$  determines the {\bf canonical map } $\pi:
+X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical ring} is
+defined to be
 \begin{align*}
@@
 The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
-The case that $\Delta = 0$ was completed in Reid \todo{cite Ried article}.
+The case that $\Delta = 0$ was completed by Reid \cite[p.
+35]{reid:infinitesimal}.
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
@@
 
-\iffalse
-\begin{lem}
-\label{lem:generation-5}
-Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
-\end{lem}
-
-The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_L$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
+%\begin{lem}
+%\label{lem:generation-5}
+%Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
+%\end{lem}
+%
+%The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_L$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
 When $g > 3$, it is easy to reduce the bound from 5 to 6.
@@
 After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation-5}.
-\fi
 
@@
 
-\iffalse
-\begin{rem}
-\label{rem:neves-omission}
-The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}.
+%\begin{rem}
+%\label{rem:neves-omission}
+%The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}.
 However, Neves states that this proof also proves Lemma ~\ref{lem:generation-5}, while it crucially omits the case of genus 2 curves.
 We produce the proof here for completeness.
-\end{rem}
-\fi
-
-\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
+%\end{rem}
+
+\begin{proof}
 To show there are no new generators in degree at least $6$, it suffices to show that if $n \geq 4$, the map
@@
 is surjective.
-Indeed, since $V= ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
+Indeed, since $V= ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint-free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
 $$\begin{tikzcd}
@@
 
-\iffalse
-\begin{lem}
-\label{lem:genus-2-generation-5}
-Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
-Then, $R_L$ is generated in degree at most $5$.
-\end{lem}
-\begin{proof}
-By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_L$ has no minimal generators in degree 6.
-Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
-Recall that all linear equivalence classes of spin divisors on $X$ have a representative of the form
-$$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
-with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
+%\begin{lem}
+%\label{lem:genus-2-generation-5}
+%Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
+%Then, $R_L$ is generated in degree at most $5$.
+%\end{lem}
+%\begin{proof}
+%By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_L$ has no minimal generators in degree 6.
+%Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
+%Recall that all linear equivalence classes of spin divisors on $X$ have a representative of the form
+%$$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
+%with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
 \todo{cite this somewhere, maybe ask david for a place to cite?
@@
 Don't use coarse notes}
-Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
+%Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
 Therefore, the image of the multiplication map
-\begin{align*}
-	Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
-\end{align*}
-is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
-which have 
-\begin{align*}
-	\di u^3|_{2L} &= -2L \\
-	\di u^2x|_{2L} &= -2L + 2P_1 \\
-	\di ux^2|_{2L} &= -2L+4P_1, \\
-	\di x^3|_{2L} &= -2L + 6P_1.
-\end{align*}
-
-\noindent
-Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
-it suffices to produce one more independent function in the image of the multiplication map.
-There are now two cases, depending on whether $H^0(X,L) = 0$.
-
-First, we deal with the case that $H^0(X,L) \neq 0$. 
-Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
+%\begin{align*}
+	%Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
+%\end{align*}
+%is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
+%which have 
+%\begin{align*}
+	%\di u^3|_{2L} &= -2L \\
+	%\di u^2x|_{2L} &= -2L + 2P_1 \\
+	%\di ux^2|_{2L} &= -2L+4P_1, \\
+	%\di x^3|_{2L} &= -2L + 6P_1.
+%\end{align*}
+%
+%\noindent
+%Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
+%it suffices to produce one more independent function in the image of the multiplication map.
+%There are now two cases, depending on whether $H^0(X,L) = 0$.
+%
+%First, we deal with the case that $H^0(X,L) \neq 0$. 
+%Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
 Hence, we know $L$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
 In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
-
-Second, suppose $H^0(X,L) = 0$.
-Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
-Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
-with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
-exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
-Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
-order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
-\end{proof}
-\fi
-
-\iffalse
-We are now equipped to prove Lemma ~\ref{lem:generation-5}, completing the desired bound on the degree of the generators.
-
-\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
-If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
-Lemma ~\ref{lem:genus-2-generation-5}.
+%
+%Second, suppose $H^0(X,L) = 0$.
+%Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
+%Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
+%we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
+%with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
+%exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
+%Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
+%order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
+%\end{proof}
+
+%We are now equipped to prove Lemma ~\ref{lem:generation-5}, completing the desired bound on the degree of the generators.
+%
+%\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
+%If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
+%Lemma ~\ref{lem:genus-2-generation-5}.
 Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$.
@@
 Hence, $R_L$ is generated in degree at most 5.
-\end{proof}
-\fi
+%\end{proof}
 
@@
 To complete the proof, it suffices to show $f \in I_{L,d}'$.
-By Lemma ~\ref{lem:reducing-degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subseteq H^0(K)$ is basepoint free.
+By Lemma ~\ref{lem:reducing-degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subseteq H^0(K)$ is basepoint-free.
 Consider the map
@@
 \label{cor:g-2-presentation-bound}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$. Then $X$ has minimal generators in degree at most 5 and minimal relations in degree at most 10.
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$
+with $g \geq 2$. Then $X$ has minimal generators in degree at most
+$5$ and minimal relations in degree at most $10$.
 \end{cor}
+
 \begin{proof}
-If $\Delta =0$, the result is immediate from Reid \todo{cite Reid}.
-Otherwise, if $\Delta > 0$, the bound on the degrees of minimal generators follows from Lemma ~\ref{lem:generation-5}, while the bound on the degrees of minimal relations follows from Proposition ~\ref{prop:relation-10}.
+If $\Delta =0$, the result is immediate from Reid. Otherwise, if
+$\Delta > 0$, the bound on the degrees of minimal generators follows
+from Lemma ~\ref{lem:generation-5}, while the bound on the degrees
+of minimal relations follows from Proposition ~\ref{prop:relation-10}.
 \end{proof}
@@
 
-We are ready to prove our main theorem ~\ref{thm:main} in the case $g \geq 2$.
-The idea of the proof is to use Lemma ~\ref{lem:generation-5} and Proposition ~\ref{prop:relation-10} to complete the base case when $L = L_X$ and then apply Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:raise-stacky-order} to complete the induction step.
+We are ready to prove our main theorem ~\ref{thm:main} in the case
+$g \geq 2$. The idea of the proof is to use Lemma
+~\ref{lem:generation-5} and Proposition ~\ref{prop:relation-10} to 
+complete the base case when $L = L_X$ and then apply Lemma
+~\ref{lem:sat-1}, Lemma ~\ref{lem:sat-2}, and Lemma
+~\ref{lem:raise-stacky-order} to complete the induction step.
 
@@
 field of study, providing incredibly helpful guidance, and being an
-excellent project mentor. We also thank Ken Ono and the Emory University
-Number Theory REU for arranging our project and providing a great
-environment for mathematical learning and collaboration. We thank
-Jorge Sentieiro Neves help pointing out Reid's bound on the maximal
-degrees of minimal generators and relations of spin canonical rings
-in high genera. Finally, we gratefully acknowledge that our
-research was financially supported by NSF Grant Award Number 1250467
-via the Emory University Number Theory REU. We deeply appreciate
-all of the support that has made our work possible
+excellent project mentor. We also thank Ken Ono and the Emory 
+University Number Theory REU for arranging our project and 
+providing a great environment for mathematical learning and 
+collaboration. We thank Jorge Sentieiro Neves for pointing out the
+bound given by Reid's work on the maximal degrees of minimal
+generators and relations of spin canonical rings in high genera.
+Finally, we gratefully acknowledge that our research was
+financially supported by NSF Grant Award Number 1250467 via the
+Emory University Number Theory REU. We deeply appreciate all of the
+support that has made our work possible.
 

### 2015-07-01 stacky_write_up/spin_cring.tex
add further question about reducing (5,10) to (4,8)

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 
-\ssec{Bounds on Generators and Relations in High Genus}
+\ssec{Bounds on Generators and Relations in High Genus}\label{ssec:bounds-high-genus}
 \todo{Make edits that you want to further incorporate Reid's paper}
@@
 The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
-The case that $\Delta = 0$ was completed in Reid \todo{cite Ried article}.
+The case that $\Delta = 0$ was completed in Reid ~\cite[Theorem 3.4]{reid:infinitesimal}\todo{cite Ried article}.
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
@@
 \begin{enumerate}
-	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms.
+	\item One direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms.
 As defined in Adler and Ramanan (in the passage immediately following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$.
@@
 Given suitable generalizations of these lemmas, one may be able to approach the problem of finding generators and relations for fractional weight modular forms using techniques similar to those in this paper.
+%
 	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense.
@@
 \end{question}
+%
 	\item As noted in Remark ~\ref{rem:explicit-generators}, the proof of Theorem ~\ref{thm:main} given in this paper gives an explicit procedure for computing the generators and relations of $R_L$ when the genus of $\sx$ is $0$ or $1$.
@@
 In particular, if Question ~\ref{ques:spin-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
+%
+	\item In Subsection \ref{ssec:bounds-high-genus}, we reference the work of Reid \cite{reid:infinitesimal}.
+We use his construction of a uniform bound on the generation of the half-canonical ring and its ideal of relations at 5 and 10 in the non-log, non-stacky case when genus is at least 2.
+We extend this bound of 5 and 10 to the log case, and then apply our inductive lemmas to add stacky points and get bounds of $\max(5,e)$ and $\max(10, 2e)$.
+Reid in fact proves something slightly stronger: that in most cases his bound is actually 3 and 6 with well-characterized exceptions.
+\begin{question}\label{ques:reduce-5,10-to-4,8}
+Can we reduce the bounds in Theorem \ref{thm:main} on generation from $\max(5,e)$ and $\max(10, 2e)$ to $\max(4,e)$ and $\max(8, 2e)$. 
+\end{question}
+\begin{rem}\label{rem:reduce-3,6}
+It is unlikely that this can be reduced further, because Lemma \ref{lem:sat-2}, which allows us to add a stacky point in genus $g>0$ saturated at 2, requires a generator in degree 4 and potentially a relation in degree 8, even when inductively adding on stacky points of stabilizer order 3.
+\end{rem}
+%
 	\todo{This last one doesn't seem particularly interesting. Should we remove it?}

### 2015-07-01 stacky_write_up/spin_cring.tex

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 In particular, if Question ~\ref{ques:spin-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
+%
+	\item In Subsection \ref{ssec:bounds-high-genus}, we reference the work of Reid \cite[p. 35]{reid:infinitesimal}.
+We use his construction of a uniform bound on the generation of the half-canonical ring and its ideal of relations at 5 and 10 in the non-log, non-stacky case when genus is at least 2.
+We extend this bound of 5 and 10 to the log case, and then apply our inductive lemmas to add stacky points and get bounds of $\max(5,e)$ and $\max(10, 2e)$.
+Reid in fact proves something slightly stronger: that in most cases his bound is actually 3 and 6 with well-characterized exceptions.
+\begin{question}\label{ques:reduce-5,10-to-4,8}
+Can we reduce the bounds in Theorem \ref{thm:main} on generation from $\max(5,e)$ and $\max(10, 2e)$ to $\max(4,e)$ and $\max(8, 2e)$. 
+\end{question}
+\begin{rem}\label{rem:reduce-3,6}
+It is unlikely that this can be reduced further, because Lemma \ref{lem:sat-2}, which allows us to add a stacky point in genus $g>0$ saturated at 2, requires a generator in degree 4 and potentially a relation in degree 8, even when inductively adding on stacky points of stabilizer order 3.
+\end{rem}
+%
 	\todo{This last one doesn't seem particularly interesting. Should we remove it?}

### 2015-07-01 stacky_write_up/spin_cring.tex
indent & linebreak further research

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 \ssec{Bounds on Generators and Relations in High Genus}
+\label{ssec:bounds-high-genus}
 \todo{Make edits that you want to further incorporate Reid's paper}
@@
 \begin{enumerate}
-	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms.
-As defined in Adler and Ramanan (in the passage immediately following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$.
-Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$.
-Fractional modular forms also make an apperance in Milnor \cite[$\mathsection$ 6]{milnor:fractional-weight}.
-In this work, Milnor shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3^{e_3} = 0$.
+	\item One direction for further research is to 
+		extend the results of this paper to divisors $D \in \di \sx$ on a 
+		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
+		divisors would translate to rings of fractional weight modular 
+		forms. As defined in Adler and Ramanan (in the passage immediately 
+		following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form 
+		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
+		line bundle $\eta$ so that there exists a line bundle $\gamma$ with 
+		$\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^
+		1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an 
+		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
+		Fractional modular forms also make an apperance in Milnor \cite[$
+		\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
+		shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e
+		_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of 
+		fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3
+		^{e_3} = 0$.
 
@@
 		\label{ques:fractional-weight}
-If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ where $K$ is the canonical divisor of $\sx$, can one bound the degrees of generators and relations of $R_D$?
+			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ 
+			where $K$ is the canonical divisor of $\sx$, can one bound the 
+			degrees of generators and relations of $R_D$?
 		\end{question}
-Note that that the above question is answered affirmatively in the case that $\sx$ has genus $0$ and $D$ is effective, as follows by inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature $(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most $2e$.
-Additionally, it may be possible to modify the proof of Lemma ~\ref{lem:raise-stacky-order} to extend to the setting of fractional weight modular forms.
-Given suitable generalizations of these lemmas, one may be able to approach the problem of finding generators and relations for fractional weight modular forms using techniques similar to those in this paper.
-	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense.
-The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner.
-In particular, Lemma ~\ref{lem:raise-stacky-order} constructs generators with non-maximal pole orders at certain points, making the relations non-generic.
+		Note that that the above question is answered affirmatively in the 
+		case that $\sx$ has genus $0$ and $D$ is effective, as follows by 
+		inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature 
+		$(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
+		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
+		$2e$. Additionally, it may be possible to modify the proof of Lemma
+		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
+		weight modular forms. Given suitable generalizations of these 
+		lemmas, one may be able to approach the problem of finding 
+		generators and relations for fractional weight modular forms using 
+		techniques similar to those in this paper.
+
+	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky},
+		the notion of a generic initial ideal is defined, which 
+		encapsulates the idea of whether the relations for $R_L$ are 
+		generically chosen, in a precise sense. The proof of Theorem
+		~\ref{thm:main} decidedly does not yield a generic initial ideal, 
+		as generators and relations are constructed in a highly nongeneric 
+		manner. In particular, Lemma ~\ref{lem:raise-stacky-order} 
+		constructs generators with non-maximal pole orders at certain 
+		points, making the relations non-generic. 
 		\begin{question}
 		\label{ques:generic-initial}
-If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$, does there exist a function $\sigma \mapsto d(\sigma)$ so that the generic initial ideal {\rm(} with some specified ordering{\rm)} is generated in degree at most $d(\sigma)$?
-Can one write down the generic initial ideal explicitly?
+			If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$,
+			does there exist a function $\sigma \mapsto d(\sigma)$ so that
+			the generic initial ideal {\rm(} with some specified ordering{\rm)}
+			is generated in degree at most $d(\sigma)$? Can one write down the
+			generic initial ideal explicitly?
 		\end{question}
-	\item As noted in Remark ~\ref{rem:explicit-generators}, the proof of Theorem ~\ref{thm:main} given in this paper gives an explicit procedure for computing the generators and relations of $R_L$ when the genus of $\sx$ is $0$ or $1$.
+
+	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
+		proof of Theorem ~\ref{thm:main} given in this paper gives an 
+		explicit procedure for computing the generators and relations of $R_
+		L$ when the genus of $\sx$ is $0$ or $1$.
 		\begin{question}
 		\label{ques:algorithm}
-Can one give an algorithm for explicitly computing the generators and relations for an arbitrary genus $g \geq 2$ curve?
+			Can one give an algorithm for explicitly computing the generators 
+			and relations for an arbitrary genus $g \geq 2$ curve?
 		\end{question}
-Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor of $X$.
-In this case our proof of Theorem ~\ref{thm:main} yields an algorithm for determining the generators of $L$.
-This raises the following Petri-like question:
+		Suppose the generators and relations of $R_{L_X}$ are known, 
+		where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the 
+		coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor 
+		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
+		algorithm for determining the generators of $L$. This raises the 
+		following Petri-like question:
 		\begin{question}
 		\label{ques:spin-canonical-petri}
-Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$?
-If so, can one give the generic ideal of $R_L$ or the generic initial ideal of $R_L$, as defined in Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}?
+			Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical 
+			divisor $L \in \di X$, can one write down a set of minimal 
+			generators and minimal relations for $R_L$? If so, can one give the 
+			generic ideal of $R_L$ or the generic initial ideal of $R_L$, as 
+			defined in Voight and Zureick Brown \cite[Definition 2.2.7]
+			{vzb:stacky}?
 		\end{question}
-In particular, if Question ~\ref{ques:spin-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
+		In particular, if Question ~\ref{ques:spin-canonical-petri} were 
+		answered affirmatively one would be able to write down explicit 
+		generators and relations for $R_L$ on a stacky curve, essentially 
+		by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
+
+	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
+		the work of Reid \cite[p. 35]{reid:infinitesimal}. We use his 
+		construction of a uniform bound on the generation of the half-
+		canonical ring and its ideal of relations at 5 and 10 in the non-
+		log, non-stacky case when genus is at least 2.  We extend this 
+		bound of 5 and 10 to the log case, and then apply our inductive 
+		lemmas to add stacky points and get bounds of $\max(5,e)$ and $\max(
+		10, 2e)$.  Reid in fact proves something slightly stronger: that in 
+		most cases his bound is actually 3 and 6 with well-characterized 
+		exceptions.
+		\begin{question}\label{ques:reduce-5,10-to-4,8}
+			Can we reduce the bounds in Theorem \ref{thm:main} on 
+			generation from $\max(5,e)$ and $\max(10, 2e)$ to $\max(4,e)$ and $
+			\max(8, 2e)$. 
+		\end{question}
+		\begin{rem}\label{rem:reduce-3,6}
+			It is unlikely that this can be reduced further, because Lemma 
+			\ref{lem:sat-2}, which allows us to add a stacky point in genus $g>0
+			$ saturated at 2, requires a generator in degree 4 and potentially 
+			a relation in degree 8, even when inductively adding on stacky 
+			points of stabilizer order 3.
+			\end{rem}
+
 	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
-	\item While Theorem ~\ref{thm:main} gives a minimal set of generators for the log spin canonical ring $R_L,$ the set of relations is not minimal.
-In many of the $g = 0$ and $g=1$ cases, it is not too difficult to see that our inductive procedure also yields a minimal set of relations for $R_L$.
-One might investigate whether the generators and relations given by the inductive proof of Theorem ~\ref{thm:main} are always minimal.
+	\item While Theorem ~\ref{thm:main} gives a minimal set of 
+		generators for the log spin canonical ring $R_L,$ the set of 
+		relations is not minimal. In many of the $g = 0$ and $g=1$ cases, 
+		it is not too difficult to see that our inductive procedure also 
+		yields a minimal set of relations for $R_L$. One might investigate 
+		whether the generators and relations given by the inductive proof 
+		of Theorem ~\ref{thm:main} are always minimal.
 		\end{enumerate}

### 2015-07-01 stacky_write_up/spin_cring.tex
ACGH citation for petri's thm

@@
 with multiplication structure corresponding to tensor product of
-sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
-theorem gives generators and relations for $R(X, K_X)$ showing that
-in most cases $R(X, K_X)$ is generated in degree 1 with relations
-in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]
-{saint-donat:proj}). This has the pleasant geometric consequence \todo{maybe use a different ref}
-that all such canonically embedded curves are scheme theoretically 
-cut out by quadratic equations.
+sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
+\cong \proj R$. When $g \geq 2$, Petri's theorem gives generators
+and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
+is generated in degree 1 with relations in degree 2
+(demonstrations are given by Saint-Donat \cite[p. 157]
+{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
+\cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
+geometric consequence that all such canonically embedded curves are 
+scheme theoretically cut out by quadratic equations.
 

### 2015-07-01 stacky_write_up/spin_cring.tex
edits to reid and admissibility

@@
 elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
-relations generated in degrees up to $\max(10, 2e_1, \ldots, 2e_r)$
+relations generated in degrees up to $2e$
 so long as $\sigma$ does not lie in a finite list of exceptional
@@
 generated as a $\BC$-algebra by elements of degree at most $e = \max
- (5$, $e_1$, $\ldots$, $e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
-then $M(\Gamma)$ has relations generated in degrees up to $\max(11,
-2e_1, \ldots, 2e_r)$. Otherwise, $M(\Gamma)$ has relations
-generated in degrees up to $\max(10, 2e_1, \ldots, 2e_r)$, so long
+ (5, e_1, \ldots , e_r)$ with relations in degree at most $2e,$ so long
 as $\sigma$ does not lie in a finite list of exceptional cases, as
@@
 \label{lem:admissible_inequality}
-The inequality (Ad-ii) of Definition ~\ref{defn:admissible} implies the
+For any $z$ as in condition (Ad-ii) of definition ~\ref{defn:admissible} the inequality (Ad-ii) implies the
 tighter inequality that
@@
 		by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
-
+\todo{Aaron, I tried to edit the following question, but it still seems a bit imprecise, and the question in particular is a bit of a long sentence.}
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
 		the work of Reid \cite[p. 35]{reid:infinitesimal}. We use his 
-		construction of a uniform bound on the generation of the half-
-		canonical ring and its ideal of relations at 5 and 10 in the non-
-		log, non-stacky case when genus is at least 2.  We extend this 
+		proof of that the 
+		spin canonical ring is generated in degree at most 5 with
+		relations in degree at most 10 in the 			
+		non-log, non-stacky case when genus is at least 2. We extend this 
 		bound of 5 and 10 to the log case, and then apply our inductive 
-		lemmas to add stacky points and get bounds of $\max(5,e)$ and $\max(
-		10, 2e)$.  Reid in fact proves something slightly stronger: that in 
+		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  Reid in fact proves something slightly stronger: that in 
 		most cases his bound is actually 3 and 6 with well-characterized 
@@
 		\begin{question}\label{ques:reduce-5,10-to-4,8}
-			Can we reduce the bounds in Theorem \ref{thm:main} on 
-			generation from $\max(5,e)$ and $\max(10, 2e)$ to $\max(4,e)$ and $
-			\max(8, 2e)$. 
+			In the case that the genus $g \geq 2,$ can we reduce the bounds in Theorem \ref{thm:main} on 
+			the degrees of generation and relations from $e = \max(5,e_1,\ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to $\max(4,e_1, \ldots, e_r)$ and $
+			\max(8, 2e_1, \ldots, 2e_r),$ apart from a finite list of exceptions?
 		\end{question}
 		\begin{rem}\label{rem:reduce-3,6}
-			It is unlikely that this can be reduced further, because Lemma 
+			It is unlikely that this can be reduced further for the case of stacky curves, because Lemma 
 			\ref{lem:sat-2}, which allows us to add a stacky point in genus $g>0
@@
 			points of stabilizer order 3.
+However, perhaps in the non-stacky case, one may be able able to generalize the result of Reid \cite[p.
+35]{reid:infinitesimal} to show that log spin canonical rings can be generated in degree at most 3 with relations in degree at most 6, apart from a well characterized list of exceptions.
 			\end{rem}

### 2015-07-01 stacky_write_up/spin_cring.tex
edited reid citation

@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-\todo{Peter: be clear what $z$ is}
+\todo{Peter: be clear what $z$ is, ask David, possibly edit this agin}
 
@@
 The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
-The case that $\Delta = 0$ was completed by Reid \cite[p.
-35]{reid:infinitesimal}.
+The case that $\Delta = 0$ was completed by Reid \cite[Theorem 3.4]{reid:infinitesimal}.
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
@@
 \begin{proof}
-If $\Delta =0$, the result is immediate from Reid. Otherwise, if
+If $\Delta =0$, the result is immediate from Reid \cite[Theorem 3.4]{reid:infinitesimal}. Otherwise, if
 $\Delta > 0$, the bound on the degrees of minimal generators follows
@@
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
-		the work of Reid \cite[p. 35]{reid:infinitesimal}. We use his 
+		the work of Reid \cite[Theorem 3.4]{reid:infinitesimal}. We use his 
 		proof of that the 
@@
 		bound of 5 and 10 to the log case, and then apply our inductive 
-		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  Reid in fact proves something slightly stronger: that in 
+		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  Reid \cite[Theorem 3.4]{reid:infinitesimal} in fact proves something slightly stronger: that in 
 		most cases his bound is actually 3 and 6 with well-characterized 
@@
 			points of stabilizer order 3.
-However, perhaps in the non-stacky case, one may be able able to generalize the result of Reid \cite[p.
-35]{reid:infinitesimal} to show that log spin canonical rings can be generated in degree at most 3 with relations in degree at most 6, apart from a well characterized list of exceptions.
+However, perhaps in the non-stacky case, one may be able able to generalize the result of Reid \cite[Theorem 3.4]{reid:infinitesimal} to show that log spin canonical rings can be generated in degree at most 3 with relations in degree at most 6, apart from a well characterized list of exceptions.
 			\end{rem}

### 2015-07-01 stacky_write_up/spin_cring.tex
combine 1st-2nd paragraphs in g0 example
Don't remember what I changed

@@
 Aaron: I'm fine with not making it an [H]}
-\begin{figure}\label{fig:s14/5-lattice}
+\begin{figure}
 \includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
 \caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each $\circ$ denotes a lattice point below $5y=14x$ which is not a best lower approximation.
-Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}
+Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
 \end{figure}
@@
 \begin{proof}
-We will only prove this in case (1), since case (2), is completely analogous.  \todo{Peter: Note to self: come back after reading proof to see if I actually buy this statement.}
+We prove this in case (1) and case (2) follows a similar procedure.
 
@@
 We now consider the case when the genus is at least 2.
-In this case, we are able to bound the degrees and relations of the spin canonical ring $R_L$.
-In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
+In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
+In this section, we do not obtain explicit presentations of $R_\halfcan.$  In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
 The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.

### 2015-07-01 stacky_write_up/spin_cring.tex
small changes to todos

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 	quotients of the upper-half plane by Fuchsian groups may be
-	translated to (log spin) canonical rings by the classical
+	translated to log spin canonical rings by the classical
 	results of Kodaira--Spencer. This work describes
@@
 
+\todo{Make sure we call all divisors spin canonical divisors}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. Often, it is useful to
-bound the degree of the generators and relations for $M(\Gamma)$
-for general Fuchsian groups $\Gamma$. In the special case that $\Gamma$
+$M(\Gamma) = \bigoplus_{k=0}^\infty M_k(\Gamma)$. One of the best ways to understand the ring of modular forms is to give a presentation of $M(\Gamma)$
+for general Fuchsian groups $\Gamma.$ In order to do so, it is extermely useful to have a bound on the degrees in which the generators and relations can occur. In the special case that $\Gamma$
 has no odd weight modular forms, Voight and Zureick-Brown
@@
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$). \todo{Ask David, is it useful to include this parenthetical? yes}
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
 Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch \todo{Probably include this in a remark below the proof}).
@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-\todo{Peter: be clear what $z$ is, ask David, possibly edit this agin}
 

### 2015-07-01 stacky_write_up/spin_cring.tex
merging small changes to todos

@@
 (0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are distinct points.
-In this example, we will exhibit a minimal presentation for $R' = R(\sx,0,\halfcan')$ and show the triple $(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
-
+\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are
+distinct points. In this example, we will exhibit a minimal
+presentation for $R' = R(\sx,0,\halfcan')$ and show the triple
+$(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
 Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}

### 2015-07-01 stacky_write_up/spin_cring.tex
add span, many typographical fixes in High Genus

@@
 \DeclareMathOperator{\sat}{sat}
+\DeclareMathOperator{\span}{span}
 
@@
 \label{eg:exception-1-5}
-Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P - Q + \frac{2}{5}P_1.$ Let $u \in (P_L)_1$ be any nonzero element.
-We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element.
-We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$.
-Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$.
-Then, we claim there is some $\alpha \in k$ so that
-
-$$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$$
+Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
+ Q + \frac{2}{5} P_1.$ Let $u \in (P_L)_1$ be any nonzero element.
+We obtain $\di u|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
+--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero
+element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
+if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0
+(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally,
+let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
+we claim there is some $\alpha \in k$ so that
+
+$$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha u y_5^2).$$
 
@@
 %where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
-$\halfcan' \in \di
-X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
+$\halfcan' \in \BQ \otimes \di X$ and  $\frac{\alpha}{\beta} \in \BQ$. 
 In
@@
 \label{lem:relations_from_generators_induction} 
-Suppose $\halfcan, \halfcan' \in \BQ \otimes \di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
+Suppose $\halfcan$, $\halfcan' \in \BQ$ $\otimes$ $\di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
 and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
@@
 		_3, y_4,$ and $y_5$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grevlex$ so that $y_3 \prec 
+	\item[(b)] Equip $k[y_3, y_4, y_5]$ with grevlex so that $y_3 \prec 
 		y_4 \prec y_5$
@@
 Since $X$ has genus 0, general
-elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $- \ord_P^{\halfcan'}(y_i) =
+elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $-\ord_P^{\halfcan'}(y_i) =
 1$. We see by pole order considerations that
@@
 \]
-we can argue similarly to Lemma $\ref{lem:sat-1}$ that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, concluding part (b).
+we can argue similarly to Lemma \ref{lem:sat-1} that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, concluding part (b).
 
@@
 ~\ref{thm:main}, holds for a curve with signature
-$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k+1}' = \cdots = e_r'$ satisfying certain admissibility (cf.
+$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' = \cdots = e_r'$ satisfying certain admissibility (cf.
 Definition ~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for a curve with
-signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta)$. 
+signature $(g; e_1', \ldots, e_k', e_{k+1}'+2,\ldots, e_r'+2; \delta)$. 
 %In order to state Lemma
@@
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ and so $H^0(X, 2L)$ is basepoint free by Riemann-Roch.
+Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ and so $H^0(X, 2L)$ is basepoint-free by Riemann-Roch.
 We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
@@
 The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
-However, the statements are different, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
+However, the statements are different, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint-free pencil contained in $H^0(X, L).$
 
@@
 \label{lem:generation-5}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$ and $\Delta > 0.$ Let $s_1,s_2 \in H^0(X,2L)$ be two independent sections such that the vector subspace $V = ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint free.
-Then, the map
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
+with $g \geq 2$ and $\Delta > 0.$ Let $s_1$, $s_2 \in H^0(X, 2L)$
+be two independent sections such that the vector subspace $V =
+\span(s_1, s_2) \subseteq H^0(K)$ is basepoint-free. Then, the map
 \begin{align*}
@@
 \end{align*}
-is surjective if $n \geq 4.$ In particular, $R_L$ is generated in degree at most $5.$
+is surjective if $n \geq 4$. In particular, $R_L$ is generated in degree at most $5.$
 \end{lem}
@@
 \begin{proof}
-To show there are no new generators in degree at least $6$, it suffices to show that if $n \geq 4$, the map
+To show there are no new generators in degree at least $6$, it
+suffices to show that if $n \geq 4$, the map
 \begin{align*}
@@
 \end{align*}
-is surjective.
-Indeed, since $V= ks_1 \oplus k s_2 \subseteq H^0(K)$ is basepoint-free, by the basepoint-free pencil trick, (see \cite[Lemma 2.6]{saint-donat:proj} for a proof,) we obtain an exact sequence
+is surjective. Indeed, since $V = \span(s_1, s_2) \subseteq
+H^0(K)$ is basepoint-free, by the basepoint-free pencil trick (see
+\cite[Lemma 2.6]{saint-donat:proj} for a proof), we obtain an exact
+sequence
 $$\begin{tikzcd}
@@
 
-We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 4.$
-Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
-By rank-nullity, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L).$$
-Ergo, $f$ is surjective.
+We wish to show $f$ is surjective. Note that $\dim_k \ker f = \dim_
+k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the
+assumption $n \geq 4.$ Additionally, $\dim_k V \otimes H^0(nL) = 2
+\cdot (n - 1)(g - 1)$, again using Riemann--Roch. By rank-nullity,
+$$\dim_k \im f = 2 \cdot (n - 1)(g - 1) - (n - 3)(g - 1) = (n + 1)(g - 1) =
+\dim_k H^0((n + 2)L)$$. Ergo, $f$ is surjective.
 \end{proof}
@@
 \label{defn:lower-ideal}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $I_{L, d}$ be the $d$th graded piece of $I_L$ and define
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -; \delta
+)$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots
+, x_n$ of $R_L$ so that we obtain a surjection $\phi: k[x_1, \ldots
+, x_n] \twoheadrightarrow R_L$ with kernel $I_L$. Let $I_{L, d}$ be
+the $d$^\text{th} graded piece of $I_L$ and define
 \[
@@
 \label{lem:reducing-degree}
-Let $(X, \Delta, L)$ be a log spin curve of genus $g \geq 2,$ so that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_L$ so that we obtain a surjection $\phi:k[x_1, \ldots, x_n] \twoheadrightarrow R_L$ with kernel $I_L$.
-Let $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ be two elements so that $k\phi(s_1) \oplus k\phi(s_2) = V \subseteq H^0(X,2L)$ is basepoint free.
-For any $f \in k[x_1, \ldots, x_n]$ such that $\deg f \leq 11,$
-there exist $g,h \in k[x_1, \ldots, x_n]_{d-2}$ so that $s_1g + s_2h = f \bmod J_{L,d}.$
+Let $(X, \Delta, L)$ be a log spin curve of genus $g \geq 2,$ so
+that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_L$ so
+that we obtain a surjection $\phi: k[x_1, \ldots, x_n]
+\twoheadrightarrow R_L$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
+\ldots, x_n]_2$ be two elements so that $\phi(s_1) k$ $\oplus$
+$\phi(s_2) k = V \subseteq H^0(X, 2L)$ is basepoint-free. For any $f \in
+k[x_1, \ldots, x_n]$ such that $\deg f \leq 11,$ there exist $g, h \in
+k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h = f \bmod J_{L, d}.$
 \end{lem}
@@
 is surjective, and $\deg f \leq 11$ guarantees
-$\deg f- \deg a_i -2 \geq 4.$
+$\deg f - \deg a_i -2 \geq 4.$
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha,\phi(h_i) = \beta$, we have $a_i \equiv s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have $a_i \equiv s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
 
@@
 \label{prop:relation-10}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$ with $g \geq 2$ and $\Delta > 0.$ Then $I_L$ is generated in degree at most degree at most $10.$
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -; \delta)$
+ with $g \geq 2$ and $\Delta > 0.$ Then $I_L$ is generated in
+degree at most degree at most $10$.
 \end{prop}
 \begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 11$.
-To complete the proof, it suffices to show $f \in I_{L,d}'$.
-By Lemma ~\ref{lem:reducing-degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$ where $\phi(s_1),\phi(s_2) \in H^0(X,2L)$ are two sections so that $k\phi(s_1) \oplus k \phi(s_2) = V \subseteq H^0(K)$ is basepoint-free.
-Consider the map
+Suppose $f \in I_L$ with $\deg f \geq 11$. To complete the proof,
+it suffices to show $f \in I_{L,d}'$. By Lemma
+~\ref{lem:reducing-degree}, it suffices to show $s_1 g + s_2 h \in
+I_{L, d}'$ where $\phi(s_ 1),\phi(s_2) \in H^0(X, 2L)$ are two sections
+so that $\span(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
+basepoint-free. Consider the map
+
 $$\begin{tikzcd}
@@
 \end{tikzcd}$$
-we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
-So, by the explicit isomorphism given in the proof of the basepoint-free pencil trick, as shown in the proof of \cite[Lemma 2.6]{saint-donat:proj}, there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$.
-Hence,
-\begin{align*}
-	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
+
+\noindent
+we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0$.
+So by the explicit isomorphism given in the proof of the basepoint-
+free pencil trick, as shown in the proof of \cite[Lemma 2.6]
+{saint-donat:proj}, there exists some $\rho \in k[x_1, \ldots, x_n]$
+so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) =
+\phi(s_2) \phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho)$. 
+Therefore,
+$g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv - s_1 \rho \bmod
+I_{k, d - 2}$. Hence,
+\begin{align*}
+	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_
+{L,d}.
 \end{align*}
@@
 
-\iffalse
-\begin{rem}
-\label{rem:relations_generation_ten}
-Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_L$ has a
-relation in degree 10. Therefore, the bound from Proposition
-~\ref{prop:relation-10}, that $I_L$ is generated in degree at most
-11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
-sharp.
-\end{rem}
-\fi
+%\begin{rem}
+%\label{rem:relations_generation_ten}
+%Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_L$ has a
+%relation in degree 10. Therefore, the bound from Proposition
+%~\ref{prop:relation-10}, that $I_L$ is generated in degree at most
+%11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
+%sharp.
+%\end{rem}
 
@@
 \begin{proof}
-If $\Delta =0$, the result is immediate from Reid \cite[Theorem 3.4]{reid:infinitesimal}. Otherwise, if
-$\Delta > 0$, the bound on the degrees of minimal generators follows
-from Lemma ~\ref{lem:generation-5}, while the bound on the degrees
-of minimal relations follows from Proposition ~\ref{prop:relation-10}.
+If $\Delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
+{reid:infinitesimal}. Otherwise, if $\Delta > 0$, the bound on the
+degrees of minimal generators follows from Lemma
+~\ref{lem:generation-5}, while the bound on the degrees of minimal
+relations follows from Proposition ~\ref{prop:relation-10}.
 \end{proof}
@@
 
-We are ready to prove our main theorem ~\ref{thm:main} in the case
+We are ready to prove our main theorem, Theorem ~\ref{thm:main} in the case
 $g \geq 2$. The idea of the proof is to use Lemma

### 2015-07-01 stacky_write_up/spin_cring.tex
fix \span issue

@@
 \newcommand\sg{{\mathscr G}}
-\newcommand \sx{\mathscr X}
+\newcommand\sx{\mathscr X}
 
@@
 \newcommand\coker{\text{coker}}
-\newcommand \spec{\text{Spec }}
-\newcommand \proj{\text{Proj }}
-\newcommand \rspec{\textit{Spec }}
-\newcommand \rproj{\textit{Proj }}
-\newcommand{\gal}{\mathrm{Gal}}
+\newcommand\spec{\text{Spec }}
+\newcommand\proj{\text{Proj }}
+\newcommand\rspec{\textit{Spec }}
+\newcommand\rproj{\textit{Proj }}
+\newcommand\gal{\mathrm{Gal}}
 
@@
 \DeclareMathOperator{\sat}{sat}
-\DeclareMathOperator{\span}{span}
+\DeclareMathOperator{\newspan}{span}
 
@@
 be two independent sections such that the vector subspace $V =
-\span(s_1, s_2) \subseteq H^0(K)$ is basepoint-free. Then, the map
+\newspan(s_1, s_2) \subseteq H^0(K)$ is basepoint-free. Then, the map
 \begin{align*}
@@
 \end{align*}
-is surjective. Indeed, since $V = \span(s_1, s_2) \subseteq
+is surjective. Indeed, since $V = \newspan(s_1, s_2) \subseteq
 H^0(K)$ is basepoint-free, by the basepoint-free pencil trick (see
@@
 , x_n] \twoheadrightarrow R_L$ with kernel $I_L$. Let $I_{L, d}$ be
-the $d$^\text{th} graded piece of $I_L$ and define
+the $d^\text{th}$ graded piece of $I_L$ and define
 \[
@@
 \twoheadrightarrow R_L$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
-\ldots, x_n]_2$ be two elements so that $\phi(s_1) k$ $\oplus$
-$\phi(s_2) k = V \subseteq H^0(X, 2L)$ is basepoint-free. For any $f \in
+\ldots, x_n]_2$ be two elements so that $\newspan(\phi(s_1), \phi(s_2))
+= V \subseteq H^0(X, 2L)$ is basepoint-free. For any $f \in
 k[x_1, \ldots, x_n]$ such that $\deg f \leq 11,$ there exist $g, h \in
@@
 I_{L, d}'$ where $\phi(s_ 1),\phi(s_2) \in H^0(X, 2L)$ are two sections
-so that $\span(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
+so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
 basepoint-free. Consider the map

### 2015-07-01 stacky_write_up/spin_cring.tex
section 5 edit

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 	quotients of the upper-half plane by Fuchsian groups may be
-	translated to log spin canonical rings by the classical
+	translated to (log spin) canonical rings by the classical
 	results of Kodaira--Spencer. This work describes
@@
 
-\todo{Make sure we call all divisors spin canonical divisors}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k=0}^\infty M_k(\Gamma)$. One of the best ways to understand the ring of modular forms is to give a presentation of $M(\Gamma)$
-for general Fuchsian groups $\Gamma.$ In order to do so, it is extermely useful to have a bound on the degrees in which the generators and relations can occur. In the special case that $\Gamma$
+$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. Often, it is useful to
+bound the degree of the generators and relations for $M(\Gamma)$
+for general Fuchsian groups $\Gamma$. In the special case that $\Gamma$
 has no odd weight modular forms, Voight and Zureick-Brown
@@
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
+3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$). \todo{Ask David, is it useful to include this parenthetical? yes}
 Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch \todo{Probably include this in a remark below the proof}).
@@
 The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+\todo{Peter: be clear what $z$ is, ask David, possibly edit this agin}
 
@@
 In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan.$  In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
-The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.
+In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g_1} and ~\ref{sec:g_0} where we not only obtain bounds, but also obtain inductive presentations.
+The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
 
@@
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ and so $H^0(X, 2L)$ is basepoint free by Riemann-Roch.
+Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint free by Riemann-Roch.
 We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
@@
 The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
-However, the statements are different, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
+However, the statements differ, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
 
@@
 We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 4.$
-Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
-By rank-nullity, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L).$$
+Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
+Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
+Therefore,
+\begin{align*}
+	\dim_k \im f 	& = 2 \cdot (n- 1)(g - 1+\frac{\delta}{2}) -(n-3)(g - 1+\frac{\delta}{2})\\
+				& = (n+ 1)(g - 1+\frac{\delta}{2}) = \dim_k H^0((n+2)L).
+\end{align*}
 Ergo, $f$ is surjective.
@@
 
-The next step is to bound the degrees of the relations of $R_L$ when $\Delta > 0$.
-This is done in Proposition ~\ref{prop:relation-10}.
-The idea of the proof of Proposition ~\ref{prop:relation-10} is to use the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
-We now fix notation for this ideal generated by lower degrees relations.
+The next step is to bound the degrees of the relations of $R_L$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
+%The idea of the proof of Proposition ~\ref{prop:relation-10} is to 
+by using the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
+In Definition ~\ref{defn:lower-ideal}, we fix notation for the ideal generated by lower degrees relations:
 

### 2015-07-01 stacky_write_up/spin_cring.tex

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 
-The main result of this subsection is that for a log spin curve with no stacky points $(X,\Delta,L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
+The main result of this subsection is that for a log spin curve with no stacky points $(X \Delta, L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
 The case that $\Delta = 0$ was completed by Reid \cite[Theorem 3.4]{reid:infinitesimal}.
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ and so $H^0(X, 2L)$ is basepoint-free by Riemann-Roch.
+Throughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint-free by Riemann-Roch.
 We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
@@
 The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
-However, the statements are different, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint-free pencil contained in $H^0(X, L).$
+However, the statements differ, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint-free pencil contained in $H^0(X, L).$
 
@@
 
-We wish to show $f$ is surjective. Note that $\dim_k \ker f = \dim_
-k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the
-assumption $n \geq 4.$ Additionally, $\dim_k V \otimes H^0(nL) = 2
-\cdot (n - 1)(g - 1)$, again using Riemann--Roch. By rank-nullity,
-$$\dim_k \im f = 2 \cdot (n - 1)(g - 1) - (n - 3)(g - 1) = (n + 1)(g - 1) =
-\dim_k H^0((n + 2)L)$$. Ergo, $f$ is surjective.
+We wish to show $f$ is surjective.
+Note that $\dim_k \ker f = \dim_k H^0((n - 2)L) = (n - 3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
+Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n - 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
+Therefore,
+\begin{align*}
+	\dim_k \im f 	& = 2 \cdot (n - 1)(g - 1+ \frac{\delta}{2}) - (n - 3)(g - 1 + \frac{\delta}{2})\\
+				& = (n + 1)(g - 1 + \frac{\delta}{2}) = \dim_k H^0((n + 2)L).
+\end{align*}
+Ergo, $f$ is surjective.
 \end{proof}

### 2015-07-01 stacky_write_up/spin_cring.tex
mid intro edits

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 
+\todo{Make the sentences in the abstract shorter}
+\todo{Make sure we call all divisors spin canonical divisors}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_k M_k(\Gamma)$. Often, it is useful to
-bound the degree of the generators and relations for $M(\Gamma)$
-for general Fuchsian groups $\Gamma$. In the special case that $\Gamma$
+$M(\Gamma) = \bigoplus_{k=0}^\infty M_k(\Gamma)$. One of the best ways to understand the ring of modular forms is to give a presentation of $M(\Gamma)$
+for general Fuchsian groups $\Gamma.$ In order to do so, it is extermely useful to have a bound on the degrees in which the generators and relations can occur. In the special case that $\Gamma$
 has no odd weight modular forms, Voight and Zureick-Brown
-\cite[Chapters 7-9]{vzb:stacky} give nice bounds.
+\cite[Chapters 7-9]{vzb:stacky} give tight bounds.
 This work extends their work to all Fuchsian groups $\Gamma$.
@@
 For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
-\backslash \BH$ is a Riemann Surface over $\BC$. It may well be
+\backslash \BH$ is a Riemann Surface over $\BC$. It may be
 that $\Gamma \backslash \BH$ is not compact, but we can form a
-space $\Gamma \backslash \BH^*$ which is a compactification of
-$\Gamma \backslash \BH,$ with associated divisor of cusps $\Delta$.
+compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in cusps, with associated divisor of cusps $\Delta$.
 In order to find generators and relations for $M(\Gamma)$, we
@@
 
-Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is
+Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$. It is
 well known that the canonical sheaf $\Omega _X,$ with associated
-canonical divisor $K_X$  determines the {\bf canonical map } $\pi:
+canonical divisor $K_X$, determines the {\bf canonical map } $\pi:
 X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical ring} is
@@
 and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
-is generated in degree 1 with relations in degree 2
-(demonstrations are given by Saint-Donat \cite[p. 157]
-{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
-\cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
+is generated in degree 1 with relations in degree 2, as shown in
+\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
+\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
 geometric consequence that all such canonically embedded curves are
-scheme theoretically cut out by quadratic equations.
+scheme theoretically cut out by degree 2 equations.
 
@@
 stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
-with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$,
+with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$, we define
 
@@
 study in this paper is the {\bf log spin canonical ring} of $(\sx,
-\Delta, \halfcan)$ is
+\Delta, \halfcan),$ notated as
 \begin{align*}
@@
 A brief overview of stacky curves, log divisors, and log spin
-canonical rings and references are given in Subsection
+canonical rings is given in Subsection
 ~\ref{ssec:stacky-background}.
@@
 %\]
-
-\begin{rem}
-\label{rem:stack-formalism}
-Stacky curves may be formalized in the language of stacks (e.g. as
-done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
-Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
-Behrend and Noohi \cite{behrend-noohi:uniformization}), but for the
-purposes of this paper, it suffices to treat $\sx$ as a scheme
-whose associated divisor group allows a finite number of stacky
-points. The remainder of the paper will primarily use the language
-of Weil divisors.
-\end{rem}
 
@@
 
-Throughout this paper, stacky curves will be assumed to be tame and
+\begin{rem}
+\label{rem:stack-formalism}
+Stacky curves may be formally defined in the language of stacks, (as
+is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
+Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
+Behrend and Noohi \cite{behrend-noohi:uniformization},) but for the
+purposes of this paper, it suffices to treat $\sx$ as a scheme
+whose associated divisor group has a finite number of stacky
+points.
+
+When viewed in the formalism of stacks, all stacky curves will be assumed to be tame and
 $k$ will always be algebraically closed. We also assume that the
 stacky curves are separably rooted, i.e. the residue field of each
-stacky points is separable. As noted in Remark
-~\ref{rem:stack-formalism}, the language of stacks will be omitted
-in this paper, as it is sufficient to treat stacky curves and
-related objects $\sx$ as a scheme whose associated divisor group
-allows for a finite number of \textbf{stacky points} which may be
-viewed heuristically as ``fractional points''. See Voight and
-Zureick-Brown for more thorough treatment of these definitions
-\cite[Chapter 5]{vzb:stacky}.
+of the stacky points is separable.
+
+With the close relation to stacks in mind, for simplicity, the remainder of this paper is primarily phrased using the language
+of Weil divisors.
+\end{rem}
 
@@
 In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g_1} and ~\ref{sec:g_0} where we not only obtain bounds, but also obtain inductive presentations.
-The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
+In this section, we do not obtain explicit presentations of $R_\halfcan.$  In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively.
+The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.
 
@@
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint free by Riemann-Roch.
+Thoughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ and so $H^0(X, 2L)$ is basepoint free by Riemann-Roch.
 We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
@@
 The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
-However, the statements differ, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
+However, the statements are different, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint free pencil contained in $H^0(X,L).$
 
@@
 We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
-Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
-Therefore,
-\begin{align*}
-	\dim_k \im f 	& = 2 \cdot (n- 1)(g - 1+\frac{\delta}{2}) -(n-3)(g - 1+\frac{\delta}{2})\\
-				& = (n+ 1)(g - 1+\frac{\delta}{2}) = \dim_k H^0((n+2)L).
-\end{align*}
+Note that $\dim_k \ker f = \dim_k H^0((n-2)L) = (n-3)(g - 1)$ using Riemann--Roch and the assumption $n \geq 4.$
+Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n- 1)(g - 1)$, again using Riemann--Roch.
+By rank-nullity, $$\dim_k \im f = 2 \cdot (n- 1)(g - 1) -(n-3)(g - 1) = (n+ 1)(g - 1) = \dim_k H^0((n+2)L).$$
 Ergo, $f$ is surjective.
@@
 
-The next step is to bound the degrees of the relations of $R_L$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
-%The idea of the proof of Proposition ~\ref{prop:relation-10} is to 
-by using the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
-In Definition ~\ref{defn:lower-ideal}, we fix notation for the ideal generated by lower degrees relations:
+The next step is to bound the degrees of the relations of $R_L$ when $\Delta > 0$.
+This is done in Proposition ~\ref{prop:relation-10}.
+The idea of the proof of Proposition ~\ref{prop:relation-10} is to use the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
+We now fix notation for this ideal generated by lower degrees relations.
 

### 2015-07-01 stacky_write_up/spin_cring.tex

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 
+\todo{Make the sentences in the abstract shorter}
 \todo{Make sure we call all divisors spin canonical divisors}
@@
 has no odd weight modular forms, Voight and Zureick-Brown
-\cite[Chapters 7-9]{vzb:stacky} give nice bounds.
+\cite[Chapters 7-9]{vzb:stacky} give tight bounds.
 This work extends their work to all Fuchsian groups $\Gamma$.

### 2015-07-01 stacky_write_up/spin_cring.tex
delete some unused macros
ex:base->eg:base, \mathbb->\B, delete unused macros

@@
 \newcommand\BH{{\mathbb H}}
-\newcommand\bO{{\mathbf O}}
-\newcommand\CC{{\mathcal C}}
 \newcommand\BN{{\mathbb N}}
@@
 \newcommand\BP{{\mathbb P}}
-\newcommand\BBZ{{\mathbb Z}}
-\newcommand\uR{\underline{R}}
-\newcommand\uZ{\underline{\BBZ}}
-\newcommand\CF{{\mathcal F}}
-\newcommand\uCF{\underline{{\mathcal F}}}
 \newcommand\BZ{{\mathbb Z}}
 \newcommand\BA{{\mathbb A}}
-\newcommand\fa{{\mathfrak a}}
-\newcommand\fp{{\mathfrak p}}
-\newcommand\fq{{\mathfrak q}}
-\newcommand\fm{{\mathfrak m}}
-\newcommand\so{{\mathscr O}}
-\newcommand\sg{{\mathscr G}}
-\newcommand\sx{\mathscr X}
-
-\newcommand\scm{{\mathscr M}}
-\newcommand\scn{{\mathscr N}}
-\newcommand\scf{{\mathscr F}}
-\newcommand\scg{{\mathscr G}}
+
 \newcommand\sco{{\mathscr O}}
-\newcommand\sch{{\mathscr H}}
-\newcommand\scl{{\mathscr L}}
-\newcommand\sci{{\mathscr I}}
 
@@
 \newcommand\proj{\text{Proj }}
-\newcommand\rspec{\textit{Spec }}
-\newcommand\rproj{\textit{Proj }}
 \newcommand\gal{\mathrm{Gal}}
 
-\newcommand \trdeg{\text{tr. deg }}
-\newcommand \codim{\text{codim}}
-\newcommand \rk{\text{rk }}
-\DeclareMathOperator\di{Div}
-\newcommand \depth{\text{depth }}
 \DeclareMathOperator{\ord}{ord}
@@
 
+\DeclareMathOperator\di{Div}
+\newcommand\sx{\mathscr X}
 \newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
@@
 linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k=0}^\infty M_k(\Gamma)$. One of the best ways to understand the ring of modular forms is to give a presentation of $M(\Gamma)$
-for general Fuchsian groups $\Gamma.$ In order to do so, it is extermely useful to have a bound on the degrees in which the generators and relations can occur. In the special case that $\Gamma$
-has no odd weight modular forms, Voight and Zureick-Brown
-\cite[Chapters 7-9]{vzb:stacky} give tight bounds.
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best
+ways to understand the ring of modular forms is to give a
+presentation of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
+In order to do so, it is extermely useful to have a bound on the
+degrees in which the generators and relations can occur. In the
+special case that $\Gamma$ has no odd weight modular forms, Voight
+and Zureick-Brown \cite[Chapters 7-9]{vzb:stacky} give tight bounds.
  This work extends their work to all Fuchsian groups $\Gamma$.
@@
 that $\Gamma \backslash \BH$ is not compact, but we can form a
-compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in cusps, with associated divisor of cusps $\Delta$.
+compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
+cusps, with associated divisor of cusps $\Delta$.
+
 In order to find generators and relations for $M(\Gamma)$, we
@@
 
-Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$. It is
-well known that the canonical sheaf $\Omega _X,$ with associated
-canonical divisor $K_X$, determines the {\bf canonical map } $\pi:
-X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical ring} is
-defined to be
+Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$.
+It is well known that the canonical sheaf $\Omega _X,$ with
+associated canonical divisor $K_X$, determines the {\bf canonical
+map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
+ring} is defined to be
 \begin{align*}
@@
 \begin{example}
-\label{ex:base-377}
+\label{eg:base-0-377}
 Let $(\sx,0,\halfcan')$ be a log spin curve with signature $\sigma =
@@
 $R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
-The details are omitted as it is analogous to Example ~\ref{ex:base-377}.
+The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
 
@@
 One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
-The verification is analogous to Example ~\ref{ex:base-377} and is omitted.
+The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
 
@@
 %In this section, we prove various inductive statements under the following setup:
-%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions.
+%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d \in\BN$ and certain saturation conditions.
 Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
@@
 We area almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
-\mathbb{Q}$-divisor.
-Whereas O'Dorney considers arbitrary $\mathbb{Q}$ divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
+\BQ$-divisor.
+Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
 Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$.
@@
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c\in \mathbb{Z}, d\in \mathbb{N}$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c \in \BN, d \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 \end{defn}
@@
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
+Suppose $P$ is not a base-point of $d\halfcan'$ for all $d \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \mathbb{N}$ such that
+for some $\alpha,\beta \in \BN$ such that
 \begin{align}
@@
 $V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
- and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j\in \mathbb{Z}_{\ge 0}$ such that
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j \in \BN_{\ge 0}$ such that
 \begin{enumerate}
@@
 Equation ~\ref{eqn:deg1-sat-ind}, for any $d
-\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+\in \BN$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
 
@@
 
-Suppose $c,d\in \mathbb{N}$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
+Suppose $c,d \in \BN$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
 \beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
@@
 \[
-	S_0 = \{u^l : l\in \mathbb{Z}_{\ge 0}\}
+	S_0 = \{u^l : l \in \BN_{\ge 0}\}
 \]
-and for each $i \in \mathbb{N}$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
+and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
 \[
@@
 
-By equation \ref{eqn:deg1-sat-ind} for $d\in \mathbb{N}$,
+By equation \ref{eqn:deg1-sat-ind} for $d \in \BN$,
 \[
@@
 \] 
-so $S$ contains elements in degree $d\in \mathbb{N}$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
+so $S$ contains elements in degree $d \in \BN$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
 Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
@@
 Notice that $S$ generates the ideal $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$; let $l$ be maximal such that $a_l\ne 0$.
-If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h\in \mathbb{N}$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
+If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
 and for all $r<h$ $\prod_{j=1}^r {y_j}^{b_j}\in S$, where $b_j=a_j$ when $j\ne i$ and $b_i=a_i+1$.
@@
 \begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i}$ for some odd $e_i\in \mathbb{N}_{\geq 3}$, then $T,$ as defined in the beginning of the proof of (b) in Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
+If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i}$ for some odd $e_i \in \BN_{\geq 3}$, then $T,$ as defined in the beginning of the proof of (b) in Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
 \end{rem}
@@
 %\[
-	%\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
+	%\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c \in \{0,1\}\rangle
 %\]
@@
 %any point $P$ occurring in a stacky divisor of $\sx$ must have 
-%coefficient lying in $\mathbb{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
+%coefficient lying in $\BN[\frac{1}{e_i}]$ (ranging over $e_i$
 %s appearing in the characteristic of $(\sx,\Delta)$).
@@
 \begin{proof}
-Recall that Case (b) is proven in Example ~\ref{ex:base-377}. For
+Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
 the remaining cases, we can use a similar method to find a
@@
 verifying these are similar to that given in Example
-~\ref{ex:base-377}.
+~\ref{eg:base-0-377}.
 
@@
 		\begin{rem}\label{rem:reduce-3,6}
-			It is unlikely that this can be reduced further for the case of stacky curves, because Lemma 
-			\ref{lem:sat-2}, which allows us to add a stacky point in genus $g>0
-			$ saturated at 2, requires a generator in degree 4 and potentially 
-			a relation in degree 8, even when inductively adding on stacky 
-			points of stabilizer order 3.
-However, perhaps in the non-stacky case, one may be able able to generalize the result of Reid \cite[Theorem 3.4]{reid:infinitesimal} to show that log spin canonical rings can be generated in degree at most 3 with relations in degree at most 6, apart from a well characterized list of exceptions.
+			It is unlikely that this can be reduced further for the case 
+			of stacky curves, because Lemma \ref{lem:sat-2}, which allows 
+			us to add a stacky point in genus $g > 0$ saturated at 2, 
+			requires a generator in degree 4 and potentially a relation in 
+			degree 8, even when inductively adding on stacky points of 
+			stabilizer order 3. However, perhaps in the non-stacky case, one 
+			may be able able to generalize the result of Reid \cite[Theorem 3.4
+			]{reid:infinitesimal} to show that log spin canonical rings can be 
+			generated in degree at most 3 with relations in degree at most 6, 
+			apart from a well characterized list of exceptions.
 			\end{rem}

### 2015-07-01 stacky_write_up/spin_cring.tex
section 5 edits

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 \newcommand\BP{{\mathbb P}}
-\newcommand\BBZ{{\mathbb Z}}
-\newcommand\uR{\underline{R}}
-\newcommand\uZ{\underline{\BBZ}}
-\newcommand\CF{{\mathcal F}}
-\newcommand\uCF{\underline{{\mathcal F}}}
 \newcommand\BZ{{\mathbb Z}}
 \newcommand\BA{{\mathbb A}}
-\newcommand\fa{{\mathfrak a}}
-\newcommand\fp{{\mathfrak p}}
-\newcommand\fq{{\mathfrak q}}
-\newcommand\fm{{\mathfrak m}}
-\newcommand\so{{\mathscr O}}
-\newcommand\sg{{\mathscr G}}
-\newcommand\sx{\mathscr X}
 
@@
 \newcommand \rk{\text{rk }}
-\DeclareMathOperator\di{Div}
 \newcommand \depth{\text{depth }}
@@
 = V \subseteq H^0(X, 2L)$ is basepoint-free. For any $f \in
-k[x_1, \ldots, x_n]$ such that $\deg f \leq 11,$ there exist $g, h \in
+k[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
 k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h = f \bmod J_{L, d}.$
@@
 % Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
-By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
+By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
+We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$
+
 By Lemma ~\ref{lem:generation-5},
@@
 \end{align*}
-is surjective, and $\deg f \leq 11$ guarantees
-$\deg f - \deg a_i -2 \geq 4.$
+is surjective, and $\deg f \geq 11$ implies that
+$\deg a_i =\deg f - \deg x_i -2 \geq 4.$
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.

### 2015-07-01 stacky_write_up/spin_cring.tex
move table caption to below table, add captionsetup
editing section 5 through 5.3

@@
 \noindent
-When the log spin curve is fixed, we usually use $R$ or $R_L$ to
+When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
 represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
@@
 %in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
-	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, L_X')$ may have no global sections.
+	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
 We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
@@
 \begin{align*}
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ in_\prec(I))_d \\
-	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I)_d &=
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ in_\prec(I))_d \\
+	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
 	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
@@
 for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
+x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
 \rangle$ can be checked by looking at the $k$-basis at each degree
@@
 We obtain $\di u|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
---Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero
+--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
 element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
@@
 (\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally,
-let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
+let $y_5 \in (R_\halfcan)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
 we claim there is some $\alpha \in k$ so that
 
-$$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha u y_5^2).$$
+$$R_\halfcan \cong k[u, y_3, y_5]/(y_3^4 - \alpha u y_5^2).$$
 
 In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_L$.
+One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_\halfcan$.
 The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
@@
 Maybe you can explain this in the proof in a sentence.}
-Furthermore, let $R_{L'} = k[x_2, x_3
+Furthermore, let $R_{\halfcan'} = k[x_2, x_3
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
@@
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$.  Define $R':= R_{L'}$.  Further, assume either 
+space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$.  Define $R':= R_{\halfcan'}$.  Further, assume either 
 \begin{enumerate}
@@
 \delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
-$e_j = e_j'$ for $j \notin J$. Define $R := R_L$.  Then the following are true:
+$e_j = e_j'$ for $j \notin J$. Define $R := R_\halfcan$.  Then the following are true:
 \begin{enumerate}
@@
 
-The main result of this subsection is that for a log spin curve with no stacky points $(X \Delta, L)$, the spin canonical ring $R_L$ is generated in degree at most $5$, with relations in degree at most $10$.
+The main result of this subsection is that for a log spin curve with no stacky points $(X \Delta, L)$, the spin canonical ring $R_\halfcan$ is generated in degree at most $5$, with relations in degree at most $10$.
 The case that $\Delta = 0$ was completed by Reid \cite[Theorem 3.4]{reid:infinitesimal}.
@@
 %\label{lem:generation-5}
-%Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_L$ is generated in degree at most $5$.
+%Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_\halfcan$ is generated in degree at most $5$.
 %\end{lem}
 %
-%The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_L$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
+%The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_\halfcan$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
 When $g > 3$, it is easy to reduce the bound from 5 to 6.
-The trickiest case is to show $R_L$ is generated in degree 5 when $g = 2$, which is done in Lemma ~\ref{lem:genus-2-generation-5}.
+The trickiest case is to show $R_\halfcan$ is generated in degree 5 when $g = 2$, which is done in Lemma ~\ref{lem:genus-2-generation-5}.
 After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation-5}.
@@
 \end{align*}
-is surjective if $n \geq 4$. In particular, $R_L$ is generated in degree at most $5.$
+is surjective if $n \geq 4$. In particular, $R_\halfcan$ is generated in degree at most $5.$
 \end{lem}
@@
 %Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
-%Then, $R_L$ is generated in degree at most $5$.
+%Then, $R_\halfcan$ is generated in degree at most $5$.
 %\end{lem}
 %\begin{proof}
-%By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_L$ has no minimal generators in degree 6.
+%By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_\halfcan$ has no minimal generators in degree 6.
 %Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
@@
 Hence, we know $L$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
-In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_L$ is generated in degree $\leq 3$.
+In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_\halfcan$ is generated in degree $\leq 3$.
 %
@@
 By Voight and Zurieck-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
-Hence, $R_L$ is generated in degree at most 5.
+Hence, $R_\halfcan$ is generated in degree at most 5.
 %\end{proof}
 
-The next step is to bound the degrees of the relations of $R_L$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
+The next step is to bound the degrees of the relations of $R_\halfcan$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
 %The idea of the proof of Proposition ~\ref{prop:relation-10} is to 
@@
 )$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots
-, x_n$ of $R_L$ so that we obtain a surjection $\phi: k[x_1, \ldots
-, x_n] \twoheadrightarrow R_L$ with kernel $I_L$. Let $I_{L, d}$ be
-the $d^\text{th}$ graded piece of $I_L$ and define
+, x_n$ of $R_\halfcan$ so that we obtain a surjection $\phi: k[x_1, \ldots
+, x_n] \twoheadrightarrow R_\halfcan$ with kernel $I_\halfcan$. Let $I_{\halfcan, d}$ be
+the $d^\text{th}$ graded piece of $I_\halfcan$ and define
 \[
-	J_{L,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{L,d-j}.
+	J_{\halfcan,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{\halfcan,d-j}.
 \]
@@
 \label{lem:reducing-degree}
-Let $(X, \Delta, L)$ be a log spin curve of genus $g \geq 2,$ so
-that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_L$ so
+Let $(X, \Delta, \halfcan)$ be a log spin curve of genus $g \geq 2,$ so
+that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_\halfcan$ so
 that we obtain a surjection $\phi: k[x_1, \ldots, x_n]
-\twoheadrightarrow R_L$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
+\twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
 \ldots, x_n]_2$ be two elements so that $\newspan(\phi(s_1), \phi(s_2))
-= V \subseteq H^0(X, 2L)$ is basepoint-free. For any $f \in
+= V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
 k[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
-k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h = f \bmod J_{L, d}.$
+k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h = f \bmod J_{\halfcan, d}.$
 \end{lem}
@@
 By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$
+We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan,\deg a_i}.$
 
@@
 \begin{align*}
-	V \otimes H^0((\deg f-\deg x_i -2)L) \rightarrow H^0((\deg f-\deg x_i)L)
+	V \otimes H^0((\deg f-\deg x_i -2)\halfcan) \rightarrow H^0((\deg f-\deg x_i)\halfcan)
 \end{align*}
@@
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Choosing $g_i,h_i$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have $a_i \equiv s_1 g_i + s_2 h_i \bmod I_{L,\deg a_i}$, as claimed.
+Choosing $g_i,h_i\in k[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have $a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan,\deg a_i}$, as claimed.
+\todo{Peter: Maybe this paragraph could be made a little easier to read?}
 
@@
 \label{prop:relation-10}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -; \delta)$
- with $g \geq 2$ and $\Delta > 0.$ Then $I_L$ is generated in
+Let $(X, \Delta, \halfcan)$ be a log spin curve of signature $(g; -; \delta)$
+ with $g \geq 2$ and $\Delta > 0.$ Then $I_\halfcan$ is generated in
 degree at most degree at most $10$.
@@
 \begin{proof}
-Suppose $f \in I_L$ with $\deg f \geq 11$. To complete the proof,
-it suffices to show $f \in I_{L,d}'$. By Lemma
+Suppose $f \in I_\halfcan$ with $\deg f \geq 11$. To complete the proof,
+it suffices to show $f \in I_{\halfcan,d}'$. By Lemma
 ~\ref{lem:reducing-degree}, it suffices to show $s_1 g + s_2 h \in
-I_{L, d}'$ where $\phi(s_ 1),\phi(s_2) \in H^0(X, 2L)$ are two sections
+I_{\halfcan, d}'$ where $\phi(s_ 1),\phi(s_2) \in H^0(X, 2L)$ are two sections
 so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
@@
 %\label{rem:relations_generation_ten}
-%Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_L$ has a
+%Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_\halfcan$ has a
 %relation in degree 10. Therefore, the bound from Proposition
@@
 ~\ref{lem:generation-5} and Proposition ~\ref{prop:relation-10} to 
-complete the base case when $L = L_X$ and then apply Lemma
+complete the base case when $L = \halfcan_X$ and then apply Lemma
 ~\ref{lem:sat-1}, Lemma ~\ref{lem:sat-2}, and Lemma
@@
 %\label{eg:exceptional-1-0}
-%In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_L \cong k[y]$, where $y$ is a generator in degree 2. 
+%In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_\halfcan \cong k[y]$, where $y$ is a generator in degree 2. 
 %\end{example}
@@
 For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-%We find that $R_L \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
+%We find that $R_\halfcan \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
 %\end{example}
@@
 %\label{eg:exception-1-e}
-%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_L \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Lemma ~\ref{lem:raise-stacky-order} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
+%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_\halfcan \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Lemma ~\ref{lem:raise-stacky-order} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
 %Furthermore, $\deg u = 2, \deg y_i = i$.
@@
 In this case, let $L_X \in \di X$ satisfy $2L_X \sim K_X + \Delta$.
-We have $\deg L_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor.
+We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor.
 Thus, without loss of generality, we may assume $L$ is an effective divisor.
@@
 
-Since $\Delta = 0$, we may write $L = L_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $L_X = 0$ or $L_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
+Since $\Delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
 
@@
 \noindent
-{\sf Case 2a: $L_X = P - Q, P \neq Q$}
+{\sf Case 2a: $\halfcan_X = P - Q, P \neq Q$}
 
@@
 Observe that $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$.
-However, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, and the relation in degree $12$ coming from $R_{L'}$, lies in a degree less than $2 \cdot 7 = 14$.
+However, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, and the relation in degree $12$ coming from $R_{\halfcan'}$, lies in a degree less than $2 \cdot 7 = 14$.
 Therefore, the Theorem holds for $L' = P - Q + \frac{3}{7}P_2$.
@@
 		the notion of a generic initial ideal is defined, which 
-		encapsulates the idea of whether the relations for $R_L$ are 
+		encapsulates the idea of whether the relations for $R_\halfcan$ are 
 		generically chosen, in a precise sense. The proof of Theorem
@@
 		\end{question}
-		Suppose the generators and relations of $R_{L_X}$ are known, 
+		Suppose the generators and relations of $R_{\halfcan_X}$ are known, 
 		where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the 
@@
 			divisor $L \in \di X$, can one write down a set of minimal 
-			generators and minimal relations for $R_L$? If so, can one give the 
-			generic ideal of $R_L$ or the generic initial ideal of $R_L$, as 
+			generators and minimal relations for $R_\halfcan$? If so, can one give the 
+			generic ideal of $R_\halfcan$ or the generic initial ideal of $R_\halfcan$, as 
 			defined in Voight and Zureick Brown \cite[Definition 2.2.7]
@@
 		answered affirmatively one would be able to write down explicit 
-		generators and relations for $R_L$ on a stacky curve, essentially 
+		generators and relations for $R_\halfcan$ on a stacky curve, essentially 
 		by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
@@
 	\item While Theorem ~\ref{thm:main} gives a minimal set of 
-		generators for the log spin canonical ring $R_L,$ the set of 
+		generators for the log spin canonical ring $R_\halfcan,$ the set of 
 		relations is not minimal. In many of the $g = 0$ and $g=1$ cases, 
 		it is not too difficult to see that our inductive procedure also 
-		yields a minimal set of relations for $R_L$. One might investigate 
+		yields a minimal set of relations for $R_\halfcan$. One might investigate 
 		whether the generators and relations given by the inductive proof 

### 2015-07-01 stacky_write_up/spin_cring.tex
read over intro

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 \newcommand\BH{{\mathbb H}}
+\newcommand\bO{{\mathbf O}}
+\newcommand\CC{{\mathcal C}}
 \newcommand\BN{{\mathbb N}}
@@
 \newcommand\BP{{\mathbb P}}
+\newcommand\BBZ{{\mathbb Z}}
+\newcommand\uR{\underline{R}}
+\newcommand\uZ{\underline{\BBZ}}
+\newcommand\CF{{\mathcal F}}
+\newcommand\uCF{\underline{{\mathcal F}}}
 \newcommand\BZ{{\mathbb Z}}
 \newcommand\BA{{\mathbb A}}
+\newcommand\fa{{\mathfrak a}}
+\newcommand\fp{{\mathfrak p}}
+\newcommand\fq{{\mathfrak q}}
+\newcommand\fm{{\mathfrak m}}
+\newcommand\so{{\mathscr O}}
+\newcommand\sg{{\mathscr G}}
+\newcommand\sx{\mathscr X}
 
@@
 \newcommand \rk{\text{rk }}
+\DeclareMathOperator\di{Div}
 \newcommand \depth{\text{depth }}
@@
 
-\DeclareMathOperator\di{Div}
-\newcommand\sx{\mathscr X}
 \newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
@@
 
-In particular, we would like to bound the degrees in which the
-log spin canonical ring and its relations are generated. Let
+In particular, we bound the degrees of generators and relations of a
+log spin canonical ring. Let
 $\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
 e_r; \delta)$. The application of O'Dorney's work to log spin
-canonical rings gives a large bound for the genus zero case in
-terms of least common multiples of the $e_i$'s \cite[Chapter 5]
+canonical rings gives a weak bound in the case $g = 0$, in
+terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
 {dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $3e$
-and relation degrees by $6e$ when $\halfcan$ is effective
+rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1,\ldots, e_r)$
+and relation degrees by $3 \cdot \max(5, e_1,\ldots, e_r)$ when $\halfcan$ is effective
 \cite[Corollary 10.4.6]{vzb:stacky}.
 
-These bounds, particularly those derived from O'Dorney's work
-in the genus zero case, are far from tight and do not collectively
+These bounds are far from tight and do not collectively
 cover all cases in all genera. The main theorem of this paper
-gives significantly tighter bounds across all cases in all
-genera on the generator and relation degrees of log spin canonical
-rings.
+gives significantly tighter bounds for any log spin canonical ring on a log spin curve.
 
@@
 elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
-relations generated in degrees up to $2e$
+relations generated in degrees at most $2e$,
 so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as listed in Table ~\ref{table:g-1-exceptional} for
+cases, as given in Table ~\ref{table:g-1-exceptional} for
 signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
@@
 \label{rem:main-weaker-assumptions}
-In fact, the theorem only needs to assume that the stacky curve
+In fact, the proof of Theorem ~\ref{thm:main} holds not only for log divisors, which must have distinct points, but also for arbitrary effective divisors
+$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one only need assume that the stacky curve
 is separably rooted, i.e. the residue field at each stacky point
-is separable. Furthermore, the proof works even when letting
-$\Delta$ be any effective divisor rather than just a log divisor.
+is separable.
 \end{rem}
 
-This theorem is proven in three different genus cases, each of
-which use similar inductive processes. The genus $g \geq 2$ case is
+Theorem ~\ref{thm:main} is proven seperately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$, each of
+which uses a similar inductive process. The genus $g \geq 2$ case is
 proven in Theorem ~\ref{thm:g-high-main}. In Theorem
@@
 ~\ref{thm:g-0-main}, we also give the respective
-genus one and genus zero results after using a similar induction
-process while dealing with more complicated base cases and
+genus one and genus zero results after dealing with more involved base cases and
 exceptional cases.
@@
 obtain bounds on the degrees of the generators and relations, but
-also yield explicit systems of generators and the initial ideal of
+also yield explicit systems of generators and an explicit initial ideal of
 relations. Furthermore, our proof of the high genus case also
 provides an inductive procedure for explicitly determining the 
-generators and initial ideal of relations for log spin canonical
+generators and initial ideal of relations of log spin canonical
 rings. Many explicit systems of generators and relations are
@@
 \cite[Section III.4]{neves:halfcan}.
+
+Furthermore, the explicit construction of generators and relations also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
+That is, in almost all cases, there is a generator of the log spin canonical ring in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$.
+Furthermore, there are many infinite families of cases which have a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
 \end{rem}
 
-The main theorem of this paper provides the following application
-to modular forms when combined with a result from Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} which itself
-follows from the classical work of Kodaira--Spencer
+The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, provides the following application
+to modular forms. Note that the result from Voight and
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately from the classical work of Kodaira--Spencer
 \cite{kodaira-spencer:deformations}.
@@
 associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
-\ldots, e_r; \delta)$. Then the ring of modular forms
-$M(\Gamma) := \bigoplus_{k = 0}^{\infty} M_k(\Gamma)$ is
+\ldots, e_r; \delta)$. Then, the ring of modular forms
+$M(\Gamma)$ is
 generated as a $\BC$-algebra by elements of degree at most $e = \max
@@
 Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct on the stabilizer order of and number of stacky points. To this end, we first review important background in
+proof will be to induct on the stabilizer order and number of stacky points. To this end, we first review important background in
 Section ~\ref{sec:background}. Then, we develop various inductive
@@
 ~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
-~\ref{thm:main} in the high genus, genus
-one, and genus zero cases respectively. Finally, in Section
+~\ref{thm:main} in the genus $ g \geq 2$, genus
+$g = 1$, and genus $g = 0$ cases respectively. Finally, in Section
 ~\ref{sec:further-questions}, we pose several questions for future
@@
 \label{sec:background}
-Here we denote various definitions and useful notation that will be
+Here we collect various definitions and useful notation that will be
 used throughout the paper. Many of the conventions come from existing
@@
 = V \subseteq H^0(X, 2L)$ is basepoint-free. For any $f \in
-k[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
+k[x_1, \ldots, x_n]$ such that $\deg f \leq 11,$ there exist $g, h \in
 k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h = f \bmod J_{L, d}.$
@@
 % Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
-By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$
-
+By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Then, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
+We will next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{L,\deg a_i}.$ 
 By Lemma ~\ref{lem:generation-5},
@@
 \end{align*}
-is surjective, and $\deg f \geq 11$ implies that
-$\deg a_i =\deg f - \deg x_i -2 \geq 4.$
+is surjective, and $\deg f \leq 11$ guarantees
+$\deg f - \deg a_i -2 \geq 4.$
 In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.

### 2015-07-01 stacky_write_up/spin_cring.tex

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 \usepackage{float}
+\usepackage{caption}
 
@@
 \DeclareMathOperator{\newspan}{span}
+\captionsetup[table]{belowskip = 4pt}
 
@@
 \begin{longtable}	{| c || c | c |}	
-	\caption{Genus 1 Base Cases}
-	\label{table:g-1-base}
-
-	\tabularnewline
-
 	\hline
@@
 
+	\caption{Genus 1 Base Cases}
+	\label{table:g-1-base}
+
 %	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
@@
 \begin{longtable}	{| c || c | c |}
-	\caption{Genus 1 Exceptional Cases}
-	\label{table:g-1-exceptional}
-
-	\tabularnewline
-
 	\hline
@@
 	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
+
+	\caption{Genus 1 Exceptional Cases}
+	\label{table:g-1-exceptional}
 
@@
 
-There are two main cases: when $\delta \geq 2$ and when $\delta = 0$
-, where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}
-. In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
+There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
+where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
+In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
 result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
@@
 	{| c | c || c |}
-	\caption{Genus 0 Saturation}
-	\label{table:g-0-sat}
-
-	\tabularnewline
-
 	\hline
@@
 	$(0; e_1, \ldots, e_r; 0)$ & not listed above & $3$ \\	\hline
+
+	\caption{Genus 0 Saturation}
+	\label{table:g-0-sat}
 \end{longtable}
@@
 	{| c || c | c | c |}
-	\caption{Genus 0 Base Cases}
-	\label{table:g-0-base-cases}
-
-	\tabularnewline
-
 	\hline
@@
 	(k) &	(0; 3, 3, 3, 3, 3; 0) & \{1, 2, 3, 4, 5\} & 5\\ \hline
+
+	\caption{Genus 0 Base Cases}
+	\label{table:g-0-base-cases}
 \end{longtable}
@@
 	{| c || c | c | c |}
-	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
-	\label{table:g-0-base-cases-degrees}
-
-	\tabularnewline
-
 	\hline
@@
 	(k) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
+
+	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
+	\label{table:g-0-base-cases-degrees}
 \end{longtable}
@@
 	{| c | c | c || c | c |}
-	\caption{Genus 0 Non-Effective Base Cases (Ad-iii)}
-	\label{table:g-0-base-cases-admissibility}
-
-	\tabularnewline
-
 	\hline
@@
 	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0 \\ \hline
+
+	\caption{Genus 0 Non-Effective Base Cases (Ad-iii)}
+	\label{table:g-0-base-cases-admissibility}
 \end{longtable}
@@
 	{| c || c | c | c |}
-	\caption{Genus 0 Exceptional Cases}
-	\label{table:g-0-exceptional}
-
-	\tabularnewline
-
 	\hline
@@
 	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $3$ \\	\hline
+
+	\caption{Genus 0 Exceptional Cases}
+	\label{table:g-0-exceptional}
 \end{longtable}

### 2015-07-01 stacky_write_up/spin_cring.tex
customlabel all Ad's, table $ fix

@@
 
+\makeatletter
+\newcommand{\customlabel}[2]{%
+   \protected@write \@auxout {}{\string \newlabel {#1}{{#2}{\thepage}{#2}{#1}{}} }%
+   \hypertarget{#1}{#2}
+}
+\makeatother
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align*}
-	R(X,K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
+	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
 \end{align*}
@@
 \begin{enumerate}
-	\item[(Ad-i)] First, 
+	\item[\customlabel{Ad-i}{(Ad-i)}] First, 
 	\begin{align*}
@@
 	\end{align*}
-		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
+		\item[\customlabel{Ad-ii}{(Ad-ii)}] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
 		\begin{align*}
@@
 		\end{align*}
-	\item[(Ad-iii)] Third, we have
+	\item[\customlabel{Ad-iii}{(Ad-iii)}] Third, we have
 		\begin{align*}
@@
 $y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
+\ref{Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{Ad-ii} We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
@@
 \halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
+\frac{9}{3} \rfloor - 9 = 2$, so \ref{Ad-iii} is satisfied and
 $(\sigma, \sx', J)$ is admissible.
@@
 We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, (Ad-i) holds.
-We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric.
+Hence, \ref{Ad-i} holds.
+We next check \ref{Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
 Here, by construction
@@
 \end{cases}.$$
-Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
-Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{Ad-ii} holds.
+Finally, to check \ref{Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
 \end{example}
@@
 %\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
 %\end{rem}
@@
 %\begin{proof}
-%To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
-Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
-Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
-%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
+%To show \ref{Ad-i} and \ref{Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{Ad-i}.
+Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{Ad-ii} satisfied so $\frac{-\ord_{Q_l}
+%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{Ad-ii} follows in genus 0?}
 %
@@
 %\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (Ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 %\end{itemize}
@@
 
-The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+The following Lemma will slightly strengthen condition \ref{Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 \label{lem:admissible_inequality}
-For any $z$ as in condition (Ad-ii) of definition ~\ref{defn:admissible} the inequality (Ad-ii) implies the
+For any $z$ as in condition \ref{Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{Ad-ii} implies the
 tighter inequality that
@@
 \begin{proof}
-We know by (Ad-ii) that
+We know by \ref{Ad-ii} that
 
@@
 \begin{proof}
-Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
+Each of the conditions \ref{Ad-i}, \ref{Ad-ii}, and \ref{Ad-iii} hold for $W$
 if they hold for $J$.
@@
 \noindent
-The assumption (Ad-iii) implies
+The assumption \ref{Ad-iii} implies
 \begin{align*}
@@
 
-By part (a), condition (Ad-ii), and Lemma
+By part (a), condition \ref{Ad-ii}, and Lemma
 ~\ref{lem:admissible_inequality} we have
@@
 {\bf Part (d):}
-To check (d), we show (Ad-i),(Ad-ii), and (Ad-iii) are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
-i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
+To check (d), we show \ref{Ad-i},\ref{Ad-ii}, and \ref{Ad-iii} are satisfied. We know \ref{Ad-i} holds by part (b), taking the $y_{
+i, e_i}$ as the generators in degree $e_i$. Next, \ref{Ad-ii} is
 strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
-Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that (Ad-iii) holds for $d > 0$
+Finally, if \ref{Ad-iii} holds for $e$ then it holds for $e + 2$ by
+definition. This is where we use that \ref{Ad-iii} holds for $d > 0$
 and not just for $d = 0$.
@@
 
+\rm{
 \begin{longtable}
@@
 
-	(a) & (0; 3, 3, 11; 0) & \{3\} & 11\\	\hline
-
-	(b) & (0; 3, 5, 9; 0) & \{3\}	& 9\\ \hline
-
-	(c) & (0; 3, 7, 7; 0) & \{2, 3\}	& 7\\ \hline
-
-	(d) & (0; 5, 5, 7; 0) & \{3\}	& 7\\ \hline
-
-	(e) & (0; 5, 7, 7; 0) & \{2, 3\}	& 7\\ \hline
-
-	(f) & (0; 7, 7, 7; 0) & \{1, 2, 3\}	& 7\\ \hline
-
-	(g) & (0; 3, 3, 3, 5; 0) & \{4\} & 5\\ \hline
-
-	(h) & (0; 3, 3, 5, 5; 0) & \{3, 4\} & 5\\ \hline
-
-	(i) & (0; 3, 5, 5, 5; 0) & \{2, 3, 4\} & 5\\ \hline
-
-	(j) & (0; 5, 5, 5, 5; 0) & \{1, 2, 3, 4\} & 5\\ \hline
-
-	(k) &	(0; 3, 3, 3, 3, 3; 0) & \{1, 2, 3, 4, 5\} & 5\\ \hline
+	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $11$ \\	\hline
+
+	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$	& $9$ \\ \hline
+
+	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
+
+	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$	& $7$ \\ \hline
+
+	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
+
+	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$	& $7$ \\ \hline
+
+	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $5$ \\ \hline
+
+	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $5$ \\ \hline
+
+	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $5$ \\ \hline
+
+	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ \\ \hline
+
+	(k) &	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ \\ \hline
 
@@
 \end{longtable}
+}
 
@@
 
-	(a) & \{3, 7, 9, 11\} & \{14, 18\} & 11\\	\hline
-
-	(b) & \{3, 5, 7, 9\} & \{12, 14\}	& 9\\ \hline
-
-	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
-
-	(d) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
-
-	(e) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline
-
-	(f) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline
-
-	(g) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline
-
-	(h) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline
-
-	(i) & \{3, 3, 4, 5, 5, 5\} &
-	\{8, 8, 8, 9, 9, 9, 10, 10, 10\} & 5\\ \hline
-
-	(j) & \{3, 3, 4, 5, 5, 5, 5\} &
-	\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\} & 5\\ \hline
-
-	(k) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
+	(a) & $\{3, 7, 9, 11\}$ & $\{14, 18\}$ & $11$ \\	\hline
+
+	(b) & $\{3, 5, 7, 9\}$ & $\{12, 14\}$ & $9$ \\ \hline
+
+	(c) & $\{3, 5, 7, 7\}$ & $\{10, 14\}$ & $7$ \\ \hline
+
+	(d) & $\{3, 5, 5, 7\}$ & $\{10, 12\}$	& $7$ \\ \hline
+
+	(e) & $\{3, 5, 5, 7, 7\}$ & $\{10, 10, 12, 12, 14\}$	& $7$ \\ \hline
+
+	(f) & $\{3, 5, 5, 7, 7, 7\}$ & $\{10, 10, 10, 12, 12, 12, 14, 14, 14\}$	& $7$ \\ \hline
+
+	(g) & $\{3, 3, 4, 5\}$ & $\{8, 9\}$ & $5$ \\ \hline
+
+	(h) & $\{3, 3, 4, 5, 5\}$ & $\{8, 8, 9, 9, 10\}$ & $5$ \\ \hline
+
+	(i) & $\{3, 3, 4, 5, 5, 5\}$ &
+	$\{8, 8, 8, 9, 9, 9, 10, 10, 10\}$ & $5$ \\ \hline
+
+	(j) & $\{3, 3, 4, 5, 5, 5, 5\}$ &
+	$\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\}$ & $5$ \\ \hline
+
+	(k) &	$\{3, 3, 3, 4, 4, 5\}$ & $\{6, 7, 7, 8, 8, 8, 9, 9, 10\}$ & $5$ \\ \hline
 
@@
 We can also always find a presentation for these cases such that
-they satisfy (Ad-i) and (Ad-ii) and that $\initial(I')$ is
+they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
 generated by products of two monomials. Again, the procedure for
@@
 
-Furthermore, each case always satisfies (Ad-iii) as demonstrated below.
+Furthermore, each case always satisfies \ref{Ad-iii} as demonstrated below.
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
@@
 
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0 \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0 \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0 \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0 \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0 \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0 \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0 \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0 \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0 \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0 \\ \hline
-
-	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0 \\ \hline
-
-	\caption{Genus 0 Non-Effective Base Cases (Ad-iii)}
+	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $1$ & $0$ \\	\hline
+
+	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
+
+	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & $2$ & $0$ \\ \hline
+
+	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
+
+	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
+
+	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $3$ & $0$ \\ \hline
+
+	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $2$ & $0$ \\ \hline
+
+	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $3$ & $0$ \\ \hline
+
+	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $4$ & $0$ \\ \hline
+
+	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ & $0$ \\ \hline
+
+	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ & $0$ \\ \hline
+
+	\caption{Genus 0 Non-Effective Base Cases \ref{Ad-iii}}
 	\label{table:g-0-base-cases-admissibility}

### 2015-07-01 stacky_write_up/spin_cring.tex
edited section 5

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 
-In particular, we bound the degrees of generators and relations of a
-log spin canonical ring. Let
+In particular, we would like to bound the degrees in which the
+log spin canonical ring and its relations are generated. Let
 $\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
 e_r; \delta)$. The application of O'Dorney's work to log spin
-canonical rings gives a weak bound in the case $g = 0$, in
-terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
+canonical rings gives a large bound for the genus zero case in
+terms of least common multiples of the $e_i$'s \cite[Chapter 5]
 {dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1,\ldots, e_r)$
-and relation degrees by $3 \cdot \max(5, e_1,\ldots, e_r)$ when $\halfcan$ is effective
+rings, Voight and Zureick-Brown bounded generator degrees by $3e$
+and relation degrees by $6e$ when $\halfcan$ is effective
 \cite[Corollary 10.4.6]{vzb:stacky}.
 
-These bounds are far from tight and do not collectively
+These bounds, particularly those derived from O'Dorney's work
+in the genus zero case, are far from tight and do not collectively
 cover all cases in all genera. The main theorem of this paper
-gives significantly tighter bounds for any log spin canonical ring on a log spin curve.
+gives significantly tighter bounds across all cases in all
+genera on the generator and relation degrees of log spin canonical
+rings.
 
@@
 elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
-relations generated in degrees at most $2e$,
+relations generated in degrees up to $2e$
 so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as given in Table ~\ref{table:g-1-exceptional} for
+cases, as listed in Table ~\ref{table:g-1-exceptional} for
 signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
@@
 \label{rem:main-weaker-assumptions}
-In fact, the proof of Theorem ~\ref{thm:main} holds not only for log divisors, which must have distinct points, but also for arbitrary effective divisors
-$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one only need assume that the stacky curve
+In fact, the theorem only needs to assume that the stacky curve
 is separably rooted, i.e. the residue field at each stacky point
-is separable.
+is separable. Furthermore, the proof works even when letting
+$\Delta$ be any effective divisor rather than just a log divisor.
 \end{rem}
 
-Theorem ~\ref{thm:main} is proven seperately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$, each of
-which uses a similar inductive process. The genus $g \geq 2$ case is
+This theorem is proven in three different genus cases, each of
+which use similar inductive processes. The genus $g \geq 2$ case is
 proven in Theorem ~\ref{thm:g-high-main}. In Theorem
@@
 ~\ref{thm:g-0-main}, we also give the respective
-genus one and genus zero results after dealing with more involved base cases and
+genus one and genus zero results after using a similar induction
+process while dealing with more complicated base cases and
 exceptional cases.
@@
 obtain bounds on the degrees of the generators and relations, but
-also yield explicit systems of generators and an explicit initial ideal of
+also yield explicit systems of generators and the initial ideal of
 relations. Furthermore, our proof of the high genus case also
 provides an inductive procedure for explicitly determining the 
-generators and initial ideal of relations of log spin canonical
+generators and initial ideal of relations for log spin canonical
 rings. Many explicit systems of generators and relations are
@@
 \cite[Section III.4]{neves:halfcan}.
-
-Furthermore, the explicit construction of generators and relations also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
-That is, in almost all cases, there is a generator of the log spin canonical ring in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$.
-Furthermore, there are many infinite families of cases which have a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
 \end{rem}
 
-The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, provides the following application
-to modular forms. Note that the result from Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately from the classical work of Kodaira--Spencer
+The main theorem of this paper provides the following application
+to modular forms when combined with a result from Voight and
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} which itself
+follows from the classical work of Kodaira--Spencer
 \cite{kodaira-spencer:deformations}.
@@
 associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
-\ldots, e_r; \delta)$. Then, the ring of modular forms
-$M(\Gamma)$ is
+\ldots, e_r; \delta)$. Then the ring of modular forms
+$M(\Gamma) := \bigoplus_{k = 0}^{\infty} M_k(\Gamma)$ is
 generated as a $\BC$-algebra by elements of degree at most $e = \max
@@
 Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct on the stabilizer order and number of stacky points. To this end, we first review important background in
+proof will be to induct on the stabilizer order of and number of stacky points. To this end, we first review important background in
 Section ~\ref{sec:background}. Then, we develop various inductive
@@
 ~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
-~\ref{thm:main} in the genus $ g \geq 2$, genus
-$g = 1$, and genus $g = 0$ cases respectively. Finally, in Section
+~\ref{thm:main} in the high genus, genus
+one, and genus zero cases respectively. Finally, in Section
 ~\ref{sec:further-questions}, we pose several questions for future
@@
 \label{sec:background}
-Here we collect various definitions and useful notation that will be
+Here we denote various definitions and useful notation that will be
 used throughout the paper. Many of the conventions come from existing
@@
 \label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ \todo{The notation i was using for these throughout the paper was $\halfcan$ and $\halfcan'$ without the $\sx$ subscripts.
+Let $(\sx, \Delta, \halfcan)$ and $(\sx', \Delta, \halfcan')$ \todo{The notation i was using for these throughout the paper was $\halfcan$ and $\halfcan'$ without the $\sx$ subscripts.
 We should make one of them consistent with the other.} be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
@@
 k[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
-k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h = f \bmod J_{\halfcan, d}.$
+k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, d}.$
 \end{lem}
@@
 it suffices to show $f \in I_{\halfcan,d}'$. By Lemma
-~\ref{lem:reducing-degree}, it suffices to show $s_1 g + s_2 h \in
+~\ref{lem:reducing-degree}, this is the same as checking $s_1 g + s_2 h \in
 I_{\halfcan, d}'$ where $\phi(s_ 1),\phi(s_2) \in H^0(X, 2L)$ are two sections
@@
 
-We now concisely summarize what we have shown.
+We now summarize what we have shown.
 
@@
 We are ready to prove our main theorem, Theorem ~\ref{thm:main} in the case
-$g \geq 2$. The idea of the proof is to use Lemma
-~\ref{lem:generation-5} and Proposition ~\ref{prop:relation-10} to 
+$g \geq 2$. The idea of the proof is to use Corollary \ref{cor:g-2-presentation-bound} to 
 complete the base case when $L = \halfcan_X$ and then apply Lemma
@@
 \label{thm:g-high-main}
-Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ be a log spin curve so
-that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
+Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ be a log spin curve 
+%so that $\sx$ has 
+with signature $(g; e_1, \ldots, e_r; \delta)$. Then the
 log spin canonical ring
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, \lfloor d L \rfloor)
-\end{align*}
-
-\noindent
-is generated as a $k$-algebra by elements of degree at most $e =
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d L )
+\end{align*}
+
+\noindent
+is generated as a $k$-algebra by elements in degree at most $e =
 \max(5, e_1, \ldots, e_r)$ with minimal relations in degree at most $2e$.
@@
 %Furthermore, there are even stronger bounds for the following
-%exceptional cases (X, :
+%exceptional cases X, :
 
 \begin{proof}
-As the base case, let $\halfcan_X \in \di X$ satisfy $2\halfcan_X \sim 2 K_X + \Delta$.
-
+As the base case, let $\halfcan=\halfcan_X \in \di X$ satisfy $2\halfcan \sim 2 K_X + \Delta$.
 By Corollary ~\ref{cor:g-2-presentation-bound}, the theorem holds for $(\sx, \Delta,
-\halfcan_X)$. Next, consider a divisor of the form $\halfcan' =
-\halfcan_X + \frac{1}{3} P_i$. Then, the theorem holds for $(\sx',
-\Delta, \halfcan')$ by Lemma ~\ref{lem:sat-2}
- if $P_i$ is a basepoint of $\halfcan'$ or by Lemma
-~\ref{lem:sat-1} if $P_i $ is not a basepoint of $L'$. Note,
-in the case $P$  is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann Roch since $\frac{\beta}{\alpha} = \frac{3}{1}=3$.
-In this case, we claim the theorem holds for $(\sx',\Delta, L')$.
-Indeed, the bound on the generators holds by part (a) of Lemmas
+\halfcan_X)$.
+
+Next, suppose the theorem holds for $\halfcan' = \halfcan_X+ \sum_{i=1}^{r-1} \frac{1}{3}P_i$ and take a divisor of the form $\halfcan = \halfcan_X + \sum_{i=1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
+If $P_r$ is a basepoint of $L'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
+Otherwise, $P_r$ is not a basepoint of $\halfcan'$, meaning that in particular $R_{\halfcan'}$ is saturated in 1.
+Therefore, since $P_r$ is a not basepoint of $\halfcan'$, Equation
+~\ref{eqn:deg1-sat-ind} holds by Riemann Roch
+% since $\frac{\beta}{\alpha} = \frac{3}{1}=3$. 
+In this case, we claim the theorem holds for $L$ by Lemma ~\ref{lem:sat-1}.  In particular, the bound on the generators holds by part (a) of Lemmas
 ~\ref{lem:sat-2} and ~\ref{lem:sat-1},
 and the bound on the relations holds by part (b) of Lemmas
-~\ref{lem:sat-2} and ~\ref{lem:sat-1}.
-
-Applying this argument $r-1$ additional times, we obtain that the Theorem holds for $(\sx', \Delta, \halfcan')$ where $\sx'$ has signature $(g;3,\ldots, 3;\delta)$ with $g \geq 2$.
-Therefore, by Corollary
+~\ref{lem:sat-2} and ~\ref{lem:sat-1}.\todo{Peter: Can we get rid of this last sentence?}
+
+We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g\ge 2$ and signature $(g;3,\ldots, 3;\delta)$. Therefore, by Corollary 
 ~\ref{cor:raise-stacky-order}, this theorem 

### 2015-07-01 stacky_write_up/spin_cring.tex
editing background, up to sat

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 
-\makeatletter
-\newcommand{\customlabel}[2]{%
-   \protected@write \@auxout {}{\string \newlabel {#1}{{#2}{\thepage}{#2}{#1}{}} }%
-   \hypertarget{#1}{#2}
-}
-\makeatother
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{align*}
-	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
+	R(X,K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
 \end{align*}
@@
 In fact, the proof of Theorem ~\ref{thm:main} holds not only for log divisors, which must have distinct points, but also for arbitrary effective divisors
-$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one only need assume that the stacky curve
+$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
 is separably rooted, i.e. the residue field at each stacky point
@@
 
-\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e.
-Robin: Aren't the base cases suitable examples?
-Aaron: Those don't show it for general e, do they?
-I don't think we really need an example, just a remark somewhere that one cannot really hope to do better than e, 2e somewhere.}
-
 \section{Background}
 \label{sec:background}
-Here we collect various definitions and useful notation that will be
+Here we collect various definitions and notation that will be
 used throughout the paper. Many of the conventions come from existing
@@
 used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
-Saint-Donat \cite{saint-donat:proj}, the book of Arbarello--
+Saint-Donat \cite{saint-donat:proj}, Arbarello--
 Cornalba--Griffiths--Harris \cite[Section III.2]
@@
 Chapter 5]{vzb:stacky}.
+
+For the remainder of this paper, fix an algebraically closed field $k$.
+This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closue.
 
@@
 
-When viewed in the formalism of stacks, all stacky curves will be assumed to be tame and
-$k$ will always be algebraically closed. We also assume that the
+In this paper, all stacky curves are assumed to be tame and
+$k$ will is assumed to be algebraically closed. We also assume that the
 stacky curves are separably rooted, i.e. the residue field of each
@@
 
-With the close relation to stacks in mind, for simplicity, the remainder of this paper is primarily phrased using the language
+With this stacks-theoretic description in mind, for simplicity, the remainder of this paper is primarily phrased using the language
 of Weil divisors.
@@
 In order to study objects associated with stacky curves, it is often
-useful to consider them in the context of ordinary schemes.
+useful to consider them in the context of schemes (instead of in the context of stacks).
 
@@
 \label{defn:coarse-space}
-Let $\sx$ be a stacky curve over $k$ with stacky points $P_1, \ldots,
+Let $\sx$ be a stacky curve over $k$ with coarse space $X$ and stacky points $P_1, \ldots,
 P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
 Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
-genus $g$. Then $X$ is the \textbf{coarse space} associated to $\sx$
-if
-
+genus $g$. Then, we notate
 \[
@@
 
-We can equip stacky curves with a divisor $\Delta$ that is a 
+We can equip stacky curves with a log divisor $\Delta$ that is a 
 sum of distinct points each with trivial stabilizer. A divisor
@@
 \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
-
-The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
-and the study of their canonical rings is the main focus of
-the work by Voight and Zureick-Brown \cite{vzb:stacky}.
-For this paper, we consider \textbf{log spin curves} which are
-triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
-and a divisor $\halfcan$ which satisfies the property that
-$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
-is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
-We also use $\halfcan_X$ to refer to the spin canonical divisor
-(also known as the half-canonical divisor, semi-canonical divisor, 
-or a theta characteristic in other literature) associated with the
-coarse space $X$ of $  \sx$, i.e. $\halfcan_X$ is a divisor such
-that $2\halfcan \sim K_X$. Furthermore, we use the following
-analogous notations:
 
@@
 
+A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is called a \textbf{log stacky curves}
+and the study of their canonical rings is the main focus of
+the work by Voight and Zureick-Brown \cite{vzb:stacky}.
+For this paper, we consider \textbf{log spin curves} which are
+triples $(\sx, \Delta, \halfcan)$ where $\sx$ is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di \sx$ satisfies
+$2\halfcan \sim K_X + \Delta + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i$. Such a divisor $\halfcan$
+is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
+We use $\halfcan_X := \lfloor L \rfloor $ to refer to the spin canonical divisor
+(also known as the half-canonical divisor, semi-canonical divisor, 
+or theta characteristic) associated to the
+coarse space $X$ of $\sx$, i.e. $\halfcan_X$ is a divisor such
+that $2\halfcan_X \sim K_X + \Delta$. Furthermore, we use the following
+analogous notation:
+
 \begin{defn}
@@
 \end{defn}
+
+\begin{rem}
+Although Definition ~\ref{defn:h0-stacky} may seem fairly ad hoc, it is naturally motivated in the context of stacks.
+See Voight and Zureick-Brown \cite[Lemma 5.4.7]{vzb:stacky} for a proof that Definition ~\ref{defn:h0-stacky} is equivalent to the stack-theoretic description.
+\end{rem}
 
@@
 represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
-:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
+:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D))$.
 If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
-degree component of $R$.
-
-\todo{Note that this result is independence of base field}
+graded component of $R$.
 
@@
 where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
-that $\halfcan \in \di \sx$ by Kodaira--Spencer
-\cite{kodaira-spencer:deformations}. If $e_i$ were even,
-then $\frac{e_i - 1}{2e_i}$ would be in reduced form and
-the denominator would be too large for $\halfcan$ to be
-in $\di \sx$.
-\todo{refine above}
+that $\halfcan \in \di \sx$. If some $e_i$ were even,
+then $\frac{e_i - 1}{2e_i}$ would be in reduced form implying $\halfcan \notin \di \sx$.
 \end{rem}
@@
 is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
-\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
+\rfloor = \deg \Delta + 2(g-1).$
 In particular, we shall often use $\deg \Delta \neq 1$.
@@
 
-\begin{defn}
-\label{def:order-sup}
-If $z$ is a rational section of $\sco(D)$ denote the order of
-zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
-\todo{where to put above?}
-
-We define the notion of the saturation of a divisor, taken from
+\ssec{Definition of Saturation}
+
+We define the notion of the saturation of a divisor, as defined in
 Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
@@
 \label{defn:sat}
-The \textbf{saturation} for a monoid $M \subseteq \BZ_{\geq 0}$,
+The \textbf{saturation} of a monoid $M \subseteq \BZ_{\geq 0}$,
 denoted $\sat(M)$, is the smallest integer $s$ such that $M
@@
 \begin{rem}
-For our purposes, it is useful to call the saturation of the
-effective monoid of a divisor $D$ as the saturation $s$ of the
-divisor $D$ on $\sx$. In this case, the saturation $s :=
-\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
-$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
-\geq s$.
+For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the saturation of $D.$
 \end{rem}
@@
 in a graded polynomial ring.
-
+\todo{possibly compactify or refer to relations}
 \begin{defn}
@@
 \begin{defn}
+\label{def:order-sup}
+If $z$ is a rational section of $\sco(D)$ denote the order of
+zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
+
+\begin{defn}
 \label{defn:admissible}
@@
 \begin{enumerate}
-	\item[\customlabel{Ad-i}{(Ad-i)}] First, 
+	\item[(Ad-i)] First, 
 	\begin{align*}
@@
 	\end{align*}
-		\item[\customlabel{Ad-ii}{(Ad-ii)}] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
+		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
 		\begin{align*}
@@
 		\end{align*}
-	\item[\customlabel{Ad-iii}{(Ad-iii)}] Third, we have
+	\item[(Ad-iii)] Third, we have
 		\begin{align*}
@@
 $y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-\ref{Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{Ad-ii} We may also choose
+(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
@@
 \halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so \ref{Ad-iii} is satisfied and
+\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
 $(\sigma, \sx', J)$ is admissible.
@@
 We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{Ad-i} holds.
-We next check \ref{Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
+Hence, (Ad-i) holds.
+We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric.
 Here, by construction
@@
 \end{cases}.$$
-Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{Ad-ii} holds.
-Finally, to check \ref{Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
+Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
 \end{example}
@@
 %\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
 %\end{rem}
@@
 %\begin{proof}
-%To show \ref{Ad-i} and \ref{Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
-Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{Ad-i}.
-Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{Ad-ii} satisfied so $\frac{-\ord_{Q_l}
-%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{Ad-ii} follows in genus 0?}
+%To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i).
+Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
+%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
 %
@@
 %\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (Ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 %\end{itemize}
@@
 
-The following Lemma will slightly strengthen condition \ref{Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 \label{lem:admissible_inequality}
-For any $z$ as in condition \ref{Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{Ad-ii} implies the
+For any $z$ as in condition (Ad-ii) of definition ~\ref{defn:admissible} the inequality (Ad-ii) implies the
 tighter inequality that
@@
 \begin{proof}
-We know by \ref{Ad-ii} that
+We know by (Ad-ii) that
 
@@
 \begin{proof}
-Each of the conditions \ref{Ad-i}, \ref{Ad-ii}, and \ref{Ad-iii} hold for $W$
+Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
 if they hold for $J$.
@@
 \noindent
-The assumption \ref{Ad-iii} implies
+The assumption (Ad-iii) implies
 \begin{align*}
@@
 
-By part (a), condition \ref{Ad-ii}, and Lemma
+By part (a), condition (Ad-ii), and Lemma
 ~\ref{lem:admissible_inequality} we have
@@
 {\bf Part (d):}
-To check (d), we show \ref{Ad-i},\ref{Ad-ii}, and \ref{Ad-iii} are satisfied. We know \ref{Ad-i} holds by part (b), taking the $y_{
-i, e_i}$ as the generators in degree $e_i$. Next, \ref{Ad-ii} is
+To check (d), we show (Ad-i),(Ad-ii), and (Ad-iii) are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
+i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
 strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
-Finally, if \ref{Ad-iii} holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that \ref{Ad-iii} holds for $d > 0$
+Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
+definition. This is where we use that (Ad-iii) holds for $d > 0$
 and not just for $d = 0$.
@@
 
-\rm{
 \begin{longtable}
@@
 
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $11$ \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$	& $9$ \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$	& $7$ \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$	& $7$ \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $5$ \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $5$ \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $5$ \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ \\ \hline
-
-	(k) &	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ \\ \hline
+	(a) & (0; 3, 3, 11; 0) & \{3\} & 11\\	\hline
+
+	(b) & (0; 3, 5, 9; 0) & \{3\}	& 9\\ \hline
+
+	(c) & (0; 3, 7, 7; 0) & \{2, 3\}	& 7\\ \hline
+
+	(d) & (0; 5, 5, 7; 0) & \{3\}	& 7\\ \hline
+
+	(e) & (0; 5, 7, 7; 0) & \{2, 3\}	& 7\\ \hline
+
+	(f) & (0; 7, 7, 7; 0) & \{1, 2, 3\}	& 7\\ \hline
+
+	(g) & (0; 3, 3, 3, 5; 0) & \{4\} & 5\\ \hline
+
+	(h) & (0; 3, 3, 5, 5; 0) & \{3, 4\} & 5\\ \hline
+
+	(i) & (0; 3, 5, 5, 5; 0) & \{2, 3, 4\} & 5\\ \hline
+
+	(j) & (0; 5, 5, 5, 5; 0) & \{1, 2, 3, 4\} & 5\\ \hline
+
+	(k) &	(0; 3, 3, 3, 3, 3; 0) & \{1, 2, 3, 4, 5\} & 5\\ \hline
 
@@
 \end{longtable}
-}
 
@@
 
-	(a) & $\{3, 7, 9, 11\}$ & $\{14, 18\}$ & $11$ \\	\hline
-
-	(b) & $\{3, 5, 7, 9\}$ & $\{12, 14\}$ & $9$ \\ \hline
-
-	(c) & $\{3, 5, 7, 7\}$ & $\{10, 14\}$ & $7$ \\ \hline
-
-	(d) & $\{3, 5, 5, 7\}$ & $\{10, 12\}$	& $7$ \\ \hline
-
-	(e) & $\{3, 5, 5, 7, 7\}$ & $\{10, 10, 12, 12, 14\}$	& $7$ \\ \hline
-
-	(f) & $\{3, 5, 5, 7, 7, 7\}$ & $\{10, 10, 10, 12, 12, 12, 14, 14, 14\}$	& $7$ \\ \hline
-
-	(g) & $\{3, 3, 4, 5\}$ & $\{8, 9\}$ & $5$ \\ \hline
-
-	(h) & $\{3, 3, 4, 5, 5\}$ & $\{8, 8, 9, 9, 10\}$ & $5$ \\ \hline
-
-	(i) & $\{3, 3, 4, 5, 5, 5\}$ &
-	$\{8, 8, 8, 9, 9, 9, 10, 10, 10\}$ & $5$ \\ \hline
-
-	(j) & $\{3, 3, 4, 5, 5, 5, 5\}$ &
-	$\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\}$ & $5$ \\ \hline
-
-	(k) &	$\{3, 3, 3, 4, 4, 5\}$ & $\{6, 7, 7, 8, 8, 8, 9, 9, 10\}$ & $5$ \\ \hline
+	(a) & \{3, 7, 9, 11\} & \{14, 18\} & 11\\	\hline
+
+	(b) & \{3, 5, 7, 9\} & \{12, 14\}	& 9\\ \hline
+
+	(c) & \{3, 5, 7, 7\} & \{10, 14\}	& 7\\ \hline
+
+	(d) & \{3, 5, 5, 7\} & \{10, 12\}	& 7\\ \hline
+
+	(e) & \{3, 5, 5, 7, 7\} & \{10, 10, 12, 12, 14\}	& 7\\ \hline
+
+	(f) & \{3, 5, 5, 7, 7, 7\} & \{10, 10, 10, 12, 12, 12, 14, 14, 14\}	& 7\\ \hline
+
+	(g) & \{3, 3, 4, 5\} & \{8, 9\} & 5\\ \hline
+
+	(h) & \{3, 3, 4, 5, 5\} & \{8, 8, 9, 9, 10\} & 5\\ \hline
+
+	(i) & \{3, 3, 4, 5, 5, 5\} &
+	\{8, 8, 8, 9, 9, 9, 10, 10, 10\} & 5\\ \hline
+
+	(j) & \{3, 3, 4, 5, 5, 5, 5\} &
+	\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\} & 5\\ \hline
+
+	(k) &	\{3, 3, 3, 4,	4, 5\} & \{6, 7, 7, 8, 8, 8, 9, 9, 10\} & 5\\ \hline
 
@@
 We can also always find a presentation for these cases such that
-they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
+they satisfy (Ad-i) and (Ad-ii) and that $\initial(I')$ is
 generated by products of two monomials. Again, the procedure for
@@
 
-Furthermore, each case always satisfies \ref{Ad-iii} as demonstrated below.
+Furthermore, each case always satisfies (Ad-iii) as demonstrated below.
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
@@
 
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $1$ & $0$ \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & $2$ & $0$ \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $3$ & $0$ \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $2$ & $0$ \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $3$ & $0$ \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $4$ & $0$ \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ & $0$ \\ \hline
-
-	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ & $0$ \\ \hline
-
-	\caption{Genus 0 Non-Effective Base Cases \ref{Ad-iii}}
+	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & 1 & 0 \\	\hline
+
+	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & 1 & 0 \\ \hline
+
+	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & 2 & 0 \\ \hline
+
+	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & 1 & 0 \\ \hline
+
+	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & 2 & 0 \\ \hline
+
+	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & 3 & 0 \\ \hline
+
+	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & 2 & 0 \\ \hline
+
+	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & 3 & 0 \\ \hline
+
+	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & 4 & 0 \\ \hline
+
+	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & 5 & 0 \\ \hline
+
+	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & 5 & 0 \\ \hline
+
+	\caption{Genus 0 Non-Effective Base Cases (Ad-iii)}
 	\label{table:g-0-base-cases-admissibility}

### 2015-07-01 stacky_write_up/spin_cring.tex
editing background, up to sat 2

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
+
+\begin{defn}
+\label{def:order-sup}
+If $z$ is a rational section of $\sco(D)$ denote the order of
+zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
 

### 2015-07-02 stacky_write_up/spin_cring.tex
edited main corollary

@@
 \begin{abstract}
-  The study of rings of modular forms arising from finite-area
+ 	We tightly bound the degrees of minimal
+	generators and relations of spin canonical rings of a stacky
+	curve equipped with an arbitrary log divisor.  Rings of modular forms arising from finite-area
 	quotients of the upper-half plane by Fuchsian groups may be
-	translated to log spin canonical rings by the classical
-	results of Kodaira--Spencer. This work describes
-	generators and relations of spin canonical rings of a stacky
-	curve equipped with an arbitrary log divisor in a
-	generalization of the classical theorems of Max Noether	and Karl
-	Petri. As an application, these results tightly bound the
-	generator and relation degrees for the aforementioned rings
-	of modular forms of arbitrary integral weight.
+	viewed as log spin canonical rings by the classical
+	results of Kodaira--Spencer. As a consequence, 
+	we obtain a tight bound on the degrees of minimal generators and relations  		
+	for rings of modular forms of arbitrary integral weight.
 \end{abstract}
@@
 
+\todo{I changed the following to incorporate the no odd weight case. Is it ok?}
+
 The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, provides the following application
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, together with Voight and Zureick-Brown ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[9.3.1]{vzb:stacky} provide the following application
 to modular forms. Note that the result from Voight and
@@
 associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
-\ldots, e_r; \delta)$. Then, the ring of modular forms
+\ldots, e_r; \delta)$. 
+If $M_k(\Gamma) = 0$ for all odd $k$, then $M(\Gamma)$ is generated in degree at most $3 \cdot\max(3,e_1,\ldots, e_r)$ with relations in degree at most $6 \cdot \max(3,e_1,\ldots, e_r)$.
+If there is some odd $k$ for which $M_k(\Gamma) \neq 0,$ then, the ring of modular forms
 $M(\Gamma)$ is
@@
 
-First, we give a definition of the graded degree of a monomial
-in a graded polynomial ring.
-\todo{possibly compactify or refer to relations}
+\todo{possibly compactify or refer to relations, Aaron: I think we should almost remove these definitions, and that these shouldn't be in environments.
+I suspect people will be familiar with them, or be able to look them up.}
+
 \begin{defn}
@@
 k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
-we define
-\[
-	\deg \alpha := \sum_{i = 1}^{n} d f_i.
+we define the {\bf degree} of $\alpha$ to be
+\[
+	\deg \alpha := \sum_{i = 1}^{n} d_i f_i.
 \]
 \end{defn}
-
-Now define the (graded) lexicographic order \textbf{grlex}
-$\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
-x_{d_n, n}]$ to be the monomial ordering such that:
 
@@
 \label{defn:grlex}
+The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
+x_{d_n, n}]$ is defined as follows.
 If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
@@
 \end{equation}
-or $\alpha$ is larger using the lexicographical ordering event of equal
-degrees:
-
+or
 \begin{equation}
@@
 	\deg \alpha = \deg \beta \text{ and }
-	\alpha \succ_{\text{lex}} \beta.
+	f_i - f_i' > 0 \text{ for the smallest } i \text{ such that } f_i \neq f_i'.
 \end{equation}
@@
 
-We can equip the polynomial ring $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$
-with the (weighted graded) reverse lexicographic order
-\textbf{grevlex} $\prec_{\text{grevlex}}$ as follows:
-
 \begin{defn}
 \label{defn:grevlex}
+The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
 If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
@@
 monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
-\succ_{\text{grevlex}} \beta$ if either $\alpha$ has larger degree:
+\succ_{\text{grevlex}} \beta$ if either
 
@@
 \end{equation}
-or $\alpha$ has a smaller right-most entry in the event of equal
-degrees:
-
+or
 \begin{equation}
@@
 usually have an inclusion $R \supseteq R'$ of log spin canonical
-rings such that $R_\halfcan$ is generated by elements $x_{d_i, i}$ and $R$
+rings such that $R_\halfcan$ is generated by elements $x_{d_i, i}$ \todo{They're usually $x_{i,e_i}$ with the degree in the second position, which is a bit strange.
+Somehow, I think we might want to switch the ordering here, though it still might be confusing.} and $R$
 is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
 natural to consider term orders which treat these sets of variables
-separately. We now present the \textbf{block term order} introduced
-by Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
+separately.
 
@@
 \label{defn:block-order}
-
-Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
+Following Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
+the \textbf{block term order} is defined as follows. Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
 x_{d_n, n}]$ be weighted polynomial rings with existing term
@@
 \label{defn:initial-term}
-Let $f \in k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a homogeneous
+Let $\prec$ be an ordering on $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ and let $f \in k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ be a homogeneous
 polynomial. The \textbf{initial term} $\initial(f)$ of $f$
@@
 
-Given a homogeneous ideal $I \subseteq k[x_{d_1, 1}$, $\ldots$,
-$x_{d_n, n}]$, we can now define the \textbf{initial ideal}
-$\initial(I)$ of $I$.
-
 \begin{defn}
@@
 Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
-$x_{d_n, n}]$. Then the initial ideal $\initial(I)$ of $I$ is
+$x_{d_n, n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
 the ideal generated by the initial terms of homogeneous polynomials
@@
 
-Furthermore, we will use Gr\"{o}bner bases, which are bases
-for these initial ideals and have many useful properties.
+%Furthermore, we will use Gr\"{o}bner bases, which are bases
+%for these initial ideals and have many useful properties.
 
@@
 \textbf{standard basis} for $I$, is a set of elements in $I$
-such that their initial terms form a basis for the initial
+such that their initial terms generate the initial
 ideal of $I$.
@@
 	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ in_\prec(I))_d \\
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial_\prec(I))_d \\
 	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
@@
 Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
 Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
@@
 Then we have a map $\phi: k[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
-\todo{Do we need to instantiate the $z_i$.
-If so, what is the best way to do so.
-Saying for indeterminates $z_1, \ldots, z_m$ seems excessive.
-Aaron: No, what you say is great!}  If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows.
+If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows.
 If $f=\prod_{i=1}^m {z_i}^{q_i}$ and $g=\prod_{i=1}^m {z_i}^{r_i}$ with $f \neq g,$ then $f\prec g$ if one of the following holds:
@@
 
-\todo{Peter: Do we want this as an [H] figure; this seems a little non-standard and can create problems with display.
-Nonetheless, I copied this format to match the figure in a later section.
-Aaron: I'm fine with not making it an [H]}
 \begin{figure}
@@
 \end{align}
-\todo{Peter: I understand why this should be true, although its not clear to me that there it easily follows.  Maybe we should explain it a little as to not confuse the reader.}
-
-\noindent
-We now apply Equation ~\eqref{eqn:order-degree} with $f = y_{i, e_i}z$, to check $y_{i,e_i}z \in R'$ in the three cases: 
+\todo{Peter: I understand why this should be true, although its not clear to me that there it easily follows.
+Maybe we should explain it a little as to not confuse the reader.
+Aaron: Can we ask David, this was clear to me in his paper, and he also didn't include it.}
+
+\noindent
+Now fix $i \in J$. We check Inequality ~\eqref{eqn:order-degree} holds with $f = y_{i, e_i}z$, implying $y_{i,e_i}z \in R'$ in the three following cases: 
 %$j \notin \{i \} \cup S(i, 0)$, $j = i,$ and $j \in S(i, 0)$.
 
-\todo{Peter: be clear with this that we aren't checking $y_{i,e_i}z\in R'$ for various cases, but rather are checking that equation 4.6 is met in various cases, giving $y_{i,e_i}z\in R'$ for a specific fixed $i$.
-}
 \vskip.1in
@@
 \label{ssec:bounds-high-genus}
-\todo{Make edits that you want to further incorporate Reid's paper}
 
@@
 \twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
-\ldots, x_n]_2$ be two elements so that $\newspan(\phi(s_1), \phi(s_2))
+\ldots, x_n]_2$ be two elements so that $\: \newspan(\phi(s_1), \phi(s_2))
 = V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
@@
 \end{align*}
-is surjective, and $\deg f \geq 11$ implies that
-$\deg a_i =\deg f - \deg x_i -2 \geq 4.$
-In particular, we can write $\phi(a_i) = \phi(s_1) \alpha + \phi(s_1) \cdot \beta$.
-Choosing $g_i,h_i\in k[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have $a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan,\deg a_i}$, as claimed.
-\todo{Peter: Maybe this paragraph could be made a little easier to read?}
+is surjective because $\deg f \geq 11$ implies that
+$$\deg a_i =\deg f - \deg x_i -2 \geq 4.$$
+In particular, there exist $\alpha,\beta \in R_L$ so that
+$$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
+Choosing $g_i,h_i\in k[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
+$$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan,\deg a_i},$$ as claimed.
 
@@
 Therefore, since $P_r$ is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann Roch
+~\ref{eqn:deg1-sat-ind} holds by Riemann Roch.
 % since $\frac{\beta}{\alpha} = \frac{3}{1}=3$. 
-In this case, we claim the theorem holds for $L$ by Lemma ~\ref{lem:sat-1}.  In particular, the bound on the generators holds by part (a) of Lemmas
-~\ref{lem:sat-2} and ~\ref{lem:sat-1},
-and the bound on the relations holds by part (b) of Lemmas
-~\ref{lem:sat-2} and ~\ref{lem:sat-1}.\todo{Peter: Can we get rid of this last sentence?}
+In this case, the theorem holds for $L$ by Lemma ~\ref{lem:sat-1}.
 
@@
 			\end{rem}
-
-	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
 	\item While Theorem ~\ref{thm:main} gives a minimal set of 

### 2015-07-02 stacky_write_up/spin_cring.tex
section 6 changes

--- 2015-07-01 stacky_write_up/spin_cring.tex
@@
 In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
-Unlike the $g \geq 2$ case, here we obtain explicit generators and relations for any log spin curve $(\sx, \Delta, L)$ with $g = 1$.
-
-The inductive strategy we will adopt to prove Theorem ~\ref{thm:main} is similar to that of the genus $g \geq 2$ case.
-In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
+We follow a similar inductive strategy as in the genus $g\geq 2$ case, except unlike in the $g \geq 2$ case we obtain explicit generators and relations here.
+
+In the case of a genus 1 curve, $X$, we know $K_X \sim 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
 We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.

### 2015-07-02 stacky_write_up/spin_cring.tex

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
-Unlike the $g \geq 2$ case, here we obtain explicit generators and relations for any log spin curve $(\sx, \Delta, L)$ with $g = 1$.
-
-The inductive strategy we will adopt to prove Theorem ~\ref{thm:main} is similar to that of the genus $g \geq 2$ case.
-In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
-We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.
+We follow a similar inductive strategy as in the genus $g\geq 2$ case, except unlike in the $g \geq 2$ case we obtain explicit generators and relations here.
+
+In the case of a genus 1 curve, $X$, we know $K_X \sim 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
+We inductively construct presentations by adding points through Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2} and incrementing the values of the $e_i$s using Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
-Note that in addition to $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ being base cases, they are also exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}.
+Note that in addition to $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ being base cases, they are also exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}.\todo{Peter: I don't understand this last sentence?
+How are they base cases?}
 
@@
 First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $, as $P$ is not a basepoint of $L'$.
+In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $\todo{Peter: Is $\lfloor L|_p\rfloor$ standard notation?
+It looks weird}, as $P$ is not a basepoint of $L'$.
 Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $L= L'+P$.
-
-Second, if $P$ is a basepoint of $L'$, then the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$.
-Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L = L'+P$.
-This shows the theorem holds for $L_X$.
-
-To complete the case that $\Delta > 0$, we only need show the theorem holds for $L$, assuming it holds for $L_X$.
-By induction, it suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i,$ with $e_i$ odd.
-Similarly to the above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}, while if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
+\todo{Peter: I don't find this paragraph (after the first sentence) very useful.
+1: I'm not sure if we even need to go through the check that it satisfies the conditions for lemma 4.5.
+2: I don't find the check clear or illuminating as written.
+Either we should reword it or remove it (feel free to disagree, of course)}
+
+Otherwise, $P$ is a basepoint of $L'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$\todo{Peter: I don't follow why we have a $+P$ here.
+lemma 4.8 requires that $L'$ satisfy $\deg(3L')\ge 2$,not $\deg(3L)\ge 2$.
+This isn't a problem though since $\Delta> 0$} Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L = L'+P$.
+The previous argument shows the theorem holds for $L_X$.
+
+To complete the case that $\Delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin divisor $L$.
+It suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
+As above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}; on the other hand, if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
 
@@
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then, by Example ~\ref{eg:base-1-33}, it follows that the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in Example ~\ref{eg:base-1-33}, the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}\todo{Peter: Is it better for us to say the signature satisfies the hypothesis rather than the tripple?}.
 Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
+\todo{Peter: Why is it immediate that $n$ threes satisfies the condition for admissibility?
+We got rid of that proof from earlier.
+In fact, didn't we find it to be false?}
 
@@
 
-This case is analogous to 2a.
+This case is analogous to 2a. \todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument?}
 \end{proof}
@@
 In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
-That, is one can start with the generators and relations for the base cases, and then inductively add in generators and relations, according to the inductive theorems.
+That, is one can start with the generators and relations found in the base cases, and inductively add in generators and relations as one adds and then increments stacky points.
 \end{rem}

### 2015-07-02 stacky_write_up/spin_cring.tex
spell check

@@
 presentation of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
-In order to do so, it is extermely useful to have a bound on the
+In order to do so, it is extremely useful to have a bound on the
 degrees in which the generators and relations can occur. In the
@@
 
-Theorem ~\ref{thm:main} is proven seperately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$, each of
+Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$, each of
 which uses a similar inductive process. The genus $g \geq 2$ case is
@@
 For the remainder of this paper, fix an algebraically closed field $k$.
-This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closue.
+This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closure.
 
@@
 In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}.
-In addition to demonstrating the algorithmic procedure for computing presetations, these examples will also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
+In addition to demonstrating the algorithmic procedure for computing presentations, these examples will also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
 
@@
 		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order with $y_3, y_4$ preceeding $x_2, \ldots, x_m$.
-\todo{In here and throughout the section, we should just enforce the convention that the $y_i$ come before the $x_j$, and then we won't have to say which preceed which.} Then,
+		order with $y_3, y_4$ preceding $x_2, \ldots, x_m$.
+\todo{In here and throughout the section, we should just enforce the convention that the $y_i$ come before the $x_j$, and then we won't have to say which precede which.} Then,
 		\begin{align*}
@@
 Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$.
-By Voight and Zurieck-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
+By Voight and Zureick-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
 Hence, $R_\halfcan$ is generated in degree at most 5.
@@
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in Example ~\ref{eg:base-1-33}, the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}\todo{Peter: Is it better for us to say the signature satisfies the hypothesis rather than the tripple?}.
+If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in Example ~\ref{eg:base-1-33}, the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}\todo{Peter: Is it better for us to say the signature satisfies the hypothesis rather than the triple?}.
 Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
@@
 		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
-		Fractional modular forms also make an apperance in Milnor \cite[$
+		Fractional modular forms also make an appearance in Milnor \cite[$
 		\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 

### 2015-07-02 stacky_write_up/spin_cring.tex
removed monomial subscripts

@@
 \label{defn:monomial-degree}
-Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
-ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
-k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
+Let $k[x_1$, $\ldots$, $x_n]$ be a graded polynomial
+ring with $\deg x_i = d_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
+k[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
 we define the {\bf degree} of $\alpha$ to be
@@
 \label{defn:grlex}
-The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
-x_{d_n, n}]$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
-monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{1}, \ldots,
+x_{n}]$ with $\deg x_i = d_i$ is defined as follows.
+If $\alpha := \prod_{i = 1}^{n} x_{i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
+monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
 \succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
@@
 The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
-monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
+If $\alpha := \prod_{i = 1}^{n} x_{i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
+monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
 \succ_{\text{grevlex}} \beta$ if either
@@
 usually have an inclusion $R \supseteq R'$ of log spin canonical
-rings such that $R_\halfcan$ is generated by elements $x_{d_i, i}$ \todo{They're usually $x_{i,e_i}$ with the degree in the second position, which is a bit strange.
-Somehow, I think we might want to switch the ordering here, though it still might be confusing.} and $R$
+rings such that $R_\halfcan$ is generated by elements $x_{i}$ and $R$
 is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
@@
 \label{defn:block-order}
-Following Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
-the \textbf{block term order} is defined as follows. Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
-x_{d_n, n}]$ be weighted polynomial rings with existing term
-orders $\prec_y$ and $\prec_x$, respectively. Let $\alpha :=
-\prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ $\prod_{i = 1}^{n} x_{d_i, i}
-^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{c_j, j}^{h_i'}
-\prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ be monomials in $k[y_{d_1', 1},
-\ldots, y_{d_m', m}] \otimes$ $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$.
-Let $\alpha_y := \prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ be the
-part of $\alpha$ in $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and
+The \textbf{block term order} is defined as follows. Let $k[y_{1}, \ldots, y_{m}]$ and $k[x_{1}, \ldots,
+x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i,\: \deg x_i = d_i.$ Further assume we are given existing term
+orders $\prec_y$ and $\prec_x$. Let $\alpha :=
+\prod_{j = 1}^{m} y_{j}^{h_i}$ $\prod_{i = 1}^{n} x_{i}
+^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
+\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $k[y_{1},
+\ldots, y_{m}] \otimes$ $k[x_{1}, \ldots, x_{n}]$.
+Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
+part of $\alpha$ in $k[y_{1}, \ldots, y_{m}]$ and
 likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
@@
 \label{defn:initial-term}
-Let $\prec$ be an ordering on $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ and let $f \in k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ be a homogeneous
+Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}],$ with $\deg x_i = d_i$ and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
 polynomial. The \textbf{initial term} $\initial(f)$ of $f$
@@
 \label{defn:initial-ideal}
-Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
-$x_{d_n, n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
+Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
+$x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
 the ideal generated by the initial terms of homogeneous polynomials
@@
 \label{defn:grobner-basis}
-Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
-$x_{d_n, n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
+Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
+$x_{n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
 \textbf{standard basis} for $I$, is a set of elements in $I$

### 2015-07-02 stacky_write_up/spin_cring.tex
use grevlex in g0 example, remove grlex

@@
 \begin{defn}
-\label{defn:grlex}
-The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{1}, \ldots,
-x_{n}]$ with $\deg x_i = d_i$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
-monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
-\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
-
-\begin{equation}
-	\deg \alpha := \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' =: \deg \beta
-\end{equation}
-or
-\begin{equation}
-\label{eqn:grlex-tie}
-	\deg \alpha = \deg \beta \text{ and }
-	f_i - f_i' > 0 \text{ for the smallest } i \text{ such that } f_i \neq f_i'.
-\end{equation}
-\end{defn}
-
-\begin{defn}
 \label{defn:grevlex}
@@
 \begin{rem}
-Note that the ordering of the variables matters in both
-Equation ~\ref{eqn:grlex-tie} and Equation ~\ref{eqn:grevlex-tie}.
+Note that the ordering of the variables matters in Equation
+~\ref{eqn:grevlex-tie}.
 \end{rem}
@@
 \begin{align*}
-	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
+	&a_1 x_{5, 1}^2 + a_2 x_{7, 2} x_{3, 1} + a_3 x_{7, 1} x_{3, 1} = 
 	0 &\text{ in degree $10$} \\
@@
 \[
-	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
-\]
-
-\noindent
-However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
-$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
+	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
+\]
+
+\noindent
+However, $x_{7, 2} x_{3, 1}$ has pole orders $(3, 3, 4)$ and
+$x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ so their
 coefficients must be zero for this equality to hold. We have a
@@
 Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
+$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
 $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
@@
 \[
-	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
+	\initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
 \]
@@
 	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
-	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
+	x_{7, 2}^2, x_{5, 1}^2 \rangle
 \end{align*}
@@
 for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
+x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{5, 1}^2
 \rangle$ can be checked by looking at the $k$-basis at each degree
@@
 Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
+k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
 initial ideal $\initial(I)$ generated by quadratics under grlex

### 2015-07-02 stacky_write_up/spin_cring.tex
reword main corollary

@@
 
-\todo{I changed the following to incorporate the no odd weight case. Is it ok?}
-
-The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, together with Voight and Zureick-Brown ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[9.3.1]{vzb:stacky} provide the following application
-to modular forms. Note that the result from Voight and
-Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately from the classical work of Kodaira--Spencer
+The main theorem of this paper, Theorem ~\ref{thm:main}, combined
+with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
+{vzb:stacky}, provides a statement on rings of modular forms.
+Together with the main theorem from Voight and Zureick-Brown \cite
+[Theorem 9.3.1]{vzb:stacky}, we have the following application to
+rings of modular forms. Note that the lemma from Voight and Zureick-
+Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
+from the classical work of Kodaira--Spencer
 \cite{kodaira-spencer:deformations}.
@@
 Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
-associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
-\ldots, e_r; \delta)$. 
-If $M_k(\Gamma) = 0$ for all odd $k$, then $M(\Gamma)$ is generated in degree at most $3 \cdot\max(3,e_1,\ldots, e_r)$ with relations in degree at most $6 \cdot \max(3,e_1,\ldots, e_r)$.
-If there is some odd $k$ for which $M_k(\Gamma) \neq 0,$ then, the ring of modular forms
-$M(\Gamma)$ is
-generated as a $\BC$-algebra by elements of degree at most $e = \max
- (5, e_1, \ldots , e_r)$ with relations in degree at most $2e,$ so long
-as $\sigma$ does not lie in a finite list of exceptional cases, as
-listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
-= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
-0$.
+associated to $\Gamma \backslash \BH$ with signature $\sigma
+= (g; e_1, \ldots, e_r; \delta)$.
+
+If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
+forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
+degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
+generated in degrees at most $6 \cdot \max(3, e_1,\ldots, e_r)$.
+
+If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
+ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
+by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
+relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
+e_r)$ so long as $\sigma$ does not lie in a finite list of
+exceptional cases which are listed and described in Table
+~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
+Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
 \end{cor}

### 2015-07-02 stacky_write_up/spin_cring.tex
add $e$ to g1 tables, uniformize g0 tables

@@
 \label{ssec:g_1_base}
-In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g=1$.
-
-\begin{longtable}	{| c || c | c |}	
+In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.
+
+\begin{longtable}	{| c || c | c | c |}	
 	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations \\
+	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
 	\hline
-	$0$ & $\{1\}$ & $\emptyset$ \\	\hline
-
-	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
-
-	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline
-
-	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
-
-	$P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline
+	$0$ & $\{1\}$ & $\emptyset$ & $1$ \\	\hline
+
+	$\frac{3}{7} P_1$ & $\{1,5,7\}$ & $\{15\}$ & $7$ \\	\hline
+
+	$\frac{1}{3} P_1 + \frac{1}{3} P_2$ & $\{1, 3, 3\}$ & $\{6\}$ & $5$ \\	\hline
+
+	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$ \\	\hline
+
+	$P - Q + \frac{1}{3} P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ & $5$ \\	\hline
 
@@
 \label{ssec:g-1-exceptional}
-Let $\sx$ be a stacky curve, with Let $P,Q$ distinct hyperelliptic fixed points on $X$.
-The following table provides a list of all cases which are not generated in degrees $e=\max(5,e_1,\ldots, e_r)$ with relations in degrees $2e$, as described in Theorem ~\ref{thm:g-1-main}.
-
-\begin{longtable}	{| c || c | c |}
+Let $\sx$ be a stacky curve, with $P, Q$ distinct hyperelliptic
+fixed points on $X$. The following table provides a list of all
+cases which are not generated in degrees $e := \max(5, e_1, \ldots,
+e_r)$ with relations in degrees $2e$, as described in Theorem
+~\ref{thm:g-1-main}.
+
+\begin{longtable}	{| c || c | c | c |}
 	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations \\
+	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
 	\hline
-	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline
-
-	$P - Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
-
-	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
-
-	$\frac{1}{3}P_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline
-
-	$\frac{2}{5}P_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline
-
-	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
+	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline
+
+	$P - Q + \frac{1}{3} P_1$ & $\{2, 3, 7\}$ & $\{14\}$ & $5$ \\	\hline
+
+	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$\\	\hline
+
+	$\frac{1}{3} P_1$ & $\{1, 6, 9\}$ & $\{18\}$ & $5$ \\	\hline
+
+	$\frac{2}{5} P_1$ & $\{1, 5, 8\}$ & $\{16\}$ & $5$ \\	\hline
+
+	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline
 
@@
 remainder of this section is dedicated to characterizing the
-saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
+saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
 base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
@@
 	\hline
-	Signature & Condition & Saturation \\
+	Signature $\sigma$ & Condition & Saturation \\
 	\hline
@@
 	\hline
-	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
+	Case & Signature $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
 	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
@@
 	\hline
-	Signature & Generator Degrees & Degrees of Relations & $e$ \\
+	Signature $\sigma$ & Generator Degrees & Degrees of Relations & $e$ \\
 	\hline

### 2015-07-02 stacky_write_up/spin_cring.tex
change title divisor -> ring, minor intro edits

@@
 
-\title{Spin canonical divisors of log stacky curves}
+\title{Spin canonical rings of log stacky curves}
 
@@
 \label{defn:divisor-floor}
-If Weil divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
+If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
 with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
@@
 
-A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is called a \textbf{log stacky curves}
-and the study of their canonical rings is the main focus of
-the work by Voight and Zureick-Brown \cite{vzb:stacky}.
-For this paper, we consider \textbf{log spin curves} which are
-triples $(\sx, \Delta, \halfcan)$ where $\sx$ is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di \sx$ satisfies
-$2\halfcan \sim K_X + \Delta + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i$. Such a divisor $\halfcan$
-is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
-We use $\halfcan_X := \lfloor L \rfloor $ to refer to the spin canonical divisor
-(also known as the half-canonical divisor, semi-canonical divisor, 
-or theta characteristic) associated to the
-coarse space $X$ of $\sx$, i.e. $\halfcan_X$ is a divisor such
-that $2\halfcan_X \sim K_X + \Delta$. Furthermore, we use the following
-analogous notation:
+A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
+called a \textbf{log stacky curves} and the study of their
+canonical rings is the main focus of the work by Voight and Zureick-
+Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
+spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
+is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
+\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
+\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
+\textbf{log spin canonical divisor} on $(\sx, \Delta)$. We use
+$\halfcan_X := \lfloor L \rfloor $ to refer to the \textbf{spin
+canonical divisor} (also known as the half-canonical divisor, semi-
+canonical divisor, or theta characteristic) associated to the
+coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
+that $2\halfcan_X \sim K_X + \Delta$). Furthermore, we use the
+following analogous notation:
 

### 2015-07-02 stacky_write_up/spin_cring.tex
minor g0 example edit

@@
 is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. It is fairly easy to see using Riemann--Roch that $\sat(\Eff(\sigma)) = 5.$
-Then the map in ~\eqref{eqn:noether-377} is surjective
-when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
+\geq 0$. It is fairly easy to see, by use of Riemann--Roch, that
+$s := \sat(\Eff(\sigma)) = 5$. Then the map in
+~\eqref{eqn:noether-377} is surjective when $d \geq 21 + s = 26$
+(i.e. $R'$ is generated up to degree 25).
 
@@
 	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
-	\text{ (mod } 7)
+	\bmod 7
 \end{align*}

### 2015-07-02 stacky_write_up/spin_cring.tex
editing moster proof

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 
-The main theorem of this paper, Theorem ~\ref{thm:main}, combined
-with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
-{vzb:stacky}, provides a statement on rings of modular forms.
-Together with the main theorem from Voight and Zureick-Brown \cite
-[Theorem 9.3.1]{vzb:stacky}, we have the following application to
-rings of modular forms. Note that the lemma from Voight and Zureick-
-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
-from the classical work of Kodaira--Spencer
+\todo{I changed the following to incorporate the no odd weight case. Is it ok?}
+
+The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, together with Voight and Zureick-Brown ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[9.3.1]{vzb:stacky} provide the following application
+to modular forms. Note that the result from Voight and
+Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately from the classical work of Kodaira--Spencer
 \cite{kodaira-spencer:deformations}.
@@
 Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
-associated to $\Gamma \backslash \BH$ with signature $\sigma
-= (g; e_1, \ldots, e_r; \delta)$.
-
-If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
-forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
-degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $6 \cdot \max(3, e_1,\ldots, e_r)$.
-
-If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
-ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
-by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
-relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
-e_r)$ so long as $\sigma$ does not lie in a finite list of
-exceptional cases which are listed and described in Table
-~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
-Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
+associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
+\ldots, e_r; \delta)$. 
+If $M_k(\Gamma) = 0$ for all odd $k$, then $M(\Gamma)$ is generated in degree at most $3 \cdot\max(3,e_1,\ldots, e_r)$ with relations in degree at most $6 \cdot \max(3,e_1,\ldots, e_r)$.
+If there is some odd $k$ for which $M_k(\Gamma) \neq 0,$ then, the ring of modular forms
+$M(\Gamma)$ is
+generated as a $\BC$-algebra by elements of degree at most $e = \max
+ (5, e_1, \ldots , e_r)$ with relations in degree at most $2e,$ so long
+as $\sigma$ does not lie in a finite list of exceptional cases, as
+listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
+= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
+0$.
 \end{cor}
@@
 \begin{defn}
+\label{defn:grlex}
+The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{1}, \ldots,
+x_{n}]$ with $\deg x_i = d_i$ is defined as follows.
+If $\alpha := \prod_{i = 1}^{n} x_{i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
+monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
+\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
+
+\begin{equation}
+	\deg \alpha := \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' =: \deg \beta
+\end{equation}
+or
+\begin{equation}
+\label{eqn:grlex-tie}
+	\deg \alpha = \deg \beta \text{ and }
+	f_i - f_i' > 0 \text{ for the smallest } i \text{ such that } f_i \neq f_i'.
+\end{equation}
+\end{defn}
+
+\begin{defn}
 \label{defn:grevlex}
@@
 \begin{rem}
-Note that the ordering of the variables matters in Equation
-~\ref{eqn:grevlex-tie}.
+Note that the ordering of the variables matters in both
+Equation ~\ref{eqn:grlex-tie} and Equation ~\ref{eqn:grevlex-tie}.
 \end{rem}
@@
 \begin{align*}
-	&a_1 x_{5, 1}^2 + a_2 x_{7, 2} x_{3, 1} + a_3 x_{7, 1} x_{3, 1} = 
+	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
 	0 &\text{ in degree $10$} \\
@@
 \[
-	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
+	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
 \]
@@
 \noindent
-However, $x_{7, 2} x_{3, 1}$ has pole orders $(3, 3, 4)$ and
-$x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ so their
+However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
+$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
 coefficients must be zero for this equality to hold. We have a
@@
 Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
+$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
 $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
@@
 \[
-	\initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
+	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
 \]
@@
 	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
-	x_{7, 2}^2, x_{5, 1}^2 \rangle
+	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
 \end{align*}
@@
 for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{5, 1}^2
+x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
 \rangle$ can be checked by looking at the $k$-basis at each degree
@@
 Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
+k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
 initial ideal $\initial(I)$ generated by quadratics under grlex
@@
 \[
-	S_i = y_j S_{i-j}.
+	S_i = y_j \cdot S_{i-j}.
 \]
@@
 {\bf Part (b):}
-Let $S$ be as above in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
+Let $S$ be as defined in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
 \[
@@
 \]
-Notice that $S$ generates the ideal $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$; let $l$ be maximal such that $a_l\ne 0$.
-If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
-and for all $r<h$ $\prod_{j=1}^r {y_j}^{b_j}\in S$, where $b_j=a_j$ when $j\ne i$ and $b_i=a_i+1$.
-Choose $(\gamma_1, \ldots, \gamma_n)$ minimal (that is, so that we cannot decrease any $\gamma_j$ and have the following still satisfied) such that each $\gamma_j\le b_j$ and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$; our recursive definition of $S$ implies that for each $1\le r< h$, we still have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
+Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $k[u, y_1, \ldots, y_n]$.
+If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
+Let $l$ be maximal such that $a_l\ne 0$.
+Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
+$$
+b_j = \begin{cases}
+	a_j &\text{ if } j \neq i\\
+	a_j + 1 &\text{ if } j=i.
+\end{cases}$$
+
+\noindent
+Then, there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
+and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
+Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
+and have the following still satisfied: each $\gamma_j\le b_j$ 
+and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
+$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
 
 We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
-Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above immediately gives (**).
-Since for each $r<h$, $\prod_{j=1}^r y_{j}^{a_j}\in S$, we get condition (***).
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
+Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).
+Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition (***) holds.
 Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
 
-Since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+\todo{how to avoid polynomials hangining over lines like this, ask david} Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 \label{ssec:g_1_base}
-In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.
-
-\begin{longtable}	{| c || c | c | c |}	
+In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g=1$.
+
+\begin{longtable}	{| c || c | c |}	
 	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	L' & Generator Degrees & Degrees of Minimal Relations \\
 	\hline
 	\hline
-	$0$ & $\{1\}$ & $\emptyset$ & $1$ \\	\hline
-
-	$\frac{3}{7} P_1$ & $\{1,5,7\}$ & $\{15\}$ & $7$ \\	\hline
-
-	$\frac{1}{3} P_1 + \frac{1}{3} P_2$ & $\{1, 3, 3\}$ & $\{6\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{1}{3} P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ & $5$ \\	\hline
+	$0$ & $\{1\}$ & $\emptyset$ \\	\hline
+
+	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
+
+	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline
+
+	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+	$P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline
 
@@
 \label{ssec:g-1-exceptional}
-Let $\sx$ be a stacky curve, with $P, Q$ distinct hyperelliptic
-fixed points on $X$. The following table provides a list of all
-cases which are not generated in degrees $e := \max(5, e_1, \ldots,
-e_r)$ with relations in degrees $2e$, as described in Theorem
-~\ref{thm:g-1-main}.
-
-\begin{longtable}	{| c || c | c | c |}
+Let $\sx$ be a stacky curve, with Let $P,Q$ distinct hyperelliptic fixed points on $X$.
+The following table provides a list of all cases which are not generated in degrees $e=\max(5,e_1,\ldots, e_r)$ with relations in degrees $2e$, as described in Theorem ~\ref{thm:g-1-main}.
+
+\begin{longtable}	{| c || c | c |}
 	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	L' & Generator Degrees & Degrees of Minimal Relations \\
 	\hline
 	\hline
-	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline
-
-	$P - Q + \frac{1}{3} P_1$ & $\{2, 3, 7\}$ & $\{14\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$\\	\hline
-
-	$\frac{1}{3} P_1$ & $\{1, 6, 9\}$ & $\{18\}$ & $5$ \\	\hline
-
-	$\frac{2}{5} P_1$ & $\{1, 5, 8\}$ & $\{16\}$ & $5$ \\	\hline
-
-	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline
+	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline
+
+	$P - Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline
+
+	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline
+
+	$\frac{1}{3}P_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline
+
+	$\frac{2}{5}P_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline
+
+	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline
 
@@
 remainder of this section is dedicated to characterizing the
-saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
+saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
 base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
@@
 	\hline
-	Signature $\sigma$ & Condition & Saturation \\
+	Signature & Condition & Saturation \\
 	\hline
@@
 	\hline
-	Case & Signature $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
+	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
 	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
@@
 	\hline
-	Signature $\sigma$ & Generator Degrees & Degrees of Relations & $e$ \\
+	Signature & Generator Degrees & Degrees of Relations & $e$ \\
 	\hline

### 2015-07-02 stacky_write_up/spin_cring.tex
read section 7

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 \label{defn:monomial-degree}
-Let $k[x_1$, $\ldots$, $x_n]$ be a graded polynomial
-ring with $\deg x_i = d_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
-k[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
+Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
+ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
+k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
 we define the {\bf degree} of $\alpha$ to be
@@
 \label{defn:grlex}
-The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{1}, \ldots,
-x_{n}]$ with $\deg x_i = d_i$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
-monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
+The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{d_1, 1}, \ldots,
+x_{d_n, n}]$ is defined as follows.
+If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
 \succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:
@@
 The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
-monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
+If $\alpha := \prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ are
+monomials in $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$, then $\alpha
 \succ_{\text{grevlex}} \beta$ if either
@@
 usually have an inclusion $R \supseteq R'$ of log spin canonical
-rings such that $R_\halfcan$ is generated by elements $x_{i}$ and $R$
+rings such that $R_\halfcan$ is generated by elements $x_{d_i, i}$ \todo{They're usually $x_{i,e_i}$ with the degree in the second position, which is a bit strange.
+Somehow, I think we might want to switch the ordering here, though it still might be confusing.} and $R$
 is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
@@
 \label{defn:block-order}
-The \textbf{block term order} is defined as follows. Let $k[y_{1}, \ldots, y_{m}]$ and $k[x_{1}, \ldots,
-x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i,\: \deg x_i = d_i.$ Further assume we are given existing term
-orders $\prec_y$ and $\prec_x$. Let $\alpha :=
-\prod_{j = 1}^{m} y_{j}^{h_i}$ $\prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
-\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $k[y_{1},
-\ldots, y_{m}] \otimes$ $k[x_{1}, \ldots, x_{n}]$.
-Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
-part of $\alpha$ in $k[y_{1}, \ldots, y_{m}]$ and
+Following Voight and Zureick-Brown \cite[Section 8.1]{vzb:stacky}.
+the \textbf{block term order} is defined as follows. Let $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and $k[x_{d_1, 1}, \ldots,
+x_{d_n, n}]$ be weighted polynomial rings with existing term
+orders $\prec_y$ and $\prec_x$, respectively. Let $\alpha :=
+\prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ $\prod_{i = 1}^{n} x_{d_i, i}
+^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{c_j, j}^{h_i'}
+\prod_{i = 1}^{n} x_{d_i, i}^{f_i'}$ be monomials in $k[y_{d_1', 1},
+\ldots, y_{d_m', m}] \otimes$ $k[x_{d_1, 1}, \ldots, x_{d_n, n}]$.
+Let $\alpha_y := \prod_{j = 1}^{m} y_{c_j, j}^{h_i}$ be the
+part of $\alpha$ in $k[y_{c_1, 1}, \ldots, y_{c_m, m}]$ and
 likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
@@
 \label{defn:initial-term}
-Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}],$ with $\deg x_i = d_i$ and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
+Let $\prec$ be an ordering on $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ and let $f \in k[x_{d_1, 1}, \ldots, x_{d_n, n}]$ be a homogeneous
 polynomial. The \textbf{initial term} $\initial(f)$ of $f$
@@
 \label{defn:initial-ideal}
-Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
-$x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
+Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
+$x_{d_n, n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
 the ideal generated by the initial terms of homogeneous polynomials
@@
 \label{defn:grobner-basis}
-Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
-$x_{n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
+Let $I$ be a homogeneous ideal of $k[x_{d_1, 1}$, $\ldots$,
+$x_{d_n, n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
 \textbf{standard basis} for $I$, is a set of elements in $I$
@@
 \[
-	S_i = y_j \cdot S_{i-j}.
+	S_i = y_j S_{i-j}.
 \]
@@
 {\bf Part (b):}
-Let $S$ be as defined in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
+Let $S$ be as above in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
 \[
@@
 \]
-Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $k[u, y_1, \ldots, y_n]$.
-If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
-Let $l$ be maximal such that $a_l\ne 0$.
-Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
-$$
-b_j = \begin{cases}
-	a_j &\text{ if } j \neq i\\
-	a_j + 1 &\text{ if } j=i.
-\end{cases}$$
-
-\noindent
-Then, there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
-and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
-Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
-and have the following still satisfied: each $\gamma_j\le b_j$ 
-and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
-$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
+Notice that $S$ generates the ideal $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$; let $l$ be maximal such that $a_l\ne 0$.
+If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
+and for all $r<h$ $\prod_{j=1}^r {y_j}^{b_j}\in S$, where $b_j=a_j$ when $j\ne i$ and $b_i=a_i+1$.
+Choose $(\gamma_1, \ldots, \gamma_n)$ minimal (that is, so that we cannot decrease any $\gamma_j$ and have the following still satisfied) such that each $\gamma_j\le b_j$ and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$; our recursive definition of $S$ implies that for each $1\le r< h$, we still have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
 
 We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
-Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition (***) holds.
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
+Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above immediately gives (**).
+Since for each $r<h$, $\prod_{j=1}^r y_{j}^{a_j}\in S$, we get condition (***).
 Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
 
-\todo{how to avoid polynomials hangining over lines like this, ask david} Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 
-There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
-where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
-In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
-result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
-0$, the proof is a rather involved induction using Lemma
-~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
-remainder of this section is dedicated to characterizing the
-saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
-base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
-cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
-before proving the main theorem in full for all $\delta$ in
-Subsection ~\ref{ssec:g-0-main}.
+As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
+In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
+result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
+On the other hand, the proof when $\delta =
+0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
+characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
+base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
+cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove\todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).
+See if you like them.}
+%before proving the main theorem in full for all $\delta$ in
+%Subsection ~\ref{ssec:g-0-main}.
 
@@
 \label{ssec:g_0_saturation}
-First, we present the saturations of the canonical divisor for
-all cases where $g = 0$ and $\delta = 0,$ as defined in Definition
-~\ref{defn:sat}. The saturations can be computed using Riemann-Roch.
+First, we present the saturations, as defined in Definition
+~\ref{defn:sat}, of the canonical divisor for
+all cases where $g = 0$ and $\delta = 0$. The saturations can be computed using Riemann-Roch.
 By classifying the saturations of all signatures, we can determine
@@
 Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
-(e.g. admissibility). We also show that that the associated spin
+(e.g. admissibility as defined in Definition \ref{defn:admissible}). We also show that that the associated spin
 canonical rings are generated in degree at most $e := \max(5, e_1,
@@
 \label{lem:g-0-admissible-cases}
-Let $(\sx', \Delta, \halfcan')$ be a log spin curve so that $\sx$
-has signature $\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R(
-\sx', \Delta, \halfcan')$ has a presentation generated as a $k$-
-algebra by elements of degree at most $e = \max(5 , e_1, \ldots, e_r
+Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature $(0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is generated by elements of degree at most $e = \max(5 , e_1, \ldots, e_r
 )$ with relations in degree at most $2e$ and $(\sx ', \halfcan', J)
 = (\sx ', -\infty + \sum_{i = 1}^{r} \subhalf{e_i} P_i, J)$ is
-admissible for the following cases:
+admissible in the following cases:
 
@@
 Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
-the remaining cases, we can use a similar method to find a
+the remaining cases, we one follow a similar method to find a
 presentation satisfying the desired conditions.
 
-The following table demonstrates that $R(\sx', 0, L')$ is
+The following table demonstrates \todo{Peter: Demonstrates maybe isn't the right word.  Really the table states it, but we want to find a better word than that.} that $R(\sx', 0, L')$ is
 generated as a $k$-algebra by elements of degree at most $e$
@@
 \end{longtable}
+\todo{Peter: Can we make a better description for the table above?}
 
@@
 they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
-generated by products of two monomials. Again, the procedure for
-verifying these are similar to that given in Example
+generated by products of two monomials. Again, the procedure to
+verify these is similar to that in Example
 ~\ref{eg:base-0-377}.
@@
 
-	(c) & $(0; 3, 7, 7; 0)$ & $\{3\}$ & $2$ & $0$ \\ \hline
+	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
 
@@
 \end{longtable}
+\todo{Peter: In case c, I changed $J=\{3\}$ to $J=\{2, 3\}$.}
+\todo{Peter: I don't particularly like split tables.  Might we consider not using [h], so its not split}
 
@@
 ~\ref{lem:raise-stacky-order}, and Corollary
-~\ref{cor:raise-stacky-order} inductively on the cases of Table
-~\ref{table:g-0-base-cases} to obtain the desired bounds on the
+~\ref{cor:raise-stacky-order} to induct from the cases of Table
+~\ref{table:g-0-base-cases} and obtain the desired bounds on the
 generator and relation degrees for log spin canonical rings of
@@
 ~\ref{ssec:g-0-main}.
-
+\todo{Peter: I don't think this paragraph should be here.
+It seems like its kind of redundant given section 7.4.
+Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}
 %Through the application of two inductively adding 
@@
 and in particular describe the only exceptions to Theorem ~\ref{thm:main}
-in the case $g = 0$.
+in the case $g = 0$.  \todo{This paragraph is kind of repetitive, and awkward.}
 
@@
 \end{longtable}
+\todo{Peter: Technically, shouldn't the first and last $e$ be 5 instead of 3, since $e=\max(5, e_i)$?}
 
@@
 the generator and relation degree. Notice that each of these
-exceptional cases, apart from $(0; 3, 5, 7; 0)$, corresponds to a
-signature with saturation not equal to
-3, 5, or 9. as seen in Table ~\ref{table:g-0-sat}. Heuristically,
-these exceptional saturations can be viewed as ``forcing'' generators
-(and thus relations) to lie in higher degrees than expected.
+exceptional cases, apart from $(0; 3, 5, 7; 0)$, has saturation not in $\{3, 5, 9\}$ as seen in Table ~\ref{table:g-0-sat}.
+Heuristically, \todo{Peter: Is heuristically the right word here?
+I interpret heuristically to mean ``providing a technique or method to solve a problem,'' whereas I think you mean something more along the lines of intuitively.}
+these exceptional saturations can be viewed as ``forcing'' generators and relations in higher degrees than expected.
 \end{rem}
@@
 \label{ssec:g-0-main}
-Now we can combine this.
+Now we can combine the base cases from Subsection \ref{ssec:g_0_base} with the inductive lemmas of Section \ref{sec:induction}.
 
@@
 n \cdot \infty$ with $n \in \BZ$. This is the classical
-case which is done, with $L$ replaced by $K$, by Voight and
+case which is done, with $L$ replaced by $K$, \todo{Peter: I don't think its helpful to say with $L$ replaced by $K$.
+It might slightly confuse the reader into thinking that replacing half canonical divisor with canonical divisor changes the problem.} by Voight and
 Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.
 
-First, let us consider the case when $\delta \geq 2$. In any such case,
-$\lfloor \halfcan \rfloor$ is an effective divisor and the conditions
-of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can apply
-the Lemma ~\ref{lem:sat-1} inductively on the classical case with no stacky points
-to get that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
+First, consider the case when $\delta \geq 2$. \todo{Peter: it feels a tiny bit redundant here, as we kind of said this in the introduction to the section.}
+ In any such cases,
+$\halfcan_X$ is an effective divisor so we can inductively apply
+the Lemma ~\ref{lem:sat-1} from the classical non-stacky case
+to deduce that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
 with relations generated up to degree $2e$.
 
-By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan$ is not effective.
-Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
-so that $\sigma$ is not one of the exceptional cases in Table
-~\ref{table:g-0-exceptional}. Note that if $r < 3$, then $\deg 
-\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
-trivial case where $R(\sx, \Delta, \halfcan) = k$. Thus, we now
-only consider the cases with $r \geq 3$.
+By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan_X$ is not effective.
+Let $\sigma = (0; e_1, \ldots, e_r; 0)$ not be one of the exceptional cases in Table
+~\ref{table:g-0-exceptional}.  We get the following three cases, depending on the value of $r$:
+
+\vskip.1in
+\noindent
+{\sf Case 1: $r<3$}
+
+If $r < 3$, then $\deg 
+\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we get the
+trivial ring $R(\sx, \Delta, \halfcan) = k$.
+
+\vskip.1in
+\noindent
+{\sf Case 2: $3\le r \le 5$}
+
+If $3\le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
+then we may apply Lemma ~\ref{lem:g-0-admissible-cases} and
+Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
+from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
+\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
+\ldots, e_r)$ with relations generated up to degree $2e$.
+
+\vskip.1in
+\noindent
+{\sf Case 3: $r > 5$}
 
@@
 $2e$.
-
-If $r \leq 5$ and $\sigma$ is not one of the exceptional cases,
-then we may similarly apply Lemma ~\ref{lem:g-0-admissible-cases} and
-Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
-from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
-\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
-\ldots, e_r)$ with relations generated up to degree $2e$.
  \end{proof}

### 2015-07-02 stacky_write_up/spin_cring.tex
some minor edits in lem sat 1

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 \begin{enumerate}
-\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $\deg(y_i)=d_i$ and $-\ord_P^{L'}(y_i)=c_i$.
+\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
+	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = d_i$ and $-\ord_P
+	^{L'}(y_i) = c_i$.
 
@@
 	\]
-Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order giving $y_1, \ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.
-If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
+	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
+	Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1,
+	\ldots, y_n]$ with the block order giving the order giving $y_1, 
+	\ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.
+
+	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
+	\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
+	\to R_{\halfcan}$ respectively, then
 
@@
 	\end{align*}
-where 
-$V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
- and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j \in \BN_{\ge 0}$ such that
+	where $V = \{x_i y_j: 1 \le i \le m, 1 \le j \le n\}$ and $U_i$ is
+	the set of monomials of the form $\prod_{j = 1}^{i} y_j^{a_j}$ with
+	$a_j \in \BN_{\ge 0}$ such that
 	\begin{enumerate}
-	\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1},$\\
-	\item[(**)] there does not exist $(b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1},$ \\
-	\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r+1}$.
+		\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$, \\
+		\item[(**)] there does not exist $(b_1, \ldots b_i) \ne (a_1,
+			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
+			c_j \ge	c_{i + 1}$, \\
+		\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
 	\end{enumerate}
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$).
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
+	in degrees at most $\beta$ with $I$ generated over $I'$ in
+	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
+	\max_{1 \leq i \leq m}(\deg(x_i)))$).
 \end{enumerate}

### 2015-07-02 stacky_write_up/spin_cring.tex

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 
-There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
-where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
-In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
-result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
-0$, the proof is a rather involved induction using Lemma
-~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
-remainder of this section is dedicated to characterizing the
-saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
-base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
-cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
-before proving the main theorem in full for all $\delta$ in
-Subsection ~\ref{ssec:g-0-main}.
+As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
+In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
+result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
+On the other hand, the proof when $\delta =
+0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
+characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
+base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
+cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove \todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).
+See if you like them.}
+%before proving the main theorem in full for all $\delta$ in
+%Subsection ~\ref{ssec:g-0-main}.
 

### 2015-07-02 stacky_write_up/spin_cring.tex
added remark of precise statement of main corollary

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 {vzb:stacky}, provides a statement on rings of modular forms.
-Together with the main theorem from Voight and Zureick-Brown \cite
+Together with the main theorems from Voight and Zureick-Brown \cite
+[Theorem 9.3.1]{vzb:stacky} and \cite
 [Theorem 9.3.1]{vzb:stacky}, we have the following application to
@@
 \end{cor}
+
+\begin{rem}
+In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $3 \cdot \max(3, e_1, \ldots, e_r)$ and relation
+bound of $6 \cdot \max(3, e_1,\ldots, e_r)$ can be reduced to $\max(3,e_1, \ldots, e_r)$ and $2 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
+~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 9.3.1]{vzb:stacky} for a more precise statement of these bounds.
+\end{rem}
 
@@
 \begin{enumerate}
-\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
-	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = d_i$ and $-\ord_P
-	^{L'}(y_i) = c_i$.
+\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $\deg(y_i)=d_i$ and $-\ord_P^{L'}(y_i)=c_i$.
 
@@
 \]
-	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
-	Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1,
-	\ldots, y_n]$ with the block order giving the order giving $y_1, 
-	\ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.
-
-	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
-	\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
-	\to R_{\halfcan}$ respectively, then
+Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with the block order giving the order giving $y_1, \ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.
+If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]\to R_{\halfcan}$ respectively, then
 
@@
 \end{align*}
-	where $V = \{x_i y_j: 1 \le i \le m, 1 \le j \le n\}$ and $U_i$ is
-	the set of monomials of the form $\prod_{j = 1}^{i} y_j^{a_j}$ with
-	$a_j \in \BN_{\ge 0}$ such that
+where 
+$V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
+ and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_j^{a_j}$ with $a_j \in \BN_{\ge 0}$ such that
 \begin{enumerate}
-		\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$, \\
-		\item[(**)] there does not exist $(b_1, \ldots b_i) \ne (a_1,
-			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
-			c_j \ge	c_{i + 1}$, \\
-		\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
+	\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1},$\\
+	\item[(**)] there does not exist $(b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ with all $b_j\le a_j$ and $\sum_{j=1}^i b_jc_j\ge c_{i+1},$ \\
+	\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r+1}$.
 \end{enumerate}
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees at most $\beta$ with $I$ generated over $I'$ in
-	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
-	\max_{1 \leq i \leq m}(\deg(x_i)))$).
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \tau)$ (where $\tau = \max(1, \max_{1\le i, m}(\deg(x_i)))$).
 \end{enumerate}
@@
 
-\todo{how to avoid polynomials hangining over lines like this, ask david} Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 \end{align}
+
 \todo{Peter: I understand why this should be true, although its not clear to me that there it easily follows.
 Maybe we should explain it a little as to not confuse the reader.
-Aaron: Can we ask David, this was clear to me in his paper, and he also didn't include it.}
+Aaron: Can we ask David, this was clear to me in his paper, and he also didn't include it.
+Say by the definition}
 
@@
 %with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
-\todo{cite this somewhere, maybe ask david for a place to cite?
-We can cite http://www.math.harvard.edu/~ctm/home/text/class/harvard/213b/14/html/home/course/course.pdf, for example, from complex analysis course notes!
-Don't use coarse notes}
 %Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.

### 2015-07-02 stacky_write_up/spin_cring.tex
g0 intro revision

@@
 \label{sec:g_0}
-We will prove that if $(\sx , \Delta, \halfcan)$ is a log spin curve and
-$\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
-then $R(\sx , \Delta, L)$ is generated in degree at most $e := \max(
-5, e_1, \ldots, e_r)$ with relations generated in degree at most $2e
-$, so long as $\sigma$ does not lie in the finite list given in Table ~\ref{table:g-0-exceptional}.
-
-As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
-In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
-result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
-On the other hand, the proof when $\delta =
-0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
-characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
-base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
-cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove \todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).
-See if you like them.}
-%before proving the main theorem in full for all $\delta$ in
-%Subsection ~\ref{ssec:g-0-main}.
+We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
+curve and $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;
+\delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
+$e := \max(5, e_1, \ldots, e_r)$ with relations generated in degree
+at most $2e$, so long as $\sigma$ does not lie in the finite list
+given in Table ~\ref{table:g-0-exceptional}.
+
+As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even. Thus,
+we can reduce the problem into two cases: $\delta \geq 2$ and
+$\delta = 0$. In the former case, $\halfcan$ is linearly equivalent
+to an effective divisor, so the result of Theorem \ref{thm:main}
+follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1}
+to add the necessary stacky points. On the other hand, the proof
+when $\delta = 0$ is more involved. We dedicate the remainder of
+this section to that case in the following steps: characterizing
+saturations points (Subsection ~\ref{ssec:g_0_saturation}),
+describing base cases (Subsection ~\ref{ssec:g_0_base}), and
+presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
+Finally, we apply inductive processes using Lemma ~\ref{lem:sat-3}
+and Lemma ~\ref{lem:raise-stacky-order} to prove the main theorem
+in the full genus zero case (Subsection ~\ref{ssec:g-0-main}).
 

### 2015-07-02 stacky_write_up/spin_cring.tex
revise intro to inductive lemmas

@@
 \label{sec:induction}
-First we present several lemmas which provide the
-inductive steps for the proof of the main theorem: Theorem
-~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
-%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
-	which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
-}{\beta}P}$ from those of $R_{\halfcan'}$, where
-%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
+First we present several lemmas which provide the inductive steps
+for the proof of the main theorem: Theorem ~\ref{thm:main}. In
+Subsection ~\ref{ssec:add-points} we prove three lemmas which
+determine the generators and relations of $R_\halfcan = R_{\halfcan'
++ \frac{\alpha }{\beta}P}$ from those of $R_{\halfcan'}$, where
 $\halfcan' \in \BQ \otimes \di X$ and $\frac{\alpha}{\beta} \in \BQ$. 
-In
-Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log spin canonical ring of a curve with signature $(g; e_1', 
-\ldots, e_\tau'; 0)$ to that of a
-curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$.
-\todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.
-There are too many clauses...}
+In Subsection ~\ref{ssec:raise-orders}, we prove an inductive lemma
+allowing us to transfer information about the log spin canonical 
+ring of a stacky curve to those of stacky curves with stabilizer
+orders incremented by $2$ and fixed log divisor and stacky points.
+
 %While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 

### 2015-07-02 stacky_write_up/spin_cring.tex
Edits to sections 8 and 9

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 
-This paper leaves open many directions for further research.
+This paper leaves open many directions for further research.\todo{Peter: This sentence sounds weird.  It's also kind of not true; as David said, we are kind of closing the topic}
 
@@
 		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors would translate to rings of fractional weight modular 
+		divisors translate to rings of fractional weight ($\frac{2}{n}$) modular 
 		forms. As defined in Adler and Ramanan (in the passage immediately 
@@
 		^{e_3} = 0$.
-
-		Having motivated the importance of fractional weight modular forms, we pose the following question:
-
+\todo{Peter: I don't know if it is so worth while giving an explicit definition and precisely defining the work already done.
+A general outline might suffice and be easier/shorter to read.}
+
+		This motivates the following question:
+
+\todo{Peter: Would this be better as a conjecture?}
 		\begin{question}
 		\label{ques:fractional-weight}
-			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ 
+			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
 			where $K$ is the canonical divisor of $\sx$, can one bound the 
@@
 		\end{question}
-		Note that that the above question is answered affirmatively in the 
-		case that $\sx$ has genus $0$ and $D$ is effective, as follows by 
-		inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature 
+		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
+		gives an affirmative answer to this question: If $\sx$ has signature 
 		$(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
 		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
-		$2e$. Additionally, it may be possible to modify the proof of Lemma
+		$2e$. 
+		It may be possible to modify the proof of Lemma
 		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
-		weight modular forms. Given suitable generalizations of these 
-		lemmas, one may be able to approach the problem of finding 
-		generators and relations for fractional weight modular forms using 
-		techniques similar to those in this paper.
-
-	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky},
-		the notion of a generic initial ideal is defined, which 
+		weight modular forms. 
+		Suitable generalizations of the 
+		lemmas of Section ~\ref{sec:induction} might allow one to 
+		follow similar questions to this paper and provide a general 
+		answer to Question ~\ref{ques:fractional-weight}.
+
+	\item Voight and Zureick Brown define
+		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
 		encapsulates the idea of whether the relations for $R_\halfcan$ are 
-		generically chosen, in a precise sense. The proof of Theorem
-		~\ref{thm:main} decidedly does not yield a generic initial ideal, 
-		as generators and relations are constructed in a highly nongeneric 
-		manner. In particular, Lemma ~\ref{lem:raise-stacky-order} 
+		generically chosen, in a precise sense. 
+		The proof of Theorem
+		~\ref{thm:main} is decidedly non-generic. 
+		In particular, Lemma ~\ref{lem:raise-stacky-order} 
 		constructs generators with non-maximal pole orders at certain 
@@
 			does there exist a function $\sigma \mapsto d(\sigma)$ so that
-			the generic initial ideal {\rm(} with some specified ordering{\rm)}
+			the generic initial ideal {\rm(}with some specified ordering{\rm)}
 			is generated in degree at most $d(\sigma)$? Can one write down the
 			generic initial ideal explicitly?
-		\end{question}
+		\end{question}\todo{Peter: This whole question is kind of confusing.  I don't know what it is trying to say.}
 
 	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
-		proof of Theorem ~\ref{thm:main} given in this paper gives an 
+		proof of Theorem ~\ref{thm:main} 
+		%given in this paper 
+		gives an 
 		explicit procedure for computing the generators and relations of $R_
-		L$ when the genus of $\sx$ is $0$ or $1$.
+		\halfcan$ when the genus of $\sx$ \todo{Peter: Minor note: should we say genus of $\sx$ or genus of $X$; did we actually define that a genus of a stacky curve equals that of its coarse space?} is $0$ or $1$.
+\todo{Peter: This question also seems like it might be the most important (as far as modular forms applications go.
+Maybe we should put it first?}
 		\begin{question}
 		\label{ques:algorithm}
-			Can one give an algorithm for explicitly computing the generators 
+			Is there an explicit procedure for computing the generators 
 			and relations for an arbitrary genus $g \geq 2$ curve?
@@
 		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
-		algorithm for determining the generators of $L$. This raises the 
+		algorithm for inductively determining the generators of $L$. 
+		This reduces Question \ref{ques:algorithm} to the 
 		following Petri-like question:
@@
 \todo{Aaron, I tried to edit the following question, but it still seems a bit imprecise, and the question in particular is a bit of a long sentence.}
+\todo{Peter @ Aaron: I think the last sentence of the question can be removed; generic isn't relevant in this part of further questions (it was relevant in part (2)).
+Also the sentence after the question can be removed.}
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
 		the work of Reid \cite[Theorem 3.4]{reid:infinitesimal}. We use his 
-		proof of that the 
+		proof that the 
 		spin canonical ring is generated in degree at most 5 with
@@
 		bound of 5 and 10 to the log case, and then apply our inductive 
-		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  Reid \cite[Theorem 3.4]{reid:infinitesimal} in fact proves something slightly stronger: that in 
+		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  However, Reid in fact proves something slightly stronger \cite[Theorem 3.4]{reid:infinitesimal}: that in 
 		most cases his bound is actually 3 and 6 with well-characterized 
 		exceptions.
-		\begin{question}\label{ques:reduce-5,10-to-4,8}
-			In the case that the genus $g \geq 2,$ can we reduce the bounds in Theorem \ref{thm:main} on 
-			the degrees of generation and relations from $e = \max(5,e_1,\ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to $\max(4,e_1, \ldots, e_r)$ and $
-			\max(8, 2e_1, \ldots, 2e_r),$ apart from a finite list of exceptions?
-		\end{question}
+		Generalizing this slightly stronger bound to the (non-stacky) log case case would allow us to inductively apply the lemmas from Section ~\ref{sec:induction} and improve Theorem ~\ref{thm:main} as follows:
+		\begin{conjecture}\label{ques:reduce-5,10-to-4,8}
+			When $g \geq 2,$ the bounds in Theorem \ref{thm:main} on 
+			the degrees of generation and relations can be reduced from 
+			$e = \max(5,e_1,\ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
+			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
+			apart from a finite list of exceptions?
+		\end{conjecture}
+		\todo{Peter: I don't like a finite list of exceptions.
+The list contains infinitely many non-isomorphic stacky curves.
+Finite family might also be imperfect.
+Can we say except when $g=2$ (I believe there will be infinitely many counterexamples there) or it lies in a finite list of exception?
+Do we believe that to be true?}
 		\begin{rem}\label{rem:reduce-3,6}
-			It is unlikely that this can be reduced further for the case 
-			of stacky curves, because Lemma \ref{lem:sat-2}, which allows 
-			us to add a stacky point in genus $g > 0$ saturated at 2, 
+			It is unlikely that these bounds can be reduced further to 
+			$e''=\max(3, e_1, \ldots, e_r)$ and $2e''$, 
+			because Lemma \ref{lem:sat-2}'s construction always
 			requires a generator in degree 4 and potentially a relation in 
-			degree 8, even when inductively adding on stacky points of 
-			stabilizer order 3. However, perhaps in the non-stacky case, one 
-			may be able able to generalize the result of Reid \cite[Theorem 3.4
-			]{reid:infinitesimal} to show that log spin canonical rings can be 
-			generated in degree at most 3 with relations in degree at most 6, 
-			apart from a well characterized list of exceptions.
+			degree 8, when adding a stacky point with stabilizer order 3. 
+%			Perhaps in the non-stacky case, one 
+%			may be able able to generalize the result of Reid \cite[Theorem 3.4
+%			]{reid:infinitesimal} to show that log spin canonical rings can be 
+%			generated in degree at most 3 with relations in degree at most 6, 
+%			apart from a well characterized list of exceptions.
 			\end{rem}
 	\item While Theorem ~\ref{thm:main} gives a minimal set of 
-		generators for the log spin canonical ring $R_\halfcan,$ the set of 
+		generators \todo{Peter: I believe this is actually not true.
+If $R_{\halfcan'}$ is minimally generated by $x_1, \ldots x_m$ and $R_\halfcan$ is generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$, then $R_{\halfcan}$ is {\emph{generated}} by $x_1, \ldots, x_m, y_1, \ldots y_n$ but not necessarily minimally.
+It's possible to have something like $y_1y_3-y_2^2=x_i$.}
+		for the log spin canonical ring $R_\halfcan,$ the set of 
 		relations is not minimal. In many of the $g = 0$ and $g=1$ cases, 
@@
 \section{Acknowledgments}
-We are grateful to David Zureick-Brown for introducing us to this
-field of study, providing incredibly helpful guidance, and being an
+We are grateful to David Zureick-Brown for introducing us to the study of stacky canonical rings, providing invaluable guidance, and being \todo{Peter: using passive voice (i.e.
+``being'') makes this sound kind of generic} an
 excellent project mentor. We also thank Ken Ono and the Emory 
@@
 providing a great environment for mathematical learning and 
-collaboration. We thank Jorge Sentieiro Neves for pointing out the
-bound given by Reid's work on the maximal degrees of minimal
+collaboration. \todo{Peter: Does it make sense to thank the REU? Ken essentially is the REU.} We thank Jorge Sentieiro Neves for pointing out the
+bounds given by Reid's work on the maximal degrees of minimal
 generators and relations of spin canonical rings in high genera.
-Finally, we gratefully acknowledge that our research was
-financially supported by NSF Grant Award Number 1250467 via the
-Emory University Number Theory REU. We deeply appreciate all of the
+Finally, we gratefully acknowledge the financial support given by NSF Grant Award Number 1250467 via the
+Emory University Number Theory REU. 
+We deeply appreciate all of the
 support that has made our work possible.

### 2015-07-02 stacky_write_up/spin_cring.tex
revise g0 admissible cases statement & proof intro

@@
 \label{lem:g-0-admissible-cases}
-Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature $(0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is generated by elements of degree at most $e = \max(5 , e_1, \ldots, e_r
-)$ with relations in degree at most $2e$ and $(\sx ', \halfcan', J)
-= (\sx ', -\infty + \sum_{i = 1}^{r} \subhalf{e_i} P_i, J)$ is
-admissible in the following cases:
+Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
+$\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
+generated by elements of degree at most $e = \max(5 , e_1, \ldots,
+e_r)$ with relations in degree at most $2e$. Furthermore, each of
+the cases in Table ~\ref{table:g-0-base-cases} satisfy the
+conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e. either $(\sx',
+\halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}
+P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
+Case (1) of Remark ~\ref{rem:three-cases}):
 
@@
 Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
-the remaining cases, we one follow a similar method to find a
-presentation satisfying the desired conditions.
-
-The following table demonstrates \todo{Peter: Demonstrates maybe isn't the right word.  Really the table states it, but we want to find a better word than that.} that $R(\sx', 0, L')$ is
-generated as a $k$-algebra by elements of degree at most $e$
-with relations in degree at most $2e$ for each case. Also note
-that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
-and any generator $z$ of $R'$.
+the remaining cases, we follow a similar method to find a
+presentation satisfying the desired conditions. The log spin
+canonical ring $R(\sx', 0, L')$ is generated as a $k$-algebra by
+elements of degree at most $e$ with relations in degree at most $2e$
+for each case as described in the following table.
 \begin{longtable}

### 2015-07-02 stacky_write_up/spin_cring.tex
edited first paragraph under thm 7.4

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 If $\sx$ has no stacky points, then we can assume that $L \sim
-n \cdot \infty$ with $n \in \BZ$. This is the classical
-case which is done, with $L$ replaced by $K$, \todo{Peter: I don't think its helpful to say with $L$ replaced by $K$.
-It might slightly confuse the reader into thinking that replacing half canonical divisor with canonical divisor changes the problem.} by Voight and
-Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.
+n \cdot \infty$ with $n \in \BZ$.
+When $n=-1$, then $R_\halfcan=k$.
+When $n=0$, then $R_\halfcan = k[x]$.
+When $n>0$, inductively applying Lemma \ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1 with relations generated in degree 2.
+All three of these cases meet the conclusion of Theorem \ref{thm:g-0-main}.
 

### 2015-07-02 stacky_write_up/spin_cring.tex
clabel *, relabel Ad, add rem:377, edit cor:raise

@@
 Section ~\ref{sec:background}. Then, we develop various inductive
-tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
-~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
+tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g-high},
+~\ref{sec:g-1}, and ~\ref{sec:g-0}, we prove Theorem
 ~\ref{thm:main} in the genus $ g \geq 2$, genus
@@
 \begin{enumerate}
-	\item[\customlabel{Ad-i}{(Ad-i)}] First, 
+	\item[\customlabel{custom:Ad-i}{(Ad-i)}] First, 
 		\begin{align*}
@@
 		\end{align*}
-		\item[\customlabel{Ad-ii}{(Ad-ii)}] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}
-^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[\customlabel{Ad-iii}{(Ad-iii)}] Third, we have
+	\item[\customlabel{custom:Ad-ii}{(Ad-ii)}] Second, every generator $z 
+		\in \{x_1, \ldots, x_m\} \cup \{y_{j, e_i'}: j\in J - \{i\} \}$ 
+		satisfies
+		\begin{align*}
+			\frac{-\ord_{Q_i}^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[\customlabel{custom:Ad-iii}{(Ad-iii)}] Third, we have
 		\begin{align*}
@@
 $y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-\ref{Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{Ad-ii} We may also choose
+\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
@@
 \halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so \ref{Ad-iii} is satisfied and
+\frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
 $(\sigma, \sx', J)$ is admissible.
@@
 We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{Ad-i} holds.
-We next check \ref{Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
+Hence, \ref{custom:Ad-i} holds.
+We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
 Here, by construction
@@
 \end{cases}.$$
-Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{Ad-ii} holds.
-Finally, to check \ref{Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
+Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
 \end{example}
+
+\begin{rem}
+\label{rem:base-0-377}
+Example ~\ref{eg:base-0-377} is one of the inductive base cases
+used in the genus zero case (Section ~\ref{sec:g-0}) as
+listed in Table ~\ref{table:g-0-base-cases}.
+\end{rem}
 
@@
 \item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T\succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
+\item $T \succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
 \item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
@@
 	\begin{enumerate}
-		\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$, \\
-		\item[(**)] there does not exist $(b_1, \ldots b_i) \ne (a_1,
+		\item[\customlabel{custom:sat-1-*}{(*)}] $\sum_{j = 1}^i a_j c_j \ge c_{i+1}$, \\
+		\item[\customlabel{custom:sat-1-**}{(**)}] there does not exist $(b_1, \ldots b_i) \ne (a_1,
 			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
 			c_j \ge	c_{i + 1}$, \\
-		\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
+		\item[\customlabel{custom:sat-1-***}{(***)}] there does not
+			exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
 	\end{enumerate}
@@
 
-We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
-Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition (***) holds.
+We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.
+Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies \ref{custom:sat-1-**}.
+Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition \ref{custom:sat-1-***} holds.
 Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
@@
 \label{ssec:raise-orders}
-In this subsection, we present Lemma
-~\ref{lem:raise-stacky-order}, whose proof is almost identical to one of Voight and Zureick-Brown \cite[Theorem 8.5.7]{vzb:stacky}.
-Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem
-~\ref{thm:main}, holds for a curve with signature
-$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' = \cdots = e_r'$ satisfying certain admissibility (cf.
-Definition ~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for a curve with
-signature $(g; e_1', \ldots, e_k', e_{k+1}'+2,\ldots, e_r'+2; \delta)$. 
+In this subsection, we present Lemma ~\ref{lem:raise-stacky-order},
+whose proof is almost identical to one of Voight and Zureick-Brown
+\cite[Theorem 8.5.7]{vzb:stacky}. Lemma
+~\ref{lem:raise-stacky-order} implies that if the main result,
+Theorem ~\ref{thm:main}, holds for a curve with signature $(g; e_1',
+\ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' =
+\cdots = e_r'$ satisfying certain admissibility (cf. Definition
+~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for
+a curve with signature $(g; e _1', \ldots, e_k', e_{k + 1}' + 2,
+\ldots, e_r' + 2; \delta)$. 
 %In order to state Lemma
@@
 %\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{custom:Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
 %\end{rem}
@@
 %\begin{proof}
-%To show \ref{Ad-i} and \ref{Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
-Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{Ad-i}.
-Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{Ad-ii} satisfied so $\frac{-\ord_{Q_l}
-%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{Ad-ii} follows in genus 0?}
+%To show \ref{custom:Ad-i} and \ref{custom:Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{custom:Ad-i}.
+Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{custom:Ad-ii} satisfied so $\frac{-\ord_{Q_l}
+%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{custom:Ad-ii} follows in genus 0?}
 %
@@
 %\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{custom:Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 %\end{itemize}
@@
 
-The following Lemma will slightly strengthen condition \ref{Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+The following Lemma will slightly strengthen condition \ref{custom:Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 \label{lem:admissible_inequality}
-For any $z$ as in condition \ref{Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{Ad-ii} implies the
+For any $z$ as in condition \ref{custom:Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{custom:Ad-ii} implies the
 tighter inequality that
@@
 \begin{proof}
-We know by \ref{Ad-ii} that
+We know by \ref{custom:Ad-ii} that
 
@@
 \begin{proof}
-Each of the conditions \ref{Ad-i}, \ref{Ad-ii}, and \ref{Ad-iii} hold for $W$
+Each of the conditions \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} hold for $W$
 if they hold for $J$.
@@
 \label{rem:three-cases}
-For our inductive arguments in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
-stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
-curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
-\delta)$, and our base cases include signatures $\sigma$ characterized by one of the following: cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
+For our inductive arguments in Theorems ~\ref{thm:g-high-main},
+~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a
+single stacky point with stabilizer order $3$. Say $(\sx, \Delta,
+\halfcan)$ is a log spin curve with signature $\sigma = (g; e_1,
+\ldots, e_r,\delta) = (g;3,\ldots, 3, \delta)$, and our base cases
+include signatures $\sigma$ characterized by one of the following:
+cases, which we will soon refer to in Lemma
+~\ref{lem:raise-stacky-order}:
+
 \begin{enumerate}
-	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
-	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
-	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
+	\item[\customlabel{custom:three-cases-1}{(1)}] $g = 0, e_1 =
+		\cdots = e_r = 3, \delta = 0$, and $r \geq 5$
+	\item[\customlabel{custom:three-cases-2}{(2)}] $g = 1, e_1 =
+		\cdots = e_r = 3, \delta = 0$, and $ r \geq 2$
+	\item[\customlabel{custom:three-cases-3}{(3)}] $g \geq 2, e_1 =
+		\cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_1,\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J,$ as in Definition ~\ref{defn:admissible} or
-	\item $\sigma$ is one of the signatures described in cases (1), (2) and (3) of Remark ~\ref{rem:three-cases} and $y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of $\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ for $1 \leq  i \leq r$.
+	\item $(\sx',\halfcan', J)$ is admissible with generators $x_1,
+		\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J$, as 
+		in Definition ~\ref{defn:admissible} or
+	\item $\sigma$ is one of the signatures described in Cases
+		\ref{custom:three-cases-1}, \ref{custom:three-cases-2} and
+		\ref{custom:three-cases-3} of Remark ~\ref{rem:three-cases} and
+		$y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of
+		$\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$
+		for $1 \leq  i \leq r$.
 \end{enumerate}
@@
 	\item[(b)]
+
 %The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
@@
 \noindent
-The assumption \ref{Ad-iii} implies
+The assumption \ref{custom:Ad-iii} implies
 \begin{align*}
@@
 
-By part (a), condition \ref{Ad-ii}, and Lemma
+By part (a), condition \ref{custom:Ad-ii}, and Lemma
 ~\ref{lem:admissible_inequality} we have
@@
 {\bf Part (d):}
-To check (d), we show \ref{Ad-i},\ref{Ad-ii}, and \ref{Ad-iii} are satisfied. We know \ref{Ad-i} holds by part (b), taking the $y_{
-i, e_i}$ as the generators in degree $e_i$. Next, \ref{Ad-ii} is
+To check (d), we show \ref{custom:Ad-i},\ref{custom:Ad-ii}, and \ref{custom:Ad-iii} are satisfied. We know \ref{custom:Ad-i} holds by part (b), taking the $y_{
+i, e_i}$ as the generators in degree $e_i$. Next, \ref{custom:Ad-ii} is
 strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
-Finally, if \ref{Ad-iii} holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that \ref{Ad-iii} holds for $d > 0$
+Finally, if \ref{custom:Ad-iii} holds for $e$ then it holds for $e + 2$ by
+definition. This is where we use that \ref{custom:Ad-iii} holds for $d > 0$
 and not just for $d = 0$.
@@
 \label{cor:raise-stacky-order}
-Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}.
-Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
-so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}.
-Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
+Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1
+',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of
+Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1,\ldots,r\}$ and
+$e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
+so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma
+~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then,
+for any spin curve $(\sx, \Delta, L)$ so that $\sx$ and $\sx'$ have
+the same coarse space $X = X'$ with the same set of stacky points,
+and $  \sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1
+\leq e_2 \leq \cdots e_r$ so that
 \begin{align*}
@@
 \end{cor}
+
 \begin{proof}
@@
 
-Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is admissible.
-
-Since $(*_0)$ holds by assumption, by induction on $i$, it suffices to show that if $(*_i)$ holds then so does $(*_{i+1}).$ 
-Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subseteq J_i$.
-Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2},$ times, for the fixed set $J_{i+1},$ we see $(*_{i+1})$ holds.
+Let $(*_i)$ denote the condition that $(\sx_i, \Delta, L_i)$
+satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and
+Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is
+admissible. Since $(*_0)$ holds by assumption, it suffices to show
+that if $(*_i)$ holds then so does $(*_{i + 1})$. Indeed, $(\sx_i,
+\halfcan_i, J_{i + 1})$ is admissible by an application of Lemma
+~\ref{lem:admissible_subset} and the fact that $J_{i + 1} \subseteq J
+_i$. Then, applying Lemma ~\ref{lem:raise-stacky-order} with the
+fixed set $J_{i + 1}$ repeatedly ($\frac{e_{i + 1} - e_i}{2}$ many
+times) yields $(*_{i + 1})$.
 \end{proof}
@@
 \section{High Genus}
-\label{sec:g_high}
+\label{sec:g-high}
 We now consider the case when the genus is at least 2.
 In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g_1} and ~\ref{sec:g_0} where we not only obtain bounds, but also obtain inductive presentations.
+In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations.
 The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
@@
 \label{cor:g-2-presentation-bound}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
 with $g \geq 2$. Then $X$ has minimal generators in degree at most
@@
 \section{Genus One}
-\label{sec:g_1}
+\label{sec:g-1}
 
@@
 \ssec{Genus One Base Cases}
-\label{ssec:g_1_base}
+\label{ssec:g-1_base}
 In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.
@@
 \section{Genus Zero}
-\label{sec:g_0}
+\label{sec:g-0}
 We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
@@
 this section to that case in the following steps: characterizing
-saturations points (Subsection ~\ref{ssec:g_0_saturation}),
-describing base cases (Subsection ~\ref{ssec:g_0_base}), and
+saturations points (Subsection ~\ref{ssec:g-0_saturation}),
+describing base cases (Subsection ~\ref{ssec:g-0_base}), and
 presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
@@
 \ssec{Saturation}
-\label{ssec:g_0_saturation}
+\label{ssec:g-0_saturation}
 First, we present the saturations, as defined in Definition
@@
 \ssec{Base Cases}
-\label{ssec:g_0_base}
+\label{ssec:g-0_base}
 In order to apply Lemma ~\ref{lem:sat-3} and Lemma
@@
 P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
-Case (1) of Remark ~\ref{rem:three-cases}):
+Case ~\ref{custom:three-cases-1} of Remark ~\ref{rem:three-cases}):
 
@@
 We can also always find a presentation for these cases such that
-they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
+they satisfy \ref{custom:Ad-i} and \ref{custom:Ad-ii} and that $\initial(I')$ is
 generated by products of two monomials. Again, the procedure to
@@
 
-Furthermore, each case always satisfies \ref{Ad-iii} as demonstrated below.
+Furthermore, each case always satisfies \ref{custom:Ad-iii} as demonstrated below.
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
@@
 
-	\caption{Genus 0 Non-Effective Base Cases \ref{Ad-iii}}
+	\caption{Genus 0 Non-Effective Base Cases \ref{custom:Ad-iii}}
 	\label{table:g-0-base-cases-admissibility}
@@
 \label{ssec:g-0-main}
-Now we can combine the base cases from Subsection \ref{ssec:g_0_base} with the inductive lemmas of Section \ref{sec:induction}.
+Now we can combine the base cases from Subsection \ref{ssec:g-0_base} with the inductive lemmas of Section \ref{sec:induction}.
 

### 2015-07-02 stacky_write_up/spin_cring.tex
read thru last monster paragraph

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 
-\todo{Make the sentences in the abstract shorter}
 \todo{Make sure we call all divisors spin canonical divisors}
@@
 \label{sec:induction}
-First we present several lemmas which provide the inductive steps
-for the proof of the main theorem: Theorem ~\ref{thm:main}. In
-Subsection ~\ref{ssec:add-points} we prove three lemmas which
-determine the generators and relations of $R_\halfcan = R_{\halfcan'
-+ \frac{\alpha }{\beta}P}$ from those of $R_{\halfcan'}$, where
+First we present several lemmas which provide the
+inductive steps for the proof of the main theorem: Theorem
+~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
+%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
+	which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
+}{\beta}P}$ from those of $R_{\halfcan'}$, where
+%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
 $\halfcan' \in \BQ \otimes \di X$ and  $\frac{\alpha}{\beta} \in \BQ$. 
-In Subsection ~\ref{ssec:raise-orders}, we prove an inductive lemma
-allowing us to transfer information about the log spin canonical 
-ring of a stacky curve to those of stacky curves with stabilizer
-orders incremented by $2$ and fixed log divisor and stacky points.
-
+In
+Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log spin canonical ring of a curve with signature $(g; e_1', 
+\ldots, e_\tau'; 0)$ to that of a
+curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$.
+\todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.
+There are too many clauses...}
 %While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
@@
 
+\todo{Say something like a monomial is in $S$ if and only if it satisfies some condition with $c_h,$ and that we use this to check the three (*) conditions.}
 We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
 Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).
@@
 The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
-Note that in addition to $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ being base cases, they are also exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}.\todo{Peter: I don't understand this last sentence?
-How are they base cases?}
+Although $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ are used as base cases for the induction, they are also exceptional cases; see Table ~\ref{table:g-1-exceptional}.
 
@@
 First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $\todo{Peter: Is $\lfloor L|_p\rfloor$ standard notation?
-It looks weird}, as $P$ is not a basepoint of $L'$.
+In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $,
+as $P$ is not a basepoint of $L'$.
 Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $L= L'+P$.
@@
 \label{sec:g_0}
-We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
-curve and $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;
-\delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
-$e := \max(5, e_1, \ldots, e_r)$ with relations generated in degree
-at most $2e$, so long as $\sigma$ does not lie in the finite list
-given in Table ~\ref{table:g-0-exceptional}.
-
-As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even. Thus,
-we can reduce the problem into two cases: $\delta \geq 2$ and
-$\delta = 0$. In the former case, $\halfcan$ is linearly equivalent
-to an effective divisor, so the result of Theorem \ref{thm:main}
-follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1}
-to add the necessary stacky points. On the other hand, the proof
-when $\delta = 0$ is more involved. We dedicate the remainder of
-this section to that case in the following steps: characterizing
-saturations points (Subsection ~\ref{ssec:g_0_saturation}),
-describing base cases (Subsection ~\ref{ssec:g_0_base}), and
-presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
-Finally, we apply inductive processes using Lemma ~\ref{lem:sat-3}
-and Lemma ~\ref{lem:raise-stacky-order} to prove the main theorem
-in the full genus zero case (Subsection ~\ref{ssec:g-0-main}).
+We will prove that if $(\sx , \Delta, \halfcan)$ is a log spin curve and
+$\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
+then $R(\sx , \Delta, L)$ is generated in degree at most $e := \max(
+5, e_1, \ldots, e_r)$ with relations generated in degree at most $2e
+$, so long as $\sigma$ does not lie in the finite list given in Table ~\ref{table:g-0-exceptional}.
+
+As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
+In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
+result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
+On the other hand, the proof when $\delta =
+0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
+characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
+base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
+cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove \todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).
+See if you like them.}
+%before proving the main theorem in full for all $\delta$ in
+%Subsection ~\ref{ssec:g-0-main}.
 
@@
 If $\sx$ has no stacky points, then we can assume that $L \sim
-n \cdot \infty$ with $n \in \BZ$.
-When $n=-1$, then $R_\halfcan=k$.
-When $n=0$, then $R_\halfcan = k[x]$.
-When $n>0$, inductively applying Lemma \ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1 with relations generated in degree 2.
-All three of these cases meet the conclusion of Theorem \ref{thm:g-0-main}.
+n \cdot \infty$ with $n \in \BZ$. This is the classical
+case which is done, with $\halfcan$ replaced by $K$, \todo{Peter: I don't think its helpful to say with $L$ replaced by $K$.
+It might slightly confuse the reader into thinking that replacing half canonical divisor with canonical divisor changes the problem.} by Voight and
+Zureick-Brown ~\cite[Section 4.2]{vzb:stacky}.
 
@@
 
-This paper leaves open many directions for further research.\todo{Peter: This sentence sounds weird.  It's also kind of not true; as David said, we are kind of closing the topic}
+This paper leaves open many directions for further research.
 
@@
 		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors translate to rings of fractional weight ($\frac{2}{n}$) modular 
+		divisors would translate to rings of fractional weight modular 
 		forms. As defined in Adler and Ramanan (in the passage immediately 
@@
 		^{e_3} = 0$.
-\todo{Peter: I don't know if it is so worth while giving an explicit definition and precisely defining the work already done.
-A general outline might suffice and be easier/shorter to read.}
-
-		This motivates the following question:
-
-\todo{Peter: Would this be better as a conjecture?}
+
+		Having motivated the importance of fractional weight modular forms, we pose the following question:
+
 		\begin{question}
 		\label{ques:fractional-weight}
-			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
+			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ 
 			where $K$ is the canonical divisor of $\sx$, can one bound the 
@@
 		\end{question}
-		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
-		gives an affirmative answer to this question: If $\sx$ has signature 
+		Note that that the above question is answered affirmatively in the 
+		case that $\sx$ has genus $0$ and $D$ is effective, as follows by 
+		inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature 
 		$(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
 		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
-		$2e$. 
-		It may be possible to modify the proof of Lemma
+		$2e$. Additionally, it may be possible to modify the proof of Lemma
 		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
-		weight modular forms. 
-		Suitable generalizations of the 
-		lemmas of Section ~\ref{sec:induction} might allow one to 
-		follow similar questions to this paper and provide a general 
-		answer to Question ~\ref{ques:fractional-weight}.
-
-	\item Voight and Zureick Brown define
-		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
+		weight modular forms. Given suitable generalizations of these 
+		lemmas, one may be able to approach the problem of finding 
+		generators and relations for fractional weight modular forms using 
+		techniques similar to those in this paper.
+
+	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky},
+		the notion of a generic initial ideal is defined, which 
 		encapsulates the idea of whether the relations for $R_\halfcan$ are 
-		generically chosen, in a precise sense. 
-		The proof of Theorem
-		~\ref{thm:main} is decidedly non-generic. 
-		In particular, Lemma ~\ref{lem:raise-stacky-order} 
+		generically chosen, in a precise sense. The proof of Theorem
+		~\ref{thm:main} decidedly does not yield a generic initial ideal, 
+		as generators and relations are constructed in a highly nongeneric 
+		manner. In particular, Lemma ~\ref{lem:raise-stacky-order} 
 		constructs generators with non-maximal pole orders at certain 
@@
 			does there exist a function $\sigma \mapsto d(\sigma)$ so that
-			the generic initial ideal {\rm(}with some specified ordering{\rm)}
+			the generic initial ideal {\rm(} with some specified ordering{\rm)}
 			is generated in degree at most $d(\sigma)$? Can one write down the
 			generic initial ideal explicitly?
-		\end{question}\todo{Peter: This whole question is kind of confusing.  I don't know what it is trying to say.}
+		\end{question}
 
 	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
-		proof of Theorem ~\ref{thm:main} 
-		%given in this paper 
-		gives an 
+		proof of Theorem ~\ref{thm:main} given in this paper gives an 
 		explicit procedure for computing the generators and relations of $R_
-		\halfcan$ when the genus of $\sx$ \todo{Peter: Minor note: should we say genus of $\sx$ or genus of $X$; did we actually define that a genus of a stacky curve equals that of its coarse space?} is $0$ or $1$.
-\todo{Peter: This question also seems like it might be the most important (as far as modular forms applications go.
-Maybe we should put it first?}
+		L$ when the genus of $\sx$ is $0$ or $1$.
 		\begin{question}
 		\label{ques:algorithm}
-			Is there an explicit procedure for computing the generators 
+			Can one give an algorithm for explicitly computing the generators 
 			and relations for an arbitrary genus $g \geq 2$ curve?
@@
 		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
-		algorithm for inductively determining the generators of $L$. 
-		This reduces Question \ref{ques:algorithm} to the 
+		algorithm for determining the generators of $L$. This raises the 
 		following Petri-like question:
@@
 \todo{Aaron, I tried to edit the following question, but it still seems a bit imprecise, and the question in particular is a bit of a long sentence.}
-\todo{Peter @ Aaron: I think the last sentence of the question can be removed; generic isn't relevant in this part of further questions (it was relevant in part (2)).
-Also the sentence after the question can be removed.}
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
 		the work of Reid \cite[Theorem 3.4]{reid:infinitesimal}. We use his 
-		proof that the 
+		proof of that the 
 		spin canonical ring is generated in degree at most 5 with
@@
 		bound of 5 and 10 to the log case, and then apply our inductive 
-		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  However, Reid in fact proves something slightly stronger \cite[Theorem 3.4]{reid:infinitesimal}: that in 
+		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  Reid \cite[Theorem 3.4]{reid:infinitesimal} in fact proves something slightly stronger: that in 
 		most cases his bound is actually 3 and 6 with well-characterized 
 		exceptions.
-		Generalizing this slightly stronger bound to the (non-stacky) log case case would allow us to inductively apply the lemmas from Section ~\ref{sec:induction} and improve Theorem ~\ref{thm:main} as follows:
-		\begin{conjecture}\label{ques:reduce-5,10-to-4,8}
-			When $g \geq 2,$ the bounds in Theorem \ref{thm:main} on 
-			the degrees of generation and relations can be reduced from 
-			$e = \max(5,e_1,\ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
-			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
-			apart from a finite list of exceptions?
-		\end{conjecture}
-		\todo{Peter: I don't like a finite list of exceptions.
-The list contains infinitely many non-isomorphic stacky curves.
-Finite family might also be imperfect.
-Can we say except when $g=2$ (I believe there will be infinitely many counterexamples there) or it lies in a finite list of exception?
-Do we believe that to be true?}
+		\begin{question}\label{ques:reduce-5,10-to-4,8}
+			In the case that the genus $g \geq 2,$ can we reduce the bounds in Theorem \ref{thm:main} on 
+			the degrees of generation and relations from $e = \max(5,e_1,\ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to $\max(4,e_1, \ldots, e_r)$ and $
+			\max(8, 2e_1, \ldots, 2e_r),$ apart from a finite list of exceptions?
+		\end{question}
 		\begin{rem}\label{rem:reduce-3,6}
-			It is unlikely that these bounds can be reduced further to 
-			$e''=\max(3, e_1, \ldots, e_r)$ and $2e''$, 
-			because Lemma \ref{lem:sat-2}'s construction always
+			It is unlikely that this can be reduced further for the case 
+			of stacky curves, because Lemma \ref{lem:sat-2}, which allows 
+			us to add a stacky point in genus $g > 0$ saturated at 2, 
 			requires a generator in degree 4 and potentially a relation in 
-			degree 8, when adding a stacky point with stabilizer order 3. 
-%			Perhaps in the non-stacky case, one 
-%			may be able able to generalize the result of Reid \cite[Theorem 3.4
-%			]{reid:infinitesimal} to show that log spin canonical rings can be 
-%			generated in degree at most 3 with relations in degree at most 6, 
-%			apart from a well characterized list of exceptions.
+			degree 8, even when inductively adding on stacky points of 
+			stabilizer order 3. However, perhaps in the non-stacky case, one 
+			may be able able to generalize the result of Reid \cite[Theorem 3.4
+			]{reid:infinitesimal} to show that log spin canonical rings can be 
+			generated in degree at most 3 with relations in degree at most 6, 
+			apart from a well characterized list of exceptions.
 			\end{rem}
 	\item While Theorem ~\ref{thm:main} gives a minimal set of 
-		generators \todo{Peter: I believe this is actually not true.
-If $R_{\halfcan'}$ is minimally generated by $x_1, \ldots x_m$ and $R_\halfcan$ is generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$, then $R_{\halfcan}$ is {\emph{generated}} by $x_1, \ldots, x_m, y_1, \ldots y_n$ but not necessarily minimally.
-It's possible to have something like $y_1y_3-y_2^2=x_i$.}
-		for the log spin canonical ring $R_\halfcan,$ the set of 
+		generators for the log spin canonical ring $R_\halfcan,$ the set of 
 		relations is not minimal. In many of the $g = 0$ and $g=1$ cases, 
@@
 \section{Acknowledgments}
-We are grateful to David Zureick-Brown for introducing us to the study of stacky canonical rings, providing invaluable guidance, and being \todo{Peter: using passive voice (i.e.
-``being'') makes this sound kind of generic} an
+We are grateful to David Zureick-Brown for introducing us to this
+field of study, providing incredibly helpful guidance, and being an
 excellent project mentor. We also thank Ken Ono and the Emory 
@@
 providing a great environment for mathematical learning and 
-collaboration. \todo{Peter: Does it make sense to thank the REU? Ken essentially is the REU.} We thank Jorge Sentieiro Neves for pointing out the
-bounds given by Reid's work on the maximal degrees of minimal
+collaboration. We thank Jorge Sentieiro Neves for pointing out the
+bound given by Reid's work on the maximal degrees of minimal
 generators and relations of spin canonical rings in high genera.
-Finally, we gratefully acknowledge the financial support given by NSF Grant Award Number 1250467 via the
-Emory University Number Theory REU. 
-We deeply appreciate all of the
+Finally, we gratefully acknowledge that our research was
+financially supported by NSF Grant Award Number 1250467 via the
+Emory University Number Theory REU. We deeply appreciate all of the
 support that has made our work possible.

### 2015-07-02 stacky_write_up/spin_cring.tex
global space inserts, L -> halfcan, abstract edit

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 \[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
+	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
 	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
@@
 %and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
-%\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{
+%\ldots, P_r$ with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{
 %\geq 2}$ if 
 %\[
-	%\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
+	%\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
 	%P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
@@
 {dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1,\ldots, e_r)$
-and relation degrees by $3 \cdot \max(5, e_1,\ldots, e_r)$ when $\halfcan$ is effective
+rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$
+and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
 \cite[Corollary 10.4.6]{vzb:stacky}.
@@
 degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $6 \cdot \max(3, e_1,\ldots, e_r)$.
+generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.
 
@@
 In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $3 \cdot \max(3, e_1, \ldots, e_r)$ and relation
-bound of $6 \cdot \max(3, e_1,\ldots, e_r)$ can be reduced to $\max(3,e_1, \ldots, e_r)$ and $2 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
+bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $\max(3,e_1, \ldots, e_r)$ and $2 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
 ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 9.3.1]{vzb:stacky} for a more precise statement of these bounds.
@@
 Let $\sx$ be a stacky curve over $k$ with coarse space $X$ and stacky points $P_1, \ldots,
-P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
+P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
 Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
@@
 The \textbf{block term order} is defined as follows. Let $k[y_{1}, \ldots, y_{m}]$ and $k[x_{1}, \ldots,
-x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i,\: \deg x_i = d_i.$ Further assume we are given existing term
+x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = d_i.$ Further assume we are given existing term
 orders $\prec_y$ and $\prec_x$. Let $\alpha :=
@@
 
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx',L',J)$
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan',J)$
 to be {\bf admissible} if $R'$ admits a presentation
@@
 \label{eg:base-1-0}
-Let $(\sx',0,L')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
+In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 \label{eg:base-0-377}
-Let $(\sx,0,\halfcan')$ be a log spin curve with signature $\sigma =
+Let $(\sx,0, \halfcan')$ be a log spin curve with signature $\sigma =
 (0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
@@
 distinct points. In this example, we will exhibit a minimal
-presentation for $R' = R(\sx,0,\halfcan')$ and show the triple
+presentation for $R' = R(\sx,0, \halfcan')$ and show the triple
 $(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
@@
 \label{eg:base-1-33}
-Let $(\sx',0 ,\halfcan')$ be a log spin curve of genus $1$ so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
 $$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx', \halfcan',\{1,2\})$ is admissible.
+and that $(\sx', \halfcan', \{1,2\})$ is admissible.
 
@@
 
-Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
+Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
 $R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
@@
 
-We next check $(\sx', \halfcan',\{1,2\})$ is admissible.
+We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
 We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
@@
 To complete the proof, it suffices to show the reverse inclusion holds.
-By (2), any polynomial $G\in k[x_1,\ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
+By (2), any polynomial $G\in k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
 Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
@@
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha,\beta \in \BN$ such that
+for some $\alpha, \beta \in \BN$ such that
 \begin{align}
 \label{eqn:deg1-sat-ind}
-	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X,\lfloor d\halfcan'
+	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X, \lfloor d\halfcan'
 	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
@@
 											 + \langle U_i: 1 \le i \le n-1 \rangle
-											 + \langle V \rangle,\\
+											 + \langle V \rangle, \\
 	\end{align*}
@@
 \alpha}{\beta}$. 
-%Note that the elements $t_1,\ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
+%Note that the elements $t_1, \ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
 Hence, by a dimension count, these sections form a $k$-basis for
@@
 \[
-	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
+	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X, \lfloor d\halfcan'
 		\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor,
@@
 \noindent
-Then, there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
+Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S$, 
 and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
@@
 
-Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Since the ideal in $k[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 		S=	&\{ y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon,\epsilon') \in \{(0,0),(0,1),(1,0)\} \} \\
+		\geq 0,(\epsilon, \epsilon') \in \{(0,0),(0,1),(1,0)\} \} \\
 		\cup \;&\{y_3^ay_4, y_3^by_5 \mid a \geq 0, b \geq 0 \}
@@
 %Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)= 1$. 
-%Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
+%Choose any $y_1\in H^0(X, \lfloor L\rfloor)$; we know by saturation arguments that $-
 %\ord_P(y_1)= 1$. Furthermore, since $\delta> 0$, we use Riemann-Roch to deduce that for 
-%all $d> 1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
+%all $d> 1$ $h^0(X, \lfloor dL\rfloor)=h^0(dL') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
 %$-vector space over $(R_{\halfcan'})_d$. In particular, this means we can generically 
-%choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$. By 
+%choose an element $y_2\in H^0(X, \lfloor 2L\rfloor)$ linearly independent from $y_1^2$. By 
 %dimension counting, we see that 
@@
 %\begin{cor}\label{cor:genus_0_positive_delta}
-%Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1, \ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)> 0$.
+%Let $\halfcan$ be a stacky log spin canonical divisor of $(X, \Delta)$ with signature $(g;e_1, \ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)> 0$.
 Then $\halfcan$ is effective so we can inductively apply Lemma ~\ref{lem:deg1_sat_ind}.
@@
 %coefficient lying in $\BN[\frac{1}{e_i}]$ (ranging over $e_i$
-%s appearing in the characteristic of $(\sx,\Delta)$).
+%s appearing in the characteristic of $(\sx, \Delta)$).
  %
@@
 %\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
-%Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
+%Let $(X, \Delta, \halfcan)\to (X, \Delta', \halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
 %Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
@@
 \label{lem:admissible_subset}
-If $(\sx',\Delta,L')$ is a log spin curve, $(\sx',L', J)$ is admissible and $W \subseteq J$ is any subset,
+If $(\sx', \Delta, \halfcan')$ is a log spin curve, $(\sx', \halfcan', J)$ is admissible and $W \subseteq J$ is any subset,
 then $(\sx', L', W)$ is also admissible.
@@
 \halfcan)$ is a log spin curve with signature $\sigma = (g; e_1,
-\ldots, e_r,\delta) = (g;3,\ldots, 3, \delta)$, and our base cases
+\ldots, e_r; \delta) = (g; 3, \ldots, 3; \delta)$, and our base cases
 include signatures $\sigma$ characterized by one of the following:
@@
 \begin{enumerate}
-	\item $(\sx',\halfcan', J)$ is admissible with generators $x_1,
+	\item $(\sx', \halfcan', J)$ is admissible with generators $x_1,
 		\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J$, as 
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1,\ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
+	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
 $k[y_{i, e_i}]_{i\in J} \otimes k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
@@
 {\bf Part (b):}
-Define $R_0 = R'$ and for $i \in \{1,\ldots, r\},$ inductively define 
+Define $R_0 = R'$ and for $i \in \{1, \ldots, r\},$ inductively define 
 $$R_i = \begin{cases}
@@
 {\bf Part (d):}
-To check (d), we show \ref{custom:Ad-i},\ref{custom:Ad-ii}, and \ref{custom:Ad-iii} are satisfied. We know \ref{custom:Ad-i} holds by part (b), taking the $y_{
+To check (d), we show \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} are satisfied. We know \ref{custom:Ad-i} holds by part (b), taking the $y_{
 i, e_i}$ as the generators in degree $e_i$. Next, \ref{custom:Ad-ii} is
@@
 \label{cor:raise-stacky-order}
-Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1
-',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of
-Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1,\ldots,r\}$ and
+Suppose $(\sx', \halfcan',J')$ is admissible with signature $\sigma' = (e_1
+', \ldots,e_r')$ or $\sigma$ satisfies one of the conditions of
+Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1, \ldots,r\}$ and
 $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
-so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma
+so that $(\sx', \Delta, L)$ satisfies the conditions of Lemma
 ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then,
@@
 the same coarse space $X = X'$ with the same set of stacky points,
-and $  \sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1
+and $  \sx$ has signature $(g; e_1, \ldots, e_r; \delta)$ with $e_1
 \leq e_2 \leq \cdots e_r$ so that
@@
 \noindent
-then Theorem ~\ref{thm:main} holds for $(\sx,\Delta,L)$.
+then Theorem ~\ref{thm:main} holds for $(\sx, \Delta, \halfcan)$.
 \end{cor}
@@
 \begin{proof}
-For $t \leq i \leq r$, let $(\sx_i,\Delta, L_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx',\Delta,L),$ and having signature $(g; e_1, \ldots.
-e_{i-1}, e_i, e_i, \ldots, e_i; \delta).$ Let
-$J_i = \{i,\ldots, r\}.$ Note that $(\sx_0,L_0,J_0) = (\sx',L',J')$ and $(\sx_r ,L_r ,J_r) = (\sx, L, \{r\})$.
+For $t \leq i \leq r$, let $(\sx_i, \Delta, \halfcan_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx', \Delta, \halfcan),$ and having signature $(g; e_1, \ldots.
+e_{i - 1}, e_i, e_i, \ldots, e_i; \delta).$ Let
+$J_i = \{i, \ldots, r\}.$ Note that $(\sx_0, \halfcan_0,J_0) = (\sx', \halfcan',J')$ and $(\sx_r , \halfcan_r ,J_r) = (\sx, L, \{r\})$.
 
@@
 %it suffices to produce one more independent function in the image of the multiplication map.
-%There are now two cases, depending on whether $H^0(X,L) = 0$.
-%
-%First, we deal with the case that $H^0(X,L) \neq 0$. 
-%Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X,L) = 1$.
+%There are now two cases, depending on whether $H^0(X, \halfcan) = 0$.
+%
+%First, we deal with the case that $H^0(X, \halfcan) \neq 0$. 
+%Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X, \halfcan) = 1$.
 Hence, we know $L$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
@@
 %
-%Second, suppose $H^0(X,L) = 0$.
+%Second, suppose $H^0(X, \halfcan) = 0$.
 %Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
 %Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-%we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X,L + 2P_1)$ 
-%with $\di g|_{2P_1 + L} = -L,$ since $H^0(X,L) = 0.$ Therefore, there must 
-%exist a function $h \in H^0(X,L+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
+%we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X, \halfcan + 2P_1)$ 
+%with $\di g|_{2P_1 + L} = -L,$ since $H^0(X, \halfcan) = 0.$ Therefore, there must 
+%exist a function $h \in H^0(X, \halfcan+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
 %Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
@@
 \begin{proof}
-% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1),\phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
+% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1), \phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
 By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan,\deg a_i}.$
+We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
 
@@
 $$\deg a_i =\deg f - \deg x_i -2 \geq 4.$$
-In particular, there exist $\alpha,\beta \in R_L$ so that
+In particular, there exist $\alpha, \beta \in R_L$ so that
 $$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
 Choosing $g_i,h_i\in k[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
-$$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan,\deg a_i},$$ as claimed.
+$$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan, \deg a_i},$$ as claimed.
 
@@
 ~\ref{lem:reducing-degree}, this is the same as checking $s_1 g + s_2 h \in
-I_{\halfcan, d}'$ where $\phi(s_ 1),\phi(s_2) \in H^0(X, 2L)$ are two sections
+I_{\halfcan, d}'$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
 so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
@@
 
-We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g\ge 2$ and signature $(g;3,\ldots, 3;\delta)$. Therefore, by Corollary 
+We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g\ge 2$ and signature $(g;3, \ldots, 3;\delta)$. Therefore, by Corollary 
 ~\ref{cor:raise-stacky-order}, this theorem 
@@
 In this case, let $L_X \in \di X$ satisfy $2L_X \sim K_X + \Delta$.
-We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx,L) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor.
+We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor.
 Thus, without loss of generality, we may assume $L$ is an effective divisor.
@@
 First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $\todo{Peter: Is $\lfloor L|_p\rfloor$ standard notation?
+In particular, we may take $u \in h^0(\sx, \halfcan)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $\todo{Peter: Is $\lfloor L|_p\rfloor$ standard notation?
 It looks weird}, as $P$ is not a basepoint of $L'$.
@@
 Second, we deal with the case that $\sx$ has at least two stacky points.
-If $(\sx',\Delta,L')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in Example ~\ref{eg:base-1-33}, the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}\todo{Peter: Is it better for us to say the signature satisfies the hypothesis rather than the triple?}.
-Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx',\Delta',L')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
+If $(\sx', \delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in Example ~\ref{eg:base-1-33}, the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}\todo{Peter: Is it better for us to say the signature satisfies the hypothesis rather than the triple?}.
+Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
 \todo{Peter: Why is it immediate that $n$ threes satisfies the condition for admissibility?
@@
 		gives an affirmative answer to this question: If $\sx$ has signature 
-		$(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
+		$(g; e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
 		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
@@
 		\label{ques:generic-initial}
-			If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$,
+			If $(\sx, \Delta, \halfcan)$ is a log spin curve with signature $\sigma$,
 			does there exist a function $\sigma \mapsto d(\sigma)$ so that
@@
 			the degrees of generation and relations can be reduced from 
-			$e = \max(5,e_1,\ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
+			$e = \max(5,e_1, \ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
 			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
@@
 \section{Acknowledgments}
-We are grateful to David Zureick-Brown for introducing us to the study of stacky canonical rings, providing invaluable guidance, and being \todo{Peter: using passive voice (i.e.
-``being'') makes this sound kind of generic} an
-excellent project mentor. We also thank Ken Ono and the Emory 
-University Number Theory REU for arranging our project and 
+We are grateful to David Zureick-Brown for introducing us to the
+study of stacky canonical rings, for providing invaluable guidance,
+and for his excellent mentorship. We also thank Ken Ono and the
+Emory University Number Theory REU for arranging our project and
 providing a great environment for mathematical learning and
-collaboration. \todo{Peter: Does it make sense to thank the REU? Ken essentially is the REU.} We thank Jorge Sentieiro Neves for pointing out the
-bounds given by Reid's work on the maximal degrees of minimal
+collaboration. We thank Jorge Sentieiro Neves for pointing out the
+bounds given by Miles Reid's work on the maximal degrees of minimal
 generators and relations of spin canonical rings in high genera.
-Finally, we gratefully acknowledge the financial support given by NSF Grant Award Number 1250467 via the
-Emory University Number Theory REU. 
-We deeply appreciate all of the
-support that has made our work possible.
+Finally, we gratefully acknowledge the financial support given by
+NSF Grant Award Number 1250467 via the Emory University Number
+Theory REU. We deeply appreciate all of the support that has made
+our work possible.
 

### 2015-07-02 stacky_write_up/spin_cring.tex

--- 2015-07-02 stacky_write_up/spin_cring.tex
@@
 
+\todo{Say something like a monomial is in $S$ if and only if it satisfies some condition with $c_h,$ and that we use this to check the three (*) conditions.}
 We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.
 Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies \ref{custom:sat-1-**}.

### 2015-07-02 stacky_write_up/spin_cring.tex
editing abstract

@@
 \begin{abstract}
- 	We tightly bound the degrees of minimal
-	generators and relations of spin canonical rings of a stacky
-	curve equipped with an arbitrary log divisor.  Rings of modular forms arising from finite-area
-	quotients of the upper-half plane by Fuchsian groups may be
-	viewed as log spin canonical rings by the classical
-	results of Kodaira--Spencer. As a consequence, 
-	we obtain a tight bound on the degrees of minimal generators and relations  		
+ 	Consider modular forms arising from finite-area
+	quotients of the upper-half plane by Fuchsian groups.  
+	By the classical results of Kodaira--Spencer, 
+	this space of modular forms may be
+	viewed as log spin canonical ring of a stacky curve.
+	In this paper, we tightly bound the degrees of minimal
+	generators and relations of log spin canonical rings and,
+	as a consequence, 
+	obtain a tight bound on the degrees of minimal generators and relations  		
 	for rings of modular forms of arbitrary integral weight.
@@
 Section ~\ref{sec:background}. Then, we develop various inductive
-tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g-high},
-~\ref{sec:g-1}, and ~\ref{sec:g-0}, we prove Theorem
+tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
+~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
 ~\ref{thm:main} in the genus $ g \geq 2$, genus
@@
 \begin{enumerate}
-	\item[\customlabel{custom:Ad-i}{(Ad-i)}] First, 
+	\item[\customlabel{Ad-i}{(Ad-i)}] First, 
 	\begin{align*}
@@
 	\end{align*}
-	\item[\customlabel{custom:Ad-ii}{(Ad-ii)}] Second, every generator $z 
-		\in \{x_1, \ldots, x_m\} \cup \{y_{j, e_i'}: j\in J - \{i\} \}$ 
-		satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-iii}{(Ad-iii)}] Third, we have
+		\item[\customlabel{Ad-ii}{(Ad-ii)}] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
+		\begin{align*}
+			\frac{-\ord_{Q_i}
+^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[\customlabel{Ad-iii}{(Ad-iii)}] Third, we have
 		\begin{align*}
@@
 $y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
+\ref{Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{Ad-ii} We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
@@
 \halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
+\frac{9}{3} \rfloor - 9 = 2$, so \ref{Ad-iii} is satisfied and
 $(\sigma, \sx', J)$ is admissible.
@@
 We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{custom:Ad-i} holds.
-We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
+Hence, \ref{Ad-i} holds.
+We next check \ref{Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
 Here, by construction
@@
 \end{cases}.$$
-Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{Ad-ii} holds.
+Finally, to check \ref{Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
 \end{example}
-
-\begin{rem}
-\label{rem:base-0-377}
-Example ~\ref{eg:base-0-377} is one of the inductive base cases
-used in the genus zero case (Section ~\ref{sec:g-0}) as
-listed in Table ~\ref{table:g-0-base-cases}.
-\end{rem}
 
@@
 \item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T \succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
+\item $T\succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
 \item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
@@
 	\begin{enumerate}
-		\item[\customlabel{custom:sat-1-*}{(*)}] $\sum_{j = 1}^i a_j c_j \ge c_{i+1}$, \\
-		\item[\customlabel{custom:sat-1-**}{(**)}] there does not exist $(b_1, \ldots b_i) \ne (a_1,
+		\item[(*)] $\sum_{j=1}^i a_j c_j \ge c_{i+1}$, \\
+		\item[(**)] there does not exist $(b_1, \ldots b_i) \ne (a_1,
 			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
 			c_j \ge	c_{i + 1}$, \\
-		\item[\customlabel{custom:sat-1-***}{(***)}] there does not
-			exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
+		\item[(***)] there does not exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
 	\end{enumerate}
@@
 
-\todo{Say something like a monomial is in $S$ if and only if it satisfies some condition with $c_h,$ and that we use this to check the three (*) conditions.}
-We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.
-Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies \ref{custom:sat-1-**}.
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition \ref{custom:sat-1-***} holds.
+We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).
+Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).
+Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).
+Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition (***) holds.
 Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
@@
 \label{ssec:raise-orders}
-In this subsection, we present Lemma ~\ref{lem:raise-stacky-order},
-whose proof is almost identical to one of Voight and Zureick-Brown
-\cite[Theorem 8.5.7]{vzb:stacky}. Lemma
-~\ref{lem:raise-stacky-order} implies that if the main result,
-Theorem ~\ref{thm:main}, holds for a curve with signature $(g; e_1',
-\ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' =
-\cdots = e_r'$ satisfying certain admissibility (cf. Definition
-~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for
-a curve with signature $(g; e _1', \ldots, e_k', e_{k + 1}' + 2,
-\ldots, e_r' + 2; \delta)$. 
+In this subsection, we present Lemma
+~\ref{lem:raise-stacky-order}, whose proof is almost identical to one of Voight and Zureick-Brown \cite[Theorem 8.5.7]{vzb:stacky}.
+Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem
+~\ref{thm:main}, holds for a curve with signature
+$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' = \cdots = e_r'$ satisfying certain admissibility (cf.
+Definition ~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for a curve with
+signature $(g; e_1', \ldots, e_k', e_{k+1}'+2,\ldots, e_r'+2; \delta)$. 
 %In order to state Lemma
@@
 %\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{custom:Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
+%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
 %\end{rem}
@@
 %\begin{proof}
-%To show \ref{custom:Ad-i} and \ref{custom:Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
-Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{custom:Ad-i}.
-Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{custom:Ad-ii} satisfied so $\frac{-\ord_{Q_l}
-%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{custom:Ad-ii} follows in genus 0?}
+%To show \ref{Ad-i} and \ref{Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
+Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{Ad-i}.
+Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{Ad-ii} satisfied so $\frac{-\ord_{Q_l}
+%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{Ad-ii} follows in genus 0?}
 %
@@
 %\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{custom:Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 %\end{itemize}
@@
 
-The following Lemma will slightly strengthen condition \ref{custom:Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+The following Lemma will slightly strengthen condition \ref{Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 \label{lem:admissible_inequality}
-For any $z$ as in condition \ref{custom:Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{custom:Ad-ii} implies the
+For any $z$ as in condition \ref{Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{Ad-ii} implies the
 tighter inequality that
@@
 \begin{proof}
-We know by \ref{custom:Ad-ii} that
+We know by \ref{Ad-ii} that
 
@@
 \begin{proof}
-Each of the conditions \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} hold for $W$
+Each of the conditions \ref{Ad-i}, \ref{Ad-ii}, and \ref{Ad-iii} hold for $W$
 if they hold for $J$.
@@
 \label{rem:three-cases}
-For our inductive arguments in Theorems ~\ref{thm:g-high-main},
-~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a
-single stacky point with stabilizer order $3$. Say $(\sx, \Delta,
-\halfcan)$ is a log spin curve with signature $\sigma = (g; e_1,
-\ldots, e_r,\delta) = (g;3,\ldots, 3, \delta)$, and our base cases
-include signatures $\sigma$ characterized by one of the following:
-cases, which we will soon refer to in Lemma
-~\ref{lem:raise-stacky-order}:
-
+For our inductive arguments in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
+stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
+curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
+\delta)$, and our base cases include signatures $\sigma$ characterized by one of the following: cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
 \begin{enumerate}
-	\item[\customlabel{custom:three-cases-1}{(1)}] $g = 0, e_1 =
-		\cdots = e_r = 3, \delta = 0$, and $r \geq 5$
-	\item[\customlabel{custom:three-cases-2}{(2)}] $g = 1, e_1 =
-		\cdots = e_r = 3, \delta = 0$, and $ r \geq 2$
-	\item[\customlabel{custom:three-cases-3}{(3)}] $g \geq 2, e_1 =
-		\cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
+	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
+	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
+	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item $(\sx',\halfcan', J)$ is admissible with generators $x_1,
-		\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J$, as 
-		in Definition ~\ref{defn:admissible} or
-	\item $\sigma$ is one of the signatures described in Cases
-		\ref{custom:three-cases-1}, \ref{custom:three-cases-2} and
-		\ref{custom:three-cases-3} of Remark ~\ref{rem:three-cases} and
-		$y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of
-		$\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$
-		for $1 \leq  i \leq r$.
+	\item  $(\sx',\halfcan', J)$ is admissible with generators $x_1,\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J,$ as in Definition ~\ref{defn:admissible} or
+	\item $\sigma$ is one of the signatures described in cases (1), (2) and (3) of Remark ~\ref{rem:three-cases} and $y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of $\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ for $1 \leq  i \leq r$.
 \end{enumerate}
@@
 	\item[(b)] 
-
 	%The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
@@
 \noindent
-The assumption \ref{custom:Ad-iii} implies
+The assumption \ref{Ad-iii} implies
 \begin{align*}
@@
 
-By part (a), condition \ref{custom:Ad-ii}, and Lemma
+By part (a), condition \ref{Ad-ii}, and Lemma
 ~\ref{lem:admissible_inequality} we have
@@
 {\bf Part (d):}
-To check (d), we show \ref{custom:Ad-i},\ref{custom:Ad-ii}, and \ref{custom:Ad-iii} are satisfied. We know \ref{custom:Ad-i} holds by part (b), taking the $y_{
-i, e_i}$ as the generators in degree $e_i$. Next, \ref{custom:Ad-ii} is
+To check (d), we show \ref{Ad-i},\ref{Ad-ii}, and \ref{Ad-iii} are satisfied. We know \ref{Ad-i} holds by part (b), taking the $y_{
+i, e_i}$ as the generators in degree $e_i$. Next, \ref{Ad-ii} is
 strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
-Finally, if \ref{custom:Ad-iii} holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that \ref{custom:Ad-iii} holds for $d > 0$
+Finally, if \ref{Ad-iii} holds for $e$ then it holds for $e + 2$ by
+definition. This is where we use that \ref{Ad-iii} holds for $d > 0$
 and not just for $d = 0$.
@@
 \label{cor:raise-stacky-order}
-Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1
-',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of
-Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1,\ldots,r\}$ and
-$e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
-so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma
-~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then,
-for any spin curve $(\sx, \Delta, L)$ so that $\sx$ and $\sx'$ have
-the same coarse space $X = X'$ with the same set of stacky points,
-and $  \sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1
-\leq e_2 \leq \cdots e_r$ so that
+Suppose $(\sx',L',J')$ is admissible with signature $\sigma' = (e_1',\ldots,e_r')$ or $\sigma$ satisfies one of the conditions of Remark ~\ref{rem:three-cases}.
+Let $J' = \{t,t+1,\ldots,r\}$ and $e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
+so that $(\sx',\Delta, L)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}.
+Then, for any spin curve $(\sx,\Delta,L)$ so that $\sx$ and $\sx'$ have the same coarse space $X = X'$ with the same set of stacky points, and $\sx$ has signature $(g;e_1,\ldots, e_r;\delta)$ with $e_1 \leq e_2 \leq \cdots e_r$ so that
 \begin{align*}
@@
 \end{cor}
-
 \begin{proof}
@@
 
-Let $(*_i)$ denote the condition that $(\sx_i, \Delta, L_i)$
-satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and
-Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is
-admissible. Since $(*_0)$ holds by assumption, it suffices to show
-that if $(*_i)$ holds then so does $(*_{i + 1})$. Indeed, $(\sx_i,
-\halfcan_i, J_{i + 1})$ is admissible by an application of Lemma
-~\ref{lem:admissible_subset} and the fact that $J_{i + 1} \subseteq J
-_i$. Then, applying Lemma ~\ref{lem:raise-stacky-order} with the
-fixed set $J_{i + 1}$ repeatedly ($\frac{e_{i + 1} - e_i}{2}$ many
-times) yields $(*_{i + 1})$.
+Let $(*_i)$ denote the condition that $(\sx_i,\Delta, L_i)$ satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is admissible.
+
+Since $(*_0)$ holds by assumption, by induction on $i$, it suffices to show that if $(*_i)$ holds then so does $(*_{i+1}).$ 
+Indeed, by applying Lemma ~\ref{lem:admissible_subset}, it follows $(\sx_i, \halfcan_i, J_{i+1})$ is admissible, as $J_{i+1} \subseteq J_i$.
+Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e_{i+1}-e_i}{2},$ times, for the fixed set $J_{i+1},$ we see $(*_{i+1})$ holds.
 \end{proof}
@@
 \section{High Genus}
-\label{sec:g-high}
+\label{sec:g_high}
 We now consider the case when the genus is at least 2.
 In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations.
+In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g_1} and ~\ref{sec:g_0} where we not only obtain bounds, but also obtain inductive presentations.
 The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
@@
 \label{cor:g-2-presentation-bound}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta)$
 with $g \geq 2$. Then $X$ has minimal generators in degree at most
@@
 \section{Genus One}
-\label{sec:g-1}
+\label{sec:g_1}
 
@@
 \ssec{Genus One Base Cases}
-\label{ssec:g-1_base}
+\label{ssec:g_1_base}
 In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.
@@
 The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
-Although $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ are used as base cases for the induction, they are also exceptional cases; see Table ~\ref{table:g-1-exceptional}.
+Note that in addition to $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ being base cases, they are also exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}.\todo{Peter: I don't understand this last sentence?
+How are they base cases?}
 
@@
 First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $,
-as $P$ is not a basepoint of $L'$.
+In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $\todo{Peter: Is $\lfloor L|_p\rfloor$ standard notation?
+It looks weird}, as $P$ is not a basepoint of $L'$.
 Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $L= L'+P$.
@@
 \section{Genus Zero}
-\label{sec:g-0}
+\label{sec:g_0}
 We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
@@
 this section to that case in the following steps: characterizing
-saturations points (Subsection ~\ref{ssec:g-0_saturation}),
-describing base cases (Subsection ~\ref{ssec:g-0_base}), and
+saturations points (Subsection ~\ref{ssec:g_0_saturation}),
+describing base cases (Subsection ~\ref{ssec:g_0_base}), and
 presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
@@
 \ssec{Saturation}
-\label{ssec:g-0_saturation}
+\label{ssec:g_0_saturation}
 First, we present the saturations, as defined in Definition
@@
 \ssec{Base Cases}
-\label{ssec:g-0_base}
+\label{ssec:g_0_base}
 In order to apply Lemma ~\ref{lem:sat-3} and Lemma
@@
 P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
-Case ~\ref{custom:three-cases-1} of Remark ~\ref{rem:three-cases}):
+Case (1) of Remark ~\ref{rem:three-cases}):
 
@@
 We can also always find a presentation for these cases such that
-they satisfy \ref{custom:Ad-i} and \ref{custom:Ad-ii} and that $\initial(I')$ is
+they satisfy \ref{Ad-i} and \ref{Ad-ii} and that $\initial(I')$ is
 generated by products of two monomials. Again, the procedure to
@@
 
-Furthermore, each case always satisfies \ref{custom:Ad-iii} as demonstrated below.
+Furthermore, each case always satisfies \ref{Ad-iii} as demonstrated below.
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
@@
 
-	\caption{Genus 0 Non-Effective Base Cases \ref{custom:Ad-iii}}
+	\caption{Genus 0 Non-Effective Base Cases \ref{Ad-iii}}
 	\label{table:g-0-base-cases-admissibility}
@@
 \label{ssec:g-0-main}
-Now we can combine the base cases from Subsection \ref{ssec:g-0_base} with the inductive lemmas of Section \ref{sec:induction}.
+Now we can combine the base cases from Subsection \ref{ssec:g_0_base} with the inductive lemmas of Section \ref{sec:induction}.
 

### 2015-07-02 stacky_write_up/spin_cring.tex

@@
 \begin{abstract}
- 	Consider modular forms arising from finite-area
-	quotients of the upper-half plane by Fuchsian groups.  
-	By the classical results of Kodaira--Spencer, 
-	this space of modular forms may be
-	viewed as log spin canonical ring of a stacky curve.
-	In this paper, we tightly bound the degrees of minimal
-	generators and relations of log spin canonical rings and,
-	as a consequence, 
-	obtain a tight bound on the degrees of minimal generators and relations  		
+ 	We tightly bound the degrees of minimal
+	generators and relations of spin canonical rings of a stacky
+	curve equipped with an arbitrary log divisor.  Rings of modular forms arising from finite-area
+	quotients of the upper-half plane by Fuchsian groups may be
+	viewed as log spin canonical rings by the classical
+	results of Kodaira--Spencer. As a consequence, 
+	we obtain a tight bound on the degrees of minimal generators and relations  		
 	for rings of modular forms of arbitrary integral weight.
@@
 
-First, if $P$ is not a basepoint of $L',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-In particular, we may take $u \in h^0(\sx, \halfcan)$ with $u \neq 0$ and $\ord_P(u) = \lfloor L|_P \rfloor $\todo{Peter: Is $\lfloor L|_p\rfloor$ standard notation?
-It looks weird}, as $P$ is not a basepoint of $L'$.
-Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg L' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $L= L'+P$.
+First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
+In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
+as $P$ is not a basepoint of $L'$.
+Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.
 \todo{Peter: I don't find this paragraph (after the first sentence) very useful.

### 2015-07-02 stacky_write_up/spin_cring.tex
noindent
backspace parens
responded to peters comments

@@
 To show (c), we wish to show that $y_{i, e_i}z \in R'$ for all generators $z$ of $R'$
-with $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$. Note that $f \in R$ further satisfies $f \in R'$ if and
+with $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$. By definition of $H^0(\sx,\halfcan')$, note that $f \in R$ further satisfies $f \in R'$ if and
 only if for all $j \in J$ we have
@@
 \end{align}
-
-\todo{Peter: I understand why this should be true, although its not clear to me that there it easily follows.
-Maybe we should explain it a little as to not confuse the reader.
-Aaron: Can we ask David, this was clear to me in his paper, and he also didn't include it.
-Say by the definition}
 
@@
 We first now show the theorem holds for $L_X$ by induction.
-Since $L$ is effective, we may induct on the degree of the divisor.
-The base case is easy: the theorem holds for $L' = 0$ by Example ~\ref{eg:base-1-0}.
-Assume it holds for $L' \in \di X$, with $L'$ effective.
-We will show it holds for $L' + P,$ verifying the inductive step.
-There are two cases, depending on whether $P$ is a basepoint of $L'$.
+Since $L_X$ is effective, we may induct on the degree of the divisor.
+The base case is easy: the theorem holds for $L_X' = 0$ by Example ~\ref{eg:base-1-0}.
+Assume it holds for $L_X' \in \di X$, with $L_X'$ effective.
+We will show it holds for $L_X' + P,$ verifying the inductive step.
+There are two cases, depending on whether $P$ is a basepoint of $L_X'$.
 
 First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
+\iffalse
 In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
-as $P$ is not a basepoint of $L'$.
-Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.
-\todo{Peter: I don't find this paragraph (after the first sentence) very useful.
+as $P$ is not a basepoint of $L_X'$.
+Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.
 1: I'm not sure if we even need to go through the check that it satisfies the conditions for lemma 4.5.
@@
 Either we should reword it or remove it (feel free to disagree, of course)}
-
-Otherwise, $P$ is a basepoint of $L'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L'+P) \geq 2$ as $\deg L' + P \geq 1$\todo{Peter: I don't follow why we have a $+P$ here.
-lemma 4.8 requires that $L'$ satisfy $\deg(3L')\ge 2$,not $\deg(3L)\ge 2$.
-This isn't a problem though since $\Delta> 0$} Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L = L'+P$.
-The previous argument shows the theorem holds for $L_X$.
+\fi
+Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.
+
+Otherwise, $P$ is a basepoint of $L_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L_X') \geq 2$ as $\deg L_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L_X = L_X'+P$.
+By induction, the theorem holds for $L_X$.
 
@@
 It suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
-As above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}; on the other hand, if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
+As above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}.
+On the other hand, if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
 
@@
 Second, we deal with the case that $\sx$ has at least two stacky points. 
-If $(\sx', \delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in Example ~\ref{eg:base-1-33}, the signature $\sigma = (1;3, 3; \delta)$ satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}\todo{Peter: Is it better for us to say the signature satisfies the hypothesis rather than the triple?}.
-Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
+If $(\sx', \delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
+Example ~\ref{eg:base-1-33}, the triple $(\sx', 0, P-Q + \frac{1}{3}P_1+\frac{1}{3}P_2)$
+satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
+Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
+Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds 
+for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
 \todo{Peter: Why is it immediate that $n$ threes satisfies the condition for admissibility?
 We got rid of that proof from earlier.
-In fact, didn't we find it to be false?}
+In fact, didn't we find it to be false?
+Aaron: I don't think so, see Remark ~\ref{rem:three-cases}.}
 
@@
 
-This case is analogous to 2a. \todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument?}
+This case is analogous to 2a: If there is only one stacky point, we start at $L = \frac{3}{7}P_1,$ and inductively increment the stabilizer order.
+Note that by Table ~\ref{table:g-1-base}, $L = \frac{3}{7}P_1,$ will have a relation in degree $15.$ However, once $e_1 \geq 9$, we have $2 \cdot e_1 > 15$, so the theorem holds for such stacky curves.
+Once the divisor as at least two stacky points, the argument proceeds as in Case 2a.
+
+\todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument? Ok, I did it imprecisely. Is this better?}
 \end{proof}
@@
 
-This paper leaves open many directions for further research.\todo{Peter: This sentence sounds weird.  It's also kind of not true; as David said, we are kind of closing the topic}
+In this section, we present several directions for further research.
 
 \begin{enumerate}
-	\item One direction for further research is to 
-		extend the results of this paper to divisors $D \in \di \sx$ on a 
-		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors translate to rings of fractional weight ($\frac{2}{n}$) modular 
-		forms. As defined in Adler and Ramanan (in the passage immediately 
-		following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form 
-		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
-		line bundle $\eta$ so that there exists a line bundle $\gamma$ with 
-		$\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^
-		1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an 
-		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
-		Fractional modular forms also make an appearance in Milnor \cite[$
-		\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
-		shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e
-		_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of 
-		fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3
-		^{e_3} = 0$.
-\todo{Peter: I don't know if it is so worth while giving an explicit definition and precisely defining the work already done.
-A general outline might suffice and be easier/shorter to read.}
-
-		This motivates the following question:
-
-\todo{Peter: Would this be better as a conjecture?}
-		\begin{question}
-		\label{ques:fractional-weight}
-			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
-			where $K$ is the canonical divisor of $\sx$, can one bound the 
-			degrees of generators and relations of $R_D$?
-		\end{question}
-		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
-		gives an affirmative answer to this question: If $\sx$ has signature 
-		$(g; e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
-		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
-		$2e$. 
-		It may be possible to modify the proof of Lemma
-		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
-		weight modular forms. 
-		Suitable generalizations of the 
-		lemmas of Section ~\ref{sec:induction} might allow one to 
-		follow similar questions to this paper and provide a general 
-		answer to Question ~\ref{ques:fractional-weight}.
-
-	\item Voight and Zureick Brown define
-		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
-		encapsulates the idea of whether the relations for $R_\halfcan$ are 
-		generically chosen, in a precise sense. 
-		The proof of Theorem
-		~\ref{thm:main} is decidedly non-generic. 
-		In particular, Lemma ~\ref{lem:raise-stacky-order} 
-		constructs generators with non-maximal pole orders at certain 
-		points, making the relations non-generic. 
-		\begin{question}
-		\label{ques:generic-initial}
-			If $(\sx, \Delta, \halfcan)$ is a log spin curve with signature $\sigma$,
-			does there exist a function $\sigma \mapsto d(\sigma)$ so that
-			the generic initial ideal {\rm(}with some specified ordering{\rm)}
-			is generated in degree at most $d(\sigma)$? Can one write down the
-			generic initial ideal explicitly?
-		\end{question}\todo{Peter: This whole question is kind of confusing.  I don't know what it is trying to say.}
 
@@
 		explicit procedure for computing the generators and relations of $R_
-		\halfcan$ when the genus of $\sx$ \todo{Peter: Minor note: should we say genus of $\sx$ or genus of $X$; did we actually define that a genus of a stacky curve equals that of its coarse space?} is $0$ or $1$.
-\todo{Peter: This question also seems like it might be the most important (as far as modular forms applications go.
-Maybe we should put it first?}
+		\halfcan$ when the genus of $X$ is $0$ or $1$.
 		\begin{question}
@@
 		\end{question}
-		In particular, if Question ~\ref{ques:spin-canonical-petri} were 
-		answered affirmatively one would be able to write down explicit 
-		generators and relations for $R_\halfcan$ on a stacky curve, essentially 
-		by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
-\todo{Aaron, I tried to edit the following question, but it still seems a bit imprecise, and the question in particular is a bit of a long sentence.}
-\todo{Peter @ Aaron: I think the last sentence of the question can be removed; generic isn't relevant in this part of further questions (it was relevant in part (2)).
-Also the sentence after the question can be removed.}
+\todo{Aaron: Peter, you said you wanted to take out the question on generic ideals, but I think it might be interesting to think about. Why do you want to remove it?}
+
+\item One direction for further research is to 
+		extend the results of this paper to divisors $D \in \di \sx$ on a 
+		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
+		divisors translate to rings of fractional weight ($\frac{2}{n}$) modular 
+		forms. As defined in Adler and Ramanan (in the passage immediately 
+		following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form 
+		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
+		line bundle $\eta$ so that there exists a line bundle $\gamma$ with 
+		$\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^
+		1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an 
+		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
+		Fractional modular forms also make an appearance in Milnor \cite[$
+		\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
+		shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e
+		_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of 
+		fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3
+		^{e_3} = 0$.
+\todo{Peter: I don't know if it is so worth while giving an explicit definition and precisely defining the work already done.
+A general outline might suffice and be easier/shorter to read.
+Aaron: I have a feeling we should define it, but I'm ok with removing the last two sentences.}
+
+		This motivates the following question:
+
+\todo{Peter: Would this be better as a conjecture? Aaron: I don't have an actual conjecture. I'm not sure what the bounds would be.}
+		\begin{question}
+		\label{ques:fractional-weight}
+			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
+			where $K$ is the canonical divisor of $\sx$, can one bound the 
+			degrees of generators and relations of $R_D$?
+		\end{question}
+		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
+		gives an affirmative answer to this question: If $\sx$ has signature 
+		$(g; e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
+		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
+		$2e$. 
+		It may be possible to modify the proof of Lemma
+		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
+		weight modular forms. 
+		Suitable generalizations of the 
+		lemmas of Section ~\ref{sec:induction} might allow one to 
+		follow similar questions to this paper and provide a general 
+		answer to Question ~\ref{ques:fractional-weight}.
+
+	\item Voight and Zureick Brown define
+		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
+		encapsulates the idea of whether the relations for $R_\halfcan$ are 
+		generically chosen, in a precise sense. 
+		The proof of Theorem
+		~\ref{thm:main} is decidedly non-generic. 
+		In particular, Lemma ~\ref{lem:raise-stacky-order} 
+		constructs generators with non-maximal pole orders at certain 
+		points, making the relations non-generic. 
+		\begin{question}
+		\label{ques:generic-initial}
+			If $(\sx, \Delta, \halfcan)$ is a log spin curve with signature $\sigma$,
+			does there exist a function $\sigma \mapsto d(\sigma)$ so that
+			the generic initial ideal {\rm(}with some specified ordering{\rm)}
+			is generated in degree at most $d(\sigma)$? Can one write down the
+			generic initial ideal explicitly?
+		\end{question}\todo{Peter: This whole question is kind of confusing.  I don't know what it is trying to say.}
+
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
@@
 		Generalizing this slightly stronger bound to the (non-stacky) log case case would allow us to inductively apply the lemmas from Section ~\ref{sec:induction} and improve Theorem ~\ref{thm:main} as follows:
-		\begin{conjecture}\label{ques:reduce-5,10-to-4,8}
-			When $g \geq 2,$ the bounds in Theorem \ref{thm:main} on 
+		\begin{question}\label{ques:reduce-5,10-to-4,8}
+			When $g \geq 2,$ can the bounds in Theorem \ref{thm:main} on 
 			the degrees of generation and relations can be reduced from 
@@
 			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
-			apart from a finite list of exceptions?
-		\end{conjecture}
+			apart from well a characterized list of exceptions?
+		\end{question}
 		\todo{Peter: I don't like a finite list of exceptions.
@@
 Can we say except when $g=2$ (I believe there will be infinitely many counterexamples there) or it lies in a finite list of exception?
-Do we believe that to be true?}
+Do we believe that to be true?
+Aaron: Since we haven't really thought about this conjecture, I'm not comfortable making it a conjecture.
+I switched it back to a question.
+Is that ok?}
 		\begin{rem}\label{rem:reduce-3,6}
@@
 			\end{rem}
-	\item While Theorem ~\ref{thm:main} gives a minimal set of 
-		generators \todo{Peter: I believe this is actually not true.
-If $R_{\halfcan'}$ is minimally generated by $x_1, \ldots x_m$ and $R_\halfcan$ is generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$, then $R_{\halfcan}$ is {\emph{generated}} by $x_1, \ldots, x_m, y_1, \ldots y_n$ but not necessarily minimally.
-It's possible to have something like $y_1y_3-y_2^2=x_i$.}
-		for the log spin canonical ring $R_\halfcan,$ the set of 
-		relations is not minimal. In many of the $g = 0$ and $g=1$ cases, 
+	\item While Theorem ~\ref{thm:main} gives a set of 
+		generators and relations
+		for the log spin canonical ring $R_\halfcan,$ these sets are not necessarily minimal
+		In many of the $g = 0$ and $g=1$ cases, 
 		it is not too difficult to see that our inductive procedure also 

### 2015-07-03 stacky_write_up/spin_cring.tex
added a couple of minor todos at beginning

@@
 \todo{Make sure we call all divisors spin canonical divisors}
-
+\todo{Write all block orders as tensors so we don't need to say the $y_i$ preceede the $x_i$.}
+\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each $\circ$ denotes a lattice point below $5y=14x$ which is not a best lower approximation.
+\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
 Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}

### 2015-07-03 stacky_write_up/spin_cring.tex
Edits to section 1 and some in section 2

@@
 $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
-linear transformations. We consider the {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best
+linear transformations. \todo{Peter: In the abstract we say finite area.  Don't we want that here as well?}  
+We consider the graded {\bf ring of modular forms}
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field?}. One of the best
 ways to understand the ring of modular forms is to give a
-presentation of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
-In order to do so, it is extremely useful to have a bound on the
+presentation as a quotient of a polynomial ring.
+%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
+To do so, it is useful to have a bound on the
 degrees in which the generators and relations can occur. In the
 special case that $\Gamma$ has no odd weight modular forms, Voight
-and Zureick-Brown \cite[Chapters 7-9]{vzb:stacky} give tight bounds.
- This work extends their work to all Fuchsian groups $\Gamma$.
+and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
+ This paper \todo{Peter: I changed ``work to paper.'' Either way, it is a little awkward, because this could refer to VZB, or the one we are writing (of course I know it is the latter, but the reader won't)} extends their work to all Fuchsian groups $\Gamma$.
 
@@
 For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
-\backslash \BH$ is a Riemann Surface over $\BC$. It may be
-that $\Gamma \backslash \BH$ is not compact, but we can form a
+\backslash \BH$ is a Riemann Surface over $\BC$.  $\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
 compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
-cusps, with associated divisor of cusps $\Delta$.
+cusps, with associated divisor of cusps $\Delta$.\todo{Peter: It is weird to have our first discussion of divisors be about the divisors of cusps.
+Shouldn't canonical or half canonical divisors be introduced first?}
 
@@
 of modular forms into the algebraic category, using a
-generalization of the GAGA principle. By \cite[Proposition 6.1.5]
-{vzb:stacky}, there is an equivalence of categories between orbifold
-curves and log stacky curves over $\BC$. Hence, for the remainder
+generalization of the GAGA principle: there is an equivalence of categories between orbifold
+curves and log stacky curves over $\BC$ \cite[Proposition 6.1.5]
+{vzb:stacky}. Hence, for the remainder
 of the paper, we will work in the algebraic category.
@@
 sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$. When $g \geq 2$, Petri's theorem gives generators
+\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$?}. When $g \geq 2$, Petri's theorem gives generators
 and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan).
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, \lfloor d \halfcan \rfloor).
 \end{align*}
@@
 e_r; \delta)$. The application of O'Dorney's work to log spin
-canonical rings gives a weak bound in the case $g = 0$, in
+canonical rings gives a weak bound in the case $g = 0$ in
 terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
@@
 and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
-\cite[Corollary 10.4.6]{vzb:stacky}.
+\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in.}
 
@@
 \label{rem:main-weaker-assumptions}
-In fact, the proof of Theorem ~\ref{thm:main} holds not only for log divisors, which must have distinct points, but also for arbitrary effective divisors
-$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
+In fact, the proof of Theorem ~\ref{thm:main} holds not only for log spin canonical divisors, which must have distinct points, but also for arbitrary effective divisors
+$\Delta$.
+\todo{Peter: $\Delta$ seems weird as the name of the divisor, since its typically reserved for log divisors.
+Also, how is this true?
+This only follows given sufficient base point freeness conditions.
+It is true when $g=0$ if that's what you meant to say.} Furthermore, one may relax the assumption that $k$ is perfect.
+Instead, one only need assume that the stacky curve
 is separably rooted, i.e. the residue field at each stacky point
@@
 \end{rem}
-
-Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$, each of
-which uses a similar inductive process. The genus $g \geq 2$ case is
-proven in Theorem ~\ref{thm:g-high-main}. In Theorem
-~\ref{thm:g-1-main} and Theorem
-~\ref{thm:g-0-main}, we also give the respective
-genus one and genus zero results after dealing with more involved base cases and
-exceptional cases.
-
+\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark?}
+
+Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.
+In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the high genus case we deduce base cases from more general arguments.
 \begin{rem}
@@
 detailed in interesting low genus examples by Neves
-\cite[Section III.4]{neves:halfcan}.
-
-Furthermore, the explicit construction of generators and relations also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
-That is, in almost all cases, there is a generator of the log spin canonical ring in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$.
-Furthermore, there are many infinite families of cases which have a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-\end{rem}
-
-The main theorem of this paper, Theorem ~\ref{thm:main}, combined
-with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
-{vzb:stacky}, provides a statement on rings of modular forms.
-Together with the main theorems from Voight and Zureick-Brown \cite
-[Theorem 9.3.1]{vzb:stacky} and \cite
-[Theorem 9.3.1]{vzb:stacky}, we have the following application to
-rings of modular forms. Note that the lemma from Voight and Zureick-
-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
-from the classical work of Kodaira--Spencer
-\cite{kodaira-spencer:deformations}.
+\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading}
+
+Furthermore, explicit constructions also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
+Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
+Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
+\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together?}
+
+%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
+%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
+%{vzb:stacky}, provides a statement on all rings of modular forms.
+Together with a theorem from Voight and Zureick-Brown \cite
+[Theorem 9.3.1]{vzb:stacky} 
+%and \cite[Theorem 9.3.1]{vzb:stacky}, 
+\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing.}
+we have the following application to
+rings of modular forms. 
+%Note that the lemma from Voight and Zureick-
+%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
+%from the classical work of Kodaira--Spencer
+%\cite{kodaira-spencer:deformations}.
 
@@
 degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.
+generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right?}
 
@@
 Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct on the stabilizer order and number of stacky points. To this end, we first review important background in
-Section ~\ref{sec:background}. Then, we develop various inductive
-tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g-high},
-~\ref{sec:g-1}, and ~\ref{sec:g-0}, we prove Theorem
-~\ref{thm:main} in the genus $ g \geq 2$, genus
-$g = 1$, and genus $g = 0$ cases respectively. Finally, in Section
+proof will be to induct first on the number of stacky points and then on the stabilizer order of those points.  To this end, we first review important background in
+Section ~\ref{sec:background}; providing essential examples in Section \ref{sec:examples}; develop various inductive
+tools in Section ~\ref{sec:induction}; and prove Theorem ~\ref{thm:main} in genus $g\ge 2$, genus $g=1$, and genus $g=0$ in Sections ~\ref{sec:g-high},
+~\ref{sec:g-1}, and ~\ref{sec:g-0} respectively.  
+Finally, in Section
 ~\ref{sec:further-questions}, we pose several questions for future
@@
 used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
-Saint-Donat \cite{saint-donat:proj}, Arbarello--
-Cornalba--Griffiths--Harris \cite[Section III.2]
+Saint-Donat \cite{saint-donat:proj}, Arbarello--Cornalba--Griffiths--Harris 
+\cite[Section III.2]
 {acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
@@
 of the stacky points is separable.
-
-With this stacks-theoretic description in mind, for simplicity, the remainder of this paper is primarily phrased using the language
+\todo{Peter: We should clarify this last statement.
+If we are assuming $k$ is algebraically closed, aren't the points automatically seperably-rooted?
+Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted?}
+
+With this stacks-theoretic description in mind, the remainder of this paper is primarily phrased using the language
 of Weil divisors.
@@
 	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial_\prec(I))_d \\
+	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial_\prec(I)_d \\
 	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle

### 2015-07-03 stacky_write_up/spin_cring.tex
sectino 2 edits

@@
 \label{defn:coarse-space}
-Let $\sx$ be a stacky curve over $k$ with coarse space $X$ and stacky points $P_1, \ldots,
+Let $\sx$ be a stacky curve over $k$ with coarse space $X$ \todo{We haven't defined a course space yet.
+Confusingly, this definition is labeled ``defn:course-space'' which made me think it was supposed to.} and stacky points $P_1, \ldots,
 P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
@@
 We can equip stacky curves with a log divisor $\Delta$ that is a 
-sum of distinct points each with trivial stabilizer. A divisor
+sum of distinct points each with trivial stabilizer.
+\todo{Peter: It isn't necessary in the proof that these log points be non-stacky, even though only such log divisors arise from modular forms.
+Need we say that?
+If so, then we should explicitly note that these are the only cases that arise.} A divisor
 $\Delta$ of this form is called a \textbf{log divisor}. We use
@@
 A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
-called a \textbf{log stacky curves} and the study of their
+called a \textbf{log stacky curve} and the study of their
 canonical rings is the main focus of the work by Voight and Zureick-
@@
 canonical divisor} (also known as the half-canonical divisor, semi-
-canonical divisor, or theta characteristic) associated to the
+canonical divisor, or theta characteristic) \todo{Peter: I think we mismatched the parenthetical.
+Also, why did we define the spin canonical rdivisor of $\halfcan_X$ especially.
+Isn't it really just a special case of the definition before.} associated to the
 coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
-that $2\halfcan_X \sim K_X + \Delta$). Furthermore, we use the
-following analogous notation:
+that $2\halfcan_X \sim K_X + \Delta$). 
+We define $H^0$ of a stacky divisor as follows:
 
@@
 \[
-	\halfcan = \sum_{i = 1}^{r} \subhalf{e_i} P_i + \sum_{i = 1}^{s} a_i P_i
+	\halfcan = \sum_{i = 1}^{r} \subhalf{e_i} P_i + \sum_{i = 1}^{s} a_i Q_i
 \]
@@
 where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
-that $\halfcan \in \di \sx$. If some $e_i$ were even,
+that $\halfcan \in \di \sx$: 
+if some $e_i$ were even,
 then $\frac{e_i - 1}{2e_i}$ would be in reduced form implying $\halfcan \notin \di \sx$.
@@
 
-We define the notion of the saturation of a divisor, as defined in
+We define the notion of the saturation of a divisor, as can be found in
 Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
@@
 \begin{equation}
-	\deg \alpha := \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' =: \deg \beta
+	\deg \alpha = \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' = \deg \beta
 \end{equation}
@@
 \label{eqn:grevlex-tie}
-	\deg \alpha = \deg \beta \text{ and }	f_i - f_i' < 0 \text{ for
+	\deg \alpha = \deg \beta \text{ and }	f_i < f_i' \text{ for
 	the	largest } i \text{ such that } f_i \neq f_i'.
@@
 bases. These will be used in the proofs of the inductive lemmas
-in Section ~\ref{sec:induction} and in the proof of Theorem
+in Section ~\ref{sec:induction} as well as in the proof of Theorem
 ~\ref{thm:main}.
@@
 \label{defn:initial-term}
-Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}],$ with $\deg x_i = d_i$ and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
+Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}]$, 
+with $\deg x_i = d_i$,
+and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
 polynomial. The \textbf{initial term} $\initial(f)$ of $f$
@@
 
-In this section, we compute several examples of computing presentations for spin canonical rings.
+In this section, we work out several examples of computing presentations for spin canonical rings.
 In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}.

### 2015-07-03 stacky_write_up/spin_cring.tex
edited sections 2 and 3

@@
 In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}.
-In addition to demonstrating the algorithmic procedure for computing presentations, these examples will also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
+In addition to providing intuition for the lemmas of Section ~\ref{sec:induction}, these examples also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
 
@@
 Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
-In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 
-Now, we check admissibility. By relabelling the
+Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). By relabelling the
 variables if necessary, we can assume that $x_{7, 1}$ corresponds
@@
 \begin{align*}
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I)_d &=
-	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial_\prec(I)_d \\
-	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
-	x_{7, 2}^2, x_{5, 1}^2 \rangle
-\end{align*}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
+	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I\right)_d &=
+	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial(I)\right)_d \\
+	&= \dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
+	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
+\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite.}
+
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left((k[x_{7, 2},
 x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{5, 1}^2
-\rangle$ can be checked by looking at the $k$-basis at each degree
+\rangle\right)_d$ can be checked by looking at the $k$-basis at each degree
 $d$.
@@
 k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
-initial ideal $\initial(I)$ generated by quadratics under grlex
+initial ideal $\initial(I)$ generated by quadratics under grevlex
 with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
@@
 Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + P_1, 3P - 3Q + P_2$ are both one dimensional, while the linear system $3P - 3Q \sim P - Q$ is zero dimensional.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
 
 Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zeros and poles.
+$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
 The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
@@
 \end{cases}.$$
-Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
+Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
+Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
 \end{example}
@@
 \label{rem:base-0-377}
-Example ~\ref{eg:base-0-377} is one of the inductive base cases
-used in the genus zero case (Section ~\ref{sec:g-0}) as
-listed in Table ~\ref{table:g-0-base-cases}.
+Examples ~\ref{eg:base-0-377} and \ref{eg:base-1-33} are used as inductive base cases in the genus 0 and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
 \end{rem}
@@
 Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
- Q + \frac{2}{5} P_1.$ Let $u \in (P_L)_1$ be any nonzero element.
+ Q + \frac{2}{5} P_1.$ Let $u \in (R_L)_1$ be any nonzero element \todo{Peter: I'm very confused.
+There are no elements in degree 1...
+Oh, I see, I think you mean $L'=\frac{2}{5}P_1$ (without the $P-Q$) maybe?}.
 We obtain $\di u|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
@@
 \]
-\todo{Aaron: This is correct, but it might be clearer to say there are no monomials in $I$ with initial term in $S$. }
+In particular, there are no monomials in $I$ with initial terms in $S$.
 Finally, note that
@@
 \noindent
-So, \todo{Aaron: Presumably this is Riemann Roch, but you should explain why, as I don't see it immediately.} there exist rational sections $t_i$ of $\sco(\lfloor d\halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
+Thus, there exist rational sections $t_i$ of $\sco(\lfloor d\halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
 for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{

### 2015-07-03 stacky_write_up/spin_cring.tex
address many peter todos, "revert" main g0 thm pf

@@
 \todo{Make sure we call all divisors spin canonical divisors}
-\todo{Write all block orders as tensors so we don't need to say the $y_i$ preceede the $x_i$.}
-\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page.}
+\todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
+\todo{Write all block orders as tensors so we don't need to say the $y_i$ precede the $x_i$.}
+\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page. Robin: do this at the end, not yet}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field?}. One of the best
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field?
+Robin: Perhaps, although modular forms are traditionally referred to as having weight $k$.
+Not sure on this one.}.
+One of the best
 ways to understand the ring of modular forms is to give a
@@
 and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
- This paper \todo{Peter: I changed ``work to paper.'' Either way, it is a little awkward, because this could refer to VZB, or the one we are writing (of course I know it is the latter, but the reader won't)} extends their work to all Fuchsian groups $\Gamma$.
+We extend their result to all Fuchsian groups $\Gamma$ in the main
+theorem of this work.
 
@@
 For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
-\backslash \BH$ is a Riemann Surface over $\BC$.  $\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
+\backslash \BH$ is a Riemann Surface over $\BC$. 
+$\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
 compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
 cusps, with associated divisor of cusps $\Delta$.\todo{Peter: It is weird to have our first discussion of divisors be about the divisors of cusps.
-Shouldn't canonical or half canonical divisors be introduced first?}
+Shouldn't canonical or half canonical divisors be introduced first?
+Robin: But this is where the log divisor comes from!}
 
@@
 of modular forms into the algebraic category, using a
-generalization of the GAGA principle: there is an equivalence of categories between orbifold
-curves and log stacky curves over $\BC$ \cite[Proposition 6.1.5]
-{vzb:stacky}. Hence, for the remainder
+generalization of the GAGA principle. By \cite[Proposition 6.1.5]
+{vzb:stacky}, there is an equivalence of categories between orbifold
+curves and log stacky curves over $\BC$. Hence, for the remainder
 of the paper, we will work in the algebraic category.
+\todo{Robin: I changed this back because the new version seemed a bit
+long and the period is perfectly acceptable here. the new version
+seemed oddly worded to me}
 
@@
 sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$?}. When $g \geq 2$, Petri's theorem gives generators
+\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$? Robin: see statement of Petri's theorem...}. When $g \geq 2$, Petri's theorem gives generators
 and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
@@
 and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
-\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in.}
+\cite[Corollary 10.4.6]{vzb:stacky}.
+\todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in.
+Robin: How?
+This solely talks about their work for the log spin canonical rings which is clearly NOT tight.
+They give a larger bound than us for a subset of the cases we check...}
 
@@
 This only follows given sufficient base point freeness conditions.
-It is true when $g=0$ if that's what you meant to say.} Furthermore, one may relax the assumption that $k$ is perfect.
+It is true when $g=0$ if that's what you meant to say.
+Robin: Throughout VZB, for example, $\Delta$ is used to represent any effective divisor.
+Where does an assumption that $\Delta$ has coefficient $1$ come into play?} Furthermore, one may relax the assumption that $k$ is perfect.
 Instead, one only need assume that the stacky curve
@@
 \end{rem}
-\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark?}
+\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark? Robin: This remark describes how the weaker conditions for which the theorem also holds.}
 
@@
 detailed in interesting low genus examples by Neves
-\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading}
+\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading Robin: how so}
 
@@
 Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together?}
+\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together?
+Robin:Isn't this remark describing whether the theorem gives explicit constructions and tight bounds?
+Those seem pretty related...}
 
@@
 %and \cite[Theorem 9.3.1]{vzb:stacky}, 
-\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing.}
+\todo{Peter: The paragraph used to be confusingly redundant.
+I think I fixed it but read through the commented out stuff to make sure it says the correct thing.
+Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer?}
 we have the following application to
@@
 degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right?}
+generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right?
+Robin: I think you are correct, although don't use $e$ since it is max(3, ...) instead of max(5, ...)}
 
@@
 \todo{Peter: We should clarify this last statement.
-If we are assuming $k$ is algebraically closed, aren't the points automatically seperably-rooted?
-Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted?}
+If we are assuming $k$ is algebraically closed, aren't the points automatically separably-rooted?
+Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted?
+Robin: Yes I guess $k$ being algebraically closed implies perfectness...
+we can use a similar statement to Remark 5.5.7 from VZB}
 
@@
 canonical divisor, or theta characteristic) \todo{Peter: I think we mismatched the parenthetical.
-Also, why did we define the spin canonical rdivisor of $\halfcan_X$ especially.
-Isn't it really just a special case of the definition before.} associated to the
+Also, why did we define the spin canonical divisor of $\halfcan_X$ especially.
+Isn't it really just a special case of the definition before.
+Robin: How?
+the parenthetical encompasses all alternate names!
+Yes it's a special case, but we never give it a name otherwise.
+You could define it as the log spin canonical divisor with zero log divisor but that somehow doesn't seem to give the right picture.} associated to the
 coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
@@
 
-Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). By relabelling the
+Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). \todo{Robin: I don't understand your edit, Peter. Admissibility is not a property of $J$.} By relabelling the
 variables if necessary, we can assume that $x_{7, 1}$ corresponds
@@
 	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
-\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite.}
+\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite. Robin: Aren't there already existing degree subscripts?}
 
@@
 First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-\iffalse
-In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
-as $P$ is not a basepoint of $L_X'$.
+
+%In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
+%as $P$ is not a basepoint of $L_X'$.
 Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.
@@
 Either we should reword it or remove it (feel free to disagree, of course)}
-\fi
+
 Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.
@@
 \noindent
-{\sf Case 2b: $L_X = 0$}
+{\sf Case 2b: $\halfcan_X = 0$}
 
@@
 
-\todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument? Ok, I did it imprecisely. Is this better?}
+\todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument? Aaron: Ok, I did it imprecisely. Is this better?}
 \end{proof}
@@
 \end{longtable}
-\todo{Peter: Can we make a better description for the table above?}
+\todo{Peter: Can we make a better description for the table above? Robin: Think of one.}
 
@@
 \end{longtable}
-\todo{Peter: In case c, I changed $J=\{3\}$ to $J=\{2, 3\}$.}
-\todo{Peter: I don't particularly like split tables.  Might we consider not using [h], so its not split}
 
@@
 
-Now we can use Lemma ~\ref{lem:sat-3}, Lemma
-~\ref{lem:raise-stacky-order}, and Corollary
-~\ref{cor:raise-stacky-order} to induct from the cases of Table
-~\ref{table:g-0-base-cases} and obtain the desired bounds on the
-generator and relation degrees for log spin canonical rings of
-genus 0 curves. This process will be carried out in Subsection
-~\ref{ssec:g-0-main}.
-\todo{Peter: I don't think this paragraph should be here.
+%Now we can use Lemma ~\ref{lem:sat-3}, Lemma
+%~\ref{lem:raise-stacky-order}, and Corollary
+%~\ref{cor:raise-stacky-order} to induct from the cases of Table
+%~\ref{table:g-0-base-cases} and obtain the desired bounds on the
+%generator and relation degrees for log spin canonical rings of
+%genus 0 curves. This process will be carried out in Subsection
+%~\ref{ssec:g-0-main}.
+%\todo{Peter: I don't think this paragraph should be here.
 It seems like its kind of redundant given section 7.4.
 Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}
+
 %Through the application of two inductively adding 
@@
 
-	$(0; 3, 3, 3; 0)$ & $\{3\}$ & $\emptyset$ & $3$ \\	\hline
+	$(0; 3, 3, 3; 0)$ & $\{3\}$ & $\emptyset$ & $5$ \\	\hline
 
@@
 
-	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $3$ \\	\hline
+	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $5$ \\	\hline
 
@@
 \end{longtable}
-\todo{Peter: Technically, shouldn't the first and last $e$ be 5 instead of 3, since $e=\max(5, e_i)$?}
 
 \begin{rem}
-These cases give all of the exceptions to the $e$ and $2e$ bounds on
-the generator and relation degree. Notice that each of these
-exceptional cases, apart from $(0; 3, 5, 7; 0)$, has saturation not in $\{3, 5, 9\}$ as seen in Table ~\ref{table:g-0-sat}.
-Heuristically, \todo{Peter: Is heuristically the right word here?
-I interpret heuristically to mean ``providing a technique or method to solve a problem,'' whereas I think you mean something more along the lines of intuitively.}
-these exceptional saturations can be viewed as ``forcing'' generators and relations in higher degrees than expected.
+These cases give all of the exceptions to the $e$ and $2e$ bounds
+on the generator and relation degree. Notice that each of these
+exceptional cases, apart from $(0; 3, 5, 7; 0)$, also has
+exceptional saturation as seen in Table ~\ref{table:g-0-sat}.
+Intuitively, these exceptional saturations can be viewed as ``
+forcing'' generators and relations in higher degrees than expected.
 \end{rem}
@@
 If $\sx$ has no stacky points, then we can assume that $L \sim
-n \cdot \infty$ with $n \in \BZ$.
-When $n=-1$, then $R_\halfcan=k$.
-When $n=0$, then $R_\halfcan = k[x]$.
-When $n>0$, inductively applying Lemma \ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1 with relations generated in degree 2.
-All three of these cases meet the conclusion of Theorem \ref{thm:g-0-main}.
-
-First, consider the case when $\delta \geq 2$. \todo{Peter: it feels a tiny bit redundant here, as we kind of said this in the introduction to the section.}
- In any such cases,
-$\halfcan_X$ is an effective divisor so we can inductively apply
-the Lemma ~\ref{lem:sat-1} from the classical non-stacky case
-to deduce that $R(\sx, \Delta, \halfcan)$ is generated up to degree $e$
-with relations generated up to degree $2e$.
-
-By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the case $\delta = 0$, so $\halfcan_X$ is not effective.
-Let $\sigma = (0; e_1, \ldots, e_r; 0)$ not be one of the exceptional cases in Table
-~\ref{table:g-0-exceptional}.  We get the following three cases, depending on the value of $r$:
+n \cdot \infty$ with $n \in \BZ_{\geq -1}$. This is a classical
+case which is done by Voight and Zureick-Brown \cite[Section 4.2]
+{vzb:stacky}. When $n = -1$, then $R_\halfcan = k$.  When $n = 0$,
+then $R_\halfcan = k[x]$.  When $n > 0$, inductively applying Lemma
+\ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1
+with relations generated in degree 2.
+
+First, let us consider the case when $\delta \geq 2$. In any such
+case, $\lfloor \halfcan \rfloor$ is an effective divisor and the
+conditions of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can
+apply the Lemma ~\ref{lem:sat-1} inductively from the classical
+case with no stacky points to get that $R(\sx, \Delta, \halfcan)$
+is generated up to degree $e$.
+
+By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the
+case $\delta = 0$, so $\halfcan$ is not necessarily effective. Let
+the signature $\sigma$ be such that it is not one of the
+exceptional cases contained in Table ~\ref{table:g-0-exceptional}. 
+We get the following three cases, depending on the value of $r$:
 
@@
 \noindent
-{\sf Case 1: $r<3$}
+{\sf Case 1: $r < 3$}
 
 If $r < 3$, then $\deg 
-\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we get the
-trivial ring $R(\sx, \Delta, \halfcan) = k$.
+\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
+trivial case where $R(\sx, \Delta, \halfcan) = k$.
 
@@
 \noindent
-{\sf Case 2: $3\le r \le 5$}
-
-If $3\le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
+{\sf Case 2: $3 \le r \le 5$}
+
+If $3 \le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
 then we may apply Lemma ~\ref{lem:g-0-admissible-cases} and
@@
 stabilizer order $3$ to case (k) of Table
-~\ref{table:g-0-base-cases}, which corresponds to $\sigma
-= (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$. This case
+~\ref{table:g-0-base-cases}, which corresponds to $(\sigma
+= (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\})$. This case
 satisfies the conditions of Lemma

### 2015-07-03 stacky_write_up/spin_cring.tex
minor things in addressing peter's todos

@@
 sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$? Robin: see statement of Petri's theorem...}. When $g \geq 2$, Petri's theorem gives generators
+\cong \proj R$ \todo{Peter: I'm confused.
+Why is this only true when $g\geq 2$?
+Robin: see statement of Petri's theorem (which actually usually assumes $g \geq 4$)...}.
+When $g \geq 2$, Petri's theorem gives generators
 and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
@@
 \end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together?
-Robin:Isn't this remark describing whether the theorem gives explicit constructions and tight bounds?
+Robin: Isn't this remark describing whether the theorem gives explicit constructions and tight bounds?
 Those seem pretty related...}
@@
 \end{longtable}
-\todo{Peter: Can we make a better description for the table above? Robin: Think of one.}
+\todo{Peter: Can we make a better description for the table above? Robin: Think of one then.}
 
@@
 \begin{proof}
-If $\sx$ has no stacky points, then we can assume that $L \sim
+\todo{Robin: I changed much of this back to the old wording. Also
+please don't randomly change three of the $\halfcan$'s to $\halfcan_X$'s
+when the latter is not used anywhere else in the section...}
+If $\sx$ has no stacky points, then we can assume that $\halfcan \sim
 n \cdot \infty$ with $n \in \BZ_{\geq -1}$. This is a classical
@@
 \begin{enumerate}
-
 	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
@@
 		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
-		Fractional modular forms also make an appearance in Milnor \cite[$
-		\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
+		Fractional modular forms also make an appearance in Milnor \cite
+		[$\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
 		shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e
@@
 			generic initial ideal explicitly?
-		\end{question}\todo{Peter: This whole question is kind of confusing.  I don't know what it is trying to say.}
+		\end{question}\todo{Peter: This whole question is kind of confusing.
+I don't know what it is trying to say.
+Robin: Maybe preface the question with saying something like ``not just the initial ideal''}
 
@@
 I switched it back to a question.
-Is that ok?}
+Is that ok?
+Robin: Perhaps give reference to Reid's characterizations?}
 		\begin{rem}\label{rem:reduce-3,6}

### 2015-07-03 stacky_write_up/spin_cring.tex
minor, log spin can divisor (manually), halfcan

@@
 
-\todo{Make sure we call all divisors spin canonical divisors}
 \todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
@@
 	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $L_X'$, rather than relative to the $\sco_X$.
+We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.
 
@@
 Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
+Before proving three lemmas that allow us to inductively add points to the support of a log spin canonical divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
 This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
@@
 \begin{rem}\label{rem:graded-P-lex-independent-of-line-bundle}
-Observe that Definition \ref{defn:graded-p-lex} remains the same if we replace $-\ord_P$ with $-\ord_P^{L'}$ for any divisor $L'$ of $X$.
+Observe that Definition \ref{defn:graded-p-lex} remains the same if we replace $-\ord_P$ with $-\ord_P^{L'}$ for any divisor $\halfcan'$ of $X$.
 \end{rem}
@@
 
-We area almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
+We are almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
 \BQ$-divisor.
@@
 If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
-Let $l$ be maximal such that $a_l\ne 0$.
+Let $\halfcan$ be maximal such that $a_l\ne 0$.
 Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
@@
 %basis element of the form described above: $y_n^0 y_j y_i u^0$). 
-%Choose the maximal $l$ such that $c_h \le c_i + c_j$; since $1 < d_i
+%Choose the maximal $\halfcan$ such that $c_h \le c_i + c_j$; since $1 < d_i
 %\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
@@
 \begin{proof}
-First, we shall show the assumptions on $g$ imply $H^0(\sx, 3L), H^0(\sx, 4L)$ are both base point free: If $g \geq 2$ then $\deg 3L > 2g - 1$ \todo{If $g = 2$ then we in fact have $\deg 3L = 3g-3 = 2g - 1.$ Is this a big problem?
-It's almost base point free, except if the point you take out yields the canonical divisor, after removing it.} and $\deg 4L > 2g - 1$, so $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
-If $g = 1$, we assume $\deg 3L \geq 2 > 2g - 1$, so we also have $\deg 4L \geq 2 > 2g - 1,$ so again $H^0(\sx, 3L)$ and $H^0(\sx, 4L)$ are base point free.
+First, we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ \todo{If $g = 2$ then we in fact have $\deg 3L = 3g - 3 = 2g - 1.$ Is this a big problem?
+It's almost basepoint-free, except if the point you take out yields the canonical divisor, after removing it.} and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
+If $g = 1$, we assume $\deg 3 \halfcan \geq 2 > 2g - 1$, so we also have $\deg 4 \halfcan \geq 2 > 2g - 1,$ so again $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
 
@@
 \label{lem:sat-3}
-Suppose $L'$ is a log spin canonical divisor of $\sx'$ with coarse
+Suppose $\halfcan'$ is a log spin canonical divisor of $\sx'$ with coarse
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
@@
 %\begin{proof}
-%Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)= 1$. 
+%Since adding $P$ to $\halfcan'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)= 1$. 
 %Choose any $y_1\in H^0(X, \lfloor L\rfloor)$; we know by saturation arguments that $-
@@
 %Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
-Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$.
-Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
+Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $\halfcan'$.
+Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $\halfcan$.
 %\end{lem}
@@
 Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{custom:Ad-i}.
-Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{custom:Ad-ii} satisfied so $\frac{-\ord_{Q_l}
+Furthermore, since $s$ is an admissible set of $\halfcan'$, in particular, we must have \ref{custom:Ad-ii} satisfied so $\frac{-\ord_{Q_l}
 %^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{custom:Ad-ii} follows in genus 0?}
@@
 %\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{custom:Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
+%\item When $g= 0$, since $\halfcan'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{custom:Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
 %\end{itemize}
@@
 %\label{lem:generation-5}
-%Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2 L \sim K +\Delta$. Then, $R_\halfcan$ is generated in degree at most $5$.
+%Let $X$ be a curve of genus $g \geq 2$ and let $\halfcan$ be a divisor with $2 L \sim K +\Delta$. Then, $R_\halfcan$ is generated in degree at most $5$.
 %\end{lem}
@@
 %Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X, \halfcan) = 1$.
-Hence, we know $L$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
+Hence, we know $\halfcan$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
 In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_\halfcan$ is generated in degree $\leq 3$.
@@
 
-Next, suppose the theorem holds for $\halfcan' = \halfcan_X+ \sum_{i=1}^{r-1} \frac{1}{3}P_i$ and take a divisor of the form $\halfcan = \halfcan_X + \sum_{i=1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
-If $P_r$ is a basepoint of $L'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
+Next, suppose the theorem holds for $\halfcan' = \halfcan_X + \sum_{i=1}^{r-1} \frac{1}{3}P_i$.
+Take a log spin canonical divisor of the form $\halfcan = \halfcan_X + \sum_{i=1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
+If $P_r$ is a basepoint of $\halfcan'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
+\todo{equals or $\sim$?}
 Otherwise, $P_r$ is not a basepoint of $\halfcan'$, meaning that in particular $R_{\halfcan'}$ is saturated in 1.
@@
 % since $\frac{\beta}{\alpha} = \frac{3}{1}=3$. 
-In this case, the theorem holds for $L$ by Lemma ~\ref{lem:sat-1}.
+In this case, the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-1}.
 
@@
 
-In the case of a genus 1 curve, $X$, we know $K_X \sim 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution.
-We inductively construct presentations by adding points through Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2} and incrementing the values of the $e_i$s using Lemma ~\ref{lem:raise-stacky-order}.
+In the case of a genus 1 curve, $X$, we know $K_X \sim 0$, and therefore the only possibilities for \todo{``log''?} spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P, Q$ are distinct points, fixed  under the hyperelliptic involution.
+We inductively construct presentations by adding points through Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2} and incrementing the values of the $e_i$'s using Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 If $\Delta > 0$, we must have $\Delta \geq 2$, by Remark ~\ref{rem:delta-not-1}.
-In this case, let $L_X \in \di X$ satisfy $2L_X \sim K_X + \Delta$.
-We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $L$ is linearly equivalent to an effective divisor.
-Thus, without loss of generality, we may assume $L$ is an effective divisor.
-
-We first now show the theorem holds for $L_X$ by induction.
-Since $L_X$ is effective, we may induct on the degree of the divisor.
-The base case is easy: the theorem holds for $L_X' = 0$ by Example ~\ref{eg:base-1-0}.
-Assume it holds for $L_X' \in \di X$, with $L_X'$ effective.
+In this case, let $\halfcan_X \in \di X$ satisfy $2 \halfcan_X \sim K_X + \Delta$.
+We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $\halfcan$ is linearly equivalent to an effective divisor.
+Thus, without loss of generality, we may assume $\halfcan$ is an effective divisor.
+
+We first now show the theorem holds for $\halfcan_X$ by induction.
+Since $\halfcan_X$ is effective, we may induct on the degree of the log spin canonical divisor.
+The base case is easy: the theorem holds for $\halfcan_X' = 0$ by Example ~\ref{eg:base-1-0}.
+Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective.
 We will show it holds for $L_X' + P,$ verifying the inductive step.
-There are two cases, depending on whether $P$ is a basepoint of $L_X'$.
+There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.
 
@@
 %In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
-%as $P$ is not a basepoint of $L_X'$.
+%as $P$ is not a basepoint of $\halfcan_X'$.
 Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.
@@
 
-Otherwise, $P$ is a basepoint of $L_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L_X') \geq 2$ as $\deg L_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L_X = L_X'+P$.
-By induction, the theorem holds for $L_X$.
-
-To complete the case that $\Delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin divisor $L$.
-It suffices to show that if the theorem holds for a divisor $L'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
-As above, if $P$ is not a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}.
-On the other hand, if $P$ is a basepoint of $L'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
+Otherwise, $P$ is a basepoint of $\halfcan_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L_X') \geq 2$ as $\deg L_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L_X = L_X'+P$.
+By induction, the theorem holds for $\halfcan_X$.
+
+To complete the case that $\Delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.
+It suffices to show that if the theorem holds for a log spin canonical divisor $\halfcan'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
+As above, if $P$ is not a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}.
+On the other hand, if $P$ is a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
 
@@
 
-Note that we are assuming $L$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points.
+Note that we are assuming $\halfcan$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points.
 
@@
 Furthermore, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Observe that $L'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$.
+Observe that $\halfcan'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$.
 However, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, and the relation in degree $12$ coming from $R_{\halfcan'}$, lies in a degree less than $2 \cdot 7 = 14$.
@@
 Note that by Table ~\ref{table:g-1-base}, $L = \frac{3}{7}P_1,$ will have a relation in degree $15.$ However, once $e_1 \geq 9$, we have $2 \cdot e_1 > 15$, so the theorem holds for such stacky curves.
-Once the divisor as at least two stacky points, the argument proceeds as in Case 2a.
+Once the log spin canonical divisor has at least two stacky points, the argument proceeds as in Case 2a.
 
@@
 First, we present the saturations, as defined in Definition
-~\ref{defn:sat}, of the canonical divisor for
+~\ref{defn:sat}, of the log spin canonical divisor for
 all cases where $g = 0$ and $\delta = 0$. The saturations can be computed using Riemann-Roch.
@@
 		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
-		algorithm for inductively determining the generators of $L$. 
+		algorithm for inductively determining the generators of $\halfcan$. 
 		This reduces Question \ref{ques:algorithm} to the 

### 2015-07-03 stacky_write_up/spin_cring.tex
fix a false statement about vzb log spin result

@@
 {dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$
-and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
+rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(e_1, \ldots, e_r)$
+and relation degrees by $6 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
 \cite[Corollary 10.4.6]{vzb:stacky}.
@@
 I think I fixed it but read through the commented out stuff to make sure it says the correct thing.
-Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer?}
+Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer?
+These are necessary.}
 we have the following application to

### 2015-07-03 stacky_write_up/spin_cring.tex
delete "excellent" from acknowledgments

@@
 study of stacky canonical rings, for providing invaluable guidance,
-and for his excellent mentorship. We also thank Ken Ono and the
+and for his mentorship. We also thank Ken Ono and the
 Emory University Number Theory REU for arranging our project and

### 2015-07-03 stacky_write_up/spin_cring.tex
cleaned up todos

@@
 \todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
-\todo{Write all block orders as tensors so we don't need to say the $y_i$ precede the $x_i$.}
-\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page. Robin: do this at the end, not yet}
+\todo{It's a bit strange how many tables are split across pages.
+Can we we make sure they each lie on a single page.
+Robin: do this at the end, not yet.
+Aaron: I changed our long tables to tables.
+Why did we use longtables at all?
+Our tables are all pretty short.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
-linear transformations. \todo{Peter: In the abstract we say finite area.  Don't we want that here as well?}  
+linear transformations, such that $\Gamma \backslash \BH$ has finite area.
 We consider the graded {\bf ring of modular forms}
@@
 Robin: Perhaps, although modular forms are traditionally referred to as having weight $k$.
-Not sure on this one.}.
+Not sure on this one.
+Aaron: I do not think this will confuse anyone.}.
 One of the best
@@
 Why is this only true when $g\geq 2$?
-Robin: see statement of Petri's theorem (which actually usually assumes $g \geq 4$)...}.
+Robin: see statement of Petri's theorem (which actually usually assumes $g \geq 4$)...
+Aaron: You need genus at least 2 for $\Omega_X$ to be ample.
+There are mild generalizations of Petri's theorem, for example those in vzb, which also compute generators and relations for hyperelliptic curves, and curves of genus 3.}.
 When $g \geq 2$, Petri's theorem gives generators
@@
 {dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(e_1, \ldots, e_r)$
-and relation degrees by $6 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
+rings, Voight and Zureick-Brown bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
+and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
 \cite[Corollary 10.4.6]{vzb:stacky}.
+Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.
 \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in.
@@
 This solely talks about their work for the log spin canonical rings which is clearly NOT tight.
-They give a larger bound than us for a subset of the cases we check...}
+They give a larger bound than us for a subset of the cases we check...
+Aaron: I think the point is that if they put in some more work, they could have reduced the bounds.
+However, I agree with Robin for two reasons: First, they didn't put in the work to get the tighter bounds.
+Second, even with a small amount of work, they would have only gotten bounds which are twice ours, as their grading is off from ours by a factor of two.}
 
@@
 Instead, one only need assume that the stacky curve
-is separably rooted, i.e. the residue field at each stacky point
-is separable.
+is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
 \end{rem}
-\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark? Robin: This remark describes how the weaker conditions for which the theorem also holds.}
 
 Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.
-In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the high genus case we deduce base cases from more general arguments.
+In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the genus $g \geq 2$ case we deduce base cases from more general arguments.
 \begin{rem}
@@
 also yield explicit systems of generators and an explicit initial ideal of
-relations. Furthermore, our proof of the high genus case also
+relations. Furthermore, our proof of the genus $g \geq 2$ case also
 provides an inductive procedure for explicitly determining the 
 generators and initial ideal of relations of log spin canonical
-rings. Many explicit systems of generators and relations are
-detailed in interesting low genus examples by Neves
-\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading Robin: how so}
-
-Furthermore, explicit constructions also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
+rings. Many explicit systems of generators and relations for curves of genus $2 \leq g \leq 15$ are
+detailed in interesting examples by Neves
+\cite[Section III.4]{neves:halfcan}. 
+\end{rem}
+\begin{rem}
+The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
 Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
 Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together?
-Robin: Isn't this remark describing whether the theorem gives explicit constructions and tight bounds?
-Those seem pretty related...}
-
-%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
-%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
-%{vzb:stacky}, provides a statement on all rings of modular forms.
-Together with a theorem from Voight and Zureick-Brown \cite
-[Theorem 9.3.1]{vzb:stacky} 
-%and \cite[Theorem 9.3.1]{vzb:stacky}, 
-\todo{Peter: The paragraph used to be confusingly redundant.
-I think I fixed it but read through the commented out stuff to make sure it says the correct thing.
-Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer?
-These are necessary.}
+\end{rem}
+
+Combining the main theorem of this paper, Theorem ~\ref{thm:main} with the main theorem from Voight and Zureick-Brown ~\cite
+[Theorem 1.4]{vzb:stacky} and a minor Lemma \cite[Lemma 10.2.1]{vzb:stacky}
 we have the following application to
@@
 forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
-degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right?
-Robin: I think you are correct, although don't use $e$ since it is max(3, ...) instead of max(5, ...)}
+degree at most $6 \cdot \max(3, e_1, \ldots, e_r)$ with relations
+generated in degrees at most $12 \cdot \max(3, e_1, \ldots, e_r)$.
 
@@
 \begin{rem}
-In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $3 \cdot \max(3, e_1, \ldots, e_r)$ and relation
-bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $\max(3,e_1, \ldots, e_r)$ and $2 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
-~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 9.3.1]{vzb:stacky} for a more precise statement of these bounds.
+\label{rem:factor-two}
+In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
+bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
+~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively.
+Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two, because our grading convention on $\bigoplus_k M_k(\Gamma)$ differs from that of Voight and Zureick-Brown by a factor of 2.
 \end{rem}
@@
 \label{ssec:stacky-background}
-A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
-geometrically-connected Deligne-Mumford stack of dimension $1$ over
-$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
-its stabilizers are coprime to char $k$.
+We begin by setting up the notation for stacky curves and canonical rings.
+Wherever possible, we opt for a more elementary scheme-theoretic approach, instead of a stack-theoretic one.
+See Remark ~\ref{rem:stack-formalism} for more details.
+
+\begin{defn}
+\label{defn:stacky-curve}
+A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
+
+\end{defn}
 
@@
 \label{rem:stack-formalism}
-Stacky curves may be formally defined in the language of stacks, (as
+Stacky curves may be formally defined in the language of stacks, as
 is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
 Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
-Behrend and Noohi \cite{behrend-noohi:uniformization},) but for the
-purposes of this paper, it suffices to treat $\sx$ as a scheme
-whose associated divisor group has a finite number of stacky
-points.
-
-In this paper, all stacky curves are assumed to be tame and
-$k$ will is assumed to be algebraically closed. We also assume that the
-stacky curves are separably rooted, i.e. the residue field of each
+Behrend and Noohi \cite{behrend-noohi:uniformization}.
+
+The results of this paper can be easily couched in terms of the language of stacks.
+If one works over an arbitrary field $k$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.
+the residue field of each
 of the stacky points is separable.
-\todo{Peter: We should clarify this last statement.
-If we are assuming $k$ is algebraically closed, aren't the points automatically separably-rooted?
-Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted?
-Robin: Yes I guess $k$ being algebraically closed implies perfectness...
-we can use a similar statement to Remark 5.5.7 from VZB}
-
-With this stacks-theoretic description in mind, the remainder of this paper is primarily phrased using the language
-of Weil divisors.
+
+With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
+of schemes.
 \end{rem}
 
-If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
-then we use $e_1, \ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
-of the stabilizer groups of the points with non-trivial
-stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
-In order to study objects associated with stacky curves, it is often
-useful to consider them in the context of schemes (instead of in the context of stacks).
-
 \begin{defn}
-\label{defn:coarse-space}
-Let $\sx$ be a stacky curve over $k$ with coarse space $X$ \todo{We haven't defined a course space yet.
-Confusingly, this definition is labeled ``defn:course-space'' which made me think it was supposed to.} and stacky points $P_1, \ldots,
+\label{defn:div-ex}
+Let $\sx$ be a stacky curve over $k$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
 P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
-Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
-genus $g$. Then, we notate
+Then, we notate
 \[
@@
 Need we say that?
-If so, then we should explicitly note that these are the only cases that arise.} A divisor
+If so, then we should explicitly note that these are the only cases that arise.
+Aaron: I don't think we need to say it, the application to modular forms still goes through whether or not we want to assume they are distinct.
+I like keeping log divisors like this so that we parallel \cite{vzb:stacky}}
+A divisor
 $\Delta$ of this form is called a \textbf{log divisor}. We use
@@
 \frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
-\textbf{log spin canonical divisor} on $(\sx, \Delta)$. We use
-$\halfcan_X := \lfloor L \rfloor $ to refer to the \textbf{spin
-canonical divisor} (also known as the half-canonical divisor, semi-
-canonical divisor, or theta characteristic) \todo{Peter: I think we mismatched the parenthetical.
-Also, why did we define the spin canonical divisor of $\halfcan_X$ especially.
-Isn't it really just a special case of the definition before.
-Robin: How?
-the parenthetical encompasses all alternate names!
-Yes it's a special case, but we never give it a name otherwise.
-You could define it as the log spin canonical divisor with zero log divisor but that somehow doesn't seem to give the right picture.} associated to the
-coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
+\textbf{log spin canonical divisor} on $(\sx, \Delta)$. Throughout the paper, we use
+the notation $\halfcan_X := \lfloor L \rfloor.$ to refer to the log spin
+canonical divisor (also known as the half-canonical divisor, 
+semi-canonical divisor, or theta characteristic) associated to the
+coarse space $X$ of $\sx.$  (i.e. $\halfcan_X$ is a divisor such
 that $2\halfcan_X \sim K_X + \Delta$). 
@@
 \cite[Chapter 2]{cls:ideals-varieties-algorithms}.
-
-\todo{possibly compactify or refer to relations, Aaron: I think we should almost remove these definitions, and that these shouldn't be in environments.
-I suspect people will be familiar with them, or be able to look them up.}
 
@@
 \label{eg:base-0-377}
-Let $(\sx,0, \halfcan')$ be a log spin curve with signature $\sigma =
+Let $(\sx',0, \halfcan')$ be a log spin curve with signature $\sigma =
 (0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
@@
 distinct points. In this example, we will exhibit a minimal
-presentation for $R' = R(\sx,0, \halfcan')$ and show the triple
+presentation for $R' = R(\sx',0, \halfcan')$ and show the triple
 $(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
@@
 
-Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). \todo{Robin: I don't understand your edit, Peter. Admissibility is not a property of $J$.} By relabelling the
+Now, we check the admissibility of $(\sx', L' ,J),$ where $J = \{2, 3\}$. By relabelling the
 variables if necessary, we can assume that $x_{7, 1}$ corresponds
@@
 \begin{align*}
-	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I\right)_d &=
-	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial(I)\right)_d \\
-	&= \dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
+	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_d &=
+	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_d \\
+	&= \dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
 	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
-\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite. Robin: Aren't there already existing degree subscripts?}
-
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left((k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{5, 1}^2
+\end{align*}
+\noindent
+for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left(k[x_{7, 2},
+x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
 \rangle\right)_d$ can be checked by looking at the $k$-basis at each degree
@@
 Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
- Q + \frac{2}{5} P_1.$ Let $u \in (R_L)_1$ be any nonzero element \todo{Peter: I'm very confused.
-There are no elements in degree 1...
-Oh, I see, I think you mean $L'=\frac{2}{5}P_1$ (without the $P-Q$) maybe?}.
-We obtain $\di u|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
---Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
+ Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_L)_2$ be any nonzero element.
+We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
+--Roch, $\dim_k (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
 element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
@@
 
-$$R_\halfcan \cong k[u, y_3, y_5]/(y_3^4 - \alpha u y_5^2).$$
+$$R_\halfcan \cong k[x_2 , y_3, y_5]/(y_3^4 - \alpha x_2 y_5^2).$$
 
@@
 
-\ssec{Adding Points}  \todo{Peter: Note to self: replace $H^0(X, \lfloor L\rfloor)$ with $H^0(\sx, L)$.}
+\ssec{Adding Points}
 \label{ssec:add-points}
@@
 	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
-	Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1,
-	\ldots, y_n]$ with the block order giving the order giving $y_1, 
-	\ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.
-
+	Definition ~\ref{defn:graded-p-lex} and $k[y_1, \ldots, y_n] \otimes k[u, x_1, \ldots, x_m]$ with block order.
 	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
@@
 In part (a), we showed that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving condition (1) of Lemma ~\ref{lem:relations_from_generators_induction}.
-Our choice of monomial order in $k[y_1, \ldots, y_n]$ and block order for $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
+Our choice of monomial order in $k[y_1, \ldots, y_n]$ and block order for $k[y_1, \ldots, y_n]\otimes k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
 
@@
 This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
-Lemma ~\ref{lem:relations_from_generators_induction} are met.
-Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).
-\todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.
-On the other hand, it is somewhat important.
-Should it be included?}
+Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).
 
@@
 		y_4$
-		and equip the ring $k[y_3, y_4, x]$ with the block 
-		order with $y_3, y_4$ preceding $x_2, \ldots, x_m$.
-\todo{In here and throughout the section, we should just enforce the convention that the $y_i$ come before the $x_j$, and then we won't have to say which precede which.} Then,
+		and equip the ring $k[y_3, y_4] \otimes k[x_2, \ldots, x_m]$ with block 
+		order. Then,
 		\begin{align*}
@@
 		y_4 \prec y_5$
-		and equip the ring $k[y_3, y_4, y_5, x_3, \ldots, x_m]$ with the block order so that $y_3, y_4, y_5$ dominate $x_3, \ldots, x_m$ \todo{Aaron: I used the word dominate, is this ok?}.  Then,
+		and equip the ring $k[y_3, y_4, y_5] \otimes k[x_3, \ldots, x_m]$ with the block order.  Then,
 		\begin{align*}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% High genus %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{High Genus}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus $\geq 2$ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Genus $\geq 2$}
 \label{sec:g-high}
@@
 
-\ssec{Bounds on Generators and Relations in High Genus}
+\ssec{Bounds on Generators and Relations in Genus $\geq 2$}
 \label{ssec:bounds-high-genus}
@@
 
-\ssec{Main Theorem for High Genus}
+\ssec{Main Theorem for Genus $\geq 2$}
 \label{ssec:g-high-main}
@@
 If $P_r$ is a basepoint of $\halfcan'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
-\todo{equals or $\sim$?}
 Otherwise, $P_r$ is not a basepoint of $\halfcan'$, meaning that in particular $R_{\halfcan'}$ is saturated in 1.
@@
 
-In the case of a genus 1 curve, $X$, we know $K_X \sim 0$, and therefore the only possibilities for \todo{``log''?} spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P, Q$ are distinct points, fixed  under the hyperelliptic involution.
+In the case of a genus 1 curve, $X$ with no stacky points, we know $K_X \sim 0$, and therefore the only possibilities for log spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P, Q$ are distinct points, fixed  under the hyperelliptic involution.
 We inductively construct presentations by adding points through Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2} and incrementing the values of the $e_i$'s using Lemma ~\ref{lem:raise-stacky-order}.
@@
 
-\begin{longtable}	{| c || c | c | c |}	
+\begin{table}	
+\begin{tabular}
+{| c || c | c | c |}	
 	\hline
@@
 	$P - Q + \frac{1}{3} P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ & $5$ \\	\hline
-
+\end{tabular}	
 	\caption{Genus 1 Base Cases}
@@
 %	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
-\end{longtable}
+\end{table}
 
@@
 
-\begin{longtable}	{| c || c | c | c |}
+\begin{table}	
+\begin{tabular}
+{| c || c | c | c |}
 	\hline
@@
 	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline
-
+	\end{tabular}
 	\caption{Genus 1 Exceptional Cases}
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \lfloor d L \rfloor)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, d L)
 \end{align*}
@@
 
-\begin{longtable}
+\begin{table}
+\begin{tabular}
 	{| c | c || c |}
@@
 	$(0; e_1, \ldots, e_r; 0)$ & not listed above & $3$ \\	\hline
-
+	\end{tabular}
 	\caption{Genus 0 Saturation}
 	\label{table:g-0-sat}
-\end{longtable}
+\end{table}
 
@@
 \rm{
-\begin{longtable}
+\begin{table}
+\begin{tabular}
 	{| c || c | c | c |}
@@
 	(k) &	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ \\ \hline
-
+	\end{tabular}
 	\caption{Genus 0 Base Cases}
 	\label{table:g-0-base-cases}
-\end{longtable}
+\end{table}
 }
@@
 elements of degree at most $e$ with relations in degree at most $2e$
-for each case as described in the following table.
-\begin{longtable}
+for each case as described in the Table ~\ref{table:g-0-base-cases-degrees}.
+\begin{table}
+\begin{tabular}
 	{| c || c | c | c |}
@@
 	(k) &	$\{3, 3, 3, 4, 4, 5\}$ & $\{6, 7, 7, 8, 8, 8, 9, 9, 10\}$ & $5$ \\ \hline
-
-	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
+	\end{tabular}
+	\caption{Generators and Relations for Genus 0 Non-effective Base Cases}
 	\label{table:g-0-base-cases-degrees}
-\end{longtable}
+\end{table}
 \todo{Peter: Can we make a better description for the table above? Robin: Think of one then.}
@@
 
-Furthermore, each case always satisfies \ref{custom:Ad-iii} as demonstrated below.
+Furthermore, each case always satisfies \ref{custom:Ad-iii} as demonstrated in table ~\ref{table:g-0-base-cases-admissibility}.
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
@@
 
-\begin{longtable}
+\begin{table}
+\begin{tabular}
 	{| c | c | c || c | c |}
@@
 	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ & $0$ \\ \hline
-
-	\caption{Genus 0 Non-Effective Base Cases \ref{custom:Ad-iii}}
+\end{tabular}	
+	\caption{Checking \ref{custom:Ad-iii} for Genus 0 Non-Effective Base Cases}
 	\label{table:g-0-base-cases-admissibility}
-\end{longtable}
+\end{table}
 
@@
 \label{ssec:g-0-exceptional}
-In this subsection, we describe the cases that would not be covered by induction.
-We present the explicit generators and relations for the remaining
+In this subsection, we describe the cases that are not covered by induction, which are also the only exceptions to Theorem ~\ref{thm:main} in the case $g = 0$.
+In table ~\ref{table:g-0-exceptional} We present the explicit generators and relations for the remaining
 cases given by signatures in the finite set
@@
 
-\noindent
-and in particular describe the only exceptions to Theorem ~\ref{thm:main}
-in the case $g = 0$.  \todo{This paragraph is kind of repetitive, and awkward.}
-
-\begin{longtable}
+\begin{table}
+\begin{tabular}
 	{| c || c | c | c |}
@@
 	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $5$ \\	\hline
-
+\end{tabular}
 	\caption{Genus 0 Exceptional Cases}
 	\label{table:g-0-exceptional}
-\end{longtable}
+\end{table}
 
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \lfloor d L \rfloor)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, L)
 \end{align*}
@@
 so long as $\sigma$ does not lie in the finite list of exceptional
-cases listed in Table ~\ref{table:g-0-exceptional}.
+cases in Table ~\ref{table:g-0-exceptional}.
 \end{thm}
@@
 \begin{proof}
-\todo{Robin: I changed much of this back to the old wording. Also
-please don't randomly change three of the $\halfcan$'s to $\halfcan_X$'s
-when the latter is not used anywhere else in the section...}
 If $\sx$ has no stacky points, then we can assume that $\halfcan \sim
@@
 		\label{ques:generic-initial}
-			If $(\sx, \Delta, \halfcan)$ is a log spin curve with signature $\sigma$,
-			does there exist a function $\sigma \mapsto d(\sigma)$ so that
-			the generic initial ideal {\rm(}with some specified ordering{\rm)}
-			is generated in degree at most $d(\sigma)$? Can one write down the
+			If $(\sx, \Delta, \halfcan)$ is a log spin curve, can one write down the
 			generic initial ideal explicitly?
-		\end{question}\todo{Peter: This whole question is kind of confusing.
-I don't know what it is trying to say.
-Robin: Maybe preface the question with saying something like ``not just the initial ideal''}
-
+		\end{question}
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 

### 2015-07-03 stacky_write_up/spin_cring.tex
fixed some todos in section 4

@@
 sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$ \todo{Peter: I'm confused.
-Why is this only true when $g\geq 2$?
-Robin: see statement of Petri's theorem (which actually usually assumes $g \geq 4$)...
-Aaron: You need genus at least 2 for $\Omega_X$ to be ample.
-There are mild generalizations of Petri's theorem, for example those in vzb, which also compute generators and relations for hyperelliptic curves, and curves of genus 3.}.
-When $g \geq 2$, Petri's theorem gives generators
+\cong \proj R$. When $g \geq 2$, Petri's theorem gives generators
 and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
@@
 Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.
-\todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in.
-Robin: How?
-This solely talks about their work for the log spin canonical rings which is clearly NOT tight.
-They give a larger bound than us for a subset of the cases we check...
-Aaron: I think the point is that if they put in some more work, they could have reduced the bounds.
-However, I agree with Robin for two reasons: First, they didn't put in the work to get the tighter bounds.
-Second, even with a small amount of work, they would have only gotten bounds which are twice ours, as their grading is off from ours by a factor of two.}
 
@@
 Robin: Throughout VZB, for example, $\Delta$ is used to represent any effective divisor.
-Where does an assumption that $\Delta$ has coefficient $1$ come into play?} Furthermore, one may relax the assumption that $k$ is perfect.
+Where does an assumption that $\Delta$ has coefficient $1$ come into play?
+Peter: All I meant with the first comment was that $D$ might make more sense then $\Delta$, because this divisor does not arise in a natural way purely from the log divisor.
+On the other hand, it doesn't really matter.}
+\todo{Peter: As for the second comment I made above, when $g>0$, we don't have the necessary base point freeness condition to apply this lemma on arbitrary divisors.} Furthermore, one may relax the assumption that $k$ is perfect.
 Instead, one only need assume that the stacky curve
@@
 sum of distinct points each with trivial stabilizer. 
-\todo{Peter: It isn't necessary in the proof that these log points be non-stacky, even though only such log divisors arise from modular forms.
-Need we say that?
-If so, then we should explicitly note that these are the only cases that arise.
-Aaron: I don't think we need to say it, the application to modular forms still goes through whether or not we want to assume they are distinct.
-I like keeping log divisors like this so that we parallel \cite{vzb:stacky}}
 A divisor
@@
 		\item[\customlabel{custom:sat-1-***}{(***)}] there does not
-			exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}\ge c_{r + 1}$.
+			exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}> c_{r + 1}$.
 	\end{enumerate}
@@
 
-\todo{Say something like a monomial is in $S$ if and only if it satisfies some condition with $c_h,$ and that we use this to check the three (*) conditions.}
 We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  
-Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.
-Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies \ref{custom:sat-1-**}.
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition \ref{custom:sat-1-***} holds.
-Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
+Notice that if $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_h\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among the subset of $c_1, \ldots c_n$ of elements not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
+Therefore, Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$, which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, meaning that $\sum_{j=1}^h {y_j}^{\gamma_j}$ satisfies \ref{custom:sat-1-*}.
+Suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for at least 1 $l$.
+Then, since for all $r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.
+Furthermore, since $(\gamma_1, \ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.
+Therefore, in particular $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.
+Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ as note above, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
+Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$.
 
@@
 We should make one of them consistent with the other.} be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
-Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, $\sat(Eff(L'))\le 2$.
+Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann-Roch $\sat(Eff(L'))\le 2$.
 \todo{Why is it automatic that the saturation is 2?
@@
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch \todo{Probably include this in a remark below the proof}).
-Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
+Suppose for $i \in \{2, 3\}$, we generically choose $x_i$ satisfying $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$. Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
 \begin{align*}
@@
 \begin{proof}
-First, we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ \todo{If $g = 2$ then we in fact have $\deg 3L = 3g - 3 = 2g - 1.$ Is this a big problem?
-It's almost basepoint-free, except if the point you take out yields the canonical divisor, after removing it.} and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
+First, note that when genus is at least we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ \todo{If $g = 2$ then we in fact have $\deg 3L = 3g - 3 = 2g - 1.$ Is this a big problem?
+It's almost basepoint-free, except if the point you take out yields the canonical divisor, after removing it.
+Peter:  Note that this is $L$ not $L'$ whose base point freeness we are talking about.
+In particular $\deg(\lfloor 3L \rfloor)=\deg(\lfloor 3L'\rfloor)+1\ge 2g> 2g-1$.} and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
 If $g = 1$, we assume $\deg 3 \halfcan \geq 2 > 2g - 1$, so we also have $\deg 4 \halfcan \geq 2 > 2g - 1,$ so again $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.

### 2015-07-03 stacky_write_up/spin_cring.tex
more edits to monster lemma

@@
 		\item[\customlabel{custom:sat-1-***}{(***)}] there does not
-			exist $r<i$ such that $\sum_{j=1}^r y_j^{a_j}> c_{r + 1}$.
+			exist $r<i$ such that $\sum_{j=1}^r a_j c_j> c_{r + 1}$.
 	\end{enumerate}
@@
 
-We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  
-Notice that if $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_h\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among the subset of $c_1, \ldots c_n$ of elements not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
-Therefore, Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$, which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, meaning that $\sum_{j=1}^h {y_j}^{\gamma_j}$ satisfies \ref{custom:sat-1-*}.
-Suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for at least 1 $l$.
-Then, since for all $r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.
+We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  
+Notice that if $r\le n$, $\omega_1, \ldots \omega_r\in \mathbb{Z}_{\ge 0}$, and $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_r\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among $c_1, \ldots c_n$ not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
+Therefore, since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$, which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$.
+Therefore $\sum_{j=1}^h {y_j}^{\gamma_j}$ satisfies \ref{custom:sat-1-*}.
+
+Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for some $l$.
+Then, for all $r< h$ we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.
 Furthermore, since $(\gamma_1, \ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.
-Therefore, in particular $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ as note above, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
+Therefore, $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.
+Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ meaning that $\sum_{j=1}^r \gamma_j c_j < c_{r+1}$, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
 Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$.

### 2015-07-03 stacky_write_up/spin_cring.tex
cleared todos

@@
 
-\todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
-\todo{It's a bit strange how many tables are split across pages.
-Can we we make sure they each lie on a single page.
-Robin: do this at the end, not yet.
-Aaron: I changed our long tables to tables.
-Why did we use longtables at all?
-Our tables are all pretty short.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field?
-Robin: Perhaps, although modular forms are traditionally referred to as having weight $k$.
-Not sure on this one.
-Aaron: I do not think this will confuse anyone.}.
-One of the best
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best
 ways to understand the ring of modular forms is to give a
@@
 compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
-cusps, with associated divisor of cusps $\Delta$.\todo{Peter: It is weird to have our first discussion of divisors be about the divisors of cusps.
-Shouldn't canonical or half canonical divisors be introduced first?
-Robin: But this is where the log divisor comes from!}
+cusps, with associated divisor of cusps $\Delta$.
 
@@
 of the paper, we will work in the algebraic category.
-\todo{Robin: I changed this back because the new version seemed a bit
-long and the period is perfectly acceptable here. the new version
-seemed oddly worded to me}
 
@@
 \label{rem:main-weaker-assumptions}
-In fact, the proof of Theorem ~\ref{thm:main} holds not only for log spin canonical divisors, which must have distinct points, but also for arbitrary effective divisors
-$\Delta$. 
-\todo{Peter: $\Delta$ seems weird as the name of the divisor, since its typically reserved for log divisors.
-Also, how is this true?
-This only follows given sufficient base point freeness conditions.
-It is true when $g=0$ if that's what you meant to say.
-Robin: Throughout VZB, for example, $\Delta$ is used to represent any effective divisor.
-Where does an assumption that $\Delta$ has coefficient $1$ come into play?
-Peter: All I meant with the first comment was that $D$ might make more sense then $\Delta$, because this divisor does not arise in a natural way purely from the log divisor.
-On the other hand, it doesn't really matter.}
-\todo{Peter: As for the second comment I made above, when $g>0$, we don't have the necessary base point freeness condition to apply this lemma on arbitrary divisors.} Furthermore, one may relax the assumption that $k$ is perfect.
-Instead, one only need assume that the stacky curve
+In fact, the proof of Theorem ~\ref{thm:main} holds with $\Delta$ replaced by an arbitrary effective divisor of the coarse space.
+ Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
 is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
@@
 \label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan)$ and $(\sx', \Delta, \halfcan')$ \todo{The notation i was using for these throughout the paper was $\halfcan$ and $\halfcan'$ without the $\sx$ subscripts.
-We should make one of them consistent with the other.} be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
+Let $(\sx, \Delta, \halfcan)$ and $(\sx', \Delta, \halfcan')$ be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
 Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann-Roch $\sat(Eff(L'))\le 2$.
-\todo{Why is it automatic that the saturation is 2?
-Maybe you can explain this in the proof in a sentence.}
 Furthermore, let $R_{\halfcan'} = k[x_2, x_3
@@
 \begin{proof}
-First, note that when genus is at least we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ \todo{If $g = 2$ then we in fact have $\deg 3L = 3g - 3 = 2g - 1.$ Is this a big problem?
-It's almost basepoint-free, except if the point you take out yields the canonical divisor, after removing it.
-Peter:  Note that this is $L$ not $L'$ whose base point freeness we are talking about.
-In particular $\deg(\lfloor 3L \rfloor)=\deg(\lfloor 3L'\rfloor)+1\ge 2g> 2g-1$.} and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
+First, note that when genus is at least we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ 
+and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
 If $g = 1$, we assume $\deg 3 \halfcan \geq 2 > 2g - 1$, so we also have $\deg 4 \halfcan \geq 2 > 2g - 1,$ so again $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
@@
 for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
-\todo{Peter: Why is it immediate that $n$ threes satisfies the condition for admissibility?
-We got rid of that proof from earlier.
-In fact, didn't we find it to be false?
-Aaron: I don't think so, see Remark ~\ref{rem:three-cases}.}
 
@@
 Once the log spin canonical divisor has at least two stacky points, the argument proceeds as in Case 2a.
-
-\todo{Peter: Maybe you should mention something about how the exceptional cases differ, and how this affects the argument? Aaron: Ok, I did it imprecisely. Is this better?}
 \end{proof}
@@
 	\end{tabular}
-	\caption{Generators and Relations for Genus 0 Non-effective Base Cases}
+	\caption{Generators and Relations for Genus 0 Base Cases}
 	\label{table:g-0-base-cases-degrees}
 \end{table}
-\todo{Peter: Can we make a better description for the table above? Robin: Think of one then.}
 
@@
 \end{tabular}	
-	\caption{Checking \ref{custom:Ad-iii} for Genus 0 Non-Effective Base Cases}
+	\caption{Checking \ref{custom:Ad-iii} for Genus 0 Base Cases}
 	\label{table:g-0-base-cases-admissibility}
@@
 			divisor $L \in \di X$, can one write down a set of minimal 
-			generators and minimal relations for $R_\halfcan$? If so, can one give the 
-			generic ideal of $R_\halfcan$ or the generic initial ideal of $R_\halfcan$, as 
-			defined in Voight and Zureick Brown \cite[Definition 2.2.7]
-			{vzb:stacky}?
+			generators and minimal relations for $R_\halfcan$?
 		\end{question}
-\todo{Aaron: Peter, you said you wanted to take out the question on generic ideals, but I think it might be interesting to think about. Why do you want to remove it?}
 
@@
 		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors translate to rings of fractional weight ($\frac{2}{n}$) modular 
-		forms. As defined in Adler and Ramanan (in the passage immediately 
-		following \cite[Corollary 24.5]{adler:moduli}), a {\bf modular form 
+		divisors translate to rings of fractional weight $\frac{2}{n}$ modular 
+		forms. A {\bf modular form 
 		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
 		line bundle $\eta$ so that there exists a line bundle $\gamma$ with 
-		$\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^
-		1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an 
-		explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. 
-		Fractional modular forms also make an appearance in Milnor \cite
-		[$\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor 
-		shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e
-		_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of 
-		fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3
-		^{e_3} = 0$.  
-\todo{Peter: I don't know if it is so worth while giving an explicit definition and precisely defining the work already done.
-A general outline might suffice and be easier/shorter to read.
-Aaron: I have a feeling we should define it, but I'm ok with removing the last two sentences.}
-
-		This motivates the following question:
-
-\todo{Peter: Would this be better as a conjecture? Aaron: I don't have an actual conjecture. I'm not sure what the bounds would be.}
+$\gamma^{\otimes a} \cong \eta$
+ and 
+ $\gamma^{n} \cong \Omega_{X(p)}^1$.
+		For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
+		[$\mathsection$ 6]{milnor:fractional-weight}.
+
 \begin{question}
@@
 		\end{question}
-\todo{Peter: I don't like a finite list of exceptions.
-The list contains infinitely many non-isomorphic stacky curves.
-Finite family might also be imperfect.
-Can we say except when $g=2$ (I believe there will be infinitely many counterexamples there) or it lies in a finite list of exception?
-Do we believe that to be true?
-Aaron: Since we haven't really thought about this conjecture, I'm not comfortable making it a conjecture.
-I switched it back to a question.
-Is that ok?
-Robin: Perhaps give reference to Reid's characterizations?}
 		\begin{rem}\label{rem:reduce-3,6}

### 2015-07-06 beamer_stacky/11_UNC_canonical-stacky/Title.tex
add VZB beamer slides

\begin{document}
\title [The canonical ring of a stacky curve]{The canonical ring of a stacky curve}

%\subtitle{Based on Beamer version 3.06}
\author[David Zureick-Brown and John Voight]{David Zureick-Brown (Emory University)
\\ John Voight (Dartmouth)}

%\institute[Emory University]{Emory University\\ Slides available at \url{http://www.mathcs.emory.edu/~dzb/slides/}}
%\institute{Emory University, Department of Mathematics and Computer Science}
\date[Nov 8, 2014]{Automorphic Forms and Related Topics\\ 
Fall Southeastern Sectional Meeting\\
 University of North Carolina at Greensboro, Greensboro, NC\\
\mbox{}\\
Nov 8, 2014\\
\mbox{}\\
% \tiny{Slides available at \url{http://www.mathcs.emory.edu/~dzb/slides/} }
}

\begin{frame}[plain]
  \titlepage
\end{frame}

%%% Use M-x ibuffer t U to replace

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-06 beamer_stacky/11_UNC_canonical-stacky/slides/slide00210.tex
add VZB beamer slides

\begin{frame}{Petri's theorem}

    Let $C$ be non-hyperelliptic, non-trigonal, not a plane quintic.

  \begin{theorem}[Enriques-Noether-Baggage-Petri]
  The canonical ring $R_C$ is generated in degree 1 with relations in degree 2.
  \end{theorem}

  \begin{remark}
    \begin{enumerate}
    \item For $C$ trigonal or a plane quintic $R_C$ is generated in degree 1 with relations in degrees 2 and 3
    \item (unless $g(C) = 3$, which has a single relation in degree 4)
    \item For $C$ hyperelliptic, there are generators in degrees 1,2, relations in degrees up to 4.
    \end{enumerate}
  \end{remark}

\end{frame}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-06 beamer_stacky/11_UNC_canonical-stacky/slides/slide00220.tex
add VZB beamer slides

\begin{frame}{Log Petri's theorem}

    Let $C$ be a curve and $\Delta$ a log divisor.

  \begin{theorem}[Voight, ZB]
  The log canonical ring $R_C$ is generated in degree at most 3 with relations in degree at most 6.
  \end{theorem}

  \begin{remark}
    Lots of exceptional cases if $0 < \deg \Delta  \leq 2$.
  \end{remark}

  \begin{remark}[Things stabilize]
    \begin{enumerate}
    \item Generators in degree 1 with relations in degree 2,3 if
      $\Delta = 3$
    \item   
     (Mumford.) Generators in degree 1 with relations in degree 2 if $\Delta \geq 4$
   \end{enumerate}
 \end{remark}

\end{frame}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-06 beamer_stacky/11_UNC_canonical-stacky/slides/slide00330.tex
add VZB beamer slides

\begin{frame}{Main theorem}

  \begin{theorem}[Voight,ZB]
Let $(\XX,\Delta)$ be a tame log stacky curve with signature $(g;e_1,\ldots,e_r;\delta)$ over a field $k$, and let $e=\max(1,e_1,\dots,e_r)$.  Then the canonical ring 
\[ R(\XX,\Delta) = \bigoplus_{d=0}^{\infty} H^0(\XX,\Omega(\Delta)^{\otimes d}) \] 
is generated as a $k$-algebra by elements of degree at most $3e$ with relations of degree at most $6e$.

  \end{theorem}

  \begin{remark}
    Moreover, if $2g-2+\delta \geq 0$, then $R(\XX,\Delta)$ is generated in degree at most $\max(3,e)$ with relations in degree at most $2\max(3,e)$.
  \end{remark}

\end{frame}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-06 beamer_stacky/11_UNC_canonical-stacky/README.sh

@@ -1,0 +1,84 @@
+
+
+
+
+## code to replace a string in every file in a folder
+
+
+
+NEWFILENAME=test
+
+## run this in the main folder and in the slides folder
+for file in *tex; do sed 's_beamerTemplate_'$NEWFILENAME'_g' $file > temp && mv temp $file; done
+
+
+
+
+## run this if necesary
+for file in *tex; do sed 's_../beamerTemplate_beamerTemplate_g' $file > temp && mv temp $file; done
+
+
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex ;
+  echo "% Title of SECTION" >> slides.tex ;
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo "   \input{slides/slide001}     %% {Title of  SLIDE}" >> slides.tex;
+  echo " "
+
+for n in {2..9}; do
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex ;
+  echo "% Title of SECTION" >> slides.tex ;
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo "   % \input{slides/slide00"$n"}     %% {Title of  SLIDE}" >> slides.tex;
+  echo " "
+done
+
+for n in {10..20}; do
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo "% Title of SECTION" >> slides.tex;
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo " %  \input{slides/slide0"$n"}     %% {Title of  SLIDE}" >> slides.tex;
+  echo " "
+done
+
[…]

### 2015-07-06 beamer_stacky/11_UNC_canonical-stacky/prepslides.sh

@@ -1,0 +1,80 @@
+## code to replace a string in every file in a folder
+
+
+
+NEWFILENAME=test
+
+## run this in the main folder and in the slides folder
+for file in *tex; do sed 's_beamerTemplate_'$NEWFILENAME'_g' $file > temp && mv temp $file; done
+
+
+
+
+## run this if necesary
+for file in *tex; do sed 's_../beamerTemplate_beamerTemplate_g' $file > temp && mv temp $file; done
+
+
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex ;
+  echo "% Title of SECTION" >> slides.tex ;
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo "   \input{slides/slide001}     %% {Title of  SLIDE}" >> slides.tex;
+  echo " "
+
+for n in {2..9}; do
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex ;
+  echo "% Title of SECTION" >> slides.tex ;
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo "   % \input{slides/slide00"$n"}     %% {Title of  SLIDE}" >> slides.tex;
+  echo " "
+done
+
+for n in {10..20}; do
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo "% Title of SECTION" >> slides.tex;
+  echo "%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%" >> slides.tex;
+  echo " %  \input{slides/slide0"$n"}     %% {Title of  SLIDE}" >> slides.tex;
+  echo " "
+done
+
[…]

### 2015-07-07 beamer_stacky_curves/11_UNC_canonical-stacky/slides.tex
rename folders, import surfaces files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Modular forms
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \input{slides/slide00100.tex}     %% {Modular forms}
     \input{slides/slide00101.tex}     %% {Ring of Modular forms}
     \input{slides/slide00102.tex}     %% {Ring of Modular forms}
   \input{slides/slide00120.tex}     %% {Rustom's conjectures}
   \input{slides/slide00110.tex}     %% {Main theorem}
   \input{slides/slide00130.tex}     %% {Kodaira--Spencer}
  \input{slides/slide00140.tex}     %% {Example: $X_0(11)$ (fundamental domain))}
   \input{slides/slide00230.tex}     %% {Example of $X_0(11)$}

% \textbf{new slide -- picture for $X_0(11)$.}
% \textbf{new slide -- picture for $X(1)$.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classical Geometry of curves
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \input{slides/slide00200.tex}     %% {Canonical map/ring}
     % \input{slides/slide00201.tex}     %% {log Canonical map/ring}
     % \input{slides/slide00130.tex}     %% {Kodaira--Spencer} (slide from before)
   \input{slides/slide00210.tex}     %% {Petri's theorem}
   \input{slides/slide00220.tex}     %% {Log petri theorem}
   \input{slides/slide00221.tex}     %% {Log petri theorem, corollary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stacky curve
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \input{slides/slide00130.tex}     %% {Kodaira--Spencer}
   \input{slides/slide00240.tex}     %% {Fundamental Domain for X(1)}
     \input{slides/slide00241.tex}     %% {Example to show they don't agree} 
   \input{slides/slide00300.tex}     %% {Fractional divisors}
   \input{slides/slide00310.tex}     %% {Floors}
   \input{slides/slide00320.tex}     %% {Example: X(1)}
   \input{slides/slide00330.tex}     %% {Main theorem}
   \input{slides/slide00340.tex}     %% {Final comments}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-07 beamer_stacky_curves/11_UNC_canonical-stacky/slides/slide00120.tex
rename folders, import surfaces files

\begin{frame}{Rustom's conjectures (2012)}

  \begin{conjecture}[Rustom]
The $\C$-algebra $M(\Gamma_0(N))$ is generated in weight at most 6 with relations in weight at most 12.    
  \end{conjecture}

-- This was proved by Wagreich in 1980/81.

\vspace{6pt}

  \begin{conjecture}[Rustom]
The $\Z\left[1/6N\right]$-algebra $M(\Gamma_0(N), \Z\left[1/6N\right])$ is generated in weight at most 6 with relations in weight at most 12.    
  \end{conjecture}

-- $M_k(\Gamma_0(N),R)$ consists of forms with $q$-expansion in $R\llbracket q\rrbracket$.

\end{frame}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-07 stacky_surface_write_up/surface-write-up.tex
rename folders, import surfaces files

--- 2015-07-03 stacky_write_up/spin_cring.tex
@@
 \newcommand\sssec{\subsubsection}
-\newcommand\BH{{\mathbb H}}
-\newcommand\BN{{\mathbb N}}
-\newcommand\BC{{\mathbb C}}
-\newcommand\BF{{\mathbb F}}
-\newcommand\BR{{\mathbb R}}
-\newcommand\BQ{{\mathbb Q}}
-\newcommand\BP{{\mathbb P}}
-\newcommand\BZ{{\mathbb Z}}
-\newcommand\BA{{\mathbb A}}
+\newcommand\bh{{\mathbb H}}
+\newcommand\bn{{\mathbb N}}
+\newcommand\bc{{\mathbb C}}
+\newcommand\bbf{{\mathbb F}}
+\newcommand\br{{\mathbb R}}
+\newcommand\bq{{\mathbb Q}}
+\newcommand\bp{{\mathbb P}}
+\newcommand\bz{{\mathbb Z}}
+\newcommand\ba{{\mathbb A}}
 
@@
 \newcommand\coker{\text{coker}}
-\newcommand\spec{\text{Spec }}
-\newcommand\proj{\text{Proj }}
 \newcommand\gal{\mathrm{Gal}}
@@
 \newcommand{\halfcan}{L}
-\DeclareMathOperator{\Supp}{Supp}
+\DeclareMathOperator{\supp}{Supp}
 \DeclareMathOperator{\initial}{in_\prec}
@@
 \DeclareMathOperator{\newspan}{span}
+\DeclareMathOperator{\proj}{Proj}
+\DeclareMathOperator{\spec}{Spec}
 \captionsetup[table]{belowskip = 4pt}
@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
-$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
-linear transformations, such that $\Gamma \backslash \BH$ has finite area.
-We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best
-ways to understand the ring of modular forms is to give a
-presentation as a quotient of a polynomial ring.
-%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
-To do so, it is useful to have a bound on the
-degrees in which the generators and relations can occur. In the
-special case that $\Gamma$ has no odd weight modular forms, Voight
-and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
-We extend their result to all Fuchsian groups $\Gamma$ in the main
-theorem of this work.
-
-We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
-For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
-\backslash \BH$ is a Riemann Surface over $\BC$. 
-$\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
-compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
-cusps, with associated divisor of cusps $\Delta$.
-
-In order to find generators and relations for $M(\Gamma)$, we
-translate the seemingly analytic question of understanding the ring
-of modular forms into the algebraic category, using a
-generalization of the GAGA principle. By \cite[Proposition 6.1.5]
-{vzb:stacky}, there is an equivalence of categories between orbifold
-curves and log stacky curves over $\BC$. Hence, for the remainder
-of the paper, we will work in the algebraic category.
-
-Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$.
-It is well known that the canonical sheaf $\Omega _X,$ with
-associated canonical divisor $K_X$, determines the {\bf canonical
-map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
-ring} is defined to be
-\begin{align*}
-	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
-\end{align*}
-
-\noindent
-with multiplication structure corresponding to tensor product of
-sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$. When $g \geq 2$, Petri's theorem gives generators
-and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
-is generated in degree 1 with relations in degree 2, as shown in
-\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
-\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
-geometric consequence that all such canonically embedded curves are
-scheme theoretically cut out by degree 2 equations.
-
-Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
-Petri's theorem in the direction of stacky curves equipped with
-log divisors. For a stacky curve $\sx$ with coarse space $X$ and
-stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
-with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$, we define
-
-\[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
-	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
-\]
-
-Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
-where $\Delta \in \di X$ is a log divisor and $2\halfcan \sim K_X +
-\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
-study in this paper is the {\bf log spin canonical ring} of $(\sx,
-\Delta, \halfcan),$ notated as
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, \lfloor d \halfcan \rfloor).
-\end{align*}
-
-\noindent
-A brief overview of stacky curves, log divisors, and log spin
-canonical rings is given in Subsection
-~\ref{ssec:stacky-background}.
-
-%If $X$ is a curve, \todo{why do you start with a curve and then
-%move to a stacky curve? shouldn't it be the opposite order?} then
-%we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
-%and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
-%\ldots, P_r$ with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{
-%\geq 2}$ if 
-%\[
-	%\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
-	%P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	%\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
-%\]
-
-%A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
-%$\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
-%\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
-%The central object of study in this paper is the {\bf log spin
-%canonical ring} of $(\sx, \Delta, \halfcan)$ is
-%\begin{align*}
-	%R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
-%\end{align*}
-
-In particular, we bound the degrees of generators and relations of a
-log spin canonical ring. Let
-$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
-e_r; \delta)$. The application of O'Dorney's work to log spin
-canonical rings gives a weak bound in the case $g = 0$ in
-terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
-{dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
-and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
-\cite[Corollary 10.4.6]{vzb:stacky}.
-Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.
-
-These bounds are far from tight and do not collectively
-cover all cases in all genera. The main theorem of this paper
-gives significantly tighter bounds for any log spin canonical ring on a log spin curve.
-
-\begin{thm}
-\label{thm:main}
-Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
-field $k$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
-e_r; \delta)$.
-
-Then the log spin canonical ring is generated as a $k$-algebra by 
-elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
-relations generated in degrees at most $2e$,
-so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as given in Table ~\ref{table:g-1-exceptional} for
-signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
-signatures with $g = 0$.
-\end{thm}
-
-\begin{rem}
-\label{rem:main-weaker-assumptions}
-In fact, the proof of Theorem ~\ref{thm:main} holds with $\Delta$ replaced by an arbitrary effective divisor of the coarse space.
- Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
-is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
-\end{rem}
-
-Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.
-In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the genus $g \geq 2$ case we deduce base cases from more general arguments.
-\begin{rem}
-\label{rem:explicit-generators}
-The proofs of the main theorems in the low genus cases not only
-obtain bounds on the degrees of the generators and relations, but
-also yield explicit systems of generators and an explicit initial ideal of
-relations. Furthermore, our proof of the genus $g \geq 2$ case also
-provides an inductive procedure for explicitly determining the 
-generators and initial ideal of relations of log spin canonical
-rings. Many explicit systems of generators and relations for curves of genus $2 \leq g \leq 15$ are
-detailed in interesting examples by Neves
-\cite[Section III.4]{neves:halfcan}. 
-\end{rem}
-\begin{rem}
-The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
-Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
-Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-\end{rem}
-
-Combining the main theorem of this paper, Theorem ~\ref{thm:main} with the main theorem from Voight and Zureick-Brown ~\cite
-[Theorem 1.4]{vzb:stacky} and a minor Lemma \cite[Lemma 10.2.1]{vzb:stacky}
-we have the following application to
-rings of modular forms. 
-%Note that the lemma from Voight and Zureick-
-%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
-%from the classical work of Kodaira--Spencer
-%\cite{kodaira-spencer:deformations}.
-
-\begin{cor}
-\label{cor:main-mod-forms}
-Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
-associated to $\Gamma \backslash \BH$ with signature $\sigma
-= (g; e_1, \ldots, e_r; \delta)$.
-
-If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
-forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
-degree at most $6 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $12 \cdot \max(3, e_1, \ldots, e_r)$.
-
-If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
-ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
-by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
-relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
-e_r)$ so long as $\sigma$ does not lie in a finite list of
-exceptional cases which are listed and described in Table
-~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
-Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
-\end{cor}
-
-\begin{rem}
-\label{rem:factor-two}
-In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
-bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
-~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively.
-Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two, because our grading convention on $\bigoplus_k M_k(\Gamma)$ differs from that of Voight and Zureick-Brown by a factor of 2.
-\end{rem}
-
-The remainder of the paper will be primarily devoted to proving
-Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct first on the number of stacky points and then on the stabilizer order of those points.  To this end, we first review important background in
-Section ~\ref{sec:background}; providing essential examples in Section \ref{sec:examples}; develop various inductive
-tools in Section ~\ref{sec:induction}; and prove Theorem ~\ref{thm:main} in genus $g\ge 2$, genus $g=1$, and genus $g=0$ in Sections ~\ref{sec:g-high},
-~\ref{sec:g-1}, and ~\ref{sec:g-0} respectively.  
-Finally, in Section
-~\ref{sec:further-questions}, we pose several questions for future
-research.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Background}
-\label{sec:background}
-Here we collect various definitions and notation that will be
-used throughout the paper. Many of the conventions come from existing
-literature. For basic references on the statements and definitions
-used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
-Saint-Donat \cite{saint-donat:proj}, Arbarello--Cornalba--Griffiths--Harris 
-\cite[Section III.2]
-{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
-Chapter 5]{vzb:stacky}.
 
-For the remainder of this paper, fix an algebraically closed field $k$.
-This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closure.
+\ssec{Notation}
 
-\ssec{Stacky Curves and Log Spin Canonical Rings}
-\label{ssec:stacky-background}
-We begin by setting up the notation for stacky curves and canonical rings.
-Wherever possible, we opt for a more elementary scheme-theoretic approach, instead of a stack-theoretic one.
-See Remark ~\ref{rem:stack-formalism} for more details.
+Write
+\begin{align*}
+	D = \sum_{i=1}^{n}\alpha_i D_i.
+\end{align*}
+where $\alpha_i \in \bq.$
 
-\begin{defn}
-\label{defn:stacky-curve}
-A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
+\section{Canonical Rings on Projective Space}
+In this section, we bound the degrees of generators and relations for divisors on $\bp^m$, for all $m \geq 1$. The $n = 1$ case was covered in \cite{dorney:canonical}.
 
-\end{defn}
+\ssec{Preliminaries on Projective Space}
 
-\begin{rem}
-\label{rem:stack-formalism}
-Stacky curves may be formally defined in the language of stacks, as
-is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
-Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
-Behrend and Noohi \cite{behrend-noohi:uniformization}.
+For the remainder of this section, we shall fix $m \geq 1$ and choose an isomorphism $\bp^m \cong \proj V$ so that $x_0,\ldots, x_m$ form a basis for $V$.
+Through the rest of this section, we will think of $x_i$ as a rational section of $H^0(\bp^m, \sco_{\bp^m})$ of degree 1.
 
-The results of this paper can be easily couched in terms of the language of stacks.
-If one works over an arbitrary field $k$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.
-the residue field of each
-of the stacky points is separable.
+Write
+\begin{align*}
+	D = \sum_{i=0}^{n}\alpha_i D_i.
+\end{align*}
+where $\alpha_i \in \bq$ and $\deg D_i = d_i$.
+Let $f_i$ be cartier divisors such that $D_i = V(f_i)$.
+We shall further assume that among there exist functions $f_0,\ldots, f_{m+1}$ form a basis for degree one rational functions on $\bp^m$.
 
-With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
-of schemes.
-\end{rem}
-
-\begin{defn}
-\label{defn:div-ex}
-Let $\sx$ be a stacky curve over $k$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
-P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
-Then, we notate
-\[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
-	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
-\]
-\end{defn}
-
-We can equip stacky curves with a log divisor $\Delta$ that is a 
-sum of distinct points each with trivial stabilizer. 
-A divisor
-$\Delta$ of this form is called a \textbf{log divisor}. We use
-$\delta := \deg \Delta$ to refer to the degree of the log divisor.
-If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
-\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
-
-\begin{defn}
-\label{defn:divisor-floor}
-If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
-with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
-\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor P_i$.
-\end{defn}
-
-A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
-called a \textbf{log stacky curve} and the study of their
-canonical rings is the main focus of the work by Voight and Zureick-
-Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
-spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
-is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
-\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
-\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
-\textbf{log spin canonical divisor} on $(\sx, \Delta)$. Throughout the paper, we use
-the notation $\halfcan_X := \lfloor L \rfloor.$ to refer to the log spin
-canonical divisor (also known as the half-canonical divisor, 
-semi-canonical divisor, or theta characteristic) associated to the
-coarse space $X$ of $\sx.$  (i.e. $\halfcan_X$ is a divisor such
-that $2\halfcan_X \sim K_X + \Delta$). 
-We define $H^0$ of a stacky divisor as follows:
-
-\begin{defn}
-\label{defn:h0-stacky}
-Let $\sx$ be a stacky curve with coarse space $X$.
-If $D \in \di \sx$ is a Weil divisor, then we define
-
-\[
-	H^0(\sx, D) := H^0(X, \lfloor D \rfloor).
-\]
-\end{defn}
-
-\begin{rem}
-Although Definition ~\ref{defn:h0-stacky} may seem fairly ad hoc, it is naturally motivated in the context of stacks.
-See Voight and Zureick-Brown \cite[Lemma 5.4.7]{vzb:stacky} for a proof that Definition ~\ref{defn:h0-stacky} is equivalent to the stack-theoretic description.
-\end{rem}
-
-\begin{defn}
-\label{defn:log-spin-canonical-ring}
-The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
-\[
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan).
-\]
-\end{defn}
-
-\noindent
-When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
-represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
-:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D))$.
-If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
-graded component of $R$.
-
-\begin{rem}
-\label{rem:odd-denom}
-Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
-\[
-	\halfcan = \sum_{i = 1}^{r} \subhalf{e_i} P_i + \sum_{i = 1}^{s} a_i Q_i
-\]
-
-\noindent
-where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
-that $\halfcan \in \di \sx$: 
-if some $e_i$ were even,
-then $\frac{e_i - 1}{2e_i}$ would be in reduced form implying $\halfcan \notin \di \sx$.
-\end{rem}
-
-\begin{rem}
-\label{rem:delta-not-1}
-Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta$
-is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
-\rfloor = \deg \Delta + 2(g-1).$
-In particular, we shall often use $\deg \Delta \neq 1$.
-\end{rem}
-
-\ssec{Definition of Saturation}
-
-We define the notion of the saturation of a divisor, as can be found in
-Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
-
-\begin{defn}
-Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
-is the monoid
-\[
-	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}.
-\]
-\end{defn}
-
-\begin{defn}
-\label{defn:sat}
-The \textbf{saturation} of a monoid $M \subseteq \BZ_{\geq 0}$,
-denoted $\sat(M)$, is the smallest integer $s$ such that $M
-\supseteq \BZ_{\geq s}$, if such an integer exists.
-\end{defn}
-
-\begin{rem}
-For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the saturation of $D.$
-\end{rem}
-
-\ssec{Monomial Ordering}
-\label{ssec:monomial-order}
-Here we give a brief overview of the three monomial orderings
-that we use. For further reference on monomial orderings,
-initial ideals, and Gr\"{o}bner bases, see Eisenbud
-\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--O'Shea
-\cite[Chapter 2]{cls:ideals-varieties-algorithms}.
-
-\begin{defn}
-\label{defn:monomial-degree}
-Let $k[x_1$, $\ldots$, $x_n]$ be a graded polynomial
-ring with $\deg x_i = d_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
-k[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
-we define the {\bf degree} of $\alpha$ to be
-\[
-	\deg \alpha := \sum_{i = 1}^{n} d_i f_i.
-\]
-\end{defn}
-
-\begin{defn}
-\label{defn:grevlex}
-The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
-monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
-\succ_{\text{grevlex}} \beta$ if either
-
-\begin{equation}
-	\deg \alpha = \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' = \deg \beta
-\end{equation}
-or
-\begin{equation}
-\label{eqn:grevlex-tie}
-	\deg \alpha = \deg \beta \text{ and }	f_i < f_i' \text{ for
-	the	largest } i \text{ such that } f_i \neq f_i'.
-\end{equation}
-\end{defn}
-
-\begin{rem}
-Note that the ordering of the variables matters in Equation
-~\ref{eqn:grevlex-tie}.
-\end{rem}
-
-Our inductive arguments in Section ~\ref{sec:induction} will
-usually have an inclusion $R \supseteq R'$ of log spin canonical
-rings such that $R_\halfcan$ is generated by elements $x_{i}$ and $R$
-is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
-natural to consider term orders which treat these sets of variables
-separately.
-
-\begin{defn}
-\label{defn:block-order}
-The \textbf{block term order} is defined as follows. Let $k[y_{1}, \ldots, y_{m}]$ and $k[x_{1}, \ldots,
-x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = d_i.$ Further assume we are given existing term
-orders $\prec_y$ and $\prec_x$. Let $\alpha :=
-\prod_{j = 1}^{m} y_{j}^{h_i}$ $\prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
-\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $k[y_{1},
-\ldots, y_{m}] \otimes$ $k[x_{1}, \ldots, x_{n}]$.
-Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
-part of $\alpha$ in $k[y_{1}, \ldots, y_{m}]$ and
-likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
-
-In the \textbf{(graded) block} (or \textbf{elimination}) term
-ordering on $k[y_{d_1', 1}, \ldots, y_{d_m', m}] \otimes k[x_{d_1, 1},
-\ldots, x_{d_n, n}]$, we define $\alpha \succ \beta$ if
-  \begin{enumerate}
-	\item[(i)] $\deg \alpha  > \deg \beta$ or
-  \item[(ii)] $\deg \alpha = \deg \beta$ and $\alpha_y \succ_y \beta_y$ or
-	\item[(iii)] $\deg \alpha = \deg \beta$ and $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$.
-  \end{enumerate}
-\end{defn}
-
-Now we give brief definitions of initial terms and Gr\"{o}bner
-bases. These will be used in the proofs of the inductive lemmas
-in Section ~\ref{sec:induction} as well as in the proof of Theorem
-~\ref{thm:main}.
-
-\begin{defn}
-\label{defn:initial-term}
-Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}]$, 
-with $\deg x_i = d_i$,
-and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
-polynomial. The \textbf{initial term} $\initial(f)$ of $f$
-is the largest monomial in the support of $f$ with respect to
-the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
-\end{defn}
-
-\begin{defn}
-\label{defn:initial-ideal}
-Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
-$x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
-the ideal generated by the initial terms of homogeneous polynomials
-in $I$:
-\[
-	\initial(I) := \langle \initial(f) \rangle_{f \in I}
-\]
-\end{defn}
-
-%Furthermore, we will use Gr\"{o}bner bases, which are bases
-%for these initial ideals and have many useful properties.
-
-\begin{defn}
-\label{defn:grobner-basis}
-Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
-$x_{n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
-\textbf{standard basis} for $I$, is a set of elements in $I$
-such that their initial terms generate the initial
-ideal of $I$.
-\end{defn}
-
-\ssec{Admissibility}
-
-In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin canonical divisors.
-
-One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that 
-%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
-	we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.
-
-\begin{defn}
-\label{def:order-sup}
-If $z$ is a rational section of $\sco(D)$ denote the order of
-zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
-
-\begin{defn}
-\label{defn:admissible}
-Let $(\sx', \Delta, L')$ be a log spin
-curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
-\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
-
-\[
-\chi_J(i) = \begin{cases}
-	1, &\text{ if }i \in J\\
-	0, &\text{ otherwise. } 
-\end{cases}
-\]
-
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan',J)$
-to be {\bf admissible} if $R'$ admits a presentation
-\begin{align*}
-	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
-\end{align*}
-
-\noindent
-with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
-three conditions hold:
-\begin{enumerate}
-	\item[\customlabel{custom:Ad-i}{(Ad-i)}] First, 
-		\begin{align*}
-		\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
-			= \frac{e_i'- 1}{2}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-ii}{(Ad-ii)}] Second, every generator $z 
-		\in \{x_1, \ldots, x_m\} \cup \{y_{j, e_i'}: j\in J - \{i\} \}$ 
-		satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-iii}{(Ad-iii)}] Third, we have
-		\begin{align*}
-			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
-		\end{align*}
-		where
-		\begin{align*}
-			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
-			\mid e_i - e_j'\}.
-		\end{align*}
-\end{enumerate}
-\end{defn}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Examples %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Examples}
-\label{sec:examples}
-
-In this section, we work out several examples of computing presentations for spin canonical rings.
-In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}.
-In addition to providing intuition for the lemmas of Section ~\ref{sec:induction}, these examples also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
-
-\begin{example}
-\label{eg:base-1-0}
-Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
-Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
-\end{example}
-
-\begin{example}
-\label{eg:base-0-377}
-Let $(\sx',0, \halfcan')$ be a log spin curve with signature $\sigma =
-(0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are
-distinct points. In this example, we will exhibit a minimal
-presentation for $R' = R(\sx',0, \halfcan')$ and show the triple
-$(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
-Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
-\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
-
-By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
+\begin{prop}
+\label{prop:pm-span-and-basis}
+The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ so that 
 \begin{align}
-\label{eqn:noether-377}
-	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor)
+\label{align:pm-span}
+\sum_{i=0}^{n} c_i \cdot d_i \cdot f_i = 0 & \text{ and } &c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
-
-\noindent
-is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
-\geq 0$. It is fairly easy to see, by use of Riemann--Roch, that
-$s := \sat(\Eff(\sigma)) = 5$. Then the map in
-~\eqref{eqn:noether-377} is surjective when $d \geq 21 + s = 26$
-(i.e. $R'$ is generated up to degree 25).
-
-For $d = 0, 1, 2, \ldots$ we have
-\[
-	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
-
-To show that these generate all of $R'$, we need to show that all
-$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
-(taking saturation into account) to see that
-
-\begin{align*}
-	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
-	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
-	\bmod 7
-\end{align*}
-
-\noindent
-are surjective. This reduces the problem to checking generation
-in the degrees of the exceptions $d \in \{8, 12, 21\}$.
-Checking the remaining cases via pole degrees shows that
-these degrees are also generated in lower degrees,
-so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
-
-Now, we check the admissibility of $(\sx', L' ,J),$ where $J = \{2, 3\}$. By relabelling the
-variables if necessary, we can assume that $x_{7, 1}$ corresponds
-to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
-correspond to the generator with maximal pole order at $P_3$. Use
-the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
-$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
-pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
-in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
-generators lying below the line as seen in Figure ~\ref{fig:377}
-(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
-(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
-and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
-$x_{7, 2}$ respectively).
-
-\begin{figure}[H]
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
-\label{fig:377}
-\end{figure}
-
-Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
-$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
-Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
-$(\sigma, \sx', J)$ is admissible.
-
-%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
-%represent the pole orders of $x_i$ at each point. Then these generators
-%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
-%respectively.
-
-We can directly see that the relations are given in degrees $10$
-and $14$. In particular, we have relations
-\begin{align*}
-	&a_1 x_{5, 1}^2 + a_2 x_{7, 2} x_{3, 1} + a_3 x_{7, 1} x_{3, 1} = 
-	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
-	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
-\end{align*}
-
-\noindent
-and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
-have that
-\[
-	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
-\]
-
-\noindent
-However, $x_{7, 2} x_{3, 1}$ has pole orders $(3, 3, 4)$ and
-$x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ so their
-coefficients must be zero for this equality to hold. We have a
-similar pole order consideration in forcing $b_1$ to be nonzero.
-
-Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
-$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
-ideal of $I$ is
-\[
-	\initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
-\]
-
-\noindent
-since $a_1$ and $b_1$ are nonzero.
-
-To demonstrate that these two relations generate all 
-relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
-all degrees $d \geq 0$. In particular,
-
-\begin{align*}
-	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_d &=
-	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_d \\
-	&= \dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
-\end{align*}
-\noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left(k[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
-\rangle\right)_d$ can be checked by looking at the $k$-basis at each degree
-$d$.
-
-Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
-initial ideal $\initial(I)$ generated by quadratics under grevlex
-with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
-%These quadratics must also determine minimal generators for $I$ by
-%Lemma ~\ref{lem:minimal_quadratic}.
-Thus, $R'$ is generated up to degree $e = 7$ with relations up to
-degree $2e = 14$, as desired.
-
-%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
-%since $e_i = 9 > e$ for all $i \in J$.
-\end{example}
-
-\begin{example}
-\label{eg:base-1-33}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx', \halfcan', \{1,2\})$ is admissible.
-
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
-Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
-
-Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
-The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
-
-We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
-We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{custom:Ad-i} holds.
-We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
-Here, by construction
-$$
-\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4
-\end{cases}.$$
-Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
-\end{example}
-
-\begin{rem}
-\label{rem:base-0-377}
-Examples ~\ref{eg:base-0-377} and \ref{eg:base-1-33} are used as inductive base cases in the genus 0 and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
-\end{rem}
-
-\begin{example}
-\label{eg:exception-1-5}
-Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
- Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_L)_2$ be any nonzero element.
-We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
---Roch, $\dim_k (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
-element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
-if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0
-(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally,
-let $y_5 \in (R_\halfcan)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
-we claim there is some $\alpha \in k$ so that
-
-$$R_\halfcan \cong k[x_2 , y_3, y_5]/(y_3^4 - \alpha x_2 y_5^2).$$
-
-In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_\halfcan$.
-The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
-
-Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
-\end{example}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive lemmas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inductive Lemmas}
-\label{sec:induction}
-First we present several lemmas which provide the inductive steps
-for the proof of the main theorem: Theorem ~\ref{thm:main}. In
-Subsection ~\ref{ssec:add-points} we prove three lemmas which
-determine the generators and relations of $R_\halfcan = R_{\halfcan'
-+ \frac{\alpha }{\beta}P}$ from those of $R_{\halfcan'}$, where
-$\halfcan' \in \BQ \otimes \di X$ and $\frac{\alpha}{\beta} \in \BQ$. 
-In Subsection ~\ref{ssec:raise-orders}, we prove an inductive lemma
-allowing us to transfer information about the log spin canonical 
-ring of a stacky curve to those of stacky curves with stabilizer
-orders incremented by $2$ and fixed log divisor and stacky points.
-
-%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
-%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
-%spin canonical divisors.
-
-%However, before we can answer these general lemmas, it is useful
-%to prove a nice result about minimal generation of ideals of
-%relations.
-%
-%\todo{Include one of the following, if the first one, include a 
-%remark for quotient}
-
-%\begin{lem}
-%\label{lem:minimal_quadratic}
-%Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
-%generated in degree 1, is equipped with a monomial ordering $\prec$.
- %Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
-%rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
-%\ldots, f_j$, where $\initial(f_i) = x_i x_j,$ and no term of $f_i$
-%is of the form $x_k$. Then, the elements $f_i$ determine minimal
-%generators for $I$.
-%\end{lem}
-%\begin{proof}
-%Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
-%degree 1. Then,
-%\[
-	%\phi : k[x_1, \ldots, x_n] \rightarrow B
-%\]
-%\noindent
-%determines a map of rings, no longer necessarily graded. Consider
-%the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
-%\todo{This ordering isn't quite right. 
-%We need to preserve the ordering on quadratic terms}
-%By
-%assumption, the kernel $I$ is generated by elements whose initial
-%terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
-%\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
-%generators for $I$ must have at least $j$ elements. Since $f_1,
-%\ldots, f_j$ is such a set, it is minimal.
-%\end{proof}
-%
-%\begin{rem}
-%In particular, in the case of
-%\[
-	%\begin{tikzcd}
-		%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
-		%\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
-		%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	%\end{tikzcd}
-%\]
-%inducing
-%\[
-	%I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
-%\]
-%\todo{how do we make this proof?}
-%\end{rem}
-%\begin{lem}
-%\label{lem:minimal_quadratic}
-%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-%generated in degree 1 that are equipped with monomial ordering $\prec$.
-%Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
-%\[
-	%\begin{tikzcd}
-	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	%\end{tikzcd}
-%\]
-%Further suppose that $I'$ is generated over $I$ by elements $f_1,
-%\ldots, f_j$ as a $k$-vector space, where $\initial(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
-%is of the form $y_i$. Then, the elements $f_i$ determine minimal
-%generators for $I'$ over $I$.
-%\end{lem}
-%
-%\begin{proof}
-%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-%degree 1. Then,
-%\[
-	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-%\]
-%\[
-	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-%\]
-%
-%
-%\noindent
-%determines map of rings, no longer necessarily graded. 
-%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Gr\"{o}bner basis,
-%\[
-	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-%\]
-%so
-%\[
-	%\dim_k (I'/I)_2=j.
-%\]
-%This implies any set of
-%generators for $I$ must have at least $j$ elements. Since $f_1,
-%\ldots, f_j$ is such a set, it is minimal.
-%\end{proof}
-%
-%\begin{rem}
-%\label{rem:minimal_quadratic_trivial_case}
-%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
-%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
-%are $k$-minimal generators for $I'$ (over the trivial base vector
-%space). 
-%\end{rem}
-%With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
-
-\ssec{Adding Points}
-\label{ssec:add-points}
-%In this section, we prove various inductive statements under the following setup:
-%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d \in\BN$ and certain saturation conditions.
-Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
-Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
-\todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph?
-Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-Before proving three lemmas that allow us to inductively add points to the support of a log spin canonical divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
-This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
-
-\begin{lem}
-\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$, $\halfcan' \in \BQ$ $\otimes$ $\di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
-and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
-Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
-\begin{enumerate}
-\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T \succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
-\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
-\begin{align*}
-	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
-\end{align*}
-\end{enumerate}
-Then,
-\begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
-	+ \langle T \rangle.
-\end{align*}
-\end{lem}
+form a spanning set for $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
+of the form $u^d \cdot \prod_{i=1}^n f_i^{c_i} $ such that
+\begin{align}
+\label{align:pm-basis}
+c_i = -\lfloor d\alpha_i \rfloor & \text{ for } & i > m
+\end{align}
+form a basis for $H^0(\bp^m, dD)$ over $k$.
+\end{prop}
 \begin{proof}
-First, notice that $I'\subseteq I$ so 
-\[
-	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
-\]
-
-Now, let $f\in T$.
-Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
-This demonstrates that $\initial(I) \supseteq T$, and hence
-\[
-	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
-\]
-
-To complete the proof, it suffices to show the reverse inclusion holds.
-By (2), any polynomial $G\in k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
-Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
-Therefore,
-\[
-	\initial(I)\subseteq R_\halfcan-S.
-\]
-In particular, there are no monomials in $I$ with initial terms in $S$.
-Finally, note that
-\[
-	\initial(I) \cap k[x_1, \ldots, x_m] = \initial(I').
-\]
-
-By (3), every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
-\begin{align*}
-	\initial(I) & \subseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
-\end{align*}
+By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
+~\eqref{align:pm-span} lie in $H^0(\bp^m,dD)$.
+To complete the proof, it suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form a basis of $H^0(\bp^m,dD)$.
+Note that there $\binom{m+ \lfloor dD \rfloor }{m}$ functions satisfying condition ~\eqref{align:pm-basis}.
+However we know $h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show that those functions satisfying condition ~\eqref{align:pm-basis} are independent.
+This follows from the assumption that $f_0,\ldots, f_n$ form a basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $ monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor $ rational functions.
 \end{proof}
 
-To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.
-The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
-\begin{defn}
-\label{defn:graded-p-lex}
-Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.
-Then we have a map $\phi: k[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
-If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows.
-If $f=\prod_{i=1}^m {z_i}^{q_i}$ and $g=\prod_{i=1}^m {z_i}^{r_i}$ with $f \neq g,$ then $f\prec g$ if one of the following holds:
-\begin{enumerate}
-\item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord_P(f) < -\ord_P(g)$
-\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i > r_i$ for the largest $i$ such that $q_i\ne r_i$
-\end{enumerate}
-\end{defn}
+\ssec{One point on Projective Space}
 
-\begin{rem}\label{rem:graded-P-lex-independent-of-line-bundle}
-Observe that Definition \ref{defn:graded-p-lex} remains the same if we replace $-\ord_P$ with $-\ord_P^{L'}$ for any divisor $\halfcan'$ of $X$.
-\end{rem}
-
-\noindent One can easily verify graded $P$-lex is a monomial ordering in the sense defined in Cox--Little--O'Shea \cite[Chapter 2, $\mathsection$ 2, Definition 1]{cls:ideals-varieties-algorithms}.
-
-We are almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
-\BQ$-divisor.
-Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
-Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$.
-Before stating Lemma ~\ref{lem:sat-1}, we recall some notation from O'Dorney \cite{dorney:canonical}.
-
-\begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c \in \BN, d \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
-\end{defn}
-Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a finite sequence
-\[
-	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
-\]
-Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
-
-\begin{figure}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
-Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
-\end{figure}
-
-We can now prove our first lemma for adding points.
-
-\begin{lem}
-\label{lem:sat-1}
-Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
-satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
-Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha, \beta \in \BN$ such that
-\begin{align}
-\label{eqn:deg1-sat-ind}
-	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X, \lfloor d\halfcan'
-	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
-	N}.
-\end{align}
-Let
-\[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
-\]
-be the positive best lower approximations of $\frac{\alpha}{\beta}$.
-Then,
-
-\begin{enumerate}
-\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
-	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = d_i$ and $-\ord_P
-	^{L'}(y_i) = c_i$.
-
-\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
-	\[
-		\ord_u(f) < \ord_u(h) \implies f\prec h.
-	\]
-	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
-	Definition ~\ref{defn:graded-p-lex} and $k[y_1, \ldots, y_n] \otimes k[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
-	\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
-	\to R_{\halfcan}$ respectively, then
-
-	\begin{align*}
-		\initial(I) &= \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
-											 + \langle U_i: 1 \le i \le n-1 \rangle
-											 + \langle V \rangle, \\
-	\end{align*}
-	where $V = \{x_i y_j: 1 \le i \le m, 1 \le j \le n\}$ and $U_i$ is
-	the set of monomials of the form $\prod_{j = 1}^{i} y_j^{a_j}$ with
-	$a_j \in \BN_{\ge 0}$ such that
-	\begin{enumerate}
-		\item[\customlabel{custom:sat-1-*}{(*)}] $\sum_{j = 1}^i a_j c_j \ge c_{i+1}$, \\
-		\item[\customlabel{custom:sat-1-**}{(**)}] there does not exist $(b_1, \ldots b_i) \ne (a_1,
-			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
-			c_j \ge	c_{i + 1}$, \\
-		\item[\customlabel{custom:sat-1-***}{(***)}] there does not
-			exist $r<i$ such that $\sum_{j=1}^r a_j c_j> c_{r + 1}$.
-	\end{enumerate}
-
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees at most $\beta$ with $I$ generated over $I'$ in
-	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
-	\max_{1 \leq i \leq m}(\deg(x_i)))$).
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-{\bf Part (a):}
-By
-Equation ~\ref{eqn:deg1-sat-ind}, for any $d
-\in \BN$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
-
-\[
-	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor.
-\]
-
-\noindent
-Thus, there exist rational sections $t_i$ of $\sco(\lfloor d\halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
-for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
-\beta} \rfloor \}$. We will the use positive best lower approximations to
-construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
-
-Let 
-\[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
-	\beta}
-\]
-
-\noindent
-be the positive best lower approximations of $\frac{
-\alpha}{\beta}$. 
-%Note that the elements $t_1, \ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
-Hence, by a dimension count, these sections form a $k$-basis for
-%$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}
-%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
-Choose a positive best lower approximation $\frac{c_i}{d_i}$.
-Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
-Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
-Hence, for each $j$,
-\[
-	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
-\]
-so the mediant inequality tells us
-\[
-	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{d_i}.
-\]
-Multiplying through by $d_i$ gives
-\[
-	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
-\]
-
-\noindent
-Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees. 
-Choose some $y_i \in(R_{
-\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-
-Suppose $c,d \in \BN$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
-\beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so 
-%  The argument goes $c_i d \ge c d_i$
-% implies c_i \frac{d}{d_i} \ge c
-% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
-% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
-% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
-% \implies the equation below:
-\[
-	\frac{c-c_i}{d-d_i}\le \frac{\alpha}{\beta}
-\]
-which implies
-\begin{equation}\label{eqn:c-from-lower-terms}
-	c_i +\left\lfloor (d-d_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
-\end{equation}
-
-Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
-\[
-	S_0 = \{u^l : l \in \BN_{\ge 0}\}
-\]
-and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
-\[
-	S_i = y_j \cdot S_{i-j}.
-\]
-Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
-\[
-	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
-\]
-Then define 
-\begin{equation}\label{eqn:sat-1-defining-S}
-	S = \cup_{i=1}^{\infty} S_i.  
-\end{equation}
-Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.
-
-By equation \ref{eqn:deg1-sat-ind} for $d \in \BN$,
-\[
-	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X, \lfloor d\halfcan'
-		\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor,
-\] 
-so $S$ contains elements in degree $d \in \BN$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
-Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
-
-{\bf Part (b):}
-Let $S$ be as defined in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
-\[
-	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
-\]
-
-We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.
-In part (a), we showed that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving condition (1) of Lemma ~\ref{lem:relations_from_generators_induction}.
-Our choice of monomial order in $k[y_1, \ldots, y_n]$ and block order for $k[y_1, \ldots, y_n]\otimes k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
-
-It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}.
-To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
-Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$.
-Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.
-Therefore, $f\in k[u, y_1, \ldots, y_n]$.
-We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
-That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\[
-	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
-\]
-Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $k[u, y_1, \ldots, y_n]$.
-If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
-Let $\halfcan$ be maximal such that $a_l\ne 0$.
-Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
-$$
-b_j = \begin{cases}
-	a_j &\text{ if } j \neq i\\
-	a_j + 1 &\text{ if } j=i.
-\end{cases}$$
-
-\noindent
-Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S$, 
-and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
-Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
-and have the following still satisfied: each $\gamma_j\le b_j$ 
-and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
-$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
-
-We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  
-Notice that if $r\le n$, $\omega_1, \ldots \omega_r\in \mathbb{Z}_{\ge 0}$, and $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_r\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among $c_1, \ldots c_n$ not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
-Therefore, since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$, which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$.
-Therefore $\sum_{j=1}^h {y_j}^{\gamma_j}$ satisfies \ref{custom:sat-1-*}.
-
-Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for some $l$.
-Then, for all $r< h$ we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.
-Furthermore, since $(\gamma_1, \ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.
-Therefore, $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ meaning that $\sum_{j=1}^r \gamma_j c_j < c_{r+1}$, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
-Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$.
-
-Since the ideal in $k[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\begin{align*}
-				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
-	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
-\end{align*}
-This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
-Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).
-
-{\bf Part (c):}
-Finally, (c) of this lemma follows immediately by looking at the constructions of parts (a) and (b).
-
-%Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
-%\frac{\alpha}{\beta}$ is not a best lower approximation than we can
-%construct an element in degree $d$ with pole degree $c$ by either $y
-%_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-%same conditions.
-This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.
-In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.
-%
-%Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.
-Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if
-%$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
-%successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-%\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-%\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
-%convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-%with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-%is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
-%expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
-%is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
-%\[
-	%x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-%\]
-%
-%\noindent
-%giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
-%the beginning}
-%
-%Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
-%< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
-%basis element of the form described above: $y_n^0 y_j y_i u^0$). 
-%Choose the maximal $\halfcan$ such that $c_h \le c_i + c_j$; since $1 < d_i
-%\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
-%so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
-%Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
-%$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
-%= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
-%best lower approximation of $\frac{\alpha}{\beta}$ with denominator
-%larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
-%know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
-%Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
-%1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
-%h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
-%appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
-%$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
-%follow a similar technique as in the previous paragraph to cancel
-%out poles of $y_i y_j$ at $P $ to find
-%\[
-	%y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-	%u^{b_l}\in R_D
-%\]
-%
-%\noindent
-%implying a relation with initial term $y_i y_j$. 
-%
-%Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
-%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
-%\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
-%{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
-%with the same pole order; following the same method as the previous
-%two paragraphs we find
-%\[
-	%y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-%\]
-%
-%\noindent
-%Similarly if $i = 1$, then we get the same result using
-%\[
-	%y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
-%\]
-%
-%\noindent
-%In both cases we deduce that $y_i y_j$ is an initial term of some relation.
-%
-%
-%Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
-%1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
-%then there are no relations with initial term a power of $y_i$
-%and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
-%note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
-%{reference to Evan's paper where he proves this} Therefore, if $i >
- %1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
-%in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
-%Following a similar technique to the previous paragraphs we find
-%\[
-	%(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-%\]
-%
-%\noindent
-%Similarly if $i = 1$ then
-%\[
-	%(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
-%\]
-%
-%\noindent
-%In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation. 
-%
-%Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
-%generated by the initial terms described in the previous paragraphs
-%together with $\initial(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
-%
-%We show that $J$ is in fact all of the initial ideal. Suppose
-%$f$ is a non-constant monomial that does not lie within $J$.
-%Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
-%there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
-%some $x_j \mid f$ or else we would have $y_i x_j \mid f$
-%contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
-%i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
-%element of a relation and divides $f$. If $d_i = 1$ as well, then
-%we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
-%$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
-%\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
-%f$. We observe that the remaining elements are precisely those of
-%the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
-%which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
-%, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
-%Therefore, by dimension counting (in each degree), we see that $J$
-%is the initial ideal of $I$.
-
-%Furthermore, since our choice of $y_i
-%$'s was generic, this is in fact the generic initial ideal.
-
-%In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
-%~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
-%basis defined above is minimal.
-%\todo{What about $\frac{\alpha}{\beta} > 1$?}
-\end{proof}
-
-\begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i}$ for some odd $e_i \in \BN_{\geq 3}$, then $T,$ as defined in the beginning of the proof of (b) in Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
-\end{rem}
-
-\begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
-When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
-\end{rem}
-
-We now restrict our attention to log canonical rings of stacky curves.
-Lemma \ref{lem:sat-1} accounts for many of the induction cases when the spin canonical ring is saturated in degree 1, as defined in Definition ~\ref{defn:sat}.
-We complement Lemma ~\ref{lem:sat-1} with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated in degree two or three.
-
-\begin{lem}
-\label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan)$ and $(\sx', \Delta, \halfcan')$ be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
-Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann-Roch $\sat(Eff(L'))\le 2$.
-Furthermore, let $R_{\halfcan'} = k[x_2, x_3
-, x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-Suppose for $i \in \{2, 3\}$, we generically choose $x_i$ satisfying $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$. Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
-\begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(h) \implies f \prec h.
-\end{align*}
-
-\noindent
-Then, the following statements hold.
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
-		\{3, 4\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements
-		$y_3, y_4,$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
-		y_4$
-		and equip the ring $k[y_3, y_4] \otimes k[x_2, \ldots, x_m]$ with block 
-		order. Then,
-		\begin{align*}
-			\initial(I) &= \initial(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
-		\end{align*}
-	%\item[(c)] Any set of minimal generators for $I'$ together with 
-		%any set of relations with leading terms as in (b) minimally 
-		%generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-First, note that when genus is at least we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ 
-and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
-If $g = 1$, we assume $\deg 3 \halfcan \geq 2 > 2g - 1$, so we also have $\deg 4 \halfcan \geq 2 > 2g - 1,$ so again $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
-
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a).
-
-A quick computation checks that
-the following set $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$:
-
-\begin{align}
-\label{eqn:sat_two_add_generator}
-	S =	& \; \{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
-\end{align}
-
-\noindent
-completing part (a).
-
-Letting
-\begin{align*}
-	T =   &\; \{ y_4 x_j \mid 2 \leq j \leq m \}\cup \{ y_4^2 \}
-\end{align*}
-a similar (but much easier) computation to that of lemma $\ref{lem:sat-1}$ determines that $S$, $T$, and $\prec,$ using the ordering defined in (b), meet the conditions of 
-Lemma \ref{lem:relations_from_generators_induction}. 
-Hence, by Lemma \ref{lem:relations_from_generators_induction}, part (b) holds.
-
-%For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
-%we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
-%Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
-In both cases we induce a relation, with initial term described in the lemma's statement.
-Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
-%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
-
-\end{proof}
-
-\begin{lem}
-\label{lem:sat-3}
-Suppose $\halfcan'$ is a log spin canonical divisor of $\sx'$ with coarse
-space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
-{\halfcan'} \cong k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
-{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
-the ordering on $k[x_3, \ldots, x_m]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-
-\noindent
-Then, the following statements hold.
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements $y
-		_3, y_4,$ and $y_5$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with grevlex so that $y_3 \prec 
-		y_4 \prec y_5$
-		and equip the ring $k[y_3, y_4, y_5] \otimes k[x_3, \ldots, x_m]$ with the block order.  Then,
-		\begin{align*}
-			\initial(I) &= \initial(I) k[y_3, y_4, y_5, x_3, \ldots, x_m] \\
-			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5\rangle.
-		\end{align*}
-	%\item[(c)] Any set of generators for $I'$ together with 
-	%	any set of relations with leading terms as in (b) 
-	%	generate $I$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-Since $X$ has genus 0, general
-elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $-\ord_P^{\halfcan'}(y_i) =
-1$. We see by pole order considerations that
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		S=	&\{ y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon, \epsilon') \in \{(0,0),(0,1),(1,0)\} \} \\
-		\cup \;&\{y_3^ay_4, y_3^by_5 \mid a \geq 0, b \geq 0 \}
-	\end{split}
-\end{align}
-
-\noindent forms a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$, which concludes part (a) of the proof.
-
-Setting
-\[
-	T = \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\} \cup \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
-\]
-we can argue similarly to Lemma \ref{lem:sat-1} that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, concluding part (b).
-
-%To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
-%_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-%suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-%,$ elements of degree $d$ in the claimed basis of
-%~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-%\rfloor $ and $b = d \bmod 3$, we have that the elements
-%
-%\begin{align*}
-	%x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
-%3+b}
-%\end{align*}
-%
-%\noindent
-%are precisely $a$ elements, which are all independent as they have
-%distinct pole orders at $P$. This completes part (a).
-%
-%To show part (b), note that the generators in
-%~\ref{eqn:add_one_generator} are precisely a set of monomials which
-%generate $k[x, y]/J$ over $k$. So, to show $J = \initial(I)$, it
-%suffices to show that all generators of $J$ lie in $\initial(I)$.
-%
-%This follows, since there exist constants $A_{i,j} \in k$ for $4
-%\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-%elements $w_{i,j} \in R'$ so that the following linear combinations
-%of elements lie in $R'$.
-%
-%\begin{align*}
-	%&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
-	%\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
-	%&y_4^2 + B_1 y_3 y_5 \\
-	%&y_4 y_5 + B_2 y_3^2 x_3 \\
-	%&y_5^2 + B_3 y_3^2 x_4
-%\end{align*}
-%
-%\noindent
-%Of course, the initial terms of these elements are precisely the
-%generators of $J$, completing (b).
-
-%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
-\end{proof}
-
-%\begin{lem}
-%\label{lem:adding_points_saturation_2_to_1_with_log}
-%Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be log spin log stacky spin 
-%curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
-%\halfcan'$, meaning that $L=L'+P$. Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
-%\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures. Suppose 
-%$\sat(\Eff(\halfcan))= 1$ and $\sat(\Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 
-%x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. Then
-%
-%\begin{enumerate}
-%\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
-%(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)> 0$ and $\{y_1^2, y_2\}$ is linearly 
-%independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-%\item[(b)] Equip $k[y_1, y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
-%x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$. 
-%Then
-%\begin{align*}
-			%\initial(I) &= \initial(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			%&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
-			%&+\langle y_2^2\rangle.
-		%\end{align*}
-%\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-%leading terms as above minimally generate $I$.
-%\end{enumerate}
-%\end{lem}
-%
-%\begin{proof}
-%Since adding $P$ to $\halfcan'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)= 1$. 
-%Choose any $y_1\in H^0(X, \lfloor L\rfloor)$; we know by saturation arguments that $-
-%\ord_P(y_1)= 1$. Furthermore, since $\delta> 0$, we use Riemann-Roch to deduce that for 
-%all $d> 1$ $h^0(X, \lfloor dL\rfloor)=h^0(dL') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
-%$-vector space over $(R_{\halfcan'})_d$. In particular, this means we can generically 
-%choose an element $y_2\in H^0(X, \lfloor 2L\rfloor)$ linearly independent from $y_1^2$. By 
-%dimension counting, we see that 
-%\[
-	%\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c \in \{0,1\}\rangle
-%\]
-%\[
-	%\langle y_1^a y_2: a\ge 0\rangle
-%\]
-%form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. This completes part (a).
-%
-%To show part (b), we note that the monomials in the basis above generate $k[x, y]/\initial_
-%\prec(I)$. Thus, it is sufficient to show that $J\subseteq \initial(I)$. For $j\ge 2$, we 
-%can choose $w_j$ in degree $\deg(x_j) + 1$ and $A_j\in k$ such that
-%\[
-	%y_2x_j -A_jy_3w_j
-%\]
-%has no pole at $P$ at thus lies in $R_{\halfcan'}$. Similarly, we can choose $B$ and $C$ 
-%such that
-%\[y^2_4+By_1^2x_2+Cy_1x_3\]
-%has no pole at $P$, so it lies in $R_{\halfcan'}$. These give us relations with initial terms 
-%as desired, concluding part (b).
-%
-%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
-%
-%\end{proof}
-%
-%\begin{lem}
-%\label{lem:adding_points_saturation_2_to_1_no_log}
-%Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be log spin log stacky spin curves 
-%with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$. Let $(g; e_1, \ldots, e_
-%\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures. 
-%Suppose $'\sat(\Eff(\halfcan))= 1$ and $'\sat(\Eff(\halfcan'))=2$. Further suppose 
-%$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. 
-%Then
-%\begin{enumerate}
-%\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
-%(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)> 1$ and $\{y_1^3, y_2\}$ is linearly 
-%independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-%\item[(b)] Equip $k[y_1, y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
-%x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$. 
-%Then
-%\begin{align*}
-			%\initial(I) &= \initial(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			%&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
-			%&+\langle y_3^2
-		%\end{align*}
-%\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-%leading terms as above minimally generate $I$.
-%\end{enumerate}
-%\end{lem}
-%\begin{proof}
-%The proof follows similarly to that of Lemma 
-%\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
-%\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
-%generator in degree 3 rather than degree 2. 
-%\end{proof}
-%
-%We prove an inductive theorem on adding 2-sat here.
-%
-%
-%We will now prove a Lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
-%reference} and O'Dorney\todo{reference}.
-%
-%\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
-%Notice that in Lemma ~\ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
-%\end{rem}
-%
-%This yields some immediate corollaries:
-%
-%\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\BQ$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
-%\end{cor}
-%
-%\begin{proof}
-%We can prove this by induction. As a base case, let $D\sim 0$. Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
-%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i = 1}^{r+ 1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
-By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
-Since $D$ is effective, the condition of equation ~\ref{eqn:deg1-sat-ind} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
-%\end{proof}
-%
-%\todo{do these corollaries fit here?}
-%
-%\begin{cor}\label{cor:genus_0_positive_delta}
-%Let $\halfcan$ be a stacky log spin canonical divisor of $(X, \Delta)$ with signature $(g;e_1, \ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)> 0$.
-Then $\halfcan$ is effective so we can inductively apply Lemma ~\ref{lem:deg1_sat_ind}.
-%\end{cor}
-%\begin{proof}
-%Since $\halfcan$ is a spin canonical divisor, 
-%\[
-	%2\halfcan=D+\sum \subhalf{e_i}P_i
-%\] 
-%where 
-%\[
-	%D\sim K_X+\Delta\sim -2\infty+ \Delta
-%\] is a divisor of $X$ (i.e. with 
-%possibly negative integer coefficients). Since $\Delta$ is non-
-%zero effective, $\deg(D)\ge - 1$.  Noting that the coefficient of 
-%any point $P$ occurring in a stacky divisor of $\sx$ must have 
-%coefficient lying in $\BN[\frac{1}{e_i}]$ (ranging over $e_i$
-%s appearing in the characteristic of $(\sx, \Delta)$).
- %
-%Since all $e_i$'s are odd, $2$ cannot appear in a denominator of the 
-%coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
- %must be a $X$-divisor. Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
-%\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$. Thus $\halfcan$ 
-%is linearly equivalent to an effective $X$ divisor plus $\sum 
-%\subhalf{i}P_i$. We have thus shown $\halfcan$ is linearly equivalent to an effective divisor. Thus, by ~\ref{cor:effective_Q_divisor_can_ring} the desired result follows.
-%\end{proof}
-
-%\todo{Move this Lemma:}
-%\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
-%Let $(X, \Delta, \halfcan)\to (X, \Delta', \halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
-%Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-%generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0. Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-%in degree at most $\bar{\tau}$.
-%Then 
-%\begin{itemize}
-%\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively. 
-%\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
-%
-%\begin{align*}
-	%\initial(I') &= \initial(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 %&+ \langle y_i x_j \rangle \\
-										 %&+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
-%\end{align*}
-%\item A Gr\"{o}bner basis with initial terms described above minimally generates $I'$ over $I$.
-%\end{itemize}
-%\end{lem}
-%\begin{proof}
-%Similar to all the other Lemmas\todo{combine sections?}
-%\end{proof}
-
-One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only the cases of Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} are needed for the remainder of this paper.
-We next turn to an inductive method to increment the $e_i$'s.
-
-\ssec{Raising Stabilizer Orders}
-\label{ssec:raise-orders}
-In this subsection, we present Lemma ~\ref{lem:raise-stacky-order},
-whose proof is almost identical to one of Voight and Zureick-Brown
-\cite[Theorem 8.5.7]{vzb:stacky}. Lemma
-~\ref{lem:raise-stacky-order} implies that if the main result,
-Theorem ~\ref{thm:main}, holds for a curve with signature $(g; e_1',
-\ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' =
-\cdots = e_r'$ satisfying certain admissibility (cf. Definition
-~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for
-a curve with signature $(g; e _1', \ldots, e_k', e_{k + 1}' + 2,
-\ldots, e_r' + 2; \delta)$. 
-%In order to state Lemma
-%~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in %Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
-
-%\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{custom:Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
-%\end{rem}
-%\todo{Peter: I'm not sure how useful this remark is.
-After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.
-The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
-
-%\begin{lem}\label{lem:n-3s-admissible}
-%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
-Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $\halfcan'$.
-Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $\halfcan$.
-%\end{lem}
-%\begin{proof}
-%To show \ref{custom:Ad-i} and \ref{custom:Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
-Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{custom:Ad-i}.
-Furthermore, since $s$ is an admissible set of $\halfcan'$, in particular, we must have \ref{custom:Ad-ii} satisfied so $\frac{-\ord_{Q_l}
-%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{custom:Ad-ii} follows in genus 0?}
-%
- %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
-%\begin{itemize}
-%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $\halfcan'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{custom:Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
-%\end{itemize}
-%\end{proof}
-
-The following Lemma will slightly strengthen condition \ref{custom:Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
-
-\begin{lem}
-\label{lem:admissible_inequality}
-For any $z$ as in condition \ref{custom:Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{custom:Ad-ii} implies the
-tighter inequality that
-
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
-\end{align*}
-\end{lem}
-
-\begin{proof}
-We know by \ref{custom:Ad-ii} that
-
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) < \deg(z) \subhalf{e_i'}
-\end{align*}
-
-\noindent
-If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'- 1}{2e_i'}$ 
-as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}
-^{\halfcan_X'}(z)$ is an integer, 
-we must have
-
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
-	\deg(z) \subhalf{e_i'} - \frac{1}{e_i'}.
-\end{align*}
-\end{proof}
-
-\begin{lem}
-\label{lem:admissible_subset}
-If $(\sx', \Delta, \halfcan')$ is a log spin curve, $(\sx', \halfcan', J)$ is admissible and $W \subseteq J$ is any subset,
-then $(\sx', L', W)$ is also admissible.
-\end{lem}
-
-\begin{proof}
-Each of the conditions \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} hold for $W$
-if they hold for $J$.
-\end{proof}
-
-\begin{rem}
-\label{rem:three-cases}
-For our inductive arguments in Theorems ~\ref{thm:g-high-main},
-~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a
-single stacky point with stabilizer order $3$. Say $(\sx, \Delta,
-\halfcan)$ is a log spin curve with signature $\sigma = (g; e_1,
-\ldots, e_r; \delta) = (g; 3, \ldots, 3; \delta)$, and our base cases
-include signatures $\sigma$ characterized by one of the following:
-cases, which we will soon refer to in Lemma
-~\ref{lem:raise-stacky-order}:
-
-\begin{enumerate}
-	\item[\customlabel{custom:three-cases-1}{(1)}] $g = 0, e_1 =
-		\cdots = e_r = 3, \delta = 0$, and $r \geq 5$
-	\item[\customlabel{custom:three-cases-2}{(2)}] $g = 1, e_1 =
-		\cdots = e_r = 3, \delta = 0$, and $ r \geq 2$
-	\item[\customlabel{custom:three-cases-3}{(3)}] $g \geq 2, e_1 =
-		\cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
-\end{enumerate}
-\end{rem}
-
-\begin{lem}
-\label{lem:raise-stacky-order}
-Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$.  Define $R':= R_{\halfcan'}$.  Further, assume either 
-\begin{enumerate}
-	\item $(\sx', \halfcan', J)$ is admissible with generators $x_1,
-		\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J$, as 
-		in Definition ~\ref{defn:admissible} or
-	\item $\sigma$ is one of the signatures described in Cases
-		\ref{custom:three-cases-1}, \ref{custom:three-cases-2} and
-		\ref{custom:three-cases-3} of Remark ~\ref{rem:three-cases} and
-		$y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of
-		$\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$
-		for $1 \leq  i \leq r$.
-\end{enumerate}
-Let
-$(\sx, \Delta, \halfcan)$ be another log spin curve
-with coarse space $X$, so that $X \cong X'$ and signature $(g; e_1, \ldots, e_r;
-\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
-$e_j = e_j'$ for $j \notin J$. Define $R := R_\halfcan$.  Then the following are true:
-\begin{enumerate}
-	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
-		H^0(\sx, e_i(K_\sx))$ so that
-		\begin{align*}
-			-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
-		\end{align*}
-		and
-		\begin{align*}
-			\frac{-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
-\subhalf{
-			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
-		\end{align*}
-		for all $j \in J$ with $j \neq i$.
-	\item[(b)]
-
-%The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
-%0,
-%		b > 0$ span $R$ over $R'$ and
-		A choice of elements $y_{1, e_1}, \ldots, y_{r, e_r}$ as in part (a) minimally
-		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
-$k[y_{i, e_i}]_{i\in J} \otimes k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
- block order.  Let $I$ be the kernel of $k[x_1, \ldots, x_m, y_{i, e_i'}, y_{i, e_i}]_{i\in J} \to R$.
-  Then,
-		\begin{align*}
-			\initial(I) \;	&= \; \initial(I')k[x, y] \\
-					&+ \; \langle y_{j, e_j}x_i  : 1\le i \le m, j\in J\rangle \\
-					&+ \; \langle y_{j, e_j}y_{i, e_i'}: i,j\in J, i\ne j\rangle \\
-					&+ \; \langle y_{j,e_j}y_{i,e_i}: i,j\in J, i\ne j\rangle.
-		\end{align*}
-	\item[(d)] The triple $(\sx, \halfcan', J)$ is admissible.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-We prove this in case (1) and case (2) follows a similar procedure.
-
-{\bf Part (a):} 
-By Definition ~\ref{defn:admissible}, for all $i\in J$
-
-\begin{align*}
-	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i-e_j'\} = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}.
-\end{align*}
-
-\noindent
-Define
-\begin{align*}
-	E_i = \sum_{j \in S(i,0)}^{}Q_j.
-\end{align*}
-
-\noindent
-The assumption \ref{custom:Ad-iii} implies
-\begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq \max(2g - 1,0),
-\end{align*}
-
-\noindent
-and so $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch.
-Hence, a general element
-\begin{align*}
-	y_{i, e_i} \in H^0(\sx', e_iL'-E_i + Q_i)
-\end{align*}
-
-\noindent
-satisfies
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \left\lfloor e_i \subhalf {e_i'} \right\rfloor + 1 =
-	\frac{e_i - 1}{2}.
-\end{align*}
-
-Noting that
-\begin{align*}
-	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor,
-\end{align*}
-
-\noindent
-we obtain an inclusion
-\begin{align*}
-	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subseteq 
-H^0(\sx, e_iL).
-\end{align*}
-
-\noindent
-meaning that $y_{i,e_i}\in H^0(\sx,e_iL)$ satisfies the first part of claim (a).
-
-We next show $y_{i, e_i}$ also satisfies the second part of the
-claim of $(a),$ by considering separately the cases in which $j
-\in S(i, 0),$ and $j \notin S(i,0)$.
-
-If $j \in S(i,0)$, then $E_i \geq Q_j$ gives $y_{i, e_i} \in H^0
-(\sx', e_iL'-E_i + Q_i)$ an extra vanishing condition at $Q_j$, so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
-	\subhalf{e_j'} - \frac{1}{e_j'}.
-\end{align*}
-
-If instead $j\ne i$ and $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
-$e_i\subhalf{e_j'} \notin \BZ$, so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq \left\lfloor  e_i\subhalf{e_j'} \right\rfloor 
-	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
-\end{align*}
-
-\noindent
-completing the proof of (a).
-
-{\bf Part (b):}
-Define $R_0 = R'$ and for $i \in \{1, \ldots, r\},$ inductively define 
-$$R_i = \begin{cases}
-	R_{i - 1} &\text{ if }i \notin J\\
-	R_{i - 1}[y_{i, e_i}] &\text{ if }i \in J. 
-\end{cases}$$
-
-\noindent
-To prove (b), it suffices to show that elements of the form $y_{i, e_
-i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $k$-basis for $R_{i}$ over $R_{i-1}$.
-These elements do not lie in $R_{i - 1}$ because the pole order of $y_{i, e_i'}^ay_{i,e_i}^b$ at $Q_i$ is larger than that of any element in the $d^{th}$ component of $R_{i - 1}$.
-Additionally, these elements are linearly independent amongst themselves because of
-injectivity of the linear map
-
-\begin{align*}
-	(a,b) \mapsto \left( \deg\left(y_{i, e_i'}^ay_{i, e_i}^b\right),-
-	\ord_{Q_i}
-^{\halfcan_X'}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
-	\begin{pmatrix}
-		e_i -2 & \frac{e_i -3}{2} \\
-		e_i	 & \frac{e_i - 1}{2}
-	\end{pmatrix}.
-\end{align*}
-
-\noindent
-Furthermore, $\{y_{i, e_i'}^a y_{i, e_i}^b:a \geq 0,
-b > 0\}$ span $R_i$ over $R_{i - 1}$, because the set of
-integer lattice points in the cone generated by the vectors $\left(e
-_i -2, \frac{e_i -3}{2} \right)$ and $\left(e_i, \frac{e_i - 1}{2}
-\right)$ is saturated, because the corresponding determinant is
-\begin{align*}
-	(e_i -2) \frac{e_i - 1}{2} - e_i \frac{e_i -3}{2} = 1.
-\end{align*}
-This completes part (b).
-
-{\bf Part (c):}
-To show (c), we wish to show that $y_{i, e_i}z \in R'$ for all generators $z$ of $R'$
-with $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$. By definition of $H^0(\sx,\halfcan')$, note that $f \in R$ further satisfies $f \in R'$ if and
-only if for all $j \in J$ we have
-\begin{align}
-\label{eqn:order-degree}
-	-\ord_{Q_j}
-^{\halfcan_X'}(f) \leq \deg (f) \left( \subhalf {e_j'} \right).
-\end{align}
-
-\noindent
-Now fix $i \in J$. We check Inequality ~\eqref{eqn:order-degree} holds with $f = y_{i, e_i}z$, implying $y_{i,e_i}z \in R'$ in the three following cases: 
-%$j \notin \{i \} \cup S(i, 0)$, $j = i,$ and $j \in S(i, 0)$.
-
-\vskip.1in
-\noindent
-{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
-
-Here, $L|_{Q_j} = L'|_{Q_j},$ so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
-^{\halfcan_X'}(z) \leq e_i \subhalf {e_j'} +
-	\deg (z) \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 2: $j =i.$}
-
-By part (a), condition \ref{custom:Ad-ii}, and Lemma
-~\ref{lem:admissible_inequality} we have
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
-^{\halfcan_X'}(z)
-	&\leq \frac{e_j - 1}{2} + \deg (z) \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg (z) \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg (z) \left( \subhalf{e_j'} \right) \\
-	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 3: $j \in S(i,0).$}
-
-In this case, we may first assume $z \neq y_{j, e_j}$, 
-as this is covered by case 2, with $i$ and $j$ reversed. 
-Hence, 
-\begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'},
-\end{align*}
-implying
-\begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}^{\halfcan_X'}(z) 
-	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
-	= \deg (y_{i, e_i}z) \subhalf{e_j'},
-\end{align*}
-completing part (c).
-
-%Next, note that the minimal generators of $I'$ together with the
-%new generators of $I$ given in (c) have independent initial terms
-%by construction, and therefore are minimal by Lemma
-%~\ref{lem:minimal_quadratic}.
-
-{\bf Part (d):}
-To check (d), we show \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} are satisfied. We know \ref{custom:Ad-i} holds by part (b), taking the $y_{
-i, e_i}$ as the generators in degree $e_i$. Next, \ref{custom:Ad-ii} is
-strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
-Finally, if \ref{custom:Ad-iii} holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that \ref{custom:Ad-iii} holds for $d > 0$
-and not just for $d = 0$.
-\end{proof}
-
-\begin{cor}
-\label{cor:raise-stacky-order}
-Suppose $(\sx', \halfcan',J')$ is admissible with signature $\sigma' = (e_1
-', \ldots,e_r')$ or $\sigma$ satisfies one of the conditions of
-Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1, \ldots,r\}$ and
-$e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
-so that $(\sx', \Delta, L)$ satisfies the conditions of Lemma
-~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then,
-for any spin curve $(\sx, \Delta, L)$ so that $\sx$ and $\sx'$ have
-the same coarse space $X = X'$ with the same set of stacky points,
-and $  \sx$ has signature $(g; e_1, \ldots, e_r; \delta)$ with $e_1
-\leq e_2 \leq \cdots e_r$ so that
-\begin{align*}
-	& e_i	= e_i' &\text{ if }i \notin J \\
-	& e_i \ge e_i' &\text{ if } i \in J
-\end{align*}
-
-\noindent
-then Theorem ~\ref{thm:main} holds for $(\sx, \Delta, \halfcan)$.
-\end{cor}
-
-\begin{proof}
-For $t \leq i \leq r$, let $(\sx_i, \Delta, \halfcan_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx', \Delta, \halfcan),$ and having signature $(g; e_1, \ldots.
-e_{i - 1}, e_i, e_i, \ldots, e_i; \delta).$ Let
-$J_i = \{i, \ldots, r\}.$ Note that $(\sx_0, \halfcan_0,J_0) = (\sx', \halfcan',J')$ and $(\sx_r , \halfcan_r ,J_r) = (\sx, L, \{r\})$.
-
-Let $(*_i)$ denote the condition that $(\sx_i, \Delta, L_i)$
-satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and
-Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is
-admissible. Since $(*_0)$ holds by assumption, it suffices to show
-that if $(*_i)$ holds then so does $(*_{i + 1})$. Indeed, $(\sx_i,
-\halfcan_i, J_{i + 1})$ is admissible by an application of Lemma
-~\ref{lem:admissible_subset} and the fact that $J_{i + 1} \subseteq J
-_i$. Then, applying Lemma ~\ref{lem:raise-stacky-order} with the
-fixed set $J_{i + 1}$ repeatedly ($\frac{e_{i + 1} - e_i}{2}$ many
-times) yields $(*_{i + 1})$.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus $\geq 2$ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Genus $\geq 2$}
-\label{sec:g-high}
-We now consider the case when the genus is at least 2.
-In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations.
-The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
-
-\ssec{Bounds on Generators and Relations in Genus $\geq 2$}
-\label{ssec:bounds-high-genus}
-
-The main result of this subsection is that for a log spin curve with no stacky points $(X \Delta, L)$, the spin canonical ring $R_\halfcan$ is generated in degree at most $5$, with relations in degree at most $10$.
-The case that $\Delta = 0$ was completed by Reid \cite[Theorem 3.4]{reid:infinitesimal}.
-For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Throughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint-free by Riemann-Roch.
-We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
-
-The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
-However, the statements differ, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint-free pencil contained in $H^0(X, L).$
-
-%\begin{lem}
-%\label{lem:generation-5}
-%Let $X$ be a curve of genus $g \geq 2$ and let $\halfcan$ be a divisor with $2 L \sim K +\Delta$. Then, $R_\halfcan$ is generated in degree at most $5$.
-%\end{lem}
-%
-%The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_\halfcan$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
-When $g > 3$, it is easy to reduce the bound from 5 to 6.
-The trickiest case is to show $R_\halfcan$ is generated in degree 5 when $g = 2$, which is done in Lemma ~\ref{lem:genus-2-generation-5}.
-After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation-5}.
-
-\begin{lem}
-\label{lem:generation-5}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
-with $g \geq 2$ and $\Delta > 0.$ Let $s_1$, $s_2 \in H^0(X, 2L)$
-be two independent sections such that the vector subspace $V =
-\newspan(s_1, s_2) \subseteq H^0(K)$ is basepoint-free. Then, the map
-\begin{align*}
-	V \otimes H^0(nL) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective if $n \geq 4$. In particular, $R_\halfcan$ is generated in degree at most $5.$
-\end{lem}
-
-%\begin{rem}
-%\label{rem:neves-omission}
-%The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}.
-However, Neves states that this proof also proves Lemma ~\ref{lem:generation-5}, while it crucially omits the case of genus 2 curves.
-We produce the proof here for completeness.
-%\end{rem}
-
-\begin{proof}
-To show there are no new generators in degree at least $6$, it
-suffices to show that if $n \geq 4$, the map
-\begin{align*}
-	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective. Indeed, since $V = \newspan(s_1, s_2) \subseteq
-H^0(K)$ is basepoint-free, by the basepoint-free pencil trick (see
-\cite[Lemma 2.6]{saint-donat:proj} for a proof), we obtain an exact
-sequence
-$$\begin{tikzcd}
-0 \ar r & H^0((n-2)L) \ar r & V \otimes H^0(nL) \ar{r}{f} & H^0((n+2)L)
-\end{tikzcd}$$
-
-We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n - 2)L) = (n - 3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
-Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n - 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
-Therefore,
-\begin{align*}
-	\dim_k \im f 	& = 2 \cdot (n - 1)(g - 1+ \frac{\delta}{2}) - (n - 3)(g - 1 + \frac{\delta}{2})\\
-				& = (n + 1)(g - 1 + \frac{\delta}{2}) = \dim_k H^0((n + 2)L).
-\end{align*}
-Ergo, $f$ is surjective.
-\end{proof}
-
-%\begin{lem}
-%\label{lem:genus-2-generation-5}
-%Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
-%Then, $R_\halfcan$ is generated in degree at most $5$.
-%\end{lem}
-%\begin{proof}
-%By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_\halfcan$ has no minimal generators in degree 6.
-%Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
-%Recall that all linear equivalence classes of spin divisors on $X$ have a representative of the form
-%$$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
-%with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
-%Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
-Therefore, the image of the multiplication map
-%\begin{align*}
-	%Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
-%\end{align*}
-%is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
-%which have 
-%\begin{align*}
-	%\di u^3|_{2L} &= -2L \\
-	%\di u^2x|_{2L} &= -2L + 2P_1 \\
-	%\di ux^2|_{2L} &= -2L+4P_1, \\
-	%\di x^3|_{2L} &= -2L + 6P_1.
-%\end{align*}
-%
-%\noindent
-%Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
-%it suffices to produce one more independent function in the image of the multiplication map.
-%There are now two cases, depending on whether $H^0(X, \halfcan) = 0$.
-%
-%First, we deal with the case that $H^0(X, \halfcan) \neq 0$. 
-%Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X, \halfcan) = 1$.
-Hence, we know $\halfcan$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
-In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_\halfcan$ is generated in degree $\leq 3$.
-%
-%Second, suppose $H^0(X, \halfcan) = 0$.
-%Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
-%Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-%we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X, \halfcan + 2P_1)$ 
-%with $\di g|_{2P_1 + L} = -L,$ since $H^0(X, \halfcan) = 0.$ Therefore, there must 
-%exist a function $h \in H^0(X, \halfcan+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
-%Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
-%order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
-%\end{proof}
-
-%We are now equipped to prove Lemma ~\ref{lem:generation-5}, completing the desired bound on the degree of the generators.
-%
-%\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
-%If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
-%Lemma ~\ref{lem:genus-2-generation-5}.
-Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$.
-By Voight and Zureick-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
-Hence, $R_\halfcan$ is generated in degree at most 5.
-%\end{proof}
-
-The next step is to bound the degrees of the relations of $R_\halfcan$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
-%The idea of the proof of Proposition ~\ref{prop:relation-10} is to 
-by using the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
-In Definition ~\ref{defn:lower-ideal}, we fix notation for the ideal generated by lower degrees relations:
-
-\begin{defn}
-\label{defn:lower-ideal}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -; \delta
-)$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots
-, x_n$ of $R_\halfcan$ so that we obtain a surjection $\phi: k[x_1, \ldots
-, x_n] \twoheadrightarrow R_\halfcan$ with kernel $I_\halfcan$. Let $I_{\halfcan, d}$ be
-the $d^\text{th}$ graded piece of $I_\halfcan$ and define
-\[
-	J_{\halfcan,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{\halfcan,d-j}.
-\]
-\end{defn}
-
-\begin{lem}
-\label{lem:reducing-degree}
-Let $(X, \Delta, \halfcan)$ be a log spin curve of genus $g \geq 2,$ so
-that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_\halfcan$ so
-that we obtain a surjection $\phi: k[x_1, \ldots, x_n]
-\twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
-\ldots, x_n]_2$ be two elements so that $\: \newspan(\phi(s_1), \phi(s_2))
-= V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
-k[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
-k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, d}.$
-\end{lem}
-\begin{proof}
-% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1), \phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
-By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
-
-By Lemma ~\ref{lem:generation-5},
-\begin{align*}
-	V \otimes H^0((\deg f-\deg x_i -2)\halfcan) \rightarrow H^0((\deg f-\deg x_i)\halfcan)
-\end{align*}
-is surjective because $\deg f \geq 11$ implies that
-$$\deg a_i =\deg f - \deg x_i -2 \geq 4.$$
-In particular, there exist $\alpha, \beta \in R_L$ so that
-$$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
-Choosing $g_i,h_i\in k[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
-$$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan, \deg a_i},$$ as claimed.
-
-Finally, we may then take $g = \sum_{i}^{}g_i x_i, \: h = \sum_{i}^{}h_i x_i,$ so that 
-\begin{align*}
-	f &\equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \\
-	&\equiv s_1 g + s_2 h \bmod J_{L,d}.
-\end{align*}
-\end{proof}
-
-\begin{prop}
-\label{prop:relation-10}
-Let $(X, \Delta, \halfcan)$ be a log spin curve of signature $(g; -; \delta)$
- with $g \geq 2$ and $\Delta > 0.$ Then $I_\halfcan$ is generated in
-degree at most degree at most $10$.
-\end{prop}
-\begin{proof}
-Suppose $f \in I_\halfcan$ with $\deg f \geq 11$. To complete the proof,
-it suffices to show $f \in I_{\halfcan,d}'$. By Lemma
-~\ref{lem:reducing-degree}, this is the same as checking $s_1 g + s_2 h \in
-I_{\halfcan, d}'$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
-so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
-basepoint-free. Consider the map
-
-$$\begin{tikzcd}
-V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
-\end{tikzcd}$$
-
-\noindent
-we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0$.
-So by the explicit isomorphism given in the proof of the basepoint-
-free pencil trick, as shown in the proof of \cite[Lemma 2.6]
-{saint-donat:proj}, there exists some $\rho \in k[x_1, \ldots, x_n]$
-so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) =
-\phi(s_2) \phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho)$. 
-Therefore,
-$g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv - s_1 \rho \bmod
-I_{k, d - 2}$. Hence,
-\begin{align*}
-	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_
-{L,d}.
-\end{align*}
-\end{proof}
-
-%\begin{rem}
-%\label{rem:relations_generation_ten}
-%Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_\halfcan$ has a
-%relation in degree 10. Therefore, the bound from Proposition
-%~\ref{prop:relation-10}, that $I_L$ is generated in degree at most
-%11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
-%sharp.
-%\end{rem}
-
-We now summarize what we have shown.
-
-\begin{cor}
-\label{cor:g-2-presentation-bound}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
-with $g \geq 2$. Then $X$ has minimal generators in degree at most
-$5$ and minimal relations in degree at most $10$.
-\end{cor}
-
-\begin{proof}
-If $\Delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
-{reid:infinitesimal}. Otherwise, if $\Delta > 0$, the bound on the
-degrees of minimal generators follows from Lemma
-~\ref{lem:generation-5}, while the bound on the degrees of minimal
-relations follows from Proposition ~\ref{prop:relation-10}.
-\end{proof}
-
-\ssec{Main Theorem for Genus $\geq 2$}
-\label{ssec:g-high-main}
-
-We are ready to prove our main theorem, Theorem ~\ref{thm:main} in the case
-$g \geq 2$. The idea of the proof is to use Corollary \ref{cor:g-2-presentation-bound} to 
-complete the base case when $L = \halfcan_X$ and then apply Lemma
-~\ref{lem:sat-1}, Lemma ~\ref{lem:sat-2}, and Lemma
-~\ref{lem:raise-stacky-order} to complete the induction step.
-
-\begin{thm}
-\label{thm:g-high-main}
-Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ be a log spin curve 
-%so that $\sx$ has 
-with signature $(g; e_1, \ldots, e_r; \delta)$. Then the
-log spin canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d L )
-\end{align*}
-
-\noindent
-is generated as a $k$-algebra by elements in degree at most $e =
-\max(5, e_1, \ldots, e_r)$ with minimal relations in degree at most $2e$.
-\end{thm}
-
-%is generated as a $k$-algebra by elements of degree at most $e =
-%\max(5, e_1, \ldots, e_r)$ with relations in degree up to $2e$.
-%
-%Furthermore, there are even stronger bounds for the following
-%exceptional cases X, :
-
-\begin{proof}
-As the base case, let $\halfcan=\halfcan_X \in \di X$ satisfy $2\halfcan \sim 2 K_X + \Delta$.
-By Corollary ~\ref{cor:g-2-presentation-bound}, the theorem holds for $(\sx, \Delta,
-\halfcan_X)$.
-
-Next, suppose the theorem holds for $\halfcan' = \halfcan_X + \sum_{i=1}^{r-1} \frac{1}{3}P_i$.
-Take a log spin canonical divisor of the form $\halfcan = \halfcan_X + \sum_{i=1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
-If $P_r$ is a basepoint of $\halfcan'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
-Otherwise, $P_r$ is not a basepoint of $\halfcan'$, meaning that in particular $R_{\halfcan'}$ is saturated in 1.
-Therefore, since $P_r$ is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann Roch.
-% since $\frac{\beta}{\alpha} = \frac{3}{1}=3$. 
-In this case, the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-1}.
-
-We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g\ge 2$ and signature $(g;3, \ldots, 3;\delta)$. Therefore, by Corollary 
-~\ref{cor:raise-stacky-order}, this theorem 
-holds for all log spin curves $(\sx, L, J)$. 
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus one %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Genus One}
-\label{sec:g-1}
-
-In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
-We follow a similar inductive strategy as in the genus $g\geq 2$ case, except unlike in the $g \geq 2$ case we obtain explicit generators and relations here.
-
-In the case of a genus 1 curve, $X$ with no stacky points, we know $K_X \sim 0$, and therefore the only possibilities for log spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P, Q$ are distinct points, fixed  under the hyperelliptic involution.
-We inductively construct presentations by adding points through Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2} and incrementing the values of the $e_i$'s using Lemma ~\ref{lem:raise-stacky-order}.
-
-\ssec{Genus One Base Cases}
-\label{ssec:g-1_base}
-In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.
-
-\begin{table}	
-\begin{tabular}
-{| c || c | c | c |}	
-	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
-	\hline
-	\hline
-	$0$ & $\{1\}$ & $\emptyset$ & $1$ \\	\hline
-
-	$\frac{3}{7} P_1$ & $\{1,5,7\}$ & $\{15\}$ & $7$ \\	\hline
-
-	$\frac{1}{3} P_1 + \frac{1}{3} P_2$ & $\{1, 3, 3\}$ & $\{6\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{1}{3} P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ & $5$ \\	\hline
-\end{tabular}	
-	\caption{Genus 1 Base Cases}
-	\label{table:g-1-base}
-
-%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
-\end{table}
-
-The cases that $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
-
-The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
-Although $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ are used as base cases for the induction, they are also exceptional cases; see Table ~\ref{table:g-1-exceptional}.
-
-\ssec{Genus One Exceptional Cases}
-\label{ssec:g-1-exceptional}
-Let $\sx$ be a stacky curve, with $P, Q$ distinct hyperelliptic
-fixed points on $X$. The following table provides a list of all
-cases which are not generated in degrees $e := \max(5, e_1, \ldots,
-e_r)$ with relations in degrees $2e$, as described in Theorem
-~\ref{thm:g-1-main}.
-
-\begin{table}	
-\begin{tabular}
-{| c || c | c | c |}
-	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
-	\hline
-	\hline
-	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline
-
-	$P - Q + \frac{1}{3} P_1$ & $\{2, 3, 7\}$ & $\{14\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$\\	\hline
-
-	$\frac{1}{3} P_1$ & $\{1, 6, 9\}$ & $\{18\}$ & $5$ \\	\hline
-
-	$\frac{2}{5} P_1$ & $\{1, 5, 8\}$ & $\{16\}$ & $5$ \\	\hline
-
-	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline
-	\end{tabular}
-	\caption{Genus 1 Exceptional Cases}
-	\label{table:g-1-exceptional}
-
-%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
-\end{table}
-
-%\begin{rem}
-%\label{rem:g-1-exceptional-e}
-%Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
-%Lemma ~\ref{lem:raise-stacky-order}.
-%\end{rem}
-
-We have already checked the case of 
-$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
-
-%\begin{example}
-%\label{eg:exceptional-1-0}
-%In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_\halfcan \cong k[y]$, where $y$ is a generator in degree 2. 
-%\end{example}
-%
-%\begin{example}
-%\label{eg:exceptional- 1-3}
-%Let $L = P - Q + \frac{1}{3}R$.
-Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$.
-For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-%We find that $R_\halfcan \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
-%\end{example}
-%
-%
-%\begin{example}
-%\label{eg:exception-1-e}
-%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_\halfcan \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Lemma ~\ref{lem:raise-stacky-order} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
-%Furthermore, $\deg u = 2, \deg y_i = i$.
-%\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
-%\end{example}
-
-\ssec{Main Theorem for Genus One}
-\label{ssec:main_g_1}
-
-We now have all the tools necessary to prove our main theorem, ~\ref{thm:main} in the case $g = 1$.
-
-\begin{thm}
-\label{thm:g-1-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
-If $g = 1$, then the log spin canonical ring
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, d L)
-\end{align*}
-
-\noindent
-is generated as a $k$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
-finite list of exceptional cases, as listed in Table
-~\ref{table:g-1-exceptional}.
-\end{thm}
-
-\begin{proof}
-
-\vskip.1in
-\noindent
-{\sf Case 1: $\Delta > 0$}
-
-If $\Delta > 0$, we must have $\Delta \geq 2$, by Remark ~\ref{rem:delta-not-1}.
-In this case, let $\halfcan_X \in \di X$ satisfy $2 \halfcan_X \sim K_X + \Delta$.
-We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $\halfcan$ is linearly equivalent to an effective divisor.
-Thus, without loss of generality, we may assume $\halfcan$ is an effective divisor.
-
-We first now show the theorem holds for $\halfcan_X$ by induction.
-Since $\halfcan_X$ is effective, we may induct on the degree of the log spin canonical divisor.
-The base case is easy: the theorem holds for $\halfcan_X' = 0$ by Example ~\ref{eg:base-1-0}.
-Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective.
-We will show it holds for $L_X' + P,$ verifying the inductive step.
-There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.
-
-First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-
-%In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
-%as $P$ is not a basepoint of $\halfcan_X'$.
-Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.
-1: I'm not sure if we even need to go through the check that it satisfies the conditions for lemma 4.5.
-2: I don't find the check clear or illuminating as written.
-Either we should reword it or remove it (feel free to disagree, of course)}
-
-Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.
-
-Otherwise, $P$ is a basepoint of $\halfcan_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L_X') \geq 2$ as $\deg L_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L_X = L_X'+P$.
-By induction, the theorem holds for $\halfcan_X$.
-
-To complete the case that $\Delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.
-It suffices to show that if the theorem holds for a log spin canonical divisor $\halfcan'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
-As above, if $P$ is not a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}.
-On the other hand, if $P$ is a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
-
-\vskip.1in
-\noindent
-{\sf Case 2: $\Delta = 0$}
-
-Since $\Delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
-
-\vskip.1in
-\noindent
-{\sf Case 2a: $\halfcan_X = P - Q, P \neq Q$}
-
-Note that we are assuming $\halfcan$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points.
-
-First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12.
-Furthermore, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Observe that $\halfcan'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$.
-However, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, and the relation in degree $12$ coming from $R_{\halfcan'}$, lies in a degree less than $2 \cdot 7 = 14$.
-Therefore, the Theorem holds for $L' = P - Q + \frac{3}{7}P_2$.
-Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P - Q + \frac{e- 1}{2e}P_1$.
-
-Second, we deal with the case that $\sx$ has at least two stacky points. 
-If $(\sx', \delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
-Example ~\ref{eg:base-1-33}, the triple $(\sx', 0, P-Q + \frac{1}{3}P_1+\frac{1}{3}P_2)$
-satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
-Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds 
-for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
-
-\vskip.1in
-\noindent
-{\sf Case 2b: $\halfcan_X = 0$}
-
-This case is analogous to 2a: If there is only one stacky point, we start at $L = \frac{3}{7}P_1,$ and inductively increment the stabilizer order.
-Note that by Table ~\ref{table:g-1-base}, $L = \frac{3}{7}P_1,$ will have a relation in degree $15.$ However, once $e_1 \geq 9$, we have $2 \cdot e_1 > 15$, so the theorem holds for such stacky curves.
-Once the log spin canonical divisor has at least two stacky points, the argument proceeds as in Case 2a.
-\end{proof}
-
-\begin{rem}
-In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
-That, is one can start with the generators and relations found in the base cases, and inductively add in generators and relations as one adds and then increments stacky points.
-\end{rem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus zero %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Genus Zero}
-\label{sec:g-0}
-We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
-curve and $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;
-\delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
-$e := \max(5, e_1, \ldots, e_r)$ with relations generated in degree
-at most $2e$, so long as $\sigma$ does not lie in the finite list
-given in Table ~\ref{table:g-0-exceptional}.
-
-As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even. Thus,
-we can reduce the problem into two cases: $\delta \geq 2$ and
-$\delta = 0$. In the former case, $\halfcan$ is linearly equivalent
-to an effective divisor, so the result of Theorem \ref{thm:main}
-follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1}
-to add the necessary stacky points. On the other hand, the proof
-when $\delta = 0$ is more involved. We dedicate the remainder of
-this section to that case in the following steps: characterizing
-saturations points (Subsection ~\ref{ssec:g-0_saturation}),
-describing base cases (Subsection ~\ref{ssec:g-0_base}), and
-presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
-Finally, we apply inductive processes using Lemma ~\ref{lem:sat-3}
-and Lemma ~\ref{lem:raise-stacky-order} to prove the main theorem
-in the full genus zero case (Subsection ~\ref{ssec:g-0-main}).
-
-\begin{rem}
-Since all points are linearly equivalent on $\BP^1_k$, we may
-assume without loss of generality that $L_X = n \infty$ for some $n
-\in \BN$ and $K_X = -2 \infty$. We will use this convention
-throughout this section.
-\end{rem}
-
-\ssec{Saturation}
-\label{ssec:g-0_saturation}
-First, we present the saturations, as defined in Definition
-~\ref{defn:sat}, of the log spin canonical divisor for
-all cases where $g = 0$ and $\delta = 0$. The saturations can be computed using Riemann-Roch.
-By classifying the saturations of all signatures, we can determine
-the base cases on which we can apply inductive lemmas from
-Section ~\ref{sec:induction}. Exceptional cases are listed first
-and generic cases follow.
-
-\begin{table}
-\begin{tabular}
-	{| c | c || c |}
-	\hline
-	Signature $\sigma$ & Condition & Saturation \\
-	\hline
-	\hline
-
-	$(0; 3, 3, 3; 0)$ & & $\infty$ \\	\hline
-
-	$(0; 3, 3, 5; 0)$ & & $18$ \\	\hline
-
-	$(0; 3, 3, 7; 0)$ & & $12$ \\	\hline
-
-	$(0; 3, 3, 9; 0)$ & & $12$ \\	\hline
-
-	$(0; 3, 5, 5; 0)$ & & $8$ \\	\hline
-
-	$(0; 5, 5, 5; 0)$ & & $8$ \\	\hline
-
-	$(0; 3, 3, 3, 3; 0)$ & & $6$ \\	\hline
-
-	\hline
-	\hline
-
-	$(0; 3, 3, k; 0)$ & $k > 9$ & $9$ \\	\hline
-
-	$(0; a, b, c; 0)$ & not listed above & $5$ \\	\hline
-
-	$(0; e_1, \ldots, e_r; 0)$ & not listed above & $3$ \\	\hline
-	\end{tabular}
-	\caption{Genus 0 Saturation}
-	\label{table:g-0-sat}
-\end{table}
-
-\ssec{Base Cases}
-\label{ssec:g-0_base}
-In order to apply Lemma ~\ref{lem:sat-3} and Lemma
-~\ref{lem:raise-stacky-order} when $\delta = 0$,
-we need to determine appropriate base cases that will
-cover all but finitely many signatures by induction.
-Here we provide such base cases and demonstrate that
-they satisfy all of the necessary conditions of
-Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
-(e.g. admissibility as defined in Definition \ref{defn:admissible}). We also show that that the associated spin
-canonical rings are generated in degree at most $e := \max(5, e_1,
-\ldots, e_r)$ with relations generated in degree at most $2e$.
-
-\begin{lem}
-\label{lem:g-0-admissible-cases}
-Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
-$\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
-generated by elements of degree at most $e = \max(5 , e_1, \ldots,
-e_r)$ with relations in degree at most $2e$. Furthermore, each of
-the cases in Table ~\ref{table:g-0-base-cases} satisfy the
-conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e. either $(\sx',
-\halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}
-P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
-Case ~\ref{custom:three-cases-1} of Remark ~\ref{rem:three-cases}):
-
-\rm{
-\begin{table}
-\begin{tabular}
-	{| c || c | c | c |}
-	\hline
-	Case & Signature $\sigma$ & $J$ & $e$\\
-	\hline
-	\hline
-
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $11$ \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$	& $9$ \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$	& $7$ \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$	& $7$ \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $5$ \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $5$ \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $5$ \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ \\ \hline
-
-	(k) &	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ \\ \hline
-	\end{tabular}
-	\caption{Genus 0 Base Cases}
-	\label{table:g-0-base-cases}
-\end{table}
-}
-
-%\noindent
-%Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
-%{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
-%\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
-%(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
-%$\initial(I')$ is minimally generated by products of two monomials.
-\end{lem}
-
-\begin{proof}
-Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
-the remaining cases, we follow a similar method to find a
-presentation satisfying the desired conditions. The log spin
-canonical ring $R(\sx', 0, L')$ is generated as a $k$-algebra by
-elements of degree at most $e$ with relations in degree at most $2e$
-for each case as described in the Table ~\ref{table:g-0-base-cases-degrees}.
-\begin{table}
-\begin{tabular}
-	{| c || c | c | c |}
-	\hline
-	Case & Generator Degrees & Degrees of Relations & $e$\\
-	\hline
-	\hline
-
-	(a) & $\{3, 7, 9, 11\}$ & $\{14, 18\}$ & $11$ \\	\hline
-
-	(b) & $\{3, 5, 7, 9\}$ & $\{12, 14\}$ & $9$ \\ \hline
-
-	(c) & $\{3, 5, 7, 7\}$ & $\{10, 14\}$ & $7$ \\ \hline
-
-	(d) & $\{3, 5, 5, 7\}$ & $\{10, 12\}$	& $7$ \\ \hline
-
-	(e) & $\{3, 5, 5, 7, 7\}$ & $\{10, 10, 12, 12, 14\}$	& $7$ \\ \hline
-
-	(f) & $\{3, 5, 5, 7, 7, 7\}$ & $\{10, 10, 10, 12, 12, 12, 14, 14, 14\}$	& $7$ \\ \hline
-
-	(g) & $\{3, 3, 4, 5\}$ & $\{8, 9\}$ & $5$ \\ \hline
-
-	(h) & $\{3, 3, 4, 5, 5\}$ & $\{8, 8, 9, 9, 10\}$ & $5$ \\ \hline
-
-	(i) & $\{3, 3, 4, 5, 5, 5\}$ &
-	$\{8, 8, 8, 9, 9, 9, 10, 10, 10\}$ & $5$ \\ \hline
-
-	(j) & $\{3, 3, 4, 5, 5, 5, 5\}$ &
-	$\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\}$ & $5$ \\ \hline
-
-	(k) &	$\{3, 3, 3, 4, 4, 5\}$ & $\{6, 7, 7, 8, 8, 8, 9, 9, 10\}$ & $5$ \\ \hline
-	\end{tabular}
-	\caption{Generators and Relations for Genus 0 Base Cases}
-	\label{table:g-0-base-cases-degrees}
-\end{table}
-
-We can also always find a presentation for these cases such that
-they satisfy \ref{custom:Ad-i} and \ref{custom:Ad-ii} and that $\initial(I')$ is
-generated by products of two monomials. Again, the procedure to
-verify these is similar to that in Example
-~\ref{eg:base-0-377}.
-
-Furthermore, each case always satisfies \ref{custom:Ad-iii} as demonstrated in table ~\ref{table:g-0-base-cases-admissibility}.
-Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
-for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i L
-\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ are
-independent of the choice of $i$.
-
-\begin{table}
-\begin{tabular}
-	{| c | c | c || c | c |}
-	\hline
-	Case & Signature $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
-	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
-	\hline
-	\hline
-
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $1$ & $0$ \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $3$ & $0$ \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $2$ & $0$ \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $3$ & $0$ \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $4$ & $0$ \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ & $0$ \\ \hline
-
-	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ & $0$ \\ \hline
-\end{tabular}	
-	\caption{Checking \ref{custom:Ad-iii} for Genus 0 Base Cases}
-	\label{table:g-0-base-cases-admissibility}
-\end{table}
-
-Thus, all of the cases are admissible and satisfy the additional
-desired conditions.
-\end{proof}
-
-%Now we can use Lemma ~\ref{lem:sat-3}, Lemma
-%~\ref{lem:raise-stacky-order}, and Corollary
-%~\ref{cor:raise-stacky-order} to induct from the cases of Table
-%~\ref{table:g-0-base-cases} and obtain the desired bounds on the
-%generator and relation degrees for log spin canonical rings of
-%genus 0 curves. This process will be carried out in Subsection
-%~\ref{ssec:g-0-main}.
-%\todo{Peter: I don't think this paragraph should be here.
-It seems like its kind of redundant given section 7.4.
-Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}
-
-%Through the application of two inductively adding 
-%points via Lemma ~\ref{lem:sat-3} and inductively raising
-%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
-%we obtain Theorem ~\ref{thm:g-0-main} for any
-%log spin curve $(\sx, \Delta, L)$ with
-%signature $\sigma$ covered by this induction process.
-%In particular, this induction process covers all signatures $\sigma
-%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
-%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
-%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
-%Before we prove the main theorem, we describe the cases not be
-%covered by induction.
-
-\ssec{Exceptional Cases}
-\label{ssec:g-0-exceptional}
-In this subsection, we describe the cases that are not covered by induction, which are also the only exceptions to Theorem ~\ref{thm:main} in the case $g = 0$.
-In table ~\ref{table:g-0-exceptional} We present the explicit generators and relations for the remaining
-cases given by signatures in the finite set
-
-\begin{align*}
-	S &:= \{(0; 3, 3, k; 0) : 3 \leq k \leq 9 \text{ odd}\} \\
-		&\cup \{(0; 3, 5, 5; 0) ,(0; 3, 5, 7; 0), (0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
-\end{align*}
-
-\begin{table}
-\begin{tabular}
-	{| c || c | c | c |}
-	\hline
-	Signature $\sigma$ & Generator Degrees & Degrees of Relations & $e$ \\
-	\hline
-	\hline
-
-	$(0; 3, 3, 3; 0)$ & $\{3\}$ & $\emptyset$ & $5$ \\	\hline
-
-	$(0; 3, 3, 5; 0)$ & $\{3, 10, 15\}$ & $\{30\}$ & $5$ \\	\hline
-
-	$(0; 3, 3, 7; 0)$ & $\{3, 7, 12\}$ & $\{24\}$ & $7$ \\	\hline
-
-	$(0; 3, 3, 9; 0)$ & $\{3, 7, 9\}$ & $\{21\}$ & $9$ \\	\hline
-
-	$(0; 3, 5, 5; 0)$ & $\{3, 5, 10\}$ & $\{20\}$ & $5$ \\	\hline
-
-	$(0; 3, 5, 7; 0)$ & $\{3, 5, 7\}$ & $\{17\}$ & $7$ \\	\hline
-
-	$(0; 5, 5, 5; 0)$ & $\{3, 5, 5\}$ & $\{15\}$ & $5$ \\	\hline
-
-	$(0; 3, 3, 3, 3; 0)$ & $\{3, 3, 4\}$ & $\{12\}$ & $5$ \\	\hline
-\end{tabular}
-	\caption{Genus 0 Exceptional Cases}
-	\label{table:g-0-exceptional}
-\end{table}
-
-\begin{rem}
-These cases give all of the exceptions to the $e$ and $2e$ bounds
-on the generator and relation degree. Notice that each of these
-exceptional cases, apart from $(0; 3, 5, 7; 0)$, also has
-exceptional saturation as seen in Table ~\ref{table:g-0-sat}.
-Intuitively, these exceptional saturations can be viewed as ``
-forcing'' generators and relations in higher degrees than expected.
-\end{rem}
-
-\ssec{Main Theorem for Genus Zero}
-\label{ssec:g-0-main}
-Now we can combine the base cases from Subsection \ref{ssec:g-0_base} with the inductive lemmas of Section \ref{sec:induction}.
-
-\begin{thm}
-\label{thm:g-0-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve,
-so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
-Then, the log spin canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, L)
-\end{align*}
-
-\noindent
-is generated as a $k$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
-so long as $\sigma$ does not lie in the finite list of exceptional
-cases in Table ~\ref{table:g-0-exceptional}.
-\end{thm}
-
-\begin{proof}
-If $\sx$ has no stacky points, then we can assume that $\halfcan \sim
-n \cdot \infty$ with $n \in \BZ_{\geq -1}$. This is a classical
-case which is done by Voight and Zureick-Brown \cite[Section 4.2]
-{vzb:stacky}. When $n = -1$, then $R_\halfcan = k$.  When $n = 0$,
-then $R_\halfcan = k[x]$.  When $n > 0$, inductively applying Lemma
-\ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1
-with relations generated in degree 2.
-
-First, let us consider the case when $\delta \geq 2$. In any such
-case, $\lfloor \halfcan \rfloor$ is an effective divisor and the
-conditions of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can
-apply the Lemma ~\ref{lem:sat-1} inductively from the classical
-case with no stacky points to get that $R(\sx, \Delta, \halfcan)$
-is generated up to degree $e$.
-
-By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the
-case $\delta = 0$, so $\halfcan$ is not necessarily effective. Let
-the signature $\sigma$ be such that it is not one of the
-exceptional cases contained in Table ~\ref{table:g-0-exceptional}. 
-We get the following three cases, depending on the value of $r$:
-
-\vskip.1in
-\noindent
-{\sf Case 1: $r < 3$}
-
-If $r < 3$, then $\deg 
-\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
-trivial case where $R(\sx, \Delta, \halfcan) = k$.
-
-\vskip.1in
-\noindent
-{\sf Case 2: $3 \le r \le 5$}
-
-If $3 \le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
-then we may apply Lemma ~\ref{lem:g-0-admissible-cases} and
-Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
-from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
-\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
-\ldots, e_r)$ with relations generated up to degree $2e$.
-
-\vskip.1in
-\noindent
-{\sf Case 3: $r > 5$}
-
-If $r > 5$, then we can use Lemma
-~\ref{lem:sat-3} to add stacky points with
-stabilizer order $3$ to case (k) of Table
-~\ref{table:g-0-base-cases}, which corresponds to $(\sigma
-= (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\})$. This case
-satisfies the conditions of Lemma
-~\ref{lem:sat-3} (recall from Table ~\ref
-{table:g-0-sat} that $\sat(\Eff(\sigma)) = 3$), and the
-immediate consequence of parts (a) and (c) of Lemma
-~\ref{lem:sat-3} is that any $R(\sx', \Delta,
-\halfcan')$ corresponding to signatures $\sigma'$ with ramification
-orders all equal to $3$ for any $r > 5$ is generated up to
-degree $e' := \max(5, e_1', \ldots, e_r')$ with relations generated
-up to degree $2e'$. Furthermore, these cases satisfy all of the
-conditions of Lemma ~\ref{lem:raise-stacky-order}. Now we can
-apply Corollary ~\ref{cor:raise-stacky-order} to deduce that
-$R(\sx, \delta, \halfcan)$ is generated up to degree $e :=
-\max(5, e_1, \ldots, e_r)$ with relations generated up to degree
-$2e$.
-\end{proof}
-
-\section{Further Research}
-\label{sec:further-questions}
-
-In this section, we present several directions for further research.
-
-\begin{enumerate}
-	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
-		proof of Theorem ~\ref{thm:main} 
-		%given in this paper 
-		gives an 
-		explicit procedure for computing the generators and relations of $R_
-		\halfcan$ when the genus of $X$ is $0$ or $1$.
-		\begin{question}
-		\label{ques:algorithm}
-			Is there an explicit procedure for computing the generators 
-			and relations for an arbitrary genus $g \geq 2$ curve?
-		\end{question}
-		Suppose the generators and relations of $R_{\halfcan_X}$ are known, 
-		where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the 
-		coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor 
-		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
-		algorithm for inductively determining the generators of $\halfcan$. 
-		This reduces Question \ref{ques:algorithm} to the 
-		following Petri-like question:
-		\begin{question}
-		\label{ques:spin-canonical-petri}
-			Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical 
-			divisor $L \in \di X$, can one write down a set of minimal 
-			generators and minimal relations for $R_\halfcan$?
-		\end{question}
-
-\item One direction for further research is to 
-		extend the results of this paper to divisors $D \in \di \sx$ on a 
-		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors translate to rings of fractional weight $\frac{2}{n}$ modular 
-		forms. A {\bf modular form 
-		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
-		line bundle $\eta$ so that there exists a line bundle $\gamma$ with 
-$\gamma^{\otimes a} \cong \eta$
- and 
- $\gamma^{n} \cong \Omega_{X(p)}^1$.
-		For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
-		[$\mathsection$ 6]{milnor:fractional-weight}.
-
-\begin{question}
-		\label{ques:fractional-weight}
-			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
-			where $K$ is the canonical divisor of $\sx$, can one bound the 
-			degrees of generators and relations of $R_D$?
-		\end{question}
-		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
-		gives an affirmative answer to this question: If $\sx$ has signature 
-		$(g; e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
-		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
-		$2e$. 
-		It may be possible to modify the proof of Lemma
-		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
-		weight modular forms. 
-		Suitable generalizations of the 
-		lemmas of Section ~\ref{sec:induction} might allow one to 
-		follow similar questions to this paper and provide a general 
-		answer to Question ~\ref{ques:fractional-weight}.
-
-	\item Voight and Zureick Brown define
-		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
-		encapsulates the idea of whether the relations for $R_\halfcan$ are 
-		generically chosen, in a precise sense. 
-		The proof of Theorem
-		~\ref{thm:main} is decidedly non-generic. 
-		In particular, Lemma ~\ref{lem:raise-stacky-order} 
-		constructs generators with non-maximal pole orders at certain 
-		points, making the relations non-generic. 
-		\begin{question}
-		\label{ques:generic-initial}
-			If $(\sx, \Delta, \halfcan)$ is a log spin curve, can one write down the
-			generic initial ideal explicitly?
-		\end{question}
-	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
-		the work of Reid \cite[Theorem 3.4]{reid:infinitesimal}. We use his 
-		proof that the 
-		spin canonical ring is generated in degree at most 5 with
-		relations in degree at most 10 in the 			
-		non-log, non-stacky case when genus is at least 2. We extend this 
-		bound of 5 and 10 to the log case, and then apply our inductive 
-		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  However, Reid in fact proves something slightly stronger \cite[Theorem 3.4]{reid:infinitesimal}: that in 
-		most cases his bound is actually 3 and 6 with well-characterized 
-		exceptions.
-		Generalizing this slightly stronger bound to the (non-stacky) log case case would allow us to inductively apply the lemmas from Section ~\ref{sec:induction} and improve Theorem ~\ref{thm:main} as follows:
-		\begin{question}\label{ques:reduce-5,10-to-4,8}
-			When $g \geq 2,$ can the bounds in Theorem \ref{thm:main} on 
-			the degrees of generation and relations can be reduced from 
-			$e = \max(5,e_1, \ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
-			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
-			apart from well a characterized list of exceptions?
-		\end{question}
-		\begin{rem}\label{rem:reduce-3,6}
-			It is unlikely that these bounds can be reduced further to 
-			$e''=\max(3, e_1, \ldots, e_r)$ and $2e''$, 
-			because Lemma \ref{lem:sat-2}'s construction always
-			requires a generator in degree 4 and potentially a relation in 
-			degree 8, when adding a stacky point with stabilizer order 3. 
-%			Perhaps in the non-stacky case, one 
-%			may be able able to generalize the result of Reid \cite[Theorem 3.4
-%			]{reid:infinitesimal} to show that log spin canonical rings can be 
-%			generated in degree at most 3 with relations in degree at most 6, 
-%			apart from a well characterized list of exceptions.
-			\end{rem}
-	\item While Theorem ~\ref{thm:main} gives a set of 
-		generators and relations
-		for the log spin canonical ring $R_\halfcan,$ these sets are not necessarily minimal
-		In many of the $g = 0$ and $g=1$ cases, 
-		it is not too difficult to see that our inductive procedure also 
-		yields a minimal set of relations for $R_\halfcan$. One might investigate 
-		whether the generators and relations given by the inductive proof 
-		of Theorem ~\ref{thm:main} are always minimal.
-		\end{enumerate}
+\ssec{Bounds for Arbitrary Divisors on Projective Space}
 
@@
 \section{Acknowledgments}
+
 We are grateful to David Zureick-Brown for introducing us to the
@@
 providing a great environment for mathematical learning and
-collaboration. We thank Jorge Sentieiro Neves for pointing out the
-bounds given by Miles Reid's work on the maximal degrees of minimal
-generators and relations of spin canonical rings in high genera.
+collaboration.
 Finally, we gratefully acknowledge the financial support given by
@@
 \nocite{*}
-\bibliography{bibliography}{}
+\bibliography{bibliography-stacky-surface}{}
 \bibliographystyle{plain}

### 2015-07-07 stacky_curves_write_up/spin_cring.tex
rename folders, import surfaces files
add surfaces radical ex, address dzb up to 11-1

--- 2015-07-03 stacky_write_up/spin_cring.tex
@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
+Let $\Gamma$ be a {\bf Fuchsian} group, i.e. \todo{tilde?}a discrete subgroup of
 $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
@@
 {dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
-and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
-\cite[Corollary 10.4.6]{vzb:stacky}.
+rings, Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
+and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective.
 Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.
@@
 \label{rem:explicit-generators}
-The proofs of the main theorems in the low genus cases not only
-obtain bounds on the degrees of the generators and relations, but
-also yield explicit systems of generators and an explicit initial ideal of
-relations. Furthermore, our proof of the genus $g \geq 2$ case also
-provides an inductive procedure for explicitly determining the 
-generators and initial ideal of relations of log spin canonical
-rings. Many explicit systems of generators and relations for curves of genus $2 \leq g \leq 15$ are
-detailed in interesting examples by Neves
+The main theorem obtains bounds on the degrees of the generators
+and relations of log spin canonical rings. However, the proof
+of the genus one and genus zero cases also yield explicit systems
+of generators and an explicit initial ideal of relations.
+Furthermore, our proof of the genus $g \geq 2$ case also provides
+an inductive procedure for explicitly determining the generators
+and initial ideal of relations of log spin canonical rings. Many
+explicit systems of generators and relations for curves of genus $2
+\leq g \leq 15$ are detailed in interesting examples by Neves
 \cite[Section III.4]{neves:halfcan}. 
@@
 that $2\halfcan_X \sim K_X + \Delta$). 
-We define $H^0$ of a stacky divisor as follows:
+We define $H^0$ of a stacky divisor as follows.
 
@@
 
-\ssec{Definition of Saturation}
+\ssec{Saturation}
 
@@
 
-In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin canonical divisors.
+Here, we define a notion of admissibility that is quite similar to the admissibility defined by Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}.
+Our notion is an adaptation the case of log spin canonical divisors.
 
@@
 
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan',J)$
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan', J)$
 to be {\bf admissible} if $R'$ admits a presentation
@@
 \geq 0$. It is fairly easy to see, by use of Riemann--Roch, that
-$s := \sat(\Eff(\sigma)) = 5$. Then the map in
-~\eqref{eqn:noether-377} is surjective when $d \geq 21 + s = 26$
-(i.e. $R'$ is generated up to degree 25).
+the saturation of $\halfcan'$ is $5$ (see Definition ~\ref{defn:sat}.
+Then the map in ~\eqref{eqn:noether-377} is surjective when $d \geq
+21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
 
@@
 \label{eg:base-1-33}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ so that $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
 $$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
@@
 The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
+\todo{alt: proj}
 
@@
 First we present several lemmas which provide the inductive steps
-for the proof of the main theorem: Theorem ~\ref{thm:main}. In
+for the proof of the main theorem (Theorem ~\ref{thm:main}). In
 Subsection ~\ref{ssec:add-points} we prove three lemmas which
@@
 Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-Before proving three lemmas that allow us to inductively add points to the support of a log spin canonical divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
+%Before proving three lemmas that allow us to inductively add points to the support of a log spin canonical divisor
+First, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
 This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
@@
 \item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T \succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S,$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
+\item $T \succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
 \item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
@@
 
-\section{Genus $\geq 2$}
+\section{Genus At Least Two}
 \label{sec:g-high}
@@
 
-\ssec{Bounds on Generators and Relations in Genus $\geq 2$}
+\ssec{Bounds on Generators and Relations in Genus At Least Two}
 \label{ssec:bounds-high-genus}
@@
 
-\ssec{Main Theorem for Genus $\geq 2$}
+\ssec{Main Theorem for Genus At Least Two}
 \label{ssec:g-high-main}

### 2015-07-07 stacky_surface_write_up/surface-write-up.tex
add surfaces radical ex, address dzb up to 11-1

@@
 \DeclareMathOperator{\spec}{Spec}
-\captionsetup[table]{belowskip = 4pt}
+%\captionsetup[table]{belowskip = 4pt}
 
@@
 \begin{abstract}
- 	Consider modular forms arising from finite-area
-	quotients of the upper-half plane by Fuchsian groups.  
-	By the classical results of Kodaira--Spencer, 
-	this space of modular forms may be
-	viewed as log spin canonical ring of a stacky curve.
-	In this paper, we tightly bound the degrees of minimal
-	generators and relations of log spin canonical rings and,
-	as a consequence, 
-	obtain a tight bound on the degrees of minimal generators and relations  		
-	for rings of modular forms of arbitrary integral weight.
+ 	Bonding generator and relation degrees of general $\bq$-divisors
+	of surfaces.
 \end{abstract}
@@
 
+\begin{rem}
+When $\langle f_1, \ldots, f_r \rangle = \langle x_0, \ldots, x_n \rangle$ (the irrelevant ideal), we may directly use the hypersurface method by considering $x_0, \ldots, x_n$ instead of the $f_i$'s.
+However, when $\sqrt{\langle f_1, \ldots, f_r \rangle} = \langle x_0, \ldots, x_n \rangle$ (or the saturation), we cannot obtain the same result from our modification of O'Dorney's method as seen in Example ~\ref{eg:radical}.
+Instead we must use ghost points and hypersurfaces.
+\end{rem}
+
+\begin{example}
+\label{eg:radical}
+As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$.
+In degree $595 = 5* 7 * 17$, this has dimension $6$, but we cannot possibly use the lattice approach, as all lower degrees only have dimension 1.
+In fact, we may construct similar examples using any $x_i^m$ for $f_i$ with appropriate coefficients.
+\end{example}
+\todo{construct class of additional examples}
+
+\section{Canonical Rings on \texorpdfstring{$\bp^1 \times \bp^1$}{}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-07 stacky_curves_write_up/spin_cring.tex
address all dzb comments (todo if not resolved)

@@
 Then we have a map $\phi: k[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
-If $P$ is a point in $X$, then $\phi$ defines a graded $P$ lexicographic order {\bf{graded $P$-lex}} on $k[z_1, \ldots, z_m]$ as follows.
+If $P$ is a point in $X$, then $\phi$ defines a graded-$P$-lexicographic order (shortened to {\bf{graded $P$-lex}}) on $k[z_1, \ldots, z_m]$ as follows.
 If $f=\prod_{i=1}^m {z_i}^{q_i}$ and $g=\prod_{i=1}^m {z_i}^{r_i}$ with $f \neq g,$ then $f\prec g$ if one of the following holds:
@@
 
-We can now prove our first lemma for adding points.
+We can now prove the first of three lemmas used to inductively add points.
+\todo{Someone verify if this is a good fix. If someone thinks it's okay then remove this.}
 
@@
 \end{lem}
+
+\todo{replace *** with something else}
 
@@
 
-\begin{align}
-\label{eqn:sat_two_add_generator}
+\begin{align*}
 	S =	& \; \{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
 	\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
-\end{align}
+\end{align*}
 
@@
 
-The following Lemma will slightly strengthen condition \ref{custom:Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+The following lemma will slightly strengthen condition \ref{custom:Ad-ii} from Definition ~\ref{defn:admissible}.
+This improvement is crucial in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
 
@@
 	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subseteq 
-H^0(\sx, e_iL).
+H^0(\sx, e_iL)
 \end{align*}
@@
 In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations.
-The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
+In this section, we do not obtain explicit presentations of $R_\halfcan$.
+This contrasts with Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations.
+The tradeoff is that in the genus zero and genus one cases, we have to deal with explicit base cases.
+In this section we apply general results.
 
@@
 \label{lem:generation-5}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g; --;\delta)$
 with $g \geq 2$ and $\Delta > 0.$ Let $s_1$, $s_2 \in H^0(X, 2L)$
@@
 \end{lem}
+
+\todo{make clear what dash means}
 
@@
 \begin{proof}
-As the base case, let $\halfcan=\halfcan_X \in \di X$ satisfy $2\halfcan \sim 2 K_X + \Delta$.
+As the base case, let $\halfcan = \halfcan_X \in \di X$ satisfy $2 \halfcan \sim 2 K_X + \Delta$.
 By Corollary ~\ref{cor:g-2-presentation-bound}, the theorem holds for $(\sx, \Delta,
@@
 Next, suppose the theorem holds for $\halfcan' = \halfcan_X + \sum_{i=1}^{r-1} \frac{1}{3}P_i$.
-Take a log spin canonical divisor of the form $\halfcan = \halfcan_X + \sum_{i=1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
+Let $\halfcan$ be a log spin canonical divisor of the form $\halfcan = \halfcan_X + \sum_{i = 1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
 If $P_r$ is a basepoint of $\halfcan'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
@@
 
-We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g\ge 2$ and signature $(g;3, \ldots, 3;\delta)$. Therefore, by Corollary 
+We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g \ge 2$ and signature $(g; 3, \ldots, 3; \delta)$. Therefore, by Corollary 
 ~\ref{cor:raise-stacky-order}, this theorem 
-holds for all log spin curves $(\sx, L, J)$. 
+holds for all log spin curves $(\sx, \Delta, \halfcan)$. 
 \end{proof}
@@
 	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	\halfcan' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
@@
 \end{tabular}
+
 \caption{Genus 1 Base Cases}
@@
 \end{table}
+\todo{make tables slightly taller}
+\todo{L apostrophe vs L dash}
 
@@
 \end{tabular}
+
 \caption{Genus 1 Exceptional Cases}
@@
 First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
+Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan = \halfcan' + P$.
 
@@
 Either we should reword it or remove it (feel free to disagree, of course)}
-
-Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan= \halfcan'+P$.
 
@@
 \end{tabular}
+
 \caption{Genus 0 Saturation}
@@
 \end{table}
+\todo{make tables slightly taller}
 
@@
 \end{tabular}
+
 \caption{Genus 0 Base Cases}
@@
 }
+\todo{make tables slightly taller}
 
@@
 \end{tabular}
+
 \caption{Generators and Relations for Genus 0 Base Cases}
@@
 \end{tabular}
+
 \caption{Checking \ref{custom:Ad-iii} for Genus 0 Base Cases}
@@
 \end{tabular}
+
 \caption{Genus 0 Exceptional Cases}
@@
 			apart from well a characterized list of exceptions?
+			\todo{list of families}
 		\end{question}

### 2015-07-07 stacky_curves_write_up/spin_cring.tex
middle of editing todos

@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, i.e. \todo{tilde?}a discrete subgroup of
+Let $\Gamma$ be a {\bf Fuchsian} group, i.e.,~ a discrete subgroup of
 $PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
@@
 The results of this paper can be easily couched in terms of the language of stacks.
-If one works over an arbitrary field $k$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.
-the residue field of each
+If one works over an arbitrary field $k$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.,~ the residue field of each
 of the stacky points is separable.
@@
 semi-canonical divisor, or theta characteristic) associated to the
-coarse space $X$ of $\sx.$  (i.e. $\halfcan_X$ is a divisor such
+coarse space $X$ of $\sx.$  (i.e.,~ $\halfcan_X$ is a divisor such
 that $2\halfcan_X \sim K_X + \Delta$). 
@@
 Then the map in ~\eqref{eqn:noether-377} is surjective when $d \geq
-21 + s = 26$ (i.e. $R'$ is generated up to degree 25).
+21 + s = 26$ (i.e.,~ $R'$ is generated up to degree 25).
 
@@
 
-\begin{rem}
-\label{rem:base-0-377}
-Examples ~\ref{eg:base-0-377} and \ref{eg:base-1-33} are used as inductive base cases in the genus 0 and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
-\end{rem}
-
 \begin{example}
 \label{eg:exception-1-5}
-Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
+Let $(\sx', 0, L')$ be a log spin curve of genus 1 with $L' = P -
  Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_L)_2$ be any nonzero element.
@@
 In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring whose $k$th graded piece has the same dimension of $R_\halfcan$.
-The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
-\todo{alt: proj}
+One can then check that the generators and relation determine a ring $R$ so that for all $j \in \BZ,$ the $j$th graded component $(R)_j$ satisfies $\dim_k (R)_j = \dim_k R_\halfcan.$ Hence, $R \cong R_\halfcan$.
+\todo{Ask David why he suggests $\proj R \cong X$?
+It seems like this is not enough to know it is the half canonical ring if there aren't enough generators.} The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
 
@@
 \end{example}
+
+\begin{rem}
+\label{rem:base-0-377}
+Examples ~\ref{eg:base-0-377}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} are used as inductive base cases in the genus 0, genus 1, and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
+\end{rem}
 
@@
 
-We can now prove the first of three lemmas used to inductively add points.
-\todo{Someone verify if this is a good fix. If someone thinks it's okay then remove this.}
+We next prove the first of three lemmas used to inductively add points.
 
@@
 	\begin{enumerate}
-		\item[\customlabel{custom:sat-1-*}{(*)}] $\sum_{j = 1}^i a_j c_j \ge c_{i+1}$, \\
-		\item[\customlabel{custom:sat-1-**}{(**)}] there does not exist $(b_1, \ldots b_i) \ne (a_1,
+		\item[\customlabel{custom:sat-1-*}{(U-1)}] $\sum_{j = 1}^i a_j c_j \ge c_{i+1}$, \\
+		\item[\customlabel{custom:sat-1-**}{(U-2)}] there does not exist $(b_1, \ldots b_i) \ne (a_1,
 			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
 			c_j \ge	c_{i + 1}$, \\
-		\item[\customlabel{custom:sat-1-***}{(***)}] there does not
+		\item[\customlabel{custom:sat-1-***}{(U-3)}] there does not
 			exist $r<i$ such that $\sum_{j=1}^r a_j c_j> c_{r + 1}$.
@@
 \end{lem}
-
-\todo{replace *** with something else}
 
@@
 %Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
-%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
+%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e.,~ $c_i, c_j \le
 %\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
@@
 	%D\sim K_X+\Delta\sim -2\infty+ \Delta
-%\] is a divisor of $X$ (i.e. with 
+%\] is a divisor of $X$ (i.e.,~ with 
 %possibly negative integer coefficients). Since $\Delta$ is non-
@@
 \label{lem:generation-5}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; --;\delta)$
+Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta),$ {\rm(}where $-$ means $X$ is a bona fide scheme and has no stacky points,{\rm)}
 with $g \geq 2$ and $\Delta > 0.$ Let $s_1$, $s_2 \in H^0(X, 2L)$
@@
 \end{lem}
-
-\todo{make clear what dash means}
 
@@
 	\hline
-	\halfcan' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\ [2pt]
 	\hline
@@
 \end{table}
+
 \todo{make tables slightly taller}
-\todo{L apostrophe vs L dash}
 
@@
 	\hline
-	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
@@
 the cases in Table ~\ref{table:g-0-base-cases} satisfy the
-conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e. either $(\sx',
+conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e.,~ either $(\sx',
 \halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}

### 2015-07-07 stacky_curves_write_up/spin_cring.tex
finished clearing todos except for 1

@@
 \captionsetup[table]{belowskip = 4pt}
+
+\renewcommand{\arraystretch}{1.2}
 
@@
 	\hline
-	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\ [2pt]
+	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
@@
 \end{table}
-
-\todo{make tables slightly taller}
 
@@
 \end{table}
-\todo{make tables slightly taller}
-\todo{L apostrophe vs L dash}
-
 %\begin{rem}
@@
 \end{table}
-\todo{make tables slightly taller}
 
@@
 }
-\todo{make tables slightly taller}
 
@@
 			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
-			apart from well a characterized list of exceptions?
-			\todo{list of families}
+			apart from well a characterized list of families?
 		\end{question}

### 2015-07-07 curves-write-up/spin_cring.tex
folder name changes

--- 2015-07-07 stacky_curves_write_up/spin_cring.tex
@@
 One can then check that the generators and relation determine a ring $R$ so that for all $j \in \BZ,$ the $j$th graded component $(R)_j$ satisfies $\dim_k (R)_j = \dim_k R_\halfcan.$ Hence, $R \cong R_\halfcan$.
-\todo{Ask David why he suggests $\proj R \cong X$?
-It seems like this is not enough to know it is the half canonical ring if there aren't enough generators.} The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
+The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
 
@@
 \end{rem}
-
+\todo{Some examples to add: possibly move one of the later examples up, possibly discuss adding one stacky point to a log divisor on $\BP^1$ without}
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive lemmas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-07 curves-write-up/spin_cring.tex
flip order of examples in curves, needs details
minor example edits

@@
 \begin{example}
+\label{eg:base-1-33}
+Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
+and that $(\sx', \halfcan', \{1,2\})$ is admissible.
+
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
+Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
+
+Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
+$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
+The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
+\todo{fill in details here.
+Use Generalized Max Noether Theorem for genus 1 curves (see Voight and Zureick-Brown \cite[Lemma 3.1.3]{vzb:stacky}.}
+
+We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
+We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
+Hence, \ref{custom:Ad-i} holds.
+We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
+Here, by construction
+\[
+\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
+	0 &\text{ if }z \in \{u, y_3\}\\
+	\frac{1}{4} &\text{ if }z = y_4
+\end{cases}.
+\]
+Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
+Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
+\end{example}
+
+\begin{example}
 \label{eg:base-0-377}
@@
 
-By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
+By the Generalized Max Noether Theorem for genus 0 curves (see Voight
 and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
@@
 in the degrees of the exceptions $d \in \{8, 12, 21\}$.
-Checking the remaining cases via pole degrees shows that
-these degrees are also generated in lower degrees,
-so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.
+Checking these remaining cases via pole degree considerations shows
+that these degrees are also generated in lower degrees. Thus, $R'$
+is generated in degrees $\{3, 5, 7, 7\}$.
 
@@
 %since $e_i = 9 > e$ for all $i \in J$.
-\end{example}
-
-\begin{example}
-\label{eg:base-1-33}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx', \halfcan', \{1,2\})$ is admissible.
-
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
-Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
-
-Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
-The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
-
-We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
-We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{custom:Ad-i} holds.
-We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
-Here, by construction
-$$
-\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4
-\end{cases}.$$
-Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
 \end{example}

### 2015-07-07 curves-write-up/spin_cring.tex
flip examples back, work on beamer

@@
 
+\newcommand{\GL}{\operatorname{GL}}
+\newcommand{\SL}{\operatorname{SL}}
+\newcommand{\PGL}{\operatorname{PGL}}
+\newcommand{\PSL}{\operatorname{PSL}}
+
 \renewcommand{\arraystretch}{1.2}
@@
 Let $\Gamma$ be a {\bf Fuchsian} group, i.e.,~ a discrete subgroup of
-$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
+$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
 linear transformations, such that $\Gamma \backslash \BH$ has finite area.
@@
 \begin{example}
-\label{eg:base-1-33}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx', \halfcan', \{1,2\})$ is admissible.
-
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
-Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
-
-Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
-The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
-\todo{fill in details here.
-Use Generalized Max Noether Theorem for genus 1 curves (see Voight and Zureick-Brown \cite[Lemma 3.1.3]{vzb:stacky}.}
-
-We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
-We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{custom:Ad-i} holds.
-We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
-Here, by construction
-\[
-\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4
-\end{cases}.
-\]
-Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
-\end{example}
-
-\begin{example}
 \label{eg:base-0-377}
@@
 \begin{example}
+\label{eg:base-1-33}
+Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
+$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
+and that $(\sx', \halfcan', \{1,2\})$ is admissible.
+
+Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
+Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
+Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
+
+Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
+$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
+The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
+
+We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
+We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
+Hence, \ref{custom:Ad-i} holds.
+We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
+Here, by construction
+\[
+\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
+	0 &\text{ if }z \in \{u, y_3\}\\
+	\frac{1}{4} &\text{ if }z = y_4
+\end{cases}.
+\]
+Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
+Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
+\end{example}
+
+\begin{example}
 \label{eg:exception-1-5}
@@
 \todo{Some examples to add: possibly move one of the later examples up, possibly discuss adding one stacky point to a log divisor on $\BP^1$ without}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive lemmas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-07 stacky_curves_write_up/spin_cring.tex
changes in wrong folder

@@
 \begin{example}
+\label{eg:}
+In this example, we shall compute the log canonical ring of $(\sx, 3 \cdot \infty, L),$ where $\sx$ has coarse space $X$, signature $(0;3;3),$ and under the identification $X \cong \BP^1$ the closed point $\infty$ in $X$ is the point in the complement of one of the affine coordinate charts.
+Let the single stacky point of $\sx$ be $P \neq \infty$.
+
+Following the technique which will later be introduced in Lemma ~\ref{lem:sat-1}, we deduce the structure of $R_L$ from the structure of the canonical ring of $R_{L_X},$ the canonical ring associated to the log spin curve of the coarse space, $(X, 3 \cdot \infty, L_X).$ Note that $R_{L_X} \cong k[x_1,x_2]$ where $\deg x_1 = \deg x_2 = 1.$ To see this, observe that by Riemann--Roch $h^0(X, L_X) = 2,$ so we will need two generators in degree 2.
+From the Generalized Max Noether Theorem for genus 0 curves, (see Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky},) the multiplication maps are surjective, implying that $R_{L_X}$ is generated in degree 1.
+There cannot be any relations because $\proj k[x_1,x_2] \cong \proj R_{L_X} \cong X$ and $X$ is 1 dimensional.
+Any relation would necessarily imply that $\proj R_{L_X}$ is at most $0$ dimensional, contradicting the fact that $L_X$ is very ample, so $\proj R_{L_X} \cong X$ is $1$ dimensional.
+
+Next, we construct the canonical ring of $R_L$ from $R_{L_X}$.
+By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1.$ We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
+\begin{align*}
+	R_L \cong k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))
+\end{align*}
+Indeed, such a relation must exist, because by Riemann--Roch, $h^0(\sx,4L)$
+
+\end{example}
+
+\begin{example}
 \label{eg:base-0-377}
@@
  and 
- $\gamma^{n} \cong \Omega_{X(p)}^1$.
+ $\gamma^{\otimes n} \cong \Omega_{X(p)}^1 \otimes \sco_{X(p)}(\Delta)$.
 		For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite

### 2015-07-07 beamer-curves/11_UNC_canonical-stacky/slides/slide00200.tex

\begin{frame}{Log canonical map/ring}

  \begin{definition}
    The \textbf{canonical map} $\phi_K\colon C \to \P^{g-1}$ is given by $P
    \mapsto [\omega_1(P):\ldots:\omega_g(P)]$.
  \end{definition}

(An embedding iff $C$ is not hyperelliptic.)

  \begin{block}{Facts}

\[C \cong \Proj R_{X,\Delta} \cong  \Proj  \bigoplus_k H^0(X, \Omega^1(\Delta)^{\otimes k}) \]

  \end{block}
  \begin{block}{Facts}
The relations among $R_{X,1}$ are the defining equations of $\phi_K(C)$.
  \end{block}

\end{frame}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ZBVoight-UNC-canonical-stacky"
%%% End:

### 2015-07-07 curves-write-up/spin_cring.tex

@@
 Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+\end{example}
+
+\begin{example}
+\label{eg:}
+In this example, we shall compute the log canonical ring of $(\sx, 3 \cdot \infty, L),$ where $\sx$ has coarse space $X$, signature $(0;3;3),$ and under the identification $X \cong \BP^1$ the closed point $\infty$ in $X$ is the point in the complement of one of the affine coordinate charts.
+Let the single stacky point of $\sx$ be $P \neq \infty$.
+
+Following the technique which will later be introduced in Lemma ~\ref{lem:sat-1}, we deduce the structure of $R_L$ from the structure of the canonical ring of $R_{L_X},$ the canonical ring associated to the log spin curve of the coarse space, $(X, 3 \cdot \infty, L_X).$ Note that $R_{L_X} \cong k[x_1,x_2]$ where $\deg x_1 = \deg x_2 = 1.$ To see this, observe that by Riemann--Roch $h^0(X, L_X) = 2,$ so we will need two generators in degree 2.
+From the Generalized Max Noether Theorem for genus 0 curves, (see Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky},) the multiplication maps are surjective, implying that $R_{L_X}$ is generated in degree 1.
+There cannot be any relations because $\proj k[x_1,x_2] \cong \proj R_{L_X} \cong X$ and $X$ is 1 dimensional.
+Any relation would necessarily imply that $\proj R_{L_X}$ is at most $0$ dimensional, contradicting the fact that $L_X$ is very ample, so $\proj R_{L_X} \cong X$ is $1$ dimensional.
+
+Next, we construct the canonical ring of $R_L$ from $R_{L_X}$.
+By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1.$ We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
+\begin{align*}
+	R_L \cong k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))
+\end{align*}
+Indeed, such a relation must exist, because by Riemann--Roch, $h^0(\sx,4L)$
+
 \end{example}

### 2015-07-07 curves-write-up/spin_cring.tex
slide name changes, mathbb -> B in curves

--- 2015-07-07 curves-write-up/spin_cring.tex
@@
 Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
-Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \BZ_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 \BQ$-divisor.
-Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
+Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\BP^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
 Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$.
@@
 	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X, \lfloor d\halfcan'
-	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
-	N}.
+	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \BN.
 \end{align}
@@
 We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  
-Notice that if $r\le n$, $\omega_1, \ldots \omega_r\in \mathbb{Z}_{\ge 0}$, and $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_r\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among $c_1, \ldots c_n$ not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
+Notice that if $r\le n$, $\omega_1, \ldots \omega_r\in \BZ_{\ge 0}$, and $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_r\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among $c_1, \ldots c_n$ not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
 Therefore, since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$, which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$.

### 2015-07-07 curves-write-up/spin_cring.tex
added new example

--- 2015-07-07 curves-write-up/spin_cring.tex
@@
 \end{align*}
-Indeed, such a relation must exist, because by Riemann--Roch, $h^0(\sx,4L)$
+First, note that $x_1,x_2,y_{1,3}$ generate all of $R_L$ from the Generalized Max Noether Theorem for genus 0 curves, as described in Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}. That is, the maps
+\begin{align*}
+	H^0(\sx,L) \otimes H^0(\sx,nL) \rightarrow H^0(\sx, (n+1)L)
+\end{align*}
+are surjective.
+Next, note that a relation of the form $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ must exist, because by Riemann--Roch, $h^0(\sx,4L ) - h^0(\sx,4L_X) = 1,$ but $x_1 y_{1,3},x_2 y_{1,3}$ define two linearly independent elements of $h^0(\sx,4L ) \setminus h^0(\sx,4L_X).$ To complete the example, it suffices to show there are no additional relations.
+First, note that $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ is necessarily irreducible because there are no relations among $x_1, x_2$ and $y_{1,3}$ in lower degrees.
+Hence, it follows that $k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) \rightarrow R_L$ is a surjection.
+Furthermore,
+$\proj k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))$ is 1 dimensional and integral, while $\proj R_L$ is also 1 dimensional.
+Therefore, the surjection must be an isomorphism, as claimed.
 

### 2015-07-07 curves-write-up/spin_cring.tex
added O'Dorney MAGMA footnote & acknowledge

@@
 describing base cases (Subsection ~\ref{ssec:g-0_base}), and
-presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
+presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional})
+\footnote{Several computations used to generate the tables in
+Subsection ~\ref{ssec:g-0_base} and Subsection
+~\ref{ssec:g-0-exceptional} were done using a modified version of
+the MAGMA code given in the work of O'Dorney \cite{dorney:canonical}.}
 Finally, we apply inductive processes using Lemma ~\ref{lem:sat-3}
@@
 generators and relations of spin canonical rings in high genera.
+We would also like to mention Evan O'Dorney for enlightening
+conversations regarding his work in this field.
 Finally, we gratefully acknowledge the financial support given by

### 2015-07-07 curves-write-up/spin_cring.tex
edited new example

--- 2015-07-07 curves-write-up/spin_cring.tex
@@
 \begin{example}
-\label{eg:}
-In this example, we shall compute the log canonical ring of $(\sx, 3 \cdot \infty, L),$ where $\sx$ has coarse space $X$, signature $(0;3;3),$ and under the identification $X \cong \BP^1$ the closed point $\infty$ in $X$ is the point in the complement of one of the affine coordinate charts.
-Let the single stacky point of $\sx$ be $P \neq \infty$.
-
-Following the technique which will later be introduced in Lemma ~\ref{lem:sat-1}, we deduce the structure of $R_L$ from the structure of the canonical ring of $R_{L_X},$ the canonical ring associated to the log spin curve of the coarse space, $(X, 3 \cdot \infty, L_X).$ Note that $R_{L_X} \cong k[x_1,x_2]$ where $\deg x_1 = \deg x_2 = 1.$ To see this, observe that by Riemann--Roch $h^0(X, L_X) = 2,$ so we will need two generators in degree 2.
-From the Generalized Max Noether Theorem for genus 0 curves, (see Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky},) the multiplication maps are surjective, implying that $R_{L_X}$ is generated in degree 1.
-There cannot be any relations because $\proj k[x_1,x_2] \cong \proj R_{L_X} \cong X$ and $X$ is 1 dimensional.
-Any relation would necessarily imply that $\proj R_{L_X}$ is at most $0$ dimensional, contradicting the fact that $L_X$ is very ample, so $\proj R_{L_X} \cong X$ is $1$ dimensional.
-
-Next, we construct the canonical ring of $R_L$ from $R_{L_X}$.
-By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1.$ We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
+\label{eg:adding-point}
+In this example, we shall compute the log canonical ring of $(\sx, 3 \infty, L),$ where $\sx$ has coarse space $X$, $\sx$ has signature $(0;3;3),$ and $\infty$ is a fixed closed point of $X,$ different from the stacky point $P_1$ with stabilizer order 3.
+
+Following the technique which will later be introduced in Lemma ~\ref{lem:sat-1}, we deduce the structure of $R_L$ from the structure of the canonical ring of $R_{L_X} := R(X,3 \infty, L_X).$
+
+Note that $R_{L_X} \cong k[x_1,x_2]$ where $\deg x_1 = \deg x_2 = 1.$ To see this, observe that by Riemann--Roch $h^0(X, L_X) = 2,$ so we will need two generators in degree $1$.
+Because $L_X$ is very ample, $R_{L_X}$ is generated in degree 1.
+To conclude, note that, $R_{L_X}$ does not have any relations.
+If there were some relation, then $\dim \proj R_{L_X} < 1$, contradictig the fact that $L_X$ is very ample, so $\proj R_{L_X} \cong X,$ which has dimension 1.
+
+Next, we construct generators and relations for $R_L,$ using those of $R_{L_X}$.
+Note that we have a natural inclusion $\iota:R_{L_X} \hookrightarrow R_L$ induced by the inclusions $H^0(\sx,L_X) \hookrightarrow H^0(\sx,L).$ By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1,$ not in the image of the inclusion $\iota$.
+We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
 \begin{align*}
@@
 \end{align*}
-First, note that $x_1,x_2,y_{1,3}$ generate all of $R_L$ from the Generalized Max Noether Theorem for genus 0 curves, as described in Voight
+First, note that $x_1,x_2,y_{1,3}$ generate all of $R_L$ from the Generalized Max Noether Theorem from Voight
 and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}. That is, the maps
 \begin{align*}
-	H^0(\sx,L) \otimes H^0(\sx,nL) \rightarrow H^0(\sx, (n+1)L)
-\end{align*}
-are surjective.
-Next, note that a relation of the form $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ must exist, because by Riemann--Roch, $h^0(\sx,4L ) - h^0(\sx,4L_X) = 1,$ but $x_1 y_{1,3},x_2 y_{1,3}$ define two linearly independent elements of $h^0(\sx,4L ) \setminus h^0(\sx,4L_X).$ To complete the example, it suffices to show there are no additional relations.
-First, note that $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ is necessarily irreducible because there are no relations among $x_1, x_2$ and $y_{1,3}$ in lower degrees.
-Hence, it follows that $k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) \rightarrow R_L$ is a surjection.
-Furthermore,
-$\proj k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))$ is 1 dimensional and integral, while $\proj R_L$ is also 1 dimensional.
-Therefore, the surjection must be an isomorphism, as claimed.
+	H^0(\sx,3L) \otimes H^0(\sx,(n-3)L) \rightarrow H^0(\sx, nL)
+\end{align*}
+are surjective for $n \geq 4$.
+A relation of the form $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)=0$ must exist because $h^0(\sx,4L ) - h^0(\sx,4L_X) = 1,$ but $x_1 y_{1,3}$ and $x_2 y_{1,3}$ define two
+linearly independent elements with nontrivial image in the 1-dimensional vector space $H^0(\sx,4L )/ H^0(\sx,4L_X).$ So, we obtain a surjection
+\begin{align}
+\label{align:surjection}
+k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) \rightarrow R_L.
+\end{align}
+To complete the example, it suffices to show there are no additional relations.
+First, note that $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ is irreducible because there are no relations among $x_1, x_2$ and $y_{1,3}$ in lower degrees.
+Hence,  $k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))$ is integral and is 2 dimensional.
+Thus, the map \eqref{align:surjection} defines a surjection from an integral 2 dimensional ring to a 2 dimensional ring.
+Therefore, it is an isomorphism.
 

### 2015-07-07 curves-write-up/spin_cring.tex
move citation closer to author in intro

@@
 
-In particular, we bound the degrees of generators and relations of a
-log spin canonical ring. Let
-$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
-e_r; \delta)$. The application of O'Dorney's work to log spin
-canonical rings gives a weak bound in the case $g = 0$ in
-terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
-{dorney:canonical}. In their treatment of log spin canonical
-rings, Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
-and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective.
-Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.
+In particular, we bound the degrees of generators and relations of
+a log spin canonical ring. Let $\sx$ be a stacky curve with
+signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. The application
+of O'Dorney's work \cite[Chapter 5]{dorney:canonical} to log spin
+canonical rings gives a weak bound in the case $g = 0$ in terms of
+the least common multiples of the $e_i$'s. In their treatment of
+log spin canonical rings, Voight and Zureick-Brown
+\cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6
+\cdot \max(e_1, \ldots, e_r)$ and relation degrees by $12 \cdot \max
+(e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
+bounds we write here differ from those stated in Voight and Zureick-
+Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because
+their grading convention differs from ours by a factor of 2.
 

### 2015-07-07 curves-write-up/spin_cring.tex
minor reword before statement of main thm
rewording first 2 pgraphs of new ex & typographical

@@
 cover all cases in all genera. The main theorem of this paper
-gives significantly tighter bounds for any log spin canonical ring on a log spin curve.
+gives significantly tighter bounds for the log spin canonical ring
+of any log spin curve.
 
@@
 \label{eg:adding-point}
-In this example, we shall compute the log canonical ring of $(\sx, 3 \infty, L),$ where $\sx$ has coarse space $X$, $\sx$ has signature $(0;3;3),$ and $\infty$ is a fixed closed point of $X,$ different from the stacky point $P_1$ with stabilizer order 3.
-
-Following the technique which will later be introduced in Lemma ~\ref{lem:sat-1}, we deduce the structure of $R_L$ from the structure of the canonical ring of $R_{L_X} := R(X,3 \infty, L_X).$
-
-Note that $R_{L_X} \cong k[x_1,x_2]$ where $\deg x_1 = \deg x_2 = 1.$ To see this, observe that by Riemann--Roch $h^0(X, L_X) = 2,$ so we will need two generators in degree $1$.
-Because $L_X$ is very ample, $R_{L_X}$ is generated in degree 1.
-To conclude, note that, $R_{L_X}$ does not have any relations.
-If there were some relation, then $\dim \proj R_{L_X} < 1$, contradictig the fact that $L_X$ is very ample, so $\proj R_{L_X} \cong X,$ which has dimension 1.
-
-Next, we construct generators and relations for $R_L,$ using those of $R_{L_X}$.
-Note that we have a natural inclusion $\iota:R_{L_X} \hookrightarrow R_L$ induced by the inclusions $H^0(\sx,L_X) \hookrightarrow H^0(\sx,L).$ By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1,$ not in the image of the inclusion $\iota$.
-We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
+Let $\sx$ be a stacky curve with coarse space $X$ and signature $(0
+; 3; 3)$. Let $P_1$ denote the lone stacky point which has stabilizer
+order $3$ and suppose $\infty$ is a fixed closed point of $X$ that is
+not equal to $P_1$.
+
+We will deduce the structure of the log spin canonical ring $R_L$
+from the structure of the spin canonical ring $R_{L_X} := R(X, 3
+\cdot \infty, L_X)$. This technique will later be generalized
+and encapsulated in the statement and proof of Lemma ~\ref{lem:sat-1}.
+
+Note that $R_{L_X} \cong k[x_1, x_2]$ where $\deg x_1 = \deg x_2 = 1.
+$ To see this, observe that we will need two generators in degree $1$
+because $h^0(X, L_X) = 2$ by Riemann--Roch. Because $L_X$ is very 
+ample, we have that $R_{L_X}$ is generated in degree 1. To
+conclude, note that $R_{L_X}$ does not have any relations. If there
+exists some relation, then $\dim \proj R_{L_X} < 1$. This would
+contradict the fact that $L_X$ is very ample. Thus, $\proj R_{L_X}
+\cong X$ which has dimension 1.
+
+Next, we construct generators and relations for $R_L$ using those
+of $R_{L_X}$. Note that we have a natural inclusion $\iota: R_{L_X}
+\hookrightarrow R_L$ induced by the inclusions $H^0(\sx, L_X)
+\hookrightarrow H^0(\sx, L).$ By Riemann Roch, we see there is some
+element $y_{1, 3} \in (R_L)_3$ with $\ord_{P_1}(y_{1, 3}) = -1,$ not
+in the image of the inclusion $\iota$. We claim that there exist $a_
+1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1, x_2]$
+such that
 \begin{align*}
@@
 \end{align*}
-First, note that $x_1,x_2,y_{1,3}$ generate all of $R_L$ from the Generalized Max Noether Theorem from Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}. That is, the maps
-\begin{align*}
-	H^0(\sx,3L) \otimes H^0(\sx,(n-3)L) \rightarrow H^0(\sx, nL)
-\end{align*}
-are surjective for $n \geq 4$.
-A relation of the form $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)=0$ must exist because $h^0(\sx,4L ) - h^0(\sx,4L_X) = 1,$ but $x_1 y_{1,3}$ and $x_2 y_{1,3}$ define two
-linearly independent elements with nontrivial image in the 1-dimensional vector space $H^0(\sx,4L )/ H^0(\sx,4L_X).$ So, we obtain a surjection
+
+First, note that $x_1, x_2, y_{1,3}$ generate all of $R_L$ from the
+Generalized Max Noether Theorem from Voight and Zureick-Brown
+\cite[Lemma 3.1.3]{vzb:stacky}. That is, the maps
+\begin{align*}
+	H^0(\sx, 3L) \otimes H^0(\sx, (n - 3)L) \rightarrow H^0(\sx, nL)
+\end{align*}
+
+\noindent
+are surjective for $n \geq 4$. A relation of the form $a_1 x_1 y_{1,
+3} +a_2 x_2 y_{1, 3} + f(x_1, x_2) = 0$ must exist because $h^0(\sx
+, 4L) - h^0(\sx, 4L_X) = 1,$ but $x_1 y_{1, 3}$ and $x_2 y_{1, 3}$
+define two linearly independent elements with nontrivial image in
+the 1-dimensional vector space $H^0(\sx, 4L) / H^0(\sx, 4L_X).$ So,
+we obtain a surjection
 \begin{align}
 \label{align:surjection}
-k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) \rightarrow R_L.
+	k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) 
+	\rightarrow R_L.
 \end{align}
-To complete the example, it suffices to show there are no additional relations.
-First, note that $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ is irreducible because there are no relations among $x_1, x_2$ and $y_{1,3}$ in lower degrees.
-Hence,  $k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))$ is integral and is 2 dimensional.
-Thus, the map \eqref{align:surjection} defines a surjection from an integral 2 dimensional ring to a 2 dimensional ring.
-Therefore, it is an isomorphism.
-
+
+To complete the example, it suffices to show there are no
+additional relations. First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
+y_{ 1, 3} + f(x_1, x_2)$ is irreducible because there are no
+relations among $x_1, x_2$ and $y_{1, 3}$ in lower degrees. Hence,
+$k[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} +
+f(x_1, x_2))$ is integral and is 2-dimensional. Thus, the map
+\eqref{align:surjection} defines a surjection from an integral
+2-dimensional ring to a 2-dimensional ring. Therefore, it is an 
+isomorphism.
 \end{example}

### 2015-07-07 curves-write-up/spin_cring.tex
surj arrow to normal arrow in g0 ex
minor example edits (e.g. n->d)

@@
 of $R_{L_X}$. Note that we have a natural inclusion $\iota: R_{L_X}
-\hookrightarrow R_L$ induced by the inclusions $H^0(\sx, L_X)
-\hookrightarrow H^0(\sx, L).$ By Riemann Roch, we see there is some
-element $y_{1, 3} \in (R_L)_3$ with $\ord_{P_1}(y_{1, 3}) = -1,$ not
-in the image of the inclusion $\iota$. We claim that there exist $a_
-1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1, x_2]$
-such that
-\begin{align*}
-	R_L \cong k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))
-\end{align*}
-
-First, note that $x_1, x_2, y_{1,3}$ generate all of $R_L$ from the
-Generalized Max Noether Theorem from Voight and Zureick-Brown
-\cite[Lemma 3.1.3]{vzb:stacky}. That is, the maps
-\begin{align*}
-	H^0(\sx, 3L) \otimes H^0(\sx, (n - 3)L) \rightarrow H^0(\sx, nL)
-\end{align*}
-
-\noindent
-are surjective for $n \geq 4$. A relation of the form $a_1 x_1 y_{1,
-3} +a_2 x_2 y_{1, 3} + f(x_1, x_2) = 0$ must exist because $h^0(\sx
-, 4L) - h^0(\sx, 4L_X) = 1,$ but $x_1 y_{1, 3}$ and $x_2 y_{1, 3}$
+\hookrightarrow R_L$ induced by the inclusions $H^0(\sx, dL_X)
+\hookrightarrow H^0(\sx, dL)$ for each $d \geq 0$. By Riemann Roch,
+we see there is some element $y_{1, 3} \in (R_L)_3$ with $\ord_{P_1}
+(y_{1, 3}) = -1$, not in the image of the inclusion $\iota$. We
+claim that there exist $a_1, a_2 \in k$ and a degree $4$ polynomial
+$f(x_1, x_2) \in k[x_1, x_2]$ such that
+\begin{align*}
+	R_L \cong k[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3}
+	+ f(x_1,x_2))
+\end{align*}
+
+First, note that $x_1, x_2, y_{1, 3}$ generate all of $R_L$ from the
+Generalized Max Noether Theorem for genus zero curves from Voight
+and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}. That is, the maps
+\begin{align*}
+	H^0(\sx, 3L) \otimes H^0(\sx, (d - 3)L) \rightarrow H^0(\sx, dL)
+\end{align*}
+
+\noindent
+are surjective for $d \geq 4$. A relation of the form $a_1 x_1 y_{1,
+3} + a_2 x_2 y_{1, 3} + f(x_1, x_2) = 0$ must exist because $h^0(\sx,
+4L) - h^0(\sx, 4L_X) = 1,$ but $x_1 y_{1, 3}$ and $x_2 y_{1, 3}$
 define two linearly independent elements with nontrivial image in
@@
 \label{align:surjection}
-	k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) 
+	k[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2)) 
 	\rightarrow R_L.
@@
 additional relations. First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
-y_{ 1, 3} + f(x_1, x_2)$ is irreducible because there are no
+y_{1, 3} + f(x_1, x_2)$ is irreducible because there are no
 relations among $x_1, x_2$ and $y_{1, 3}$ in lower degrees. Hence,
@@
 	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	(d - 3) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
 	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
 	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	(d - 7) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
 	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5

### 2015-07-07 curves-write-up/spin_cring.tex
remove done todo
1 change to example 3.2

@@
 from the structure of the spin canonical ring $R_{L_X} := R(X, 3
-\cdot \infty, L_X)$. This technique will later be generalized
-and encapsulated in the statement and proof of Lemma ~\ref{lem:sat-1}.
+\cdot \infty, L_X)$. This technique will later be generalized in Lemma ~\ref{lem:sat-1}.
 
@@
 \end{rem}
-\todo{Some examples to add: possibly move one of the later examples up, possibly discuss adding one stacky point to a log divisor on $\BP^1$ without}
 

### 2015-07-08 curves-write-up/spin_cring.tex
added brian and voight's comments

@@
 
+\todo{Think about John's comment to regrade the ring.}
+\todo{Brian: Don't write out author's name every time.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 presentation as a quotient of a polynomial ring.
+\todo{Brian: Also, sentence 3 of paragraph 1 of the Introduction is debatable (depends on what is meant by “understand”…); e.g., how do you propose to find generators for $M_1(\Gamma)$ when not known to be 0?}
 %of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
@@
 of modular forms into the algebraic category, using a
-generalization of the GAGA principle. By \cite[Proposition 6.1.5]
+generalization of the GAGA principle.
+\todo{brain: The appeal to stacky GAGA on page 1 sweeps a bit under the rug.
+I suppose you noticed (as I just did upon glancing at [14] on the arxiv) that the proof of Prop.
+6.1.5 in [14] seems to pass in silence over the removal of the properness hypothesis (which, in the scheme case — no stacks — requires using something like the little Picard theorem or some other device to deal with avoidance of essential singularities).
+That is moot for you since only the proper case is relevant for your motivation.
+More importantly, since the entire discussion is about spaces of sections of coherent sheaves, one should address stacky GAGA at the level of such $H^0$’s, which is not part of Prop.
+6.1.5 in [14], to have adequately treated the motivation.
+On line -1 of last paragraph on page 1, should say X is proper and geometrically connected over k.
+Note that the proof of Lemma 10.2.1 in [14] gives a thoroughly analytic construction of the line bundle (no ad hoc stuff with divisors), so to link it back to the algebraic case one is using an honest GAGA comparison at the level of categories of coherent sheaves too (with refinement for line bundles).}
+ By \cite[Proposition 6.1.5]
 {vzb:stacky}, there is an equivalence of categories between orbifold
@@
 \]
-
+\todo{Check this takes care of brian's comment 0.}
 Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
-where $\Delta \in \di X$ is a log divisor and $2\halfcan \sim K_X +
+where $\Delta \in \di X$ is a log divisor and $L \in \di \sx$ satisfies $2\halfcan \sim K_X +
 \Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
@@
 Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
+\todo{Explain this in more detail later, as asked by Brian}
 \end{rem}
@@
 \end{cor}
-
+\todo{Add somewhere that if there is an odd $k$ with nonzero weight, it will generally have to occur in weight 3, according to brian 2.}
 \begin{rem}
@@
 \end{rem}
+
+\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0).
+Further, if $L_X$ is effective, then generation will be in weight at most 3.}
 
@@
 \end{rem}
-
+\todo{brain: Although Def.
+2.3 makes sense for any $e_i > 1$, is this the “right” notion when char(k) divides some $e_i$?
+(The “corresponding” stack would not be tame, for example, so I’d be hesitant to think that various notions building on Def.
+2.3 are really appropriate if char(k) divides some $e_i$; of course, the main motivation comes from char.
+0….).}
 \begin{defn}
@@
 called a \textbf{log stacky curve} and the study of their
-canonical rings is the main focus of the work by Voight and Zureick-
-Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
+canonical rings is the main focus of the work by Voight and 
+Zureick-Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
 spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
@@
 When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
-represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
-:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D))$.
+represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, \sco(D))
+:= H^0(\sx, D)$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D)),$ where $\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$
+\todo{Check the above answers brian's objection 4. Also, can $X$ be non-integral, then there might be a problem with the above definition.}
 If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
@@
 \label{def:order-sup}
-If $z$ is a rational section of $\sco(D)$ denote the order of
+Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
 zero of $z$ at $P$ by $\ord_P^D(z)$.
@@
 		line bundle $\eta$ so that there exists a line bundle $\gamma$ with
-$\gamma^{\otimes a} \cong \eta$
+$\gamma^{\otimes a} \cong \eta$ \todo{In item 2 of section 8, I see no reason to specifically focus on X(p).
+(I am also skeptical that the definition given there is appropriate; for weight k/2 with odd k it seems not the right definition.
+I’ve never looked at [2] or [9].)}
  and 

### 2015-07-08 curves-write-up/spin_cring.tex
edited some of brians comments

@@
 
-Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$.
+Let $X$ be a smooth proper geometrically-integral algebraic curve of genus $g$ over a field $k$.
 It is well known that the canonical sheaf $\Omega _X,$ with
@@
 \end{rem}
-\todo{brain: Although Def.
-2.3 makes sense for any $e_i > 1$, is this the “right” notion when char(k) divides some $e_i$?
-(The “corresponding” stack would not be tame, for example, so I’d be hesitant to think that various notions building on Def.
-2.3 are really appropriate if char(k) divides some $e_i$; of course, the main motivation comes from char.
-0….).}
+
 \begin{defn}
@@
 		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors translate to rings of fractional weight $\frac{2}{n}$ modular
-		forms. A {\bf modular form 
-		of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a 
-		line bundle $\eta$ so that there exists a line bundle $\gamma$ with
-$\gamma^{\otimes a} \cong \eta$ \todo{In item 2 of section 8, I see no reason to specifically focus on X(p).
-(I am also skeptical that the definition given there is appropriate; for weight k/2 with odd k it seems not the right definition.
-I’ve never looked at [2] or [9].)}
- and 
- $\gamma^{\otimes n} \cong \Omega_{X(p)}^1 \otimes \sco_{X(p)}(\Delta)$.
-		For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
+		divisors often arise as rings of fractional weight $\frac{2}{n}$ modular
+		forms. For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
 		[$\mathsection$ 6]{milnor:fractional-weight}.

### 2015-07-08 curves-write-up/spin_cring.tex
responded to trivial brian comments

@@
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best
-ways to understand the ring of modular forms is to give a
-presentation as a quotient of a polynomial ring.
-\todo{Brian: Also, sentence 3 of paragraph 1 of the Introduction is debatable (depends on what is meant by “understand”…); e.g., how do you propose to find generators for $M_1(\Gamma)$ when not known to be 0?}
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to desribe the ring $M(\Gamma),$ is to write down a presentation.
 %of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
@@
 \]
-\todo{Check this takes care of brian's comment 0.}
 Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
@@
 := H^0(\sx, D)$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D)),$ where $\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$
-\todo{Check the above answers brian's objection 4. Also, can $X$ be non-integral, then there might be a problem with the above definition.}
 If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$

### 2015-07-08 curves-write-up/spin_cring.tex
moved o(D) definition

@@
 \label{defn:h0-stacky}
+Recall the standard notation 
+$$\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$$
 Let $\sx$ be a stacky curve with coarse space $X$.
 If $D \in \di \sx$ is a Weil divisor, then we define
-
-\[
-	H^0(\sx, D) := H^0(X, \lfloor D \rfloor).
-\]
+\begin{align*}
+	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
+	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
+	h^0(\sx, \sco(D)) &:= \dim_k H^0(\sx, \sco(D))
+\end{align*}
+If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
+graded component of $R$.
+
 \end{defn}
@@
 When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
-represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, \sco(D))
-:= H^0(\sx, D)$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D)),$ where $\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$
-If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
-graded component of $R$.
+represent $R(\sx, \Delta, \halfcan)$.
 

### 2015-07-08 curves-write-up/spin_cring.tex
remark 8.6 changes

@@
 			When $g \geq 2,$ can the bounds in Theorem \ref{thm:main} on 
-			the degrees of generation and relations can be reduced from 
-			$e = \max(5,e_1, \ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
-			$e'=\max(4,e_1, \ldots, e_r)$ and $2e'$, 
+			the degrees of generation and relations be reduced from 
+			$e := \max(5, e_1, \ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
+			$e' := \max(4, e_1, \ldots, e_r)$ and $2e'$, 
 			apart from well a characterized list of families?
@@
 		\begin{rem}\label{rem:reduce-3,6}
-			It is unlikely that these bounds can be reduced further to 
-			$e''=\max(3, e_1, \ldots, e_r)$ and $2e''$, 
-			because Lemma \ref{lem:sat-2}'s construction always
-			requires a generator in degree 4 and potentially a relation in 
-			degree 8, when adding a stacky point with stabilizer order 3. 
+			Note that when $L$ is not effective and $\sx$ has a stacky point, $R_L$ must have a generator in degree 4 with maximal pole order at one of the stacky points.
+Therefore, these bounds cannot in general be reduced further to
+			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e''$.
 %			Perhaps in the non-stacky case, one 

### 2015-07-08 curves-write-up/spin_cring.tex
field k -> \Bk, indices k -> \ell

@@
 \newcommand\BA{{\mathbb A}}
+\newcommand\Bk{{\Bbbk}}
 
@@
 
-Let $X$ be a smooth proper geometrically-integral algebraic curve of genus $g$ over a field $k$.
+Let $X$ be a smooth proper geometrically-integral algebraic curve of genus $g$ over a field $\Bk$.
 It is well known that the canonical sheaf $\Omega _X,$ with
 associated canonical divisor $K_X$, determines the {\bf canonical
-map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
+map } $\pi: X \rightarrow \BP_\Bk^{g - 1}$. Then, the {\bf canonical
 ring} is defined to be
@@
 Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
-field $k$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
+field $\Bk$, so that $\sx$ has signature $\sigma = (g; e_1, \ldots,
 e_r; \delta)$.
 
-Then the log spin canonical ring is generated as a $k$-algebra by 
+Then the log spin canonical ring is generated as a $\Bk$-algebra by 
 elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
@@
 In fact, the proof of Theorem ~\ref{thm:main} holds with $\Delta$ replaced by an arbitrary effective divisor of the coarse space.
- Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
+ Furthermore, one may relax the assumption that $\Bk$ is perfect. Instead, one only need assume that the stacky curve
 is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
@@
 
-For the remainder of this paper, fix an algebraically closed field $k$.
+For the remainder of this paper, fix an algebraically closed field $\Bk$.
 This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closure.
@@
 \label{defn:stacky-curve}
-A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
+A \textbf{stacky curve} $\sx$ over an algebraically closed field $\Bk$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
 
@@
 The results of this paper can be easily couched in terms of the language of stacks.
-If one works over an arbitrary field $k$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.,~ the residue field of each
+If one works over an arbitrary field $\Bk$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.,~ the residue field of each
 of the stacky points is separable.
@@
 \label{defn:div-ex}
-Let $\sx$ be a stacky curve over $k$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
+Let $\sx$ be a stacky curve over $\Bk$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
 P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
@@
 Recall the standard notation 
-$$\sco(D) = \{f \in k(X)^\times : \di f + D \geq 0 \}.$$
+$$\sco(D) = \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
 Let $\sx$ be a stacky curve with coarse space $X$.
@@
 	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
-	h^0(\sx, \sco(D)) &:= \dim_k H^0(\sx, \sco(D))
+	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
 \end{align*}
@@
 \label{defn:monomial-degree}
-Let $k[x_1$, $\ldots$, $x_n]$ be a graded polynomial
+Let $\Bk[x_1$, $\ldots$, $x_n]$ be a graded polynomial
 ring with $\deg x_i = d_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
-k[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
+\Bk[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
 we define the {\bf degree} of $\alpha$ to be
@@
 ^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
-monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
+monomials in $\Bk[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
 \succ_{\text{grevlex}} \beta$ if either
@@
 \label{defn:block-order}
-The \textbf{block term order} is defined as follows. Let $k[y_{1}, \ldots, y_{m}]$ and $k[x_{1}, \ldots,
+The \textbf{block term order} is defined as follows. Let $\Bk[y_{1}, \ldots, y_{m}]$ and $\Bk[x_{1}, \ldots,
 x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = d_i.$ Further assume we are given existing term
@@
 ^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
-\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $k[y_{1},
-\ldots, y_{m}] \otimes$ $k[x_{1}, \ldots, x_{n}]$.
+\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $\Bk[y_{1},
+\ldots, y_{m}] \otimes$ $\Bk[x_{1}, \ldots, x_{n}]$.
 Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
-part of $\alpha$ in $k[y_{1}, \ldots, y_{m}]$ and
+part of $\alpha$ in $\Bk[y_{1}, \ldots, y_{m}]$ and
 likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
@@
 In the \textbf{(graded) block} (or \textbf{elimination}) term
-ordering on $k[y_{d_1', 1}, \ldots, y_{d_m', m}] \otimes k[x_{d_1, 1},
+ordering on $\Bk[y_{d_1', 1}, \ldots, y_{d_m', m}] \otimes \Bk[x_{d_1, 1},
 \ldots, x_{d_n, n}]$, we define $\alpha \succ \beta$ if
@@
 \label{defn:initial-term}
-Let $\prec$ be an ordering on $k[x_{1}$, $\ldots$, $x_{n}]$, 
+Let $\prec$ be an ordering on $\Bk[x_{1}$, $\ldots$, $x_{n}]$, 
 with $\deg x_i = d_i$,
-and let $f \in k[x_{1}, \ldots, x_{n}]$ be a homogeneous
+and let $f \in \Bk[x_{1}, \ldots, x_{n}]$ be a homogeneous
 polynomial. The \textbf{initial term} $\initial(f)$ of $f$
@@
 \label{defn:initial-ideal}
-Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
+Let $I$ be a homogeneous ideal of $\Bk[x_{1}$, $\ldots$,
 $x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
@@
 \label{defn:grobner-basis}
-Let $I$ be a homogeneous ideal of $k[x_{1}$, $\ldots$,
+Let $I$ be a homogeneous ideal of $\Bk[x_{1}$, $\ldots$,
 $x_{n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
@@
 \begin{align*}
-	R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i, e_i'}]_{i \in J} \right)/I'
+	R' \cong \left( \Bk[x_1, \ldots, x_m] \otimes \Bk[y_{i, e_i'}]_{i \in J} \right)/I'
 \end{align*}
@@
 Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
-Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
+Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 
-Note that $R_{L_X} \cong k[x_1, x_2]$ where $\deg x_1 = \deg x_2 = 1.
+Note that $R_{L_X} \cong \Bk[x_1, x_2]$ where $\deg x_1 = \deg x_2 = 1.
 $ To see this, observe that we will need two generators in degree $1$
@@
 (y_{1, 3}) = -1$, not in the image of the inclusion $\iota$. We
-claim that there exist $a_1, a_2 \in k$ and a degree $4$ polynomial
-$f(x_1, x_2) \in k[x_1, x_2]$ such that
-\begin{align*}
-	R_L \cong k[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3}
+claim that there exist $a_1, a_2 \in \Bk$ and a degree $4$ polynomial
+$f(x_1, x_2) \in \Bk[x_1, x_2]$ such that
+\begin{align*}
+	R_L \cong \Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3}
 	+ f(x_1,x_2))
@@
 \label{align:surjection}
-	k[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2)) 
+	\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2)) 
 	\rightarrow R_L.
@@
 relations among $x_1, x_2$ and $y_{1, 3}$ in lower degrees. Hence,
-$k[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} +
+$\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} +
 f(x_1, x_2))$ is integral and is 2-dimensional. Thus, the map
@@
 \[
-	\dim_k H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+	\dim_\Bk H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
 \]
@@
 Let $I$ be the ideal generated by these relations in
-$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
+$\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
 $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
@@
 To demonstrate that these two relations generate all 
-relations, we show that $\dim_k (R')_d = \dim_k
-(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
+relations, we show that $\dim_\Bk (R')_d = \dim_\Bk
+(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
 all degrees $d \geq 0$. In particular,
@@
 \begin{align*}
-	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_d &=
-	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_d \\
-	&= \dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
+	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_d &=
+	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_d \\
+	&= \dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
 	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
@@
 \noindent
-for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left(k[x_{7, 2},
+for all $d \geq 0$. But the fact $\dim_\Bk (R')_d = \dim_\Bk \left(\Bk[x_{7, 2},
 x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
-\rangle\right)_d$ can be checked by looking at the $k$-basis at each degree
+\rangle\right)_d$ can be checked by looking at the $\Bk$-basis at each degree
 $d$.
@@
 Therefore, the canonical ring $R'$ has presentation $R' =
-k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
+\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
 initial ideal $\initial(I)$ generated by quadratics under grevlex
@@
 Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong k[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
+$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
 and that $(\sx', \halfcan', \{1,2\})$ is admissible.
@@
 
-Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
-$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
+Then, there exist constants $\alpha, \beta, \gamma \in \Bk$ so that 
+$R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $\Bk$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
 The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
@@
 We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
---Roch, $\dim_k (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
+--Roch, $\dim_\Bk (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
 element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
@@
 let $y_5 \in (R_\halfcan)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
-we claim there is some $\alpha \in k$ so that
-
-$$R_\halfcan \cong k[x_2 , y_3, y_5]/(y_3^4 - \alpha x_2 y_5^2).$$
+we claim there is some $\alpha \in \Bk$ so that
+
+$$R_\halfcan \cong \Bk[x_2 , y_3, y_5]/(y_3^4 - \alpha x_2 y_5^2).$$
 
 In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring $R$ so that for all $j \in \BZ,$ the $j$th graded component $(R)_j$ satisfies $\dim_k (R)_j = \dim_k R_\halfcan.$ Hence, $R \cong R_\halfcan$.
+One can then check that the generators and relation determine a ring $R$ so that for all $j \in \BZ,$ the $j$th graded component $(R)_j$ satisfies $\dim_\Bk (R)_j = \dim_\Bk R_\halfcan.$ Hence, $R \cong R_\halfcan$.
 The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
@@
 %Before proving three lemmas that allow us to inductively add points to the support of a log spin canonical divisor
-First, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m] \to R_D$.
+First, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $\Bk[x_1, \ldots, x_m] \to R_D$.
 This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
@@
 and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':k[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:k[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
+$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
 \begin{enumerate}
-\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T \succ S\succ k[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S$ which are bigger than all monomials in $k[x_1, \ldots, x_n]${\rm)}
-\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
-\begin{align*}
-	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[x_1, \ldots, x_m]
+\item $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_\halfcan'$
+\item $T \succ S\succ \Bk[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S$ which are bigger than all monomials in $\Bk[x_1, \ldots, x_n]${\rm)}
+\item All monomials in $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
+\begin{align*}
+	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[x_1, \ldots, x_m]
 \end{align*}
@@
 \begin{align*}
-	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]
+	\initial(I) & = \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]
 	+ \langle T \rangle.
@@
 \[
-	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
+	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
 \]
@@
 Now, let $f\in T$.
-Since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in k$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
+Since $S$ forms a $\Bk$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in \Bk$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
 This demonstrates that $\initial(I) \supseteq T$, and hence
 \[
-	\initial(I)\supseteq \initial(I')k[x_1, \ldots, x_m, y_1, \ldots, y_n].
+	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
 \]
@@
 To complete the proof, it suffices to show the reverse inclusion holds.
-By (2), any polynomial $G\in k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
-Furthermore, since $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
+By (2), any polynomial $G\in \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
+Furthermore, since $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
 Therefore,
@@
 \[
-	\initial(I) \cap k[x_1, \ldots, x_m] = \initial(I').
+	\initial(I) \cap \Bk[x_1, \ldots, x_m] = \initial(I').
 \]
 
-By (3), every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
-\begin{align*}
-	\initial(I) & \subseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
+By (3), every monomial of $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
+\begin{align*}
+	\initial(I) & \subseteq \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
 \end{align*}
@@
 Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.
-Then we have a map $\phi: k[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
-If $P$ is a point in $X$, then $\phi$ defines a graded-$P$-lexicographic order (shortened to {\bf{graded $P$-lex}}) on $k[z_1, \ldots, z_m]$ as follows.
+Then we have a map $\phi: \Bk[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
+If $P$ is a point in $X$, then $\phi$ defines a graded-$P$-lexicographic order (shortened to {\bf{graded $P$-lex}}) on $\Bk[z_1, \ldots, z_m]$ as follows.
 If $f=\prod_{i=1}^m {z_i}^{q_i}$ and $g=\prod_{i=1}^m {z_i}^{r_i}$ with $f \neq g,$ then $f\prec g$ if one of the following holds:
@@
 
-\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
+\item[(b)] Choose an ordering $\prec$ on $\Bk[u, x_1, \ldots, x_m]$ such that
 	\[
@@
 	\]
-	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
-	Definition ~\ref{defn:graded-p-lex} and $k[y_1, \ldots, y_n] \otimes k[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
-	\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
+	Equip $\Bk[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
+	Definition ~\ref{defn:graded-p-lex} and $\Bk[y_1, \ldots, y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
+	If $I'$ and $I$ are the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
+	\to R_{\halfcan'}$ and $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
 	\to R_{\halfcan}$ respectively, then
@@
 	\begin{align*}
-		\initial(I) &= \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
+		\initial(I) &= \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
 											 + \langle U_i: 1 \le i \le n-1 \rangle
@@
 
-Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
+Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
 \[
@@
 so $S$ contains elements in degree $d \in \BN$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
-Thus, by dimension counting, $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
+Thus, by dimension counting, $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
 
@@
 We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.
-In part (a), we showed that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving condition (1) of Lemma ~\ref{lem:relations_from_generators_induction}.
-Our choice of monomial order in $k[y_1, \ldots, y_n]$ and block order for $k[y_1, \ldots, y_n]\otimes k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ k[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
+In part (a), we showed that $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving condition (1) of Lemma ~\ref{lem:relations_from_generators_induction}.
+Our choice of monomial order in $\Bk[y_1, \ldots, y_n]$ and block order for $\Bk[y_1, \ldots, y_n]\otimes \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ \Bk[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
 
 It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}.
-To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
+To do this, suppose $f\in \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $\Bk[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
 Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$.
 Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.
-Therefore, $f\in k[u, y_1, \ldots, y_n]$.
-We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.
-That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Therefore, $f\in \Bk[u, y_1, \ldots, y_n]$.
+We note that $S$ generates $y_j \cdot (\Bk[u,y_1, \ldots, y_n])$ as a $\Bk$-algebra.
+That is, all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \[
-	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
+	\Bk[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]\right). 
 \]
-Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $k[u, y_1, \ldots, y_n]$.
+Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $\Bk[u, y_1, \ldots, y_n]$.
 If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
@@
 
-Since the ideal in $k[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\begin{align*}
-				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
-	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
+Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+\begin{align*}
+				& \Bk[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
+	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[u, x_1, \ldots, x_m].
 \end{align*}
@@
 Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann-Roch $\sat(Eff(L'))\le 2$.
-Furthermore, let $R_{\halfcan'} = k[x_2, x_3
+Furthermore, let $R_{\halfcan'} = \Bk[x_2, x_3
 , x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
 3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-Suppose for $i \in \{2, 3\}$, we generically choose $x_i$ satisfying $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$. Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
+Suppose for $i \in \{2, 3\}$, we generically choose $x_i$ satisfying $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$. Choose an ordering on $\Bk[x_2, \ldots, x_m]$ that satisfies
 \begin{align*}
@@
 		$y_3, y_4,$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $k[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
+	\item[(b)] Equip $\Bk[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
 		y_4$
-		and equip the ring $k[y_3, y_4] \otimes k[x_2, \ldots, x_m]$ with block 
+		and equip the ring $\Bk[y_3, y_4] \otimes \Bk[x_2, \ldots, x_m]$ with block 
 		order. Then,
 		\begin{align*}
-			\initial(I) &= \initial(I')k[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
+			\initial(I) &= \initial(I')\Bk[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
 		\end{align*}
@@
 A quick computation checks that
-the following set $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$:
+the following set $S$ is a $\Bk$ basis for $R_\halfcan$ over $R_{\halfcan'}$:
 
@@
 space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
-{\halfcan'} \cong k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
+{\halfcan'} \cong \Bk[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
 {1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
-the ordering on $k[x_3, \ldots, x_m]$ satisfies
+the ordering on $\Bk[x_3, \ldots, x_m]$ satisfies
 \begin{align*}
@@
 		_3, y_4,$ and $y_5$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $k[y_3, y_4, y_5]$ with grevlex so that $y_3 \prec 
+	\item[(b)] Equip $\Bk[y_3, y_4, y_5]$ with grevlex so that $y_3 \prec 
 		y_4 \prec y_5$
-		and equip the ring $k[y_3, y_4, y_5] \otimes k[x_3, \ldots, x_m]$ with the block order.  Then,
-		\begin{align*}
-			\initial(I) &= \initial(I) k[y_3, y_4, y_5, x_3, \ldots, x_m] \\
+		and equip the ring $\Bk[y_3, y_4, y_5] \otimes \Bk[x_3, \ldots, x_m]$ with the block order.  Then,
+		\begin{align*}
+			\initial(I) &= \initial(I) \Bk[y_3, y_4, y_5, x_3, \ldots, x_m] \\
 			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
@@
 
-\noindent forms a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$, which concludes part (a) of the proof.
+\noindent forms a $\Bk$ basis for $R_\halfcan$ over $R_{\halfcan'}$, which concludes part (a) of the proof.
 
@@
 Theorem ~\ref{thm:main}, holds for a curve with signature $(g; e_1',
-\ldots, e_k', e_{k+1}' \ldots, e_r';\delta)$ with $e_{k + 1}' =
+\ldots, e_\ell', e_{\ell + 1}' \ldots, e_r';\delta)$ with $e_{\ell + 1}' =
 \cdots = e_r'$ satisfying certain admissibility (cf. Definition
 ~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for
-a curve with signature $(g; e _1', \ldots, e_k', e_{k + 1}' + 2,
+a curve with signature $(g; e_1', \ldots, e_\ell', e_{\ell + 1}' + 2,
 \ldots, e_r' + 2; \delta)$. 
@@
 		generate $R$ over $R'$.
-	\item[(c)] Endow $k[y_{i, e_i}]_{i\in J}$ and $ k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
-$k[y_{i, e_i}]_{i\in J} \otimes k[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
- block order.  Let $I$ be the kernel of $k[x_1, \ldots, x_m, y_{i, e_i'}, y_{i, e_i}]_{i\in J} \to R$.
+	\item[(c)] Endow $\Bk[y_{i, e_i}]_{i\in J}$ and $ \Bk[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
+$\Bk[y_{i, e_i}]_{i\in J} \otimes \Bk[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
+ block order.  Let $I$ be the kernel of $\Bk[x_1, \ldots, x_m, y_{i, e_i'}, y_{i, e_i}]_{i\in J} \to R$.
   Then,
 		\begin{align*}
-			\initial(I) \;	&= \; \initial(I')k[x, y] \\
+			\initial(I) \;	&= \; \initial(I')\Bk[x, y] \\
 					&+ \; \langle y_{j, e_j}x_i  : 1\le i \le m, j\in J\rangle \\
@@
 To prove (b), it suffices to show that elements of the form $y_{i, e_
-i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $k$-basis for $R_{i}$ over $R_{i-1}$.
+i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $\Bk$-basis for $R_{i}$ over $R_{i-1}$.
 These elements do not lie in $R_{i - 1}$ because the pole order of $y_{i, e_i'}^ay_{i,e_i}^b$ at $Q_i$ is larger than that of any element in the $d^{th}$ component of $R_{i - 1}$.
@@
 \noindent
-Now fix $i \in J$. We check Inequality ~\eqref{eqn:order-degree} holds with $f = y_{i, e_i}z$, implying $y_{i,e_i}z \in R'$ in the three following cases: 
+Now fix $i \in J$. We check that Inequality ~\eqref{eqn:order-degree} holds with $f = y_{i, e_i}z$, implying $y_{i,e_i}z \in R'$ in the three following cases: 
 %$j \notin \{i \} \cup S(i, 0)$, $j = i,$ and $j \in S(i, 0)$.
@@
 We wish to show $f$ is surjective.
-Note that $\dim_k \ker f = \dim_k H^0((n - 2)L) = (n - 3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
-Additionally, $\dim_k V \otimes H^0(nL) = 2 \cdot (n - 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
+Note that $\dim_\Bk \ker f = \dim_\Bk H^0((n - 2)L) = (n - 3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
+Additionally, $\dim_\Bk V \otimes H^0(nL) = 2 \cdot (n - 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
 Therefore,
 \begin{align*}
-	\dim_k \im f 	& = 2 \cdot (n - 1)(g - 1+ \frac{\delta}{2}) - (n - 3)(g - 1 + \frac{\delta}{2})\\
-				& = (n + 1)(g - 1 + \frac{\delta}{2}) = \dim_k H^0((n + 2)L).
+	\dim_\Bk \im f 	& = 2 \cdot (n - 1)(g - 1+ \frac{\delta}{2}) - (n - 3)(g - 1 + \frac{\delta}{2})\\
+				& = (n + 1)(g - 1 + \frac{\delta}{2}) = \dim_\Bk H^0((n + 2)L).
 \end{align*}
@@
 )$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots
-, x_n$ of $R_\halfcan$ so that we obtain a surjection $\phi: k[x_1, \ldots
+, x_n$ of $R_\halfcan$ so that we obtain a surjection $\phi: \Bk[x_1, \ldots
 , x_n] \twoheadrightarrow R_\halfcan$ with kernel $I_\halfcan$. Let $I_{\halfcan, d}$ be
@@
 \[
-	J_{\halfcan,d} = \sum_{j = 1}^{d- 1}k[x_1, \ldots, x_n]_j \cdot I_{\halfcan,d-j}.
+	J_{\halfcan,d} = \sum_{j = 1}^{d- 1}\Bk[x_1, \ldots, x_n]_j \cdot I_{\halfcan,d-j}.
 \]
@@
 that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_\halfcan$ so
-that we obtain a surjection $\phi: k[x_1, \ldots, x_n]
-\twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in k[x_1,
+that we obtain a surjection $\phi: \Bk[x_1, \ldots, x_n]
+\twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in \Bk[x_1,
 \ldots, x_n]_2$ be two elements so that $\: \newspan(\phi(s_1), \phi(s_2))
 = V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
-k[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
-k[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, d}.$
+\Bk[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
+\Bk[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, d}.$
 \end{lem}
@@
 % Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1), \phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
-By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in k[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in k[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
+By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in \Bk[x_1, \ldots, x_n]_{d-\deg x_i}$.
+We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in \Bk[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
 
@@
 $$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
-Choosing $g_i,h_i\in k[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
+Choosing $g_i,h_i\in \Bk[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
 $$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan, \deg a_i},$$ as claimed.
@@
 free pencil trick, as shown in the proof of \cite[Lemma 2.6]
-{saint-donat:proj}, there exists some $\rho \in k[x_1, \ldots, x_n]$
+{saint-donat:proj}, there exists some $\rho \in \Bk[x_1, \ldots, x_n]$
 so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) =
@@
 Therefore,
-$g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv - s_1 \rho \bmod
-I_{k, d - 2}$. Hence,
+$g \equiv s_2 \rho \bmod I_{\halfcan, d-2}$ and $h \equiv - s_1 \rho \bmod
+I_{\halfcan, d - 2}$. Hence,
 \begin{align*}
@@
 \noindent
-is generated as a $k$-algebra by elements in degree at most $e =
+is generated as a $\Bk$-algebra by elements in degree at most $e =
 \max(5, e_1, \ldots, e_r)$ with minimal relations in degree at most $2e$.
@@
 \noindent
-is generated as a $k$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
+is generated as a $\Bk$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
 finite list of exceptional cases, as listed in Table
@@
 \begin{rem}
-Since all points are linearly equivalent on $\BP^1_k$, we may
-assume without loss of generality that $L_X = n \infty$ for some $n
+Since all points are linearly equivalent on $\BP^1_\Bk$, we may
+assume without loss of generality that $\halfcan_X = n \infty$ for some $n
 \in \BN$ and $K_X = -2 \infty$. We will use this convention
@@
 
-	$(0; 3, 3, k; 0)$ & $k > 9$ & $9$ \\	\hline
+	$(0; 3, 3, \ell; 0)$ & $\ell > 9$ & $9$ \\	\hline
 
@@
 presentation satisfying the desired conditions. The log spin
-canonical ring $R(\sx', 0, L')$ is generated as a $k$-algebra by
+canonical ring $R(\sx', 0, L')$ is generated as a $\Bk$-algebra by
 elements of degree at most $e$ with relations in degree at most $2e$
@@
 Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
-for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i L
+for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i \halfcan
 \rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ are
@@
 \begin{align*}
-	S &:= \{(0; 3, 3, k; 0) : 3 \leq k \leq 9 \text{ odd}\} \\
+	S &:= \{(0; 3, 3, \ell; 0) : 3 \leq \ell \leq 9 \text{ odd}\} \\
 		&\cup \{(0; 3, 5, 5; 0) ,(0; 3, 5, 7; 0), (0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
@@
 \noindent
-is generated as a $k$-algebra by elements of degree at most $e =
+is generated as a $\Bk$-algebra by elements of degree at most $e =
 \max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
@@
 case which is done by Voight and Zureick-Brown \cite[Section 4.2]
-{vzb:stacky}. When $n = -1$, then $R_\halfcan = k$.  When $n = 0$,
-then $R_\halfcan = k[x]$.  When $n > 0$, inductively applying Lemma
+{vzb:stacky}. When $n = -1$, then $R_\halfcan = \Bk$.  When $n = 0$,
+then $R_\halfcan = \Bk[x]$.  When $n > 0$, inductively applying Lemma
 \ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1
@@
 \lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
-trivial case where $R(\sx, \Delta, \halfcan) = k$.
+trivial case where $R(\sx, \Delta, \halfcan) = \Bk$.
 
@@
 
-	\item Voight and Zureick Brown define
+	\item Voight and Zureick-Brown define
 		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 

### 2015-07-08 curves-write-up/spin_cring.tex
edits for more meaty comment, mid edit

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 \todo{Think about John's comment to regrade the ring.}
-\todo{Brian: Don't write out author's name every time.}
 
@@
 generalization of the GAGA principle.
-\todo{brain: The appeal to stacky GAGA on page 1 sweeps a bit under the rug.
-I suppose you noticed (as I just did upon glancing at [14] on the arxiv) that the proof of Prop.
-6.1.5 in [14] seems to pass in silence over the removal of the properness hypothesis (which, in the scheme case — no stacks — requires using something like the little Picard theorem or some other device to deal with avoidance of essential singularities).
-That is moot for you since only the proper case is relevant for your motivation.
-More importantly, since the entire discussion is about spaces of sections of coherent sheaves, one should address stacky GAGA at the level of such $H^0$’s, which is not part of Prop.
-6.1.5 in [14], to have adequately treated the motivation.
-On line -1 of last paragraph on page 1, should say X is proper and geometrically connected over k.
-Note that the proof of Lemma 10.2.1 in [14] gives a thoroughly analytic construction of the line bundle (no ad hoc stuff with divisors), so to link it back to the algebraic case one is using an honest GAGA comparison at the level of categories of coherent sheaves too (with refinement for line bundles).}
  By \cite[Proposition 6.1.5]
@@
 \end{cor}
-\todo{Add somewhere that if there is an odd $k$ with nonzero weight, it will generally have to occur in weight 3, according to brian 2.}
+
+\begin{rem}
+\label{rem:gen-at-most-three}
+In the case that $M(\Gamma)$ has some odd weight modular form, it in fact has an odd weight modular form in weight $3$.
+This holds in the case that the genus $g \geq 2$ because $\deg \lfloor 3L \rfloor > 2g-1,$ so by Riemann--Roch, $\dim_k H^0(\sx,3L) > 0,$ implying there must be some generator in weight $1$ or $3$.
+The case that $M(\Gamma)$ has a generator in degree 1 or 3 when $g(X) = 0$ or $1$ follows from the fact that it has such a generator in the base cases given in Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}.
+Hence, the bound on the degree of generators and relations in the case that $M(\Gamma)$ has some odd weight modular form, given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
+\end{rem}
+
+\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0).
+Further, if $L_X$ is effective, then generation will be in weight at most 3.}
+\begin{example}
+\label{eg:congruence-bounds}
+Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup.
+Then, since the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the action of $\Gamma$ can only have points with stabilizer order 2 and 3.
+Furthermore, if $\Gamma$ has some odd weight modular form, then it must have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}).
+Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is generated in degree at most $5$ with a relation in degree at most $12$.
+Furthermore, if the coarse space associated $\Gamma$ does not have .
+\end{example}
+
 \begin{rem}
@@
 \end{rem}
-
-\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0).
-Further, if $L_X$ is effective, then generation will be in weight at most 3.}
 
@@
 \label{defn:stacky-curve}
-A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
+A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$ is the datum of a smooth proper integral scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
 
@@
 In this section, we present several directions for further research.
-
+\todo{Edit to eliminate John's confusions}
 \begin{enumerate}
@@
 generators and relations of spin canonical rings in high genera.
-We would also like to mention Evan O'Dorney for enlightening
-conversations regarding his work in this field.
+We thank Brian Conrad and John Voight for helpful comments on this paper.
+The first author would also like to mention Joseph Harris and Evan O'Dorney for several enlightening conversations related to Petri's Theorem.
 Finally, we gratefully acknowledge the financial support given by

### 2015-07-08 curves-write-up/spin_cring.tex

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 \label{defn:stacky-curve}
-A \textbf{stacky curve} $\sx$ over an algebraically closed field $\Bk$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
-
+A \textbf{stacky curve} $\sx$ over an algebraically closed field $\Bk$ is the datum of a smooth proper integral scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
 \end{defn}

### 2015-07-08 curves-write-up/spin_cring.tex
d -> k globally except for best lower approx

@@
 \begin{align*}
-	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
+	R(X, K_X) = \bigoplus_{k \geq 0} H^0(X, kK_X),
 \end{align*}
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, \lfloor d \halfcan \rfloor).
+	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor).
 \end{align*}
@@
 \end{align*}
-If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
+If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
 graded component of $R$.
@@
 \[
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d \halfcan).
+	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
 \]
@@
 \[
-	\Eff(D) = \{d \in \BZ_{\geq 0} : \deg \lfloor dD \rfloor \geq 0 \}.
+	\Eff(D) = \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
 \]
@@
 Let $\Bk[x_1$, $\ldots$, $x_n]$ be a graded polynomial
-ring with $\deg x_i = d_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
+ring with $\deg x_i = k_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
 \Bk[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
@@
 \[
-	\deg \alpha := \sum_{i = 1}^{n} d_i f_i.
+	\deg \alpha := \sum_{i = 1}^{n} k_i f_i.
 \]
@@
 \begin{equation}
-	\deg \alpha = \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' = \deg \beta
+	\deg \alpha = \sum_{i = 1}^{n} k_i f_i  > \sum_{i = 1}^{n} k_i f_i' = \deg \beta
 \end{equation}
@@
 The \textbf{block term order} is defined as follows. Let $\Bk[y_{1}, \ldots, y_{m}]$ and $\Bk[x_{1}, \ldots,
-x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = d_i.$ Further assume we are given existing term
+x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = k_i.$ Further assume we are given existing term
 orders $\prec_y$ and $\prec_x$. Let $\alpha :=
@@
 In the \textbf{(graded) block} (or \textbf{elimination}) term
-ordering on $\Bk[y_{d_1', 1}, \ldots, y_{d_m', m}] \otimes \Bk[x_{d_1, 1},
-\ldots, x_{d_n, n}]$, we define $\alpha \succ \beta$ if
+ordering on $\Bk[y_{k_1', 1}, \ldots, y_{k_m', m}] \otimes \Bk[x_{k_1, 1},
+\ldots, x_{k_n, n}]$, we define $\alpha \succ \beta$ if
   \begin{enumerate}
@@
 Let $\prec$ be an ordering on $\Bk[x_{1}$, $\ldots$, $x_{n}]$, 
-with $\deg x_i = d_i$,
+with $\deg x_i = k_i$,
 and let $f \in \Bk[x_{1}, \ldots, x_{n}]$ be a homogeneous
@@
 		\begin{align*}
-			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
+			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{k \geq 0} \# S_{\sigma, J}(i, k)
 		\end{align*}
@@
 		\begin{align*}
-			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
+			S_{\sigma, J}(i, k) := \{j \in J : j \neq i \text{ and } e_j'+2k
 			\mid e_i - e_j'\}.
@@
 Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
-Counting dimensions, we see $h^0(\sx, dL')=1$ for all $d\in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
+Counting dimensions, we see $h^0(\sx, k\halfcan')=1$ for all $k \in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
 \end{example}
@@
 of $R_{L_X}$. Note that we have a natural inclusion $\iota: R_{L_X}
-\hookrightarrow R_L$ induced by the inclusions $H^0(\sx, dL_X)
-\hookrightarrow H^0(\sx, dL)$ for each $d \geq 0$. By Riemann Roch,
+\hookrightarrow R_L$ induced by the inclusions $H^0(\sx, k\halfcan_X)
+\hookrightarrow H^0(\sx, k\halfcan)$ for each $k \geq 0$. By Riemann Roch,
 we see there is some element $y_{1, 3} \in (R_L)_3$ with $\ord_{P_1}
@@
 \begin{align*}
-	H^0(\sx, 3L) \otimes H^0(\sx, (d - 3)L) \rightarrow H^0(\sx, dL)
-\end{align*}
-
-\noindent
-are surjective for $d \geq 4$. A relation of the form $a_1 x_1 y_{1,
+	H^0(\sx, 3L) \otimes H^0(\sx, (k - 3)L) \rightarrow H^0(\sx, k\halfcan)
+\end{align*}
+
+\noindent
+are surjective for $k \geq 4$. A relation of the form $a_1 x_1 y_{1,
 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2) = 0$ must exist because $h^0(\sx,
@@
 \label{eg:base-0-377}
-Let $(\sx',0, \halfcan')$ be a log spin curve with signature $\sigma =
+Let $(\sx', 0, \halfcan')$ be a log spin curve with signature $\sigma =
 (0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are
+\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1, P_2,$ and $P_3$ are
 distinct points. In this example, we will exhibit a minimal
-presentation for $R' = R(\sx',0, \halfcan')$ and show the triple
+presentation for $R' = R(\sx', 0, \halfcan')$ and show the triple
 $(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
-Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
-\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.
+Notice that $\deg \lfloor k K_{\sx'} \rfloor= -k + \lfloor \frac{k}{3}
+\rfloor + 2 \lfloor \frac{3k}{7} \rfloor$.
 
@@
 	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor)
+	(k - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
+	k \halfcan' \rfloor)
 \end{align}
@@
 \noindent
-is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
+is surjective whenever $\deg (\lfloor (k - 21) \halfcan' \rfloor)
 \geq 0$. It is fairly easy to see, by use of Riemann--Roch, that
 the saturation of $\halfcan'$ is $5$ (see Definition ~\ref{defn:sat}.
-Then the map in ~\eqref{eqn:noether-377} is surjective when $d \geq
+Then the map in ~\eqref{eqn:noether-377} is surjective when $k \geq
 21 + s = 26$ (i.e.,~ $R'$ is generated up to degree 25).
 
-For $d = 0, 1, 2, \ldots$ we have
+For $k = 0, 1, 2, \ldots$ we have
 \[
-	\dim_\Bk H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+	\dim_\Bk H^0 (\sx', k \halfcan') = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
 \]
@@
 so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i K_{\sx'})$.
+x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i \halfcan')$.
 
 To show that these generate all of $R'$, we need to show that all
-$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
-and $7 < d \leq 25$. Note that we can again use Max Noether's theorem
+$H^0 (\sx', k \halfcan')$ are generated by lower degrees for $k = 6$
+and $7 < k \leq 25$. Note that we can again use Max Noether's theorem
 (taking saturation into account) to see that
@@
 	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 3) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
+	(k - 3) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
+	k \halfcan' \rfloor) \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
 	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(d - 7) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
-	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
+	(k - 7) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
+	k \halfcan' \rfloor) \text{ if } k \geq 6, k \not\equiv 0, 5
 	\bmod 7
@@
 are surjective. This reduces the problem to checking generation
-in the degrees of the exceptions $d \in \{8, 12, 21\}$.
+in the degrees of the exceptions $k \in \{8, 12, 21\}$.
 Checking these remaining cases via pole degree considerations shows
@@
 pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
+generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3k}{7}$
 in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
@@
 
-Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
-$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
-0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
+Also note that $e_j' + 2k = 7 + 2k \nmid 2 = e_i - e_j'$ for all
+$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $k \geq
+0$. Thus, $s_{\sigma, J}(i, k) = \emptyset$ for each $i \in J$.
 Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
@@
 To demonstrate that these two relations generate all 
-relations, we show that $\dim_\Bk (R')_d = \dim_\Bk
-(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_d$ for 
-all degrees $d \geq 0$. In particular,
-
-\begin{align*}
-	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_d &=
-	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_d \\
+relations, we show that $\dim_\Bk (R')_k = \dim_\Bk
+(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_k$ for 
+all degrees $k \geq 0$. In particular,
+
+\begin{align*}
+	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_k &=
+	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_k \\
 	&= \dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
-\end{align*}
-\noindent
-for all $d \geq 0$. But the fact $\dim_\Bk (R')_d = \dim_\Bk \left(\Bk[x_{7, 2},
+	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_k
+\end{align*}
+\noindent
+for all $k \geq 0$. But the fact $\dim_\Bk (R')_k = \dim_\Bk \left(\Bk[x_{7, 2},
 x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
-\rangle\right)_d$ can be checked by looking at the $\Bk$-basis at each degree
-$d$.
+\rangle\right)_k$ can be checked by looking at the $\Bk$-basis at each degree
+$k$.
 
@@
 Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
+Finally, to check \ref{custom:Ad-iii}, note that $\max_{k \geq 0}S_{\sigma,J}(i,k) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
 \end{example}
@@
 satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $d\halfcan'$ for all $d \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
+Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
@@
 \label{eqn:deg1-sat-ind}
-	h^0(X, \lfloor{d\halfcan}\rfloor) &= h^0(X, \lfloor d\halfcan'
-	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor &&\text{ for all } d \in \mathbb{
+	h^0(X, \lfloor k \halfcan \rfloor) &= h^0(X, \lfloor k \halfcan'
+	\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor &&\text{ for all } k \in \mathbb{
 	N}.
@@
 \item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
-	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = d_i$ and $-\ord_P
+	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = k_i$ and $-\ord_P
 	^{L'}(y_i) = c_i$.
@@
 \[
-	h^0 (X, d \halfcan ) = h^0(X, d\halfcan') + \lfloor d\frac{\alpha}{\beta}\rfloor.
+	h^0 (X, d \halfcan ) = h^0(X, d \halfcan') + \lfloor d \frac{\alpha}{\beta}\rfloor.
 \]
@@
 \noindent
-Thus, there exist rational sections $t_i$ of $\sco(\lfloor d\halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
+Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
 for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
@@
 
-Suppose $c,d \in \BN$ so that $d\le \beta,$  $\frac{c}{d} < \frac{\alpha}{
+Suppose $c,d \in \BN$ so that $k \le \beta$,  $\frac{c}{d} < \frac{\alpha}{
 \beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
@@
 \begin{equation}\label{eqn:sat-1-defining-S}
-	S = \cup_{i=1}^{\infty} S_i.  
+	S = \bigcup_{i=1}^{\infty} S_i.  
 \end{equation}
@@
 \[
-	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X, \lfloor d\halfcan'
+	h^0(X, \lfloor d \halfcan \rfloor) = h^0(X, \lfloor d \halfcan'
 		\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor,
@@
 \[
-	\Bk[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]\right). 
+	\Bk[u, x_1, \ldots, x_m] \cup V \cup \left(\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]\right). 
 \]
@@
 
-Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}
@@
 %\ord_P(y_1)= 1$. Furthermore, since $\delta> 0$, we use Riemann-Roch to deduce that for 
-%all $d> 1$ $h^0(X, \lfloor dL\rfloor)=h^0(dL') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
+%all $d> 1$ $h^0(X, \lfloor k\halfcan\rfloor)=h^0(k\halfcan') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
 %$-vector space over $(R_{\halfcan'})_d$. In particular, this means we can generically 
@@
 i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $\Bk$-basis for $R_{i}$ over $R_{i-1}$.
-These elements do not lie in $R_{i - 1}$ because the pole order of $y_{i, e_i'}^ay_{i,e_i}^b$ at $Q_i$ is larger than that of any element in the $d^{th}$ component of $R_{i - 1}$.
+These elements do not lie in $R_{i - 1}$ because the pole order of $y_{i, e_i'}^ay_{i,e_i}^b$ at $Q_i$ is larger than that of any element in the $k^{th}$ component of $R_{i - 1}$.
 Additionally, these elements are linearly independent amongst themselves because of
@@
 Finally, if \ref{custom:Ad-iii} holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that \ref{custom:Ad-iii} holds for $d > 0$
-and not just for $d = 0$.
+definition. This is where we use that \ref{custom:Ad-iii} holds for $k > 0$
+and not just for $k = 0$.
 \end{proof}
@@
 , x_n$ of $R_\halfcan$ so that we obtain a surjection $\phi: \Bk[x_1, \ldots
-, x_n] \twoheadrightarrow R_\halfcan$ with kernel $I_\halfcan$. Let $I_{\halfcan, d}$ be
-the $d^\text{th}$ graded piece of $I_\halfcan$ and define
+, x_n] \twoheadrightarrow R_\halfcan$ with kernel $I_\halfcan$. Let $I_{\halfcan, k}$ be
+the $k^\text{th}$ graded piece of $I_\halfcan$ and define
 \[
-	J_{\halfcan,d} = \sum_{j = 1}^{d- 1}\Bk[x_1, \ldots, x_n]_j \cdot I_{\halfcan,d-j}.
+	J_{\halfcan,k} = \sum_{j = 1}^{k - 1}\Bk[x_1, \ldots, x_n]_j \cdot I_{\halfcan,k-j}.
 \]
@@
 \Bk[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
-\Bk[x_1, \ldots, x_n]_{d - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, d}.$
+\Bk[x_1, \ldots, x_n]_{k - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, k}.$
 \end{lem}
@@
 % Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1), \phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
-By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in \Bk[x_1, \ldots, x_n]_{d-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in \Bk[x_1, \ldots, x_n]_{d - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
+By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in \Bk[x_1, \ldots, x_n]_{k-\deg x_i}$.
+We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in \Bk[x_1, \ldots, x_n]_{k - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
 
@@
 	f &\equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \\
-	&\equiv s_1 g + s_2 h \bmod J_{L,d}.
+	&\equiv s_1 g + s_2 h \bmod J_{L,k}.
 \end{align*}
@@
 Suppose $f \in I_\halfcan$ with $\deg f \geq 11$. To complete the proof,
-it suffices to show $f \in I_{\halfcan,d}'$. By Lemma
+it suffices to show $f \in I_{\halfcan,k}'$. By Lemma
 ~\ref{lem:reducing-degree}, this is the same as checking $s_1 g + s_2 h \in
-I_{\halfcan, d}'$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
+I_{\halfcan, k}'$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
 so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
@@
 Therefore,
-$g \equiv s_2 \rho \bmod I_{\halfcan, d-2}$ and $h \equiv - s_1 \rho \bmod
-I_{\halfcan, d - 2}$. Hence,
+$g \equiv s_2 \rho \bmod I_{\halfcan, k-2}$ and $h \equiv - s_1 \rho \bmod
+I_{\halfcan, k - 2}$. Hence,
 \begin{align*}
 	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_
-{L,d}.
+{L,k}.
 \end{align*}
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(\sx, d L )
+	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(\sx, k L )
 \end{align*}
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, d L)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{k = 0}^\infty H^0(\sx, k L)
 \end{align*}
@@
 for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i \halfcan
-\rfloor$ and $\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ are
+\rfloor$ and $\max_{k \geq 0} \#S_{(\sigma, J)}(i)$ are
 independent of the choice of $i$.
@@
 	Case & Signature $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
-	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
+	$\max_{k \geq 0} \#S_{(\sigma, J)}(i)$ \\
 	\hline
@@
 \begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, L)
+	R(\sx, \Delta, \halfcan) = \bigoplus_{k = 0}^\infty H^0(\sx, L)
 \end{align*}
@@
 If $r < 3$, then $\deg 
-\lfloor d \halfcan \rfloor < 0$ for all $d \geq 0$ so we have the
+\lfloor k \halfcan \rfloor < 0$ for all $k \geq 0$ so we have the
 trivial case where $R(\sx, \Delta, \halfcan) = \Bk$.

### 2015-07-08 curves-write-up/spin_cring.tex
one more of brians comment to fill

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 
-\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0).
-Further, if $L_X$ is effective, then generation will be in weight at most 3.}
 \begin{example}
 \label{eg:congruence-bounds}
-Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup.
-Then, since the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the action of $\Gamma$ can only have points with stabilizer order 2 and 3.
-Furthermore, if $\Gamma$ has some odd weight modular form, then it must have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}).
-Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is generated in degree at most $5$ with a relation in degree at most $12$.
-Furthermore, if the coarse space associated $\Gamma$ does not have .
+Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since 
+the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the 
+action of $\Gamma$ can only have points with stabilizer order 2 and 3. 
+Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
+have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
+Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
+generated in degree at most $5$ with relations in degree at most $12$. 
+Furthermore, if the coarse space associated $\Gamma$ does not have, 
+$(0;3,3,3,3;0),$ there are relations in degree at most $10$, as follows 
+from the list of exceptional cases in Tables ~\ref{table:genus-0-exceptional-cases} and ~\ref{table:genus-0-exceptional}.
 \end{example}

### 2015-07-08 curves-write-up/spin_cring.tex
revise odd weight rem, grading convention note

@@
 \label{rem:gen-at-most-three}
-In the case that $M(\Gamma)$ has some odd weight modular form, it in fact has an odd weight modular form in weight $3$.
-This holds in the case that the genus $g \geq 2$ because $\deg \lfloor 3L \rfloor > 2g-1,$ so by Riemann--Roch, $\dim_k H^0(\sx,3L) > 0,$ implying there must be some generator in weight $1$ or $3$.
-The case that $M(\Gamma)$ has a generator in degree 1 or 3 when $g(X) = 0$ or $1$ follows from the fact that it has such a generator in the base cases given in Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}.
-Hence, the bound on the degree of generators and relations in the case that $M(\Gamma)$ has some odd weight modular form, given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
+If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$.
+When $g \geq 2$, we see that this is true because $\dim_k H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$.
+When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases} so there is an odd weight modular form in weight $3$ in general.
+A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
 \end{rem}
@@
 ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively.
-Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two, because our grading convention on $\bigoplus_k M_k(\Gamma)$ differs from that of Voight and Zureick-Brown by a factor of 2.
+Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two.
+Our grading convention for log spin canonical rings uses weight $k$ for the degree whereas Voight and Zureick-Brown $d = 2k$ for degree.
 \end{rem}

### 2015-07-08 curves-write-up/spin_cring.tex
d's changed to k's

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 
+\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0).
+Further, if $L_X$ is effective, then generation will be in weight at most 3.}
 \begin{example}
 \label{eg:congruence-bounds}
-Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since 
-the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the 
-action of $\Gamma$ can only have points with stabilizer order 2 and 3. 
-Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
-have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
-Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
-generated in degree at most $5$ with relations in degree at most $12$. 
-Furthermore, if the coarse space associated $\Gamma$ does not have, 
-$(0;3,3,3,3;0),$ there are relations in degree at most $10$, as follows 
-from the list of exceptional cases in Tables ~\ref{table:genus-0-exceptional-cases} and ~\ref{table:genus-0-exceptional}.
+Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup.
+Then, since the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the action of $\Gamma$ can only have points with stabilizer order 2 and 3.
+Furthermore, if $\Gamma$ has some odd weight modular form, then it must have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}).
+Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is generated in degree at most $5$ with a relation in degree at most $12$.
+Furthermore, if the coarse space associated $\Gamma$ does not have .
 \end{example}
@@
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c \in \BN, d \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
+If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{k}$ (written in reduced form with $c \in \BN, k \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{k'}\in \mathbf{Q}$ with $0<k'<k$ and $\frac{c}{k}\le \frac{c'}{k'}$.
 \end{defn}
@@
 \[
-	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
+	0=\frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \frac{\alpha}{\beta}.
 \]
@@
 \[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
+	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
 \]
@@
 By
-Equation ~\ref{eqn:deg1-sat-ind}, for any $d
-\in \BN$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
+Equation ~\ref{eqn:deg1-sat-ind}, for any $k
+\in \BN$ such that $\lfloor k \frac{ \alpha}{\beta} \rfloor > 0$,
 
 \[
-	h^0 (X, d \halfcan ) = h^0(X, d \halfcan') + \lfloor d \frac{\alpha}{\beta}\rfloor.
+	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \lfloor k \frac{\alpha}{\beta}\rfloor.
 \]
@@
 %For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
-Choose a positive best lower approximation $\frac{c_i}{d_i}$.
-Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
+Choose a positive best lower approximation $\frac{c_i}{k_i}$.
+Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$.
 Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
@@
 \[
-	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
+	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
 \]
@@
 \[
-	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{d_i}.
+	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
 \]
-Multiplying through by $d_i$ gives
+Multiplying through by $k_i$ gives
 \[
@@
 \noindent
-Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
+Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
 lower degrees. 
 Choose some $y_i \in(R_{
-\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-
-Suppose $c,d \in \BN$ so that $k \le \beta$,  $\frac{c}{d} < \frac{\alpha}{
-\beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so 
-%  The argument goes $c_i d \ge c d_i$
-% implies c_i \frac{d}{d_i} \ge c
-% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
-% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
-% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
+\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
+
+Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
+\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
+best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so 
+%  The argument goes $c_i d \ge c k_i$
+% implies c_i \frac{k}{k_i} \ge c
+% implies c_i + \frac{k-k_i}{k_i}c_i \ge c
+% \implies c_i (k-k_i) \frac{c_i}{k_i}\ge c
+% so since everything is an integer $c_i +\lfloor (k - k_i) \frac{c_i}{k_i}\rfloor \ge c$
 % \implies the equation below:
 \[
-	\frac{c-c_i}{d-d_i}\le \frac{\alpha}{\beta}
+	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
 \]
@@
 \begin{equation}\label{eqn:c-from-lower-terms}
-	c_i +\left\lfloor (d-d_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
+	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
 \end{equation}
@@
 
-By equation \ref{eqn:deg1-sat-ind} for $d \in \BN$,
+By equation \ref{eqn:deg1-sat-ind} for $k \in \BN$,
 \[
-	h^0(X, \lfloor d \halfcan \rfloor) = h^0(X, \lfloor d \halfcan'
-		\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor,
+	h^0(X, \lfloor k \halfcan \rfloor) = h^0(X, \lfloor k \halfcan'
+		\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor,
 \] 
-so $S$ contains elements in degree $d \in \BN$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
+so $S$ contains elements in degree $k \in \BN$ with each pole order in $\{1 \ldots, \lfloor k\frac{\alpha}{\beta}\rfloor\}$.
 Thus, by dimension counting, $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
@@
 Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
-$$
+\[
 b_j = \begin{cases}
@@
 	a_j + 1 &\text{ if } j=i.
-\end{cases}$$
+\end{cases}
+\]
 
@@
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
+The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{k_i}$ with $k_i=1$).
 When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.

### 2015-07-08 curves-write-up/spin_cring.tex

@@
 \label{rem:gen-at-most-three}
-In the case that $M(\Gamma)$ has some odd weight modular form, it in fact has an odd weight modular form in weight $3$.
-This holds in the case that the genus $g \geq 2$ because $\deg \lfloor 3L \rfloor > 2g-1,$ so by Riemann--Roch, $\dim_k H^0(\sx,3L) > 0,$ implying there must be some generator in weight $1$ or $3$.
-The case that $M(\Gamma)$ has a generator in degree 1 or 3 when $g(X) = 0$ or $1$ follows from the fact that it has such a generator in the base cases given in Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}.
-Hence, the bound on the degree of generators and relations in the case that $M(\Gamma)$ has some odd weight modular form, given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
+If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$.
+When $g \geq 2$, we see that this is true because $\dim_k H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$.
+When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases} so there is an odd weight modular form in weight $3$ in general.
+A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
 \end{rem}
 
-\todo{Add example saying all congruence subgroups with a form of odd weight are generated in weight at most 5 with relations in weight at most 12, (which can be reduced to 10 if the signature is not (0;3,3,3,3;0).
-Further, if $L_X$ is effective, then generation will be in weight at most 3.}
 \begin{example}
 \label{eg:congruence-bounds}
-Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup.
-Then, since the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the action of $\Gamma$ can only have points with stabilizer order 2 and 3.
-Furthermore, if $\Gamma$ has some odd weight modular form, then it must have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}).
-Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is generated in degree at most $5$ with a relation in degree at most $12$.
-Furthermore, if the coarse space associated $\Gamma$ does not have .
+Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since 
+the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the 
+action of $\Gamma$ can only have points with stabilizer order 2 and 3. 
+Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
+have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
+Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
+generated in degree at most $5$ with relations in degree at most $12$. 
+Furthermore, if the coarse space associated $\Gamma$ does not have, 
+$(0;3,3,3,3;0),$ there are relations in degree at most $10$, as follows 
+from the list of exceptional cases in Tables ~\ref{table:genus-0-exceptional-cases} and ~\ref{table:genus-0-exceptional}.
 \end{example}

### 2015-07-08 curves-write-up/spin_cring.tex
\sx with floored divisor -> \sx no floor divisor
title change, bold group in Fuchsian group

@@
 
-\title{Spin canonical rings of log stacky curves}
+\title{Canonical rings of log spin stacky curves}
 
@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian} group, i.e.,~ a discrete subgroup of
+Let $\Gamma$ be a {\bf Fuchsian group}, i.e.,~ a discrete subgroup of
 $\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
@@
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to desribe the ring $M(\Gamma),$ is to write down a presentation.
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma),$ is to write down a presentation.
 %of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
@@
 \label{eqn:noether-377}
-	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(k - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
-	k \halfcan' \rfloor)
+	H^0 (\sx', 21 \cdot \halfcan') \otimes H^0 (\sx',
+	(k - 21) \halfcan') \rightarrow H^0 (\sx',
+	k \halfcan')
 \end{align}
@@
 \begin{align*}
-	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(k - 3) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
-	k \halfcan' \rfloor) \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
-	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
-	(k - 7) \halfcan' \rfloor) \rightarrow H^0 (\sx', \lfloor
-	k \halfcan' \rfloor) \text{ if } k \geq 6, k \not\equiv 0, 5
+	&H^0 (\sx', 3 \halfcan') \otimes H^0 (\sx',
+	(k - 3) \halfcan') \rightarrow H^0 (\sx',
+	k \halfcan') \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
+	&H^0 (\sx', 7 \halfcan') \otimes H^0 (\sx',
+	(k - 7) \halfcan') \rightarrow H^0 (\sx',
+	k \halfcan') \text{ if } k \geq 6, k \not\equiv 0, 5
 	\bmod 7

### 2015-07-08 curves-write-up/spin_cring.tex
bounds acheived

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 
-\todo{Think about John's comment to regrade the ring.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 of the genus one and genus zero cases also yield explicit systems
-of generators and an explicit initial ideal of relations.
+of generators and an explicit initial ideal of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
 Furthermore, our proof of the genus $g \geq 2$ case also provides
@@
 Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-\todo{Explain this in more detail later, as asked by Brian}
+For further detail, see Remarks ~\ref{rem:genus-0-explicit-bound}, ~\ref{rem:genus-1-explicit-bound}, and ~\ref{rem:genus-2-explicit-bound} in the cases that the genus is $0,1,$ or $\geq 2$ respectively.
 \end{rem}
@@
 \begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{k}$ (written in reduced form with $c \in \BN, k \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{k'}\in \mathbf{Q}$ with $0<k'<k$ and $\frac{c}{k}\le \frac{c'}{k'}$.
+If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{d}$ (written in reduced form with $c \in \BN, d \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{d'}\in \mathbf{Q}$ with $0<d'<d$ and $\frac{c}{d}\le \frac{c'}{d'}$.
 \end{defn}
@@
 \[
-	0=\frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \frac{\alpha}{\beta}.
+	0=\frac{c_0}{d_0} < \frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{\alpha}{\beta}.
 \]
@@
 \[
-	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
+	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
 \]
@@
 By
-Equation ~\ref{eqn:deg1-sat-ind}, for any $k
-\in \BN$ such that $\lfloor k \frac{ \alpha}{\beta} \rfloor > 0$,
+Equation ~\ref{eqn:deg1-sat-ind}, for any $d
+\in \BN$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,
 
 \[
-	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \lfloor k \frac{\alpha}{\beta}\rfloor.
+	h^0 (X, d \halfcan ) = h^0(X, d \halfcan') + \lfloor d \frac{\alpha}{\beta}\rfloor.
 \]
@@
 %For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
-Choose a positive best lower approximation $\frac{c_i}{k_i}$.
-Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$.
+Choose a positive best lower approximation $\frac{c_i}{d_i}$.
+Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = d_i$ and $\deg(z_j)<d_i$ for all $j\in \{1, \ldots r\}$.
 Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
@@
 \[
-	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
+	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{d_i},
 \]
@@
 \[
-	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
+	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{d_i}.
 \]
-Multiplying through by $k_i$ gives
+Multiplying through by $d_i$ gives
 \[
@@
 \noindent
-Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
+Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
 lower degrees. 
 Choose some $y_i \in(R_{
-\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-
-Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
-\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so 
-%  The argument goes $c_i d \ge c k_i$
-% implies c_i \frac{k}{k_i} \ge c
-% implies c_i + \frac{k-k_i}{k_i}c_i \ge c
-% \implies c_i (k-k_i) \frac{c_i}{k_i}\ge c
-% so since everything is an integer $c_i +\lfloor (k - k_i) \frac{c_i}{k_i}\rfloor \ge c$
+\halfcan})_{d_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
+
+Suppose $c,d \in \BN$ so that $k \le \beta$,  $\frac{c}{d} < \frac{\alpha}{
+\beta},$ and $\frac{c}{d}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
+best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d},$ so 
+%  The argument goes $c_i d \ge c d_i$
+% implies c_i \frac{d}{d_i} \ge c
+% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
+% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
+% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
 % \implies the equation below:
 \[
-	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
+	\frac{c-c_i}{d-d_i}\le \frac{\alpha}{\beta}
 \]
@@
 \begin{equation}\label{eqn:c-from-lower-terms}
-	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
+	c_i +\left\lfloor (d-d_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
 \end{equation}
@@
 
-By equation \ref{eqn:deg1-sat-ind} for $k \in \BN$,
+By equation \ref{eqn:deg1-sat-ind} for $d \in \BN$,
 \[
-	h^0(X, \lfloor k \halfcan \rfloor) = h^0(X, \lfloor k \halfcan'
-		\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor,
+	h^0(X, \lfloor d \halfcan \rfloor) = h^0(X, \lfloor d \halfcan'
+		\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor,
 \] 
-so $S$ contains elements in degree $k \in \BN$ with each pole order in $\{1 \ldots, \lfloor k\frac{\alpha}{\beta}\rfloor\}$.
+so $S$ contains elements in degree $d \in \BN$ with each pole order in $\{1 \ldots, \lfloor d\frac{\alpha}{\beta}\rfloor\}$.
 Thus, by dimension counting, $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
@@
 Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
-\[
+$$
 b_j = \begin{cases}
@@
 	a_j + 1 &\text{ if } j=i.
-\end{cases}
-\]
+\end{cases}$$
 
@@
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{k_i}$ with $k_i=1$).
+The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{d_i}$ with $d_i=1$).
 When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
@@
 \begin{proof}
-We prove this in case (1) and case (2) follows a similar procedure.
+We prove this in case (1). Case (2) follows a similar procedure.
 
@@
 
+\begin{rem}
+\label{rem:genus-2-explicit-bound}
+Using the terminology from the proof of Theorem ~\ref{thm:g-high-main}, if $e = \max(e_1,\ldots, e_r) \geq 5$, we see that $R_L,$ has a generator in precisely $e$.
+This follows from the inductive application of Lemmas ~\ref{lem:sat-1} and \ref{lem:sat-2}, which, at the last step, add a minimal generator of $R_L$ over $R_L'$ in degree $e$.
+Similarly, this inductive application shows that our given presentation has a relation in degree $2e-4$.
+\end{rem}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus one %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{rem}
+\label{rem:genus-1-explicit-bound}
 In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
 That, is one can start with the generators and relations found in the base cases, and inductively add in generators and relations as one adds and then increments stacky points.
+Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, when $e = \max(5,e_1,\ldots, e_r) \geq 5$ we obtain that $R_L$ has a generator in degree $e$ and a relation in degree at least $2e - 4$.
+Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, at least in our construction, there is a relation in degree $2e$.
 \end{rem}
@@
 \end{proof}
+
+\begin{rem}
+\label{rem:genus-0-explicit-bound}
+Just like the case of genus 1, as described in Remark ~\ref{rem:genus-1-explicit-bound}, the proof of Theorem ~\ref{thm:g-0-main} gives an explicit construction of the generators and relations for the log spin canonical ring $R_L$.
+Furthermore, similarly to the description given in Remarks in ~\ref{rem:genus-2-explicit-bound} and Remark ~\ref{rem:genus-0-explicit-bound}, when $e = \max(e_1, \ldots, e_r) \geq 5,$ there is a generator in degree $e$ and a relation in degree at most $2e$.
+This can be seen from the inductive application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref{lem:sat-3}.
+Additionally, as in the case of genus 1, if there are $1 \leq i < j \leq r$ with $e = e_i = e_j$ then there is a relation in degree $2e$.
+\end{rem}
 

### 2015-07-08 curves-write-up/spin_cring.tex
insert comma...

@@
 
-The main result of this subsection is that for a log spin curve with no stacky points $(X \Delta, L)$, the spin canonical ring $R_\halfcan$ is generated in degree at most $5$, with relations in degree at most $10$.
+The main result of this subsection is that for a log spin curve with no stacky points $(X, \Delta, L)$, the spin canonical ring $R_\halfcan$ is generated in degree at most $5$, with relations in degree at most $10$.
 The case that $\Delta = 0$ was completed by Reid \cite[Theorem 3.4]{reid:infinitesimal}.

### 2015-07-08 curves-write-up/spin_cring.tex
Surface -> surface

@@
 For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
-\backslash \BH$ is a Riemann Surface over $\BC$. 
+\backslash \BH$ is a Riemann surface over $\BC$. 
 $\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
-compact Riemann Surface, $\Gamma \backslash \BH^*,$ by adding in
+compact Riemann surface, $\Gamma \backslash \BH^*,$ by adding in
 cusps, with associated divisor of cusps $\Delta$.

### 2015-07-08 curves-write-up/spin_cring.tex
further research question 1 edit

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 
-\title{Canonical rings of log spin stacky curves}
+\title{Spin canonical rings of log stacky curves}
 
@@
 
+\todo{Think about John's comment to regrade the ring.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian group}, i.e.,~ a discrete subgroup of
+Let $\Gamma$ be a {\bf Fuchsian} group, i.e.,~ a discrete subgroup of
 $\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
@@
 of the genus one and genus zero cases also yield explicit systems
-of generators and an explicit initial ideal of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
+of generators and an explicit initial ideal of relations.
 Furthermore, our proof of the genus $g \geq 2$ case also provides
@@
 Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-For further detail, see Remarks ~\ref{rem:genus-0-explicit-bound}, ~\ref{rem:genus-1-explicit-bound}, and ~\ref{rem:genus-2-explicit-bound} in the cases that the genus is $0,1,$ or $\geq 2$ respectively.
+\todo{Explain this in more detail later, as asked by Brian}
 \end{rem}
@@
 \begin{proof}
-We prove this in case (1). Case (2) follows a similar procedure.
+We prove this in case (1) and case (2) follows a similar procedure.
 
@@
 
-\begin{rem}
-\label{rem:genus-2-explicit-bound}
-Using the terminology from the proof of Theorem ~\ref{thm:g-high-main}, if $e = \max(e_1,\ldots, e_r) \geq 5$, we see that $R_L,$ has a generator in precisely $e$.
-This follows from the inductive application of Lemmas ~\ref{lem:sat-1} and \ref{lem:sat-2}, which, at the last step, add a minimal generator of $R_L$ over $R_L'$ in degree $e$.
-Similarly, this inductive application shows that our given presentation has a relation in degree $2e-4$.
-\end{rem}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus one %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{rem}
-\label{rem:genus-1-explicit-bound}
 In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
 That, is one can start with the generators and relations found in the base cases, and inductively add in generators and relations as one adds and then increments stacky points.
-Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, when $e = \max(5,e_1,\ldots, e_r) \geq 5$ we obtain that $R_L$ has a generator in degree $e$ and a relation in degree at least $2e - 4$.
-Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, at least in our construction, there is a relation in degree $2e$.
 \end{rem}
@@
 
-\begin{rem}
-\label{rem:genus-0-explicit-bound}
-Just like the case of genus 1, as described in Remark ~\ref{rem:genus-1-explicit-bound}, the proof of Theorem ~\ref{thm:g-0-main} gives an explicit construction of the generators and relations for the log spin canonical ring $R_L$.
-Furthermore, similarly to the description given in Remarks in ~\ref{rem:genus-2-explicit-bound} and Remark ~\ref{rem:genus-0-explicit-bound}, when $e = \max(e_1, \ldots, e_r) \geq 5,$ there is a generator in degree $e$ and a relation in degree at most $2e$.
-This can be seen from the inductive application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref{lem:sat-3}.
-Additionally, as in the case of genus 1, if there are $1 \leq i < j \leq r$ with $e = e_i = e_j$ then there is a relation in degree $2e$.
-\end{rem}
-
 \section{Further Research}
@@
 		proof of Theorem ~\ref{thm:main} 
-		%given in this paper 
 		gives an 
 		explicit procedure for computing the generators and relations of $R_
-		\halfcan$ when the genus of $X$ is $0$ or $1$.
-		\begin{question}
-		\label{ques:algorithm}
-			Is there an explicit procedure for computing the generators 
-			and relations for an arbitrary genus $g \geq 2$ curve?
-		\end{question}
-		Suppose the generators and relations of $R_{\halfcan_X}$ are known, 
-		where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the 
-		coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor 
-		of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an 
-		algorithm for inductively determining the generators of $\halfcan$. 
-		This reduces Question \ref{ques:algorithm} to the 
-		following Petri-like question:
+		\halfcan$ when the genus of $\sx$ is $0$ or $1$.
+When $\sx$ has genus at least 2, Lemmas ~\ref{lem:sat-1} and $\ref{lem:sat-2}$ allow us to explicitly construct a presentation from a presentation of its coarse space $X$.
+However, computing a presentation of a general curve $X$ requires nontrivial computation.
+This suggests the following Petri-like question:
 		\begin{question}
 		\label{ques:spin-canonical-petri}
-			Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical 
-			divisor $L \in \di X$, can one write down a set of minimal 
-			generators and minimal relations for $R_\halfcan$?
+			Is there a general structure theorem for of a set minimal 
+			generators and minimal relations for $R_\halfcan$, a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical 
+			divisor $L \in \di X$?
 		\end{question}
@@
 		divisors often arise as rings of fractional weight $\frac{2}{n}$ modular
-		forms. For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli}) and Milnor \cite
+		forms. For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli} and Milnor \cite
 		[$\mathsection$ 6]{milnor:fractional-weight}.

### 2015-07-08 curves-write-up/spin_cring.tex
eliminate the todos....

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 In this section, we present several directions for further research.
-\todo{Edit to eliminate John's confusions}
 \begin{enumerate}

### 2015-07-08 curves-write-up/spin_cring.tex
edits to question 8.1

@@
 		\halfcan$ when the genus of $\sx$ is $0$ or $1$.
-When $\sx$ has genus at least 2, Lemmas ~\ref{lem:sat-1} and $\ref{lem:sat-2}$ allow us to explicitly construct a presentation from a presentation of its coarse space $X$.
-However, computing a presentation of a general curve $X$ requires nontrivial computation.
+When $\sx$ has genus at least 2, Lemmas ~\ref{lem:sat-1} and $\ref{lem:sat-2}$ allow us to explicitly construct a presentation of $R_\halfcan$ from a presentation of $R_{L_X}$ where $X$ is the coarse space $X$.
+However, obtaining a presentation for $X$ requires nontrivial computation.
 This suggests the following Petri-like question:
@@
 		\label{ques:spin-canonical-petri}
-			Is there a general structure theorem for of a set minimal 
-			generators and minimal relations for $R_\halfcan$, a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical 
-			divisor $L \in \di X$?
+			Is there a general structure theorem describing a set of minimal 
+			generators and relations of $R_{\halfcan}$ where $(X, \Delta, L))$ is a log spin curve with no stacky points?
 		\end{question}

### 2015-07-08 curves-write-up/spin_cring.tex
remove extra space
revisions to g-0-sat and defn:sat, other minor

@@
 \[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
+	\di \sx := \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
 	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
@@
 Recall the standard notation 
-$$\sco(D) = \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
+$$\sco(D) := \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
 Let $\sx$ be a stacky curve with coarse space $X$.
@@
 \[
-	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
+	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
 \]
@@
 \label{rem:odd-denom}
-Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
+Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that $\halfcan$ is of the form
 \[
@@
 \ssec{Saturation}
-
-We define the notion of the saturation of a divisor, as can be found in
-Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
+We define the notion of the saturation of a divisor, as can be
+found in Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
+The classification of the saturations of log spin canonical
+divisors are used in the proof of the main theorem and the various
+lemmas in Section ~\ref{sec:induction}.
 
@@
 \[
-	\Eff(D) = \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
+	\Eff(D) := \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
 \]
@@
 \label{defn:sat}
-The \textbf{saturation} of a monoid $M \subseteq \BZ_{\geq 0}$,
+The \textbf{saturation of a monoid} $M \subseteq \BZ_{\geq 0}$,
 denoted $\sat(M)$, is the smallest integer $s$ such that $M
@@
 \begin{rem}
-For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the saturation of $D.$
+For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the
+\textbf{saturation of a divisor} $D$. For examples,
+see Subsection ~\ref{ssec:g-0-saturation}.
 \end{rem}
@@
 this section to that case in the following steps: characterizing
-saturations points (Subsection ~\ref{ssec:g-0_saturation}),
-describing base cases (Subsection ~\ref{ssec:g-0_base}), and
+saturations (Subsection ~\ref{ssec:g-0-saturation}),
+describing base cases (Subsection ~\ref{ssec:g-0-base}), and
 presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional})
 \footnote{Several computations used to generate the tables in
-Subsection ~\ref{ssec:g-0_base} and Subsection
+Subsection ~\ref{ssec:g-0-base} and Subsection
 ~\ref{ssec:g-0-exceptional} were done using a modified version of
@@
 \ssec{Saturation}
-\label{ssec:g-0_saturation}
-First, we present the saturations, as defined in Definition
-~\ref{defn:sat}, of the log spin canonical divisor for
-all cases where $g = 0$ and $\delta = 0$. The saturations can be computed using Riemann-Roch.
-By classifying the saturations of all signatures, we can determine
-the base cases on which we can apply inductive lemmas from
-Section ~\ref{sec:induction}. Exceptional cases are listed first
-and generic cases follow.
+\label{ssec:g-0-saturation}
+First, we present the saturations of the log spin canonical divisor
+for all cases where $g = 0$ and $\delta = 0$ (recall Definition
+~\ref{defn:sat} in Table ~\ref{table:g-0-sat}. The saturations can
+be computed using Riemann-Roch. By classifying the saturations of
+all signatures, we can determine the base cases on which we can
+apply inductive lemmas from Section ~\ref{sec:induction}. Note that
+the saturations of log spin canonical divisors only depend on the
+signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
+are listed first and generic cases follow.
 
@@
 \ssec{Base Cases}
-\label{ssec:g-0_base}
+\label{ssec:g-0-base}
 In order to apply Lemma ~\ref{lem:sat-3} and Lemma
@@
 Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
-(e.g. admissibility as defined in Definition \ref{defn:admissible}). We also show that that the associated spin
+(e.g. admissibility as defined in Definition \ref{defn:admissible}).
+We also show that that the associated log spin
 canonical rings are generated in degree at most $e := \max(5, e_1,
@@
 Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
-$\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
+$\sigma := (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
 generated by elements of degree at most $e = \max(5 , e_1, \ldots,
@@
 exceptional saturation as seen in Table ~\ref{table:g-0-sat}.
-Intuitively, these exceptional saturations can be viewed as ``
-forcing'' generators and relations in higher degrees than expected.
+Intuitively, these exceptional saturations can be viewed as
+``forcing'' generators and relations in higher degrees than expected.
 \end{rem}
@@
 \label{ssec:g-0-main}
-Now we can combine the base cases from Subsection \ref{ssec:g-0_base} with the inductive lemmas of Section \ref{sec:induction}.
+Now we can combine the base cases from Subsection \ref{ssec:g-0-base} with the inductive lemmas of Section \ref{sec:induction}.
 

### 2015-07-08 curves-write-up/spin_cring.tex
added generation 4

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 an inductive procedure for explicitly determining the generators
-and initial ideal of relations of log spin canonical rings. Many
+and initial ideal of relations of log spin canonical rings from a presentation of the canonical ring of the coarse space. Many
 explicit systems of generators and relations for curves of genus $2
@@
 When $g \geq 2$, we see that this is true because $\dim_k H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$.
-When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases} so there is an odd weight modular form in weight $3$ in general.
+When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases}.
+Hence, there is an odd weight modular form in weight $3$ in general.
 A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
@@
 \label{eg:congruence-bounds}
-Suppose $\Gamma \subset SL_2(\BZ)$ is a congruence subgroup. Then, since 
-the action  of $SL_2(\BZ)$ has points with stabilizer order 2 and 3, the 
-action of $\Gamma$ can only have points with stabilizer order 2 and 3. 
+Suppose $\Gamma \subset SL_2(\BZ)$ is any congruence subgroup. Then, since
+the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer order 1, 2 and 3, and has a cusp, the 
+action of $\Gamma$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
 Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
@@
 Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
-generated in degree at most $5$ with relations in degree at most $12$. 
-Furthermore, if the coarse space associated $\Gamma$ does not have, 
-$(0;3,3,3,3;0),$ there are relations in degree at most $10$, as follows 
-from the list of exceptional cases in Tables ~\ref{table:genus-0-exceptional-cases} and ~\ref{table:genus-0-exceptional}.
+generated in degree at most $5$ with relations in degree at most $10$.
+In fact, it is not difficult to reduce generation in weight at most 5 to generation in weight at most 4, as noted in Remark ~\ref{rem:cusp-generation-4}.
+Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because there is a cusp, so $\delta > 0$.
 \end{example}
@@
 \label{rem:genus-2-explicit-bound}
-Using the terminology from the proof of Theorem ~\ref{thm:g-high-main}, if $e = \max(e_1,\ldots, e_r) \geq 5$, we see that $R_L,$ has a generator in precisely $e$.
-This follows from the inductive application of Lemmas ~\ref{lem:sat-1} and \ref{lem:sat-2}, which, at the last step, add a minimal generator of $R_L$ over $R_L'$ in degree $e$.
-Similarly, this inductive application shows that our given presentation has a relation in degree $2e-4$.
+For this remark, we retain the terminology from the proof of Theorem ~\ref{thm:g-high-main}.
+Suppose $e :=  \max(e_1,\ldots, e_r).$ Then, $R_L$ has a generator in degree $e$ when $e \geq 5$ and a relation in degree at least $2e-4$ when $e \geq 7$.
+Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively
+applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, we obtain that $R_L$ is minimally generated over $R_{L'}$ by an element in degree $e,$ assuming $e \geq 5$.
+Furthermore, if $e \geq 7$ and $e_i = e,$
+then there must be a relation with leading term $y_{i,e_i} \cdot y_{i,e_i-4}.$ Hence, there is a relation in degree at least $2e - 4$. 
+Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there are $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, there is necessarily a relation with leading term $y_{i, e_i} \cdot y_{j, e_j}$ in degree $2e$.
+
+This analysis also applies to the cases that $g = 0$ and $g = 1$.
 \end{rem}
@@
 \label{rem:genus-1-explicit-bound}
-In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
-That, is one can start with the generators and relations found in the base cases, and inductively add in generators and relations as one adds and then increments stacky points.
-Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, when $e = \max(5,e_1,\ldots, e_r) \geq 5$ we obtain that $R_L$ has a generator in degree $e$ and a relation in degree at least $2e - 4$.
-Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, at least in our construction, there is a relation in degree $2e$.
+In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, the proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
+That, is one can start with the generators and relations found in the base cases and inductively add in generators and relations as one adds and then increments stacky points.
+As described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e: = \max(e_1,\ldots, e_r) \geq 7$, there is necessarily a generator in degree $e$ and a relation in degree $2e$.
 \end{rem}
@@
 n \cdot \infty$ with $n \in \BZ_{\geq -1}$. This is a classical
-case which is done by Voight and Zureick-Brown \cite[Section 4.2]
+case done by Voight and Zureick-Brown \cite[Section 4.2]
 {vzb:stacky}. When $n = -1$, then $R_\halfcan = \Bk$.  When $n = 0$,
@@
 \label{rem:genus-0-explicit-bound}
-Just like the case of genus 1, as described in Remark ~\ref{rem:genus-1-explicit-bound}, the proof of Theorem ~\ref{thm:g-0-main} gives an explicit construction of the generators and relations for the log spin canonical ring $R_L$.
-Furthermore, similarly to the description given in Remarks in ~\ref{rem:genus-2-explicit-bound} and Remark ~\ref{rem:genus-0-explicit-bound}, when $e = \max(e_1, \ldots, e_r) \geq 5,$ there is a generator in degree $e$ and a relation in degree at most $2e$.
+Similarly to the case of genus 1, as described in Remark ~\ref{rem:genus-1-explicit-bound}, the proof of Theorem ~\ref{thm:g-0-main} gives an explicit construction of the generators and relations for the log spin canonical ring $R_L$.
+Furthermore, as described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e := \max(e_1, \ldots, e_r)$ is at least $7$, there is a generator in degree $e$ and a relation in degree at least $2e-4$.
 This can be seen from the inductive application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref{lem:sat-3}.
-Additionally, as in the case of genus 1, if there are $1 \leq i < j \leq r$ with $e = e_i = e_j$ then there is a relation in degree $2e$.
+\end{rem}
+
+\begin{rem}
+\label{rem:cusp-generation-4}
+Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}.
+A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in degree at most 4.
+This is $\delta > 0$, so $L_X$ is effective.
+Addtionally, $R_{L_X}$ is generated in degree 1, and inductively applying Lemma ~\ref{lem:sat-1} only adds generators in degree 3 and 4.
+Therefore, $R_L$ is generated in degree at most 4.
+Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in degree at most 4.
 \end{rem}

### 2015-07-08 curves-write-up/spin_cring.tex
editing introduction

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 \begin{abstract}
- 	Consider modular forms arising from finite-area
-	quotients of the upper-half plane by Fuchsian groups.  
+ 	Consider modular forms arising from a finite-area
+	quotient of the upper-half plane by a Fuchsian group.  
 	By the classical results of Kodaira--Spencer, 
 	this space of modular forms may be
-	viewed as log spin canonical ring of a stacky curve.
+	viewed as a log spin canonical ring of a stacky curve.
 	In this paper, we tightly bound the degrees of minimal
-	generators and relations of log spin canonical rings and,
-	as a consequence, 
+	generators and relations of log spin canonical rings.  
+	As a consequence, we
 	obtain a tight bound on the degrees of minimal generators and relations  		
@@
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma),$ is to write down a presentation.
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma)$ is to write down a presentation.
 %of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
@@
 \begin{align*}
-	R(X, K_X) = \bigoplus_{k \geq 0} H^0(X, kK_X),
+	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
 \end{align*}
@@
 sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$. When $g \geq 2$, Petri's theorem gives generators
-and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
-is generated in degree 1 with relations in degree 2, as shown in
-\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
-\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
+\cong \proj R$. When $g \geq 2$, Petri's theorem 
+shows that, in most cases, $R(X, K_X)$
+is generated in degree 1 with relations in degree 2 (see
+Saint-Donat \cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
+\cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
 geometric consequence that all such canonically embedded curves are
-scheme theoretically cut out by degree 2 equations.
+scheme-theoretically cut out by degree 2 equations.
 
@@
 study in this paper is the {\bf log spin canonical ring} of $(\sx,
-\Delta, \halfcan),$ notated as
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor).
+\Delta, \halfcan),$ defined as
+\begin{align*}
+	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor).
 \end{align*}
@@
 Then the log spin canonical ring is generated as a $\Bk$-algebra by 
-elements of degree at most $e = \max(5, e_1, \ldots, e_r)$ with
+elements of degree at most $e := \max(5, e_1, \ldots, e_r)$ with
 relations generated in degrees at most $2e$,
@@
 Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.
-In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the genus $g \geq 2$ case we deduce base cases from more general arguments.
+In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.
 \begin{rem}
 \label{rem:explicit-generators}
-The main theorem obtains bounds on the degrees of the generators
-and relations of log spin canonical rings. However, the proof
-of the genus one and genus zero cases also yield explicit systems
-of generators and an explicit initial ideal of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
-Furthermore, our proof of the genus $g \geq 2$ case also provides
+%The main theorem obtains bounds on the degrees of the generators
+%and relations of log spin canonical rings. 
+In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
+of the genus one and genus zero cases of our main theorem also yield explicit systems
+of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
+Although our proof of the genus $g \geq 2$ case provides
 an inductive procedure for explicitly determining the generators
-and initial ideal of relations of log spin canonical rings. Many
+and initial ideal of relations of a log spin canonical ring given generators and relations of the corresponding ring on the coarse space, actually computing such generators and relations of log spin canonical on the coarse space can be difficult.
+Many
 explicit systems of generators and relations for curves of genus $2
@@
 \[
-	\di \sx := \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
+	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
 	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
@@
 Recall the standard notation 
-$$\sco(D) := \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
+$$\sco(D) = \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
 Let $\sx$ be a stacky curve with coarse space $X$.
@@
 \[
-	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
+	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
 \]
@@
 \label{rem:odd-denom}
-Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that $\halfcan$ is of the form
+Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that
 \[
@@
 \ssec{Saturation}
-We define the notion of the saturation of a divisor, as can be
-found in Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
-The classification of the saturations of log spin canonical
-divisors are used in the proof of the main theorem and the various
-lemmas in Section ~\ref{sec:induction}.
+
+We define the notion of the saturation of a divisor, as can be found in
+Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
 
@@
 \[
-	\Eff(D) := \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
+	\Eff(D) = \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
 \]
@@
 \label{defn:sat}
-The \textbf{saturation of a monoid} $M \subseteq \BZ_{\geq 0}$,
+The \textbf{saturation} of a monoid $M \subseteq \BZ_{\geq 0}$,
 denoted $\sat(M)$, is the smallest integer $s$ such that $M
@@
 \begin{rem}
-For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the
-\textbf{saturation of a divisor} $D$. For examples,
-see Subsection ~\ref{ssec:g-0-saturation}.
+For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the saturation of $D.$
 \end{rem}
@@
 this section to that case in the following steps: characterizing
-saturations (Subsection ~\ref{ssec:g-0-saturation}),
-describing base cases (Subsection ~\ref{ssec:g-0-base}), and
+saturations points (Subsection ~\ref{ssec:g-0_saturation}),
+describing base cases (Subsection ~\ref{ssec:g-0_base}), and
 presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional})
 \footnote{Several computations used to generate the tables in
-Subsection ~\ref{ssec:g-0-base} and Subsection
+Subsection ~\ref{ssec:g-0_base} and Subsection
 ~\ref{ssec:g-0-exceptional} were done using a modified version of
@@
 \ssec{Saturation}
-\label{ssec:g-0-saturation}
-First, we present the saturations of the log spin canonical divisor
-for all cases where $g = 0$ and $\delta = 0$ (recall Definition
-~\ref{defn:sat} in Table ~\ref{table:g-0-sat}. The saturations can
-be computed using Riemann-Roch. By classifying the saturations of
-all signatures, we can determine the base cases on which we can
-apply inductive lemmas from Section ~\ref{sec:induction}. Note that
-the saturations of log spin canonical divisors only depend on the
-signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
-are listed first and generic cases follow.
+\label{ssec:g-0_saturation}
+First, we present the saturations, as defined in Definition
+~\ref{defn:sat}, of the log spin canonical divisor for
+all cases where $g = 0$ and $\delta = 0$. The saturations can be computed using Riemann-Roch.
+By classifying the saturations of all signatures, we can determine
+the base cases on which we can apply inductive lemmas from
+Section ~\ref{sec:induction}. Exceptional cases are listed first
+and generic cases follow.
 
@@
 \ssec{Base Cases}
-\label{ssec:g-0-base}
+\label{ssec:g-0_base}
 In order to apply Lemma ~\ref{lem:sat-3} and Lemma
@@
 Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
-(e.g. admissibility as defined in Definition \ref{defn:admissible}).
-We also show that that the associated log spin
+(e.g. admissibility as defined in Definition \ref{defn:admissible}). We also show that that the associated spin
 canonical rings are generated in degree at most $e := \max(5, e_1,
@@
 Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
-$\sigma := (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
+$\sigma = (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
 generated by elements of degree at most $e = \max(5 , e_1, \ldots,
@@
 exceptional saturation as seen in Table ~\ref{table:g-0-sat}.
-Intuitively, these exceptional saturations can be viewed as
-``forcing'' generators and relations in higher degrees than expected.
+Intuitively, these exceptional saturations can be viewed as ``
+forcing'' generators and relations in higher degrees than expected.
 \end{rem}
@@
 \label{ssec:g-0-main}
-Now we can combine the base cases from Subsection \ref{ssec:g-0-base} with the inductive lemmas of Section \ref{sec:induction}.
+Now we can combine the base cases from Subsection \ref{ssec:g-0_base} with the inductive lemmas of Section \ref{sec:induction}.
 

### 2015-07-08 curves-write-up/spin_cring.tex

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.
-In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the genus $g \geq 2$ case we deduce base cases from more general arguments.
+In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.
 \begin{rem}
 \label{rem:explicit-generators}
-The main theorem obtains bounds on the degrees of the generators
-and relations of log spin canonical rings. However, the proof
-of the genus one and genus zero cases also yield explicit systems
-of generators and an explicit initial ideal of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
-Furthermore, our proof of the genus $g \geq 2$ case also provides
+%The main theorem obtains bounds on the degrees of the generators
+%and relations of log spin canonical rings. 
+In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
+of the genus one and genus zero cases of our main theorem also yield explicit systems
+of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
+Furthermore, our proof of the genus $g \geq 2$ case provides
 an inductive procedure for explicitly determining the generators
-and initial ideal of relations of log spin canonical rings from a presentation of the canonical ring of the coarse space. Many
+and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.
+Many
 explicit systems of generators and relations for curves of genus $2

### 2015-07-08 curves-write-up/spin_cring.tex
edits to remarks on congruence subgroups

@@
 generated in degree at most $5$ with relations in degree at most $10$.
-In fact, it is not difficult to reduce generation in weight at most 5 to generation in weight at most 4, as noted in Remark ~\ref{rem:cusp-generation-4}.
+In fact, it is not difficult to reduce generation in weight at most 5 to generation in weight at most 4 with relations in weight at most 8, as noted in Remark ~\ref{rem:cusp-generation-4}.
 Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because there is a cusp, so $\delta > 0$.
@@
 Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}.
-A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in degree at most 4.
-This is $\delta > 0$, so $L_X$ is effective.
-Addtionally, $R_{L_X}$ is generated in degree 1, and inductively applying Lemma ~\ref{lem:sat-1} only adds generators in degree 3 and 4.
-Therefore, $R_L$ is generated in degree at most 4.
-Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in degree at most 4.
+A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in weight at most 4.
+Since $\delta > 0$, $L_X$ is effective.
+Addtionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8.
+Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8.
+Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in weight at most 4 with relations in weight at most 8.
 \end{rem}

### 2015-07-08 curves-write-up/spin_cring.tex
dk edits

@@
 If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$.
-When $g \geq 2$, we see that this is true because $\dim_k H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$.
+When $g \geq 2$, we see that this is true because $\dim_\Bk H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$.
 When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases}.
@@
 Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
-for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
+for any $i \in \{0, \ldots, \lfloor k \frac{\alpha}{
 \beta} \rfloor \}$. We will the use positive best lower approximations to
@@
 \[
-	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
+	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
 	\beta}

### 2015-07-08 curves-write-up/spin_cring.tex
changed additionally

@@
 Since $\delta > 0$, $L_X$ is effective.
-Addtionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8.
+Additionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8.
 Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8.

### 2015-07-08 curves-write-up/spin_cring.tex
some rewording to new remarks from aaron

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, the proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
-That, is one can start with the generators and relations found in the base cases and inductively add in generators and relations as one adds and then increments stacky points.
-As described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e: = \max(e_1,\ldots, e_r) \geq 7$, there is necessarily a generator in degree $e$ and a relation in degree $2e$.
+One can start with the generators and relations found in the base cases and inductively add generators and relations as one adds stacky points and increments stabilizer orders.
+As described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e := \max(e_1,\ldots, e_r) \geq 7$, there is necessarily a generator in degree $e$ and a relation in degree $2e$.
 \end{rem}
@@
 \label{rem:genus-0-explicit-bound}
-Similarly to the case of genus 1, as described in Remark ~\ref{rem:genus-1-explicit-bound}, the proof of Theorem ~\ref{thm:g-0-main} gives an explicit construction of the generators and relations for the log spin canonical ring $R_L$.
-Furthermore, as described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e := \max(e_1, \ldots, e_r)$ is at least $7$, there is a generator in degree $e$ and a relation in degree at least $2e-4$.
-This can be seen from the inductive application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref{lem:sat-3}.
+The proof of Theorem ~\ref{thm:g-0-main} in genus zero gives an
+explicit construction of the generators and relations for the log
+spin canonical ring $R_L$. This is similar to the case of genus 1
+in Remark ~\ref{rem:genus-1-explicit-bound}. Furthermore, there is
+a generator in degree $e$ and a relation in degree at least $2e-4$
+when $e := \max(e_1, \ldots, e_r)$ is at least $7$ (see Remark ~\ref
+{rem:genus-2-explicit-bound}). This can be seen from the inductive
+application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref
+{lem:sat-3}.
 \end{rem}
@@
 \label{rem:cusp-generation-4}
-Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}.
-A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in weight at most 4.
-Since $\delta > 0$, $L_X$ is effective.
-Addtionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8.
-Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8.
-Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in weight at most 4 with relations in weight at most 8.
+Here, we describe how to obtain a slightly better bound for our
+application to modular forms from example ~\ref{eg:congruence-bounds}.
+A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that,
+if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$
+, then $R_L$ is generated in weight at most 4. Since $\delta > 0$,
+$L_X$ is effective. Additionally, $R_{L_X}$ is generated in weight 1
+, and inductive applications of Lemma ~\ref{lem:sat-1} only add
+generators in weights 3 and 4 and relations in weight at most 8.
+Therefore, $R_L$ is generated in weight at most 4 with relations in
+weight at most 8. Note that a similar analysis of the proof of
+Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence
+subgroups are generated in weight at most 4 with relations in
+weight at most 8.
 \end{rem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%% Further Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-08 curves-write-up/spin_cring.tex

@@
 Here, we describe how to obtain a slightly better bound for our
-application to modular forms from example ~\ref{eg:congruence-bounds}.
+application to modular forms from Example ~\ref{eg:congruence-bounds}.
 A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that,
-if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$
-, then $R_L$ is generated in weight at most 4. Since $\delta > 0$,
-$L_X$ is effective. Additionally, $R_{L_X}$ is generated in weight 1
-, and inductive applications of Lemma ~\ref{lem:sat-1} only add
+if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$,
+then $R_L$ is generated in weight at most 4. Since $\delta > 0$,
+$L_X$ is effective. Additionally, $R_{L_X}$ is generated in weight 1,
+and inductive applications of Lemma ~\ref{lem:sat-1} only add
 generators in weights 3 and 4 and relations in weight at most 8.

### 2015-07-08 curves-write-up/spin_cring.tex
fix typo in further q 2

@@
 		gives an affirmative answer to this question: If $\sx$ has signature 
-		$(g; e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
+		$(g; e_1, \ldots, e_r; \delta)$ then $R_D$ is generated in degree at 
 		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most

### 2015-07-08 curves-write-up/arXiv versions/spin_cring_arXiv_v1.tex
minor edits, add arxiv v1 version
i.e.,
remark revised before g0sat

--- 2015-07-08 curves-write-up/spin_cring.tex
@@
 \usepackage{subfiles}
-%\usepackage{mathpazo} not a huge fan
 \usepackage{euler}
@@
 
-%\addtolength{\oddsidemargin}{-.5 in}
-	%\addtolength{\evensidemargin}{-.4 in}
-	%\addtolength{\textwidth}{1 in}
-%
-	%\addtolength{\topmargin}{0 in}
-	%\addtolength{\textheight}{0 in}
-
 \RequirePackage{color}
@@
 
-%\usepackage{hyperref}
-  %\hypersetup{colorlinks=true,citecolor=blue}
-
 \usepackage{tikz}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%
-%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \newtheorem{cor}[thm]{Corollary}
-	\newtheorem{claim}[thm]{Claim}
 	\newtheorem{question}[thm]{Question}
@@
   \newtheorem{example}[thm]{Example}
-  \newtheorem{exer}[thm]{Exercise}
-  \newtheorem{ctexample}[thm]{Counterexample}
-  \newtheorem{convention}[thm]{Convention}
-	\newtheorem{conjecture}[thm]{Conjecture}
 
@@
 	\newtheorem{rem}[thm]{Remark}
-  \newtheorem{note}[thm]{Notation}
-  \newtheorem*{note*}{Notation}
-  \newtheorem{case}{Case}
 
@@
 
-\newcommand\nc{\newcommand}
-\nc\on{\operatorname}
-\nc\renc{\renewcommand}
 \newcommand\ssec{\subsection}
-\newcommand\sssec{\subsubsection}
 \newcommand\BH{{\mathbb H}}
@@
 \newcommand\BC{{\mathbb C}}
-\newcommand\BF{{\mathbb F}}
 \newcommand\BR{{\mathbb R}}
@@
 \newcommand\BZ{{\mathbb Z}}
-\newcommand\BA{{\mathbb A}}
 \newcommand\Bk{{\Bbbk}}
@@
 
-\newcommand{\id}{\mathrm{id}}
 \newcommand\im{\text{im }}
-\newcommand\coker{\text{coker}}
-\newcommand\spec{\text{Spec }}
 \newcommand\proj{\text{Proj }}
-\newcommand\gal{\mathrm{Gal}}
 
@@
 \newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
-\newcommand{\se}[1]{\section*{Problem #1}}
 \newcommand{\halfcan}{L}
@@
 \DeclareMathOperator{\initial}{in_\prec}
-\DeclareMathOperator{\gin}{gin}
 \DeclareMathOperator{\Eff}{Eff}
@@
 
-\newcommand{\GL}{\operatorname{GL}}
-\newcommand{\SL}{\operatorname{SL}}
-\newcommand{\PGL}{\operatorname{PGL}}
 \newcommand{\PSL}{\operatorname{PSL}}
@@
 \begin{abstract}
- 	Consider modular forms arising from a finite-area
-	quotient of the upper-half plane by a Fuchsian group.  
-	By the classical results of Kodaira--Spencer, 
-	this space of modular forms may be
-	viewed as a log spin canonical ring of a stacky curve.
-	In this paper, we tightly bound the degrees of minimal
-	generators and relations of log spin canonical rings.  
-	As a consequence, we
-	obtain a tight bound on the degrees of minimal generators and relations  		
-	for rings of modular forms of arbitrary integral weight.
+ 	Consider modular forms arising from a finite-area quotient of the
+	upper-half plane by a Fuchsian group. By the classical results of
+	Kodaira--Spencer, this space of modular forms may be viewed as a
+	log spin canonical ring of a stacky curve. In this paper, we
+	tightly bound the degrees of minimal generators and relations of
+	log spin canonical rings. As a consequence, we obtain a tight bound
+	on the degrees of minimal generators and relations for rings of
+	modular forms of arbitrary integral weight.
 \end{abstract}
@@
 \section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian group}, i.e.,~ a discrete subgroup of
+Let $\Gamma$ be a {\bf Fuchsian group}, i.e.~ a discrete subgroup of
 $\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
@@
 \backslash \BH$ is a Riemann surface over $\BC$. 
-$\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
-compact Riemann surface, $\Gamma \backslash \BH^*,$ by adding in
-cusps, with associated divisor of cusps $\Delta$.
+Although $\Gamma \backslash \BH$ may be non-compact, we can form a
+compact Riemann surface $\Gamma \backslash \BH^*$ by adding in
+cusps (with associated divisor of cusps $\Delta$).
 
@@
 generalization of the GAGA principle.
-By \cite[Proposition 6.1.5]
+As shown by Voight and Zureick-Brown \cite[Proposition 6.1.5]
 {vzb:stacky}, there is an equivalence of categories between orbifold
-curves and log stacky curves over $\BC$. Hence, for the remainder
+curves and log stacky curves over $\BC$. For the remainder
 of the paper, we will work in the algebraic category.
@@
 with multiplication structure corresponding to tensor product of
-sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
-\cong \proj R$. When $g \geq 2$, Petri's theorem 
+sections. In the case that $g \geq 2$, $\Omega_X$ is ample and
+therefore $X \cong \proj R$. When $g \geq 2$, Petri's theorem 
 shows that, in most cases, $R(X, K_X)$
@@
 ~\ref{ssec:stacky-background}.
-
-%If $X$ is a curve, \todo{why do you start with a curve and then
-%move to a stacky curve? shouldn't it be the opposite order?} then
-%we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$
-%and {\bf stacky points} (also called {\bf{fractional points}}) $P_1,
-%\ldots, P_r$ with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{
-%\geq 2}$ if 
-%\[
-	%\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
-	%P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	%\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X
-%\]
-
-%A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where
-%$\Delta \in \di X$ is a log divisor and $2\halfcan = K_X +
-%\Delta + \sum_{i=1}^{r} \subhalf{e_i} P_i.$
-%The central object of study in this paper is the {\bf log spin
-%canonical ring} of $(\sx, \Delta, \halfcan)$ is
-%\begin{align*}
-	%R(\sx, \Delta, \halfcan) = \bigoplus_{d \geq 0} H^0(X, d \halfcan)
-%\end{align*}
 
@@
 rings of modular forms.
-%Note that the lemma from Voight and Zureick-
-%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
-%from the classical work of Kodaira--Spencer
-%\cite{kodaira-spencer:deformations}.
 
@@
 
-The results of this paper can be easily couched in terms of the language of stacks.
-If one works over an arbitrary field $\Bk$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.,~ the residue field of each
+The results of this paper can be easily phrased in terms of the language of stacks.
+If one works over an arbitrary field $\Bk$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.~ the residue field of each
 of the stacky points is separable.
@@
 semi-canonical divisor, or theta characteristic) associated to the
-coarse space $X$ of $\sx.$  (i.e.,~ $\halfcan_X$ is a divisor such
+coarse space $X$ of $\sx.$  (i.e.~ $\halfcan_X$ is a divisor such
 that $2\halfcan_X \sim K_X + \Delta$). 
@@
 
-%Furthermore, we will use Gr\"{o}bner bases, which are bases
-%for these initial ideals and have many useful properties.
-
 \begin{defn}
@@
 \ssec{Admissibility}
-
 Here, we define a notion of admissibility that is quite similar to the admissibility defined by Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}.
@@
 One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
-%in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ 
 we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
@@
 Then the map in ~\eqref{eqn:noether-377} is surjective when $k \geq
-21 + s = 26$ (i.e.,~ $R'$ is generated up to degree 25).
+21 + s = 26$ (i.e.~ $R'$ is generated up to degree 25).
 
@@
 \begin{figure}[H]
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\includegraphics{spin-377-pic-pics.pdf} \\
 \caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
@@
 
-%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
-%represent the pole orders of $x_i$ at each point. Then these generators
-%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
-%respectively.
-
 We can directly see that the relations are given in degrees $10$
@@
 with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
-%These quadratics must also determine minimal generators for $I$ by
-%Lemma ~\ref{lem:minimal_quadratic}.
 Thus, $R'$ is generated up to degree $e = 7$ with relations up to
 degree $2e = 14$, as desired.
-
-%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
-%since $e_i = 9 > e$ for all $i \in J$.
 \end{example}
@@
 
-%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
-%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
-%spin canonical divisors.
-
-%However, before we can answer these general lemmas, it is useful
-%to prove a nice result about minimal generation of ideals of
-%relations.
-%
-%\todo{Include one of the following, if the first one, include a 
-%remark for quotient}
-
-%\begin{lem}
-%\label{lem:minimal_quadratic}
-%Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
-%generated in degree 1, is equipped with a monomial ordering $\prec$.
- %Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
-%rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
-%\ldots, f_j$, where $\initial(f_i) = x_i x_j,$ and no term of $f_i$
-%is of the form $x_k$. Then, the elements $f_i$ determine minimal
-%generators for $I$.
-%\end{lem}
-%\begin{proof}
-%Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
-%degree 1. Then,
-%\[
-	%\phi : k[x_1, \ldots, x_n] \rightarrow B
-%\]
-%\noindent
-%determines a map of rings, no longer necessarily graded. Consider
-%the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
-%\todo{This ordering isn't quite right. 
-%We need to preserve the ordering on quadratic terms}
-%By
-%assumption, the kernel $I$ is generated by elements whose initial
-%terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
-%\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
-%generators for $I$ must have at least $j$ elements. Since $f_1,
-%\ldots, f_j$ is such a set, it is minimal.
-%\end{proof}
-%
-%\begin{rem}
-%In particular, in the case of
-%\[
-	%\begin{tikzcd}
-		%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
-		%\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
-		%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	%\end{tikzcd}
-%\]
-%inducing
-%\[
-	%I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
-%\]
-%\todo{how do we make this proof?}
-%\end{rem}
-%\begin{lem}
-%\label{lem:minimal_quadratic}
-%Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
-%generated in degree 1 that are equipped with monomial ordering $\prec$.
-%Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
-%rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
-%\[
-	%\begin{tikzcd}
-	%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
-	%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
-	%\end{tikzcd}
-%\]
-%Further suppose that $I'$ is generated over $I$ by elements $f_1,
-%\ldots, f_j$ as a $k$-vector space, where $\initial(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
-%is of the form $y_i$. Then, the elements $f_i$ determine minimal
-%generators for $I'$ over $I$.
-%\end{lem}
-%
-%\begin{proof}
-%Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
-%degree 1. Then,
-%\[
-	%\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
-%\]
-%\[
-	%\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
-%\]
-%
-%
-%\noindent
-%determines map of rings, no longer necessarily graded. 
-%By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent. By the theory of Gr\"{o}bner basis,
-%\[
-	%\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
-%\]
-%so
-%\[
-	%\dim_k (I'/I)_2=j.
-%\]
-%This implies any set of
-%generators for $I$ must have at least $j$ elements. Since $f_1,
-%\ldots, f_j$ is such a set, it is minimal.
-%\end{proof}
-%
-%\begin{rem}
-%\label{rem:minimal_quadratic_trivial_case}
-%It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
-%case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
-%are $k$-minimal generators for $I'$ (over the trivial base vector
-%space). 
-%\end{rem}
-%With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
-
 \ssec{Adding Points}
 \label{ssec:add-points}
-%In this section, we prove various inductive statements under the following setup:
-%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d \in\BN$ and certain saturation conditions.
-Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.
-Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).
-\todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph?
-Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
-%Before proving three lemmas that allow us to inductively add points to the support of a log spin canonical divisor
 First, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $\Bk[x_1, \ldots, x_m] \to R_D$.
@@
 \begin{figure}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+\includegraphics{spin-lower-approximations-pic-pics.pdf}
 \caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
@@
 Finally, (c) of this lemma follows immediately by looking at the constructions of parts (a) and (b).  
-
-%Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
-%\frac{\alpha}{\beta}$ is not a best lower approximation than we can
-%construct an element in degree $d$ with pole degree $c$ by either $y
-%_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
-%same conditions.
-This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.
-In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.
-%
-%Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.
-Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if
-%$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
-%successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
-%\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
-%\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
-%convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
-%with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
-%is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
-%expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
-%is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
-%\[
-	%x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
-%\]
-%
-%\noindent
-%giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
-%the beginning}
-%
-%Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
-%< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
-%basis element of the form described above: $y_n^0 y_j y_i u^0$). 
-%Choose the maximal $\halfcan$ such that $c_h \le c_i + c_j$; since $1 < d_i
-%\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
-%so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
-%Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
-%$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
-%= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
-%best lower approximation of $\frac{\alpha}{\beta}$ with denominator
-%larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
-%know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
-%Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
-%1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
-%h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
-%appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
-%$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
-%follow a similar technique as in the previous paragraph to cancel
-%out poles of $y_i y_j$ at $P $ to find
-%\[
-	%y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
-	%u^{b_l}\in R_D
-%\]
-%
-%\noindent
-%implying a relation with initial term $y_i y_j$. 
-%
-%Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
-%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e.,~ $c_i, c_j \le
-%\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
-%{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
-%with the same pole order; following the same method as the previous
-%two paragraphs we find
-%\[
-	%y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
-%\]
-%
-%\noindent
-%Similarly if $i = 1$, then we get the same result using
-%\[
-	%y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
-%\]
-%
-%\noindent
-%In both cases we deduce that $y_i y_j$ is an initial term of some relation.
-%
-%
-%Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
-%1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
-%then there are no relations with initial term a power of $y_i$
-%and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
-%note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
-%{reference to Evan's paper where he proves this} Therefore, if $i >
- %1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
-%in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
-%Following a similar technique to the previous paragraphs we find
-%\[
-	%(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
-%\]
-%
-%\noindent
-%Similarly if $i = 1$ then
-%\[
-	%(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
-%\]
-%
-%\noindent
-%In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation. 
-%
-%Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
-%generated by the initial terms described in the previous paragraphs
-%together with $\initial(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
-%
-%We show that $J$ is in fact all of the initial ideal. Suppose
-%$f$ is a non-constant monomial that does not lie within $J$.
-%Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
-%there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
-%some $x_j \mid f$ or else we would have $y_i x_j \mid f$
-%contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
-%i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
-%element of a relation and divides $f$. If $d_i = 1$ as well, then
-%we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
-%$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
-%\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
-%f$. We observe that the remaining elements are precisely those of
-%the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
-%which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
-%, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
-%Therefore, by dimension counting (in each degree), we see that $J$
-%is the initial ideal of $I$.
-
-%Furthermore, since our choice of $y_i
-%$'s was generic, this is in fact the generic initial ideal.
-
-%In the case when all $\frac{\alpha}{\beta}\le 1$, Lemma
-%~\ref{lem:minimal_quadratic} immediately tells us that the Gr\"{o}bner
-%basis defined above is minimal.
-%\todo{What about $\frac{\alpha}{\beta} > 1$?}
 \end{proof}
@@
 		\end{align*}
-	%\item[(c)] Any set of minimal generators for $I'$ together with 
-		%any set of relations with leading terms as in (b) minimally 
-		%generate $I$.
 \end{enumerate}
@@
 Hence, by Lemma \ref{lem:relations_from_generators_induction}, part (b) holds.
-
-%For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
-%we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
-%Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$.
-In both cases we induce a relation, with initial term described in the lemma's statement.
-Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
-%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
-
 \end{proof}
@@
 		\end{align*}
-	%\item[(c)] Any set of generators for $I'$ together with 
-	%	any set of relations with leading terms as in (b) 
-	%	generate $I$.
 \end{enumerate}
@@
 we can argue similarly to Lemma \ref{lem:sat-1} that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, concluding part (b).
-
-%To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
-%_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
-%suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
-%,$ elements of degree $d$ in the claimed basis of
-%~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
-%\rfloor $ and $b = d \bmod 3$, we have that the elements
-%
-%\begin{align*}
-	%x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
-%3+b}
-%\end{align*}
-%
-%\noindent
-%are precisely $a$ elements, which are all independent as they have
-%distinct pole orders at $P$. This completes part (a).
-%
-%To show part (b), note that the generators in
-%~\ref{eqn:add_one_generator} are precisely a set of monomials which
-%generate $k[x, y]/J$ over $k$. So, to show $J = \initial(I)$, it
-%suffices to show that all generators of $J$ lie in $\initial(I)$.
-%
-%This follows, since there exist constants $A_{i,j} \in k$ for $4
-%\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
-%elements $w_{i,j} \in R'$ so that the following linear combinations
-%of elements lie in $R'$.
-%
-%\begin{align*}
-	%&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
-	%\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
-	%&y_4^2 + B_1 y_3 y_5 \\
-	%&y_4 y_5 + B_2 y_3^2 x_3 \\
-	%&y_5^2 + B_3 y_3^2 x_4
-%\end{align*}
-%
-%\noindent
-%Of course, the initial terms of these elements are precisely the
-%generators of $J$, completing (b).
-
-%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}
 \end{proof}
-
-%\begin{lem}
-%\label{lem:adding_points_saturation_2_to_1_with_log}
-%Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be log spin log stacky spin 
-%curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
-%\halfcan'$, meaning that $L=L'+P$. Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
-%\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures. Suppose 
-%$\sat(\Eff(\halfcan))= 1$ and $\sat(\Eff(\halfcan'))=2$. Further suppose $R_{\halfcan'} = k[x_2, 
-%x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. Then
-%
-%\begin{enumerate}
-%\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
-%(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)> 0$ and $\{y_1^2, y_2\}$ is linearly 
-%independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-%\item[(b)] Equip $k[y_1, y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
-%x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$. 
-%Then
-%\begin{align*}
-			%\initial(I) &= \initial(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			%&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
-			%&+\langle y_2^2\rangle.
-		%\end{align*}
-%\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-%leading terms as above minimally generate $I$.
-%\end{enumerate}
-%\end{lem}
-%
-%\begin{proof}
-%Since adding $P$ to $\halfcan'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)= 1$. 
-%Choose any $y_1\in H^0(X, \lfloor L\rfloor)$; we know by saturation arguments that $-
-%\ord_P(y_1)= 1$. Furthermore, since $\delta> 0$, we use Riemann-Roch to deduce that for 
-%all $d> 1$ $h^0(X, \lfloor k\halfcan\rfloor)=h^0(k\halfcan') +d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
-%$-vector space over $(R_{\halfcan'})_d$. In particular, this means we can generically 
-%choose an element $y_2\in H^0(X, \lfloor 2L\rfloor)$ linearly independent from $y_1^2$. By 
-%dimension counting, we see that 
-%\[
-	%\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c \in \{0,1\}\rangle
-%\]
-%\[
-	%\langle y_1^a y_2: a\ge 0\rangle
-%\]
-%form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. This completes part (a).
-%
-%To show part (b), we note that the monomials in the basis above generate $k[x, y]/\initial_
-%\prec(I)$. Thus, it is sufficient to show that $J\subseteq \initial(I)$. For $j\ge 2$, we 
-%can choose $w_j$ in degree $\deg(x_j) + 1$ and $A_j\in k$ such that
-%\[
-	%y_2x_j -A_jy_3w_j
-%\]
-%has no pole at $P$ at thus lies in $R_{\halfcan'}$. Similarly, we can choose $B$ and $C$ 
-%such that
-%\[y^2_4+By_1^2x_2+Cy_1x_3\]
-%has no pole at $P$, so it lies in $R_{\halfcan'}$. These give us relations with initial terms 
-%as desired, concluding part (b).
-%
-%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
-%
-%\end{proof}
-%
-%\begin{lem}
-%\label{lem:adding_points_saturation_2_to_1_no_log}
-%Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be log spin log stacky spin curves 
-%with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$. Let $(g; e_1, \ldots, e_
-%\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures. 
-%Suppose $'\sat(\Eff(\halfcan))= 1$ and $'\sat(\Eff(\halfcan'))=2$. Further suppose 
-%$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$. 
-%Then
-%\begin{enumerate}
-%\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
-%(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)> 1$ and $\{y_1^3, y_2\}$ is linearly 
-%independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
-%\item[(b)] Equip $k[y_1, y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
-%x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$. 
-%Then
-%\begin{align*}
-			%\initial(I) &= \initial(I')k[x_2, \ldots, x_m, y_1, y_2] \\
-			%&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
-			%&+\langle y_3^2
-		%\end{align*}
-%\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
-%leading terms as above minimally generate $I$.
-%\end{enumerate}
-%\end{lem}
-%\begin{proof}
-%The proof follows similarly to that of Lemma 
-%\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
-%\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
-%generator in degree 3 rather than degree 2. 
-%\end{proof}
-%
-%We prove an inductive theorem on adding 2-sat here.
-%
-%
-%We will now prove a Lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
-%reference} and O'Dorney\todo{reference}.
-%
-%\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
-%Notice that in Lemma ~\ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\bar{d}, \beta)$ with relations generated in degree at most $\max(\bar{\tau}, \bar{d} + \beta, 2 \beta)$
-%\end{rem}
-%
-%This yields some immediate corollaries:
-%
-%\begin{cor}\label{cor:effective_Q_divisor_can_ring}
-%If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\BQ$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
-%\end{cor}
-%
-%\begin{proof}
-%We can prove this by induction. As a base case, let $D\sim 0$. Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
-%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i = 1}^{r+ 1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.
-By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.
-Since $D$ is effective, the condition of equation ~\ref{eqn:deg1-sat-ind} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
-%\end{proof}
-%
-%\todo{do these corollaries fit here?}
-%
-%\begin{cor}\label{cor:genus_0_positive_delta}
-%Let $\halfcan$ be a stacky log spin canonical divisor of $(X, \Delta)$ with signature $(g;e_1, \ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)> 0$.
-Then $\halfcan$ is effective so we can inductively apply Lemma ~\ref{lem:deg1_sat_ind}.
-%\end{cor}
-%\begin{proof}
-%Since $\halfcan$ is a spin canonical divisor, 
-%\[
-	%2\halfcan=D+\sum \subhalf{e_i}P_i
-%\] 
-%where 
-%\[
-	%D\sim K_X+\Delta\sim -2\infty+ \Delta
-%\] is a divisor of $X$ (i.e.,~ with 
-%possibly negative integer coefficients). Since $\Delta$ is non-
-%zero effective, $\deg(D)\ge - 1$.  Noting that the coefficient of 
-%any point $P$ occurring in a stacky divisor of $\sx$ must have 
-%coefficient lying in $\BN[\frac{1}{e_i}]$ (ranging over $e_i$
-%s appearing in the characteristic of $(\sx, \Delta)$).
- %
-%Since all $e_i$'s are odd, $2$ cannot appear in a denominator of the 
-%coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
- %must be a $X$-divisor. Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
-%\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$. Thus $\halfcan$ 
-%is linearly equivalent to an effective $X$ divisor plus $\sum 
-%\subhalf{i}P_i$. We have thus shown $\halfcan$ is linearly equivalent to an effective divisor. Thus, by ~\ref{cor:effective_Q_divisor_can_ring} the desired result follows.
-%\end{proof}
-
-%\todo{Move this Lemma:}
-%\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
-%Let $(X, \Delta, \halfcan)\to (X, \Delta', \halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.
-%Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
-%generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0. Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
-%in degree at most $\bar{\tau}$.
-%Then 
-%\begin{itemize}
-%\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively. 
-%\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
-%
-%\begin{align*}
-	%\initial(I') &= \initial(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
-										 %&+ \langle y_i x_j \rangle \\
-										 %&+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
-%\end{align*}
-%\item A Gr\"{o}bner basis with initial terms described above minimally generates $I'$ over $I$.
-%\end{itemize}
-%\end{lem}
-%\begin{proof}
-%Similar to all the other Lemmas\todo{combine sections?}
-%\end{proof}
 
@@
 \ldots, e_r' + 2; \delta)$.
-%In order to state Lemma
-%~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in %Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.
-
-%\begin{rem}
-%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{custom:Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
-%\end{rem}
-%\todo{Peter: I'm not sure how useful this remark is.
-After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.
-The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}
-
-%\begin{lem}\label{lem:n-3s-admissible}
-%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$.
-Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $\halfcan'$.
-Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $\halfcan$.
-%\end{lem}
-%\begin{proof}
-%To show \ref{custom:Ad-i} and \ref{custom:Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$).
-Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{custom:Ad-i}.
-Furthermore, since $s$ is an admissible set of $\halfcan'$, in particular, we must have \ref{custom:Ad-ii} satisfied so $\frac{-\ord_{Q_l}
-%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{custom:Ad-ii} follows in genus 0?}
-%
- %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
-%\begin{itemize}
-%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
-%\item When $g= 0$, since $\halfcan'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{custom:Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
-%\end{itemize}
-%\end{proof}
 
@@
 		for all $j \in J$ with $j \neq i$.
-	\item[(b)]
-
-%The monomials $y_{i, e_i'}^a \cdot y_{i, e_i}^b$ with $a \geq 
-%0,
-%		b > 0$ span $R$ over $R'$ and
-		A choice of elements $y_{1, e_1}, \ldots, y_{r, e_r}$ as in part (a) minimally
+	\item[(b)] A choice of elements $y_{1, e_1}, \ldots, y_{r, e_r}$ as in part (a) minimally
 		generate $R$ over $R'$.
@@
 Now fix $i \in J$. We check that Inequality ~\eqref{eqn:order-degree} holds with $f = y_{i, e_i}z$, implying $y_{i,e_i}z \in R'$ in the three following cases:
-%$j \notin \{i \} \cup S(i, 0)$, $j = i,$ and $j \in S(i, 0)$.
 
@@
 completing part (c).
-
-%Next, note that the minimal generators of $I'$ together with the
-%new generators of $I$ given in (c) have independent initial terms
-%by construction, and therefore are minimal by Lemma
-%~\ref{lem:minimal_quadratic}.
 
@@
 
-%\begin{lem}
-%\label{lem:generation-5}
-%Let $X$ be a curve of genus $g \geq 2$ and let $\halfcan$ be a divisor with $2 L \sim K +\Delta$. Then, $R_\halfcan$ is generated in degree at most $5$.
-%\end{lem}
-%
-%The strategy of the proof of Lemma ~\ref{lem:generation-5} is to use Riemann--Roch and the basepoint-free pencil trick to show that $R_\halfcan$ is generated in degree at most $6,$ as is done in Lemma ~\ref{lem:semicanonical_generation}.
-When $g > 3$, it is easy to reduce the bound from 5 to 6.
-The trickiest case is to show $R_\halfcan$ is generated in degree 5 when $g = 2$, which is done in Lemma ~\ref{lem:genus-2-generation-5}.
-After proving these 2 lemmas, we concisely prove Lemma ~\ref{lem:generation-5}.
-
 \begin{lem}
@@
 \end{lem}
-
-%\begin{rem}
-%\label{rem:neves-omission}
-%The following proof of Lemma ~\ref{lem:semicanonical_generation} is shown in Neves \cite[Proposition III.4]{neves:halfcan}.
-However, Neves states that this proof also proves Lemma ~\ref{lem:generation-5}, while it crucially omits the case of genus 2 curves.
-We produce the proof here for completeness.
-%\end{rem}
 
@@
 
-%\begin{lem}
-%\label{lem:genus-2-generation-5}
-%Let $X$ be a smooth genus 2 curve with canonical divisor $K$ and let $L \in \di X$ be so that $2L \sim K$. 
-%Then, $R_\halfcan$ is generated in degree at most $5$.
-%\end{lem}
-%\begin{proof}
-%By Lemma ~\ref{lem:semicanonical_generation} it suffices to show $R_\halfcan$ has no minimal generators in degree 6.
-%Let $P_1, \ldots, P_6$ be the six hyperelliptic fixed points of $X$. 
-%Recall that all linear equivalence classes of spin divisors on $X$ have a representative of the form
-%$$L = P_1 + \sum_{i =2}^{6} \epsilon_i (P_1 - P_i),$$ 
-%with $\epsilon_i \in \{0,1\},$ and not all $\epsilon_i = 1$.
-%Note that $H^0(X,K)$ is spanned by rational functions $u, x$ with $\di u|_{2L} = -2L, \di x|_{2L} = -2L + 2P_1,$ where $u,x$ are though of as rational functions.
-Therefore, the image of the multiplication map
-%\begin{align*}
-	%Sym^3 H^0(X,2L) \rightarrow H^0(X,6L)
-%\end{align*}
-%is 4 dimensional by Riemann--Roch, with image spanned by $u^3,u^2x,ux^2, x^3$, 
-%which have 
-%\begin{align*}
-	%\di u^3|_{2L} &= -2L \\
-	%\di u^2x|_{2L} &= -2L + 2P_1 \\
-	%\di ux^2|_{2L} &= -2L+4P_1, \\
-	%\di x^3|_{2L} &= -2L + 6P_1.
-%\end{align*}
-%
-%\noindent
-%Since $H^0(X,6L)$ is 5 dimensional by Riemann--Roch,
-%it suffices to produce one more independent function in the image of the multiplication map.
-%There are now two cases, depending on whether $H^0(X, \halfcan) = 0$.
-%
-%First, we deal with the case that $H^0(X, \halfcan) \neq 0$. 
-%Then, since $X \not \cong \BP^1_k,$ and $\deg L = 1$, we must have $H^0(X, \halfcan) = 1$.
-Hence, we know $\halfcan$ is effective, so up to linear equivalence, we may assume $L = P$ where $P$ is hyperelliptic fixed.
-In this case, it is shown in \cite{neves:halfcan}[Theorem III.19] that $R_\halfcan$ is generated in degree $\leq 3$.
-%
-%Second, suppose $H^0(X, \halfcan) = 0$.
-%Note that because $\deg 3L = 3$, we have by Riemann--Roch that $H^0(X,3L) = 2$. 
-%Note additionally that $3L \sim K + L \sim 2P_1 + L$. Since $3L$ is base point free, by Riemann--Roch
-%we have that there exists a rational function $f$ with $\di f|_{2P_1 + L} = -2P_1 - L.$ Additionally, there are no functions $g \in H^0(X, \halfcan + 2P_1)$ 
-%with $\di g|_{2P_1 + L} = -L,$ since $H^0(X, \halfcan) = 0.$ Therefore, there must 
-%exist a function $h \in H^0(X, \halfcan+2P_1)$ so that $\di h|_{L + 2P_1} = -L - P_1$.
-%Then, $h \cdot f \in H^0(X,2L + 4P_1) \cong H^0(X,6L)$ has a pole of odd 
-%order at $P_1$, and is therefore independent from the image of $\sym^3 H^0(X,3L)$.
-%\end{proof}
-
-%We are now equipped to prove Lemma ~\ref{lem:generation-5}, completing the desired bound on the degree of the generators.
-%
-%\begin{proof}[Proof of Lemma ~\ref{lem:generation-5}]
-%If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
-%Lemma ~\ref{lem:genus-2-generation-5}.
-Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$.
-By Voight and Zureick-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6.
-Hence, $R_\halfcan$ is generated in degree at most 5.
-%\end{proof}
-
 The next step is to bound the degrees of the relations of $R_\halfcan$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
-%The idea of the proof of Proposition ~\ref{prop:relation-10} is to 
 by using the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
@@
 \twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in \Bk[x_1,
-\ldots, x_n]_2$ be two elements so that $\: \newspan(\phi(s_1), \phi(s_2))
-= V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
+\ldots, x_n]_2$ be two elements so that $\: \newspan(\phi(s_1), \phi(s_2))$
+$= V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
 \Bk[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
@@
 \begin{proof}
-% Choose $s_1,s_2 \in k[x_1, \ldots, x_n]_2$ so that $\phi(s_1), \phi(s_2) \in H^0(2L)$ generate a base point free pencil $V = k \phi(s_1) \oplus k \phi(s_2)\subseteq H^0(X,2L)$.
 By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in \Bk[x_1, \ldots, x_n]_{k-\deg x_i}$.
@@
 
-%\begin{rem}
-%\label{rem:relations_generation_ten}
-%Let $X$ be a curve of genus $g = 2$ and $P$ a closed point of $X$. In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$, then $R_\halfcan$ has a
-%relation in degree 10. Therefore, the bound from Proposition
-%~\ref{prop:relation-10}, that $I_L$ is generated in degree at most
-%11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
-%sharp.
-%\end{rem}
-
 We now summarize what we have shown.
@@
 Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ be a log spin curve
-%so that $\sx$ has 
 with signature $(g; e_1, \ldots, e_r; \delta)$. Then the
@@
 \end{thm}
-
-%is generated as a $k$-algebra by elements of degree at most $e =
-%\max(5, e_1, \ldots, e_r)$ with relations in degree up to $2e$.
-%
-%Furthermore, there are even stronger bounds for the following
-%exceptional cases X, :
 
@@
 ~\ref{eqn:deg1-sat-ind} holds by Riemann Roch.
-% since $\frac{\beta}{\alpha} = \frac{3}{1}=3$. 
 In this case, the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-1}.
@@
 \label{table:g-1-base}
-
-%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
 \end{table}
@@
 \label{table:g-1-exceptional}
-
-%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
 \end{table}
-%\begin{rem}
-%\label{rem:g-1-exceptional-e}
-%Note that for $e > 5$ generators and relations for $L = P - Q + \frac{e- 1}{2e}R$, which has signature $(1;e;0)$, can be computed inductively $L' = P - Q + \frac{(e-2) - 1}{2(e - 2)}R$ using 
-%Lemma ~\ref{lem:raise-stacky-order}.
-%\end{rem}
 
@@
 $L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
-
-%\begin{example}
-%\label{eg:exceptional-1-0}
-%In the case $L=P - Q.$ Then, we have $R_{(2k+ 1)L} \cong 0$ while $R_{2kL} \cong k$, with a single generator in degree 2. Therefore, $R_\halfcan \cong k[y]$, where $y$ is a generator in degree 2. 
-%\end{example}
-%
-%\begin{example}
-%\label{eg:exceptional- 1-3}
-%Let $L = P - Q + \frac{1}{3}R$.
-Since $P \neq Q$, we see $h^0(L) = 0,$ and we know $h^0(2L) = h^0(K) = 1$.
-For $n > 2$, we have $\deg nL > 0$ and so by Riemann--Roch, we have $h^0(nL) = \deg \lfloor nL/3 \rfloor.$ Next,
-%We find that $R_\halfcan \cong k[u, x,z]/(z^2 - ux^4),$ where $\deg u = 2, \deg x = 3, \deg z = 7$ so that $\di u|_L = -2P + 2Q, \di x|_L = -3P + 3Q - R, \di z|_L = -7P + 7Q - 2R.$\todo{This is unfinished}
-%\end{example}
-%
-%
-%\begin{example}
-%\label{eg:exception-1-e}
-%Let $L = P - Q + \frac{e- 1}{2e}P_1.$ Here, we claim $R_\halfcan \cong k[u, y_3, y_5, \ldots, y_e]/I_e,$ where we define $I_5 = y_3^4 - uy_5^2$ and $I_e$ is inductively defied via Lemma ~\ref{lem:raise-stacky-order} so that $in(I_e) = in(I_{e-2})k[u, y_3, \ldots, y_e] + \langle y_e z \mid z \neq y_e, y_{e-2} \rangle.$
-%Furthermore, $\deg u = 2, \deg y_i = i$.
-%\todo{Note that here there is a quartic generator of $I$ in degree 12, providing exceptions to minimality by quadrics and an exception to the relation bound when $e = 5$.}
-%\end{example}
 
@@
 Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan = \halfcan' + P$.
-
-%In particular, we may take $u \in h^0(\sx,L)$ with $u \neq 0$ and $\ord_P(u) = \lfloor \halfcan|_P \rfloor $,
-%as $P$ is not a basepoint of $\halfcan_X'$.
-Furthermore, Equation ~\ref{eqn:deg1-sat-ind} is satisfied by Riemann Roch, since $\deg \halfcan' \geq 1.$   \todo{Peter: I don't find this paragraph (after the first sentence) very useful.
-1: I'm not sure if we even need to go through the check that it satisfies the conditions for lemma 4.5.
-2: I don't find the check clear or illuminating as written.
-Either we should reword it or remove it (feel free to disagree, of course)}
 
@@
 \begin{rem}
-Since all points are linearly equivalent on $\BP^1_\Bk$, we may
-assume without loss of generality that $\halfcan_X = n \infty$ for some $n
-\in \BN$ and $K_X = -2 \infty$. We will use this convention
+Since all points are linearly equivalent on $\BP^1_\Bk$, 
+$\halfcan_X \sim n \infty$ for some $n \in \BN$ and
+$K_X \sim -2 \infty$. We will use this convention
 throughout this section.
@@
 the cases in Table ~\ref{table:g-0-base-cases} satisfy the
-conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e.,~ either $(\sx',
+conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e.~ either $(\sx',
 \halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}
@@
 
-%\noindent
-%Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
-%{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
-%\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
-%(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
-%$\initial(I')$ is minimally generated by products of two monomials.
 \end{lem}
@@
 \end{proof}
-
-%Now we can use Lemma ~\ref{lem:sat-3}, Lemma
-%~\ref{lem:raise-stacky-order}, and Corollary
-%~\ref{cor:raise-stacky-order} to induct from the cases of Table
-%~\ref{table:g-0-base-cases} and obtain the desired bounds on the
-%generator and relation degrees for log spin canonical rings of
-%genus 0 curves. This process will be carried out in Subsection
-%~\ref{ssec:g-0-main}.
-%\todo{Peter: I don't think this paragraph should be here.
-It seems like its kind of redundant given section 7.4.
-Maybe, we could just, say something like ``these provide the base cases, from which we will induct in section 7.4.''}
-
-%Through the application of two inductively adding 
-%points via Lemma ~\ref{lem:sat-3} and inductively raising
-%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
-%we obtain Theorem ~\ref{thm:g-0-main} for any
-%log spin curve $(\sx, \Delta, L)$ with
-%signature $\sigma$ covered by this induction process.
-%In particular, this induction process covers all signatures $\sigma
-%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
-%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
-%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
-%Before we prove the main theorem, we describe the cases not be
-%covered by induction.
 
@@
 
-\item One direction for further research is to 
-		extend the results of this paper to divisors $D \in \di \sx$ on a 
-		stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such 
-		divisors often arise as rings of fractional weight $\frac{2}{n}$ modular
-		forms. For more details on fractional weight modular forms, see Adler and Ramanan \cite[p. 96]{adler:moduli} and Milnor \cite
-		[$\mathsection$ 6]{milnor:fractional-weight}.
+\item One direction for further research is to extend the results
+	of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx$, 
+	where $nD \sim K.$ The canonical rings of such divisors often
+	arise as rings of fractional weight $\frac{2}{n}$ modular forms.
+	For more details on fractional weight modular forms, see Adler and
+	Ramanan \cite[p. 96]{adler:moduli} and Milnor
+	\cite[$\mathsection$ 6]{milnor:fractional-weight}.
 
@@
 			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e''$.
-%			Perhaps in the non-stacky case, one 
-%			may be able able to generalize the result of Reid \cite[Theorem 3.4
-%			]{reid:infinitesimal} to show that log spin canonical rings can be 
-%			generated in degree at most 3 with relations in degree at most 6, 
-%			apart from a well characterized list of exceptions.
 			\end{rem}
@@
 study of stacky canonical rings, for providing invaluable guidance,
-and for his mentorship. We also thank Ken Ono and the
-Emory University Number Theory REU for arranging our project and
+and for his mentorship. We also thank Ken Ono and the Emory
+University Number Theory REU for arranging our project and
 providing a great environment for mathematical learning and
@@
 bounds given by Miles Reid's work on the maximal degrees of minimal
-generators and relations of spin canonical rings in high genera.
-We thank Brian Conrad and John Voight for helpful comments on this paper.
-The first author would also like to mention Joseph Harris and Evan O'Dorney for several enlightening conversations related to Petri's Theorem.
-Finally, we gratefully acknowledge the financial support given by
-NSF Grant Award Number 1250467 via the Emory University Number
-Theory REU. We deeply appreciate all of the support that has made
-our work possible.
+generators and relations of spin canonical rings in high genera. We also
+thank Brian Conrad and John Voight for helpful comments on this
+paper. The first author would also like to mention Joseph Harris
+and Evan O'Dorney for several enlightening conversations related to
+Petri's Theorem. Finally, we gratefully acknowledge the financial
+support given by NSF Grant Award Number 1250467 via the Emory
+University Number Theory REU. We deeply appreciate all of the
+support that has made our work possible.
 

### 2015-07-08 curves-write-up/arXiv versions/spin_cring_arXiv_v1.tex
remove subfiles, minor edits

@@
 \usepackage{mathrsfs}
-\usepackage{subfiles}
 \usepackage{euler}
@@
 In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.
+
 \begin{rem}
@@
 \end{rem}
+
 \begin{rem}
 The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
-Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
+In almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
 Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
@@
 Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there are $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, there is necessarily a relation with leading term $y_{i, e_i} \cdot y_{j, e_j}$ in degree $2e$.
-
 This analysis also applies to the cases that $g = 0$ and $g = 1$.

### 2015-07-08 curves-write-up/spin_cring.tex
remove subfiles, minor edits

@@
 %Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
-%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e.,~ $c_i, c_j \le
+%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e.~ $c_i, c_j \le
 %\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
@@
 	%D\sim K_X+\Delta\sim -2\infty+ \Delta
-%\] is a divisor of $X$ (i.e.,~ with 
+%\] is a divisor of $X$ (i.e.~ with 
 %possibly negative integer coefficients). Since $\Delta$ is non-

### 2015-07-09 curves-write-up/arXiv versions/spin_cring_arXiv_v1.tex
edits to remark on M(Gamma)

@@
 generated in degree at most $5$ with relations in degree at most $10$.
-In fact, it is not difficult to reduce generation in weight at most 5 to generation in weight at most 4 with relations in weight at most 8, as noted in Remark ~\ref{rem:cusp-generation-4}.
+In fact, it is not difficult to show $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
 Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because there is a cusp, so $\delta > 0$.
@@
 Here, we describe how to obtain a slightly better bound for our
-application to modular forms from Example ~\ref{eg:congruence-bounds}.
-A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that,
+application to modular forms from Example ~\ref{eg:congruence-bounds} in the cases $g=0$ and $g=1$.
+When $g=0$, a careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that,
 if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$,

### 2015-07-09 surfaces-write-up/surface-write-up.tex
added lattice generation proposition

--- 2015-07-07 stacky_surface_write_up/surface-write-up.tex
@@
 
+\section{Lemmas for Generation and Relations}
+
+\begin{prop}
+\label{prop:cone-generation}
+Let $n,t \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$ and let $k_i^j \in \bz$ with $1 \leq i \leq n, 1 \leq j \leq t.$ Define
+\begin{align*}
+	\Sigma = \{(d,c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
+\end{align*}
+Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_n$.
+Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
+\end{prop}
+\begin{proof}
+By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{n}a_i e_i$ with $a_i \in \br$.
+Let $\{a\} := a - \lfloor a \rfloor$ denote the fractional part of $a$.
+Let $\lambda = \sum_{i=1}^{n}\{a_i\}$.
+Hence, we can write $\sigma = \lambda + \sum_{i=1}^{n}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_n$, which all have first coordinate less than $\sum_{i=1}^{n}\delta_i$.
+Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
+\end{proof}
+
 \section{Canonical Rings on Projective Space}
@@
 \todo{construct class of additional examples}
+\todo{The example above needs to be changed because $x_0^2$ can be replaced by $2x_0$}
 

### 2015-07-09 surfaces-write-up/surface-write-up.tex
lemma for P^1xP^1

@@
 \section{Canonical Rings on \texorpdfstring{$\bp^1 \times \bp^1$}{}}
+\begin{lem}
+If $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in \mathbb{P}^1\times \mathbb{P}^1$, such that $C_1, \ldots, C_4$ are independent hyperplanes.
+Then each $C_i$ corresponds to a bi-homogeneous polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
+Then $D$ is generated in degree at most \todo{add} with relations in degree at most \todo{add}.
+\end{lem}
+\begin{proof}
+Let $(d_i, d_i')$ be the bi-degrees of $f_i$.
+
+Notice that if $\gamma \in (R_D)_d$, then 
+\[
+	g = \sum_{i=1}^m {f_i}^{a_i}
+\]
+where each $a_i \ge - \alpha_i d_i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$.  Then we can view $g$ inside of the lattice
+$S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$. 
+From here, determining a spanning set for $(R_D)_d$ reduces to finding the extremal rays of $S$ \todo{cite previous lemma}.
+
+To do this, we extend the method of O'Dorney \todo{cite}.
+We first view the cone $T\subseteq \mathbb{R}^{n+1}$ given by elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge -\alpha_i d$ for all $i$ and $\sum_{i=1}^n a_i (d_i + d_i') =0$.
+By O'Dorney, this has extremal rays given by
+\[
+	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i} \alpha_j(d_j+ d_j')}{d_i + d_i'}, -\alpha_{i+1}, \ldots, - \alpha_m).
+\]
+Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_m$.
+We can then intersect the hyperplane $H$ given $\sum_{i=1}^m  d_i X_i = 0$.
+The extremal rays of $S$ are given by the set of $e_i$ contained in $H$ together with the points of intersection $e_{i,j}$ of $H$ and the line segment connecting $e_i, e_j \not \in H$.
+
+ We can calculate the following elements of $R_D$ whose corresponding lattice points lie on these extremal rays:
+
+For $i \in \{1, \ldots, m\}$ satisfying 
+\begin{equation}\label{eqn:condition-for-e_i}
+	d_i \sum_{l=1}^m d_l' \alpha_l = d_i' \sum_{l=1}^m d_l \alpha_l,
+\end{equation}
+define
+\[
+	\epsilon_i := (\prod_{l=1}^m f_l^{-\alpha l_i d_i}) (f_i^{\ell_i \sum_{l=1}^m \alpha_l d_l}) \in H^0(\ell_i d_i D).
+\]
+\todo{Peter: This equation above is very asymmetric in $d_i$ and $d_i'$.
+Can we replace this with something in degree $\gcd(d_i, d_i')$?
+Otherwise, maybe its wrong and no such element actually exists in that degree (I think it exists, but will check again later to be sure)?}
+For $i, j \in \{1, \ldots, m\}$ satisfying
+\begin{equation}\label{eqn:condition-e_i,j-i}
+	d_i \sum_{l=1}^m \alpha_l d_l' > d_i' \sum_{l=1}^m \alpha_i d_l
+\end{equation}
+and
+\begin{equation}\label{eqn:condition-e_i,j-j}
+	d_j \sum_{l=1}^m \alpha_l d_l' < d_j' \sum_{l=1}^m \alpha_j d_l
+\end{equation}
+then define
+\[
+	\epsilon_{i, j} = (\prod_{l=1}^m f_l^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(l_{i,j}(d_i d_j' - d_j d_i')\ell_{i,j}D)
+\]
+where
+\[
+	s_1 = d_j' \sum_{l \ne i,j} \alpha_l d_l - d_j \sum_{l\ne i, j} \alpha_l d_l'
+\]
+and
+\[
+	s_2 = d_i' \sum_{l \ne i,j} \alpha_l d_l - d_i \sum_{l\ne i, j} \alpha_l d_l'.
+\]
+Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
+$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most \todo{insert number}.
+\end{proof}
 

### 2015-07-10 curves-write-up/spin-cring.tex
rename old version, modify last further res. item

--- 2015-07-09 curves-write-up/arXiv versions/spin_cring_arXiv_v1.tex
@@
 \geq 0$. It is fairly easy to see, by use of Riemann--Roch, that
-the saturation of $\halfcan'$ is $5$ (see Definition ~\ref{defn:sat}.
+the saturation of $\halfcan'$ is $5$ (see Definition ~\ref{defn:sat}).
 Then the map in ~\eqref{eqn:noether-377} is surjective when $k \geq
@@
 \begin{figure}[H]
-\includegraphics{spin-377-pic-pics.pdf} \\
+\includegraphics{pics/spin-377-pic-pics.pdf} \\
 \caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
@@
 \begin{figure}
-\includegraphics{spin-lower-approximations-pic-pics.pdf}
+\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
 \caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
@@
 		generators and relations
-		for the log spin canonical ring $R_\halfcan,$ these sets are not necessarily minimal
-		In many of the $g = 0$ and $g=1$ cases, 
-		it is not too difficult to see that our inductive procedure also 
+		for the log spin canonical ring $R_\halfcan,$ these sets are not necessarily minimal.
+		In many of the $g = 0$ and $g = 1$ cases, 
+		it is not too difficult to see that our inductive procedure
 		yields a minimal set of relations for $R_\halfcan$. One might investigate 

### 2015-07-10 curves-write-up/spin-cring.tex
implement dzb's comments (or todo them)

@@
 geometric consequence that all such canonically embedded curves are
-scheme-theoretically cut out by degree 2 equations.
+scheme-theoretically cut out by degree 2 equations. \todo{reword ``all such''}
 
@@
 Petri's theorem in the direction of stacky curves equipped with
-log divisors. For a stacky curve $\sx$ with coarse space $X$ and
+log divisors \todo{reword}. For a stacky curve $\sx$ with coarse space $X$ and
 stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
@@
 
-In particular, we bound the degrees of generators and relations of
+Our main theorem is to bound the degrees of generators and relations of
 a log spin canonical ring. Let $\sx$ be a stacky curve with
@@
 (e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
-bounds we write here differ from those stated in Voight and Zureick-
+bounds we deduce differ from those stated in Voight and Zureick-
 Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because
@@
 Suppose $\Gamma \subset SL_2(\BZ)$ is any congruence subgroup. Then, since
-the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer order 1, 2 and 3, and has a cusp, the 
+the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer
+order 1, 2 and 3, and has at least one cusp, the
 action of $\Gamma$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
@@
 			Is there a general structure theorem describing a set of minimal 
-			generators and relations of $R_{\halfcan}$ where $(X, \Delta, L))$ is a log spin curve with no stacky points?
+			generators and relations of $R_{\halfcan}$ where $(X, \Delta, L)$ is a log spin curve with no stacky points?
 		\end{question}
@@
 		answer to Question ~\ref{ques:fractional-weight}.
-
-	\item Voight and Zureick-Brown define
+		\\
+
+	\item Voight and Zureick-Brown define \todo{reword}
 		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
@@
 		\end{question}
+
 	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 

### 2015-07-10 curves-write-up/spin-cring.tex
nsf grant number edit
edited david's remaining comments

@@
 \cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
-geometric consequence that all such canonically embedded curves are
-scheme-theoretically cut out by degree 2 equations. \todo{reword ``all such''}
+geometric consequence that canonically embedded curves which are not hyperelliptic, trigonal, or a plane quintic are
+scheme-theoretically cut out by degree 2 equations.
 
@@
 Petri's theorem in the direction of stacky curves equipped with
-log divisors \todo{reword}. For a stacky curve $\sx$ with coarse space $X$ and
+log spin canonical divisors. For a stacky curve $\sx$ with coarse space $X$ and
 stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
@@
 \]
-Then a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
-where $\Delta \in \di X$ is a log divisor and $L \in \di \sx$ satisfies $2\halfcan \sim K_X +
+Then, a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
+where $\Delta \in \di X$ is a log divisor and $L \in \di \sx$ is a {\bf log spin canonical divisor}, meaning $2\halfcan \sim K_X +
 \Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
@@
 
-	\item Voight and Zureick-Brown define \todo{reword}
-		the notion of a generic initial ideal \cite[Definition 2.2.7]{vzb:stacky}, which 
+	\item The generic initial ideal
 		encapsulates the idea of whether the relations for $R_\halfcan$ are 
-		generically chosen, in a precise sense. 
+		generically chosen. See Voight and Zureick-Brown \cite[Definition 2.2.7]{vzb:stacky} for a precise definition of the generic initial ideal.
 		The proof of Theorem

### 2015-07-10 curves-write-up/spin-cring.tex
changed a period

@@
 Therefore, these bounds cannot in general be reduced further to
-			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e''$.
+			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e.''$
 			\end{rem}
@@
 bounds given by Miles Reid's work on the maximal degrees of minimal
-generators and relations of spin canonical rings in high genera. We also
-thank Brian Conrad and John Voight for helpful comments on this
-paper. The first author would also like to mention Joseph Harris
-and Evan O'Dorney for several enlightening conversations related to
-Petri's Theorem. Finally, we gratefully acknowledge the financial
-support given by NSF Grant Award Number 1250467 via the Emory
-University Number Theory REU. We deeply appreciate all of the
-support that has made our work possible.
+generators and relations of spin canonical rings in high genera. We
+also thank Brian Conrad and John Voight for helpful comments on
+this paper. The first author would also like to mention Joseph
+Harris and Evan O'Dorney for several enlightening conversations
+related to Petri's Theorem. Finally, we gratefully acknowledge the
+support of the National Science Foundation (grant number DMS-1250467).
+We deeply appreciate all of the support that has made our work
+possible.
 

### 2015-07-10 curves-write-up/spin-cring.tex
delete extra space

@@
 we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0$.
-So by the explicit isomorphism given in the proof of the basepoint-
-free pencil trick, as shown in the proof of \cite[Lemma 2.6]
+So by the explicit isomorphism given in the proof of the
+basepoint-free pencil trick, as shown in the proof of \cite[Lemma 2.6]
 {saint-donat:proj}, there exists some $\rho \in \Bk[x_1, \ldots, x_n]$

### 2015-07-10 curves-write-up/spin-cring.tex
delete remaining comments

@@
 \label{rem:explicit-generators}
-%The main theorem obtains bounds on the degrees of the generators
-%and relations of log spin canonical rings. 
 In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
@@
 \alpha}{\beta}$. 
-%Note that the elements $t_1, \ldots, t_{\lfloor d_i \frac{\alpha}{\beta}\rfloor}$ in $(R_{\halfcan})_{d_i}$ with $\ord_P^{\halfcan'}(t_i) = i$ are linearly independent over $(R_{\halfcan'})_d$.
-Hence, by a dimension count, these sections form a $k$-basis for
-%$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.\todo{take out two sentences}
-%For any $1\le i < j \le n$, we have $\frac{c_i}{d_i} < \frac{c_j}{d_j}$.  
 Choose a positive best lower approximation $\frac{c_i}{k_i}$.
@@
 best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
-%  The argument goes $c_i d \ge c k_i$
-% implies c_i \frac{k}{k_i} \ge c
-% implies c_i + \frac{k-k_i}{k_i}c_i \ge c
-% \implies c_i (k-k_i) \frac{c_i}{k_i}\ge c
-% so since everything is an integer $c_i +\lfloor (k - k_i) \frac{c_i}{k_i}\rfloor \ge c$
-% \implies the equation below:
 \[
@@
 \]
+
+\noindent
 which implies

### 2015-07-10 curves-write-up/spin-cring.tex
exact sequence longrightarrow's
include g \geq 4 phrasing

@@
 \cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
-geometric consequence that canonically embedded curves which are not hyperelliptic, trigonal, or a plane quintic are
-scheme-theoretically cut out by degree 2 equations.
+geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic, trigonal, or a plane quintic are scheme-theoretically cut out by degree 2 equations.
 
@@
 sequence
-$$\begin{tikzcd}
-0 \ar r & H^0((n-2)L) \ar r & V \otimes H^0(nL) \ar{r}{f} & H^0((n+2)L)
-\end{tikzcd}$$
+\begin{align*}
+0 \longrightarrow H^0((n - 2)\halfcan) \longrightarrow V \otimes
+H^0(n \halfcan) \overset{f}{\longrightarrow} H^0((n + 2)\halfcan)
+\end{align*}
 

### 2015-07-10 surfaces-write-up/surface-write-up.tex
include g \geq 4 phrasing
don't know what changes are made?
surfaces: add theorem statement for one pt

@@
 \ssec{Notation}
-
+\begin{convention}
 Write
@@
 \end{align*}
-where $\alpha_i \in \bq.$
+where $\alpha_i \in \bq$.
+\end{convention}
+
+\begin{convention}
+Let $\{x_0, \ldots, x_m\}$ be coordinates for $\bp^m$. Let
+$\vec{v} = (v_0, \ldots, v_m) \in \br^{m + 1}$. Then write
+\[
+	x_{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
+\]
+\end{convention}
 
@@
 where $\alpha_i \in \bq$ and $\deg D_i = d_i$.
-Let $f_i$ be cartier divisors such that $D_i = V(f_i)$.
+Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
 We shall further assume that among there exist functions $f_0,\ldots, f_{m+1}$ form a basis for degree one rational functions on $\bp^m$.
@@
 
+\begin{rem}
+Remark about how we can assume divisor only consists of hyperplanes
+by taking the Veronese embedding.
+\end{rem}
+
 \ssec{One point on Projective Space}
+\label{ssec:proj-one-point}
+
+\begin{thm}
+\label{thm:proj-one-point}
+Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
+$\bp^m$. Let $D = \frac{a}{b} H$, with $a, b \in \bz$ and $H =
+V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$. Let
+\[
+	\left\lfloor \frac{a}{b} \right\rfloor = \frac{c_0}{d_0} < \frac{c_1}{d_1} <
+	\ldots < \frac{c_r}{d_r} = \frac{a}{b}
+\]
+
+\noindent
+be the best lower approximations of $\frac{a}{b}$. Then the
+canonical ring
+\[
+	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
+\]
+
+\noindent
+has a minimal presentation consisting of the $\sum_{i = 0}^{r}
+{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
+where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
+v_j = c_i$ and $z$ relations of the form
+\[
+	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
+\]
+
+\noindent
+when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
+\todo{fix this condition to make it right}
+or of the form
+
+\[
+	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
+\]
+
+\noindent
+when $\vec{u} + \vec{v} = \vec{w} + \vec{z}$.
+\end{thm}
+
+\begin{proof}
+
+\end{proof}
 
@@
 \]
-where each $a_i \ge - \alpha_i d_i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$.  Then we can view $g$ inside of the lattice
+where each $a_i \ge - \alpha_i d_i$, $\sum_{i=1}^m a_i d = 0$, and $\sum_{i=1}^m a_i d_i' = 0$.  Then we can view $g$ inside of the lattice
 $S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$. 
@@
 \[
-	\epsilon_i := (\prod_{l=1}^m f_l^{-\alpha l_i d_i}) (f_i^{\ell_i \sum_{l=1}^m \alpha_l d_l}) \in H^0(\ell_i d_i D).
+	\epsilon_i := (\prod_{l \ne i} f_l^{-\alpha l_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{l \ne i} \alpha_l (d_l + d_l')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
 \]
@@
 \[
-	\epsilon_{i, j} = (\prod_{l=1}^m f_l^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(l_{i,j}(d_i d_j' - d_j d_i')\ell_{i,j}D)
+	\epsilon_{i, j} = (\prod_{l=1}^m f_l^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
 \]
@@
 
-We are grateful to David Zureick-Brown for introducing us to the
-study of stacky canonical rings, for providing invaluable guidance,
+We are grateful to David Zureick-Brown for introducing us to this
+subject, for providing invaluable guidance,
 and for his mentorship. We also thank Ken Ono and the

### 2015-07-10 surfaces-write-up/surface-write-up.tex
l's changed to k's
subscript vector -> superscript vector

@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
+{{m + i} \choose {i}}$ generators $\frac{u^{d_i} x^{\vec{v}}}{x_k^{c_i}}$
 where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
-v_j = c_i$ and $z$ relations of the form
-\[
-	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
-\]
-
-\noindent
-when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
-\todo{fix this condition to make it right}
-or of the form
+v_j = c_i$ and $z$ \todo{how many?} relations of the form
 
 \[
-	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
+	x^{\vec{u}} x^{\vec{v}} = x^{\vec{w}} x^{\vec{z}}
 \]
@@
 \begin{proof}
-
+We know $u$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
+were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
 \end{proof}
@@
 \begin{equation}\label{eqn:condition-for-e_i}
-	d_i \sum_{l=1}^m d_l' \alpha_l = d_i' \sum_{l=1}^m d_l \alpha_l,
+	d_i \sum_{k=1}^m d_k' \alpha_k = d_i' \sum_{k=1}^m d_k \alpha_k,
 \end{equation}
@@
 \[
-	\epsilon_i := (\prod_{l \ne i} f_l^{-\alpha l_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{l \ne i} \alpha_l (d_l + d_l')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
+	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{k \ne i} \alpha_k (d_k + d_k')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
 \]
@@
 \begin{equation}\label{eqn:condition-e_i,j-i}
-	d_i \sum_{l=1}^m \alpha_l d_l' > d_i' \sum_{l=1}^m \alpha_i d_l
+	d_i \sum_{k=1}^m \alpha_k d_k' > d_i' \sum_{k=1}^m \alpha_k d_k
 \end{equation}
@@
 \begin{equation}\label{eqn:condition-e_i,j-j}
-	d_j \sum_{l=1}^m \alpha_l d_l' < d_j' \sum_{l=1}^m \alpha_j d_l
+	d_j \sum_{k=1}^m \alpha_k d_k' < d_j' \sum_{k=1}^m \alpha_k d_k
 \end{equation}
@@
 \[
-	\epsilon_{i, j} = (\prod_{l=1}^m f_l^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
+	\epsilon_{i, j} = (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
 \]
@@
 \[
-	s_1 = d_j' \sum_{l \ne i,j} \alpha_l d_l - d_j \sum_{l\ne i, j} \alpha_l d_l'
+	s_1 = d_j' \sum_{k \ne i,j} \alpha_k d_k - d_j \sum_{k\ne i, j} \alpha_k d_k'
 \]
@@
 \[
-	s_2 = d_i' \sum_{l \ne i,j} \alpha_l d_l - d_i \sum_{l\ne i, j} \alpha_l d_l'.
+	s_2 = d_i' \sum_{k \ne i,j} \alpha_k d_k - d_i \sum_{k \ne i, j} \alpha_k d_k'.
 \]

### 2015-07-10 surfaces-write-up/surface-write-up.tex
surfaces one point some revisions, def f_v

@@
 by taking the Veronese embedding.
+\todo{do this}
 \end{rem}
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $\frac{u^{d_i} x^{\vec{v}}}{x_k^{c_i}}$
-where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
-v_j = c_i$ and $z$ \todo{how many?} relations of the form
-
+{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{d_i}
+x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
+relations of the form
 \[
@@
 \begin{proof}
-We know $u$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
+We know $f_0$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
 were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
+$f_{\vec{v}} = f_{\vec{w}} f_{\vec{z}}$ for some $f_{\vec{w}},
+f_{\vec{z}} \in R_D$ with $\deg \vec{w}, \deg \vec{z} < \deg \vec{v}$.
 \end{proof}

### 2015-07-10 surfaces-write-up/surface-write-up.tex
changed lemma on P1xP1 to include hirzabrook surfaces and give explicit degrees

--- 2015-07-10 surfaces-write-up/surface-write-up.tex
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $\frac{u^{d_i} x^{\vec{v}}}{x_k^{c_i}}$
+{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
 where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
-v_j = c_i$ and $z$ \todo{how many?} relations of the form
+v_j = c_i$ and $z$ relations of the form
+\[
+	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
+\]
+
+\noindent
+when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
+\todo{fix this condition to make it right}
+or of the form
 
 \[
-	x^{\vec{u}} x^{\vec{v}} = x^{\vec{w}} x^{\vec{z}}
+	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
 \]
@@
 \begin{proof}
-We know $u$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
-were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
+
 \end{proof}
@@
 
-\section{Canonical Rings on \texorpdfstring{$\bp^1 \times \bp^1$}{}}
+\section{Canonical Rings on \texorpdfstring{$F_k$}{}}
+\begin{defn}
+Suppose $D = \sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(F_k)$.  Then define 
+\begin{equation}\label{eqn:define-T=(D)}
+	T_=(D) = \left\{i \in \{1, \ldots, m\}: d_i \sum_{k=1}^m d_k' \alpha_k = d_i' \sum_{k=1}^m d_k \alpha_k \right\},
+\end{equation}
+\begin{equation}\label{eqn:define-T+(D)}
+	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} d_i \sum_{k=1}^m \alpha_k d_k' > d_i' \sum_{k=1}^m \alpha_k d_k \right\},
+\end{equation}
+and
+\begin{equation}\label{eqn:define-T-(D)}
+	T_-(D) = \left\{ j \in \{1, \ldots, m\}: d_j \sum_{k=1}^m \alpha_k d_k' < d_j' \sum_{k=1}^m \alpha_k d_k s \right\}.
+\end{equation}
+\end{defn}
+
 \begin{lem}
-If $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in \mathbb{P}^1\times \mathbb{P}^1$, such that $C_1, \ldots, C_4$ are independent hyperplanes.
-Then each $C_i$ corresponds to a bi-homogeneous polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
-Then $D$ is generated in degree at most \todo{add} with relations in degree at most \todo{add}.
+If $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such that $C_1, \ldots, C_4$ are independent curves with bi-degrees (1,0), (1,0), (0,1), and (0,1) respectively.
+Then each $C_i$ corresponds to a polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
+Then $D$ is generated in degree at most
+\[
+	\sum_{i\in T_=(D)} \gcd(d_i, d_i')\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (d_i d_j'- d_j d_i')\ell_{i,j}
+\]
+ with relations in degree at most \todo{add}.
 \end{lem}
@@
 
-For $i \in \{1, \ldots, m\}$ satisfying 
-\begin{equation}\label{eqn:condition-for-e_i}
-	d_i \sum_{k=1}^m d_k' \alpha_k = d_i' \sum_{k=1}^m d_k \alpha_k,
-\end{equation}
+For $i \in T_=(D)$
 define
@@
 \]
-\todo{Peter: This equation above is very asymmetric in $d_i$ and $d_i'$.
-Can we replace this with something in degree $\gcd(d_i, d_i')$?
-Otherwise, maybe its wrong and no such element actually exists in that degree (I think it exists, but will check again later to be sure)?}
-For $i, j \in \{1, \ldots, m\}$ satisfying
-\begin{equation}\label{eqn:condition-e_i,j-i}
-	d_i \sum_{k=1}^m \alpha_k d_k' > d_i' \sum_{k=1}^m \alpha_k d_k
-\end{equation}
-and
-\begin{equation}\label{eqn:condition-e_i,j-j}
-	d_j \sum_{k=1}^m \alpha_k d_k' < d_j' \sum_{k=1}^m \alpha_k d_k
-\end{equation}
-then define
+For $i \in T_+(D)$ and $j \in T_-(D)$, define
 \[
@@
 Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
-$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most \todo{insert number}.
+$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most
+\[
+	\sum_{i\in T_=(D)} \gcd(d_i, d_i')\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (d_i d_j'- d_j d_i')\ell_{i,j}.
+\]
+
 \end{proof}

### 2015-07-10 surfaces-write-up/surface-write-up.tex

@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
-where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
-v_j = c_i$ and $z$ relations of the form
+{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{d_i}
+x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
+relations of the form
 \[
-	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
-\]
-
-\noindent
-when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
-\todo{fix this condition to make it right}
-or of the form
-
-\[
-	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
+	x^{\vec{u}} x^{\vec{v}} = x^{\vec{w}} x^{\vec{z}}
 \]
@@
 \begin{proof}
-
+We know $f_0$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
+were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
+$f_{\vec{v}} = f_{\vec{w}} f_{\vec{z}}$ for some $f_{\vec{w}},
+f_{\vec{z}} \in R_D$ with $\deg \vec{w}, \deg \vec{z} < \deg \vec{v}$.
 \end{proof}

### 2015-07-10 surfaces-write-up/surface-write-up.tex
added relations gernal lemmas

@@
 \newcommand\ba{{\mathbb A}}
+\newcommand\bk{{\Bbbk}}
 
@@
 \end{align*}
-Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_n$.
+Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
 Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
+Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{r}\delta_i$ and $w_1,\ldots, w_r \in \bz$.
 \end{prop}
 \begin{proof}
-By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{n}a_i e_i$ with $a_i \in \br$.
+By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{r}a_i e_i$ with $a_i \in \br$.
 Let $\{a\} := a - \lfloor a \rfloor$ denote the fractional part of $a$.
-Let $\lambda = \sum_{i=1}^{n}\{a_i\}$.
-Hence, we can write $\sigma = \lambda + \sum_{i=1}^{n}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_n$, which all have first coordinate less than $\sum_{i=1}^{n}\delta_i$.
-Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
+Let $\lambda = \sum_{i=1}^{r}\{a_i\}$.
+Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\delta_i$.
+Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{r}\delta_i$.
+\end{proof}
+
+\begin{lem}
+\label{lem:composite-map}
+Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$.
+Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D, x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
+Then, define
+\begin{align*}
+	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n}a_ic_i = \sum_{i=1}^{} b_i c_i. \rangle 
+\end{align*}
+In this case, we have a factorization of $\phi$ given by maps $\chi, \psi$ defined by
+\todo{Make this have mapsto on bottom}
+$$\begin{tikzcd}
+\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+x_i \ar r & u^{d_i}y_1^{c_{i1}} \cdots y_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}
+\end{tikzcd}$$
+Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$ is at most the maximum of the minimal degree of generation of $\ker \chi$ and the minimal degree of generation of $\ker \psi$.
+\end{lem}
+\begin{proof}
+Note that we have an exact sequence
+$$\begin{tikzcd}
+0 \ar r & \ker \chi \ar r & \ker \phi \ar r & \ker \psi \ar r & 0
+\end{tikzcd}.$$
+To see this, note that the left map is an inclusion because $\phi = \chi \circ \psi$.
+Next, the right map, given by $\chi|_{\ker \phi}:\ker \phi \rightarrow \ker \psi$ is a surjection, again because $\phi = \chi \circ \psi$.
+The composition of the two maps is $0$ by definition of the kernel of $\chi$.
+Finally, if $a \in \ker \phi$ and $a$ lies in the kernel of the right map, then by definition $\chi(a) = 0$.
+\end{proof}
+
+\begin{lem}
+\label{lem:bound-ker-chi}
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees less than $\sum_{i=1}^{r}d_r-1$.
+\end{lem}
+\begin{proof}
+Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
+Now, letting $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ so that we can write $\lambda_i = \sum_{i=1}^{r}a_i e_i$ with $0 \leq a_i < 1$ for all $i$.
+Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in the above canonical form, yielding a relation in degree at most $\deg \lambda_i + \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$ Furthermore, these relations generate all relations, as one can apply a sequence of these relations to put any $\sigma \in \Sigma$ into canonical form.
 \end{proof}
@@
 
+\todo{possibly change this to only have two equations}
 \begin{prop}
@@
 \end{proof}
+\todo{the following bound is the generation bound beginning from evan's paper}
+
+\ssec{One point on Projective Space}
+\label{ssec:proj-one-point}
 
@@
 by taking the Veronese embedding.
-\todo{do this}
+\todo{Robin: do this}
 \end{rem}
-
-\ssec{One point on Projective Space}
-\label{ssec:proj-one-point}
 

### 2015-07-11 surfaces-write-up/surface-write-up.tex
surfaces title change, curves abs one-word edit
add def lower approx, first half 1pt pf, add pic

@@
 
-\title{Spin canonical rings of log stacky curves}
+\title{Canonical rings of rational divisors on projective space and Hirzebruch surfaces}
 
@@
 \section{Background}
+
+\begin{defn}
+\label{defn:lower-approximation}
+If $\frac{\alpha}{\beta}\in \bq$, then $\frac{c}{k}$ (written in
+reduced form with $c \in \bn, k \in \bn$) is a {\bf{best lower
+approximation}} to $\frac{\alpha}{\beta}$ if there does not exist
+any $\frac{c'}{k'}\in \bq$ with $0 < k'<k$ and $\frac{c}{k} \le
+\frac{c'}{k'}$.
+\end{defn}
+
+Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative
+best lower approximations of $\frac{\alpha}{\beta}$ form a finite
+sequence
+\[
+	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \frac{\alpha}{\beta}.
+\]
+Figure \ref{fig:s14/5-lattice} gives a pictorial representation of
+the positive best lower approximations of $\frac{\alpha}{\beta} =
+\frac{14}{5}$.
+
+\begin{figure}
+\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+\caption{This figure shows each non-negative best lower
+approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best
+lower approximation and each ``$\circ$'' denotes a lattice point
+below $5y=14x$ which is not a best lower approximation.  Note that
+the non-negative best lower approximations generate the monoid of
+lattice points in the first quadrant satisfying  $5y \le 14x$, with
+the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$.}
+\label{fig:s14/5-lattice}
+\end{figure}
 
@@
 Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \frac{a}{b} H$, with $a, b \in \bz$ and $H =
-V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$. Let
+$\bp^m$. Let $D = \alpha H$, with $\alpha = \frac{a}{b} \in \bq$
+and $H = V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$.
+Let
 \[
-	\left\lfloor \frac{a}{b} \right\rfloor = \frac{c_0}{d_0} < \frac{c_1}{d_1} <
-	\ldots < \frac{c_r}{d_r} = \frac{a}{b}
+	\left\lfloor \frac{a}{b} \right\rfloor = \frac{c_0}{d_0} <
+	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{a}{b}
 \]
@@
 \noindent
-be the best lower approximations of $\frac{a}{b}$. Then the
+be the best lower approximations of $\alpha$. Then the
 canonical ring
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{d_i}
-x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
-relations of the form
+{{m + i} \choose {i}}$ many generators $f_{d_i, \vec{v}} :=
+\frac{u^{d_i} x^{\vec{v}}} {x_k^{c_i}}$ where $\vec{v} \in
+\bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
+many relations of the form
 \[
@@
 \begin{proof}
-We know $f_0$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
-were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
-$f_{\vec{v}} = f_{\vec{w}} f_{\vec{z}}$ for some $f_{\vec{w}},
-f_{\vec{z}} \in R_D$ with $\deg \vec{w}, \deg \vec{z} < \deg \vec{v}$.
+We know $\{f_{0, \vec{u}} : \deg \vec{u} = \left\lfloor \frac{a}{b}
+\right\rfloor \}$ are minimal generators in degree $1$. If
+$f_{d_i, \vec{v}}$ were not minimal for $\deg \vec{v} = c_i$ for
+some $i > 0$, then $f_{d_i, \vec{v}} = f_{s, \vec{w}}
+f_{t, \vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
+\bz_{\geq 0}^{m + 1}$. In particular, we see that 
+\begin{align*}
+	&d_i = s + t \\
+	&c_i = \deg \vec{v} = \deg \vec{w} + \deg \vec{z}
+\end{align*}
+
+\noindent
+so $\frac{c_i}{d_i}$ is the mediant of the rational numbers
+$\frac{\deg \vec{w}}{s}, \frac{\deg \vec{z}}{t}$ which both
+do not exceed $\alpha$. One of $\frac{\deg \vec{w}}{s},
+\frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
+and $s$ and $t$ are both less than $d_i$, so we have a contradiction 
+of $\frac{c_i}{d_i}$ being a best lower approximation of $\alpha$
+(see Definition ~\ref{defn:lower-approximation}).
+
+Now we show that no further generators are necessary. Let $\vec{x}_i
+:= (d_i, c_i) \in \bz^2$ a lattice point.
+
 \end{proof}
@@
 
-\section{Canonical Rings on \texorpdfstring{$F_k$}{}}
+\section{Canonical Rings on Hirzebruch Surfaces}
 \begin{defn}

### 2015-07-11 surfaces-write-up/surface-write-up.tex
finished 1-pt generator proof, relations are left

@@
 \begin{abstract}
- 	Bonding generator and relation degrees of general $\bq$-divisors
-	of surfaces.
+ 	Bounding generator and relation degrees of general $\bq$-divisors
+	on projective spaces $\bp^n$ and Hirzebruch surfaces.
 \end{abstract}
@@
 by taking the Veronese embedding.
-\todo{Robin: do this}
+\todo{write}
 \end{rem}
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ many generators $f_{d_i, \vec{v}} :=
+{{m + i} \choose {i}}$ many generators $f_{d_i}^{\vec{v}} :=
 \frac{u^{d_i} x^{\vec{v}}} {x_k^{c_i}}$ where $\vec{v} \in
@@
 \[
-	x^{\vec{u}} x^{\vec{v}} = x^{\vec{w}} x^{\vec{z}}
+	f_{d_i}^{\vec{v}} f_{d_j}^{\vec{w}} = f_{d_k}^{\vec{y}} f_{d_\ell}^{\vec{z}}
 \]
@@
 \noindent
-when $\vec{u} + \vec{v} = \vec{w} + \vec{z}$.
+when $d_i + d_j = d_k + d_\ell$ and $\vec{v} + \vec{w} = \vec{y} +
+\vec{z}$.
 \end{thm}
@@
 \begin{proof}
-We know $\{f_{0, \vec{u}} : \deg \vec{u} = \left\lfloor \frac{a}{b}
-\right\rfloor \}$ are minimal generators in degree $1$. If
-$f_{d_i, \vec{v}}$ were not minimal for $\deg \vec{v} = c_i$ for
-some $i > 0$, then $f_{d_i, \vec{v}} = f_{s, \vec{w}}
-f_{t, \vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
+We know $\{f_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{a}{b}
+\right\rfloor \}$ are minimal generators in degree $1$. Now let $i >
+0$. If $f_{d_i}^{\vec{v}}$ were not minimal for some $\vec{v}$ such
+that $\deg \vec{v} = c_i$, then $f_{d_i}^{\vec{v}} = f_{s}^{\vec{w}}
+f_{t}^{\vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
 \bz_{\geq 0}^{m + 1}$. In particular, we see that 
@@
 
-Now we show that no further generators are necessary. Let $\vec{x}_i
-:= (d_i, c_i) \in \bz^2$ a lattice point.
+Now we show that no further generators are necessary. As done in
+the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
+{dorney:canonical}, each lattice point $(d, c) \in \bz^2$ such that
+$c \leq d \alpha$ is a nonnegative linear combination of $\vec{x}_i$
+and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in \bz^2$.
+Consequently, any element $\frac{u^{d} x^{\vec{v}}} {x_k^{c}} \in
+R_D$ is expressible as
+\begin{align*}
+	\frac{u^{d} x^{\vec{v}}} {x_k^{c}} = \frac{u^{d_i} x^{\vec{w}}}
+	{x_k^{c_i}} \frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}}
+\end{align*}
 
+\noindent
+where $\vec{w}, \vec{z} \in \bz_{\geq 0}^{m + 1}$ such that $\deg
+\vec{w} = c_i, \deg \vec{z} = c_{i + 1}$. But these are precisely
+two generators of the form $f_{d_i}^{\vec{w}}$ and $f_{d_{i + 1}}
+^{\vec{z}}$ as prescribed in the theorem statement.
+
+\todo{relations}
 \end{proof}

### 2015-07-11 surfaces-write-up/surface-write-up.tex
... I didn't think I made any changes

--- 2015-07-10 surfaces-write-up/surface-write-up.tex
@@
 \newcommand\ba{{\mathbb A}}
-\newcommand\bk{{\Bbbk}}
 
@@
 \end{align*}
-Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
+Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_n$.
 Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
-Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{r}\delta_i$ and $w_1,\ldots, w_r \in \bz$.
 \end{prop}
 \begin{proof}
-By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{r}a_i e_i$ with $a_i \in \br$.
+By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{n}a_i e_i$ with $a_i \in \br$.
 Let $\{a\} := a - \lfloor a \rfloor$ denote the fractional part of $a$.
-Let $\lambda = \sum_{i=1}^{r}\{a_i\}$.
-Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\delta_i$.
-Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{r}\delta_i$.
-\end{proof}
-
-\begin{lem}
-\label{lem:composite-map}
-Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$.
-Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D, x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
-Then, define
-\begin{align*}
-	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n}a_ic_i = \sum_{i=1}^{} b_i c_i. \rangle 
-\end{align*}
-In this case, we have a factorization of $\phi$ given by maps $\chi, \psi$ defined by
-\todo{Make this have mapsto on bottom}
-$$\begin{tikzcd}
-\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \ar r & u^{d_i}y_1^{c_{i1}} \cdots y_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}
-\end{tikzcd}$$
-Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$ is at most the maximum of the minimal degree of generation of $\ker \chi$ and the minimal degree of generation of $\ker \psi$.
-\end{lem}
-\begin{proof}
-Note that we have an exact sequence
-$$\begin{tikzcd}
-0 \ar r & \ker \chi \ar r & \ker \phi \ar r & \ker \psi \ar r & 0
-\end{tikzcd}.$$
-To see this, note that the left map is an inclusion because $\phi = \chi \circ \psi$.
-Next, the right map, given by $\chi|_{\ker \phi}:\ker \phi \rightarrow \ker \psi$ is a surjection, again because $\phi = \chi \circ \psi$.
-The composition of the two maps is $0$ by definition of the kernel of $\chi$.
-Finally, if $a \in \ker \phi$ and $a$ lies in the kernel of the right map, then by definition $\chi(a) = 0$.
-\end{proof}
-
-\begin{lem}
-\label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees less than $\sum_{i=1}^{r}d_r-1$.
-\end{lem}
-\begin{proof}
-Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
-Now, letting $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ so that we can write $\lambda_i = \sum_{i=1}^{r}a_i e_i$ with $0 \leq a_i < 1$ for all $i$.
-Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in the above canonical form, yielding a relation in degree at most $\deg \lambda_i + \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$ Furthermore, these relations generate all relations, as one can apply a sequence of these relations to put any $\sigma \in \Sigma$ into canonical form.
+Let $\lambda = \sum_{i=1}^{n}\{a_i\}$.
+Hence, we can write $\sigma = \lambda + \sum_{i=1}^{n}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_n$, which all have first coordinate less than $\sum_{i=1}^{n}\delta_i$.
+Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
 \end{proof}
@@
 \end{align*}
-where $\alpha_i \in \bq$ and $\deg D_i = d_i$.
+where $\alpha_i \in \bq$ and $\deg D_i = a_i$.
 Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
@@
 
-\todo{possibly change this to only have two equations}
 \begin{prop}
@@
 \label{align:pm-span}
-\sum_{i=0}^{n} c_i \cdot d_i \cdot f_i = 0 & \text{ and } &c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=0}^{n} c_i \cdot a_i \cdot f_i = 0 & \text{ and } &c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 \end{proof}
-\todo{the following bound is the generation bound beginning from evan's paper}
-
-\ssec{One point on Projective Space}
-\label{ssec:proj-one-point}
 
@@
 by taking the Veronese embedding.
-\todo{Robin: do this}
+\todo{do this}
 \end{rem}
+
+\ssec{One point on Projective Space}
+\label{ssec:proj-one-point}
 
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{d_i}
+{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{a_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
@@
 \section{Canonical Rings on \texorpdfstring{$F_k$}{}}
+Let $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such that $C_1, \ldots, C_4$ are independent curves with bi-degrees (1,0), (1,0), (0,1), and (0,1) respectively.
+Let $C_i = V(f_i)$ where $f_i \in \mathscr{O}(a_i, b_i)$.
+Then each $C_i$ corresponds to a polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
 \begin{defn}
@@
 \begin{equation}\label{eqn:define-T=(D)}
-	T_=(D) = \left\{i \in \{1, \ldots, m\}: d_i \sum_{k=1}^m d_k' \alpha_k = d_i' \sum_{k=1}^m d_k \alpha_k \right\},
+	T_=(D) = \left\{i \in \{1, \ldots, m\}: a_i \sum_{k=1}^m b_k \alpha_k = b_i \sum_{k=1}^m a_k \alpha_k \right\},
 \end{equation}
 \begin{equation}\label{eqn:define-T+(D)}
-	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} d_i \sum_{k=1}^m \alpha_k d_k' > d_i' \sum_{k=1}^m \alpha_k d_k \right\},
+	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} a_i \sum_{k=1}^m \alpha_k b_k > b_i \sum_{k=1}^m \alpha_k a_k \right\},
 \end{equation}
@@
 \begin{equation}\label{eqn:define-T-(D)}
-	T_-(D) = \left\{ j \in \{1, \ldots, m\}: d_j \sum_{k=1}^m \alpha_k d_k' < d_j' \sum_{k=1}^m \alpha_k d_k s \right\}.
+	T_-(D) = \left\{ j \in \{1, \ldots, m\}: a_j \sum_{k=1}^m \alpha_k b_k < b_j \sum_{k=1}^m \alpha_k a_k s \right\}.
 \end{equation}
@@
 \begin{lem}
-If $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such that $C_1, \ldots, C_4$ are independent curves with bi-degrees (1,0), (1,0), (0,1), and (0,1) respectively.
-Then each $C_i$ corresponds to a polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
-Then $D$ is generated in degree at most
+$R_D$ is generated in degree at most
 \[
-	\sum_{i\in T_=(D)} \gcd(d_i, d_i')\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (d_i d_j'- d_j d_i')\ell_{i,j}
+	\sum_{i\in T_=(D)} \gcd(a_i, b_i)\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (a_i b_j- a_j b_i)\ell_{i,j}.
 \]
- with relations in degree at most \todo{add}.
 \end{lem}
 \begin{proof}
-Let $(d_i, d_i')$ be the bi-degrees of $f_i$.
+Let $(a_i, b_i)$ be the bi-degrees of $f_i$.
 
@@
 \[
-	g = \sum_{i=1}^m {f_i}^{a_i}
+	g = \sum_{i=1}^m {f_i}^{c_i}
 \]
-where each $a_i \ge - \alpha_i d_i$, $\sum_{i=1}^m a_i d = 0$, and $\sum_{i=1}^m a_i d_i' = 0$.  Then we can view $g$ inside of the lattice
-$S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$. 
+where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^m c_i a_i = 0$, and $\sum_{i=1}^m c_i b_i = 0$.  Then we can view $g$ inside of the lattice
+$S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m c_i a_i = 0$, and $\sum_{i=1}^m c_i b_i = 0$. 
 From here, determining a spanning set for $(R_D)_d$ reduces to finding the extremal rays of $S$ \todo{cite previous lemma}.
@@
 To do this, we extend the method of O'Dorney \todo{cite}.
-We first view the cone $T\subseteq \mathbb{R}^{n+1}$ given by elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge -\alpha_i d$ for all $i$ and $\sum_{i=1}^n a_i (d_i + d_i') =0$.
+We first view the cone $T\subseteq \mathbb{R}^{n+1}$ given by elements of the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for all $i$ and $\sum_{i=1}^n c_i (a_i + b_i) =0$.
 By O'Dorney, this has extremal rays given by
 \[
-	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i} \alpha_j(d_j+ d_j')}{d_i + d_i'}, -\alpha_{i+1}, \ldots, - \alpha_m).
+	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i} \alpha_j(a_j+ b_j)}{a_i + b_i}, -\alpha_{i+1}, \ldots, - \alpha_m).
 \]
 Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_m$.
-We can then intersect the hyperplane $H$ given $\sum_{i=1}^m  d_i X_i = 0$.
+We can then intersect the hyperplane $H$ given $\sum_{i=1}^m  a_i X_i = 0$.
 The extremal rays of $S$ are given by the set of $e_i$ contained in $H$ together with the points of intersection $e_{i,j}$ of $H$ and the line segment connecting $e_i, e_j \not \in H$.
@@
 \[
-	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{k \ne i} \alpha_k (d_k + d_k')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
+	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(a_i, b_i)}) (f_i^{\ell_i \frac{\gcd(a_i, b_i)}{a_i + b_i}\sum_{k \ne i} \alpha_k (a_k + b_k)}) \in H^0(\ell_i \gcd(a_i, b_i) D).
 \]
@@
 \[
-	\epsilon_{i, j} = (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
+	\epsilon_{i, j} = (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (a_i b_j - a_j b_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(a_i b_j - a_j b_i)D)
 \]
@@
 \[
-	s_1 = d_j' \sum_{k \ne i,j} \alpha_k d_k - d_j \sum_{k\ne i, j} \alpha_k d_k'
+	s_1 = b_j \sum_{k \ne i,j} \alpha_k a_k - a_j \sum_{k\ne i, j} \alpha_k b_k
 \]
@@
 \[
-	s_2 = d_i' \sum_{k \ne i,j} \alpha_k d_k - d_i \sum_{k \ne i, j} \alpha_k d_k'.
+	s_2 = b_i \sum_{k \ne i,j} \alpha_k a_k - a_i \sum_{k \ne i, j} \alpha_k b_k.
 \]
@@
 \[
-	\sum_{i\in T_=(D)} \gcd(d_i, d_i')\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (d_i d_j'- d_j d_i')\ell_{i,j}.
+	\sum_{i\in T_=(D)} \gcd(a_i, b_i)\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (a_i b_j- a_j b_i)\ell_{i,j}.
 \]
+\end{proof}
+
+\todo{factor $\phi$ through $\psi$ and $\chi$.}
+\begin{lem}
+$\ker(\psi)$ is generated in degree at most \todo{insert number}.
+\end{lem}
+\begin{proof}
+We first claim that $\psi$ has a relation of the form
+\[
+	(y_j - \beta_j)\prod_{i=1}^m {y_i}^{c_{i}}
+\]
+whenever $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, and $\beta_j \in k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(a_j, b_j)$.
+To find such a $\beta$, we simply write $\epsilon_j$ as a polynomial in $\epsilon_1, \ldots \epsilon _4$.
 

### 2015-07-11 surfaces-write-up/surface-write-up.tex

--- 2015-07-11 surfaces-write-up/surface-write-up.tex
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ many generators $f_{d_i}^{\vec{v}} :=
-\frac{u^{d_i} x^{\vec{v}}} {x_k^{c_i}}$ where $\vec{v} \in
-\bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
-many relations of the form
+{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{a_i}
+x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
+relations of the form
 \[
@@
 
-\section{Canonical Rings on Hirzebruch Surfaces}
+\section{Canonical Rings on \texorpdfstring{$F_k$}{}}
+Let $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such that $C_1, \ldots, C_4$ are independent curves with bi-degrees (1,0), (1,0), (0,1), and (0,1) respectively.
+Let $C_i = V(f_i)$ where $f_i \in \mathscr{O}(a_i, b_i)$.
+Then each $C_i$ corresponds to a polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
 \begin{defn}

### 2015-07-11 surfaces-write-up/surface-write-up.tex
edits to hirzabruch lemma

@@
 To do this, we extend the method of O'Dorney \todo{cite}.
-We first view the cone $T\subseteq \mathbb{R}^{n+1}$ given by elements of the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for all $i$ and $\sum_{i=1}^n c_i (a_i + b_i) =0$.
+We first view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for all $i$ and $\sum_{i=1}^n c_i (a_i + b_i) =0$.
 By O'Dorney, this has extremal rays given by
@@
 Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_m$.
-We can then intersect the hyperplane $H$ given $\sum_{i=1}^m  a_i X_i = 0$.
+We can then intersect the hyperplane $H$ given $\sum_{i=1}^m  a_i X_i = 0$ to get a subspace $S$.
 The extremal rays of $S$ are given by the set of $e_i$ contained in $H$ together with the points of intersection $e_{i,j}$ of $H$ and the line segment connecting $e_i, e_j \not \in H$.
@@
 We first claim that $\psi$ has a relation of the form
-\[
+\begin{equation}\label{eqn:relations-psi}
 	(y_j - \beta_j)\prod_{i=1}^m {y_i}^{c_{i}}
-\]
-whenever $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, and $\beta_j \in k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(a_j, b_j)$.
+\end{equation}
+for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $a_j + \sum_{i=1}^m a_i c_i = 0$, $b_j + \sum_{i=1}^m b_i c_i = 0$, and $\beta_j \in k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(a_j, b_j)$.
 To find such a $\beta$, we simply write $\epsilon_j$ as a polynomial in $\epsilon_1, \ldots \epsilon _4$.
+Furthermore, these generate all relations, since they allow us to reduce any $\prod_{i=1}^n \epsilon_i^{r_i}$ to a canonical form.
+\todo{add reference to earlier description of canonical form.}
+
+Note that we can view the relations from Equation \ref{eqn:relations-psi} as an element of $\mathbb{R}^{n+1}$ given by $(d, c_1, \ldots, c_n)$.
+Let $S'\subseteq \mathbb{R}^+$ be the set of $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$, $a_j + \sum_{i=1}^m a_i c_i = 0$, and $b_j + \sum_{i=1}^m b_i c_i = 0$.
+Note that $S'$ is a translation of $S$ by
 

### 2015-07-12 surfaces-write-up/surface-write-up.tex
spacing & name change hirzebruch section

--- 2015-07-11 surfaces-write-up/surface-write-up.tex
@@
 
-\section{Canonical Rings on \texorpdfstring{$F_k$}{}}
-Let $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such that $C_1, \ldots, C_4$ are independent curves with bi-degrees (1,0), (1,0), (0,1), and (0,1) respectively.
-Let $C_i = V(f_i)$ where $f_i \in \mathscr{O}(a_i, b_i)$.
-Then each $C_i$ corresponds to a polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.
+\section{Canonical Rings on Hirzebruch surfaces}
+Let $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such
+that $C_1, \ldots, C_4$ are independent curves with bi-degrees $(1,0)
+, (1,0), (0,1)$, and $(0,1)$ respectively. Let $C_i = V(f_i)$ where
+$f_i \in \mathscr{O}(a_i, b_i)$. Then each $C_i$ corresponds to a
+polynomial $f_i$ where $f_1$ and $f_2$ are independent linear
+polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
+linear polynomials in $y_0$ and $y_1$.
+
 \begin{defn}
-Suppose $D = \sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(F_k)$.  Then define 
+Suppose $D = \sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(F_
+k)$. Then define 
 \begin{equation}\label{eqn:define-T=(D)}
-	T_=(D) = \left\{i \in \{1, \ldots, m\}: a_i \sum_{k=1}^m b_k \alpha_k = b_i \sum_{k=1}^m a_k \alpha_k \right\},
+	T_=(D) = \left\{i \in \{1, \ldots, m\}: a_i \sum_{k=1}^m b_k 
+\alpha_k = b_i \sum_{k=1}^m a_k \alpha_k \right\},
 \end{equation}
+
 \begin{equation}\label{eqn:define-T+(D)}
-	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} a_i \sum_{k=1}^m \alpha_k b_k > b_i \sum_{k=1}^m \alpha_k a_k \right\},
+	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} 
+a_i \sum_{k=1}^m \alpha_k b_k > b_i \sum_{k=1}^m \alpha_k a_k 
+\right\},
 \end{equation}
+
+\noindent
 and
 \begin{equation}\label{eqn:define-T-(D)}
-	T_-(D) = \left\{ j \in \{1, \ldots, m\}: a_j \sum_{k=1}^m \alpha_k b_k < b_j \sum_{k=1}^m \alpha_k a_k s \right\}.
+	T_-(D) = \left\{ j \in \{1, \ldots, m\}: a_j \sum_{k=1}^m \alpha_
+k b_k < b_j \sum_{k=1}^m \alpha_k a_k s \right\}.
 \end{equation}
@@
 \end{lem}
+
 \begin{proof}
-Let $(a_i, b_i)$ be the bi-degrees of $f_i$.
-
-Notice that if $\gamma \in (R_D)_d$, then 
+Let $(a_i, b_i)$ be the bi-degrees of $f_i$. Notice that if $\gamma
+\in (R_D)_d$, then 
 \[
@@
 \]
-where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^m c_i a_i = 0$, and $\sum_{i=1}^m c_i b_i = 0$.  Then we can view $g$ inside of the lattice
-$S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m c_i a_i = 0$, and $\sum_{i=1}^m c_i b_i = 0$. 
-From here, determining a spanning set for $(R_D)_d$ reduces to finding the extremal rays of $S$ \todo{cite previous lemma}.
 
-To do this, we extend the method of O'Dorney \todo{cite}.
-We first view the cone $T\subseteq \mathbb{R}^{n+1}$ given by elements of the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for all $i$ and $\sum_{i=1}^n c_i (a_i + b_i) =0$.
-By O'Dorney, this has extremal rays given by
+\noindent
+where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^m c_i a_i = 0$,
+and $\sum_{i=1}^m c_i b_i = 0$. Then we can view $g$ inside of the
+lattice $S \subseteq \mathbb{R}^{n + 1}$ given by ordered elements of
+the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge - d \alpha_i$
+for all $i$, $\sum_{i=1}^m c_i a_i = 0$, and $\sum_{i = 1}^m c_i b_i =
+ 0$. From here, determining a spanning set for $(R_D)_d$ reduces to
+finding the extremal rays of $S$ \todo{cite previous lemma}.
+
+To do this, we extend the method of O'Dorney \todo{cite}. We first
+view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
+form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for
+all $i$ and $\sum_{i = 1}^n c_i (a_i + b_i) =0$. By O'Dorney, this
+has extremal rays given by
+
 \[
-	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i} \alpha_j(a_j+ b_j)}{a_i + b_i}, -\alpha_{i+1}, \ldots, - \alpha_m).
+	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
+	\alpha_j(a_j+ b_j)}{a_i + b_i}, -\alpha_{i + 1}, \ldots, - \alpha_m).
 \]
+
 Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_m$.
-We can then intersect the hyperplane $H$ given $\sum_{i=1}^m  a_i X_i = 0$.
-The extremal rays of $S$ are given by the set of $e_i$ contained in $H$ together with the points of intersection $e_{i,j}$ of $H$ and the line segment connecting $e_i, e_j \not \in H$.
+We can then intersect the hyperplane $H$ given $\sum_{i=1}^m a_i X_i
+= 0$ to get a subspace $S$. The extremal rays of $S$ are given
+by the set of $e_i$ contained in $H$ together with the points of
+intersection $e_{i,j}$ of $H$ and the line segment connecting $e_i,
+e_j \not \in H$.
 
- We can calculate the following elements of $R_D$ whose corresponding lattice points lie on these extremal rays:
+We can calculate the following elements of $R_D$ whose
+corresponding lattice points lie on these extremal rays:
 
@@
 \[
-	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(a_i, b_i)}) (f_i^{\ell_i \frac{\gcd(a_i, b_i)}{a_i + b_i}\sum_{k \ne i} \alpha_k (a_k + b_k)}) \in H^0(\ell_i \gcd(a_i, b_i) D).
+	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(a_i, b_i)})
+	(f_i^{\ell_i \frac{\gcd(a_i, b_i)}{a_i + b_i}\sum_{k \ne i}
+	\alpha_k (a_k + b_k)}) \in H^0(\ell_i \gcd(a_i, b_i) D).
 \]
+
 For $i \in T_+(D)$ and $j \in T_-(D)$, define
 \[
-	\epsilon_{i, j} = (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (a_i b_j - a_j b_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(a_i b_j - a_j b_i)D)
+	\epsilon_{i, j} := (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (a_i b_
+j - a_j b_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(a_i b_j - 
+a_j b_i)D)
 \]
+
 where
 \[
-	s_1 = b_j \sum_{k \ne i,j} \alpha_k a_k - a_j \sum_{k\ne i, j} \alpha_k b_k
+	s_1 = b_j \sum_{k \ne i,j} \alpha_k a_k - a_j \sum_{k\ne i, j}
+	\alpha_k b_k
 \]
+
+\noindent
 and
 \[
-	s_2 = b_i \sum_{k \ne i,j} \alpha_k a_k - a_i \sum_{k \ne i, j} \alpha_k b_k.
+	s_2 = b_i \sum_{k \ne i,j} \alpha_k a_k - a_i \sum_{k \ne i, j}
+	\alpha_k b_k.
 \]
-Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
-$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most
+
+Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given 
+above, satisfying the respective conditions.
+$E$ satisfies the conditions of proposition \todo{cite earlier 
+proposition}, so by applying that proposition $R_D$ is generated in 
+degree at most
 \[
-	\sum_{i\in T_=(D)} \gcd(a_i, b_i)\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (a_i b_j- a_j b_i)\ell_{i,j}.
+	\sum_{i\in T_=(D)} \gcd(a_i, b_i)\ell_i + \sum_{i\in T_+(D) \atop
+	j \in T_-(D)} (a_i b_j- a_j b_i)\ell_{i,j}.
 \]
@@
 \end{lem}
+
 \begin{proof}
 We first claim that $\psi$ has a relation of the form
-\[
+\begin{equation}\label{eqn:relations-psi}
 	(y_j - \beta_j)\prod_{i=1}^m {y_i}^{c_{i}}
-\]
-whenever $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, and $\beta_j \in k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(a_j, b_j)$.
-To find such a $\beta$, we simply write $\epsilon_j$ as a polynomial in $\epsilon_1, \ldots \epsilon _4$.
+\end{equation}
+
+\noindent
+for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $a_j + \sum_{i = 1}
+^m a_i c_i = 0$, $b_j + \sum_{i=1}^m b_i c_i = 0$, and $\beta_j \in
+k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(a_j,
+b_j)$.
+
+To find such a $\beta$, we simply write $\epsilon_j$ as a 
+polynomial in $\epsilon_1, \ldots \epsilon _4$. Furthermore, these
+generate all relations, since they allow us to reduce any $\prod_{i =
+1}^n \epsilon_i^{r_i}$ to a canonical form. \todo{add reference to
+earlier description of canonical form.}
+
+Note that we can view the relations from Equation
+\ref{eqn:relations-psi} as an element of $\mathbb{R}^{n+1}$ given
+by $(d, c_1, \ldots, c_n)$.  Let $S'\subseteq \mathbb{R}^{+}$ be the
+set of $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$,
+$a_j + \sum_{i = 1}^m a_i c_i = 0$, and $b_j + \sum_{i=1}^m b_i c_i
+= 0$.  Note that $S'$ is a translation of $S$ by \todo{finish}
 
@@
 \section{Acknowledgments}
-
 We are grateful to David Zureick-Brown for introducing us to this

### 2015-07-12 surfaces-write-up/surface-write-up.tex
minor edit to use Z_{\geq 0}^2

@@
 the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
-{dorney:canonical}, each lattice point $(d, c) \in \bz^2$ such that
-$c \leq d \alpha$ is a nonnegative linear combination of $\vec{x}_i$
-and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in \bz^2$.
-Consequently, any element $\frac{u^{d} x^{\vec{v}}} {x_k^{c}} \in
-R_D$ is expressible as
+{dorney:canonical}, each lattice point $(d, c) \in \bz_{\geq 0}^2$
+such that $c \leq d \alpha$ is a nonnegative linear combination of
+$\vec{x}_i$ and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in
+\bz^2$. Consequently, any element $\frac{u^{d} x^{\vec{v}}}
+{x_k^{c}} \in R_D$ is expressible as
 \begin{align*}

### 2015-07-12 surfaces-write-up/surface-write-up.tex
surfaces: f->F in 1-pt

@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $f_{\vec{v}} := \frac{u^{a_i}
+{{m + i} \choose {i}}$ generators $F_{\vec{v}} := \frac{u^{a_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
@@
 \[
-	f_{d_i}^{\vec{v}} f_{d_j}^{\vec{w}} = f_{d_k}^{\vec{y}} f_{d_\ell}^{\vec{z}}
+	F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}} = F_{d_k}^{\vec{y}} F_{d_\ell}^{\vec{z}}
 \]
@@
 \begin{proof}
-We know $\{f_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{a}{b}
+We know $\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{a}{b}
 \right\rfloor \}$ are minimal generators in degree $1$. Now let $i >
-0$. If $f_{d_i}^{\vec{v}}$ were not minimal for some $\vec{v}$ such
-that $\deg \vec{v} = c_i$, then $f_{d_i}^{\vec{v}} = f_{s}^{\vec{w}}
-f_{t}^{\vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
+0$. If $F_{d_i}^{\vec{v}}$ were not minimal for some $\vec{v}$ such
+that $\deg \vec{v} = c_i$, then $F_{d_i}^{\vec{v}} = F_{s}^{\vec{w}}
+F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
 \bz_{\geq 0}^{m + 1}$. In particular, we see that 
@@
 {dorney:canonical}, each lattice point $(d, c) \in \bz_{\geq 0}^2$
-such that $c \leq d \alpha$ is a nonnegative linear combination of
+such that $c \leq d \alpha$ is a non-negative linear combination of
 $\vec{x}_i$ and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in
@@
 \vec{w} = c_i, \deg \vec{z} = c_{i + 1}$. But these are precisely
-two generators of the form $f_{d_i}^{\vec{w}}$ and $f_{d_{i + 1}}
+two generators of the form $F_{d_i}^{\vec{w}}$ and $F_{d_{i + 1}}
 ^{\vec{z}}$ as prescribed in the theorem statement.

### 2015-07-12 curves-write-up/spin-cring.tex
surfaces title change, curves abs one-word edit
fix defn best lower approx

@@
 	upper-half plane by a Fuchsian group. By the classical results of
-	Kodaira--Spencer, this space of modular forms may be viewed as a
+	Kodaira--Spencer, this space of modular forms may be viewed as the
 	log spin canonical ring of a stacky curve. In this paper, we
@@
 
-\begin{defn}\label{den:lower-approximation}
-If $\frac{\alpha}{\beta}\in \BQ$, then $\frac{c}{k}$ (written in reduced form with $c \in \BN, k \in \BN$) is a {\bf{best lower approximation}} to $\frac{\alpha}{\beta}$ if there does not exist any $\frac{c'}{k'}\in \mathbf{Q}$ with $0<k'<k$ and $\frac{c}{k}\le \frac{c'}{k'}$.
+\begin{defn}
+\label{defn:lower-approximation}
+If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
+$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
+\textbf{best lower approximation} to $\alpha$ if there does not
+exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
+$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
 \end{defn}
-Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative best lower approximations of $\frac{\alpha}{\beta}$ form a finite sequence
-\[
-	0=\frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \frac{\alpha}{\beta}.
-\]
-Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\frac{\alpha}{\beta}=\frac{14}{5}$.
+
+\begin{rem}
+\label{rem:lower-approximation}
+Note that all integers less than or equal to $\lfloor \alpha \rfloor$
+are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
+then the non-negative best lower approximations of
+$\alpha$ form a finite sequence
+\[
+	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
+\]
+
+\noindent
+Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
+\end{rem}
 
@@
 \]
-be the positive best lower approximations of $\frac{\alpha}{\beta}$.
+be the positive best lower approximations of $\frac{\alpha}{\beta}$
+(similar to Remark ~\ref{rem:lower-approximation}).
 Then,
@@
 \noindent
-be the positive best lower approximations of $\frac{
-\alpha}{\beta}$. 
+be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
 Choose a positive best lower approximation $\frac{c_i}{k_i}$.

### 2015-07-12 surfaces-write-up/surface-write-up.tex
fix defn best lower approx

@@
 \label{defn:lower-approximation}
-If $\frac{\alpha}{\beta}\in \bq$, then $\frac{c}{k}$ (written in
-reduced form with $c \in \bn, k \in \bn$) is a {\bf{best lower
-approximation}} to $\frac{\alpha}{\beta}$ if there does not exist
-any $\frac{c'}{k'}\in \bq$ with $0 < k'<k$ and $\frac{c}{k} \le
-\frac{c'}{k'}$.
+If $\alpha \in \br$, then a rational number $\frac{c}{k} \leq \alpha
+$ (written in reduced form with $c \in \bz, k \in \bn$) is a
+\textbf{best lower approximation} to $\alpha$ if there does not
+exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
+$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
 \end{defn}
 
-Moreover, if $\frac{\alpha}{\beta}\ge 0$, then the non-negative
-best lower approximations of $\frac{\alpha}{\beta}$ form a finite
-sequence
+\begin{rem}
+\label{rem:lower-approximation}
+Note that all integers less than or equal to $\lfloor \alpha \rfloor$
+are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
+then the non-negative best lower approximations of
+$\alpha$ form a finite sequence
 \[
-	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \frac{\alpha}{\beta}.
+	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
 \]
-Figure \ref{fig:s14/5-lattice} gives a pictorial representation of
-the positive best lower approximations of $\frac{\alpha}{\beta} =
-\frac{14}{5}$.
+
+\noindent
+Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
+\end{rem}
 

### 2015-07-12 surfaces-write-up/surface-write-up.tex
add todos
add macros for bidegrees a, b

@@
 
-%%%%%%%%%%%%%%%%%%%%% cring custom commands %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% csurfaces custom commands %%%%%%%%%%%%%%%%%%%%%%%%%
 
 \DeclareMathOperator\di{Div}
-\newcommand\sx{\mathscr X}
+\newcommand\bida{a}
+\newcommand\bidb{b}
 \newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
@@
 \section{Background}
+
+\todo{macros: hirzebruch, degrees}
 
@@
 Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{r}\delta_i$ and $w_1,\ldots, w_r \in \bz$.
+
+\todo{define bidegrees a_i and b_i}
 \end{prop}
+
 \begin{proof}
-By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{r}a_i e_i$ with $a_i \in \br$.
+By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{r} \bida_i e_i$ with $\bida_i \in \br$.
 Let $\{a\} := a - \lfloor a \rfloor$ denote the fractional part of $a$.
-Let $\lambda = \sum_{i=1}^{r}\{a_i\}$.
-Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\delta_i$.
+Let $\lambda = \sum_{i=1}^{r}\{\bida_i\}$.
+Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor \bida_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\delta_i$.
 Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{r}\delta_i$.
@@
 \begin{align*}
-	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n}a_ic_i = \sum_{i=1}^{} b_i c_i. \rangle 
+	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{} \bidb_i c_i. \rangle 
 \end{align*}
@@
 Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
-Now, letting $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ so that we can write $\lambda_i = \sum_{i=1}^{r}a_i e_i$ with $0 \leq a_i < 1$ for all $i$.
+Now, letting $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ so that we can write $\lambda_i = \sum_{i=1}^{r}\bida_i e_i$ with $0 \leq \bida_i < 1$ for all $i$.
 Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in the above canonical form, yielding a relation in degree at most $\deg \lambda_i + \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$ Furthermore, these relations generate all relations, as one can apply a sequence of these relations to put any $\sigma \in \Sigma$ into canonical form.
@@
 \end{align*}
-where $\alpha_i \in \bq$ and $\deg D_i = a_i$.
+where $\alpha_i \in \bq$ and $\deg D_i = \bida_i$.
 Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
@@
 \label{align:pm-span}
-\sum_{i=0}^{n} c_i \cdot a_i \cdot f_i = 0 & \text{ and } &c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=0}^{n} c_i \cdot \bida_i \cdot f_i = 0 & \text{ and } &c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $F_{\vec{v}} := \frac{u^{a_i}
+{{m + i} \choose {i}}$ generators $F_{\vec{v}^{d_i} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
@@
 
+\todo{change thm to be inductive for adding pts, giving result on
+effective divisors}
+\todo{remark on not doing two points}
+
 \ssec{Bounds for Arbitrary Divisors on Projective Space}
@@
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $C_i = V(f_i)$ where
-$f_i \in \mathscr{O}(a_i, b_i)$. Then each $C_i$ corresponds to a
+$f_i \in \mathscr{O}(\bida_i, \bidb_i)$. Then each $C_i$ corresponds to a
 polynomial $f_i$ where $f_1$ and $f_2$ are independent linear
@@
 \begin{equation}\label{eqn:define-T=(D)}
-	T_=(D) = \left\{i \in \{1, \ldots, m\}: a_i \sum_{k=1}^m b_k 
-\alpha_k = b_i \sum_{k=1}^m a_k \alpha_k \right\},
+	T_=(D) = \left\{i \in \{1, \ldots, m\}: \bida_i \sum_{k=1}^m \bidb_k 
+\alpha_k = \bidb_i \sum_{k=1}^m \bida_k \alpha_k \right\},
 \end{equation}
@@
 	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} 
-a_i \sum_{k=1}^m \alpha_k b_k > b_i \sum_{k=1}^m \alpha_k a_k 
+\bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^m \alpha_k \bida_k 
 \right\},
@@
 \begin{equation}\label{eqn:define-T-(D)}
-	T_-(D) = \left\{ j \in \{1, \ldots, m\}: a_j \sum_{k=1}^m \alpha_
-k b_k < b_j \sum_{k=1}^m \alpha_k a_k s \right\}.
+	T_-(D) = \left\{ j \in \{1, \ldots, m\}: \bida_j \sum_{k=1}^m \alpha_
+k \bidb_k < \bidb_j \sum_{k=1}^m \alpha_k \bida_k s \right\}.
 \end{equation}
@@
 \[
-	\sum_{i\in T_=(D)} \gcd(a_i, b_i)\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (a_i b_j- a_j b_i)\ell_{i,j}.
+	\sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
 \]
@@
 \begin{proof}
-Let $(a_i, b_i)$ be the bi-degrees of $f_i$. Notice that if $\gamma
+Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. Notice that if $\gamma
 \in (R_D)_d$, then 
@@
 \noindent
-where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^m c_i a_i = 0$,
-and $\sum_{i=1}^m c_i b_i = 0$. Then we can view $g$ inside of the
+where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^m c_i \bida_i = 0$,
+and $\sum_{i=1}^m c_i \bidb_i = 0$. Then we can view $g$ inside of the
 lattice $S \subseteq \mathbb{R}^{n + 1}$ given by ordered elements of
 the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge - d \alpha_i$
-for all $i$, $\sum_{i=1}^m c_i a_i = 0$, and $\sum_{i = 1}^m c_i b_i =
+for all $i$, $\sum_{i=1}^m c_i \bida_i = 0$, and $\sum_{i = 1}^m c_i \bidb_i =
  0$. From here, determining a spanning set for $(R_D)_d$ reduces to
@@
 form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for
-all $i$ and $\sum_{i = 1}^n c_i (a_i + b_i) =0$. By O'Dorney, this
+all $i$ and $\sum_{i = 1}^n c_i (\bida_i + \bidb_i) =0$. By O'Dorney, this
 has extremal rays given by
@@
 	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
-	\alpha_j(a_j+ b_j)}{a_i + b_i}, -\alpha_{i + 1}, \ldots, - \alpha_m).
+	\alpha_j(\bida_j+ \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1}, \ldots, - \alpha_m).
 \]
@@
 Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_m$.
-We can then intersect the hyperplane $H$ given $\sum_{i=1}^m a_i X_i
+We can then intersect the hyperplane $H$ given $\sum_{i=1}^m \bida_i X_i
 = 0$ to get a subspace $S$. The extremal rays of $S$ are given
@@
 \[
-	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(a_i, b_i)})
-	(f_i^{\ell_i \frac{\gcd(a_i, b_i)}{a_i + b_i}\sum_{k \ne i}
-	\alpha_k (a_k + b_k)}) \in H^0(\ell_i \gcd(a_i, b_i) D).
+	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(\bida_i, \bidb_i)})
+	(f_i^{\ell_i \frac{\gcd(\bida_i, \bidb_i)}{\bida_i + \bidb_i}\sum_{k \ne i}
+	\alpha_k (\bida_k + \bidb_k)}) \in H^0(\ell_i \gcd(\bida_i, \bidb_i) D).
 \]
@@
 \[
-	\epsilon_{i, j} := (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (a_i b_
-j - a_j b_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(a_i b_j - 
-a_j b_i)D)
+	\epsilon_{i, j} := (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (\bida_i \bidb_
+j - \bida_j \bidb_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(\bida_i \bidb_j - 
+\bida_j \bidb_i)D)
 \]
@@
 \[
-	s_1 = b_j \sum_{k \ne i,j} \alpha_k a_k - a_j \sum_{k\ne i, j}
-	\alpha_k b_k
+	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k\ne i, j}
+	\alpha_k \bidb_k
 \]
@@
 \[
-	s_2 = b_i \sum_{k \ne i,j} \alpha_k a_k - a_i \sum_{k \ne i, j}
-	\alpha_k b_k.
+	s_2 = \bidb_i \sum_{k \ne i,j} \alpha_k \bida_k - \bida_i \sum_{k \ne i, j}
+	\alpha_k \bidb_k.
 \]
@@
 \[
-	\sum_{i\in T_=(D)} \gcd(a_i, b_i)\ell_i + \sum_{i\in T_+(D) \atop
-	j \in T_-(D)} (a_i b_j- a_j b_i)\ell_{i,j}.
+	\sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in T_+(D) \atop
+	j \in T_-(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
 \]
@@
 \noindent
-for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $a_j + \sum_{i = 1}
-^m a_i c_i = 0$, $b_j + \sum_{i=1}^m b_i c_i = 0$, and $\beta_j \in
-k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(a_j,
-b_j)$.
+for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
+^m \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^m \bidb_i c_i = 0$, and $\beta_j \in
+k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida_j,
+\bidb_j)$.
 
@@
 set of $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$,
-$a_j + \sum_{i = 1}^m a_i c_i = 0$, and $b_j + \sum_{i=1}^m b_i c_i
+$\bida_j + \sum_{i = 1}^m \bida_i c_i = 0$, and $\bidb_j + \sum_{i=1}^m \bidb_i c_i
 = 0$.  Note that $S'$ is a translation of $S$ by \todo{finish}

### 2015-07-12 surfaces-write-up/surface-write-up.tex
fix todo, missing }, delete some old macros

@@
 \newcommand\bidb{b}
-\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
-\newcommand{\se}[1]{\section*{Problem #1}}
-\newcommand{\halfcan}{L}
+
 \DeclareMathOperator{\supp}{Supp}
@@
 
-\todo{define bidegrees a_i and b_i}
+\todo{define bidegrees $a_i$ and $b_i$}
 \end{prop}
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $F_{\vec{v}^{d_i} := \frac{u^{d_i}
+{{m + i} \choose {i}}$ generators $F_{\vec{v}}^{d_i} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$

### 2015-07-12 surfaces-write-up/surface-write-up.tex
hirzebruch macro, change a, b -> c, d in 1pt

@@
 \newcommand\bidb{b}
+\newcommand\hirz{\mathbb{F}}
 
@@
 
-\todo{macros: hirzebruch, degrees}
+\todo{macros: degrees}
 
@@
 \[
-	\left\lfloor \frac{a}{b} \right\rfloor = \frac{c_0}{d_0} <
-	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{a}{b}
+	\left\lfloor \frac{c}{d} \right\rfloor = \frac{c_0}{d_0} <
+	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{c}{d}
 \]
@@
 the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
-{dorney:canonical}, each lattice point $(d, c) \in \bz_{\geq 0}^2$
-such that $c \leq d \alpha$ is a non-negative linear combination of
+{dorney:canonical}, each lattice point $(d', c') \in \bz_{\geq 0}^2$
+such that $c' \leq d' \alpha$ is a non-negative linear combination of
 $\vec{x}_i$ and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in
-\bz^2$. Consequently, any element $\frac{u^{d} x^{\vec{v}}}
-{x_k^{c}} \in R_D$ is expressible as
+\bz^2$. Consequently, any element $\frac{u^{d'} x^{\vec{v}}}
+{x_k^{c'}} \in R_D$ is expressible as
 \begin{align*}
-	\frac{u^{d} x^{\vec{v}}} {x_k^{c}} = \frac{u^{d_i} x^{\vec{w}}}
+	\frac{u^{d'} x^{\vec{v}}} {x_k^{c'}} = \frac{u^{d_i} x^{\vec{w}}}
 	{x_k^{c_i}} \frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}}

### 2015-07-12 curves-write-up/spin-cring.tex
edited congruence example

@@
 \label{eg:congruence-bounds}
-Suppose $\Gamma \subset SL_2(\BZ)$ is any congruence subgroup. Then, since
+In this example, we deduce bounds on the weight of generators and relations of the ring of modular forms associated to any congruence subgroup $\Gamma \subset SL_2(\BZ)$. Since
 the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer
 order 1, 2 and 3, and has at least one cusp, the
-action of $\Gamma$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
-Furthermore, if $\Gamma$ has some odd weight modular form, then it must 
-have no points with stabilizer order 2 (see Remark ~\ref{rem:odd-denom}). 
+action of $\Gamma$ on $\BH$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
+
+If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$.
+This follows in the case $g > 0$ from Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky} and in the case that $g = 0$ from \cite[Theorem 9.3.1]{vzb:stacky}.
+Note that when $g = 0$ the exceptional cases of \cite[Theorem 9.3.1]{vzb:stacky} do not occur because $\delta > 0$.
+
+Furthermore, if $\Gamma$ has some nonzero odd weight modular form, then it must 
+have no points with stabilizer order 2 by Remark ~\ref{rem:odd-denom}. 
 Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
 generated in degree at most $5$ with relations in degree at most $10$.
-In fact, it is not difficult to show $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
-Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because there is a cusp, so $\delta > 0$.
+In fact, it is not difficult to show $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
+Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because $\Gamma$ has a cusp, so $\delta > 0$.
 \end{example}

### 2015-07-12 surfaces-write-up/surface-write-up.tex

@@
 \newcommand\bidb{b}
+\newcommand\pdeg{\delta}
 \newcommand\hirz{\mathbb{F}}
@@
 \section{Background}
-
-\todo{macros: degrees}
 
@@
 \begin{align*}
-	\Sigma = \{(d,c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
+	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
 \end{align*}
-Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
-Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
-Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{r}\delta_i$ and $w_1,\ldots, w_r \in \bz$.
+Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\pdeg^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
+Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\pdeg_i$.
+Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{r}\pdeg_i$ and $w_1,\ldots, w_r \in \bz$.
 
@@
 \begin{proof}
+\todo{define $\pdeg$, $\bida$, and $\bidb$}
 By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{r} \bida_i e_i$ with $\bida_i \in \br$.
@@
 Let $\lambda = \sum_{i=1}^{r}\{\bida_i\}$.
-Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor \bida_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\delta_i$.
-Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{r}\delta_i$.
+Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor \bida_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\pdeg_i$.
+Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{r}\pdeg_i$.
 \end{proof}
@@
 \begin{proof}
+\todo{define $\bida$ and $\bidb$}
 Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
@@
 \end{align}
+
+\noindent
+\todo{the above ``and'' needs to be placed better}
 form a spanning set for $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
@@
 \end{align}
+
+\noindent
 form a basis for $H^0(\bp^m, dD)$ over $k$.
 \end{prop}
+
 \begin{proof}
@@
 Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \alpha H$, with $\alpha = \frac{a}{b} \in \bq$
+$\bp^m$. Let $D = \alpha H$, with $\alpha = \frac{p}{q} \in \bq$
 and $H = V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$.
@@
 \[
-	\left\lfloor \frac{c}{d} \right\rfloor = \frac{c_0}{d_0} <
-	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{c}{d}
+	\left\lfloor \frac{p}{q} \right\rfloor = \frac{c_0}{d_0} <
+	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{p}{q}
 \]
@@
 \begin{proof}
-We know $\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{a}{b}
+We know $\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{p}{q}
 \right\rfloor \}$ are minimal generators in degree $1$. Now let $i >
@@
 the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
-{dorney:canonical}, each lattice point $(d', c') \in \bz_{\geq 0}^2$
-such that $c' \leq d' \alpha$ is a non-negative linear combination of
+{dorney:canonical}, each lattice point $(\delta, \gamma) \in \bz_{\geq 0}^2$
+such that $c \leq d \alpha$ is a non-negative linear combination of
 $\vec{x}_i$ and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in
-\bz^2$. Consequently, any element $\frac{u^{d'} x^{\vec{v}}}
-{x_k^{c'}} \in R_D$ is expressible as
+\bz^2$. Consequently, any element $\frac{u^{\delta} x^{\vec{v}}}
+{x_k^{\gamma}} \in R_D$ is expressible as
 \begin{align*}
-	\frac{u^{d'} x^{\vec{v}}} {x_k^{c'}} = \frac{u^{d_i} x^{\vec{w}}}
+	\frac{u^{\delta} x^{\vec{v}}} {x_k^{\gamma}} = \frac{u^{d_i} x^{\vec{w}}}
 	{x_k^{c_i}} \frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}}
@@
 view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
-form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$ for
+form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -d \alpha_i$ for
 all $i$ and $\sum_{i = 1}^n c_i (\bida_i + \bidb_i) =0$. By O'Dorney, this
@@
 by the set of $e_i$ contained in $H$ together with the points of
-intersection $e_{i,j}$ of $H$ and the line segment connecting $e_i,
-e_j \not \in H$.
+intersection $e_{i, j}$ of $H$ and the edges of the simplex
+connecting the $e_i, e_j \not \in H$.
+\todo{more detail above}
 

### 2015-07-13 curves-write-up/spin-cring.tex
some edits to congruence example

@@
 If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$.
-This follows in the case $g > 0$ from Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky} and in the case that $g = 0$ from \cite[Theorem 9.3.1]{vzb:stacky}.
-Note that when $g = 0$ the exceptional cases of \cite[Theorem 9.3.1]{vzb:stacky} do not occur because $\delta > 0$.
-
-Furthermore, if $\Gamma$ has some nonzero odd weight modular form, then it must 
+This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky}.
+Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.
+
+If $\Gamma$ has some nonzero odd weight modular form, then it must 
 have no points with stabilizer order 2 by Remark ~\ref{rem:odd-denom}. 
@@
 generated in degree at most $5$ with relations in degree at most $10$.
-In fact, it is not difficult to show $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
+Furthermore, it is not difficult to show that $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
 Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because $\Gamma$ has a cusp, so $\delta > 0$.

### 2015-07-13 surfaces-write-up/surface-write-up.tex
lemma 5.3 edits

@@
 \[
-	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(\bida_i, \bidb_i)})
+	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha_k \ell_i \gcd(\bida_i, \bidb_i)})
 	(f_i^{\ell_i \frac{\gcd(\bida_i, \bidb_i)}{\bida_i + \bidb_i}\sum_{k \ne i}
@@
 \[
-	\epsilon_{i, j} := (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (\bida_i \bidb_
+	\epsilon_{i, j} := (\prod_{k = 1}^m f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
 j - \bida_j \bidb_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(\bida_i \bidb_j - 
@@
 	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k\ne i, j}
-	\alpha_k \bidb_k
+	\alpha_k \bidb_k = b_j (\alpha_i a_i + \alpha_j a_j) - a_j (\alpha_i b_i + \alpha_j b_j)
 \]
@@
 \[
-	s_2 = \bidb_i \sum_{k \ne i,j} \alpha_k \bida_k - \bida_i \sum_{k \ne i, j}
-	\alpha_k \bidb_k.
+	s_2 = -\bidb_i \sum_{k \ne i,j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
+	\alpha_k \bidb_k = -b_i (\alpha_i a_i + \alpha_j a_j) + a_i (\alpha_i b_i + \alpha_j b_j).
 \]
@@
 \begin{equation}\label{eqn:relations-psi}
-	(y_j - \beta_j)\prod_{i=1}^m {y_i}^{c_{i}}
+	(y_j - \beta_j)\prod_{i=1}^n {y_i}^{c_{i}}
 \end{equation}
@@
 for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
-^m \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^m \bidb_i c_i = 0$, and $\beta_j \in
+^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in
 k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida_j,
@@
 Note that we can view the relations from Equation
-\ref{eqn:relations-psi} as an element of $\mathbb{R}^{n+1}$ given
-by $(d, c_1, \ldots, c_n)$.  Let $S'\subseteq \mathbb{R}^{+}$ be the
-set of $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -\alpha_i d$,
-$\bida_j + \sum_{i = 1}^m \bida_i c_i = 0$, and $\bidb_j + \sum_{i=1}^m \bidb_i c_i
-= 0$.  Note that $S'$ is a translation of $S$ by \todo{finish}
+\ref{eqn:relations-psi} as an element of $S$ given
+by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  Let $S'\subseteq (\mathbb{R}_{\ge 0})^{n+1}$ be the
+set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
+$\bida_j + \sum_{i = 1}^m \bida_i c_i = 0$, and $\bidb_j + \sum_{i=1}^n \bidb_i c_i
+= 0$.  A careful computation deduces that $\gamma (d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots, c_n)$ is of the form 
+\[
+	E + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k},
+\] 
+where $E$ is $\mathbb{R}_{\ge 0}$
+combination of elements in 
+\[
+	\{e_i \mbox{ if } i\in S\} \cup \{e_{i,j}: j\in S_- \mbox{ if } i \in S_+\} \cup \{e_{j,i}: j\in S_+ \mbox{ if } i \in S_-\}
+\]
+given by lattice point $(d_E, w_1, \ldots, w_n)$ with $w_i = 1$.  These conditions imply that 
+\[
+	d_E \le \left\{ \begin{split}  \ell_i \gcd(\bida_i, \bidb_i) \mbox{ if } i \in S_= 
+			\\ \max_{j\in S_-}(\ell_{i,j} (\bida_i \bidb_
+j - \bida_j \bidb_i)) \mbox{ if } i\in S_+ \\
+			\\ \max_{j\in S_+}(\ell_{j, i} (\bida_j \bidb_
+i - \bida_i \bidb_j)) \mbox{ if } i \in S_- \end{split}  \right.
+\]
+
+Let $M$ be the set of monomials of $\beta_j$.  Then for $m\in M$, the corresponding lattice point is of the form
+\[
+	E_m + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k}
+\]
+where $E_m$ is a $\mathbb{R}_{\ge 0}$ combination of elements in
+\[
+	\{e_j : j\in T_= \cap \{1, 2, 3, 4\}\} \cup \{e_{j, k}: j\in T_= \cap \{1, 2, 3, 4\}, k\in T_-\} \cup \{e_{k,j}: k\in T_+, j\in T_- \cap \{1, 2, 3, 4\}\}.
+\]
 

### 2015-07-13 surfaces-write-up/surface-write-up.tex
surfaces 1pt modify relations and gen statement

@@
 \[
-	F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}} = F_{d_k}^{\vec{y}} F_{d_\ell}^{\vec{z}}
+	G_{d_i, d_j}^{\vec{v}, \vec{w}} = F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}}
+	- (F_{d_k}^{\vec{y}})^{g_{i, j}} (F_{d_\ell}^{\vec{z}})^{g_{i, j}}
 \]
@@
 \begin{proof}
-We know $\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{p}{q}
-\right\rfloor \}$ are minimal generators in degree $1$. Now let $i >
+We know $\left\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{p}{q}
+\right\rfloor \right\}$ are minimal generators in degree $1$. Now let $i >
 0$. If $F_{d_i}^{\vec{v}}$ were not minimal for some $\vec{v}$ such
@@
 the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
-{dorney:canonical}, each lattice point $(\delta, \gamma) \in \bz_{\geq 0}^2$
-such that $c \leq d \alpha$ is a non-negative linear combination of
-$\vec{x}_i$ and $\vec{x}_{i + 1}$ where $\vec{x}_i := (d_i, c_i) \in
-\bz^2$. Consequently, any element $\frac{u^{\delta} x^{\vec{v}}}
-{x_k^{\gamma}} \in R_D$ is expressible as
+{dorney:canonical}, each lattice point $(\beta, \gamma) \in
+\bz_{\geq 0}^2$ such that $c \leq d \alpha$ is a non-negative
+linear combination of $\vec{x}_i$ and $\vec{x}_{i + 1}$ where
+$\vec{x}_i := (d_i, c_i) \in \bz^2$. Consequently, if $(\beta,
+\gamma) = h _1 (d_i, c_i) + h_2 (d_{i + 1}, c_{i + 1})$ for $h_1,
+h_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta} x^{\vec{v}}}
+{x_k^{ \gamma}} \in R_D$ is expressible as
 \begin{align*}
-	\frac{u^{\delta} x^{\vec{v}}} {x_k^{\gamma}} = \frac{u^{d_i} x^{\vec{w}}}
-	{x_k^{c_i}} \frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = (\frac{u^{d_i} x^{\vec{w}}}
+	{x_k^{c_i}})^{h_1} (\frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}})^{h_2}
 \end{align*}
@@
 \noindent
-where $\vec{w}, \vec{z} \in \bz_{\geq 0}^{m + 1}$ such that $\deg
+for some $\vec{w}, \vec{z} \in \bz_{\geq 0}^{m + 1}$ such that $\deg
 \vec{w} = c_i, \deg \vec{z} = c_{i + 1}$. But these are precisely
-two generators of the form $F_{d_i}^{\vec{w}}$ and $F_{d_{i + 1}}
-^{\vec{z}}$ as prescribed in the theorem statement.
+powers of two generators of the form $F_{d_i}^{\vec{w}}$ and
+$F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.
 

### 2015-07-13 surfaces-write-up/surface-write-up.tex
lemma 5.3 edits

--- 2015-07-13 surfaces-write-up/surface-write-up.tex
@@
 \[
-	\sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in T_+(D) \atop
+	\sigma = \sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in T_+(D) \atop
 	j \in T_-(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
@@
 \begin{equation}\label{eqn:relations-psi}
-	(y_j - \beta_j)\prod_{i=1}^n {y_i}^{c_{i}}
+	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{i}}
 \end{equation}
@@
 \[
-	\{e_i \mbox{ if } i\in S\} \cup \{e_{i,j}: j\in S_- \mbox{ if } i \in S_+\} \cup \{e_{j,i}: j\in S_+ \mbox{ if } i \in S_-\}
+	\{e_i \mbox{ if } i\in S\} \cup \{e_{i,j}: j\in S_- \mbox{ if } i \in S_+\} \cup \{e_{j,i}: j\in S_+ \mbox{ if } i \in S_-\}.
 \]
-given by lattice point $(d_E, w_1, \ldots, w_n)$ with $w_i = 1$.  These conditions imply that 
+
+Let $M$ be the set of monomials of $\beta_j$.  Then for $\mu\in M$, the corresponding lattice point is of the form
 \[
-	d_E \le \left\{ \begin{split}  \ell_i \gcd(\bida_i, \bidb_i) \mbox{ if } i \in S_= 
+	E_\mu + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k}
+\]
+where $E_\mu$ is a $\mathbb{R}_{\ge 0}$-combination of elements in
+\begin{align*}
+			& \{e_j : j\in T_= \cap \{1, 2, 3, 4\}\} \\
+	\cup \; 	& \{e_{j, k}: j\in T_= \cap \{1, 2, 3, 4\}, k\in T_-\}\\
+	\cup \; 	& \{e_{k,j}: k\in T_+, j\in T_- \cap \{1, 2, 3, 4\}\}.
+\end{align*}
+
+Let $F\in R_D$ correspond to $E + \sum_{k\in T_=} (r_k) e_k + \sum_{h\in T_+ \atop k\in T_-} (r_{h,k}) e_{h,k}$ where $(r)$ signifies the fractional part of $r$.
+Similarly, let $F_\mu \in R_D$ correspond to $E_\mu + \sum_{h\in T_+ \atop k\in T_-} (r_{h,k}) e_{h,k}$.
+Then $F - \sum_{\mu\in M} F_\mu = 0$ gives us a relation in degree at most
+\[
+	\sigma + \deg(F),
+\]
+which generates $(z_i - \beta_i) \prod_{i=1}^n y_i^{c_i}$
+We can bound $\deg(F)$ by
+\[
+	\deg(F) \le \left\{ \begin{split}  \ell_i \gcd(\bida_i, \bidb_i) \mbox{ if } i \in S_= 
 			\\ \max_{j\in S_-}(\ell_{i,j} (\bida_i \bidb_
@@
 \]
-
-Let $M$ be the set of monomials of $\beta_j$.  Then for $m\in M$, the corresponding lattice point is of the form
+Therefore, $\ker(\psi)$ is generated in degree at most
 \[
-	E_m + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k}
-\]
-where $E_m$ is a $\mathbb{R}_{\ge 0}$ combination of elements in
-\[
-	\{e_j : j\in T_= \cap \{1, 2, 3, 4\}\} \cup \{e_{j, k}: j\in T_= \cap \{1, 2, 3, 4\}, k\in T_-\} \cup \{e_{k,j}: k\in T_+, j\in T_- \cap \{1, 2, 3, 4\}\}.
+	\tau = \sigma
+	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
 \]

### 2015-07-13 surfaces-write-up/surface-write-up.tex
major rewrite 1pt statement, add some defs to 1pt

@@
 \newcommand\hirz{\mathbb{F}}
+\newcommand\mss{\mathscr{S}}
 
@@
 
+\begin{defn}
+\label{defn:vec-sum}
+For $\vec{v} \in \br^n$, denote $\deg \vec{v} := \sum_{i = 0}
+^n v_i$ (i.e. the taxicab metric).
+Let $\mss_i := \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
+\sum_{i = 0} ^{m + 1} v_i = c_i\}$ be the set of $\bz_{\geq 0}
+^{m + 1}$-vectors with sum of components equal to $c_i$.
+\end{defn}
+
+\begin{defn}
+\label{defn:vec-order}
+Let $\vec{v}, \vec{w} \in \br^n$ be two vectors. Let $i$
+be the right-most coordinate such that $v_i$ is nonzero
+and $j$ be the left-most coordinate such that $w_j$ is
+nonzero. Define $\vec{v} \prec \vec{w}$ if $i \leq j$.
+\end{defn}
+
 \begin{thm}
@@
 \[
-	\left\lfloor \frac{p}{q} \right\rfloor = \frac{c_0}{d_0} <
+	0 = \frac{c_0}{d_0} <
 	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{p}{q}
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $F_{\vec{v}}^{d_i} := \frac{u^{d_i}
+{{m + i} \choose {i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
-relations of the form
-\[
-	G_{d_i, d_j}^{\vec{v}, \vec{w}} = F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}}
-	- (F_{d_k}^{\vec{y}})^{g_{i, j}} (F_{d_\ell}^{\vec{z}})^{g_{i, j}}
-\]
+such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has $z$
+many \todo{how many?} relations of the following two types.
+
+For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
+\vec{w} \in \mss_j$, there is a relation of the form either
+\begin{flalign*}
+	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+	- \prod_{\vec{y} \in \mss_{k_{i, j}}} (F_{k_{i, j}}^{\vec{y}})
+	^{g_{\vec{y}}} &(i < k_{i, j} < j) \\
+	\text{or} \\
+	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+	- \prod_{\substack{\vec{y} \in \mss_{k_{i, j}} \\ \vec{z} \in
+	\mss_{k_{i, j} + 1}}} (F_{k_{i, j}}^{\vec{y}})^{g_{\vec{y}}} \;
+	(F_{k_{i, j} + 1}^{\vec{z}})^{h_{\vec{z}}}
+	&(i < k_{i, j} < k_{i, j} + 1 < j).
+\end{flalign*}
+
+Furthermore, there are the relations for each $(i, j)$ with
+$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
+\mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
+~\ref{defn:vec-order}) of the form 
+\begin{align*}
+	&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+	- F_i^{\vec{y}} F_j^{\vec{w}} \\
+\end{align*}
 
 \noindent
-when $d_i + d_j = d_k + d_\ell$ and $\vec{v} + \vec{w} = \vec{y} +
-\vec{z}$.
+where $\vec{y} \in \mss_i$ and $\vec{w} \in \mss_j$ are the unique
+vectors such that $\vec{y} \prec \vec{w}$.
 \end{thm}
@@
 \begin{proof}
-We know $\left\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{p}{q}
-\right\rfloor \right\}$ are minimal generators in degree $1$. Now let $i >
-0$. If $F_{d_i}^{\vec{v}}$ were not minimal for some $\vec{v}$ such
-that $\deg \vec{v} = c_i$, then $F_{d_i}^{\vec{v}} = F_{s}^{\vec{w}}
-F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
-\bz_{\geq 0}^{m + 1}$. In particular, we see that 
+We know $\left\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor
+\frac{p}{q} \right\rfloor \right\}$ are minimal generators in
+degree $1$. Now let $i > 0$. Suppose $F_i^{\vec{v}}$ were not
+minimal for some $\vec{v} \in \mss_i$. Then $F_i^{\vec{v}} =
+F_{s}^{\vec{w}} F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and
+$\vec{w}, \vec{z} \in \bz_{ \geq 0}^{m + 1}$. In particular, we see
+that 
 \begin{align*}
@@
 $\vec{x}_i := (d_i, c_i) \in \bz^2$. Consequently, if $(\beta,
-\gamma) = h _1 (d_i, c_i) + h_2 (d_{i + 1}, c_{i + 1})$ for $h_1,
-h_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta} x^{\vec{v}}}
-{x_k^{ \gamma}} \in R_D$ is expressible as
+\gamma) = \ell_1 (d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for
+$\ell_1, \ell_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta}
+x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
 \begin{align*}
-	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = (\frac{u^{d_i} x^{\vec{w}}}
-	{x_k^{c_i}})^{h_1} (\frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}})^{h_2}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}
+	x^{\vec{w}}} {x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}
+	x^{\vec{z}}} {x_k^{c_{i + 1}}}\right)^{\ell_2}
 \end{align*}
@@
 \noindent
-for some $\vec{w}, \vec{z} \in \bz_{\geq 0}^{m + 1}$ such that $\deg
-\vec{w} = c_i, \deg \vec{z} = c_{i + 1}$. But these are precisely
-powers of two generators of the form $F_{d_i}^{\vec{w}}$ and
-$F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.
+for some $\vec{w} \in \mss_i, \vec{z} \in \mss_{i + 1}$. But these
+are precisely powers of two generators of the form $F_i^{\vec{w}}$
+and $F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.
 

### 2015-07-13 surfaces-write-up/surface-write-up.tex
added saucy intro

--- 2015-07-13 surfaces-write-up/surface-write-up.tex
@@
 \section{Introduction}
+\todo{Clean up this stuff on siegel modular forms, hilbert modular forms, say something about hasse keel program, canoncical rings studied before}
+
+\todo{Might be reasonable to think about higher dimensional rational varieties that are similar to these hirzebruch surfaces.}
+
+\todo{The following stuff is almost nonsensical now, will be edited much more soon}
+
+Hasse keel program, birational map from $proj R(K + \Delta)$ to $M_2$, they showed finite generation, we're giving explicit generators and bounds.
+
+The work in this paper also yields bounds for certain rings of Hilbert modular forms. Recall that a Hilbert modular form is a generalization of modular forms to multiple variables.
+
+Siegel modular forms are a generalization of modular forms on the Siegel upper half plane to automorphic forms on the Siegel upper half space.
+Explicitly, the Siegel uper half space is $\mathscr H \cong \bc^n/\Lambda$ and siegel modular forms are functions on $Sp_{2g} \backslash \mathscr H.$ Then, modular functions are differentials invariant under the action of $Sp_{2g}$.
+In the case that $\Gamma \backslash \mathscr H$.
+
+Example: the Siegel 2-upper half plane $\bc^2/\Lambda$ Note that $\bc^2/\Lambda$ is algebraic if and only if there exists a hermitial form on $\Lambda$.
+Then, $Sp_{2g}$ acts on algebraic lattices.
+The quotient by this gives you the space of abelian varieties.
+This might be an open subset of projective space, according to David, 65$\%$.
 
@@
 $$\begin{tikzcd}
-0 \ar r & \ker \chi \ar r & \ker \phi \ar r & \ker \psi \ar r & 0
-\end{tikzcd}.$$
+0 \ar r & \ker \chi \ar r & \ker \phi \ar r & \ker \psi \ar r & 0.
+\end{tikzcd}$$
 To see this, note that the left map is an inclusion because $\phi = \chi \circ \psi$.
@@
 \label{align:pm-span}
-\sum_{i=0}^{n} c_i \cdot \bida_i \cdot f_i = 0 & \text{ and } &c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=0}^{n} c_i \cdot \bida_i \cdot f_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 \noindent
-\todo{the above ``and'' needs to be placed better}
 form a spanning set for $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
@@
 \label{align:pm-basis}
-c_i = -\lfloor d\alpha_i \rfloor & \text{ for } & i > m
+c_i = -\lfloor d\alpha_i \rfloor && \text{ for } && i > m
 \end{align}
@@
 \end{proof}
+
 \todo{the following bound is the generation bound beginning from evan's paper}
@@
 \[
-	\sigma = \sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in T_+(D) \atop
+	\sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in T_+(D) \atop
 	j \in T_-(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
@@
 \begin{equation}\label{eqn:relations-psi}
-	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{i}}
+	(y_j - \beta_j)\prod_{i=1}^n {y_i}^{c_{i}}
 \end{equation}
@@
 \[
-	\{e_i \mbox{ if } i\in S\} \cup \{e_{i,j}: j\in S_- \mbox{ if } i \in S_+\} \cup \{e_{j,i}: j\in S_+ \mbox{ if } i \in S_-\}.
+	\{e_i \mbox{ if } i\in S\} \cup \{e_{i,j}: j\in S_- \mbox{ if } i \in S_+\} \cup \{e_{j,i}: j\in S_+ \mbox{ if } i \in S_-\}
 \]
-
-Let $M$ be the set of monomials of $\beta_j$.  Then for $\mu\in M$, the corresponding lattice point is of the form
+given by lattice point $(d_E, w_1, \ldots, w_n)$ with $w_i = 1$.  These conditions imply that 
 \[
-	E_\mu + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k}
-\]
-where $E_\mu$ is a $\mathbb{R}_{\ge 0}$-combination of elements in
-\begin{align*}
-			& \{e_j : j\in T_= \cap \{1, 2, 3, 4\}\} \\
-	\cup \; 	& \{e_{j, k}: j\in T_= \cap \{1, 2, 3, 4\}, k\in T_-\}\\
-	\cup \; 	& \{e_{k,j}: k\in T_+, j\in T_- \cap \{1, 2, 3, 4\}\}.
-\end{align*}
-
-Let $F\in R_D$ correspond to $E + \sum_{k\in T_=} (r_k) e_k + \sum_{h\in T_+ \atop k\in T_-} (r_{h,k}) e_{h,k}$ where $(r)$ signifies the fractional part of $r$.
-Similarly, let $F_\mu \in R_D$ correspond to $E_\mu + \sum_{h\in T_+ \atop k\in T_-} (r_{h,k}) e_{h,k}$.
-Then $F - \sum_{\mu\in M} F_\mu = 0$ gives us a relation in degree at most
-\[
-	\sigma + \deg(F),
-\]
-which generates $(z_i - \beta_i) \prod_{i=1}^n y_i^{c_i}$
-We can bound $\deg(F)$ by
-\[
-	\deg(F) \le \left\{ \begin{split}  \ell_i \gcd(\bida_i, \bidb_i) \mbox{ if } i \in S_= 
+	d_E \le \left\{ \begin{split}  \ell_i \gcd(\bida_i, \bidb_i) \mbox{ if } i \in S_= 
 			\\ \max_{j\in S_-}(\ell_{i,j} (\bida_i \bidb_
@@
 \]
-Therefore, $\ker(\psi)$ is generated in degree at most
+
+Let $M$ be the set of monomials of $\beta_j$.  Then for $m\in M$, the corresponding lattice point is of the form
 \[
-	\tau = \sigma
-	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+	E_m + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k}
+\]
+where $E_m$ is a $\mathbb{R}_{\ge 0}$ combination of elements in
+\[
+	\{e_j : j\in T_= \cap \{1, 2, 3, 4\}\} \cup \{e_{j, k}: j\in T_= \cap \{1, 2, 3, 4\}, k\in T_-\} \cup \{e_{k,j}: k\in T_+, j\in T_- \cap \{1, 2, 3, 4\}\}.
 \]

### 2015-07-13 surfaces-write-up/surface-write-up.tex
edits to section 5 and 4?

--- 2015-07-13 surfaces-write-up/surface-write-up.tex
@@
 \newcommand\hirz{\mathbb{F}}
-\newcommand\mss{\mathscr{S}}
 
@@
 Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$.
-Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D, x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
+Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
 Then, define
 \begin{align*}
-	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{} \bidb_i c_i. \rangle 
+	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
 \end{align*}
-In this case, we have a factorization of $\phi$ given by maps $\chi, \psi$ defined by
+In this case, we can factor $\phi$ through map;s $\chi, \psi$ defined by
 \todo{Make this have mapsto on bottom}
@@
 
-\begin{defn}
-\label{defn:vec-sum}
-For $\vec{v} \in \br^n$, denote $\deg \vec{v} := \sum_{i = 0}
-^n v_i$ (i.e. the taxicab metric).
-Let $\mss_i := \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
-\sum_{i = 0} ^{m + 1} v_i = c_i\}$ be the set of $\bz_{\geq 0}
-^{m + 1}$-vectors with sum of components equal to $c_i$.
-\end{defn}
-
-\begin{defn}
-\label{defn:vec-order}
-Let $\vec{v}, \vec{w} \in \br^n$ be two vectors. Let $i$
-be the right-most coordinate such that $v_i$ is nonzero
-and $j$ be the left-most coordinate such that $w_j$ is
-nonzero. Define $\vec{v} \prec \vec{w}$ if $i \leq j$.
-\end{defn}
-
 \begin{thm}
@@
 \[
-	0 = \frac{c_0}{d_0} <
+	\left\lfloor \frac{p}{q} \right\rfloor = \frac{c_0}{d_0} <
 	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{p}{q}
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
+{{m + i} \choose {i}}$ generators $F_{\vec{v}}^{d_i} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has $z$
-many \todo{how many?} relations of the following two types.
-
-For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
-\vec{w} \in \mss_j$, there is a relation of the form either
-\begin{flalign*}
-	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- \prod_{\vec{y} \in \mss_{k_{i, j}}} (F_{k_{i, j}}^{\vec{y}})
-	^{g_{\vec{y}}} &(i < k_{i, j} < j) \\
-	\text{or} \\
-	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- \prod_{\substack{\vec{y} \in \mss_{k_{i, j}} \\ \vec{z} \in
-	\mss_{k_{i, j} + 1}}} (F_{k_{i, j}}^{\vec{y}})^{g_{\vec{y}}} \;
-	(F_{k_{i, j} + 1}^{\vec{z}})^{h_{\vec{z}}}
-	&(i < k_{i, j} < k_{i, j} + 1 < j).
-\end{flalign*}
-
-Furthermore, there are the relations for each $(i, j)$ with
-$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
-\mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
-~\ref{defn:vec-order}) of the form 
-\begin{align*}
-	&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- F_i^{\vec{y}} F_j^{\vec{w}} \\
-\end{align*}
+such that $\sum_{j = 0}^{m} v_j = c_i$ and $z$ \todo{how many?}
+relations of the form
+\[
+	G_{d_i, d_j}^{\vec{v}, \vec{w}} = F_{d_i}^{\vec{v}} F_{d_j}^{\vec{w}}
+	- (F_{d_k}^{\vec{y}})^{g_{i, j}} (F_{d_\ell}^{\vec{z}})^{g_{i, j}}
+\]
 
 \noindent
-where $\vec{y} \in \mss_i$ and $\vec{w} \in \mss_j$ are the unique
-vectors such that $\vec{y} \prec \vec{w}$.
+when $d_i + d_j = d_k + d_\ell$ and $\vec{v} + \vec{w} = \vec{y} +
+\vec{z}$.
 \end{thm}
@@
 \begin{proof}
-We know $\left\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor
-\frac{p}{q} \right\rfloor \right\}$ are minimal generators in
-degree $1$. Now let $i > 0$. Suppose $F_i^{\vec{v}}$ were not
-minimal for some $\vec{v} \in \mss_i$. Then $F_i^{\vec{v}} =
-F_{s}^{\vec{w}} F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and
-$\vec{w}, \vec{z} \in \bz_{ \geq 0}^{m + 1}$. In particular, we see
-that 
+We know $\left\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor \frac{p}{q}
+\right\rfloor \right\}$ are minimal generators in degree $1$. Now let $i >
+0$. If $F_{d_i}^{\vec{v}}$ were not minimal for some $\vec{v}$ such
+that $\deg \vec{v} = c_i$, then $F_{d_i}^{\vec{v}} = F_{s}^{\vec{w}}
+F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and $\vec{w}, \vec{z} \in
+\bz_{\geq 0}^{m + 1}$. In particular, we see that 
 \begin{align*}
@@
 $\vec{x}_i := (d_i, c_i) \in \bz^2$. Consequently, if $(\beta,
-\gamma) = \ell_1 (d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for
-$\ell_1, \ell_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta}
-x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
+\gamma) = h _1 (d_i, c_i) + h_2 (d_{i + 1}, c_{i + 1})$ for $h_1,
+h_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta} x^{\vec{v}}}
+{x_k^{ \gamma}} \in R_D$ is expressible as
 \begin{align*}
-	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}
-	x^{\vec{w}}} {x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}
-	x^{\vec{z}}} {x_k^{c_{i + 1}}}\right)^{\ell_2}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = (\frac{u^{d_i} x^{\vec{w}}}
+	{x_k^{c_i}})^{h_1} (\frac{u^{d_{i + 1}} x^{\vec{z}}} {x_k^{c_{i + 1}}})^{h_2}
 \end{align*}
@@
 \noindent
-for some $\vec{w} \in \mss_i, \vec{z} \in \mss_{i + 1}$. But these
-are precisely powers of two generators of the form $F_i^{\vec{w}}$
-and $F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.
+for some $\vec{w}, \vec{z} \in \bz_{\geq 0}^{m + 1}$ such that $\deg
+\vec{w} = c_i, \deg \vec{z} = c_{i + 1}$. But these are precisely
+powers of two generators of the form $F_{d_i}^{\vec{w}}$ and
+$F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.
 
@@
 \todo{The example above needs to be changed because $x_0^2$ can be replaced by $2x_0$}
+
+\begin{lem}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^n$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$.  
+\end{lem}
 
@@
 above, satisfying the respective conditions.
-$E$ satisfies the conditions of proposition \todo{cite earlier 
-proposition}, so by applying that proposition $R_D$ is generated in 
+$E$ satisfies the conditions of proposition \ref{prop:cone-generation}, so by applying that proposition $R_D$ is generated in 
 degree at most

### 2015-07-13 surfaces-write-up/surface-write-up.tex

--- 2015-07-13 surfaces-write-up/surface-write-up.tex
@@
 
+\begin{lem}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^n$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$.  
+\end{lem}
+
 \section{Canonical Rings on Hirzebruch surfaces}

### 2015-07-13 surfaces-write-up/surface-write-up.tex
add canonical form snippet
added P^n lemma statement 4.7
response to comments on general lemmas

@@
 \end{align*}
-Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\pdeg^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
+Let $e_1, \ldots, e_t \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_t$.
 Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\pdeg_i$.
-Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{r}\pdeg_i$ and $w_1,\ldots, w_r \in \bz$.
+Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,\ldots, w_t \in \bz$.
 
@@
 \begin{proof}
-\todo{define $\pdeg$, $\bida$, and $\bidb$}
-By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{r} \bida_i e_i$ with $\bida_i \in \br$.
-Let $\{a\} := a - \lfloor a \rfloor$ denote the fractional part of $a$.
-Let $\lambda = \sum_{i=1}^{r}\{\bida_i\}$.
-Hence, we can write $\sigma = \lambda + \sum_{i=1}^{r}\lfloor \bida_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_r$, which all have first coordinate less than $\sum_{i=1}^{r}\pdeg_i$.
-Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{r}\pdeg_i$.
+\todo{define $\pdeg$, $\bida$, and $\bidb$ Aaron: $\pdeg$ was defined in the lemma statement. The $a_i$ were just real numbers, not bidegrees. I'll change the letter.}
+By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{t} r_i e_i$ with $r_i \in \br$.
+Let $\{r\} := r - \lfloor r \rfloor$ denote the fractional part of $r$.
+Let $\lambda = \sum_{i=1}^{t}\{r_i\}$.
+Hence, we can write $\sigma = \lambda + \sum_{i=1}^{t}\lfloor r_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_t$, which all have first coordinate less than $\sum_{i=1}^{t}r_i$.
+Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{t}r_i$.
 \end{proof}
@@
 \begin{proof}
-\todo{define $\bida$ and $\bidb$}
+\todo{define $\bida$ and $\bidb$ Do we have to do this? In the lemma statement I said we were retaining the notation of Lemma ~\ref{lem:composite-map}}
 Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
@@
 \todo{relations}
+Canonical form of 
+\[
+	\prod_{\substack{0 \leq i \leq m + 1 \\ \vec{y}
+	\in \mss_i}} (F_i^{\vec{y}})^{g_{\vec{y}}}
+\]
+
+\noindent
+where the indices with
+some nonzero $g_{\vec{y}}$ are consecutive.
 \end{proof}
@@
 \begin{lem}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^n$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$.  
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^n$.
+Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$.
+Then $R_D$ is generated in degree at most    and relations in degree at most  .
+\todo{insert numbers}
 \end{lem}

### 2015-07-14 surfaces-write-up/surface-write-up.tex
add beamer comment/todo, remove a surface todo

@@
 \begin{proof}
-\todo{define $\bida$ and $\bidb$ Do we have to do this? In the lemma statement I said we were retaining the notation of Lemma ~\ref{lem:composite-map}}
 Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.

### 2015-07-14 curves-write-up/spin-cring.tex
curves: in cong ex, re-cite thm 9.3.1
fixed jorge's name

@@
 If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$.
-This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4]{vzb:stacky}.
+This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4 and Theorem 9.3.1]{vzb:stacky}.
 Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.
@@
 providing a great environment for mathematical learning and
-collaboration. We thank Jorge Sentieiro Neves for pointing out the
+collaboration. We thank Jorge Neves for pointing out the
 bounds given by Miles Reid's work on the maximal degrees of minimal

### 2015-07-14 curves-write-up/spin-cring.tex
edited shou-wu's easy comments

@@
 \label{defn:h0-stacky}
-Recall the standard notation 
-$$\sco(D) := \{f \in \Bk(X)^\times : \di f + D \geq 0 \}.$$
+Recall the standard notation for the line bundle $\sco(D)$ on an integral normal scheme $X$ associated to a divisor $D \in \di X$:
+$$\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \}.$$
 Let $\sx$ be a stacky curve with coarse space $X$.
@@
 \label{eg:base-1-0}
-Let $(\sx',0, \halfcan')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$.
+Let $(\sx',0, \halfcan')$ be a log spin curve of genus $g = 1,$ with $\halfcan' = 0$.
 Counting dimensions, we see $h^0(\sx, k\halfcan')=1$ for all $k \in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
@@
 \label{eg:adding-point}
-Let $\sx$ be a stacky curve with coarse space $X$ and signature $(0
-; 3; 3)$. Let $P_1$ denote the lone stacky point which has stabilizer
+Let $(\sx,3 \cdot \infty, L)$ be a stacky curve with coarse space $X$ and signature 
+$(0; 3; 3)$. Let $P_1$ denote the lone stacky point which has stabilizer
 order $3$ and suppose $\infty$ is a fixed closed point of $X$ that is
@@
 
-We will deduce the structure of the log spin canonical ring $R_L$
+Recall the notation $L_X = \lfloor L \rfloor \in \di X$. We will deduce the structure of the log spin canonical ring $R_L$
 from the structure of the spin canonical ring $R_{L_X} := R(X, 3

### 2015-07-14 surfaces-write-up/surface-write-up.tex
removed stupid ;
what? I made changes since the last push?

--- 2015-07-13 surfaces-write-up/surface-write-up.tex
@@
 \end{align*}
-Let $e_1, \ldots, e_t \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_t$.
+Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
 Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\pdeg_i$.
@@
 \begin{lem}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^n$.
-Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$.
-Then $R_D$ is generated in degree at most    and relations in degree at most  .
-\todo{insert numbers}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.
+Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$.
+Then $R_D$ is generated in degree at most $\sum_{i=1}^n \ell_i a_i$.
+% and relations in degree at most  .\todo{insert numbers}
 \end{lem}
+\begin{proof}
+Let 
+\begin{align*}
+	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
+\end{align*}
+We note that $\Sigma$ has extremal rays given by the lattice points $e_i$ corresponding to
+\[
+	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}
+\]
+for each $i\in \{1, \ldots n\}$.  Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degree less than
+\[
+	\sum_{i=1}^n \ell_i a_i.
+\]
+\end{proof}
 

### 2015-07-14 surfaces-write-up/surface-write-up.tex

@@
 \end{align*}
-In this case, we can factor $\phi$ through map;s $\chi, \psi$ defined by
+In this case, we can factor $\phi$ through maps $\chi, \psi$ defined by
 \todo{Make this have mapsto on bottom}

### 2015-07-14 surfaces-write-up/surface-write-up.tex
manually undo peter's silly push

@@
 \end{align*}
-Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.
-Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\pdeg_i$.
-Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,\ldots, w_t \in \bz$.
+
+\noindent
+Let $e_1, \ldots, e_t \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i,
+\ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$,
+meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of
+$e_1, \ldots, e_t$.  Then, as a semigroup, $\Sigma$ is generated by
+elements whose first coordinate is less than $\sum_{i = 1}^{n} \pdeg_i$
+. Furthermore, every element $\sigma \in \Sigma$ can be written in
+a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with the first
+coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,
+\ldots, w_t \in \bz$.
 

### 2015-07-14 surfaces-write-up/surface-write-up.tex
add Shou-Wu to acknowledgements

--- 2015-07-14 surfaces-write-up/surface-write-up.tex
@@
 \DeclareMathOperator{\spec}{Spec}
+\DeclareMathOperator{\Te}{T_=}
+\DeclareMathOperator{\Tp}{T_+}
+\DeclareMathOperator{\Tm}{T_-}
 %\captionsetup[table]{belowskip = 4pt}
@@
 
-\begin{lem}
+\begin{lem} \label{P-m-generators}
 Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.
@@
 
+\todo{Discussion of factoring $\phi$ through $\psi$ and $\chi$}
+
+\begin{lem}\label{P-m-relations-psi}
+$\ker(\psi)$ is generated in degree at most \todo{insert number}.
+\end{lem}
+\begin{proof}
+We first claim that $\psi$ has a relation of the form
+\begin{equation}\label{eqn:relations-psi}
+	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{i}}
+\end{equation}
+
+\noindent
+for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
+^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in
+k[z_1, \ldots, y_3]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida)$.
+
+To find such a $\beta$, we simply write $\epsilon_j$ as a 
+polynomial in $\epsilon_1, \ldots \epsilon _3$. Furthermore, these
+generate all relations, since they allow us to reduce any $\prod_{i =
+1}^n \epsilon_i^{r_i}$ to a canonical form. \todo{add reference to
+earlier description of canonical form.}
+\end{proof}
+
 \section{Canonical Rings on Hirzebruch surfaces}
@@
 \begin{equation}\label{eqn:define-T=(D)}
-	T_=(D) = \left\{i \in \{1, \ldots, m\}: \bida_i \sum_{k=1}^m \bidb_k 
+	\Te(D) = \left\{i \in \{1, \ldots, m\}: \bida_i \sum_{k=1}^m \bidb_k 
 \alpha_k = \bidb_i \sum_{k=1}^m \bida_k \alpha_k \right\},
@@
 \begin{equation}\label{eqn:define-T+(D)}
-	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} 
+	\Tp(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} 
 \bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^m \alpha_k \bida_k 
@@
 \begin{equation}\label{eqn:define-T-(D)}
-	T_-(D) = \left\{ j \in \{1, \ldots, m\}: \bida_j \sum_{k=1}^m \alpha_
+	\Tm(D) = \left\{ j \in \{1, \ldots, m\}: \bida_j \sum_{k=1}^m \alpha_
 k \bidb_k < \bidb_j \sum_{k=1}^m \alpha_k \bida_k s \right\}.
@@
 \[
-	\sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
+	\sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{i\in \Tp(D) \atop j\in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
 \]
@@
 
-For $i \in T_=(D)$
+For $i \in \Te(D)$
 define
@@
 
-For $i \in T_+(D)$ and $j \in T_-(D)$, define
+For $i \in \Tp(D)$ and $j \in \Tm(D)$, define
 \[
@@
 \[
-	\sigma = \sum_{i\in T_=(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in T_+(D) \atop
-	j \in T_-(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in \Tp(D) \atop
+	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
 \]
@@
 \begin{lem}
-$\ker(\psi)$ is generated in degree at most \todo{insert number}.
+$\ker(\psi)$ is generated in degree at most
+\[
+	\tau = \sigma
+	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+\]
 \end{lem}
@@
 ^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in
-k[y_1, \ldots, y_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida_j,
+k[z_1, \ldots, z_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida_j,
 \bidb_j)$.
@@
 \[
-	E + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k},
+	E + \sum_{k\in \Te} r_k e_k + \sum_{h\in \Tp \atop k\in \Tm} r_{h,k} e_{h,k},
 \] 
@@
 \[
-	E_\mu + \sum_{k\in T_=} r_k e_k + \sum_{h\in T_+ \atop k\in T_-} r_{h,k} e_{h,k}
+	E_\mu + \sum_{k\in \Te} r_k e_k + \sum_{h\in \Tp \atop k\in \Tm} r_{h,k} e_{h,k}
 \]
@@
 \begin{align*}
-			& \{e_j : j\in T_= \cap \{1, 2, 3, 4\}\} \\
-	\cup \; 	& \{e_{j, k}: j\in T_= \cap \{1, 2, 3, 4\}, k\in T_-\}\\
-	\cup \; 	& \{e_{k,j}: k\in T_+, j\in T_- \cap \{1, 2, 3, 4\}\}.
+			& \{e_j : j\in \Te \cap \{1, 2, 3, 4\}\} \\
+	\cup \; 	& \{e_{j, k}: j\in \Te \cap \{1, 2, 3, 4\}, k\in \Tm\}\\
+	\cup \; 	& \{e_{k,j}: k\in \Tp, j\in \Tm \cap \{1, 2, 3, 4\}\}.
 \end{align*}
 
-Let $F\in R_D$ correspond to $E + \sum_{k\in T_=} (r_k) e_k + \sum_{h\in T_+ \atop k\in T_-} (r_{h,k}) e_{h,k}$ where $(r)$ signifies the fractional part of $r$.
-Similarly, let $F_\mu \in R_D$ correspond to $E_\mu + \sum_{h\in T_+ \atop k\in T_-} (r_{h,k}) e_{h,k}$.
+Let $F\in R_D$ correspond to $E + \sum_{k\in \Te} (r_k) e_k + \sum_{h\in \Tp \atop k\in \Tm} (r_{h,k}) e_{h,k}$ where $(r)$ signifies the fractional part of $r$.
+Similarly, let $F_\mu \in R_D$ correspond to $E_\mu + \sum_{h\in \Tp \atop k\in \Tm} (r_{h,k}) e_{h,k}$.
 Then $F - \sum_{\mu\in M} F_\mu = 0$ gives us a relation in degree at most

### 2015-07-14 curves-write-up/spin-cring.tex
add Shou-Wu to acknowledgements
move admissibility and give appropriate rewrite

@@
 
-\ssec{Admissibility}
-Here, we define a notion of admissibility that is quite similar to the admissibility defined by Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}.
-Our notion is an adaptation the case of log spin canonical divisors.
-
-One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
-we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.
-
-\begin{defn}
-\label{def:order-sup}
-Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
-zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
-
-\begin{defn}
-\label{defn:admissible}
-Let $(\sx', \Delta, L')$ be a log spin
-curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
-\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
-
-\[
-\chi_J(i) = \begin{cases}
-	1, &\text{ if }i \in J\\
-	0, &\text{ otherwise. } 
-\end{cases}
-\]
-
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan', J)$
-to be {\bf admissible} if $R'$ admits a presentation
-\begin{align*}
-	R' \cong \left( \Bk[x_1, \ldots, x_m] \otimes \Bk[y_{i, e_i'}]_{i \in J} \right)/I'
-\end{align*}
-
-\noindent
-with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
-three conditions hold:
-\begin{enumerate}
-	\item[\customlabel{custom:Ad-i}{(Ad-i)}] First, 
-		\begin{align*}
-		\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
-			= \frac{e_i'- 1}{2}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-ii}{(Ad-ii)}] Second, every generator $z 
-		\in \{x_1, \ldots, x_m\} \cup \{y_{j, e_i'}: j\in J - \{i\} \}$ 
-		satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-iii}{(Ad-iii)}] Third, we have
-		\begin{align*}
-			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{k \geq 0} \# S_{\sigma, J}(i, k)
-		\end{align*}
-		where
-		\begin{align*}
-			S_{\sigma, J}(i, k) := \{j \in J : j \neq i \text{ and } e_j'+2k
-			\mid e_i - e_j'\}.
-		\end{align*}
-\end{enumerate}
-\end{defn}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%% Examples %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Now, we check the admissibility of $(\sx', L' ,J),$ where $J = \{2, 3\}$. By relabelling the
-variables if necessary, we can assume that $x_{7, 1}$ corresponds
-to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
-correspond to the generator with maximal pole order at $P_3$. Use
-the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
-$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
-\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
-pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3k}{7}$
-in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
-generators lying below the line as seen in Figure ~\ref{fig:377}
-(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
-(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
-and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
-$x_{7, 2}$ respectively).
-
-\begin{figure}[H]
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
-\label{fig:377}
-\end{figure}
-
-Also note that $e_j' + 2k = 7 + 2k \nmid 2 = e_i - e_j'$ for all
-$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $k \geq
-0$. Thus, $s_{\sigma, J}(i, k) = \emptyset$ for each $i \in J$.
-Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
-$(\sigma, \sx', J)$ is admissible.
+By relabelling the variables if necessary, we can assume that $x_{7
+, 1}$ corresponds to the generator with maximal pole order at $P_2$ 
+and $x_{7, 2}$ correspond to the generator with maximal pole order 
+at $P_3$.
 
@@
 degree $2e = 14$, as desired.
+
+We will come back to this example when checking a condition called
+admissibility that we will need later. \todo{ref}
 \end{example}
@@
 \ldots, e_\ell', e_{\ell + 1}' \ldots, e_r';\delta)$ with $e_{\ell + 1}' =
-\cdots = e_r'$ satisfying certain admissibility (cf. Definition
+\cdots = e_r'$ satisfying an admissibility condition (cf. Definition
 ~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for
@@
 
-The following lemma will slightly strengthen condition \ref{custom:Ad-ii} from Definition ~\ref{defn:admissible}.
-This improvement is crucial in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.
+First, we present a definition of admissibility.
+Here, we define a notion of admissibility that is quite similar to the admissibility defined by Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}.
+Our notion is an adaptation the case of log spin canonical divisors.
+
+One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
+we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
+We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.
+
+\begin{defn}
+\label{def:order-sup}
+Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
+zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
+
+\begin{defn}
+\label{defn:admissible}
+Let $(\sx', \Delta, L')$ be a log spin
+curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
+\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
+
+\[
+\chi_J(i) = \begin{cases}
+	1, &\text{ if }i \in J\\
+	0, &\text{ otherwise. } 
+\end{cases}
+\]
+
+Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan', J)$
+to be {\bf admissible} if $R'$ admits a presentation
+\begin{align*}
+	R' \cong \left( \Bk[x_1, \ldots, x_m] \otimes \Bk[y_{i, e_i'}]_{i \in J} \right)/I'
+\end{align*}
+
+\noindent
+with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
+three conditions hold:
+\begin{enumerate}
+	\item[\customlabel{custom:Ad-i}{(Ad-i)}] First, 
+		\begin{align*}
+		\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
+			= \frac{e_i'- 1}{2}.
+		\end{align*}
+	\item[\customlabel{custom:Ad-ii}{(Ad-ii)}] Second, every generator $z 
+		\in \{x_1, \ldots, x_m\} \cup \{y_{j, e_i'}: j\in J - \{i\} \}$ 
+		satisfies
+		\begin{align*}
+			\frac{-\ord_{Q_i}^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
+		\end{align*}
+	\item[\customlabel{custom:Ad-iii}{(Ad-iii)}] Third, we have
+		\begin{align*}
+			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{k \geq 0} \# S_{\sigma, J}(i, k)
+		\end{align*}
+		where
+		\begin{align*}
+			S_{\sigma, J}(i, k) := \{j \in J : j \neq i \text{ and } e_j'+2k
+			\mid e_i - e_j'\}.
+		\end{align*}
+\end{enumerate}
+\end{defn}
+
+\begin{example}
+\label{eg:base-0-377-adm}
+Here, we explicitly check the admissibility of the example from
+Example ~\ref{eg:base-0-377}. Recall that the setup is that
+$(\sx', 0, \halfcan'$ is a log spin curve with signature $\sigma := (0; 3, 7, 7; 0)$
+and $\halfcan' \sim -\infty + \frac{1}{3}P_1 + \frac{3}{7}P_2 + \frac{3}{7}P_3$,
+where $P_1, P_2$, and $P_3$ are distinct points. We demonstrate
+that $(\sx', \halfcan', J)$ is admissible where $J = \{2, 3\}$.
+
+As shown in Example ~\ref{eg:base-0-377}, the log spin canonical
+rings corresponding to this case have a presentation
+$\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
+$x_{i, j} \in H^0(\sx', i \halfcan')$. Furthermore, we were
+able to chose generators such that $x_{7, 1}$ has maximal pole
+order at $P_2$ and $x_{7, 2}$ has maximal pole order at $P_3$.
+
+Use the presentation given above with $y _{2, e_2'} :=
+x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
+We see that $(\sx', \halfcan', J)$ immediately satisfies
+\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
+pole orders of the generators such that $y_{i, e_i'}$ is the only
+generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3k}{7}$
+in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
+generators lying below the line as seen in Figure ~\ref{fig:377}
+(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
+(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
+and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
+$x_{7, 2}$ respectively).
+
+\begin{figure}[H]
+\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\label{fig:377}
+\end{figure}
+
+Also note that $e_j' + 2k = 7 + 2k \nmid 2 = e_i - e_j'$ for all
+$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $k \geq
+0$. Thus, $s_{\sigma, J}(i, k) = \emptyset$ for each $i \in J$.
+Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
+\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
+\frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
+$(\sigma, \sx', J)$ is admissible.
+\end{example}
+
+The following lemma will slightly strengthen condition
+\ref{custom:Ad-ii} from Definition ~\ref{defn:admissible}.
+This improvement is crucial in the proof of part (c) of Lemma
+~\ref{lem:raise-stacky-order}.
 
@@
 \begin{proof}
-Recall that Case (b) is proven in Example ~\ref{eg:base-0-377}. For
+Recall that the generator and relation degree bounds for Case (b)
+are proven in Example ~\ref{eg:base-0-377} and the admissibility
+condition is checked in Example ~\ref{eg:base-0-377-adm}. For
 the remaining cases, we follow a similar method to find a
@@
 elements of degree at most $e$ with relations in degree at most $2e$
-for each case as described in the Table ~\ref{table:g-0-base-cases-degrees}.
+for each case as described in the Table
+~\ref{table:g-0-base-cases-degrees}.
 \begin{table}
@@
 verify these is similar to that in Example
-~\ref{eg:base-0-377}.
+~\ref{eg:base-0-377} and Example ~\ref{eg:base-0-377-adm}.
 
@@
 generators and relations of spin canonical rings in high genera. We
-also thank Brian Conrad and John Voight for helpful comments on
+also thank Brian Conrad, John Voight, and Shou-Wu Zhang for helpful comments on
 this paper. The first author would also like to mention Joseph

### 2015-07-14 curves-write-up/spin-cring.tex
fix some halfcans, added an i.e. for L_X

@@
 
-Recall the notation $L_X = \lfloor L \rfloor \in \di X$. We will deduce the structure of the log spin canonical ring $R_L$
-from the structure of the spin canonical ring $R_{L_X} := R(X, 3
-\cdot \infty, L_X)$. This technique will later be generalized in Lemma ~\ref{lem:sat-1}.
-
-Note that $R_{L_X} \cong \Bk[x_1, x_2]$ where $\deg x_1 = \deg x_2 = 1.
+Recall the notation $\halfcan_X = \lfloor L \rfloor \in \di X$
+(i.e.~ the divisor without any stacky points). We will deduce the
+structure of the log spin canonical ring $R_\halfcan$ from the
+structure of the spin canonical ring $R_{\halfcan_X} := R(X, 3 \cdot
+ \infty, \halfcan_X)$. This technique will later be generalized in
+Lemma ~\ref{lem:sat-1}.
+
+Note that $R_{\halfcan_X} \cong \Bk[x_1, x_2]$ where $\deg x_1 = \deg x_2 = 1.
 $ To see this, observe that we will need two generators in degree $1$
-because $h^0(X, L_X) = 2$ by Riemann--Roch. Because $L_X$ is very 
-ample, we have that $R_{L_X}$ is generated in degree 1. To
-conclude, note that $R_{L_X}$ does not have any relations. If there
-exists some relation, then $\dim \proj R_{L_X} < 1$. This would
-contradict the fact that $L_X$ is very ample. Thus, $\proj R_{L_X}
+because $h^0(X, \halfcan_X) = 2$ by Riemann--Roch. Because $\halfcan_X$ is very 
+ample, we have that $R_{\halfcan_X}$ is generated in degree 1. To
+conclude, note that $R_{\halfcan_X}$ does not have any relations. If there
+exists some relation, then $\dim \proj R_{\halfcan_X} < 1$. This would
+contradict the fact that $\halfcan_X$ is very ample. Thus, $\proj R_{\halfcan_X}
 \cong X$ which has dimension 1.
 
-Next, we construct generators and relations for $R_L$ using those
-of $R_{L_X}$. Note that we have a natural inclusion $\iota: R_{L_X}
-\hookrightarrow R_L$ induced by the inclusions $H^0(\sx, k\halfcan_X)
+Next, we construct generators and relations for $R_\halfcan$ using those
+of $R_{\halfcan_X}$. Note that we have a natural inclusion $\iota: R_{\halfcan_X}
+\hookrightarrow R_\halfcan$ induced by the inclusions $H^0(\sx, k\halfcan_X)
 \hookrightarrow H^0(\sx, k\halfcan)$ for each $k \geq 0$. By Riemann Roch,
-we see there is some element $y_{1, 3} \in (R_L)_3$ with $\ord_{P_1}
+we see there is some element $y_{1, 3} \in (R_\halfcan)_3$ with $\ord_{P_1}
 (y_{1, 3}) = -1$, not in the image of the inclusion $\iota$. We
@@
 \begin{align*}
-	R_L \cong \Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3}
+	R_\halfcan \cong \Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3}
 	+ f(x_1,x_2))
@@
 
-First, note that $x_1, x_2, y_{1, 3}$ generate all of $R_L$ from the
+First, note that $x_1, x_2, y_{1, 3}$ generate all of $R_\halfcan$ from the
 Generalized Max Noether Theorem for genus zero curves from Voight
@@
 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2) = 0$ must exist because $h^0(\sx,
-4L) - h^0(\sx, 4L_X) = 1,$ but $x_1 y_{1, 3}$ and $x_2 y_{1, 3}$
+4L) - h^0(\sx, 4\halfcan_X) = 1,$ but $x_1 y_{1, 3}$ and $x_2 y_{1, 3}$
 define two linearly independent elements with nontrivial image in
-the 1-dimensional vector space $H^0(\sx, 4L) / H^0(\sx, 4L_X).$ So,
+the 1-dimensional vector space $H^0(\sx, 4L) / H^0(\sx, 4\halfcan_X).$ So,
 we obtain a surjection
@@
 	\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2)) 
-	\rightarrow R_L.
+	\rightarrow R_\halfcan.
 \end{align}
@@
 Let $(\sx', 0, L')$ be a log spin curve of genus 1 with $L' = P -
- Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_L)_2$ be any nonzero element.
+ Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_\halfcan)_2$ be any nonzero element.
 We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
@@
 One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
-we cannot assume that $\{P_i\} \cap \Supp(L_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
+we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
 We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.
@@
 $$\deg a_i =\deg f - \deg x_i -2 \geq 4.$$
-In particular, there exist $\alpha, \beta \in R_L$ so that
+In particular, there exist $\alpha, \beta \in R_\halfcan$ so that
 $$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
@@
 For this remark, we retain the terminology from the proof of Theorem ~\ref{thm:g-high-main}.
-Suppose $e :=  \max(e_1,\ldots, e_r).$ Then, $R_L$ has a generator in degree $e$ when $e \geq 5$ and a relation in degree at least $2e-4$ when $e \geq 7$.
+Suppose $e :=  \max(e_1,\ldots, e_r).$ Then, $R_\halfcan$ has a generator in degree $e$ when $e \geq 5$ and a relation in degree at least $2e-4$ when $e \geq 7$.
 Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively
-applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, we obtain that $R_L$ is minimally generated over $R_{L'}$ by an element in degree $e,$ assuming $e \geq 5$.
+applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, we obtain that $R_\halfcan$ is minimally generated over $R_{L'}$ by an element in degree $e,$ assuming $e \geq 5$.
 Furthermore, if $e \geq 7$ and $e_i = e,$
@@
 Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective.
-We will show it holds for $L_X' + P,$ verifying the inductive step.
+We will show it holds for $\halfcan_X' + P,$ verifying the inductive step.
 There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.
@@
 
-Otherwise, $P$ is a basepoint of $\halfcan_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(L_X') \geq 2$ as $\deg L_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $L_X = L_X'+P$.
+Otherwise, $P$ is a basepoint of $\halfcan_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(\halfcan_X') \geq 2$ as $\deg \halfcan_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $\halfcan_X = \halfcan_X'+P$.
 By induction, the theorem holds for $\halfcan_X$.
@@
 explicit construction of the generators and relations for the log
-spin canonical ring $R_L$. This is similar to the case of genus 1
+spin canonical ring $R_\halfcan$. This is similar to the case of genus 1
 in Remark ~\ref{rem:genus-1-explicit-bound}. Furthermore, there is
@@
 if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$,
-then $R_L$ is generated in weight at most 4. Since $\delta > 0$,
-$L_X$ is effective. Additionally, $R_{L_X}$ is generated in weight 1,
+then $R_\halfcan$ is generated in weight at most 4. Since $\delta > 0$,
+$\halfcan_X$ is effective. Additionally, $R_{\halfcan_X}$ is generated in weight 1,
 and inductive applications of Lemma ~\ref{lem:sat-1} only add
 generators in weights 3 and 4 and relations in weight at most 8.
-Therefore, $R_L$ is generated in weight at most 4 with relations in
+Therefore, $R_\halfcan$ is generated in weight at most 4 with relations in
 weight at most 8. Note that a similar analysis of the proof of
@@
 		\halfcan$ when the genus of $\sx$ is $0$ or $1$.
-When $\sx$ has genus at least 2, Lemmas ~\ref{lem:sat-1} and $\ref{lem:sat-2}$ allow us to explicitly construct a presentation of $R_\halfcan$ from a presentation of $R_{L_X}$ where $X$ is the coarse space $X$.
+When $\sx$ has genus at least 2, Lemmas ~\ref{lem:sat-1} and $\ref{lem:sat-2}$ allow us to explicitly construct a presentation of $R_\halfcan$ from a presentation of $R_{\halfcan_X}$ where $X$ is the coarse space $X$.
 However, obtaining a presentation for $X$ requires nontrivial computation.
@@
 		\begin{rem}\label{rem:reduce-3,6}
-			Note that when $L$ is not effective and $\sx$ has a stacky point, $R_L$ must have a generator in degree 4 with maximal pole order at one of the stacky points.
+			Note that when $L$ is not effective and $\sx$ has a stacky point, $R_\halfcan$ must have a generator in degree 4 with maximal pole order at one of the stacky points.
 Therefore, these bounds cannot in general be reduced further to

### 2015-07-14 curves-write-up/spin-cring.tex
minor curves def edit

@@
 Recall the standard notation for the line bundle $\sco(D)$ on an integral normal scheme $X$ associated to a divisor $D \in \di X$:
-$$\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \}.$$
+\[
+	\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \}.
+\]
+
+\noindent
 Let $\sx$ be a stacky curve with coarse space $X$.

### 2015-07-14 surfaces-write-up/surface-write-up.tex
lemma on generation of ker(psi) for P^m

@@
 Let 
-\begin{align*}
+\begin{align}\label{eqn:Sigma-def}
 	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
-\end{align*}
+\end{align}
 We note that $\Sigma$ has extremal rays given by the lattice points $e_i$ corresponding to
-\[
+\begin{equation}\label{eqn:epilon-def-P-m}
 	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}
-\]
+\end{equation}
 for each $i\in \{1, \ldots n\}$.  Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degree less than
@@
 \begin{lem}\label{P-m-relations-psi}
-$\ker(\psi)$ is generated in degree at most \todo{insert number}.
+$\ker(\psi)$ is generated in degree at most 
+\[
+	\delta_i + \sum_{i=1}^n \ell_i a_i.
+\]
 \end{lem}
@@
 \begin{equation}\label{eqn:relations-psi}
-	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{i}}
+	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{j}}
 \end{equation}
@@
 earlier description of canonical form.}
+
+Now we bound the degree of generation of these relations for a fixed $z_i$.
+We associate $(z_i - \beta_j)\prod_{j=1}^n z_j^{c_j}$ that has degree $d$ with the lattice point $(d, c_1, \ldots, c_n)$.
+Let $\Sigma_i \subseteq \mathbb{R}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
+Then we see $\Sigma_i$ is a translation of $\Sigma$ (see Equation \ref{eqn:Sigma-def}) by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
+
+Therefore, we can write any element of $\Sigma'$ as
+\[
+	\delta_i + \sum_{j=1}^n r_j e_j
+\]
+for $r_j \in \mathbb{R}$ for each $j$.
+
+Whenever some $r_j \ge 1$, we can generate the generation at hand by one of lower degree by factoring out the section $\epsilon_j$ corresponding to the lattice point $e_j$ (see Equation \ref{eqn:epilon-def-P-m}).
+Therefore, we can bound the degree of generation of $\ker(\psi)$ by
+\[
+	\delta_i + \sum_{i=1}^n \ell_i a_i.
+\]
 \end{proof}

### 2015-07-14 curves-write-up/spin-cring.tex
change curves acknowledgments order slightly

@@
 providing a great environment for mathematical learning and
-collaboration. We thank Jorge Neves for pointing out the
-bounds given by Miles Reid's work on the maximal degrees of minimal
-generators and relations of spin canonical rings in high genera. We
-also thank Brian Conrad, John Voight, and Shou-Wu Zhang for helpful comments on
-this paper. The first author would also like to mention Joseph
-Harris and Evan O'Dorney for several enlightening conversations
-related to Petri's Theorem. Finally, we gratefully acknowledge the
-support of the National Science Foundation (grant number DMS-1250467).
-We deeply appreciate all of the support that has made our work
-possible.
+collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
+Zhang for helpful comments on this paper. We also thank Jorge Neves
+for pointing out the bounds given by Miles Reid's work on the
+maximal degrees of minimal generators and relations of spin
+canonical rings in high genera. The first author would also like to
+mention Joseph Harris and Evan O'Dorney for several enlightening
+conversations related to Petri's Theorem. Finally, we gratefully
+acknowledge the support of the National Science Foundation (grant
+number DMS-1250467). We deeply appreciate all of the support that
+has made our work possible.
 

### 2015-07-14 curves-write-up/spin-cring.tex
move eg-1-33 admissibility

@@
 distinct points. In this example, we will exhibit a minimal
-presentation for $R' = R(\sx', 0, \halfcan')$ and show the triple
-$(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
+presentation for $R' = R(\sx', 0, \halfcan')$ and show that $R'$ is
+generated as a $Bk$-algebra in degrees up to $e := \max(5, 3, 7, 7) = 7$
+with relations generated in degrees up to $2e = 14$.
 Notice that $\deg \lfloor k K_{\sx'} \rfloor= -k + \lfloor \frac{k}{3}
@@
 
-We will come back to this example when checking a condition called
-admissibility that we will need later. \todo{ref}
+We will come back to this example in Example ~\ref{eg:base-0-377-adm}
+when checking an admissibility condition that is defined later
+(Definition ~\ref{defn:admissible}).
 \end{example}
@@
 \label{eg:base-1-33}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show
-$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$
-and that $(\sx', \halfcan', \{1,2\})$ is admissible.
+Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show that
+$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$.
 
@@
 
-We next check $(\sx', \halfcan', \{1,2\})$ is admissible.
-We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{custom:Ad-i} holds.
-We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
-Here, by construction
-\[
-\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4
-\end{cases}.
-\]
-Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{k \geq 0}S_{\sigma,J}(i,k) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
+Again, we will come back to this example in Example
+~\ref{eg:base-1-33-adm} to check admissibility.
 \end{example}
@@
 
+Before using this admissibility condition in the lemmas of
+this section, we give a few explicit examples for which admissibility
+holds.
+
 \begin{example}
@@
 where $P_1, P_2$, and $P_3$ are distinct points. We demonstrate
-that $(\sx', \halfcan', J)$ is admissible where $J = \{2, 3\}$.
+that $(\sx', \halfcan', \{2, 3\})$ is admissible.
 
@@
 x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
-We see that $(\sx', \halfcan', J)$ immediately satisfies
-\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
+We see that $(\sx', \halfcan', \{2, 3\})$ immediately satisfies
+\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we
+check \ref{custom:Ad-ii} We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
@@
 \frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
-$(\sigma, \sx', J)$ is admissible.
+$(\sigma, \sx', \{2, 3\})$ is admissible.
+\end{example}
+
+\begin{example}
+\label{eg:base-1-33-adm}
+Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with
+$\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$, as in Example
+~\ref{eg:base-1-33}. Here, we check that $(\sx', \halfcan', \{1,2\})$
+is admissible.
+
+Recall that
+$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$.
+We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
+Hence, \ref{custom:Ad-i} holds.
+We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
+Here, by construction
+\[
+\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
+	0 &\text{ if }z \in \{u, y_3\}\\
+	\frac{1}{4} &\text{ if }z = y_4
+\end{cases}.
+\]
+
+\noindent
+Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
+Finally, to check \ref{custom:Ad-iii}, note that $\max_{k \geq 0}S_{\sigma,J}(i,k) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
 \end{example}
@@
 \begin{proof}
-Recall that the generator and relation degree bounds for Case (b)
+Recall that the generator and relation degree bounds for case (b)
 are proven in Example ~\ref{eg:base-0-377} and the admissibility

### 2015-07-14 surfaces-write-up/surface-write-up.tex
P^m added text between lemmas on bounds

@@
 \begin{align*}
-	\Sigma = \langle u^d y_1^{c_1} \cdots y_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+	\Sigma = \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
 \end{align*}
@@
 \todo{Make this have mapsto on bottom}
-$$\begin{tikzcd}
+\[
+\begin{tikzcd}
 \bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \ar r & u^{d_i}y_1^{c_{i1}} \cdots y_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}
-\end{tikzcd}$$
+x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}
+\end{tikzcd}
+\]
 Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$ is at most the maximum of the minimal degree of generation of $\ker \chi$ and the minimal degree of generation of $\ker \psi$.
@@
 Note that we have an exact sequence
-$$\begin{tikzcd}
+\[
+\begin{tikzcd}
 0 \ar r & \ker \chi \ar r & \ker \phi \ar r & \ker \psi \ar r & 0.
-\end{tikzcd}$$
+\end{tikzcd}
+\]
 To see this, note that the left map is an inclusion because $\phi = \chi \circ \psi$.
@@
 \label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees less than $\sum_{i=1}^{r}d_r-1$.
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees less than $2(\sum_{i=1}^{r}d_r-1)$.
 \end{lem}
@@
 
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 \begin{lem} \label{P-m-generators}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.
-Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$.
-Then $R_D$ is generated in degree at most $\sum_{i=1}^n \ell_i a_i$.
+$R_D$ is generated in degree at most $\sum_{i=1}^n \ell_i a_i$.
 % and relations in degree at most  .\todo{insert numbers}
@@
 
-\todo{Discussion of factoring $\phi$ through $\psi$ and $\chi$}
+Let $x_1, \ldots x_r$ be the generators given by lemma  \ref{P-m-generators}, and $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through 
+\[
+	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+\]
+into
+\[
+\begin{tikzcd}
+\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+\end{tikzcd}
+\]
+
+Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ less than
+\[
+	\sum_{i=1}^n \ell_i a_i.
+\]
+Finally, we calculate the degree of generation of $\psi$:
 
@@
 Whenever some $r_j \ge 1$, we can generate the generation at hand by one of lower degree by factoring out the section $\epsilon_j$ corresponding to the lattice point $e_j$ (see Equation \ref{eqn:epilon-def-P-m}).
-Therefore, we can bound the degree of generation of $\ker(\psi)$ by
+Therefore, we can bound the degree of generation of $\ker(\psi)$ less than
 \[
@@
 \end{proof}
+
+Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma \ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
+\[
+	\max(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i).
+\]
+
+Combining these results, we get the following theorem:
+
+\begin{thm}\label{P-m-generators/relations}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Then $R_D$ is generated in degree at most 
+\[
+	\sum_{i=1}^n \ell_i a_i
+\]
+with relations generated in degree at most
+\[
+	\max(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i).
+\]
+\end{thm}
 

### 2015-07-14 curves-write-up/spin-cring.tex
finish moving/removing admissibility from examples

@@
 In this section, we work out several examples of computing presentations for spin canonical rings.
-In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}.
 In addition to providing intuition for the lemmas of Section ~\ref{sec:induction}, these examples also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
@@
 degree $2e = 14$, as desired.
-
-We will come back to this example in Example ~\ref{eg:base-0-377-adm}
-when checking an admissibility condition that is defined later
-(Definition ~\ref{defn:admissible}).
 \end{example}
@@
 The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
-
-Again, we will come back to this example in Example
-~\ref{eg:base-1-33-adm} to check admissibility.
 \end{example}
@@
 The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
-
-Note that $(\sx', \halfcan', \{1\})$ is admissible, as can be checked in a fashion analogous to the verification in Example ~\ref{eg:base-1-33}.
 \end{example}
@@
 \label{rem:base-0-377}
-Examples ~\ref{eg:base-0-377}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} are used as inductive base cases in the genus 0, genus 1, and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
+Examples ~\ref{eg:base-0-377}, \ref{eg:base-1-33}, and
+\ref{eg:exception-1-5} are used as inductive base cases in the
+genus 0, genus 1, and genus 1 sections respectively (see Tables
+~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
+
+We will come back to Examples ~\ref{eg:base-0-377} and
+\ref{eg:base-1-33} in Examples ~\ref{eg:base-0-377-adm} and
+\ref{eg:base-1-33-adm}, respectively, when checking an
+admissibility condition that will be defined when introducing the
+lemmas used in Subsection ~\ref{ssec:raise-orders} (see Definition
+~\ref{defn:admissible}).
 \end{rem}

### 2015-07-14 surfaces-write-up/surface-write-up.tex
middle of minor changes todos

--- 2015-07-14 surfaces-write-up/surface-write-up.tex
@@
 \ldots, w_t \in \bz$.
-
-\todo{define bidegrees $a_i$ and $b_i$}
 \end{prop}
@@
 \begin{proof}
-\todo{define $\pdeg$, $\bida$, and $\bidb$ Aaron: $\pdeg$ was defined in the lemma statement. The $a_i$ were just real numbers, not bidegrees. I'll change the letter.}
 By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{t} r_i e_i$ with $r_i \in \br$.
@@
 Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
-Then, define
+Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$ Then, define
 \begin{align*}
@@
 
+\begin{eg}
+\label{eg:hyperplane}
+
+\end{eg}
+
 \begin{example}
 \label{eg:radical}
+In this example, we justify the necessity of adding ghost points for the bounds obtained in Lemma ~\ref{P-m-generators}, which are also necessary when the divisors are not all contained in a hyperplanes.
+
  As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$.

### 2015-07-14 surfaces-write-up/surface-write-up.tex
fixed example
edited some more of example
more minor edits to examples, remember to fill out hyperplane example

@@
 \DeclareMathOperator{\Tm}{T_-}
+\DeclareMathOperator{\num}{p}
+\DeclareMathOperator{\den}{q}
 %\captionsetup[table]{belowskip = 4pt}
@@
 
-\begin{eg}
+\begin{example}
 \label{eg:hyperplane}
+Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0), H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$.
+Then, $R_D$ has generators in degree $2$ and $3$ which can be written as $u^2 \frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees less than $5$ the elements of $R_D$ can all be expressed as rational functions in $x_0, x_1$.
+However, in degree $6$, there is the rational function $\frac{x_1^2 x_2}{x_0^3}.$ Since this involves $x_2$, it must be a generator.
 
-\end{eg}
+This example easily generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{d}{s}$
+\end{example}
 
@@
 \[
-	\max(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i).
+	\max \left(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i \right).
 \]

### 2015-07-14 surfaces-write-up/surface-write-up.tex
polished hirzebruch section

--- 2015-07-14 surfaces-write-up/surface-write-up.tex
@@
 \ldots, w_t \in \bz$.
+
+\todo{define bidegrees $a_i$ and $b_i$}
 \end{prop}
@@
 \begin{proof}
+\todo{define $\pdeg$, $\bida$, and $\bidb$ Aaron: $\pdeg$ was defined in the lemma statement. The $a_i$ were just real numbers, not bidegrees. I'll change the letter.}
 By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{t} r_i e_i$ with $r_i \in \br$.
@@
 Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
-Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$ Then, define
+Then, define
 \begin{align*}
@@
 
-\begin{eg}
-\label{eg:hyperplane}
-
-\end{eg}
-
 \begin{example}
 \label{eg:radical}
-In this example, we justify the necessity of adding ghost points for the bounds obtained in Lemma ~\ref{P-m-generators}, which are also necessary when the divisors are not all contained in a hyperplanes.
-
 As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$.
@@
 \section{Canonical Rings on Hirzebruch surfaces}
-Let $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such
+Let $D=\sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(\hirz_
+k)$ for some curve $C_i$ of $\hirz_k$, such
 that $C_1, \ldots, C_4$ are independent curves with bi-degrees $(1,0)
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $C_i = V(f_i)$ where
-$f_i \in \mathscr{O}(\bida_i, \bidb_i)$. Then each $C_i$ corresponds to a
-polynomial $f_i$ where $f_1$ and $f_2$ are independent linear
+$f_i \in \mathscr{O}(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
@@
 \begin{defn}
-Suppose $D = \sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(F_
-k)$. Then define 
+Define 
 \begin{equation}\label{eqn:define-T=(D)}
@@
 
-\begin{lem}
+\begin{lem}\label{Hirzebruch-generators}
 $R_D$ is generated in degree at most
@@
 $E$ satisfies the conditions of proposition \ref{prop:cone-generation}, so by applying that proposition $R_D$ is generated in 
-degree at most
+degree less than
 \[
@@
 
-\todo{factor $\phi$ through $\psi$ and $\chi$.}
+Let $x_1, \ldots x_r$ be the generators given by lemma  \ref{Hirzebruch-generators}, and $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through 
+\[
+	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+\]
+into
+\[
+\begin{tikzcd}
+\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+\end{tikzcd}
+\]
+
+Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ less than
+\[
+	2 \sigma
+\]
+Finally, we calculate the degree of generation of $\psi$:
+
 \begin{lem}
-$\ker(\psi)$ is generated in degree at most
+$\ker(\psi)$ is generated in less than
 \[
@@
 \]
-which generates $(z_i - \beta_i) \prod_{i=1}^n y_i^{c_i}$
+which divides $(z_i - \beta_i) \prod_{i=1}^n y_i^{c_i}$.
 We can bound $\deg(F)$ by
@@
 \]
+\end{proof}
 
-\end{proof}
+Combining these results, we get the following theorem:
+
+\begin{thm}\label{Hirzebruch-generators/relations}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
+linear polynomials in $y_0$ and $y_1$.
+Then $R_D$ is generated in degree less than 
+\[
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in \Tp(D) \atop
+	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}
+\]
+with relations generated in degree less than 
+\[
+	\max(2 \sigma, \sigma + \tau)
+\]
+where
+\[
+	\tau = \sigma
+	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+\]
+\end{thm}
 

### 2015-07-14 curves-write-up/spin-cring.tex

@@
 
-First, we present a definition of admissibility.
-Here, we define a notion of admissibility that is quite similar to the admissibility defined by Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}.
-Our notion is an adaptation the case of log spin canonical divisors.
+First, we define a notion of admissibility that is quite similar to
+the admissibility defined by Voight and Zureick-Brown
+\cite[Definition 8.5.1]{vzb:stacky}. Our notion is an adaptation
+the case of log spin canonical divisors.
 

### 2015-07-14 surfaces-write-up/surface-write-up.tex

@@
 \begin{example}
+\label{eg:hyperplane}
+Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0), H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$.
+Then, $R_D$ has generators in degree $2$ and $3$ which can be written as $u^2 \frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees less than $5$ the elements of $R_D$ can all be expressed as rational functions in $x_0, x_1$.
+However, in degree $6$, there is the rational function $\frac{x_1^2 x_2}{x_0^3}.$ Since this involves $x_2$, it must be a generator.
+
+This example easily generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{d}{s}$
+\end{example}
+
+\begin{example}
 \label{eg:radical}
+In this example, we justify the necessity of adding ghost points for the bounds obtained in Lemma ~\ref{P-m-generators}, which are also necessary when the divisors are not all contained in a hyperplanes.
+
  As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$.

### 2015-07-14 surfaces-write-up/surface-write-up.tex
fix generators 1pt

@@
 \noindent
-where $\vec{y} \in \mss_i$ and $\vec{w} \in \mss_j$ are the unique
-vectors such that $\vec{y} \prec \vec{w}$.
+where $\vec{y}$ and $\vec{w}$ are the unique
+vectors in $\mss_i$ and $\mss_j$, respectively, such that $\vec{y}
+\prec \vec{w}$.
 \end{thm}
@@
 linear combination of $\vec{x}_i$ and $\vec{x}_{i + 1}$ where
-$\vec{x}_i := (d_i, c_i) \in \bz^2$. Consequently, if $(\beta,
-\gamma) = \ell_1 (d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for
-$\ell_1, \ell_2 \in \bz_{ \geq 0}$, then any element $\frac{u^{\beta}
+$\vec{x}_i := (d_i, c_i) \in \bz^2$. Let $(\beta, \gamma) = \ell_1
+(d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for $\ell_1, \ell_2 \in
+\bz_{\geq 0}$. Consequently, any element $\frac{u^{\beta}
 x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
 \begin{align*}
-	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}
-	x^{\vec{w}}} {x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}
-	x^{\vec{z}}} {x_k^{c_{i + 1}}}\right)^{\ell_2}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}}
+	{x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}}
+	{x_k^{c_{i + 1}}}\right)^{\ell_2} x^{\vec{v}}.
 \end{align*}
@@
 \noindent
-for some $\vec{w} \in \mss_i, \vec{z} \in \mss_{i + 1}$. But these
-are precisely powers of two generators of the form $F_i^{\vec{w}}$
-and $F_{d_{i + 1}}^{\vec{z}}$ as prescribed in the theorem statement.
+We can break $\vec{v}$ into a sum of $\ell_1$ many vectors
+$\vec{w}_{(j)}$ in $\mss_2$ and $\ell_2$ many vectors $\vec{z}_{(k)}$
+in $\mss_2$ to give a decomposition
+\begin{align*}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{j = 1}
+	^{\ell_1} \frac{u^{d_i} x^{\vec{w}_{(j)}}} {x_k^{c_i}}
+	\prod_{k = 1}^{\ell_2} \frac{u^{d_{i + 1}} x^{\vec{z}_{(k)}}}
+	{x_k^{c_{i + 1}}}
+\end{align*}
+into products of generators $F_i^{\vec{w}_{(j)}}$
+and $F_{d_{i + 1}}^{\vec{z}_{(k)}}$ which are in the form
+prescribed in the theorem statement.
 

### 2015-07-14 curves-write-up/spin-cring.tex
moved some admissibility

@@
 \newcommand\ssec{\subsection}
+\newcommand\sssec{\subsubsection}
 \newcommand\BH{{\mathbb H}}
@@
 \begin{defn}
+\label{defn:order-sup}
+Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
+zero of $z$ at $P$ by $\ord_P^D(z)$.
+\end{defn}
+
+\begin{defn}
 \label{defn:log-spin-canonical-ring}
@@
 \end{lem}
+
+\sssec*{Idea of Proof:} To get $\supseteq$, we use the fact that
+
 \begin{proof}
@@
 we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X$.
-
-\begin{defn}
-\label{def:order-sup}
-Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
-zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
+We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X,$ using Definition ~\ref{defn:order-sup}.
 
@@
 
-The cases that $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
+Generators and relations $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
+Note that admissibility for $L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ is verified in Example ~\ref{eg:base-1-33-adm}.
+The verification of admissibility for the other cases is similar.
 

### 2015-07-14 curves-write-up/spin-cring.tex
minor curves acknowledgment edit

@@
 collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
-Zhang for helpful comments on this paper. We also thank Jorge Neves
+Zhang for helpful comments on this paper and thank Jorge Neves
 for pointing out the bounds given by Miles Reid's work on the

### 2015-07-14 curves-write-up/spin-cring.tex
edits to example 4.12: admissibility check

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 \label{eg:base-0-377-adm}
-Here, we explicitly check the admissibility of the example from
+Here, we explicitly check admissibility in the context of
 Example ~\ref{eg:base-0-377}. Recall that the setup is that
-$(\sx', 0, \halfcan'$ is a log spin curve with signature $\sigma := (0; 3, 7, 7; 0)$
+$(\sx', 0, \halfcan')$ is a log spin curve with signature $\sigma := (0; 3, 7, 7; 0)$
 and $\halfcan' \sim -\infty + \frac{1}{3}P_1 + \frac{3}{7}P_2 + \frac{3}{7}P_3$,
@@
 As shown in Example ~\ref{eg:base-0-377}, the log spin canonical
-rings corresponding to this case have a presentation
+ring corresponding to $(\sx', 0, \halfcan')$ has a presentation
 $\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
@@
 \ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we
-check \ref{custom:Ad-ii} We may also choose
+check \ref{custom:Ad-ii}.  We may also choose
 pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3k}{7}$
+generator lying on the line $-ord_{P_i}(z) = \deg (\frac{3k}{7} z)$
 in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other

### 2015-07-14 curves-write-up/spin-cring.tex
added ideas of proofs

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 
-\sssec*{Idea of Proof:} To get $\supseteq$, we use the fact that
+\sssec*{Idea of Proof:} To show $\supseteq$, we show $T \subset \initial(I),$ which follows immediately from $(1)$ and $(2)$.
+Then, $\subseteq$ follows from condition $(3)$, since $(1)$ implies $S$ is a basis, so no terms in $S$ can be contained in $\initial(I)$.
 
@@
 
+\sssec*{Idea of proof:} The proof will be fairly involved.
+To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each best lower approximation.
+We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$, showing that the set of elements we produce forms a basis.
+
+Next, part (b) immediately follows from an application of Lemma ~\ref{relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{relations_from_generators_induction}.
+The first two hypotheses follow immediately from the construction of block order.
+Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{relations_from_generators_induction}.
+
 \begin{proof}
@@
 \[
-	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \lfloor k \frac{\alpha}{\beta}\rfloor.
+	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \left\lfloor k \frac{\alpha}{\beta} \right\rfloor.
 \]
@@
 
+\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}.
+The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$.
+Part (b) follows by noting that the generators in Part (a) form an independent set, as can be seen by noting that the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$.
+To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$.
+We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound.
+Part (d) follows fairly easily from the definition of admissibility.
+
 \begin{proof}
@@
 \end{thm}
+
+\sssec*{Idea of Proof:} We check the theorem in two cases, depending on whether $\Delta > 0$.
+If $\Delta > 0$, we first check that the theorem holds for $L_X$ by adding in log points, and then check it holds for $L$ by raising the stabilizer orders of stacky points in a sequence of steps.
+When raising the stacky orders, it is important that we increment the stabilizer orders of the maximum possible number of stacky points at each step, so that the corresponding set will remain admissible.
+The check for $\Delta = 0$ is similar, although in this case we do not need to add in log points, only stacky points, and we will need to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.
 
@@
 \end{thm}
+
+\sssec*{Idea of proof:} The method of this proof is almost identical to that of Theorem ~\ref{thm:g-1-main}.
+When $\delta > 0$, we first add in log points, and then increment the stabilizer orders of stacky points, checking that the theorem holds at each step.
+The more technical case occurs when $\delta = 0$, in which case we simply increment the stabilizer orders of stacky points starting from one of our base cases, and check that every stacky curve can be reached by a sequence of admissible incrementations from a base case.
 
@@
 collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
-Zhang for helpful comments on this paper and thank Jorge Neves
+Zhang for helpful comments on this paper. We also thank Jorge Neves
 for pointing out the bounds given by Miles Reid's work on the

### 2015-07-14 surfaces-write-up/surface-write-up.tex

@@
 	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- \prod_{\vec{y} \in \mss_{k_{i, j}}} (F_{k_{i, j}}^{\vec{y}})
-	^{g_{\vec{y}}} &(i < k_{i, j} < j) \\
+	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})
+	^{g_{\vec{y}}} &(i < h_{i, j} < j) \\
 	\text{or} \\
 	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- \prod_{\substack{\vec{y} \in \mss_{k_{i, j}} \\ \vec{z} \in
-	\mss_{k_{i, j} + 1}}} (F_{k_{i, j}}^{\vec{y}})^{g_{\vec{y}}} \;
-	(F_{k_{i, j} + 1}^{\vec{z}})^{h_{\vec{z}}}
-	&(i < k_{i, j} < k_{i, j} + 1 < j).
+	- \prod_{\substack{\vec{y} \in \mss_{h_{i, j}} \\ \vec{z} \in
+	\mss_{h_{i, j} + 1}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}} \;
+	(F_{k_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}}
+	&(i < h_{i, j} < h_{i, j} + 1 < j).
 \end{flalign*}
@@
 Furthermore, there are the relations for each $(i, j)$ with
-$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
-\mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
+$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{z} \in
+\mss_j$ with $\vec{v} \not\prec \vec{z}$ (see Definition
 ~\ref{defn:vec-order}) of the form 
 \begin{align*}
-	&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- F_i^{\vec{y}} F_j^{\vec{w}} \\
+	&L_{i, j}^{\vec{v}, \vec{z}} = F_i^{\vec{v}} F_j^{\vec{z}}
+	- F_i^{\vec{y}} F_j^{\vec{z}} \\
 \end{align*}
@@
 \noindent
-where $\vec{y}$ and $\vec{w}$ are the unique
+where $\vec{y}$ and $\vec{z}$ are the unique
 vectors in $\mss_i$ and $\mss_j$, respectively, such that $\vec{y}
-\prec \vec{w}$.
+\prec \vec{z}$.
 \end{thm}
@@
 minimal for some $\vec{v} \in \mss_i$. Then $F_i^{\vec{v}} =
-F_{s}^{\vec{w}} F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and
-$\vec{w}, \vec{z} \in \bz_{ \geq 0}^{m + 1}$. In particular, we see
+F_{s}^{\vec{y}} F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and
+$\vec{y}, \vec{z} \in \bz_{ \geq 0}^{m + 1}$. In particular, we see
 that 
@@
 	&d_i = s + t \\
-	&c_i = \deg \vec{v} = \deg \vec{w} + \deg \vec{z}
+	&c_i = \deg \vec{v} = \deg \vec{y} + \deg \vec{z}
 \end{align*}
@@
 so $\frac{c_i}{d_i}$ is the mediant of the rational numbers
-$\frac{\deg \vec{w}}{s}, \frac{\deg \vec{z}}{t}$ which both
-do not exceed $\alpha$. One of $\frac{\deg \vec{w}}{s},
+$\frac{\deg \vec{y}}{s}, \frac{\deg \vec{z}}{t}$ which both
+do not exceed $\alpha$. One of $\frac{\deg \vec{y}}{s},
 \frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
@@
 {dorney:canonical}, each lattice point $(\beta, \gamma) \in
-\bz_{\geq 0}^2$ such that $c \leq d \alpha$ is a non-negative
-linear combination of $\vec{x}_i$ and $\vec{x}_{i + 1}$ where
-$\vec{x}_i := (d_i, c_i) \in \bz^2$. Let $(\beta, \gamma) = \ell_1
-(d_i, c_i) + \ell_2 (d_{i + 1}, c_{i + 1})$ for $\ell_1, \ell_2 \in
+\bz_{\geq 0}^2$ such that $\gamma \leq \beta \alpha$ is a non-negative
+linear combination of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
+some $h \in \{0, \ldots, r\}$. Let $(\beta, \gamma) = \ell_1
+(d_h, c_h) + \ell_2 (d_{h + 1}, c_{h + 1})$ for $\ell_1, \ell_2 \in
 \bz_{\geq 0}$. Consequently, any element $\frac{u^{\beta}
@@
 \begin{align*}
-	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_i}}
-	{x_k^{c_i}}\right)^{\ell_1} \left(\frac{u^{d_{i + 1}}}
-	{x_k^{c_{i + 1}}}\right)^{\ell_2} x^{\vec{v}}.
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_h}}
+	{x_k^{c_h}}\right)^{\ell_1} \left(\frac{u^{d_{h + 1}}}
+	{x_k^{c_{h + 1}}}\right)^{\ell_2} x^{\vec{v}}.
 \end{align*}
@@
 \begin{align*}
-	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{j = 1}
-	^{\ell_1} \frac{u^{d_i} x^{\vec{w}_{(j)}}} {x_k^{c_i}}
-	\prod_{k = 1}^{\ell_2} \frac{u^{d_{i + 1}} x^{\vec{z}_{(k)}}}
-	{x_k^{c_{i + 1}}}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{\lambda = 1}
+	^{\ell_1} \frac{u^{d_h} x^{\vec{w}_{(\lambda)}}} {x_k^{c_h}}
+	\prod_{\lambda = 1}^{\ell_2} \frac{u^{d_{h + 1}} x^{\vec{z}_{(\lambda)}}}
+	{x_k^{c_{h + 1}}}
 \end{align*}
-into products of generators $F_i^{\vec{w}_{(j)}}$
-and $F_{d_{i + 1}}^{\vec{z}_{(k)}}$ which are in the form
+
+\noindent
+consisting of products of generators $F_h^{\vec{y}_{(\lambda)}}$
+and $F_{h + 1}^{\vec{z}_{(\lambda)}}$ which are in the form
 prescribed in the theorem statement.
+
+In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
+has a decomposition of this form for some $h_{i, j}$. We also have
+that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
+$\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
+$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. The demonstration that
+$h_{i, j} \neq i$ is equivalent to the proof given by O'Dorney
+\cite[Theorem 6]{dorney:canonical}.
 

### 2015-07-14 curves-write-up/spin-cring.tex
fix idea of proof refs

@@
 
-Next, part (b) immediately follows from an application of Lemma ~\ref{relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{relations_from_generators_induction}.
+Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}.
 The first two hypotheses follow immediately from the construction of block order.
-Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{relations_from_generators_induction}.
+Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{lem:relations_from_generators_induction}.
 

### 2015-07-14 surfaces-write-up/surface-write-up.tex
various edits to surfaces

--- 2015-07-14 surfaces-write-up/surface-write-up.tex
@@
 \end{align*}
-where $\alpha_i \in \bq$.
+where $\alpha_i \in \bq$. \todo{Peter: What are the $D_i$'s.}
 \end{convention}
@@
 \section{Canonical Rings on Projective Space}
-In this section, we bound the degrees of generators and relations for divisors on $\bp^m$, for all $m \geq 1$. The $n = 1$ case was covered in \cite{dorney:canonical}.
+In this section, we bound the degrees of generators and relations for divisors on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case was covered in \cite{dorney:canonical}.
 
@@
 For the remainder of this section, we shall fix $m \geq 1$ and choose an isomorphism $\bp^m \cong \proj V$ so that $x_0,\ldots, x_m$ form a basis for $V$.
-Through the rest of this section, we will think of $x_i$ as a rational section of $H^0(\bp^m, \sco_{\bp^m})$ of degree 1.
+We will think of $x_i$ as a rational section of $H^0(\bp^m, \sco_{\bp^m})$ of degree 1.
 
@@
 Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
-We shall further assume that among there exist functions $f_0,\ldots, f_{m+1}$ form a basis for degree one rational functions on $\bp^m$.
+We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$.
+\todo{Peter: Make reference to ghost points here?}
+\todo{Peter: Also, this is a poorly placed statement of our assumption, because we are not assuming that for the one point/induction case that follows right?}
 
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ so that 
+The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying
 \begin{align}
@@
 form a spanning set for $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
-of the form $u^d \cdot \prod_{i=1}^n f_i^{c_i} $ such that
+of the form $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying
 \begin{align}

### 2015-07-14 curves-write-up/spin-cring.tex
edit first idea of proof

@@
 
-\sssec*{Idea of Proof:} To show $\supseteq$, we show $T \subset \initial(I),$ which follows immediately from $(1)$ and $(2)$.
-Then, $\subseteq$ follows from condition $(3)$, since $(1)$ implies $S$ is a basis, so no terms in $S$ can be contained in $\initial(I)$.
+\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
+Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms terms in $S$ can be contained in $\initial(I)$ since $(1)$ implies that $S$ is a basis.
 

### 2015-07-14 curves-write-up/spin-cring.tex
deleted repeated word I entered in first idea of pf

@@
 \sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms terms in $S$ can be contained in $\initial(I)$ since $(1)$ implies that $S$ is a basis.
+Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
 

### 2015-07-14 curves-write-up/spin-cring.tex
edits to second idea of pf

@@
 	Equip $\Bk[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
-	Definition ~\ref{defn:graded-p-lex} and $\Bk[y_1, \ldots, y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
+	Definition ~\ref{defn:graded-p-lex}, and equip $\Bk[y_1, \ldots,
+	y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
 	If $I'$ and $I$ are the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
@@
 \sssec*{Idea of proof:} The proof will be fairly involved.
-To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each best lower approximation.
-We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$, showing that the set of elements we produce forms a basis.
-
-Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}.
-The first two hypotheses follow immediately from the construction of block order.
-Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{lem:relations_from_generators_induction}.
+To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each best lower approximation.
+We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.
+
+Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction} so we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}.
+The first two hypotheses follow immediately from the definition of block order.
+Checking the third condition is quite technical but follows from certain slope conditions derived from the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
 

### 2015-07-14 curves-write-up/spin-cring.tex
small edits to max and parens

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 be the positive best lower approximations of $\frac{\alpha}{\beta}$
-(similar to Remark ~\ref{rem:lower-approximation}).
+{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
 Then,
@@
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees at most $\beta$ with $I$ generated over $I'$ in
-	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
-	\max_{1 \leq i \leq m}(\deg(x_i)))$).
+\item[(c)] Let $\tau = \max(1,
+	\max_{1 \leq i \leq m}(\deg(x_i)))$. Then, $R_\halfcan$ is generated over $R_\halfcan'$
+	in degrees up to $\beta$ with $I$ generated over $I'$ in
+	degrees up to $\max(2 \beta, \beta + \tau).$
 \end{enumerate}

### 2015-07-14 curves-write-up/spin-cring.tex
curves edit third idea of pf

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 
-By equation \ref{eqn:deg1-sat-ind} for $k \in \BN$,
+By Equation ~\ref{eqn:deg1-sat-ind} for $k \in \BN$,
 \[
@@
 
-\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}.
+\sssec*{Idea of proof:} The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}.
 The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$.
-Part (b) follows by noting that the generators in Part (a) form an independent set, as can be seen by noting that the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$.
-To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$.
-We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound.
+Part (b) follows by noting that the generators in Part (a) form an independent set which can be seen by noting that the sub-lattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$.
+To check part (c), we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole orders.
 Part (d) follows fairly easily from the definition of admissibility.

### 2015-07-14 curves-write-up/spin-cring.tex
edits to idea of proof below monster

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 
-\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
+\sssec*{Idea of Proof:} To show $\supseteq$, we show $T \subset \initial(I),$ which follows immediately from $(1)$ and $(2)$.
+Then, $\subseteq$ follows from condition $(3)$, since $(1)$ implies $S$ is a basis, so no terms in $S$ can be contained in $\initial(I)$.
 
@@
 be the positive best lower approximations of $\frac{\alpha}{\beta}$
-{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
+(similar to Remark ~\ref{rem:lower-approximation}).
 Then,
@@
 
-\item[(c)] Let $\tau = \max(1,
-	\max_{1 \leq i \leq m}(\deg(x_i)))$. Then, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees up to $\beta$ with $I$ generated over $I'$ in
-	degrees up to $\max(2 \beta, \beta + \tau).$
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
+	in degrees at most $\beta$ with $I$ generated over $I'$ in
+	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
+	\max_{1 \leq i \leq m}(\deg(x_i)))$).
 \end{enumerate}
@@
 \sssec*{Idea of proof:} The proof will be fairly involved.
-To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each best lower approximation.
+To show part (a), we first define an set of generators of $R_\halfcan$ over $R_{\halfcan'}$, with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$.
 We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$, showing that the set of elements we produce forms a basis.
 
-Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}.
+Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, so we only need verify the hypotheses of that lemma.
 The first two hypotheses follow immediately from the construction of block order.

### 2015-07-14 curves-write-up/spin-cring.tex
removed a we show that

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 \sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
+Then, $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
 

### 2015-07-14 curves-write-up/spin-cring.tex
line break 4th idea of pf

@@
 \sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-Then, $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
+Then, we show that $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
 
@@
 \sssec*{Idea of proof:} The proof will be fairly involved.
-To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each best lower approximation.
+To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$.
 We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.
 
-Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction} so we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}.
+Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, reducing the proof to verifying the hypotheses of that lemma. 
 The first two hypotheses follow immediately from the definition of block order.
-Checking the third condition is quite technical but follows from certain slope conditions derived from the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
+Checking the third condition is quite technical, but the conditions follow from certain slope conditions, given by ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
 

### 2015-07-14 curves-write-up/spin-cring.tex

@@
 
-\sssec*{Idea of Proof:} We check the theorem in two cases, depending on whether $\Delta > 0$.
-If $\Delta > 0$, we first check that the theorem holds for $L_X$ by adding in log points, and then check it holds for $L$ by raising the stabilizer orders of stacky points in a sequence of steps.
-When raising the stacky orders, it is important that we increment the stabilizer orders of the maximum possible number of stacky points at each step, so that the corresponding set will remain admissible.
-The check for $\Delta = 0$ is similar, although in this case we do not need to add in log points, only stacky points, and we will need to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.
+\sssec*{Idea of Proof:}
+We check the theorem in two cases, depending on whether $\Delta > 0$.
+If $\Delta > 0$, we first check that the theorem holds for $L_X$
+by adding in log points, and then check it holds for $L$ by raising
+the stabilizer orders of stacky points in a sequence of steps. When
+raising the stacky orders, it is important that we increment the
+stabilizer orders of the maximum possible number of stacky points
+at each step, so that the corresponding set will remain admissible.
+The check for $\Delta = 0$ is similar, although in this case we do
+not need to add in log points, only stacky points, and we will need
+to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.
 
@@
 Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective.
-We will show it holds for $\halfcan_X' + P,$ verifying the inductive step.
+We will show it holds for $\halfcan_X' + P$, verifying the inductive step.
 There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.

### 2015-07-14 curves-write-up/spin-cring.tex
edited third idea

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 
-By Equation ~\ref{eqn:deg1-sat-ind} for $k \in \BN$,
+By equation \ref{eqn:deg1-sat-ind} for $k \in \BN$,
 \[
@@
 
-\sssec*{Idea of proof:} The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}.
+\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}.
 The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$.
-Part (b) follows by noting that the generators in Part (a) form an independent set which can be seen by noting that the sub-lattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J$.
-To check part (c), we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole orders.
+Part (b) follows because the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J,$ so the generators in Part (a) generate all of $R_\halfcan$ over $R_{\halfcan'}$.
+To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$.
+We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound.
 Part (d) follows fairly easily from the definition of admissibility.

### 2015-07-14 curves-write-up/spin-cring.tex
minor edit to 4th idea of pf, 3rd idea of pf

@@
 We check the theorem in two cases, depending on whether $\Delta > 0$.
-If $\Delta > 0$, we first check that the theorem holds for $L_X$
-by adding in log points, and then check it holds for $L$ by raising
+If $\Delta > 0$, we first check that the theorem holds for $\halfcan_X$
+by inductively adding in log points to the base case of $\halfcan_X'
+= 0$. Then we check that it holds for $\halfcan$ by raising
 the stabilizer orders of stacky points in a sequence of steps. When

### 2015-07-14 curves-write-up/spin-cring.tex
reinstate previous changes

@@
 
-\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}.
-The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$.
-Part (b) follows because the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J,$ so the generators in Part (a) generate all of $R_\halfcan$ over $R_{\halfcan'}$.
-To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$.
-We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound.
-Part (d) follows fairly easily from the definition of admissibility.
+\sssec*{Idea of proof:}
+The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch
+and condition ~\ref{custom:Ad-iii}. The inequality in Part (a)
+follows from the fact that $\halfcan$ is similar to $\halfcan'$,
+but with some of the $e_i$ incremented by $2$. Part (b) follows
+because the sub-lattice spanned by $y_{i, e_i}$ and $y_{i, e_i'}$
+has determinant $1$ for $i \in J$, so the generators in Part (a)
+generate all of $R_\halfcan$ over $R_{\halfcan'}$. To check part (c),
+we construct relations between the generators of $R_{\halfcan}$
+over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$
+if and only if its pole order at $P_i$ for $i \in J$ is not too
+large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole
+orders. Part (d) follows fairly easily from the definition of
+admissibility.
 

### 2015-07-14 curves-write-up/spin-cring.tex
line break second idea of pf, minor edits to 4th
modify 4th idea, \Delta -> \delta in cases, lbr 5th

@@
 
-\sssec*{Idea of proof:} The proof will be fairly involved.
-To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$.
-We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.
-
-Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, reducing the proof to verifying the hypotheses of that lemma. 
-The first two hypotheses follow immediately from the definition of block order.
-Checking the third condition is quite technical, but the conditions follow from certain slope conditions, given by ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
+\sssec*{Idea of proof:}
+The proof will be fairly involved. To show part (a), we first
+define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$
+with one generator corresponding to each positive best lower
+approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch
+to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
+show that the set of elements we produce forms a basis.
+
+Next, part (b) immediately follows from the conclusion of Lemma
+~\ref{lem:relations_from_generators_induction}, reducing the proof
+to verifying the hypotheses of that lemma. The first two hypotheses
+follow immediately from the definition of block order. Checking the
+third condition is quite technical, but the conditions follow from
+certain slope conditions, given by ~\ref{custom:sat-1-*},
+~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
 
@@
 
-\sssec*{Idea of proof:}
+\sssec*{Idea of Proof:}
 The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch
@@
 \begin{proof}
-If $\Delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
-{reid:infinitesimal}. Otherwise, if $\Delta > 0$, the bound on the
+If $\delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
+{reid:infinitesimal}. Otherwise, if $\delta > 0$, the bound on the
 degrees of minimal generators follows from Lemma
@@
 \sssec*{Idea of Proof:}
-We check the theorem in two cases, depending on whether $\Delta > 0$.
-If $\Delta > 0$, we first check that the theorem holds for $\halfcan_X$
-by inductively adding in log points to the base case of $\halfcan_X'
-= 0$. Then we check that it holds for $\halfcan$ by raising
-the stabilizer orders of stacky points in a sequence of steps. When
-raising the stacky orders, it is important that we increment the
-stabilizer orders of the maximum possible number of stacky points
-at each step, so that the corresponding set will remain admissible.
-The check for $\Delta = 0$ is similar, although in this case we do
+We check the theorem in two cases, depending on whether $\delta > 0$.
+If $\delta > 0$, we first check that the theorem holds for
+$\halfcan_X$ by inductively adding in log points to the base case of$
+\halfcan_X' = 0$. Then we check that the theorem holds for $\halfcan$
+by adding stacky points and then inductively raising the 
+stabilizer orders of stacky points in the following sequence of 
+steps. When raising the stacky orders, it is important that we 
+increment the stabilizer orders of as many stacky points as 
+possible to maintain admissibility for the maximal possible sets of 
+stacky points. Then, we may also use the fact that raising the 
+stabilizer orders of any subset of these maximal sets of stacky 
+points will still preserve admissibility.
+
+The check for $\delta = 0$ is similar, although in this case we do
 not need to add in log points, only stacky points, and we will need
@@
 \noindent
-{\sf Case 1: $\Delta > 0$}
-
-If $\Delta > 0$, we must have $\Delta \geq 2$, by Remark ~\ref{rem:delta-not-1}.
+{\sf Case 1: $\delta > 0$}
+
+If $\delta > 0$, we must have $\delta \geq 2$, by Remark ~\ref{rem:delta-not-1}.
 In this case, let $\halfcan_X \in \di X$ satisfy $2 \halfcan_X \sim K_X + \Delta$.
@@
 
-To complete the case that $\Delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.
+To complete the case that $\delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.
 It suffices to show that if the theorem holds for a log spin canonical divisor $\halfcan'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
@@
 \noindent
-{\sf Case 2: $\Delta = 0$}
-
-Since $\Delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
+{\sf Case 2: $\delta = 0$}
+
+Since $\delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
 
@@
 Second, we deal with the case that $\sx$ has at least two stacky points. 
-If $(\sx', \delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
+If $(\sx', \Delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
 Example ~\ref{eg:base-1-33}, the triple $(\sx', 0, P-Q + \frac{1}{3}P_1+\frac{1}{3}P_2)$
 satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
+Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \Delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
 Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds 
@@
 
-\sssec*{Idea of proof:} The method of this proof is almost identical to that of Theorem ~\ref{thm:g-1-main}.
-When $\delta > 0$, we first add in log points, and then increment the stabilizer orders of stacky points, checking that the theorem holds at each step.
-The more technical case occurs when $\delta = 0$, in which case we simply increment the stabilizer orders of stacky points starting from one of our base cases, and check that every stacky curve can be reached by a sequence of admissible incrementations from a base case.
+\sssec*{Idea of Proof:}
+The method of this proof is almost identical to that of Theorem
+~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points,
+and then increment the stabilizer orders of stacky points, checking
+that the theorem holds at each step. The more technical case occurs
+when $\delta = 0$, in which case we simply increment the stabilizer
+orders of stacky points starting from one of our base cases, and
+check that every stacky curve can be reached by a sequence of
+admissible incrementations from a base case.
 

### 2015-07-14 curves-write-up/spin-cring.tex
our->several in 5th idea of pf

@@
 when $\delta = 0$, in which case we simply increment the stabilizer
-orders of stacky points starting from one of our base cases, and
+orders of stacky points starting from one of several base cases, and
 check that every stacky curve can be reached by a sequence of

### 2015-07-14 surfaces-write-up/surface-write-up.tex
added some examples for ghost points

@@
 \DeclareMathOperator{\den}{q}
+\DeclareMathOperator{\lcm}{lcm}
 %\captionsetup[table]{belowskip = 4pt}
@@
 
-This example easily generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{d}{s}$
+This example generalizes slightly to any divisor of the form $D = \frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes \bq,$ with $k \in \bn$, showing that there will always exist a generator in degree $a(a+1).$
+
+This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
+Then, if $D_i = V(f_i)$ where all $f_i$ can be written as a polynomial function in $x_0, \ldots, x_{m-1},$ we have $R_D$ always has a generator in degree $\lcm(\den_i \cdot \bida_i)$.
 \end{example}
+
+\begin{rem}
+\label{rem:ghost-motivation}
+Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\ref[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
+The reason for this is that the divisors may ``be contained in a hyperplane,'' i.e., be expressable as functions in $m$ of the $m+1$ variables on $\bp^m$.
+This problem can easily be circumvented by adding in ``ghost points.'' That is, we may add divisors of the form $0 \cdot H_i$ to $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$, then $f_0, \ldots, f_n$
+\end{rem}
 
@@
 \label{eg:radical}
-In this example, we justify the necessity of adding ghost points for the bounds obtained in Lemma ~\ref{P-m-generators}, which are also necessary when the divisors are not all contained in a hyperplanes.
+In this example, we show that it is still, in general, necessary to add ghost points, even when the irreducible components of a divisor are not all contained in a hyperplane.
 
- As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$.
-In degree $595 = 5* 7 * 17$, this has dimension $6$, but we cannot possibly use the lattice approach, as all lower degrees only have dimension 1.
-In fact, we may construct similar examples using any $x_i^m$ for $f_i$ with appropriate coefficients.
+Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 + x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) + \frac{1}{596}V(x_1^2 + x_2^2 + x_3^2)$.
+In degree $355216 = 5* 7 * 17 * 596$, this has dimension $10$.
+\todo{Clarify what this example means by the lattice approach}
+However, we possibly use the lattice approach, as all lower degrees only have dimension 1. In fact, we may construct similar examples using any set of degree $n$ divisor with very small degree.
 \end{example}

### 2015-07-14 curves-write-up/spin-cring.tex
edit to idea of proof in monster lemma

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 \sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-Then, $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.
+We deduce $\subseteq$ by noting that we can reduce any monomial in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ to a monomial in the basis $S$ via a set of relations whose initial terms include each monomial in $\initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle$.
 
@@
 
-\sssec*{Idea of proof:} The proof will be fairly involved.
-To show part (a), we first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$ with one generator corresponding to each positive best lower approximation of $\frac{\alpha}{\beta}$.
-We then use Riemann--Roch to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and show that the set of elements we produce forms a basis.
-
-Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, reducing the proof to verifying the hypotheses of that lemma. 
-The first two hypotheses follow immediately from the definition of block order.
-Checking the third condition is quite technical, but the conditions follow from certain slope conditions, given by ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
+\sssec*{Idea of proof:}
+The proof will be fairly involved. To show part (a), we first
+define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$
+with one generator corresponding to each positive best lower
+approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch
+to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
+show that the set of elements we produce forms a basis.
+
+Next, part (b) immediately follows from the conclusion of Lemma
+~\ref{lem:relations_from_generators_induction}, reducing the proof
+to verifying the hypotheses of that lemma. The first two hypotheses
+follow immediately from the definition of block order. Checking the
+third condition is quite technical, but follows from the construction of $V$ and the $U_i$'s.
 
@@
 by inductively adding in log points to the base case of $\halfcan_X'
-= 0$. Then we check that it holds for $\halfcan$ by raising
-the stabilizer orders of stacky points in a sequence of steps. When
+= 0$. Then we check that the theorem holds for $\halfcan$ by adding
+stacky points and then inductively raising the stabilizer orders of
+stacky points in the following sequence of steps. When
 raising the stacky orders, it is important that we increment the

### 2015-07-14 curves-write-up/spin-cring.tex

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 follow immediately from the definition of block order. Checking the
-third condition is quite technical, but the conditions follow from
-certain slope conditions, given by ~\ref{custom:sat-1-*},
-~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.
+third condition is quite technical, but follows from the construction of $V$ and the $U_i$'s.
 

### 2015-07-14 curves-write-up/spin-cring.tex
reinstate parens fix, sigma :=
discovered :rocket:

@@
 	y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ and $I$ are the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
-	\to R_{\halfcan'}$ and $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
-	\to R_{\halfcan}$ respectively, then
+	If $I'$ is the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
+	\to R_{\halfcan'}$ and $I$ is the ideal of relations of
+	$\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]	\to R_{\halfcan}$, then
 
@@
 											 + \langle U_i: 1 \le i \le n-1 \rangle
-											 + \langle V \rangle, \\
+											 + \langle V \rangle \\
 	\end{align*}
@@
 
-\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees at most $\beta$ with $I$ generated over $I'$ in
-	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
-	\max_{1 \leq i \leq m}(\deg(x_i)))$).
+\item[(c)] Let $\tau = \max(1, \max_{1 \leq i \leq m}(\deg(x_i)))$.
+	Then, $R_\halfcan$ is generated over $R_\halfcan'$
+	in degrees up to $\beta$ with $I$ generated over $I'$ in
+	degrees up to $\max(2 \beta, \beta + \tau).$
 \end{enumerate}
@@
 single stacky point with stabilizer order $3$. Say $(\sx, \Delta,
-\halfcan)$ is a log spin curve with signature $\sigma = (g; e_1,
+\halfcan)$ is a log spin curve with signature $\sigma := (g; e_1,
 \ldots, e_r; \delta) = (g; 3, \ldots, 3; \delta)$, and our base cases
@@
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$.  Define $R':= R_{\halfcan'}$.  Further, assume either 
+space $X'$ and signature $\sigma := (g; e_1', \ldots, e_r'; \delta)$.
+Define $R':= R_{\halfcan'}$.  Further, assume either 
 \begin{enumerate}
@@
 \label{thm:g-1-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
+Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has
+signature $\sigma := (1; e_1, \ldots, e_r; \delta)$.
 If $g = 1$, then the log spin canonical ring
@@
 We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
-curve and $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;
+curve and $\sx$ has signature $\sigma := (0; e_1, \ldots, e_r;
 \delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
@@
 Let $(\sx, \Delta, \halfcan)$ log spin curve,
-so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
+so that $\sx$ has signature $\sigma := (0; e_1, \ldots, e_r; \delta)$.
 Then, the log spin canonical ring

### 2015-07-14 curves-write-up/spin-cring.tex
delete comment, hunt for extra lines

@@
 $\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
-linear transformations, such that $\Gamma \backslash \BH$ has finite area.
+linear transformations, such that $\Gamma \backslash \BH$ has
+finite area.
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma)$ is to write down a presentation.
-%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$.
+One of the best ways to describe the ring $M(\Gamma)$ is to write
+down a presentation.
 To do so, it is useful to have a bound on the
@@
 \label{sec:g-1}
-
 In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
@@
 \label{sec:further-questions}
-
 In this section, we present several directions for further research.

### 2015-07-14 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
add arXiv-v2 files, close missing parens

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 \label{ssec:g-0-saturation}
-First, we present the saturations of the log spin canonical divisor
-for all cases where $g = 0$ and $\delta = 0$ (recall Definition
-~\ref{defn:sat} in Table ~\ref{table:g-0-sat}. The saturations can
-be computed using Riemann-Roch. By classifying the saturations of
-all signatures, we can determine the base cases on which we can
-apply inductive lemmas from Section ~\ref{sec:induction}. Note that
-the saturations of log spin canonical divisors only depend on the
-signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
-are listed first and generic cases follow.
-
 \begin{table}
@@
 \end{table}
+
+First, we present the saturations of the log spin canonical divisor
+(recall Definition ~\ref{defn:sat}) for all cases where $g = 0$ and
+$\delta = 0$ in Table ~\ref{table:g-0-sat}. The saturations can
+be computed using Riemann-Roch. By classifying the saturations of
+all signatures, we can determine the base cases on which we can
+apply inductive lemmas from Section ~\ref{sec:induction}. Note that
+the saturations of log spin canonical divisors only depend on the
+signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
+are listed first and generic cases follow.
 

### 2015-07-15 curves-write-up/spin-cring.tex
curves abs: space mod forms -> ring mod forms

@@
 	upper-half plane by a Fuchsian group. By the classical results of
-	Kodaira--Spencer, this space of modular forms may be viewed as the
+	Kodaira--Spencer, this ring of modular forms may be viewed as the
 	log spin canonical ring of a stacky curve. In this paper, we

### 2015-07-15 curves-write-up/spin-cring.tex
pre-arxiv-2 edits

@@
 \[
-	\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \}.
+	\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \} \cup \{0\}.
 \]
@@
 One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
-we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $H^0(X, \halfcan_X')$ may have no global sections.
+we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $ \halfcan_X'$ may have no nonzero global sections.
 We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X,$ using Definition ~\ref{defn:order-sup}.
@@
 Recall that
-$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$.
+$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u).$$
 We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
@@
 	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4
-\end{cases}.
+	\frac{1}{4} &\text{ if }z = y_4.
+\end{cases}
 \]
@@
 
-Generators and relations $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
-Note that admissibility for $L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ is verified in Example ~\ref{eg:base-1-33-adm}.
+Generators and relations for $R_{L'}$ with $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
+Note that admissibility for $(\sx',0,P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2)$ is verified in Example ~\ref{eg:base-1-33-adm}.
 The verification of admissibility for the other cases is similar.
@@
 that the theorem holds at each step. The more technical case occurs
-when $\delta = 0$, in which case we simply increment the stabilizer
-orders of stacky points starting from one of several base cases, and
+when $\delta = 0$. In this case, we increment the stabilizer
+orders of stacky points starting from one of the base cases, and
 check that every stacky curve can be reached by a sequence of

### 2015-07-15 curves-write-up/spin-cring.tex
minor edits to idea of proof of monster lemma

--- 2015-07-14 curves-write-up/spin-cring.tex
@@
 $\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
-linear transformations, such that $\Gamma \backslash \BH$ has
-finite area.
+linear transformations, such that $\Gamma \backslash \BH$ has finite area.
 We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$.
-One of the best ways to describe the ring $M(\Gamma)$ is to write
-down a presentation.
+$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma)$ is to write down a presentation.
+%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
 To do so, it is useful to have a bound on the
@@
 	y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ is the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
-	\to R_{\halfcan'}$ and $I$ is the ideal of relations of
-	$\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]	\to R_{\halfcan}$, then
+	If $I'$ and $I$ are the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
+	\to R_{\halfcan'}$ and $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
+	\to R_{\halfcan}$ respectively, then
 
@@
 											 + \langle U_i: 1 \le i \le n-1 \rangle
-											 + \langle V \rangle \\
+											 + \langle V \rangle, \\
 	\end{align*}
@@
 
-\item[(c)] Let $\tau = \max(1, \max_{1 \leq i \leq m}(\deg(x_i)))$.
-	Then, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees up to $\beta$ with $I$ generated over $I'$ in
-	degrees up to $\max(2 \beta, \beta + \tau).$
+\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$
+	in degrees at most $\beta$ with $I$ generated over $I'$ in
+	degrees at most $\max(2 \beta, \beta + \tau)$ (where $\tau = \max(1,
+	\max_{1 \leq i \leq m}(\deg(x_i)))$).
 \end{enumerate}
@@
 single stacky point with stabilizer order $3$. Say $(\sx, \Delta,
-\halfcan)$ is a log spin curve with signature $\sigma := (g; e_1,
+\halfcan)$ is a log spin curve with signature $\sigma = (g; e_1,
 \ldots, e_r; \delta) = (g; 3, \ldots, 3; \delta)$, and our base cases
@@
 Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma := (g; e_1', \ldots, e_r'; \delta)$.
-Define $R':= R_{\halfcan'}$.  Further, assume either 
+space $X'$ and signature $\sigma = (g; e_1', \ldots, e_r'; \delta)$.  Define $R':= R_{\halfcan'}$.  Further, assume either 
 \begin{enumerate}
@@
 \label{sec:g-1}
+
 In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
@@
 \label{thm:g-1-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has
-signature $\sigma := (1; e_1, \ldots, e_r; \delta)$.
+Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
 If $g = 1$, then the log spin canonical ring
@@
 \sssec*{Idea of Proof:}
-We check the theorem in two cases, depending on whether $\delta > 0$.
+We check the theorem in two cases, depending on if $\delta > 0$.
 If $\delta > 0$, we first check that the theorem holds for
-$\halfcan_X$ by inductively adding in log points to the base case of$
+$\halfcan_X$ by inductively adding in log points to the base case of $
 \halfcan_X' = 0$. Then we check that the theorem holds for $\halfcan$
@@
 We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
-curve and $\sx$ has signature $\sigma := (0; e_1, \ldots, e_r;
+curve and $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;
 \delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
@@
 Let $(\sx, \Delta, \halfcan)$ log spin curve,
-so that $\sx$ has signature $\sigma := (0; e_1, \ldots, e_r; \delta)$.
+so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
 Then, the log spin canonical ring
@@
 \label{sec:further-questions}
+
 In this section, we present several directions for further research.

### 2015-07-15 curves-write-up/spin-cring.tex
fixed bad plural

--- 2015-07-15 curves-write-up/spin-cring.tex
@@
 	y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ is the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
+	If $I'$ is the ideal of relations of $\Bk[u, x_1, \ldots, x_m]
 	\to R_{\halfcan'}$ and $I$ is the ideal of relations of

### 2015-07-15 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
curves: minor edit intro, further qs

@@
 and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
-We extend their result to all Fuchsian groups $\Gamma$ in the main
-theorem of this work.
+The main theorem of this work extends their result to all Fuchsian
+groups $\Gamma$.
 
@@
 	of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx$, 
-	where $nD \sim K.$ The canonical rings of such divisors often
-	arise as rings of fractional weight $\frac{2}{n}$ modular forms.
+	where $nD \sim K$ for some integer $n$ greater than $2$. The
+	canonical rings	of such divisors often arise as rings of
+	fractional weight $\frac{2}{n}$ modular forms.
 	For more details on fractional weight modular forms, see Adler and

### 2015-07-15 curves-write-up/spin-cring.tex
curves: minor edit intro, further qs

@@
 	y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ is the ideal of relations of $\Bk[u, x_1, \ldots, x_m]
+	If $I'$ is the ideals of relations of $\Bk[u, x_1, \ldots, x_m]
 	\to R_{\halfcan'}$ and $I$ is the ideal of relations of

### 2015-07-15 curves-write-up/spin-cring.tex
curves: parallelism , R--R, figure cap, mainthms

@@
 \cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
-geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic, trigonal, or a plane quintic are scheme-theoretically cut out by degree 2 equations.
+geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic curves, trigonal curves, or plane quintics are scheme-theoretically cut out by degree 2 equations.
 
@@
 
-Our main theorem is to bound the degrees of generators and relations of
-a log spin canonical ring. Let $\sx$ be a stacky curve with
-signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. The application
-of O'Dorney's work \cite[Chapter 5]{dorney:canonical} to log spin
-canonical rings gives a weak bound in the case $g = 0$ in terms of
-the least common multiples of the $e_i$'s. In their treatment of
-log spin canonical rings, Voight and Zureick-Brown
+Our main theorem is to bound the degrees of generators and
+relations of a log spin canonical ring. Let $\sx$ be a stacky curve
+with signature $\sigma := (g; e_1, \ldots, e_r; \delta)$. The
+application of O'Dorney's work \cite[Chapter 5]{dorney:canonical}
+to log spin canonical rings gives a weak bound in the case $g = 0$
+in terms of the least common multiples of the $e_i$'s. In their
+treatment of log spin canonical rings, Voight and Zureick-Brown
 \cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6
@@
  (e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
-bounds we deduce differ from those stated in Voight and Zureick-
-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because
-their grading convention differs from ours by a factor of 2.
+bounds we deduce differ from those stated in Voight and
+Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2
+because their grading convention differs from ours by a factor of 2.
 
@@
 \hookrightarrow R_\halfcan$ induced by the inclusions $H^0(\sx, k\halfcan_X)
-\hookrightarrow H^0(\sx, k\halfcan)$ for each $k \geq 0$. By Riemann Roch,
+\hookrightarrow H^0(\sx, k\halfcan)$ for each $k \geq 0$. By Riemann--Roch,
 we see there is some element $y_{1, 3} \in (R_\halfcan)_3$ with $\ord_{P_1}
@@
  Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_\halfcan)_2$ be any nonzero element.
-We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
---Roch, $\dim_\Bk (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
-element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
-if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0
-(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally,
-let $y_5 \in (R_\halfcan)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
-we claim there is some $\alpha \in \Bk$ so that
+We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by
+Riemann--Roch, $\dim_\Bk (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$
+be any nonzero element. We obtain $\di y_3|_{P_1} = -P_1,$ by
+Riemann--Roch, since if $y_3$ did not have a pole at $R$, we would
+obtain $y_3 \in H^0 (\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as
+$P \neq Q$. Finally, let $y_5 \in (R_\halfcan)_5$ be an element with
+$y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in \Bk$
+so that
 
@@
 Let $(\sx, \Delta, \halfcan)$ and $(\sx', \Delta, \halfcan')$ be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
-Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann-Roch $\sat(Eff(L'))\le 2$.
+Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann--Roch $\sat(Eff(L'))\le 2$.
 Furthermore, let $R_{\halfcan'} = \Bk[x_2, x_3
@@
 		$y_3, y_4,$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $\Bk[y_3, y_4]$ with $grevlex$ so that $y_3 \prec 
+	\item[(b)] Equip $\Bk[y_3, y_4]$ with grevlex so that $y_3 \prec 
 		y_4$
@@
 
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann-Roch, proving part (a).
-
-A quick computation checks that
-the following set $S$ is a $\Bk$ basis for $R_\halfcan$ over $R_{\halfcan'}$:
+Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann--Roch, proving part (a).
+
+A quick computation checks that the set
 
@@
 \noindent
+is a $\Bk$ basis for $R_\halfcan$ over $R_{\halfcan'}$, thus
 completing part (a).
@@
 \includegraphics{pics/spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\caption{Generators in the $(\deg z, -ord_{P_2}(z))$ lattice}
 \label{fig:377}
@@
 $(\sx, \Delta, \halfcan)$ be another log spin curve
-with coarse space $X$, so that $X \cong X'$ and signature $(g; e_1, \ldots, e_r;
+with coarse space $X$, so that $X \cong X'$ and with signature $(g; e_1, \ldots, e_r;
 \delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
@@
 and so $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
-Riemann Roch.
+Riemann--Roch.
 Hence, a general element
@@
 For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Throughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint-free by Riemann-Roch.
+Throughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint-free by Riemann--Roch.
 We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
@@
 with signature $(g; e_1, \ldots, e_r; \delta)$. Then the
-log spin canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{k \geq 0} H^0(\sx, k L )
-\end{align*}
-
-\noindent
+log spin canonical ring $R(\sx, \Delta, \halfcan)$
 is generated as a $\Bk$-algebra by elements in degree at most $e =
@@
 Therefore, since $P_r$ is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann Roch.
+~\ref{eqn:deg1-sat-ind} holds by Riemann--Roch.
 In this case, the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-1}.
@@
 \label{thm:g-1-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve so that $\sx$ has
+Let $(\sx, \Delta, \halfcan)$ log spin curve with
 signature $\sigma := (1; e_1, \ldots, e_r; \delta)$.
-If $g = 1$, then the log spin canonical ring
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{k = 0}^\infty H^0(\sx, k L)
-\end{align*}
-
-\noindent
+If $g = 1$, then the log spin canonical ring $R(\sx, \Delta, \halfcan)$
 is generated as a $\Bk$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
@@
 $\delta = 0$ in Table ~\ref{table:g-0-sat}. The saturations can
-be computed using Riemann-Roch. By classifying the saturations of
+be computed using Riemann--Roch. By classifying the saturations of
 all signatures, we can determine the base cases on which we can
@@
 \label{thm:g-0-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve,
-so that $\sx$ has signature $\sigma := (0; e_1, \ldots, e_r; \delta)$.
-Then, the log spin canonical ring
-
-\begin{align*}
-	R(\sx, \Delta, \halfcan) = \bigoplus_{k = 0}^\infty H^0(\sx, L)
-\end{align*}
-
-\noindent
+Let $(\sx, \Delta, \halfcan)$ log spin curve with signature
+$\sigma := (0; e_1, \ldots, e_r; \delta)$.
+Then, the log spin canonical ring $R(\sx, \Delta, \halfcan)$
 is generated as a $\Bk$-algebra by elements of degree at most $e =

### 2015-07-15 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
arXiv-v2 update

@@
 \includegraphics{spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_i}(z))$ lattice}
+\caption{Generators in the $(\deg z, -ord_{P_2}(z))$ lattice}
 \label{fig:377}

### 2015-07-15 surfaces-write-up/surface-write-up.tex
added some further questions and added tiff formatted pictures

@@
 \DeclareMathOperator{\lcm}{lcm}
+\DeclareMathOperator{\Pic}{Pic}
 %\captionsetup[table]{belowskip = 4pt}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%% Further Questions %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusion}
+This paper extends the work of O'Dorney on $\mathbb{P}^1$ to $\mathbb{P}^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
+The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar ideas to O'Dorney's method on $\mathbb{P}^1$.
+
+We can view $\hirz_0$ as $\mathbb{P}^1\times \mathbb{P}^1$ and more generally $\hirz_k$ as a $\mathbb{P}^1$ bundle over $\mathbb{P}^1$.
+One might hope that similar ideas could be generalized to all bundles.
+Specifically:
+\begin{question}\label{qn:general-product/bundle}
+Suppose $X$ and $Y$ are schemes.
+Let $D$ be a divisor on $X\times Y$ or more generally for $X$ bundles over $Y$.
+Can  generated by $x_1, \ldots x_m$ and $y_1, \ldots, y_{m'}$ with ideal of relations generated by $f_1, \ldots, f_n$ and $g_1, \ldots g_{n'}$.
+Then can we find a generators and relations for $X\times Y$ or more generally for $X$ bundles over $Y$?
+\end{question}
+An obvious obstruction to this is the fact that we critically used the fact that $\hirz_k$ has well-defined bi-degrees.  Unfortunately, in general $\Pic(X \times Y) \not \cong \Pic(X) \times \Pic(Y)$.
+
+Alternatively, we can view $\hirz_1$ as $\mathbb{P}^2$ blown up at a point.  This suggests the following question:
+\begin{question}\label{qn:general-blowup}
+Given a scheme $X$ generated by $x_1, \ldots, x_m$ with ideal of relations generated by $f_1, \ldots, f_n$.  Then can we describe generators and relations of $X$ blown up at some point $P$?
+\end{question}
+Fortunately, the picard group of $X$ blown up at a point is the same as that of $X$ times an additional copy of $\bz$.
+Perhaps analyzing the argument from \ref{Hirzebruch-generators/relations} in the case of $\hirz_k$ from the perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by the blowup, might suggest a general method for blowups.
+
+Answering question \ref{qn:general-blowup} would in fact provide an answer for all rational surfaces, via the minimal model program for surfaces \todo{Reference}.
+One might to provide an analogous result to \ref{Hirzebruch-generators/relations} in the case of all minimal surfaces:
+\begin{question}\label{qn:general-minimal-surface}
+Can we provide bounds on all minimal 
+\end{question}
+
 %%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-15 surfaces-write-up/surface-write-up.tex

@@
 Suppose $X$ and $Y$ are schemes.
-Let $D$ be a divisor on $X\times Y$ or more generally for $X$ bundles over $Y$.
-Can  generated by $x_1, \ldots x_m$ and $y_1, \ldots, y_{m'}$ with ideal of relations generated by $f_1, \ldots, f_n$ and $g_1, \ldots g_{n'}$.
-Then can we find a generators and relations for $X\times Y$ or more generally for $X$ bundles over $Y$?
+Let $D$ be a divisor on $X\times Y$ or more generally on an $X$ bundles over $Y$.
+Can we describe $D$ in terms of divisors $D_1, \ldots D_n$ on $X$ and $D_1', \ldots d_n'$ on $Y$.
+Furthermore, can we find generators for $R_D$ and its ideal of relations using those of the $R_{D_i}$'s and $R_{D_j'}$'s?
 \end{question}
-An obvious obstruction to this is the fact that we critically used the fact that $\hirz_k$ has well-defined bi-degrees.  Unfortunately, in general $\Pic(X \times Y) \not \cong \Pic(X) \times \Pic(Y)$.
+An immediate obstruction to this is the fact that we critically used the fact that $\hirz_k$ has well-defined bi-degrees.
+Unfortunately, in general $\Pic(X \times Y) \not \cong \Pic(X) \times \Pic(Y)$.
 
@@
 \begin{question}\label{qn:general-blowup}
-Given a scheme $X$ generated by $x_1, \ldots, x_m$ with ideal of relations generated by $f_1, \ldots, f_n$.  Then can we describe generators and relations of $X$ blown up at some point $P$?
+Let $X$ be a scheme.
+Let $X'$ be the blowup of $X$ at a point $P$ with a divisor $D$.
+First, is there a way to express $D$ in terms of divisors $D_1, \ldots, D_n$ on $X$?
+Furthermore, is there a way to describe generators and relations of $R_D$ in terms of those of $R_{D_i}$ for all $i$.
 \end{question}
@@
 \begin{question}\label{qn:general-minimal-surface}
-Can we provide bounds on all minimal 
+Can we describe generators and relations of $R_D$ for $D$ a divisor on an arbitrary minimal surface $X$?
 \end{question}

### 2015-07-15 surfaces-write-up/surface-write-up.tex
some 1pt additions

@@
 $\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
-$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. The demonstration that
+$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore, we have that
 $h_{i, j} \neq i$ is equivalent to the proof given by O'Dorney
-\cite[Theorem 6]{dorney:canonical}.
+\cite[Theorem 6]{dorney:canonical}. This gives the relations
+$G_{i, j}^{\vec{v}, \vec{w}}$.
+
+The application of $G_{i, j}^{\vec{v}, \vec{w}}$ can be used
+to transform any monomial in the $F_i^{\vec{v}}$'s involving
+indices that differ by more than $1$ to a monomial in the $F_i
+^{\vec{v}}$'s involving indices that differ by at most $1$.
+
+Furthermore, we have relations
 

### 2015-07-15 surfaces-write-up/surface-write-up.tex
edits to section 4 of surfaces

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
-We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$.
-\todo{Peter: Make reference to ghost points here?}
-\todo{Peter: Also, this is a poorly placed statement of our assumption, because we are not assuming that for the one point/induction case that follows right?}
+\todo{Should this say $D_i$ is a Cartier divisor.
+Also should we say $\deg(f_i)= \bida_i$ rather than $\deg(D_i)$.}
+We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$. \todo{Peter: Make reference to ghost points here?}
 
@@
 \label{align:pm-span}
-\sum_{i=0}^{n} c_i \cdot \bida_i \cdot f_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=1}^{n} c_i \cdot \bida_i \cdot f_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 
-\todo{the following bound is the generation bound beginning from evan's paper}
+We first restrict attention to the case $n=1$, so $D = \alpha D_i$.
 
@@
 Instead we must use ghost points and hypersurfaces.
-\end{rem}
+\end{rem} \todo{Peter: What is the purpose of this remark?  The only method we have extends to ghost points so that this is satisfied.}
 
@@
 
-This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
+This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and \todo{Peter: We need some condition that $D_i$'s be irreducible divisors or something.} $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
 Then, if $D_i = V(f_i)$ where all $f_i$ can be written as a polynomial function in $x_0, \ldots, x_{m-1},$ we have $R_D$ always has a generator in degree $\lcm(\den_i \cdot \bida_i)$.

### 2015-07-15 surfaces-write-up/surface-write-up.tex
finish 1pt pf with remaining relations

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 Let $\mss_i := \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
-\sum_{i = 0} ^{m + 1} v_i = c_i\}$ be the set of $\bz_{\geq 0}
-^{m + 1}$-vectors with sum of components equal to $c_i$.
+\sum_{i = 0} ^{m + 1} v_i = c_i\}$ be the set of points in
+$\bz_{\geq 0}^{m + 1}$ with sum of components equal to $c_i$.
 \end{defn}
@@
 Furthermore, there are the relations for each $(i, j)$ with
-$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{z} \in
-\mss_j$ with $\vec{v} \not\prec \vec{z}$ (see Definition
+$j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
+\mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
 ~\ref{defn:vec-order}) of the form
 \begin{align*}
-	&L_{i, j}^{\vec{v}, \vec{z}} = F_i^{\vec{v}} F_j^{\vec{z}}
+	&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
 	- F_i^{\vec{y}} F_j^{\vec{z}} \\
@@
 vectors in $\mss_i$ and $\mss_j$, respectively, such that $\vec{y}
-\prec \vec{z}$.
++ \vec{z} = \vec{v} + \vec{w}$ and $\vec{y} \prec \vec{z}$.
 \end{thm}
@@
 \noindent
-We can break $\vec{v}$ into a sum of $\ell_1$ many vectors
+We can then break $\vec{v}$ into a sum of $\ell_1$ many vectors
 $\vec{w}_{(j)}$ in $\mss_2$ and $\ell_2$ many vectors $\vec{z}_{(k)}$
@@
 
-Furthermore, we have relations
-
-\todo{relations}
-Canonical form of 
-\[
-	\prod_{\substack{0 \leq i \leq m + 1 \\ \vec{y}
-	\in \mss_i}} (F_i^{\vec{y}})^{g_{\vec{y}}}
-\]
+We also have relations involving generators in consecutive
+indices. Suppose $F_i^{\vec{v}}$ and $F_j^{\vec{w}}$ are
+generators with $j = i$ or $j = i + 1$ and $\vec{v} \in
+\mss_i, \vec{w} \in \mss_j$ with $\vec{v} \not\prec \vec{w}$.
+Let $\vec{y}$ and $\vec{z}$ be the unique vectors in $\mss_i$ and
+$\mss_j$, respectively, such that $\vec{y} + \vec{z} = \vec{v} +
+\vec{w}$ and $\vec{y} \prec \vec{z}$ (i.e.~ the nonzero indices
+of $\vec{y}$ followed by those of $\vec{z}$ give an increasing
+sequence). Then we see that
+\begin{align*}
+	F_i^{\vec{v}} F_j^{\vec{w}} = x^{\vec{v} + \vec{w}}
+																 \left(\frac{u^{d_i}}{x_k^{c_i}}\right)
+																 \left(\frac{u^{d_j}}{x_k^{c_j}}\right)
+															= x^{\vec{y} + \vec{z}}
+																 \left(\frac{u^{d_i}}{x_k^{c_i}}\right)
+																 \left(\frac{u^{d_j}}{x_k^{c_j}}\right)
+															= F_i^{\vec{y}} F_j^{\vec{z}}
+\end{align*}
 
 \noindent 
-where the indices with
-some nonzero $g_{\vec{y}}$ are consecutive.
+which give the relations $L_{i, j}^{\vec{v}, \vec{w}}$.
+
+Now, we may apply the relations $L_{i, j}^{\vec{v}, \vec{w}}$
+to any monomial in the $F_i^{\vec{v}}$'s involving
+indices that differ by at most $1$ to produce the canonical form
+\begin{align*}
+	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(1)}}} \cdots
+	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(\ell_1)}}}
+	(F_{i + 1}^{\vec{w}_{(1)}})^{g_{\vec{w}_{(1)}}} \cdots
+	(F_{i + 1}^{\vec{w}_{(\ell_2)}})^{g_{\vec{w}_{(\ell_2)}}}
+\end{align*}
+
+\noindent
+where $\vec{v}_{(1)} \prec \vec{v}_{(2)} \prec \ldots \prec
+\vec{v}_{(\ell_1)} \prec \vec{w}_{(1)} \prec \ldots \prec
+\vec{w}_{(\ell_2)}$. Consequently, the relations of form
+$G_{i, j}^{\vec{v}, \vec{w}}$ and of form $L_{i, j}^{\vec{v},
+\vec{w}}$ generate all the relations among the $F_{i}^{\vec{v},
+\vec{w}}$.
 \end{proof}
@@
 \todo{change thm to be inductive for adding pts, giving result on
-effective divisors}
+effective divisors?}
 \todo{remark on not doing two points}
@@
 \ssec{Bounds for Arbitrary Divisors on Projective Space}
-
 \begin{rem}
@@
 \noindent
-for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
+for some $d \in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
 ^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in

### 2015-07-15 surfaces-write-up/surface-write-up.tex

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 \noindent
-Let $e_1, \ldots, e_t \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i,
-\ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$,
+Suppose $e_1, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_1^i,
+\ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
 meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of
@@
 \label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees less than $2(\sum_{i=1}^{r}d_r-1)$.
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
 \end{lem}
@@
 \label{rem:ghost-motivation}
-Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\ref[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
+Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\cite[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
 The reason for this is that the divisors may ``be contained in a hyperplane,'' i.e., be expressable as functions in $m$ of the $m+1$ variables on $\bp^m$.
@@
 
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+We now move on offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
+
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 \begin{lem} \label{P-m-generators}
@@
 \begin{align}\label{eqn:Sigma-def}
-	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
+	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
 \end{align}
-We note that $\Sigma$ has extremal rays given by the lattice points $e_i$ corresponding to
+We note that $\Sigma$ has extremal rays given by the lattice points 
+\begin{equation}\label{defn:e_i-P-n}
+	e_i = (\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j, -\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i)
+\end{equation}
+for each $i\in \{1, \ldots n\}$.
+Viewed inside of $R_D$, we have $e_i$ corresponding to
 \begin{equation}\label{eqn:epilon-def-P-m}
-	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}
+	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
 \end{equation}
-for each $i\in \{1, \ldots n\}$.  Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degree less than
+Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
 \[
@@
 
-Let $x_1, \ldots x_r$ be the generators given by lemma  \ref{P-m-generators}, and $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through 
+Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i \bida_i$ (given by lemma \ref{P-m-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
+We can factor $\phi$ through
 \[
-	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in \mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
 \]
-into
+by
 \[
@@
 
-Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ less than
+By Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
 \[
-	\sum_{i=1}^n \ell_i a_i.
+	2 \sum_{i=1}^n \ell_i a_i.
 \]
@@
 \begin{lem}\label{P-m-relations-psi}
-$\ker(\psi)$ is generated in degree at most 
+$\ker(\psi)$ is generated in degree less than
 \[
-	\delta_i + \sum_{i=1}^n \ell_i a_i.
+	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
 \]
@@
 \begin{proof}
-We first claim that $\psi$ has a relation of the form
+We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
 \begin{equation}\label{eqn:relations-psi}
-	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{j}}
+	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
 \end{equation}
@@
 \noindent
-for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
-^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in
-k[z_1, \ldots, y_3]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida)$.
+for all $d\in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_j + \sum_{i = 1}
+^n \bida_i c_i = 0$.
 
@@
 generate all relations, since they allow us to reduce any $\prod_{i =
-1}^n \epsilon_i^{r_i}$ to a canonical form. \todo{add reference to
-earlier description of canonical form.}
+1}^n \epsilon_i^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.
 
-Now we bound the degree of generation of these relations for a fixed $z_i$.
-We associate $(z_i - \beta_j)\prod_{j=1}^n z_j^{c_j}$ that has degree $d$ with the lattice point $(d, c_1, \ldots, c_n)$.
-Let $\Sigma_i \subseteq \mathbb{R}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
-Then we see $\Sigma_i$ is a translation of $\Sigma$ (see Equation \ref{eqn:Sigma-def}) by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
+We now fix $z_i$ and bound the degree of generation of this set of relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$.
+We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.
+Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
+Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e_i-P-n}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
 
@@
 \]
-for $r_j \in \mathbb{R}$ for each $j$.
+where $r_j \in \mathbb{R}$ for each $j$.
 
-Whenever some $r_j \ge 1$, we can generate the generation at hand by one of lower degree by factoring out the section $\epsilon_j$ corresponding to the lattice point $e_j$ (see Equation \ref{eqn:epilon-def-P-m}).
-Therefore, we can bound the degree of generation of $\ker(\psi)$ less than
+Whenever some $r_j \ge 1$, we can generate the relation at hand by one of lower degree by factoring out a copy of $\epsilon_j$ (see Equation \ref{eqn:epilon-def-P-m}).
+Therefore, $\ker(\psi)$ is generated in degrees less than
 \[
-	\delta_i + \sum_{i=1}^n \ell_i a_i.
+	\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.
 \]
@@
 
-Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma \ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
+Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $2\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma \ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
 \[
-	\max \left(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
 \]
@@
 \[
-	\max \left(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
 \]
@@
 \section{Canonical Rings on Hirzebruch surfaces}
-Let $D=\sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(\hirz_
-k)$ for some curve $C_i$ of $\hirz_k$, such
+Let $D=\sum_{i=1}^n \alpha_i C_i \in \mathbb{Q} \otimes \di(\hirz_
+k)$ for some irreducible curves $C_1, \ldots C_n$ of $\hirz_k$, such
 that $C_1, \ldots, C_4$ are independent curves with bi-degrees $(1,0)
@@
 \begin{equation}\label{eqn:define-T=(D)}
-	\Te(D) = \left\{i \in \{1, \ldots, m\}: \bida_i \sum_{k=1}^m \bidb_k 
-\alpha_k = \bidb_i \sum_{k=1}^m \bida_k \alpha_k \right\},
+	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
+\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
 \end{equation}
@@
 \begin{equation}\label{eqn:define-T+(D)}
-	\Tp(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} 
-\bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^m \alpha_k \bida_k 
+	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k=1}^n} 
+\bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^n \alpha_k \bida_k 
 \right\},
@@
 \begin{equation}\label{eqn:define-T-(D)}
-	\Tm(D) = \left\{ j \in \{1, \ldots, m\}: \bida_j \sum_{k=1}^m \alpha_
-k \bidb_k < \bidb_j \sum_{k=1}^m \alpha_k \bida_k s \right\}.
+	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k=1}^n \alpha_
+k \bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k s \right\}.
 \end{equation}

### 2015-07-15 surfaces-write-up/surface-write-up.tex

@@
 \noindent
-for all $d\in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_j + \sum_{i = 1}
+for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_j + \sum_{i = 1}
 ^n \bida_i c_i = 0$.

### 2015-07-15 surfaces-write-up/surface-write-up.tex
1pt: number of gens/rels

@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + i} \choose {i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
+{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has $z$
-many \todo{how many?} relations of the following two types.
+such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has
+relations of the following two types.
 

### 2015-07-15 surfaces-write-up/surface-write-up.tex
added intro over my pay-grade/head

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 \section{Introduction}
-\todo{Clean up this stuff on siegel modular forms, hilbert modular forms, say something about hasse keel program, canoncical rings studied before}
 
-\todo{Might be reasonable to think about higher dimensional rational varieties that are similar to these hirzebruch surfaces.}
-
-\todo{The following stuff is almost nonsensical now, will be edited much more soon}
-
+\todo{write more about hassett keel program}
+\cite{hassett:classical-and-minimal-models}
 Hasse keel program, birational map from $proj R(K + \Delta)$ to $M_2$, they showed finite generation, we're giving explicit generators and bounds.
 
-The work in this paper also yields bounds for certain rings of Hilbert modular forms. Recall that a Hilbert modular form is a generalization of modular forms to multiple variables.
+The work in this paper also yields bounds for certain rings of Hilbert 
+modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
+modular forms are both to higher dimensions variables. In the case of 
+Hilbert Modular forms, one considers modular forms on an $m$ fold product 
+of upper half planes, which transform under the action of finite index 
+subgroups of the groups of positive determinant matrices. Similarly, Siegel 
+modular forms are modular forms on the Siegel upper half space which are 
+stable under the action of the symplectic group. While in general these 
+quotients can be quite complicated spaces, in the case that the resulting 
+quotient spaces are isomorphic to $\bp^m$ for some $m$, or some Hirzebruch 
+surface, our main result gives a method for bounding the degree of 
+generators and relations for the corresponding rings of Hilbert modular 
+forms and Siegel modular forms. Namely, as in \cite{vzb:stacky}, one can 
+port these modular form groups from the analytic category to the algebraic 
+category, and then view the ring of modular forms as a certain stacky 
+canonical ring on our underlying algebraic space.
+\todo{include references}
 
-Siegel modular forms are a generalization of modular forms on the Siegel upper half plane to automorphic forms on the Siegel upper half space.
-Explicitly, the Siegel uper half space is $\mathscr H \cong \bc^n/\Lambda$ and siegel modular forms are functions on $Sp_{2g} \backslash \mathscr H.$ Then, modular functions are differentials invariant under the action of $Sp_{2g}$.
-In the case that $\Gamma \backslash \mathscr H$.
-
+\todo{Possibly keep or delete following example}
 Example: the Siegel 2-upper half plane $\bc^2/\Lambda$ Note that $\bc^2/\Lambda$ is algebraic if and only if there exists a hermitial form on $\Lambda$.
@@
 \noindent
-Suppose $e_1, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_1^i,
-\ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
+Let $e_1, \ldots, e_t \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i,
+\ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$,
 meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of
@@
 \label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees less than $2(\sum_{i=1}^{r}d_r-1)$.
 \end{lem}
@@
 Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
-\todo{Should this say $D_i$ is a Cartier divisor.
-Also should we say $\deg(f_i)= \bida_i$ rather than $\deg(D_i)$.}
-We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$. \todo{Peter: Make reference to ghost points here?}
+We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$.
+\todo{Peter: Make reference to ghost points here?}
+\todo{Peter: Also, this is a poorly placed statement of our assumption, because we are not assuming that for the one point/induction case that follows right?}
 
@@
 \label{align:pm-span}
-\sum_{i=1}^{n} c_i \cdot \bida_i \cdot f_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=0}^{n} c_i \cdot \bida_i \cdot f_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 
-We first restrict attention to the case $n=1$, so $D = \alpha D_i$.
+\todo{the following bound is the generation bound beginning from evan's paper}
 
@@
 Instead we must use ghost points and hypersurfaces.
-\end{rem} \todo{Peter: What is the purpose of this remark?  The only method we have extends to ghost points so that this is satisfied.}
+\end{rem}
 
@@
 
-This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and \todo{Peter: We need some condition that $D_i$'s be irreducible divisors or something.} $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
+This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
 Then, if $D_i = V(f_i)$ where all $f_i$ can be written as a polynomial function in $x_0, \ldots, x_{m-1},$ we have $R_D$ always has a generator in degree $\lcm(\den_i \cdot \bida_i)$.
@@
 \label{rem:ghost-motivation}
-Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\cite[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
+Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\ref[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
 The reason for this is that the divisors may ``be contained in a hyperplane,'' i.e., be expressable as functions in $m$ of the $m+1$ variables on $\bp^m$.
@@
 
-We now move on offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
-
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 \begin{lem} \label{P-m-generators}
@@
 \begin{align}\label{eqn:Sigma-def}
-	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
+	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
 \end{align}
-We note that $\Sigma$ has extremal rays given by the lattice points 
-\begin{equation}\label{defn:e_i-P-n}
-	e_i = (\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j, -\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i)
+We note that $\Sigma$ has extremal rays given by the lattice points $e_i$ corresponding to
+\begin{equation}\label{eqn:epilon-def-P-m}
+	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}
 \end{equation}
-for each $i\in \{1, \ldots n\}$.
-Viewed inside of $R_D$, we have $e_i$ corresponding to
-\begin{equation}\label{eqn:epilon-def-P-m}
-	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
-\end{equation}
-Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
+for each $i\in \{1, \ldots n\}$.  Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degree less than
 \[
@@
 
-Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i \bida_i$ (given by lemma \ref{P-m-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
-We can factor $\phi$ through
+Let $x_1, \ldots x_r$ be the generators given by lemma  \ref{P-m-generators}, and $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through 
 \[
-	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in \mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
 \]
-by
+into
 \[
@@
 
-By Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
+Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ less than
 \[
-	2 \sum_{i=1}^n \ell_i a_i.
+	\sum_{i=1}^n \ell_i a_i.
 \]
@@
 \begin{lem}\label{P-m-relations-psi}
-$\ker(\psi)$ is generated in degree less than
+$\ker(\psi)$ is generated in degree at most 
 \[
-	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
+	\delta_i + \sum_{i=1}^n \ell_i a_i.
 \]
@@
 \begin{proof}
-We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
+We first claim that $\psi$ has a relation of the form
 \begin{equation}\label{eqn:relations-psi}
-	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
+	(z_i - \beta_j)\prod_{j=1}^n {z_j}^{c_{j}}
 \end{equation}
@@
 \noindent
-for all $d\in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_j + \sum_{i = 1}
-^n \bida_i c_i = 0$.
+for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
+^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in
+k[z_1, \ldots, y_3]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida)$.
 
@@
 generate all relations, since they allow us to reduce any $\prod_{i =
-1}^n \epsilon_i^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.
+1}^n \epsilon_i^{r_i}$ to a canonical form. \todo{add reference to
+earlier description of canonical form.}
 
-We now fix $z_i$ and bound the degree of generation of this set of relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$.
-We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.
-Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
-Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e_i-P-n}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
+Now we bound the degree of generation of these relations for a fixed $z_i$.
+We associate $(z_i - \beta_j)\prod_{j=1}^n z_j^{c_j}$ that has degree $d$ with the lattice point $(d, c_1, \ldots, c_n)$.
+Let $\Sigma_i \subseteq \mathbb{R}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
+Then we see $\Sigma_i$ is a translation of $\Sigma$ (see Equation \ref{eqn:Sigma-def}) by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
 
@@
 \]
-where $r_j \in \mathbb{R}$ for each $j$.
+for $r_j \in \mathbb{R}$ for each $j$.
 
-Whenever some $r_j \ge 1$, we can generate the relation at hand by one of lower degree by factoring out a copy of $\epsilon_j$ (see Equation \ref{eqn:epilon-def-P-m}).
-Therefore, $\ker(\psi)$ is generated in degrees less than
+Whenever some $r_j \ge 1$, we can generate the generation at hand by one of lower degree by factoring out the section $\epsilon_j$ corresponding to the lattice point $e_j$ (see Equation \ref{eqn:epilon-def-P-m}).
+Therefore, we can bound the degree of generation of $\ker(\psi)$ less than
 \[
-	\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.
+	\delta_i + \sum_{i=1}^n \ell_i a_i.
 \]
@@
 
-Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $2\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma \ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
+Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma \ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i \right).
 \]
@@
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(\sum_{i=1}^n \ell_i a_i, \delta_i + \sum_{i=1}^n \ell_i a_i \right).
 \]
@@
 \section{Canonical Rings on Hirzebruch surfaces}
-Let $D=\sum_{i=1}^n \alpha_i C_i \in \mathbb{Q} \otimes \di(\hirz_
-k)$ for some irreducible curves $C_1, \ldots C_n$ of $\hirz_k$, such
+Let $D=\sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(\hirz_
+k)$ for some curve $C_i$ of $\hirz_k$, such
 that $C_1, \ldots, C_4$ are independent curves with bi-degrees $(1,0)
@@
 \begin{equation}\label{eqn:define-T=(D)}
-	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
-\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
+	\Te(D) = \left\{i \in \{1, \ldots, m\}: \bida_i \sum_{k=1}^m \bidb_k 
+\alpha_k = \bidb_i \sum_{k=1}^m \bida_k \alpha_k \right\},
 \end{equation}
@@
 \begin{equation}\label{eqn:define-T+(D)}
-	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k=1}^n} 
-\bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^n \alpha_k \bida_k 
+	\Tp(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} 
+\bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^m \alpha_k \bida_k 
 \right\},
@@
 \begin{equation}\label{eqn:define-T-(D)}
-	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k=1}^n \alpha_
-k \bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k s \right\}.
+	\Tm(D) = \left\{ j \in \{1, \ldots, m\}: \bida_j \sum_{k=1}^m \alpha_
+k \bidb_k < \bidb_j \sum_{k=1}^m \alpha_k \bida_k s \right\}.
 \end{equation}

### 2015-07-15 surfaces-write-up/surface-write-up.tex
surfaces: fix some convention defs
edits to relations bound theorems in sections 4/5

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 has a minimal presentation consisting of the $\sum_{i = 0}^{r}
-{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
+{{m + i} \choose {i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has
-relations of the following two types.
+such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has $z$
+many \todo{how many?} relations of the following two types.
 
@@
 \noindent
-for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_j + \sum_{i = 1}
-^n \bida_i c_i = 0$.
+for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
+^n \bida_j c_j = 0$.
 
-To find such a $\beta$, we simply write $\epsilon_j$ as a 
-polynomial in $\epsilon_1, \ldots \epsilon _3$. Furthermore, these
-generate all relations, since they allow us to reduce any $\prod_{i =
-1}^n \epsilon_i^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.
+To find such a $\beta$, we simply write $f_i$ as a 
+polynomial in $f_1, \ldots f_3$. Furthermore, these
+generate all relations, since they allow us to reduce any $\prod_{j =
+1}^n f_j^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.
 
@@
 \[
-	g = \sum_{i=1}^m {f_i}^{c_i}
+	g = \sum_{i=1}^n {f_i}^{c_i}
 \]
@@
 \noindent
-where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^m c_i \bida_i = 0$,
-and $\sum_{i=1}^m c_i \bidb_i = 0$. Then we can view $g$ inside of the
+where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^n c_i \bida_i = 0$,
+and $\sum_{i=1}^n c_i \bidb_i = 0$. Then we can view $g$ inside of the
 lattice $S \subseteq \mathbb{R}^{n + 1}$ given by ordered elements of
 the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge - d \alpha_i$
-for all $i$, $\sum_{i=1}^m c_i \bida_i = 0$, and $\sum_{i = 1}^m c_i \bidb_i =
+for all $i$, $\sum_{i=1}^n c_i \bida_i = 0$, and $\sum_{i = 1}^n c_i \bidb_i =
  0$. From here, determining a spanning set for $(R_D)_d$ reduces to
-finding the extremal rays of $S$ \todo{cite previous lemma}.
+finding the extremal rays of $S$ by Proposition \ref{prop:cone-generation}.
 
-To do this, we extend the method of O'Dorney \todo{cite}. We first
+To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
+We first
 view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
@@
 
-Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_m$.
-We can then intersect the hyperplane $H$ given $\sum_{i=1}^m \bida_i X_i
-= 0$ to get a subspace $S$. The extremal rays of $S$ are given
-by the set of $e_i$ contained in $H$ together with the points of
-intersection $e_{i, j}$ of $H$ and the edges of the simplex
-connecting the $e_i, e_j \not \in H$.
+Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_n$.
+We can intersect $\Delta^{n-1}$ with the hyperplane $H$ given by 
+$\sum_{i=1}^n \bida_i X_i = 0$
+ to get a subspace $S \subseteq \Delta^{n-1}$. The extremal rays of $S$ must lie on the edges of $\Delta$ \todo{Peter: Do we need to cite/argue this, or is it clear?} and are thus given
+by the set of $e_i$ contained in $H$ together with the points $e_{i, j}$ given by intersections of $H$ with edges of the simplex
+connecting $e_i, e_j \not \in H$.
 \todo{more detail above}
 
-We can calculate the following elements of $R_D$ whose
+We can calculate elements of $R_D$ whose
 corresponding lattice points lie on these extremal rays:
@@
 \[
-	\epsilon_{i, j} := (\prod_{k = 1}^m f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
+	\epsilon_{i, j} := (\prod_{k \ne i,j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
 j - \bida_j \bidb_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(\bida_i \bidb_j - 
@@
 above, satisfying the respective conditions.
-$E$ satisfies the conditions of proposition \ref{prop:cone-generation}, so by applying that proposition $R_D$ is generated in 
+The lattice points corresponding to elements of $E$ satisfies the conditions of proposition \ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
 degree less than
@@
 
-Let $x_1, \ldots x_r$ be the generators given by lemma  \ref{Hirzebruch-generators}, and $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through 
+Let $x_1, \ldots x_r$ be the generators of $R_D$ in degree less than $\sigma$ (as given by lemma \ref{Hirzebruch-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
+We can factor $\phi$ through
 \[
@@
 
-Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ less than
-\[
-	2 \sigma
-\]
+Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degrees of generation of $\ker(\chi)$ below
+$2 \sigma$.
 Finally, we calculate the degree of generation of $\psi$:
@@
 \noindent
-for some $d\in \mathbb{N}$, $c_i \ge -\alpha_i d$, $\bida_j + \sum_{i = 1}
-^n \bida_i c_i = 0$, $\bidb_j + \sum_{i=1}^n \bidb_i c_i = 0$, and $\beta_j \in
-k[z_1, \ldots, z_4]$ satisfies $\psi(\beta_j)\in \mathscr{O}(\bida_j,
-\bidb_j)$.
+for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
+^n \bida_j c_j = 0$ and $\bidb_i + \sum_{i=1}^n \bidb_j c_j = 0$.
 
-To find such a $\beta$, we simply write $\epsilon_j$ as a 
-polynomial in $\epsilon_1, \ldots \epsilon _4$. Furthermore, these
-generate all relations, since they allow us to reduce any $\prod_{i =
-1}^n \epsilon_i^{r_i}$ to a canonical form. \todo{add reference to
-earlier description of canonical form.}
+To find such a $\beta$, we simply write $f_i$ as a 
+polynomial in $f_1, \ldots f_4$. Furthermore, these
+generate all relations, since they allow us to reduce any $\prod_{j =
+1}^n f_j^{r_j}$ to the canonical form (see Proposition \ref{prop:cone-generation}).  \todo{Peter: I think the canonical form given in the proposition isn't the one we actually want.}
 

### 2015-07-15 surfaces-write-up/surface-write-up.tex
background mumbo-jumbo

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 
-The work in this paper also yields bounds for certain rings of Hilbert 
+\todo{Hassett-keel, see reference in davids paper about parametrizing $\alpha$ and considering stacky divisors.
+Would want to know whether they are a moduli space, though we just give generators and relations.
+This is one of the few examples other than that of nagata dealing with stacky surfaces.}
+
+The work in this paper also has relations to certain rings of Hilbert 
 modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
@@
 modular forms are modular forms on the Siegel upper half space which are 
-stable under the action of the symplectic group. While in general these 
-quotients can be quite complicated spaces, in the case that the resulting 
-quotient spaces are isomorphic to $\bp^m$ for some $m$, or some Hirzebruch 
-surface, our main result gives a method for bounding the degree of 
-generators and relations for the corresponding rings of Hilbert modular 
-forms and Siegel modular forms. Namely, as in \cite{vzb:stacky}, one can 
-port these modular form groups from the analytic category to the algebraic 
-category, and then view the ring of modular forms as a certain stacky 
-canonical ring on our underlying algebraic space.
+stable under the action of the symplectic group.
+
+Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, which allows one to translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
+We expect that  will similarly allow one to generalize yield an eqivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
+In particular, this will allow us to translate rings of Hilbert Modular forms and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
+Thereby, our techniques would give a bound on generators and relations for Hilbert and Siegel modular forms with certain underlying spaces.
 \todo{include references}
+
+Another closely related topic is the Hassett-Kell program, which aims to describe log canonical models of the form
+\begin{align*}
+	\overline {\mathscr M}_g(\alpha) := \oplus_{d \geq 0}H^0 \left( \overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} + \alpha\delta \rfloor  \right) 
+\end{align*}
+in terms of certain moduli spaces.
+Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of kodaira dimension 1.
+A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of fractional divisors.
+\todo{Add references}
 

### 2015-07-15 surfaces-write-up/surface-write-up.tex

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 \begin{convention}
-Let $\{x_0, \ldots, x_m\}$ be coordinates for $\bp^m$. Let
+Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
 $\vec{v} = (v_0, \ldots, v_m) \in \br^{m + 1}$. Then write
 \[
-	x_{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
+	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
 \]

### 2015-07-15 surfaces-write-up/surface-write-up.tex
thm on effective, add related remarks to 1pt

@@
 
-\ssec{One point on Projective Space}
+\ssec{One Hypersurface on Projective Space}
 \label{ssec:proj-one-point}
@@
 \begin{rem}
+\label{rem:proj-veronese}
 Remark about how we can assume divisor only consists of hyperplanes
@@
 	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(1)}}} \cdots
-	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(\ell_1)}}}
+	(F_i^{\vec{v}_{(\ell_1)}})^{g_{\vec{v}_{(\ell_1)}}}
 	(F_{i + 1}^{\vec{w}_{(1)}})^{g_{\vec{w}_{(1)}}} \cdots
@@
 
-\todo{change thm to be inductive for adding pts, giving result on
-effective divisors?}
-\todo{remark on not doing two points}
+\begin{rem}
+\label{rem:proj-two-points}
+Note that we cannot extend this result to the case when
+$D$ is supported at two hypersurfaces with arbitrary rational
+coefficients in the same manner that O'Dorney does for the
+$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
+in Example ~\ref{eg:hyperplane}, the degrees of generation of the
+canonical ring of a general $\bq$-divisor containing two
+hyperplanes cannot be bounded so tightly. The two-point
+$\bp^1$ result leverages particular facts about the structure of
+$\bp^1$.
+\end{rem}
+
+\begin{rem}
+\label{rem:proj-one-point-ind}
+Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
+can be immediately generalized to work inductively. If $D = D' + H$
+for some hyperplane $H$, then we can use the proof above to show
+the canonical ring $R_D$ is generated over $R_D'$ by the same
+generators and with the same relations given in Theorem
+~\ref{thm:proj-one-points}.
+\end{rem}
+
+\begin{thm}
+\label{thm:proj-effective}
+Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
+$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i H_i$, with $\alpha_i =
+\frac{p_i}{q_i} \in \bq$ and each $H_i$ a hypersurface of
+$\bp^m$, be an effective divisor on $\bp^m$.
+
+Then the canonical ring
+\[
+	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
+\]
+
+\noindent
+is generated in degrees up to $\max_{1 \leq i \leq n}{q_i}$ with
+relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$
+\end{thm}
+
+\begin{proof}
+First, we apply Remark ~\ref{rem:proj-veronese} to reduce the
+problem to letting each $H_i$ be a hyperplane of $\bp^m$.
+Then, the proof follows from applying Remark
+~\ref{rem:proj-one-point-ind} inductively on a one-hyperplane case
+from Theorem ~\ref{them:proj-one-point}.
+\end{proof}
 

### 2015-07-15 surfaces-write-up/surface-write-up.tex
minor edits to beginning general lemmata

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 \todo{write more about hassett keel program}
-\cite{hassett:classical-and-minimal-models}
-Hasse keel program, birational map from $proj R(K + \Delta)$ to $M_2$, they showed finite generation, we're giving explicit generators and bounds.
 
@@
 
-Another closely related topic is the Hassett-Kell program, which aims to describe log canonical models of the form
+Another closely related topic is the Hassett-Kell program 
+initiated in \todo{ was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
 \begin{align*}
@@
 \todo{Add references}
-
-\todo{Possibly keep or delete following example}
-Example: the Siegel 2-upper half plane $\bc^2/\Lambda$ Note that $\bc^2/\Lambda$ is algebraic if and only if there exists a hermitial form on $\Lambda$.
-Then, $Sp_{2g}$ acts on algebraic lattices.
-The quotient by this gives you the space of abelian varieties.
-This might be an open subset of projective space, according to David, 65$\%$.
 
@@
 \label{prop:cone-generation}
-Let $n,t \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$ and let $k_i^j \in \bz$ with $1 \leq i \leq n, 1 \leq j \leq t.$ Define
+Let $n \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$, and let $a_i, b_i \in \bz$ with $1 \leq i \leq n.$ Define
 \begin{align*}
-	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
+	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}a_i = \sum_{i=1}^{n}b_i = 0\}
 \end{align*}
@@
 $e_1, \ldots, e_t$.  Then, as a semigroup, $\Sigma$ is generated by
-elements whose first coordinate is less than $\sum_{i = 1}^{n} \pdeg_i$
+elements whose first coordinate is less than $\sum_{i = 1}^{t} \pdeg_i$
 . Furthermore, every element $\sigma \in \Sigma$ can be written in
@@
 coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,
-\ldots, w_t \in \bz$.
+\ldots, w_t \in \bz_{\geq 0}$.
 \end{prop}
@@
 \begin{proof}
-By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{t} r_i e_i$ with $r_i \in \br$.
+By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_{i=1}^{t} r_i e_i$ with $r_i \in \br$.
 Let $\{r\} := r - \lfloor r \rfloor$ denote the fractional part of $r$.
 Let $\lambda = \sum_{i=1}^{t}\{r_i\}$.
-Hence, we can write $\sigma = \lambda + \sum_{i=1}^{t}\lfloor r_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_t$, which all have first coordinate less than $\sum_{i=1}^{t}r_i$.
-Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{t}r_i$.
+Whence, we can write $\sigma = \lambda + \sum_{i=1}^{t}\lfloor r_i \rfloor e_i.$ Consequently, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_t$, which all have first coordinate less than $\sum_{i=1}^{t}r_i$.
+Ergo, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{t}r_i$.
 \end{proof}

### 2015-07-16 surfaces-write-up/surface-write-up.tex
ref fixes

@@
 generators and with the same relations given in Theorem
-~\ref{thm:proj-one-points}.
+~\ref{thm:proj-one-point}.
 \end{rem}
@@
 ~\ref{rem:proj-one-point-ind} inductively on a one-hyperplane case
-from Theorem ~\ref{them:proj-one-point}.
+from Theorem ~\ref{thm:proj-one-point}.
 \end{proof}

### 2015-07-16 surfaces-write-up/surface-write-up.tex
fixed equation names
surfaces: first writing of veronese remark

@@
 
-\ssec{One Hypersurface on Projective Space}
+\ssec{Effective Divisors of Hypersurfaces on Projective Space}
 \label{ssec:proj-one-point}
@@
 \label{rem:proj-veronese}
-Remark about how we can assume divisor only consists of hyperplanes
-by taking the Veronese embedding.
-\todo{write}
+For any divisor $D = \sum_{i = 0}^{n} \alpha_i C_i$ on $\bp^m$
+with each $C_i$ a hypersurface, we can use the Veronese mappings
+to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
+with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are hypersurfaces
+in $\bp^{m'}$.
 \end{rem}
@@
 Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i H_i$, with $\alpha_i =
-\frac{p_i}{q_i} \in \bq$ and each $H_i$ a hypersurface of
+$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i C_i$, with $\alpha_i =
+\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
 $\bp^m$, be an effective divisor on $\bp^m$.
@@
 We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
-\begin{equation}\label{eqn:relations-psi}
+\begin{equation}\label{eqn:relations-psi-P-n}
 	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
@@
 We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
-\begin{equation}\label{eqn:relations-psi}
+\begin{equation}\label{eqn:relations-psi-hirz}
 	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edited projective preliminaries

--- 2015-07-15 surfaces-write-up/surface-write-up.tex
@@
 \begin{align*}
-	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}a_i = \sum_{i=1}^{n}b_i = 0\}
+	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}a_i = \sum_{i=1}^{n}b_i = 0 \right \}
 \end{align*}
@@
 . Furthermore, every element $\sigma \in \Sigma$ can be written in
-a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with the first
-coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,
+a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with $\lambda = \sum_{i=1}^{r}s_i e_i$ with $0 \leq s_i < 1,$ the first
+coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i,$ and $w_1,
 \ldots, w_t \in \bz_{\geq 0}$.
@@
 \begin{align*}
-	\Sigma = \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
-\end{align*}
-In this case, we can factor $\phi$ through maps $\chi, \psi$ defined by
+	\Sigma = \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i = 0 \rangle. 
+\end{align*}
+In this case, we can factor $\phi$ as a composition of $\chi$ and $\psi$ defined by
 \todo{Make this have mapsto on bottom}
@@
 \bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}
+x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
@@
 \begin{proof}
-Note that we have an exact sequence
+First, we show there is an exact sequence
 \[
 \begin{tikzcd}
-0 \ar r & \ker \chi \ar r & \ker \phi \ar r & \ker \psi \ar r & 0.
+0 \ar {r} & \ker \chi \ar{r}{\rho} & \ker \phi \ar {r}{\tau} & \ker \psi \ar r & 0.
 \end{tikzcd}
 \]
-To see this, note that the left map is an inclusion because $\phi = \chi \circ \psi$.
-Next, the right map, given by $\chi|_{\ker \phi}:\ker \phi \rightarrow \ker \psi$ is a surjection, again because $\phi = \chi \circ \psi$.
-The composition of the two maps is $0$ by definition of the kernel of $\chi$.
-Finally, if $a \in \ker \phi$ and $a$ lies in the kernel of the right map, then by definition $\chi(a) = 0$.
+To see this, note that $\rho$ is injective and $\tau$ is surjective\ because $\phi = \chi \circ \psi$.
+Additionally, $\tau \circ \rho = 0$ by definition of the kernel of $\chi$.
+Finally, if $a \in\ker \tau$, then by definition $\chi(a) = 0,$ so $a \in \im \rho$.
+
+This shows that lifts of generators of $\ker \psi$ together with images of generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
 \end{proof}
@@
 \label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ has a system of generators in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ is generated in degrees up to $2(\sum_{i=1}^{r}d_r-1)$.
 \end{lem}
@@
 Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
-Now, letting $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ so that we can write $\lambda_i = \sum_{i=1}^{r}\bida_i e_i$ with $0 \leq \bida_i < 1$ for all $i$.
-Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in the above canonical form, yielding a relation in degree at most $\deg \lambda_i + \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$ Furthermore, these relations generate all relations, as one can apply a sequence of these relations to put any $\sigma \in \Sigma$ into canonical form.
+Now, let $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be written in the form $\lambda_i = \sum_{i=1}^{r}r_i e_i$ with $0 \leq r_i < 1.$ Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in the above canonical form, yielding a relation in degree at most $\deg \lambda_i + \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$ Furthermore, these relations generate all relations, as one can apply a sequence of these relations to put any $\sigma \in \Sigma$ into canonical form $\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Proposition ~\ref{prop:cone-generation}.
 \end{proof}
@@
 \end{align*}
-where $\alpha_i \in \bq$ and $\deg D_i = \bida_i$.
-Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$.
-\todo{Should this say $D_i$ is a Cartier divisor.
-Also should we say $\deg(f_i)= \bida_i$ rather than $\deg(D_i)$.}
-We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$. \todo{Peter: Make reference to ghost points here?}
+where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. Let $D_i$ be Cartier divisors such that $D_i = V(f_i)$.
+We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$.
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edits up to effective hypersurfaces

@@
 \label{align:pm-span}
-\sum_{i=1}^{n} c_i \cdot \bida_i \cdot f_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=1}^{n} c_i \cdot \bida_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 However we know $h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show that those functions satisfying condition ~\eqref{align:pm-basis} are independent.
-This follows from the assumption that $f_0,\ldots, f_n$ form a basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $ monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor $ rational functions.
+This follows from the assumption that $f_0,\ldots f_n$ form a basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $ monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor $ rational functions.
 \end{proof}
 
-We first restrict attention to the case $n=1$, so $D = \alpha D_i$.
-
-\ssec{Effective Divisors of Hypersurfaces on Projective Space}
+\ssec{Effective Divisors on Projective Space}
 \label{ssec:proj-one-point}
+
+In this subsection, we restrict attention to the case of effective divisors.
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edit curves with brian's new edits, veronese in P^n

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 \label{ssec:proj-one-point}
-
-\begin{rem}
-\label{rem:proj-veronese}
-For any divisor $D = \sum_{i = 0}^{n} \alpha_i C_i$ on $\bp^m$
-with each $C_i$ a hypersurface, we can use the Veronese mappings
-to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
-with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are hypersurfaces
-in $\bp^{m'}$.
-\end{rem}
+\todo{intro}
 
@@
 \label{rem:proj-one-point-ind}
-Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
+The method of proof for Theorem ~\ref{thm:proj-one-point}
 can be immediately generalized to work inductively. If $D = D' + H$
@@
 
+\begin{rem}
+\label{rem:proj-veronese}
+For any divisor $D = \sum_{i = 0}^{n} \alpha_i C_i$ on $\bp^m$
+with each $C_i$ a hypersurface and $\alpha_i \in \br$, we can use
+the Veronese mappings to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
+with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are 
+hypersurfaces
+in $\bp^{m'}$.
+\end{rem}
+
 \begin{thm}
@@
 \begin{proof}
-First, we apply Remark ~\ref{rem:proj-veronese} to reduce the
-problem to letting each $H_i$ be a hyperplane of $\bp^m$.
-Then, the proof follows from applying Remark
-~\ref{rem:proj-one-point-ind} inductively on a one-hyperplane case
-from Theorem ~\ref{thm:proj-one-point}.
+We derive the result from the following inductive argument.
+If $n = 0$, i.e.~ $D = 0$, then we are done.
+Now, we look to inductively add hypersurfaces.
+If $D' = \sum_{i = 0}^{n} \alpha_i C_i$ is some $\bq$-divisor
+on $\bp^m$, then we look at $D = D' + C$ where $C$ is a
+hypersurface of degree $\pdeg$. Now use the Veronese mapping
+to view $D$ as a divisor on $\bp^{m ({m + \pdeg} \choose \pdeg - 1)}$
+and the image of $C$ as the intersection of a Veronese variety
+with a hyperplane. Then we can reduce inductively adding hypersurfaces
+to the case of adding hyperplanes. However, this is accomplished
+by the method used in Theorem ~\ref{thm:proj-one-point} in an
+inductive manner as mentioned in Remark ~\ref{rem:proj-one-point-ind}.
 \end{proof}

### 2015-07-16 surfaces-write-up/surface-write-up.tex
curves remove bad fix from before, remove rem

@@
 ~\ref{thm:proj-one-point}.
-\end{rem}
-
-\begin{rem}
-\label{rem:proj-veronese}
-For any divisor $D = \sum_{i = 0}^{n} \alpha_i C_i$ on $\bp^m$
-with each $C_i$ a hypersurface and $\alpha_i \in \br$, we can use
-the Veronese mappings to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
-with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are 
-hypersurfaces
-in $\bp^{m'}$.
 \end{rem}

### 2015-07-16 surfaces-write-up/surface-write-up.tex
minor intro edit

@@
 modular forms are both to higher dimensions variables. In the case of 
-Hilbert Modular forms, one considers modular forms on an $m$ fold product 
-of upper half planes, which transform under the action of finite index 
+Hilbert Modular forms, one considers modular forms on a product of $m$
+upper half planes, which transform under the action of finite index 
 subgroups of the groups of positive determinant matrices. Similarly, Siegel 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
intro add relation to curve canrings, add lrz to bib

@@
 
-Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, which allows one to translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
+By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, one can translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
 We expect that  will similarly allow one to generalize yield an eqivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
@@
 
-Another closely related topic is the Hassett-Kell program 
+Another closely related topic is the Hassett-Keel program 
 initiated in \todo{ was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
@@
 \todo{Add references}
+
+Furthermore, this work extends the study of canonical rings of
+$\bq$-divisors on curves, as done by O'Dorney \cite{dorney:canonical},
+Voight--Zureick-Brown \cite{vzb:stacky}, and Landesman--Ruhm--Zhang
+\cite{lrz:spin-cring}, to general projective space and Hirzebruch
+surfaces.
+
+\todo{more!}
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edits to projective space section

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 \begin{convention}
-Write
-\begin{align*}
-	D = \sum_{i=1}^{n}\alpha_i D_i.
-\end{align*}
-where $\alpha_i \in \bq$. \todo{Peter: What are the $D_i$'s.}
+Notate a fractional (weil) divisor
+\begin{align*}
+	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes \bq.
+\end{align*}
+where $\alpha_i \in \bq$ and $D_i \in \di X$ is an irreducible divisor.
 \end{convention}
@@
 However we know $h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show that those functions satisfying condition ~\eqref{align:pm-basis} are independent.
-This follows from the assumption that $f_0,\ldots, f_n$ form a basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $ monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor $ rational functions.
+This follows from the assumption that $f_0,\ldots f_n$ form a basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $ monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor $ rational functions.
 \end{proof}
 
-We first restrict attention to the case $n=1$, so $D = \alpha D_i$.
-
-\ssec{Effective Divisors of Hypersurfaces on Projective Space}
+\ssec{Effective Divisors on Projective Space}
 \label{ssec:proj-one-point}
-\todo{intro}
+
+In this subsection, we restrict attention to the case of effective divisors.
+
+\begin{rem}
+\label{rem:proj-veronese}
+For any divisor $D = \sum_{i = 0}^{n} \alpha_i D_i$ on $\bp^m$
+with each $D_i$ a hypersurface, we can use the Veronese mappings
+to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
+with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are hypersurfaces
+in $\bp^{m'}$.
+\end{rem}
 
@@
 \label{rem:proj-one-point-ind}
-The method of proof for Theorem ~\ref{thm:proj-one-point}
+Note that the method of proof for Theorem ~\ref{thm:proj-one-point}
 can be immediately generalized to work inductively. If $D = D' + H$
@@
 Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i C_i$, with $\alpha_i =
-\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
+$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i D_i$, with $\alpha_i =
+\frac{p_i}{q_i} \in \bq$ and each $D_i$ a hypersurface of
 $\bp^m$, be an effective divisor on $\bp^m$.
@@
 \begin{proof}
-We derive the result from the following inductive argument.
-If $n = 0$, i.e.~ $D = 0$, then we are done.
-Now, we look to inductively add hypersurfaces.
-If $D' = \sum_{i = 0}^{n} \alpha_i C_i$ is some $\bq$-divisor
-on $\bp^m$, then we look at $D = D' + C$ where $C$ is a
-hypersurface of degree $\pdeg$. Now use the Veronese mapping
-to view $D$ as a divisor on $\bp^{m ({m + \pdeg} \choose \pdeg - 1)}$
-and the image of $C$ as the intersection of a Veronese variety
-with a hyperplane. Then we can reduce inductively adding hypersurfaces
-to the case of adding hyperplanes. However, this is accomplished
-by the method used in Theorem ~\ref{thm:proj-one-point} in an
-inductive manner as mentioned in Remark ~\ref{rem:proj-one-point-ind}.
+First, we apply Remark ~\ref{rem:proj-veronese} to reduce the
+problem to letting each $H_i$ be a hyperplane of $\bp^m$.
+Then, the proof follows from applying Remark
+~\ref{rem:proj-one-point-ind} inductively on a one-hyperplane case
+from Theorem ~\ref{thm:proj-one-point}.
 \end{proof}
@@
 \ssec{Bounds for Arbitrary Divisors on Projective Space}
-\begin{rem}
-When $\langle f_1, \ldots, f_r \rangle = \langle x_0, \ldots, x_n \rangle$ (the irrelevant ideal), we may directly use the hypersurface method by considering $x_0, \ldots, x_n$ instead of the $f_i$'s.
-However, when $\sqrt{\langle f_1, \ldots, f_r \rangle} = \langle x_0, \ldots, x_n \rangle$ (or the saturation), we cannot obtain the same result from our modification of O'Dorney's method as seen in Example ~\ref{eg:radical}.
-Instead we must use ghost points and hypersurfaces.
-\end{rem} \todo{Peter: What is the purpose of this remark?  The only method we have extends to ghost points so that this is satisfied.}
 
@@
 
-Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 + x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) + \frac{1}{596}V(x_1^2 + x_2^2 + x_3^2)$.
-In degree $355216 = 5* 7 * 17 * 596$, this has dimension $10$.
+Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 + x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) - \frac{1}{596}V(x_1^2 + x_2^2 + x_3^2)$.
+In degree $355216 = 5 \cdot 7 \cdot 17 \cdot 596$, this has dimension $10$.
 \todo{Clarify what this example means by the lattice approach}
@@
 
-We now move on offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
-
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+We now offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
+
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$.
+\todo{Aaron: Do we want to make the convention somewhere that $f_1,\ldots, f_{m+1}$ generate $O(1)$?}
+
 \begin{lem} \label{P-m-generators}
-$R_D$ is generated in degree at most $\sum_{i=1}^n \ell_i a_i$.
+$R_D$ is generated in degrees up to $\sum_{i=1}^n \ell_i a_i.$
 % and relations in degree at most  .\todo{insert numbers}
@@
 \begin{align}\label{eqn:Sigma-def}
-	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}.
+	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0 \right \}.
 \end{align}
@@
 \begin{equation}\label{defn:e_i-P-n}
-	e_i = (\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j, -\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i)
+	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j, -\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
 \end{equation}
 for each $i\in \{1, \ldots n\}$.
-Viewed inside of $R_D$, we have $e_i$ corresponding to
+Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
+\[
+	\sum_{i=1}^n \ell_i a_i.
+\]
+\end{proof}
+
+\begin{rem}
+\label{rem:pm-extremal-rays}
+Note for future reference that the extremal rays of the cone $\Sigma$, as defined in the proof of Lemma ~\ref{P-m-generators} correspond to the elements
 \begin{equation}\label{eqn:epilon-def-P-m}
@@
 \end{equation}
-Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
-\[
-	\sum_{i=1}^n \ell_i a_i.
-\]
-\end{proof}
+\end{rem}
 
 Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i \bida_i$ (given by lemma \ref{P-m-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
-We can factor $\phi$ through
-\[
-	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in \mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+We can factor $\phi$ through the semigroup ring
+\[
+	\bk[\Sigma] =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in \mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i \rangle. 
 \]
@@
 
-By Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
-\[
-	2 \sum_{i=1}^n \ell_i a_i.
-\]
-Finally, we calculate the degree of generation of $\psi$:
+By Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ and we next calculate the degree of generation of $\ker \psi$:
 
 \begin{lem}\label{P-m-relations-psi}
-$\ker(\psi)$ is generated in degree less than
+$\ker(\psi)$ is generated in degrees up to
 \[
@@
 \begin{proof}
-We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
+We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
 \begin{equation}\label{eqn:relations-psi-P-n}
@@
 
-To find such a $\beta$, we simply write $f_i$ as a 
-polynomial in $f_1, \ldots f_3$. Furthermore, these
+To find such a $\beta_i$, we simply write $f_i$ as a 
+polynomial in $f_1, \ldots f_{m+1}$. Furthermore, these
 generate all relations, since they allow us to reduce any $\prod_{j =
@@
 \begin{thm}\label{P-m-generators/relations}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 Then $R_D$ is generated in degree at most 
@@
 \section{Canonical Rings on Hirzebruch surfaces}
-Let $D=\sum_{i=1}^n \alpha_i C_i \in \mathbb{Q} \otimes \di(\hirz_
-k)$ for some irreducible curves $C_1, \ldots C_n$ of $\hirz_k$, such
-that $C_1, \ldots, C_4$ are independent curves with bi-degrees $(1,0)
-, (1,0), (0,1)$, and $(0,1)$ respectively. Let $C_i = V(f_i)$ where
+Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
+k).$ such
+that $D_1, \ldots, D_4$ are distinct divisors with bi-degrees $(1,0)
+, (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
 $f_i \in \mathscr{O}(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
@@
 \begin{thm}\label{Hirzebruch-generators/relations}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+Let $D = \sum_{i=1}^n \alpha_i D_i$ for curves $D_i$ on $\hirz_k$.  Let $D_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
@@
 \section{Conclusion}
-This paper extends the work of O'Dorney on $\mathbb{P}^1$ to $\mathbb{P}^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
-The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar ideas to O'Dorney's method on $\mathbb{P}^1$.
-
-We can view $\hirz_0$ as $\mathbb{P}^1\times \mathbb{P}^1$ and more generally $\hirz_k$ as a $\mathbb{P}^1$ bundle over $\mathbb{P}^1$.
-One might hope that similar ideas could be generalized to all bundles.
-Specifically:
+This paper extends the work of O'Dorney on $\bp^1$ to $\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
+The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar ideas to O'Dorney's method on $\bp^1$.
+
+We can view $\hirz_0$ as $\bp^1\times \bp^1$ and more generally $\hirz_k$ as a $\bp^1$ bundle over $\bp^1$.  One might hope that similar ideas could be generalized to all bundles.  Specifically:
 \begin{question}\label{qn:general-product/bundle}
@@
 
-Alternatively, we can view $\hirz_1$ as $\mathbb{P}^2$ blown up at a point.  This suggests the following question:
+Alternatively, we can view $\hirz_1$ as $\bp^2$ blown up at a point.  This suggests the following question:
 \begin{question}\label{qn:general-blowup}

### 2015-07-16 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
add colon

@@
 
-Let $X$ be a smooth proper geometrically-integral algebraic curve of genus $g$ over a field $\Bk$.
+Let $X$ be a smooth proper geometrically-connected algebraic curve of genus $g$ over a field $\Bk$.
 It is well known that the canonical sheaf $\Omega _X,$ with
@@
 \begin{align*}
-	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
+	R(X, K_X) := \bigoplus_{d \geq 0} H^0(X, dK_X),
 \end{align*}
@@
 \label{defn:order-sup}
-Let $D \in \di \sx.$ If $z$ is a rational section of $\sco(D)$ denote the order of
+Let $D \in \di \sx.$ If $z \neq 0$ is a rational section of $\sco(D)$ denote the order of
 zero of $z$ at $P$ by $\ord_P^D(z)$.
@@
 and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
+$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals of relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 

### 2015-07-16 surfaces-write-up/surface-write-up.tex

@@
 In this subsection, we restrict attention to the case of effective divisors.
-
-\begin{rem}
-\label{rem:proj-veronese}
-For any divisor $D = \sum_{i = 0}^{n} \alpha_i D_i$ on $\bp^m$
-with each $D_i$ a hypersurface, we can use the Veronese mappings
-to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
-with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are hypersurfaces
-in $\bp^{m'}$.
-\end{rem}
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
surfaces: add main results, minor other edits

@@
 modular forms are both to higher dimensions variables. In the case of 
-Hilbert Modular forms, one considers modular forms on a product of $m$
+Hilbert modular forms, one considers modular forms on a product of $m$
 upper half planes, which transform under the action of finite index 
@@
 By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, one can translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
-We expect that  will similarly allow one to generalize yield an eqivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
-In particular, this will allow us to translate rings of Hilbert Modular forms and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
+We expect that  will similarly allow one to generalize yield an equivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
+In particular, this will allow us to translate rings of Hilbert modular forms and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
 Thereby, our techniques would give a bound on generators and relations for Hilbert and Siegel modular forms with certain underlying spaces.
@@
 in terms of certain moduli spaces.
-Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of kodaira dimension 1.
+Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of Kodaira dimension 1.
 A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of fractional divisors.
@@
 \todo{more!}
+
+\ssec{Main Results}
+
+\todo{put main results! use restate, maybe?}
+
+\begin{thm}
+\label{thm:proj-effective-intro}
+Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
+$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i C_i$, with $\alpha_i =
+\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
+$\bp^m$, be an effective divisor on $\bp^m$.
+
+Then the canonical ring
+\[
+	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
+\]
+
+\noindent
+is generated in degrees up to $\max_{1 \leq i \leq n}{q_i}$ with
+relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$
+\end{thm}
+
+\todo{transition}
+
+\begin{thm}
+\label{proj-generators-relations-intro}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Then $R_D$ is generated in degree at most 
+\[
+	\sum_{i=1}^n \ell_i a_i
+\]
+with relations generated in degree at most
+\[
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+\]
+\end{thm}
+
+\todo{transition}
+
+\begin{thm}
+\label{hirz-generators-relations}
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
+linear polynomials in $y_0$ and $y_1$.
+Then $R_D$ is generated in degree less than 
+\[
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in \Tp(D) \atop
+	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}
+\]
+with relations generated in degree less than 
+\[
+	\max(2 \sigma, \sigma + \tau)
+\]
+where
+\[
+	\tau = \sigma
+	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+\]
+\end{thm}
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
some edits on proof of relations

@@
 $\ker(\psi)$ is generated in degrees up to
-\[
+\begin{align}
+\label{eqn:pm-relation-degree}
 	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
-\]
+\end{align}
+
 \end{lem}
@@
 We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
-\begin{equation}\label{eqn:relations-psi-P-n}
+\begin{equation}\label{eqn:pm-relations-psi}
 	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
@@
 
-To find such a $\beta_i$, we simply write $f_i$ as a 
-polynomial in $f_1, \ldots f_{m+1}$. Furthermore, these
+We define the $\beta_i$ above so that $\beta_i$ is the expansion of $f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m+1}]$.
+Furthermore, the relations given in Equation ~\eqref{eqn:pm-relations-psi}
 generate all relations, since they allow us to reduce any $\prod_{j =
@@
 
-We now fix $z_i$ and bound the degree of generation of this set of relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$.
+For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. 
+To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by Equation ~\eqref{eqn:pm-relation-degree}.
 We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.

### 2015-07-16 surfaces-write-up/surface-write-up.tex
surfaces: massive relabelling and fixing refs

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 Another closely related topic is the Hassett-Keel program 
-initiated in \todo{ was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
+initiated in \todo{was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
 \begin{align*}
@@
 \begin{thm}
-\label{hirz-generators-relations}
+\label{lem:hirz-generators-relations}
 Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
@@
 \noindent
-Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
+Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
 \end{rem}
@@
 
-\begin{lem} \label{P-m-generators}
+\begin{lem} \label{lem:proj-generators}
 $R_D$ is generated in degrees up to $\sum_{i=1}^n \ell_i a_i.$
@@
 We note that $\Sigma$ has extremal rays given by the lattice points 
-\begin{equation}\label{defn:e_i-P-n}
+\begin{equation}\label{defn:e-i-proj}
 	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j, -\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
@@
 for each $i\in \{1, \ldots n\}$.
-Therefore, applying proposition \ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
+Therefore, applying Proposition ~\ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
 \[
@@
 \label{rem:pm-extremal-rays}
-Note for future reference that the extremal rays of the cone $\Sigma$, as defined in the proof of Lemma ~\ref{P-m-generators} correspond to the elements
-\begin{equation}\label{eqn:epilon-def-P-m}
+Note for future reference that the extremal rays of the cone $\Sigma$, as defined in the proof of Lemma ~\ref{lem:proj-generators} correspond to the elements
+\begin{equation}
+\label{eqn:epsilon-def-proj}
 	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
@@
 
-Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i \bida_i$ (given by lemma \ref{P-m-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
+Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i \bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
 We can factor $\phi$ through the semigroup ring
@@
 
-By Lemma \ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ and we next calculate the degree of generation of $\ker \psi$:
-
-\begin{lem}\label{P-m-relations-psi}
+By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ and we next calculate the degree of generation of $\ker \psi$:
+
+\begin{lem}
+\label{proj-relations-psi}
 $\ker(\psi)$ is generated in degrees up to
@@
 \end{lem}
+
 \begin{proof}
 We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
-\begin{equation}\label{eqn:relations-psi-P-n}
+\begin{equation}
+\label{eqn:relations-psi-proj}
 	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_i}$ to a canonical form as given by Proposition \ref{prop:cone-generation}.
+1}^n f_j^{r_i}$ to a canonical form as given by Proposition ~\ref{prop:cone-generation}.
 
@@
 Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
-Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e_i-P-n}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
+Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Definition ~\ref{defn:e-i-proj}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
 
@@
 
-Whenever some $r_j \ge 1$, we can generate the relation at hand by one of lower degree by factoring out a copy of $\epsilon_j$ (see Equation \ref{eqn:epilon-def-P-m}).
+Whenever some $r_j \ge 1$, we can generate the relation at hand by one of lower degree by factoring out a copy of $\epsilon_j$ (see Equation ~\ref{eqn:epsilon-def-proj}).
 Therefore, $\ker(\psi)$ is generated in degrees less than
@@
 
-Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $2\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma \ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
+Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $2\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
 \[
@@
 
-\begin{thm}\label{P-m-generators/relations}
+\begin{thm}
+\label{lem:proj-generators-relations}
 Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
@@
 Define 
-\begin{equation}\label{eqn:define-T=(D)}
+\begin{equation}
+\label{eqn:define-T=(D)}
 	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
@@
 
-\begin{equation}\label{eqn:define-T+(D)}
+\begin{equation}
+\label{eqn:define-T+(D)}
 	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k=1}^n} 
@@
 and
-\begin{equation}\label{eqn:define-T-(D)}
-	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k=1}^n \alpha_
-k \bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k s \right\}.
+\begin{equation}
+\label{eqn:define-T-(D)}
+	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k=1}^n \alpha_k
+	\bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k s \right\}.
 \end{equation}
@@
 
-\begin{lem}\label{Hirzebruch-generators}
+\begin{lem}
+\label{lem:hirz-generators}
 $R_D$ is generated in degree at most
@@
  0$. From here, determining a spanning set for $(R_D)_d$ reduces to
-finding the extremal rays of $S$ by Proposition \ref{prop:cone-generation}.
+finding the extremal rays of $S$ by Proposition ~\ref{prop:cone-generation}.
 
@@
 above, satisfying the respective conditions.
-The lattice points corresponding to elements of $E$ satisfies the conditions of proposition \ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
+The lattice points corresponding to elements of $E$ satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
 degree less than
@@
 
-Let $x_1, \ldots x_r$ be the generators of $R_D$ in degree less than $\sigma$ (as given by lemma \ref{Hirzebruch-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
+Let $x_1, \ldots x_r$ be the generators of $R_D$ in degree less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
 We can factor $\phi$ through
@@
 
-Applying Lemma \ref{lem:bound-ker-chi}, we can bound the degrees of generation of $\ker(\chi)$ below
+Applying Lemma ~\ref{lem:bound-ker-chi}, we can bound the degrees of generation of $\ker(\chi)$ below
 $2 \sigma$.
@@
 We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
-\begin{equation}\label{eqn:relations-psi-hirz}
+\begin{equation}
+\label{eqn:hirz-relations-psi}
 	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_j}$ to the canonical form (see Proposition \ref{prop:cone-generation}).  \todo{Peter: I think the canonical form given in the proposition isn't the one we actually want.}
+1}^n f_j^{r_j}$ to the canonical form (see Proposition ~\ref{prop:cone-generation}).  \todo{Peter: I think the canonical form given in the proposition isn't the one we actually want.}
 
 Note that we can view the relations from Equation
-\ref{eqn:relations-psi} as an element of $S$ given
+~\ref{eqn:hirz-relations-psi} \todo{is this the right ref?} as an element of $S$ given
 by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  Let $S'\subseteq (\mathbb{R}_{\ge 0})^{n+1}$ be the
@@
 
-\begin{thm}\label{Hirzebruch-generators/relations}
+\begin{thm}
+\label{thm:hirz-generators-relations}
 Let $D = \sum_{i=1}^n \alpha_i D_i$ for curves $D_i$ on $\hirz_k$.  Let $D_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
@@
 We can view $\hirz_0$ as $\bp^1\times \bp^1$ and more generally $\hirz_k$ as a $\bp^1$ bundle over $\bp^1$.  One might hope that similar ideas could be generalized to all bundles.  Specifically:
-\begin{question}\label{qn:general-product/bundle}
+\begin{question}
+\label{qn:general-product-bundle}
 Suppose $X$ and $Y$ are schemes.
@@
 \end{question}
+
 An immediate obstruction to this is the fact that we critically used the fact that $\hirz_k$ has well-defined bi-degrees.
@@
 Alternatively, we can view $\hirz_1$ as $\bp^2$ blown up at a point.  This suggests the following question:
-\begin{question}\label{qn:general-blowup}
+\begin{question}
+\label{qn:general-blowup}
 Let $X$ be a scheme.
@@
 \end{question}
-Fortunately, the picard group of $X$ blown up at a point is the same as that of $X$ times an additional copy of $\bz$.
-Perhaps analyzing the argument from \ref{Hirzebruch-generators/relations} in the case of $\hirz_k$ from the perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by the blowup, might suggest a general method for blowups.
-
-Answering question \ref{qn:general-blowup} would in fact provide an answer for all rational surfaces, via the minimal model program for surfaces \todo{Reference}.
-One might to provide an analogous result to \ref{Hirzebruch-generators/relations} in the case of all minimal surfaces:
-\begin{question}\label{qn:general-minimal-surface}
+
+Fortunately, the Picard group of $X$ blown up at a point is the same as that of $X$ times an additional copy of $\bz$.
+Perhaps analyzing the argument from Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not the theorem with the same name} in the case of $\hirz_k$ from the perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by the blowup, might suggest a general method for blowups.
+
+Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for all rational surfaces, via the minimal model program for surfaces \todo{Reference}.
+One might to provide an analogous result to Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not the theorem with the same name} in the case of all minimal surfaces:
+\begin{question}
+\label{qn:general-minimal-surface}
 Can we describe generators and relations of $R_D$ for $D$ a divisor on an arbitrary minimal surface $X$?

### 2015-07-16 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex

@@
 and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideals of relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
+$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideal of relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
 Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 

### 2015-07-16 surfaces-write-up/surface-write-up.tex

@@
 \begin{lem}
-\label{proj-relations-psi}
+\label{lem:proj-relations-psi}
 $\ker(\psi)$ is generated in degrees up to
-\[
+\begin{align}
+\label{eqn:pm-relation-degree}
 	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
-\]
+\end{align}
+
 \end{lem}
@@
 
-To find such a $\beta_i$, we simply write $f_i$ as a 
-polynomial in $f_1, \ldots f_{m+1}$. Furthermore, these
+We define the $\beta_i$ above so that $\beta_i$ is the expansion of $f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m+1}]$.
+Furthermore, the relations given in Equation ~\eqref{eqn:pm-relation-degree}
 generate all relations, since they allow us to reduce any $\prod_{j =
@@
 
-We now fix $z_i$ and bound the degree of generation of this set of relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$.
+For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. 
+To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by Equation ~\eqref{eqn:pm-relation-degree}.
 We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.
 Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
-Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Definition ~\ref{defn:e-i-proj}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
+Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e-i-proj}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edited projective non-1-point sections

@@
 \maketitle
-
+\todo{make title shorter so it doesn't overlap with page numbers}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
-
-\todo{write more about hassett keel program}
 
@@
 \end{align}
+\todo{Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.}
 We note that $\Sigma$ has extremal rays given by the lattice points 
@@
 For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. 
-To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by Equation ~\eqref{eqn:pm-relation-degree}.
-We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n)$ where $d$ is its degree.
-Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
-Then we see $\Sigma_i$ is contained in the $\mathbb{R}_{\ge 0}$-span of $e_1, \ldots, e_n$ (as defined in Equation \ref{defn:e-i-proj}) translated by by $\delta_i = (\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)})$.
-
-Therefore, we can write any element of $\Sigma'$ as
+To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by 
+Equation ~\eqref{eqn:pm-relation-degree}.  We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n) \in \Sigma,$ as defined in Equation ~\eqref{eqn:Sigma-def}.  
+Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.  Let 
+\begin{align*}
+	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
+\end{align*}
+Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\br_{\geq 0}}(e_1, \ldots, e_n)$ with $e_i$ as defined in Equation \ref{defn:e-i-proj}.
+Therefore, we can write any element of $\Sigma_i$ as
 \[
@@
 
-Whenever some $r_j \ge 1$, we can generate the relation at hand by one of lower degree by factoring out a copy of $\epsilon_j$ (see Equation ~\ref{eqn:epsilon-def-proj}).
+Whenever some $r_j \ge 1$, we can generate the relation $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j} = \epsilon_j \cdot h,$ where $\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and $h \in \Sigma_i$.
 Therefore, $\ker(\psi)$ is generated in degrees less than
@@
 
-Therefore, since $\ker(\chi)$ and $\ker(\psi)$ are generated in degrees less than $2\sum_{i=1}^n \ell_i a_i$ and $\delta_i + \sum_{i=1}^n \ell_i a_i$ respectively, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
-\[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
-\]
-
-Combining these results, we get the following theorem:
+Combining the above results, we obtain the following theorem:
 
@@
 \end{thm}
+\begin{proof}
+The bound on degree of generation is precisely the content of Lemma ~\ref{lem:proj-generators}. It only remains to bound the degree of relations.
+By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma ~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.$ Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
+\[
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+\]
+\end{proof}
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
rename annales folder, bigoplus
fix some equations in surfaces, line breaks
some hirz generators rewording

@@
 \begin{align*}
-	\overline {\mathscr M}_g(\alpha) := \oplus_{d \geq 0}H^0 \left( \overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} + \alpha\delta \rfloor  \right) 
+	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0}H^0 \left( \overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} + \alpha\delta \rfloor  \right) 
 \end{align*}
@@
 \label{lem:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
+Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further 
+suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
@@
 \[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in \Tp(D) \atop
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i
+	\in \Tp(D) \atop
 	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}
 \]
+
+\noindent
 with relations generated in degree less than 
@@
 \]
+
+\noindent
 where
@@
 	\tau = \sigma
-	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i \in
+	S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
+	\right).
 \]
@@
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
-We first
-view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
+We first view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
 form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -d \alpha_i$ for
-all $i$ and $\sum_{i = 1}^n c_i (\bida_i + \bidb_i) =0$. By O'Dorney, this
+all $i$ and $\sum_{i = 1}^n c_i (\bida_i + \bidb_i) = 0$. By O'Dorney, this
 has extremal rays given by
@@
 We can intersect $\Delta^{n-1}$ with the hyperplane $H$ given by
-$\sum_{i=1}^n \bida_i X_i = 0$
- to get a subspace $S \subseteq \Delta^{n-1}$. The extremal rays of $S$ must lie on the edges of $\Delta$ \todo{Peter: Do we need to cite/argue this, or is it clear?} and are thus given
-by the set of $e_i$ contained in $H$ together with the points $e_{i, j}$ given by intersections of $H$ with edges of the simplex
-connecting $e_i, e_j \not \in H$.
+$\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S \subseteq \Delta
+^{n-1}$. The extremal rays of $S$ must lie on the edges of $\Delta
+^{n - 1}$ \todo{Peter: Do we need to cite/argue this, or is it clear?}.
+Thus, the extremal rays of $S$ are given by the set of $e_i$
+contained in $H$ and by the points $e_{i, j}$ that are the
+intersections of $H$ with edges of the simplex connecting the
+distinct $e_i, e_j$ not contained in $\in H$.
 \todo{more detail above}
@@
 \[
-	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i. \rangle 
+	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d
+	\alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i.
+	\rangle 
 \]

### 2015-07-16 surfaces-write-up/surface-write-up.tex
surfaces: clean peter's equations, atop -> sstack

@@
 \[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i
-	\in \Tp(D) \atop
-	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
+	\sum_{\substack{i	\in \Tp(D) \\	j \in \Tm(D)}} (\bida_i
+	\bidb_j - \bida_j \bidb_i)\ell_{i,j}
 \]
@@
 	\tau = \sigma
-	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i \in
-	S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
-	\right).
+	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{
+	\substack{i \in	S_+ \\ j\in S_-}}(\ell_{i,j} (\bida_i \bidb_j
+	- \bida_j \bidb_i))	\right).
 \]
@@
 \label{eqn:define-T+(D)}
-	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k=1}^n} 
-\bida_i \sum_{k=1}^m \alpha_k \bidb_k > \bidb_i \sum_{k=1}^n \alpha_k \bida_k 
+	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k = 1}^n} 
+	\bida_i \sum_{k = 1}^m \alpha_k \bidb_k > \bidb_i \sum_{k = 1}^n \alpha_k \bida_k 
 \right\},
@@
 \label{eqn:define-T-(D)}
-	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k=1}^n \alpha_k
+	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k = 1}^n \alpha_k
 	\bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k s \right\}.
@@
 \[
-	\sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{i\in \Tp(D) \atop j\in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
+	\sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
+	{i \in \Tp(D) \\ j\in \Tm(D)}} (\bida_i \bidb_j - \bida_j \bidb_i)
+	\ell	_{i,j}.
 \]
@@
 \[
-	g = \sum_{i=1}^n {f_i}^{c_i}
+	g = \sum_{i = 1}^n {f_i}^{c_i}
 \]
@@
 	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
-	\alpha_j(\bida_j+ \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1}, \ldots, - \alpha_m).
+	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
+	\ldots, -\alpha_m).
 \]
@@
 \[
-	\epsilon_{i, j} := (\prod_{k \ne i,j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
-j - \bida_j \bidb_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(\bida_i \bidb_j - 
-\bida_j \bidb_i)D)
+	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
+	j - \bida_j \bidb_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i, j}
+	(\bida_i \bidb_j - \bida_j \bidb_i) D \right)
 \]
@@
 \[
-	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k\ne i, j}
+	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
 	\alpha_k \bidb_k = b_j (\alpha_i a_i + \alpha_j a_j) - a_j (\alpha_i b_i + \alpha_j b_j)
@@
 \[
-	s_2 = -\bidb_i \sum_{k \ne i,j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
+	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
 	\alpha_k \bidb_k = -b_i (\alpha_i a_i + \alpha_j a_j) + a_i (\alpha_i b_i + \alpha_j b_j).
@@
 \[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in \Tp(D) \atop
-	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{\substack{
+	i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
 \]
@@
 	\tau = \sigma
-	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i \in
-	S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
+	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
+	i \in	S_+ \\ j\in S_-}} (\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
 	\right).
@@
 \[
-	E + \sum_{k\in \Te} r_k e_k + \sum_{h\in \Tp \atop k\in \Tm} r_{h,k} e_{h,k},
-\] 
+	E + \sum_{k\in \Te} r_k e_k + \sum_{\substack{h \in \Tp \\ k \in \Tm}} r_{h,k} e_{h,k}
+\]
+
+\noindent
 where $E$ is $\mathbb{R}_{\ge 0}$
@@
 \[
-	\{e_i \mbox{ if } i\in S\} \cup \{e_{i,j}: j\in S_- \mbox{ if } i \in S_+\} \cup \{e_{j,i}: j\in S_+ \mbox{ if } i \in S_-\}.
+	\{e_i \mbox{ if } i \in S\} \cup \{e_{i, j}: j \in S_- \mbox{ if }
+	i	\in S_+ \} \cup \{e_{j, i}: j \in S_+ \mbox{ if } i \in S_- \}.
 \]
@@
 \[
-	E_\mu + \sum_{k\in \Te} r_k e_k + \sum_{h\in \Tp \atop k\in \Tm} r_{h,k} e_{h,k}
+	E_\mu + \sum_{k\in \Te} r_k e_k + \sum_{\substack{
+	h \in \Tp \\ k \in \Tm}} r_{h,k} e_{h,k}
 \]
@@
 
-Let $F\in R_D$ correspond to $E + \sum_{k\in \Te} (r_k) e_k + \sum_{h\in \Tp \atop k\in \Tm} (r_{h,k}) e_{h,k}$ where $(r)$ signifies the fractional part of $r$.
-Similarly, let $F_\mu \in R_D$ correspond to $E_\mu + \sum_{h\in \Tp \atop k\in \Tm} (r_{h,k}) e_{h,k}$.
-Then $F - \sum_{\mu\in M} F_\mu = 0$ gives us a relation in degree at most
-\[
-	\sigma + \deg(F),
-\]
+Let $F\in R_D$ correspond to $E + \sum_{k\in \Te} (r_k) e_k + \sum_{
+\substack{h \in \Tp \\ k \in \Tm}} (r_{h,k}) e_{h,k}$ where $(r)$
+ signifies the fractional part of $r$.  Similarly, let $F_\mu \in
+R_D$ correspond to $E_\mu + \sum_{\substack{h \in \Tp \\ k\in \Tm}}
+(r_{h,k}) e_{h,k}$. Then $F - \sum_{\mu\in M} F_\mu = 0$ gives us a
+relation in degree at most
+\[
+	\sigma + \deg(F)
+\]
+
+\noindent
 which divides $(z_i - \beta_i) \prod_{i=1}^n y_i^{c_i}$.
@@
 \[
-	\deg(F) \le \left\{ \begin{split}  \ell_i \gcd(\bida_i, \bidb_i) \mbox{ if } i \in S_= 
-			\\ \max_{j\in S_-}(\ell_{i,j} (\bida_i \bidb_
-j - \bida_j \bidb_i)) \mbox{ if } i\in S_+ \\
-			\\ \max_{j\in S_+}(\ell_{j, i} (\bida_j \bidb_
-i - \bida_i \bidb_j)) \mbox{ if } i \in S_- \end{split}  \right.
-\]
+	\deg(F) \le \left\{ \begin{split}
+	\ell_i \gcd(\bida_i, \bidb_i)	\mbox{ if } i \in S_= \\
+	\max_{j \in S_-}(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i))
+	\mbox{ if } i \in S_+ \\
+	\max_{j \in S_+}(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j))
+	\mbox{ if } i \in S_- \end{split}  \right.
+\]
+
+\noindent
 Therefore, $\ker(\psi)$ is generated in degree at most
@@
 	\tau = \sigma
-	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+	+ \max \left(\max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
+	i \in S_+ \\ j \in S_-}} (\ell_{i, j} (\bida_i \bidb_j - \bida_j
+	\bidb_i)) \right).
 \]
@@
 \[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{i\in \Tp(D) \atop
-	j \in \Tm(D)} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}
-\]
+	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
+	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
+	- \bida_j \bidb_i) \ell_{i, j}
+\]
+
+\noindent
 with relations generated in degree less than 
@@
 	\tau = \sigma
-	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{i\in S_+ \atop j\in S_-}(\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))).
+	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
+	i \in S_+ \\ j \in S_-}}(\ell_{i, j} (\bida_i \bidb_j - \bida_j
+	\bidb_i))).
 \]

### 2015-07-16 surfaces-write-up/surface-write-up.tex

@@
 
+\DeclareMathOperator{\fr}{frac}
 \DeclareMathOperator{\supp}{Supp}
@@
 \begin{convention}
-Notate a fractional (weil) divisor
+Notate a fractional (Weil) divisor
 \begin{align*}
@@
 $e_1, \ldots, e_t$.  Then, as a semigroup, $\Sigma$ is generated by
-elements whose first coordinate is less than $\sum_{i = 1}^{t} \pdeg_i$
-. Furthermore, every element $\sigma \in \Sigma$ can be written in
-a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with $\lambda = \sum_{i=1}^{r}s_i e_i$ with $0 \leq s_i < 1,$ the first
-coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i,$ and $w_1,
-\ldots, w_t \in \bz_{\geq 0}$.
+elements whose first coordinate is less than $\sum_{i = 1}^{t}
+\pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be
+written in a canonical form $\lambda + \sum_{i = 1}^{t} w_i e_i$ 
+with $\lambda = \sum_{i = 1}^{r} s_i e_i$ with $0 \leq s_i < 1$, the
+first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$,
+and $w_1, \ldots, w_t \in \bz_{\geq 0}$.
 \end{prop}
@@
 \begin{proof}
-By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_{i=1}^{t} r_i e_i$ with $r_i \in \br$.
-Let $\{r\} := r - \lfloor r \rfloor$ denote the fractional part of $r$.
-Let $\lambda = \sum_{i=1}^{t}\{r_i\}$.
-Whence, we can write $\sigma = \lambda + \sum_{i=1}^{t}\lfloor r_i \rfloor e_i.$ Consequently, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_t$, which all have first coordinate less than $\sum_{i=1}^{t}r_i$.
-Ergo, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{t}r_i$.
+By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
+{i = 1}^{t} r_i e_i$ with $r_i \in \br$. Let $\fr(r) := r - \lfloor r
+\rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 1}
+^{t} \fr(r_i)$. Whence, we can write $\sigma = \lambda + \sum_{i = 1}
+^{t} \lfloor r_i \rfloor e_i.$ Consequently, $\sigma$ lies in the
+$\bz_{\geq 0}$ span of $\lambda, e_1, \ldots, e_t$, which all have
+first coordinate less than $\sum_{i=1}^{t} r_i$. Ergo, $\Sigma$ is
+generated by elements whose first coordinate is less than
+$\sum_{i = 1}^{t} r_i$.
 \end{proof}
@@
 \begin{align*}
-			& \{e_j : j\in \Te \cap \{1, 2, 3, 4\}\} \\
-	\cup \; 	& \{e_{j, k}: j\in \Te \cap \{1, 2, 3, 4\}, k\in \Tm\}\\
-	\cup \; 	& \{e_{k,j}: k\in \Tp, j\in \Tm \cap \{1, 2, 3, 4\}\}.
-\end{align*}
-
-Let $F\in R_D$ correspond to $E + \sum_{k\in \Te} (r_k) e_k + \sum_{
-\substack{h \in \Tp \\ k \in \Tm}} (r_{h,k}) e_{h,k}$ where $(r)$
- signifies the fractional part of $r$.  Similarly, let $F_\mu \in
-R_D$ correspond to $E_\mu + \sum_{\substack{h \in \Tp \\ k\in \Tm}}
-(r_{h,k}) e_{h,k}$. Then $F - \sum_{\mu\in M} F_\mu = 0$ gives us a
+	\{e_j : j \in \{1, 2, 3, 4\} \cap \Te\}
+	&\cup \; \{e_{j, k}: k \in \Tm, \; j \in \{1, 2, 3, 4\} \cap \Te\} \\
+	&\cup \; \{e_{k, j}: k \in \Tp, \; j \in \{1, 2, 3, 4\} \cap \Tm\}.
+\end{align*}
+
+Let $F \in R_D$ correspond to the lattice point
+\[
+	E + \sum_{k \in \Te} \fr(r_k) e_k + \sum_{\substack{h \in \Tp \\
+	k \in \Tm}} \fr(r_{h,k}) e_{h,k}
+\]
+
+\noindent
+where $\fr(r)$ signifies the fractional part of $r$.  Similarly, let $F_\mu
+\in R_D$ correspond to the lattice point
+\[
+	E_\mu + \sum_{\substack{h \in \Tp \\ k \in \Tm}} \fr(r_{h,k}) e_{h,k}.
+\]
+
+\noindent
+Then $F - \sum_{\mu \in M} F_\mu = 0$ gives us a
 relation in degree at most
@@
 \noindent
-which divides $(z_i - \beta_i) \prod_{i=1}^n y_i^{c_i}$.
+which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$.
 We can bound $\deg(F)$ by
 \[
-	\deg(F) \le \left\{ \begin{split}
-	\ell_i \gcd(\bida_i, \bidb_i)	\mbox{ if } i \in S_= \\
-	\max_{j \in S_-}(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i))
-	\mbox{ if } i \in S_+ \\
-	\max_{j \in S_+}(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j))
-	\mbox{ if } i \in S_- \end{split}  \right.
+	\deg(F) \le \begin{cases}
+	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in S_= \\
+	\max_{j \in S_-} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
+	&\mbox{ if } i \in S_+ \\
+	\max_{j \in S_+} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
+	&\mbox{ if } i \in S_- \end{cases}.
 \]
@@
 	\tau = \sigma
-	+ \max \left(\max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
-	i \in S_+ \\ j \in S_-}} (\ell_{i, j} (\bida_i \bidb_j - \bida_j
-	\bidb_i)) \right).
+	+ \max \left(\max_{i\in S_=} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
+	\; \max_{\substack{i \in S_+ \\ j \in S_-}} \bigl(\ell_{i, j}
+	(\bida_i \bidb_j - \bida_j
+	\bidb_i) \bigr) \right).
 \]
@@
 	\tau = \sigma
-	+ \max( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
-	i \in S_+ \\ j \in S_-}}(\ell_{i, j} (\bida_i \bidb_j - \bida_j
-	\bidb_i))).
+	+ \max \left( \max_{i\in S_=} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
+	\max_{\substack{i \in S_+ \\ j \in S_-}} \bigl(\ell_{i, j}
+	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
 \]

### 2015-07-16 surfaces-write-up/surface-write-up.tex
mathscr{O}->sco

@@
 Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
-Let $C_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further 
+Let $C_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further 
 suppose $f_1$ and $f_2$ are independent linear
@@
 \label{defn:lower-approximation}
-If $\alpha \in \br$, then a rational number $\frac{c}{k} \leq \alpha
-$ (written in reduced form with $c \in \bz, k \in \bn$) is a
+If $\alpha \in \br$, then a rational number $\frac{c}{k} \leq \alpha$
+(written in reduced form with $c \in \bz, k \in \bn$) is a
 \textbf{best lower approximation} to $\alpha$ if there does not
@@
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
-$f_i \in \mathscr{O}(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
+$f_i \in \sco(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i$ for curves $D_i$ on $\hirz_k$.  Let $D_i = V(f_i)$ where $f_i \in \mathscr{P}(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+Let $D = \sum_{i=1}^n \alpha_i D_i$ for curves $D_i$ on $\hirz_k$.  Let $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent

### 2015-07-16 surfaces-write-up/surface-write-up.tex
S's changed to T's
fractional/rational divisors -> Q-divisor

@@
 
-\title{Canonical rings of rational divisors on projective space and Hirzebruch surfaces}
+\title{Canonical rings of $\bq$-divisors on projective space and Hirzebruch surfaces}
 
@@
 in terms of certain moduli spaces.
-Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of Kodaira dimension 1.
-A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of fractional divisors.
+$\bq$-divisors on surfaces also naturally appear when considering the canonical ring of surfaces of Kodaira dimension 1.
+A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of $\bq$-divisors.
 \todo{Add references}
@@
 	\tau = \sigma
-	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{
-	\substack{i \in	S_+ \\ j\in S_-}}(\ell_{i,j} (\bida_i \bidb_j
+	+ \max \left( \max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{
+	\substack{i \in	\Tp \\ j\in \Tm}}(\ell_{i,j} (\bida_i \bidb_j
 	- \bida_j \bidb_i))	\right).
@@
 \begin{convention}
-Notate a fractional (Weil) divisor
+Notate a (Weil) $\bq$-divisor
 \begin{align*}
@@
 \end{align*}
+
+\noindent
 where $\alpha_i \in \bq$ and $D_i \in \di X$ is an irreducible divisor.
@@
 	\tau = \sigma
-	+ \max \left( \max_{i\in S_=}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
-	i \in	S_+ \\ j\in S_-}} (\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
+	+ \max \left( \max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
+	i \in	\Tp \\ j\in \Tm}} (\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
 	\right).
@@
 \[
-	\{e_i \mbox{ if } i \in S\} \cup \{e_{i, j}: j \in S_- \mbox{ if }
-	i	\in S_+ \} \cup \{e_{j, i}: j \in S_+ \mbox{ if } i \in S_- \}.
+	\{e_i \mbox{ if } i \in S\} \cup \{e_{i, j}: j \in \Tm \mbox{ if }
+	i	\in \Tp \} \cup \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.
 \]
@@
 	\deg(F) \le \begin{cases}
-	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in S_= \\
-	\max_{j \in S_-} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
-	&\mbox{ if } i \in S_+ \\
-	\max_{j \in S_+} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
-	&\mbox{ if } i \in S_- \end{cases}.
+	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
+	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
+	&\mbox{ if } i \in \Tp \\
+	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
+	&\mbox{ if } i \in \Tm \end{cases}.
 \]
@@
 	\tau = \sigma
-	+ \max \left(\max_{i\in S_=} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
-	\; \max_{\substack{i \in S_+ \\ j \in S_-}} \bigl(\ell_{i, j}
+	+ \max \left(\max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
+	\; \max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
 	(\bida_i \bidb_j - \bida_j
@@
 	\tau = \sigma
-	+ \max \left( \max_{i\in S_=} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
-	\max_{\substack{i \in S_+ \\ j \in S_-}} \bigl(\ell_{i, j}
+	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
+	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
 	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).

### 2015-07-16 surfaces-write-up/surface-write-up.tex
editing 1 pt mid edits

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 
-In this subsection, we restrict attention to the case of effective divisors.
+In this subsection, we restrict attention to the case of effective fractional divisors $D \in \bq \otimes \di \bp^m$.
 
@@
 For $\vec{v} \in \br^n$, denote $\deg \vec{v} := \sum_{i = 0}
-^n v_i$ (i.e. the taxicab metric).
-Let $\mss_i := \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
-\sum_{i = 0} ^{m + 1} v_i = c_i\}$ be the set of points in
-$\bz_{\geq 0}^{m + 1}$ with sum of components equal to $c_i$.
+^n v_i$.
+Let 
+\begin{align*}
+	\mss_i := \left \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
+\deg \vec v = c_i \right\}.	
+\end{align*}
 \end{defn}
@@
 \label{defn:vec-order}
-Let $\vec{v}, \vec{w} \in \br^n$ be two vectors. Let $i$
-be the right-most coordinate such that $v_i$ is nonzero
-and $j$ be the left-most coordinate such that $w_j$ is
+Let $\vec{v}, \vec{w} \in \br^n$. Let $i \in \{1,\ldots, n\}$
+be the biggest index such that $v_i$ is nonzero
+and $j \in \{1,\ldots, n\}$ be the smallest index such that $w_j$ is
 nonzero. Define $\vec{v} \prec \vec{w}$ if $i \leq j$.
@@
 \label{thm:proj-one-point}
-Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \alpha H$, with $\alpha = \frac{p}{q} \in \bq$
-and $H = V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$.
+Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D = \alpha H$, with $\alpha = \frac{p}{q} \in \bq$
+and $H := V(x_k)$ a hyperplane of $\bp^m$.
 Let
@@
 \noindent
-be the best lower approximations of $\alpha$. Then the
+be the best lower approximations of $\alpha$. Then, the
 canonical ring
@@
 {{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
-x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has
-relations of the following two types.
-
-For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
+x^{\vec{v}}}{x_k^{c_i}}$ where $1 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+with $\deg \vec v = c_i$. Furthermore, it has
+relations of the following two types:
+\begin{enumerate}
+	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
 \vec{w} \in \mss_j$, there is a relation of the form either
@@
 \end{flalign*}
-
-Furthermore, there are the relations for each $(i, j)$ with
+	\item For each $(i, j)$ with
 $j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
 \mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
-~\ref{defn:vec-order}) of the form
+~\ref{defn:vec-order}) there is a relation of the form
 \begin{align*}
@@
 \end{align*}
+
+\end{enumerate}
 

### 2015-07-16 surfaces-write-up/surface-write-up.tex
rewording extremal rays of hirz gen/rels

@@
 \section{Introduction}
+For any Weil $\bq$-divisor
 
@@
 \[
-	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
+	e_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
 	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
@@
 ^{n - 1}$ \todo{Peter: Do we need to cite/argue this, or is it clear?}.
-Thus, the extremal rays of $S$ are given by the set of $e_i$
-contained in $H$ and by the points $e_{i, j}$ that are the
-intersections of $H$ with edges of the simplex connecting the
-distinct $e_i, e_j$ not contained in $\in H$.
+Thus, the extremal rays of $S$ are given by the $e_i$'s
+contained in $H$ and the intersection points $e_{i, j}$ of $H$
+and the edges $\overline{e_i e_j}$ of the simplex between
+distinct $e_i, e_j$ not contained in $H$.
 \todo{more detail above}
@@
 
-For $i \in \Te(D)$
-define
+For $i \in \Te(D)$, define \todo{below section needs to be simplified, maybe
+by introducing new variables}
 \[
@@
 
+\noindent
 where

### 2015-07-16 surfaces-write-up/surface-write-up.tex
section 5.2 edits

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%
+%%%%%%%%%%%%%%%
 
@@
 
-\title{Canonical rings of $\bq$-divisors on projective space and Hirzebruch surfaces}
+\title{Canonical rings of rational divisors on projective space and Hirzebruch surfaces}
 
@@
 in terms of certain moduli spaces.
-$\bq$-divisors on surfaces also naturally appear when considering the canonical ring of surfaces of Kodaira dimension 1.
-A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of $\bq$-divisors.
+Fractional divisors on surfaces also naturally appear when considering the canonical ring of surfaces of Kodaira dimension 1.
+A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of fractional divisors.
 \todo{Add references}
@@
 \begin{convention}
-Notate a (Weil) $\bq$-divisor
+Notate a fractional (Weil) divisor
 \begin{align*}
@@
 \end{align*}
-
-\noindent
 where $\alpha_i \in \bq$ and $D_i \in \di X$ is an irreducible divisor.
@@
 
-In this subsection, we restrict attention to the case of effective fractional divisors $D \in \bq \otimes \di \bp^m$.
+In this subsection, we restrict attention to the case of effective divisors.
 
@@
 For $\vec{v} \in \br^n$, denote $\deg \vec{v} := \sum_{i = 0}
-^n v_i$.
-Let 
-\begin{align*}
-	\mss_i := \left \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
-\deg \vec v = c_i \right\}.	
-\end{align*}
+^n v_i$ (i.e. the taxicab metric).
+Let $\mss_i := \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
+\sum_{i = 0} ^{m + 1} v_i = c_i\}$ be the set of points in
+$\bz_{\geq 0}^{m + 1}$ with sum of components equal to $c_i$.
 \end{defn}
@@
 \label{defn:vec-order}
-Let $\vec{v}, \vec{w} \in \br^n$. Let $i \in \{1,\ldots, n\}$
-be the biggest index such that $v_i$ is nonzero
-and $j \in \{1,\ldots, n\}$ be the smallest index such that $w_j$ is
+Let $\vec{v}, \vec{w} \in \br^n$ be two vectors. Let $i$
+be the right-most coordinate such that $v_i$ is nonzero
+and $j$ be the left-most coordinate such that $w_j$ is
 nonzero. Define $\vec{v} \prec \vec{w}$ if $i \leq j$.
@@
 \label{thm:proj-one-point}
-Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D = \alpha H$, with $\alpha = \frac{p}{q} \in \bq$
-and $H := V(x_k)$ a hyperplane of $\bp^m$.
+Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
+$\bp^m$. Let $D = \alpha H$, with $\alpha = \frac{p}{q} \in \bq$
+and $H = V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$.
 Let
@@
 \noindent
-be the best lower approximations of $\alpha$. Then, the
+be the best lower approximations of $\alpha$. Then the
 canonical ring
@@
 {{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
-x^{\vec{v}}}{x_k^{c_i}}$ where $1 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-with $\deg \vec v = c_i$. Furthermore, it has
-relations of the following two types:
-\begin{enumerate}
-	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
+x^{\vec{v}}}{x_k^{c_i}}$ where $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+such that $\sum_{j = 0}^{m} v_j = c_i$. Furthermore, it has
+relations of the following two types.
+
+For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
 \vec{w} \in \mss_j$, there is a relation of the form either
@@
 \end{flalign*}
-	\item For each $(i, j)$ with
+
+Furthermore, there are the relations for each $(i, j)$ with
 $j = i$ or $j = i + 1$ and each $\vec{v} \in \mss_i, \vec{w} \in
 \mss_j$ with $\vec{v} \not\prec \vec{w}$ (see Definition
-~\ref{defn:vec-order}) there is a relation of the form
+~\ref{defn:vec-order}) of the form
 \begin{align*}
@@
 \end{align*}
-
-\end{enumerate}
 
@@
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
-$f_i \in \sco(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
+$f_i \in \sco(\bida_i, \bidb_i)$.  
+Then, $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$.
+linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch surfaces before this paragraph; especially, describe what it's sections look like.}
 
@@
 \begin{proof}
-Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. Notice that if $\gamma
+%Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. 
+Notice that if $\gamma
 \in (R_D)_d$, then 
@@
 where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^n c_i \bida_i = 0$,
-and $\sum_{i=1}^n c_i \bidb_i = 0$. Then we can view $g$ inside of the
+and $\sum_{i=1}^n c_i \bidb_i = 0$. Then we can any view $g$ inside the
 lattice $S \subseteq \mathbb{R}^{n + 1}$ given by ordered elements of
@@
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
-We first view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
-form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -d \alpha_i$ for
-all $i$ and $\sum_{i = 1}^n c_i (\bida_i + \bidb_i) = 0$. By O'Dorney, this
+We first consider the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
+form $(d, r_1, \ldots, r_n)$ satisfying $r_i \ge -d \alpha_i$ for
+all $i$ and $\sum_{i = 1}^n r_i (\bida_i + \bidb_i) = 0$.  This
 has extremal rays given by
@@
 The lattice points corresponding to elements of $E$ satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
-degree less than
+degrees less than
 \[
@@
 
-Let $x_1, \ldots x_r$ be the generators of $R_D$ in degree less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
+Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
 We can factor $\phi$ through
@@
 
-Applying Lemma ~\ref{lem:bound-ker-chi}, we can bound the degrees of generation of $\ker(\chi)$ below
+Applying Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
 $2 \sigma$.

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edits to section 5

@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_i}$ to a canonical form as given by Proposition ~\ref{prop:cone-generation}.
+1}^n f_j^{r_i}$ to a canonical form, with $r_i = -\lfloor d \alpha_i\rfloor$ whenever $i  > m + 1$.
 
@@
 Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
-k).$ such
+m).$ such
 that $D_1, \ldots, D_4$ are distinct divisors with bi-degrees $(1,0)
@@
 	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k = 1}^n} 
-	\bida_i \sum_{k = 1}^m \alpha_k \bidb_k > \bidb_i \sum_{k = 1}^n \alpha_k \bida_k 
+	\bida_i \sum_{k = 1}^n \alpha_k \bidb_k > \bidb_i \sum_{k = 1}^n \alpha_k \bida_k 
 \right\},
@@
 
-Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given 
-above, satisfying the respective conditions.
-The lattice points corresponding to elements of $E$ satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
+The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
 degrees less than
@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_j}$ to the canonical form (see Proposition ~\ref{prop:cone-generation}).  \todo{Peter: I think the canonical form given in the proposition isn't the one we actually want.}
-
-Note that we can view the relations from Equation
-~\ref{eqn:hirz-relations-psi} \todo{is this the right ref?} as an element of $S$ given
+1}^n f_j^{r_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$.
+
+Note that we can view a relation from Equation
+~\ref{eqn:hirz-relations-psi} as an element of $S$ given
 by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  Let $S'\subseteq (\mathbb{R}_{\ge 0})^{n+1}$ be the
-set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
-$\bida_j + \sum_{i = 1}^m \bida_i c_i = 0$, and $\bidb_j + \sum_{i=1}^n \bidb_i c_i
-= 0$.  A careful computation deduces that $\gamma (d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots, c_n)$ is of the form 
+set of $(d, r_1, \ldots, r_{i-1}, r_i + 1, r_{i+1}, \ldots , r_n)$ satisfying $r_i \ge -\alpha_i d$,
+$\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
+= 0$.  A careful computation deduces that $\gamma \in S'$ is of the form 
 \[

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edits to 5.3

@@
 
-Note that we can view a relation from Equation
-~\ref{eqn:hirz-relations-psi} as an element of $S$ given
-by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  Let $S'\subseteq (\mathbb{R}_{\ge 0})^{n+1}$ be the
-set of $(d, r_1, \ldots, r_{i-1}, r_i + 1, r_{i+1}, \ldots , r_n)$ satisfying $r_i \ge -\alpha_i d$,
+%Note that we can view a relation from Equation
+%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
+%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
+Let $S'\subseteq S$ be the
+set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
 $\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
-= 0$.  A careful computation deduces that $\gamma \in S'$ is of the form 
+= 0$.  A careful computation deduces that the lattice point corresponding to $y_i \prod_{j=1}^n {y_j}^{c_j}$ is of the form 
 \[
@@
 \noindent
-where $E$ is $\mathbb{R}_{\ge 0}$
+where $E$ is in degree $\mathbb{R}_{\ge 0}$
 combination of elements in 
 \[
-	\{e_i \mbox{ if } i \in S\} \cup \{e_{i, j}: j \in \Tm \mbox{ if }
+	\{e_j: j\in \{i\} \cap S\} \cup \{e_{i, j}: j \in \Tm \mbox{ if }
 	i	\in \Tp \} \cup \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edited most of one point

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 \section{Introduction}
-For any Weil $\bq$-divisor
 
@@
 \end{rem}
+\todo{possibly define mediant}
 
@@
 	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- \prod_{\substack{\vec{y} \in \mss_{h_{i, j}} \\ \vec{z} \in
-	\mss_{h_{i, j} + 1}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}} \;
-	(F_{k_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}}
+	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}}
+	\cdot \prod_{ \vec{z} \in
+	\mss_{h_{i, j} + 1}} (F_{k_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}}
 	&(i < h_{i, j} < h_{i, j} + 1 < j).
@@
 \end{thm}
-
+\todo{Write idea of proof}
 \begin{proof}
-We know $\left\{F_{0}^{\vec{v}} : \deg \vec{v} = \left\lfloor
+We will first check that $F^{\vec v}_i$ determine a system of minimal generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} : \deg \vec{v} = \left\lfloor
 \frac{p}{q} \right\rfloor \right\}$ are minimal generators in
-degree $1$. Now let $i > 0$. Suppose $F_i^{\vec{v}}$ were not
+degree $1$. Now let $i > 1$. Suppose $F_i^{\vec{v}}$ were not
 minimal for some $\vec{v} \in \mss_i$. Then $F_i^{\vec{v}} =
@@
 \frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
-and $s$ and $t$ are both less than $d_i$, so we have a contradiction 
-of $\frac{c_i}{d_i}$ being a best lower approximation of $\alpha$
+and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that $\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
 (see Definition ~\ref{defn:lower-approximation}).
 
-Now we show that no further generators are necessary. As done in
-the proof of the $\bp^1$ case by O'Dorney \cite[Theorem 6]
-{dorney:canonical}, each lattice point $(\beta, \gamma) \in
-\bz_{\geq 0}^2$ such that $\gamma \leq \beta \alpha$ is a non-negative
-linear combination of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
-some $h \in \{0, \ldots, r\}$. Let $(\beta, \gamma) = \ell_1
-(d_h, c_h) + \ell_2 (d_{h + 1}, c_{h + 1})$ for $\ell_1, \ell_2 \in
-\bz_{\geq 0}$. Consequently, any element $\frac{u^{\beta}
+Next we show that $F^{\vec v}_i$ generate all of $R_D$. In the case $m = 1$, O'Dorney \cite[Theorem 6]
+{dorney:canonical} demonstrates that each lattice point $(\beta, \gamma) \in
+\bz_{\geq 0}^2$ with $\gamma \leq \beta \alpha$ lies in the $\bz_{\geq 0}$ span of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
+some $h \in \{0, \ldots, r\}$. Let $(\beta, \gamma) = \kappa_1
+(d_h, c_h) + \kappa_2 (d_{h + 1}, c_{h + 1})$ for $\kappa_1, \kappa_2 \in
+\bz_{\geq 0}$. Any element $\frac{u^{\beta}
 x^{\vec{v}}} {x_k^{ \gamma}} \in R_D$ is expressible as
@@
 	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_h}}
-	{x_k^{c_h}}\right)^{\ell_1} \left(\frac{u^{d_{h + 1}}}
-	{x_k^{c_{h + 1}}}\right)^{\ell_2} x^{\vec{v}}.
-\end{align*}
-
-\noindent
-We can then break $\vec{v}$ into a sum of $\ell_1$ many vectors
-$\vec{w}_{(j)}$ in $\mss_2$ and $\ell_2$ many vectors $\vec{z}_{(k)}$
-in $\mss_2$ to give a decomposition
-\begin{align*}
+	{x_k^{c_h}}\right)^{\kappa_1} \left(\frac{u^{d_{h + 1}}}
+	{x_k^{c_{h + 1}}}\right)^{\kappa_2} x^{\vec{v}}.
+\end{align*}
+
+\noindent
+We can then write $\vec{v}  = \sum_{\lambda=1}^{\kappa_1}\vec{w}_{(\lambda)} + \sum_{\eta=1}^{\kappa_2} \vec z_{(\eta)}$ with $w_{(\lambda)} \in \mss_h$ and $z_{(\eta)} \in \mss_{h+1}$ to give a decomposition
+\begin{align}
+\label{eqn:one-point-canonical-form}
 	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{\lambda = 1}
-	^{\ell_1} \frac{u^{d_h} x^{\vec{w}_{(\lambda)}}} {x_k^{c_h}}
-	\prod_{\lambda = 1}^{\ell_2} \frac{u^{d_{h + 1}} x^{\vec{z}_{(\lambda)}}}
+	^{\kappa_1} \frac{u^{d_h} x^{\vec{w}_{(\lambda)}}} {x_k^{c_h}}
+	\prod_{\eta = 1}^{\kappa_2} \frac{u^{d_{h + 1}} x^{\vec{z}_{(\eta)}}}
 	{x_k^{c_{h + 1}}}
-\end{align*}
-
+\end{align}
 \noindent
 consisting of products of generators $F_h^{\vec{y}_{(\lambda)}}$
-and $F_{h + 1}^{\vec{z}_{(\lambda)}}$ which are in the form
+and $F_{h + 1}^{\vec{z}_{(\eta)}}$ which are in the form
 prescribed in the theorem statement.
-
+Since we wrote an arbitrary monomial $\frac{u^{\beta} x^{\vec{v}}}{x_k^\gamma} \in R_D$ as a product of generators, this shows that $F_i^{\vec v}$ minimally generate $R_D$.
+
+Next, we show that the relations given in the statement of the theorem generate all relations. 
 In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
-has a decomposition of this form for some $h_{i, j}$. We also have
+has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} where $h$ depends on $i, j$, so we notate $h = h_{i, j} \in \{1, \ldots, r\}$. We also have
 that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
@@
 $(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore, we have that
-$h_{i, j} \neq i$ is equivalent to the proof given by O'Dorney
+$h_{i, j} \neq i, j-1$ as can be shown in the same manner as the analogous statement in O'Dorney
 \cite[Theorem 6]{dorney:canonical}. This gives the relations
@@
 	\left(\frac{u^{d_j}}{x_k^{c_j}}\right)
-															= F_i^{\vec{y}} F_j^{\vec{z}}
+	= F_i^{\vec{y}} F_j^{\vec{z}},
 \end{align*}
@@
 	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(1)}}} \cdots
-	(F_i^{\vec{v}_{(\ell_1)}})^{g_{\vec{v}_{(\ell_1)}}}
+	(F_i^{\vec{v}_{(\kappa_1)}})^{g_{\vec{v}_{(\kappa_1)}}}
 	(F_{i + 1}^{\vec{w}_{(1)}})^{g_{\vec{w}_{(1)}}} \cdots
-	(F_{i + 1}^{\vec{w}_{(\ell_2)}})^{g_{\vec{w}_{(\ell_2)}}}
+	(F_{i + 1}^{\vec{w}_{(\kappa_2)}})^{g_{\vec{w}_{(\kappa_2)}}}
 \end{align*}
@@
 where $\vec{v}_{(1)} \prec \vec{v}_{(2)} \prec \ldots \prec
-\vec{v}_{(\ell_1)} \prec \vec{w}_{(1)} \prec \ldots \prec
-\vec{w}_{(\ell_2)}$. Consequently, the relations of form
+\vec{v}_{(\kappa_1)} \prec \vec{w}_{(1)} \prec \ldots \prec
+\vec{w}_{(\kappa_2)}$. Consequently, the relations of form
 $G_{i, j}^{\vec{v}, \vec{w}}$ and of form $L_{i, j}^{\vec{v},
@@
 in Example ~\ref{eg:hyperplane}, the degrees of generation of the
-canonical ring of a general $\bq$-divisor containing two
+canonical ring of a general $\bq$-divisor supported on two
 hyperplanes cannot be bounded so tightly. The two-point
 $\bp^1$ result leverages particular facts about the structure of
-$\bp^1$.
+$\bp^1$. \todo{Possibly say what facts?}
 \end{rem}
@@
 The method of proof for Theorem ~\ref{thm:proj-one-point}
-can be immediately generalized to work inductively. If $D = D' + H$
-for some hyperplane $H$, then we can use the proof above to show
+can be immediately generalized to work inductively. If $D = D' + \alpha H$
+for some hyperplane $\alpha H$, then we can use the proof above to show
 the canonical ring $R_D$ is generated over $R_D'$ by the same
@@
 \end{rem}
-
+\todo{Perhaps we should consider restating the above theorem in this form, and then say for simplicity we prove it when the base is 0?}
 \begin{thm}
@@
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
-$f_i \in \sco(\bida_i, \bidb_i)$.  
-Then, $f_1$ and $f_2$ are independent linear
+$f_i \in \sco(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch surfaces before this paragraph; especially, describe what it's sections look like.}
+linear polynomials in $y_0$ and $y_1$.
 
@@
 \begin{proof}
-%Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. 
-Notice that if $\gamma
+Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. Notice that if $\gamma
 \in (R_D)_d$, then 
@@
 where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^n c_i \bida_i = 0$,
-and $\sum_{i=1}^n c_i \bidb_i = 0$. Then we can any view $g$ inside the
+and $\sum_{i=1}^n c_i \bidb_i = 0$. Then we can view $g$ inside of the
 lattice $S \subseteq \mathbb{R}^{n + 1}$ given by ordered elements of
@@
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
-We first consider the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
-form $(d, r_1, \ldots, r_n)$ satisfying $r_i \ge -d \alpha_i$ for
-all $i$ and $\sum_{i = 1}^n r_i (\bida_i + \bidb_i) = 0$.  This
+We first view the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
+form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge -d \alpha_i$ for
+all $i$ and $\sum_{i = 1}^n c_i (\bida_i + \bidb_i) = 0$. By O'Dorney, this
 has extremal rays given by
@@
 \[
-	e_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
+	e_i = (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
 	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
@@
 ^{n - 1}$ \todo{Peter: Do we need to cite/argue this, or is it clear?}.
-Thus, the extremal rays of $S$ are given by the $e_i$'s
-contained in $H$ and the intersection points $e_{i, j}$ of $H$
-and the edges $\overline{e_i e_j}$ of the simplex between
-distinct $e_i, e_j$ not contained in $H$.
+Thus, the extremal rays of $S$ are given by the set of $e_i$
+contained in $H$ and by the points $e_{i, j}$ that are the
+intersections of $H$ with edges of the simplex connecting the
+distinct $e_i, e_j$ not contained in $\in H$.
 \todo{more detail above}
@@
 
-For $i \in \Te(D)$, define \todo{below section needs to be simplified, maybe
-by introducing new variables}
+For $i \in \Te(D)$
+define
 \[
@@
 
-\noindent
 where
@@
 The lattice points corresponding to elements of $E$ satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
-degrees less than
+degree less than
 \[
@@
 
-Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
+Let $x_1, \ldots x_r$ be the generators of $R_D$ in degree less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
 We can factor $\phi$ through
@@
 
-Applying Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
+Applying Lemma ~\ref{lem:bound-ker-chi}, we can bound the degrees of generation of $\ker(\chi)$ below
 $2 \sigma$.

### 2015-07-16 surfaces-write-up/surface-write-up.tex

@@
 Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
-k).$ such
+m).$ such
 that $D_1, \ldots, D_4$ are distinct divisors with bi-degrees $(1,0)
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
-$f_i \in \sco(\bida_i, \bidb_i)$.  Suppose $f_1$ and $f_2$ are independent linear
+$f_i \in \sco(\bida_i, \bidb_i)$.  
+Then, $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$.
+linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch surfaces before this paragraph; especially, describe what it's sections look like.}
 
@@
 
-Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given 
-above, satisfying the respective conditions.
-The lattice points corresponding to elements of $E$ satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
-degree less than
+The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
+degrees less than
 \[
@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_j}$ to the canonical form (see Proposition ~\ref{prop:cone-generation}).  \todo{Peter: I think the canonical form given in the proposition isn't the one we actually want.}
-
-Note that we can view the relations from Equation
-~\ref{eqn:hirz-relations-psi} \todo{is this the right ref?} as an element of $S$ given
-by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  Let $S'\subseteq (\mathbb{R}_{\ge 0})^{n+1}$ be the
+1}^n f_j^{r_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$.
+
+%Note that we can view a relation from Equation
+%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
+%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
+Let $S'\subseteq S$ be the
 set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
-$\bida_j + \sum_{i = 1}^m \bida_i c_i = 0$, and $\bidb_j + \sum_{i=1}^n \bidb_i c_i
-= 0$.  A careful computation deduces that $\gamma (d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots, c_n)$ is of the form 
+$\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
+= 0$.  A careful computation deduces that the lattice point corresponding to $y_i \prod_{j=1}^n {y_j}^{c_j}$ is of the form 
 \[

### 2015-07-16 surfaces-write-up/surface-write-up.tex
add intro first two paragraphs

@@
 \section{Introduction}
-For any Weil $\bq$-divisor
+For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
+\textbf{canonical ring} $R(X, D) := \bigoplus_{d \geq 0} H^0(X, dD)$
+has connections to rings of Hilbert and Siegel modular forms. In the
+study of these canonical rings, it is natural to describe
+presentations. We study the generators and relations of canonical
+rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
+When $D$ is a general $\bq$-divisor on any $\bp^m$ or on any
+$\hirz_m$, we give bounds on the generators and relations of
+$R(X, D)$. In particular, we give a complete description of the
+canonical ring when $X = \bp^m$ and $D$ is an $\bq$-divisor
+containing one hypersurface and give stronger bounds when
+$D$ is any effective $\bq$-divisor on $\bp^m$.
+
+In part, this work is motivated by moving to generalize the work
+of O'Dorney \cite{dorney:canonical} who gives similar descriptions
+of canonical rings for general $\bq$-divisors on $\bp^1$. For
+particular $\bq$ divisors on stacky curves, the work by
+Voight--Zureick-Brown \cite{vzb:stacky} and Landesman--Ruhm--Zhang
+\cite{lrz:spin-cring} on log spin canonical rings provides
+useful bounds on rings of modular forms of Fuchsian groups.
+The results of this work may have applications to Hilbert
+and Siegel modular forms. \todo{reword last sentence}
 

### 2015-07-17 surfaces-write-up/surface-write-up.tex
changed title
editing ... sleepy ... very sleepywefoewifhoewifhw

@@
 
-\title{Canonical rings of $\bq$-divisors on projective space and Hirzebruch surfaces}
+\title{Canonical rings of $\bq$-divisors on Minimal Rational Surfaces}
 
@@
 can be immediately generalized to work inductively. If $D = D' + \alpha H$
-for some hyperplane $\alpha H$, then we can use the proof above to show
+for some hyperplane $H$, then the proof of Theorem ~\ref{thm:proj-one-point}, mutatis mutandis, extends to show
 the canonical ring $R_D$ is generated over $R_D'$ by the same
@@
 \label{thm:proj-effective}
-Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i D_i$, with $\alpha_i =
-\frac{p_i}{q_i} \in \bq$ and each $D_i$ a hypersurface of
-$\bp^m$, be an effective divisor on $\bp^m$.
+Let $[x_0, \ldots, x_m]$ be a projective coordinate system for
+$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i D_i \in \bq \otimes \bp^m$, with $\alpha_i =
+\frac{p_i}{q_i} \in \bq$.
 
 Then the canonical ring
-\[
-	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
-\]
-
-\noindent
+$R_D$
 is generated in degrees up to $\max_{1 \leq i \leq n}{q_i}$ with
-relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$
+relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$.
 \end{thm}
@@
 Now, we look to inductively add hypersurfaces.
-If $D' = \sum_{i = 0}^{n} \alpha_i C_i$ is some $\bq$-divisor
+If $D' = \sum_{i = 0}^{n} \alpha_i D_i$ is some $\bq$-divisor
 on $\bp^m$, then we look at $D = D' + C$ where $C$ is a
-hypersurface of degree $\pdeg$. Now use the Veronese mapping
-to view $D$ as a divisor on $\bp^{m ({m + \pdeg} \choose \pdeg - 1)}$
+hypersurface of degree $\pdeg$. \todo{Aaron: rewrite this to make sense} Now use the Veronese mapping
+to view $C$ as a hypersurface on $\bp^{\binom{{m + \pdeg}}{ \pdeg} -1 }$
 and the image of $C$ as the intersection of a Veronese variety
@@
 \section{Conclusion}
-This paper extends the work of O'Dorney on $\bp^1$ to $\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
-The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar ideas to O'Dorney's method on $\bp^1$.
+This paper extends the work of O'Dorney \cite{dorney:canonical} on $\bp^1$ to $\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
+The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar methods to that of O'Dorney's for $\bp^1$.
 

### 2015-07-17 surfaces-write-up/surface-write-up.tex
some minor beamer edits
move background into lemmas, 1pt; section labels

@@
 \todo{make title shorter so it doesn't overlap with page numbers}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
+\label{sec:intro}
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
@@
 
-\section{Background}
+\section{Lemmas for Generation and Relations}
+\label{sec:lemmas}
 
@@
 
-\begin{convention}
-Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
-$\vec{v} = (v_0, \ldots, v_m) \in \br^{m + 1}$. Then write
-\[
-	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
-\]
-\end{convention}
-
-\section{Lemmas for Generation and Relations}
+Now we give a result describing the generators of a cone via its
+extremal rays.
+\todo{write more transition}
 
@@
 \label{prop:cone-generation}
-Let $n \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$, and let $a_i, b_i \in \bz$ with $1 \leq i \leq n.$ Define
+Let $n \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$, and let
+$a_i, b_i \in \bz$ with $1 \leq i \leq n.$ Define
 \begin{align*}
-	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}a_i = \sum_{i=1}^{n}b_i = 0 \right \}
+	\Sigma := \left \{(d, c_1, \ldots, c_n) \in \bz^{n + 1} : c_i \geq -
+	d \alpha_i, 1 \leq i \leq n \text{ and } \sum_{i = 1}^{n} a_i =
+	\sum_{i	= 1}^{n}b_i = 0 \right \}
 \end{align*}
@@
 \ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
-meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of
-$e_1, \ldots, e_t$.  Then, as a semigroup, $\Sigma$ is generated by
+i.e.~ $\Sigma$ is contained in the $R_{\geq 0}$ span of
+$e_1, \ldots, e_t$.
+
+Then, as a semigroup, $\Sigma$ is generated by
 elements whose first coordinate is less than $\sum_{i = 1}^{t}
@@
 \section{Canonical Rings on Projective Space}
+\label{sec:proj}
 In this section, we bound the degrees of generators and relations for divisors on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case was covered in \cite{dorney:canonical}.
@@
 
-In this subsection, we restrict attention to the case of effective fractional divisors $D \in \bq \otimes \di \bp^m$.
+In this subsection, we restrict attention to the case of effective
+fractional divisors $D \in \bq \otimes \di \bp^m$. We completely
+characterize the canonical rings when $D$ consists of one
+hypersurface and give strong bounds on generator and relation
+degrees for general effective divisors $D$.
+
+\begin{convention}
+Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
+$\vec{v} = (v_0, \ldots, v_m) \in \br^{m + 1}$. Then write
+\[
+	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
+\]
+\end{convention}
 
@@
 \section{Canonical Rings on Hirzebruch surfaces}
+\label{sec:hirz}
 Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
@@
 \section{Conclusion}
+\label{sec:conc}
 This paper extends the work of O'Dorney \cite{dorney:canonical} on $\bp^1$ to $\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
@@
 \section{Acknowledgments}
+\label{sec:ack}
 We are grateful to David Zureick-Brown for introducing us to this

### 2015-07-17 surfaces-write-up/surface-write-up.tex
Changes to 5.3

--- 2015-07-16 surfaces-write-up/surface-write-up.tex
@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$.
+1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}
 
@@
 %by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
-Let $S'\subseteq S$ be the
+Let $\Sigma'\subseteq \Sigma$ be the \todo{change all $S$ to sigma's}
 set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
 $\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
-= 0$.  A careful computation deduces that the lattice point corresponding to $y_i \prod_{j=1}^n {y_j}^{c_j}$ is of the form 
-\[
-	E + \sum_{k\in \Te} r_k e_k + \sum_{\substack{h \in \Tp \\ k \in \Tm}} r_{h,k} e_{h,k}
-\]
-
-\noindent
-where $E$ is in degree $\mathbb{R}_{\ge 0}$
-combination of elements in 
-\[
-	\{e_j: j\in \{i\} \cap S\} \cup \{e_{i, j}: j \in \Tm \mbox{ if }
-	i	\in \Tp \} \cup \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.
-\]
+= 0$.
+Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.
+Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}$ for $r\in \Tp, k\in \Tm$.
+Let $V$ be the set of $e_i$ $e_{i,j}$ and $e_{j,i}$ as $j$ ranges that exist (i.e.
+$e_i$ if the hyperplane from lemma \ref{lem:hirz-generators} intersects $e_i$, and the $e_{i,j}$'s or $e_{j,i}$'s if the hyperplane intersects the corresponding edge of the simplex).
+A careful computation deduces that if $e_i$ exists
+\[
+	l
+\]
+\[
+	\lambda + E
+\]
+
+\noindent
+where $\lambda\in S$ and
+\[
+	k
+\]
+
+\[
+	\deg(E) \le \begin{cases}
+	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
+	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
+	&\mbox{ if } i \in \Tp \\
+	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
+	&\mbox{ if } i \in \Tm \end{cases}.
+\]
+
+ $= V_1 \cup V_2 \cup V_3$ where
+\begin{align*}
+	&	V_1 = \{ \{e_i\} \mbox{ if }
+	&	V_2= \{e_{i, j}: j \in \Tm \mbox{ if } i	\in \Tp \}
+	&	V_3=  \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.
+\end{align*}
 
@@
 \]
-where $E_\mu$ is a $\mathbb{R}_{\ge 0}$-combination of elements in
+where $E_\mu$ is in degree
+\[
+	\deg(F) \le \begin{cases}
+	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
+	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
+	&\mbox{ if } i \in \Tp \\
+	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
+	&\mbox{ if } i \in \Tm \end{cases}.
+\]
+
+a $\mathbb{R}_{\ge 0}$-combination of elements in
 \begin{align*}

### 2015-07-17 surfaces-write-up/surface-write-up.tex
merged

@@
 = 0$.  
-Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.
-Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}$ for $r\in \Tp, k\in \Tm$.
-Let $V$ be the set of $e_i$ $e_{i,j}$ and $e_{j,i}$ as $j$ ranges that exist (i.e.
-$e_i$ if the hyperplane from lemma \ref{lem:hirz-generators} intersects $e_i$, and the $e_{i,j}$'s or $e_{j,i}$'s if the hyperplane intersects the corresponding edge of the simplex).
-A careful computation deduces that if $e_i$ exists
-\[
-	l
-\]
-\[
-	\lambda + E
-\]
-
-\noindent
-where $\lambda\in S$ and
-\[
-	k
-\]
-
+Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}$ for $r\in \Tp, k\in \Tm$.  
+For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$ component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$ component $\kappa_{j,i}''$.
+Then a careful computation deduces that 
+%if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
+\[
+	\sigma = \lambda + E
+\]
+where $\lambda \in \Sigma$ and
+\begin{equation}\label{eqn:hirz-E-translation}
+	E = \begin{cases}
+	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
+	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \br, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
+	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \br, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
+	\end{cases}.
+\end{equation}
+
+\noindent
+From this, we can deduce that
 \[
@@
 \]
-
- $= V_1 \cup V_2 \cup V_3$ where
-\begin{align*}
-	&	V_1 = \{ \{e_i\} \mbox{ if }
-	&	V_2= \{e_{i, j}: j \in \Tm \mbox{ if } i	\in \Tp \}
-	&	V_3=  \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.
-\end{align*}
-
-Let $M$ be the set of monomials of $\beta_j$.  Then for $\mu\in M$, the corresponding lattice point is of the form
-\[
-	E_\mu + \sum_{k\in \Te} r_k e_k + \sum_{\substack{
-	h \in \Tp \\ k \in \Tm}} r_{h,k} e_{h,k}
-\]
-where $E_\mu$ is in degree
-\[
-	\deg(F) \le \begin{cases}
-	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
-	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
-	&\mbox{ if } i \in \Tp \\
-	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
-	&\mbox{ if } i \in \Tm \end{cases}.
-\]
-
-a $\mathbb{R}_{\ge 0}$-combination of elements in
-\begin{align*}
-	\{e_j : j \in \{1, 2, 3, 4\} \cap \Te\}
-	&\cup \; \{e_{j, k}: k \in \Tm, \; j \in \{1, 2, 3, 4\} \cap \Te\} \\
-	&\cup \; \{e_{k, j}: k \in \Tp, \; j \in \{1, 2, 3, 4\} \cap \Tm\}.
-\end{align*}
-
-Let $F \in R_D$ correspond to the lattice point
-\[
-	E + \sum_{k \in \Te} \fr(r_k) e_k + \sum_{\substack{h \in \Tp \\
-	k \in \Tm}} \fr(r_{h,k}) e_{h,k}
-\]
-
-\noindent
-where $\fr(r)$ signifies the fractional part of $r$.  Similarly, let $F_\mu
-\in R_D$ correspond to the lattice point
-\[
-	E_\mu + \sum_{\substack{h \in \Tp \\ k \in \Tm}} \fr(r_{h,k}) e_{h,k}.
-\]
-
-\noindent
-Then $F - \sum_{\mu \in M} F_\mu = 0$ gives us a
+Let $M$ be the set of monomials terms of $\beta_j$.  Then for $\mu\in M$, we can further compute that the lattice point corresponding to $\mu \prod_{j=1}^n {f_i}^{c_i}$ is of the form
+\[
+	\sigma + E_\mu
+\]
+where $E_\mu$ is defined similarly to $E$ (in particular, they lie in the same degree).
+
+Let $F\in R_D$ corresponding to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
+Then $F - \sum_{\mu \in M} F_\mu = 0$ induces a
 relation in degree at most
@@
 which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$.
-We can bound $\deg(F)$ by
-\[
-	\deg(F) \le \begin{cases}
+We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
+\[
+	\deg(F) = \deg(E) \le \begin{cases}
 	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\

### 2015-07-17 surfaces-write-up/surface-write-up.tex
comments and edits on hirzebruch

@@
 \todo{make title shorter so it doesn't overlap with page numbers}
+\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most''}
 
@@
 
+\todo{Include summary of what each of the sections do.}
+
 \section{Lemmas for Generation and Relations}
@@
 
-\ssec{Notation}
 \begin{convention}
@@
 
+We now offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
+
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ $\deg(f_i) = a_i$ for all $i$.
+
+For the remainder of this section, we shall make the additional assumption that 
+\begin{align}
+\label{eqn:pm-basis-assumption}
+	f_1, \ldots, f_{m+1} \text{ form a } \bk \text{ basis of all degree 1 functions.}
+\end{align}
+
+Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$.
+Before doing so, we justify the assumption ~\eqref{eqn:bpm-basis-assumption} through a several convincing examples.
+
 \begin{example}
@@
 The reason for this is that the divisors may ``be contained in a hyperplane,'' i.e., be expressable as functions in $m$ of the $m+1$ variables on $\bp^m$.
-This problem can easily be circumvented by adding in ``ghost points.'' That is, we may add divisors of the form $0 \cdot H_i$ to $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$, then $f_0, \ldots, f_n$
+This problem can easily be circumvented by adding in ``ghost points.'' That is, we may add divisors of the form $0 \cdot H_i$ to $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$, then $f_0, \ldots, f_n$.
+
+In Example ~\ref{eg:radical}, we show that it is still, in general, necessary to add ghost points, even when the irreducible components of a divisor are not all contained in a hyperplane.
 \end{rem}
@@
 \label{eg:radical}
-In this example, we show that it is still, in general, necessary to add ghost points, even when the irreducible components of a divisor are not all contained in a hyperplane.
-
 Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 + x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) - \frac{1}{596}V(x_1^2 + x_2^2 + x_3^2)$.
@@
 \todo{construct class of additional examples}
-\todo{The example above needs to be changed because $x_0^2$ can be replaced by $2x_0$}
-
-We now offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
-
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$.
-\todo{Aaron: Do we want to make the convention somewhere that $f_1,\ldots, f_{m+1}$ generate $O(1)$?}
+
+Having justified the necessity of adding ghost points, we proceed to bound the number of generators and relations.
 
@@
 
-Combining the above results, we obtain the following theorem:
+Combining the above results, we obtain the following bound on the degrees of generators and relations of $R_D$.
 
 \begin{thm}
-\label{lem:proj-generators-relations}
+\label{thm:proj-generators-relations}
 Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
@@
 \label{sec:hirz}
+
+In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
+
+\todo{Aaron: Give some definitions to make clear what the structure of divisors are}
+\todo{Aaron: clarify that $R_D$ is assumed to have both positive bidegrees}
+\todo{Aaron: Have $\ell_{i,j}$ been defined?}
 Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
 m).$ such
-that $D_1, \ldots, D_4$ are distinct divisors with bi-degrees $(1,0)
+that $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)
 , (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
@@
 	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k = 1}^n \alpha_k
-	\bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k s \right\}.
+	\bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k \right\}.
 \end{equation}
@@
 %Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. 
-Notice that if $\gamma
-\in (R_D)_d$, then 
+Suppose $\gamma
+\in (R_D)_d$. \todo{Aaron: Why is $\gamma$ defined? It doesn't seem to be used anywhere.}
+ Then 
 \[
@@
 where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^n c_i \bida_i = 0$,
-and $\sum_{i=1}^n c_i \bidb_i = 0$. Then we can any view $g$ inside the
-lattice $S \subseteq \mathbb{R}^{n + 1}$ given by ordered elements of
-the form $(d, c_1, \ldots, c_n)$ satisfying $c_i \ge - d \alpha_i$
-for all $i$, $\sum_{i=1}^n c_i \bida_i = 0$, and $\sum_{i = 1}^n c_i \bidb_i =
- 0$. From here, determining a spanning set for $(R_D)_d$ reduces to
-finding the extremal rays of $S$ by Proposition ~\ref{prop:cone-generation}.
-
+and $\sum_{i=1}^n c_i \bidb_i = 0$. We can any view $\sigma$ inside the
+lattice 
+\begin{align*}
+	\Sigma = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge - d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i \bida_i = \sum_{i = 1}^n c_i \bidb_i = 0 \}.	
+\end{align*}
+
+By Proposition ~\ref{prop:cone-generation}, in order to determining a spanning set for $(R_D)_d,$ it suffices to find the extremal rays of $\Sigma.$
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
-We first consider the cone inside of $\mathbb{R}^{n+1}$ given by elements of the
-form $(d, r_1, \ldots, r_n)$ satisfying $r_i \ge -d \alpha_i$ for
-all $i$ and $\sum_{i = 1}^n r_i (\bida_i + \bidb_i) = 0$.  This
+We first consider the subcone $\Sigma_1 \subset \Sigma$
+given by
+\begin{align*}
+	\Sigma_1 = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge - d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0 \}.	
+\end{align*}
+Then, $\Sigma_1$
 has extremal rays given by
@@
 	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
-	\ldots, -\alpha_m).
-\]
+	\ldots, -\alpha_n).
+\]
+for $1 \leq i \leq n$.
 
@@
 \]
-
-The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of Proposition ~\ref{prop:cone-generation}, so by applying that proposition, $R_D$ is generated in 
-degrees less than
+\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here.}
+
+The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of Proposition ~\ref{prop:cone-generation}, $R_D$ is generated in 
+degrees less than the sum of the degrees of the $e_i$ and $e_{i,j}$, which is
 \[
@@
 \]
+\todo{Aaron: Do you use $\sigma$ later?
+We are usually reserving $\sigma$ for a lattice point.
+Perhaps something like $\delta$ would be more appropriate if you want to refer to it later.
+Also, you should number if if you want to refer to it later.
+In general, it's bad style to define things in the proofs.
+This could have been defined prior to the theorem statement as well, which would simplify the statement.
+We should also then clarify that $\sigma$ depends on $D$.}
+
 \end{proof}
@@
 Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
-We can factor $\phi$ through
-\[
-	\Sigma =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d
-	\alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i.
-	\rangle 
-\]
-into
+We can factor $\phi$ through the semigroup ring
+\[
+	\bk[\Sigma] = \left \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d
+	\alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i
+	\right \rangle.
+\]
+by
 \[
@@
 
-Applying Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
+By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
 $2 \sigma$.
@@
 \end{thm}
+\todo{Aaron: Shouldn't $\tau$ not include $\sigma$?}
+
+\todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.}
 

### 2015-07-17 surfaces-write-up/surface-write-up.tex
edit references

@@
 Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$.
-Before doing so, we justify the assumption ~\eqref{eqn:bpm-basis-assumption} through a several convincing examples.
+Before doing so, we justify the assumption ~\eqref{eqn:pm-basis-assumption} through a several convincing examples.
 
@@
 
-In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
+In this section, the main aim is to prove Theorem ~\ref{thm:hirz-generators-relations}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
 
@@
 \begin{proof}
-We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
+We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ \todo{Aaron: Say where these polynomials live in}
+ such that $\psi$ has relations of the form
 \begin{equation}
@@
 \noindent
-for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
+for all $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is not used above, is $d$ supposed to be $i$?}
+ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
 ^n \bida_j c_j = 0$ and $\bidb_i + \sum_{i=1}^n \bidb_j c_j = 0$.
 
-To find such a $\beta$, we simply write $f_i$ as a 
+To find such a $\beta$, \todo{Aaron: why is there no $i$ subscript? I changed this in the $\bp^m$ case, probably copy past, mutatis mutandis}
+ we simply write $f_i$ as a 
 polynomial in $f_1, \ldots f_4$. Furthermore, these
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i$ for curves $D_i$ on $\hirz_k$.  Let $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
 linear polynomials in $y_0$ and $y_1$.
-Then $R_D$ is generated in degree less than 
+Then $R_D$ is generated in degrees at most
 \[
@@
 \noindent
-with relations generated in degree less than 
+with relations generated in degrees at most 
 \[

### 2015-07-17 surfaces-write-up/surface-write-up.tex

@@
 Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$.
-Before doing so, we justify the assumption ~\eqref{eqn:pm-basis-assumption} through a several convincing examples.
+Before doing so, we justify the assumption ~\eqref{eqn:bpm-basis-assumption} through a several convincing examples.
 
@@
 
-In this section, the main aim is to prove Theorem ~\ref{thm:hirz-generators-relations}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
+In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
 

### 2015-07-17 surfaces-write-up/surface-write-up.tex
some line breaks

@@
 \label{eg:hyperplane}
-Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0), H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$.
-Then, $R_D$ has generators in degree $2$ and $3$ which can be written as $u^2 \frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees less than $5$ the elements of $R_D$ can all be expressed as rational functions in $x_0, x_1$.
-However, in degree $6$, there is the rational function $\frac{x_1^2 x_2}{x_0^3}.$ Since this involves $x_2$, it must be a generator.
-
-This example generalizes slightly to any divisor of the form $D = \frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes \bq,$ with $k \in \bn$, showing that there will always exist a generator in degree $a(a+1).$
-
-This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
-Then, if $D_i = V(f_i)$ where all $f_i$ can be written as a polynomial function in $x_0, \ldots, x_{m-1},$ we have $R_D$ always has a generator in degree $\lcm(\den_i \cdot \bida_i)$.
+Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0),
+H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$. Then, $R_D$
+has generators in degree $2$ and $3$ which can be written as $u^2
+\frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees
+less than $5$ the elements of $R_D$ can all be expressed as
+rational functions in $x_0, x_1$. However, in degree $6$, there is
+the rational function $\frac{x_1^2 x_2}{x_0^3}$. Since this
+involves $x_2$, it must be a generator.
+
+This example generalizes slightly to any divisor of the form $D =
+\frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes \bq,$ with
+$k \in \bn$, showing that there will always exist a generator in
+degree $a(a + 1)$.
+
+This example further generalizes to the following situation:
+Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
+\otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm
+_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$. Then, if $D_i = V(f_i)$
+where all $f_i$ can be written as a polynomial function in $x_0,
+\ldots, x_{m-1},$ we have $R_D$ always has a generator in degree
+$\lcm(\den_i \cdot \bida_i)$.
 \end{example}
@@
 \label{rem:ghost-motivation}
-Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\cite[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
-The reason for this is that the divisors may ``be contained in a hyperplane,'' i.e., be expressable as functions in $m$ of the $m+1$ variables on $\bp^m$.
-This problem can easily be circumvented by adding in ``ghost points.'' That is, we may add divisors of the form $0 \cdot H_i$ to $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$, then $f_0, \ldots, f_n$.
-
-In Example ~\ref{eg:radical}, we show that it is still, in general, necessary to add ghost points, even when the irreducible components of a divisor are not all contained in a hyperplane.
+Example ~\ref{eg:hyperplane} shows that the naive generalization of
+~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
+$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
+that the divisors may ``be contained in a hyperplane,'' i.e.~ be
+expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
+This problem can easily be circumvented by adding in ``ghost
+points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
+$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
+then $f_0, \ldots, f_n$.
+
+In Example ~\ref{eg:radical}, we show that it is still, in general,
+necessary to add ghost points, even when the irreducible components
+of a divisor are not all contained in a hyperplane.
 \end{rem}
@@
 
-In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
+In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any Hirzebruch surface.
 

### 2015-07-17 surfaces-write-up/surface-write-up.tex

@@
 \label{sec:hirz}
-
-In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any Hirzebruch surface.
+In this section, the main aim is to prove Theorem
+~\ref{thm:hirz-generators-relations}, bounding the degree of
+generators and relations of the canonical ring of a $\bq$-divisor
+on any Hirzebruch surface.
 

### 2015-07-17 surfaces-write-up/surface-write-up.tex
many line breaks, cleanups, relabel an eqn, add -

@@
 \begin{align}
-\label{eqn:pm-relation-degree}
+\label{eqn:proj-relation-degree}
 	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
@@
 \begin{proof}
-We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
+We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$
+such that $\ker \psi$ is generated by
 \begin{equation}
@@
 \noindent
-for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
-^n \bida_j c_j = 0$.
-
-We define the $\beta_i$ above so that $\beta_i$ is the expansion of $f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m+1}]$.
-Furthermore, the relations given in Equation ~\eqref{eqn:pm-relation-degree}
-generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{r_i}$ to a canonical form, with $r_i = -\lfloor d \alpha_i\rfloor$ whenever $i  > m + 1$.
-
-For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. 
-To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by 
-Equation ~\eqref{eqn:pm-relation-degree}.  We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n) \in \Sigma,$ as defined in Equation ~\eqref{eqn:Sigma-def}.  
-Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.  Let 
-\begin{align*}
-	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
-\end{align*}
-Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\br_{\geq 0}}(e_1, \ldots, e_n)$ with $e_i$ as defined in Equation \ref{defn:e-i-proj}.
-Therefore, we can write any element of $\Sigma_i$ as
+for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying
+$\bida_i + \sum_{j = 1}^n \bida_j c_j = 0$.
+
+We define the $\beta_i$ above so that $\beta_i$ is the expansion of
+$f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m + 1}]$.
+Furthermore, the relations given in Equation
+~\eqref{eqn:proj-relation-degree} generate all relations, since they
+allow us to reduce any $ \prod_{j = 1}^n f_j^{r_i}$ to a canonical
+form, with $r_i = -\lfloor  d \alpha_i\rfloor$ whenever $i  > m + 1$.
+
+For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. To
+complete the proof, it suffices to bound the degree of generation
+of the relations of the form $(z_i - \beta_i) \prod_{j = 1}^n
+z_j^{c_j}$, by Equation ~\eqref{eqn:proj-relation-degree}. We first
+associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1,
+\ldots, c_n) \in \Sigma,$ as defined in Equation
+~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \mathbb{Z}^{n + 1}$
+be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying
+$r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
+Let
+\begin{align*}
+	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)},
+	\ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
+\end{align*}
+
+\noindent
+Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\br_{\geq 0}}
+(e_1, \ldots, e_n)$ with $e_i$ as defined in Equation
+~\ref{defn:e-i-proj}. Therefore, we can write any element of
+$\Sigma_i$ as
 \[
@@
 
-Whenever some $r_j \ge 1$, we can generate the relation $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j} = \epsilon_j \cdot h,$ where $\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and $h \in \Sigma_i$.
-Therefore, $\ker(\psi)$ is generated in degrees less than
+Whenever some $r_j \ge 1$, we can generate the relation $(z_i -
+\beta_i)\prod_{j=1}^n z_j^{c_j} = \epsilon_j \cdot h,$ where
+$\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and
+$h \in \Sigma_i$. Therefore, $\ker(\psi)$ is generated in degrees
+less than
 \[
@@
 
-Combining the above results, we obtain the following bound on the degrees of generators and relations of $R_D$.
+Combining the above results, we obtain the following bound on the
+degrees of generators and relations of $R_D$.
 
@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let
+$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
+$D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 Then $R_D$ is generated in degree at most 
@@
 \]
+
+\noindent
 with relations generated in degree at most
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
+	(	\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
 \]
 \end{thm}
+
 \begin{proof}
-The bound on degree of generation is precisely the content of Lemma ~\ref{lem:proj-generators}. It only remains to bound the degree of relations.
-By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma ~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.$ Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
-\[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+The bound on degree of generation is precisely the content of Lemma 
+~\ref{lem:proj-generators}. It only remains to bound the degree of 
+relations.
+
+By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees 
+up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma ~\ref{lem:proj-
+relations-psi}, $\ker(\psi),$ is generated in degrees up to $\frac{
+\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.$ Consequently, Lemma ~
+\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in 
+degrees less than
+\[
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
+	(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
 \]
@@
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
-We first consider the subcone $\Sigma_1 \subset \Sigma$
+We first consider the sub-cone $\Sigma_1 \subset \Sigma$
 given by
@@
 
+\noindent
 For $i \in \Tp(D)$ and $j \in \Tm(D)$, define
@@
 \]
+
+\noindent
 by

### 2015-07-17 surfaces-write-up/surface-write-up.tex
fix ref

@@
 By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees 
-up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma ~\ref{lem:proj-
-relations-psi}, $\ker(\psi),$ is generated in degrees up to $\frac{
-\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.$ Consequently, Lemma ~
-\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in 
-degrees less than
+up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
+~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in
+degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i$. 
+Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$
+is generated in degrees less than
 \[

### 2015-07-17 surfaces-write-up/surface-write-up.tex
editing final theorem, but possibly conflicting with peter

@@
 Let $\Sigma'\subseteq \Sigma$ be the \todo{change all $S$ to sigma's}
-set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
-$\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
-= 0$.
-Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}$ for $r\in \Tp, k\in \Tm$.  
+set
+\begin{align*}
+	\Sigma' = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
+	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
+= 0 \}
+\end{align*}
+
+Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
 For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$ component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$ component $\kappa_{j,i}''$.

### 2015-07-17 surfaces-write-up/surface-write-up.tex
delete extraneous .

@@
 \todo{Aaron: Have $\ell_{i,j}$ been defined?}
-Let $D=\sum_{i=1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di(\hirz_
-m).$ such
+Let $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$ such
 that $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)

### 2015-07-17 surfaces-write-up/surface-write-up.tex
small edit to last lemma

--- 2015-07-17 surfaces-write-up/surface-write-up.tex
@@
 \label{eg:hyperplane}
-Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0),
-H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$. Then, $R_D$
-has generators in degree $2$ and $3$ which can be written as $u^2
-\frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees
-less than $5$ the elements of $R_D$ can all be expressed as
-rational functions in $x_0, x_1$. However, in degree $6$, there is
-the rational function $\frac{x_1^2 x_2}{x_0^3}$. Since this
-involves $x_2$, it must be a generator.
-
-This example generalizes slightly to any divisor of the form $D =
-\frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes \bq,$ with
-$k \in \bn$, showing that there will always exist a generator in
-degree $a(a + 1)$.
-
-This example further generalizes to the following situation:
-Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
-\otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm
-_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$. Then, if $D_i = V(f_i)$
-where all $f_i$ can be written as a polynomial function in $x_0,
-\ldots, x_{m-1},$ we have $R_D$ always has a generator in degree
-$\lcm(\den_i \cdot \bida_i)$.
+Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0), H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$.
+Then, $R_D$ has generators in degree $2$ and $3$ which can be written as $u^2 \frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees less than $5$ the elements of $R_D$ can all be expressed as rational functions in $x_0, x_1$.
+However, in degree $6$, there is the rational function $\frac{x_1^2 x_2}{x_0^3}.$ Since this involves $x_2$, it must be a generator.
+
+This example generalizes slightly to any divisor of the form $D = \frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes \bq,$ with $k \in \bn$, showing that there will always exist a generator in degree $a(a+1).$
+
+This example further generalizes to the following situation: Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$.
+Then, if $D_i = V(f_i)$ where all $f_i$ can be written as a polynomial function in $x_0, \ldots, x_{m-1},$ we have $R_D$ always has a generator in degree $\lcm(\den_i \cdot \bida_i)$.
 \end{example}
@@
 \label{rem:ghost-motivation}
-Example ~\ref{eg:hyperplane} shows that the naive generalization of
-~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
-$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
-that the divisors may ``be contained in a hyperplane,'' i.e.~ be
-expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
-This problem can easily be circumvented by adding in ``ghost
-points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
-$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
-then $f_0, \ldots, f_n$.
-
-In Example ~\ref{eg:radical}, we show that it is still, in general,
-necessary to add ghost points, even when the irreducible components
-of a divisor are not all contained in a hyperplane.
+Example ~\ref{eg:hyperplane} shows that the naive generalization of ~\cite[Theorem 8]{dorney:canonical} of generation in degree at most $\sum_{i=1}^{n}\ell_i$ cannot possibly hold.
+The reason for this is that the divisors may ``be contained in a hyperplane,'' i.e., be expressable as functions in $m$ of the $m+1$ variables on $\bp^m$.
+This problem can easily be circumvented by adding in ``ghost points.'' That is, we may add divisors of the form $0 \cdot H_i$ to $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$, then $f_0, \ldots, f_n$.
+
+In Example ~\ref{eg:radical}, we show that it is still, in general, necessary to add ghost points, even when the irreducible components of a divisor are not all contained in a hyperplane.
 \end{rem}
@@
 \begin{align}
-\label{eqn:proj-relation-degree}
+\label{eqn:pm-relation-degree}
 	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
@@
 \begin{proof}
-We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$
-such that $\ker \psi$ is generated by
+We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$ such that $\ker \psi$ is generated by
 \begin{equation}
@@
 \noindent
-for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying
-$\bida_i + \sum_{j = 1}^n \bida_j c_j = 0$.
-
-We define the $\beta_i$ above so that $\beta_i$ is the expansion of
-$f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m + 1}]$.
-Furthermore, the relations given in Equation
-~\eqref{eqn:proj-relation-degree} generate all relations, since they
-allow us to reduce any $ \prod_{j = 1}^n f_j^{r_i}$ to a canonical
-form, with $r_i = -\lfloor  d \alpha_i\rfloor$ whenever $i  > m + 1$.
-
-For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. To
-complete the proof, it suffices to bound the degree of generation
-of the relations of the form $(z_i - \beta_i) \prod_{j = 1}^n
-z_j^{c_j}$, by Equation ~\eqref{eqn:proj-relation-degree}. We first
-associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1,
-\ldots, c_n) \in \Sigma,$ as defined in Equation
-~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \mathbb{Z}^{n + 1}$
-be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying
-$r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
-Let
-\begin{align*}
-	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)},
-	\ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
-\end{align*}
-
-\noindent
-Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\br_{\geq 0}}
-(e_1, \ldots, e_n)$ with $e_i$ as defined in Equation
-~\ref{defn:e-i-proj}. Therefore, we can write any element of
-$\Sigma_i$ as
+for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
+^n \bida_j c_j = 0$.
+
+We define the $\beta_i$ above so that $\beta_i$ is the expansion of $f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m+1}]$.
+Furthermore, the relations given in Equation ~\eqref{eqn:pm-relation-degree}
+generate all relations, since they allow us to reduce any $\prod_{j =
+1}^n f_j^{r_i}$ to a canonical form, with $r_i = -\lfloor d \alpha_i\rfloor$ whenever $i  > m + 1$.
+
+For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. 
+To complete the proof, it suffices to bound the degree of generation of the relations of the form $(z_i - \beta_i) \prod_{j=1}^n z_j^{c_j}$, by 
+Equation ~\eqref{eqn:pm-relation-degree}.  We first associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1, \ldots, c_n) \in \Sigma,$ as defined in Equation ~\eqref{eqn:Sigma-def}.  
+Let $\Sigma_i \subseteq \mathbb{Z}^{n+1}$ be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying $r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.  Let 
+\begin{align*}
+	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)}, \ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
+\end{align*}
+Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\br_{\geq 0}}(e_1, \ldots, e_n)$ with $e_i$ as defined in Equation \ref{defn:e-i-proj}.
+Therefore, we can write any element of $\Sigma_i$ as
 \[
@@
 
-Whenever some $r_j \ge 1$, we can generate the relation $(z_i -
-\beta_i)\prod_{j=1}^n z_j^{c_j} = \epsilon_j \cdot h,$ where
-$\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and
-$h \in \Sigma_i$. Therefore, $\ker(\psi)$ is generated in degrees
-less than
+Whenever some $r_j \ge 1$, we can generate the relation $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j} = \epsilon_j \cdot h,$ where $\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and $h \in \Sigma_i$.
+Therefore, $\ker(\psi)$ is generated in degrees less than
 \[
@@
 
-Combining the above results, we obtain the following bound on the
-degrees of generators and relations of $R_D$.
+Combining the above results, we obtain the following bound on the degrees of generators and relations of $R_D$.
 
@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let
-$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
-$D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 Then $R_D$ is generated in degree at most 
@@
 \]
-
-\noindent
 with relations generated in degree at most
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(	\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
 \]
 \end{thm}
-
 \begin{proof}
-The bound on degree of generation is precisely the content of Lemma 
-~\ref{lem:proj-generators}. It only remains to bound the degree of 
-relations.
-
-By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees 
-up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
-~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in
-degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i$. 
-Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$
-is generated in degrees less than
-\[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+The bound on degree of generation is precisely the content of Lemma ~\ref{lem:proj-generators}. It only remains to bound the degree of relations.
+By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma ~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.$ Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in degrees less than
+\[
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
 \]
@@
 \label{sec:hirz}
-In this section, the main aim is to prove Theorem
-~\ref{thm:hirz-generators-relations}, bounding the degree of
-generators and relations of the canonical ring of a $\bq$-divisor
-on any Hirzebruch surface.
+
+In this section, the main aim is to prove Theorem ~\ref{thm:hirz-generators-relations}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any hirzebruch surface.
 
@@
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
-We first consider the sub-cone $\Sigma_1 \subset \Sigma$
+We first consider the subcone $\Sigma_1 \subset \Sigma$
 given by
@@
 
-\noindent
 For $i \in \Tp(D)$ and $j \in \Tm(D)$, define
@@
 \]
-
-\noindent
 by
@@
 \noindent
-for all $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is not used above, is $d$ supposed to be $i$?}
+for any degree $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is not used above, is $d$ supposed to be $i$? Peter: Fixed?}
  and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
-^n \bida_j c_j = 0$ and $\bidb_i + \sum_{i=1}^n \bidb_j c_j = 0$.
+^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
 

### 2015-07-21 surfaces-write-up/surface-write-up.tex
two pts p^1 remark edit last sentence precisely
remove some completed todos
added linebreaks

@@
 \maketitle
-\todo{make title shorter so it doesn't overlap with page numbers}
 \todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most''}
@@
 
-By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, one can translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
-We expect that  will similarly allow one to generalize yield an equivalence of categories between an appropriate subcategory of $m$-dimensional orbifolds and a subcategory of $m$-dimensional algebraic spaces.
-In particular, this will allow us to translate rings of Hilbert modular forms and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
-Thereby, our techniques would give a bound on generators and relations for Hilbert and Siegel modular forms with certain underlying spaces.
+By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
+one can translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
+We expect that  will similarly allow one to generalize yield an equivalence of
+categories between an appropriate subcategory of $m$-dimensional orbifolds and
+a subcategory of $m$-dimensional algebraic spaces.
+In particular, this will allow us to translate rings of Hilbert modular forms
+and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a
+Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
+Thereby, our techniques would give a bound on generators and relations for
+Hilbert and Siegel modular forms with certain underlying spaces.
 \todo{include references}
@@
 \end{align*}
-in terms of certain moduli spaces.
-$\bq$-divisors on surfaces also naturally appear when considering the canonical ring of surfaces of Kodaira dimension 1.
-A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and their canonical ring are most naturally described in the setting of $\bq$-divisors.
-\todo{Add references}
+in terms of certain moduli spaces. $\bq$-divisors on surfaces also naturally
+appear when considering the canonical ring of surfaces of Kodaira dimension 1.
+A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and
+their canonical ring are most naturally described in the setting of
+$\bq$-divisors. \todo{Add references}
 
@@
 \label{proj-generators-relations-intro}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let
+$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$
+for all $i$; suppose $\deg(f_i) = a_i$. 
 Then $R_D$ is generated in degree at most 
@@
 \end{rem}
-\todo{possibly define mediant}
 
@@
 \label{lem:composite-map}
-Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$.
-Suppose we have a surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i \mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
-Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$ Then, define
+Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$. Suppose we have a
+surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i
+\mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
+Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$
+Then, define
 \begin{align*}
@@
 \]
-Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$ is at most the maximum of the minimal degree of generation of $\ker \chi$ and the minimal degree of generation of $\ker \psi$.
+Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$
+is at most the maximum of the minimal degree of generation of $\ker \chi$ and
+the minimal degree of generation of $\ker \psi$.
 \end{lem}
@@
 \]
-To see this, note that $\rho$ is injective and $\tau$ is surjective\ because $\phi = \chi \circ \psi$.
-Additionally, $\tau \circ \rho = 0$ by definition of the kernel of $\chi$.
-Finally, if $a \in\ker \tau$, then by definition $\chi(a) = 0,$ so $a \in \im \rho$.
-
-This shows that lifts of generators of $\ker \psi$ together with images of generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
+To see this, note that $\rho$ is injective and $\tau$ is surjective\ because
+$\phi = \chi \circ \psi$. Additionally, $\tau \circ \rho = 0$ by definition of
+the kernel of $\chi$. Finally, if $a \in\ker \tau$, then by definition $\chi(a)
+= 0,$ so $a \in \im \rho$.
+
+This shows that lifts of generators of $\ker \psi$ together with images of
+generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
 \end{proof}
@@
 \label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$ is generated in degrees up to $2(\sum_{i=1}^{r}d_r-1)$.
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
+extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$
+is generated in degrees up to $2(\sum_{i=1}^{r}d_r-1)$.
 \end{lem}
 \begin{proof}
-Since $e_1, \ldots, e_r$ are extremal rays, by Proposition ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{r}e_i$.
-Now, let $\lambda_0 := 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be written in the form $\lambda_i = \sum_{i=1}^{r}r_i e_i$ with $0 \leq r_i < 1.$ Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in the above canonical form, yielding a relation in degree at most $\deg \lambda_i + \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$ Furthermore, these relations generate all relations, as one can apply a sequence of these relations to put any $\sigma \in \Sigma$ into canonical form $\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Proposition ~\ref{prop:cone-generation}.
+Since $e_1, \ldots, e_r$ are extremal rays, by Proposition
+~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
+in a canonical form $\lambda + \sum_{i=1}^{r}e_i$. Now, let $\lambda_0 :=
+0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be
+written in the form $\lambda_i = \sum_{i=1}^{r}r_i e_i$ with $0 \leq r_i < 1.$
+Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in
+the above canonical form, yielding a relation in degree at most $\deg \lambda_i
++ \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$
+Furthermore, these relations generate all relations, as one can apply a
+sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
+$\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Proposition
+~\ref{prop:cone-generation}.
 \end{proof}
@@
 \label{sec:proj}
-In this section, we bound the degrees of generators and relations for divisors on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case was covered in \cite{dorney:canonical}.
+In this section, we bound the degrees of generators and relations for divisors
+on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case was covered in
+\cite{dorney:canonical}.
 
@@
 
-For the remainder of this section, we shall fix $m \geq 1$ and choose an isomorphism $\bp^m \cong \proj V$ so that $x_0,\ldots, x_m$ form a basis for $V$.
-We will think of $x_i$ as a rational section of $H^0(\bp^m, \sco_{\bp^m})$ of degree 1.
+For the remainder of this section, we shall fix $m \geq 1$ and choose an
+isomorphism $\bp^m \cong \proj V$ so that $x_0,\ldots, x_m$ form a basis for
+$V$.  We will think of $x_i$ as a rational section of $H^0(\bp^m,
+\sco_{\bp^m})$ of degree 1.
 
@@
 \end{align*}
-where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. Let $D_i$ be Cartier divisors such that $D_i = V(f_i)$.
-We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a basis for degree one rational functions on $\bp^m$.
+where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. Let $D_i$ be
+Cartier divisors such that $D_i = V(f_i)$.
+We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a
+basis for degree one rational functions on $\bp^m$.
 
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-~\eqref{align:pm-span} lie in $H^0(\bp^m,dD)$.
-To complete the proof, it suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form a basis of $H^0(\bp^m,dD)$.
-Note that there $\binom{m+ \lfloor dD \rfloor }{m}$ functions satisfying condition ~\eqref{align:pm-basis}.
-However we know $h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show that those functions satisfying condition ~\eqref{align:pm-basis} are independent.
-This follows from the assumption that $f_0,\ldots f_n$ form a basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $ monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor $ rational functions.
+~\eqref{align:pm-span} lie in $H^0(\bp^m,dD)$. To complete the proof, it
+suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
+a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \lfloor dD \rfloor }{m}$
+functions satisfying condition ~\eqref{align:pm-basis}. However we know
+$h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show
+that those functions satisfying condition ~\eqref{align:pm-basis} are
+independent. This follows from the assumption that $f_0,\ldots f_n$ form a
+basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $
+monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor
+$ rational functions.
 \end{proof}
@@
 \begin{proof}
-We will first check that $F^{\vec v}_i$ determine a system of minimal generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} : \deg \vec{v} = \left\lfloor
+We will first check that $F^{\vec v}_i$ determine a system of minimal
+generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} : \deg \vec{v} =
+\left\lfloor
 \frac{p}{q} \right\rfloor \right\}$ are minimal generators in
@@
 \frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
-and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that $\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
+and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that
+$\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
 (see Definition ~\ref{defn:lower-approximation}).
@@
 {dorney:canonical} demonstrates that each lattice point $(\beta, \gamma) \in
-\bz_{\geq 0}^2$ with $\gamma \leq \beta \alpha$ lies in the $\bz_{\geq 0}$ span of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
+\bz_{\geq 0}^2$ with $\gamma \leq \beta \alpha$ lies in the $\bz_{\geq 0}$ span
+of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
 some $h \in \{0, \ldots, r\}$. Let $(\beta, \gamma) = \kappa_1
@@
 \noindent
-We can then write $\vec{v}  = \sum_{\lambda=1}^{\kappa_1}\vec{w}_{(\lambda)} + \sum_{\eta=1}^{\kappa_2} \vec z_{(\eta)}$ with $w_{(\lambda)} \in \mss_h$ and $z_{(\eta)} \in \mss_{h+1}$ to give a decomposition
+We can then write $\vec{v}  = \sum_{\lambda=1}^{\kappa_1}\vec{w}_{(\lambda)} +
+\sum_{\eta=1}^{\kappa_2} \vec z_{(\eta)}$ with $w_{(\lambda)} \in \mss_h$ and
+$z_{(\eta)} \in \mss_{h+1}$ to give a decomposition
 \begin{align}
@@
 and $F_{h + 1}^{\vec{z}_{(\eta)}}$ which are in the form
-prescribed in the theorem statement.
-Since we wrote an arbitrary monomial $\frac{u^{\beta} x^{\vec{v}}}{x_k^\gamma} \in R_D$ as a product of generators, this shows that $F_i^{\vec v}$ minimally generate $R_D$.
+prescribed in the theorem statement. Since we wrote an arbitrary monomial
+$\frac{u^{\beta} x^{\vec{v}}}{x_k^\gamma} \in R_D$ as a product of generators,
+this shows that $F_i^{\vec v}$ minimally generate $R_D$.
 
@@
 In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
-has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} where $h$ depends on $i, j$, so we notate $h = h_{i, j} \in \{1, \ldots, r\}$. We also have
+has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} where $h$
+depends on $i, j$, so we notate $h = h_{i, j} \in \{1, \ldots, r\}$. We also
+have
 that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
@@
 hyperplanes cannot be bounded so tightly. The two-point
-$\bp^1$ result leverages particular facts about the structure of
-$\bp^1$. \todo{Possibly say what facts?}
+$\bp^1$ result leverages the fact that $\bp^1$ has two
+independent coordinates.
 \end{rem}
@@
 
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ $\deg(f_i) = a_i$ for all $i$.
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be
+homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$
+$\deg(f_i) = a_i$ for all $i$.
 
@@
 
-Our first aim in this section is to prove Theorem ~\ref{thm:proj-generators-relations} bounding the number of generators and relations of $R_D$.
-Before doing so, we justify the assumption ~\eqref{eqn:pm-basis-assumption} through a several convincing examples.
+Our first aim in this section is to prove Theorem
+~\ref{thm:proj-generators-relations} bounding the number of generators and
+relations of $R_D$. Before doing so, we justify the assumption
+~\eqref{eqn:pm-basis-assumption} through a several convincing examples.
 
@@
 \label{eg:radical}
-Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 + x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) - \frac{1}{596}V(x_1^2 + x_2^2 + x_3^2)$.
-In degree $355216 = 5 \cdot 7 \cdot 17 \cdot 596$, this has dimension $10$.
+Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 +
+x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) - \frac{1}{596}V(x_1^2 + x_2^2 +
+x_3^2)$. In degree $355216 = 5 \cdot 7 \cdot 17 \cdot 596$, this has dimension
+$10$. 
 \todo{Clarify what this example means by the lattice approach}
-However, we possibly use the lattice approach, as all lower degrees only have dimension 1. In fact, we may construct similar examples using any set of degree $n$ divisor with very small degree.
+However, we possibly use the lattice approach, as all lower degrees only have
+dimension 1. In fact, we may construct similar examples using any set of degree
+$n$ divisor with very small degree.
 \end{example}
@@
 
-Having justified the necessity of adding ghost points, we proceed to bound the number of generators and relations.
+Having justified the necessity of adding ghost points, we proceed to bound the
+number of generators and relations.
 
@@
 \begin{align}\label{eqn:Sigma-def}
-	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0 \right \}.
+	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
+\alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
+\right \}.
 \end{align}
@@
 \begin{equation}\label{defn:e-i-proj}
-	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j, -\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
+	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
+-\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j,
+-\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
 \end{equation}
@@
 \label{rem:pm-extremal-rays}
-Note for future reference that the extremal rays of the cone $\Sigma$, as defined in the proof of Lemma ~\ref{lem:proj-generators} correspond to the elements
+Note for future reference that the extremal rays of the cone $\Sigma$, as
+defined in the proof of Lemma ~\ref{lem:proj-generators} correspond to the
+elements
 \begin{equation}
@@
 
-Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i \bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
-We can factor $\phi$ through the semigroup ring
-\[
-	\bk[\Sigma] =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in \mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i \rangle. 
+Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i
+\bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let $\phi$ be the
+surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through the
+semigroup ring 
+\[
+	\bk[\Sigma] =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in
+\mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i =
+\sum_{i=1}^{n} \bidb_i c_i \rangle. 
 \]
@@
 
-By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ and we next calculate the degree of generation of $\ker \psi$:
+By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of
+$\ker(\chi)$ and we next calculate the degree of generation of $\ker \psi$:
 
@@
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch surfaces before this paragraph; especially, describe what it's sections look like.}
+linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch
+surfaces before this paragraph; especially, describe what it's sections look
+like.}
 
@@
 \begin{align*}
-	\Sigma = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge - d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i \bida_i = \sum_{i = 1}^n c_i \bidb_i = 0 \}.	
+	\Sigma = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge - d
+\alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i \bida_i = \sum_{i =
+1}^n c_i \bidb_i = 0 \}.	
 \end{align*}
 
-By Proposition ~\ref{prop:cone-generation}, in order to determining a spanning set for $(R_D)_d,$ it suffices to find the extremal rays of $\Sigma.$
+By Proposition ~\ref{prop:cone-generation}, in order to determining a spanning
+set for $(R_D)_d,$ it suffices to find the extremal rays of $\Sigma.$
 To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
@@
 \begin{align*}
-	\Sigma_1 = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge - d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0 \}.	
+	\Sigma_1 = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge -
+d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0
+\}.	
 \end{align*}
@@
 
-The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of Proposition ~\ref{prop:cone-generation}, $R_D$ is generated in 
+The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of
+Proposition ~\ref{prop:cone-generation}, $R_D$ is generated in 
 degrees less than the sum of the degrees of the $e_i$ and $e_{i,j}$, which is
@@
 \]
-\todo{Aaron: Do you use $\sigma$ later?
-We are usually reserving $\sigma$ for a lattice point.
-Perhaps something like $\delta$ would be more appropriate if you want to refer to it later.
-Also, you should number if if you want to refer to it later.
-In general, it's bad style to define things in the proofs.
-This could have been defined prior to the theorem statement as well, which would simplify the statement.
-We should also then clarify that $\sigma$ depends on $D$.}
+\todo{Aaron: Do you use $\sigma$ later? We are usually reserving $\sigma$ for a
+lattice point. Perhaps something like $\delta$ would be more appropriate if you
+want to refer to it later. Also, you should number if if you want to refer to
+it later. In general, it's bad style to define things in the proofs. This could
+have been defined prior to the theorem statement as well, which would simplify
+the statement. We should also then clarify that $\sigma$ depends on $D$.}
 
@@
 
-Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\sigma$ (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the surjection $k[x_1, \ldots x_r] \to R_D$.
-We can factor $\phi$ through the semigroup ring
+Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\sigma$
+(as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the
+surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through the
+semigroup ring 
 \[
@@
 \begin{proof}
-We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ \todo{Aaron: Say where these polynomials live in}
+We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ \todo{Aaron:
+Say where these polynomials live in}
  such that $\psi$ has relations of the form
@@
 \noindent
-for any degree $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is not used above, is $d$ supposed to be $i$? Peter: Fixed?}
+for any degree $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is
+not used above, is $d$ supposed to be $i$? Peter: Fixed?}
  and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
@@
 
-To find such a $\beta$, \todo{Aaron: why is there no $i$ subscript? I changed this in the $\bp^m$ case, probably copy past, mutatis mutandis}
+To find such a $\beta$, \todo{Aaron: why is there no $i$ subscript? I changed
+this in the $\bp^m$ case, probably copy past, mutatis mutandis}
  we simply write $f_i$ as a 
@@
 generate all relations, since they allow us to reduce any $\prod_{j =
-1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i \rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}
+1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
+\rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}
 
@@
 
-Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
-For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$ component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$ component $\kappa_{j,i}''$.
-Then a careful computation deduces that 
+Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n
+{y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in
+\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
+For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
+component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in
+degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$
+component $\kappa_{j,i}''$.
+Then a careful computation implies that 
 %if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
@@
 \]
-Let $M$ be the set of monomials terms of $\beta_j$.  Then for $\mu\in M$, we can further compute that the lattice point corresponding to $\mu \prod_{j=1}^n {f_i}^{c_i}$ is of the form
+Let $M$ be the set of monomials terms of $\beta_j$.  Then for $\mu\in M$, we
+can further compute that the lattice point corresponding to $\mu \prod_{j=1}^n
+{f_i}^{c_i}$ is of the form
 \[
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are independent linear
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i =
+V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
+independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
@@
 \label{sec:conc}
-This paper extends the work of O'Dorney \cite{dorney:canonical} on $\bp^1$ to $\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and relations of canonical rings of arbitrary divisors $D$.
-The methods for deducing bounds on generators and relations of $\hirz_k$ applied similar methods to that of O'Dorney's for $\bp^1$.
-
-We can view $\hirz_0$ as $\bp^1\times \bp^1$ and more generally $\hirz_k$ as a $\bp^1$ bundle over $\bp^1$.  One might hope that similar ideas could be generalized to all bundles.  Specifically:
+This paper extends the work of O'Dorney \cite{dorney:canonical} on $\bp^1$ to
+$\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and
+relations of canonical rings of arbitrary divisors $D$.  The methods for
+deducing bounds on generators and relations of $\hirz_k$ applied similar
+methods to that of O'Dorney's for $\bp^1$.
+
+We can view $\hirz_0$ as $\bp^1\times \bp^1$ and more generally $\hirz_k$ as a
+$\bp^1$ bundle over $\bp^1$.  One might hope that similar ideas could be
+generalized to all bundles.  Specifically:
 \begin{question}
 \label{qn:general-product-bundle}
-Suppose $X$ and $Y$ are schemes.
-Let $D$ be a divisor on $X\times Y$ or more generally on an $X$ bundles over $Y$.
-Can we describe $D$ in terms of divisors $D_1, \ldots D_n$ on $X$ and $D_1', \ldots d_n'$ on $Y$.
-Furthermore, can we find generators for $R_D$ and its ideal of relations using those of the $R_{D_i}$'s and $R_{D_j'}$'s?
+Suppose $X$ and $Y$ are schemes.  Let $D$ be a divisor on $X\times Y$ or more
+generally on an $X$ bundles over $Y$.  Can we describe $D$ in terms of divisors
+$D_1, \ldots D_n$ on $X$ and $D_1', \ldots d_n'$ on $Y$.  Furthermore, can we
+find generators for $R_D$ and its ideal of relations using those of the
+$R_{D_i}$'s and $R_{D_j'}$'s?
 \end{question}
 
-An immediate obstruction to this is the fact that we critically used the fact that $\hirz_k$ has well-defined bi-degrees.
-Unfortunately, in general $\Pic(X \times Y) \not \cong \Pic(X) \times \Pic(Y)$.
-
-Alternatively, we can view $\hirz_1$ as $\bp^2$ blown up at a point.  This suggests the following question:
+An immediate obstruction to this is the fact that we critically used the fact
+that $\hirz_k$ has well-defined bi-degrees.  Unfortunately, in general $\Pic(X
+\times Y) \not \cong \Pic(X) \times \Pic(Y)$.
+
+Alternatively, we can view $\hirz_1$ as $\bp^2$ blown up at a point.  This
+suggests the following question:
 \begin{question}
 \label{qn:general-blowup}
-Let $X$ be a scheme.
-Let $X'$ be the blowup of $X$ at a point $P$ with a divisor $D$.
-First, is there a way to express $D$ in terms of divisors $D_1, \ldots, D_n$ on $X$?
-Furthermore, is there a way to describe generators and relations of $R_D$ in terms of those of $R_{D_i}$ for all $i$.
+Let $X$ be a scheme.  Let $X'$ be the blowup of $X$ at a point $P$ with a
+divisor $D$.  First, is there a way to express $D$ in terms of divisors $D_1,
+\ldots, D_n$ on $X$?  Furthermore, is there a way to describe generators and
+relations of $R_D$ in terms of those of $R_{D_i}$ for all $i$.
 \end{question}
 
-Fortunately, the Picard group of $X$ blown up at a point is the same as that of $X$ times an additional copy of $\bz$.
-Perhaps analyzing the argument from Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not the theorem with the same name} in the case of $\hirz_k$ from the perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by the blowup, might suggest a general method for blowups.
-
-Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for all rational surfaces, via the minimal model program for surfaces \todo{Reference}.
-One might to provide an analogous result to Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not the theorem with the same name} in the case of all minimal surfaces:
+Fortunately, the Picard group of $X$ blown up at a point is the same as that of
+$X$ times an additional copy of $\bz$.  Perhaps analyzing the argument from
+Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma
+and not the theorem with the same name} in the case of $\hirz_k$ from the
+perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by
+the blowup, might suggest a general method for blowups.
+
+Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for
+all rational surfaces, via the minimal model program for surfaces
+\todo{Reference}.  One might to provide an analogous result to Lemma
+~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not
+the theorem with the same name} in the case of all minimal surfaces:
 \begin{question}
 \label{qn:general-minimal-surface}
-Can we describe generators and relations of $R_D$ for $D$ a divisor on an arbitrary minimal surface $X$?
+Can we describe generators and relations of $R_D$ for $D$ a divisor on an
+arbitrary minimal surface $X$?
 \end{question}

### 2015-07-22 surfaces-write-up/surface-write-up.tex
edits to lemma 4.2

@@
 \[
-	\sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
+	\sigma = \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
 	{i \in \Tp(D) \\ j\in \Tm(D)}} (\bida_i \bidb_j - \bida_j \bidb_i)
@@
 %Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. 
-Suppose $\gamma
-\in (R_D)_d$. \todo{Aaron: Why is $\gamma$ defined? It doesn't seem to be used anywhere.}
+Suppose $g
+\in (R_D)_d$.
  Then 
@@
 \noindent
-where each $c_i \ge - \alpha_i c_i$, $\sum_{i=1}^n c_i \bida_i = 0$,
-and $\sum_{i=1}^n c_i \bidb_i = 0$. We can any view $\sigma$ inside the
+for some $c_i \ge - \alpha_i d$ such that $\sum_{i=1}^n c_i \bida_i = 0$
+and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $\sigma$ inside the
 lattice 
@@
 $\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S \subseteq \Delta
-^{n-1}$. The extremal rays of $S$ must lie on the edges of $\Delta
-^{n - 1}$ \todo{Peter: Do we need to cite/argue this, or is it clear?}.
-Thus, the extremal rays of $S$ are given by the $e_i$'s
+^{n-1}$.  Since $\Sigma \subseteq S$, if each extremal rays of $S$ contains an element of the lattice $\Sigma$, then those representatives in $\Sigma$ are in fact the extremal rays of $\Sigma$.
+
+The extremal rays of $S$ must lie on the edges of $\Delta
+^{n - 1}$, \todo{Peter: Do we need to cite/argue this, or is it clear?}
+and are given by the $e_i$'s
 contained in $H$ and the intersection points $e_{i, j}$ of $H$
-and the edges $\overline{e_i e_j}$ of the simplex between
+together with the edges $\overline{e_i e_j}$ of the simplex between
 distinct $e_i, e_j$ not contained in $H$.
-\todo{more detail above}
-
-We can calculate elements of $R_D$ whose
-corresponding lattice points lie on these extremal rays:
+\todo{more detail above;  Peter: resolved?}
+The following are elements of $R_D$ whose corresponding lattice point lies on each of the above extremal rays:
 
@@
 by introducing new variables}
-\[
+\begin{equation}\label{eqn:epsilon_i}
 	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha_k \ell_i \gcd(\bida_i, \bidb_i)})
@@
 	\alpha_k (\bida_k + \bidb_k)}) \in H^0(\ell_i \gcd(\bida_i, \bidb_i) D).
-\]
+\end{equation}
 
@@
 For $i \in \Tp(D)$ and $j \in \Tm(D)$, define
-\[
+\begin{equation}\label{eqn:epsilon_i,j}
 	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
-	j - \bida_j \bidb_i)}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i, j}
-	(\bida_i \bidb_j - \bida_j \bidb_i) D \right)
-\]
+	j - \bida_j \bidb_i)} {f_i}^{s_1} {f_j}^{s_2}\right) \in H^0(\ell_{i, j}
+	(\bida_i \bidb_j - \bida_j \bidb_i) D
+\end{equation}
 
@@
 
-The set of $e_i$ and $e_{i,j}$ given above satisfies the conditions of
-Proposition ~\ref{prop:cone-generation}, $R_D$ is generated in 
+The set of $e_i$'s and $e_{i,j}$'s corresponding to the $\epsilon_i$'s and $\epsilon_{i,j}$'s given above satisfies the conditions of
+Proposition ~\ref{prop:cone-generation}, implying that $R_D$ is generated in 
 degrees less than the sum of the degrees of the $e_i$ and $e_{i,j}$, which is

### 2015-07-22 surfaces-write-up/surface-write-up.tex
edited intro and abstract

@@
 \begin{abstract}
- 	Bounding generator and relation degrees of general $\bq$-divisors
-	on projective spaces $\bp^n$ and Hirzebruch surfaces.
+ 	We give bounds on the degree of generation and relations of
+	canonical rings of arbitrary $\bq$-divisors
+	on projective spaces of all dimensions
+	and Hirzebruch surfaces.
 \end{abstract}
@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{canonical ring} $R(X, D) := \bigoplus_{d \geq 0} H^0(X, dD)$
-has connections to rings of Hilbert and Siegel modular forms. In the
-study of these canonical rings, it is natural to describe
-presentations. We study the generators and relations of canonical
+\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} H^0(X, \lfloor dD \rfloor)$.
+We study the generators and relations of canonical
 rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
@@
 $R(X, D)$. In particular, we give a complete description of the
-canonical ring when $X = \bp^m$ and $D$ is an $\bq$-divisor
-containing one hypersurface and give stronger bounds when
-$D$ is any effective $\bq$-divisor on $\bp^m$.
-
-In part, this work is motivated by moving to generalize the work
-of O'Dorney \cite{dorney:canonical} who gives similar descriptions
+canonical ring when $X = \bp^m$ and $D$ is any effective
+$\bq$-divisor.
+
+In part, this work is motivated by
+of O'Dorney \cite{dorney:canonical}, who gives similar descriptions
 of canonical rings for general $\bq$-divisors on $\bp^1$. For
@@
 useful bounds on rings of modular forms of Fuchsian groups.
-The results of this work may have applications to Hilbert
-and Siegel modular forms. \todo{reword last sentence}
-
-\todo{Hassett-keel, see reference in davids paper about parametrizing $\alpha$ and considering stacky divisors.
-Would want to know whether they are a moduli space, though we just give generators and relations.
-This is one of the few examples other than that of nagata dealing with stacky surfaces.}
-
-The work in this paper also has relations to certain rings of Hilbert 
+
+The work in this paper may help calculate a presentation of certain rings of Hilbert 
 modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
-modular forms are both to higher dimensions variables. In the case of 
-Hilbert modular forms, one considers modular forms on a product of $m$
-upper half planes, which transform under the action of finite index 
-subgroups of the groups of positive determinant matrices. Similarly, Siegel 
-modular forms are modular forms on the Siegel upper half space which are 
-stable under the action of the symplectic group.
-
+modular forms are both generalizations of modular forms to higher dimensions.
 By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
-one can translate the analytic category of 1-dimensional complex orbifolds to the algebraic category of stacky curves. 
-We expect that  will similarly allow one to generalize yield an equivalence of
+one can translate the analytic category of 1-dimensional complex orbifolds to
+the algebraic category of stacky curves. 
+We expect that one can generalize this result to yield an equivalence of
 categories between an appropriate subcategory of $m$-dimensional orbifolds and
 a subcategory of $m$-dimensional algebraic spaces.
-In particular, this will allow us to translate rings of Hilbert modular forms
-and Siegel modular forms whose underlying space is isomorphic to $\bp^m$ or a
+In particular, this would allow us to translate rings of Hilbert modular forms
+and Siegel modular forms whose coarse space is a projective space or a
 Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
@@
 Another closely related topic is the Hassett-Keel program 
-initiated in \todo{was it actually initiated here? check vzb.} \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
-\begin{align*}
-	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0}H^0 \left( \overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} + \alpha\delta \rfloor  \right) 
-\end{align*}
-in terms of certain moduli spaces. $\bq$-divisors on surfaces also naturally
+initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
+\begin{align*}
+	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0}H^0 \left(
+	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
+	\alpha\delta \rfloor  \right) 
+\end{align*}
+in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
 appear when considering the canonical ring of surfaces of Kodaira dimension 1.
@@
 
-Furthermore, this work extends the study of canonical rings of
+\todo{Aaron: This pararaph was already stated above. Can we remove it?}
+This work extends the study of canonical rings of
 $\bq$-divisors on curves, as done by O'Dorney \cite{dorney:canonical},
@@
 
-\todo{more!}
+\todo{more! Aaron: I think this is plenty of introduction}
 
@@
 \todo{put main results! use restate, maybe?}
-
+\todo{Aaron: Some of these theorem statements have been copied from older versions of the statements
+and not updated to reflect the difference. I agree we should use Theorem-restate, but we should make
+sure to copy the ones stated below, and not copy these ones}
 \begin{thm}
@@
 
-\todo{Include summary of what each of the sections do.}
+\todo{Include summary of what each of the sections do.}0
 

### 2015-07-23 surfaces-write-up/surface-write-up.tex
added todo to move lemmas section
surfaces: delete random hanging 0
surfaces: some intro motivation rework

@@
 
-In part, this work is motivated by
-of O'Dorney \cite{dorney:canonical}, who gives similar descriptions
-of canonical rings for general $\bq$-divisors on $\bp^1$. For
-particular $\bq$ divisors on stacky curves, the work by
-Voight--Zureick-Brown \cite{vzb:stacky} and Landesman--Ruhm--Zhang
-\cite{lrz:spin-cring} on log spin canonical rings provides
-useful bounds on rings of modular forms of Fuchsian groups.
+In part, this work is motivated by a recent paper by
+O'Dorney \cite{dorney:canonical} who gives similar descriptions
+of canonical rings for general $\bq$-divisors on $\bp^1$. This
+study also has connections to the papers by Voight--Zureick-Brown 
+\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring} on log 
+spin canonical rings of particular $\bq$ divisors on stacky curves which 
+provide bounds on rings of modular forms of Fuchsian groups.
 
@@
 
-\todo{Include summary of what each of the sections do.}0
-
+\todo{Include summary of what each of the sections do.}
+\todo{Incorperate the following section into the pm section}
 \section{Lemmas for Generation and Relations}

### 2015-07-23 surfaces-write-up/surface-write-up.tex
Changes to hirzebruch section

--- 2015-07-22 surfaces-write-up/surface-write-up.tex
@@
 $R_D$ is generated in degree at most
-\[
-	\sigma = \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
+\begin{equation}\label{eqn:def-sigma}
+	\rho = \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
 	{i \in \Tp(D) \\ j\in \Tm(D)}} (\bida_i \bidb_j - \bida_j \bidb_i)
 	\ell	_{i,j}.
-\]
+\end{equation}
 \end{lem}
@@
 for some $c_i \ge - \alpha_i d$ such that $\sum_{i=1}^n c_i \bida_i = 0$
-and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $\sigma$ inside the
+and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $g$ inside the
 lattice 
@@
 \begin{equation}\label{eqn:epsilon_i}
-	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha_k \ell_i \gcd(\bida_i, \bidb_i)})
+	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k \ell_i \gcd(\bida_i, \bidb_i)}\right)
 	(f_i^{\ell_i \frac{\gcd(\bida_i, \bidb_i)}{\bida_i + \bidb_i}\sum_{k \ne i}
@@
 	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
-	j - \bida_j \bidb_i)} {f_i}^{s_1} {f_j}^{s_2}\right) \in H^0(\ell_{i, j}
-	(\bida_i \bidb_j - \bida_j \bidb_i) D
+	j - \bida_j \bidb_i)} \right){f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i, j}
+	(\bida_i \bidb_j - \bida_j \bidb_i) D)
 \end{equation}
@@
 \todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here.}
-
-The set of $e_i$'s and $e_{i,j}$'s corresponding to the $\epsilon_i$'s and $\epsilon_{i,j}$'s given above satisfies the conditions of
-Proposition ~\ref{prop:cone-generation}, implying that $R_D$ is generated in 
-degrees less than the sum of the degrees of the $e_i$ and $e_{i,j}$, which is
-\[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{\substack{
+A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays given by the $e_i$'s and $e_{i,j}$'s.
+
+Thus Proposition ~\ref{prop:cone-generation} implies that $R_D$ is generated in 
+degrees less than the sum of the degrees of the $\epsilon_i$'s and $\epsilon_{i,j}$'s, which is
+\[
+	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{\substack{
 	i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
@@
 have been defined prior to the theorem statement as well, which would simplify
-the statement. We should also then clarify that $\sigma$ depends on $D$.}
+the statement. We should also then clarify that $\sigma$ depends on $D$.  \\
+Peter: $\sigma$ replaced by $\rho$. It's also defined now in the lemma statement rather than its proof.  
+}
 
@@
 
-Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\sigma$
+Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\rho$
 (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the
@@
 By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
-$2 \sigma$.
+$2 \rho$.
 Finally, we calculate the degree of generation of $\psi$:
@@
 \[
-	\tau = \sigma
-	+ \max \left( \max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
+	\tau : = \rho
+	+ \max \left(\max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
 	i \in	\Tp \\ j\in \Tm}} (\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
@@
 \begin{proof}
-We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ \todo{Aaron:
-Say where these polynomials live in}
+We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
  such that $\psi$ has relations of the form
@@
 \noindent
-for any degree $d \in \mathbb{N}$ \todo{Aaron: This confuses me because $d$ is
-not used above, is $d$ supposed to be $i$? Peter: Fixed?}
+whenever there is some degree $d \in \mathbb{N}$
 and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
@@
 
-To find such a $\beta$, \todo{Aaron: why is there no $i$ subscript? I changed
-this in the $\bp^m$ case, probably copy past, mutatis mutandis}
+To find such a $\beta_i$,
 we simply write $f_i$ as a 
@@
 For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
-component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in
-degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$
-component $\kappa_{j,i}''$.
-Then a careful computation implies that 
+component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \br$ and let $e_{j,k}$ (when it exists) lie in
+degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
+component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \br$
+Then a careful computation deduces that 
 %if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
-\[
+\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
 	\sigma = \lambda + E
-\]
+\end{equation}
 where $\lambda \in \Sigma$ and
@@
 \]
-Let $M$ be the set of monomials terms of $\beta_j$.  Then for $\mu\in M$, we
-can further compute that the lattice point corresponding to $\mu \prod_{j=1}^n
+Let $M$ be the set of monomials terms of $\beta_i$.  Then for $\mu\in M$, we
+can further compute that the lattice point, $\sigma_\mu$, corresponding to $\mu \prod_{j=1}^n
 {f_i}^{c_i}$ is of the form
 \[
-	\sigma + E_\mu
-\]
-where $E_\mu$ is defined similarly to $E$ (in particular, they lie in the same degree).
+	\sigma_\mu = \lambda + E_\mu
+\]
+where $\lambda \in \Sigma$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} (in particular, they lie in the same degree).
 
@@
 \[
-	\sigma + \deg(F)
+	\rho + \deg(F)
 \]
@@
 \[
-	\tau = \sigma
+	\tau = \rho
 	+ \max \left(\max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
@@
 \[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
+	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
 	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
@@
 \[
-	\max(2 \sigma, \sigma + \tau)
+	\max(2 \rho, \tau)
 \]
@@
 \end{thm}
-\todo{Aaron: Shouldn't $\tau$ not include $\sigma$?}
+\todo{Aaron: Shouldn't $\tau$ not include $\sigma$?  Peter: Fixed}
 

### 2015-07-24 surfaces-write-up/surface-write-up.tex
changes to section 4

@@
 \begin{thm}
-\label{proj-generators-relations-intro}
+\label{thm:proj-generators-relations-intro}
 Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let
@@
 \begin{thm}
-\label{lem:hirz-generators-relations}
+\label{thm:hirz-generators-relations}
 Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
@@
 
+\begin{defn}\label{def:ell_i}
+Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$. \todo{Peter: better notation for fraction?}  Then notate
+\[\ell_i = \lcm_{j\ne i}(k_i).\]
+\end{defn}
+
 \begin{lem} \label{lem:proj-generators}
@@
 
-\todo{Aaron: Give some definitions to make clear what the structure of divisors are}
-\todo{Aaron: clarify that $R_D$ is assumed to have both positive bidegrees}
-\todo{Aaron: Have $\ell_{i,j}$ been defined?}
-Let $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$ such
-that $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)
-, (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
+We can talk about sections of $\hirz_m$ in terms of polynomials in $u,v, w,x$; furthermore we can talk about bi-degrees of a monomial $u^a v^{b} w^c x^d$ given by $(a + b + mc, c + d)$.
+Sections on open subsets of $\hirz_m$ look like polynomials with each monomial having the same bidegrees, and rational sections have both bidegrees 0.
+\todo{Peter @ Aaron: can you add your exact sequence argument for why this is true?}
+
+Why can write $\bq$-divisors of $\hirz_m$ as $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$, where each $D_i = V(f_i)$ for some polynomial $f_i$, with each monomial having the same bidegrees.
+Since sections on $H^0(dD)$ must be rational sections, they must have both bidegrees non-negative, meaning that both bidegrees of $D$ must be non-negative for $R_D$ to be non-trivial.
+
+For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)$
+, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
 $f_i \in \sco(\bida_i, \bidb_i)$.  
@@
 surfaces before this paragraph; especially, describe what it's sections look
-like.}
+like. \\
+Peter: Fixed?
+}
 
@@
 \end{equation}
+\end{defn}
+
+\begin{defn}\label{def:ell_ij}
+Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$. \todo{Peter: better notation for fraction?}  Then notate
+\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\]
 \end{defn}
@@
 
-By Proposition ~\ref{prop:cone-generation}, in order to determining a spanning
+In order to determine a generating
 set for $(R_D)_d,$ it suffices to find the extremal rays of $\Sigma.$
@@
 d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0
-\}.	
+\},
 \end{align*}
-Then, $\Sigma_1$
+which
 has extremal rays given by
@@
 
-Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_n$.
-We can intersect $\Delta^{n-1}$ with the hyperplane $H$ given by
-$\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S \subseteq \Delta
-^{n-1}$.  Since $\Sigma \subseteq S$, if each extremal rays of $S$ contains an element of the lattice $\Sigma$, then those representatives in $\Sigma$ are in fact the extremal rays of $\Sigma$.
-
-The extremal rays of $S$ must lie on the edges of $\Delta
-^{n - 1}$, \todo{Peter: Do we need to cite/argue this, or is it clear?}
+Let $S$ be the $\mathbb{R}_{\ge 0}$ span of $e_1, \ldots e_n$.
+We can intersect $S$ with the hyperplane $H$ given by
+$\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S' \subseteq S$.
+Then, as long as each extremal rays of $S'$ contains an element of the lattice $\Sigma$, those representatives must in fact the extremal rays of $\Sigma'$.
+
+The extremal rays of $S'$ can be represented by points lying only on the edges of 
+$\overline{e_i e_j}$
 and are given by the $e_i$'s
@@
 \todo{more detail above;  Peter: resolved?}
-The following are elements of $R_D$ whose corresponding lattice point lies on each of the above extremal rays:
-
-For $i \in \Te(D)$, define \todo{below section needs to be simplified, maybe
-by introducing new variables}
+The following are elements of $R_D$ correspond to lattice point on each of the extremal rays listed above:
+
+For $i \in \Te(D)$, define $\epsilon_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
+\todo{below section needs to be simplified, maybe
+by introducing new variables; 
+Peter: I replaced some terms with degrees $d_i$ and $d_{i,j}$}
 \begin{equation}\label{eqn:epsilon_i}
-	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k \ell_i \gcd(\bida_i, \bidb_i)}\right)
-	(f_i^{\ell_i \frac{\gcd(\bida_i, \bidb_i)}{\bida_i + \bidb_i}\sum_{k \ne i}
-	\alpha_k (\bida_k + \bidb_k)}) \in H^0(\ell_i \gcd(\bida_i, \bidb_i) D).
+	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k d_i}\right)
+	f_i^{ \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
+	\alpha_k (\bida_k + \bidb_k)}.
 \end{equation}
@@
 \noindent
-For $i \in \Tp(D)$ and $j \in \Tm(D)$, define
+For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $\epsilon_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
 \begin{equation}\label{eqn:epsilon_i,j}
-	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
-	j - \bida_j \bidb_i)} \right){f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i, j}
-	(\bida_i \bidb_j - \bida_j \bidb_i) D)
+	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k d_{i,j}} \right){f_i}^{s_1} {f_j}^{s_2}
 \end{equation}
@@
 	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
-	\alpha_k \bidb_k = b_j (\alpha_i a_i + \alpha_j a_j) - a_j (\alpha_i b_i + \alpha_j b_j)
+	\alpha_k \bidb_k
 \]
@@
 	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
-	\alpha_k \bidb_k = -b_i (\alpha_i a_i + \alpha_j a_j) + a_i (\alpha_i b_i + \alpha_j b_j).
-\]
-\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here.}
-A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays given by the $e_i$'s and $e_{i,j}$'s.
-
-Thus Proposition ~\ref{prop:cone-generation} implies that $R_D$ is generated in 
+	\alpha_k \bidb_k.
+\]
+\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here. \\
+Peter: I have a slight leaning towards this notation, because the algebraic object is use more later (I think, although I'll check to make sure); also, I think writing out the ordered tuple would actually be harder, because there is no product notation, and it can be hard to denote the cordinates.}
+A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays represented by the $e_i$'s and $e_{i,j}$'s, respectively.
+\begin{rem}
+For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a (possibly) different representative of it's extremal ray say that their lattice points correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
+\end{rem}\todo{Peter: I don't like having a remark inside of a proof.
+Also, it feels like this could reasonably be replaced with a better constructed/organized proof, so that $e_i$'s are just defined this way initially; let me know if you see a good way to do so...
+As for Aaron's comment above, we could do something like that, except we already defined $e_i$'s to be something different, which might be equally/more confusing.}
+
+Thus,
+Proposition ~\ref{prop:cone-generation} implies that 
+$R_D$ is generated in 
 degrees less than the sum of the degrees of the $\epsilon_i$'s and $\epsilon_{i,j}$'s, which is
@@
 \begin{lem}
-$\ker(\psi)$ is generated in less than
+$\ker(\psi)$ is generated in degrees less than
 \[
@@
 \begin{proof}
-We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
- such that $\psi$ has relations of the form
+We first claim that there exist $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
+ such that $\ker(\psi)$ has relations of the form
 \begin{equation}
@@
 whenever there is some degree $d \in \mathbb{N}$
-and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
+and $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
 ^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
@@
 1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
-\rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}
+\rfloor$ whenever $i > 4$.
 
@@
 %by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
-Let $\Sigma'\subseteq \Sigma$ be the \todo{change all $S$ to sigma's}
+Let $\Omega\subseteq \Sigma$ be the 
 set
 \begin{align*}
-	\Sigma' = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
+	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
 	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
@@
 
-Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n
-{y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in
+Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
+{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
 \Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
@@
 \noindent
-which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$.
+which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$ (recall that $\rho$, defined in Equation \ref{eqn:def-sigma}, is an upper bound for generation degree).
 We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
@@
 \end{thm}
+\begin{proof}
+The generation degree bound is as stated in Lemma \ref{lem:hirz-generators}.
+By Proposition \ref{lem:composite-map}, the degree of generation of $\ker(\phi)$ is at most the maximum of the generation degrees of $\ker(\chi)$ and $\ker(\psi)$, giving us the desired relations bound.
+\end{proof}
+
 \todo{Aaron: Shouldn't $\tau$ not include $\sigma$?  Peter: Fixed}
 
-\todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.}
+\todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.\\
+Peter: Better?}
 
@@
 $X$ times an additional copy of $\bz$.  Perhaps analyzing the argument from
-Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma
-and not the theorem with the same name} in the case of $\hirz_k$ from the
+Lemma ~\ref{thm:hirz-generators-relations} in the case of $\hirz_1$ from the
 perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by
@@
 all rational surfaces, via the minimal model program for surfaces
-\todo{Reference}.  One might to provide an analogous result to Lemma
-~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not
-the theorem with the same name} in the case of all minimal surfaces:
+\todo{Reference}.  One might then hope to further extend these results to all minimal surfaces:
 \begin{question}

### 2015-07-25 surfaces-write-up/surface-write-up.tex
surfaces: fixed multiply-defined label in intro

@@
 
-\todo{Aaron: This pararaph was already stated above. Can we remove it?}
+\todo{Aaron: This paragraph was already stated above. Can we remove it?}
 This work extends the study of canonical rings of
@@
 \begin{thm}
-\label{thm:hirz-generators-relations}
+\label{thm:hirz-generators-relations-intro}
 Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
@@
 \todo{Include summary of what each of the sections do.}
-\todo{Incorperate the following section into the pm section}
+\todo{Incorporate the following section into the pm section}
 \section{Lemmas for Generation and Relations}

### 2015-07-25 surfaces-write-up/surface-write-up.tex
surfaces: minor intro rewording, implement restate

--- 2015-07-24 surfaces-write-up/surface-write-up.tex
@@
 \usepackage{caption}
+\usepackage{thmtools}
+\usepackage{thm-restate}
 
@@
 In part, this work is motivated by a recent paper by
-O'Dorney \cite{dorney:canonical} who gives similar descriptions
+O'Dorney \cite{dorney:canonical}, which gives similar descriptions
 of canonical rings for general $\bq$-divisors on $\bp^1$. This
 study also has connections to the papers by Voight--Zureick-Brown 
-\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring} on log 
-spin canonical rings of particular $\bq$ divisors on stacky curves which 
-provide bounds on rings of modular forms of Fuchsian groups.
+\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring}
+on log spin canonical rings on stacky curves which provide bounds
+on rings of modular forms of Fuchsian groups through the study
+of particular $\bq$-divisors on curves.
 
@@
 
-\todo{Aaron: This pararaph was already stated above. Can we remove it?}
-This work extends the study of canonical rings of
-$\bq$-divisors on curves, as done by O'Dorney \cite{dorney:canonical},
-Voight--Zureick-Brown \cite{vzb:stacky}, and Landesman--Ruhm--Zhang
-\cite{lrz:spin-cring}, to general projective space and Hirzebruch
-surfaces.
-
-\todo{more! Aaron: I think this is plenty of introduction}
-
 \ssec{Main Results}
-
-\todo{put main results! use restate, maybe?}
 \todo{Aaron: Some of these theorem statements have been copied from older versions of the statements
 and not updated to reflect the difference. I agree we should use Theorem-restate, but we should make
-sure to copy the ones stated below, and not copy these ones}
+sure to copy the ones stated below, and not copy these ones. Robin: thm-restate only allows you to restate earlier theorems and not later ones, so the main thms must appear numbered as 1.-}
 \begin{thm}
@@
 
-\begin{thm}
-\label{thm:proj-generators-relations-intro}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let
-$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$
-for all $i$; suppose $\deg(f_i) = a_i$. 
+\begin{restatable}{thm}{restateproj}
+\label{thm:proj-generators-relations}
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let
+$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
+$D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
 Then $R_D$ is generated in degree at most 
@@
 \]
+
+\noindent
 with relations generated in degree at most
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
-\]
-\end{thm}
+	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
+	(	\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+\]
+\end{restatable}
 
@@
 
-\begin{thm}
+\begin{restatable}{thm}{hirzrestate}
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
-Let $C_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further 
-suppose $f_1$ and $f_2$ are independent linear
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i =
+V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
+independent linear
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
 linear polynomials in $y_0$ and $y_1$.
-Then $R_D$ is generated in degree less than 
-\[
-	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
-	\sum_{\substack{i	\in \Tp(D) \\	j \in \Tm(D)}} (\bida_i
-	\bidb_j - \bida_j \bidb_i)\ell_{i,j}
-\]
-
-\noindent
-with relations generated in degree less than 
-\[
-	\max(2 \sigma, \sigma + \tau)
+Then $R_D$ is generated in degrees at most
+\[
+	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
+	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
+	- \bida_j \bidb_i) \ell_{i, j}
+\]
+
+\noindent
+with relations generated in degrees at most 
+\[
+	\max(2 \rho, \tau)
 \]
@@
 	\tau = \sigma
-	+ \max \left( \max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{
-	\substack{i \in	\Tp \\ j\in \Tm}}(\ell_{i,j} (\bida_i \bidb_j
-	- \bida_j \bidb_i))	\right).
-\]
-\end{thm}
+	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
+	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
+	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
+\]
+\end{restatable}
 
 \todo{Include summary of what each of the sections do.}
-\todo{Incorperate the following section into the pm section}
+\todo{Incorporate the following section into the $\bp^{m}$ section}
+
 \section{Lemmas for Generation and Relations}
@@
 
-Combining the above results, we obtain the following bound on the
-degrees of generators and relations of $R_D$.
-
-\begin{thm}
-\label{thm:proj-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let
-$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
-$D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
-Then $R_D$ is generated in degree at most 
-\[
-	\sum_{i=1}^n \ell_i a_i
-\]
-
-\noindent
-with relations generated in degree at most
-\[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(	\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
-\]
-\end{thm}
+By combining these results, we get our main theorem bounding
+the generator and relation degrees of the canonical ring of
+$\bq$-divisors on projective space.
+
+\restateproj*
 
@@
 \end{proof}
+
+\todo{say something about ghost points?}
 
@@
 
-Combining these results, we get the following theorem:
-
-\begin{thm}
-\label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i =
-V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
-independent linear
-polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$.
-Then $R_D$ is generated in degrees at most
-\[
-	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
-	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
-	- \bida_j \bidb_i) \ell_{i, j}
-\]
-
-\noindent
-with relations generated in degrees at most 
-\[
-	\max(2 \rho, \tau)
-\]
-
-\noindent
-where
-\[
-	\tau = \sigma
-	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
-	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
-	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
-\]
-\end{thm}
+By combining these results, we get our main theorem bounding
+the generator and relation degrees of the canonical ring of
+$\bq$-divisors on Hirzebruch surfaces.
+
+\hirzrestate*
+
 \begin{proof}
@@
 
-\todo{Aaron: Shouldn't $\tau$ not include $\sigma$?  Peter: Fixed}
-
+\todo{add something about ghost points?}
 \todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.\\

### 2015-07-26 surfaces-write-up/surface-write-up.tex
responded mostly to todos in hirzebruch section, replaced reals by rationls

@@
 \label{defn:lower-approximation}
-If $\alpha \in \br$, then a rational number $\frac{c}{k} \leq \alpha$
+If $\alpha \in \bq$, then a rational number $\frac{c}{k} \leq \alpha$
 (written in reduced form with $c \in \bz, k \in \bn$) is a
@@
 \ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
-i.e.~ $\Sigma$ is contained in the $R_{\geq 0}$ span of
+i.e.~ $\Sigma$ is contained in the $\bq_{\geq 0}$ span of
 $e_1, \ldots, e_t$.
@@
 By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
-{i = 1}^{t} r_i e_i$ with $r_i \in \br$. Let $\fr(r) := r - \lfloor r
+{i = 1}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) := r - \lfloor r
 \rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 1}
@@
 Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
-$\vec{v} = (v_0, \ldots, v_m) \in \br^{m + 1}$. Then write
+$\vec{v} = (v_0, \ldots, v_m) \in \bq^{m + 1}$. Then write
 \[
@@
 \label{defn:vec-sum}
-For $\vec{v} \in \br^n$, denote $\deg \vec{v} := \sum_{i = 0}
+For $\vec{v} \in \bq^n$, denote $\deg \vec{v} := \sum_{i = 0}
 ^n v_i$.
@@
 \label{defn:vec-order}
-Let $\vec{v}, \vec{w} \in \br^n$. Let $i \in \{1,\ldots, n\}$
+Let $\vec{v}, \vec{w} \in \bq^n$. Let $i \in \{1,\ldots, n\}$
 be the biggest index such that $v_i$ is nonzero
@@
 \begin{defn}\label{def:ell_i}
-Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$. \todo{Peter: better notation for fraction?}  Then notate
+Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
+\todo{Peter: better notation for fraction?
+Aaron: This seems fine to me.
+Are you saying you want a better notation, or asking if this is a better notation?}  Then notate
 \[\ell_i = \lcm_{j\ne i}(k_i).\]
@@
 $R_D$ is generated in degrees up to $\sum_{i=1}^n \ell_i a_i.$
-% and relations in degree at most  .\todo{insert numbers}
+
 \end{lem}
@@
 \end{align}
-\todo{Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.}
+\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.}
 We note that $\Sigma$ has extremal rays given by the lattice points 
@@
 \label{lem:proj-relations-psi}
-$\ker(\psi)$ is generated in degrees up to
+$\ker \psi$ is generated in degrees up to
 \begin{align}
@@
 \noindent
-Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\br_{\geq 0}}
+Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\bq_{\geq 0}}
 (e_1, \ldots, e_n)$ with $e_i$ as defined in Equation
@@
 $\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and
-$h \in \Sigma_i$. Therefore, $\ker(\psi)$ is generated in degrees
+$h \in \Sigma_i$. Therefore, $\ker \psi$ is generated in degrees
 less than
@@
 up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
-~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in
+~\ref{lem:proj-relations-psi}, $\ker \psi,$ is generated in
 degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i$. 
-Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$
+Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker \phi$
 is generated in degrees less than
@@
 
-We can talk about sections of $\hirz_m$ in terms of polynomials in $u,v, w,x$; furthermore we can talk about bi-degrees of a monomial $u^a v^{b} w^c x^d$ given by $(a + b + mc, c + d)$.
-Sections on open subsets of $\hirz_m$ look like polynomials with each monomial having the same bidegrees, and rational sections have both bidegrees 0.
-\todo{Peter @ Aaron: can you add your exact sequence argument for why this is true?}
-
-Why can write $\bq$-divisors of $\hirz_m$ as $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$, where each $D_i = V(f_i)$ for some polynomial $f_i$, with each monomial having the same bidegrees.
-Since sections on $H^0(dD)$ must be rational sections, they must have both bidegrees non-negative, meaning that both bidegrees of $D$ must be non-negative for $R_D$ to be non-trivial.
-
-For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)$
+Sections of a line bundle $\mathscr L$ on $\hirz_m$ can be written as
+polynomials in $u,v, w,x$.
+Furthermore we define the bi-degree of a monomial $u^a v^{b} w^c x^d$
+on $\hirz_n$ to be
+$(a + b + mc, c + d)$.  Rational section of $\hirz_m$ can be written as
+rational functions where each monomial has bi-degree 0. To see this, 
+observe
+$\Pic(\hirz_m) \cong \bz \times \bz$, where the class of a line bundle
+in $\Pic(\hirz_m)$
+is determined by its bi-degree, as follows from the excision exact sequence
+for class groups.
+
+For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
+distinct divisors with bi-degrees $(1,0)$
 , $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
@@
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch
-surfaces before this paragraph; especially, describe what it's sections look
-like. \\
-Peter: Fixed?
-}
-
+linear polynomials in $y_0$ and $y_1$.
 \begin{defn}
@@
 \begin{defn}\label{def:ell_ij}
-Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$. \todo{Peter: better notation for fraction?}  Then notate
+Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
+\todo{Peter: better notation for fraction? Aaron: I like this notation}  Then notate
 \[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\]
@@
 \begin{equation}\label{eqn:def-sigma}
-	\rho = \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
+	\rho := \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
 	{i \in \Tp(D) \\ j\in \Tm(D)}} (\bida_i \bidb_j - \bida_j \bidb_i)
@@
 Suppose $g
-\in (R_D)_d$.
+\in (R_D)_d$ is a monomial.
  Then 
 \[
-	g = \sum_{i = 1}^n {f_i}^{c_i}
+	g = \prod_{i = 1}^n {f_i}^{c_i}
 \]
@@
 for some $c_i \ge - \alpha_i d$ such that $\sum_{i=1}^n c_i \bida_i = 0$
-and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $g$ inside the
+and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $g$ as an element of the
 lattice 
@@
 
-Let $S$ be the $\mathbb{R}_{\ge 0}$ span of $e_1, \ldots e_n$.
-We can intersect $S$ with the hyperplane $H$ given by
-$\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S' \subseteq S$.
-Then, as long as each extremal rays of $S'$ contains an element of the lattice $\Sigma$, those representatives must in fact the extremal rays of $\Sigma'$.
-
-The extremal rays of $S'$ can be represented by points lying only on the edges of 
-$\overline{e_i e_j}$
-and are given by the $e_i$'s
-contained in $H$ and the intersection points $e_{i, j}$ of $H$
-together with the edges $\overline{e_i e_j}$ of the simplex between
-distinct $e_i, e_j$ not contained in $H$.
-\todo{more detail above;  Peter: resolved?}
-The following are elements of $R_D$ correspond to lattice point on each of the extremal rays listed above:
-
+Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $e_1, \ldots e_n$.
+We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
+V(\sum_{i=1}^n \bida_i X_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap \Sigma_1
+\otimes_\bz \bq$.  Then, the extremal rays of $\Sigma$ are precisely the extremal 
+rays of $\Sigma \otimes_\bz \bq$.
+
+The extremal rays of $\Sigma \otimes_\bz \bq$ can be represented by points
+lying only on the edges 
+$\overline{e_i e_j}$.
+The extremal rays are spanned by those $e_i$'s
+which are contained in $H$ together with intersection points $e_{i, j}$ which
+can be expressed as $H \cap \overline{e_i e_j},$ where $i \neq j$ and $e_i,
+e_j \notin H$. Note that $e_{i,j}$ is only defined in the case
+$\# \{H \cap \overline{e_i, e_j}\} = 1$.
+
+The following are elements of $R_D$ correspond to the extremal rays of
+$\Sigma$.
+\todo{Aaron: can we rephrase the above to say the images of the $\epsilon_i, \epsilon_{ij}$ lie on the extremal rays?}
 For $i \in \Te(D)$, define $\epsilon_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
@@
 \]
-\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here. \\
-Peter: I have a slight leaning towards this notation, because the algebraic object is use more later (I think, although I'll check to make sure); also, I think writing out the ordered tuple would actually be harder, because there is no product notation, and it can be hard to denote the cordinates.}
+\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We
+don't use the $\epsilon$ here, and we do use the $e$ here. \\
+Peter: I have a slight leaning towards this notation, because the algebraic
+object is use more later (I think, although I'll check to make sure); also, I
+think writing out the ordered tuple would actually be harder, because there is
+no product notation, and it can be hard to denote the cordinates.
+
+Aaron: I did
+a search for $\epsilon$ and the last time it is mentioned is inside this proof.
+In fact, while the $\epsilon$ are not referred to later, the $e_{ij}$ are referred to!
+The ordered tuple will look slightly longer, but it is less confusing then
+switching from tuple notation to
+product notation for no reason, especially when it isn't used again.
+It's confusing for the reader who is thinking in terms of lattice points
+to suddently switch to thinking in a ring. At the very least, you should say 
+it is the preimage of the map from the lattice to the canonical ring, since the
+current use of corresponding isn't ever made clear, but
+this would probably then take a bunch more space too, and I would also find this significantly more confusing than just saying the lattice points.}
 A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays represented by the $e_i$'s and $e_{i,j}$'s, respectively.
@@
 For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a (possibly) different representative of it's extremal ray say that their lattice points correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
-\end{rem}\todo{Peter: I don't like having a remark inside of a proof.
-Also, it feels like this could reasonably be replaced with a better constructed/organized proof, so that $e_i$'s are just defined this way initially; let me know if you see a good way to do so...
-As for Aaron's comment above, we could do something like that, except we already defined $e_i$'s to be something different, which might be equally/more confusing.}
-
+\end{rem}
+
+\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels
+like this could reasonably be replaced with a better constructed/organized
+proof, so that $e_i$'s are just defined this way initially; let me know if you
+see a good way to do so...  As for Aaron's comment above, we could do something
+like that, except we already defined $e_i$'s to be something different, which
+might be equally/more confusing.
+Aaron: I also don't like this here, just because it isn't really a remark,
+its more of a notational convention, and it doesn't really belong in the proof.
+I also think it's confusing to switch notation in the middle of a proof.
+Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
+proof, and should really be $e_{ij}$, as I was explaining in my previous todo.
+Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
+appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.}
 Thus,
@@
 \]
-\todo{Aaron: Do you use $\sigma$ later? We are usually reserving $\sigma$ for a
-lattice point. Perhaps something like $\delta$ would be more appropriate if you
-want to refer to it later. Also, you should number if if you want to refer to
-it later. In general, it's bad style to define things in the proofs. This could
-have been defined prior to the theorem statement as well, which would simplify
-the statement. We should also then clarify that $\sigma$ depends on $D$.  \\
-Peter: $\sigma$ replaced by $\rho$. It's also defined now in the lemma statement rather than its proof.  
-}
-
 \end{proof}
@@
 \begin{lem}
-$\ker(\psi)$ is generated in degrees less than
+\label{lem:hirz-bound-ker-psi}
+$\ker \psi$ is generated in degrees less than
 \[
@@
 We first claim that there exist $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
- such that $\ker(\psi)$ has relations of the form
+ such that $\ker \psi$ has relations of the form
 \begin{equation}
@@
 For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
-component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \br$ and let $e_{j,k}$ (when it exists) lie in
+component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
 degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
-component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \br$
+component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
 Then a careful computation deduces that
+
+\todo{Aaron: What is $\sigma$ here? Is it $\rho$?}
 %if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
@@
 	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
-	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \br, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
-	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \br, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
+	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
+	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
 	\end{cases}.
@@
 Let $M$ be the set of monomials terms of $\beta_i$.  Then for $\mu\in M$, we
-can further compute that the lattice point, $\sigma_\mu$, corresponding to $\mu \prod_{j=1}^n
+\todo{Aaron: What is $M$?}
+\todo{Aaron: Again, why do we keep defining lattce points in
+	terms of elements in the canonical ring? Why not just
+write out what the lattice points are in coordinates?}
+can further compute that the lattice point, $\sigma_\mu$, corresponding to $\mu :=
+\prod_{j=1}^n
 {f_i}^{c_i}$ is of the form
@@
 where $\lambda \in \Sigma$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} (in particular, they lie in the same degree).
-
+\todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
+	the sum of an element and a set? Same question for $\sigma$ above.
+	Also, I do not know what $E_\mu$ is. You really have to define it,
+since there's no way to check the validity of this proof without it.}
 Let $F\in R_D$ corresponding to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
@@
 \noindent
-Therefore, $\ker(\psi)$ is generated in degree at most
+Therefore, $\ker \psi$ is generated in degree at most
 \[
@@
 The generation degree bound is as stated in Lemma \ref{lem:hirz-generators}.
-By Proposition \ref{lem:composite-map}, the degree of generation of $\ker(\phi)$ is at most the maximum of the generation degrees of $\ker(\chi)$ and $\ker(\psi)$, giving us the desired relations bound.
+By Proposition \ref{lem:composite-map}, the degree of generation of
+$\ker \phi$ is at most the maximum of the generation degrees of $\ker(\chi)$
+and $\ker \psi$, giving us the desired relations bound. The bound on $\ker(\chi)$
+follows from Lemma ~\ref{lem:bound-ker-chi} and the bound on $\ker \psi$
+follows from Lemma ~\ref{lem:hirz-bound-ker-psi}.
+$\ker \psi$ follows from 
 \end{proof}

### 2015-07-27 surfaces-write-up/surface-write-up.tex
surfaces: comment on todos in hirz, ker spacing

@@
 By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of
-$\ker(\chi)$ and we next calculate the degree of generation of $\ker \psi$:
+$\ker \chi $ and we next calculate the degree of generation of $\ker \psi$:
 
@@
 
-By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees 
+By ~\ref{lem:bound-ker-chi}, $\ker \chi$ is generated in degrees 
 up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
@@
 current use of corresponding isn't ever made clear, but
-this would probably then take a bunch more space too, and I would also find this significantly more confusing than just saying the lattice points.}
-A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays represented by the $e_i$'s and $e_{i,j}$'s, respectively.
+this would probably then take a bunch more space too, and I would also find this significantly more confusing than just saying the lattice points.
+
+Robin: Yeah, I thought that we had agreed upon doing the entire
+proof in terms of the lattice points and then occasionally giving
+the algebraic translation (and noting that it is simply the
+algebraic translation) rather than this ``in-between'' sort of
+thing. I agree with Aaron that it's confusing for a reader who has
+not gone through the details before.}
+
+A quick calculation deduces that these $\epsilon_i$'s and
+$\epsilon_{i,j}$'s lie on the extremal rays represented by the
+$e_i$'s and $e_{i,j}$'s, respectively.
 \begin{rem}
@@
 Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
-appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.}
-Thus,
-Proposition ~\ref{prop:cone-generation} implies that 
+appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.
+Robin: agree with Aaron here.}
+
+Thus, Proposition ~\ref{prop:cone-generation} implies that 
 $R_D$ is generated in 
@@
 
-By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker(\chi)$ below
+By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of $\ker \chi$ below
 $2 \rho$.
@@
 By Proposition \ref{lem:composite-map}, the degree of generation of
-$\ker \phi$ is at most the maximum of the generation degrees of $\ker(\chi)$
-and $\ker \psi$, giving us the desired relations bound. The bound on $\ker(\chi)$
+$\ker \phi$ is at most the maximum of the generation degrees of $\ker \chi$
+and $\ker \psi$, giving us the desired relations bound. The bound on $\ker \chi$
 follows from Lemma ~\ref{lem:bound-ker-chi} and the bound on $\ker \psi$

### 2015-07-27 surfaces-write-up/surface-write-up.tex
some edits to relations lemma for hirz

@@
 Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
-\todo{Peter: better notation for fraction? Aaron: I like this notation}  Then notate
+Then notate
 \[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\]
@@
 component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
-Then a careful computation deduces that
-
-\todo{Aaron: What is $\sigma$ here? Is it $\rho$?}
+Then a careful computation deduces that we can write
+
+\todo{Aaron: What is $\sigma$ here? Is it $\rho$? \\
+Peter: Should have been $\omega$...}
 %if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
 \begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
-	\sigma = \lambda + E
+	\omega = \lambda + E
 \end{equation}
-where $\lambda \in \Sigma$ and
+for some $\lambda \in \Sigma$ and $E$ of the form
 \begin{equation}\label{eqn:hirz-E-translation}
@@
 \noindent
-From this, we can deduce that
+From this, we can further deduce that for such an $E$,
 \[
@@
 \]
-Let $M$ be the set of monomials terms of $\beta_i$.  Then for $\mu\in M$, we
-\todo{Aaron: What is $M$?}
+Let $M$ be the set of monomials terms of $\beta_i$.  Then for $\mu = \prod_{j=1}^n
+{f_i}^{c_i}\in M$, we
+\todo{Aaron: What is $M$? \\
+Peter: I don't quite follow this question... Is your objection that ``the set of monomial terms of $\beta_i$'' is too imprecise?}
 \todo{Aaron: Again, why do we keep defining lattce points in
 	terms of elements in the canonical ring? Why not just
-write out what the lattice points are in coordinates?}
-can further compute that the lattice point, $\sigma_\mu$, corresponding to $\mu :=
-\prod_{j=1}^n
-{f_i}^{c_i}$ is of the form
-\[
-	\sigma_\mu = \lambda + E_\mu
-\]
-where $\lambda \in \Sigma$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} (in particular, they lie in the same degree).
+write out what the lattice points are in coordinates? \\ 
+Peter: Fixed?}
+can further compute that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$, corresponding to $\mu
+$ is of the form
+\[
+	\omega_\mu = \lambda + E_\mu
+\]
+where $\lambda \in \Sigma$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation}:
+\begin{equation}\label{eqn:hirz-E_mu-translation}
+E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j} e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in \Tp}} q_{j,i} e_{i,j}\right)
+\end{equation}
+for some $q_i$'s, $q_{i,j}$'s and $q_{j,i}$'s (for appropriate $i$'s and $j$'s) in $\bq_{\ge 0}$.  
 \todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
@@
 	Also, I do not know what $E_\mu$ is. You really have to define it,
-since there's no way to check the validity of this proof without it.}
+since there's no way to check the validity of this proof without it.  \\
+Peter: $E$ and $E_\mu$ are elements, not sets...}
+Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.
+
 Let $F\in R_D$ corresponding to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  

### 2015-07-28 surfaces-write-up/surface-write-up.tex
removing sentient computations...

@@
 component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
-Then a careful computation deduces that we can write
+By a careful computation, we can write
 

### 2015-07-28 surfaces-write-up/surface-write-up.tex
responses to peter's hirzebruch comments and more comments that are confusing me

@@
 Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
-\todo{Peter: better notation for fraction?
-Aaron: This seems fine to me.
-Are you saying you want a better notation, or asking if this is a better notation?}  Then notate
+Then notate
 \[\ell_i = \lcm_{j\ne i}(k_i).\]
@@
 component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
-By a careful computation, we can write
-
-\todo{Aaron: What is $\sigma$ here? Is it $\rho$? \\
-Peter: Should have been $\omega$...}
-%if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
+By a careful computation, we can find $\lambda \in \Sigma$ 
+\todo{Aaron: Is it at all possible to write down what $\lambda$ and the $r_{i,j}$ are?
+I suspect we should be able to write them in a couple lines, which would
+definitely clarify how we're getting the bound on degree $E$. While I agree
+it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
+to say what the $r_{i,j}$ and $\lambda$ are.}
+and $r_{i,j} \in \bq$ so that we can write
 \begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
-	\omega = \lambda + E
+-	\sigma = \lambda + E
  \end{equation}
-for some $\lambda \in \Sigma$ and $E$ of the form
+with $E$ of the form
 \begin{equation}\label{eqn:hirz-E-translation}
@@
 \todo{Aaron: What is $M$? \\
-Peter: I don't quite follow this question... Is your objection that ``the set of monomial terms of $\beta_i$'' is too imprecise?}
+Peter: I don't quite follow this question... Is your objection that ``the set of monomial terms of $\beta_i$'' is too imprecise?
+
+Aaron: Sorry, I was trying to say that
+I don't understand what ``the set of monomials in terms of beta i'' means.
+Do you just mean that $M = \{\psi(\beta_1), \ldots, \psi(\beta_n)\}$?
+
+However, I'm really baffled as to why you want to apply $\psi$ to the
+$\beta_i$, since two lines later, you then apply the reverse correspondence
+and want to work back in the semigroupring. Why don't you just stay in the
+semigroup ring the whole time?
+I think I'm misunderstanding this, but is $\omega_\mu$ just equal to
+$\beta_i$ for some $i$? Also, why is $\omega_\mu$ missing a $d$ index
+as its first index?
+}
 \todo{Aaron: Again, why do we keep defining lattce points in
@@
 write out what the lattice points are in coordinates? \\ 
-Peter: Fixed?}
-can further compute that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$, corresponding to $\mu
+Peter: Fixed?
+
+Aaron: I like that $E$ is defined in terms of $e_i$.
+I'm still confused about $\omega$ and $\mu$ though. see my above comment.
+}
+can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ and $\lambda \in
+\Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
+corresponding to $\mu
 $ is of the form
@@
 \]
-where $\lambda \in \Sigma$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation}:
+where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} by
 \begin{equation}\label{eqn:hirz-E_mu-translation}
-E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j} e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in \Tp}} q_{j,i} e_{i,j}\right)
+E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) +
+\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}
+e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
+\Tp}} q_{j,i} e_{i,j}\right).
 \end{equation}
-for some $q_i$'s, $q_{i,j}$'s and $q_{j,i}$'s (for appropriate $i$'s and $j$'s) in $\bq_{\ge 0}$.  
 \todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
@@
 since there's no way to check the validity of this proof without it.  \\
-Peter: $E$ and $E_\mu$ are elements, not sets...}
+Peter: $E$ and $E_\mu$ are elements, not sets...
+
+Aaron: My mistake. Thanks for writing it out though. However,
+since $E, E_\mu$ are so similar, why not defining them so that they look similar?
+I.e., why not define them either both in three cases as $E$
+or both as sums as $E_\mu$. It's confusing that they are the same, but not
+written in a parallel fashion.
+}
 Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.
@@
 \todo{add something about ghost points?}
-\todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.\\
-Peter: Better?}
 

### 2015-07-29 surfaces-write-up/surface-write-up.tex
added some intro references

@@
 
-The work in this paper may help calculate a presentation of certain rings of Hilbert 
+The work in this paper may help calculate a presentation of certain rings of
+Hilbert 
 modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
-modular forms are both generalizations of modular forms to higher dimensions.
+modular forms are both generalizations of modular forms to higher dimensions,
+as described in \cite{geer:siegel-moduar} and \cite{bruinier:hilbert-modular}.
 By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
@@
 Hilbert and Siegel modular forms with certain underlying spaces.
-\todo{include references}
 
@@
 appear when considering the canonical ring of surfaces of Kodaira dimension 1.
-A surface has Kodaira dimension 1 if and only if it is an elliptic surface, and
+A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
+barthHPV:compactComplexSurfaces}, and
 their canonical ring are most naturally described in the setting of
-$\bq$-divisors. \todo{Add references}
+$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
 

### 2015-07-30 surfaces-write-up/surface-write-up.tex
fixed some todos

@@
 
-\begin{rem}
+\begin{rem}\todo{Peter: maybe move this out of a remark and just say it with the previous example?  As it stands, the previous example is a little unclear as to what its purpose is...}
 \label{rem:ghost-motivation}
@@
 $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
-then $f_0, \ldots, f_n$.
+then $\bk[f_0, \ldots, f_m]$ has transcendence degree $m+1$ over $\bk$.
 
@@
 \end{align}
-\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.}
+\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.  \\
+Peter: I like having the statement of the lemma being nice and consise; also the statement has nothing to do with this geometric picture, so I find it more natural to have the geometric side contained in the proof.
+I also don't quite see why it is so bad to reference something from inside a previous proof; a reader can surely locate it...
+}
 We note that $\Sigma$ has extremal rays given by the lattice points 
@@
 
-\todo{say something about ghost points?}
+\todo{say something about ghost points? Peter: Haven't we already done that at the begining of the section?}
 
@@
 linear polynomials in $y_0$ and $y_1$.
+In order to achieve this condition on $D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e.
+divisors with of the desired form with a coefficient $\alpha_i = 0$).
 \begin{defn}
@@
 \[
-	e_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
+	\epsilon_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
 	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
@@
 
-Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $e_1, \ldots e_n$.
+Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $\epsilon_1, \ldots \epsilon_n$.
 We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
@@
 
-The following are elements of $R_D$ correspond to the extremal rays of
-$\Sigma$.
-\todo{Aaron: can we rephrase the above to say the images of the $\epsilon_i, \epsilon_{ij}$ lie on the extremal rays?}
-For $i \in \Te(D)$, define $\epsilon_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
-\todo{below section needs to be simplified, maybe
-by introducing new variables; 
-Peter: I replaced some terms with degrees $d_i$ and $d_{i,j}$}
+From this we can deduce the representatives of $\Sigma$ lying on its extremal rays given by the following:
+For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
 \begin{equation}\label{eqn:epsilon_i}
-	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k d_i}\right)
-	f_i^{ \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
-	\alpha_k (\bida_k + \bidb_k)}.
+	e_i := (-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
+	\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
 \end{equation}
@@
 \noindent
-For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $\epsilon_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
+For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
 \begin{equation}\label{eqn:epsilon_i,j}
-	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k d_{i,j}} \right){f_i}^{s_1} {f_j}^{s_2}
+	\begin{split}& e_{i,j} := (-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
+	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
+	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
+	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
+	\end{split}
 \end{equation}
-
-\noindent
-where
-\[
-	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
-	\alpha_k \bidb_k
-\]
-
-\noindent
-and
-\[
-	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
-	\alpha_k \bidb_k.
-\]
-\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We
-don't use the $\epsilon$ here, and we do use the $e$ here. \\
-Peter: I have a slight leaning towards this notation, because the algebraic
-object is use more later (I think, although I'll check to make sure); also, I
-think writing out the ordered tuple would actually be harder, because there is
-no product notation, and it can be hard to denote the cordinates.
-
-Aaron: I did
-a search for $\epsilon$ and the last time it is mentioned is inside this proof.
-In fact, while the $\epsilon$ are not referred to later, the $e_{ij}$ are referred to!
-The ordered tuple will look slightly longer, but it is less confusing then
-switching from tuple notation to
-product notation for no reason, especially when it isn't used again.
-It's confusing for the reader who is thinking in terms of lattice points
-to suddently switch to thinking in a ring. At the very least, you should say 
-it is the preimage of the map from the lattice to the canonical ring, since the
-current use of corresponding isn't ever made clear, but
-this would probably then take a bunch more space too, and I would also find this significantly more confusing than just saying the lattice points.
-
-Robin: Yeah, I thought that we had agreed upon doing the entire
-proof in terms of the lattice points and then occasionally giving
-the algebraic translation (and noting that it is simply the
-algebraic translation) rather than this ``in-between'' sort of
-thing. I agree with Aaron that it's confusing for a reader who has
-not gone through the details before.}
-
-A quick calculation deduces that these $\epsilon_i$'s and
-$\epsilon_{i,j}$'s lie on the extremal rays represented by the
-$e_i$'s and $e_{i,j}$'s, respectively.
-\begin{rem}
-For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a (possibly) different representative of it's extremal ray say that their lattice points correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
-\end{rem}
-
-\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels
-like this could reasonably be replaced with a better constructed/organized
-proof, so that $e_i$'s are just defined this way initially; let me know if you
-see a good way to do so...  As for Aaron's comment above, we could do something
-like that, except we already defined $e_i$'s to be something different, which
-might be equally/more confusing.
-Aaron: I also don't like this here, just because it isn't really a remark,
-its more of a notational convention, and it doesn't really belong in the proof.
-I also think it's confusing to switch notation in the middle of a proof.
-Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
-proof, and should really be $e_{ij}$, as I was explaining in my previous todo.
-Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
-appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.
-Robin: agree with Aaron here.}
+Note that the above expression is for when $i < j$, but a small rearangement gives when $j < i$.
+\todo{Peter: I changed the above expression, but I'm still feel a little dubious that this is easier to read...}
+
+%\noindent
+%where
+%\[
+%	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
+%	\alpha_k \bidb_k
+%\]
+%
+%\noindent
+%and
+%\[
+%	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
+%	\alpha_k \bidb_k.
+%\]
+
+A quick calculation deduces that these $e_i$'s and
+$e_i{i,j}$'s lie on the extremal rays of $\Sigma$.
+%\begin{rem}
+%For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a %(possibly) different representative of it's extremal ray say that their lattice points %correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
+%\end{rem}
+
+%\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels
+%like this could reasonably be replaced with a better constructed/organized
+%proof, so that $e_i$'s are just defined this way initially; let me know if you
+%see a good way to do so...  As for Aaron's comment above, we could do something
+%like that, except we already defined $e_i$'s to be something different, which
+%might be equally/more confusing.
+%Aaron: I also don't like this here, just because it isn't really a remark,
+%its more of a notational convention, and it doesn't really belong in the proof.
+%I also think it's confusing to switch notation in the middle of a proof.
+%Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
+%proof, and should really be $e_{ij}$, as I was explaining in my previous todo.
+%Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
+%appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.
+%Robin: agree with Aaron here.}
 
@@
 it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
-to say what the $r_{i,j}$ and $\lambda$ are.}
-and $r_{i,j} \in \bq$ so that we can write
+to say what the $r_{i,j}$ and $\lambda$ are.
+\\
+Peter: There is not a unique choice of the $r_{i,j}$'s.
+When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.}
+and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
 \begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
--	\sigma = \lambda + E
+	\sigma = \lambda + E
  \end{equation}
@@
 as its first index?
-}
-\todo{Aaron: Again, why do we keep defining lattce points in
-	terms of elements in the canonical ring? Why not just
-write out what the lattice points are in coordinates? \\ 
-Peter: Fixed?
-
-Aaron: I like that $E$ is defined in terms of $e_i$.
-I'm still confused about $\omega$ and $\mu$ though. see my above comment.
+\\
+Peter: $\beta_i$'s are polynomials in $f_1, \ldots f_4$.  By the monomial terms in $\beta_i$ I mean look at each monomial appearing in this polynomial and take the set of those.
 }
@@
 written in a parallel fashion.
+\\
+Peter: Well...
+We had a conversation a while ago that saying something like $j \in \{i\} \cap T_=$ might look a little funny (saying $j$ ranging over the set of i intersect $T_=$ meaning $j$ either ranges over the emptyset or the singleton set of $i$).
+I We could make this change in the first one if it is preferable.
+On the other hand, transforming the second into the form of the first would be terribly ugly (like 12 cases, some of which are sumed together...
+or something like that...).
 }
@@
 \end{proof}
-
-\todo{add something about ghost points?}
 

### 2015-07-30 surfaces-write-up/surface-write-up.tex
made bibtex work

@@
 modular forms are both generalizations of modular forms to higher dimensions,
-as described in \cite{geer:siegel-moduar} and \cite{bruinier:hilbert-modular}.
+as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
 By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 

### 2015-07-30 surfaces-write-up/surface-write-up.tex
surfaces: reword 1pt to eff, add idea of pf to eff

@@
 \ssec{Main Results}
-\todo{Aaron: Some of these theorem statements have been copied from older versions of the statements
-and not updated to reflect the difference. I agree we should use Theorem-restate, but we should make
-sure to copy the ones stated below, and not copy these ones. Robin: thm-restate only allows you to restate earlier theorems and not later ones, so the main thms must appear numbered as 1.-}
 \begin{thm}
@@
 \label{thm:proj-one-point}
-Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D = \alpha H$, with $\alpha = \frac{p}{q} \in \bq$
-and $H := V(x_k)$ a hyperplane of $\bp^m$.
+Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D' \in \bq
+\otimes \div \bp^m$ and $D = D' + \alpha H$, with $\alpha =
+\frac{p}{q} \in \bq$ and $H := V(x_k)$ a hyperplane of $\bp^m$.
 Let
@@
 \noindent
-has a minimal presentation consisting of the $\sum_{i = 0}^{r}
+has a minimal presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
 {{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
@@
 with $\deg \vec v = c_i$. Furthermore, it has
-relations of the following two types:
+relations generated \todo{over $R_{D'}$?} by the following two types:
 \begin{enumerate}
@@
 \end{thm}
-\todo{Write idea of proof}
+
+\sssec*{Idea of Proof:}
+The proof follows in four steps. First, we demonstrate that
+the $F_{i}^{\vec{v}}$'s form a set of minimal generators of $R_D$
+over $R_{D'}$ by leveraging the fact that $F_{i}^{\vec{v}}$ has
+``maximal pole order'' at some coordinate among rational functions
+in degree $i$. Then, the relations $G_{i, j}^{\vec{v}, \vec{w}}$
+follow from the demonstration that the $F_{i}^{\vec{v}}$'s generate
+all of $R_D$ over $R_{D'}$. We derive the relations
+$L_{i, j}^{\vec{v}, \vec{w}}$ by considering when products of
+generators in neighboring degrees are equal. Finally, we demonstrate
+that $G_{i, j}^{\vec{v}, \vec{w}}$'s and $L_{i, j}^{\vec{v}, \vec{w}}$'s
+generate all of the relations by using them to reduce elements of
+$R_D$ to a canonical form.
+
 \begin{proof}
+For simplicity, we give a proof for when $D' = 0$.
 We will first check that $F^{\vec v}_i$ determine a system of minimal
@@
 
-\begin{rem}
-\label{rem:proj-one-point-ind}
-The method of proof for Theorem ~\ref{thm:proj-one-point}
-can be immediately generalized to work inductively. If $D = D' + \alpha H$
-for some hyperplane $H$, then the proof of Theorem ~\ref{thm:proj-one-point}, mutatis mutandis, extends to show
-the canonical ring $R_D$ is generated over $R_D'$ by the same
-generators and with the same relations given in Theorem
-~\ref{thm:proj-one-point}.
-\end{rem}
-\todo{Perhaps we should consider restating the above theorem in this form, and then say for simplicity we prove it when the base is 0?}
+%\begin{rem}
+%\label{rem:proj-one-point-ind}
+%The method of proof for Theorem ~\ref{thm:proj-one-point}
+%can be immediately generalized to work inductively. If $D = D' + \alpha H$
+%for some hyperplane $H$, then the proof of Theorem ~\ref{thm:proj-one-point}, mutatis mutandis, extends to show
+%the canonical ring $R_D$ is generated over $R_D'$ by the same
+%generators and with the same relations given in Theorem
+%~\ref{thm:proj-one-point}.
+%\end{rem}
+
 \begin{thm}
@@
 
-Then the canonical ring
-$R_D$
+Then the canonical ring $R_D$
 is generated in degrees up to $\max_{1 \leq i \leq n}{q_i}$ with
@@
 If $D' = \sum_{i = 0}^{n} \alpha_i D_i$ is some $\bq$-divisor
-on $\bp^m$, then we look at $D = D' + C$ where $C$ is a
-hypersurface of degree $\pdeg$. \todo{Aaron: rewrite this to make sense} Now use the Veronese mapping
-to view $C$ as a hypersurface on $\bp^{\binom{{m + \pdeg}}{ \pdeg} -1 }$
+on $\bp^m$, then we look at $R_D$ where $D = D' + C$ for some
+degree $\pdeg$ hypersurface $C$. Now use the Veronese mapping
+to view $C$ as a hypersurface on $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$
 and the image of $C$ as the intersection of a Veronese variety
-with a hyperplane. Then we can reduce inductively adding hypersurfaces
-to the case of adding hyperplanes. However, this is accomplished
+with a hyperplane. Then we can reduce the process of inductively
+adding hypersurfaces to when the hypersurfaces are hyperplanes. However, this is accomplished
 by the method used in Theorem ~\ref{thm:proj-one-point} in an

### 2015-07-30 surfaces-write-up/surface-write-up.tex
responses to peter's comments such as trying to standardize the use of the term extremal rays

@@
 $D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
-then $\bk[f_0, \ldots, f_m]$ has transcendence degree $m+1$ over $\bk$.
+then $f_0, \ldots, f_m$ cut out linearly independent
+hyperplanes in $\bp^m$.
 
@@
 \end{align}
-\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.  \\
-Peter: I like having the statement of the lemma being nice and consise; also the statement has nothing to do with this geometric picture, so I find it more natural to have the geometric side contained in the proof.
-I also don't quite see why it is so bad to reference something from inside a previous proof; a reader can surely locate it...
+\todo{Aaron: Possibly take this definition out of the proof, and move it into
+	the setup, since we want to reference it later.  \\
+Peter: I like having the statement of the lemma being nice and consise; also
+the statement has nothing to do with this geometric picture, so I find it more
+natural to have the geometric side contained in the proof.  I also don't quite
+see why it is so bad to reference something from inside a previous proof; a
+reader can surely locate it...
+
+Aaron: In general, I like the idea of having proofs self contained,
+so that one should only refer to the proof statement, not the
+body of the proof.
+I'm not very strongly tied to this idea though, and I think it's fine. I think it's fine.
 }
@@
 polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$.
-In order to achieve this condition on $D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e.
-divisors with of the desired form with a coefficient $\alpha_i = 0$).
+linear polynomials in $y_0$ and $y_1$.  In order to achieve this condition on
+$D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e.
+divisors with of the desired form with a coefficient $0$).
 \begin{defn}
@@
 $\overline{e_i e_j}$.
-The extremal rays are spanned by those $e_i$'s
+The extremal rays are given by multiples of those $\epsilon_i$'s
 which are contained in $H$ together with intersection points $e_{i, j}$ which
@@
 
-From this we can deduce the representatives of $\Sigma$ lying on its extremal rays given by the following:
+From this we can deduce that a set of extremal rays of $\Sigma$ are given as follows:
 For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
@@
 \noindent
-For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
+For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
 \begin{equation}\label{eqn:epsilon_i,j}
@@
 \end{equation}
-Note that the above expression is for when $i < j$, but a small rearangement gives when $j < i$.
-\todo{Peter: I changed the above expression, but I'm still feel a little dubious that this is easier to read...}
+Note that the above expression makes sense when $i < j$, but one
+can similarly define $e_{i,j}$ when $j < i$.  
+\todo{Peter: I changed the above expression,
+but I'm still feel a little dubious that this is easier to read...
+
+Aaron: I agree this is harder to read. Why don't we just write
+$e_{i,j} = a e_i + b e_j$ (where of course you replace a and b by explicit
+constants). Wouldn't that be much cleaner? Also, I think we should
+explicitly state what the small rearrangement is to switch 
+$i$ and $j$, but perhaps it won't be relevant if you write $e_{ij} $
+as a linear combination of $e_i, e_j$.}
 
@@
 
-A quick calculation deduces that these $e_i$'s and
-$e_i{i,j}$'s lie on the extremal rays of $\Sigma$.
+Since these $e_i$ are multiples of $\epsilon_i$ and these
+$e_{i,j}$ are points of intersection of $H$ with
+$\overline {e_ie_j}$ such that neither $e_i$ nor $e_j$
+are contained in $H$, these form a set of extremal rays of $\Sigma$.
 %\begin{rem}
@@
 To find such a $\beta_i$,
+\todo{Aaron: Shouldn't we say something above like, the kernel
+	is bounded by the maximum of something over all $i$,
+	so for the remainder of the proof, we fix an $i$.
+	Also, I think it would help if things
+	that depend on $i$, such as $E,\sigma,\lambda$
+have an $i$ subscript.}
 we simply write $f_i$ as a 
@@
 	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
-= 0 \}
+= 0 \}.
 \end{align*}
@@
 Peter: There is not a unique choice of the $r_{i,j}$'s.
-When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.}
+When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.
+
+Aaron: OK. In that case, why don't you say that? Since I didn't understand those constraints on $r_{i,j}$, I think
+the reader would probably also be lost without explicitly writing those constraints.
+Also, what about $\lambda$? Is that uniquely determined?}
 and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
@@
 }
-can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ and $\lambda \in
+can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ 
+\todo{Aaron: Would it be reasonable to given these $q_{ij}$ a $\mu$
+superscript or subscript to indicate dependence on $\mu$?}
+and $\lambda \in
 \Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
@@
 \]
-where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} by
+where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined by
+
 \begin{equation}\label{eqn:hirz-E_mu-translation}
@@
 \end{equation}
-\todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
-	the sum of an element and a set? Same question for $\sigma$ above.
-	Also, I do not know what $E_\mu$ is. You really have to define it,
-since there's no way to check the validity of this proof without it.  \\
-Peter: $E$ and $E_\mu$ are elements, not sets...
-
-Aaron: My mistake. Thanks for writing it out though. However,
-since $E, E_\mu$ are so similar, why not defining them so that they look similar?
-I.e., why not define them either both in three cases as $E$
-or both as sums as $E_\mu$. It's confusing that they are the same, but not
-written in a parallel fashion.
-\\
-Peter: Well...
-We had a conversation a while ago that saying something like $j \in \{i\} \cap T_=$ might look a little funny (saying $j$ ranging over the set of i intersect $T_=$ meaning $j$ either ranges over the emptyset or the singleton set of $i$).
-I We could make this change in the first one if it is preferable.
-On the other hand, transforming the second into the form of the first would be terribly ugly (like 12 cases, some of which are sumed together...
-or something like that...).
-}
+
 Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.
 
-Let $F\in R_D$ corresponding to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
+Let $F\in R_D$ correspond to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
 Then $F - \sum_{\mu \in M} F_\mu = 0$ induces a

### 2015-07-30 surfaces-write-up/surface-write-up.tex
made veronese proof clearer

@@
 \ssec{Main Results}
-\begin{thm}
+
+\begin{restatable}{thm}{restateeffective}
 \label{thm:proj-effective-intro}
-Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
-$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i C_i$, with $\alpha_i =
+Let $D = \sum_{i = 1}^{n} \alpha_i C_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
 \frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
@@
 relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$
-\end{thm}
+\end{restatable}
 
@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$. Let
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$. Let
 $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \hirz_k.$ Let $D_i =
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_k.$ Let $D_i =
 V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
@@
 Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D' \in \bq
-\otimes \div \bp^m$ and $D = D' + \alpha H$, with $\alpha =
+\otimes \di \bp^m$ and $D = D' + \alpha H$, with $\alpha =
 \frac{p}{q} \in \bq$ and $H := V(x_k)$ a hyperplane of $\bp^m$.
@@
 the $F_{i}^{\vec{v}}$'s form a set of minimal generators of $R_D$
-over $R_{D'}$ by leveraging the fact that $F_{i}^{\vec{v}}$ has
-``maximal pole order'' at some coordinate among rational functions
-in degree $i$. Then, the relations $G_{i, j}^{\vec{v}, \vec{w}}$
-follow from the demonstration that the $F_{i}^{\vec{v}}$'s generate
-all of $R_D$ over $R_{D'}$. We derive the relations
+over $R_{D'}$ using their construction in terms of best lower
+approximations to $\alpha$. Then, since the $F_{i}^{\vec{v}}$ generate
+all of $R_D$ over $R_{D'}$, we obtain the
+relations $G_{i, j}^{\vec{v}, \vec{w}}$.
+We derive the relations
 $L_{i, j}^{\vec{v}, \vec{w}}$ by considering when products of
@@
 that $G_{i, j}^{\vec{v}, \vec{w}}$'s and $L_{i, j}^{\vec{v}, \vec{w}}$'s
-generate all of the relations by using them to reduce elements of
+generate all of the relations by using them to reduce arbitrary
+elements of
 $R_D$ to a canonical form.
@@
 \begin{proof}
-For simplicity, we give a proof for when $D' = 0$.
+For simplicity, we give a proof for when $D' = 0$, but the general
+can be analogously proved by replacing the orders of zeros and poles
+by the order of zeros and poles relative to $D'$. That is,
+one can work with rational sections of $\mathscr O_{\bp^m}(D')$
+instead of rational sections of $\mathscr O_{\bp^m}$,
+and the following proof goes through otherwise unchanged.
+\todo{Aaron: Has anyone actually gone through the proof
+	for general effective divisors carefully, to make
+sure the above claim is correct?}
 We will first check that $F^{\vec v}_i$ determine a system of minimal
@@
 
-\begin{thm}
-\label{thm:proj-effective}
-Let $[x_0, \ldots, x_m]$ be a projective coordinate system for
-$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i D_i \in \bq \otimes \bp^m$, with $\alpha_i =
-\frac{p_i}{q_i} \in \bq$.
-
-Then the canonical ring $R_D$
-is generated in degrees up to $\max_{1 \leq i \leq n}{q_i}$ with
-relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$.
-\end{thm}
+\restateeffective*
 
 \begin{proof}
-We derive the result from the following inductive argument.
+We proceed by induction on $n$.
 If $n = 0$, i.e.~ $D = 0$, then we are done.
-Now, we look to inductively add hypersurfaces.
-If $D' = \sum_{i = 0}^{n} \alpha_i D_i$ is some $\bq$-divisor
-on $\bp^m$, then we look at $R_D$ where $D = D' + C$ for some
-degree $\pdeg$ hypersurface $C$. Now use the Veronese mapping
-to view $C$ as a hypersurface on $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$
-and the image of $C$ as the intersection of a Veronese variety
-with a hyperplane. Then we can reduce the process of inductively
-adding hypersurfaces to when the hypersurfaces are hyperplanes. However, this is accomplished
-by the method used in Theorem ~\ref{thm:proj-one-point} in an
-inductive manner as mentioned in Remark ~\ref{rem:proj-one-point-ind}.
+Now, we inductively add hypersurfaces.
+Let $D' = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bq\di \bp^m$, 
+for which the theorem holds. It suffices to show
+the theorem holds for $D \in \di \bq \otimes_\bq \bp^m$, where $D = D' + C$ for some
+degree $\pdeg$ hypersurface $C$.
+If $C$ were a hyperplane, we would then be done, by Theorem ~\ref{thm:proj-one-point}.
+
+To complete the theorem, we reduce the case that $C$ is a general hypersurface
+to the case that $C$ is a hyperplane, essentially by using the Veronese embedding.
+
+If $C$ is of degree $\pdeg$, then we construct the veronese embedding
+$\nu_\pdeg^m: \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
+so that the image of $C$ is the intersection of 
+a hyperplane in $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$ with $\nu_\pdeg^m(\bp^m)$.
+Now, note that the ring $H^0(\bp^m, C)$ is isomorphic to the
+$\pdeg$ veronese subring of $R_{V(x_0)}$, and so
+the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
+restricting to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
+Therefore, we can bound the degree of generators and relations of
+$R_D$ over $R_{D'}$ by the degree of generators and
+relations for $R_C \cong R_H.$
+This reduces the case of a hypersurface $C$ to
+a hyperplane $H$, completeting the proof by Theorem
+~\ref{thm:proj-one-point}.
 \end{proof}

### 2015-07-31 surfaces-write-up/surface-write-up.tex
responses/fixes to todos

@@
 I'm not very strongly tied to this idea though, and I think it's fine. I think it's fine.
+\\
+Peter: I understand where your objection is coming from.  However, I don't see a good way to fix it without creating a very ugly statement of the lemma.
 }
@@
 \begin{equation}\label{eqn:epsilon_i}
-	e_i := (-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
-	\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
+	e_i := d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
+	%\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
 \end{equation}
@@
 \begin{equation}\label{eqn:epsilon_i,j}
-	\begin{split}& e_{i,j} := (-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
-	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
-	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
-	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
-	\end{split}
+e_{i,j} := \frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_k \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i + \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
+%	
+%	(-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
+%	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
+%	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
+%	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
+%	\end{split}
 \end{equation}
-Note that the above expression makes sense when $i < j$, but one
-can similarly define $e_{i,j}$ when $j < i$.  
-\todo{Peter: I changed the above expression,
-but I'm still feel a little dubious that this is easier to read...
-
-Aaron: I agree this is harder to read. Why don't we just write
-$e_{i,j} = a e_i + b e_j$ (where of course you replace a and b by explicit
-constants). Wouldn't that be much cleaner? Also, I think we should
-explicitly state what the small rearrangement is to switch 
-$i$ and $j$, but perhaps it won't be relevant if you write $e_{ij} $
-as a linear combination of $e_i, e_j$.}
 
@@
 	that depend on $i$, such as $E,\sigma,\lambda$
-have an $i$ subscript.}
+have an $i$ subscript.
+
+Peter: Better (on the first comment?
+As for the second, that might be a little tricky, because we already have $E_\mu$, so we would have to do something like $E_{i,\mu}$ (which we could of course do...)}
 we simply write $f_i$ as a 
@@
 1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
-\rfloor$ whenever $i > 4$.
+\rfloor$ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
 
@@
 degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
-component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
+component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
 By a careful computation, we can find $\lambda \in \Sigma$ 
-\todo{Aaron: Is it at all possible to write down what $\lambda$ and the $r_{i,j}$ are?
-I suspect we should be able to write them in a couple lines, which would
-definitely clarify how we're getting the bound on degree $E$. While I agree
-it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
-to say what the $r_{i,j}$ and $\lambda$ are.
-\\
-Peter: There is not a unique choice of the $r_{i,j}$'s.
-When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.
-
-Aaron: OK. In that case, why don't you say that? Since I didn't understand those constraints on $r_{i,j}$, I think
-the reader would probably also be lost without explicitly writing those constraints.
-Also, what about $\lambda$? Is that uniquely determined?}
 and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
@@
 	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
-	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
+	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tp} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
 	\end{cases}.
 \end{equation}
-
-\noindent
+Specifically, if we write out $\sigma = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.
+Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.
+
 From this, we can further deduce that for such an $E$,
@@
 can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ 
-\todo{Aaron: Would it be reasonable to given these $q_{ij}$ a $\mu$
-superscript or subscript to indicate dependence on $\mu$?}
 and $\lambda \in
@@
 \begin{equation}\label{eqn:hirz-E_mu-translation}
-E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) +
-\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}
+E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i^\mu e_i\right) +
+\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}^\mu
 e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
-\Tp}} q_{j,i} e_{i,j}\right).
+\Tp}} q_{j,i}^\mu e_{i,j}\right).
 \end{equation}

### 2015-07-31 surfaces-write-up/surface-write-up.tex
confused about sigma

@@
 \end{align}
-\todo{Aaron: Possibly take this definition out of the proof, and move it into
-	the setup, since we want to reference it later.  \\
-Peter: I like having the statement of the lemma being nice and consise; also
-the statement has nothing to do with this geometric picture, so I find it more
-natural to have the geometric side contained in the proof.  I also don't quite
-see why it is so bad to reference something from inside a previous proof; a
-reader can surely locate it...
-
-Aaron: In general, I like the idea of having proofs self contained,
-so that one should only refer to the proof statement, not the
-body of the proof.
-I'm not very strongly tied to this idea though, and I think it's fine. I think it's fine.
-\\
-Peter: I understand where your objection is coming from.  However, I don't see a good way to fix it without creating a very ugly statement of the lemma.
-}
+
 We note that $\Sigma$ has extremal rays given by the lattice points 
@@
 Peter: Better (on the first comment?
-As for the second, that might be a little tricky, because we already have $E_\mu$, so we would have to do something like $E_{i,\mu}$ (which we could of course do...)}
+As for the second, that might be a little tricky, because we already have $E_\mu$, so we would have to do something like $E_{i,\mu}$ (which we could of course do...)
+
+Aaron: Does $E_\mu$ depend on $i$? I thought it didn't, but if it does, then we should definitely do $E_{i,\mu}$ since I didn't
+realize it depends on $i$. If $E_\mu$ doesn't depend on $i$, then we can just write $E_i$, and $E_\mu$,
+and there is no danger of confusion because the subscripts live in different categories.}
 we simply write $f_i$ as a 
@@
  \end{equation}
+
+\todo{Is $\sigma = \omega$? If not I'm very confused, since I don't see $\sigma$ defined anywhere before or after
+	but it seems like the key to the whole proof.
+}
 with $E$ of the form

### 2015-07-31 surfaces-write-up/surface-write-up.tex
responding to todos in sections 3/4

@@
 \maketitle
-\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most''}
+\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most.''\\
+Peter: I prefer ``Generated in degrees at most'' (plural).}
 
@@
 In this case, we can factor $\phi$ as a composition of $\chi$ and $\psi$ defined by
-\todo{Make this have mapsto on bottom}
 \[
@@
 \bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+x_i \arrow[mapsto]{r} & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \arrow[mapsto]{r} & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
@@
 realize it depends on $i$. If $E_\mu$ doesn't depend on $i$, then we can just write $E_i$, and $E_\mu$,
-and there is no danger of confusion because the subscripts live in different categories.}
+and there is no danger of confusion because the subscripts live in different categories.
+\\
+Peter:  Yes, essentially everything in the remainder of this proof depends on $i$, e.g.: $\omega$, $\lambda$ (depends on $i$ as well as the choice of $r_{i,j}$'s), $E$, all $E_\mu$'s, $F$, $F_\mu$'s; I think that is everything.
+I do not believe it would be helpful to add subscripts to all of these.
+Instead maybe it would be better just to have one sentence that very clearly says everything in the following proof fixes $i$ and depends on $i$.
+}
 we simply write $f_i$ as a 
@@
 \begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
-	\sigma = \lambda + E
+	\omega = \lambda + E
  \end{equation}
@@
 	but it seems like the key to the whole proof.
+	\\
+Peter: Oops, sorry, I changed some of the $\sigma$'s to $\omega$'s but clearly not all of them.
+Maybe I should have used a macro...
+I fixed the ones I saw, but let me know if you see any more $\sigma$'s popping up anywhere.
 }
@@
 \end{equation}
-Specifically, if we write out $\sigma = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.
+Specifically, if we write out $\omega = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.
 Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.

### 2015-07-31 surfaces-write-up/surface-write-up.tex
confused about i subscripts

@@
 \todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most.''\\
-Peter: I prefer ``Generated in degrees at most'' (plural).}
+Peter: I prefer ``Generated in degrees at most'' (plural).
+
+Aaron: What does plural mean here?
+I was thinking of doing something along the lines of
+$R$ is generated in degree at most $g$ with relations in degree at most $r$.}
 
@@
 Instead maybe it would be better just to have one sentence that very clearly says everything in the following proof fixes $i$ and depends on $i$.
+
+Aaron: How does $E_\mu$ depend on $i$? If you'd prefer to just say everything depends on $i$, I'm ok with it, though I still think including $i$ subscripts would be slightly
+preferable.
+Perhaps just say near the beginning a list of all the things that will depend on $i$.
+I don't think you can say "everything for the remainder of the proof depends on i", because that's not true, e.g., $\ell_j$ for $j \neq i$ doesn't depend on $i$, though of course this is very confusing because you write $\ell_i$ in the definition of $\deg E$.
+(Won't this be more difficult than just writing a supscript or superscript $i$ though?)
 }
@@
 
-\todo{Is $\sigma = \omega$? If not I'm very confused, since I don't see $\sigma$ defined anywhere before or after
-	but it seems like the key to the whole proof.
-	\\
-Peter: Oops, sorry, I changed some of the $\sigma$'s to $\omega$'s but clearly not all of them.
-Maybe I should have used a macro...
-I fixed the ones I saw, but let me know if you see any more $\sigma$'s popping up anywhere.
+\todo{Aaron:
+Does $E$ depend on $\omega$? I.e. have we fixed an $\omega$ for the rest of the proof?
+If so, why can we do this?
 }
+\todo{Aaron: If $i$ has been fixed for the remainder of the proof, why 
+are we using $i$ as dummy subscripts everywhere?}
 with $E$ of the form

### 2015-07-31 surfaces-write-up/surface-write-up.tex
responses to todos

@@
 I was thinking of doing something along the lines of
-$R$ is generated in degree at most $g$ with relations in degree at most $r$.}
+$R$ is generated in degree at most $g$ with relations in degree at most $r$. \\
+Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$.}
 
@@
 (Won't this be more difficult than just writing a supscript or superscript $i$ though?)
+\\
+Peter: Where does $\ell_j$ appear?
+It may be a typo...
+I can't remember...
+I think there are only $\ell_i$'s and $\ell_{i,j}$'s.
+Anyway, what I meant was every new variable defined after this point depends on $i$, not every variable used.
 }
@@
 If so, why can we do this?
+\\
+Your write, it depends on $\omega$, not just $i$.
+We can do this, because we will take the maximum over all $\omega$.
+What I mean by this, is for any starting relation (with initial term $\omega$ under some appropriate order) we reduce it to a different relation of the form described in the proof.
+We then take the maximum of the degrees of the relation that any $\omega$ is reduced to.
 }
 \todo{Aaron: If $i$ has been fixed for the remainder of the proof, why 
-are we using $i$ as dummy subscripts everywhere?}
+are we using $i$ as dummy subscripts everywhere?\\
+I don't follow; as in $e_i$'s?  or $e_{i,j}$'s?  $i$ is fixed in all of these statements, whereas $j$ ranges as necessary ($j$ is not fixed).}
 with $E$ of the form

### 2015-08-01 surfaces-write-up/surface-write-up.tex
fixed periods after case environments
edtis to section 4

@@
 \begin{equation}\label{eqn:epsilon_i,j}
-e_{i,j} := \frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_k \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i + \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
+e_{i,j} := \frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i + \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
 %	
@@
 
-Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
-{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
+Let $\omega\in \Omega$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
 \Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  

### 2015-08-01 surfaces-write-up/surface-write-up.tex
edits to 4.4- don't read yet

@@
 
-Peter: Better (on the first comment?
+Peter: Better (on the first comment)?
 As for the second, that might be a little tricky, because we already have $E_\mu$, so we would have to do something like $E_{i,\mu}$ (which we could of course do...)
@@
 polynomial in $f_1, \ldots f_4$. Furthermore, these
-generate all relations, since they allow us to reduce any $\prod_{j =
+generate all relations, since they allow us to reduce any monomial $\prod_{j =
 1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
@@
 
-%Note that we can view a relation from Equation
-%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
-%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
-Let $\Omega\subseteq \Sigma$ be the 
-set
-\begin{align*}
-	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
-	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
-= 0 \}.
-\end{align*}
-
-Let $\omega\in \Omega$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
-\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
+We now wish to bound the degree of generation the ideal of relations generated by these.
+To do this, we first fix $i$ and a relation of the form $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ (note that we ignore the case $i\in \{1, 2, 3, 4\}$ as in those cases all relations listed above are just the trivial relation because $\beta_i = f_i$).
+Our goal is to find a relation that the divides this, but whose degree we can bound.
+We do so by considering the lattice points corresponding to the monomials appearing in the relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda_\omega\in \Sigma$ that we can factor out of each monomial, to get a relation below a bounded degree.
+The following argument makes this precise:
+
+%Let $\Omega\subseteq \Sigma$ be the 
+%set
+%\begin{align*}
+%	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
+%	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
+%= 0 \}.
+%\end{align*}
+
+Consider a relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ with corresponding lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
+Then we can write $\sigma$ as a sum of $s_j e_j$'s for $j\in
+\Te$ and $s_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
 For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
@@
 degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
-component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
-By a careful computation, we can find $\lambda \in \Sigma$ 
-and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
-\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
-	\omega = \lambda + E
+component $-\alpha_k d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
+
+We note that for $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ to be a relation, every monomial must actually lie in $R_D$; this implies that $s_i\kappa_i\ge 1$, $\sum_{j\in \Tm} s_{i,j}\kappa_{i,j}' \ge 1$, and $\sum_{j\in \Tp} s_{i,j}\kappa_{j,i}'' \ge 1$ if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$ respectively.
+
+If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
+Define $E$ by
+\begin{equation}\label{eqn:hirz-E-translation}
+	E := \begin{cases}
+	\frac{1}{\kappa_i} e_i  &  \mbox{ if }i\in \Te\\
+	\sum_{j\in \Tm} r_{i,j} e_{i,j} & \mbox{ if } i\in \Tp\\
+	\sum_{j\in \Tp} r_{j,i} e_{j,i} 	& \mbox{ if } i\in \Tm.
+	\end{cases}
 \end{equation}
-
-\todo{Aaron:
-Does $E$ depend on $\omega$? I.e. have we fixed an $\omega$ for the rest of the proof?
-If so, why can we do this?
-\\
-Your write, it depends on $\omega$, not just $i$.
-We can do this, because we will take the maximum over all $\omega$.
-What I mean by this, is for any starting relation (with initial term $\omega$ under some appropriate order) we reduce it to a different relation of the form described in the proof.
-We then take the maximum of the degrees of the relation that any $\omega$ is reduced to.
-}
-\todo{Aaron: If $i$ has been fixed for the remainder of the proof, why 
-are we using $i$ as dummy subscripts everywhere?\\
-I don't follow; as in $e_i$'s?  or $e_{i,j}$'s?  $i$ is fixed in all of these statements, whereas $j$ ranges as necessary ($j$ is not fixed).}
-with $E$ of the form
-\begin{equation}\label{eqn:hirz-E-translation}
-	E = \begin{cases}
-	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
-	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
-	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tp} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
-	\end{cases}.
+Define
+\begin{equation}\label{eqn:defn-lambda}
+	\lambda = \sigma - E\in \Sigma.
  \end{equation}
-Specifically, if we write out $\omega = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.
-Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.
-
-From this, we can further deduce that for such an $E$,
+Note that
 \[
@@
 	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
-	&\mbox{ if } i \in \Tm \end{cases}.
-\]
-Let $M$ be the set of monomials terms of $\beta_i$.  Then for $\mu = \prod_{j=1}^n
-{f_i}^{c_i}\in M$, we
-\todo{Aaron: What is $M$? \\
-Peter: I don't quite follow this question... Is your objection that ``the set of monomial terms of $\beta_i$'' is too imprecise?
-
-Aaron: Sorry, I was trying to say that
-I don't understand what ``the set of monomials in terms of beta i'' means.
-Do you just mean that $M = \{\psi(\beta_1), \ldots, \psi(\beta_n)\}$?
-
-However, I'm really baffled as to why you want to apply $\psi$ to the
-$\beta_i$, since two lines later, you then apply the reverse correspondence
-and want to work back in the semigroupring. Why don't you just stay in the
-semigroup ring the whole time?
-I think I'm misunderstanding this, but is $\omega_\mu$ just equal to
-$\beta_i$ for some $i$? Also, why is $\omega_\mu$ missing a $d$ index
-as its first index?
-\\
-Peter: $\beta_i$'s are polynomials in $f_1, \ldots f_4$.  By the monomial terms in $\beta_i$ I mean look at each monomial appearing in this polynomial and take the set of those.
-}
-can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ 
-and $\lambda \in
-\Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
-corresponding to $\mu
-$ is of the form
-\[
-	\omega_\mu = \lambda + E_\mu
-\]
-where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined by
-
-\begin{equation}\label{eqn:hirz-E_mu-translation}
-E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i^\mu e_i\right) +
-\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}^\mu
-e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
-\Tp}} q_{j,i}^\mu e_{i,j}\right).
-\end{equation}
-
-Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.
-
-Let $F\in R_D$ correspond to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
-Then $F - \sum_{\mu \in M} F_\mu = 0$ induces a
-relation in degree at most
-\[
-	\rho + \deg(F)
-\]
-
-\noindent
-which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$ (recall that $\rho$, defined in Equation \ref{eqn:def-sigma}, is an upper bound for generation degree).
+	&\mbox{ if } i \in \Tm. \end{cases}
+\]
+
+Let $M_i$ be the set of monomials terms of $\beta_i$ (recall $\beta_i$ is a polynomial in $f_1, \ldots f_4$).  Let $\mu = \prod_{j=1}^4
+{f_j}^{h_j}\in M_i$ and consider the lattice point (in the same degree $d$ as $\sigma$)
+\[
+	\sigma_\mu = (d, c_1 + h_1, \ldots, c_4+h_4, c_5, \ldots, c_n).
+\]
+Define 
+\[
+	E_\mu = \sigma_\mu - \lambda.
+\]
+A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}'s$) and has the same degree as $E$.
+
+Let $F\in R_D$ be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.  
+Then $F - \sum_{\mu \in M} F_\mu = 0$ is a relation %in degree
+%\[
+%	\deg(F) = \deg(E)
+%\]
+which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$. 
 We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
@@
 	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
-	&\mbox{ if } i \in \Tm \end{cases}.
+	&\mbox{ if } i \in \Tm. \end{cases}
 	\]

### 2015-08-02 surfaces-write-up/surface-write-up.tex
respond to notation todo

@@
 $R$ is generated in degree at most $g$ with relations in degree at most $r$. \\
-Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$.}
+
+Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$. \\
+
+Robin: Agree with Peter, because it's more accurate to say that the generators in $R$ lie in degrees $\leq r$.}
 

### 2015-08-02 surfaces-write-up/surface-write-up.tex
agree with you guys for degrees at most...
fixed error in 4.4 proof

--- 2015-08-01 surfaces-write-up/surface-write-up.tex
@@
 \[
-	\tau = \sigma
+	\tau = \rho
 	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
@@
 From this we can deduce that a set of extremal rays of $\Sigma$ are given as follows:
-For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
+For $i \in \Te(D)$, define $e_i \in R_D$ in degree 
+\[
+	d_i = \ell_i \gcd(a_i, b_i)
+\]
+by 
 \begin{equation}\label{eqn:epsilon_i}
@@
 \noindent
-For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
+For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree 
+\[
+	d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)
+\]
+by
 \begin{equation}\label{eqn:epsilon_i,j}
@@
 
+If $i\in \Te$ define $r_i := \frac{1}{\kappa_i}$.
 If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
+For $j,k\ne i$, define all $r_j$ and $r_{j,k}$'s to be 0.
 Define $E$ by
 \begin{equation}\label{eqn:hirz-E-translation}
-	E := \begin{cases}
-	\frac{1}{\kappa_i} e_i  &  \mbox{ if }i\in \Te\\
-	\sum_{j\in \Tm} r_{i,j} e_{i,j} & \mbox{ if } i\in \Tp\\
-	\sum_{j\in \Tp} r_{j,i} e_{j,i} 	& \mbox{ if } i\in \Tm.
-	\end{cases}
+	E := \sum_{j\in \Te} (s_j - \lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}.
 \end{equation}
@@
 \begin{equation}\label{eqn:defn-lambda}
-	\lambda = \sigma - E\in \Sigma.
+	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
  \end{equation}
@@
 \[
-	\deg(E) \le \begin{cases}
+	\deg(E) \le \rho + \begin{cases}
 	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
@@
 \]
+where $\rho$ is as in Equation \ref{eqn:def-sigma}.
 
@@
 \]
-A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}'s$) and has the same degree as $E$.
+A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}s$) and has the same degree as $E$.
 
 Let $F\in R_D$ be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.  
-Then $F - \sum_{\mu \in M} F_\mu = 0$ is a relation %in degree
+Then $F - \sum_{\mu \in M_i} F_\mu = 0$ is a relation %in degree
 %\[
@@
 %\]
-which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$. 
+which divides $(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 
 We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
 \[
-	\deg(F) = \deg(E) \le \begin{cases}
+	\deg(F) = \deg(E) \le \rho + \begin{cases}
 	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\

### 2015-08-02 surfaces-write-up/surface-write-up.tex

@@
 $R$ is generated in degree at most $g$ with relations in degree at most $r$. \\
-Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$.}
+
+Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$. \\
+
+Robin: Agree with Peter, because it's more accurate to say that the generators in $R$ lie in degrees $\leq r$.
+
+Aaron: Ah, I didn't see the degrees was pluralized, but now I do, and I agree. Let's adapt this convention.}
 

### 2015-08-03 surfaces-write-up/surface-write-up.tex
clean up minor todos / abbrev first todo

--- 2015-08-02 surfaces-write-up/surface-write-up.tex
@@
 \maketitle
-\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most.''\\
-Peter: I prefer ``Generated in degrees at most'' (plural).
-
-Aaron: What does plural mean here?
-I was thinking of doing something along the lines of
-$R$ is generated in degree at most $g$ with relations in degree at most $r$. \\
-Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$.}
+\todo{Standardize ``generation in degrees at most.''}
 
@@
 with $\deg \vec v = c_i$. Furthermore, it has
-relations generated \todo{over $R_{D'}$?} by the following two types:
+relations generated by the following two forms:
 \begin{enumerate}
@@
 
-\todo{say something about ghost points? Peter: Haven't we already done that at the begining of the section?}
-
 \section{Canonical Rings on Hirzebruch surfaces}

### 2015-08-04 surfaces-write-up/surface-write-up.tex
revisions on last thm, it's looking much better, Peter!

@@
 \label{eqn:define-T-(D)}
-	\Tm(D) = \left\{ j \in \{1, \ldots, n\}: \bida_j \sum_{k = 1}^n \alpha_k
-	\bidb_k < \bidb_j \sum_{k=1}^n \alpha_k \bida_k \right\}.
+	\Tm(D) = \left\{ i \in \{1, \ldots, n\}: \bida_i \sum_{k = 1}^n \alpha_k
+	\bidb_k < \bidb_i \sum_{k=1}^n \alpha_k \bida_k \right\}.
 \end{equation}
@@
 by
-\begin{equation}\label{eqn:epsilon_i,j}
-e_{i,j} := \frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i + \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
+\begin{align}\label{eqn:epsilon_i,j}
+e_{i,j} := &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
+&+ \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
 %	
@@
 %	\end{split}
-\end{equation}
+\end{align}
 
@@
 \noindent
-whenever there is some degree $d \in \mathbb{N}$
-and $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
+lying in degree $d \in \mathbb{N}$
+with $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
 ^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
 
-To find such a $\beta_i$,
+We claim such a $\beta_i$,
 \todo{Aaron: Shouldn't we say something above like, the kernel
@@
 Anyway, what I meant was every new variable defined after this point depends on $i$, not every variable used.
+
+Aaron: You're right, I was confused. It is just $l_{i,j}$.
 }
-we simply write $f_i$ as a 
-polynomial in $f_1, \ldots f_4$. Furthermore, these
+can be expressed as a polynomial $\beta_i(f_1,f_2,f_3,f_4)$ with 
+$\beta_i(f_1,f_2,f_3,f_4) = f_i$
+as elements of $\bk[\Sigma],$ which is possible as $f_1,f_2,f_3,f_4$ generate $\Sigma,$ and hence generate $\bk[\Sigma]$. Furthermore, these
 generate all relations, since they allow us to reduce any monomial $\prod_{j =
 1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
-\rfloor$ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
+\rfloor$
+\todo{Aaron: Should $r_i$ be $c_i$ or should $c_i$ be $r_i$?}
+\todo{Aaron: Am I misremembering, or did we agree on the phone that you would put $i$ subscripts on all the things that depend on $i$?
+If not, weren't you at least going to say somewhere which things depend on $i$?}
+ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
 
 We now wish to bound the degree of generation the ideal of relations generated by these.
-To do this, we first fix $i$ and a relation of the form $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ (note that we ignore the case $i\in \{1, 2, 3, 4\}$ as in those cases all relations listed above are just the trivial relation because $\beta_i = f_i$).
+To do this, we first fix $i$ and a relation of the form $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0.$ Note that there are no relations for $i\in \{1, 2, 3, 4\}$ as $\beta_i = f_i$.
 Our goal is to find a relation that the divides this, but whose degree we can bound.
-We do so by considering the lattice points corresponding to the monomials appearing in the relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda_\omega\in \Sigma$ that we can factor out of each monomial, to get a relation below a bounded degree.
-The following argument makes this precise:
+We do so by considering the lattice points corresponding to the monomials appearing in the relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda_\omega\in \Sigma$
+\todo{How can you define $\lambda_\omega$ without yet defining $\omega$?
+Also, you only define $\lambda$ later, not $\lambda_\omega$. I don't even think you define $\omega$ later.
+} that we can factor out of each monomial, to get a relation below a bounded degree.  The following argument makes this precise:
 
@@
 \Te$ and $s_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
-For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
-component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
-degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
-component $-\alpha_k d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
-
-We note that for $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ to be a relation, every monomial must actually lie in $R_D$; this implies that $s_i\kappa_i\ge 1$, $\sum_{j\in \Tm} s_{i,j}\kappa_{i,j}' \ge 1$, and $\sum_{j\in \Tp} s_{i,j}\kappa_{j,i}'' \ge 1$ if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$ respectively.
+For convenience, defing $d_j := \deg e_j$ (when it exists) and let the $j^{th}$
+component of $e_j$ be $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$.
+Also, let $d_{j,k} := \deg e_{j,k}$ (when it exists) and let the $j^{th}$ component of $e_{j,k}$ be $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and the $k^{th}$
+component be $-\alpha_k d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
+
+For $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$ to be a relation, it must, in particular, be an element of $R_D$.
+This implies that $s_i\kappa_i\ge 1$, $\sum_{j\in \Tm} s_{i,j}\kappa_{i,j}' \ge 1$, and $\sum_{j\in \Tp} s_{i,j}\kappa_{j,i}'' \ge 1$ if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$ respectively.
 
@@
 If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
-For $j,k\ne i$, define all $r_j$ and $r_{j,k}$'s to be 0.
+For $j\ne i$, define $r_j := 0$ and for all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} := 0$.
 Define $E$ by
@@
 where $\rho$ is as in Equation \ref{eqn:def-sigma}.
-
-Let $M_i$ be the set of monomials terms of $\beta_i$ (recall $\beta_i$ is a polynomial in $f_1, \ldots f_4$).  Let $\mu = \prod_{j=1}^4
-{f_j}^{h_j}\in M_i$ and consider the lattice point (in the same degree $d$ as $\sigma$)
+\todo{Aaron: Is one of these terms corresponding to $E$ and the other to $\lambda$? If so, can you say which?}
+
+Let $M_i$ be the set of monomials terms of $\beta_i = \beta_i(f_1, \ldots f_4)$.  Let $\mu = \prod_{j=1}^4
+{f_j}^{h_j}\in M_i$ and consider the lattice point 
 \[
@@
 \]
+where $d = \deg \sigma$.
 Define 
@@
 \]
-A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}s$) and has the same degree as $E$.
-
-Let $F\in R_D$ be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.  
+A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}$'s \todo{should one of these be $r_i$'s?}) and has the same degree as $E$.
+
+Let $F\in R_D$
+\todo{Aaron: Didn't we agree you would write these as $\psi(E)$ or something like that?} be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.
 Then $F - \sum_{\mu \in M_i} F_\mu = 0$ is a relation %in degree

### 2015-08-04 surfaces-write-up/surface-write-up.tex
I don't recall making the change it says I made... oops...
deal with peter's merge conflict...
responding to todos

@@
 
+In section 2, we discuss background knowledge and present some useful lemmas.  In section 3 we focus on projective spaces: $\mathbb{P}^n$ and prove the following two results:
 \begin{restatable}{thm}{restateeffective}
@@
 \end{restatable}
-
-\todo{transition}
 
@@
 
-\todo{transition}
+\noindent
+In section 4, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
 
@@
 
-\todo{Include summary of what each of the sections do.}
-\todo{Incorporate the following section into the $\bp^{m}$ section}
+\noindent
+Together, Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} provide bounds on generators and relations for the canonical ring of $\mathbb{Q}$-divisors of all minimal rational surfaces.
+Section 5 concludes the paper and discusses further questions.
+
+\todo{Incorporate the following section into the $\bp^{m}$ section
+\\
+Peter: I'm not sure what this refers to...  Can you be more specific}
 
@@
 $10$. 
-\todo{Clarify what this example means by the lattice approach}
+\todo{Clarify what this example means by the lattice approach 
+\\
+Peter: Maybe we should put this after the ensuing proofs.
+That way, rather than saying the Lattice Approach, we could say that this example illustrates how the prveious method requires us to add ghost points (and is false otherwise).}
 However, we possibly use the lattice approach, as all lower degrees only have
@@
 We claim such a $\beta_i$,
-\todo{Aaron: Shouldn't we say something above like, the kernel
-	is bounded by the maximum of something over all $i$,
-	so for the remainder of the proof, we fix an $i$.
-	Also, I think it would help if things
-	that depend on $i$, such as $E,\sigma,\lambda$
-have an $i$ subscript.
-
-Peter: Better (on the first comment)?
-As for the second, that might be a little tricky, because we already have $E_\mu$, so we would have to do something like $E_{i,\mu}$ (which we could of course do...)
-
-Aaron: Does $E_\mu$ depend on $i$? I thought it didn't, but if it does, then we should definitely do $E_{i,\mu}$ since I didn't
-realize it depends on $i$. If $E_\mu$ doesn't depend on $i$, then we can just write $E_i$, and $E_\mu$,
-and there is no danger of confusion because the subscripts live in different categories.
-\\
-Peter:  Yes, essentially everything in the remainder of this proof depends on $i$, e.g.: $\omega$, $\lambda$ (depends on $i$ as well as the choice of $r_{i,j}$'s), $E$, all $E_\mu$'s, $F$, $F_\mu$'s; I think that is everything.
-I do not believe it would be helpful to add subscripts to all of these.
-Instead maybe it would be better just to have one sentence that very clearly says everything in the following proof fixes $i$ and depends on $i$.
-
-Aaron: How does $E_\mu$ depend on $i$? If you'd prefer to just say everything depends on $i$, I'm ok with it, though I still think including $i$ subscripts would be slightly
-preferable.
-Perhaps just say near the beginning a list of all the things that will depend on $i$.
-I don't think you can say "everything for the remainder of the proof depends on i", because that's not true, e.g., $\ell_j$ for $j \neq i$ doesn't depend on $i$, though of course this is very confusing because you write $\ell_i$ in the definition of $\deg E$.
-(Won't this be more difficult than just writing a supscript or superscript $i$ though?)
-\\
-Peter: Where does $\ell_j$ appear?
-It may be a typo...
-I can't remember...
-I think there are only $\ell_i$'s and $\ell_{i,j}$'s.
-Anyway, what I meant was every new variable defined after this point depends on $i$, not every variable used.
-
-Aaron: You're right, I was confused. It is just $l_{i,j}$.
-}
 can be expressed as a polynomial $\beta_i(f_1,f_2,f_3,f_4)$ with 
@@
 generate all relations, since they allow us to reduce any monomial $\prod_{j =
-1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
+1}^n f_j^{r_j}$ to the canonical form where $r_j = - \lfloor d \alpha_i
 \rfloor$
-\todo{Aaron: Should $r_i$ be $c_i$ or should $c_i$ be $r_i$?}
 \todo{Aaron: Am I misremembering, or did we agree on the phone that you would put $i$ subscripts on all the things that depend on $i$?
-If not, weren't you at least going to say somewhere which things depend on $i$?}
- whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
+If not, weren't you at least going to say somewhere which things depend on $i$?
+\\
+Peter: I still don't entirely agree that explaining the dependency is important.
+What I mean by this is that the proof fixes $i, \sigma,$ etc.
+and proves the desired result.
+Proving it for each possible choice of course proves the general result; however, it doesn't seem important to me whether or not the intermediate variables are the same in the proof for $i'$ and $\sigma'$ than for $i$ and $\sigma$.
+Either way the proof is valid.
+This is why I have been somewhat resistant (sorry if annoyingly so...)to adding them in.
+
+On a side note, in some cases actually writing them in would be cumbersome, e.g. replacing $s_{j,k}$ with $s_{j,k,\sigma}$ (since there is one choice of $s_{j,k}$ for every $\sigma$.
+
+If you want, can you tell me exactly which variables would be helpful in understanding the proof to know their dependencies?
+}
+ whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
 
 We now wish to bound the degree of generation the ideal of relations generated by these.
-To do this, we first fix $i$ and a relation of the form $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0.$ Note that there are no relations for $i\in \{1, 2, 3, 4\}$ as $\beta_i = f_i$.
+To do this, we first fix $i$ and a relation of the form $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0.$ Note that there are no relations for $i\in \{1, 2, 3, 4\}$ as $\beta_i = f_i$; thus we restrict attention to $i \ge 5$.
 Our goal is to find a relation that the divides this, but whose degree we can bound.
-We do so by considering the lattice points corresponding to the monomials appearing in the relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda_\omega\in \Sigma$
-\todo{How can you define $\lambda_\omega$ without yet defining $\omega$?
-Also, you only define $\lambda$ later, not $\lambda_\omega$. I don't even think you define $\omega$ later.
-} that we can factor out of each monomial, to get a relation below a bounded degree.  The following argument makes this precise:
+We do so by considering the lattice points corresponding to the monomials appearing in the relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda\in \Sigma$
+that we can factor out of each monomial, to get a relation below a bounded degree.  The following argument makes this precise:
 
@@
 where $\rho$ is as in Equation \ref{eqn:def-sigma}.
-\todo{Aaron: Is one of these terms corresponding to $E$ and the other to $\lambda$? If so, can you say which?}
+\todo{Aaron: Is one of these terms corresponding to $E$ and the other to $\lambda$? If so, can you say which?\\
+Peter: No, one corresponds to $r_j$ and one to the fractional part of $s_j - r_j$.}
 
@@
 \]
-A quick computation deduces that $E_\mu$ lies in $\Sigma$ (using the condition on the $r_{i,j}$'s and $r_{j,i}$'s \todo{should one of these be $r_i$'s?}) and has the same degree as $E$.
-
-Let $F\in R_D$
-\todo{Aaron: Didn't we agree you would write these as $\psi(E)$ or something like that?} be the monomial given by the lattice point $E$ and $F_\mu \in R_D$ be the monomial given by the lattice point $E_\mu$ for each $\mu \in M_i$.
+A quick computation deduces that $E_\mu$ lies in $\Sigma$ 
+%(using the condition on the $r_{i,j}$'s and $r_{j,i}s$) \todo{should one of these be $r_i$'s?}.
+\\ Peter: No, but I'm not sure if the parenthetical is helpful anyway.
+$r_i$ isn't define or used (hopefully...) anywhere.)
+and has the same degree as $E$.
+
+Let $F = \Psi(E) \in R_D$
+\todo{Aaron: Didn't we agree you would write these as $\psi(E)$ or something like that? 
+\\
+Peter: Okay, I'm still a little unhappy with with the identification of lattice points in $\Sigma$ with monomials (since $\Psi$ maps monomials in a polynomial ring to monomials in $R_D$), but I made the change} and $F_\mu = \psi(E_\mu) \in R_D$ for each $\mu \in M_i$.
 Then $F - \sum_{\mu \in M_i} F_\mu = 0$ is a relation %in degree

### 2015-08-04 surfaces-write-up/surface-write-up.tex
generated in degrees at most

@@
 \maketitle
-\todo{Standardize ``generation in degrees at most.''}
+\todo{Standardize ``generation in degrees at most.''  \\
+Peter: Fixed, although sometimes we say ``generated in degrees less than'' which is meant to be distinct (less than rather than less then or equal to).}
 
@@
 \noindent
-is generated in degrees up to $\max_{1 \leq i \leq n}{q_i}$ with
-relations generated in degrees up to $2 \max_{1 \leq i \leq n}{q_i}$
+is generated in degrees at most $\max_{1 \leq i \leq n}{q_i}$ with
+relations generated in degrees at most $2 \max_{1 \leq i \leq n}{q_i}$
 \end{restatable}
@@
 $D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
-Then $R_D$ is generated in degree at most 
+Then $R_D$ is generated in degrees at most 
 \[
@@
 \noindent
-with relations generated in degree at most
+with relations generated in degrees at most
 \[
@@
 extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$
-is generated in degrees up to $2(\sum_{i=1}^{r}d_r-1)$.
+is generated in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
 \end{lem}
@@
 \begin{lem} \label{lem:proj-generators}
-$R_D$ is generated in degrees up to $\sum_{i=1}^n \ell_i a_i.$
+$R_D$ is generated in degrees at most $\sum_{i=1}^n \ell_i a_i.$
 
@@
 \label{lem:proj-relations-psi}
-$\ker \psi$ is generated in degrees up to
+$\ker \psi$ is generated in degrees at most
 \begin{align}
@@
 By ~\ref{lem:bound-ker-chi}, $\ker \chi$ is generated in degrees 
-up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
+at most $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
 ~\ref{lem:proj-relations-psi}, $\ker \psi,$ is generated in
@@
 \label{lem:hirz-generators}
-$R_D$ is generated in degree at most
+$R_D$ is generated in degrees at most
 \begin{equation}\label{eqn:def-sigma}
@@
 \noindent
-Therefore, $\ker \psi$ is generated in degree at most
+Therefore, $\ker \psi$ is generated in degreesat most
 \[

### 2015-08-04 surfaces-write-up/surface-write-up.tex
added space
read through and made some changes

@@
 rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
-When $D$ is a general $\bq$-divisor on any $\bp^m$ or on any
+When $D$ is a general $\bq$-divisor on any $\bp^m$ or on any Hirzebruch Surface
 $\hirz_m$, we give bounds on the generators and relations of
@@
 \cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring}
-on log spin canonical rings on stacky curves which provide bounds
+on canonical rings of stacky curves which provide bounds
 on rings of modular forms of Fuchsian groups through the study
 of particular $\bq$-divisors on curves.
+\todo{Peter: I think this is too much specificity about our result.
+I think everything after ``stacky curves'' should be eliminated, as it seems a little self-promoting.}
 
@@
 modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
-modular forms are both generalizations of modular forms to higher dimensions,
+modular forms are two generalizations of modular forms to higher dimensions,
 as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
-By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
+By Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
 one can translate the analytic category of 1-dimensional complex orbifolds to
@@
 Hilbert and Siegel modular forms with certain underlying spaces.
+\todo{Peter:  Hmm...
+this is very vague.
+It almost feels like a further question type statement, then a statement of why what we're doing matters.
+I guess the real issue, as we have sort of discussed, is that there are not any clear motivating reasons why one would actually use what we have done...
+Oh well}
 
@@
 
-In section 2, we discuss background knowledge and present some useful lemmas.  In section 3 we focus on projective spaces: $\mathbb{P}^n$ and prove the following two results:
+In Section \ref{sec:lemmas}, we discuss background knowledge and present some useful lemmas.
+In Section \ref{sec:proj} we focus on projective spaces: $\mathbb{P}^n$ and prove the following two results:
 \begin{restatable}{thm}{restateeffective}
@@
 \noindent
-In section 4, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
+In section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
 
@@
 Together, Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} provide bounds on generators and relations for the canonical ring of $\mathbb{Q}$-divisors of all minimal rational surfaces.
-Section 5 concludes the paper and discusses further questions.
+Section \ref{sec:conc} concludes the paper and discusses further questions.
 
@@
 
-Now we give a result describing the generators of a cone via its
-extremal rays.
-\todo{write more transition}
+We now present some preliminary results which will be used to prove Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} in Sections \ref{sec:proj} and \ref{sec:hirz} respectively.
+%Now we give a result describing the generators of a cone via its
+%extremal rays.
+%\todo{write more transition}
 
@@
 In this section, we bound the degrees of generators and relations for divisors
-on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case was covered in
+on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case restricts to the results of
 \cite{dorney:canonical}.
@@
 For the remainder of this section, we shall fix $m \geq 1$ and choose an
-isomorphism $\bp^m \cong \proj V$ so that $x_0,\ldots, x_m$ form a basis for
-$V$.  We will think of $x_i$ as a rational section of $H^0(\bp^m,
+isomorphism $\bp^m \cong \proj V$ for some vector space $V$ with basis $x_0,\ldots, x_m$.  We will think of $x_i$ as a rational section of $H^0(\bp^m,
 \sco_{\bp^m})$ of degree 1.
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying
+The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying \todo{Peter: Why do we include this $u$?  IN the later sections, I don't use this notation and we should standardize.}
 \begin{align}
@@
 c_i = -\lfloor d\alpha_i \rfloor && \text{ for } && i > m
-\end{align}
+\end{align}\todo{Peter: Should be for $i> m+1$ right?
+Looking below I see an $f_0$, where as above $f_i$ ranges 1 to $n$.
+We should choose whether or not 0 is included in the indexing and fix the section to match that convention.}
 
@@
 characterize the canonical rings when $D$ consists of one
-hypersurface and give strong bounds on generator and relation
+hypersurface and give strong \todo{Peter: I'm opposed to the inclusion of the word strong, as it ambiguous and subjective.
+I think we should either replace it with tight, and then explicitly say later how it is tight, or just get rid of the adjective.} bounds on generator and relation
 degrees for general effective divisors $D$.
@@
 Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
-$\vec{v} = (v_0, \ldots, v_m) \in \bq^{m + 1}$. Then write
+$\vec{v} = (v_0, \ldots, v_m) \in \bq^{m + 1}$.
+\todo{Peter: do we want to allow $\vec{v}\in \mathbb{Q}^{m+1}$ rather than $\mathbb{Z}^{m+1}$?
+I'm not sure if the arguments actually need the generality (and if so, it is a little worrisome since fractional powers aren't clearly defined algebraically.}  Then write
 \[
@@
 	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
-\vec{w} \in \mss_j$, there is a relation of the form either
+\vec{w} \in \mss_j$, there is a relation of the form: either
 \begin{flalign*}
@@
 	&(i < h_{i, j} < h_{i, j} + 1 < j).
-\end{flalign*}
+\end{flalign*} \todo{Peter: Can you clarify when these two cases occur: i.e.
+does the first only occur if $j = h_{i,j}+1$; otherwise, in cases when $i< h_{i,j} < h_{i,j} + 1< j$, do we get relations of both forms?}
 	\item For each $(i, j)$ with
@@
 \noindent
-Therefore, $\ker \psi$ is generated in degreesat most
+Therefore, $\ker \psi$ is generated in degrees at most
 \[
@@
 Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for
-all rational surfaces, via the minimal model program for surfaces
-\todo{Reference}.  One might then hope to further extend these results to all minimal surfaces:
+all rational surfaces, via the minimal model program for surfaces.  One might then hope to further extend these results to all minimal surfaces:
 \begin{question}

### 2015-08-04 surfaces-write-up/surface-write-up.tex
some clarifying edits in the pf of proj-eff, respond to one of Peter's todos

@@
 \end{align*}
+
+\noindent
+be the set of vectors of degree $c_i$.
 \end{defn}
@@
 	&(i < h_{i, j} < h_{i, j} + 1 < j).
-\end{flalign*} \todo{Peter: Can you clarify when these two cases occur: i.e.
-does the first only occur if $j = h_{i,j}+1$; otherwise, in cases when $i< h_{i,j} < h_{i,j} + 1< j$, do we get relations of both forms?}
+\end{flalign*}
+\todo{Peter: Can you clarify when these two cases occur: i.e. does the first 
+only occur if $j = h_{i,j}+1$; otherwise, in cases when $i< h_{i,j} < h_{i,j} + 1< 
+j$, do we get relations of both forms? \\
+Robin: It purely depends on whether the product $F_i^{\vec{v}} F_j^{\vec{w}} 
+$ happens to lie on the ray given by $\frac{c_{h_{i, j}}}{d_{h_{i, j}}}$ which is 
+not clearly determined by $i$ or $j$ from what I can see... Unless you see 
+something else. Only one relation exists for each $(i, j)$ and it is exactly one 
+of the two forms. I figured that the ``either'' made that clear, no?}
 	\item For each $(i, j)$ with
@@
 In particular, if $j \geq i + 2$ then $F_i^{\vec{v}} F_j^{\vec{w}}$
-has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} where $h$
-depends on $i, j$, so we notate $h = h_{i, j} \in \{1, \ldots, r\}$. We also
-have
-that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
+has a decomposition of the form ~\eqref{eqn:one-point-canonical-form} of 
+products of generators in adjacent degrees where $h$
+depends on $i$ and $ j$, so we notate $h_{i, j} := h \in \{1, \ldots, r\}$. We 
+also have that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
 $\bz_{\geq 0}$-span of $(d_{h_{i, j}}, c_{h_{i, j}})$ and
-$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore, we have that
-$h_{i, j} \neq i, j-1$ as can be shown in the same manner as the analogous statement in O'Dorney
+$(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore,
+$h_{i, j} \neq i$ and $h_{i, j} \neq j - 1$ by the proof of the analogous 
+statement in $bp^1$ given by O'Dorney
 \cite[Theorem 6]{dorney:canonical}. This gives the relations

### 2015-08-04 surfaces-write-up/surface-write-up.tex
started indexing at 0 and other responses

@@
 \label{thm:proj-effective-intro}
-Let $D = \sum_{i = 1}^{n} \alpha_i C_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
+Let $D = \sum_{i = 0}^{n} \alpha_i C_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
 \frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$. Let
+Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$. Let
 $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
@@
 \[
-	\sum_{i=1}^n \ell_i a_i
+	\sum_{i=0}^n \ell_i a_i
 \]
@@
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(	\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{1\le i \le n}
+	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
 \]
@@
 \label{sec:lemmas}
+
+\todo{Aaron: weren't we going to take this section out and move it into the later sections?}
 
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying \todo{Peter: Why do we include this $u$?  IN the later sections, I don't use this notation and we should standardize.}
+The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying \todo{Peter: Why
+do we include this $u$?  IN the later sections, I don't use this notation and
+we should standardize.
+
+Aaron: Isn't it necessary to distinguish the functions? For instance, we could consider $f_0$ either as a function in degree 1 or 2 for $D = \frac{1}{2}x_0$, and we need
+$u^d$ to distinguish which degree it lives in.
+I think we will need to go through and include the $d$ throughout.
+Do you think there's a way to avoid including the $d$?
+}
 \begin{align}
 \label{align:pm-span}
-\sum_{i=1}^{n} c_i \cdot \bida_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=0}^{n} c_i \cdot \bida_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
 \end{align}
@@
 form a spanning set for $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
-of the form $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying
+of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying
 \begin{align}
@@
 Looking below I see an $f_0$, where as above $f_i$ ranges 1 to $n$.
-We should choose whether or not 0 is included in the indexing and fix the section to match that convention.}
+We should choose whether or not 0 is included in the indexing and fix the section to match that convention.
+
+Aaron: I tried to fix it at $0$ everywhere. If probably missed a few places, so keep your eyes peeled.
+}
 
@@
 characterize the canonical rings when $D$ consists of one
-hypersurface and give strong \todo{Peter: I'm opposed to the inclusion of the word strong, as it ambiguous and subjective.
-I think we should either replace it with tight, and then explicitly say later how it is tight, or just get rid of the adjective.} bounds on generator and relation
+hypersurface and give tight bounds on generator and relation
 degrees for general effective divisors $D$.
-
+\todo{Aaron: make a remark as to why these bounds are tight}
 \begin{convention}
@@
 \todo{Peter: do we want to allow $\vec{v}\in \mathbb{Q}^{m+1}$ rather than $\mathbb{Z}^{m+1}$?
-I'm not sure if the arguments actually need the generality (and if so, it is a little worrisome since fractional powers aren't clearly defined algebraically.}  Then write
+I'm not sure if the arguments actually need the generality (and if so, it is a little worrisome since fractional powers aren't clearly defined algebraically.
+
+Aaron: No, these vectors should just lie in $\bz$. They're just used
+to given an ordering on monomials.
+}  Then write
 \[
@@
 
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be
+Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be
 homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$
@@
 \label{eqn:pm-basis-assumption}
-	f_1, \ldots, f_{m+1} \text{ form a } \bk \text{ basis of all degree 1 functions.}
+	f_0, \ldots, f_{m} \text{ form a } \bk \text{ basis of all degree 1 functions.}
 \end{align}
@@
 This example further generalizes to the following situation:
-Suppose $D = \sum_{i=1}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
+Suppose $D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
 \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm
@@
 ~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
-$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
+$\sum_{i=0}^{n}\ell_i$ cannot possibly hold. The reason for this is
 that the divisors may ``be contained in a hyperplane,'' i.e.~ be
@@
 points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
-$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
+$D$, and reorder so that if $D = \sum_{i=0}^{n}\alpha_i V(f_i)$,
 then $f_0, \ldots, f_m$ cut out linearly independent
@@
 \begin{defn}\label{def:ell_i}
-Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
+Let $D = \sum_{i=0}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
 Then notate
@@
 \begin{lem} \label{lem:proj-generators}
-$R_D$ is generated in degrees at most $\sum_{i=1}^n \ell_i a_i.$
+$R_D$ is generated in degrees at most $\sum_{i=0}^n \ell_i a_i.$
 
@@
 \[
-	\sum_{i=1}^n \ell_i a_i.
+	\sum_{i=0}^n \ell_i a_i.
 \]
@@
 \[
-	\bk[\Sigma] =  \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \in
-\mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=1}^{n} \bida_i c_i =
-\sum_{i=1}^{n} \bidb_i c_i \rangle. 
+	\bk[\Sigma] =  \langle u^d z_0^{c_0} \cdots z_n^{c_n} : c_i \in
+\mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=0}^{n} \bida_i c_i =
+\sum_{i=0}^{n} \bidb_i c_i \rangle. 
 \]
@@
 \bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+x_i \ar r & u^{d_i}z_0^{c_{i0}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
@@
 \label{eqn:relations-psi-proj}
-	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
+	(z_i - \beta_i)\prod_{j=0}^n {z_j}^{c_{j}}
 \end{equation}
@@
 for all $d \in \mathbb{N}$ and $c_i \ge -\alpha_i d$ satisfying
-$\bida_i + \sum_{j = 1}^n \bida_j c_j = 0$.
+$\bida_i + \sum_{j = 0}^n \bida_j c_j = 0$.
 
 We define the $\beta_i$ above so that $\beta_i$ is the expansion of
-$f_i$ when viewed as a polynomial in $k[f_1,\ldots, f_{m + 1}]$.
+$f_i$ when viewed as a polynomial in $k[f_0,\ldots, f_{m}]$.
 Furthermore, the relations given in Equation
 ~\eqref{eqn:proj-relation-degree} generate all relations, since they
-allow us to reduce any $ \prod_{j = 1}^n f_j^{r_i}$ to a canonical
-form, with $r_i = -\lfloor  d \alpha_i\rfloor$ whenever $i  > m + 1$.
+allow us to reduce any $ \prod_{j = 0}^n f_j^{r_i}$ to a canonical
+form, with $r_i = -\lfloor  d \alpha_i\rfloor$ whenever $i  > m$.
 
@@
 z_j^{c_j}$, by Equation ~\eqref{eqn:proj-relation-degree}. We first
-associate $(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ with $(d, c_1,
+associate $(z_i - \beta_i)\prod_{j=0}^n z_j^{c_j}$ with $(d, c_1,
 \ldots, c_n) \in \Sigma,$ as defined in Equation
-~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \mathbb{Z}^{n + 1}$
+~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \mathbb{Z}^{n + 2}$
 be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying
-$r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=1}^n r_j a_j = -a_i$.
+$r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=0}^n r_j a_j = -a_i$.
 Let
 \begin{align*}
-	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_1 a_1}{\deg(D)},
+	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_0 a_0}{\deg(D)},
 	\ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
@@
 Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\bq_{\geq 0}}
-(e_1, \ldots, e_n)$ with $e_i$ as defined in Equation
+(e_0, \ldots, e_n)$ with $e_i$ as defined in Equation
 ~\ref{defn:e-i-proj}. Therefore, we can write any element of
@@
 \[
-	\delta_i + \sum_{j=1}^n r_j e_j
+	\delta_i + \sum_{j=0}^n r_j e_j
 \]
@@
 \[
-	\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.
+	\frac{\bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
 \]
@@
 By ~\ref{lem:bound-ker-chi}, $\ker \chi$ is generated in degrees 
-at most $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
+at most $2\sum_{i=0}^n \ell_i a_i$ and by Lemma
 ~\ref{lem:proj-relations-psi}, $\ker \psi,$ is generated in
-degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i$. 
+degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i$. 
 Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker \phi$
@@
 \[
-	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
+	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{1\le i \le n}
+	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
 \]

### 2015-08-06 surfaces-write-up/surface-write-up.tex
some todos like F_mu as iota circ psi

@@
 
-\todo{Incorporate the following section into the $\bp^{m}$ section
+\todo{Aaron: Incorporate the following section into the $\bp^{m}$ section
 \\
-Peter: I'm not sure what this refers to...  Can you be more specific}
+Peter: I'm not sure what this refers to...  Can you be more specific \\
+
+Aaron: A couple of weeks ago, we agreed that we would remove the general lemmas section, and just
+merge it with the $\bp^m$ section. So, I was saying that we should do this.}
 
@@
 \label{sec:lemmas}
-
-\todo{Aaron: weren't we going to take this section out and move it into the later sections?}
 
@@
 We now present some preliminary results which will be used to prove Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} in Sections \ref{sec:proj} and \ref{sec:hirz} respectively.
-%Now we give a result describing the generators of a cone via its
-%extremal rays.
-%\todo{write more transition}
 
@@
 	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
-\vec{w} \in \mss_j$, there is a relation of the form: either
+\vec{w} \in \mss_j$, there is a relation of the form either
 \begin{flalign*}
@@
 \\
-Peter: I still don't entirely agree that explaining the dependency is important.
-What I mean by this is that the proof fixes $i, \sigma,$ etc.
-and proves the desired result.
-Proving it for each possible choice of course proves the general result; however, it doesn't seem important to me whether or not the intermediate variables are the same in the proof for $i'$ and $\sigma'$ than for $i$ and $\sigma$.
-Either way the proof is valid.
-This is why I have been somewhat resistant (sorry if annoyingly so...)to adding them in.
-
-On a side note, in some cases actually writing them in would be cumbersome, e.g. replacing $s_{j,k}$ with $s_{j,k,\sigma}$ (since there is one choice of $s_{j,k}$ for every $\sigma$.
-
-If you want, can you tell me exactly which variables would be helpful in understanding the proof to know their dependencies?
+Peter: I still don't entirely agree that explaining the dependency is
+important.  What I mean by this is that the proof fixes $i, \sigma,$ etc. and
+proves the desired result.  Proving it for each possible choice of course
+proves the general result; however, it doesn't seem important to me whether or
+not the intermediate variables are the same in the proof for $i'$ and $\sigma'$
+than for $i$ and $\sigma$.  Either way the proof is valid.  This is why I have
+been somewhat resistant (sorry if annoyingly so...)to adding them in.
+
+On a side note, in some cases actually writing them in would be cumbersome,
+e.g. replacing $s_{j,k}$ with $s_{j,k,\sigma}$ (since there is one choice of
+$s_{j,k}$ for every $\sigma$.
+
+If you want, can you tell me exactly which variables would be helpful in
+understanding the proof to know their dependencies?
+
+Aaron: Ok, I'll stop bugging you about it. I just thought we
+should add it because I didn't understand that it depended
+on $i$ when I read it. Maybe we can see what David
+has to say about it when he reads it?
+Also, I don't see why calling $s_{j,k}$ by $s_{j,k,\sigma}$ is cumbersome,
+that seems fine to me.
 }
+
  whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
@@
 A quick computation deduces that $E_\mu$ lies in $\Sigma$ 
-%(using the condition on the $r_{i,j}$'s and $r_{j,i}s$) \todo{should one of these be $r_i$'s?}.
-\\ Peter: No, but I'm not sure if the parenthetical is helpful anyway.
-$r_i$ isn't define or used (hopefully...) anywhere.)
 and has the same degree as $E$.
@@
 \\
-Peter: Okay, I'm still a little unhappy with with the identification of lattice points in $\Sigma$ with monomials (since $\Psi$ maps monomials in a polynomial ring to monomials in $R_D$), but I made the change} and $F_\mu = \psi(E_\mu) \in R_D$ for each $\mu \in M_i$.
+Peter: Okay, I'm still a little unhappy with with the identification of lattice
+points in $\Sigma$ with monomials (since $\Psi$ maps monomials in a polynomial
+ring to monomials in $R_D$), but I made the change
+Aaron: Thanks. If you're unhappy, you can always just define the map $\iota:\Sigma \rightarrow \bk[\Sigma]$ and say $F_\mu = \iota \circ \psi (E_\mu)$}
+ and $F_\mu = \psi(E_\mu)
+\in R_D$ for each $\mu \in M_i$.  
 Then $F - \sum_{\mu \in M_i} F_\mu = 0$ is a relation %in degree

### 2015-08-06 surfaces-write-up/surface-write-up.tex
address bq^n -> bz^n todo on vector exp notation

@@
 on rings of modular forms of Fuchsian groups through the study
-of particular $\bq$-divisors on curves.
-\todo{Peter: I think this is too much specificity about our result.
-I think everything after ``stacky curves'' should be eliminated, as it seems a little self-promoting.}
+of particular $\bq$-divisors on curves.  \todo{I think this is too much 
+specificity about our result.  I think everything after ``stacky curves'' should be 
+eliminated, as it seems a little self-promoting.}
 
@@
 Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
-$\vec{v} = (v_0, \ldots, v_m) \in \bq^{m + 1}$.
-\todo{Peter: do we want to allow $\vec{v}\in \mathbb{Q}^{m+1}$ rather than $\mathbb{Z}^{m+1}$?
-I'm not sure if the arguments actually need the generality (and if so, it is a little worrisome since fractional powers aren't clearly defined algebraically.
-
-Aaron: No, these vectors should just lie in $\bz$. They're just used
-to given an ordering on monomials.
-}  Then write
+$\vec{v} = (v_0, \ldots, v_m) \in \bz^{m + 1}$.  Then write
 \[
@@
 \label{defn:vec-sum}
-For $\vec{v} \in \bq^n$, denote $\deg \vec{v} := \sum_{i = 0}
+For $\vec{v} \in \bz^n$, denote $\deg \vec{v} := \sum_{i = 0}
 ^n v_i$.
@@
 \label{defn:vec-order}
-Let $\vec{v}, \vec{w} \in \bq^n$. Let $i \in \{1,\ldots, n\}$
+Let $\vec{v}, \vec{w} \in \bz^n$. Let $i \in \{1,\ldots, n\}$
 be the biggest index such that $v_i$ is nonzero

### 2015-08-06 surfaces-write-up/surface-write-up.tex
added remark on tightness of bounds

@@
 In this subsection, we restrict attention to the case of effective
-fractional divisors $D \in \bq \otimes \di \bp^m$. We completely
-characterize the canonical rings when $D$ consists of one
-hypersurface and give tight bounds on generator and relation
-degrees for general effective divisors $D$.
+fractional divisors $D \in \bq \otimes \di \bp^m$. We give an explicit presentation of the canonical rings when $D$ is an effective
+divisor.
+
 \todo{Aaron: make a remark as to why these bounds are tight}
@@
 \label{defn:vec-order}
-Let $\vec{v}, \vec{w} \in \bz^n$. Let $i \in \{1,\ldots, n\}$
+Let $\vec{v}, \vec{w} \in \bz^{m+1}$. Let $i \in \{0,\ldots, m\}$
 be the biggest index such that $v_i$ is nonzero
-and $j \in \{1,\ldots, n\}$ be the smallest index such that $w_j$ is
+and $j \in \{0,\ldots, m\}$ be the smallest index such that $w_j$ is
 nonzero. Define $\vec{v} \prec \vec{w}$ if $i \leq j$.
@@
 Note that we cannot extend this result to the case when
-$D$ is supported at two hypersurfaces with arbitrary rational
+$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
 coefficients in the same manner that O'Dorney does for the
@@
 \end{proof}
+
+\begin{rem}
+\label{rem:exact-effective-bounds}
+Note that the proof of Theorem ~\ref{thm:proj-effective-intro} not only gives bounds on the degrees of the generators and relations, but actually gives an explicit method for computing the presentaiton.
+In particular, these bounds are tight.
+The generator bound is always acheived and the bound on the relations is achieved if $m \geq 2$.
+\end{rem}
 

### 2015-08-07 surfaces-write-up/surface-write-up.tex
encorporated section 2 into section 3, still need to add transitions though

@@
 
-In Section \ref{sec:lemmas}, we discuss background knowledge and present some useful lemmas.
-In Section \ref{sec:proj} we focus on projective spaces: $\mathbb{P}^n$ and prove the following two results:
+In Section \ref{sec:proj} we prove the following two results bounding
+the degree of generators and relations of
+stacky canoincal rings on $\bp^m$:
 \begin{restatable}{thm}{restateeffective}
@@
 \noindent
-Together, Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} provide bounds on generators and relations for the canonical ring of $\mathbb{Q}$-divisors of all minimal rational surfaces.
+Together, Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} provide bounds on generators and relations for the canonical ring of $\bq$-divisors of all minimal rational surfaces.
 Section \ref{sec:conc} concludes the paper and discusses further questions.
 
-\todo{Aaron: Incorporate the following section into the $\bp^{m}$ section
-\\
-Peter: I'm not sure what this refers to...  Can you be more specific \\
-
-Aaron: A couple of weeks ago, we agreed that we would remove the general lemmas section, and just
-merge it with the $\bp^m$ section. So, I was saying that we should do this.}
-
-\section{Lemmas for Generation and Relations}
-\label{sec:lemmas}
-
-\begin{defn}
-\label{defn:lower-approximation}
-If $\alpha \in \bq$, then a rational number $\frac{c}{k} \leq \alpha$
-(written in reduced form with $c \in \bz, k \in \bn$) is a
-\textbf{best lower approximation} to $\alpha$ if there does not
-exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
-$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
-\end{defn}
-
-\begin{rem}
-\label{rem:lower-approximation}
-Note that all integers less than or equal to $\lfloor \alpha \rfloor$
-are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
-then the non-negative best lower approximations of
-$\alpha$ form a finite sequence
-\[
-	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
-\]
-
-\noindent
-Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
-\end{rem}
-
-\begin{figure}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower
-approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best
-lower approximation and each ``$\circ$'' denotes a lattice point
-below $5y=14x$ which is not a best lower approximation.  Note that
-the non-negative best lower approximations generate the monoid of
-lattice points in the first quadrant satisfying  $5y \le 14x$, with
-the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$.}
-\label{fig:s14/5-lattice}
-\end{figure}
-
+\ssec{Notations and Conventions}
+\todo{Aaron: State other notations used here. I think there are few enough that we can just do it in a paragraph or two at the end of the introduction here.}
 \begin{convention}
@@
 \noindent
-where $\alpha_i \in \bq$ and $D_i \in \di X$ is an irreducible divisor.
+where $\alpha_i \in \bq$ and $D_i \in \di X$ is an irreducible divisor. When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$.
 \end{convention}
-
-We now present some preliminary results which will be used to prove Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} in Sections \ref{sec:proj} and \ref{sec:hirz} respectively.
-
-\begin{prop}
-\label{prop:cone-generation}
-Let $n \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$, and let
-$a_i, b_i \in \bz$ with $1 \leq i \leq n.$ Define
-\begin{align*}
-	\Sigma := \left \{(d, c_1, \ldots, c_n) \in \bz^{n + 1} : c_i \geq -
-	d \alpha_i, 1 \leq i \leq n \text{ and } \sum_{i = 1}^{n} a_i =
-	\sum_{i	= 1}^{n}b_i = 0 \right \}
-\end{align*}
-
-\noindent
-Suppose $e_1, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_1^i,
-\ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
-i.e.~ $\Sigma$ is contained in the $\bq_{\geq 0}$ span of
-$e_1, \ldots, e_t$.
-
-Then, as a semigroup, $\Sigma$ is generated by
-elements whose first coordinate is less than $\sum_{i = 1}^{t}
-\pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be
-written in a canonical form $\lambda + \sum_{i = 1}^{t} w_i e_i$ 
-with $\lambda = \sum_{i = 1}^{r} s_i e_i$ with $0 \leq s_i < 1$, the
-first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$,
-and $w_1, \ldots, w_t \in \bz_{\geq 0}$.
-\end{prop}
-
-\begin{proof}
-By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
-{i = 1}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) := r - \lfloor r
-\rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 1}
-^{t} \fr(r_i)$. Whence, we can write $\sigma = \lambda + \sum_{i = 1}
-^{t} \lfloor r_i \rfloor e_i.$ Consequently, $\sigma$ lies in the
-$\bz_{\geq 0}$ span of $\lambda, e_1, \ldots, e_t$, which all have
-first coordinate less than $\sum_{i=1}^{t} r_i$. Ergo, $\Sigma$ is
-generated by elements whose first coordinate is less than
-$\sum_{i = 1}^{t} r_i$.
-\end{proof}
-
-\begin{lem}
-\label{lem:composite-map}
-Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$. Suppose we have a
-surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i
-\mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
-Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$
-Then, define
-\begin{align*}
-	\Sigma = \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i = 0 \rangle. 
-\end{align*}
-In this case, we can factor $\phi$ as a composition of $\chi$ and $\psi$ defined by
-\[
-\begin{tikzcd}
-\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \arrow[mapsto]{r} & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \arrow[mapsto]{r} & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
-\end{tikzcd}
-\]
-Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$
-is at most the maximum of the minimal degree of generation of $\ker \chi$ and
-the minimal degree of generation of $\ker \psi$.
-\end{lem}
-\begin{proof}
-First, we show there is an exact sequence
-\[
-\begin{tikzcd}
-0 \ar {r} & \ker \chi \ar{r}{\rho} & \ker \phi \ar {r}{\tau} & \ker \psi \ar r & 0.
-\end{tikzcd}
-\]
-To see this, note that $\rho$ is injective and $\tau$ is surjective\ because
-$\phi = \chi \circ \psi$. Additionally, $\tau \circ \rho = 0$ by definition of
-the kernel of $\chi$. Finally, if $a \in\ker \tau$, then by definition $\chi(a)
-= 0,$ so $a \in \im \rho$.
-
-This shows that lifts of generators of $\ker \psi$ together with images of
-generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
-\end{proof}
-
-\begin{lem}
-\label{lem:bound-ker-chi}
-Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
-extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$
-is generated in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
-\end{lem}
-\begin{proof}
-Since $e_1, \ldots, e_r$ are extremal rays, by Proposition
-~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
-in a canonical form $\lambda + \sum_{i=1}^{r}e_i$. Now, let $\lambda_0 :=
-0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be
-written in the form $\lambda_i = \sum_{i=1}^{r}r_i e_i$ with $0 \leq r_i < 1.$
-Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in
-the above canonical form, yielding a relation in degree at most $\deg \lambda_i
-+ \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$
-Furthermore, these relations generate all relations, as one can apply a
-sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
-$\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Proposition
-~\ref{prop:cone-generation}.
-\end{proof}
 
@@
 \todo{construct class of additional examples}
-
+\todo{Throughout this section, include some more transition, explaining which lemmas are general and will be used again for hirzebruch surfaces and which lemmas will be used only for $\bp^m$.}
 Having justified the necessity of adding ghost points, we proceed to bound the
 number of generators and relations.
+
+\begin{defn}
+\label{defn:lower-approximation}
+If $\alpha \in \bq$, then a rational number $\frac{c}{k} \leq \alpha$
+(written in reduced form with $c \in \bz, k \in \bn$) is a
+\textbf{best lower approximation} to $\alpha$ if there does not
+exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
+$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
+\end{defn}
+
+\begin{rem}
+\label{rem:lower-approximation}
+Note that all integers less than or equal to $\lfloor \alpha \rfloor$
+are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
+then the non-negative best lower approximations of
+$\alpha$ form a finite sequence
+\[
+	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
+\]
+
+\noindent
+Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
+\end{rem}
+
+\begin{figure}
+\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+\caption{This figure shows each non-negative best lower
+approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best
+lower approximation and each ``$\circ$'' denotes a lattice point
+below $5y=14x$ which is not a best lower approximation.  Note that
+the non-negative best lower approximations generate the monoid of
+lattice points in the first quadrant satisfying  $5y \le 14x$, with
+the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$.}
+\label{fig:s14/5-lattice}
+\end{figure}
+
+We now present some preliminary results which will be used to prove Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} in Sections \ref{sec:proj} and \ref{sec:hirz} respectively.
+
+\begin{prop}
+\label{prop:cone-generation}
+Let $n \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$, and let
+$a_i, b_i \in \bz$ with $1 \leq i \leq n.$ Define
+\begin{align*}
+	\Sigma := \left \{(d, c_1, \ldots, c_n) \in \bz^{n + 1} : c_i \geq -
+	d \alpha_i, 1 \leq i \leq n \text{ and } \sum_{i = 1}^{n} a_i =
+	\sum_{i	= 1}^{n}b_i = 0 \right \}
+\end{align*}
+
+\noindent
+Suppose $e_1, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_1^i,
+\ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
+i.e.~ $\Sigma$ is contained in the $\bq_{\geq 0}$ span of
+$e_1, \ldots, e_t$.
+
+Then, as a semigroup, $\Sigma$ is generated by
+elements whose first coordinate is less than $\sum_{i = 1}^{t}
+\pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be
+written in a canonical form $\lambda + \sum_{i = 1}^{t} w_i e_i$ 
+with $\lambda = \sum_{i = 1}^{r} s_i e_i$ with $0 \leq s_i < 1$, the
+first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$,
+and $w_1, \ldots, w_t \in \bz_{\geq 0}$.
+\end{prop}
+
+\begin{proof}
+By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
+{i = 1}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) := r - \lfloor r
+\rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 1}
+^{t} \fr(r_i)$. Whence, we can write $\sigma = \lambda + \sum_{i = 1}
+^{t} \lfloor r_i \rfloor e_i.$ Consequently, $\sigma$ lies in the
+$\bz_{\geq 0}$ span of $\lambda, e_1, \ldots, e_t$, which all have
+first coordinate less than $\sum_{i=1}^{t} r_i$. Ergo, $\Sigma$ is
+generated by elements whose first coordinate is less than
+$\sum_{i = 1}^{t} r_i$.
+\end{proof}
 
@@
 	\bk[\Sigma] =  \langle u^d z_0^{c_0} \cdots z_n^{c_n} : c_i \in
-\mathbb{Z}, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=0}^{n} \bida_i c_i =
+\bz, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=0}^{n} \bida_i c_i =
 \sum_{i=0}^{n} \bidb_i c_i \rangle. 
@@
 
+\begin{lem}
+\label{lem:composite-map}
+Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$. Suppose we have a
+surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i
+\mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
+Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$
+Then, define
+\begin{align*}
+	\Sigma = \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i = 0 \rangle. 
+\end{align*}
+In this case, we can factor $\phi$ as a composition of $\chi$ and $\psi$ defined by
+\[
+\begin{tikzcd}
+\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+x_i \arrow[mapsto]{r} & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \arrow[mapsto]{r} & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+\end{tikzcd}
+\]
+Assuming $\chi$ is surjective, the minimal degree of generation of $\ker \phi$
+is at most the maximum of the minimal degree of generation of $\ker \chi$ and
+the minimal degree of generation of $\ker \psi$.
+\end{lem}
+\begin{proof}
+First, we show there is an exact sequence
+\[
+\begin{tikzcd}
+0 \ar {r} & \ker \chi \ar{r}{\rho} & \ker \phi \ar {r}{\tau} & \ker \psi \ar r & 0.
+\end{tikzcd}
+\]
+To see this, note that $\rho$ is injective and $\tau$ is surjective\ because
+$\phi = \chi \circ \psi$. Additionally, $\tau \circ \rho = 0$ by definition of
+the kernel of $\chi$. Finally, if $a \in\ker \tau$, then by definition $\chi(a)
+= 0,$ so $a \in \im \rho$.
+
+This shows that lifts of generators of $\ker \psi$ together with images of
+generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
+\end{proof}
+
+\begin{lem}
+\label{lem:bound-ker-chi}
+Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
+extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$
+is generated in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
+\end{lem}
+\begin{proof}
+Since $e_1, \ldots, e_r$ are extremal rays, by Proposition
+~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
+in a canonical form $\lambda + \sum_{i=1}^{r}e_i$. Now, let $\lambda_0 :=
+0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be
+written in the form $\lambda_i = \sum_{i=1}^{r}r_i e_i$ with $0 \leq r_i < 1.$
+Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in
+the above canonical form, yielding a relation in degree at most $\deg \lambda_i
++ \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$
+Furthermore, these relations generate all relations, as one can apply a
+sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
+$\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Proposition
+~\ref{prop:cone-generation}.
+\end{proof}
 \begin{lem}
@@
 \ldots, c_n) \in \Sigma,$ as defined in Equation
-~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \mathbb{Z}^{n + 2}$
+~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \bz^{n + 2}$
 be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying
@@
 Lemma ~\ref{thm:hirz-generators-relations} in the case of $\hirz_1$ from the
-perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by
+perspective of adding a copy of $\bz$ to the Picard group, as induced by
 the blowup, might suggest a general method for blowups.

### 2015-08-07 surfaces-write-up/surface-write-up.tex
fixed almost all todos

@@
 \maketitle
-\todo{Standardize ``generation in degrees at most.''  \\
-Peter: Fixed, although sometimes we say ``generated in degrees less than'' which is meant to be distinct (less than rather than less then or equal to).}
 
@@
 \cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring}
-on canonical rings of stacky curves which provide bounds
-on rings of modular forms of Fuchsian groups through the study
-of particular $\bq$-divisors on curves.  \todo{I think this is too much 
-specificity about our result.  I think everything after ``stacky curves'' should be 
-eliminated, as it seems a little self-promoting.}
-
-The work in this paper may help calculate a presentation of certain rings of
+which provide tight bounds on generators and relations
+of canonical rings on arbitrary stacky curves.
+
+We expect the work in this paper will help calculate a presentation of certain rings of
 Hilbert 
@@
 Hilbert and Siegel modular forms with certain underlying spaces.
-\todo{Peter:  Hmm...
-this is very vague.
-It almost feels like a further question type statement, then a statement of why what we're doing matters.
-I guess the real issue, as we have sort of discussed, is that there are not any clear motivating reasons why one would actually use what we have done...
-Oh well}
 
@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$. Let
+Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
+Then notate
+\[\ell_i = \lcm_{j\ne i}(k_i).\]. 
+Let
 $f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_k.$ Let $D_i =
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_k$ 
+where $\alpha_i = \frac{c_i}{k_i}$.
+Then notate
+\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 
+Let $D_i =
 V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
@@
 \ssec{Notations and Conventions}
-\todo{Aaron: State other notations used here. I think there are few enough that we can just do it in a paragraph or two at the end of the introduction here.}
-\begin{convention}
 Notate a (Weil) $\bq$-divisor
@@
 \noindent
-where $\alpha_i \in \bq$ and $D_i \in \di X$ is an irreducible divisor. When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$.
-\end{convention}
-
+where $\alpha_i \in \bq$ and $D_i \in \di X$ is an integral codimension 1 closed subscheme of $X$.
+When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$.
+For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_i)$
+and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ Let $
+	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)$
+denote the canonical ring associated to the $\bq$ divisor $D$.
 \section{Canonical Rings on Projective Space}
@@
 In this section, we bound the degrees of generators and relations for divisors
-on $\bp^m$, for all $m \geq 1$. The $\bp^1$ case restricts to the results of
-\cite{dorney:canonical}.
-
-\ssec{Preliminaries on Projective Space}
+on $\bp^m$, for all $m \geq 1$ in Theorem ~\ref{thm:proj-effective-intro}. 
+The $\bp^1$ case restricts to the results of
+\cite{dorney:canonical}. We also give an explicit description of the
+generators of the canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}
 
@@
 \sco_{\bp^m})$ of degree 1.
+
+\ssec{Preliminaries on Projective Space}
+Before bounding the degree of generation and relations of
+canonical rings on projective space, we first
+describe a particular choice of basis for $R_D$ as a $\bk$ bector space.
 
@@
 The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying \todo{Peter: Why
-do we include this $u$?  IN the later sections, I don't use this notation and
+do we include this $u$?  In the later sections, I don't use this notation and
 we should standardize.
@@
 }
+
 \begin{align}
@@
 
-\todo{Aaron: make a remark as to why these bounds are tight}
 \begin{convention}
@@
 
+Next, we define an ordering on the vectors, which will allow us
+to present a system of relations for $R_D$. Although it is not
+stated explicitly later, in the case that $D = \alpha_1 D_1$, the relations in Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to this ordering.
+
 \begin{defn}
@@
 \end{defn}
+
+We are now ready to give an inductive method for computing
+the generators and relations of $R_D$ in terms of $R_{D'}$, 
+in the case that $D' = R_D + \alpha H$ for $H$ a hyperplane.
+The statement and proofs are natural generalizations of
+\cite[Theorem 6]{dorney:canonical}.
 
@@
 \end{flalign*}
-\todo{Peter: Can you clarify when these two cases occur: i.e. does the first 
-only occur if $j = h_{i,j}+1$; otherwise, in cases when $i< h_{i,j} < h_{i,j} + 1< 
-j$, do we get relations of both forms? \\
-Robin: It purely depends on whether the product $F_i^{\vec{v}} F_j^{\vec{w}} 
-$ happens to lie on the ray given by $\frac{c_{h_{i, j}}}{d_{h_{i, j}}}$ which is 
-not clearly determined by $i$ or $j$ from what I can see... Unless you see 
-something else. Only one relation exists for each $(i, j)$ and it is exactly one 
-of the two forms. I figured that the ``either'' made that clear, no?}
 	\item For each $(i, j)$ with
@@
 and the following proof goes through otherwise unchanged.
-\todo{Aaron: Has anyone actually gone through the proof
-	for general effective divisors carefully, to make
-sure the above claim is correct?}
+
 We will first check that $F^{\vec v}_i$ determine a system of minimal
@@
 
+The above Theorem ~\ref{thm:proj-one-point} allows us to inductively
+compute presentations of effective divisors which are supported on
+hyperplanes, but for $m \geq 2$, there are hypersurfaces which
+are not unions of hyperplanes. We now adress this general case, giving an inductive presentation of canonical rings of effective divisors, and a tight bound on the degrees of their generators and
+relations.
+
 \restateeffective*
@@
 \label{eg:hyperplane}
+In this example,we show that the naive generalization of
+~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
+$\sum_{i=0}^{n}\ell_i$ cannot possibly hold. The reason for this is
+that the divisors may ``be contained in a hyperplane,'' i.e.~ be
+expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
+
 Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0),
@@
 
-\begin{rem}\todo{Peter: maybe move this out of a remark and just say it with the previous example?  As it stands, the previous example is a little unclear as to what its purpose is...}
+\begin{rem}
 \label{rem:ghost-motivation}
-Example ~\ref{eg:hyperplane} shows that the naive generalization of
-~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
-$\sum_{i=0}^{n}\ell_i$ cannot possibly hold. The reason for this is
-that the divisors may ``be contained in a hyperplane,'' i.e.~ be
-expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
-This problem can easily be circumvented by adding in ``ghost
+The problem that a divisor may be contained in a hyperplane, 
+as illustrated in Example ~\ref{eg:hyperplane}, can easily be circumvented by adding in ``ghost
 points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
@@
 x_3^2)$. In degree $355216 = 5 \cdot 7 \cdot 17 \cdot 596$, this has dimension
-$10$. 
-\todo{Clarify what this example means by the lattice approach 
-\\
-Peter: Maybe we should put this after the ensuing proofs.
-That way, rather than saying the Lattice Approach, we could say that this example illustrates how the prveious method requires us to add ghost points (and is false otherwise).}
-However, we possibly use the lattice approach, as all lower degrees only have
-dimension 1. In fact, we may construct similar examples using any set of degree
+$6$.
+However,  approach, as all lower degrees only have
+dimension at most 1. Therefore, we cannot hope to bound the degree
+of generation of $R_D$ as a linear combination of $\ell_i$,
+in analogy to ~\ref[Theorem 8]{dorney:canonical}
+unless we require that $D$ includes ghost points. That is, unless
+$D_0,\ldots D_m$ are taken to be hyperplanes spanning $\bp^m$.
+In fact, we may construct similar examples using any set of degree
 $n$ divisor with very small degree.
 \end{example}
-\todo{construct class of additional examples}
-\todo{Throughout this section, include some more transition, explaining which lemmas are general and will be used again for hirzebruch surfaces and which lemmas will be used only for $\bp^m$.}
+
 Having justified the necessity of adding ghost points, we proceed to bound the
-number of generators and relations.
+number of generators and relations of arbitrary $\bq$-divisors in 
+projective space. We bound the generators in Lemma ~\ref{lem:proj-
+generators}, and we use Lemmas ~\ref{lem:composite-map}, ~\ref{lem:bound-ker-chi}, and ~\ref{lem:proj-relations-psi} to bound the 
+degree of relations in the proof of Theorem ~\ref{thm:proj-generators-relations}.
+Note that Proposition ~\ref{prop:cone-generation}, Lemma ~\ref{lem:composite-map}, and Lemma ~\ref{lem:bound-ker-chi} are quite
+general and will be used in Section ~\ref{sec:hirz} to bound the 
+degree of generators and relations on Hirzebruch surfaces.
 
@@
 
-We now present some preliminary results which will be used to prove Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} in Sections \ref{sec:proj} and \ref{sec:hirz} respectively.
-
 \begin{prop}
@@
 
-\begin{defn}\label{def:ell_i}
-Let $D = \sum_{i=0}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate
-\[\ell_i = \lcm_{j\ne i}(k_i).\]
-\end{defn}
+Using Proposition ~\ref{prop:cone generation}, in order to bound
+the degree of generation of $R_D$, we only need bound
+the degrees of generators of an associated cone. We now carry out
+this strategy.
 
@@
 \bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let $\phi$ be the
-surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through the
+surjection $k[x_1, \ldots x_r] \to R_D$.
+For the remainder of the section, we aim to bound the degree of relations
+of $R_D$, or equivalently, the degree of generation of $\ker \phi$.
+  We can factor $\phi$ through the
 semigroup ring 
@@
 
-By Lemma ~\ref{lem:bound-ker-chi}, we can bound the degree of generation of
-$\ker \chi $ and we next calculate the degree of generation of $\ker \psi$:
+We next show in Lemma ~\ref{lem:composite-map} that the degree of 
+generators for $\ker \phi$, which is the same as the degree of relations
+of $R_D$ can be bounded in terms of the degree of generators for
+$\ker \chi$ and for $\ker \psi$.
+In Lemma ~\ref{lem:bound-ker-chi}, we bound the degree of generation of
+$\ker \chi $ and we then calculate the degree of generation of $\ker \psi$ in Lemma ~\ref{lem:proj-relations-psi}
 
@@
 
-\begin{defn}\label{def:ell_ij}
-Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate
-\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\]
-\end{defn}
-
 \begin{lem}
@@
 \end{equation}
-Define
-\begin{equation}\label{eqn:defn-lambda}
-	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
- \end{equation}
+
 Note that
@@
 where $\rho$ is as in Equation \ref{eqn:def-sigma}.
+
 \todo{Aaron: Is one of these terms corresponding to $E$ and the other to $\lambda$? If so, can you say which?\\
-Peter: No, one corresponds to $r_j$ and one to the fractional part of $s_j - r_j$.}
+Peter: No, one corresponds to $r_j$ and one to the fractional part of $s_j - r_j$.
+
+Aaron: Ok, can you give a 1-2 sentence explanation then, just saying
+which which corresponds to which?
+}
+
+Define
+\begin{equation}\label{eqn:defn-lambda}
+	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
+ \end{equation}
 
@@
 
-Let $F = \Psi(E) \in R_D$
-\todo{Aaron: Didn't we agree you would write these as $\psi(E)$ or something like that? 
-\\
-Peter: Okay, I'm still a little unhappy with with the identification of lattice
-points in $\Sigma$ with monomials (since $\Psi$ maps monomials in a polynomial
-ring to monomials in $R_D$), but I made the change
-Aaron: Thanks. If you're unhappy, you can always just define the map $\iota:\Sigma \rightarrow \bk[\Sigma]$ and say $F_\mu = \iota \circ \psi (E_\mu)$}
- and $F_\mu = \psi(E_\mu)
+Let $F = \Psi(E) \in R_D$ and $F_\mu = \psi(E_\mu)
 \in R_D$ for each $\mu \in M_i$.  

### 2015-08-07 surfaces-write-up/surface-write-up.tex
added description for degree of $

@@
 \begin{equation}\label{eqn:hirz-E-translation}
-	E := \sum_{j\in \Te} (s_j - \lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}.
+E := 	\sum_{j\in \Te} (s_j - \lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}
 \end{equation}
@@
 where $\rho$ is as in Equation \ref{eqn:def-sigma}.
+In this sum the $\rho$ term corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_{j,k} - r_{j,k}$'s, whereas the second term corresponds to the sums of $r_j$'s and $r_{j,k}$'s (noting that in equation \ref{eqn:hirz-E-translation} $s_j - \lfloor s_j - r_j \rfloor$ equals $r_j$ plus the fractional part of $s_j - r_j$, and a similar statement holds for $s_{j,k} - \lfloor s_{j,k} - r_{j,k}$).
 

### 2015-08-07 surfaces-write-up/surface-write-up.tex
eliminated todos/moved to front

@@
 
+\todo{Make sure to include $u^d$ everywhere necessary}
+\todo{Make sure to index starting from 0 in $\bp^m$ section}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying \todo{Peter: Why
-do we include this $u$?  In the later sections, I don't use this notation and
-we should standardize.
-
-Aaron: Isn't it necessary to distinguish the functions? For instance, we could consider $f_0$ either as a function in degree 1 or 2 for $D = \frac{1}{2}x_0$, and we need
-$u^d$ to distinguish which degree it lives in.
-I think we will need to go through and include the $d$ throughout.
-Do you think there's a way to avoid including the $d$?
-}
+The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying
 
@@
 c_i = -\lfloor d\alpha_i \rfloor && \text{ for } && i > m
-\end{align}\todo{Peter: Should be for $i> m+1$ right?
-Looking below I see an $f_0$, where as above $f_i$ ranges 1 to $n$.
-We should choose whether or not 0 is included in the indexing and fix the section to match that convention.
-
-Aaron: I tried to fix it at $0$ everywhere. If probably missed a few places, so keep your eyes peeled.
-}
+\end{align}
 
@@
 %Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
-%proof, and should really be $e_{ij}$, as I was explaining in my previous todo.
+%proof, and should really be $e_{ij}$, as I was explaining in my previous note.
 %Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
@@
 \rfloor$
-\todo{Aaron: Am I misremembering, or did we agree on the phone that you would put $i$ subscripts on all the things that depend on $i$?
-If not, weren't you at least going to say somewhere which things depend on $i$?
-\\
-Peter: I still don't entirely agree that explaining the dependency is
-important.  What I mean by this is that the proof fixes $i, \sigma,$ etc. and
-proves the desired result.  Proving it for each possible choice of course
-proves the general result; however, it doesn't seem important to me whether or
-not the intermediate variables are the same in the proof for $i'$ and $\sigma'$
-than for $i$ and $\sigma$.  Either way the proof is valid.  This is why I have
-been somewhat resistant (sorry if annoyingly so...)to adding them in.
-
-On a side note, in some cases actually writing them in would be cumbersome,
-e.g. replacing $s_{j,k}$ with $s_{j,k,\sigma}$ (since there is one choice of
-$s_{j,k}$ for every $\sigma$.
-
-If you want, can you tell me exactly which variables would be helpful in
-understanding the proof to know their dependencies?
-
-Aaron: Ok, I'll stop bugging you about it. I just thought we
-should add it because I didn't understand that it depended
-on $i$ when I read it. Maybe we can see what David
-has to say about it when he reads it?
-Also, I don't see why calling $s_{j,k}$ by $s_{j,k,\sigma}$ is cumbersome,
-that seems fine to me.
-}
 
@@
 In this sum the $\rho$ term corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_{j,k} - r_{j,k}$'s, whereas the second term corresponds to the sums of $r_j$'s and $r_{j,k}$'s (noting that in equation \ref{eqn:hirz-E-translation} $s_j - \lfloor s_j - r_j \rfloor$ equals $r_j$ plus the fractional part of $s_j - r_j$, and a similar statement holds for $s_{j,k} - \lfloor s_{j,k} - r_{j,k}$).
-
-\todo{Aaron: Is one of these terms corresponding to $E$ and the other to $\lambda$? If so, can you say which?\\
-Peter: No, one corresponds to $r_j$ and one to the fractional part of $s_j - r_j$.
-
-Aaron: Ok, can you give a 1-2 sentence explanation then, just saying
-which which corresponds to which?
-}
 

### 2015-08-07 surfaces-write-up/surface-write-up.tex
edited all but big theorem in effective pm

@@
 Then notate
-\[\ell_i = \lcm_{j\ne i}(k_i).\]. 
+\[\ell_i = \lcm_{j\ne i}(k_i).\] 
 Let
@@
 In this subsection, we restrict attention to the case of effective
-fractional divisors $D \in \bq \otimes \di \bp^m$. We give an explicit presentation of the canonical rings when $D$ is an effective
+fractional divisors $D \in \bq \otimes \di \bp^m$. We give an explicit presentation of the canonical ring when $D$ is an effective
 divisor.
@@
 \[
-	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
+	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}.
 \]
@@
 \noindent
-be the set of vectors of degree $c_i$.
 \end{defn}
 
-Next, we define an ordering on the vectors, which will allow us
-to present a system of relations for $R_D$. Although it is not
-stated explicitly later, in the case that $D = \alpha_1 D_1$, the relations in Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to this ordering.
+Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
+stated explicitly later, in the case that $D = \alpha_1 D_1$ is supported on a single hypersurface, the relations in Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to this ordering.
 
@@
 and $j \in \{0,\ldots, m\}$ be the smallest index such that $w_j$ is
-nonzero. Define $\vec{v} \prec \vec{w}$ if $i \leq j$.
+nonzero. Define a partial ordering on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
 \end{defn}
@@
 We are now ready to give an inductive method for computing
-the generators and relations of $R_D$ in terms of $R_{D'}$, 
+the generators and relations of $R_D$ in terms of $R_{D'}$ 
 in the case that $D' = R_D + \alpha H$ for $H$ a hyperplane.
@@
 
-The above Theorem ~\ref{thm:proj-one-point} allows us to inductively
+Theorem ~\ref{thm:proj-one-point} gives an inductive procedure to
 compute presentations of effective divisors which are supported on
-hyperplanes, but for $m \geq 2$, there are hypersurfaces which
+hyperplanes. However, for $m \geq 2$, there are hypersurfaces which
 are not unions of hyperplanes. We now adress this general case, giving an inductive presentation of canonical rings of effective divisors, and a tight bound on the degrees of their generators and
@@
 Let $D' = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bq\di \bp^m$, 
-for which the theorem holds. It suffices to show
-the theorem holds for $D \in \di \bq \otimes_\bq \bp^m$, where $D = D' + C$ for some
+and assume the theorem holds for $D'$. It suffices to show
+the theorem holds for $D \in \di \bq \otimes_\bq \bp^m$, where $D = D' + \alpha C$ for some
 degree $\pdeg$ hypersurface $C$.
@@
 To complete the theorem, we reduce the case that $C$ is a general hypersurface
-to the case that $C$ is a hyperplane, essentially by using the Veronese embedding.
-
-If $C$ is of degree $\pdeg$, then we construct the veronese embedding
+to the case that $C$ is a hyperplane, by using the Veronese embedding.
+
+If $C$ is of degree $\pdeg$, consider the veronese embedding
 $\nu_\pdeg^m: \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
@@
 a hyperplane in $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$ with $\nu_\pdeg^m(\bp^m)$.
-Now, note that the ring $H^0(\bp^m, C)$ is isomorphic to the
-$\pdeg$ veronese subring of $R_{V(x_0)}$, and so
+Now, note that the ring $R_{\alpha C}$ is isomorphic to the
+$\pdeg$ veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} H^0(\bp^m, d \alpha V(x_0))$ and so
 the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
-restricting to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
+restricted to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
 Therefore, we can bound the degree of generators and relations of

### 2015-08-07 surfaces-write-up/surface-write-up.tex
aaron's second round edits through 2.2

@@
 \begin{document}
-
 \begin{abstract}
@@
 	on projective spaces of all dimensions
-	and Hirzebruch surfaces.
+	and Hirzebruch surfaces. We also give an explicit presentation 		and tight bounds on the
+	generators and relations of the canonical ring of an effective
+	stacky divisor on projective spaces of all dimensions.
 \end{abstract}
@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} H^0(X, \lfloor dD \rfloor)$.
+\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
+track of indexing.
 We study the generators and relations of canonical
 rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
-When $D$ is a general $\bq$-divisor on any $\bp^m$ or on any Hirzebruch Surface
+When $D$ is a general $\bq$-divisor on $\bp^m$ or
 $\hirz_m$, we give bounds on the generators and relations of
@@
 study also has connections to the papers by Voight--Zureick-Brown 
-\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring}
+\cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring},
 which provide tight bounds on generators and relations
 of canonical rings on arbitrary stacky curves.
+
+Another closely related topic is the Hassett-Keel program 
+initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
+\begin{align*}
+	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
+	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
+	\alpha\delta \rfloor  \right) 
+\end{align*}
+in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
+appear when considering the canonical ring of surfaces of Kodaira dimension 1.
+A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
+barthHPV:compactComplexSurfaces}, and
+the canonical rings of elliptic surfaces most naturally described in the setting of
+$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
 
@@
 
-Another closely related topic is the Hassett-Keel program 
-initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
-\begin{align*}
-	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0}H^0 \left(
-	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
-	\alpha\delta \rfloor  \right) 
-\end{align*}
-in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
-appear when considering the canonical ring of surfaces of Kodaira dimension 1.
-A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
-barthHPV:compactComplexSurfaces}, and
-their canonical ring are most naturally described in the setting of
-$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
-
-\ssec{Main Results}
+\ssec{Main Results and Outline}
 
@@
 the degree of generators and relations of
-stacky canoincal rings on $\bp^m$:
+stacky canonical rings on $\bp^m$:
 \begin{restatable}{thm}{restateeffective}
 \label{thm:proj-effective-intro}
-Let $D = \sum_{i = 0}^{n} \alpha_i C_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
-\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
-$\bp^m$, be an effective divisor on $\bp^m$.
+Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
+\frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i$ be a hypersurface of
+$\bp^m$.
 
@@
 \[
-	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
-\]
-
-\noindent
-is generated in degrees at most $\max_{1 \leq i \leq n}{q_i}$ with
-relations generated in degrees at most $2 \max_{1 \leq i \leq n}{q_i}$
+	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
+\]
+
+\noindent
+is generated in degrees at most $\max_{1 \leq i \leq n}{k_i}$ with
+relations generated in degrees at most $2 \max_{1 \leq i \leq n}{k_i}$
 \end{restatable}
@@
 Let
-$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
-$D_i = V(f_i)$ for all $i$; suppose $\deg(f_i) = a_i$. 
+$f_0, \ldots, f_n$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
+$D_i = V(f_i)$ for all $i$, $\deg(f_i) = a_i,$ and $f_0,\ldots, f_m$ are independent linear polynomials. 
 Then $R_D$ is generated in degrees at most 
@@
 For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_i)$
-and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ Let $
-	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)$
-denote the canonical ring associated to the $\bq$ divisor $D$.
+and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
+\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
+\lfloor \alpha_i \rfloor P_i$. Let $
+	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
+denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
+is a graded ring, we denote the $d$th graded component of $R$ by $R_d$.
 \section{Canonical Rings on Projective Space}
@@
 Cartier divisors such that $D_i = V(f_i)$.
-We shall further assume that (after reordering) $f_0,\ldots, f_{m}$ form a
+We shall further assume that (possibly after reordering) $f_0,\ldots, f_{m}$ form a
 basis for degree one rational functions on $\bp^m$.
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i}$ satisfying
+The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i} \in (R_D)_d$ satisfying
 
@@
 independent. This follows from the assumption that $f_0,\ldots f_n$ form a
-basis of degree 1 rational functions, and so degree $\lfloor d \deg D \rfloor $
-monomials in $f_0,\ldots, f_n$ form a basis of degree $\lfloor d \deg D \rfloor
-$ rational functions.
+basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$ of degree degree $\lfloor d \deg D \rfloor $
+form a basis of degree $\lfloor d \deg D \rfloor$ rational functions.
 \end{proof}
@@
 \[
-	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
+	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
 \]
@@
 with $\deg \vec v = c_i$. Furthermore, it has
-relations generated by the following two forms:
+relations generated by the following two classes of elements.
 \begin{enumerate}
@@
 $\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
-(see Definition ~\ref{defn:lower-approximation}).
+(see Definition ~\ref{defn:lower-approximation}). Therefore, none of the $F_i^{\vec v}$ are redundant.
 
@@
 of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
-some $h \in \{0, \ldots, r\}$. Let $(\beta, \gamma) = \kappa_1
+some $h \in \{0, \ldots, r\}$. A similar strategy works in the case $m > 1$. Let $(\beta, \gamma) = \kappa_1
 (d_h, c_h) + \kappa_2 (d_{h + 1}, c_{h + 1})$ for $\kappa_1, \kappa_2 \in
@@
 $(d_{h_{i, j} + 1}, c_{h_{i, j} + 1})$. Furthermore,
-$h_{i, j} \neq i$ and $h_{i, j} \neq j - 1$ by the proof of the analogous 
-statement in $bp^1$ given by O'Dorney
-\cite[Theorem 6]{dorney:canonical}. This gives the relations
+$h_{i, j} \neq i$ and $h_{i, j} \neq j - 1$
+as follows from an analogous proof to that given by O'Dorney
+\cite[Theorem 6]{dorney:canonical} for the case of
+$\bp^1$. This gives the relations
 $G_{i, j}^{\vec{v}, \vec{w}}$.
 
-The application of $G_{i, j}^{\vec{v}, \vec{w}}$ can be used
+One can use the relations $G_{i, j}^{\vec{v}, \vec{w}}$
 to transform any monomial in the $F_i^{\vec{v}}$'s involving
@@
 hyperplanes cannot be bounded so tightly. The two-point
-$\bp^1$ result leverages the fact that $\bp^1$ has two
-independent coordinates.
+$\bp^1$ result leverages the fact that $\bp^1$ has precisely two
+independent coordinates, so that two distinct integral subschemes
+cannot be equations of only $m$ of the $m+1$ coordinates.
 \end{rem}
@@
 Now, note that the ring $R_{\alpha C}$ is isomorphic to the
-$\pdeg$ veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} H^0(\bp^m, d \alpha V(x_0))$ and so
+$\pdeg$ veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0))$ and so
 the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$

### 2015-08-07 surfaces-write-up/surface-write-up.tex
undo Peter's introduction of a strange typographical error
edits to conclusions

@@
 
-\section{Conclusion}
+\section{Further Questions}
 \label{sec:conc}
-This paper extends the work of O'Dorney \cite{dorney:canonical} on $\bp^1$ to
-$\bp^m$ and Hirzebruch Surfaces, bounding the degrees of generation and
-relations of canonical rings of arbitrary divisors $D$.  The methods for
-deducing bounds on generators and relations of $\hirz_k$ applied similar
-methods to that of O'Dorney's for $\bp^1$.
-
-We can view $\hirz_0$ as $\bp^1\times \bp^1$ and more generally $\hirz_k$ as a
-$\bp^1$ bundle over $\bp^1$.  One might hope that similar ideas could be
-generalized to all bundles.  Specifically:
-\begin{question}
-\label{qn:general-product-bundle}
-Suppose $X$ and $Y$ are schemes.  Let $D$ be a divisor on $X\times Y$ or more
-generally on an $X$ bundles over $Y$.  Can we describe $D$ in terms of divisors
-$D_1, \ldots D_n$ on $X$ and $D_1', \ldots d_n'$ on $Y$.  Furthermore, can we
-find generators for $R_D$ and its ideal of relations using those of the
-$R_{D_i}$'s and $R_{D_j'}$'s?
-\end{question}
-
-An immediate obstruction to this is the fact that we critically used the fact
-that $\hirz_k$ has well-defined bi-degrees.  Unfortunately, in general $\Pic(X
-\times Y) \not \cong \Pic(X) \times \Pic(Y)$.
-
-Alternatively, we can view $\hirz_1$ as $\bp^2$ blown up at a point.  This
-suggests the following question:
-\begin{question}
-\label{qn:general-blowup}
-Let $X$ be a scheme.  Let $X'$ be the blowup of $X$ at a point $P$ with a
-divisor $D$.  First, is there a way to express $D$ in terms of divisors $D_1,
-\ldots, D_n$ on $X$?  Furthermore, is there a way to describe generators and
-relations of $R_D$ in terms of those of $R_{D_i}$ for all $i$.
-\end{question}
-
-Fortunately, the Picard group of $X$ blown up at a point is the same as that of
-$X$ times an additional copy of $\bz$.  Perhaps analyzing the argument from
-Lemma ~\ref{thm:hirz-generators-relations} in the case of $\hirz_1$ from the
-perspective of adding a copy of $\bz$ to the Picard group, as induced by
-the blowup, might suggest a general method for blowups.
-
-Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for
-all rational surfaces, via the minimal model program for surfaces.  One might then hope to further extend these results to all minimal surfaces:
+In this section, we briefly state some further questions.
+
+Recall that every minimal rational surface is either isomorphic to
+$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$. By Theorems
+~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations
+of arbitrary canonical rings on any minimal rational surface. A
+natural extension of our results is the following.
 \begin{question}
@@
 Can we describe generators and relations of $R_D$ for $D$ a divisor on an
-arbitrary minimal surface $X$?
+arbitrary rational surface $X$?
 \end{question}
+
+By the classification of rational surfaces, every rational surface
+can be obtained from a minimal rational surface by a sequence of blow-ups \todo{Aaron: Include reference}. Therefore, to answer Question \ref{qn:general-minimal-surface} affirmatively, it suffices
+to bound the degree of generators and relations of the 
+canonical ring of a divisor on a blow-up of that surface in terms of the canonical ring of a divisor on that surface.
+
+Another direction to generalize the work in this paper
+would be to try to express canonical rings of $\bq$-divisors on
+$X \times Y$ in terms of $X$ and $Y$. In this paper,
+we bounded the degrees of presentations on canonical rings on $\bp^1 \times \bp^1 \cong \hirz_0$.
+Perhaps similar techniques can be used to bound
+degrees of presentaitons on canonical rings on $(\bp^1)^k$ or
+more generally on $(\bp^1)^{i_1} \times \cdots (\bp^k)^{i_k}.$
+One might further try to generalize this to bounding degrees of presentations on bundles over $\bp^m$ or on more general
+products of schemes.
 

### 2015-08-07 surfaces-write-up/surface-write-up.tex
aaron second round edits up to generators of pm

@@
 When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$.
+The degree of $D$ is by definition $\deg D = \sum_{i=1}^{n}\alpha_i$.
 For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_i)$
@@
 
-We now offer bounds on generators and relations of $R_D$ for a general divisor $D$ on $\bp^m$.
+We now offer bounds on generators and relations of $R_D$ for a general $\bq$-divisor $D \in \bq \otimes_\bq \di \bp^m$.
 
@@
 ~\ref{thm:proj-generators-relations} bounding the number of generators and
-relations of $R_D$. Before doing so, we justify the assumption
-~\eqref{eqn:pm-basis-assumption} through a several convincing examples.
+relations of $R_D$. Before doing so, we justify the importance of assumption
+~\eqref{eqn:pm-basis-assumption} with several illustrative examples.
 
@@
 $\sum_{i=0}^{n}\ell_i$ cannot possibly hold. The reason for this is
-that the divisors may ``be contained in a hyperplane,'' i.e.~ be
+that the divisors may be
 expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
 
-Suppose $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0),
+Concretely, take $D = \frac{1}{2}H_0 - \frac{1}{3}H_1$ where $H_0 = V(x_0),
 H_1 = V(x_1)$ are two coordinate hyperplanes in $\bp^2$. Then, $R_D$
@@
 \frac{x_1}{x_0}, u^3 \frac{x_1}{x_0}.$ In fact, for all degrees
-less than $5$ the elements of $R_D$ can all be expressed as
+less than $5$, the elements of $R_D$ can all be expressed as
 rational functions in $x_0, x_1$. However, in degree $6$, there is
-the rational function $\frac{x_1^2 x_2}{x_0^3}$. Since this
+$u^6 \frac{x_1^2 x_2}{x_0^3}$. Since this
 involves $x_2$, it must be a generator.
@@
 where all $f_i$ can be written as a polynomial function in $x_0,
-\ldots, x_{m-1},$ we have $R_D$ always has a generator in degree
+\ldots, x_{m-1},$ it follows that $R_D$ always has a generator in degree
 $\lcm(\den_i \cdot \bida_i)$.
@@
 
-\begin{rem}
-\label{rem:ghost-motivation}
-The problem that a divisor may be contained in a hyperplane, 
+The problem that a divisor may be
+expressible as functions in $m$ of the $m+1$ variables on $\bp^m$, 
 as illustrated in Example ~\ref{eg:hyperplane}, can easily be circumvented by adding in ``ghost
@@
 $D$, and reorder so that if $D = \sum_{i=0}^{n}\alpha_i V(f_i)$,
-then $f_0, \ldots, f_m$ cut out linearly independent
-hyperplanes in $\bp^m$.
+then $f_0, \ldots, f_m$ are independent linear functions in
+$x_0,\ldots, x_m$.
 
@@
 necessary to add ghost points, even when the irreducible components
-of a divisor are not all contained in a hyperplane.
-\end{rem}
+of a divisor are not all
+expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
 
@@
 of generation of $R_D$ as a linear combination of $\ell_i$,
-in analogy to ~\ref[Theorem 8]{dorney:canonical}
+in analogy to \cite[Theorem 8]{dorney:canonical}
 unless we require that $D$ includes ghost points. That is, unless
-$D_0,\ldots D_m$ are taken to be hyperplanes spanning $\bp^m$.
-In fact, we may construct similar examples using any set of degree
-$n$ divisor with very small degree.
+$D_0,\ldots D_m$ are taken to be linearly independent hyperplanes.
 \end{example}
@@
 number of generators and relations of arbitrary $\bq$-divisors in 
-projective space. We bound the generators in Lemma ~\ref{lem:proj-
-generators}, and we use Lemmas ~\ref{lem:composite-map}, ~\ref{lem:bound-ker-chi}, and ~\ref{lem:proj-relations-psi} to bound the 
+projective space. We bound the generators in Lemma ~\ref{lem:proj-generators}, and we use Lemmas ~\ref{lem:composite-map}, ~\ref{lem:bound-ker-chi}, and ~\ref{lem:proj-relations-psi} to bound the 
 degree of relations in the proof of Theorem ~\ref{thm:proj-generators-relations}.
 Note that Proposition ~\ref{prop:cone-generation}, Lemma ~\ref{lem:composite-map}, and Lemma ~\ref{lem:bound-ker-chi} are quite
-general and will be used in Section ~\ref{sec:hirz} to bound the 
+general and will also be used in Section ~\ref{sec:hirz} to bound the 
 degree of generators and relations on Hirzebruch surfaces.
@@
 \noindent
-Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
+Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the best lower approximations of $\alpha = \frac{14}{5}$.
 \end{rem}
@@
 \pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be
-written in a canonical form $\lambda + \sum_{i = 1}^{t} w_i e_i$ 
-with $\lambda = \sum_{i = 1}^{r} s_i e_i$ with $0 \leq s_i < 1$, the
-first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$,
-and $w_1, \ldots, w_t \in \bz_{\geq 0}$.
+written in a canonical form \[\sigma = \lambda + \sum_{i = 1}^{t} w_i e_i\]
+with $w_1, \ldots, w_t \in \bz_{\geq 0}$,
+$0 \leq s_i < 1$, and $\lambda = \sum_{i = 1}^{r} s_i e_i$ 
+so that the
+first coordinate of $\lambda$ is less than $\sum_{i=1}^{t}\pdeg_i$.
 \end{prop}
@@
 
-Using Proposition ~\ref{prop:cone generation}, in order to bound
+By Proposition ~\ref{prop:cone generation}, in order to bound
 the degree of generation of $R_D$, we only need bound
-the degrees of generators of an associated cone. We now carry out
+the degrees of extremal rays of an associated cone. We now carry out
 this strategy.
@@
 \begin{lem} \label{lem:proj-generators}
-$R_D$ is generated in degrees at most $\sum_{i=0}^n \ell_i a_i.$
+Let $D = \sum_{i=1}^{n} \alpha_i D_i \in \bq \otimes \di \bp^m,$ where
+$\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
+$\ell_i = \lcm_{j \neq i} (k_i)$. Then, $R_D$ is generated in degrees at most $\sum_{i=0}^n \ell_i \bida_i.$
 
@@
 \[
-	\sum_{i=0}^n \ell_i a_i.
+	\sum_{i=0}^n \ell_i \bida_i.
 \]
@@
 \begin{equation}\label{eqn:hirz-E-translation}
-E := 	\sum_{j\in \Te} (s_j - \lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}
+	E := \sum_{j\in \Te} (s_j - \lfloor s_j - r_j \rfloor) e_j + \sum_{\substack{j \in 
+	\Tp \\ k \in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k} \rfloor) e_{j,k}.
 \end{equation}

### 2015-08-08 surfaces-write-up/surface-write-up.tex
cite eisenbud--harris on min surfaces, add eisenbud--harris to bib

@@
 Recall that every minimal rational surface is either isomorphic to
-$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$. By Theorems
+$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$ \todo{also cite 
+eisenbud--harris here?}. By Theorems
 ~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations
@@
 
-By the classification of rational surfaces, every rational surface
-can be obtained from a minimal rational surface by a sequence of blow-ups \todo{Aaron: Include reference}. Therefore, to answer Question \ref{qn:general-minimal-surface} affirmatively, it suffices
+Every rational surface can be obtained from a minimal rational surface by a 
+sequence of blow-ups \cite{eisenbud-harris:minimal}. Therefore, to answer 
+Question \ref{qn:general-minimal-surface} affirmatively, it suffices
 to bound the degree of generators and relations of the 

### 2015-08-08 surfaces-write-up/surface-write-up.tex
added u-powers

@@
 
-By Proposition ~\ref{prop:cone generation}, in order to bound
+By Proposition ~\ref{prop:cone-generation}, in order to bound
 the degree of generation of $R_D$, we only need bound
@@
 \label{eqn:epsilon-def-proj}
-	\epsilon_i = \prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
+	\epsilon_i = u^{\ell_i a_i}\prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
 \end{equation}
@@
 \label{eqn:relations-psi-proj}
-	(z_i - \beta_i)\prod_{j=0}^n {z_j}^{c_{j}}
+	u^d(z_i - \beta_i)\prod_{j=0}^n {z_j}^{c_{j}}
 \end{equation}
@@
 \[
-	g = \prod_{i = 1}^n {f_i}^{c_i}
-\]
-
-\noindent
-for some $c_i \ge - \alpha_i d$ such that $\sum_{i=1}^n c_i \bida_i = 0$
-and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $g$ as an element of the
+	g = u^d \prod_{i = 1}^n {f_i}^{c_i}
+\]
+
+\noindent
+for some $c_i \ge - \alpha_i d$ for all $i$ such that $\sum_{i=1}^n c_i \bida_i = 0$
+and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $g$ as an element $(d, c_1, \ldots, c_n)$ of the
 lattice 
 \begin{align*}
-	\Sigma = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge - d
-\alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i \bida_i = \sum_{i =
-1}^n c_i \bidb_i = 0 \}.	
+	\Sigma = \{ (d', c_1', \ldots, c_n') \in \bz_{\geq 0}^{n+1} : c_i' \ge - d
+\alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i' \bida_i = \sum_{i =
+1}^n c_i' \bidb_i = 0 \}.	
 \end{align*}
@@
 \label{eqn:hirz-relations-psi}
-	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
+	u^d(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
 \end{equation}
@@
 \noindent
-lying in degree $d \in \mathbb{N}$
+lying in some degree $d \in \mathbb{N}$
 with $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
@@
 
-Consider a relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ with corresponding lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
+Consider a relation $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ with corresponding lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
 Then we can write $\sigma$ as a sum of $s_j e_j$'s for $j\in
@@
 
-For $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$ to be a relation, it must, in particular, be an element of $R_D$.
+For $u^d (f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$ to be a relation, it must, in particular, be an element of $R_D$.
 This implies that $s_i\kappa_i\ge 1$, $\sum_{j\in \Tm} s_{i,j}\kappa_{i,j}' \ge 1$, and $\sum_{j\in \Tp} s_{i,j}\kappa_{j,i}'' \ge 1$ if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$ respectively.

### 2015-08-08 surfaces-write-up/surface-write-up.tex
edited through section 2

@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
+Let $\bp^m$ have projective coordinates $x_0,\ldots, x_m$. Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
 Then notate
@@
 $f_0, \ldots, f_n$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
-$D_i = V(f_i)$ for all $i$, $\deg(f_i) = a_i,$ and $f_0,\ldots, f_m$ are independent linear polynomials. 
+$D_i = V(f_i)$ for all $i$, $\deg(f_i) = a_i,$ and $f_0,\ldots, f_m$ are independent linear polynomials in $x_0, \ldots, x_m$. 
 Then $R_D$ is generated in degrees at most 
@@
 \[
-	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
+	2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
+	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
 \]
@@
 In section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
-
+\todo{todo: explain what u,v,w,x are here}
 \begin{restatable}{thm}{hirzrestate}
@@
 independent linear
-polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$.
+polynomials in $u$ and $v$ and $f_3$ and $f_4$ are independent
+linear polynomials in $w$ and $x$.
 Then $R_D$ is generated in degrees at most
@@
 \otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm
-_{1 \leq i \leq n}(\den_i \cdot \bida_i)}$. Then, if $D_i = V(f_i)$
+_{0 \leq i \leq n}(\den_i \cdot \bida_i)}$. Then, if $D_i = V(f_i)$
 where all $f_i$ can be written as a polynomial function in $x_0,
@@
 \pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be
-written in a canonical form \[\sigma = \lambda + \sum_{i = 1}^{t} w_i e_i\]
+written in a canonical form
+
+\begin{equation}
+	\label{eqn:sigma-canonical-form}
+	\sigma = \lambda + \sum_{i = 1}^{t} w_i e_i
+\end{equation}
+
 with $w_1, \ldots, w_t \in \bz_{\geq 0}$,
@@
 Let 
-\begin{align}\label{eqn:Sigma-def}
+\begin{align}\label{eqn:Sigma-defn}
 	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
@@
 
-We note that $\Sigma$ has extremal rays given by the lattice points 
-\begin{equation}\label{defn:e-i-proj}
+Observe that $\Sigma$ has extremal rays given by the lattice points 
+\begin{equation}\label{eqn:e-i-proj}
 	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
@@
 
-\begin{rem}
-\label{rem:pm-extremal-rays}
-Note for future reference that the extremal rays of the cone $\Sigma$, as
-defined in the proof of Lemma ~\ref{lem:proj-generators} correspond to the
-elements
-\begin{equation}
-\label{eqn:epsilon-def-proj}
-	\epsilon_i = u^{\ell_i a_i}\prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
-\end{equation}
-\end{rem}
-
-Let $x_1, \ldots x_r$ be the generators in degrees at most $\sum_{i=1}^n \ell_i
-\bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let $\phi$ be the
-surjection $k[x_1, \ldots x_r] \to R_D$.
+Let $w_1, \ldots w_r$ be the generators in degrees at most $\sum_{i=0}^n \ell_i
+\bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let 
+$\phi:k[w_1, \ldots w_r] \to R_D$ be the natural surjection.
 For the remainder of the section, we aim to bound the degree of relations
@@
 semigroup ring
+
 \[
@@
 by
-\[
-\begin{tikzcd}
-\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \ar r & u^{d_i}z_0^{c_{i0}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+\begin{equation}
+\label{eqn:factor-through-semigroup-ring}
+\begin{tikzcd}[baseline=(current  bounding  box.center)]
+\bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+w_i \ar r & u^{d_i}z_0^{c_{i0}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_0^{c_{i0}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
-\]
-
-We next show in Lemma ~\ref{lem:composite-map} that the degree of 
+\end{equation}
+
+\begin{rem}
+\label{rem:pm-extremal-rays}
+Note for future reference that the extremal rays of the cone $\Sigma$, as
+defined in Equation ~\eqref{eqn:e-i-proj} correspond to the
+elements
+\begin{equation}
+\label{eqn:epsilon-def-proj}
+	\epsilon_i := \psi(e_i) = u^{\ell_i a_i}\prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
+\end{equation}
+\end{rem}
+
+In Lemma ~\ref{lem:composite-map} we show that the degree of the
 generators for $\ker \phi$, which is the same as the degree of relations
-of $R_D$ can be bounded in terms of the degree of generators for
+of $R_D$, is bounded by the maximum of the degree of generators for
 $\ker \chi$ and for $\ker \psi$.
 In Lemma ~\ref{lem:bound-ker-chi}, we bound the degree of generation of
-$\ker \chi $ and we then calculate the degree of generation of $\ker \psi$ in Lemma ~\ref{lem:proj-relations-psi}
+$\ker \chi $ and we bound the degree of generation of $\ker \psi$ in Lemma ~\ref{lem:proj-relations-psi}
 
@@
 \label{lem:composite-map}
-Let $D = \sum_{i=1}^{n}\alpha_i D_i$ where $D_i = V(f_i)$. Suppose we have a
-surjection $\phi: \bk[x_1,x_2,\ldots, x_r] \rightarrow R_D$ given by $x_i
-\mapsto p_i(f_1, \ldots, f_n),$ where $p_i$ is a monomial in $f_1,\ldots, f_n$.
-Let $\bida_1, \ldots, \bida_n, \bidb_1, \ldots, \bidb_n \in \bz_{\geq 0}.$
+Lex $X$ be an arbitrary scheme and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
+surjection $\phi: \bk[w_1,w_2,\ldots, w_r] \rightarrow R_D$ given by $w_i
+\mapsto p_i(f_0, \ldots, f_n),$ where $p_i$ is a monomial in $f_0,\ldots, f_n$.
+Let $\bida_0, \ldots, \bida_n, \bidb_0, \ldots, \bidb_n \in \bz_{\geq 0}.$
 Then, define
 \begin{align*}
-	\Sigma = \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i = 0 \rangle. 
+	\Sigma = \langle u^d z_0^{c_0} \cdots z_n^{c_n} : c_i \geq -d \alpha_i, \sum_{i=0}^{n} \bida_i c_i = \sum_{i=0}^{n} \bidb_i c_i = 0 \rangle. 
 \end{align*}
@@
 \begin{tikzcd}
-\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-x_i \arrow[mapsto]{r} & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \arrow[mapsto]{r} & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+\bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+w_i \arrow[mapsto]{r} & u^{d_i}z_0^{c_{i0}} \cdots z_n^{c_{in}} \arrow[mapsto]{r} & u^{d_i}f_0^{c_{i0}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
@@
 sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
-$\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Proposition
-~\ref{prop:cone-generation}.
+$\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Equation
+~\eqref{eqn:sigma-canonical-form}.
 \end{proof}
@@
 \label{lem:proj-relations-psi}
-$\ker \psi$ is generated in degrees at most
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes \di \bp^m,$ where
+$\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
+$\ell_i = \lcm_{j \neq i} (k_i)$. Define $\Sigma$ as in Equation
+~\eqref{eqn:Sigma-defn} and $\psi$ as ~\eqref{eqn:factor-through-semigroup-ring}. Then, $\ker \psi$ is generated in degrees at most
 \begin{align}
 \label{eqn:proj-relation-degree}
-	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
+	\frac{\max_{0\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=0}^n \ell_i a_i.
 \end{align}
@@
 \begin{proof}
-We first claim there exist $\beta_1, \ldots, \beta_n \in k[\Sigma]$
+We claim there exist $\beta_0, \ldots, \beta_n \in k[\Sigma]$
 such that $\ker \psi$ is generated by
@@
 
-We define the $\beta_i$ above so that $\beta_i$ is the expansion of
-$f_i$ when viewed as a polynomial in $k[f_0,\ldots, f_{m}]$.
+Indeed, define the $\beta_i$ above so that $\psi(\beta_i) = \beta_i(z_0, \ldots, z_m)= \psi(z_i) \in R_D.$ This is possible by Proposition ~\ref{prop:pm-span-and-basis}.
 Furthermore, the relations given in Equation
-~\eqref{eqn:proj-relation-degree} generate all relations, since they
-allow us to reduce any $ \prod_{j = 0}^n f_j^{r_i}$ to a canonical
-form, with $r_i = -\lfloor  d \alpha_i\rfloor$ whenever $i  > m$.
-
-For the remainder of the proof, fix $i \in \{1,\ldots, n\}$. To
+~\eqref{eqn:relations-psi-proj} generate all relations, since they
+allow us to reduce any $u^d \prod_{j = 0}^n z_j^{c_i}$ to a canonical
+form, with $c_i = -\lfloor  d \alpha_i\rfloor$ whenever $i  > m$.
+
+For the remainder of the proof, fix $i \in \{0,\ldots, n\}$. To
 complete the proof, it suffices to bound the degree of generation
-of the relations of the form $(z_i - \beta_i) \prod_{j = 1}^n
-z_j^{c_j}$, by Equation ~\eqref{eqn:proj-relation-degree}. We first
-associate $(z_i - \beta_i)\prod_{j=0}^n z_j^{c_j}$ with $(d, c_1,
-\ldots, c_n) \in \Sigma,$ as defined in Equation
-~\eqref{eqn:Sigma-def}. Let $\Sigma_i \subseteq \bz^{n + 2}$
-be the set of points of the form $(d, r_1, \ldots, r_n)$ satisfying
-$r_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=0}^n r_j a_j = -a_i$.
+of the relations of the form $u^d(z_i - \beta_i) \prod_{j = 0}^n
+z_j^{c_j}$, by Equation ~\eqref{eqn:proj-relation-degree}. For
+a given monomial
+$u^d(z_i - \beta_i)\prod_{j=0}^n z_j^{c_j} \in \bk[\Sigma]$, we associate it with the corresponding element $(d, c_0,\ldots, c_n) \in\Sigma$. Let $\Sigma_i \subseteq \bz^{n + 2}$
+be the set of points of the form $(d, c_0, \ldots, c_n)$ satisfying
+$c_j \ge -d \alpha_j$ for all $j$ and $\sum_{j=0}^n c_j a_j = -a_i$.
 Let
@@
 \noindent
-Then we see $\Sigma_i \subseteq \delta_i + \newspan_{\bq_{\geq 0}}
-(e_0, \ldots, e_n)$ with $e_i$ as defined in Equation
-~\ref{defn:e-i-proj}. Therefore, we can write any element of
-$\Sigma_i$ as
-\[
-	\delta_i + \sum_{j=0}^n r_j e_j
-\]
-where $r_j \in \mathbb{R}$ for each $j$.
-
-Whenever some $r_j \ge 1$, we can generate the relation $(z_i -
-\beta_i)\prod_{j=1}^n z_j^{c_j} = \epsilon_j \cdot h,$ where
-$\epsilon_j$ was defined in Equation ~\ref{eqn:epsilon-def-proj} and
-$h \in \Sigma_i$. Therefore, $\ker \psi$ is generated in degrees
-less than
-\[
-	\frac{\bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
+Then we see $\Sigma_i = \{\sigma \in \Sigma | \sigma - \delta_i \in \newspan_{\bq_{\geq 0}}
+(e_0, \ldots, e_n)\}$ with $e_i$ as defined in Equation
+~\ref{eqn:e-i-proj}. Therefore, we can write any element of
+$\Sigma_i$ uniquely as
+\[
+	\delta_i + \sum_{j=0}^n c_j e_j
+\]
+where $c_j \in \mathbb{R}$ for each $j$.
+
+Whenever some there is some $j$ for which $c_j \ge 1$, we can write the relation $u^d(z_i -
+\beta_i)\prod_{j=0}^n z_j^{c_j} = e_j h,$ for some
+$h \in \Sigma_i$. Therefore, for a fixed $i$, relations of the form
+$u^d(z_i - \beta_i)\prod_{j=0}^n z_j^{c_j} \in \bk[\Sigma]$ are
+generated by those in degrees less than
+\[
+	\frac{\bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i,
+\]
+as $\deg \delta_i = \frac{a_i}{\deg(D)}$. Hence,
+$\ker \psi$ is generated in degrees less than
+\[
+	\frac{\max_{0 \leq i \leq n} \bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i,
 \]
@@
 
-By combining these results, we get our main theorem bounding
-the generator and relation degrees of the canonical ring of
-$\bq$-divisors on projective space.
+By combining the above results, we get our main theorem bounding
+the generator and relation degrees of the canonical ring of any
+$\bq$-divisor on projective space.
 
@@
 ~\ref{lem:proj-relations-psi}, $\ker \psi,$ is generated in
-degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i$. 
+degrees up to $\frac{\max_{0 \leq i \leq n} \bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i$. 
 Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker \phi$
@@
 \[
-	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{1\le i \le n}
-	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
+	2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
+	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
 \]
@@
 Then, $f_1$ and $f_2$ are independent linear
-polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
-linear polynomials in $y_0$ and $y_1$.  In order to achieve this condition on
+polynomials in $u$ and $v$ and $f_3$ and $f_4$ are independent
+linear polynomials in $w$ and $x$.  In order to achieve this condition on
 $D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e.
@@
 We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
-V(\sum_{i=1}^n \bida_i X_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap \Sigma_1
+V(\sum_{i=1}^n \bida_i x_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap \Sigma_1
 \otimes_\bz \bq$.  Then, the extremal rays of $\Sigma$ are precisely the extremal 
@@
 
-Let $x_1, \ldots x_r$ be the generators of $R_D$ in degrees less than $\rho$
+Let $w_1, \ldots w_r$ be the generators of $R_D$ in degrees less than $\rho$
 (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the
-surjection $k[x_1, \ldots x_r] \to R_D$.  We can factor $\phi$ through the
+surjection $k[w_1, \ldots w_r] \to R_D$.  We can factor $\phi$ through the
 semigroup ring 
@@
 \begin{tikzcd}
-	\bk[x_1,\ldots, x_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-	x_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+	\bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
+	w_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
 \end{tikzcd}

### 2015-08-08 surfaces-write-up/surface-write-up.tex
aaron second read through section 3, edited all except last big proof

@@
 In section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
-\todo{todo: explain what u,v,w,x are here}
 \begin{restatable}{thm}{hirzrestate}
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_k$ 
+Let $u,v,z,w$ be the coordinates for the Hirzebruch surface $\hirz_m$, as described at the beginning of section ~\ref{sec:hirz}. Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_m$ 
 where $\alpha_i = \frac{c_i}{k_i}$.
@@
 \end{equation}
-
-\begin{rem}
-\label{rem:pm-extremal-rays}
-Note for future reference that the extremal rays of the cone $\Sigma$, as
-defined in Equation ~\eqref{eqn:e-i-proj} correspond to the
-elements
-\begin{equation}
-\label{eqn:epsilon-def-proj}
-	\epsilon_i := \psi(e_i) = u^{\ell_i a_i}\prod_{j\ne i} (f_j)^{-\alpha_j \ell_i a_i} {f_i}^{\ell_i \sum_{j\ne i} \alpha_j a_j}\in R_D.
-\end{equation}
-\end{rem}
 
@@
 
+One way to describe the hirzebruch surface $\hirz_m$ is as a quotient
+\[
+\hirz_m \cong (\ba^2 \setminus \{0\}) \times (\ba^2 \setminus \{0\})/\mathbb G_m \times \mathbb G_m
+\]
+where $\mathbb G_m$ is the multiplicative subgroup of $\ba^1$, and the action of $\mathbb G_m \times \mathbb G_m$ is given by
+$(\lambda, \mu) \cdot (u:v; z:w) \mapsto (\lambda u: \lambda v; \mu z: \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{counting-cubic}.
+\todo{add counting-cubic (as found in our Dropbox/stacky-REU/references folder to bibliography} Hence, one can think of
+$\hirz_m$ as a $\bp^1$ bundle where $u,v$ are the coordinates on
+$\bp^1$ and $z,w$ are the coordinates on the fiber.
 Sections of a line bundle $\mathscr L$ on $\hirz_m$ can be written as
-polynomials in $u,v, w,x$.
-Furthermore we define the bi-degree of a monomial $u^a v^{b} w^c x^d$
+rational functions in $z, w, u, v$.
+Furthermore we define the bi-degree of a monomial $u^a v^{b} z^c w^d$
 on $\hirz_n$ to be
-$(a + b + mc, c + d)$.  Rational section of $\hirz_m$ can be written as
+$(a + b + mc, c + d)$. Rational sections of $\hirz_m$ can be written as
 rational functions where each monomial has bi-degree 0. To see this, 
@@
 distinct divisors with bi-degrees $(1,0)$
-, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
-$f_i \in \sco(\bida_i, \bidb_i)$.  
-Then, $f_1$ and $f_2$ are independent linear
+, $(1,0)$, $(0,1)$, and $(0,1)$ respectively with $D_i = V(f_i)$ for $1 \leq i \leq 4$ with $f_i \in \sco(\bida_i, \bidb_i)$.  
+In order to achieve this condition on
+$D_1, \ldots D_4$, it may be necessary to add in ``ghost divisors'' (i.e.
+divisors with of the desired form with a coefficient $0$).
+Also, note that, $f_1$ and $f_2$ are independent linear
 polynomials in $u$ and $v$ and $f_3$ and $f_4$ are independent
-linear polynomials in $w$ and $x$.  In order to achieve this condition on
-$D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e.
-divisors with of the desired form with a coefficient $0$).
+linear polynomials in $z$ and $w$.
+Analogously to Proposition ~\ref{prop:pm-span-and-basis} for the case
+of $\bp^m$, all rational functions on $\hirz_m$
+can be written uniquely in a form where their numerator is a function
+of only $f_1,f_2,f_3$, and $f_4$.
+\todo{Aaron: Do either of you think we should write out this as
+a proposition more clearly? I'm fine either way, but it was something
+missing which I thought I should point out.}
+
 \begin{defn}
@@
 \label{lem:hirz-generators}
-$R_D$ is generated in degrees at most
+For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \bq \otimes_\bz \hirz_m$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the canonical ring $R_D$ is generated in degrees at most
 \begin{equation}\label{eqn:def-sigma}
@@
 \noindent
-for some $c_i \ge - \alpha_i d$ for all $i$ such that $\sum_{i=1}^n c_i \bida_i = 0$
+for some $c_i \ge - \alpha_i d$ such that $\sum_{i=1}^n c_i \bida_i = 0$
 and $\sum_{i=1}^n c_i \bidb_i = 0$. We can view $g$ as an element $(d, c_1, \ldots, c_n)$ of the
@@
 We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
-V(\sum_{i=1}^n \bida_i x_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap \Sigma_1
-\otimes_\bz \bq$.  Then, the extremal rays of $\Sigma$ are precisely the extremal 
+V(\sum_{i=1}^n \bida_i x_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap (\Sigma_1
+\otimes_\bz \bq)$.  Then, the extremal rays of $\Sigma$ are precisely the extremal 
 rays of $\Sigma \otimes_\bz \bq$.
@@
 
-From this we can deduce that a set of extremal rays of $\Sigma$ are given as follows:
-For $i \in \Te(D)$, define $e_i \in R_D$ in degree 
+From this geometric description of the extremal rays, we can write
+the extremal rays algebraically as follows.
+For $i \in \Te(D)$, define $e_i \in \bk[\Sigma]$ in degree 
 \[
@@
 \noindent
-For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree 
+For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in \bk[\Sigma]$ in degree 
 \[
@@
 $R_D$ is generated in 
-degrees less than the sum of the degrees of the $\epsilon_i$'s and $\epsilon_{i,j}$'s, which is
+degrees less than the sum of the degrees of the $e_i$ and $e_{i,j}$, which is
 \[
@@
 (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the
-surjection $k[w_1, \ldots w_r] \to R_D$.  We can factor $\phi$ through the
+surjection $k[w_1, \ldots w_r] \to R_D$. As in Section ~\ref{sec:proj}, we can factor $\phi$ through the
 semigroup ring 
@@
 	\alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i
-	\right \rangle.
+	\right \rangle
 \]
@@
 ^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
-
+\todo{Aaron: The next two paragraphs are missing a lot of $u^d$ degree prefixes. Can one of you add them in and go through the proof
+to make sure there are no others missing?}
 We claim such a $\beta_i$,
@@
 follows from Lemma ~\ref{lem:hirz-bound-ker-psi}.
-$\ker \psi$ follows from 
 \end{proof}

### 2015-08-08 surfaces-write-up/surface-write-up.tex
fixed some ^d$'s

@@
 a proposition more clearly? I'm fine either way, but it was something
-missing which I thought I should point out.}
+missing which I thought I should point out. \\
+Peter: The one line argument is ``Every numerator is a polynomial in $u, v, z, w$; we can generate $u$ and $v$ from $f_1$ and $f_2$, and we can generate $z$ and $w$ from $f_3$ and $f_4$.''  This can be added if you want}
 
@@
 \todo{Aaron: The next two paragraphs are missing a lot of $u^d$ degree prefixes. Can one of you add them in and go through the proof
-to make sure there are no others missing?}
-We claim such a $\beta_i$,
-can be expressed as a polynomial $\beta_i(f_1,f_2,f_3,f_4)$ with 
-$\beta_i(f_1,f_2,f_3,f_4) = f_i$
-as elements of $\bk[\Sigma],$ which is possible as $f_1,f_2,f_3,f_4$ generate $\Sigma,$ and hence generate $\bk[\Sigma]$. Furthermore, these
-generate all relations, since they allow us to reduce any monomial $\prod_{j =
+to make sure there are no others missing?\\
+Peter: I added a bunch.  Should be better (although quite possibly missed a few more).}
+Specifically, $\beta_i$,
+is the polynomial obtained by expressing $f_i$ as a polynomial in $f_1, f_2, f_3, f_4$.
+%$\beta_i(f_1,f_2,f_3,f_4)$ with 
+%$\beta_i(f_1,f_2,f_3,f_4) = f_i$
+%as elements of $\bk[\Sigma],$ which is possible as $f_1,f_2,f_3,f_4$ %generate $\Sigma,$ and hence generate $\bk[\Sigma]$. 
+Furthermore, these
+generate all relations, since they allow us to reduce any monomial $u^d\prod_{j =
 1}^n f_j^{r_j}$ to the canonical form where $r_j = - \lfloor d \alpha_i
 \rfloor$
-
 whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
@@
 We now wish to bound the degree of generation the ideal of relations generated by these.
-To do this, we first fix $i$ and a relation of the form $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0.$ Note that there are no relations for $i\in \{1, 2, 3, 4\}$ as $\beta_i = f_i$; thus we restrict attention to $i \ge 5$.
+To do this, we first fix $i$ and a relation of the form $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0.$ Note that there are no relations for $i\in \{1, 2, 3, 4\}$ as $\beta_i = f_i$; thus we restrict attention to $i \ge 5$.
 Our goal is to find a relation that the divides this, but whose degree we can bound.
-We do so by considering the lattice points corresponding to the monomials appearing in the relation $(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda\in \Sigma$
+We do so by considering the lattice points corresponding to the monomials appearing in the relation $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda\in \Sigma$
 that we can factor out of each monomial, to get a relation below a bounded degree.  The following argument makes this precise:
@@
 
-Consider a relation $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ with corresponding lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
+Consider a relation $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ and let it correspond to the lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
 Then we can write $\sigma$ as a sum of $s_j e_j$'s for $j\in
 \Te$ and $s_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
-For convenience, defing $d_j := \deg e_j$ (when it exists) and let the $j^{th}$
+For convenience, define $d_j := \deg e_j$ (when it exists) and let the $j^{th}$
 component of $e_j$ be $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$.
@@
 
-For $u^d (f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$ to be a relation, it must, in particular, be an element of $R_D$.
+Since $u^d (f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$ is a relation, each monomial of it must be an element of $R_D$.
 This implies that $s_i\kappa_i\ge 1$, $\sum_{j\in \Tm} s_{i,j}\kappa_{i,j}' \ge 1$, and $\sum_{j\in \Tp} s_{i,j}\kappa_{j,i}'' \ge 1$ if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$ respectively.
@@
 %\]
-which divides $(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 
+which divides $u^d(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 
 We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by

### 2015-08-08 surfaces-write-up/surface-write-up.tex
responded to basis for hirzebruch comment

@@
 missing which I thought I should point out. \\
-Peter: The one line argument is ``Every numerator is a polynomial in $u, v, z, w$; we can generate $u$ and $v$ from $f_1$ and $f_2$, and we can generate $z$ and $w$ from $f_3$ and $f_4$.''  This can be added if you want}
+Peter: The one line argument is ``Every numerator is a polynomial in $u, v, z, w$; we can generate $u$ and $v$ from $f_1$ and $f_2$, and we can generate $z$ and $w$ from $f_3$ and $f_4$.''  This can be added if you want
+
+Aaron: I agree that argument is obvious. I was more referring to the analog
+of proposition ~\ref{prop:pm-span-and-basis}, that is, how to show
+every numerator is a polynomial in $u,v,z,w$. This would probably be
+an argument that takes a couple paragraphs.
+}
 

### 2015-08-08 surfaces-write-up/surface-write-up.tex
aaron edited second time through whole paper

@@
 \[
-	2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
-	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
+	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
+	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
 \]
@@
 denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
-is a graded ring, we denote the $d$th graded component of $R$ by $R_d$.
+is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
+$\fr(r) := r - \lfloor r
+\rfloor$ denote the fractional part of $r$.
 \section{Canonical Rings on Projective Space}
@@
 \[
-	\frac{\max_{0 \leq i \leq n} \bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i,
+	\frac{\max_{0 \leq i \leq n} \bida_i}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
 \]
@@
 \[
-	2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
-	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i.
+	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
+	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
 \]
@@
 \begin{proof}
-We first claim that there exist $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
+We first claim that there exist $u^{\deg z_1}\beta_1, \ldots, u^{\deg z_n} \beta_n\in \bk[uz_1, uz_2, uz_3, uz_4]$
 such that $\ker \psi$ has relations of the form
@@
 Specifically, $\beta_i$,
-is the polynomial obtained by expressing $f_i$ as a polynomial in $f_1, f_2, f_3, f_4$.
-%$\beta_i(f_1,f_2,f_3,f_4)$ with 
-%$\beta_i(f_1,f_2,f_3,f_4) = f_i$
-%as elements of $\bk[\Sigma],$ which is possible as $f_1,f_2,f_3,f_4$ %generate $\Sigma,$ and hence generate $\bk[\Sigma]$. 
-Furthermore, these
+is the polynomial $\beta_i(z_1,z_2,z_3,z_4)$ so that
+$\beta_i(z_1,z_2,z_3,z_4) - z_i \in \ker \psi$. Such an element
+$\beta$ exists and is unique because rational functions
+whose numerators are polynomials in $f_1,f_2,f_3,f_4$ form a basis
+of all rational functions in $R_D$. Furthermore, these
 generate all relations, since they allow us to reduce any monomial $u^d\prod_{j =
-1}^n f_j^{r_j}$ to the canonical form where $r_j = - \lfloor d \alpha_i
+1}^n z_j^{r_j}$ to the canonical form where $r_j = - \lfloor d \alpha_i
 \rfloor$
-whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.
-
-We now wish to bound the degree of generation the ideal of relations generated by these.
-To do this, we first fix $i$ and a relation of the form $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0.$ Note that there are no relations for $i\in \{1, 2, 3, 4\}$ as $\beta_i = f_i$; thus we restrict attention to $i \ge 5$.
-Our goal is to find a relation that the divides this, but whose degree we can bound.
-We do so by considering the lattice points corresponding to the monomials appearing in the relation $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$, and finding some $\lambda\in \Sigma$
-that we can factor out of each monomial, to get a relation below a bounded degree.  The following argument makes this precise:
+whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(\beta_i  -z_i) \cap \ker(\psi)$ for each $i$.
+
+To bound the degree of generation of the ideal 
+$(\beta_i - z_i) \cap \ker(\psi)$, {\bf for the remainder of the proof,} we fix $i \in \{1,\ldots, n\}$ and a relation of 
+the form $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}.$ Note that there 
+are no relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in \bk[\Sigma]$. Thus we restrict attention to $i \ge 5$. Our goal 
+is to show that if $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ has 
+sufficiently high degree, then there is another relation dividing it. 
+We do so by considering the lattice points corresponding to the 
+monomials appearing in the relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$, and finding a fixed $\lambda\in \Sigma$
+that we can simultaneously factor out of all monomials.
 
@@
 
-Consider a relation $u^d(f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}=0$ and let it correspond to the lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
+Consider a relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ and let it correspond to the lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
 Then we can write $\sigma$ as a sum of $s_j e_j$'s for $j\in
@@
 
-Since $u^d (f_i - \beta_i)\prod_{j=1}^n f_j^{c_j}$ is a relation, each monomial of it must be an element of $R_D$.
+Since $u^d (z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ is a relation, each monomial of it must be an element of $\Sigma$.
 This implies that $s_i\kappa_i\ge 1$, $\sum_{j\in \Tm} s_{i,j}\kappa_{i,j}' \ge 1$, and $\sum_{j\in \Tp} s_{i,j}\kappa_{j,i}'' \ge 1$ if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$ respectively.
@@
 If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
-For $j\ne i$, define $r_j := 0$ and for all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} := 0$.
+For $j\ne i$, define $r_j := 0.$ For all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} := 0$.
 Define $E$ by
@@
 Note that
-\[
+\begin{align}
+\label{eqn:e-bound}
 	\deg(E) \le \rho + \begin{cases}
@@
 	&\mbox{ if } i \in \Tm. \end{cases}
-\]
-where $\rho$ is as in Equation \ref{eqn:def-sigma}.
-In this sum the $\rho$ term corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_{j,k} - r_{j,k}$'s, whereas the second term corresponds to the sums of $r_j$'s and $r_{j,k}$'s (noting that in equation \ref{eqn:hirz-E-translation} $s_j - \lfloor s_j - r_j \rfloor$ equals $r_j$ plus the fractional part of $s_j - r_j$, and a similar statement holds for $s_{j,k} - \lfloor s_{j,k} - r_{j,k}$).
+\end{align}
+where $\rho$ is as in Equation \ref{eqn:def-sigma}. To obtain the
+bound given in Equation ~\eqref{eqn:e-bound}, the $\rho$ term corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_{j,k} - r_{j,k}$'s, whereas the second term corresponds to the sums of $r_j$'s and $r_{j,k}$'s (noting that in equation \ref{eqn:hirz-E-translation} $s_j - \lfloor s_j - r_j \rfloor= r_j + \fr(s_j - r_j)$).
 
@@
 
-Let $M_i$ be the set of monomials terms of $\beta_i = \beta_i(f_1, \ldots f_4)$.  Let $\mu = \prod_{j=1}^4
-{f_j}^{h_j}\in M_i$ and consider the lattice point 
+Let $M_i$ be the set of monomials terms of $\beta_i = \beta_i(z_1, \ldots z_4)$.  Let $\mu = \prod_{j=1}^4
+{z_j}^{h_j}\in M_i$ and consider the lattice point 
 \[
@@
 \]
-A quick computation deduces that $E_\mu$ lies in $\Sigma$ 
+From the definitions, $E_\mu$ lies in $\Sigma$ 
 and has the same degree as $E$.
 
-Let $F = \Psi(E) \in R_D$ and $F_\mu = \psi(E_\mu)
-\in R_D$ for each $\mu \in M_i$.  
-Then $F - \sum_{\mu \in M_i} F_\mu = 0$ is a relation %in degree
-%\[
-%	\deg(F) = \deg(E)
-%\]
-which divides $u^d(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 
-We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
-\[
-	\deg(F) = \deg(E) \le \rho + \begin{cases}
-	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
-	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
-	&\mbox{ if } i \in \Tp \\
-	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
-	&\mbox{ if } i \in \Tm. \end{cases}
-	\]
-
-\noindent
-Therefore, $\ker \psi$ is generated in degrees at most
+Finally, by construction, $E - \sum_{\mu \in M_i} E_\mu \in \ker \psi$ and
+divides $u^d(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 
+Furthermore, we have already bounded $\deg(E)$ in Equation ~\eqref{eqn:e-bound}.
+Finally, recall $\ker \psi$ is generated by relations of the form $u^d(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$ as
+$i$ ranges between $1$ and $n$. Thus, taking the maximum over all $i$ 
+of our bound in Equation ~\eqref{eqn:e-bound}, we see $\ker \psi$ is generated in degrees at most
 \[
@@
 
-By combining these results, we get our main theorem bounding
+By combining the above results, we get our main theorem bounding
 the generator and relation degrees of the canonical ring of
@@
 Recall that every minimal rational surface is either isomorphic to
-$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$ \todo{also cite 
-eisenbud--harris here?}. By Theorems
+$\bp^2$ or $\hirz_m$ for some $m \geq 0, m \neq 1$ \cite{eisenbud-harris:minimal}. By Theorems
 ~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations

### 2015-08-08 surfaces-write-up/surface-write-up.tex
did spellcheck

@@
 canonical rings on projective space, we first
-describe a particular choice of basis for $R_D$ as a $\bk$ bector space.
+describe a particular choice of basis for $R_D$ as a $\bk$ vector space.
 
@@
 hyperplanes. However, for $m \geq 2$, there are hypersurfaces which
-are not unions of hyperplanes. We now adress this general case, giving an inductive presentation of canonical rings of effective divisors, and a tight bound on the degrees of their generators and
+are not unions of hyperplanes. We now address this general case, giving an inductive presentation of canonical rings of effective divisors, and a tight bound on the degrees of their generators and
 relations.
@@
 
-If $C$ is of degree $\pdeg$, consider the veronese embedding
+If $C$ is of degree $\pdeg$, consider the Veronese embedding
 $\nu_\pdeg^m: \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
@@
 Now, note that the ring $R_{\alpha C}$ is isomorphic to the
-$\pdeg$ veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0))$ and so
+$\pdeg$ Veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0))$ and so
 the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
@@
 This reduces the case of a hypersurface $C$ to
-a hyperplane $H$, completeting the proof by Theorem
+a hyperplane $H$, completing the proof by Theorem
 ~\ref{thm:proj-one-point}.
@@
 \label{rem:exact-effective-bounds}
-Note that the proof of Theorem ~\ref{thm:proj-effective-intro} not only gives bounds on the degrees of the generators and relations, but actually gives an explicit method for computing the presentaiton.
+Note that the proof of Theorem ~\ref{thm:proj-effective-intro} not only gives bounds on the degrees of the generators and relations, but actually gives an explicit method for computing the presentation.
 In particular, these bounds are tight.
-The generator bound is always acheived and the bound on the relations is achieved if $m \geq 2$.
+The generator bound is always achieved and the bound on the relations is achieved if $m \geq 2$.
 \end{rem}
@@
 
-One way to describe the hirzebruch surface $\hirz_m$ is as a quotient
+One way to describe the Hirzebruch surface $\hirz_m$ is as a quotient
 \[
@@
 Perhaps similar techniques can be used to bound
-degrees of presentaitons on canonical rings on $(\bp^1)^k$ or
+degrees of presentations on canonical rings on $(\bp^1)^k$ or
 more generally on $(\bp^1)^{i_1} \times \cdots (\bp^k)^{i_k}.$

### 2015-08-09 surfaces-write-up/surface-write-up.tex
add counting-cubic ref

@@
 where $\mathbb G_m$ is the multiplicative subgroup of $\ba^1$, and the action of $\mathbb G_m \times \mathbb G_m$ is given by
-$(\lambda, \mu) \cdot (u:v; z:w) \mapsto (\lambda u: \lambda v; \mu z: \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{counting-cubic}.
-\todo{add counting-cubic (as found in our Dropbox/stacky-REU/references folder to bibliography} Hence, one can think of
+$(\lambda, \mu) \cdot (u:v; z:w) \mapsto (\lambda u: \lambda v; \mu z: \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{zhao:counting-cubic}. Hence, one can think of
 $\hirz_m$ as a $\bp^1$ bundle where $u,v$ are the coordinates on

### 2015-08-09 surfaces-write-up/surface-write-up.tex
intro M_g explanation todo

@@
 Another closely related topic is the Hassett-Keel program 
-initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
+initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form \todo{Robin: define $\mathscr{M}_g$? Not sure what this is.}
 \begin{align*}

### 2015-08-09 surfaces-write-up/surface-write-up.tex
minor rewording, add one clarification todo

@@
 \noindent
-In section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
+In Section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
 \begin{restatable}{thm}{hirzrestate}
 \label{thm:hirz-generators-relations}
-Let $u,v,z,w$ be the coordinates for the Hirzebruch surface $\hirz_m$, as described at the beginning of section ~\ref{sec:hirz}. Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_m$ 
+Let $u,v,z,w$ be the coordinates for the Hirzebruch surface $\hirz_m$, as described at the beginning of Section ~\ref{sec:hirz}. Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_m$ 
 where $\alpha_i = \frac{c_i}{k_i}$.
@@
 
-Our first aim in this section is to prove Theorem
+The first aim of this section is to prove Theorem
 ~\ref{thm:proj-generators-relations} bounding the number of generators and
@@
 
-For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
-distinct divisors with bi-degrees $(1,0)$
-, $(1,0)$, $(0,1)$, and $(0,1)$ respectively with $D_i = V(f_i)$ for $1 \leq i \leq 4$ with $f_i \in \sco(\bida_i, \bidb_i)$.  
-In order to achieve this condition on
+For the remainder of this section, we will assume that $D_1, D_2, D_
+3, D_4$ are distinct divisors with bi-degrees $(1, 0)$, $(1, 0)$, $(
+0, 1), (0, 1)$ respectively with $D_i = V(f_i)$ for $1 \leq i \leq 4
+$ with $f_i \in \sco(\bida_i, \bidb_i)$.
+
+In order to achieve this condition on \todo{write ``this''}
 $D_1, \ldots D_4$, it may be necessary to add in ``ghost divisors'' (i.e.

### 2015-08-09 surfaces-write-up/surface-write-up.tex
fixed robin's easy todos like mg

--- 2015-08-09 surfaces-write-up/surface-write-up.tex
@@
 \end{align*}
-in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
+in terms of certain moduli spaces, where $\overline {\mathscr M_g}$ is the
+moduli space of stable genus $g$ curves.
+Moreover, $\bq$-divisors on surfaces also naturally
 appear when considering the canonical ring of surfaces of Kodaira dimension 1.
@@
 where $\mathbb G_m$ is the multiplicative subgroup of $\ba^1$, and the action of $\mathbb G_m \times \mathbb G_m$ is given by
-$(\lambda, \mu) \cdot (u:v; z:w) \mapsto (\lambda u: \lambda v; \mu z: \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{zhao:counting-cubic}. Hence, one can think of
+$(\lambda, \mu) \cdot (u:v; z:w) \mapsto (\lambda u: \lambda v; \mu z: \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{counting-cubic}.
+\todo{add counting-cubic (as found in our Dropbox/stacky-REU/references folder to bibliography} Hence, one can think of
 $\hirz_m$ as a $\bp^1$ bundle where $u,v$ are the coordinates on
@@
 , $(1,0)$, $(0,1)$, and $(0,1)$ respectively with $D_i = V(f_i)$ for $1 \leq i \leq 4$ with $f_i \in \sco(\bida_i, \bidb_i)$.  
-In order to achieve this condition on
+In order to achieve the above condition on the bi-degrees of
 $D_1, \ldots D_4$, it may be necessary to add in ``ghost divisors'' (i.e.

### 2015-08-09 surfaces-write-up/surface-write-up.tex
merged bc forgot to pull first

--- 2015-08-09 surfaces-write-up/surface-write-up.tex
@@
 
-For the remainder of this section, we will assume that $D_1, D_2, D_
-3, D_4$ are distinct divisors with bi-degrees $(1, 0)$, $(1, 0)$, $(
-0, 1), (0, 1)$ respectively with $D_i = V(f_i)$ for $1 \leq i \leq 4
-$ with $f_i \in \sco(\bida_i, \bidb_i)$.
-
-In order to achieve this condition on \todo{write ``this''}
+For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
+distinct divisors with bi-degrees $(1,0)$
+, $(1,0)$, $(0,1)$, and $(0,1)$ respectively with $D_i = V(f_i)$ for $1 \leq i \leq 4$ with $f_i \in \sco(\bida_i, \bidb_i)$.  
+In order to achieve the above condition on the bi-degrees of
+
 $D_1, \ldots D_4$, it may be necessary to add in ``ghost divisors'' (i.e.

### 2015-08-09 surfaces-write-up/surface-write-up.tex
made a few edits in early sections

@@
 \textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
-track of indexing.
+track of degree.
 We study the generators and relations of canonical
-rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
+rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$ \todo{Peter: Bad to have $m$ as both the dimension of $\bp$ and the coefficient for the hirzebruch surface?}.
 When $D$ is a general $\bq$-divisor on $\bp^m$ or
 $\hirz_m$, we give bounds on the generators and relations of
-$R(X, D)$. In particular, we give a complete description of the
+$R(X, D)$.
+In particular, we give a complete description \todo{Peter: The phrase ``complete description'' is ambiguous and might be objectionable to a reader.
+Is ``minimal presentation'' better?} of the
 canonical ring when $X = \bp^m$ and $D$ is any effective
@@
 which provide tight bounds on generators and relations
-of canonical rings on arbitrary stacky curves.
-
-Another closely related topic is the Hassett-Keel program 
-initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form \todo{Robin: define $\mathscr{M}_g$? Not sure what this is.}
+of canonical rings and spin canonical rings, respectively, on arbitrary stacky curves.
+
+Another closely related topic is the Hassett-Keel program \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form \todo{Robin: define $\mathscr{M}_g$?
+Not sure what this is.
+\\
+Peter: Isn't it defined in the line below?  (Maybe it was added after your comment)}
 \begin{align*}
@@
 as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
-By Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
+Voight and Zureick-Brown show that 
 one can translate the analytic category of 1-dimensional complex orbifolds to
-the algebraic category of stacky curves. 
+the algebraic category of stacky curves \cite[Proposition 6.1.5]{vzb:stacky}. 
 We expect that one can generalize this result to yield an equivalence of
@@
 basis for degree one rational functions on $\bp^m$.
+\todo{Peter: This assumption is inconsistent with a comment made later (see next todo); later, we allow for there to be only one $D_i$ ($D= D_i$), which contradicts $m>0$.}
 
@@
 Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
-stated explicitly later, in the case that $D = \alpha_1 D_1$ is supported on a single hypersurface, the relations in Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to this ordering.
+stated explicitly later, in the case that $D = \alpha_1 D_1$ \todo{Peter: Inconsistent with previous assumption.
+To be clear it doesn't matter for any proofs, because that assumption is not necessary until after this section.
+I suggest we find some way to move that assumption from earlier until after the effective case.} is supported on a single hypersurface, the relations in Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to this ordering.
 
@@
 In order to achieve the above condition on the bi-degrees of
-
 $D_1, \ldots D_4$, it may be necessary to add in ``ghost divisors'' (i.e.

### 2015-08-09 surfaces-write-up/surface-write-up.tex
added response to todo
removed some todos

@@
 
-\todo{Make sure to include $u^d$ everywhere necessary}
-\todo{Make sure to index starting from 0 in $\bp^m$ section}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We study the generators and relations of canonical
-rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$ \todo{Peter: Bad to have $m$ as both the dimension of $\bp$ and the coefficient for the hirzebruch surface?}.
+rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$ \todo{Peter: Bad to have $m$ as both the dimension of $\bp$ and the coefficient for the hirzebruch surface?
+
+Aaron: It doesn't seem like this would cause any confusing to me. They're always discussed separately.
+}.
 When $D$ is a general $\bq$-divisor on $\bp^m$ or
 $\hirz_m$, we give bounds on the generators and relations of
-$R(X, D)$.
-In particular, we give a complete description \todo{Peter: The phrase ``complete description'' is ambiguous and might be objectionable to a reader.
-Is ``minimal presentation'' better?} of the
+$R(X, D)$. In particular, we give a minimal presentation of the
 canonical ring when $X = \bp^m$ and $D$ is any effective
@@
 
-Another closely related topic is the Hassett-Keel program \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form \todo{Robin: define $\mathscr{M}_g$?
-Not sure what this is.
-\\
-Peter: Isn't it defined in the line below?  (Maybe it was added after your comment)}
+Another closely related topic is the Hassett-Keel program \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form 
 \begin{align*}
@@
 Cartier divisors such that $D_i = V(f_i)$.
-We shall further assume that (possibly after reordering) $f_0,\ldots, f_{m}$ form a
+We shall further assume for this subsection that (possibly after reordering) $f_0,\ldots, f_{m}$ form a
 basis for degree one rational functions on $\bp^m$.
-\todo{Peter: This assumption is inconsistent with a comment made later (see next todo); later, we allow for there to be only one $D_i$ ($D= D_i$), which contradicts $m>0$.}
 
@@
 Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
-stated explicitly later, in the case that $D = \alpha_1 D_1$ \todo{Peter: Inconsistent with previous assumption.
-To be clear it doesn't matter for any proofs, because that assumption is not necessary until after this section.
-I suggest we find some way to move that assumption from earlier until after the effective case.} is supported on a single hypersurface, the relations in Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to this ordering.
+stated explicitly later, in the case that $D = \alpha_1 D_1$ is supported on a single hypersurface, the relations in
+Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to
+this ordering.
 
@@
 For the remainder of this section, we shall make the additional assumption that 
-\begin{align}
-\label{eqn:pm-basis-assumption}
-	f_0, \ldots, f_{m} \text{ form a } \bk \text{ basis of all degree 1 functions.}
-\end{align}
+\begin{align} \label{eqn:pm-basis-assumption} f_0, \ldots, f_{m} \text{ form a
+	} \bk \text{ basis of all degree 1 functions.} \end{align}
 
@@
 an argument that takes a couple paragraphs.
+\\
+Peter: I see what you mean.  What was the argument for that again.  It was some exact sequence thing you came up with right?
 }
@@
 ^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.
-\todo{Aaron: The next two paragraphs are missing a lot of $u^d$ degree prefixes. Can one of you add them in and go through the proof
-to make sure there are no others missing?\\
-Peter: I added a bunch.  Should be better (although quite possibly missed a few more).}
 Specifically, $\beta_i$,

### 2015-08-09 surfaces-write-up/surface-write-up.tex
a few more edits; I'm ready to send to David.  Any objections?

@@
 We study the generators and relations of canonical
-rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$ \todo{Peter: Bad to have $m$ as both the dimension of $\bp$ and the coefficient for the hirzebruch surface?
-
-Aaron: It doesn't seem like this would cause any confusing to me. They're always discussed separately.
-}.
+rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
 When $D$ is a general $\bq$-divisor on $\bp^m$ or
@@
 of only $f_1,f_2,f_3$, and $f_4$.
-\todo{Aaron: Do either of you think we should write out this as
-a proposition more clearly? I'm fine either way, but it was something
-missing which I thought I should point out. \\
-Peter: The one line argument is ``Every numerator is a polynomial in $u, v, z, w$; we can generate $u$ and $v$ from $f_1$ and $f_2$, and we can generate $z$ and $w$ from $f_3$ and $f_4$.''  This can be added if you want
-
-Aaron: I agree that argument is obvious. I was more referring to the analog
-of proposition ~\ref{prop:pm-span-and-basis}, that is, how to show
-every numerator is a polynomial in $u,v,z,w$. This would probably be
-an argument that takes a couple paragraphs.
-\\
-Peter: I see what you mean.  What was the argument for that again.  It was some exact sequence thing you came up with right?
-}
 
@@
 \label{sec:conc}
-In this section, we briefly state some further questions.
+%In this section, we briefly state some further questions.  \todo{Peter: Redundant (see title of section...)?}
 
@@
 to bound the degree of generators and relations of the 
-canonical ring of a divisor on a blow-up of that surface in terms of the canonical ring of a divisor on that surface.
+canonical ring of a divisor on a blow-up of that surface in terms of canonical rings of some associated divisors on that original surface.
 
@@
 would be to try to express canonical rings of $\bq$-divisors on
-$X \times Y$ in terms of $X$ and $Y$. In this paper,
+$X \times Y$ in terms of those on $X$ and $Y$. In this paper,
 we bounded the degrees of presentations on canonical rings on $\bp^1 \times \bp^1 \cong \hirz_0$.

### 2015-08-09 surfaces-write-up/surface-write-up.tex
minor change in further questions, ready for david

@@
 to bound the degree of generators and relations of the 
-canonical ring of a divisor on a blow-up of that surface in terms of canonical rings of some associated divisors on that original surface.
+canonical ring of a divisor on a blow-up of that surface $S$ in terms of 
+the canonical
+rings of some associated divisors on $S$.
 

### 2015-08-09 surfaces-write-up/surface-write-up.tex
reworded further quesitons again

@@
 to bound the degree of generators and relations of the 
-canonical ring of a divisor on a blow-up of that surface $S$ in terms of 
-the canonical
-rings of some associated divisors on $S$.
+canonical ring of a divisor on a blow-up of a given surface
+in terms of the canonical
+rings of some associated divisors that given surface.
 

### 2015-08-10 surfaces-write-up/surface-write-up.tex
fixed lcm k_i

@@
 Then notate
-\[\ell_i = \lcm_{j\ne i}(k_i).\] 
+\[\ell_i = \lcm_{j\ne i}(k_j).\] 
 Let
@@
 The degree of $D$ is by definition $\deg D = \sum_{i=1}^{n}\alpha_i$.
-For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_i)$
+For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_j)$
 and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
@@
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
-$\ell_i = \lcm_{j \neq i} (k_i)$. Then, $R_D$ is generated in degrees at most $\sum_{i=0}^n \ell_i \bida_i.$
+$\ell_i = \lcm_{j \neq i} (k_j)$. Then, $R_D$ is generated in degrees at most $\sum_{i=0}^n \ell_i \bida_i.$
 
@@
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
-$\ell_i = \lcm_{j \neq i} (k_i)$. Define $\Sigma$ as in Equation
+$\ell_i = \lcm_{j \neq i} (k_j)$. Define $\Sigma$ as in Equation
 ~\eqref{eqn:Sigma-defn} and $\psi$ as ~\eqref{eqn:factor-through-semigroup-ring}. Then, $\ker \psi$ is generated in degrees at most

### 2015-08-15 surfaces-write-up/surface-write-up.tex
edits to introduction

@@
 	and Hirzebruch surfaces. We also give an explicit presentation 		and tight bounds on the
-	generators and relations of the canonical ring of an effective
-	stacky divisor on projective spaces of all dimensions.
+	generators and relations of the canonical ring of effective
+	stacky divisors on projective spaces of any dimensions.
 \end{abstract}
@@
 Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
-Thereby, our techniques would give a bound on generators and relations for
-Hilbert and Siegel modular forms with certain underlying spaces.
+Thereby, our techniques would give a bound on generators and relations for such
+Hilbert and Siegel modular forms.
 
@@
 Let $\bp^m$ have projective coordinates $x_0,\ldots, x_m$. Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate
+Then notate \todo{Peter: It seems a bit weird to me how we define this notation.
+It is used throughout the paper and defined here, but after this point it is never redefined nor is it referenced to this definition.
+Would it be good to make this into an equation and reference the first time it is used in section 2?}
 \[\ell_i = \lcm_{j\ne i}(k_j).\] 
@@
 where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate
+Then notate \todo{Peter: Same comment as above.}
 \[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 

### 2015-08-15 surfaces-write-up/surface-write-up.tex
undid some ungrammatical edits, responded to todo on ells

@@
 	on projective spaces of all dimensions
-	and Hirzebruch surfaces. We also give an explicit presentation 		and tight bounds on the
-	generators and relations of the canonical ring of effective
-	stacky divisors on projective spaces of any dimensions.
+	and Hirzebruch surfaces. We also give
+	an inductive presentation of the canonical ring of 
+	any effective stacky divisor on projective space.
 \end{abstract}
@@
 Thereby, our techniques would give a bound on generators and relations for such
-Hilbert and Siegel modular forms.
+rings of Hilbert and Siegel modular forms.
 
@@
 Let $\bp^m$ have projective coordinates $x_0,\ldots, x_m$. Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate \todo{Peter: It seems a bit weird to me how we define this notation.
-It is used throughout the paper and defined here, but after this point it is never redefined nor is it referenced to this definition.
-Would it be good to make this into an equation and reference the first time it is used in section 2?}
+Then notate \todo{Peter: It seems a bit weird to me how we define this
+notation.  It is used throughout the paper and defined here, but after this
+point it is never redefined nor is it referenced to this definition.  Would it
+be good to make this into an equation and reference the first time it is used
+in section 2?
+
+Aaron: Actually, it is redefined several times later. For example, see the notations and
+conventions at the end of the intro. I think it's defined elsewhere as well.
+It's fine to reference it here and refer to it later
+if you'd like to do that though.
+}
 \[\ell_i = \lcm_{j\ne i}(k_j).\] 

### 2015-08-16 surfaces-write-up/surface-write-up.tex
slightly reworded abstract
edits to section 2

--- 2015-08-10 surfaces-write-up/surface-write-up.tex
@@
 	on projective spaces of all dimensions
-	and Hirzebruch surfaces. We also give an explicit presentation 		and tight bounds on the
-	generators and relations of the canonical ring of an effective
-	stacky divisor on projective spaces of all dimensions.
+	and Hirzebruch surfaces. We also give
+	exact bounds on the degree of generators and relations of the canonical
+	ring of any effective stacky divisor on projective space.
 \end{abstract}
@@
 Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
-Thereby, our techniques would give a bound on generators and relations for
-Hilbert and Siegel modular forms with certain underlying spaces.
+Thereby, our techniques would give a bound on generators and relations for such
+rings of Hilbert and Siegel modular forms.
 
@@
 We shall further assume for this subsection that (possibly after reordering) $f_0,\ldots, f_{m}$ form a
-basis for degree one rational functions on $\bp^m$.
+basis for degree one rational functions on $\bp^m$.  This may necessitate the inclusion of ``Ghost Divisors'' $D_i$ with coefficients $\alpha_i = 0$.
 
@@
 \noindent
-form a spanning set for $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
-of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying
+span $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
+of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation \ref{align:pm-span} and
 \begin{align}
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-~\eqref{align:pm-span} lie in $H^0(\bp^m,dD)$. To complete the proof, it
+~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$, and all functions of that form lie in $H^0(\mathbb{P}^m, dD)$. To complete the proof, it
 suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
-a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \lfloor dD \rfloor }{m}$
+a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \lfloor dD \rfloor }{m}$ \todo{Peter: $\lfloor dD\rfloor$ is a divisor, not a number.  Do we mean $\deg(\lfloor dD \rfloor)$?}
 functions satisfying condition ~\eqref{align:pm-basis}. However we know
@@
 independent. This follows from the assumption that $f_0,\ldots f_n$ form a
-basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$ of degree degree $\lfloor d \deg D \rfloor $
+basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$ of degree $\lfloor d \deg D \rfloor $ \todo{Peter: Why are we looking at monomials in this degree?
+Don't we want to say monomials in degree $d$ or something?}
 form a basis of degree $\lfloor d \deg D \rfloor$ rational functions.
@@
 \deg \vec v = c_i \right\}.	
-\end{align*}
+\end{align*}\todo{Peter: Should we say ``with $c_i$ as in section 2.1?''}
 
@@
 and $j \in \{0,\ldots, m\}$ be the smallest index such that $w_j$ is
-nonzero. Define a partial ordering on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
+nonzero.
+Define a partial ordering on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
+\todo{Peter: Why do we have $i$ defined as the biggest and $j$ defined as the smallest?
+Anyway, I don't believe this is a partial ordering.
+Specifically, I don't believe it satisfies antisymmetry:
+\\
+Let $m=1$.
+$\vec{v}= (1,0), \vec(w) = (2,0)$.
+Then $\vec{w} \prec \vec{w}$ and $\vec{w} \prec{v}$, which by antisymmetry should imply $\vec{v} = \vec{w}$.
+I'm not sure if I am missing something simple in the definition ...
+but this seems to contradict it being a partial order.
+Maybe we don't actually care that it is a partial order though\ldots.}
 \end{defn}

### 2015-08-16 surfaces-write-up/surface-write-up.tex
changed partial ordering to relations

@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$, and all functions of that form lie in $H^0(\mathbb{P}^m, dD)$. To complete the proof, it
+~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$, and all functions of that form lie in $H^0(\mathbb{P}^m, dD)$.
+\todo{Aaron: Peter, what do you mean when you say ``all functions of that form lie in...''? How is
+this different from saying that functions satisfying that equation lie in $H^0$?}
+To complete the proof, it
 suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
-a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \lfloor dD \rfloor }{m}$ \todo{Peter: $\lfloor dD\rfloor$ is a divisor, not a number.  Do we mean $\deg(\lfloor dD \rfloor)$?}
+a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \deg \lfloor dD \rfloor }{m}$
 functions satisfying condition ~\eqref{align:pm-basis}. However we know
-$h^0(\bp^m,dD) = \binom{m+ \lfloor dD \rfloor }{m},$ so it suffices to show
+$h^0(\bp^m,dD) = \binom{m+ \deg \lfloor dD \rfloor }{m},$ so it suffices to show
 that those functions satisfying condition ~\eqref{align:pm-basis} are
 independent. This follows from the assumption that $f_0,\ldots f_n$ form a
-basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$ of degree $\lfloor d \deg D \rfloor $ \todo{Peter: Why are we looking at monomials in this degree?
-Don't we want to say monomials in degree $d$ or something?}
-form a basis of degree $\lfloor d \deg D \rfloor$ rational functions.
+basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$
+of degree $\deg \lfloor d \deg D \rfloor $ \todo{Peter: Why are we looking at
+monomials in this degree?  Don't we want to say monomials in degree $d$ or
+something?
+
+Aaron: You're right it was a typo. I fixed it now though. The monomials
+in this degree are precisely those monomials which
+are a basis for $H^0(dD).$ If we just took monomials in degree d,
+those would only form bases in the case $\deg D = 1$. Here, we're talking
+about a k basis, so the fact that there is a d there doesn't really matter,
+we only care about generatord for the vector space $H^0(dD)$ where $dD$ is some
+arbitrary divisor.
+}
+form a basis of degree $\deg \lfloor d  D \rfloor$ rational functions.
 \end{proof}
@@
 ^n v_i$.
-Let 
+For a given sequence of numbers $c_0, \ldots, c_r$, (which
+we will later take to be the best lower approximations
+for a certain divisor) let 
 \begin{align*}
@@
 \deg \vec v = c_i \right\}.	
-\end{align*}\todo{Peter: Should we say ``with $c_i$ as in section 2.1?''}
+\end{align*}
 
@@
 nonzero.
-Define a partial ordering on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
+Define a relation on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
 \todo{Peter: Why do we have $i$ defined as the biggest and $j$ defined as the smallest?
@@
 \\
-Let $m=1$.
-$\vec{v}= (1,0), \vec(w) = (2,0)$.
-Then $\vec{w} \prec \vec{w}$ and $\vec{w} \prec{v}$, which by antisymmetry should imply $\vec{v} = \vec{w}$.
-I'm not sure if I am missing something simple in the definition ...
-but this seems to contradict it being a partial order.
-Maybe we don't actually care that it is a partial order though\ldots.}
+Let $m=1$.  $\vec{v}= (1,0), \vec(w) = (2,0)$.  Then $\vec{w} \prec \vec{w}$
+and $\vec{w} \prec{v}$, which by antisymmetry should imply $\vec{v} = \vec{w}$.
+I'm not sure if I am missing something simple in the definition ... but this
+seems to contradict it being a partial order.  Maybe we don't actually care
+that it is a partial order though\ldots.
+
+Aaron: Good catch. You're right though, that it's not important
+that it is a partial ordering. I changed it to a relation.
+}
 \end{defn}

### 2015-08-17 surfaces-write-up/surface-write-up.tex
edited david's comments except for a couple todos at the beginning

@@
 \maketitle
-
+\todo{Aaron: Remove labels which are not referenced}
+\todo{Aaron: Make sure indexing at 0 is correct in projective space
+section, particularly toward the end}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
+\textbf{canonical ring} is $R(X, D) \colon = \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
 track of degree.
@@
 \begin{align*}
-	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
+	\overline {\mathscr M}_g(\alpha) \colon = \bigoplus_{d \geq 0} u^d H^0 \left(
 	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
@@
 \[
-	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
+	R_D \colon = \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
 \]
@@
 \label{thm:proj-generators-relations}
-Let $\bp^m$ have projective coordinates $x_0,\ldots, x_m$. Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where $\alpha_i = \frac{c_i}{k_i}$.
+Let $\bp^m$ have projective coordinates $x_0,\ldots, x_m$. Let
+$f_0, \ldots, f_n$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
+for $1 \leq i \leq n$ we have $D_i = V(f_i)$ and $\deg(f_i) = a_i,$ and such that $f_0,\ldots, f_m$ are independent linear polynomials in $x_0, \ldots, x_m$. 
+Let $D =
+\sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where
+$\alpha_i = \frac{c_i}{k_i}$.
 Then notate 
 \[\ell_i = \lcm_{j\ne i}(k_j).\] 
-Let
-$f_0, \ldots, f_n$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
-$D_i = V(f_i)$ for all $i$, $\deg(f_i) = a_i,$ and $f_0,\ldots, f_m$ are independent linear polynomials in $x_0, \ldots, x_m$. 
 Then $R_D$ is generated in degrees at most 
@@
 \label{thm:hirz-generators-relations}
-Let $u,v,z,w$ be the coordinates for the Hirzebruch surface $\hirz_m$, as described at the beginning of Section ~\ref{sec:hirz}. Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq \otimes_\bq \di \hirz_m$ 
-where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate
-\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 
-Let $D_i =
+Let $u,v,z,w$ be the coordinates for the Hirzebruch surface
+$\hirz_m$, as described at the beginning of Section
+~\ref{sec:hirz}. For $1 \leq i \leq n$, let $D_i =
 V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
@@
 linear polynomials in $w$ and $x$.
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq
+\otimes_\bq \di \hirz_m$ 
+where $\alpha_i = \frac{c_i}{k_i}$.
+Then notate
+\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 
 Then $R_D$ is generated in degrees at most
@@
 \noindent
-Together, Theorems \ref{thm:proj-generators-relations} and \ref{thm:hirz-generators-relations} provide bounds on generators and relations for the canonical ring of $\bq$-divisors of all minimal rational surfaces.
-Section \ref{sec:conc} concludes the paper and discusses further questions.
+By the classification of minimal rational surfaces
+as either $\bp^2$ or a Hirzebruch surface \cite{eisenbud-harris:minimal},
+Theorems \ref{thm:proj-generators-relations} and
+\ref{thm:hirz-generators-relations} provide bounds on generators
+and relations for the canonical ring of any $\bq$-divisor on any
+minimal rational surface. Section \ref{sec:conc} discusses further questions.
 
 \ssec{Notations and Conventions}
-Notate a (Weil) $\bq$-divisor
+Let $D$ be a (Weil) $\bq$-divisor of the form
 \begin{align*}
@@
 \noindent
-where $\alpha_i \in \bq$ and $D_i \in \di X$ is an integral codimension 1 closed subscheme of $X$.
-When it is convenient to do so, we shall sometimes start the indexing at $0$, so that $i$ runs from $0$ to $n$.
-The degree of $D$ is by definition $\deg D = \sum_{i=1}^{n}\alpha_i$.
-For such a divisor $D$ with $\alpha_i = \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_j)$
+where $\alpha_i \in \bq$ and $D_i \in \di X$ is an integral
+codimension 1 closed subscheme of $X$. When it is convenient to do
+so, we shall sometimes start the indexing at $0$, so that $i$ runs
+from $0$ to $n$. Define the degree of $D$ by $\deg D \colon =
+\sum_{i=1}^{n}\alpha_i$. For such a divisor $D$ with $\alpha_i =
+\frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_j)$
 and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
-\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
+\rfloor \in \di X$ is defined to be $\lfloor D \rfloor \colon = \sum_{i = 1}^{n}
 \lfloor \alpha_i \rfloor P_i$. Let $
-	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
+	R_D \colon = \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
 denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
 is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
-$\fr(r) := r - \lfloor r
-\rfloor$ denote the fractional part of $r$.
-\section{Canonical Rings on Projective Space}
+$\fr(r) \colon = r - \lfloor r
+\rfloor$ denote the fractional part of $r$. Throughout, we
+shall work over a fixed base field $\bk$.
+
+\section{Canonical Rings of Projective Space}
 \label{sec:proj}
-In this section, we bound the degrees of generators and relations for divisors
-on $\bp^m$, for all $m \geq 1$ in Theorem ~\ref{thm:proj-effective-intro}. 
+Let $\bk$ be a field and let $\bp^m$ denote $m$-dimensional
+projective space over $\bk$. In this section, we bound the degrees
+of generators and relations for divisors
+on $\bp^m$, for all $m \geq 1$ in Theorem
+~\ref{thm:proj-effective-intro}. 
 The $\bp^1$ case restricts to the results of
@@
 
-For the remainder of this section, we shall fix $m \geq 1$ and choose an
-isomorphism $\bp^m \cong \proj V$ for some vector space $V$ with basis $x_0,\ldots, x_m$.  We will think of $x_i$ as a rational section of $H^0(\bp^m,
-\sco_{\bp^m})$ of degree 1.
+For the remainder of this section, we shall fix $m \geq 1$ and
+choose an
+isomorphism $\bp^m \cong \proj V$ for some vector space $V$ with
+basis $x_0,\ldots, x_m$.
 
@@
 canonical rings on projective space, we first
-describe a particular choice of basis for $R_D$ as a $\bk$ vector space.
-
-Write
-\begin{align*}
+describe a particular choice of basis for $R_D$ as a $\bk$ vector
+space.
+
+Write \begin{align*}
 	D = \sum_{i=0}^{n}\alpha_i D_i.
 \end{align*}
-where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. Let $D_i$ be
-Cartier divisors such that $D_i = V(f_i)$.
-We shall further assume for this subsection that (possibly after reordering) $f_0,\ldots, f_{m}$ form a
-basis for degree one rational functions on $\bp^m$.  This may necessitate the inclusion of ``Ghost Divisors'' $D_i$ with coefficients $\alpha_i = 0$.
+where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. 
+Choose $f_i$ so that $D_i = V(f_i)$.
+We shall further assume for this subsection that (possibly after
+reordering) $f_0,\ldots, f_{m}$ are $m$ independent linear forms
+on $\bp^m$.  This may necessitate the inclusion of ``Ghost Divisors'' $D_i$ with coefficients $\alpha_i = 0$.
 
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=1}^n f_i^{c_i} \in (R_D)_d$ satisfying
+The functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ satisfying
 
@@
 \label{align:pm-span}
-\sum_{i=0}^{n} c_i \cdot \bida_i = 0 && \text{ and } &&c_i \geq \lfloor \alpha_i d\rfloor	
+\sum_{i=0}^{n} c_i \cdot \bida_i = 0 && \text{ and } &&c_i \geq
+-\lfloor d\alpha_i \rfloor	
 \end{align}
@@
 \noindent
-span $H^0(\bp^m, dD)$ over $k$. Furthermore, functions 
+span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, functions 
 of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation \ref{align:pm-span} and
@@
 \noindent
-form a basis for $H^0(\bp^m, dD)$ over $k$.
+form a basis for $H^0(\bp^m, dD)$ over $\bk$.
 \end{prop}
@@
 suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
-a basis of $H^0(\bp^m,dD)$. Note that there $\binom{m+ \deg \lfloor dD \rfloor }{m}$
+a basis of $H^0(\bp^m,dD)$. Note that there are $\binom{m+ \deg \lfloor dD \rfloor }{m}$
 functions satisfying condition ~\eqref{align:pm-basis}. However we know
@@
 that those functions satisfying condition ~\eqref{align:pm-basis} are
-independent. This follows from the assumption that $f_0,\ldots f_n$ form a
-basis of degree 1 rational functions, and so all monomials in $f_0,\ldots, f_m$
+independent. This follows from the assumption that $f_0,\ldots f_m$ form a
+basis of linear forms, and so all monomials in $f_0,\ldots, f_m$
 of degree $\deg \lfloor d \deg D \rfloor $ \todo{Peter: Why are we looking at
@@
 those would only form bases in the case $\deg D = 1$. Here, we're talking
-about a k basis, so the fact that there is a d there doesn't really matter,
+about a $\bk$ basis, so the fact that there is a d there doesn't really matter,
 we only care about generatord for the vector space $H^0(dD)$ where $dD$ is some
@@
 \begin{convention}
-Let $[x_0, \ldots, x_m]$ be coordinates for $\bp^m$. Let
+Let $\bp^m \cong \proj \bk[x_0, \ldots, x_m]$. Let
 $\vec{v} = (v_0, \ldots, v_m) \in \bz^{m + 1}$.  Then write
 \[
-	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}.
+	x^{\vec{v}} \colon = \prod_{i = 0}^{m} x_i^{v_i}.
 \]
@@
 \label{defn:vec-sum}
-For $\vec{v} \in \bz^n$, denote $\deg \vec{v} := \sum_{i = 0}
+For $\vec{v} \in \bz^n$, denote $\deg \vec{v} \colon = \sum_{i = 0}
 ^n v_i$.
@@
 \begin{align*}
-	\mss_i := \left \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
+	\mss_i \colon = \left \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
 \deg \vec v = c_i \right\}.	
@@
 \noindent
-\end{defn}
+.\end{defn}
 
@@
 the generators and relations of $R_D$ in terms of $R_{D'}$ 
-in the case that $D' = R_D + \alpha H$ for $H$ a hyperplane.
+in the case that $D' = R_D + \alpha H$ for $H$ a hyperplane and
+$\alpha$ positive.
 The statement and proofs are natural generalizations of
@@
 \otimes \di \bp^m$ and $D = D' + \alpha H$, with $\alpha =
-\frac{p}{q} \in \bq$ and $H := V(x_k)$ a hyperplane of $\bp^m$.
+\frac{p}{q} \in \bq_{>0}$ and $H \colon = V(x_k)$ a hyperplane of $\bp^m$.
 Let
@@
 	0 = \frac{c_0}{d_0} <
-	\frac{c_1}{d_1} < \ldots < \frac{c_r}{d_r} = \frac{p}{q}
+	\frac{c_1}{d_1} < \cdots < \frac{c_r}{d_r} = \frac{p}{q}
 \]
@@
 has a minimal presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
-{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
+{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} \colon = \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $1 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
@@
 We will first check that $F^{\vec v}_i$ determine a system of minimal
-generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} : \deg \vec{v} =
+generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} \colon \deg \vec{v} =
 \left\lfloor
@@
 products of generators in adjacent degrees where $h$
-depends on $i$ and $ j$, so we notate $h_{i, j} := h \in \{1, \ldots, r\}$. We 
+depends on $i$ and $ j$, so we notate $h_{i, j} \colon = h \in \{1, \ldots, r\}$. We 
 also have that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
@@
 If $C$ is of degree $\pdeg$, consider the Veronese embedding
-$\nu_\pdeg^m: \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
+$\nu_\pdeg^m \colon \bp^m \rightarrow \bp^{\binom{m+\pdeg}{\pdeg}-1}$
 so that the image of $C$ is the intersection of 
@@
 For the remainder of this section, we shall make the additional assumption that 
-\begin{align} \label{eqn:pm-basis-assumption} f_0, \ldots, f_{m} \text{ form a
-	} \bk \text{ basis of all degree 1 functions.} \end{align}
+\begin{align} \label{eqn:pm-basis-assumption} f_0, \ldots, f_{m}
+	\text{ are $m$ independent linear forms.} \end{align}
 
@@
 This example further generalizes to the following situation:
-Suppose $D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
-\otimes \bq,$ where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm
+Suppose 
+\[
+	D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
+\otimes \bq,
+\]
+where $\deg D_i = \bida_i$ and $\deg D = \frac{1}{\lcm
 _{0 \leq i \leq n}(\den_i \cdot \bida_i)}$. Then, if $D_i = V(f_i)$
@@
 
-The problem that a divisor may be
-expressible as functions in $m$ of the $m+1$ variables on $\bp^m$, 
-as illustrated in Example ~\ref{eg:hyperplane}, can easily be circumvented by adding in ``ghost
+As illustrated in Example ~\ref{eg:hyperplane}, 
+when all components in the support of divisor can be 
+written in terms of $m$ of the $m+1$ variables on $\bp^m$,
+we cannot hope to bound the degree of generation
+by anything less than the sum of the least common multiples of
+the denominators. This issue can easily be circumvented by adding in ``ghost
 points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
@@
 \begin{align*}
-	\Sigma := \left \{(d, c_1, \ldots, c_n) \in \bz^{n + 1} : c_i \geq -
+	\Sigma \colon = \left \{(d, c_1, \ldots, c_n) \in \bz^{n + 1} \colon c_i \geq -
 	d \alpha_i, 1 \leq i \leq n \text{ and } \sum_{i = 1}^{n} a_i =
-	\sum_{i	= 1}^{n}b_i = 0 \right \}
+	\sum_{i	= 1}^{n}b_i = 0 \right \}.
 \end{align*}
@@
 
+\noindent
 with $w_1, \ldots, w_t \in \bz_{\geq 0}$,
@@
 By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
-{i = 1}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) := r - \lfloor r
+{i = 1}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) \colon = r - \lfloor r
 \rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 1}
@@
 \begin{lem} \label{lem:proj-generators}
-Let $D = \sum_{i=1}^{n} \alpha_i D_i \in \bq \otimes \di \bp^m,$ where
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes \di \bp^m,$ where
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
@@
 \begin{align}\label{eqn:Sigma-defn}
-	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
+	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} \colon c_i \geq - d
 \alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
@@
 \bida_i$ (given by Lemma ~\ref{lem:proj-generators}), and let 
-$\phi:k[w_1, \ldots w_r] \to R_D$ be the natural surjection.
+$\phi \colon \bk[w_1, \ldots w_r] \to R_D$ be the natural surjection.
 For the remainder of the section, we aim to bound the degree of relations
@@
 \[
-	\bk[\Sigma] =  \langle u^d z_0^{c_0} \cdots z_n^{c_n} : c_i \in
+	\bk[\Sigma] =  \langle u^d z_0^{c_0} \cdots z_n^{c_n} \colon c_i \in
 \bz, \; c_i \geq -d \alpha_i, \mbox{ and }\sum_{i=0}^{n} \bida_i c_i =
@@
 Lex $X$ be an arbitrary scheme and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
-surjection $\phi: \bk[w_1,w_2,\ldots, w_r] \rightarrow R_D$ given by $w_i
+surjection $\phi\colon \bk[w_1,w_2,\ldots, w_r] \rightarrow R_D$ given by $w_i
 \mapsto p_i(f_0, \ldots, f_n),$ where $p_i$ is a monomial in $f_0,\ldots, f_n$.
@@
 ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
-in a canonical form $\lambda + \sum_{i=1}^{r}e_i$. Now, let $\lambda_0 :=
+in a canonical form $\lambda + \sum_{i=1}^{r}e_i$. Now, let $\lambda_0 \colon =
 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be
@@
 
-\section{Canonical Rings on Hirzebruch surfaces}
+\section{Canonical Rings of Hirzebruch surfaces}
 \label{sec:hirz}
-In this section, the main aim is to prove Theorem
+The aim of this section is to prove Theorem
 ~\ref{thm:hirz-generators-relations}, bounding the degree of
@@
 where $\mathbb G_m$ is the multiplicative subgroup of $\ba^1$, and the action of $\mathbb G_m \times \mathbb G_m$ is given by
-$(\lambda, \mu) \cdot (u:v; z:w) \mapsto (\lambda u: \lambda v; \mu z: \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{zhao:counting-cubic}. Hence, one can think of
+$(\lambda, \mu) \cdot (u\colon v; z\colon w) \mapsto (\lambda u\colon \lambda v; \mu z\colon \lambda^{-m} \mu w),$ as described in \cite[p.~ 6]{zhao:counting-cubic}. Hence, one can think of
 $\hirz_m$ as a $\bp^1$ bundle where $u,v$ are the coordinates on
@@
 Define 
-\begin{equation}
-\label{eqn:define-T=(D)}
+\begin{equation*}
 	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
 \alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
-\end{equation}
-
-\begin{equation}
-\label{eqn:define-T+(D)}
-	\Tp(D) = \left\{ i \in \{1, \ldots, n\}:  \vphantom{\sum_{k = 1}^n} 
+\end{equation*}
+
+\begin{equation*}
+	\Tp(D) = \left\{ i \in \{1, \ldots, n\}\colon  \vphantom{\sum_{k = 1}^n} 
 	\bida_i \sum_{k = 1}^n \alpha_k \bidb_k > \bidb_i \sum_{k = 1}^n \alpha_k \bida_k 
 \right\},
-\end{equation}
+\end{equation*}
 
@@
 and
-\begin{equation}
-\label{eqn:define-T-(D)}
-	\Tm(D) = \left\{ i \in \{1, \ldots, n\}: \bida_i \sum_{k = 1}^n \alpha_k
+\begin{equation*}
+	\Tm(D) = \left\{ i \in \{1, \ldots, n\}\colon \bida_i \sum_{k = 1}^n \alpha_k
 	\bidb_k < \bidb_i \sum_{k=1}^n \alpha_k \bida_k \right\}.
-\end{equation}
+\end{equation*}
 \end{defn}
@@
 \begin{equation}\label{eqn:def-sigma}
-	\rho := \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
+	\rho \colon = \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
 	{i \in \Tp(D) \\ j\in \Tm(D)}} (\bida_i \bidb_j - \bida_j \bidb_i)
@@
 \begin{align*}
-	\Sigma = \{ (d', c_1', \ldots, c_n') \in \bz_{\geq 0}^{n+1} : c_i' \ge - d
+	\Sigma = \left\{ (d', c_1', \ldots, c_n') \in \bz_{\geq 0}^{n+1} \colon c_i' \ge - d
 \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i' \bida_i = \sum_{i =
-1}^n c_i' \bidb_i = 0 \}.	
+1}^n c_i' \bidb_i = 0 \right \}.	
 \end{align*}
@@
 \begin{align*}
-	\Sigma_1 = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge -
+	\Sigma_1 = \left\{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} \colon c_i \ge -
 d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0
-\},
+\right\},
 \end{align*}
@@
 \[
-	\epsilon_i := (1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
+	\epsilon_i \colon = \left(1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
 	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
-	\ldots, -\alpha_n).
+	\ldots, -\alpha_n \right).
 \]
@@
 Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $\epsilon_1, \ldots \epsilon_n$.
-We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
+We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H \colon =
 V(\sum_{i=1}^n \bida_i x_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap (\Sigma_1
@@
 \begin{equation}\label{eqn:epsilon_i}
-	e_i := d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
+	e_i \colon = d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
 	%\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
@@
 \begin{align}\label{eqn:epsilon_i,j}
-e_{i,j} := &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
+e_{i,j} \colon = &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
 &+ \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
@@
 
-Let $w_1, \ldots w_r$ be the generators of $R_D$ in degrees less than $\rho$
+Let $w_1, \ldots, w_r$ be the generators of $R_D$ in degrees less than $\rho$
 (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the
@@
 \[
-	\bk[\Sigma] = \left \langle u^d z_1^{c_1} \cdots z_n^{c_n} : c_i \geq -d
+	\bk[\Sigma] = \left \langle u^d z_1^{c_1} \cdots z_n^{c_n} \colon c_i \geq -d
 	\alpha_i, \sum_{i=1}^{n} \bida_i c_i = \sum_{i=1}^{n} \bidb_i c_i
@@
 \[
-	\tau : = \rho
+	\tau \colon = \rho
 	+ \max \left(\max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
@@
 
-Consider a relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ and let it correspond to the lattice point $\sigma: = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
+Consider a relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ and let it correspond to the lattice point $\sigma\colon = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
 Then we can write $\sigma$ as a sum of $s_j e_j$'s for $j\in
 \Te$ and $s_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
-For convenience, define $d_j := \deg e_j$ (when it exists) and let the $j^{th}$
+For convenience, define $d_j \colon = \deg e_j$ (when it exists) and let the $j^{th}$
 component of $e_j$ be $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$.
-Also, let $d_{j,k} := \deg e_{j,k}$ (when it exists) and let the $j^{th}$ component of $e_{j,k}$ be $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and the $k^{th}$
+Also, let $d_{j,k} \colon = \deg e_{j,k}$ (when it exists) and let the $j^{th}$ component of $e_{j,k}$ be $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and the $k^{th}$
 component be $-\alpha_k d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
@@
 
-If $i\in \Te$ define $r_i := \frac{1}{\kappa_i}$.
+If $i\in \Te$ define $r_i \colon = \frac{1}{\kappa_i}$.
 If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
-For $j\ne i$, define $r_j := 0.$ For all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} := 0$.
+For $j\ne i$, define $r_j \colon = 0.$ For all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} \colon = 0$.
 Define $E$ by
 \begin{equation}\label{eqn:hirz-E-translation}
-	E := \sum_{j\in \Te} (s_j - \lfloor s_j - r_j \rfloor) e_j + \sum_{\substack{j \in 
+	E \colon = \sum_{j\in \Te} (s_j - \lfloor s_j - r_j \rfloor) e_j + \sum_{\substack{j \in 
 	\Tp \\ k \in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k} \rfloor) e_{j,k}.
@@
 \begin{equation}\label{eqn:defn-lambda}
-	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
+	\lambda \colon = \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
  \end{equation}

### 2015-08-17 surfaces-write-up/surface-write-up.tex
responded to shouwu's comments

@@
 \label{thm:proj-generators-relations}
-Let $\bp^m$ have projective coordinates $x_0,\ldots, x_m$. Let
-$f_0, \ldots, f_n$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that
-for $1 \leq i \leq n$ we have $D_i = V(f_i)$ and $\deg(f_i) = a_i,$ and such that $f_0,\ldots, f_m$ are independent linear polynomials in $x_0, \ldots, x_m$. 
 Let $D =
-\sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ where
-$\alpha_i = \frac{c_i}{k_i}$.
-Then notate 
+\sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ 
+with $\alpha_i = \frac{c_i}{k_i}\in \bq.$ Let $\bp^m \cong \proj \bk[x_0,\ldots, x_m]$ with
+$f_0, \ldots, f_n \in \bk[x_0, \ldots, x_m]$ such that
+for $1 \leq i \leq n$ we have $D_i = V(f_i)$ and $\deg(f_i) = a_i.$
+Further, after reordering the terms of $D$, and possibly adding in
+$D_i$ with coefficient $\alpha_i = 0$, assume that $f_0,\ldots, f_m$ are independent linear
+polynomials in $x_0, \ldots, x_m$. 
+Define 
 \[\ell_i = \lcm_{j\ne i}(k_j).\] 
@@
 \noindent
-In Section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces and prove the following theorem:
+In Section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces. Recall that for each $m \geq 0$ we can define the
+Hirzebruch surface $F_m := \proj(\sym^\bullet \sco_{\bp^1} \oplus
+\sco_{\bp^1}(m)),$ or as a quotient of an open subscheme of
+$\ba^4$ by a 
+kweighted action, as is done in the
+beginning of Section \ref{sec:hirz}.
+Note that Hirzebruch surfaces are normal
+and locally factorial, being $\bp^1$ bundles over
+$\bp^1$, and therefore the natural map from Cartier
+divisors to Weil divisors is an isomorphism.
+In other words, all Cartier divisors arise as the zero locus
+of a section of some line bundle. The analogous fact for
+projective space was also implicitly used in Theorems
+~\ref{thm:proj-effective-intro} and ~\ref{thm:proj-generators-relations}.
+
 \begin{restatable}{thm}{hirzrestate}
 \label{thm:hirz-generators-relations}
+Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq
+\otimes_\bq \di \hirz_m$ 
+where $\alpha_i = \frac{c_i}{k_i}$.
 Let $u,v,z,w$ be the coordinates for the Hirzebruch surface
@@
 ~\ref{sec:hirz}. For $1 \leq i \leq n$, let $D_i =
-V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further suppose $f_1$ and $f_2$ are
+V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further, after reordering
+the $D_i$ and possibly adding $D_i$ with corresponding $\alpha_i = 0$, suppose $f_1$ and $f_2$ are
 independent linear
@@
 linear polynomials in $w$ and $x$.
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq
-\otimes_\bq \di \hirz_m$ 
-where $\alpha_i = \frac{c_i}{k_i}$.
-Then notate
+Define
 \[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 
@@
 from $0$ to $n$. Define the degree of $D$ by $\deg D \colon =
-\sum_{i=1}^{n}\alpha_i$. For such a divisor $D$ with $\alpha_i =
+\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. For such a divisor $D$ with $\alpha_i =
 \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_j)$

### 2015-08-17 surfaces-write-up/surface-write-up.tex
edits to my prevoius edits

@@
 section, particularly toward the end}
+\todo{Aaron: Make sure to use $\bk$ instead of $k$ for the field}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent
-In Section \ref{sec:hirz}, we shift our attention to Hirzebruch Surfaces. Recall that for each $m \geq 0$ we can define the
+In Section \ref{sec:hirz}, we shift our attention to Hirzebruch surfaces. Recall that for each $m \geq 0$ we can define the
 Hirzebruch surface $F_m := \proj(\sym^\bullet \sco_{\bp^1} \oplus
@@
 $\ba^4$ by a 
-kweighted action, as is done in the
+weighted action, as is done in the
 beginning of Section \ref{sec:hirz}.
@@
 In other words, all Cartier divisors arise as the zero locus
-of a section of some line bundle. The analogous fact for
+of a section of some line bundle. We implicitly use this in the
+statement of the following theorem. The analogous fact for
 projective space was also implicitly used in Theorems
@@
 \ssec{Notations and Conventions}
+We will use $m \in \bz$ to index the dimension of a given projective
+space $\bp^m$ or the type of the hirzebruch surface $\hirz_m$.
 Let $D$ be a (Weil) $\bq$-divisor of the form
@@
 \noindent
-where $\alpha_i \in \bq$ and $D_i \in \di X$ is an integral
+where $n \in \bz$ indexes the number of irreducible divisors in 
+the above expansion of $D$, $\alpha_i \in \bq$, and $D_i \in \di X$ is an integral
 codimension 1 closed subscheme of $X$. When it is convenient to do
@@
 \begin{align} \label{eqn:pm-basis-assumption} f_0, \ldots, f_{m}
-	\text{ are $m$ independent linear forms.} \end{align}
+	\text{ are independent linear forms.} \end{align}
 

### 2015-08-17 surfaces-write-up/surface-write-up.tex
added F_n are regular

@@
 beginning of Section \ref{sec:hirz}.
-Note that Hirzebruch surfaces are normal
+Note that Hirzebruch surfaces are regular, normal,
 and locally factorial, being $\bp^1$ bundles over

### 2015-08-17 surfaces-write-up/surface-write-up.tex
minor change to thm 1.1 of shou-wu
fixing some todos, and more edits to section 2

@@
 \maketitle
-\todo{Aaron: Remove labels which are not referenced}
+\todo{Aaron: Remove labels which are not referenced
+\\
+Peter: I did this for a few of them, but I'm wondering what the purpose of this is.  It appears the same in the PDF either way right?}
 \todo{Aaron: Make sure indexing at 0 is correct in projective space
 section, particularly toward the end}
-\todo{Aaron: Make sure to use $\bk$ instead of $k$ for the field}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent
-is generated in degrees at most $\max_{1 \leq i \leq n}{k_i}$ with
-relations generated in degrees at most $2 \max_{1 \leq i \leq n}{k_i}$
+is generated in degrees at most $\max_{0 \leq i \leq n}{k_i}$ with
+relations generated in degrees at most $2 \max_{0 \leq i \leq n}{k_i}$
 \end{restatable}
@@
 	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes \bq.
-\end{align*}
+\end{align*}\todo{Peter: Do we want this indexing from 0 or 1, since we use 0 for $\bp^m$ and $1$ for $\mathbb{F}_m$.}
 
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$, and all functions of that form lie in $H^0(\mathbb{P}^m, dD)$.
+~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$, and all functions of $H^0(\mathbb{P}^m, dD)$ are of that form.
 \todo{Aaron: Peter, what do you mean when you say ``all functions of that form lie in...''? How is
-this different from saying that functions satisfying that equation lie in $H^0$?}
+this different from saying that functions satisfying that equation lie in $H^0$?
+\\
+Peter:  Oops, meant to write the converse statement, but accidently just restated the original statement-it's fixed now.}
 To complete the proof, it
@@
 basis of linear forms, and so all monomials in $f_0,\ldots, f_m$
-of degree $\deg \lfloor d \deg D \rfloor $ \todo{Peter: Why are we looking at
-monomials in this degree?  Don't we want to say monomials in degree $d$ or
-something?
-
-Aaron: You're right it was a typo. I fixed it now though. The monomials
-in this degree are precisely those monomials which
-are a basis for $H^0(dD).$ If we just took monomials in degree d,
-those would only form bases in the case $\deg D = 1$. Here, we're talking
-about a $\bk$ basis, so the fact that there is a d there doesn't really matter,
-we only care about generatord for the vector space $H^0(dD)$ where $dD$ is some
-arbitrary divisor.
-}
+of degree $\deg \lfloor d \deg D \rfloor $
 form a basis of degree $\deg \lfloor d  D \rfloor$ rational functions.
@@
 Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
-stated explicitly later, in the case that $D = \alpha_1 D_1$ is supported on a single hypersurface, the relations in
+stated explicitly later, in the case that $D = \alpha_0 D_0$ is supported on a single hypersurface, the relations in
 Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to
@@
 and $j \in \{0,\ldots, m\}$ be the smallest index such that $w_j$ is
-nonzero.
-Define a relation on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
-\todo{Peter: Why do we have $i$ defined as the biggest and $j$ defined as the smallest?
-Anyway, I don't believe this is a partial ordering.
-Specifically, I don't believe it satisfies antisymmetry:
-\\
-Let $m=1$.  $\vec{v}= (1,0), \vec(w) = (2,0)$.  Then $\vec{w} \prec \vec{w}$
-and $\vec{w} \prec{v}$, which by antisymmetry should imply $\vec{v} = \vec{w}$.
-I'm not sure if I am missing something simple in the definition ... but this
-seems to contradict it being a partial order.  Maybe we don't actually care
-that it is a partial order though\ldots.
-
-Aaron: Good catch. You're right though, that it's not important
-that it is a partial ordering. I changed it to a relation.
-}
+nonzero. Define a relation on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
 \end{defn}
@@
 {{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} \colon = \frac{u^{d_i}
-x^{\vec{v}}}{x_k^{c_i}}$ where $1 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+x^{\vec{v}}}{x_k^{c_i}}$ where $0 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
 with $\deg \vec v = c_i$. Furthermore, it has
@@
 all of $R_D$ over $R_{D'}$, we obtain the
-relations $G_{i, j}^{\vec{v}, \vec{w}}$.
+relations $G_{i, j}^{\vec{v}, \vec{w}}$ \todo{Peter: hmm... this doesn't say much about how we get the $G_{i,j}$'s.}.
 We derive the relations
@@
 \label{prop:cone-generation}
-Let $n \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$, and let
-$a_i, b_i \in \bz$ with $1 \leq i \leq n.$ Define
+Let $n \in \bz,$ let $\alpha_0, \ldots, \alpha_n \in \bq$, and let
+$a_i, b_i \in \bz$ with $0 \leq i \leq n.$ Define
 \begin{align*}
-	\Sigma \colon = \left \{(d, c_1, \ldots, c_n) \in \bz^{n + 1} \colon c_i \geq -
-	d \alpha_i, 1 \leq i \leq n \text{ and } \sum_{i = 1}^{n} a_i =
+	\Sigma \colon = \left \{(d, c_0, \ldots, c_n) \in \bz^{n + 2} \colon c_i \geq -
+	d \alpha_i, 0 \leq i \leq n \text{ and } \sum_{i = 0}^{n} a_i =
 	\sum_{i	= 1}^{n}b_i = 0 \right \}.
@@
 \noindent
-Suppose $e_1, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_1^i,
+Suppose $e_0, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_0^i,
 \ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
 i.e.~ $\Sigma$ is contained in the $\bq_{\geq 0}$ span of
-$e_1, \ldots, e_t$.
+$e_0, \ldots, e_n$.
 
@@
 	\label{eqn:sigma-canonical-form}
-	\sigma = \lambda + \sum_{i = 1}^{t} w_i e_i
+	\sigma = \lambda + \sum_{i = 0}^{t} w_i e_i
 \end{equation}
@@
 \noindent
-with $w_1, \ldots, w_t \in \bz_{\geq 0}$,
-$0 \leq s_i < 1$, and $\lambda = \sum_{i = 1}^{r} s_i e_i$ 
+with $w_1, \ldots, w_t \in \bz_{\geq 0}$ \todo{Peter: Replace $w$ with a different letter, since we use it later to mean something else.},
+$0 \leq s_i < 1$, and $\lambda = \sum_{i = 0}^{r} s_i e_i$ 
 so that the
@@
 By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
-{i = 1}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) \colon = r - \lfloor r
-\rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 1}
-^{t} \fr(r_i)$. Whence, we can write $\sigma = \lambda + \sum_{i = 1}
+{i = 0}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) \colon = r - \lfloor r
+\rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 0}
+^{t} \fr(r_i)$. Whence, we can write $\sigma = \lambda + \sum_{i = 0}
 ^{t} \lfloor r_i \rfloor e_i.$ Consequently, $\sigma$ lies in the
-$\bz_{\geq 0}$ span of $\lambda, e_1, \ldots, e_t$, which all have
-first coordinate less than $\sum_{i=1}^{t} r_i$. Ergo, $\Sigma$ is
+$\bz_{\geq 0}$ span of $\lambda, e_0, \ldots, e_t$, which all have
+first coordinate less than $\sum_{i=0}^{t} r_i$. Ergo, $\Sigma$ is
 generated by elements whose first coordinate is less than
-$\sum_{i = 1}^{t} r_i$.
+$\sum_{i = 0}^{t} r_i$.
 \end{proof}
@@
 \begin{align}\label{eqn:Sigma-defn}
-	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} \colon c_i \geq - d
-\alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
+	\Sigma = \left \{(d, c_0, \ldots, c_n) \in \bz^{n+2} \colon c_i \geq - d
+\alpha_i, \; 0 \leq i \leq n, \text{ and } \sum_{i=0}^{n} \ell_i \bida_i = 0
 \right \}.
@@
 \begin{equation}\label{eqn:e-i-proj}
-	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
+	e_i = \left(\ell_i \bida_i, - \alpha_0 \ell_i \bida_i, \ldots
 -\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j,
@@
 \end{equation}
-for each $i\in \{1, \ldots n\}$.
+for each $i\in \{0, \ldots n\}$.
 Therefore, applying Proposition ~\ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
@@
 Lex $X$ be an arbitrary scheme and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
-surjection $\phi\colon \bk[w_1,w_2,\ldots, w_r] \rightarrow R_D$ given by $w_i
+surjection $\phi\colon \bk[w_1,\ldots, w_r] \rightarrow R_D$ given by $w_i
 \mapsto p_i(f_0, \ldots, f_n),$ where $p_i$ is a monomial in $f_0,\ldots, f_n$.
@@
 Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
-extremal rays $e_1,\ldots, e_r$ in degrees $d_1, \ldots, d_r$ then $\ker \chi$
-is generated in degrees at most $2(\sum_{i=1}^{r}d_r-1)$.
+extremal rays $e_0,\ldots, e_n$ in degrees $d_0, \ldots, d_n$ then $\ker \chi$
+is generated in degrees at most $2(\sum_{i=0}^{n}d_i-1)$.
 \end{lem}
 \begin{proof}
-Since $e_1, \ldots, e_r$ are extremal rays, by Proposition
+Since $e_0, \ldots, e_n$ are extremal rays, by Proposition
 ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
-in a canonical form $\lambda + \sum_{i=1}^{r}e_i$. Now, let $\lambda_0 \colon =
+in a canonical form $\lambda + \sum_{i=0}^{n} r_i e_i$. Now, let $\lambda_0 \colon =
 0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be
-written in the form $\lambda_i = \sum_{i=1}^{r}r_i e_i$ with $0 \leq r_i < 1.$
+written in the form $\lambda_i = \sum_{i=0}^{n}r_i e_i$ with $0 \leq r_i < 1.$ \todo{Peter: This sentence needs rephrasing.  1: misuse of $i$ as index.  2: misuse of $m$ as index ($\bp^m$).}
 Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in
 the above canonical form, yielding a relation in degree at most $\deg \lambda_i
-+ \deg \lambda_j \leq 2 \cdot \left( \sum_{i=1}^{r}d_r -1 \right).$
++ \deg \lambda_j \leq 2 \cdot \left( \sum_{i=0}^{n}d_i -1 \right).$
 Furthermore, these relations generate all relations, as one can apply a
 sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
-$\sigma = \lambda + \sum_{i=1}^{r}w_i e_i$ as in Equation
+$\sigma = \lambda + \sum_{i=0}^{n}w_i e_i$ as in Equation
 ~\eqref{eqn:sigma-canonical-form}.
@@
 \begin{proof}
-We claim there exist $\beta_0, \ldots, \beta_n \in k[\Sigma]$
+We claim there exist $\beta_0, \ldots, \beta_n \in \bk[\Sigma]$
 such that $\ker \psi$ is generated by
@@
 by 
-\begin{equation}\label{eqn:epsilon_i}
+\begin{equation}
 	e_i \colon = d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
@@
 by
-\begin{align}\label{eqn:epsilon_i,j}
+\begin{align}
 e_{i,j} \colon = &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
@@
 (as given by Lemma ~\ref{lem:hirz-generators}), and let $\phi$ be the
-surjection $k[w_1, \ldots w_r] \to R_D$. As in Section ~\ref{sec:proj}, we can factor $\phi$ through the
+surjection $\bk[w_1, \ldots w_r] \to R_D$. As in Section ~\ref{sec:proj}, we can factor $\phi$ through the
 semigroup ring 
@@
 \begin{equation}
-\label{eqn:hirz-relations-psi}
 	u^d(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
@@
 Define
-\begin{equation}\label{eqn:defn-lambda}
+\begin{equation}
 	\lambda \colon = \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.

### 2015-08-17 surfaces-write-up/surface-write-up.tex
respond to peters comments like misuse of m for indexing lambda

@@
 \\
-Peter: I did this for a few of them, but I'm wondering what the purpose of this is.  It appears the same in the PDF either way right?}
+Peter: I did this for a few of them, but I'm wondering what the
+purpose of this is.  It appears the same in the PDF either way
+right?
+
+Aaron: Well, the point is to actually remove the references
+numbers from equations which aren't referenced, since this
+removes clutter. That is, put a star after the environment
+name (change begin{equation} to begin{equation*}).
+I think it makes sense not to label things
+if you don't use those labels, and 
+David recommended doing this in his comments.
+}
 \todo{Aaron: Make sure indexing at 0 is correct in projective space
@@
 Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
-\frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i$ be a hypersurface of
-$\bp^m$.
+\frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i \in \di \bp^m$ be an integral divisor.
 
@@
 is generated in degrees at most $\max_{0 \leq i \leq n}{k_i}$ with
-relations generated in degrees at most $2 \max_{0 \leq i \leq n}{k_i}$
+relations generated in degrees at most $2 \max_{0 \leq i \leq n}{k_i}$.
 \end{restatable}
@@
 	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes \bq.
-\end{align*}\todo{Peter: Do we want this indexing from 0 or 1, since we use 0 for $\bp^m$ and $1$ for $\mathbb{F}_m$.}
+\end{align*}\todo{Peter: Do we want this indexing from 0 or 1,
+	since we use 0 for $\bp^m$ and $1$ for $\mathbb{F}_m$.
+
+Aaron: Read the next two sentences. I think 1 is fine.}
 
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$, and all functions of $H^0(\mathbb{P}^m, dD)$ are of that form.
+~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$.
 \todo{Aaron: Peter, what do you mean when you say ``all functions of that form lie in...''? How is
@@
 \\
-Peter:  Oops, meant to write the converse statement, but accidently just restated the original statement-it's fixed now.}
+Peter:  Oops, meant to write the converse statement, but accidently
+just restated the original statement-it's fixed now.
+
+Aaron: Well, it should really be all such functions are linear
+combinations of things in that form. However,
+that's what I proved in the next couple setences. I.e.,
+the remainder of the proof is showing that this set is indeed
+a basis. I removed your added clause.
+}
 To complete the proof, it
@@
 approximations to $\alpha$. Then, since the $F_{i}^{\vec{v}}$ generate
-all of $R_D$ over $R_{D'}$, we obtain the
-relations $G_{i, j}^{\vec{v}, \vec{w}}$ \todo{Peter: hmm... this doesn't say much about how we get the $G_{i,j}$'s.}.
-We derive the relations
+all of $R_D$ over $R_{D'}$, and the leading terms of
+$G_{i,j}^{\vec v, \vec w}$ lies in $R_{D'}$, we obtain the
+relations $G_{i, j}^{\vec{v}, \vec{w}}$. We derive the relations
 $L_{i, j}^{\vec{v}, \vec{w}}$ by considering when products of
@@
 ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
-in a canonical form $\lambda + \sum_{i=0}^{n} r_i e_i$. Now, let $\lambda_0 \colon =
-0,\lambda_1, \ldots, \lambda_m$ be all elements of $\Sigma$ which can be
-written in the form $\lambda_i = \sum_{i=0}^{n}r_i e_i$ with $0 \leq r_i < 1.$ \todo{Peter: This sentence needs rephrasing.  1: misuse of $i$ as index.  2: misuse of $m$ as index ($\bp^m$).}
-Then, for any $1 \leq i \leq j \leq m,$ we can write $\lambda_i + \lambda_j$ in
-the above canonical form, yielding a relation in degree at most $\deg \lambda_i
-+ \deg \lambda_j \leq 2 \cdot \left( \sum_{i=0}^{n}d_i -1 \right).$
+in a canonical form $\lambda + \sum_{i=0}^{n} r_i e_i$. Now, let
+$\lambda_0 \colon =
+0,\lambda_1, \ldots, \lambda_t$ be all elements of $\Sigma$ which
+can be
+written in the form $\lambda_i = \sum_{i=0}^{n}r_i e_i$ with $0
+\leq r_i < 1.$ Then, for any $1 \leq j \leq k \leq t,$ we can write $\lambda_j + \lambda_k$ in
+the above canonical form, yielding a relation in degree at most $\deg \lambda_j
++ \deg \lambda_k\leq 2 \cdot \left( \sum_{i=0}^{n}d_i -1 \right).$
 Furthermore, these relations generate all relations, as one can apply a

### 2015-08-17 surfaces-write-up/surface-write-up.tex
added accent

@@
 stated explicitly later, in the case that $D = \alpha_0 D_0$ is supported on a single hypersurface, the relations in
-Theorem ~\ref{thm:proj-one-point} form a reduced grobner basis with respect to
+Theorem ~\ref{thm:proj-one-point} form a reduced gr\"{o}bner basis with respect to
 this ordering.

### 2015-08-18 surfaces-write-up/surface-write-up.tex
got rid of equation numbers when un-referenced

@@
 \maketitle
-\todo{Aaron: Remove labels which are not referenced
+\todo{Aaron: Make sure indexing at 0 is correct in projective space
+section, particularly toward the end.
 \\
-Peter: I did this for a few of them, but I'm wondering what the
-purpose of this is.  It appears the same in the PDF either way
-right?
-
-Aaron: Well, the point is to actually remove the references
-numbers from equations which aren't referenced, since this
-removes clutter. That is, put a star after the environment
-name (change begin{equation} to begin{equation*}).
-I think it makes sense not to label things
-if you don't use those labels, and 
-David recommended doing this in his comments.
-}
-\todo{Aaron: Make sure indexing at 0 is correct in projective space
-section, particularly toward the end}
+Peter: Think I got all of them.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 ~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$.
-\todo{Aaron: Peter, what do you mean when you say ``all functions of that form lie in...''? How is
-this different from saying that functions satisfying that equation lie in $H^0$?
-\\
-Peter:  Oops, meant to write the converse statement, but accidently
-just restated the original statement-it's fixed now.
-
-Aaron: Well, it should really be all such functions are linear
-combinations of things in that form. However,
-that's what I proved in the next couple setences. I.e.,
-the remainder of the proof is showing that this set is indeed
-a basis. I removed your added clause.
-}
 To complete the proof, it
@@
 \label{lem:composite-map}
-Lex $X$ be an arbitrary scheme and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
+Let $X$ be an arbitrary scheme and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
 surjection $\phi\colon \bk[w_1,\ldots, w_r] \rightarrow R_D$ given by $w_i
@@
 by 
-\begin{equation}
-	e_i \colon = d_i \epsilon_i %(-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
-	%\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
-\end{equation}
+\[
+	e_i \colon = d_i \epsilon_i.
+\]
 
@@
 by
-\begin{align}
+\begin{align*}
 e_{i,j} \colon = &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
 &+ \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
-%	
-%	(-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
-%	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
-%	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
-%	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
-%	\end{split}
-\end{align}
-
-%\noindent
-%where
-%\[
-%	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
-%	\alpha_k \bidb_k
-%\]
-%
-%\noindent
-%and
-%\[
-%	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
-%	\alpha_k \bidb_k.
-%\]
+\end{align*}
 
@@
 such that $\ker \psi$ has relations of the form
-\begin{equation}
+\[
 	u^d(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
-\end{equation}
+\]
 
@@
 Define
-\begin{equation}
+\[
 	\lambda \colon = \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
- \end{equation}
+\]
 

### 2015-08-18 surfaces-write-up/surface-write-up.tex
fixed more 0's to 1's, cleared old comments, spell check

@@
 \maketitle
-\todo{Aaron: Make sure indexing at 0 is correct in projective space
-section, particularly toward the end.
-\\
-Peter: Think I got all of them.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We will use $m \in \bz$ to index the dimension of a given projective
-space $\bp^m$ or the type of the hirzebruch surface $\hirz_m$.
+space $\bp^m$ or the type of the Hirzebruch surface $\hirz_m$.
 Let $D$ be a (Weil) $\bq$-divisor of the form
@@
 	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes \bq.
-\end{align*}\todo{Peter: Do we want this indexing from 0 or 1,
-	since we use 0 for $\bp^m$ and $1$ for $\mathbb{F}_m$.
-
-Aaron: Read the next two sentences. I think 1 is fine.}
-
-\noindent
+\end{align*}\noindent
 where $n \in \bz$ indexes the number of irreducible divisors in 
@@
 
-%\begin{rem}
-%\label{rem:proj-one-point-ind}
-%The method of proof for Theorem ~\ref{thm:proj-one-point}
-%can be immediately generalized to work inductively. If $D = D' + \alpha H$
-%for some hyperplane $H$, then the proof of Theorem ~\ref{thm:proj-one-point}, mutatis mutandis, extends to show
-%the canonical ring $R_D$ is generated over $R_D'$ by the same
-%generators and with the same relations given in Theorem
-%~\ref{thm:proj-one-point}.
-%\end{rem}
-
 Theorem ~\ref{thm:proj-one-point} gives an inductive procedure to
@@
 $k \in \bn$, showing that there will always exist a generator in
-degree $a(a + 1)$.
+degree $k(k + 1)$.
 
@@
 	d \alpha_i, 0 \leq i \leq n \text{ and } \sum_{i = 0}^{n} a_i =
-	\sum_{i	= 1}^{n}b_i = 0 \right \}.
+	\sum_{i	= 0}^{n}b_i = 0 \right \}.
 \end{align*}
@@
 Then, as a semigroup, $\Sigma$ is generated by
-elements whose first coordinate is less than $\sum_{i = 1}^{t}
+elements whose first coordinate is less than $\sum_{i = 0}^{t}
 \pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be
@@
 	\label{eqn:sigma-canonical-form}
-	\sigma = \lambda + \sum_{i = 0}^{t} w_i e_i
+	\sigma = \lambda + \sum_{i = 0}^{t} \zeta_i e_i
 \end{equation}
@@
 \noindent
-with $w_1, \ldots, w_t \in \bz_{\geq 0}$ \todo{Peter: Replace $w$ with a different letter, since we use it later to mean something else.},
-$0 \leq s_i < 1$, and $\lambda = \sum_{i = 0}^{r} s_i e_i$ 
+with $\zeta_1, \ldots, \zeta_t \in \bz_{\geq 0}$ $0 \leq s_i < 1$, and $\lambda = \sum_{i = 0}^{r} s_i e_i$ 
 so that the
-first coordinate of $\lambda$ is less than $\sum_{i=1}^{t}\pdeg_i$.
+first coordinate of $\lambda$ is less than $\sum_{i=0}^{t}\pdeg_i$.
 \end{prop}
@@
 Retaining the notation of Lemma ~\ref{lem:composite-map}, if $\Sigma$ has
-extremal rays $e_0,\ldots, e_n$ in degrees $d_0, \ldots, d_n$ then $\ker \chi$
-is generated in degrees at most $2(\sum_{i=0}^{n}d_i-1)$.
+extremal rays $e_0,\ldots, e_t$ in degrees $d_0, \ldots, d_t$ then $\ker \chi$
+is generated in degrees at most $2(\sum_{i=0}^{t}d_i-1)$.
 \end{lem}
 \begin{proof}
-Since $e_0, \ldots, e_n$ are extremal rays, by Proposition
+Since $e_0, \ldots, e_t$ are extremal rays, by Proposition
 ~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
-in a canonical form $\lambda + \sum_{i=0}^{n} r_i e_i$. Now, let
+in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$. Now, let
 $\lambda_0 \colon =
-0,\lambda_1, \ldots, \lambda_t$ be all elements of $\Sigma$ which
+0,\lambda_1, \ldots, \lambda_r$ be all elements of $\Sigma$ which
 can be
-written in the form $\lambda_i = \sum_{i=0}^{n}r_i e_i$ with $0
-\leq r_i < 1.$ Then, for any $1 \leq j \leq k \leq t,$ we can write $\lambda_j + \lambda_k$ in
+written in the form $\lambda_j = \sum_{i=0}^{t}\zeta_i e_i$ with $0
+\leq \zeta_i < 1.$ Then, for any $1 \leq j \leq k \leq r,$ we can write $\lambda_j + \lambda_k$ in
 the above canonical form, yielding a relation in degree at most $\deg \lambda_j
-+ \deg \lambda_k\leq 2 \cdot \left( \sum_{i=0}^{n}d_i -1 \right).$
++ \deg \lambda_k\leq 2 \cdot \left( \sum_{i=0}^{t}d_i -1 \right).$
 Furthermore, these relations generate all relations, as one can apply a
 sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
-$\sigma = \lambda + \sum_{i=0}^{n}w_i e_i$ as in Equation
+$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ as in Equation
 ~\eqref{eqn:sigma-canonical-form}.
@@
 \begin{align*}
-	\delta_i = \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_0 a_0}{\deg(D)},
+	\delta_i := \left(\frac{a_i}{\deg(D)}, -\frac{\alpha_0 a_0}{\deg(D)},
 	\ldots, - \frac{\alpha_n a_n}{\deg(D)} \right).
@@
 \begin{proof}
-%Let $(\bida_i, \bidb_i)$ be the bi-degrees of $f_i$. 
 Suppose $g
@@
 are contained in $H$, these form a set of extremal rays of $\Sigma$.
-%\begin{rem}
-%For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a %(possibly) different representative of it's extremal ray say that their lattice points %correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
-%\end{rem}
-
-%\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels
-%like this could reasonably be replaced with a better constructed/organized
-%proof, so that $e_i$'s are just defined this way initially; let me know if you
-%see a good way to do so...  As for Aaron's comment above, we could do something
-%like that, except we already defined $e_i$'s to be something different, which
-%might be equally/more confusing.
-%Aaron: I also don't like this here, just because it isn't really a remark,
-%its more of a notational convention, and it doesn't really belong in the proof.
-%I also think it's confusing to switch notation in the middle of a proof.
-%Earlier in the proof, we should just call the $e_{ij}$ something like $\hat{e_{ij}}$. Then, we should never define $\epsilon_{ij}$, since it's only used in this
-%proof, and should really be $e_{ij}$, as I was explaining in my previous note.
-%Instead of defining $\epsilon_{ij}$, just define $e_{ij}$ which are the
-%appropriately scaled $\hat{e_{ij}}$ and everything will be much clearer.
-%Robin: agree with Aaron here.}
 
@@
 
-%Let $\Omega\subseteq \Sigma$ be the 
-%set
-%\begin{align*}
-%	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
-%	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
-%= 0 \}.
-%\end{align*}
-
 Consider a relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ and let it correspond to the lattice point $\sigma\colon = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
@@
 \label{sec:conc}
-%In this section, we briefly state some further questions.  \todo{Peter: Redundant (see title of section...)?}
-
 Recall that every minimal rational surface is either isomorphic to
@@
 \label{sec:ack}
-We are grateful to David Zureick-Brown for introducing us to this
-subject, for providing invaluable guidance,
-and for his mentorship. We also thank Ken Ono and the
+We are grateful to David Zureick-Brown for suggesting this problem 
+and for providing invaluable guidance. We also thank Ken Ono and the
 Emory University Number Theory REU for arranging our project and

### 2015-08-18 surfaces-write-up/surface-write-up.tex
mentioened degree leq 0 case

@@
 ~\ref{thm:proj-effective-intro}.
+Note that if $\deg D < 0$ the
+canonical ring is concentrated in degree 0, and if
+$\deg D = 0$, then the canonical ring has a single
+generator. Therefore, for the remainder of this section,
+we shall assume $\deg D > 0$.
 The $\bp^1$ case restricts to the results of
@@
 
+Furthermore, similarly to the case of projective space, 
+we will restrict to the case that $D$ is a divisor
+for which both of its bi-degrees are positive. We now justify this
+restriction. If either of the bidegrees of $D$ are negative,
+then the canonical ring is concentrated in degree 0. If one of the
+bidegrees is 0, say the first one is 0, then $R_D$ is isomorphic
+to $R_{D'}$, where $D' \in \bq \otimes_\bq \di \bp^1$, 
+where $D'$ can be written as a sum of divisors whose degrees
+are multiples of the second bidegree of $D$. Since the case of
+$\bp^1$ has already been analyzed in \cite{canonical:dorney}, we
+are justified in assuming that both bi-degrees of $D$ are positive.
+
 For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are

### 2015-08-18 surfaces-write-up/surface-write-up.tex
added dashes

@@
 for which both of its bi-degrees are positive. We now justify this
-restriction. If either of the bidegrees of $D$ are negative,
+restriction. If either of the bi-degrees of $D$ are negative,
 then the canonical ring is concentrated in degree 0. If one of the
-bidegrees is 0, say the first one is 0, then $R_D$ is isomorphic
+bi-degrees is 0, say the first one is 0, then $R_D$ is isomorphic
 to $R_{D'}$, where $D' \in \bq \otimes_\bq \di \bp^1$, 
 where $D'$ can be written as a sum of divisors whose degrees
-are multiples of the second bidegree of $D$. Since the case of
+are multiples of the second bi-degree of $D$. Since the case of
 $\bp^1$ has already been analyzed in \cite{canonical:dorney}, we

### 2015-08-18 surfaces-write-up/surface-write-up.tex
added period
fixed reference

@@
 are multiples of the second bi-degree of $D$. Since the case of
-$\bp^1$ has already been analyzed in \cite{canonical:dorney}, we
+$\bp^1$ has already been analyzed in \cite{dorney:canonical}, we
 are justified in assuming that both bi-degrees of $D$ are positive.
@@
 e_{i,j} \colon = &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
-&+ \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j
+&+ \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j.
 \end{align*}

### 2015-08-18 surfaces-write-up/surface-write-up.tex
added remark on tightness of bounds to intro

@@
 \end{restatable}
-
-\noindent
+\begin{rem}\label{rem:proj-tight-bounds} Note that the bounds
+	given in Theorem ~\ref{thm:proj-effective-intro}
+are tight and are typically attained, as explained in
+Remark ~\ref{rem:exact-effective-bounds}.
+Additionally, the bounds given in Theorem 
+~\ref{thm:proj-generators-relations} are asymptotically
+tight to within a factor of two 
+for the following class of divisors. Consider
+a divisor 
+$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bq \di \bp^m$
+such that $H_i$ are hyperplanes,  
+$q_i$ are pairwise coprime integers, and $p_i$ are chosen
+so that $\deg D = \frac{1}{2 \prod_{i=0}^n}q_i$. Further,
+choose a linear subspace $\pi: \bp^1 \rightarrow \bp^m$  generically so that
+$\pi^* D = \sum_{i=0}^n \frac{p_i}{2q_i}P_i$, 
+where $P_i$ are distinct points in $\bp^1$. To choose such a map
+$\pi$, we may need to assume that the base field is infinite.
+Note that by the Remark immediately following Theorem 8 in 
+\cite{dorney:canonical},
+the given bounds on the generators and relations of
+$R_{\pi^*D}$ are within
+a factor of two of the degree of generation and relations of
+$R_{\pi^*D}$. Finally, since restriction map
+$R_D \rightarrow R_{\pi^*D}$ induced by the restriction maps
+on cohomology $H^0(\bp^m, dD) \rightarrow H^0(\bp^1, \pi^*(dD))
+\cong H^0(\bp^1, d\pi^* D)$ are surjective, we obtain that
+the bounds for the generators and relations of $R_D$ also
+agree with the degree of generation and relations 
+to within a factor of two.
+ \end{rem}
+
 In Section \ref{sec:hirz}, we shift our attention to Hirzebruch surfaces. Recall that for each $m \geq 0$ we can define the

### 2015-08-18 surfaces-write-up/surface-write-up.tex
im: cap grobner

@@
 stated explicitly later, in the case that $D = \alpha_0 D_0$ is supported on a single hypersurface, the relations in
-Theorem ~\ref{thm:proj-one-point} form a reduced gr\"{o}bner basis with respect to
-this ordering.
+Theorem ~\ref{thm:proj-one-point} form a reduced Gr\"{o}bner basis with 
+respect to this ordering.
 

### 2015-08-19 surfaces-write-up/surface-write-up.tex
last sweep for aaron before submission

@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{canonical ring} is $R(X, D) \colon = \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
+\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
 track of degree.
@@
 \cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring},
-which provide tight bounds on generators and relations
-of canonical rings and spin canonical rings, respectively, on arbitrary stacky curves.
+which provide tight bounds on the degree of generators and relations
+of log canonical rings and log spin canonical rings on arbitrary
+stacky curves.
 
@@
 \begin{align*}
-	\overline {\mathscr M}_g(\alpha) \colon = \bigoplus_{d \geq 0} u^d H^0 \left(
+	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
 	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
@@
 \label{thm:proj-effective-intro}
-Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bz \otimes_\bz \di \bp^m$, with $\alpha_i =
+Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, with $\alpha_i =
 \frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i \in \di \bp^m$ be an integral divisor.
@@
 \[
-	R_D \colon = \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
+	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
 \]
@@
 a divisor 
-$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bq \di \bp^m$
+$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bz \di \bp^m$
 such that $H_i$ are hyperplanes,  
@@
 \cong H^0(\bp^1, d\pi^* D)$ are surjective, we obtain that
-the bounds for the generators and relations of $R_D$ also
+the bounds for the generators and relations of $R_D$ given in
+Theorem ~\ref{thm:proj-generators-relations} also
 agree with the degree of generation and relations 
@@
 Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq
-\otimes_\bq \di \hirz_m$ 
+\otimes_\bz \di \hirz_m$ 
 where $\alpha_i = \frac{c_i}{k_i}$.
@@
 \begin{align*}
-	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes \bq.
+	D = \sum_{i=1}^{n}\alpha_i D_i \in \bq \otimes_\bz \di X.
 \end{align*}\noindent
@@
 so, we shall sometimes start the indexing at $0$, so that $i$ runs
-from $0$ to $n$. Define the degree of $D$ by $\deg D \colon =
-\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. For such a divisor $D$ with $\alpha_i =
+from $0$ to $n$. For such a divisor $D$ with $\alpha_i =
 \frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_j)$
-and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
-\rfloor \in \di X$ is defined to be $\lfloor D \rfloor \colon = \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor P_i$. Let $
-	R_D \colon = \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
+and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ In the case $X = \bp^m$, define the degree of $D$ by $\deg D :=
+\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
+\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
+\lfloor \alpha_i \rfloor D_i$. Let $
+	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
 denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
 is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
-$\fr(r) \colon = r - \lfloor r
+$\fr(r) := r - \lfloor r
 \rfloor$ denote the fractional part of $r$. Throughout, we
-shall work over a fixed base field $\bk$.
+shall work over a fixed base field $\bk$. If $D \in \bq \otimes_\bz
+\di X$ is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
 
@@
 In this subsection, we restrict attention to the case of effective
-fractional divisors $D \in \bq \otimes \di \bp^m$. We give an explicit presentation of the canonical ring when $D$ is an effective
+fractional divisors $D \in \bq \otimes_\bz \di \bp^m$. We give an explicit presentation of the canonical ring when $D$ is an effective
 divisor.
@@
 \[
-	x^{\vec{v}} \colon = \prod_{i = 0}^{m} x_i^{v_i}.
+	x^{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}.
 \]
@@
 \label{defn:vec-sum}
-For $\vec{v} \in \bz^n$, denote $\deg \vec{v} \colon = \sum_{i = 0}
+For $\vec{v} \in \bz^n$, denote $\deg \vec{v} := \sum_{i = 0}
 ^n v_i$.
@@
 \begin{align*}
-	\mss_i \colon = \left \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
+	\mss_i := \left \{\vec{v} \in \bz_{\geq 0}^{m + 1} \; : \;
 \deg \vec v = c_i \right\}.	
@@
 \noindent
-.\end{defn}
+\end{defn}
 
@@
 Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D' \in \bq
-\otimes \di \bp^m$ and $D = D' + \alpha H$, with $\alpha =
-\frac{p}{q} \in \bq_{>0}$ and $H \colon = V(x_k)$ a hyperplane of $\bp^m$.
+\otimes_\bz \di \bp^m$ and $D = D' + \alpha H$, with $\alpha =
+\frac{p}{q} \in \bq_{>0}$ and $H := V(x_k)$ a hyperplane of $\bp^m$.
 Let
@@
 has a minimal presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
-{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} \colon = \frac{u^{d_i}
+{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $0 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
@@
 products of generators in adjacent degrees where $h$
-depends on $i$ and $ j$, so we notate $h_{i, j} \colon = h \in \{1, \ldots, r\}$. We 
+depends on $i$ and $ j$, so we notate $h_{i, j} := h \in \{1, \ldots, r\}$. We 
 also have that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the
@@
 Now, we inductively add hypersurfaces.
-Let $D' = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bq\di \bp^m$, 
+Let $D' = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, 
 and assume the theorem holds for $D'$. It suffices to show
-the theorem holds for $D \in \di \bq \otimes_\bq \bp^m$, where $D = D' + \alpha C$ for some
+the theorem holds for $D \in \di \bq \otimes_\bz \bp^m$, where $D = D' + \alpha C$ for some
 degree $\pdeg$ hypersurface $C$.
@@
 
-We now offer bounds on generators and relations of $R_D$ for a general $\bq$-divisor $D \in \bq \otimes_\bq \di \bp^m$.
-
-Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes \di \bp^m$ and let $f_i$ be
+We now offer bounds on generators and relations of $R_D$ for a general $\bq$-divisor $D \in \bq \otimes_\bz \di \bp^m$.
+
+Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ and let $f_i$ be
 homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$
@@
 rational functions in $x_0, x_1$. However, in degree $6$, there is
-$u^6 \frac{x_1^2 x_2}{x_0^3}$. Since this
+$u^6 \cdot \frac{x_1^2 x_2}{x_0^3}$. Since this
 involves $x_2$, it must be a generator.
@@
 This example generalizes slightly to any divisor of the form $D =
-\frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes \bq,$ with
+\frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \bq \otimes_\bz \di \bp^2,$ with
 $k \in \bn$, showing that there will always exist a generator in
@@
 	D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
-\otimes \bq,
+\otimes_\bz \bq,
 \]
@@
 \begin{align*}
-	\Sigma \colon = \left \{(d, c_0, \ldots, c_n) \in \bz^{n + 2} \colon c_i \geq -
+	\Sigma := \left \{(d, c_0, \ldots, c_n) \in \bz^{n + 2} \colon c_i \geq -
 	d \alpha_i, 0 \leq i \leq n \text{ and } \sum_{i = 0}^{n} a_i =
@@
 \noindent
-with $\zeta_1, \ldots, \zeta_t \in \bz_{\geq 0}$ $0 \leq s_i < 1$, and $\lambda = \sum_{i = 0}^{r} s_i e_i$ 
+with $\zeta_1, \ldots, \zeta_t \in \bz_{\geq 0}$, $0 \leq s_i < 1$, and $\lambda = \sum_{i = 0}^{r} s_i e_i$ 
 so that the
@@
 By assumption, $\sigma \in \Sigma$ can be written as $\sigma = \sum_
-{i = 0}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) \colon = r - \lfloor r
+{i = 0}^{t} r_i e_i$ with $r_i \in \bq$. Let $\fr(r) := r - \lfloor r
 \rfloor$ denote the fractional part of $r$. Let $\lambda = \sum_{i = 0}
@@
 $\bz_{\geq 0}$ span of $\lambda, e_0, \ldots, e_t$, which all have
-first coordinate less than $\sum_{i=0}^{t} r_i$. Ergo, $\Sigma$ is
+first coordinate less than $\sum_{i=0}^{t} \pdeg_i$. Ergo, $\Sigma$ is
 generated by elements whose first coordinate is less than
-$\sum_{i = 0}^{t} r_i$.
+$\sum_{i = 0}^{t} \pdeg_i$.
 \end{proof}
@@
 \begin{lem} \label{lem:proj-generators}
-Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes \di \bp^m,$ where
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m,$ where
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
@@
 \bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-w_i \ar r & u^{d_i}z_0^{c_{i0}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_0^{c_{i0}} \cdots f_n^{c_{in}}.
+w_i \ar[mapsto]{r} & u^{d_i}z_0^{c_{i0}} \cdots z_n^{c_{in}} \ar[mapsto]{r} & u^{d_i}f_0^{c_{i0}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
@@
 In Lemma ~\ref{lem:bound-ker-chi}, we bound the degree of generation of
-$\ker \chi $ and we bound the degree of generation of $\ker \psi$ in Lemma ~\ref{lem:proj-relations-psi}
+$\ker \chi $, and we bound the degree of generation of $\ker \psi$ in Lemma ~\ref{lem:proj-relations-psi}
 
@@
 in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$. Now, let
-$\lambda_0 \colon =
+$\lambda_0 :=
 0,\lambda_1, \ldots, \lambda_r$ be all elements of $\Sigma$ which
 can be
-written in the form $\lambda_j = \sum_{i=0}^{t}\zeta_i e_i$ with $0
-\leq \zeta_i < 1.$ Then, for any $1 \leq j \leq k \leq r,$ we can write $\lambda_j + \lambda_k$ in
+written in the form $\lambda_j = \sum_{i=0}^{t}s_i e_i$ with $0
+\leq s_i < 1.$ Then, for any $1 \leq j \leq k \leq r,$ we can write $\lambda_j + \lambda_k$ in
 the above canonical form, yielding a relation in degree at most $\deg \lambda_j
@@
 \label{lem:proj-relations-psi}
-Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes \di \bp^m,$ where
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m,$ where
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
@@
 
-One way to describe the Hirzebruch surface $\hirz_m$ is as a quotient
+One way to describe the Hirzebruch surface $\hirz_m$ is as a
+quotient,
 \[
@@
 bi-degrees is 0, say the first one is 0, then $R_D$ is isomorphic
-to $R_{D'}$, where $D' \in \bq \otimes_\bq \di \bp^1$, 
+to $R_{D'}$, where $D' \in \bq \otimes_\bz \di \bp^1$, 
 where $D'$ can be written as a sum of divisors whose degrees
@@
 \begin{equation}\label{eqn:def-sigma}
-	\rho \colon = \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
+	\rho := \sum_{i \in \Te(D)} \gcd(\bida_i, \bidb_i) \ell_i + \sum_{\substack
 	{i \in \Tp(D) \\ j\in \Tm(D)}} (\bida_i \bidb_j - \bida_j \bidb_i)
@@
 \[
-	\epsilon_i \colon = \left(1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
+	\epsilon_i := \left(1, -\alpha_1, \ldots, -\alpha_{i-1}, \frac{\sum_{j \ne i}
 	\alpha_j (\bida_j + \bidb_j)}{\bida_i + \bidb_i}, -\alpha_{i + 1},
@@
 Let $\Sigma_1 \otimes_\bz \bq$ be the $\bq_{\ge 0}$ span of $\epsilon_1, \ldots \epsilon_n$.
-We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H \colon =
+We can intersect $\Sigma_1 \otimes_\bz \bq$ with the hyperplane $H :=
 V(\sum_{i=1}^n \bida_i x_i)$  to get the subspace $\Sigma \otimes_\bz \bq = H \cap (\Sigma_1
@@
 \[
-	e_i \colon = d_i \epsilon_i.
+	e_i := d_i \epsilon_i.
 \]
@@
 \begin{align*}
-e_{i,j} \colon = &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
+e_{i,j} := &\frac{a_j\sum_{k\ne i,j} d_{i,j}\alpha_k b_k - b_j\sum_{k \ne i,j} d_{i,j} \alpha_k a_k}{a_ib_j - b_i a_j} \epsilon_i \\
 &+ \frac{a_i \sum_{k\ne i,j} d_{i,j} \alpha_k b_k - b_i\sum_{k\ne i,j} d_{i,j} \alpha_ka_k}{a_jb_i - b_j a_i} \epsilon_j.
@@
 	\bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
-	w_i \ar r & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar r & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
+	w_i \ar[mapsto]{r} & u^{d_i}z_1^{c_{i1}} \cdots z_n^{c_{in}} \ar[mapsto]{r} & u^{d_i}f_1^{c_{i1}} \cdots f_n^{c_{in}}.
 \end{tikzcd}
@@
 \label{lem:hirz-bound-ker-psi}
-$\ker \psi$ is generated in degrees less than
-\[
-	\tau \colon = \rho
+Let $\rho$ be as in Equation ~\eqref{eqn:def-sigma}. Then, $\ker \psi$ is generated in degrees less than
+\[
+	\tau := \rho
 	+ \max \left(\max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
@@
 
-Consider a relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ and let it correspond to the lattice point $\sigma\colon = (d, c_1, \ldots, c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
+Consider a relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ and
+let it correspond to the lattice point $\sigma := (d, c_1, \ldots,
+c_{i-1}, c_{i}+1, c_{i+1}, \ldots, c_n) \in \Sigma$.
 Then we can write $\sigma$ as a sum of $s_j e_j$'s for $j\in
 \Te$ and $s_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
-For convenience, define $d_j \colon = \deg e_j$ (when it exists) and let the $j^{th}$
+For convenience, define $d_j := \deg e_j$ (when it exists) and let the $j^{th}$
 component of $e_j$ be $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$.
-Also, let $d_{j,k} \colon = \deg e_{j,k}$ (when it exists) and let the $j^{th}$ component of $e_{j,k}$ be $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and the $k^{th}$
+Also, let $d_{j,k} := \deg e_{j,k}$ (when it exists) and let the $j^{th}$ component of $e_{j,k}$ be $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and the $k^{th}$
 component be $-\alpha_k d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$.
@@
 
-If $i\in \Te$ define $r_i \colon = \frac{1}{\kappa_i}$.
+If $i\in \Te$ define $r_i := \frac{1}{\kappa_i}$.
 If $i\in \Tp$ choose $r_{i,j}\in \bq_{\ge 0}$ for all $j\in \Tm$ such that $\sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1$; similarly, if $i\in \Tm$ choose $r_{j,i}\in \bq_{\ge 0}$ for all $j\in \Tp$ such that $\sum_{j\in \Tm} r_{j,i}\kappa_{j,i}'' = 1$.
-For $j\ne i$, define $r_j \colon = 0.$ For all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} \colon = 0$.
+For $j\ne i$, define $r_j := 0.$ For all pairs $(j,k)$ so that $j \neq i$ and $k \neq i$ define $r_{j,k} := 0$.
 Define $E$ by
 \begin{equation}\label{eqn:hirz-E-translation}
-	E \colon = \sum_{j\in \Te} (s_j - \lfloor s_j - r_j \rfloor) e_j + \sum_{\substack{j \in 
+	E := \sum_{j\in \Te} (s_j - \lfloor s_j - r_j \rfloor) e_j + \sum_{\substack{j \in 
 	\Tp \\ k \in \Tm}} (s_{j,k} - \lfloor s_{j,k} - r_{j,k} \rfloor) e_{j,k}.
@@
 \[
-	\lambda \colon = \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
+	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
 \]
@@
 
-Finally, by construction, $E - \sum_{\mu \in M_i} E_\mu \in \ker \psi$ and
+By construction, $E - \sum_{\mu \in M_i} E_\mu \in \ker \psi$ and
 divides $u^d(z_i - \beta_i) \prod_{j = 1}^n z_j^{c_j}$. 

### 2015-08-19 surfaces-write-up/surface-write-up.tex
one minor edit to last sweet of changes
edits to the second half of the paper

@@
 \[
-	D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m
-\otimes_\bz \bq,
+	D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \bq
+	\otimes_\bz \bq \di \bp^m,
 \]
@@
 generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
-\end{proof}
+\end{proof}\todo{Peter: Maybe we can get rid of most of this proof, and replace it with: ``The proof follows by examining the exact sequence $0 \to \ker\chi \to \ker \phi \to \ker \psi \to 0$.''  I don't think it is necessary to prove why this is an exact sequence, as it is taught in a first commutative algebra course.}
 
@@
 \begin{proof}
-Since $e_0, \ldots, e_t$ are extremal rays, by Proposition
-~\ref{prop:cone-generation}, every element $\sigma \in \Sigma$ can be written
-in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$. Now, let
+Since $e_0, \ldots, e_t$ are extremal rays, Proposition
+~\ref{prop:cone-generation} tells us that every element $\sigma \in \Sigma$ can be written
+in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$ where all $\zeta_i \in \mathbb{Z}_{\ge 0}$.  Let
 $\lambda_0 :=
@@
 \leq s_i < 1.$ Then, for any $1 \leq j \leq k \leq r,$ we can write $\lambda_j + \lambda_k$ in
-the above canonical form, yielding a relation in degree at most $\deg \lambda_j
+the above canonical form, yielding a (possibly trivial) relation in degree at most $\deg \lambda_j
 + \deg \lambda_k\leq 2 \cdot \left( \sum_{i=0}^{t}d_i -1 \right).$
@@
 sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
-$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ as in Equation
-~\eqref{eqn:sigma-canonical-form}.
+$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ from proposition Proposition
+~\ref{prop:cone-generation}.
+%as in Equation
+%~\eqref{eqn:sigma-canonical-form}.
 \end{proof}
@@
 
-Indeed, define the $\beta_i$ above so that $\psi(\beta_i) = \beta_i(z_0, \ldots, z_m)= \psi(z_i) \in R_D.$ This is possible by Proposition ~\ref{prop:pm-span-and-basis}.
+Indeed, define the $\beta_i$ as a polynomial in $z_0, \ldots, z_m$ such that $\psi(\beta_i) = \psi(z_i) = f_i \in R_D.$ This is possible by Proposition ~\ref{prop:pm-span-and-basis}.
 Furthermore, the relations given in Equation
@@
 $(a + b + mc, c + d)$. Rational sections of $\hirz_m$ can be written as
-rational functions where each monomial has bi-degree 0. To see this, 
+rational functions with numerators and denominators with the same bi-degrees. To see this, 
 observe
@@
 we will restrict to the case that $D$ is a divisor
-for which both of its bi-degrees are positive. We now justify this
+for which both of its bi-degrees are positive \todo{Do we need to specify what we mean by the bi-degrees of a divisor, or will that be apparent to a reader?}. We now justify this
 restriction. If either of the bi-degrees of $D$ are negative,
@@
 To bound the degree of generation of the ideal 
-$(\beta_i - z_i) \cap \ker(\psi)$, {\bf for the remainder of the proof,} we fix $i \in \{1,\ldots, n\}$ and a relation of 
-the form $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}.$ Note that there 
+$(\beta_i - z_i) \cap \ker(\psi)$, we fix $i \in \{1,\ldots, n\}$ and a relation of 
+the form $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ {\bf for the remainder of the proof}.  Note that there 
 are no relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in \bk[\Sigma]$. Thus we restrict attention to $i \ge 5$. Our goal 
@@
 Theory REU. We deeply appreciate all of the support that has made
-our work possible.
+our work possible.\todo{Peter: Add acknowledgements to a few more peopled - Robin's dad; was there anyone else?}
 

### 2015-08-20 surfaces-write-up/surface-write-up.tex
answered peters pre-arxiv todos

@@
 \begin{proof}
-First, we show there is an exact sequence
+First, note that surjectivity of $\chi$ implies we have an exact sequence
 \[
@@
 \]
-To see this, note that $\rho$ is injective and $\tau$ is surjective\ because
-$\phi = \chi \circ \psi$. Additionally, $\tau \circ \rho = 0$ by definition of
-the kernel of $\chi$. Finally, if $a \in\ker \tau$, then by definition $\chi(a)
-= 0,$ so $a \in \im \rho$.
-
 This shows that lifts of generators of $\ker \psi$ together with images of
 generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
-\end{proof}\todo{Peter: Maybe we can get rid of most of this proof, and replace it with: ``The proof follows by examining the exact sequence $0 \to \ker\chi \to \ker \phi \to \ker \psi \to 0$.''  I don't think it is necessary to prove why this is an exact sequence, as it is taught in a first commutative algebra course.}
-
+\end{proof}
 \begin{lem}
@@
 Since $e_0, \ldots, e_t$ are extremal rays, Proposition
-~\ref{prop:cone-generation} tells us that every element $\sigma \in \Sigma$ can be written
+~\ref{prop:cone-generation} implies every element $\sigma \in \Sigma$ can be written
 in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$ where all $\zeta_i \in \mathbb{Z}_{\ge 0}$.  Let
@@
 we will restrict to the case that $D$ is a divisor
-for which both of its bi-degrees are positive \todo{Do we need to specify what we mean by the bi-degrees of a divisor, or will that be apparent to a reader?}. We now justify this
+for which both of its bi-degrees are positive. We now justify this
 restriction. If either of the bi-degrees of $D$ are negative,
@@
 We are grateful to David Zureick-Brown for suggesting this problem 
-and for providing invaluable guidance. We also thank Ken Ono and the
+and for providing invaluable guidance. We thank Shou-Wu Zhang and Peter
+Landesman for reading this paper and proving helpful suggestions.
+We also thank Ken Ono and the
 Emory University Number Theory REU for arranging our project and
@@
 Theory REU. We deeply appreciate all of the support that has made
-our work possible.\todo{Peter: Add acknowledgements to a few more peopled - Robin's dad; was there anyone else?}
+our work possible.
 

### 2015-08-20 surfaces-write-up/surface-write-up.tex
removed doubled proposition

@@
 sequence of these relations to put any $\sigma \in \Sigma$ into canonical form
-$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ from proposition Proposition
+$\sigma = \lambda + \sum_{i=0}^{t}\zeta_i e_i$ from Proposition
 ~\ref{prop:cone-generation}.

### 2015-08-20 surfaces-write-up/surface-write-up.tex
cleared percentages and spell check
surfaces: various revisions, rewrite acknowledgments

@@
 \begin{proof}
-First, note that surjectivity of $\chi$ implies we have an exact sequence
+The proof follows by examining the exact sequence
 \[
@@
 \]
-This shows that lifts of generators of $\ker \psi$ together with images of
-generators of $\ker \chi$ generate all of $\ker \phi,$ as desired. 
 \end{proof}
+
 \begin{lem}
@@
 Since $e_0, \ldots, e_t$ are extremal rays, Proposition
-~\ref{prop:cone-generation} implies every element $\sigma \in \Sigma$ can be written
+~\ref{prop:cone-generation} tells us that every element $\sigma \in \Sigma$ can be written
 in a canonical form $\lambda + \sum_{i=0}^{t} \zeta_i e_i$ where all $\zeta_i \in \mathbb{Z}_{\ge 0}$.  Let
@@
 \label{sec:ack}
-We are grateful to David Zureick-Brown for suggesting this problem 
-and for providing invaluable guidance. We thank Shou-Wu Zhang and Peter
-Landesman for reading this paper and proving helpful suggestions.
-We also thank Ken Ono and the
+We are grateful to David Zureick-Brown for offering great advice on
+this project, for many useful suggestions on this paper, and for
+many valuable conversations. We would like to thank Ken Ono and the
 Emory University Number Theory REU for arranging our project and
-providing a great environment for mathematical learning and
-collaboration.
-Finally, we gratefully acknowledge the financial support given by
-NSF Grant Award Number 1250467 via the Emory University Number
-Theory REU. We deeply appreciate all of the support that has made
-our work possible.
+for the great support that we have received. We also thank Peter
+Landesman and Shou-Wu Zhang for offering helpful comments and
+insights on this paper. Finally, we would like to acknowledge the
+support of the National Science Foundation (grant number DMS-1250467
+).
 

### 2015-08-20 surfaces-write-up/surface-write-up.tex

--- 2015-08-20 surfaces-write-up/surface-write-up.tex
@@
 \definecolor{myblue}{rgb}{0,0,0.65}
-
-%\usepackage{hyperref}
-  %\hypersetup{colorlinks=true,citecolor=blue}
 
@@
 \DeclareMathOperator{\Pic}{Pic}
-%\captionsetup[table]{belowskip = 4pt}
-
 \makeatletter
@@
 \]
+
 This shows that lifts of generators of $\ker \psi$ together with images of
@@
 \end{proof}
+
 \begin{lem}
@@
 ~\ref{prop:cone-generation}.
-%as in Equation
-%~\eqref{eqn:sigma-canonical-form}.
 \end{proof}
@@
 \label{sec:ack}
-We are grateful to David Zureick-Brown for suggesting this problem 
-and for providing invaluable guidance. We thank Shou-Wu Zhang and Peter
-Landesman for reading this paper and proving helpful suggestions.
-We also thank Ken Ono and the
+We are grateful to David Zureick-Brown for offering great advice on
+this project, for many useful suggestions on this paper, and for
+many valuable conversations. We thank Peter
+Landesman and Shou-Wu Zhang for offering helpful comments and
+suggestions for this paper. We also thank Ken Ono and the
 Emory University Number Theory REU for arranging our project and
-providing a great environment for mathematical learning and
-collaboration.
-Finally, we gratefully acknowledge the financial support given by
-NSF Grant Award Number 1250467 via the Emory University Number
-Theory REU. We deeply appreciate all of the support that has made
-our work possible.
+for the great support that we have received. Finally, we would like to acknowledge the
+support of the National Science Foundation (grant number DMS-1250467
+).
 

### 2015-08-20 surfaces-write-up/arXiv-versions/surface-write-up-arXiv-v1.tex
surfaces: various minor rewordings, add arXiv1

--- 2015-08-20 surfaces-write-up/surface-write-up.tex
@@
  	We give bounds on the degree of generation and relations of
-	canonical rings of arbitrary $\bq$-divisors
-	on projective spaces of all dimensions
-	and Hirzebruch surfaces. We also give
-	exact bounds on the degree of generators and relations of the canonical
-	ring of any effective stacky divisor on projective space.
+	canonical rings of arbitrary $\bq$-divisors on projective spaces of 
+	all dimensions and Hirzebruch surfaces. We also give exact bounds 
+	on the degree of generators and relations of the canonical ring of 
+	any effective stacky divisor on projective space.
 \end{abstract}
@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
+\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d
+H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
 track of degree.
@@
 Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, with $\alpha_i =
-\frac{c_i}{k_i} \in \bq_{> 0}$ and let each $D_i \in \di \bp^m$ be an integral divisor.
+\frac{c_i}{k_i} \in \bq_{> 0}$ and each $D_i \in \di \bp^m$ an integral divisor.
 
@@
 \label{thm:proj-generators-relations}
-Let $D =
-\sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ 
-with $\alpha_i = \frac{c_i}{k_i}\in \bq.$ Let $\bp^m \cong \proj \bk[x_0,\ldots, x_m]$ with
-$f_0, \ldots, f_n \in \bk[x_0, \ldots, x_m]$ such that
-for $1 \leq i \leq n$ we have $D_i = V(f_i)$ and $\deg(f_i) = a_i.$
-Further, after reordering the terms of $D$, and possibly adding in
-$D_i$ with coefficient $\alpha_i = 0$, assume that $f_0,\ldots, f_m$ are independent linear
-polynomials in $x_0, \ldots, x_m$. 
-Define 
-\[\ell_i = \lcm_{j\ne i}(k_j).\] 
+Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
+as in Theorem ~\ref{thm:proj-effective-intro}. Write $\ell_i := \lcm
+_{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
+\bk[x_0, \ldots, x_m]$. Now suppose that $f_0, \ldots, f_n$ contain
+$m$ independent linear polynomials in $x_0, \ldots, x_m$ (with possibly
+zero coefficients $\alpha_j$).
+
 Then $R_D$ is generated in degrees at most 
@@
 \end{restatable}
+
 \begin{rem}\label{rem:proj-tight-bounds} Note that the bounds
@@
 Note that Hirzebruch surfaces are regular, normal,
-and locally factorial, being $\bp^1$ bundles over
-$\bp^1$, and therefore the natural map from Cartier
+and locally factorial, being $\bp^1$-bundles over
+$\bp^1$. Therefore,, the natural map from Cartier
 divisors to Weil divisors is an isomorphism.
@@
 span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, functions 
-of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation \ref{align:pm-span} and
+of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation ~\eqref{align:pm-span} and
 \begin{align}
@@
 independent coordinates, so that two distinct integral subschemes
-cannot be equations of only $m$ of the $m+1$ coordinates.
+cannot repreesnt equations of only $m$ of the $m+1$ coordinates.
 \end{rem}
@@
 \label{lem:proj-relations-psi}
-Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m,$ where
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, where
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
 $\ell_i = \lcm_{j \neq i} (k_j)$. Define $\Sigma$ as in Equation
-~\eqref{eqn:Sigma-defn} and $\psi$ as ~\eqref{eqn:factor-through-semigroup-ring}. Then, $\ker \psi$ is generated in degrees at most
+~\eqref{eqn:Sigma-defn} and $\psi$ as in Equation
+~\eqref{eqn:factor-through-semigroup-ring}. Then, $\ker \psi$ is
+generated in degrees at most
 \begin{align}
@@
 $\beta$ exists and is unique because rational functions
-whose numerators are polynomials in $f_1,f_2,f_3,f_4$ form a basis
+whose numerators are polynomials in $f_1, f_2, f_3, f_4$ form a basis
 of all rational functions in $R_D$. Furthermore, these
 generate all relations, since they allow us to reduce any monomial $u^d\prod_{j =
-1}^n z_j^{r_j}$ to the canonical form where $r_j = - \lfloor d \alpha_i
-\rfloor$
-whenever $j > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(\beta_i  -z_i) \cap \ker(\psi)$ for each $i$.
-
-To bound the degree of generation of the ideal 
-$(\beta_i - z_i) \cap \ker(\psi)$, we fix $i \in \{1,\ldots, n\}$ and a relation of 
-the form $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ {\bf for the remainder of the proof}.  Note that there 
-are no relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in \bk[\Sigma]$. Thus we restrict attention to $i \ge 5$. Our goal 
-is to show that if $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ has 
-sufficiently high degree, then there is another relation dividing it. 
-We do so by considering the lattice points corresponding to the 
-monomials appearing in the relation $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$, and finding a fixed $\lambda\in \Sigma$
-that we can simultaneously factor out of all monomials.
+1}^n z_j^{r_j}$ to the canonical form where $r_j = -\lfloor d \alpha_i
+\rfloor$ whenever $j > 4$. To bound the degree of generation of these relations,
+we bound the degree of generation of the ideal $(\beta_i - z_i) \cap
+\ker(\psi)$ for each $i$.
+
+\textbf{For the remainder of this proof:} we fix $i \in \{1, \ldots,
+n\}$ and fix a relation of the form $u^d (z_i - \beta_i) \prod_{j =
+1}^n z_j^{c_j}$ as we seek to bound the degree of generation of the
+ideal $(\beta_i - z_i) \cap \ker(\psi)$. Note that there are no
+relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in
+\bk[\Sigma]$. Thus we restrict attention to $i \ge 5$. Our goal is
+to show that if $u^d(z_i - \beta_i)\prod_{j=1}^n z_j^{c_j}$ has
+sufficiently high degree, then there is another relation dividing
+it. We do so by considering the lattice points corresponding to the
+monomials appearing in the relation $u^d(z_i - \beta_i)\prod_{j=1}^
+n z_j^{c_j}$, and finding a fixed $\lambda\in \Sigma$ that we can
+simultaneously factor out of all monomials.
 
@@
 \end{align}
-where $\rho$ is as in Equation \ref{eqn:def-sigma}. To obtain the
-bound given in Equation ~\eqref{eqn:e-bound}, the $\rho$ term corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_{j,k} - r_{j,k}$'s, whereas the second term corresponds to the sums of $r_j$'s and $r_{j,k}$'s (noting that in equation \ref{eqn:hirz-E-translation} $s_j - \lfloor s_j - r_j \rfloor= r_j + \fr(s_j - r_j)$).
+
+\noindent
+where $\rho$ is as in Equation ~\eqref{eqn:def-sigma}. To obtain the
+bound given in Equation ~\eqref{eqn:e-bound}, the $\rho$ term 
+corresponds to the sums of fractional parts of $s_j - r_j$'s and $s_
+{j, k} - r_{j, k}$'s whereas the second term corresponds to the sums 
+of $r_j$'s and $r_{j, k}$'s (noting that in Equation
+~\ref{eqn:hirz-E-translation}, $s_j - \lfloor s_j - r_j \rfloor =
+r_j + \fr(s_j - r_j)$).
 
@@
 \[
-	\lambda := \sigma - E = \sum_{j\in \Te} (\lfloor s_j - r_j\rfloor) e_j + \sum_{\substack{j\in \Tp \\ k\in \Tm}} ( \lfloor s_{j,k} - r_{j,k}\rfloor)e_{j,k}\in \Sigma.
-\]
-
+	\lambda := \sigma - E = \sum_{j \in \Te} (\lfloor s_j - r_j \rfloor)
+	e_j + \sum_{\substack{j \in \Tp \\ k \in \Tm}} ( \lfloor s_{j, k} -
+	r_{j, k} \rfloor) e_{j, k} \in \Sigma.
+\]
+
+\noindent
 Let $M_i$ be the set of monomials terms of $\beta_i = \beta_i(z_1, \ldots z_4)$.  Let $\mu = \prod_{j=1}^4
@@
 \label{qn:general-minimal-surface}
-Can we describe generators and relations of $R_D$ for $D$ a divisor on an
+Can we describe generators and relations of $R_D$ for a divisor $D$ on an
 arbitrary rational surface $X$?
@@
 for the great support that we have received. Finally, we would like to acknowledge the
-support of the National Science Foundation (grant number DMS-1250467
-).
+support of the National Science Foundation (grant number DMS-1250467).
 

### 2015-08-20 surfaces-write-up/surface-write-up.tex
edits to robin's arxiv posted version

@@
 the degree of generators and relations of
-stacky canonical rings on $\bp^m$:
+stacky canonical rings on $\bp^m$. The first applies
+to effective $\bq$-divisors and the second applies to arbitrary
+$\bq$-divisors.
 \begin{restatable}{thm}{restateeffective}
@@
 \label{thm:proj-generators-relations}
-Let $D =
-\sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ 
-with $\alpha_i = \frac{c_i}{k_i}\in \bq.$ Let $\bp^m \cong \proj \bk[x_0,\ldots, x_m]$ with
+Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
+with $\alpha_i = \frac{c_i}{k_i}\in \bq.$ Let $\bp^m \cong
+\proj \bk[x_0,\ldots, x_m]$ with
 $f_0, \ldots, f_n \in \bk[x_0, \ldots, x_m]$ such that
@@
 \[\ell_i = \lcm_{j\ne i}(k_j).\]
+
 Then $R_D$ is generated in degrees at most 
@@
 Note that Hirzebruch surfaces are regular, normal,
-and locally factorial, being $\bp^1$ bundles over
-$\bp^1$, and therefore the natural map from Cartier
+and locally factorial, being $\bp^1$-bundles over
+$\bp^1$. Therefore, the natural map from Cartier
 divisors to Weil divisors is an isomorphism.
@@
 independent coordinates, so that two distinct integral subschemes
-cannot be equations of only $m$ of the $m+1$ coordinates.
+cannot represent equations of only $m$ of the $m+1$ coordinates.
 \end{rem}

### 2015-08-20 surfaces-write-up/surface-write-up.tex
surfaces: reuse revision of thm 1.2 statement with \bq

@@
 Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
-with $\alpha_i = \frac{c_i}{k_i}\in \bq.$ Let $\bp^m \cong
-\proj \bk[x_0,\ldots, x_m]$ with
-$f_0, \ldots, f_n \in \bk[x_0, \ldots, x_m]$ such that
-for $1 \leq i \leq n$ we have $D_i = V(f_i)$ and $\deg(f_i) = a_i.$
-Further, after reordering the terms of $D$, and possibly adding in
-$D_i$ with coefficient $\alpha_i = 0$, assume that $f_0,\ldots, f_m$ are independent linear
-polynomials in $x_0, \ldots, x_m$. 
-Define 
-\[\ell_i = \lcm_{j\ne i}(k_j).\]
+with $\alpha_i = \frac{c_i}{k_i}\in \bq$. Write $\ell_i := \lcm
+_{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
+\bk[x_0, \ldots, x_m]$. Now suppose that $f_0, \ldots, f_n$ contain
+$m$ independent linear polynomials in $x_0, \ldots, x_m$ \rm(with possibly
+zero coefficients $\alpha_j$\rm).
 

### 2015-08-20 surfaces-write-up/surface-write-up.tex
surfaces: further revisions to statements of proj/hirz

@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
+Let $D = \sum_{i = 0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
 with $\alpha_i = \frac{c_i}{k_i}\in \bq$. Write $\ell_i := \lcm
 _{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
-\bk[x_0, \ldots, x_m]$. Now suppose that $f_0, \ldots, f_n$ contain
-$m$ independent linear polynomials in $x_0, \ldots, x_m$ \rm(with possibly
-zero coefficients $\alpha_j$\rm).
+\bk[x_0, \ldots, x_m]$ and let each $D_i = V(f_i)$ with $f_i \in \bk[x_0, \ldots, 
+x_m]$. Now suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
+linear polynomials in $x_0, \ldots, x_m$ \rm(with corresponding 
+$\alpha_j$ possibly zero\rm).
 
@@
 \[
-	\sum_{i=0}^n \ell_i a_i
+	\sum_{i = 0}^n \ell_i a_i
 \]
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq
-\otimes_\bz \di \hirz_m$ 
-where $\alpha_i = \frac{c_i}{k_i}$.
-Let $u,v,z,w$ be the coordinates for the Hirzebruch surface
+Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
+\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i}$.
+Write $\ell_i := \lcm_{j \ne i}(k_j)$.
+Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
 $\hirz_m$, as described at the beginning of Section
-~\ref{sec:hirz}. For $1 \leq i \leq n$, let $D_i =
-V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further, after reordering
-the $D_i$ and possibly adding $D_i$ with corresponding $\alpha_i = 0$, suppose $f_1$ and $f_2$ are
-independent linear
-polynomials in $u$ and $v$ and $f_3$ and $f_4$ are independent
-linear polynomials in $w$ and $x$.
-Define
-\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 
+~\ref{sec:hirz}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
+Now suppose that $\{f_0, \ldots, f_n\}$ contains two independent 
+linear polynomials in $u, v$ and two independent linear polynomials in
+$w, x$ \rm(with corresponding $\alpha_j$ possibly zero\rm).
+
 Then $R_D$ is generated in degrees at most

### 2015-08-20 surfaces-write-up/surface-write-up.tex
changing 0 to 1 in hirz and fixing rms, ell i to ell ij

@@
 x_m]$. Now suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
-linear polynomials in $x_0, \ldots, x_m$ \rm(with corresponding 
-$\alpha_j$ possibly zero\rm).
+linear polynomials in $x_0, \ldots, x_m$ {\rm(}with corresponding 
+$\alpha_j$ possibly zero{\rm)}.
 
@@
 \otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i}$.
-Write $\ell_i := \lcm_{j \ne i}(k_j)$.
+Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
 Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
@@
 ~\ref{sec:hirz}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
-Now suppose that $\{f_0, \ldots, f_n\}$ contains two independent 
+Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 
 linear polynomials in $u, v$ and two independent linear polynomials in
-$w, x$ \rm(with corresponding $\alpha_j$ possibly zero\rm).
+$w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.
 

### 2015-08-20 surfaces-write-up/surface-write-up.tex
reference Te definition in hirzebruch statement

@@
 $\hirz_m$, as described at the beginning of Section
-~\ref{sec:hirz}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
+~\ref{sec:hirz} and define $\Te, \Tp, \Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
 Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 
@@
 \begin{defn}
+\label{defn:t-defn}
 Define 

### 2015-08-20 surfaces-write-up/surface-write-up.tex
added in q
added and

--- 2015-08-20 surfaces-write-up/surface-write-up.tex
@@
 Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
-\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i}$.
+\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$.
 Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
@@
 $\hirz_m$, as described at the beginning of Section
-~\ref{sec:hirz}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
+~\ref{sec:hirz} and define $\Te, \Tp$, and $\Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
 Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 

### 2015-08-23 surfaces-write-up/arXiv-versions/surface-write-up-arXiv-v1.tex
surfaces: reflect actual arXiv-v1 version

@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
-as in Theorem ~\ref{thm:proj-effective-intro}. Write $\ell_i := \lcm
+Let $D = \sum_{i = 0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
+with $\alpha_i = \frac{c_i}{k_i}\in \bq$. Write $\ell_i := \lcm
 _{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
-\bk[x_0, \ldots, x_m]$. Now suppose that $f_0, \ldots, f_n$ contain
-$m$ independent linear polynomials in $x_0, \ldots, x_m$ (with possibly
-zero coefficients $\alpha_j$).
+\bk[x_0, \ldots, x_m]$ and let each $D_i = V(f_i)$ with $f_i \in \bk[x_0, \ldots, 
+x_m]$. Now suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
+linear polynomials in $x_0, \ldots, x_m$ {\rm(}with corresponding 
+$\alpha_j$ possibly zero{\rm)}.
 
@@
 and locally factorial, being $\bp^1$-bundles over
-$\bp^1$. Therefore,, the natural map from Cartier
+$\bp^1$. Therefore, the natural map from Cartier
 divisors to Weil divisors is an isomorphism.
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i=1}^n \alpha_i D_i \in \bq
-\otimes_\bz \di \hirz_m$ 
-where $\alpha_i = \frac{c_i}{k_i}$.
-Let $u,v,z,w$ be the coordinates for the Hirzebruch surface
+Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
+\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$.
+Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
+Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
 $\hirz_m$, as described at the beginning of Section
-~\ref{sec:hirz}. For $1 \leq i \leq n$, let $D_i =
-V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further, after reordering
-the $D_i$ and possibly adding $D_i$ with corresponding $\alpha_i = 0$, suppose $f_1$ and $f_2$ are
-independent linear
-polynomials in $u$ and $v$ and $f_3$ and $f_4$ are independent
-linear polynomials in $w$ and $x$.
-Define
-\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\] 
+~\ref{sec:hirz} and define $\Te, \Tp$, and $\Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
+Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 
+linear polynomials in $u, v$ and two independent linear polynomials in
+$w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.
+
 Then $R_D$ is generated in degrees at most
@@
 independent coordinates, so that two distinct integral subschemes
-cannot repreesnt equations of only $m$ of the $m+1$ coordinates.
+cannot represent equations of only $m$ of the $m+1$ coordinates.
 \end{rem}
@@
 \begin{figure}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+\includegraphics{spin-lower-approximations-pic-pics.pdf}
 \caption{This figure shows each non-negative best lower

### 2015-08-29 poster-curves/spin-canonical-poster.tex
added posters

--- 2015-07-16 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
@@
-%%%%%%%%%%%%%%%%%%%%%
-%   AMS packages    %
-%%%%%%%%%%%%%%%%%%%%%
-\documentclass{amsart}
+\documentclass[landscape, a0, largefonts]{sciposter}
+\usepackage{tcolorbox}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{bm}
+\usepackage{multicol}
+\usepackage{graphicx}
+\usepackage[english]{babel}
+\usepackage{color}
+\usepackage{wrapfig}
+\usepackage{caption}
+\usepackage{booktabs}
+\usepackage{array}
+\usepackage{ytableau}
+\usepackage{verbatim}
+\usepackage[vcentermath]{youngtab}
+\newlabel{fig2:a}{{I(a)}{1}}
+\newlabel{fig2:b}{{I(b)}{1}}
+\newlabel{fig:i}{{II(c)}{1}}
+\newlabel{fig:ii}{{II(d)}{1}}
+\newlabel{fig:iii}{{II(e)}{1}}
+\newlabel{fig3:c}{{III(f)}{1}}
+\newlabel{fig3:d}{{III(g)}{1}}
+\newlabel{fig4:i}{{IV(h)}{1}}
+\newlabel{fig4:ii}{{IV(i)}{1}}
+\newcommand{\Q}{\mathbb{Q}}
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\row}{\mathfrak{row}}
+\newcommand{\oh}{\operatorname{outerhook}}
+\newcommand{\col}{\mathfrak{col}}
+\newcommand{\lis}{\mathfrak{lis}}
+\newcommand{\lds}{\mathfrak{lds}}
+\newcommand{\sss}{\scriptstyle} %% for tableaux
+\newcommand{\swap}{\operatorname{swap}}
+\newcommand{\jdt}{\operatorname{jdt}}
+\newcommand{\std}{\operatorname{std}}
+%\usepackage{fancybullets}
+%\usepackage{other packages you may want to use}
 
-\usepackage{amsmath}
 \usepackage{amsxtra}
@@
 \theoremstyle{plain}
-  \newtheorem{thm}{Theorem}[section]
+  \newtheorem{thm}{Theorem}
   \newtheorem{prop}[thm]{Proposition}
@@
 	\newtheorem{rem}[thm]{Remark}
-
-\numberwithin{equation}{section}
 
@@
 
-\newcommand{\PSL}{\operatorname{PSL}}
+%\definecolor{BoxCol}{cmyk}{0.9,0.9,0.9}
+% uncomment for grey background to \section boxes 
+% for use with default option boxedsections
 
-\renewcommand{\arraystretch}{1.2}
+\definecolor{mainCol}{rgb}{1,1,1} %background
+\definecolor{BoxCol}{rgb}{.1,.1,.3} 
+\definecolor{TextCol}{rgb}{0.2,0.5,0.5}
+\definecolor{SectionCol}{rgb}{1,1,1} %section header
+\definecolor{ShadeCol}{rgb}{.9,.95,.9}
+\definecolor{lightpurple}{rgb}{.1,.1,.3} %title box shade
+\definecolor{navy}{rgb}{0.2,0.3,0.5} 	
+\definecolor{white}{rgb}{1,1,1}
+\def\NN{{\mathbb{N}}}
+\def\RR{{\mathbb{R}}}
+\newcommand{\Z}{\mathbb{Z}} 
+%\definecolor{BoxCol}{rgb}{0.9,0.9,1}
+% uncomment for light blue background to \section boxes 
+% for use with default option boxedsections
 
-\makeatletter
-\newcommand{\customlabel}[2]{%
-   \protected@write \@auxout {}{\string \newlabel {#1}{{#2}{\thepage}{#2}{#1}{}} }%
-   \hypertarget{#1}{#2}
-}
-\makeatother
+%\definecolor{SectionCol}{rgb}{0,0,0.5}
+% uncomment for dark blue \section text
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{\vspace{.5cm} \textcolor{white} {Spin Canonical Rings of Log Stacky Curves}}
 
-\title{Spin canonical rings of log stacky curves}
+% Note: only give author names, not institute
+\author{\textcolor{white}{Aaron Landesman, Peter Ruhm, and Robin Zhang}}
 
-\author{Aaron Landesman}
-\address[Aaron Landesman]{Department of Mathematics, Harvard University}
-\email{aaronlandesman@college.harvard.edu}
+%\email[Aaron Landesman]{aaronlandesman@college.harvard.edu}
 
-\author{Peter Ruhm}
-\address[Peter Ruhm]{Department of Mathematics, Stanford University}
-\email{pruhm@stanford.edu}
+% insert correct institute name
+\institute{\vspace{-.25cm} \textcolor{white}{Harvard University, Stanford University, Stanford University}}
 
-\author{Robin Zhang}
-\address[Robin Zhang]{Department of Mathematics, Stanford University}
-\email{robinz16@stanford.edu}
+%\date is unused by the current \maketitle
 
-\date{\today}
+%\leftlogo[0.9]{nsf_logo.png}  % defines logo to left of title (with scale factor)
+%\rightlogo[1.0]{umnlogo.png} % same but on right
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
+%*** facultative: where the poster was presented (appears as a left footer):
+  %\conference{LSU Discover Research Day, 2014, Baton Rouge, LA}
 
-\begin{abstract}
+%*** print the poster header defined above: title, authors, affiliations:
+ \fbox{\colorbox{lightpurple}{\maketitle}}
+\\
+\\
+  \begin{multicols}{3}
+	  \begin{tcolorbox}
+	  \section*{Abstract}
+
  	Consider modular forms arising from a finite-area quotient of the
@@
 	modular forms of arbitrary integral weight.
-\end{abstract}
+\end{tcolorbox}
 
-\maketitle
+  \section*{\textsc{Notation}}
+  \begin{align*}
+	  \Bbbk & & \text{Perfect Field} \\
+	  \sx & & \text{Stacky Curve} \\
+	  X & & \text{Coarse Space} \\
+	  g & & \text{Genus} \\
+	  \Delta & & \text{Log Divisor} \\
+	  \delta & & \text{Degree of Log Divisor} \\
+	  P_1, \ldots, P_r \in \text{Spec } X & & \text{Stacky Points} \\
+	  e_1, \ldots, e_r \in \BZ_{\geq 2}  & & \text{Stacky Orders} \\
+	  (g; e_1,\ldots, e_r; \delta) & & \text{Signature} \\
+	\lfloor \sum_{i=1}^n \alpha_i P_i \rfloor := \sum_{i=1} \lfloor \alpha_i\rfloor P_i & & \text{Floor of a Stacky Divisor} \\
+	K_X & & \text{Canonical Divisor of Coarse Space} \\
+	K_\sx := K_X + \sum_{i=1}^n \frac{e_i-1}{e_i} P_i & & \text{Canonical Divisor of Stacky Curve} \\
+	(\sx, \Delta, L), 2L \sim K_\sx + \Delta & & \text{Log Spin Curve} \\
+	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor) & & \text{Log Spin Canonical Ring}
+  \end{align*}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-Let $\Gamma$ be a {\bf Fuchsian group}, i.e.~ a discrete subgroup of
-$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
-linear transformations, such that $\Gamma \backslash \BH$ has
-finite area.
-We consider the graded {\bf ring of modular forms}
-$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$.
-One of the best ways to describe the ring $M(\Gamma)$ is to write
-down a presentation.
-To do so, it is useful to have a bound on the
-degrees in which the generators and relations can occur. In the
-special case that $\Gamma$ has no odd weight modular forms, Voight
-and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
-The main theorem of this work extends their result to all Fuchsian
-groups $\Gamma$.
-
-We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
-For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
-\backslash \BH$ is a Riemann surface over $\BC$. 
-Although $\Gamma \backslash \BH$ may be non-compact, we can form a
-compact Riemann surface $\Gamma \backslash \BH^*$ by adding in
-cusps (with associated divisor of cusps $\Delta$).
-
-In order to find generators and relations for $M(\Gamma)$, we
-translate the seemingly analytic question of understanding the ring
-of modular forms into the algebraic category, using a
-generalization of the GAGA principle.
-As shown by Voight and Zureick-Brown \cite[Proposition 6.1.5]
-{vzb:stacky}, there is an equivalence of categories between orbifold
-curves and log stacky curves over $\BC$. For the remainder
-of the paper, we will work in the algebraic category.
+  \section*{\textsc{Introduction}}
 
@@
 
-Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize 
-Petri's theorem in the direction of stacky curves equipped with
-log spin canonical divisors. For a stacky curve $\sx$ with coarse space $X$ and
-stacky points (also called ``fractional points'') $P_1, \ldots, P_r$
-with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$, we define
+Our main theorem is to bound the degrees of generators and
+relations of a log spin canonical ring. In 
+~\cite[Theorem 1.4]{vzb:stacky}, Voight and Zureick-Brown tightly
+bounde the degree of generation and
+relations of a log spin canonical ring.
 
-\[
-	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
-	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
-\]
-Then, a {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$
-where $\Delta \in \di X$ is a log divisor and $L \in \di \sx$ is a {\bf log spin canonical divisor}, meaning $2\halfcan \sim K_X +
-\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
-study in this paper is the {\bf log spin canonical ring} of $(\sx,
-\Delta, \halfcan),$ defined as
-\begin{align*}
-	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(X, \lfloor k \halfcan \rfloor).
-\end{align*}
-
-\noindent
-A brief overview of stacky curves, log divisors, and log spin
-canonical rings is given in Subsection
-~\ref{ssec:stacky-background}.
-
-Our main theorem is to bound the degrees of generators and
-relations of a log spin canonical ring. Let $\sx$ be a stacky curve
-with signature $\sigma := (g; e_1, \ldots, e_r; \delta)$. The
-application of O'Dorney's work \cite[Chapter 5]{dorney:canonical}
-to log spin canonical rings gives a weak bound in the case $g = 0$
-in terms of the least common multiples of the $e_i$'s. In their
-treatment of log spin canonical rings, Voight and Zureick-Brown
-\cite[Corollary 10.4.6]{vzb:stacky} bounded generator degrees by $6
-\cdot \max(e_1, \ldots, e_r)$ and relation degrees by $12 \cdot \max
- (e_1, \ldots, e_ r)$ when $\halfcan$ is effective. Note that the
-bounds we deduce differ from those stated in Voight and
-Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2
-because their grading convention differs from ours by a factor of 2.
-
-These bounds are far from tight and do not collectively
-cover all cases in all genera. The main theorem of this paper
-gives significantly tighter bounds for the log spin canonical ring
-of any log spin curve.
+  \section*{\textsc{Main Result}}
 
@@
 \end{thm}
-
-\begin{rem}
-\label{rem:main-weaker-assumptions}
-In fact, the proof of Theorem ~\ref{thm:main} holds with $\Delta$ replaced by an arbitrary effective divisor of the coarse space.
- Furthermore, one may relax the assumption that $\Bk$ is perfect. Instead, one only need assume that the stacky curve
-is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
-\end{rem}
-
-Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.
-In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.
-
-\begin{rem}
-\label{rem:explicit-generators}
-In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
-of the genus one and genus zero cases of our main theorem also yield explicit systems
-of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
-Furthermore, our proof of the genus $g \geq 2$ case provides
-an inductive procedure for explicitly determining the generators
-and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.
-Many
-explicit systems of generators and relations for curves of genus $2
-\leq g \leq 15$ are detailed in interesting examples by Neves
-\cite[Section III.4]{neves:halfcan}. 
-\end{rem}
-
-\begin{rem}
-The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
-In almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
-Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
-For further detail, see Remarks ~\ref{rem:genus-0-explicit-bound}, ~\ref{rem:genus-1-explicit-bound}, and ~\ref{rem:genus-2-explicit-bound} in the cases that the genus is $0,1,$ or $\geq 2$ respectively.
-\end{rem}
-
-Combining the main theorem of this paper, Theorem ~\ref{thm:main} with the main theorem from Voight and Zureick-Brown ~\cite
-[Theorem 1.4]{vzb:stacky} and a minor Lemma \cite[Lemma 10.2.1]{vzb:stacky}
-we have the following application to
-rings of modular forms.
-
-\begin{cor}
-\label{cor:main-mod-forms}
-Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
-associated to $\Gamma \backslash \BH$ with signature $\sigma
-= (g; e_1, \ldots, e_r; \delta)$.
-
-If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
-forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
-degree at most $6 \cdot \max(3, e_1, \ldots, e_r)$ with relations
-generated in degrees at most $12 \cdot \max(3, e_1, \ldots, e_r)$.
-
-If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
-ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
-by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
-relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
-e_r)$ so long as $\sigma$ does not lie in a finite list of
-exceptional cases which are listed and described in Table
-~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
-Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
-\end{cor}
-
-\begin{rem}
-\label{rem:gen-at-most-three}
-If $M(\Gamma)$ has some odd weight modular form, then it has an odd weight modular form in weight $3$.
-When $g \geq 2$, we see that this is true because $\dim_\Bk H^0(\sx, 3\halfcan) > 0$ by Riemann--Roch and the fact that $\deg \lfloor 3\halfcan \rfloor > 2g - 1$.
-When the genus is zero or one, we see that there is a generator in weight $1$ or weight $3$ in the base cases given in Table ~\ref{table:g-1-base} and Table ~\ref{table:g-0-base-cases}.
-Hence, there is an odd weight modular form in weight $3$ in general.
-A consequence of this observation is that the bound on the degree of generators and relations when $M(\Gamma)$ has some odd weight modular form, as given in Corollary ~\ref{cor:main-mod-forms}, is closely related to the degree of the minimal odd weight modular form.
-\end{rem}
-
-\begin{example}
-\label{eg:congruence-bounds}
-In this example, we deduce bounds on the weight of generators and relations of the ring of modular forms associated to any congruence subgroup $\Gamma \subset SL_2(\BZ)$. Since
-the action  of $SL_2(\BZ)$ on $\BH$ only has points with stabilizer
-order 1, 2 and 3, and has at least one cusp, the
-action of $\Gamma$ on $\BH$ can only have points with stabilizer order 1, 2 and 3, and has at least one cusp.
-
-If $\Gamma$ has no nonzero odd weight modular forms, then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$.
-This follows from work by Voight and Zureick-Brown \cite[Theorem 1.4 and Theorem 9.3.1]{vzb:stacky}.
-Note that the exceptional cases of their result \cite[Theorem 9.3.1]{vzb:stacky}, which happen when the genus is zero, do not occur because $\delta > 0$.
-
-If $\Gamma$ has some nonzero odd weight modular form, then it must 
-have no points with stabilizer order 2 by Remark ~\ref{rem:odd-denom}. 
-Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
-generated in degree at most $5$ with relations in degree at most $10$.
-Furthermore, it is not difficult to show that $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
-Note that the exceptional cases in Tables ~\ref{table:g-1-exceptional} and ~\ref{table:g-0-exceptional} do not occur because $\Gamma$ has a cusp, so $\delta > 0$.
-\end{example}
-
-\begin{rem}
-\label{rem:factor-two}
-In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
-bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
-~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively.
-Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two.
-Our grading convention for log spin canonical rings uses weight $k$ for the degree whereas Voight and Zureick-Brown $d = 2k$ for degree.
-\end{rem}
-
-The remainder of the paper will be primarily devoted to proving
-Theorem ~\ref{thm:main}. The idea of the
-proof will be to induct first on the number of stacky points and then on the stabilizer order of those points.  To this end, we first review important background in
-Section ~\ref{sec:background}; providing essential examples in Section \ref{sec:examples}; develop various inductive
-tools in Section ~\ref{sec:induction}; and prove Theorem ~\ref{thm:main} in genus $g\ge 2$, genus $g=1$, and genus $g=0$ in Sections ~\ref{sec:g-high},
-~\ref{sec:g-1}, and ~\ref{sec:g-0} respectively.  
-Finally, in Section
-~\ref{sec:further-questions}, we pose several questions for future
-research.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Background}
-\label{sec:background}
-Here we collect various definitions and notation that will be
-used throughout the paper. Many of the conventions come from existing
-literature. For basic references on the statements and definitions
-used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
-Saint-Donat \cite{saint-donat:proj}, Arbarello--Cornalba--Griffiths--Harris 
-\cite[Section III.2]
-{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
-Chapter 5]{vzb:stacky}.
-
-For the remainder of this paper, fix an algebraically closed field $\Bk$.
-This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closure.
-
-\ssec{Stacky Curves and Log Spin Canonical Rings}
-\label{ssec:stacky-background}
-We begin by setting up the notation for stacky curves and canonical rings.
-Wherever possible, we opt for a more elementary scheme-theoretic approach, instead of a stack-theoretic one.
-See Remark ~\ref{rem:stack-formalism} for more details.
-
-\begin{defn}
-\label{defn:stacky-curve}
-A \textbf{stacky curve} $\sx$ over an algebraically closed field $\Bk$ is the datum of a smooth proper integral scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.
-\end{defn}
-
-\begin{rem}
-\label{rem:stack-formalism}
-Stacky curves may be formally defined in the language of stacks, as
-is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
-Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
-Behrend and Noohi \cite{behrend-noohi:uniformization}.
-
-The results of this paper can be easily phrased in terms of the language of stacks.
-If one works over an arbitrary field $\Bk$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e.~ the residue field of each
-of the stacky points is separable.
-
-With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
-of schemes.
-\end{rem}
-
-\begin{defn}
-\label{defn:div-ex}
-Let $\sx$ be a stacky curve over $\Bk$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
-P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
-Then, we notate
-\[
-	\di \sx := \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
-	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
-	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
-\]
-\end{defn}
-
-We can equip stacky curves with a log divisor $\Delta$ that is a 
-sum of distinct points each with trivial stabilizer. 
-A divisor
-$\Delta$ of this form is called a \textbf{log divisor}. We use
-$\delta := \deg \Delta$ to refer to the degree of the log divisor.
-If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
-\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.
-
-\begin{defn}
-\label{defn:divisor-floor}
-If divisor $D \in \di \sx$ and $D = \sum_{i = 1}^{n} \alpha_i P_i$
-with $\alpha_i \in \BQ$, the floor of a divisor $\lfloor D
-\rfloor$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor P_i$.
-\end{defn}
-
-A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
-called a \textbf{log stacky curve} and the study of their
-canonical rings is the main focus of the work by Voight and 
-Zureick-Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
-spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
-is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
-\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
-\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
-\textbf{log spin canonical divisor} on $(\sx, \Delta)$. Throughout the paper, we use
-the notation $\halfcan_X := \lfloor L \rfloor.$ to refer to the log spin
-canonical divisor (also known as the half-canonical divisor, 
-semi-canonical divisor, or theta characteristic) associated to the
-coarse space $X$ of $\sx.$  (i.e.~ $\halfcan_X$ is a divisor such
-that $2\halfcan_X \sim K_X + \Delta$). 
-We define $H^0$ of a stacky divisor as follows.
-
-\begin{defn}
-\label{defn:h0-stacky}
-Recall the standard notation for the line bundle $\sco(D)$ on an integral normal scheme $X$ associated to a divisor $D \in \di X$:
-\[
-	\Gamma(U, \sco(D)) := \{f \in \Bk(X)^\times : \di|_U f + D|_U \geq 0 \} \cup \{0\}.
-\]
-
-\noindent
-Let $\sx$ be a stacky curve with coarse space $X$.
-If $D \in \di \sx$ is a Weil divisor, then we define
-\begin{align*}
-	H^0(\sx, D) &:= H^0(X, \lfloor D \rfloor)\\
-	H^0(\sx, \sco(D)) &:= H^0(\sx, D)\\
-	h^0(\sx, \sco(D)) &:= \dim_\Bk H^0(\sx, \sco(D))
-\end{align*}
-If $R$ is a graded ring, then we let $(R)_k$ refer to the $k^\text{th}$
-graded component of $R$.
-
-\end{defn}
-
-\begin{rem}
-Although Definition ~\ref{defn:h0-stacky} may seem fairly ad hoc, it is naturally motivated in the context of stacks.
-See Voight and Zureick-Brown \cite[Lemma 5.4.7]{vzb:stacky} for a proof that Definition ~\ref{defn:h0-stacky} is equivalent to the stack-theoretic description.
-\end{rem}
-
-\begin{defn}
-\label{defn:order-sup}
-Let $D \in \di \sx.$ If $z \neq 0$ is a rational section of $\sco(D)$ denote the order of
-zero of $z$ at $P$ by $\ord_P^D(z)$.
-\end{defn}
-
-\begin{defn}
-\label{defn:log-spin-canonical-ring}
-The {\bf log spin canonical ring} of $(\sx, \Delta, \halfcan)$ is
-\[
-	R(\sx, \Delta, \halfcan) := \bigoplus_{k \geq 0} H^0(\sx, k \halfcan).
-\]
-\end{defn}
-
-\noindent
-When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
-represent $R(\sx, \Delta, \halfcan)$.
-
-\begin{rem}
-\label{rem:odd-denom}
-Suppose $(\sx, \Delta, L)$ is a log spin curve. Note that $\halfcan$ is of the form
-\[
-	\halfcan = \sum_{i = 1}^{r} \subhalf{e_i} P_i + \sum_{i = 1}^{s} a_i Q_i
-\]
-
-\noindent
-where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
-that $\halfcan \in \di \sx$: 
-if some $e_i$ were even,
-then $\frac{e_i - 1}{2e_i}$ would be in reduced form implying $\halfcan \notin \di \sx$.
-\end{rem}
-
-\begin{rem}
-\label{rem:delta-not-1}
-Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta$
-is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
-\rfloor = \deg \Delta + 2(g-1).$
-In particular, we shall often use $\deg \Delta \neq 1$.
-\end{rem}
-
-\ssec{Saturation}
-We define the notion of the saturation of a divisor, as can be
-found in Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.
-The classification of the saturations of log spin canonical
-divisors are used in the proof of the main theorem and the various
-lemmas in Section ~\ref{sec:induction}.
-
-\begin{defn}
-Let $D$ be a divisor on $\sx$. The \textbf{effective monoid} of $D$
-is the monoid
-\[
-	\Eff(D) := \{k \in \BZ_{\geq 0} : \deg \lfloor kD \rfloor \geq 0 \}.
-\]
-\end{defn}
-
-\begin{defn}
-\label{defn:sat}
-The \textbf{saturation of a monoid} $M \subseteq \BZ_{\geq 0}$,
-denoted $\sat(M)$, is the smallest integer $s$ such that $M
-\supseteq \BZ_{\geq s}$, if such an integer exists.
-\end{defn}
-
-\begin{rem}
-For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the
-\textbf{saturation of a divisor} $D$. For examples,
-see Subsection ~\ref{ssec:g-0-saturation}.
-\end{rem}
-
-\ssec{Monomial Ordering}
-\label{ssec:monomial-order}
-Here we give a brief overview of the three monomial orderings
-that we use. For further reference on monomial orderings,
-initial ideals, and Gr\"{o}bner bases, see Eisenbud
-\cite[Section 15.9]{eisenbud:comm-alg} and Cox--Little--O'Shea
-\cite[Chapter 2]{cls:ideals-varieties-algorithms}.
-
-\begin{defn}
-\label{defn:monomial-degree}
-Let $\Bk[x_1$, $\ldots$, $x_n]$ be a graded polynomial
-ring with $\deg x_i = k_i$ and let $\alpha := \prod_{i = 1}^{n} x_{i}^{f_i} \in
-\Bk[x_{1}$, $\ldots$, $x_{n}]$ be a monomial. Then
-we define the {\bf degree} of $\alpha$ to be
-\[
-	\deg \alpha := \sum_{i = 1}^{n} k_i f_i.
-\]
-\end{defn}
-
-\begin{defn}
-\label{defn:grevlex}
-The {\bf graded reverse lexicographic order}, or {\bf grevlex} $\prec_{\text{grevlex}}$ is defined as follows.
-If $\alpha := \prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
-monomials in $\Bk[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
-\succ_{\text{grevlex}} \beta$ if either
-
-\begin{equation}
-	\deg \alpha = \sum_{i = 1}^{n} k_i f_i  > \sum_{i = 1}^{n} k_i f_i' = \deg \beta
-\end{equation}
-or
-\begin{equation}
-\label{eqn:grevlex-tie}
-	\deg \alpha = \deg \beta \text{ and }	f_i < f_i' \text{ for
-	the	largest } i \text{ such that } f_i \neq f_i'.
-\end{equation}
-\end{defn}
-
-\begin{rem}
-Note that the ordering of the variables matters in Equation
-~\ref{eqn:grevlex-tie}.
-\end{rem}
-
-Our inductive arguments in Section ~\ref{sec:induction} will
-usually have an inclusion $R \supseteq R'$ of log spin canonical
-rings such that $R_\halfcan$ is generated by elements $x_{i}$ and $R$
-is generated over $R_{\halfcan'}$ by elements $y_j$. In these cases, it is
-natural to consider term orders which treat these sets of variables
-separately.
-
-\begin{defn}
-\label{defn:block-order}
-The \textbf{block term order} is defined as follows. Let $\Bk[y_{1}, \ldots, y_{m}]$ and $\Bk[x_{1}, \ldots,
-x_{n}]$ be weighted polynomial rings with $\deg y_i = c_i, \: \deg x_i = k_i.$ Further assume we are given existing term
-orders $\prec_y$ and $\prec_x$. Let $\alpha :=
-\prod_{j = 1}^{m} y_{j}^{h_i}$ $\prod_{i = 1}^{n} x_{i}
-^{f_i}$ and $\beta := \prod_{j = 1}^{m} y_{j}^{h_i'}
-\prod_{i = 1}^{n} x_{i}^{f_i'}$ be monomials in $\Bk[y_{1},
-\ldots, y_{m}] \otimes$ $\Bk[x_{1}, \ldots, x_{n}]$.
-Let $\alpha_y := \prod_{j = 1}^{m} y_{j}^{h_i}$ be the
-part of $\alpha$ in $\Bk[y_{1}, \ldots, y_{m}]$ and
-likewise with $\alpha_x$, $\beta_y$, and $\beta_x$.
-
-In the \textbf{(graded) block} (or \textbf{elimination}) term
-ordering on $\Bk[y_{k_1', 1}, \ldots, y_{k_m', m}] \otimes \Bk[x_{k_1, 1},
-\ldots, x_{k_n, n}]$, we define $\alpha \succ \beta$ if
-  \begin{enumerate}
-	\item[(i)] $\deg \alpha  > \deg \beta$ or
-  \item[(ii)] $\deg \alpha = \deg \beta$ and $\alpha_y \succ_y \beta_y$ or
-	\item[(iii)] $\deg \alpha = \deg \beta$ and $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$.
-  \end{enumerate}
-\end{defn}
-
-Now we give brief definitions of initial terms and Gr\"{o}bner
-bases. These will be used in the proofs of the inductive lemmas
-in Section ~\ref{sec:induction} as well as in the proof of Theorem
-~\ref{thm:main}.
-
-\begin{defn}
-\label{defn:initial-term}
-Let $\prec$ be an ordering on $\Bk[x_{1}$, $\ldots$, $x_{n}]$, 
-with $\deg x_i = k_i$,
-and let $f \in \Bk[x_{1}, \ldots, x_{n}]$ be a homogeneous
-polynomial. The \textbf{initial term} $\initial(f)$ of $f$
-is the largest monomial in the support of $f$ with respect to
-the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
-\end{defn}
-
-\begin{defn}
-\label{defn:initial-ideal}
-Let $I$ be a homogeneous ideal of $\Bk[x_{1}$, $\ldots$,
-$x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
-the ideal generated by the initial terms of homogeneous polynomials
-in $I$:
-\[
-	\initial(I) := \langle \initial(f) \rangle_{f \in I}
-\]
-\end{defn}
-
-\begin{defn}
-\label{defn:grobner-basis}
-Let $I$ be a homogeneous ideal of $\Bk[x_{1}$, $\ldots$,
-$x_{n}]$. A \textbf{Gr\"obner basis} for $I$, also known as a
-\textbf{standard basis} for $I$, is a set of elements in $I$
-such that their initial terms generate the initial
-ideal of $I$.
-\end{defn}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Examples %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Examples}
-\label{sec:examples}
-
-In this section, we work out several examples of computing presentations for spin canonical rings.
-In addition to providing intuition for the lemmas of Section ~\ref{sec:induction}, these examples also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.
-
-\begin{example}
-\label{eg:base-1-0}
-Let $(\sx',0, \halfcan')$ be a log spin curve of genus $g = 1,$ with $\halfcan' = 0$.
-Counting dimensions, we see $h^0(\sx, k\halfcan')=1$ for all $k \in \mathbb{Z}_{\ge 0}$ so it is immediately clear that $R_{\halfcan'} \cong \Bk[x]$ with $x$ a generator in degree 1.
-\end{example}
-
-\begin{example}
-\label{eg:adding-point}
-Let $(\sx,3 \cdot \infty, L)$ be a stacky curve with coarse space $X$ and signature 
-$(0; 3; 3)$. Let $P_1$ denote the lone stacky point which has stabilizer
-order $3$ and suppose $\infty$ is a fixed closed point of $X$ that is
-not equal to $P_1$.
-
-Recall the notation $\halfcan_X = \lfloor L \rfloor \in \di X$
-(i.e.~ the divisor without any stacky points). We will deduce the
-structure of the log spin canonical ring $R_\halfcan$ from the
-structure of the spin canonical ring $R_{\halfcan_X} := R(X, 3 \cdot
- \infty, \halfcan_X)$. This technique will later be generalized in
-Lemma ~\ref{lem:sat-1}.
-
-Note that $R_{\halfcan_X} \cong \Bk[x_1, x_2]$ where $\deg x_1 = \deg x_2 = 1.
-$ To see this, observe that we will need two generators in degree $1$
-because $h^0(X, \halfcan_X) = 2$ by Riemann--Roch. Because $\halfcan_X$ is very 
-ample, we have that $R_{\halfcan_X}$ is generated in degree 1. To
-conclude, note that $R_{\halfcan_X}$ does not have any relations. If there
-exists some relation, then $\dim \proj R_{\halfcan_X} < 1$. This would
-contradict the fact that $\halfcan_X$ is very ample. Thus, $\proj R_{\halfcan_X}
-\cong X$ which has dimension 1.
-
-Next, we construct generators and relations for $R_\halfcan$ using those
-of $R_{\halfcan_X}$. Note that we have a natural inclusion $\iota: R_{\halfcan_X}
-\hookrightarrow R_\halfcan$ induced by the inclusions $H^0(\sx, k\halfcan_X)
-\hookrightarrow H^0(\sx, k\halfcan)$ for each $k \geq 0$. By Riemann--Roch,
-we see there is some element $y_{1, 3} \in (R_\halfcan)_3$ with $\ord_{P_1}
-(y_{1, 3}) = -1$, not in the image of the inclusion $\iota$. We
-claim that there exist $a_1, a_2 \in \Bk$ and a degree $4$ polynomial
-$f(x_1, x_2) \in \Bk[x_1, x_2]$ such that
-\begin{align*}
-	R_\halfcan \cong \Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3}
-	+ f(x_1,x_2))
-\end{align*}
-
-First, note that $x_1, x_2, y_{1, 3}$ generate all of $R_\halfcan$ from the
-Generalized Max Noether Theorem for genus zero curves from Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}. That is, the maps
-\begin{align*}
-	H^0(\sx, 3L) \otimes H^0(\sx, (k - 3)L) \rightarrow H^0(\sx, k\halfcan)
-\end{align*}
-
-\noindent
-are surjective for $k \geq 4$. A relation of the form $a_1 x_1 y_{1,
-3} + a_2 x_2 y_{1, 3} + f(x_1, x_2) = 0$ must exist because $h^0(\sx,
-4L) - h^0(\sx, 4\halfcan_X) = 1,$ but $x_1 y_{1, 3}$ and $x_2 y_{1, 3}$
-define two linearly independent elements with nontrivial image in
-the 1-dimensional vector space $H^0(\sx, 4L) / H^0(\sx, 4\halfcan_X).$ So,
-we obtain a surjection
-\begin{align}
-\label{align:surjection}
-	\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} + f(x_1, x_2)) 
-	\rightarrow R_\halfcan.
-\end{align}
-
-To complete the example, it suffices to show there are no
-additional relations. First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
-y_{1, 3} + f(x_1, x_2)$ is irreducible because there are no
-relations among $x_1, x_2$ and $y_{1, 3}$ in lower degrees. Hence,
-$\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} +
-f(x_1, x_2))$ is integral and is 2-dimensional. Thus, the map
-\eqref{align:surjection} defines a surjection from an integral
-2-dimensional ring to a 2-dimensional ring. Therefore, it is an 
-isomorphism.
-\end{example}
-
-\begin{example}
-\label{eg:base-0-377}
-Let $(\sx', 0, \halfcan')$ be a log spin curve with signature $\sigma =
-(0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
-\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1, P_2,$ and $P_3$ are
-distinct points. In this example, we will exhibit a minimal
-presentation for $R' = R(\sx', 0, \halfcan')$ and show that $R'$ is
-generated as a $Bk$-algebra in degrees up to $e := \max(5, 3, 7, 7) = 7$
-with relations generated in degrees up to $2e = 14$.
-Notice that $\deg \lfloor k K_{\sx'} \rfloor= -k + \lfloor \frac{k}{3}
-\rfloor + 2 \lfloor \frac{3k}{7} \rfloor$.
-
-By the Generalized Max Noether Theorem for genus 0 curves (see Voight
-and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
-\begin{align}
-\label{eqn:noether-377}
-	H^0 (\sx', 21 \cdot \halfcan') \otimes H^0 (\sx',
-	(k - 21) \halfcan') \rightarrow H^0 (\sx',
-	k \halfcan')
-\end{align}
-
-\noindent
-is surjective whenever $\deg (\lfloor (k - 21) \halfcan' \rfloor)
-\geq 0$. It is fairly easy to see, by use of Riemann--Roch, that
-the saturation of $\halfcan'$ is $5$ (see Definition ~\ref{defn:sat}).
-Then the map in ~\eqref{eqn:noether-377} is surjective when $k \geq
-21 + s = 26$ (i.e.~ $R'$ is generated up to degree 25).
-
-For $k = 0, 1, 2, \ldots$ we have
-\[
-	\dim_\Bk H^0 (\sx', k \halfcan') = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i \halfcan')$.
-
-To show that these generate all of $R'$, we need to show that all
-$H^0 (\sx', k \halfcan')$ are generated by lower degrees for $k = 6$
-and $7 < k \leq 25$. Note that we can again use Max Noether's theorem
-(taking saturation into account) to see that
-
-\begin{align*}
-	&H^0 (\sx', 3 \halfcan') \otimes H^0 (\sx',
-	(k - 3) \halfcan') \rightarrow H^0 (\sx',
-	k \halfcan') \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
-	&H^0 (\sx', 7 \halfcan') \otimes H^0 (\sx',
-	(k - 7) \halfcan') \rightarrow H^0 (\sx',
-	k \halfcan') \text{ if } k \geq 6, k \not\equiv 0, 5
-	\bmod 7
-\end{align*}
-
-\noindent
-are surjective. This reduces the problem to checking generation
-in the degrees of the exceptions $k \in \{8, 12, 21\}$.
-Checking these remaining cases via pole degree considerations shows
-that these degrees are also generated in lower degrees. Thus, $R'$
-is generated in degrees $\{3, 5, 7, 7\}$.
-
-By relabelling the variables if necessary, we can assume that $x_{7
-, 1}$ corresponds to the generator with maximal pole order at $P_2$ 
-and $x_{7, 2}$ correspond to the generator with maximal pole order 
-at $P_3$.
-
-We can directly see that the relations are given in degrees $10$
-and $14$. In particular, we have relations
-\begin{align*}
-	&a_1 x_{5, 1}^2 + a_2 x_{7, 2} x_{3, 1} + a_3 x_{7, 1} x_{3, 1} = 
-	0 &\text{ in degree $10$} \\
-	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
-	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
-\end{align*}
-
-\noindent
-and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
-have that
-\[
-	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
-\]
-
-\noindent
-However, $x_{7, 2} x_{3, 1}$ has pole orders $(3, 3, 4)$ and
-$x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ so their
-coefficients must be zero for this equality to hold. We have a
-similar pole order consideration in forcing $b_1$ to be nonzero.
-
-Let $I$ be the ideal generated by these relations in
-$\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
-$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
-ideal of $I$ is
-\[
-	\initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
-\]
-
-\noindent
-since $a_1$ and $b_1$ are nonzero.
-
-To demonstrate that these two relations generate all 
-relations, we show that $\dim_\Bk (R')_k = \dim_\Bk
-(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_k$ for 
-all degrees $k \geq 0$. In particular,
-
-\begin{align*}
-	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_k &=
-	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_k \\
-	&= \dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_k
-\end{align*}
-\noindent
-for all $k \geq 0$. But the fact $\dim_\Bk (R')_k = \dim_\Bk \left(\Bk[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
-\rangle\right)_k$ can be checked by looking at the $\Bk$-basis at each degree
-$k$.
-
-Therefore, the canonical ring $R'$ has presentation $R' =
-\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
-initial ideal $\initial(I)$ generated by quadratics under grevlex
-with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
-Thus, $R'$ is generated up to degree $e = 7$ with relations up to
-degree $2e = 14$, as desired.
-\end{example}
-
-\begin{example}
-\label{eg:base-1-33}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show that
-$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$.
-
-Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_1$ but not at $P_2$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P_2$ but not at $P_1$.
-Let $y_4 \in H^0(\sx,4\halfcan')$ be an element with a pole of order 1 at both $P_1$ and $P_2$.
-Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q \sim P - Q$, $3P - 3Q + P_1$, and $3P - 3Q + P_1 + P_2$ are 0, 1, and 2 dimensional respectively.
-
-Then, there exist constants $\alpha, \beta, \gamma \in \Bk$ so that 
-$R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $\Bk$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
-The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
-\end{example}
-
-\begin{example}
-\label{eg:exception-1-5}
-Let $(\sx', 0, L')$ be a log spin curve of genus 1 with $L' = P -
- Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_\halfcan)_2$ be any nonzero element.
-We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by
-Riemann--Roch, $\dim_\Bk (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$
-be any nonzero element. We obtain $\di y_3|_{P_1} = -P_1,$ by
-Riemann--Roch, since if $y_3$ did not have a pole at $R$, we would
-obtain $y_3 \in H^0 (\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as
-$P \neq Q$. Finally, let $y_5 \in (R_\halfcan)_5$ be an element with
-$y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in \Bk$
-so that
-
-$$R_\halfcan \cong \Bk[x_2 , y_3, y_5]/(y_3^4 - \alpha x_2 y_5^2).$$
-
-In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring $R$ so that for all $j \in \BZ,$ the $j$th graded component $(R)_j$ satisfies $\dim_\Bk (R)_j = \dim_\Bk R_\halfcan.$ Hence, $R \cong R_\halfcan$.
-The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
-\end{example}
-
-\begin{rem}
-\label{rem:base-0-377}
-Examples ~\ref{eg:base-0-377}, \ref{eg:base-1-33}, and
-\ref{eg:exception-1-5} are used as inductive base cases in the
-genus 0, genus 1, and genus 1 sections respectively (see Tables
-~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
-
-We will come back to Examples ~\ref{eg:base-0-377} and
-\ref{eg:base-1-33} in Examples ~\ref{eg:base-0-377-adm} and
-\ref{eg:base-1-33-adm}, respectively, when checking an
-admissibility condition that will be defined when introducing the
-lemmas used in Subsection ~\ref{ssec:raise-orders} (see Definition
-~\ref{defn:admissible}).
-\end{rem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive lemmas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inductive Lemmas}
-\label{sec:induction}
-First we present several lemmas which provide the inductive steps
-for the proof of the main theorem (Theorem ~\ref{thm:main}). In
-Subsection ~\ref{ssec:add-points} we prove three lemmas which
-determine the generators and relations of $R_\halfcan = R_{\halfcan'
-+ \frac{\alpha }{\beta}P}$ from those of $R_{\halfcan'}$, where
-$\halfcan' \in \BQ \otimes \di X$ and $\frac{\alpha}{\beta} \in \BQ$. 
-In Subsection ~\ref{ssec:raise-orders}, we prove an inductive lemma
-allowing us to transfer information about the log spin canonical 
-ring of a stacky curve to those of stacky curves with stabilizer
-orders incremented by $2$ and fixed log divisor and stacky points.
-
-\ssec{Adding Points}
-\label{ssec:add-points}
-First, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $\Bk[x_1, \ldots, x_m] \to R_D$.
-This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.
-
-\begin{lem}
-\label{lem:relations_from_generators_induction} 
-Suppose $\halfcan$, $\halfcan' \in \BQ$ $\otimes$ $\di X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, such that $R_{\halfcan'}$ generated by $x_1, \ldots, x_m$
-and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over 
-$R_{\halfcan'}$.  Let $I'$ and $I$ be the ideal of relations of $\phi':\Bk[x_1, \ldots, x_m]\to R_{\halfcan'}$ and $\phi:\Bk[x_1, \ldots, x_m, y_1, \ldots y_n]\to R_{\halfcan}$ respectively.
-Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and a monomial ordering $\prec$ such 
-\begin{enumerate}
-\item $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_\halfcan'$
-\item $T \succ S\succ \Bk[x_1, \ldots, x_n]$ {\rm(}meaning all monomials in $T$ are bigger than all monomials in $S$ which are bigger than all monomials in $\Bk[x_1, \ldots, x_n]${\rm)}
-\item  All monomials in $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
-\begin{align*}
-	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[x_1, \ldots, x_m]
-\end{align*}
-\end{enumerate}
-Then,
-\begin{align*}
-	\initial(I) & = \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]
-	+ \langle T \rangle.
-\end{align*}
-\end{lem}
-
-\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-We deduce $\subseteq$ by noting that we can reduce any monomial in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ to a monomial in the basis $S$ via a set of relations whose initial terms include each monomial in $\initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle$.
-
-\begin{proof}
-First, notice that $I'\subseteq I$ so 
-\[
-	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
-\]
-
-Now, let $f\in T$.
-Since $S$ forms a $\Bk$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in \Bk$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
-This demonstrates that $\initial(I) \supseteq T$, and hence
-\[
-	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
-\]
-
-To complete the proof, it suffices to show the reverse inclusion holds.
-By (2), any polynomial $G\in \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
-Furthermore, since $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
-Therefore,
-\[
-	\initial(I)\subseteq R_\halfcan-S.
-\]
-In particular, there are no monomials in $I$ with initial terms in $S$.
-Finally, note that
-\[
-	\initial(I) \cap \Bk[x_1, \ldots, x_m] = \initial(I').
-\]
-
-By (3), every monomial of $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
-\begin{align*}
-	\initial(I) & \subseteq \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
-\end{align*}
-\end{proof}
-
-To apply Lemma \ref{lem:relations_from_generators_induction}, we will need an appropriate monomial ordering.
-The following definition provides the necessary ordering for the Lemma \ref{lem:sat-1}.
-\begin{defn}
-\label{defn:graded-p-lex}
-Suppose $\halfcan$ is a divisor of $X$ such that $R_\halfcan$ is generated by $x_1, \ldots x_m$.
-Then we have a map $\phi: \Bk[z_1, \ldots z_m] \rightarrow R_\halfcan, z_i\mapsto x_i$.
-If $P$ is a point in $X$, then $\phi$ defines a graded-$P$-lexicographic order (shortened to {\bf{graded $P$-lex}}) on $\Bk[z_1, \ldots, z_m]$ as follows.
-If $f=\prod_{i=1}^m {z_i}^{q_i}$ and $g=\prod_{i=1}^m {z_i}^{r_i}$ with $f \neq g,$ then $f\prec g$ if one of the following holds:
-\begin{enumerate}
-\item $\deg(f) < \deg(g)$
-\item $\deg(f) = \deg(g)$ and $-\ord_P(f) < -\ord_P(g)$
-\item $\deg(f) = \deg(g)$, $-\ord_P(f) = -\ord_P(g)$, and $q_i > r_i$ for the largest $i$ such that $q_i\ne r_i$
-\end{enumerate}
-\end{defn}
-
-\begin{rem}\label{rem:graded-P-lex-independent-of-line-bundle}
-Observe that Definition \ref{defn:graded-p-lex} remains the same if we replace $-\ord_P$ with $-\ord_P^{L'}$ for any divisor $\halfcan'$ of $X$.
-\end{rem}
-
-\noindent One can easily verify graded $P$-lex is a monomial ordering in the sense defined in Cox--Little--O'Shea \cite[Chapter 2, $\mathsection$ 2, Definition 1]{cls:ideals-varieties-algorithms}.
-
-We are almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
-\BQ$-divisor.
-Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
-Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$.
-Before stating Lemma ~\ref{lem:sat-1}, we recall some notation from O'Dorney \cite{dorney:canonical}.
-
-\begin{defn}
-\label{defn:lower-approximation}
-If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
-$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
-\textbf{best lower approximation} to $\alpha$ if there does not
-exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
-$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
-\end{defn}
-
-\begin{rem}
-\label{rem:lower-approximation}
-Note that all integers less than or equal to $\lfloor \alpha \rfloor$
-are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
-then the non-negative best lower approximations of
-$\alpha$ form a finite sequence
-\[
-	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
-\]
-
-\noindent
-Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
-\end{rem}
-
-\begin{figure}
-\includegraphics{spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
-Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
-\end{figure}
-
-We next prove the first of three lemmas used to inductively add points.
-
-\begin{lem}
-\label{lem:sat-1}
-Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
-satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
-Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.
-Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha, \beta \in \BN$ such that
-\begin{align}
-\label{eqn:deg1-sat-ind}
-	h^0(X, \lfloor k \halfcan \rfloor) &= h^0(X, \lfloor k \halfcan'
-	\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor &&\text{ for all } k \in \mathbb{
-	N}.
-\end{align}
-Let
-\[
-	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
-\]
-be the positive best lower approximations of $\frac{\alpha}{\beta}$
-{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
-Then,
-
-\begin{enumerate}
-\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
-	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = k_i$ and $-\ord_P
-	^{L'}(y_i) = c_i$.
-
-\item[(b)] Choose an ordering $\prec$ on $\Bk[u, x_1, \ldots, x_m]$ such that
-	\[
-		\ord_u(f) < \ord_u(h) \implies f\prec h.
-	\]
-	Equip $\Bk[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
-	Definition ~\ref{defn:graded-p-lex}, and equip $\Bk[y_1, \ldots,
-	y_n] \otimes \Bk[u, x_1, \ldots, x_m]$ with block order.
-	If $I'$ is the ideal of relations of $\Bk[u, x_1, \ldots, x_m]
-	\to R_{\halfcan'}$ and $I$ is the ideal of relations of
-	$\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]	\to R_{\halfcan}$, then
-
-	\begin{align*}
-		\initial(I) &= \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
-											 + \langle U_i: 1 \le i \le n-1 \rangle
-											 + \langle V \rangle \\
-	\end{align*}
-	where $V = \{x_i y_j: 1 \le i \le m, 1 \le j \le n\}$ and $U_i$ is
-	the set of monomials of the form $\prod_{j = 1}^{i} y_j^{a_j}$ with
-	$a_j \in \BN_{\ge 0}$ such that
-	\begin{enumerate}
-		\item[\customlabel{custom:sat-1-*}{(U-1)}] $\sum_{j = 1}^i a_j c_j \ge c_{i+1}$, \\
-		\item[\customlabel{custom:sat-1-**}{(U-2)}] there does not exist $(b_1, \ldots b_i) \ne (a_1,
-			\ldots a_i)$ with all $b_j \le a_j$ and $\sum_{j = 1}^i b_j
-			c_j \ge	c_{i + 1}$, \\
-		\item[\customlabel{custom:sat-1-***}{(U-3)}] there does not
-			exist $r<i$ such that $\sum_{j=1}^r a_j c_j> c_{r + 1}$.
-	\end{enumerate}
-
-\item[(c)] Let $\tau = \max(1, \max_{1 \leq i \leq m}(\deg(x_i)))$.
-	Then, $R_\halfcan$ is generated over $R_\halfcan'$
-	in degrees up to $\beta$ with $I$ generated over $I'$ in
-	degrees up to $\max(2 \beta, \beta + \tau).$
-\end{enumerate}
-\end{lem}
-
-\sssec*{Idea of proof:}
-The proof will be fairly involved. To show part (a), we first
-define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$
-with one generator corresponding to each positive best lower
-approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch
-to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
-show that the set of elements we produce forms a basis.
-
-Next, part (b) immediately follows from the conclusion of Lemma
-~\ref{lem:relations_from_generators_induction}, reducing the proof
-to verifying the hypotheses of that lemma. The first two hypotheses
-follow immediately from the definition of block order. Checking the
-third condition is quite technical, but follows from the construction of $V$ and the $U_i$'s.
-
-\begin{proof}
-{\bf Part (a):}
-By
-Equation ~\ref{eqn:deg1-sat-ind}, for any $k
-\in \BN$ such that $\lfloor k \frac{ \alpha}{\beta} \rfloor > 0$,
-
-\[
-	h^0 (X, k \halfcan ) = h^0(X, k \halfcan') + \left\lfloor k \frac{\alpha}{\beta} \right\rfloor.
-\]
-
-\noindent
-Thus, there exist rational sections $t_i$ of $\sco(\lfloor k \halfcan \rfloor)$ with $\ord_P^{L'}(t_i) = i$
-for any $i \in \{0, \ldots, \lfloor k \frac{\alpha}{
-\beta} \rfloor \}$. We will the use positive best lower approximations to
-construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
-
-Let 
-\[
-	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
-	\beta}
-\]
-
-\noindent
-be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
-Choose a positive best lower approximation $\frac{c_i}{k_i}$.
-Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$.
-Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
-Hence, for each $j$,
-\[
-	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
-\]
-so the mediant inequality tells us
-\[
-	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
-\]
-Multiplying through by $k_i$ gives
-\[
-	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
-\]
-
-\noindent
-Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees. 
-Choose some $y_i \in(R_{
-\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-
-Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
-\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
-\[
-	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
-\]
-
-\noindent
-which implies
-\begin{equation}\label{eqn:c-from-lower-terms}
-	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
-\end{equation}
-
-Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
-\[
-	S_0 = \{u^l : l \in \BN_{\ge 0}\}
-\]
-and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
-\[
-	S_i = y_j \cdot S_{i-j}.
-\]
-Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
-\[
-	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
-\]
-Then define 
-\begin{equation}\label{eqn:sat-1-defining-S}
-	S = \bigcup_{i=1}^{\infty} S_i.  
-\end{equation}
-Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.
-
-By Equation ~\ref{eqn:deg1-sat-ind} for $k \in \BN$,
-\[
-	h^0(X, \lfloor k \halfcan \rfloor) = h^0(X, \lfloor k \halfcan'
-		\rfloor) + \left\lfloor k \frac{\alpha} {\beta} \right \rfloor,
-\] 
-so $S$ contains elements in degree $k \in \BN$ with each pole order in $\{1 \ldots, \lfloor k\frac{\alpha}{\beta}\rfloor\}$.
-Thus, by dimension counting, $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$, and we have proven part (a).
-
-{\bf Part (b):}
-Let $S$ be as defined in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
-\[
-	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
-\]
-
-We check that $S$, $T$, and $\prec$ meet the hypothesis of Lemma \ref{lem:relations_from_generators_induction}.
-In part (a), we showed that $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$ giving condition (1) of Lemma ~\ref{lem:relations_from_generators_induction}.
-Our choice of monomial order in $\Bk[y_1, \ldots, y_n]$ and block order for $\Bk[y_1, \ldots, y_n]\otimes \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ implies that $T\succ S\succ \Bk[u, x_1, \ldots, x_m]$, giving condition (2) of Lemma \ref{lem:relations_from_generators_induction}.
-
-It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}.
-To do this, suppose $f\in \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $\Bk[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.
-Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$.
-Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.
-Therefore, $f\in \Bk[u, y_1, \ldots, y_n]$.
-We note that $S$ generates $y_j \cdot (\Bk[u,y_1, \ldots, y_n])$ as a $\Bk$-algebra.
-That is, all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\[
-	\Bk[u, x_1, \ldots, x_m] \cup V \cup \left(\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]\right). 
-\]
-Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $\Bk[u, y_1, \ldots, y_n]$.
-If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
-Let $\halfcan$ be maximal such that $a_l\ne 0$.
-Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
-\[
-b_j = \begin{cases}
-	a_j &\text{ if } j \neq i\\
-	a_j + 1 &\text{ if } j=i.
-\end{cases}
-\]
-
-\noindent
-Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S$, 
-and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
-Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
-and have the following still satisfied: each $\gamma_j\le b_j$ 
-and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
-$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
-
-We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  
-Notice that if $r\le n$, $\omega_1, \ldots \omega_r\in \mathbb{Z}_{\ge 0}$, and $\prod_{j=1}^r y_j^{\omega_j}\in S$, then our definition of $S$ implies $y_r\prod_{j=1}^r y_j^{\omega_j}\in S$ if and only if $c_r$ is maximal among $c_1, \ldots c_n$ not greater than than $c_r + \sum_{j=1}^r c_j \omega_j$.
-Therefore, since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$, which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$.
-Therefore $\sum_{j=1}^h {y_j}^{\gamma_j}$ satisfies \ref{custom:sat-1-*}.
-
-Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for some $l$.
-Then, for all $r< h$ we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.
-Furthermore, since $(\gamma_1, \ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.
-Therefore, $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.
-Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{\gamma_j}\in S$ meaning that $\sum_{j=1}^r \gamma_j c_j < c_{r+1}$, condition \ref{custom:sat-1-***} holds for $\prod_{j=1}^h y_j^{\gamma_j}$.  
-Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{h}$.
-
-Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
-\begin{align*}
-				& \Bk[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
-	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[u, x_1, \ldots, x_m].
-\end{align*}
-This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
-Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).
-
-{\bf Part (c):}
-Finally, (c) of this lemma follows immediately by looking at the constructions of parts (a) and (b).  
-\end{proof}
-
-\begin{rem}\label{rem:quad-gen}
-If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_i}$ for some odd $e_i \in \BN_{\geq 3}$, then $T,$ as defined in the beginning of the proof of (b) in Lemma \ref{lem:sat-1} consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
-\end{rem}
-
-\begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{k_i}$ with $k_i=1$).
-When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.
-\end{rem}
-
-We now restrict our attention to log canonical rings of stacky curves.
-Lemma \ref{lem:sat-1} accounts for many of the induction cases when the spin canonical ring is saturated in degree 1, as defined in Definition ~\ref{defn:sat}.
-We complement Lemma ~\ref{lem:sat-1} with the following two lemmas that allow us to inductively add points, under certain conditions when the spin canonical ring is saturated in degree two or three.
-
-\begin{lem}
-\label{lem:sat-2}
-Let $(\sx, \Delta, \halfcan)$ and $(\sx', \Delta, \halfcan')$ be log spin curves with the same coarse space $X = X'$ having signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$, where $e_r=3$.
-Suppose $g > 0,$ and, if $g = 1,$ then $\deg 3\halfcan' \geq 2.$ Then, by Riemann--Roch $\sat(Eff(L'))\le 2$.
-Furthermore, let $R_{\halfcan'} = \Bk[x_2, x_3
-, x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
-3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
-Suppose for $i \in \{2, 3\}$, we generically choose $x_i$ satisfying $\deg x_i = i$ and $\ord_P^{\halfcan'}(x_i)= 0$. Choose an ordering on $\Bk[x_2, \ldots, x_m]$ that satisfies
-\begin{align*}
-	\ord_{x_2}(f) < \ord_{x_2}(h) \implies f \prec h.
-\end{align*}
-
-\noindent
-Then, the following statements hold.
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in
-		\{3, 4\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements
-		$y_3, y_4,$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $\Bk[y_3, y_4]$ with grevlex so that $y_3 \prec 
-		y_4$
-		and equip the ring $\Bk[y_3, y_4] \otimes \Bk[x_2, \ldots, x_m]$ with block 
-		order. Then,
-		\begin{align*}
-			\initial(I) &= \initial(I')\Bk[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
-		\end{align*}
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-First, note that when genus is at least we shall show the assumptions on $g$ imply $H^0(\sx, 3 \halfcan), H^0(\sx, 4 \halfcan)$ are both basepoint-free: If $g \geq 2$ then $\deg 3 \halfcan > 2g - 1$ 
-and $\deg 4 \halfcan > 2g - 1$, so $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
-If $g = 1$, we assume $\deg 3 \halfcan \geq 2 > 2g - 1$, so we also have $\deg 4 \halfcan \geq 2 > 2g - 1,$ so again $H^0(\sx, 3 \halfcan)$ and $H^0(\sx, 4 \halfcan)$ are base point free.
-
-Therefore, general elements $y_3$ and $y_4$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ by Riemann--Roch, proving part (a).
-
-A quick computation checks that the set
-
-\begin{align*}
-	S =	& \; \{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
-	\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
-\end{align*}
-
-\noindent
-is a $\Bk$ basis for $R_\halfcan$ over $R_{\halfcan'}$, thus
-completing part (a).
-
-Letting
-\begin{align*}
-	T =   &\; \{ y_4 x_j \mid 2 \leq j \leq m \}\cup \{ y_4^2 \}
-\end{align*}
-a similar (but much easier) computation to that of lemma $\ref{lem:sat-1}$ determines that $S$, $T$, and $\prec,$ using the ordering defined in (b), meet the conditions of 
-Lemma \ref{lem:relations_from_generators_induction}. 
-Hence, by Lemma \ref{lem:relations_from_generators_induction}, part (b) holds.
-\end{proof}
-
-\begin{lem}
-\label{lem:sat-3}
-Suppose $\halfcan'$ is a log spin canonical divisor of $\sx'$ with coarse
-space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
-{\halfcan'} \cong \Bk[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
-{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
-the ordering on $\Bk[x_3, \ldots, x_m]$ satisfies
-\begin{align*}
-	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
-\end{align*}
-
-\noindent
-Then, the following statements hold.
-
-\begin{enumerate}
-	\item[(a)] General elements  $y_i \in H^0(\sx, iL)$ for $i \in \{3,
-		4,5\}$ satisfy $-\ord_P^{\halfcan'}(y_i) = 1$ and any such choice of elements $y
-		_3, y_4,$ and $y_5$ minimally generate $R_\halfcan$ over $R_{\halfcan'}$.
-	\item[(b)] Equip $\Bk[y_3, y_4, y_5]$ with grevlex so that $y_3 \prec 
-		y_4 \prec y_5$
-		and equip the ring $\Bk[y_3, y_4, y_5] \otimes \Bk[x_3, \ldots, x_m]$ with the block order.  Then,
-		\begin{align*}
-			\initial(I) &= \initial(I) \Bk[y_3, y_4, y_5, x_3, \ldots, x_m] \\
-			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
-			&+ \langle y_i y_k \mid 4 \leq i \leq j \leq 5\rangle.
-		\end{align*}
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-Since $X$ has genus 0, general
-elements $y_3, y_4,$ and $y_5$ in weights 3, 4, and 5 respectively satisfy $-\ord_P^{\halfcan'}(y_i) =
-1$. We see by pole order considerations that
-
-\begin{align}
-\label{eqn:add_one_generator}
-	\begin{split}
-		S=	&\{ y_3^ax_3^b x_4^\epsilon x_5^{\epsilon'} \mid a \geq 0, b 
-		\geq 0,(\epsilon, \epsilon') \in \{(0,0),(0,1),(1,0)\} \} \\
-		\cup \;&\{y_3^ay_4, y_3^by_5 \mid a \geq 0, b \geq 0 \}
-	\end{split}
-\end{align}
-
-\noindent forms a $\Bk$ basis for $R_\halfcan$ over $R_{\halfcan'}$, which concludes part (a) of the proof.
-
-Setting
-\[
-	T = \{ y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\} \cup \{ y_i y_k \mid 4 \leq i \leq j \leq 5\} 
-\]
-we can argue similarly to Lemma \ref{lem:sat-1} that $S$ and $T$ along with $\prec$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, concluding part (b).
-\end{proof}
-
-One can prove similar results in cases with different conditions on saturation, base-point freeness, and the coefficients of added points, but only the cases of Lemmas ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} are needed for the remainder of this paper.
-We next turn to an inductive method to increment the $e_i$'s.
-
-\ssec{Raising Stabilizer Orders}
-\label{ssec:raise-orders}
-In this subsection, we present Lemma ~\ref{lem:raise-stacky-order},
-whose proof is almost identical to one of Voight and Zureick-Brown
-\cite[Theorem 8.5.7]{vzb:stacky}. Lemma
-~\ref{lem:raise-stacky-order} implies that if the main result,
-Theorem ~\ref{thm:main}, holds for a curve with signature $(g; e_1',
-\ldots, e_\ell', e_{\ell + 1}' \ldots, e_r';\delta)$ with $e_{\ell + 1}' =
-\cdots = e_r'$ satisfying an admissibility condition (cf. Definition
-~\ref{defn:admissible}), then Theorem ~\ref{thm:main} also holds for
-a curve with signature $(g; e_1', \ldots, e_\ell', e_{\ell + 1}' + 2,
-\ldots, e_r' + 2; \delta)$.
-
-First, we define a notion of admissibility that is quite similar to
-the admissibility defined by Voight and Zureick-Brown
-\cite[Definition 8.5.1]{vzb:stacky}. Our notion is an adaptation
-the case of log spin canonical divisors.
-
-One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and that of Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky} is that
-we cannot assume that $\{P_i\} \cap \Supp(\halfcan_X') = \emptyset$, as $ \halfcan_X'$ may have no nonzero global sections.
-We circumvent this issue by working with the orders of zeros and poles relative to $\halfcan_X'$, rather than relative to the $\sco_X,$ using Definition ~\ref{defn:order-sup}.
-
-\begin{defn}
-\label{defn:admissible}
-Let $(\sx', \Delta, L')$ be a log spin
-curve, with coarse space $X$ and stacky points $Q_1, \ldots, Q_r$.  Let $J \subset
-\{1, \ldots, r\}$. Let $e_i := e_i'+ 2 \chi_J (i)$ where
-
-\[
-\chi_J(i) = \begin{cases}
-	1, &\text{ if }i \in J\\
-	0, &\text{ otherwise. } 
-\end{cases}
-\]
-
-Let $R'$ be the canonical ring associated to $\sx'$. Define $(\sx', \halfcan', J)$
-to be {\bf admissible} if $R'$ admits a presentation
-\begin{align*}
-	R' \cong \left( \Bk[x_1, \ldots, x_m] \otimes \Bk[y_{i, e_i'}]_{i \in J} \right)/I'
-\end{align*}
-
-\noindent
-with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
-three conditions hold:
-\begin{enumerate}
-	\item[\customlabel{custom:Ad-i}{(Ad-i)}] First, 
-		\begin{align*}
-		\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
-			= \frac{e_i'- 1}{2}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-ii}{(Ad-ii)}] Second, every generator $z 
-		\in \{x_1, \ldots, x_m\} \cup \{y_{j, e_i'}: j\in J - \{i\} \}$ 
-		satisfies
-		\begin{align*}
-			\frac{-\ord_{Q_i}^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
-		\end{align*}
-	\item[\customlabel{custom:Ad-iii}{(Ad-iii)}] Third, we have
-		\begin{align*}
-			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{k \geq 0} \# S_{\sigma, J}(i, k)
-		\end{align*}
-		where
-		\begin{align*}
-			S_{\sigma, J}(i, k) := \{j \in J : j \neq i \text{ and } e_j'+2k
-			\mid e_i - e_j'\}.
-		\end{align*}
-\end{enumerate}
-\end{defn}
-
-Before using this admissibility condition in the lemmas of
-this section, we give a few explicit examples for which admissibility
-holds.
-
-\begin{example}
-\label{eg:base-0-377-adm}
-Here, we explicitly check admissibility in the context of
-Example ~\ref{eg:base-0-377}. Recall that the setup is that
-$(\sx', 0, \halfcan')$ is a log spin curve with signature $\sigma := (0; 3, 7, 7; 0)$
-and $\halfcan' \sim -\infty + \frac{1}{3}P_1 + \frac{3}{7}P_2 + \frac{3}{7}P_3$,
-where $P_1, P_2$, and $P_3$ are distinct points. We demonstrate
-that $(\sx', \halfcan', \{2, 3\})$ is admissible.
-
-As shown in Example ~\ref{eg:base-0-377}, the log spin canonical
-ring corresponding to $(\sx', 0, \halfcan')$ has a presentation
-$\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
-$x_{i, j} \in H^0(\sx', i \halfcan')$. Furthermore, we were
-able to chose generators such that $x_{7, 1}$ has maximal pole
-order at $P_2$ and $x_{7, 2}$ has maximal pole order at $P_3$.
-
-Use the presentation given above with $y _{2, e_2'} :=
-x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$.
-We see that $(\sx', \halfcan', \{2, 3\})$ immediately satisfies
-\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we
-check \ref{custom:Ad-ii}.  We may also choose
-pole orders of the generators such that $y_{i, e_i'}$ is the only
-generator lying on the line $-ord_{P_i}(z) = \deg (\frac{3k}{7} z)$
-in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
-generators lying below the line as seen in Figure ~\ref{fig:377}
-(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
-(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
-and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
-$x_{7, 2}$ respectively).
-
-\begin{figure}[H]
-\includegraphics{spin-377-pic-pics.pdf} \\
-\caption{Generators in the $(\deg z, -ord_{P_2}(z))$ lattice}
-\label{fig:377}
-\end{figure}
-
-Also note that $e_j' + 2k = 7 + 2k \nmid 2 = e_i - e_j'$ for all
-$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $k \geq
-0$. Thus, $s_{\sigma, J}(i, k) = \emptyset$ for each $i \in J$.
-Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
-\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
-\frac{9}{3} \rfloor - 9 = 2$, so \ref{custom:Ad-iii} is satisfied and
-$(\sigma, \sx', \{2, 3\})$ is admissible.
-\end{example}
-
-\begin{example}
-\label{eg:base-1-33-adm}
-Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with
-$\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$, as in Example
-~\ref{eg:base-1-33}. Here, we check that $(\sx', \halfcan', \{1,2\})$
-is admissible.
-
-Recall that
-$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u).$$
-We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction.
-Hence, \ref{custom:Ad-i} holds.
-We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric.
-Here, by construction
-\[
-\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
-	0 &\text{ if }z \in \{u, y_3\}\\
-	\frac{1}{4} &\text{ if }z = y_4.
-\end{cases}
-\]
-
-\noindent
-Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
-Finally, to check \ref{custom:Ad-iii}, note that $\max_{k \geq 0}S_{\sigma,J}(i,k) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
-\end{example}
-
-The following lemma will slightly strengthen condition
-\ref{custom:Ad-ii} from Definition ~\ref{defn:admissible}.
-This improvement is crucial in the proof of part (c) of Lemma
-~\ref{lem:raise-stacky-order}.
-
-\begin{lem}
-\label{lem:admissible_inequality}
-For any $z$ as in condition \ref{custom:Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{custom:Ad-ii} implies the
-tighter inequality that
-
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} -\frac{1}{e_i'}
-\end{align*}
-\end{lem}
-
-\begin{proof}
-We know by \ref{custom:Ad-ii} that
-
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) < \deg(z) \subhalf{e_i'}
-\end{align*}
-
-\noindent
-If we write $\frac{\alpha}{\beta} = \deg(z) \frac{e_i'- 1}{2e_i'}$ 
-as a fraction in lowest terms, then we see $\beta \mid e_i'$ since $
-e_i'- 1$ is even. Therefore, since $-\ord_{Q_i}
-^{\halfcan_X'}(z)$ is an integer, 
-we must have
-
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(z) \leq \deg(z) \subhalf{e_i'} - \frac{1}{\beta} \leq 
-	\deg(z) \subhalf{e_i'} - \frac{1}{e_i'}.
-\end{align*}
-\end{proof}
-
-\begin{lem}
-\label{lem:admissible_subset}
-If $(\sx', \Delta, \halfcan')$ is a log spin curve, $(\sx', \halfcan', J)$ is admissible and $W \subseteq J$ is any subset,
-then $(\sx', L', W)$ is also admissible.
-\end{lem}
-
-\begin{proof}
-Each of the conditions \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} hold for $W$
-if they hold for $J$.
-\end{proof}
-
-\begin{rem}
-\label{rem:three-cases}
-For our inductive arguments in Theorems ~\ref{thm:g-high-main},
-~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a
-single stacky point with stabilizer order $3$. Say $(\sx, \Delta,
-\halfcan)$ is a log spin curve with signature $\sigma := (g; e_1,
-\ldots, e_r; \delta) = (g; 3, \ldots, 3; \delta)$, and our base cases
-include signatures $\sigma$ characterized by one of the following:
-cases, which we will soon refer to in Lemma
-~\ref{lem:raise-stacky-order}:
-
-\begin{enumerate}
-	\item[\customlabel{custom:three-cases-1}{(1)}] $g = 0, e_1 =
-		\cdots = e_r = 3, \delta = 0$, and $r \geq 5$
-	\item[\customlabel{custom:three-cases-2}{(2)}] $g = 1, e_1 =
-		\cdots = e_r = 3, \delta = 0$, and $ r \geq 2$
-	\item[\customlabel{custom:three-cases-3}{(3)}] $g \geq 2, e_1 =
-		\cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
-\end{enumerate}
-\end{rem}
-
-\begin{lem}
-\label{lem:raise-stacky-order}
-Suppose $(\sx', \Delta, \halfcan')$ is a log spin curve with coarse
-space $X'$ and signature $\sigma := (g; e_1', \ldots, e_r'; \delta)$.
-Define $R':= R_{\halfcan'}$.  Further, assume either 
-\begin{enumerate}
-	\item $(\sx', \halfcan', J)$ is admissible with generators $x_1,
-		\ldots, x_m \in R'$ and $y_{i, e_i'} \in R' $ for all $i \in J$, as 
-		in Definition ~\ref{defn:admissible} or
-	\item $\sigma$ is one of the signatures described in Cases
-		\ref{custom:three-cases-1}, \ref{custom:three-cases-2} and
-		\ref{custom:three-cases-3} of Remark ~\ref{rem:three-cases} and
-		$y_{1, 3} = y_{2,3} = \ldots= y_{r,3}$ is a rational section of
-		$\sco(\halfcan_X)$ with $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$
-		for $1 \leq  i \leq r$.
-\end{enumerate}
-Let
-$(\sx, \Delta, \halfcan)$ be another log spin curve
-with coarse space $X$, so that $X \cong X'$ and with signature $(g; e_1, \ldots, e_r;
-\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
-$e_j = e_j'$ for $j \notin J$. Define $R := R_\halfcan$.  Then the following are true:
-\begin{enumerate}
-	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
-		H^0(\sx, e_i(K_\sx))$ so that
-		\begin{align*}
-			-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
-		\end{align*}
-		and
-		\begin{align*}
-			\frac{-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
-\subhalf{
-			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
-		\end{align*}
-		for all $j \in J$ with $j \neq i$.
-	\item[(b)] A choice of elements $y_{1, e_1}, \ldots, y_{r, e_r}$ as in part (a) minimally
-		generate $R$ over $R'$.
-	\item[(c)] Endow $\Bk[y_{i, e_i}]_{i\in J}$ and $ \Bk[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$ with graded monomial orders and give 
-$\Bk[y_{i, e_i}]_{i\in J} \otimes \Bk[x_1, \ldots, x_m, y_{i, e_i'}]_{i\in J}$
- block order.  Let $I$ be the kernel of $\Bk[x_1, \ldots, x_m, y_{i, e_i'}, y_{i, e_i}]_{i\in J} \to R$.
-  Then,
-		\begin{align*}
-			\initial(I) \;	&= \; \initial(I')\Bk[x, y] \\
-					&+ \; \langle y_{j, e_j}x_i  : 1\le i \le m, j\in J\rangle \\
-					&+ \; \langle y_{j, e_j}y_{i, e_i'}: i,j\in J, i\ne j\rangle \\
-					&+ \; \langle y_{j,e_j}y_{i,e_i}: i,j\in J, i\ne j\rangle.
-		\end{align*}
-	\item[(d)] The triple $(\sx, \halfcan', J)$ is admissible.
-\end{enumerate}
-\end{lem}
-
-\sssec*{Idea of Proof:}
-The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch
-and condition ~\ref{custom:Ad-iii}. The inequality in Part (a)
-follows from the fact that $\halfcan$ is similar to $\halfcan'$,
-but with some of the $e_i$ incremented by $2$. Part (b) follows
-because the sub-lattice spanned by $y_{i, e_i}$ and $y_{i, e_i'}$
-has determinant $1$ for $i \in J$, so the generators in Part (a)
-generate all of $R_\halfcan$ over $R_{\halfcan'}$. To check part (c),
-we construct relations between the generators of $R_{\halfcan}$
-over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$
-if and only if its pole order at $P_i$ for $i \in J$ is not too
-large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole
-orders. Part (d) follows fairly easily from the definition of
-admissibility.
-
-\begin{proof}
-We prove this in case (1). Case (2) follows a similar procedure.
-
-{\bf Part (a):} 
-By Definition ~\ref{defn:admissible}, for all $i\in J$
-
-\begin{align*}
-	S(i,0) = \{j \in J : j \neq i \text{ and }e_j' \mid e_i-e_j'\} = \{j \in J : j \neq i \text{ and }e_j' \mid e_i\}.
-\end{align*}
-
-\noindent
-Define
-\begin{align*}
-	E_i = \sum_{j \in S(i,0)}^{}Q_j.
-\end{align*}
-
-\noindent
-The assumption \ref{custom:Ad-iii} implies
-\begin{align*}
-	\deg \left( e_i L' - E_i \right) \geq \max(2g - 1,0),
-\end{align*}
-
-\noindent
-and so $H^0(\sx', e_iL'-E_i + Q_i)$ is base point free by 
-Riemann--Roch.
-Hence, a general element
-\begin{align*}
-	y_{i, e_i} \in H^0(\sx', e_iL'-E_i + Q_i)
-\end{align*}
-
-\noindent
-satisfies
-\begin{align*}
-	-\ord_{Q_i}
-^{\halfcan_X'}(y_{i, e_i}) = \left\lfloor e_i \subhalf {e_i'} \right\rfloor + 1 =
-	\frac{e_i - 1}{2}.
-\end{align*}
-
-Noting that
-\begin{align*}
-	\lfloor e_i L' \rfloor + Q_i \leq \lfloor e_i L \rfloor,
-\end{align*}
-
-\noindent
-we obtain an inclusion
-\begin{align*}
-	H^0(\sx', e_iL'-E_i + Q_i) \rightarrow H^0(\sx, e_iL - E_i) \subseteq 
-H^0(\sx, e_iL)
-\end{align*}
-
-\noindent
-meaning that $y_{i,e_i}\in H^0(\sx,e_iL)$ satisfies the first part of claim (a).
-
-We next show $y_{i, e_i}$ also satisfies the second part of the
-claim of $(a),$ by considering separately the cases in which $j
-\in S(i, 0),$ and $j \notin S(i,0)$.
-
-If $j \in S(i,0)$, then $E_i \geq Q_j$ gives $y_{i, e_i} \in H^0
-(\sx', e_iL'-E_i + Q_i)$ an extra vanishing condition at $Q_j$, so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq e_i\subhalf {e_j'} - 1 \leq e_i 
-	\subhalf{e_j'} - \frac{1}{e_j'}.
-\end{align*}
-
-If instead $j\ne i$ and $j \notin S(i,0)$, then since $e_j' \nmid e_i$, we know
-$e_i\subhalf{e_j'} \notin \BZ$, so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i}) \leq \left\lfloor  e_i\subhalf{e_j'} \right\rfloor 
-	\leq e_i\subhalf{e_j'} - \frac{1}{e_j'},
-\end{align*}
-
-\noindent
-completing the proof of (a).
-
-{\bf Part (b):}
-Define $R_0 = R'$ and for $i \in \{1, \ldots, r\},$ inductively define 
-$$R_i = \begin{cases}
-	R_{i - 1} &\text{ if }i \notin J\\
-	R_{i - 1}[y_{i, e_i}] &\text{ if }i \in J. 
-\end{cases}$$
-
-\noindent
-To prove (b), it suffices to show that elements of the form $y_{i, e_
-i'}^ay_{i, e_i}^b$ with $a \geq 0, b > 0$ form a $\Bk$-basis for $R_{i}$ over $R_{i-1}$.
-These elements do not lie in $R_{i - 1}$ because the pole order of $y_{i, e_i'}^ay_{i,e_i}^b$ at $Q_i$ is larger than that of any element in the $k^{th}$ component of $R_{i - 1}$.
-Additionally, these elements are linearly independent amongst themselves because of
-injectivity of the linear map
-
-\begin{align*}
-	(a,b) \mapsto \left( \deg\left(y_{i, e_i'}^ay_{i, e_i}^b\right),-
-	\ord_{Q_i}
-^{\halfcan_X'}\left( y_{i, e_i'}^ay_{i, e_i}^b \right)  \right) = (a,b) 
-	\begin{pmatrix}
-		e_i -2 & \frac{e_i -3}{2} \\
-		e_i	 & \frac{e_i - 1}{2}
-	\end{pmatrix}.
-\end{align*}
-
-\noindent
-Furthermore, $\{y_{i, e_i'}^a y_{i, e_i}^b:a \geq 0,
-b > 0\}$ span $R_i$ over $R_{i - 1}$, because the set of
-integer lattice points in the cone generated by the vectors $\left(e
-_i -2, \frac{e_i -3}{2} \right)$ and $\left(e_i, \frac{e_i - 1}{2}
-\right)$ is saturated, because the corresponding determinant is
-\begin{align*}
-	(e_i -2) \frac{e_i - 1}{2} - e_i \frac{e_i -3}{2} = 1.
-\end{align*}
-This completes part (b).
-
-{\bf Part (c):}
-To show (c), we wish to show that $y_{i, e_i}z \in R'$ for all generators $z$ of $R'$
-with $z \neq y_{i, e_i} \text{ and } z \neq y_{i, e_i'}$. By definition of $H^0(\sx,\halfcan')$, note that $f \in R$ further satisfies $f \in R'$ if and
-only if for all $j \in J$ we have
-\begin{align}
-\label{eqn:order-degree}
-	-\ord_{Q_j}
-^{\halfcan_X'}(f) \leq \deg (f) \left( \subhalf {e_j'} \right).
-\end{align}
-
-\noindent
-Now fix $i \in J$. We check that Inequality ~\eqref{eqn:order-degree} holds with $f = y_{i, e_i}z$, implying $y_{i,e_i}z \in R'$ in the three following cases:
-
-\vskip.1in
-\noindent
-{\sf Case 1: $j \notin \{i \} \cup S(i,0).$}
-
-Here, $L|_{Q_j} = L'|_{Q_j},$ so
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
-^{\halfcan_X'}(z) \leq e_i \subhalf {e_j'} +
-	\deg (z) \subhalf {e_j'} = \deg (y_{i, e_i}z) \subhalf{e_j'}. 
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 2: $j =i.$}
-
-By part (a), condition \ref{custom:Ad-ii}, and Lemma
-~\ref{lem:admissible_inequality} we have
-\begin{align*}
-	-\ord_{Q_j}
-^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
-^{\halfcan_X'}(z)
-	&\leq \frac{e_j - 1}{2} + \deg (z) \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
-	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg (z) \left( \subhalf{e_j'} \right) \\
-	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg (z) \left( \subhalf{e_j'} \right) \\
-	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
-\end{align*}
-
-\vskip.1in
-\noindent
-{\sf Case 3: $j \in S(i,0).$}
-
-In this case, we may first assume $z \neq y_{j, e_j}$, 
-as this is covered by case 2, with $i$ and $j$ reversed. 
-Hence, 
-\begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(z) \leq \deg z \subhalf{e_j'},
-\end{align*}
-implying
-\begin{align*}
-	-\ord_{Q_j}^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}^{\halfcan_X'}(z) 
-	&\leq  e_i \subhalf{e_j'} + \deg z \subhalf{e_j'} 
-	= \deg (y_{i, e_i}z) \subhalf{e_j'},
-\end{align*}
-completing part (c).
-
-{\bf Part (d):}
-To check (d), we show \ref{custom:Ad-i}, \ref{custom:Ad-ii}, and \ref{custom:Ad-iii} are satisfied. We know \ref{custom:Ad-i} holds by part (b), taking the $y_{
-i, e_i}$ as the generators in degree $e_i$. Next, \ref{custom:Ad-ii} is
-strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
-Finally, if \ref{custom:Ad-iii} holds for $e$ then it holds for $e + 2$ by
-definition. This is where we use that \ref{custom:Ad-iii} holds for $k > 0$
-and not just for $k = 0$.
-\end{proof}
-
-\begin{cor}
-\label{cor:raise-stacky-order}
-Suppose $(\sx', \halfcan',J')$ is admissible with signature $\sigma' = (e_1
-', \ldots,e_r')$ or $\sigma$ satisfies one of the conditions of
-Remark ~\ref{rem:three-cases}. Let $J' = \{t,t+1, \ldots,r\}$ and
-$e_1' \leq e_2' \leq \cdots \leq e_t' = e_{t+1}' =\cdots = e_r'$,
-so that $(\sx', \Delta, L)$ satisfies the conditions of Lemma
-~\ref{lem:raise-stacky-order} and Theorem ~\ref{thm:main}. Then,
-for any spin curve $(\sx, \Delta, L)$ so that $\sx$ and $\sx'$ have
-the same coarse space $X = X'$ with the same set of stacky points,
-and $  \sx$ has signature $(g; e_1, \ldots, e_r; \delta)$ with $e_1
-\leq e_2 \leq \cdots e_r$ so that
-\begin{align*}
-	& e_i	= e_i' &\text{ if }i \notin J \\
-	& e_i \ge e_i' &\text{ if } i \in J
-\end{align*}
-
-\noindent
-then Theorem ~\ref{thm:main} holds for $(\sx, \Delta, \halfcan)$.
-\end{cor}
-
-\begin{proof}
-For $t \leq i \leq r$, let $(\sx_i, \Delta, \halfcan_i)$ be the log spin curve with coarse space $X_i$ so that $X_i = X',$ with the same stacky points as $(\sx', \Delta, \halfcan),$ and having signature $(g; e_1, \ldots.
-e_{i - 1}, e_i, e_i, \ldots, e_i; \delta).$ Let
-$J_i = \{i, \ldots, r\}.$ Note that $(\sx_0, \halfcan_0,J_0) = (\sx', \halfcan',J')$ and $(\sx_r , \halfcan_r ,J_r) = (\sx, L, \{r\})$.
-
-Let $(*_i)$ denote the condition that $(\sx_i, \Delta, L_i)$
-satisfies the conditions of Lemma ~\ref{lem:raise-stacky-order} and
-Theorem ~\ref{thm:main}, and $(\sx_i, \halfcan_i, J_i)$ is
-admissible. Since $(*_0)$ holds by assumption, it suffices to show
-that if $(*_i)$ holds then so does $(*_{i + 1})$. Indeed, $(\sx_i,
-\halfcan_i, J_{i + 1})$ is admissible by an application of Lemma
-~\ref{lem:admissible_subset} and the fact that $J_{i + 1} \subseteq J
-_i$. Then, applying Lemma ~\ref{lem:raise-stacky-order} with the
-fixed set $J_{i + 1}$ repeatedly ($\frac{e_{i + 1} - e_i}{2}$ many
-times) yields $(*_{i + 1})$.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus $\geq 2$ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Genus At Least Two}
-\label{sec:g-high}
-We now consider the case when the genus is at least 2.
-In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations.
-In this section, we do not obtain explicit presentations of $R_\halfcan$.
-This contrasts with Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations.
-The tradeoff is that in the genus zero and genus one cases, we have to deal with explicit base cases.
-In this section we apply general results.
-
-\ssec{Bounds on Generators and Relations in Genus At Least Two}
-\label{ssec:bounds-high-genus}
-
-The main result of this subsection is that for a log spin curve with no stacky points $(X, \Delta, L)$, the spin canonical ring $R_\halfcan$ is generated in degree at most $5$, with relations in degree at most $10$.
-The case that $\Delta = 0$ was completed by Reid \cite[Theorem 3.4]{reid:infinitesimal}.
-For $\Delta > 0$, the generation bound is shown in Lemma ~\ref{lem:generation-5} and the relations bound is shown in Lemma ~\ref{prop:relation-10}.
-Throughout this subsection, we will implicitly use Remark ~\ref{rem:delta-not-1}, which implies $\deg 2L \geq 2g$ so $H^0(X, 2L)$ is basepoint-free by Riemann--Roch.
-We summarize the results of this subsection in Corollary ~\ref{cor:g-2-presentation-bound}.
-
-The proofs of this subsection results are similar to those in Neves ~\cite[Proposition III.4 and Proposition III.12]{neves:halfcan}.
-However, the statements differ, as we assume $\Delta > 0$ instead of $\Delta = 0$ and do not assume there is a basepoint-free pencil contained in $H^0(X, L).$
-
-\begin{lem}
-\label{lem:generation-5}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g;-;\delta),$ {\rm(}where $-$ means $X$ is a bona fide scheme and has no stacky points,{\rm)}
-with $g \geq 2$ and $\Delta > 0.$ Let $s_1$, $s_2 \in H^0(X, 2L)$
-be two independent sections such that the vector subspace $V =
-\newspan(s_1, s_2) \subseteq H^0(K)$ is basepoint-free. Then, the map
-\begin{align*}
-	V \otimes H^0(nL) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective if $n \geq 4$. In particular, $R_\halfcan$ is generated in degree at most $5.$
-\end{lem}
-
-\begin{proof}
-To show there are no new generators in degree at least $6$, it
-suffices to show that if $n \geq 4$, the map
-\begin{align*}
-	H^0(nL) \otimes H^0(2L) \rightarrow H^0((n+2)L)
-\end{align*}
-is surjective. Indeed, since $V = \newspan(s_1, s_2) \subseteq
-H^0(K)$ is basepoint-free, by the basepoint-free pencil trick (see
-\cite[Lemma 2.6]{saint-donat:proj} for a proof), we obtain an exact
-sequence
-\begin{align*}
-0 \longrightarrow H^0((n - 2)\halfcan) \longrightarrow V \otimes
-H^0(n \halfcan) \overset{f}{\longrightarrow} H^0((n + 2)\halfcan)
-\end{align*}
-
-We wish to show $f$ is surjective.
-Note that $\dim_\Bk \ker f = \dim_\Bk H^0((n - 2)L) = (n - 3)(g - 1+\frac{\delta}{2})$ using Riemann--Roch and the assumption $n \geq 4.$
-Additionally, $\dim_\Bk V \otimes H^0(nL) = 2 \cdot (n - 1)(g - 1+\frac{\delta}{2})$, again using Riemann--Roch.
-Therefore,
-\begin{align*}
-	\dim_\Bk \im f 	& = 2 \cdot (n - 1)(g - 1+ \frac{\delta}{2}) - (n - 3)(g - 1 + \frac{\delta}{2})\\
-				& = (n + 1)(g - 1 + \frac{\delta}{2}) = \dim_\Bk H^0((n + 2)L).
-\end{align*}
-Ergo, $f$ is surjective.
-\end{proof}
-
-The next step is to bound the degrees of the relations of $R_\halfcan$ when $\Delta > 0$. This is done in Proposition ~\ref{prop:relation-10}
-by using the basepoint-free pencil trick to show that if a relation lies in a sufficiently high degree, it lies in the ideal generated by the relations in lower degrees.
-In Definition ~\ref{defn:lower-ideal}, we fix notation for the ideal generated by lower degrees relations:
-
-\begin{defn}
-\label{defn:lower-ideal}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -; \delta
-)$ with $g \geq 2$ and $\Delta > 0.$ Choose generators $x_1, \ldots
-, x_n$ of $R_\halfcan$ so that we obtain a surjection $\phi: \Bk[x_1, \ldots
-, x_n] \twoheadrightarrow R_\halfcan$ with kernel $I_\halfcan$. Let $I_{\halfcan, k}$ be
-the $k^\text{th}$ graded piece of $I_\halfcan$ and define
-\[
-	J_{\halfcan,k} = \sum_{j = 1}^{k - 1}\Bk[x_1, \ldots, x_n]_j \cdot I_{\halfcan,k-j}.
-\]
-\end{defn}
-
-\begin{lem}
-\label{lem:reducing-degree}
-Let $(X, \Delta, \halfcan)$ be a log spin curve of genus $g \geq 2,$ so
-that $\Delta > 0.$ Choose generators $x_1, \ldots, x_n$ of $R_\halfcan$ so
-that we obtain a surjection $\phi: \Bk[x_1, \ldots, x_n]
-\twoheadrightarrow R_\halfcan$ with kernel $I_L$. Let $s_1, s_2 \in \Bk[x_1,
-\ldots, x_n]_2$ be two elements so that $\: \newspan(\phi(s_1), \phi(s_2))$
-$= V \subseteq H^0(X, 2\halfcan)$ is basepoint-free. For any $f \in
-\Bk[x_1, \ldots, x_n]$ such that $\deg f \geq 11,$ there exist $g, h \in
-\Bk[x_1, \ldots, x_n]_{k - 2}$ so that $s_1 g + s_2 h \equiv f \bmod J_{\halfcan, k}.$
-\end{lem}
-\begin{proof}
-By Lemma ~\ref{lem:generation-5}, $\deg x_i \leq 5$ for $1 \leq i \leq n$. Therefore, we may write $f = \sum_{i = 1}^{n}a_i x_i$ with $a_i \in \Bk[x_1, \ldots, x_n]_{k-\deg x_i}$.
-We next show that for all $1 \leq i \leq n$ there exist $g_i, h_i \in \Bk[x_1, \ldots, x_n]_{k - \deg x_i - 2}$ so that $a_i = s_1g_i + s_2h_i \bmod I_{\halfcan, \deg a_i}.$
-
-By Lemma ~\ref{lem:generation-5},
-\begin{align*}
-	V \otimes H^0((\deg f-\deg x_i -2)\halfcan) \rightarrow H^0((\deg f-\deg x_i)\halfcan)
-\end{align*}
-is surjective because $\deg f \geq 11$ implies that
-$$\deg a_i =\deg f - \deg x_i -2 \geq 4.$$
-In particular, there exist $\alpha, \beta \in R_\halfcan$ so that
-$$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
-Choosing $g_i,h_i\in \Bk[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
-$$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan, \deg a_i},$$ as claimed.
-
-Finally, we may then take $g = \sum_{i}^{}g_i x_i, \: h = \sum_{i}^{}h_i x_i,$ so that 
-\begin{align*}
-	f &\equiv \sum_{i}^{}a_i x_i \equiv \sum_{i}^{}(s_1g_i + s_2h_i)x_i \equiv s_1 \left( \sum_{i}^{}g_i x_i \right) + s_2 \left( \sum_{i}^{}h_i x_i \right) \\
-	&\equiv s_1 g + s_2 h \bmod J_{L,k}.
-\end{align*}
-\end{proof}
-
-\begin{prop}
-\label{prop:relation-10}
-Let $(X, \Delta, \halfcan)$ be a log spin curve of signature $(g; -; \delta)$
- with $g \geq 2$ and $\Delta > 0.$ Then $I_\halfcan$ is generated in
-degree at most degree at most $10$.
-\end{prop}
-\begin{proof}
-Suppose $f \in I_\halfcan$ with $\deg f \geq 11$. To complete the proof,
-it suffices to show $f \in I_{\halfcan,k}'$. By Lemma
-~\ref{lem:reducing-degree}, this is the same as checking $s_1 g + s_2 h \in
-I_{\halfcan, k}'$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
-so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is
-basepoint-free. Consider the map
-
-$$\begin{tikzcd}
-V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
-\end{tikzcd}$$
-
-\noindent
-we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0$.
-So by the explicit isomorphism given in the proof of the
-basepoint-free pencil trick, as shown in the proof of \cite[Lemma 2.6]
-{saint-donat:proj}, there exists some $\rho \in \Bk[x_1, \ldots, x_n]$
-so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) =
-\phi(s_2) \phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho)$. 
-Therefore,
-$g \equiv s_2 \rho \bmod I_{\halfcan, k-2}$ and $h \equiv - s_1 \rho \bmod
-I_{\halfcan, k - 2}$. Hence,
-\begin{align*}
-	s_1g + s_2h \equiv s_1(s_2\rho) + s_2(-s_1 \rho) \equiv 0 \bmod J_
-{L,k}.
-\end{align*}
-\end{proof}
-
-We now summarize what we have shown.
-
-\begin{cor}
-\label{cor:g-2-presentation-bound}
-Let $(X, \Delta, L)$ be a log spin curve of signature $(g; -;\delta)$
-with $g \geq 2$. Then $X$ has minimal generators in degree at most
-$5$ and minimal relations in degree at most $10$.
-\end{cor}
-
-\begin{proof}
-If $\delta = 0$, the result is immediate from Reid \cite[Theorem 3.4]
-{reid:infinitesimal}. Otherwise, if $\delta > 0$, the bound on the
-degrees of minimal generators follows from Lemma
-~\ref{lem:generation-5}, while the bound on the degrees of minimal
-relations follows from Proposition ~\ref{prop:relation-10}.
-\end{proof}
-
-\ssec{Main Theorem for Genus At Least Two}
-\label{ssec:g-high-main}
-
-We are ready to prove our main theorem, Theorem ~\ref{thm:main} in the case
-$g \geq 2$. The idea of the proof is to use Corollary \ref{cor:g-2-presentation-bound} to 
-complete the base case when $L = \halfcan_X$ and then apply Lemma
-~\ref{lem:sat-1}, Lemma ~\ref{lem:sat-2}, and Lemma
-~\ref{lem:raise-stacky-order} to complete the induction step.
-
-\begin{thm}
-\label{thm:g-high-main}
-Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ be a log spin curve
-with signature $(g; e_1, \ldots, e_r; \delta)$. Then the
-log spin canonical ring $R(\sx, \Delta, \halfcan)$
-is generated as a $\Bk$-algebra by elements in degree at most $e =
-\max(5, e_1, \ldots, e_r)$ with minimal relations in degree at most $2e$.
-\end{thm}
-
-\begin{proof}
-As the base case, let $\halfcan = \halfcan_X \in \di X$ satisfy $2 \halfcan \sim 2 K_X + \Delta$.
-By Corollary ~\ref{cor:g-2-presentation-bound}, the theorem holds for $(\sx, \Delta,
-\halfcan_X)$.
-
-Next, suppose the theorem holds for $\halfcan' = \halfcan_X + \sum_{i=1}^{r-1} \frac{1}{3}P_i$.
-Let $\halfcan$ be a log spin canonical divisor of the form $\halfcan = \halfcan_X + \sum_{i = 1}^r \frac{1}{3} P_i$, which means that $\halfcan = \halfcan' + \frac{1}{3} P_r$.
-If $P_r$ is a basepoint of $\halfcan'$, then the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-2}.
-Otherwise, $P_r$ is not a basepoint of $\halfcan'$, meaning that in particular $R_{\halfcan'}$ is saturated in 1.
-Therefore, since $P_r$ is a not basepoint of $\halfcan'$, Equation
-~\ref{eqn:deg1-sat-ind} holds by Riemann--Roch.
-In this case, the theorem holds for $\halfcan$ by Lemma ~\ref{lem:sat-1}.
-
-We have thus shown the theorem for all $(\sx, \Delta, \halfcan)$ with $g \ge 2$ and signature $(g; 3, \ldots, 3; \delta)$. Therefore, by Corollary 
-~\ref{cor:raise-stacky-order}, this theorem 
-holds for all log spin curves $(\sx, \Delta, \halfcan)$. 
-\end{proof}
-
-\begin{rem}
-\label{rem:genus-2-explicit-bound}
-For this remark, we retain the terminology from the proof of Theorem ~\ref{thm:g-high-main}.
-Suppose $e :=  \max(e_1,\ldots, e_r).$ Then, $R_\halfcan$ has a generator in degree $e$ when $e \geq 5$ and a relation in degree at least $2e-4$ when $e \geq 7$.
-Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively
-applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, we obtain that $R_\halfcan$ is minimally generated over $R_{L'}$ by an element in degree $e,$ assuming $e \geq 5$.
-Furthermore, if $e \geq 7$ and $e_i = e,$
-then there must be a relation with leading term $y_{i,e_i} \cdot y_{i,e_i-4}.$ Hence, there is a relation in degree at least $2e - 4$. 
-Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there are $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, there is necessarily a relation with leading term $y_{i, e_i} \cdot y_{j, e_j}$ in degree $2e$.
-This analysis also applies to the cases that $g = 0$ and $g = 1$.
-\end{rem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus one %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Genus One}
-\label{sec:g-1}
-In this section, we prove Theorem ~\ref{thm:main} in the case that $g = 1$.
-We follow a similar inductive strategy as in the genus $g\geq 2$ case, except unlike in the $g \geq 2$ case we obtain explicit generators and relations here.
-
-In the case of a genus 1 curve, $X$ with no stacky points, we know $K_X \sim 0$, and therefore the only possibilities for log spin canonical divisors are $\halfcan' \sim 0$ or $\halfcan' \sim P - Q$ where $P, Q$ are distinct points, fixed  under the hyperelliptic involution.
-We inductively construct presentations by adding points through Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2} and incrementing the values of the $e_i$'s using Lemma ~\ref{lem:raise-stacky-order}.
-
-\ssec{Genus One Base Cases}
-\label{ssec:g-1_base}
-In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.
+{\bf Proof idea:} First, check this holds when $\Delta \in \di X$,
+either by hand in $g = 0, 1$ or by 
+\cite[$\mathsection$ 6]{milnor:fractional-weight} when $g \geq 2$.
+Then, inductively add in fractional points, showing that if
+it holds for a given divisor $\Delta$ it holds for
+$\Delta + \frac{e-1}{2e}P$.
 
 \begin{table}
-\begin{tabular}
-{| c || c | c | c |}	
-	\hline
-	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
-	\hline
-	\hline
-	$0$ & $\{1\}$ & $\emptyset$ & $1$ \\	\hline
-
-	$\frac{3}{7} P_1$ & $\{1,5,7\}$ & $\{15\}$ & $7$ \\	\hline
-
-	$\frac{1}{3} P_1 + \frac{1}{3} P_2$ & $\{1, 3, 3\}$ & $\{6\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{1}{3} P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ & $5$ \\	\hline
-\end{tabular}
-
-\caption{Genus 1 Base Cases}
-\label{table:g-1-base}
-\end{table}
-
-Generators and relations for $R_{L'}$ with $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.
-Note that admissibility for $(\sx',0,P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2)$ is verified in Example ~\ref{eg:base-1-33-adm}.
-The verification of admissibility for the other cases is similar.
-
-The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed.
-Although $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ are used as base cases for the induction, they are also exceptional cases; see Table ~\ref{table:g-1-exceptional}.
-
-\ssec{Genus One Exceptional Cases}
-\label{ssec:g-1-exceptional}
-Let $\sx$ be a stacky curve, with $P, Q$ distinct hyperelliptic
-fixed points on $X$. The following table provides a list of all
-cases which are not generated in degrees $e := \max(5, e_1, \ldots,
-e_r)$ with relations in degrees $2e$, as described in Theorem
-~\ref{thm:g-1-main}.
-
-\begin{table}	
-\begin{tabular}
-{| c || c | c | c |}
-	\hline
-	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
-	\hline
-	\hline
-	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline
-
-	$P - Q + \frac{1}{3} P_1$ & $\{2, 3, 7\}$ & $\{14\}$ & $5$ \\	\hline
-
-	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$\\	\hline
-
-	$\frac{1}{3} P_1$ & $\{1, 6, 9\}$ & $\{18\}$ & $5$ \\	\hline
-
-	$\frac{2}{5} P_1$ & $\{1, 5, 8\}$ & $\{16\}$ & $5$ \\	\hline
-
-	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline
-\end{tabular}
-
-\caption{Genus 1 Exceptional Cases}
-\label{table:g-1-exceptional}
-\end{table}
-
-We have already checked the case of 
-$L' = P - Q + \frac{1}{5}P_1$ above in Example ~\ref{eg:exception-1-5}. The other cases are similar.
-
-\ssec{Main Theorem for Genus One}
-\label{ssec:main_g_1}
-
-We now have all the tools necessary to prove our main theorem, ~\ref{thm:main} in the case $g = 1$.
-
-\begin{thm}
-\label{thm:g-1-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve with
-signature $\sigma := (1; e_1, \ldots, e_r; \delta)$.
-If $g = 1$, then the log spin canonical ring $R(\sx, \Delta, \halfcan)$
-is generated as a $\Bk$-algebra by elements of degree at most $\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e,$ so long as $\sigma$ does not lie in a
-finite list of exceptional cases, as listed in Table
-~\ref{table:g-1-exceptional}.
-\end{thm}
-
-\sssec*{Idea of Proof:}
-We check the theorem in two cases, depending on if $\delta > 0$.
-If $\delta > 0$, we first check that the theorem holds for
-$\halfcan_X$ by inductively adding in log points to the base case of $
-\halfcan_X' = 0$. Then we check that the theorem holds for $\halfcan$
-by adding stacky points and then inductively raising the 
-stabilizer orders of stacky points in the following sequence of 
-steps. When raising the stacky orders, it is important that we 
-increment the stabilizer orders of as many stacky points as 
-possible to maintain admissibility for the maximal possible sets of 
-stacky points. Then, we may also use the fact that raising the 
-stabilizer orders of any subset of these maximal sets of stacky 
-points will still preserve admissibility.
-
-The check for $\delta = 0$ is similar, although in this case we do
-not need to add in log points, only stacky points, and we will need
-to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.
-
-\begin{proof}
-
-\vskip.1in
-\noindent
-{\sf Case 1: $\delta > 0$}
-
-If $\delta > 0$, we must have $\delta \geq 2$, by Remark ~\ref{rem:delta-not-1}.
-In this case, let $\halfcan_X \in \di X$ satisfy $2 \halfcan_X \sim K_X + \Delta$.
-We have $\deg \halfcan_X \geq 1$, so, by Riemann--Roch, $h^0(\sx, \halfcan) \geq 1.$ Therefore, $\halfcan$ is linearly equivalent to an effective divisor.
-Thus, without loss of generality, we may assume $\halfcan$ is an effective divisor.
-
-We first now show the theorem holds for $\halfcan_X$ by induction.
-Since $\halfcan_X$ is effective, we may induct on the degree of the log spin canonical divisor.
-The base case is easy: the theorem holds for $\halfcan_X' = 0$ by Example ~\ref{eg:base-1-0}.
-Assume it holds for $\halfcan_X' \in \di X$, with $\halfcan_X'$ effective.
-We will show it holds for $\halfcan_X' + P$, verifying the inductive step.
-There are two cases, depending on whether $P$ is a basepoint of $\halfcan_X'$.
-
-First, if $P$ is not a basepoint of $\halfcan',$ then the hypotheses of Lemma ~\ref{lem:sat-1} are satisfied.
-Therefore, by Lemma ~\ref{lem:sat-1}, the theorem holds for $\halfcan = \halfcan' + P$.
-
-Otherwise, $P$ is a basepoint of $\halfcan_X'$, so the hypotheses of Lemma ~\ref{lem:sat-2} are satisfied since $\deg 3(\halfcan_X') \geq 2$ as $\deg \halfcan_X' \geq 1.$ Therefore, by Lemma ~\ref{lem:sat-2}, the theorem holds for $\halfcan_X = \halfcan_X'+P$.
-By induction, the theorem holds for $\halfcan_X$.
-
-To complete the case that $\delta > 0$, we now need show the theorem holds for a \emph{stacky} log spin canonical divisor $\halfcan$.
-It suffices to show that if the theorem holds for a log spin canonical divisor $\halfcan'$ with $\deg \lfloor L' \rfloor > 0$, then it holds for $L' + \subhalf {e_i}P_i$ with $e_i$ odd.
-As above, if $P$ is not a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-1}.
-On the other hand, if $P$ is a basepoint of $\halfcan'$ then the theorem holds for $L' + \subhalf {e_i}P_i$ by Lemma ~\ref{lem:sat-2}.
-
-\vskip.1in
-\noindent
-{\sf Case 2: $\delta = 0$}
-
-Since $\delta = 0$, we may write $\halfcan = \halfcan_X + \sum_{i = 1}^{r}\subhalf{e_i}P_i.$ There are now two further subcases, depending on whether $\halfcan_X = 0$ or $\halfcan_X = P - Q$ for $P$ and $Q$ two distinct hyperelliptic fixed  points.
-
-\vskip.1in
-\noindent
-{\sf Case 2a: $\halfcan_X = P - Q, P \neq Q$}
-
-Note that we are assuming $\halfcan$ is not one of the exceptional cases listed in Table ~\ref{table:g-1-exceptional}, so we may either assume $\sx$ has 1 stacky point with $e_1 > 5$ or at least 2 stacky points.
-
-First, we deal with the case $\sx$ has at least 1 stacky point.
-By Example ~\ref{eg:exception-1-5}, if $L' = P - Q + \frac{2}{5}P_1,$ then $R_{\halfcan'}$ is generated in degrees $2,3,$ and $5$ with a single relation in degree 12.
-Furthermore, $(\sx, \halfcan', \{1\})$ is admissible, and satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Observe that $\halfcan'$ itself is an exceptional case, as it has a generator in degree $12 > 2 \cdot 5$.
-However, after applying Lemma ~\ref{lem:raise-stacky-order}, we see that $P - Q + \frac{3}{7}P_2$ does satisfy the constraints of this theorem, because only relations in degree $\leq 14 = 2 \cdot 7$ are added, and the relation in degree $12$ coming from $R_{\halfcan'}$, lies in a degree less than $2 \cdot 7 = 14$.
-Therefore, the Theorem holds for $L' = P - Q + \frac{3}{7}P_2$.
-Then, applying Lemma ~\ref{lem:raise-stacky-order} $\frac{e-7}{2}$ times shows that the Theorem holds for $L = P - Q + \frac{e- 1}{2e}P_1$.
-
-Second, we deal with the case that $\sx$ has at least two stacky points. 
-If $(\sx', \Delta, \halfcan')$ is a spin canonical curve so that $L' = P - Q + \frac{1}{3}P_1+ \frac{1}{3}P_2$, then as found in 
-Example ~\ref{eg:base-1-33}, the triple $(\sx', 0, P-Q + \frac{1}{3}P_1+\frac{1}{3}P_2)$
-satisfies the hypotheses of Lemma ~\ref{lem:raise-stacky-order}.
-Therefore, applying Lemma ~\ref{lem:sat-2} $r-2$ times, we see that the theorem holds for $(\sx', \Delta', \halfcan')$ with $L' = P - Q + \sum_{i = 1}^{r}\frac{1}{3}P_i.$ 
-Finally, by Corollary ~\ref{cor:raise-stacky-order}, this theorem holds 
-for $L' = P - Q + \sum_{i = 1}^{r}\subhalf {e_i}P_i$, as desired.
-
-\vskip.1in
-\noindent
-{\sf Case 2b: $\halfcan_X = 0$}
-
-This case is analogous to 2a: If there is only one stacky point, we start at $L = \frac{3}{7}P_1,$ and inductively increment the stabilizer order.
-Note that by Table ~\ref{table:g-1-base}, $L = \frac{3}{7}P_1,$ will have a relation in degree $15.$ However, once $e_1 \geq 9$, we have $2 \cdot e_1 > 15$, so the theorem holds for such stacky curves.
-Once the log spin canonical divisor has at least two stacky points, the argument proceeds as in Case 2a.
-\end{proof}
-
-\begin{rem}
-\label{rem:genus-1-explicit-bound}
-In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, the proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations.
-One can start with the generators and relations found in the base cases and inductively add generators and relations as one adds stacky points and increments stabilizer orders.
-As described in Remark ~\ref{rem:genus-2-explicit-bound}, when $e := \max(e_1,\ldots, e_r) \geq 7$, there is necessarily a generator in degree $e$ and a relation in degree $2e$.
-\end{rem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus zero %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Genus Zero}
-\label{sec:g-0}
-We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
-curve and $\sx$ has signature $\sigma := (0; e_1, \ldots, e_r;
-\delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
-$e := \max(5, e_1, \ldots, e_r)$ with relations generated in degree
-at most $2e$, so long as $\sigma$ does not lie in the finite list
-given in Table ~\ref{table:g-0-exceptional}.
-
-As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even. Thus,
-we can reduce the problem into two cases: $\delta \geq 2$ and
-$\delta = 0$. In the former case, $\halfcan$ is linearly equivalent
-to an effective divisor, so the result of Theorem \ref{thm:main}
-follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1}
-to add the necessary stacky points. On the other hand, the proof
-when $\delta = 0$ is more involved. We dedicate the remainder of
-this section to that case in the following steps: characterizing
-saturations (Subsection ~\ref{ssec:g-0-saturation}),
-describing base cases (Subsection ~\ref{ssec:g-0-base}), and
-presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional})
-\footnote{Several computations used to generate the tables in
-Subsection ~\ref{ssec:g-0-base} and Subsection
-~\ref{ssec:g-0-exceptional} were done using a modified version of
-the MAGMA code given in the work of O'Dorney \cite{dorney:canonical}.}
-Finally, we apply inductive processes using Lemma ~\ref{lem:sat-3}
-and Lemma ~\ref{lem:raise-stacky-order} to prove the main theorem
-in the full genus zero case (Subsection ~\ref{ssec:g-0-main}).
-
-\begin{rem}
-Since all points are linearly equivalent on $\BP^1_\Bk$, 
-$\halfcan_X \sim n \infty$ for some $n \in \BN$ and
-$K_X \sim -2 \infty$. We will use this convention
-throughout this section.
-\end{rem}
-
-\ssec{Saturation}
-\label{ssec:g-0-saturation}
-\begin{table}
-\begin{tabular}
-	{| c | c || c |}
-	\hline
-	Signature $\sigma$ & Condition & Saturation \\
-	\hline
-	\hline
-
-	$(0; 3, 3, 3; 0)$ & & $\infty$ \\	\hline
-
-	$(0; 3, 3, 5; 0)$ & & $18$ \\	\hline
-
-	$(0; 3, 3, 7; 0)$ & & $12$ \\	\hline
-
-	$(0; 3, 3, 9; 0)$ & & $12$ \\	\hline
-
-	$(0; 3, 5, 5; 0)$ & & $8$ \\	\hline
-
-	$(0; 5, 5, 5; 0)$ & & $8$ \\	\hline
-
-	$(0; 3, 3, 3, 3; 0)$ & & $6$ \\	\hline
-
-	\hline
-	\hline
-
-	$(0; 3, 3, \ell; 0)$ & $\ell > 9$ & $9$ \\	\hline
-
-	$(0; a, b, c; 0)$ & not listed above & $5$ \\	\hline
-
-	$(0; e_1, \ldots, e_r; 0)$ & not listed above & $3$ \\	\hline
-\end{tabular}
-
-\caption{Genus 0 Saturation}
-\label{table:g-0-sat}
-\end{table}
-
-First, we present the saturations of the log spin canonical divisor
-(recall Definition ~\ref{defn:sat}) for all cases where $g = 0$ and
-$\delta = 0$ in Table ~\ref{table:g-0-sat}. The saturations can
-be computed using Riemann--Roch. By classifying the saturations of
-all signatures, we can determine the base cases on which we can
-apply inductive lemmas from Section ~\ref{sec:induction}. Note that
-the saturations of log spin canonical divisors only depend on the
-signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
-are listed first and generic cases follow.
-
-\ssec{Base Cases}
-\label{ssec:g-0-base}
-In order to apply Lemma ~\ref{lem:sat-3} and Lemma
-~\ref{lem:raise-stacky-order} when $\delta = 0$,
-we need to determine appropriate base cases that will
-cover all but finitely many signatures by induction.
-Here we provide such base cases and demonstrate that
-they satisfy all of the necessary conditions of
-Lemma ~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}
-(e.g. admissibility as defined in Definition \ref{defn:admissible}).
-We also show that that the associated log spin
-canonical rings are generated in degree at most $e := \max(5, e_1,
-\ldots, e_r)$ with relations generated in degree at most $2e$.
-
-\begin{lem}
-\label{lem:g-0-admissible-cases}
-Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
-$\sigma := (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
-generated by elements of degree at most $e = \max(5 , e_1, \ldots,
-e_r)$ with relations in degree at most $2e$. Furthermore, each of
-the cases in Table ~\ref{table:g-0-base-cases} satisfy the
-conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e.~ either $(\sx',
-\halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}
-P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
-Case ~\ref{custom:three-cases-1} of Remark ~\ref{rem:three-cases}):
-
-\rm{
-\begin{table}
-\begin{tabular}
-	{| c || c | c | c |}
-	\hline
-	Case & Signature $\sigma$ & $J$ & $e$\\
-	\hline
-	\hline
-
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $11$ \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$	& $9$ \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$	& $7$ \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$	& $7$ \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $5$ \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $5$ \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $5$ \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ \\ \hline
-
-	(k) &	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ \\ \hline
-\end{tabular}
-
-\caption{Genus 0 Base Cases}
-\label{table:g-0-base-cases}
-\end{table}
-}
-
-\end{lem}
-
-\begin{proof}
-Recall that the generator and relation degree bounds for case (b)
-are proven in Example ~\ref{eg:base-0-377} and the admissibility
-condition is checked in Example ~\ref{eg:base-0-377-adm}. For
-the remaining cases, we follow a similar method to find a
-presentation satisfying the desired conditions. The log spin
-canonical ring $R(\sx', 0, L')$ is generated as a $\Bk$-algebra by
-elements of degree at most $e$ with relations in degree at most $2e$
-for each case as described in the Table
-~\ref{table:g-0-base-cases-degrees}.
-\begin{table}
-\begin{tabular}
-	{| c || c | c | c |}
-	\hline
-	Case & Generator Degrees & Degrees of Relations & $e$\\
-	\hline
-	\hline
-
-	(a) & $\{3, 7, 9, 11\}$ & $\{14, 18\}$ & $11$ \\	\hline
-
-	(b) & $\{3, 5, 7, 9\}$ & $\{12, 14\}$ & $9$ \\ \hline
-
-	(c) & $\{3, 5, 7, 7\}$ & $\{10, 14\}$ & $7$ \\ \hline
-
-	(d) & $\{3, 5, 5, 7\}$ & $\{10, 12\}$	& $7$ \\ \hline
-
-	(e) & $\{3, 5, 5, 7, 7\}$ & $\{10, 10, 12, 12, 14\}$	& $7$ \\ \hline
-
-	(f) & $\{3, 5, 5, 7, 7, 7\}$ & $\{10, 10, 10, 12, 12, 12, 14, 14, 14\}$	& $7$ \\ \hline
-
-	(g) & $\{3, 3, 4, 5\}$ & $\{8, 9\}$ & $5$ \\ \hline
-
-	(h) & $\{3, 3, 4, 5, 5\}$ & $\{8, 8, 9, 9, 10\}$ & $5$ \\ \hline
-
-	(i) & $\{3, 3, 4, 5, 5, 5\}$ &
-	$\{8, 8, 8, 9, 9, 9, 10, 10, 10\}$ & $5$ \\ \hline
-
-	(j) & $\{3, 3, 4, 5, 5, 5, 5\}$ &
-	$\{8, 8, 8, 8, 9, 9, 9, 9, 10, 10, 10, 10, 10, 10\}$ & $5$ \\ \hline
-
-	(k) &	$\{3, 3, 3, 4, 4, 5\}$ & $\{6, 7, 7, 8, 8, 8, 9, 9, 10\}$ & $5$ \\ \hline
-\end{tabular}
-
-\caption{Generators and Relations for Genus 0 Base Cases}
-\label{table:g-0-base-cases-degrees}
-\end{table}
-
-We can also always find a presentation for these cases such that
-they satisfy \ref{custom:Ad-i} and \ref{custom:Ad-ii} and that $\initial(I')$ is
-generated by products of two monomials. Again, the procedure to
-verify these is similar to that in Example
-~\ref{eg:base-0-377} and Example ~\ref{eg:base-0-377-adm}.
-
-Furthermore, each case always satisfies \ref{custom:Ad-iii} as demonstrated in table ~\ref{table:g-0-base-cases-admissibility}.
-Notice that the $e_i$ and $\{e_j' : j \neq i\}$ are equivalent
-for any choice of $i \in J$ for these cases, so $\deg \lfloor e_i \halfcan
-\rfloor$ and $\max_{k \geq 0} \#S_{(\sigma, J)}(i)$ are
-independent of the choice of $i$.
-
-\begin{table}
-\begin{tabular}
-	{| c | c | c || c | c |}
-	\hline
-	Case & Signature $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
-	$\max_{k \geq 0} \#S_{(\sigma, J)}(i)$ \\
-	\hline
-	\hline
-
-	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $1$ & $0$ \\	\hline
-
-	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
-
-	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
-
-	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$ & $1$ & $0$ \\ \hline
-
-	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $2$ & $0$ \\ \hline
-
-	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$ & $3$ & $0$ \\ \hline
-
-	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $2$ & $0$ \\ \hline
-
-	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $3$ & $0$ \\ \hline
-
-	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $4$ & $0$ \\ \hline
-
-	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ & $0$ \\ \hline
-
-	(k) & $(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ & $0$ \\ \hline
-\end{tabular}
-
-\caption{Checking \ref{custom:Ad-iii} for Genus 0 Base Cases}
-\label{table:g-0-base-cases-admissibility}
-\end{table}
-
-Thus, all of the cases are admissible and satisfy the additional
-desired conditions.
-\end{proof}
-
-\ssec{Exceptional Cases}
-\label{ssec:g-0-exceptional}
-In this subsection, we describe the cases that are not covered by induction, which are also the only exceptions to Theorem ~\ref{thm:main} in the case $g = 0$.
-In table ~\ref{table:g-0-exceptional} We present the explicit generators and relations for the remaining
-cases given by signatures in the finite set
-
-\begin{align*}
-	S &:= \{(0; 3, 3, \ell; 0) : 3 \leq \ell \leq 9 \text{ odd}\} \\
-		&\cup \{(0; 3, 5, 5; 0) ,(0; 3, 5, 7; 0), (0; 5, 5, 5; 0), (0; 3, 3, 3, 3; 0)\}
-\end{align*}
-
-\begin{table}
+\captionsetup{type=figure}
+\begin{center}
 \begin{tabular}
@@
 \end{tabular}
-
+\end{center}
 \caption{Genus 0 Exceptional Cases}
@@
 
-\begin{rem}
-These cases give all of the exceptions to the $e$ and $2e$ bounds
-on the generator and relation degree. Notice that each of these
-exceptional cases, apart from $(0; 3, 5, 7; 0)$, also has
-exceptional saturation as seen in Table ~\ref{table:g-0-sat}.
-Intuitively, these exceptional saturations can be viewed as
-``forcing'' generators and relations in higher degrees than expected.
-\end{rem}
+\begin{table}	
+\captionsetup{type=figure}
+\begin{center}
+\begin{tabular}
+{| c || c | c | c |}
+	\hline
+	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	\hline
+	\hline
+	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline
 
-\ssec{Main Theorem for Genus Zero}
-\label{ssec:g-0-main}
-Now we can combine the base cases from Subsection \ref{ssec:g-0-base} with the inductive lemmas of Section \ref{sec:induction}.
+	$P - Q + \frac{1}{3} P_1$ & $\{2, 3, 7\}$ & $\{14\}$ & $5$ \\	\hline
 
-\begin{thm}
-\label{thm:g-0-main}
-Let $(\sx, \Delta, \halfcan)$ log spin curve with signature
-$\sigma := (0; e_1, \ldots, e_r; \delta)$.
-Then, the log spin canonical ring $R(\sx, \Delta, \halfcan)$
-is generated as a $\Bk$-algebra by elements of degree at most $e =
-\max(5, e_1, \ldots, e_r)$ and has relations in degree at most $2e$,
-so long as $\sigma$ does not lie in the finite list of exceptional
-cases in Table ~\ref{table:g-0-exceptional}.
-\end{thm}
+	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$\\	\hline
 
-\sssec*{Idea of Proof:}
-The method of this proof is almost identical to that of Theorem
-~\ref{thm:g-1-main}. When $\delta > 0$, we first add in log points,
-and then increment the stabilizer orders of stacky points, checking
-that the theorem holds at each step. The more technical case occurs
-when $\delta = 0$. In this case, we increment the stabilizer
-orders of stacky points starting from one of the base cases, and
-check that every stacky curve can be reached by a sequence of
-admissible incrementations from a base case.
+	$\frac{1}{3} P_1$ & $\{1, 6, 9\}$ & $\{18\}$ & $5$ \\	\hline
 
-\begin{proof}
-If $\sx$ has no stacky points, then we can assume that $\halfcan \sim
-n \cdot \infty$ with $n \in \BZ_{\geq -1}$. This is a classical
-case done by Voight and Zureick-Brown \cite[Section 4.2]
-{vzb:stacky}. When $n = -1$, then $R_\halfcan = \Bk$.  When $n = 0$,
-then $R_\halfcan = \Bk[x]$.  When $n > 0$, inductively applying Lemma
-\ref{lem:sat-1} tells us that $R_\halfcan$ is generated in degree 1
-with relations generated in degree 2.
+	$\frac{2}{5} P_1$ & $\{1, 5, 8\}$ & $\{16\}$ & $5$ \\	\hline
 
-First, let us consider the case when $\delta \geq 2$. In any such
-case, $\lfloor \halfcan \rfloor$ is an effective divisor and the
-conditions of Lemma ~\ref{lem:sat-1} are satisfied. Thus, we can
-apply the Lemma ~\ref{lem:sat-1} inductively from the classical
-case with no stacky points to get that $R(\sx, \Delta, \halfcan)$
-is generated up to degree $e$.
+	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline
+\end{tabular}
 
-By Remark ~\ref{rem:delta-not-1}, it only remains to deal with the
-case $\delta = 0$, so $\halfcan$ is not necessarily effective. Let
-the signature $\sigma$ be such that it is not one of the
-exceptional cases contained in Table ~\ref{table:g-0-exceptional}. 
-We get the following three cases, depending on the value of $r$:
+\end{center}
+\caption{Genus 1 Exceptional Cases}
+\label{table:g-1-exceptional}
+\end{table}
 
-\vskip.1in
-\noindent
-{\sf Case 1: $r < 3$}
+\section*{Applications to Modular Forms}
 
-If $r < 3$, then $\deg 
-\lfloor k \halfcan \rfloor < 0$ for all $k \geq 0$ so we have the
-trivial case where $R(\sx, \Delta, \halfcan) = \Bk$.
+\begin{cor}
+\label{cor:main-mod-forms}
+Let $\Gamma$ be a Fuchsian, i.e., $\Gamma \backslash \BH$ has finite area, group and $\sx$ the stacky curve
+associated to $\Gamma \backslash \BH$ with signature $\sigma
+= (g; e_1, \ldots, e_r; \delta)$.
 
-\vskip.1in
-\noindent
-{\sf Case 2: $3 \le r \le 5$}
+Except in an explicit finite list of cases, the
+ring of modular forms $M(\Gamma)$ is generated as a $k$-algebra
+by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
+relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
+e_r)$.
+\end{cor}
 
-If $3 \le r \leq 5$ and $\sigma$ is not one of the exceptional cases,
-then we may apply Lemma ~\ref{lem:g-0-admissible-cases} and
-Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
-from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
-\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
-\ldots, e_r)$ with relations generated up to degree $2e$.
+\begin{example}
+\label{eg:congruence-bounds}
+Suppose $\Gamma \subset SL_2(\BZ)$ is any congruence subgroup.
+Then $\Gamma$ is generated in weight at most $6$ with relations in weight at most $12$. Further, if  $\Gamma$ has some nonzero odd weight modular form, $M(\Gamma)$ is 
+generated in degree at most $5$ with relations in degree at most $10$. 
+If additionally, the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, then $M(\Gamma)$ is generated in weight at most $4$ with
+relations in weight at most $8$.\end{example}
 
-\vskip.1in
-\noindent
-{\sf Case 3: $r > 5$}
-
-If $r > 5$, then we can use Lemma
-~\ref{lem:sat-3} to add stacky points with
-stabilizer order $3$ to case (k) of Table
-~\ref{table:g-0-base-cases}, which corresponds to $(\sigma
-= (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\})$. This case
-satisfies the conditions of Lemma
-~\ref{lem:sat-3} (recall from Table ~\ref
-{table:g-0-sat} that $\sat(\Eff(\sigma)) = 3$), and the
-immediate consequence of parts (a) and (c) of Lemma
-~\ref{lem:sat-3} is that any $R(\sx', \Delta,
-\halfcan')$ corresponding to signatures $\sigma'$ with ramification
-orders all equal to $3$ for any $r > 5$ is generated up to
-degree $e' := \max(5, e_1', \ldots, e_r')$ with relations generated
-up to degree $2e'$. Furthermore, these cases satisfy all of the
-conditions of Lemma ~\ref{lem:raise-stacky-order}. Now we can
-apply Corollary ~\ref{cor:raise-stacky-order} to deduce that
-$R(\sx, \delta, \halfcan)$ is generated up to degree $e :=
-\max(5, e_1, \ldots, e_r)$ with relations generated up to degree
-$2e$.
-\end{proof}
-
-\begin{rem}
-\label{rem:genus-0-explicit-bound}
-The proof of Theorem ~\ref{thm:g-0-main} in genus zero gives an
-explicit construction of the generators and relations for the log
-spin canonical ring $R_\halfcan$. This is similar to the case of genus 1
-in Remark ~\ref{rem:genus-1-explicit-bound}. Furthermore, there is
-a generator in degree $e$ and a relation in degree at least $2e-4$
-when $e := \max(e_1, \ldots, e_r)$ is at least $7$ (see Remark ~\ref
-{rem:genus-2-explicit-bound}). This can be seen from the inductive
-application of Lemmas ~\ref{lem:sat-1}, \ref{lem:sat-2}, and \ref
-{lem:sat-3}.
-\end{rem}
-
-\begin{rem}
-\label{rem:cusp-generation-4}
-Here, we describe how to obtain a slightly better bound for our
-application to modular forms from Example ~\ref{eg:congruence-bounds} in the cases $g=0$ and $g=1$.
-When $g=0$, a careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that,
-if $\Delta > 0$ and $\sx$ has signature $(0; 3, \ldots, 3; \delta)$,
-then $R_\halfcan$ is generated in weight at most 4. Since $\delta > 0$,
-$\halfcan_X$ is effective. Additionally, $R_{\halfcan_X}$ is generated in weight 1,
-and inductive applications of Lemma ~\ref{lem:sat-1} only add
-generators in weights 3 and 4 and relations in weight at most 8.
-Therefore, $R_\halfcan$ is generated in weight at most 4 with relations in
-weight at most 8. Note that a similar analysis of the proof of
-Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence
-subgroups are generated in weight at most 4 with relations in
-weight at most 8.
-\end{rem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%% Further Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Further Research}
-\label{sec:further-questions}
-In this section, we present several directions for further research.
-\begin{enumerate}
-	\item As noted in Remark ~\ref{rem:explicit-generators}, the 
-		proof of Theorem ~\ref{thm:main} 
-		gives an 
-		explicit procedure for computing the generators and relations of $R_
-		\halfcan$ when the genus of $\sx$ is $0$ or $1$.
-When $\sx$ has genus at least 2, Lemmas ~\ref{lem:sat-1} and $\ref{lem:sat-2}$ allow us to explicitly construct a presentation of $R_\halfcan$ from a presentation of $R_{\halfcan_X}$ where $X$ is the coarse space $X$.
-However, obtaining a presentation for $X$ requires nontrivial computation.
-This suggests the following Petri-like question:
-		\begin{question}
-		\label{ques:spin-canonical-petri}
-			Is there a general structure theorem describing a set of minimal 
-			generators and relations of $R_{\halfcan}$ where $(X, \Delta, L)$ is a log spin curve with no stacky points?
-		\end{question}
-
-\item One direction for further research is to extend the results
-	of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx$, 
-	where $nD \sim K$ for some integer $n$ greater than $2$. The
-	canonical rings	of such divisors often arise as rings of
-	fractional weight $\frac{2}{n}$ modular forms.
-	For more details on fractional weight modular forms, see Adler and
-	Ramanan \cite[p. 96]{adler:moduli} and Milnor
-	\cite[$\mathsection$ 6]{milnor:fractional-weight}.
-
-\begin{question}
-		\label{ques:fractional-weight}
-			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
-			where $K$ is the canonical divisor of $\sx$, can one bound the 
-			degrees of generators and relations of $R_D$?
-		\end{question}
-		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
-		gives an affirmative answer to this question: If $\sx$ has signature 
-		$(g; e_1, \ldots, e_r; \delta)$ then $R_D$ is generated in degree at 
-		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
-		$2e$. 
-		It may be possible to modify the proof of Lemma
-		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
-		weight modular forms. 
-		Suitable generalizations of the 
-		lemmas of Section ~\ref{sec:induction} might allow one to 
-		follow similar questions to this paper and provide a general 
-		answer to Question ~\ref{ques:fractional-weight}.
-		\\
-
-	\item The generic initial ideal
-		encapsulates the idea of whether the relations for $R_\halfcan$ are 
-		generically chosen. See Voight and Zureick-Brown \cite[Definition 2.2.7]{vzb:stacky} for a precise definition of the generic initial ideal.
-		The proof of Theorem
-		~\ref{thm:main} is decidedly non-generic. 
-		In particular, Lemma ~\ref{lem:raise-stacky-order} 
-		constructs generators with non-maximal pole orders at certain 
-		points, making the relations non-generic. 
-		\begin{question}
-		\label{ques:generic-initial}
-			If $(\sx, \Delta, \halfcan)$ is a log spin curve, can one write down the
-			generic initial ideal explicitly?
-		\end{question}
-
-	\item In Subsection \ref{ssec:bounds-high-genus}, we reference 
-		the work of Reid \cite[Theorem 3.4]{reid:infinitesimal}. We use his 
-		proof that the 
-		spin canonical ring is generated in degree at most 5 with
-		relations in degree at most 10 in the 			
-		non-log, non-stacky case when genus is at least 2. We extend this 
-		bound of 5 and 10 to the log case, and then apply our inductive 
-		lemmas to add stacky points and obtain bounds of $e = \max(5,e_1, \ldots, e_r)$ and $2e$.  However, Reid in fact proves something slightly stronger \cite[Theorem 3.4]{reid:infinitesimal}: that in 
-		most cases his bound is actually 3 and 6 with well-characterized 
-		exceptions.
-		Generalizing this slightly stronger bound to the (non-stacky) log case case would allow us to inductively apply the lemmas from Section ~\ref{sec:induction} and improve Theorem ~\ref{thm:main} as follows:
-		\begin{question}\label{ques:reduce-5,10-to-4,8}
-			When $g \geq 2,$ can the bounds in Theorem \ref{thm:main} on 
-			the degrees of generation and relations be reduced from 
-			$e := \max(5, e_1, \ldots, e_r)$ and $\max(10, 2e_1, \ldots, 2e_r)$ to 
-			$e' := \max(4, e_1, \ldots, e_r)$ and $2e'$, 
-			apart from well a characterized list of families?
-		\end{question}
-		\begin{rem}\label{rem:reduce-3,6}
-			Note that when $L$ is not effective and $\sx$ has a stacky point, $R_\halfcan$ must have a generator in degree 4 with maximal pole order at one of the stacky points.
-Therefore, these bounds cannot in general be reduced further to
-			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e.''$
-			\end{rem}
-	\item While Theorem ~\ref{thm:main} gives a set of 
-		generators and relations
-		for the log spin canonical ring $R_\halfcan,$ these sets are not necessarily minimal.
-		In many of the $g = 0$ and $g = 1$ cases, 
-		it is not too difficult to see that our inductive procedure
-		yields a minimal set of relations for $R_\halfcan$. One might investigate 
-		whether the generators and relations given by the inductive proof 
-		of Theorem ~\ref{thm:main} are always minimal.
-		\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Acknowledgments}
+\section*{Acknowledgments}
 We are grateful to David Zureick-Brown for introducing us to the
 study of stacky canonical rings, for providing invaluable guidance,
-and for his mentorship. We also thank Ken Ono and the Emory
-University Number Theory REU for arranging our project and
-providing a great environment for mathematical learning and
-collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
-Zhang for helpful comments on this paper and thank Jorge Neves
-for pointing out the bounds given by Miles Reid's work on the
-maximal degrees of minimal generators and relations of spin
-canonical rings in high genera. The first author would also like to
-mention Joseph Harris and Evan O'Dorney for several enlightening
-conversations related to Petri's Theorem. Finally, we gratefully
+and for his mentorship. We also thank Ken Ono for arranging our project. We thank Brian Conrad, John Voight, and Shou-Wu
+Zhang, and Jorge Neves
+for helpful comments. Finally, we
 acknowledge the support of the National Science Foundation (grant
-number DMS-1250467). We deeply appreciate all of the support that
-has made our work possible.
-
+number DMS-1250467).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\todo{Remove some of these references}
 \nocite{*}
@@
 
+\end{multicols}
 \end{document}

### 2015-08-30 poster-curves/spin-canonical-poster-v2.tex
made better looking version of poster

--- 2015-08-29 poster-curves/spin-canonical-poster.tex
@@
-\documentclass[landscape, a0, largefonts]{sciposter}
-\usepackage{tcolorbox}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{bm}
-\usepackage{multicol}
-\usepackage{graphicx}
-\usepackage[english]{babel}
-\usepackage{color}
-\usepackage{wrapfig}
-\usepackage{caption}
-\usepackage{booktabs}
-\usepackage{array}
-\usepackage{ytableau}
-\usepackage{verbatim}
-\usepackage[vcentermath]{youngtab}
-\newlabel{fig2:a}{{I(a)}{1}}
-\newlabel{fig2:b}{{I(b)}{1}}
-\newlabel{fig:i}{{II(c)}{1}}
-\newlabel{fig:ii}{{II(d)}{1}}
-\newlabel{fig:iii}{{II(e)}{1}}
-\newlabel{fig3:c}{{III(f)}{1}}
-\newlabel{fig3:d}{{III(g)}{1}}
-\newlabel{fig4:i}{{IV(h)}{1}}
-\newlabel{fig4:ii}{{IV(i)}{1}}
-\newcommand{\Q}{\mathbb{Q}}
-\newcommand{\N}{\mathbb{N}}
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\row}{\mathfrak{row}}
-\newcommand{\oh}{\operatorname{outerhook}}
-\newcommand{\col}{\mathfrak{col}}
-\newcommand{\lis}{\mathfrak{lis}}
-\newcommand{\lds}{\mathfrak{lds}}
-\newcommand{\sss}{\scriptstyle} %% for tableaux
-\newcommand{\swap}{\operatorname{swap}}
-\newcommand{\jdt}{\operatorname{jdt}}
-\newcommand{\std}{\operatorname{std}}
-%\usepackage{fancybullets}
-%\usepackage{other packages you may want to use}
+\documentclass[a0,landscape, draft]{a0poster}
+\usepackage{etex}
+
+\usepackage{tikz,pgfplots,calc}
+\usepackage{graphicx,lipsum}
+
+\definecolor{emoryBlue}{RGB}{1, 33, 105}
 
@@
 \usepackage[all]{xy}
-\usepackage{graphicx}
+
 \usepackage{tikz-cd}
@@
 
-\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
-\def\listtodoname{List of Todos}
-\def\listoftodos{\@starttoc{tdo}\listtodoname}
+\usepackage{booktabs}
+\usepackage[font=Large,labelfont=bf]{caption}
+\usepackage{wrapfig}
 
@@
 
-\usepackage{tikz}
-\usepackage{tikz-cd}
 \usetikzlibrary{matrix,arrows,decorations.pathmorphing}
-
-%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%%%%%%%%%%%%%%
-
-\theoremstyle{plain}
-  \newtheorem{thm}{Theorem}
-  \newtheorem{prop}[thm]{Proposition}
-  \newtheorem{lem}[thm]{Lemma}
-  \newtheorem{cor}[thm]{Corollary}
-	\newtheorem{question}[thm]{Question}
-
-\theoremstyle{definition}
-  \newtheorem{defn}[thm]{Definition}
-  \newtheorem{example}[thm]{Example}
-
-\theoremstyle{remark}
-	\newtheorem{rem}[thm]{Remark}
 
@@
 
-\newcommand\ssec{\subsection}
-\newcommand\sssec{\subsubsection}
 \newcommand\BH{{\mathbb H}}
@@
 \definecolor{white}{rgb}{1,1,1}
-\def\NN{{\mathbb{N}}}
-\def\RR{{\mathbb{R}}}
-\newcommand{\Z}{\mathbb{Z}} 
-%\definecolor{BoxCol}{rgb}{0.9,0.9,1}
-% uncomment for light blue background to \section boxes 
-% for use with default option boxedsections
 
-%\definecolor{SectionCol}{rgb}{0,0,0.5}
-% uncomment for dark blue \section text
+%Formatting for Poster Sections
+\newcommand{\psection}[1] 
+{
+	\begin{center}
+		\begin{tikzpicture}
+			\draw [emoryBlue,line width=0.1cm] (-14,-1)--(-14,1)--(14,1)--(14,-1)--cycle;
+			\draw[emoryBlue, line width=0.1cm] (-14,0)--(-17,0);
+			\draw[emoryBlue,line width=0.1cm] (14,0)--(17,0);
+			\draw (0,0)node[anchor=center,rotate=0]{\bfseries  \fontsize{43}{0}\selectfont {}{#1}};
+		\end{tikzpicture}
+	\end{center}
+	\vspace{0.001\textheight}
+}
 
-\title{\vspace{.5cm} \textcolor{white} {Spin Canonical Rings of Log Stacky Curves}}
+%Formatting for Less Important Sections
+\newcommand{\smpsection}[1]
+{
+	\begin{center}
+		\begin{tikzpicture}
+			\draw[emoryBlue,line width=0.1cm] (-5,-1)--(5,-1);
+			\draw (0,0)node[anchor=center,rotate=0]{\bfseries  \fontsize{30}{0}\selectfont {}{#1}};
+		\end{tikzpicture}
+	\end{center}
+	\vskip .1cm
+}
 
-% Note: only give author names, not institute
-\author{\textcolor{white}{Aaron Landesman, Peter Ruhm, and Robin Zhang}}
+\usepackage{multicol} 
+\columnsep = 100pt 
+\columnseprule = 3pt
 
-%\email[Aaron Landesman]{aaronlandesman@college.harvard.edu}
+\usepackage{amsfonts, amsmath, amsthm, amssymb}
+\usepackage{empheq}
 
-% insert correct institute name
-\institute{\vspace{-.25cm} \textcolor{white}{Harvard University, Stanford University, Stanford University}}
+%Style Files
 
-%\date is unused by the current \maketitle
+\usepackage{amsthm}
+\newtheorem*{theorem}{Theorem}
+\newtheorem*{corollary}{Corollary}
+\newtheorem*{lemma}{Lemma}
 
-%\leftlogo[0.9]{nsf_logo.png}  % defines logo to left of title (with scale factor)
-%\rightlogo[1.0]{umnlogo.png} % same but on right
+\theoremstyle{definition}
+\newtheorem*{example}{Example}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newtheorem*{remark}{Remark}
+\newtheorem*{definition}{Definition}
+\newtheorem*{fact}{Fact}
+\newtheorem*{note}{Note}
+\newtheorem*{idea}{Proof Idea}
 
 \begin{document}
-%*** facultative: where the poster was presented (appears as a left footer):
-  %\conference{LSU Discover Research Day, 2014, Baton Rouge, LA}
+%%%%%%%%%%%%%%
+%Poster Title%
+%%%%%%%%%%%%%%
+	\begin{center}
+		\begin{minipage}[b]{\linewidth}
+	\begin{center}
+			%Title
+			\veryHuge \color{emoryBlue} \textbf{Spin Canonical Rings of Log Stacky Curves} \color{black}\\ 
+			%Author
+			\Large Aaron Landesman, Peter Ruhm, and Robin Zhang \hskip 1cm - \hskip 1cm Harvard University, Stanford University, and Stanford University \\
+		\end{center}
+		\end{minipage}
+	\end{center}
+	\vspace{1cm} 
+%%%%%%%%%%%%%%%%%%%%%
+%End of Poster Title%
+%%%%%%%%%%%%%%%%%%%%%
 
-%*** print the poster header defined above: title, authors, affiliations:
- \fbox{\colorbox{lightpurple}{\maketitle}}
-\\
-\\
 \begin{multicols}{3} 
-	  \begin{tcolorbox}
-	  \section*{Abstract}
+	%%%%%%%%%%%%%%%%%
+	%Poster Abstract%
+	%%%%%%%%%%%%%%%%%
+	\framebox[1.05\width]{\parbox[c]{.95\columnwidth}{
+		\begin{center}
+			\begin{tikzpicture}
+				\draw[emoryBlue,line width=0.1cm] (-3,-.8)--(3,-.8);
+				\draw (0,0)node[anchor=center,rotate=0]{\bfseries  \fontsize{40}{0}\selectfont {}{Abstract}};
+			\end{tikzpicture}
+		\end{center}
+	\Large
 
@@
 	modular forms of arbitrary integral weight.
-\end{tcolorbox}
+	\vskip .5cm
+	}}
+	%%%%%%%%%%%%%%%%%%%%%%%%
+	%End of Poster Abstract%
+	%%%%%%%%%%%%%%%%%%%%%%%%
 
-  \section*{\textsc{Notation}}
+\Large
+\smpsection{Notation}
   \begin{align*}
@@
 
-  \section*{\textsc{Introduction}}
+\psection{Introduction}
 
@@
 is generated in degree 1 with relations in degree 2 (see
-Saint-Donat \cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
-\cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
+Saint-Donat \cite[p. 157]{saint-donat:proj}. This has the pleasant 
 geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic curves, trigonal curves, or plane quintics are scheme-theoretically cut out by degree 2 equations.
+
+%%%%%%%%
+		%End of First Column
+	%%%%%%%%
+
+	\columnbreak
+
+	\psection{Main Result}
 
@@
 ~\cite[Theorem 1.4]{vzb:stacky}, Voight and Zureick-Brown tightly
-bounde the degree of generation and
-relations of a log spin canonical ring.
+bound the degree of generation and
+relations of a log canonical ring.
 
-  \section*{\textsc{Main Result}}
-
-\begin{thm}
-\label{thm:main}
+\begin{theorem}
+\label{theorem:main}
 Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect
@@
 signatures with $g = 0$.
-\end{thm}
+\end{theorem}
 {\bf Proof idea:} First, check this holds when $\Delta \in \di X$,
@@
 it holds for a given divisor $\Delta$ it holds for
-$\Delta + \frac{e-1}{2e}P$.
+$\Delta + \frac{e-1}{e}P$.
 
-\begin{table}
-\captionsetup{type=figure}
-\begin{center}
+\begin{minipage}{38cm}
+\centering
+%\begin{wraptable}{l}{12cm}
+
 \begin{tabular}
@@
 \end{tabular}
-\end{center}
-\caption{Genus 0 Exceptional Cases}
+
 \label{table:g-0-exceptional}
-\end{table}
+\captionof{table}{Genus 0 Exceptional Cases}
+%\end{wraptable}
+\end{minipage}
 
-\begin{table}	
-\captionsetup{type=figure}
+\begin{minipage}{38cm}
+\centering
+
+%\begin{wraptable}{l}{12cm}
+
 \begin{center}
@@
 \end{center}
-\caption{Genus 1 Exceptional Cases}
+
 \label{table:g-1-exceptional}
-\end{table}
 
-\section*{Applications to Modular Forms}
+\captionof{table}{Genus 1 Exceptional Cases}
+%\end{wraptable}
+\end{minipage}
 
-\begin{cor}
-\label{cor:main-mod-forms}
+\psection{Application to Modular Forms}
+
+\begin{corollary}
+\label{corollary:main-mod-forms}
 Let $\Gamma$ be a Fuchsian, i.e., $\Gamma \backslash \BH$ has finite area, group and $\sx$ the stacky curve
@@
 e_r)$.
-\end{cor}
+\end{corollary}
+
+\columnbreak
 
@@
 
-\section*{Acknowledgments}
+%%%Bibliography
+\nocite{*}
+\bibliography{bibliography}{}
+\bibliographystyle{plain}
+
+%%%Acknowledgements
+
+\psection{Acknowledgements}
 We are grateful to David Zureick-Brown for introducing us to the
@@
 number DMS-1250467).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{Remove some of these references}
-\nocite{*}
-\bibliography{bibliography}{}
-\bibliographystyle{plain}
-
 \end{multicols}

### 2015-09-23 poster-curves/spin-canonical-poster-v2.tex
editing stacky poster

@@
 	Kodaira--Spencer, this ring of modular forms may be viewed as the
-	log spin canonical ring of a stacky curve. In this paper, we
+	log spin canonical ring of a stacky curve. We
 	tightly bound the degrees of minimal generators and relations of
@@
 	  (g; e_1,\ldots, e_r; \delta) & & \text{Signature} \\
-	\lfloor \sum_{i=1}^n \alpha_i P_i \rfloor := \sum_{i=1} \lfloor \alpha_i\rfloor P_i & & \text{Floor of a Stacky Divisor} \\
+	\left\lfloor \sum_{i=1}^n \alpha_i P_i \right\rfloor := \sum_{i=1} \lfloor \alpha_i\rfloor P_i & & \text{Floor of a Stacky Divisor} \\
 	K_X & & \text{Canonical Divisor of Coarse Space} \\

### 2015-09-23 poster-curves/spin-canonical-poster-v2.tex
aarons preprinting edits to poster

@@
 so long as $\sigma$ does not lie in a finite list of exceptional
-cases, as given in Table ~\ref{table:g-1-exceptional} for
-signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional} for
-signatures with $g = 0$.
+cases, as given in Table 1 for
+signatures with $g = 0$ and Table 2 for
+signatures with $g = 1$.
 \end{theorem}
@@
 Then, inductively add in fractional points, showing that if
-it holds for a given divisor $\Delta$ it holds for
+it holds for a given divisor $\Delta$, then it holds for
 $\Delta + \frac{e-1}{e}P$.
+\vspace{.2cm}
 
@@
 \label{corollary:main-mod-forms}
-Let $\Gamma$ be a Fuchsian, i.e., $\Gamma \backslash \BH$ has finite area, group and $\sx$ the stacky curve
+Let $\Gamma$ be a Fuchsian group, i.e., $\Gamma \backslash \BH$ has finite area,and let $\sx$ be a stacky curve
 associated to $\Gamma \backslash \BH$ with signature $\sigma

### 2015-09-25 poster-curves/spin-canonical-poster-v2.tex
edited saint-donat
posters: turn draft mode off
edited last poster example, corrected some more typos

@@
-\documentclass[a0,landscape, draft]{a0poster}
+\documentclass[a0,landscape]{a0poster}
 \usepackage{etex}
@@
 \noindent
-with multiplication structure corresponding to tensor product of
+with multiplication corresponding to tensor product of
 sections. In the case that $g \geq 2$, $\Omega_X$ is ample and
@@
 shows that, in most cases, $R(X, K_X)$
-is generated in degree 1 with relations in degree 2 (see
-Saint-Donat \cite[p. 157]{saint-donat:proj}. This has the pleasant 
+is generated in degree 1 with relations in degree 2 \cite[p. 157]{saint-donat:proj}. This has the pleasant 
 geometric consequence that canonically embedded curves of genus $\geq 4$ which are not hyperelliptic curves, trigonal curves, or plane quintics are scheme-theoretically cut out by degree 2 equations.
@@
 	\hline
-	$\halfcan'$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
+	$\halfcan$ & Generator Degrees & Degrees of Minimal Relations & $e$ \\
 	\hline
@@
 \label{corollary:main-mod-forms}
-Let $\Gamma$ be a Fuchsian group, i.e., $\Gamma \backslash \BH$ has finite area,and let $\sx$ be a stacky curve
+Let $\Gamma$ be a Fuchsian group, i.e., $\Gamma \backslash \BH$ has finite
+area, and let $\sx$ be a stacky curve
 associated to $\Gamma \backslash \BH$ with signature $\sigma
@@
 Except in an explicit finite list of cases, the
-ring of modular forms $M(\Gamma)$ is generated as a $k$-algebra
+ring of modular forms $M(\Gamma)$ is generated as a $\Bbbk$-algebra
 by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
@@
 relations in weight at most $8$.\end{example}
+
+\begin{example}  
+	\hspace{1mm}
+	\begin{center}
+    $D = K + \Delta = \frac{1}{2}P + \frac{2}{3}Q -\infty$
+  \end{center}
+
+\begin{center}
+\begin{tabular}{ |c| c| c| c|c|}
+\hline
+$d$ & $\lfloor dD \rfloor$ & $\deg \lfloor dD \rfloor$ &  $\dim H^0(X,\lfloor dD \rfloor)$  & $M_{2d}(SL_2(\BZ))$  \\ 
+\hline
+0& 0& 0&  1& 1 \\ 
+1&$-\infty$&-1& 0&  0 \\  
+2&$P + Q -2\infty$&0& 1&  $E_4$  \\
+3&$P + 2Q -3\infty$&0& 1&  $E_6$  \\
+4&$2P + 2Q -4\infty$&0& 1&  $E_4^2$  \\
+5&$2P + 3Q -5\infty$&0& 1&  $E_4E_6$  \\
+6&$3P + 4Q -6\infty$&1& 2& $E_4^3, E_6^2$   \\
+\hline
+\end{tabular}
+\end{center}
+\end{example}
 

### 2015-10-03 curves-write-up/spin-cring.tex
changed degree to weight
fixed some minor typos I noticed in the paper

--- 2015-07-16 curves-write-up/spin-cring.tex
@@
 where $\Delta \in \di X$ is a log divisor and $L \in \di \sx$ is a {\bf log spin canonical divisor}, meaning $2\halfcan \sim K_X +
-\Delta + \sum_{i = 1}^{r} \subhalf{e_i} P_i$. The central object of
+\Delta + \sum_{i = 1}^{r} \frac{e_i-1}{e_i} P_i$. The central object of
 study in this paper is the {\bf log spin canonical ring} of $(\sx,
@@
 Therefore, by Corollary ~\ref{cor:main-mod-forms}, $M(\Gamma)$ is 
-generated in degree at most $5$ with relations in degree at most $10$.
+generated in weight at most $5$ with relations in weight at most $10$.
 Furthermore, it is not difficult to show that $M(\Gamma)$ is generated in weight at most 4 with relations in weight at most 8 when the genus of the stacky curve associated to $\Gamma \backslash \BH^*$ is 0 or 1, as noted in Remark ~\ref{rem:cusp-generation-4}.
@@
 $$\deg a_i =\deg f - \deg x_i -2 \geq 4.$$
-In particular, there exist $\alpha, \beta \in R_\halfcan$ so that
-$$\phi(a_i) = \phi(s_1) \cdot \alpha + \phi(s_1) \cdot \beta.$$ 
-Choosing $g_i,h_i\in \Bk[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha, \phi(h_i) = \beta$, we have 
+In particular, there exist $\alpha_i, \beta_i \in R_\halfcan$ so that
+$$\phi(a_i) = \phi(s_1) \cdot \alpha_i + \phi(s_2) \cdot \beta_i.$$ 
+Choosing $g_i,h_i\in \Bk[x_1, \ldots, x_n]_{\deg(a_i)-2}$ for $1 \leq i \leq n$ so that $\phi(g_i) = \alpha_i, \phi(h_i) = \beta_i$, we have 
 $$a_i \equiv s_1 g_i + s_2 h_i \bmod I_{\halfcan, \deg a_i},$$ as claimed.
@@
  with $g \geq 2$ and $\Delta > 0.$ Then $I_\halfcan$ is generated in
-degree at most degree at most $10$.
+degree at most $10$.
 \end{prop}
@@
 Suppose $f \in I_\halfcan$ with $\deg f \geq 11$. To complete the proof,
-it suffices to show $f \in I_{\halfcan,k}'$. By Lemma
+it suffices to show $f \in J_{\halfcan,k}$. By Lemma
 ~\ref{lem:reducing-degree}, this is the same as checking $s_1 g + s_2 h \in
-I_{\halfcan, k}'$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
+J_{\halfcan, k}$ where $\phi(s_ 1), \phi(s_2) \in H^0(X, 2L)$ are two sections
 so that $\newspan(\phi(s_ 1), \phi(s_2)) = V \subseteq H^0(K)$ is

### 2015-10-17 curves-write-up/AIF/changes-summary.tex
added changes summary file to AIF

%        File: changes-summary.tex
%     Created: Sat Oct 17 11:00 AM 2015 E
% Last Change: Sat Oct 17 11:00 AM 2015 E
%
%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass[10 pt]{amsart}

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{subfiles}
\usepackage{mathpazo}
\usepackage{euler}
\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}

\addtolength{\oddsidemargin}{-.5 in}
\addtolength{\evensidemargin}{-.4 in}
\addtolength{\textwidth}{1 in}
\addtolength{\topmargin}{0 in}
\addtolength{\textheight}{0 in}

\RequirePackage{color}
\definecolor{myred}{rgb}{0.75,0,0}
\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{myblue}{rgb}{0,0,0.65}

\usepackage{hyperref}
\hypersetup{colorlinks=true,citecolor=blue}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{counterexample}[theorem]{Counterexample}
\newtheorem{convention}[theorem]{Convention}
\newtheorem{question}[theorem]{Question}
\newtheorem{conjecture}[theorem]{Conjecture} 
\newtheorem{warning}[theorem]{Warning}
\newtheorem{fact}[theorem]{Fact}
\theoremstyle{remark}
\newtheorem{notation}[theorem]{Notation}
\numberwithin{equation}{section}

\newcommand\nc{\newcommand}
\nc\on{\operatorname}
\nc\renc{\renewcommand}
\newcommand\se{\section}
\newcommand\ssec{\subsection}
\newcommand\sssec{\subsubsection}
\newcommand\bn{{\mathbb N}}
\newcommand\bc{{\mathbb C}}
\newcommand\br{{\mathbb R}}
\newcommand\bq{{\mathbb Q}}
\newcommand\bp{{\mathbb P}}
\newcommand\CF{{\mathcal F}}
\newcommand\bz{{\mathbb Z}}
\newcommand\ba{{\mathbb A}}
\newcommand\fa{{\mathfrak a}}
\newcommand\fp{{\mathfrak p}}
\newcommand\fq{{\mathfrak q}}
\newcommand\fm{{\mathfrak m}}
\newcommand\so{{\mathscr O}}
\newcommand\sg{{\mathscr G}}

\newcommand\scm{{\mathscr M}}
\newcommand\scn{{\mathscr N}}
\newcommand\scf{{\mathscr F}}
\newcommand\scg{{\mathscr G}}
\newcommand\sco{{\mathscr O}}
\newcommand\sch{{\mathscr H}}
\newcommand\scl{{\mathscr L}}
\newcommand\sci{{\mathscr I}}

\newcommand \ra{\rightarrow}
\newcommand{\id}{\mathrm{id}}
\newcommand\im{\text{im }}
\newcommand\coker{\text{coker}}
\newcommand \spec{\text{Spec }}
\newcommand \proj{\text{Proj }}
\newcommand \rspec{\textit{Spec }}
\newcommand \rproj{\textit{Proj }}
\newcommand \mg{{\mathscr M_g}}

\DeclareMathOperator\ord{ord}

\newcommand \trdeg{\text{tr. deg }}
\newcommand \codim{\text{codim}}
\newcommand \rk{\text{rk }}
\newcommand \di{\text{div }}
\newcommand \depth{\text{depth }}
\DeclareMathOperator\pic{Pic}
\DeclareMathOperator\lcm{lcm}
\DeclareMathOperator\rank{rank}
\DeclareMathOperator\vol{Vol}
\DeclareMathOperator\supp{Supp}

\def\listtodoname{List of Todos}
\def\listoftodos{\@starttoc{tdo}\listtodoname}

\title{Summary of Changes in response to Referee's Report}
\author{Aaron Landesman, Peter Ruhm, and Robin Zhang}

\begin{document}

\maketitle

Here are the changes we have made in response to the referee's suggestions.

\begin{enumerate}
	\item 
\end{enumerate}

\end{document}

### 2015-11-02 curves-write-up/AIF/changes-summary.tex
curves: add todos and starter stubs for AIF edits

@@
 \begin{enumerate}
-	\item 
+	\item Paragraph/remark on Gorenstein-ness in ``Introduction''
+		section
+	\item Use Hilbert polynomial in Example $\_\_\_$
+	\item Replace ``best lower approximation'' with Hirzebruch--Jung
+		fractions
+	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
+		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
+		we range over all $e'_i$ instead of odd $e_i$.
 \end{enumerate}

### 2015-11-02 curves-write-up/spin-cring.tex
moved period
curves: add todos and starter stubs for AIF edits

@@
 
+\todo{Remark or paragraph on Gorenstein-ness}
+``Orbifold canonical curves are projectively Gorenstein''
+from an old result of Kei-ichi Watanabe. The spin case
+follows from projective Cohen-Macaulay which follows from
+projectively normal as seen when taking the complete
+space of sections.
+\todo{Robin: This is probably better fit in the introduction
+than background. Per the reviewer, this is the primary
+interest in taking the orbifold canonical class to be in
+the form that we have. However, it seems strange in the current
+place that I plopped it in.}
+
 Our main theorem is to bound the degrees of generators and
@@
 graded component of $R$.
-
 \end{defn}
@@
 \label{sec:examples}
+
+\todo{Use Hilbert polynomial in an example}
 
@@
 \label{defn:lower-approximation}
+\todo{Replace this notation with Hirzebruch--Jung fractions}
 If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
@@
 Therefore, these bounds cannot in general be reduced further to
-			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e.''$
+			$e'' := \max(3, e_1, \ldots, e_r)$ and $2e''$.
 			\end{rem}

### 2015-11-28 curves-write-up/AIF/changes-summary.tex
added gorensteinness remark in background

@@
 \maketitle
-
+\section{Changes Made}
 Here are the changes we have made in response to the referee's suggestions.
@@
 \begin{enumerate}
-	\item Paragraph/remark on Gorenstein-ness in ``Introduction''
-		section
+	\item We added a remark on Gorensteinness of the log canonical ring following
+	the definition of a log spin canonical ring in the background section.
 	\item Use Hilbert polynomial in Example $\_\_\_$

### 2015-11-28 curves-write-up/spin-cring.tex
added gorensteinness remark in background

@@
 \end{defn}
+
+\begin{rem}
+	The log canonical ring, defined to be the direct sum of the even graded pieces of the log spin canonical ring,
+	is Gorenstein. It is Cohen Macaulay from \cite[Example 2.5(a)]{watanabe:some-remarks-concerning-demazure's-construction-of-normal-graded-rings}
+	and then Gorenstein by \cite[Corollary 2.9]{watanabe:some-remarks-concerning-demazure's-construction-of-normal-graded-rings}.
+	In particular, this tells us a log spin canonical curve, the projectivization of a log spin canonical ring,
+	is projectively Gorenstein.
+\end{rem}
 

### 2015-11-28 curves-write-up/AIF/changes-summary.tex
responses to log stackiness comment of referee not being gorenstein

@@
 	the definition of a log spin canonical ring in the background section.
+	We noticed in comment 1 that the referee made a comment saying
+	``Cohen-Macaulay and
+projectively Gorenstein follows as usual (of course, provided there are
+no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
+it to mean that the canonical ring may not be Gorenstein if it is of the form
+\begin{align*}
+	\oplus_n H^0(X, P + n L)
+\end{align*}
+for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
+\begin{align*}
+	\oplus_n H^0(X, n L)
+\end{align*}
+for $L$ a fractional divisor, so this would not pose an issue.
 	\item Use Hilbert polynomial in Example $\_\_\_$

### 2015-11-29 curves-write-up/spin-cring.tex
curves: shorten new bib entry, delete old gorenstein rem

--- 2015-11-02 curves-write-up/spin-cring.tex
@@
 
-\todo{Remark or paragraph on Gorenstein-ness}
-``Orbifold canonical curves are projectively Gorenstein''
-from an old result of Kei-ichi Watanabe. The spin case
-follows from projective Cohen-Macaulay which follows from
-projectively normal as seen when taking the complete
-space of sections.
-\todo{Robin: This is probably better fit in the introduction
-than background. Per the reviewer, this is the primary
-interest in taking the orbifold canonical class to be in
-the form that we have. However, it seems strange in the current
-place that I plopped it in.}
-
 Our main theorem is to bound the degrees of generators and
@@
 \end{defn}
+
+\begin{rem}
+\label{rem:gorenstein}
+	The log canonical ring, defined to be the direct sum of the even
+	graded pieces of the log spin canonical ring, is Gorenstein. It is
+	Cohen Macaulay from \cite[Example 2.5(a)]
+	{watanabe:demazure-normal-graded} and then Gorenstein by
+	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
+	particular, this tells us a log spin canonical curve, the
+	projectivization of a log spin canonical ring, is projectively
+	Gorenstein.
+\end{rem}
 

### 2015-11-29 curves-write-up/spin-cring.tex
curves: minor edits to gorenstein rem

@@
 	graded pieces of the log spin canonical ring, is Gorenstein. It is
-	Cohen Macaulay from \cite[Example 2.5(a)]
+	Cohen--Macaulay from \cite[Example 2.5(a)]
 	{watanabe:demazure-normal-graded} and then Gorenstein by
 	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
-	particular, this tells us a log spin canonical curve, the
+	particular, this tells us that a log spin canonical curve, the
 	projectivization of a log spin canonical ring, is projectively

### 2016-01-01 curves-write-up/AIF/changes-summary.tex
curves: add some response to e_i -> s_i suggestion

@@
 		fractions
-	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
-		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
-		we range over all $e'_i$ instead of odd $e_i$.
+\end{enumerate}
+
+\section{Other suggestions}
+The referee also made the following suggestions.
+
+\begin{enumerate}
+	\item Change notation from $\frac{e_i - 1}{2 e_i}$
+		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$ and
+		we range over all integers $s_i$ instead of odd integers $e_i$.
+\end{enumerate}
+
+We decided not to implement the above suggestions for the following
+reasons, respectively.
+
+\begin{enumerate}
+	\item Firstly, we maintained the $e_i$ notation for consistency
+	with the notation established in Voight--Zureick-Brown. These
+	$e_i$ correspond to the stabilizer orders in the log spin
+	canonical ring case considered there. Furthermore, we often
+	list degrees of generation and relations enumerated by signatures
+	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
+	the	form $\min(5, e_1, \ldots, e_n)$ which are more natural to
+	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
+	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
+	2s_n + 1)$.
 \end{enumerate}

### 2016-01-02 curves-write-up/spin-cring.tex
Updated MONSTER LEMMA

--- 2015-11-29 curves-write-up/spin-cring.tex
@@
 graded component of $R$.
+
 \end{defn}
-
-\begin{rem}
-\label{rem:gorenstein}
-	The log canonical ring, defined to be the direct sum of the even
-	graded pieces of the log spin canonical ring, is Gorenstein. It is
-	Cohen Macaulay from \cite[Example 2.5(a)]
-	{watanabe:demazure-normal-graded} and then Gorenstein by
-	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
-	particular, this tells us a log spin canonical curve, the
-	projectivization of a log spin canonical ring, is projectively
-	Gorenstein.
-\end{rem}
 
@@
 \label{sec:examples}
-
-\todo{Use Hilbert polynomial in an example}
 
@@
 We are almost ready to state Lemma ~\ref{lem:sat-1}, which will yield an inductive procedure for determining the generators and relations of $R_D$, where $D \in \di \BP^1$ is an effective $
-\BQ$-divisor.
-Whereas O'Dorney considers arbitrary $\BQ$-divisors in $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are able to obtain much tighter bounds.
-Moreover, Lemma ~\ref{lem:sat-1} also extends to curves of genus $g > 0$.
-Before stating Lemma ~\ref{lem:sat-1}, we recall some notation from O'Dorney \cite{dorney:canonical}.
-
-\begin{defn}
-\label{defn:lower-approximation}
-\todo{Replace this notation with Hirzebruch--Jung fractions}
-If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
-$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
-\textbf{best lower approximation} to $\alpha$ if there does not
-exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
-$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
-\end{defn}
-
-\begin{rem}
-\label{rem:lower-approximation}
-Note that all integers less than or equal to $\lfloor \alpha \rfloor$
-are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
-then the non-negative best lower approximations of
-$\alpha$ form a finite sequence
-\[
-	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
-\]
-
-\noindent
-Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
-\end{rem}
+\BQ$-divisor. Whereas O'Dorney considers arbitrary $\BQ$-divisors in
+$Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict
+attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are
+able to obtain much tighter bounds.  Moreover, Lemma ~\ref{lem:sat-1}
+also extends to curves of genus $g > 0$. 
+%Before stating Lemma
+%~\ref{lem:sat-1}, we recall some theory from continued fractions.
+
+%\begin{defn}
+%\label{defn:lower-approximation}
+%If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
+%$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
+%\textbf{best lower approximation} to $\alpha$ if there does not
+%exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
+%$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
+%\end{defn}
+
+%\begin{rem}
+%\label{rem:lower-approximation}
+%Note that all integers less than or equal to $\lfloor \alpha \rfloor$
+%are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
+%then the non-negative best lower approximations of
+%$\alpha$ form a finite sequence
+%\[
+%	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \%alpha.
+%\]
+%
+% proves 
+%\begin{defn}\label{defn:cont-fract}
+%Let $[a_1, \ldots, a_n]$ be the (Hirzebruch-Jung) continued fraction
+%on $a_1, \ldots, a_n$ (given by $1 + \frac{1}{a_1+\frac{1}{... + \frac{1}{a_n}}}$).
+%\end{defn}
+%\begin{prop}\label{prop:primitives}
+%The primitives 
+%\end{prop}
+
+%\noindent
+%Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the posi%tive best lower approximations of $\alpha = \frac{14}{5}$.
+%\end{rem}
 
@@
 \end{figure}
+\todo{Is this figure (figure 1)  still useful anywhere?}
 
@@
 Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
-for some $\alpha, \beta \in \BN$ such that
+for some $\alpha, \beta \in \BN$ such that $\frac{\alpha}{\beta}$ is reduced and
 \begin{align}
@@
 \end{align}
-Let
-\[
-	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
-\]
-be the positive best lower approximations of $\frac{\alpha}{\beta}$
-{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
+%Let
+%\[
+%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
+%\]
+%be the positive best lower approximations of $\frac{\alpha}{\beta}$
+%{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
 Then,
@@
 \item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by 
-	elements $y_1, \ldots, y_n$ such that $\deg(y_i) = k_i$ and $-\ord_P
-	^{L'}(y_i) = c_i$.
+	elements $y_1, \ldots, y_n$ where $\deg(y_i) = k_i<\beta$, $-\ord_P
+	^{L'}(y_i) = c_i$ for some $k_i$'s and $c_i$'s such that $c_i<c_{i+1}\le \alpha$ and $k_i\le k_{i+1}\le \beta$ for all $i$.
 
@@
 
-\sssec*{Idea of proof:}
-The proof will be fairly involved. To show part (a), we first
-define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$
-with one generator corresponding to each positive best lower
-approximation of $\frac{\alpha}{\beta}$. We then use Riemann--Roch
+\sssec*{Idea of proof:}\todo{Update subsection}
+The proof will be fairly involved. To show part (a), we first apply 
+literature on continued fractions to 
+define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
+We then use Riemann--Roch
 to count the dimension of $R_\halfcan$ over $R_{\halfcan'}$ and
@@
 for any $i \in \{0, \ldots, \lfloor k \frac{\alpha}{
-\beta} \rfloor \}$. We will the use positive best lower approximations to
-construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
-
-Let 
-\[
-	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
-	\beta}
-\]
-
-\noindent
-be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
-Choose a positive best lower approximation $\frac{c_i}{k_i}$.
+\beta} \rfloor \}$.
+This reduces the problem at hand to finding the primitives of the cone in $\mathbb{Z}\times \mathbb{Z}$ bounded by $y=0$ and $y=\frac{\alpha}{\beta}x$.
+
+Literature on Cohn's geometric interpretation of hirzabruch jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).
+Note that if two primitives had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$ and thus could not both be generators; thus all the $c_i$'s (their $y$ coordinates) are distinct, and we can thus order them with $c_i<c_{i+1}$ for all $i$.
+Furthermore, note that in any degree $k$ greater than 1, there can be at most one new primitive, since we can construct points with $y$ coordinates between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in degree 1 and degree $k-1$, and these new primitives have pole order greater than all primitives of smaller $x$-coordinate.
+Therefore, the ordering of primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values $k_i$'s are also in weakly increasing order.
+Finally, let $y_1, \ldots, y_n$ be elements of $R_Lx$ with pole orders given by $c_1,\ldots, c_n$ and degrees given by the $x$ coordinates of the corresponding primitives.
+%We will the use positive best lower approximations to
+%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
+%
+%Let 
+%\[
+%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
+%	\beta}
+%\]
+%
+%\noindent
+%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
+%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.
 Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$.
@@
 Hence, for each $j$,
-\[
-	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
-\]
-so the mediant inequality tells us
-\[
-	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
-\]
-Multiplying through by $k_i$ gives
-\[
-	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\ord^{\halfcan'}_P(z_j) < c_i .
-\]
-
-\noindent
-Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
-lower degrees. 
-Choose some $y_i \in(R_{
-\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-
-Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
-\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
-\[
-	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
-\]
-
-\noindent
-which implies
-\begin{equation}\label{eqn:c-from-lower-terms}
-	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
-\end{equation}
-
-Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
+%\[
+%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
+%\]
+%so the mediant inequality tells us
+%\[
+%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
+%\]
+%Multiplying through by $k_i$ gives
+%\[
+%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
+%\]
+
+%\noindent
+%Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
+%lower degrees. 
+%Choose some $y_i \in(R_{
+%\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
+%
+%Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
+%\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
+%best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
+%\[
+%	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
+%\]
+%
+%\noindent
+%which implies
+%\begin{equation}\label{eqn:c-from-lower-terms}
+%	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
+%\end{equation}
+
+We now recursively define a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
 \[
@@
 If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$.
-Let $\halfcan$ be maximal such that $a_l\ne 0$.
+Let $l$ be maximal such that $a_l\ne 0$.
 Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
@@
 \noindent
-Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S$, 
-and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
+Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S\cup S_0$, 
+and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S \cup S_0$. \todo{Check whether all these $S$ need to be changed to $S\cup S_0$ like here.}   
 Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
 and have the following still satisfied: each $\gamma_j\le b_j$ 
-and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
-$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.
+and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S\cup S_0.$ Our recursive definition of 
+$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S\cup S_0$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S\cup S_0$.
 
@@
 
-Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
+Since the ideal in $\Bk[u, y_1, \ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot \Bk[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ contains every monomial in $\bigcup_{i=1}^n y_i \cdot \Bk[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $\Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
 \begin{align*}

### 2016-01-05 curves-write-up/spin-cring.tex

@@
 graded component of $R$.
-
 \end{defn}
+
+\begin{rem}
+\label{rem:gorenstein}
+	The log canonical ring, defined to be the direct sum of the even
+	graded pieces of the log spin canonical ring, is Gorenstein. It is
+	Cohen--Macaulay from \cite[Example 2.5(a)]
+	{watanabe:demazure-normal-graded} and then Gorenstein by
+	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
+	particular, this tells us that a log spin canonical curve, the
+	projectivization of a log spin canonical ring, is projectively
+	Gorenstein.
+\end{rem}
 
@@
 
-\begin{figure}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
+%\begin{figure}
+%\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
+%\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
 Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
 \end{figure}
-\todo{Is this figure (figure 1)  still useful anywhere?}
+%\todo{Is this figure (figure 1)  still useful anywhere?}
 

### 2016-01-08 curves-write-up/spin-cring.tex
curves: comment out a line causing error
curves: fix name of HJ

@@
 Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
-\end{figure}
+%\end{figure}
 %\todo{Is this figure (figure 1)  still useful anywhere?}
@@
 
-Literature on Cohn's geometric interpretation of hirzabruch jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).
+Literature on Cohn's geometric interpretation of Hirzebruch--Jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).
 Note that if two primitives had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$ and thus could not both be generators; thus all the $c_i$'s (their $y$ coordinates) are distinct, and we can thus order them with $c_i<c_{i+1}$ for all $i$.

### 2016-01-12 curves-write-up/spin-cring.tex
added in hilbert series calculations

@@
 Here we collect various definitions and notation that will be
-used throughout the paper. Many of the conventions come from existing
-literature. For basic references on the statements and definitions
+used throughout the paper. For basic references on the statements and definitions
 used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
@@
 To complete the example, it suffices to show there are no
-additional relations. First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
+additional relations. 
+One method would be to use \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch}
+to write down the Hilbert series and then check this agrees with the
+Hilbert series of the ring we constructed above.
+Here is an alternative method:
+First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
 y_{1, 3} + f(x_1, x_2)$ is irreducible because there are no
@@
 presentation for $R' = R(\sx', 0, \halfcan')$ and show that $R'$ is
-generated as a $Bk$-algebra in degrees up to $e := \max(5, 3, 7, 7) = 7$
+generated as a $\Bk$-algebra in degrees up to $e := \max(5, 3, 7, 7) = 7$
 with relations generated in degrees up to $2e = 14$.
@@
 \rfloor + 2 \lfloor \frac{3k}{7} \rfloor$.
+
+First, by \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch},
+\todo{in theorem 3.1, it states n is at least 2, what is going on?}
+the Hilbert series of this log spin curve is
+\begin{align*}
+	P_{(\sx', 0, \halfcan')}(k) &= \frac{1-2k + k^2 -2k^3 + k^4}{(1-k)^2} + \frac{k^3}{(1 - k)(1 - k^3)} + 2 \frac{k^3 + k^5 + k^7}{(1-k)(1-k^7)}.
+\end{align*}
+For $k = 0, 1, 2, \ldots$ we have
+\[
+	P_{(\sx', 0, \halfcan')}(k) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
+\]
+
+\noindent
+so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
+x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i \halfcan')$.
 
@@
 
-For $k = 0, 1, 2, \ldots$ we have
-\[
-	\dim_\Bk H^0 (\sx', k \halfcan') = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
-\]
-
-\noindent
-so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
-x_{7, 2}$ with $x_{i, j} \in H^0(\sx', i \halfcan')$.
-
 To show that these generate all of $R'$, we need to show that all
 $H^0 (\sx', k \halfcan')$ are generated by lower degrees for $k = 6$
-and $7 < k \leq 25$. Note that we can again use Max Noether's theorem
-(taking saturation into account) to see that
-
-\begin{align*}
-	&H^0 (\sx', 3 \halfcan') \otimes H^0 (\sx',
-	(k - 3) \halfcan') \rightarrow H^0 (\sx',
-	k \halfcan') \text{ if } k \geq 12 \text{ and } 3 \nmid k \\
-	&H^0 (\sx', 7 \halfcan') \otimes H^0 (\sx',
-	(k - 7) \halfcan') \rightarrow H^0 (\sx',
-	k \halfcan') \text{ if } k \geq 6, k \not\equiv 0, 5
-	\bmod 7
-\end{align*}
-
-\noindent
-are surjective. This reduces the problem to checking generation
-in the degrees of the exceptions $k \in \{8, 12, 21\}$.
-Checking these remaining cases via pole degree considerations shows
-that these degrees are also generated in lower degrees. Thus, $R'$
+and $7 < k \leq 25$. This can be seen by
+checking these remaining cases via pole degree considerations
+or using the generalized Max Noether's theorem. Thus, $R'$
 is generated in degrees $\{3, 5, 7, 7\}$.
@@
 at $P_3$.
-
-We can directly see that the relations are given in degrees $10$
-and $14$. In particular, we have relations
+We then have two relations
 \begin{align*}
@@
 	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
-	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
-\end{align*}
-
-\noindent
-and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
-have that
+	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$.}
+\end{align*}
+
+\noindent
+Note that $a_1$ and $b_1$ are both nonzero. For example, if $a_1 = 0$,
+we would have
 \[
-	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
+	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}.
 \]
@@
 \noindent
-However, $x_{7, 2} x_{3, 1}$ has pole orders $(3, 3, 4)$ and
-$x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ so their
-coefficients must be zero for this equality to hold. We have a
-similar pole order consideration in forcing $b_1$ to be nonzero.
+implying that $a_2 = a_3 = 0$, which would mean there is no relation at all.
+A similar pole order consideration in forcing $b_1$ to be nonzero.
 
@@
 \noindent
-since $a_1$ and $b_1$ are nonzero.
-
-To demonstrate that these two relations generate all 
-relations, we show that $\dim_\Bk (R')_k = \dim_\Bk
-(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \initial(I))_k$ for 
-all degrees $k \geq 0$. In particular,
-
-\begin{align*}
-	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_k &=
-	\dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_k \\
-	&= \dim_\Bk \left(\Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
-	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_k
-\end{align*}
-\noindent
-for all $k \geq 0$. But the fact $\dim_\Bk (R')_k = \dim_\Bk \left(\Bk[x_{7, 2},
-x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
-\rangle\right)_k$ can be checked by looking at the $\Bk$-basis at each degree
-$k$.
+since $a_1$ and $b_1$ are nonzero. Since this ring has Hilbert series
+equal to $P_{(\sx', 0, \halfcan')}(k)$, we have found all the relations.
 
@@
 Then, there exist constants $\alpha, \beta, \gamma \in \Bk$ so that 
-$R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $\Bk$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
+$R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first 
+write down the Hilbert series of $(R_{\halfcan'})_n$ over $\Bk$ using \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch}, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
 The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
@@
 
-In order to show this is an isomorphism, one can use Riemann--Roch and pole order considerations at $P_1$ to check the above relation exists.
-One can then check that the generators and relation determine a ring $R$ so that for all $j \in \BZ,$ the $j$th graded component $(R)_j$ satisfies $\dim_\Bk (R)_j = \dim_\Bk R_\halfcan.$ Hence, $R \cong R_\halfcan$.
+In order to show this is an isomorphism, one can write down the Hilbert series using \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch} and then use pole order considerations at $P_1$ to check the above relation exists.
+One can then check that the generators and relation determine a ring with the desired Hilbert series.
 The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
@@
 $Div(\mathbb{P}^1)$ \cite[Theorem 8]{dorney:canonical}, we restrict
-attention to effective divisors and in Lemma ~\ref{lem:sat-1} we are
-able to obtain much tighter bounds.  Moreover, Lemma ~\ref{lem:sat-1}
+attention to effective divisors and in Lemma ~\ref{lem:sat-1} we
+obtain much tighter bounds.  Moreover, Lemma ~\ref{lem:sat-1}
 also extends to curves of genus $g > 0$. 
@@
 \sssec*{Idea of proof:}\todo{Update subsection}
-The proof will be fairly involved. To show part (a), we first apply 
-literature on continued fractions to 
-define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
+The proof will be fairly involved. To show part (a), we 
+first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
 We then use Riemann--Roch
@@
 \beta} \rfloor \}$.
-This reduces the problem at hand to finding the primitives of the cone in $\mathbb{Z}\times \mathbb{Z}$ bounded by $y=0$ and $y=\frac{\alpha}{\beta}x$.
-
-Literature on Cohn's geometric interpretation of Hirzebruch--Jung fractions offers us an explicit formula for these primitives (Proposition 4.3 \todo{cite and add to bibtex}); one observes they all lie in degrees at most $\beta$ (since points in degree $\gamma=\beta+\omega$ can by written as a sum of points in degree $\beta$ with those in degree $\omega$).
-Note that if two primitives had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$ and thus could not both be generators; thus all the $c_i$'s (their $y$ coordinates) are distinct, and we can thus order them with $c_i<c_{i+1}$ for all $i$.
-Furthermore, note that in any degree $k$ greater than 1, there can be at most one new primitive, since we can construct points with $y$ coordinates between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in degree 1 and degree $k-1$, and these new primitives have pole order greater than all primitives of smaller $x$-coordinate.
-Therefore, the ordering of primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values $k_i$'s are also in weakly increasing order.
-Finally, let $y_1, \ldots, y_n$ be elements of $R_Lx$ with pole orders given by $c_1,\ldots, c_n$ and degrees given by the $x$ coordinates of the corresponding primitives.
+This reduces the problem at hand to finding the primitives of the cone in $\mathbb{Z}\times \mathbb{Z}$ with $x$ and $y$ coordinates,
+bounded by the lines $y=0$ and $y=\frac{\alpha}{\beta}x$.
+
+Cohn's geometric interpretation of Hirzebruch--Jung fractions, as described in 
+\cite{popescuP:the-geometry-of-continued-fractions-and-the-topology-of-surface-singularities} 
+yields an explicit formula for these primitives, as given in \cite[Proposition 4.3]{popescuP:the-geometry-of-continued-fractions-and-the-topology-of-surface-singularities}.
+All primitives lie in degrees at most $\beta$
+(since points in degree $\gamma=\beta+\omega$ can be written as a sum of points
+in degree $\beta$ with those in degree $\omega$).  Note that if two primitives
+had the same $y$ coordinate, then they would differ by a multiple of $(1,0)$
+and thus could not both be generators. So, all the $c_i$'s (the $y$-coordinates
+of the primitives) are distinct, and we may assume $c_i<c_{i+1}$ for
+all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be
+at most one new primitive,
+\todo{Aaron: What does ``new'' primitive mean? Does it mean the same thing as ``at most one primitive''
+without the word new?}
+since we can construct points with $y$ coordinates
+between 0 and $\lfloor k\frac{\alpha}{\beta}\rfloor$ as a sum of elements in
+degree 1 and degree $k-1$, and these new primitives have pole order greater
+than all primitives of smaller $x$-coordinate.  Therefore, the ordering of
+primitives with $c_i<c_{i+1}$ for all $i$ also ensures that the $x$-values
+$k_i$ are in weakly increasing order.  Finally, let $y_1, \ldots, y_n$
+be elements of $R_Lx$
+\todo{Aaron: What is $R_Lx$? Should this just be $R_L$?}
+with pole orders given by $c_1,\ldots, c_n$ and degrees
+given by the $x$ coordinates of the corresponding primitives.
 %We will the use positive best lower approximations to
@@
 \]
-and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
+and for each $i \in \BN$, suppose $c_j$ is the maximal element of $c_1, \ldots, c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
 \[

### 2016-01-12 curves-write-up/AIF/changes-summary.tex
edited changes-summary adding in difference for hilbert polynomials

@@
 for $L$ a fractional divisor, so this would not pose an issue.
-	\item Use Hilbert polynomial in Example $\_\_\_$
-	\item Replace ``best lower approximation'' with Hirzebruch--Jung
+	\item We included Hilbert polynomial in Examples $3.2- 3.5$.
+	\item We replaced ``best lower approximation'' with Hirzebruch--Jung
 		fractions
@@
 The referee also made the following suggestions.
-
+\todo{Aaron: Since there's only one thing here, can we remove this enumerate?
+Alternatively, if we do end up including more than one of these, can we give the suggestion
+and response together, instead of listing all the suggestions and then all the responses?}
 \begin{enumerate}

### 2016-01-13 curves-write-up/AIF/changes-summary.tex
added in references to zhou's thesis

--- 2015-11-28 curves-write-up/AIF/changes-summary.tex
@@
 for $L$ a fractional divisor, so this would not pose an issue.
-	\item Use Hilbert polynomial in Example $\_\_\_$
-	\item Replace ``best lower approximation'' with Hirzebruch--Jung
-		fractions
-	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
-		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
-		we range over all $e'_i$ instead of odd $e_i$.
+	\item We included Hilbert polynomial in Examples $3.2- 3.5$.
+	\item We included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
+		and $-2 \bmod r_i$ near the end of subsection 2.1.
+	\item We replaced ``best lower approximation'' with Hirzebruch--Jung
+		fractions. This not only allowed us to delete the unnecessary, nonstandard definition
+		of ``best lower approximation,''
+		but also allowed us to shorten and
+		clarify our proof of the rather
+		technical Lemma 4.4 (which was
+		Lemma 4.6 in the previous version).
+\end{enumerate}
+
+\section{Other suggestions}
+The referee also made the following notational suggestions,
+and here we include reasons we would prefer not to implement.
+
+\begin{enumerate}
+	\item One suggestion was to change the notation from $\frac{e_i - 1}{2 e_i}$
+		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
+		First, we would like to keep our notation because we often
+	list degrees of generation and relations by signatures
+	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
+	the form $\min(5, e_1, \ldots, e_n)$. These
+	seem simpler to
+	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
+	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
+	2s_n + 1)$. Second, because we will be using $e_i$
+	so frequently in our analysis, the paper is shortened
+	by writing $e_i$ instead of $2s_i+1$.
+	Third, we maintained the $e_i$ notation for consistency
+	with the notation established in Voight--Zureick-Brown.
+	Fourth, since one of our main applications is to modular forms,
+	the number theorists reading it may have an easier time translating
+	to modular curves whose signature is written with $e_i$ rather than $s_i$.
+	\item One suggestion was to use orbifold terminology instead
+		of stacky terminology. Since this paper is in many
+		ways intimately tied with Voight--Zureick-Brown,
+		we would like to keep the use of stacky terminology
+		in order to remain compatible with that paper.
+	\item One suggestion was to remove the signature invariant
+		and use the more general terminology from the
+		Ice cream paper. We agree that it is
+		somewhat difficult to generalize the
+		signature terminology,
+		and we also note that this signature is commonly used in referring
+		to modular curves. Since one of the important
+		applications of this paper is to rings of modular
+		forms, the signature will play a useful role for
+		those interested in the translation to modular curves.
+		Once again, we would also like to keep the signature
+		to remain compatible with Voight--Zureick-Brown.
 \end{enumerate}

### 2016-01-13 curves-write-up/spin-cring.tex
added in references to zhou's thesis

@@
 \begin{rem}
+	Except in degenerate cases,
+	such as when the signature is $(0;3,3,3;0)$
+	as covered in the first line of Table ~\ref{table:g-0-exceptional},
+	we have the following important restriction on the generators
+	of $R_L$. For each $e_i$ in the signature of $\sx$, there
+	will be at least one generator
+	with degree $0 \bmod e_i$ and at least one generator
+	with degree $-2 \bmod e_i$.
+	Although this is an important restriction on the genertors,
+	we will not use this in the remainder of the paper.
+\end{rem}
+
+\begin{rem}
 \label{rem:delta-not-1}
@@
 
-\todo{Use Hilbert polynomial in an example}
-
 In this section, we work out several examples of computing presentations for spin canonical rings.
@@
 \end{example}
+
+\begin{rem}
+	\label{remark:hilbert-series}
+	In the following examples, in order to find the Hilbert series of
+	a stacky curve, we will cite
+	\cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}.
+	Note that
+	\cite[Theorem 3.1]{buckleyRZ:ice-cream-orbifold-and-riemann-roch},
+	restates \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
+	with the restriction that the dimension of the orbifold (which is the same
+	as a stacky curve in dimension 1, by \cite[Proposition 6.1.5]{vzb:stacky},)	
+	is strictly more than 1.
+	This restriction is made because in birational geometry orbifolds
+	usually refer to a normal variety ramified only in codimension at least 2,
+	while the stacky points we are dealing with appear in codimension 1.
+\end{rem}
 
@@
 additional relations. 
-One method would be to use \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch}
+One method would be to use \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
 to write down the Hilbert series and then check this agrees with the
@@
 
-First, by \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch},
-\todo{in theorem 3.1, it states n is at least 2, what is going on?}
+First, by \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series},
 the Hilbert series of this log spin curve is
@@
 $R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first 
-write down the Hilbert series of $(R_{\halfcan'})_n$ over $\Bk$ using \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch}, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
+write down the Hilbert series of $(R_{\halfcan'})_n$ over $\Bk$ using \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series},
+ then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order.
 The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
@@
 
-In order to show this is an isomorphism, one can write down the Hilbert series using \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch} and then use pole order considerations at $P_1$ to check the above relation exists.
+In order to show this is an isomorphism, one can write down the Hilbert series using \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
+ and then use pole order considerations at $P_1$ to check the above relation exists.
 One can then check that the generators and relation determine a ring with the desired Hilbert series.
@@
 maximal degrees of minimal generators and relations of spin
-canonical rings in high genera. The first author would also like to
+canonical rings in high genera.
+We thank Miles Reid for clarifying how to
+find the Hilbert series of stacky curves.
+The first author would also like to
 mention Joseph Harris and Evan O'Dorney for several enlightening

### 2016-01-13 curves-write-up/AIF/changes-summary.tex
changed bibliography style and minor further edits

@@
 for $L$ a fractional divisor, so this would not pose an issue.
-	\item We included Hilbert polynomial in Examples $3.2- 3.5$.
+	\item We included Hilbert polynomial in Examples $3.3- 3.6$.
+		Throughout we reference Theorem 4.2.1 of Zhou's thesis,
+		but also include remark 3.2 explaining that we could also use
+		Theorem 3.1 of Buckley, Reid, and Zhou's paper.
 	\item We included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
@@
 The referee also made the following notational suggestions,
-and here we include reasons we would prefer not to implement.
+and here we include reasons we would prefer not to implement them.
 

### 2016-01-18 curves-write-up/spin-cring.tex

@@
 	Note that
-	\cite[Theorem 3.1]{buckleyRZ:ice-cream-orbifold-and-riemann-roch},
+	\cite[Theorem 3.1]{buckleyRZ:ice-cream-orbifold-and-riemann-roch}
 	restates \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
@@
 \bibliography{bibliography}{}
-\bibliographystyle{plain}
+\bibliographystyle{alpha}
 

### 2016-01-18 curves-write-up/spin-cring.tex
fixed todos

@@
 
-\sssec*{Idea of proof:}\todo{Update subsection}
-The proof will be fairly involved. To show part (a), we 
+\sssec*{Idea of proof:}
+The proof will be fairly involved. To show part (a), we use Riemann-Roch to reduce the
+problem to one of finding primitives of cones; we then apply previous work on continued fractions to deduce these primitives.
+We conclude this part of the problem, showing by dimension count, that these primitives induce all the generators of $R_L$ over $R_L$'.
+
 first define a set of generators of $R_\halfcan$ over $R_{\halfcan'}$. 
@@
 all $i$.  Furthermore, note that in any degree $k$ greater than 1, there can be
-at most one new primitive,
-\todo{Aaron: What does ``new'' primitive mean? Does it mean the same thing as ``at most one primitive''
-without the word new?}
+at most one primitive,
 since we can construct points with $y$ coordinates
@@
 $k_i$ are in weakly increasing order.  Finally, let $y_1, \ldots, y_n$
-be elements of $R_Lx$
-\todo{Aaron: What is $R_Lx$? Should this just be $R_L$?}
+be elements of $R_L$
 with pole orders given by $c_1,\ldots, c_n$ and degrees
@@
 Then, there is some $h \in \BN$ such that $i \le h \le \max(i, l)$ satisfying $\prod_{j = 1}^h y_j^{b_j}\not\in S\cup S_0$, 
-and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S \cup S_0$. \todo{Check whether all these $S$ need to be changed to $S\cup S_0$ like here.}   
+and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S \cup S_0$.  
 Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
@@
 
-Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that $\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for some $l$.
-Then, for all $r< h$ we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have $\prod_{j=1}^r {y_j}^{\omega_j}\in S$.
-Furthermore, since $(\gamma_1, \ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.
+Next, suppose we choose $\omega_1, \ldots, \omega_h$ such that
+$\omega_j\le \gamma_j$ for all $j$ and $\omega_l \le \gamma_l$ for
+some $l$.  Then, for all $r< h$ we have $\prod_{j=1}^r
+{y_j}^{\gamma_j}\in S$, implying that for all $r< h$ we also have
+$\prod_{j=1}^r {y_j}^{\omega_j}\in S$.  Furthermore, since $(\gamma_1,
+\ldots, \gamma_h)$ was chosen to be minimal to satisfy the previous
+condition and that $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S\cup S_0$, we have $\prod_{j=1}^h {y_j}^{\omega_j}\in S$.
 Therefore, $c_h$ is minimal among $c_1, \ldots c_n$ that is not greater than $\sum_{j=1}^h c_j \omega_j$, so in particular $\sum_{j=1}^h c_j\omega_j < c_{h+1}$; therefore, $\prod_{j=1}^h {y_j}^{\gamma_j}$ satisfies condition \ref{custom:sat-1-**}.

### 2016-01-18 curves-write-up/spin-cring.tex
deleted up commented out code
did spell check

@@
 	with degree $-2 \bmod e_i$.
-	Although this is an important restriction on the genertors,
+	Although this is an important restriction on the generators,
 	we will not use this in the remainder of the paper.
@@
 	is strictly more than 1.
-	This restriction is made because in birational geometry orbifolds
+	The statement holds equally well when the dimension is $1$,
+	but this restriction is included in
+	\cite[Theorem 3.1]{buckleyRZ:ice-cream-orbifold-and-riemann-roch}
+	because in birational geometry ``orbifolds''
 	usually refer to a normal variety ramified only in codimension at least 2,
@@
 also extends to curves of genus $g > 0$. 
-%Before stating Lemma
-%~\ref{lem:sat-1}, we recall some theory from continued fractions.
-
-%\begin{defn}
-%\label{defn:lower-approximation}
-%If $\alpha \in \BR$, then a rational number $\frac{c}{k} \leq \alpha
-%$ (written in reduced form with $c \in \BZ, k \in \BN$) is a
-%\textbf{best lower approximation} to $\alpha$ if there does not
-%exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
-%$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
-%\end{defn}
-
-%\begin{rem}
-%\label{rem:lower-approximation}
-%Note that all integers less than or equal to $\lfloor \alpha \rfloor$
-%are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
-%then the non-negative best lower approximations of
-%$\alpha$ form a finite sequence
-%\[
-%	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \%alpha.
-%\]
-%
-% proves 
-%\begin{defn}\label{defn:cont-fract}
-%Let $[a_1, \ldots, a_n]$ be the (Hirzebruch-Jung) continued fraction
-%on $a_1, \ldots, a_n$ (given by $1 + \frac{1}{a_1+\frac{1}{... + \frac{1}{a_n}}}$).
-%\end{defn}
-%\begin{prop}\label{prop:primitives}
-%The primitives 
-%\end{prop}
-
-%\noindent
-%Figure \ref{fig:s14/5-lattice} gives a pictorial representation of the posi%tive best lower approximations of $\alpha = \frac{14}{5}$.
-%\end{rem}
-
-%\begin{figure}
-%\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-%\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.
-Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
-%\end{figure}
-%\todo{Is this figure (figure 1)  still useful anywhere?}
-
 We next prove the first of three lemmas used to inductively add points.
@@
 \end{align}
-%Let
-%\[
-%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{\beta}
-%\]
-%be the positive best lower approximations of $\frac{\alpha}{\beta}$
-%{\rm(}similar to Remark ~\ref{rem:lower-approximation}{\rm)}.
 Then,
@@
 problem to one of finding primitives of cones; we then apply previous work on continued fractions to deduce these primitives.
-We conclude this part of the problem, showing by dimension count, that these primitives induce all the generators of $R_L$ over $R_L$'.
+To conclude this part of the problem, we show by dimension count that these primitives induce all the generators of $R_L$ over $R_L$'.
 
@@
 given by the $x$ coordinates of the corresponding primitives.
-%We will the use positive best lower approximations to
-%construct the generators $y_1, \ldots, y_n$ as described in the lemma's statement.
-%
-%Let 
-%\[
-%	0 < \frac{c_1}{k_1} < \ldots < \frac{c_n}{k_n} = \frac{\alpha}{
-%	\beta}
-%\]
-%
-%\noindent
-%be the positive best lower approximations of $\frac{\alpha}{\beta}$. 
-%5Choose a positive best lower approximation $\frac{c_i}{k_i}$.
-Choose $z_1, \ldots, z_r \in R_\halfcan$ so that $\sum_{j=1}^r \deg(z_j) = k_i$ and $\deg(z_j)<k_i$ for all $j\in \{1, \ldots r\}$.
-Observe that $\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)}< \frac{\alpha}{\beta}$, for each $j$.
-Hence, for each $j$,
-%\[
-%	\frac{-\ord_P^{\halfcan'}(z_j)}{\deg(z_j)} < \frac{c_i}{k_i},
-%\]
-%so the mediant inequality tells us
-%\[
-%	\frac{\sum_{j=1}^n -\ord^{\halfcan'}_P(z_j)}{\sum_{j=1}^n z_j } < \frac{c_i}{k_i}.
-%\]
-%Multiplying through by $k_i$ gives
-%\[
-%	-\ord^{\halfcan'}_P \left(\prod_{j=1}^n z_j \right) = \sum_{j=1}^n -\%ord^{\halfcan'}_P(z_j) < c_i .
-%\]
-
-%\noindent
-%Thus, the elements of $(R_{\halfcan})_{k_i}$ with pole order $c_i$ at $P$ are not generated by 
-%lower degrees. 
-%Choose some $y_i \in(R_{
-%\halfcan})_{k_i}$ with $-\ord_{P}^{L'}(y_i)=c_i$.
-%
-%Suppose $c,k \in \BN$ so that $k \le \beta$,  $\frac{c}{k} < \frac{\alpha}{
-%\beta},$ and $\frac{c}{k}$ is not a best lower approximation of $\frac{\alpha}{\beta}$. Choose a
-%best lower approximation $\frac{c_i}{k_i}$ with $c_i$ maximal such that $k_i< k$.  This implies $\frac{c_i}{k_i}\ge \frac{c}{k},$ so
-%\[
-%	\frac{c-c_i}{k-k_i}\le \frac{\alpha}{\beta}
-%\]
-%
-%\noindent
-%which implies
-%\begin{equation}\label{eqn:c-from-lower-terms}
-%	c_i +\left\lfloor (k-k_i) \frac{\alpha}{\beta} \right\rfloor \ge c.
-%\end{equation}
 

### 2016-01-18 curves-write-up/AIF/changes-summary.tex
slight edit to changes re referee's comment

@@
 	the definition of a log spin canonical ring in the background section.
-	We noticed in comment 1 that the referee made a comment saying
+	We noticed that the referee made a comment saying
 	``Cohen-Macaulay and

### 2016-01-25 curves-write-up/AIF/changes-summary.tex
added david's comments to AIF referee report and paper

@@
 \begin{enumerate}
-	\item We added a remark on Gorensteinness of the log canonical ring following
+	\item In response to referee comment (1), we added Remark 2.6 on Gorensteinness of the log canonical ring following
 	the definition of a log spin canonical ring in the background section.
@@
 for $L$ a fractional divisor, so this would not pose an issue.
-	\item We included Hilbert polynomial in Examples $3.3- 3.6$.
+	\item In response to referee comment (2), we included Hilbert polynomials in Examples $3.3- 3.6$.
 		Throughout we reference Theorem 4.2.1 of Zhou's thesis,
@@
 		Theorem 3.1 of Buckley, Reid, and Zhou's paper.
-	\item We included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
+	\item In response to referee comment (3), we included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
 		and $-2 \bmod r_i$ near the end of subsection 2.1.
-	\item We replaced ``best lower approximation'' with Hirzebruch--Jung
+	\item In response to referee comment (4), we replaced ``best lower approximation'' with Hirzebruch--Jung
 		fractions. This not only allowed us to delete the unnecessary, nonstandard definition
@@
 \begin{enumerate}
-	\item One suggestion was to change the notation from $\frac{e_i - 1}{2 e_i}$
+	\item Toward the end of referee comment (1), the referee suggests
+		to change the notation from $\frac{e_i - 1}{2 e_i}$
 		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
@@
 	to modular curves whose signature is written with $e_i$ rather than $s_i$.
-	\item One suggestion was to use orbifold terminology instead
-		of stacky terminology. Since this paper is in many
+	\item Prior to referee comment (1), the referee suggests we use orbifold terminology instead
+		of stacky terminology. 
+		One reason we'd like to keep stacky terminology is
+		that the results of this paper hold over a finite field,
+		and in the context of finite fields, it seems more natural to work with
+		stacks rather than orbifolds.
+		Also, since this paper is in many
 		ways intimately tied with Voight--Zureick-Brown,
@@
 		in order to remain compatible with that paper.
-	\item One suggestion was to remove the signature invariant
+	\item Prior to referee comment (1), the referee suggests to remove the signature invariant
 		and use the more general terminology from the

### 2016-01-25 curves-write-up/spin-cring.tex
added david's comments to AIF referee report and paper

@@
 \[
-	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}.
+	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
 \]
@@
 Let $(\sx',0 , \halfcan')$ be a log spin curve of genus $1$ with $\halfcan' = P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$. In this example, we show that
-$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u)$$.
+$$R_{\halfcan'} \cong \Bk[u, x_3, y_3, y_4]/(x_3 y_3- \alpha uy_4, y_4^2 - \beta x_3^2 u - \gamma y_3^2u).$$
 
@@
 \ref{eg:exception-1-5} are used as inductive base cases in the
-genus 0, genus 1, and genus 1 sections respectively (see Tables
+genus 0 and genus 1 sections (see Tables
 ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
@@
 \label{lem:sat-1}
-Let $X$ be a genus $g$ curve and $\halfcan' \in \BQ \otimes \di X$
-satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
+Let $X$ be a genus $g$ curve and let $\halfcan' \in \BQ \otimes \di X$
+satisfy $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$.
 Suppose $P$ is not a base-point of $k\halfcan'$ for all $k \in \BN$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\tau$ for some $\tau\in \BN$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.

### 2016-01-27 curves-write-up/AIF/changes-summary.tex
changes: minor grammatical edits

@@
 The referee also made the following notational suggestions,
-and here we include reasons we would prefer not to implement them.
+and here we include reasons for why we would prefer not to
+implement them.
 
@@
 	Fourth, since one of our main applications is to modular forms,
-	the number theorists reading it may have an easier time translating
-	to modular curves whose signature is written with $e_i$ rather than $s_i$.
-	\item Prior to referee comment (1), the referee suggests we use orbifold terminology instead
+	number theorists reading the paper may have an easier time
+	translating the work to the context of modular curves whose 
+	signatures are written with $e_i$ rather than $s_i$.
+	\item Prior to referee comment (1), the referee suggests we use 
+orbifold terminology instead
 		of stacky terminology. 
@@
 		that the results of this paper hold over a finite field,
-		and in the context of finite fields, it seems more natural to work with
-		stacks rather than orbifolds.
+		and it seems more natural to 
+work with	stacks rather than orbifolds in the context of finite fields.
 		Also, since this paper is in many
@@
 		in order to remain compatible with that paper.
-	\item Prior to referee comment (1), the referee suggests to remove the signature invariant
+	\item Prior to referee comment (1), the referee suggests to 
+remove the signature invariant
 		and use the more general terminology from the
@@
 		signature terminology,
-		and we also note that this signature is commonly used in referring
+		and we also note that this signature is commonly used in 
+referring
 		to modular curves. Since one of the important

### 2016-01-27 curves-write-up/AIF/changes-summary.tex
changes: even more minor grammatical changes

@@
 		and use the more general terminology from the
-		Ice cream paper. We agree that it is
+		``ice cream paper''. We agree that it is
 		somewhat difficult to generalize the
-		signature terminology,
-		and we also note that this signature is commonly used in 
-referring
+		signature terminology, but we also note that this signature is
+		commonly used in referring
 		to modular curves. Since one of the important

### 2016-02-23 curves-write-up/AIF/spin-cring-AIF.tex
add AIF style version of paper

--- 2016-01-25 curves-write-up/spin-cring.tex
@@
 %%%%%%%%%%%%%%%%%%%%%
-\documentclass{amsart}
+\documentclass[AmsartStyle]{cedram-aif}
 
@@
 
-\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
-\def\listtodoname{List of Todos}
-\def\listoftodos{\@starttoc{tdo}\listtodoname}
-
-\RequirePackage{color}
-\definecolor{myred}{rgb}{0.75,0,0}
-\definecolor{mygreen}{rgb}{0,0.5,0}
-\definecolor{myblue}{rgb}{0,0,0.65}
+%\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
+%\def\listtodoname{List of Todos}
+%\def\listoftodos{\@starttoc{tdo}\listtodoname}
+%
+%\RequirePackage{color}
+%\definecolor{myred}{rgb}{0.75,0,0}
+%\definecolor{mygreen}{rgb}{0,0.5,0}
+%\definecolor{myblue}{rgb}{0,0,0.65}
 
@@
 \theoremstyle{plain}
-  \newtheorem{thm}{Theorem}[section]
-  \newtheorem{prop}[thm]{Proposition}
-  \newtheorem{lem}[thm]{Lemma}
-  \newtheorem{cor}[thm]{Corollary}
-	\newtheorem{question}[thm]{Question}
+  %\newtheorem{thm}{Theorem}[section]
+  %\newtheorem{prop}{Proposition}
+  \newtheorem{lem}{Lemma}
+  \newtheorem{cor}{Corollary}
+	\newtheorem{question}{Question}
 
 \theoremstyle{definition}
-  \newtheorem{defn}[thm]{Definition}
-  \newtheorem{example}[thm]{Example}
+  \newtheorem{defn}{Definition}
+  \newtheorem{example}{Example}
 
 \theoremstyle{remark}
-	\newtheorem{rem}[thm]{Remark}
+	\newtheorem{rem}{Remark}
 
@@
 \DeclareMathOperator{\Supp}{Supp}
-\DeclareMathOperator{\initial}{in_\prec}
+\DeclareMathOperator{\Initial}{in_\prec}
 \DeclareMathOperator{\Eff}{Eff}
@@
 and let $f \in \Bk[x_{1}, \ldots, x_{n}]$ be a homogeneous
-polynomial. The \textbf{initial term} $\initial(f)$ of $f$
+polynomial. The \textbf{initial term} $\Initial(f)$ of $f$
 is the largest monomial in the support of $f$ with respect to
-the ordering $\prec$. Furthermore, we set $\initial(0) := 0$.
+the ordering $\prec$. Furthermore, we set $\Initial(0) := 0$.
 \end{defn}
@@
 Let $I$ be a homogeneous ideal of $\Bk[x_{1}$, $\ldots$,
-$x_{n}]$. Then the {\bf initial ideal} $\initial(I)$ of $I$ is
+$x_{n}]$. Then the {\bf initial ideal} $\Initial(I)$ of $I$ is
 the ideal generated by the initial terms of homogeneous polynomials
@@
 \[
-	\initial(I) := \langle \initial(f) \rangle_{f \in I}
+	\Initial(I) := \langle \Initial(f) \rangle_{f \in I}
 \]
@@
 \[
-	\initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
+	\Initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
 \]
@@
 \Bk[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
-initial ideal $\initial(I)$ generated by quadratics under grevlex
+initial ideal $\Initial(I)$ generated by quadratics under grevlex
 with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
@@
 \begin{align*}
-	S \; \cup\; \langle T\rangle \; \cup \; \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[x_1, \ldots, x_m]
+	S \; \cup\; \langle T\rangle \; \cup \; \Initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[x_1, \ldots, x_m]
 \end{align*}
@@
 \begin{align*}
-	\initial(I) & = \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]
+	\Initial(I) & = \Initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]
 	+ \langle T \rangle.
@@
 
-\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
-We deduce $\subseteq$ by noting that we can reduce any monomial in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ to a monomial in the basis $S$ via a set of relations whose initial terms include each monomial in $\initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle$.
+\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \Initial(I)$, which follows immediately from $(1)$ and $(2)$.
+We deduce $\subseteq$ by noting that we can reduce any monomial in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ to a monomial in the basis $S$ via a set of relations whose initial terms include each monomial in $\Initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle$.
 
@@
 \[
-	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
+	\Initial(I)\supseteq \Initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
 \]
@@
 Since $S$ forms a $\Bk$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$ by (1), we can write a relation $f - (\sum_{g\in S'} C_g g)-r=0$ for some finite subset $S'\subseteq S_{\deg(f)}$, $C_g\in \Bk$ for all $g\in S'$, and $r\in R_{\halfcan'}$.
-This demonstrates that $\initial(I) \supseteq T$, and hence
+This demonstrates that $\Initial(I) \supseteq T$, and hence
 \[
-	\initial(I)\supseteq \initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
+	\Initial(I)\supseteq \Initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].
 \]
@@
 To complete the proof, it suffices to show the reverse inclusion holds.
-By (2), any polynomial $G\in \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\initial(\phi(G)) \in S$ cannot have a term in $T$.
-Furthermore, since $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \initial(I)$.
+By (2), any polynomial $G\in \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ with $\Initial(\phi(G)) \in S$ cannot have a term in $T$.
+Furthermore, since $S$ forms a $\Bk$-basis for $R_\halfcan$ over $R_{\halfcan'}$ by (1), and $\Initial(\phi(G)) \in S,$ we obtain $\phi(G) \notin R_{\halfcan'} \subseteq R_\halfcan.$ Thus, $G=0$ is not a relation, so $f\not\in \Initial(I)$.
 Therefore,
 \[
-	\initial(I)\subseteq R_\halfcan-S.
+	\Initial(I)\subseteq R_\halfcan-S.
 \]
@@
 \[
-	\initial(I) \cap \Bk[x_1, \ldots, x_m] = \initial(I').
+	\Initial(I) \cap \Bk[x_1, \ldots, x_m] = \Initial(I').
 \]
 
-By (3), every monomial of $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
-\begin{align*}
-	\initial(I) & \subseteq \initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
+By (3), every monomial of $\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\Initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n].$ Therefore,
+\begin{align*}
+	\Initial(I) & \subseteq \Initial(I') \Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle.
 \end{align*}
@@
 	\begin{align*}
-		\initial(I) &= \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
+		\Initial(I) &= \Initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] 
 											 + \langle U_i: 1 \le i \le n-1 \rangle
@@
 				& \Bk[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
-	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[u, x_1, \ldots, x_m].
+	\subseteq \; 	& S \cup \langle T\rangle \cup \Initial(I') \Bk[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; \Bk[u, x_1, \ldots, x_m].
 \end{align*}
@@
 		\begin{align*}
-			\initial(I) &= \initial(I')\Bk[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
+			\Initial(I) &= \Initial(I')\Bk[x, y_3, y_4]+\langle y_4 x_j \mid 2 \leq j \leq m \rangle +\langle y_4^2 \rangle.
 		\end{align*}
@@
 		\begin{align*}
-			\initial(I) &= \initial(I) \Bk[y_3, y_4, y_5, x_3, \ldots, x_m] \\
+			\Initial(I) &= \Initial(I) \Bk[y_3, y_4, y_5, x_3, \ldots, x_m] \\
 			&+ \langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
@@
 \begin{figure}[H]
-\includegraphics{pics/spin-377-pic-pics.pdf} \\
+\includegraphics{spin-377-pic-pics.pdf} \\
 \caption{Generators in the $(\deg z, -ord_{P_2}(z))$ lattice}
@@
 		\begin{align*}
-			\initial(I) \;	&= \; \initial(I')\Bk[x, y] \\
+			\Initial(I) \;	&= \; \Initial(I')\Bk[x, y] \\
 					&+ \; \langle y_{j, e_j}x_i  : 1\le i \le m, j\in J\rangle \\
@@
 We can also always find a presentation for these cases such that
-they satisfy \ref{custom:Ad-i} and \ref{custom:Ad-ii} and that $\initial(I')$ is
+they satisfy \ref{custom:Ad-i} and \ref{custom:Ad-ii} and that $\Initial(I')$ is
 generated by products of two monomials. Again, the procedure to

### 2016-02-23 curves-write-up/AIF/spin-cring-metadata.tex
curves: first french translations

--- 2016-01-25 curves-write-up/AIF/changes-summary.tex
@@
 
-\title{Summary of Changes in response to Referee's Report}
+\title{Metadata for ``Spin canonical rings of log stacky curves''}
 \author{Aaron Landesman, Peter Ruhm, and Robin Zhang}
@@
 \maketitle
-\section{Changes Made}
-Here are the changes we have made in response to the referee's suggestions.
 
 \begin{enumerate}
-	\item In response to referee comment (1), we added Remark 2.6 on Gorensteinness of the log canonical ring following
-	the definition of a log spin canonical ring in the background section.
-	We noticed that the referee made a comment saying
-	``Cohen-Macaulay and
-projectively Gorenstein follows as usual (of course, provided there are
-no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
-it to mean that the canonical ring may not be Gorenstein if it is of the form
-\begin{align*}
-	\oplus_n H^0(X, P + n L)
-\end{align*}
-for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
-\begin{align*}
-	\oplus_n H^0(X, n L)
-\end{align*}
-for $L$ a fractional divisor, so this would not pose an issue.
-	\item In response to referee comment (2), we included Hilbert polynomials in Examples $3.3- 3.6$.
-		Throughout we reference Theorem 4.2.1 of Zhou's thesis,
-		but also include remark 3.2 explaining that we could also use
-		Theorem 3.1 of Buckley, Reid, and Zhou's paper.
-	\item In response to referee comment (3), we included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
-		and $-2 \bmod r_i$ near the end of subsection 2.1.
-	\item In response to referee comment (4), we replaced ``best lower approximation'' with Hirzebruch--Jung
-		fractions. This not only allowed us to delete the unnecessary, nonstandard definition
-		of ``best lower approximation,''
-		but also allowed us to shorten and
-		clarify our proof of the rather
-		technical Lemma 4.4 (which was
-		Lemma 4.6 in the previous version).
-\end{enumerate}
-
-\section{Other suggestions}
-The referee also made the following notational suggestions,
-and here we include reasons we would prefer not to implement them.
-
-\begin{enumerate}
-	\item Toward the end of referee comment (1), the referee suggests
-		to change the notation from $\frac{e_i - 1}{2 e_i}$
-		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
-		First, we would like to keep our notation because we often
-	list degrees of generation and relations by signatures
-	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
-	the form $\min(5, e_1, \ldots, e_n)$. These
-	seem simpler to
-	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
-	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
-	2s_n + 1)$. Second, because we will be using $e_i$
-	so frequently in our analysis, the paper is shortened
-	by writing $e_i$ instead of $2s_i+1$.
-	Third, we maintained the $e_i$ notation for consistency
-	with the notation established in Voight--Zureick-Brown.
-	Fourth, since one of our main applications is to modular forms,
-	the number theorists reading it may have an easier time translating
-	to modular curves whose signature is written with $e_i$ rather than $s_i$.
-	\item Prior to referee comment (1), the referee suggests we use orbifold terminology instead
-		of stacky terminology. 
-		One reason we'd like to keep stacky terminology is
-		that the results of this paper hold over a finite field,
-		and in the context of finite fields, it seems more natural to work with
-		stacks rather than orbifolds.
-		Also, since this paper is in many
-		ways intimately tied with Voight--Zureick-Brown,
-		we would like to keep the use of stacky terminology
-		in order to remain compatible with that paper.
-	\item Prior to referee comment (1), the referee suggests to remove the signature invariant
-		and use the more general terminology from the
-		Ice cream paper. We agree that it is
-		somewhat difficult to generalize the
-		signature terminology,
-		and we also note that this signature is commonly used in referring
-		to modular curves. Since one of the important
-		applications of this paper is to rings of modular
-		forms, the signature will play a useful role for
-		those interested in the translation to modular curves.
-		Once again, we would also like to keep the signature
-		to remain compatible with Voight--Zureick-Brown.
+	\item Title (English): Spin canonical rings of log stacky curves \\
+		Titre (Fran\c{c}ais): Anneaux log-canoniques de spin des
+		courbes de champs alg\'{e}briques
+	\item Abstract (English): Consider modular forms arising from a
+		finite-area quotient of the upper-half plane by a Fuchsian group.
+		By the classical results of Kodaira--Spencer, this ring of
+		modular forms may be viewed as the log spin canonical ring of a
+		stacky curve. In this paper, we tightly bound the degrees of
+		minimal generators and relations of log spin canonical rings.
+		As a 	consequence, we obtain a tight bound on the degrees of
+		minimal generators and relations for rings of modular forms of
+		arbitrary integral weight. \\
+		Abstrait (Fran\c{c}ais): Consid\'{e}rez formes modulaires
+		d\'{e}coulant d'une quotient d'aire-finie du demi-plan
+		sup\'{e}rieur par un groupe fuchsien. Par les r\'{e}sultats
+		classiques de Kodaira--Spencer, cet anneau de formes modulaires
+		peut \^{e}tre consid\'{e}r\'{e} comme l'anneau log-canonique de
+		spin d'un courbe de champs alg\'{e}briques. Dans cet article, nous
+		lions \'{e}troitement les degr\'{e}s de g\'{e}n\'{e}rateurs
+		minimaux et les relations minimes de l'anneau log-canonique de spin
+		d'un courbe de champs alg\'{e}briques. Par conséquent, on obtient
+		un virage serr\'{e} li\'{e} sur les degr\'{e}s de
+		g\'{e}n\'{e}rateurs minimaux et relations minimes pour les anneaux
+		de formes modulaires de poids arbitraires int\'{e}grantes.
   \end{enumerate}

### 2016-02-24 curves-write-up/AIF/spin-cring-metadata.tex
curves: add remaining metadata

@@
 		de formes modulaires de poids arbitraires int\'{e}grantes.
+	\item Running title (English): Spin canonical rings of log stacky
+		curves \\
+		Titre courant (Fran\c{c}ais): Anneaux log-canoniques de spin des
+		courbes de champs alg\'{e}briques
+	\item Keywords (English): Modular forms, canonical rings, theta
+		characteristic, Petri's theorem, stacks, Groebner basis \\
+		Mots-cl\'{e}s (Fran\c{c}ais): Formes modulaires, anneaux canoniques,
+		th\^{e}ta-caract\'{e}ristiques, th\'{e}or\`{e}me de P\'{e}tri,
+		champs alg\'{e}briques, base de Gr\"{o}bner
+	\item Mathematics Subject Classification (MSC): 14Q05, 11F11
   \end{enumerate}

### 2016-03-07 curves-write-up/AIF/spin-cring-metadata.tex
curves: metadata & arXiv update

@@
 		Titre (Fran\c{c}ais): Anneaux log-canoniques de spin des
-		courbes de champs alg\'{e}briques
+		courbes champ\^{e}tres
 	\item Abstract (English): Consider modular forms arising from a
@@
 		peut \^{e}tre consid\'{e}r\'{e} comme l'anneau log-canonique de
-		spin d'un courbe de champs alg\'{e}briques. Dans cet article, nous
+		spin d'un courbe champ\^{e}tre. Dans cet article, nous
 		lions \'{e}troitement les degr\'{e}s de g\'{e}n\'{e}rateurs
 		minimaux et les relations minimes de l'anneau log-canonique de spin
-		d'un courbe de champs alg\'{e}briques. Par conséquent, on obtient
+		d'un courbe champ\^{e}tre. Par conséquent, on obtient
 		un virage serr\'{e} li\'{e} sur les degr\'{e}s de
@@
 		Titre courant (Fran\c{c}ais): Anneaux log-canoniques de spin des
-		courbes de champs alg\'{e}briques
+		courbes champ\^{e}tres
 	\item Keywords (English): Modular forms, canonical rings, theta

### 2016-03-11 curves-write-up/AIF/spin-cring-metadata.tex
curves: final metadata update

@@
 	\item Title (English): Spin canonical rings of log stacky curves \\
-		Titre (Fran\c{c}ais): Anneaux log-canoniques de spin des
+		Titre (Fran\c{c}ais): Anneaux log-canoniques \`{a} spin des
 		courbes champ\^{e}tres
@@
 		arbitrary integral weight. \\
-		Abstrait (Fran\c{c}ais): Consid\'{e}rez formes modulaires
-		d\'{e}coulant d'une quotient d'aire-finie du demi-plan
-		sup\'{e}rieur par un groupe fuchsien. Par les r\'{e}sultats
-		classiques de Kodaira--Spencer, cet anneau de formes modulaires
-		peut \^{e}tre consid\'{e}r\'{e} comme l'anneau log-canonique de
-		spin d'un courbe champ\^{e}tre. Dans cet article, nous
-		lions \'{e}troitement les degr\'{e}s de g\'{e}n\'{e}rateurs
-		minimaux et les relations minimes de l'anneau log-canonique de spin
-		d'un courbe champ\^{e}tre. Par conséquent, on obtient
-		un virage serr\'{e} li\'{e} sur les degr\'{e}s de
-		g\'{e}n\'{e}rateurs minimaux et relations minimes pour les anneaux
-		de formes modulaires de poids arbitraires int\'{e}grantes.
+		R\'{e}sum\'{e} (Fran\c{c}ais): Consid\'{e}rons les formes
+		modulaires d'un quotient d'aire finie du demi-plan
+		de Poincar\'{e} par un groupe fuchsien. D'apr\`{e}s un
+		r\'{e}sultat classique de Kodaira--Spencer, cet anneau de
+		formes modulaires	peut \^{e}tre consid\'{e}r\'{e} comme
+		l'anneau log-canonique \`{a} spin d'une courbe champ\^{e}tre.
+		Dans cet article, nous  obtenons une borne optimale pour les
+		degr\'{e}s des g\'{e}n\'{e}rateurs minimaux et des relations
+		minimales d'un tel anneau, et donc des anneaux de formes
+		modulaires de poids entier arbitraire.
 	\item Running title (English): Spin canonical rings of log stacky
 		curves \\
-		Titre courant (Fran\c{c}ais): Anneaux log-canoniques de spin des
+		Titre courant (Fran\c{c}ais): Anneaux log-canoniques \`{a} spin des
 		courbes champ\^{e}tres

### 2016-03-19 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
adding response to MRL referee and fixing many issues

%        File: changes-summary.tex
%     Created: Sat Oct 17 11:00 AM 2015 E
% Last Change: Sat Oct 17 11:00 AM 2015 E
%
%%%%%%%%%%%%%%%%%%%%%
%   AMS packages    %
%%%%%%%%%%%%%%%%%%%%%
\documentclass[10 pt]{amsart}

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{subfiles}
\usepackage{mathpazo}
\usepackage{euler}
\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}

\addtolength{\oddsidemargin}{-.5 in}
\addtolength{\evensidemargin}{-.4 in}
\addtolength{\textwidth}{1 in}
\addtolength{\topmargin}{0 in}
\addtolength{\textheight}{0 in}

\RequirePackage{color}
\definecolor{myred}{rgb}{0.75,0,0}
\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{myblue}{rgb}{0,0,0.65}

\usepackage{hyperref}
\hypersetup{colorlinks=true,citecolor=blue}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{counterexample}[theorem]{Counterexample}
\newtheorem{convention}[theorem]{Convention}
\newtheorem{question}[theorem]{Question}
\newtheorem{conjecture}[theorem]{Conjecture} 
\newtheorem{warning}[theorem]{Warning}
\newtheorem{fact}[theorem]{Fact}
\theoremstyle{remark}
\newtheorem{notation}[theorem]{Notation}
\numberwithin{equation}{section}

\newcommand\nc{\newcommand}
\nc\on{\operatorname}
\nc\renc{\renewcommand}
\newcommand\se{\section}
\newcommand\ssec{\subsection}
\newcommand\sssec{\subsubsection}
\newcommand\bn{{\mathbb N}}
\newcommand\bc{{\mathbb C}}
\newcommand\br{{\mathbb R}}
\newcommand\bq{{\mathbb Q}}
\newcommand\bp{{\mathbb P}}
\newcommand\CF{{\mathcal F}}
\newcommand\bz{{\mathbb Z}}
\newcommand\ba{{\mathbb A}}
\newcommand\fa{{\mathfrak a}}
\newcommand\fp{{\mathfrak p}}
\newcommand\fq{{\mathfrak q}}
\newcommand\fm{{\mathfrak m}}
\newcommand\so{{\mathscr O}}
\newcommand\sg{{\mathscr G}}

\newcommand\scm{{\mathscr M}}
\newcommand\scn{{\mathscr N}}
\newcommand\scf{{\mathscr F}}
\newcommand\scg{{\mathscr G}}
\newcommand\sco{{\mathscr O}}
\newcommand\sch{{\mathscr H}}
\newcommand\scl{{\mathscr L}}
\newcommand\sci{{\mathscr I}}

\newcommand \ra{\rightarrow}
\newcommand{\id}{\mathrm{id}}
\newcommand\im{\text{im }}
\newcommand\coker{\text{coker}}
\newcommand \spec{\text{Spec }}
\newcommand \proj{\text{Proj }}
\newcommand \rspec{\textit{Spec }}
\newcommand \rproj{\textit{Proj }}
\newcommand \mg{{\mathscr M_g}}

\DeclareMathOperator\ord{ord}

\newcommand \trdeg{\text{tr. deg }}
\newcommand \codim{\text{codim}}
\newcommand \rk{\text{rk }}
\newcommand \di{\text{div }}
\newcommand \depth{\text{depth }}
\DeclareMathOperator\pic{Pic}
\DeclareMathOperator\lcm{lcm}
\DeclareMathOperator\rank{rank}
\DeclareMathOperator\vol{Vol}
\DeclareMathOperator\supp{Supp}

\def\listtodoname{List of Todos}
\def\listoftodos{\@starttoc{tdo}\listtodoname}

\title{Summary of Changes in response to Referee's Report}
\author{Aaron Landesman, Peter Ruhm, and Robin Zhang}

\begin{document}

\maketitle
\section{Changes Made}
Here are the changes we have made in response to the referee's suggestions.
\todo{make sure the theorem number here reflect the new numberings}
\begin{enumerate}
	\item \todo{Ask David how the new version sounds} We explained
		in more detail how our potential application
		for Hilbert modular forms and the difficulty in producing
		an explicit example.
	\item \todo{do this} For example, why give in Section 1.1 the main results in a form
The presentation can be improved quite a lot.
that the reader can only understand if he/she first reads later sections. 
\todo{Reorganize the intro so as to introduce notations and conventions first,
since the referee wants this}
	\item In all our main theorems, we now say that $c_i/k_i$ is in reduced form. 
	\item In Thm 1.2,  k is a field. Throughout our paper, the results hold for arbitrary fields, but we may assume the field is algebraically closed because the generator and relation degrees are preserved by base change to the algebraic closure. We have now included and clarified this in the ``Notations and Conventions'' subsection at the end of the Introduction.
	\item In the previous version we submitted, Page 2, line -9, $deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$. This is now fixed.
		\todo{Say where}
	\item \todo{Make Thm. 1.4 readable by including necessary notations
		before it}
	\item Section 2 starts with definitions that should have come earlier. (Was Section
1.1 added in a later stage ?) Page 5, line 7, reference to things that come later.
\item In Thm 2.5 the best lower approximations are not explained. These come later
(page 9 and 10).
\item 
	\todo{I remember seeing something wrong with the bibliography, but can't find it now. Do you know what the referee is talking about?} The bibliography should be updated and misprints corrected.

\end{enumerate}

\end{document}

### 2016-03-19 surfaces-write-up/surface-write-up.tex
adding response to MRL referee and fixing many issues

@@
 
-\title{Canonical rings of $\bq$-divisors on Minimal Rational Surfaces}
+\title{Canonical rings of $\bq$-divisors on minimal rational surfaces}
 
@@
 	on the degree of generators and relations of the canonical ring of 
-	any effective stacky divisor on projective space.
+	any effective $\bq$-divisor on projective space.
 \end{abstract}
@@
 Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
-Thereby, our techniques would give a bound on generators and relations for such
-rings of Hilbert and Siegel modular forms.
+Thereby, if our results could be extended to all rational surfaces,
+they would give a bound on generators and relations for such
+rings of Hilbert and Siegel modular forms parameterized by rational
+Hilbert and Siegel modular surfaces.
+This would be interesting because such modular surfaces tend to be
+immensely complicated: ``Already for $g = 2$, the boundary of this fundamental domain is complicated; Gottschling found that it possesses $28$ boundary pieces'' \cite[p.\ 7]{geer:siegel-modular}.
+Since these varieties are so complicated, it is difficult
+to give explicit examples in which we can completely work out the canonical
+ring of a modular surface.
+Although we did not obtain a bound on the degree of generators and relations
+for general rational surfaces, its enough work to get a result for the class of rational varieties we consider.
 
@@
 Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, with $\alpha_i =
-\frac{c_i}{k_i} \in \bq_{> 0}$ and each $D_i \in \di \bp^m$ an integral divisor.
+\frac{c_i}{k_i} \in \bq_{> 0}$ in reduced form and each $D_i \in \di \bp^m$ an integral divisor.
 
@@
 Let $D = \sum_{i = 0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
-with $\alpha_i = \frac{c_i}{k_i}\in \bq$. Write $\ell_i := \lcm
+with $\alpha_i = \frac{c_i}{k_i}\in \bq$ in reduced form. Write $\ell_i := \lcm
 _{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
@@
 $q_i$ are pairwise coprime integers, and $p_i$ are chosen
-so that $\deg D = \frac{1}{2 \prod_{i=0}^n}q_i$. Further,
+so that $\deg D = \frac{1}{2 \prod_{i=0}^n q_i}$. Further,
 choose a linear subspace $\pi: \bp^1 \rightarrow \bp^m$  generically so that
@@
 Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
-\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$.
+\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.
 Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
@@
 $\fr(r) := r - \lfloor r
-\rfloor$ denote the fractional part of $r$. Throughout, we
-shall work over a fixed base field $\bk$. If $D \in \bq \otimes_\bz
+\rfloor$ denote the fractional part of $r$. 
+Throughout, we work over a fixed algebraically closed field $\bk$.
+Since generator and relation degrees are preserved under base change to the algebraic closure, assuming that $\bk$ is algebraically closed is no restriction
+on generality and the results hold equally well over an arbitrary field.
+
+If $D \in \bq \otimes_\bz
 \di X$ is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
@@
 \nocite{*}
-\bibliography{bibliography-stacky-surface}{}
-\bibliographystyle{plain}
+\bibliography{bibliography-stacky-surface}
+\bibliographystyle{alpha}
 

### 2016-05-26 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
update bib with AIF
surfaces: update bib lecture notes format
surfaces: update o'dorney ref
surfaces: addressed all but one remaining issue

@@
 		an explicit example.
-	\item \todo{do this} For example, why give in Section 1.1 the main results in a form
-The presentation can be improved quite a lot.
-that the reader can only understand if he/she first reads later sections. 
+	\item ``For example, why give in Section 1.1 the main results in a form
+that the reader can only understand if he/she first reads later sections. ``
 \todo{Reorganize the intro so as to introduce notations and conventions first,
-since the referee wants this}
+since the referee wants this; the cleaner alternative (since the main results
+should be stated in a clear-to-understand format without excessive notation)
+would be to rephrase the theorems for the main results section without using
+explicity notation}
 	\item In all our main theorems, we now say that $c_i/k_i$ is in reduced form. 
@@
 We have now included and clarified this in the ``Notations and Conventions'' subsection at the end of the Introduction.
-	\item In the previous version we submitted, Page 2, line -9, $deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$. This is now fixed.
-		\todo{Say where}
+	\item On page 2, line -9 of the previous version, $\deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$ and is now corrected.
 	\item \todo{Make Thm. 1.4 readable by including necessary notations
 		before it}
-	\item Section 2 starts with definitions that should have come earlier. (Was Section
-1.1 added in a later stage ?) Page 5, line 7, reference to things that come later.
-\item In Thm 2.5 the best lower approximations are not explained. These come later
-(page 9 and 10).
-\item 
-	\todo{I remember seeing something wrong with the bibliography, but can't find it now. Do you know what the referee is talking about?} The bibliography should be updated and misprints corrected.
+	\item \todo{Section 2 starts with definitions that should have come earlier. (Was Section
+1.1 added in a later stage ?)}
+	\item The reference to later items given on page 5, line 7 of the previous version
+	has been moved to Remark (rem:proj-grobner).
+\item The use of best lower approximations has been replaced by the use of
+convergents of Hirzebruch-Jung continued fractions which are equivalent and
+well-known.
+\item The references for the O'Dorney and Landesman--Ruhm--Zhang papers have been updated.
+The citation format of the Bruinier and Van Der Geer references have been updated to reflect their status as lecture notes.
 

### 2016-05-26 surfaces-write-up/surface-write-up.tex
surfaces: addressed all but one remaining issue

@@
 ^n v_i$.
-For a given sequence of numbers $c_0, \ldots, c_r$, (which
-we will later take to be the best lower approximations
-for a certain divisor) let 
+For a given sequence of numbers $c_0, \ldots, c_r$, let 
 \begin{align*}
@@
 
-Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
-stated explicitly later, in the case that $D = \alpha_0 D_0$ is supported on a single hypersurface, the relations in
-Theorem ~\ref{thm:proj-one-point} form a reduced Gr\"{o}bner basis with 
-respect to this ordering.
+Next, we define an ordering on these vectors, which will be used to
+give a presentation for $R_D$.
 
@@
 \noindent
-be the best lower approximations of $\alpha$. Then, the
-canonical ring
+be the convergents of the Hirzebruch-Jung continued fraction of
+$\alpha$. Then, the canonical ring
 \[
@@
 the $F_{i}^{\vec{v}}$'s form a set of minimal generators of $R_D$
-over $R_{D'}$ using their construction in terms of best lower
-approximations to $\alpha$. Then, since the $F_{i}^{\vec{v}}$ generate
+over $R_{D'}$ using their construction in terms of convergents of the
+Hirzebruch-Jung continued fraction of$\alpha$. Then, since the
+$F_{i}^{\vec{v}}$ generate
 all of $R_D$ over $R_{D'}$, and the leading terms of
@@
 and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that
-$\frac{c_i}{d_i}$ is a best lower approximation of $\alpha$
-(see Definition ~\ref{defn:lower-approximation}). Therefore, none of the $F_i^{\vec v}$ are redundant.
+$\frac{c_i}{d_i}$ is a convergent of the Hirzebruch-Jung continued
+fraction of $\alpha$. Therefore, none of the $F_i^{\vec v}$ are redundant.
 
@@
 \begin{rem}
+\label{rem:proj-grobner}
+	In the case that $D = \alpha_0 D_0$ is supported on a single
+	hypersurface, the relations in Theorem ~\ref{thm:proj-one-point}
+	form a reduced Gr\"{o}bner basis with respect to the ordering
+	given in Definition~\ref{defn:vec-order}.
+\end{rem}
+
+\begin{rem}
 \label{rem:proj-two-points}
@@
 degree of generators and relations on Hirzebruch surfaces.
-
-\begin{defn}
-\label{defn:lower-approximation}
-If $\alpha \in \bq$, then a rational number $\frac{c}{k} \leq \alpha$
-(written in reduced form with $c \in \bz, k \in \bn$) is a
-\textbf{best lower approximation} to $\alpha$ if there does not
-exist $\frac{c'}{k'}\in \mathbf{Q}$ such that $0 < k'< k$ and
-$\frac{c}{k} \le \frac{c'}{k'} \le \alpha$. 
-\end{defn}
-
-\begin{rem}
-\label{rem:lower-approximation}
-Note that all integers less than or equal to $\lfloor \alpha \rfloor$
-are best lower approximations to $\alpha$. Also, if $\alpha \ge 0$,
-then the non-negative best lower approximations of
-$\alpha$ form a finite sequence
-\[
-	0 = \frac{c_0}{k_0} < \frac{c_1}{k_1} < \ldots < \frac{c_r}{k_r} = \alpha.
-\]
-
-\noindent
-Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the best lower approximations of $\alpha = \frac{14}{5}$.
-\end{rem}
-
-\begin{figure}
-\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
-\caption{This figure shows each non-negative best lower
-approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best
-lower approximation and each ``$\circ$'' denotes a lattice point
-below $5y=14x$ which is not a best lower approximation.  Note that
-the non-negative best lower approximations generate the monoid of
-lattice points in the first quadrant satisfying  $5y \le 14x$, with
-the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$.}
-\label{fig:s14/5-lattice}
-\end{figure}
 

### 2016-05-29 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
added urls to bibliography

@@
 
+\usepackage{xr}
+\externaldocument{../surface-write-up}
+
 \def\listtodoname{List of Todos}
@@
 	\item In all our main theorems, we now say that $c_i/k_i$ is in reduced form. 
-	\item In Thm 1.2,  k is a field.
+	\item In Theorem \autoref{thm:proj-generators-relations},  k is a field.
 Throughout our paper, the results hold for arbitrary fields, but we may assume the field is algebraically closed because the generator and relation degrees are preserved by base change to the algebraic closure.
@@
 	\item The reference to later items given on page 5, line 7 of the previous version
-	has been moved to Remark (rem:proj-grobner).
+		has been moved to Remark \autoref{rem:proj-grobner}.
 \item The use of best lower approximations has been replaced by the use of
@@
 well-known.
-\item The references for the O'Dorney and Landesman--Ruhm--Zhang papers have been updated.
-The citation format of the Bruinier and Van Der Geer references have been updated to reflect their status as lecture notes.
+\item The references for the O'Dorney and Landesman--Ruhm--Zhang papers have been updated. The citation for arxiv articles now includes the arxiv reference numbers.
 

### 2016-05-29 curves-write-up/spin-cring.tex
added urls to bibliography

@@
 \begin{rem}\label{rem:sat-1-gen-lem-generic}
-The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive best lower approximation $\frac{c_i}{k_i}$ with $k_i=1$).
+The generators in Lemma \ref{lem:sat-1} are generic if $\frac{\alpha}{\beta}\le 1$ (since there is at most one positive $\frac{c_i}{k_i}$ with $k_i=1$).
 When $\frac{\alpha}{\beta}>1$, the choice of generators in degrees great than 1 is generic; furthermore, we can make the choice in degree 1 generic by choosing $\lfloor \frac{\alpha}{\beta}\rfloor$ linearly independent elements in degree 1 with pole at $P$ of order $\lfloor \frac{\alpha}{\beta}\rfloor$ rather than elements with poles of order $1, \ldots, \lfloor \frac{\alpha}{\beta}\rfloor$; this requires minor complications in the construction of generators of the ideal of relations.

### 2016-05-29 surfaces-write-up/surface-write-up.tex
added urls to bibliography

@@
 over $R_{D'}$ using their construction in terms of convergents of the
-Hirzebruch-Jung continued fraction of$\alpha$. Then, since the
+Hirzebruch-Jung continued fraction of $\alpha$. Then, since the
 $F_{i}^{\vec{v}}$ generate

### 2016-06-27 surfaces-write-up/surface-write-up.tex
theorem 1.4 changes
fixed theorem

@@
 \otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.
-Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
 Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
 $\hirz_m$, as described at the beginning of Section
-~\ref{sec:hirz} and define $\Te, \Tp$, and $\Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
-Now suppose that $\{f_1, \ldots, f_n\}$ contains two independent 
+~\ref{sec:hirz} and suppose that $\{f_1, \ldots, f_n\}$
+contains two independent 
 linear polynomials in $u, v$ and two independent linear polynomials in
@@
 \[
-	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
-	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
-	- \bida_j \bidb_i) \ell_{i, j}
+	\rho = \lcm_{1\le i\le n}(k_i)\sum_{1\le i\le j\le n} \bida_i \bidb_i
 \]
@@
 \[
-	\max(2 \rho, \tau)
-\]
-
-\noindent
-where
-\[
-	\tau = \rho
-	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
-	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
-	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
+	2\rho
 \]
 \end{restatable}
+\begin{rem}
+Theorem \ref{thm:hirz-generators-relations-full} provides a more precise bound.
+\end{rem}
 
@@
 	(\bida_i \bidb_j - \bida_j
-	\bidb_i) \bigr) \right).
+	\bidb_i) \bigr) \right)\le 2\rho.
 \]
@@
 
-\hirzrestate*
-
+\begin{thm}
+\label{thm:hirz-generators-relations-full}
+Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
+\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.
+Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
+Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
+$\hirz_m$, as described at the beginning of Section
+~\ref{sec:hirz} and suppose that $\{f_1, \ldots, f_n\}$
+contains two independent 
+linear polynomials in $u, v$ and two independent linear polynomials in
+$w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.
+Define $\Te, \Tp$, and $\Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
+
+Then $R_D$ is generated in degrees at most
+\[
+	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
+	\sum_{\substack{i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j
+	- \bida_j \bidb_i) \ell_{i, j}
+\]
+
+\noindent
+with relations generated in degrees at most 
+\[
+	2\rho
+\]
+\end{thm}
+\begin{rem}
+This implies theorem \ref{thm:hirz-generators-relations}.
+\end{rem}
 \begin{proof}

### 2016-07-21 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
surfaces: some cleanup, response writing

@@
 	\item On page 2, line -9 of the previous version, $\deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$ and is now corrected.
-	\item \todo{Make Thm. 1.4 readable by including necessary notations
-		before it}
-	\item \todo{Section 2 starts with definitions that should have come earlier. (Was Section
-1.1 added in a later stage ?)}
+	\item Theorem 1.4 has been rewritten into a simpler form by reducing some
+	notation unnecessary to understanding the general idea.
 	\item The reference to later items given on page 5, line 7 of the previous version
@@
 \item The references for the O'Dorney and Landesman--Ruhm--Zhang papers have been updated. The citation for arxiv articles now includes the arxiv reference numbers.
+\item The conditions of Proposition 2.1 have been reorganized for clarity.
 

### 2016-07-21 surfaces-write-up/surface-write-up.tex
surfaces: some cleanup, response writing

@@
 \usepackage{thm-restate}
+\usepackage{enumitem}
 
@@
 reordering) $f_0,\ldots, f_{m}$ are $m$ independent linear forms
-on $\bp^m$.  This may necessitate the inclusion of ``Ghost Divisors'' $D_i$ with coefficients $\alpha_i = 0$.
+on $\bp^m$.  This may necessitate the inclusion of ``ghost divisors'' $D_i$ with coefficients $\alpha_i = 0$.
 
@@
 The functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ satisfying
-
-\begin{align}
-\label{align:pm-span}
-\sum_{i=0}^{n} c_i \cdot \bida_i = 0 && \text{ and } &&c_i \geq
--\lfloor d\alpha_i \rfloor	
-\end{align}
-
-\noindent
-span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, functions 
-of the form $u^d \cdot \prod_{i=0}^n f_i^{c_i}$ satisfying Equation ~\eqref{align:pm-span} and
-\begin{align}
-\label{align:pm-basis}
-c_i = -\lfloor d\alpha_i \rfloor && \text{ for } && i > m
-\end{align}
+both of the following conditions
+
+\begin{enumerate}
+	\item $\sum_{i=0}^{n} c_i \cdot \bida_i = 0$
+	\item $c_i \geq - \lfloor d \alpha_i \rfloor$
+\end{enumerate}
+
+\noindent
+span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, such functions 
+that also satisfy
+\begin{enumerate}[resume]
+	\item $c_i = -\lfloor d\alpha_i \rfloor \text{ for } i > m$
+\end{enumerate}
 
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-~\eqref{align:pm-span} lie in $H^0(\mathbb{P}^m,dD)$.
+(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$.
 To complete the proof, it
-suffices to check functions satisfying conditions ~\eqref{align:pm-basis} form
+suffices to check functions satisfying conditions (1-3) form
 a basis of $H^0(\bp^m,dD)$. Note that there are $\binom{m+ \deg \lfloor dD \rfloor }{m}$
-functions satisfying condition ~\eqref{align:pm-basis}. However we know
+functions satisfying conditions (1-3). However we know
 $h^0(\bp^m,dD) = \binom{m+ \deg \lfloor dD \rfloor }{m},$ so it suffices to show
-that those functions satisfying condition ~\eqref{align:pm-basis} are
+that those functions satisfying conditions (1-3) are
 independent. This follows from the assumption that $f_0,\ldots f_m$ form a
 basis of linear forms, and so all monomials in $f_0,\ldots, f_m$
-of degree $\deg \lfloor d \deg D \rfloor $
+of degree $\deg \lfloor d (\deg D) \rfloor $
 form a basis of degree $\deg \lfloor d  D \rfloor$ rational functions.

### 2016-07-21 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
surfaces: split tightness rem, move notation ssec

--- 2016-05-29 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
@@
 		an explicit example.
-	\item ``For example, why give in Section 1.1 the main results in a form
-that the reader can only understand if he/she first reads later sections. ``
-\todo{Reorganize the intro so as to introduce notations and conventions first,
-since the referee wants this; the cleaner alternative (since the main results
-should be stated in a clear-to-understand format without excessive notation)
-would be to rephrase the theorems for the main results section without using
-explicity notation}
-	\item In all our main theorems, we now say that $c_i/k_i$ is in reduced form. 
-	\item In Theorem \autoref{thm:proj-generators-relations},  k is a field.
+	\item In all of the main theorems, it says that $\frac{c_i}{k_i}$ is in reduced form. 
+	\item In Theorem \autoref{thm:proj-generators-relations}, $k$ is a field.
 Throughout our paper, the results hold for arbitrary fields, but we may assume the field is algebraically closed because the generator and relation degrees are preserved by base change to the algebraic closure.
@@
 	\item On page 2, line -9 of the previous version, $\deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$ and is now corrected.
-	\item \todo{Make Thm. 1.4 readable by including necessary notations
-		before it}
-	\item \todo{Section 2 starts with definitions that should have come earlier. (Was Section
-1.1 added in a later stage ?)}
+	\item Theorem 1.4 (now \autoref{thm:hirz-generators-relations}) has been rewritten into a simpler form by reducing some
+	notation unnecessary to understanding the general idea.
+	\item Subsection 1.2 has now been moved to immediately precede Subsection 1.1 as a standalone paragraph.
 	\item The reference to later items given on page 5, line 7 of the previous version
@@
 \item The references for the O'Dorney and Landesman--Ruhm--Zhang papers have been updated. The citation for arxiv articles now includes the arxiv reference numbers.
+\item The conditions of Proposition~\autoref{prop:pm-span-and-basis} have been reorganized for clarity.
+\item Remark 1.3 has been split into what is now Remark~\autoref{rem:proj-tight-bounds-eff} and Remark~\autoref{rem:proj-tight-bounds} (with
+some material moved to Remark~\autoref{rem:exact-noneff-bounds}).
 

### 2016-07-21 surfaces-write-up/surface-write-up.tex
surfaces: split tightness rem, move notation ssec

@@
 
+We will use $m \in \bz$ to index the dimension of a given projective
+space $\bp^m$ or the type of the Hirzebruch surface $\hirz_m$.
+Let $D$ be a (Weil) $\bq$-divisor of the form
+\begin{align*}
+	D = \sum_{i=1}^{n}\alpha_i D_i \in \bq \otimes_\bz \di X.
+\end{align*}\noindent
+where $n \in \bz$ indexes the number of irreducible divisors in 
+the above expansion of $D$, $\alpha_i \in \bq$, and $D_i \in \di X$ is an integral
+codimension 1 closed subscheme of $X$. When it is convenient to do
+so, we shall sometimes start the indexing at $0$, so that $i$ runs
+from $0$ to $n$. In the case $X = \bp^m$, define the degree of $D$ by $\deg D :=
+\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
+\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
+\lfloor \alpha_i \rfloor D_i$. Let $
+	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
+denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
+is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
+$\fr(r) := r - \lfloor r
+\rfloor$ denote the fractional part of $r$. 
+Throughout, we work over a fixed algebraically closed field $\bk$.
+Since generator and relation degrees are preserved under base change to the algebraic closure, assuming that $\bk$ is algebraically closed is no restriction
+on generality and the results hold equally well over an arbitrary field.
+If $D \in \bq \otimes_\bz
+\di X$ is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
+
 \ssec{Main Results and Outline}
+\label{ssec:main}
 
@@
 
+\begin{rem}
+\label{rem:proj-tight-bounds-eff}
+Note that the bounds
+given in Theorem ~\ref{thm:proj-effective-intro}
+are tight and are typically attained, as explained in
+Remark ~\ref{rem:exact-effective-bounds}.
+\end{rem}
+
 \begin{restatable}{thm}{restateproj}
@@
 
-\begin{rem}\label{rem:proj-tight-bounds} Note that the bounds
-	given in Theorem ~\ref{thm:proj-effective-intro}
-are tight and are typically attained, as explained in
-Remark ~\ref{rem:exact-effective-bounds}.
-Additionally, the bounds given in Theorem 
+\begin{rem}
+\label{rem:proj-tight-bounds}
+Note that the bounds given in Theorem 
 ~\ref{thm:proj-generators-relations} are asymptotically
 tight to within a factor of two 
-for the following class of divisors. Consider
-a divisor 
-$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bz \di \bp^m$
-such that $H_i$ are hyperplanes,  
-$q_i$ are pairwise coprime integers, and $p_i$ are chosen
-so that $\deg D = \frac{1}{2 \prod_{i=0}^n q_i}$. Further,
-choose a linear subspace $\pi: \bp^1 \rightarrow \bp^m$  generically so that
-$\pi^* D = \sum_{i=0}^n \frac{p_i}{2q_i}P_i$, 
-where $P_i$ are distinct points in $\bp^1$. To choose such a map
-$\pi$, we may need to assume that the base field is infinite.
-Note that by the Remark immediately following Theorem 8 in 
-\cite{dorney:canonical},
-the given bounds on the generators and relations of
-$R_{\pi^*D}$ are within
-a factor of two of the degree of generation and relations of
-$R_{\pi^*D}$. Finally, since restriction map
-$R_D \rightarrow R_{\pi^*D}$ induced by the restriction maps
-on cohomology $H^0(\bp^m, dD) \rightarrow H^0(\bp^1, \pi^*(dD))
-\cong H^0(\bp^1, d\pi^* D)$ are surjective, we obtain that
-the bounds for the generators and relations of $R_D$ given in
-Theorem ~\ref{thm:proj-generators-relations} also
-agree with the degree of generation and relations 
-to within a factor of two.
+for a class of divisors described in
+Remark~\ref{rem:exact-noneff-bounds}.
 \end{rem}
@@
 
-\begin{restatable}{thm}{hirzrestate}
+\begin{thm}
 \label{thm:hirz-generators-relations}
@@
 \]
-\end{restatable}
+\end{thm}
+
 \begin{rem}
-Theorem \ref{thm:hirz-generators-relations-full} provides a more precise bound.
+Theorem~\ref{thm:hirz-generators-relations} is restated with a more precise
+bound in Theorem~\ref{thm:hirz-generators-relations-full}.
 \end{rem}
@@
 minimal rational surface. Section \ref{sec:conc} discusses further questions.
-
-\ssec{Notations and Conventions}
-We will use $m \in \bz$ to index the dimension of a given projective
-space $\bp^m$ or the type of the Hirzebruch surface $\hirz_m$.
-Let $D$ be a (Weil) $\bq$-divisor of the form
-\begin{align*}
-	D = \sum_{i=1}^{n}\alpha_i D_i \in \bq \otimes_\bz \di X.
-\end{align*}\noindent
-where $n \in \bz$ indexes the number of irreducible divisors in 
-the above expansion of $D$, $\alpha_i \in \bq$, and $D_i \in \di X$ is an integral
-codimension 1 closed subscheme of $X$. When it is convenient to do
-so, we shall sometimes start the indexing at $0$, so that $i$ runs
-from $0$ to $n$. For such a divisor $D$ with $\alpha_i =
-\frac{c_i}{k_i}$ let $\ell_i = \lcm_{j\ne i}(k_j)$
-and let $\ell_{i,j} = \lcm_{h\ne i,j}(k_h).$ In the case $X = \bp^m$, define the degree of $D$ by $\deg D :=
-\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
-\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor D_i$. Let $
-	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
-denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
-is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
-$\fr(r) := r - \lfloor r
-\rfloor$ denote the fractional part of $r$. 
-Throughout, we work over a fixed algebraically closed field $\bk$.
-Since generator and relation degrees are preserved under base change to the algebraic closure, assuming that $\bk$ is algebraically closed is no restriction
-on generality and the results hold equally well over an arbitrary field.
-
-If $D \in \bq \otimes_\bz
-\di X$ is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
 
@@
 
+\begin{rem}
+\label{rem:exact-noneff-bounds}
+The bounds given in Theorem 
+~\ref{thm:proj-generators-relations} are asymptotically
+tight to within a factor of two 
+for the following class of divisors. Consider
+a divisor 
+$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bz \di \bp^m$
+such that $H_i$ are hyperplanes,  
+$q_i$ are pairwise coprime integers, and $p_i$ are chosen
+so that $\deg D = \frac{1}{2 \prod_{i=0}^n q_i}$. Further,
+choose a linear subspace $\pi: \bp^1 \rightarrow \bp^m$  generically so that
+$\pi^* D = \sum_{i=0}^n \frac{p_i}{2q_i}P_i$, 
+where $P_i$ are distinct points in $\bp^1$. To choose such a map
+$\pi$, we may need to assume that the base field is infinite.
+Note that by the Remark immediately following Theorem 8 in 
+\cite{dorney:canonical},
+the given bounds on the generators and relations of
+$R_{\pi^*D}$ are within
+a factor of two of the degree of generation and relations of
+$R_{\pi^*D}$. Finally, since restriction map
+$R_D \rightarrow R_{\pi^*D}$ induced by the restriction maps
+on cohomology $H^0(\bp^m, dD) \rightarrow H^0(\bp^1, \pi^*(dD))
+\cong H^0(\bp^1, d\pi^* D)$ are surjective, we obtain that
+the bounds for the generators and relations of $R_D$ given in
+Theorem ~\ref{thm:proj-generators-relations} also
+agree with the degree of generation and relations 
+to within a factor of two.
+\end{rem}
+
 \section{Canonical Rings of Hirzebruch surfaces}

### 2016-07-24 surfaces-write-up/surface-write-up.tex
for merge
fixed a_i,b_i missing
minor edits to intro

@@
 barthHPV:compactComplexSurfaces}, and
-the canonical rings of elliptic surfaces most naturally described in the setting of
+the canonical rings of elliptic surfaces are most naturally described in the setting of
 $\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
@@
 Although we did not obtain a bound on the degree of generators and relations
-for general rational surfaces, its enough work to get a result for the class of rational varieties we consider.
-
-We will use $m \in \bz$ to index the dimension of a given projective
-space $\bp^m$ or the type of the Hirzebruch surface $\hirz_m$.
+for general rational surfaces, the restricted class of rational varieties we consider still required significant work.
+
+\subsection{Notation}
+We now define some notation used throughout the paper.
+Use $m \in \bz$ to index the dimension of a given projective
+space $\bp^m$ and the type of the Hirzebruch surface $\hirz_m$.
 Let $D$ be a (Weil) $\bq$-divisor of the form
@@
 \rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor D_i$. Let $
-	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
-denote the canonical ring associated to the $\bq$-divisor $D$. If $R$
+\lfloor \alpha_i \rfloor D_i$. Let 
+$R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
+denote the canonical ring associated to the $\bq$-divisor $D$. 
+So, $R_D$ is notation for $R(X,D)$ when $X$ is understood from context.
+If $R$
 is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
@@
 
-Then the canonical ring
-\[
-	R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)
-\]
-
-\noindent
+Then the canonical ring $R_D$
 is generated in degrees at most $\max_{0 \leq i \leq n}{k_i}$ with
@@
 _{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
-\bk[x_0, \ldots, x_m]$ and let each $D_i = V(f_i)$ with $f_i \in \bk[x_0, \ldots, 
+\bk[x_0, \ldots, x_m]$ and define $D_i := V(f_i)$, for some $f_i \in \bk[x_0, \ldots, 
 x_m]$. Now suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
-linear polynomials in $x_0, \ldots, x_m$ {\rm(}with corresponding 
-$\alpha_j$ possibly zero{\rm)}.
+linear polynomials in $x_0, \ldots, x_m$ {\rm(}where we allow for 
+$\alpha_j = 0$ in the expansion of $D${\rm)}.
 
 Then $R_D$ is generated in degrees at most 
-\[
-	\sum_{i = 0}^n \ell_i a_i
-\]
-
-\noindent
+$\sum_{i = 0}^n \ell_i a_i$
 with relations generated in degrees at most
@@
 Hirzebruch surface $F_m := \proj(\sym^\bullet \sco_{\bp^1} \oplus
-\sco_{\bp^1}(m)),$ or as a quotient of an open subscheme of
-$\ba^4$ by a 
-weighted action, as is done in the
-beginning of Section \ref{sec:hirz}.
-Note that Hirzebruch surfaces are regular, normal,
-and locally factorial, being $\bp^1$-bundles over
-$\bp^1$. Therefore, the natural map from Cartier
+\sco_{\bp^1}(m))$ as a projective bundle over $\bp^1$.
+Let $u,v$ the projective coordinates on the base $\bp^1$ and let $z,w$ be the projective coordinates
+on the fiber, as defined more precisely at the beginning of
+\ref{sec:hirz}.
+Since Hirzebruch surfaces are smooth, the natural map from Cartier
 divisors to Weil divisors is an isomorphism.
@@
 \otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.  
+Let each $D_i = V(f_i)$, where $f_i \in \sco(a_i, b_i)$.
 Let $u, v, z, w$ be the coordinates for the Hirzebruch surface
-$\hirz_m$, as described at the beginning of Section
-~\ref{sec:hirz} and suppose that $\{f_1, \ldots, f_n\}$
+$\hirz_m$, and suppose that $\{f_1, \ldots, f_n\}$
 contains two independent 
 linear polynomials in $u, v$ and two independent linear polynomials in
-$w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.
+$w, x$ {\rm(}where we allow for $\alpha_j = 0$ in the expansion of $D${\rm)}.
 
@@
 \[
-	\rho = \lcm_{1\le i\le n}(k_i)\sum_{1\le i\le j\le n} \bida_i \bidb_i
-\]
-
+	\lcm_{1\le i\le n}(k_i)\cdot \left(\sum_{1\le i\le j\le n} \bida_i \bidb_i\right) 
+\]
 \noindent
@@
 \[
-	2\rho
+	2 \cdot \lcm_{1\le i\le n}(k_i) \cdot \left( \sum_{1\le i\le j\le n} \bida_i \bidb_i\right) 
 \]
 \end{thm}
-
 \begin{rem}
@@
 \begin{tikzcd}
-0 \ar {r} & \ker \chi \ar{r}{\rho} & \ker \phi \ar {r}{\tau} & \ker \psi \ar r & 0.
+0 \ar {r} & \ker \chi \ar{r} & \ker \phi \ar {r} & \ker \psi \ar r & 0.
 \end{tikzcd}
 \]
-
 This shows that lifts of generators of $\ker \psi$ together with images of
@@
 $w, x$ {\rm(}with corresponding $\alpha_j$ possibly zero{\rm)}.
-Define $\Te, \Tp$, and $\Tm$ as in Definition ~\ref{defn:t-defn}. Let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
+Recall $\Te, \Tp$, and $\Tm$ as given in Definition ~\ref{defn:t-defn} and let each $D_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$.
 
@@
 \noindent
-with relations generated in degrees at most 
-\[
-	2\rho
-\]
+with relations generated in degrees at most $2 \rho$.
 \end{thm}
-\begin{rem}
-This implies theorem \ref{thm:hirz-generators-relations}.
-\end{rem}
+%\begin{rem}
+%This implies theorem \ref{thm:hirz-generators-relations}.
+%\end{rem}
 \begin{proof}

### 2016-08-04 surfaces-write-up/surface-write-up.tex
modified hilbert rational surfaces

@@
 
-We expect the work in this paper will help calculate a presentation of certain rings of
+\subsection{Modular Forms}
+The work in this paper was motivated by 
+potential applications to
+calculating a presentation of certain rings of
 Hilbert 
-modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
+modular forms and Siegel modular forms. 
+Recall that Hilbert and Siegel 
 modular forms are two generalizations of modular forms to higher dimensions,
@@
 the algebraic category of stacky curves \cite[Proposition 6.1.5]{vzb:stacky}. 
-We expect that one can generalize this result to yield an equivalence of
+If one could generalize this result to yield an equivalence of
 categories between an appropriate subcategory of $m$-dimensional orbifolds and
-a subcategory of $m$-dimensional algebraic spaces.
-In particular, this would allow us to translate rings of Hilbert modular forms
+a subcategory of $m$-dimensional algebraic spaces,
+this would allow us to translate rings of Hilbert modular forms
 and Siegel modular forms whose coarse space is a projective space or a
@@
 immensely complicated: ``Already for $g = 2$, the boundary of this fundamental domain is complicated; Gottschling found that it possesses $28$ boundary pieces'' \cite[p.\ 7]{geer:siegel-modular}.
-Since these varieties are so complicated, it is difficult
-to give explicit examples in which we can completely work out the canonical
-ring of a modular surface.
+Since our results only apply to minimal rational surfaces, and because the rings of Hilbert and Siegel modular forms are so complex, we were unable
+to use our work to compute the canonical ring of an explicit modular surface.
 Although we did not obtain a bound on the degree of generators and relations

### 2016-08-07 surfaces-write-up/surface-paper.tex
moved surface write up to surface paper

--- 2016-08-04 surfaces-write-up/surface-write-up.tex
@@
  	We give bounds on the degree of generation and relations of
+	generalized 
 	canonical rings of arbitrary $\bq$-divisors on projective spaces of 
 	all dimensions and Hirzebruch surfaces. We also give exact bounds 
-	on the degree of generators and relations of the canonical ring of 
+	on the degree of generators and relations of the generalized
+	canonical ring of 
 	any effective $\bq$-divisor on projective space.
@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d
+\textbf{generalized canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d
 H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep

### 2016-08-07 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
surfaces: take out todo on response thm numberings
moved surface write up to surface paper
made canonical ring to generalized canonical ring

@@
 \usepackage{xr}
-\externaldocument{../surface-write-up}
+\externaldocument{../surface-paper}
 
@@
 Here are the changes we have made in response to the referee's suggestions.
-\todo{make sure the theorem number here reflect the new numberings}
 \begin{enumerate}
-	\item \todo{Ask David how the new version sounds} We explained
+	\item We changed the name ``canonical ring'' to ``generalized canonical ring,'' as the referee suggested,
+		since the canonical ring is really
+		$R_K$ (i.e., it is the generalized canonical ring $R_D$ as we have defined it in the case $D = K$).
+	\item We explained
 		in more detail how our potential application
@@
 		notation unnecessary to understanding the general idea.
+We then state it more precisely as \autoref{thm:hirz-generators-relations-full}.
+The statement of \autoref{thm:hirz-generators-relations-full} has also been simplified, since we noticed the previously defined quantity $\tau$ was unnecessary.
 	\item Subsection 1.2 has now been moved to immediately precede Subsection 1.1 as a standalone paragraph.
@@
 \end{enumerate}
-
 \end{document}

### 2016-08-07 surfaces-write-up/surface-paper.tex
made canonical ring to generalized canonical ring

@@
 
-\title{Canonical rings of $\bq$-divisors on minimal rational surfaces}
+\title{Generalized canonical rings of $\bq$-divisors on minimal rational surfaces}
 
@@
 track of degree.
-We study the generators and relations of canonical
+We study the generators and relations of generalized canonical
 rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
@@
 $R(X, D)$. In particular, we give a minimal presentation of the
-canonical ring when $X = \bp^m$ and $D$ is any effective
+generalized canonical ring when $X = \bp^m$ and $D$ is any effective
 $\bq$-divisor.
@@
 O'Dorney \cite{dorney:canonical}, which gives similar descriptions
-of canonical rings for general $\bq$-divisors on $\bp^1$. This
+of generalized canonical rings for general $\bq$-divisors on $\bp^1$. This
 study also has connections to the papers by Voight--Zureick-Brown 
@@
 $R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
-denote the canonical ring associated to the $\bq$-divisor $D$. 
+denote the generalized canonical ring associated to the $\bq$-divisor $D$. 
 So, $R_D$ is notation for $R(X,D)$ when $X$ is understood from context.
@@
 the degree of generators and relations of
-stacky canonical rings on $\bp^m$. The first applies
+generalized canonical rings on $\bp^m$. The first applies
 to effective $\bq$-divisors and the second applies to arbitrary
@@
 
-Then the canonical ring $R_D$
+Then the generalized canonical ring $R_D$
 is generated in degrees at most $\max_{0 \leq i \leq n}{k_i}$ with
@@
 \ref{thm:hirz-generators-relations} provide bounds on generators
-and relations for the canonical ring of any $\bq$-divisor on any
+and relations for the generalized canonical ring of any $\bq$-divisor on any
 minimal rational surface. Section \ref{sec:conc} discusses further questions.
@@
 Note that if $\deg D < 0$ the
-canonical ring is concentrated in degree 0, and if
-$\deg D = 0$, then the canonical ring has a single
+generalized canonical ring is concentrated in degree 0, and if
+$\deg D = 0$, then the generalized canonical ring has a single
 generator. Therefore, for the remainder of this section,
@@
 \cite{dorney:canonical}. We also give an explicit description of the
-generators of the canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}
+generators of the generalized canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}
 
@@
 Before bounding the degree of generation and relations of
-canonical rings on projective space, we first
+generalized canonical rings on projective space, we first
 describe a particular choice of basis for $R_D$ as a $\bk$ vector
@@
 In this subsection, we restrict attention to the case of effective
-fractional divisors $D \in \bq \otimes_\bz \di \bp^m$. We give an explicit presentation of the canonical ring when $D$ is an effective
+fractional divisors $D \in \bq \otimes_\bz \di \bp^m$. We give an explicit presentation of the generalized canonical ring when $D$ is an effective
 divisor.
@@
 be the convergents of the Hirzebruch-Jung continued fraction of
-$\alpha$. Then, the canonical ring
+$\alpha$. Then, the generalized canonical ring
 \[
@@
 in Example ~\ref{eg:hyperplane}, the degrees of generation of the
-canonical ring of a general $\bq$-divisor supported on two
+generalized canonical ring of a general $\bq$-divisor supported on two
 hyperplanes cannot be bounded so tightly. The two-point
@@
 hyperplanes. However, for $m \geq 2$, there are hypersurfaces which
-are not unions of hyperplanes. We now address this general case, giving an inductive presentation of canonical rings of effective divisors, and a tight bound on the degrees of their generators and
+are not unions of hyperplanes.
+We now address this general case, giving an inductive presentation of generalized canonical rings of effective divisors, and a tight bound on the degrees of their generators and
 relations.
@@
 $\pdeg$ Veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0))$ and so
-the canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
+the generalized canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
 restricted to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
@@
 By combining the above results, we get our main theorem bounding
-the generator and relation degrees of the canonical ring of any
+the generator and relation degrees of the generalized canonical ring of any
 $\bq$-divisor on projective space.
@@
 ~\ref{thm:hirz-generators-relations}, bounding the degree of
-generators and relations of the canonical ring of a $\bq$-divisor
+generators and relations of the generalized canonical ring of a $\bq$-divisor
 on any Hirzebruch surface.
@@
 restriction. If either of the bi-degrees of $D$ are negative,
-then the canonical ring is concentrated in degree 0. If one of the
+then the generalized canonical ring is concentrated in degree 0. If one of the
 bi-degrees is 0, say the first one is 0, then $R_D$ is isomorphic
@@
 \label{lem:hirz-generators}
-For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \bq \otimes_\bz \hirz_m$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the canonical ring $R_D$ is generated in degrees at most
+For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \bq \otimes_\bz \hirz_m$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the generalized canonical ring $R_D$ is generated in degrees at most
 \begin{equation}\label{eqn:def-sigma}
@@
 ~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations
-of arbitrary canonical rings on any minimal rational surface. A
+of arbitrary generalized canonical rings on any minimal rational surface. A
 natural extension of our results is the following.
@@
 to bound the degree of generators and relations of the 
-canonical ring of a divisor on a blow-up of a given surface
-in terms of the canonical
+generalized canonical ring of a divisor on a blow-up of a given surface
+in terms of the generalized canonical
 rings of some associated divisors that given surface.
@@
 Another direction to generalize the work in this paper
-would be to try to express canonical rings of $\bq$-divisors on
+would be to try to express generalized canonical rings of $\bq$-divisors on
 $X \times Y$ in terms of those on $X$ and $Y$. In this paper,
-we bounded the degrees of presentations on canonical rings on $\bp^1 \times \bp^1 \cong \hirz_0$.
+we bounded the degrees of presentations on generalized canonical rings on $\bp^1 \times \bp^1 \cong \hirz_0$.
 Perhaps similar techniques can be used to bound
-degrees of presentations on canonical rings on $(\bp^1)^k$ or
+degrees of presentations on generalized canonical rings on $(\bp^1)^k$ or
 more generally on $(\bp^1)^{i_1} \times \cdots (\bp^k)^{i_k}.$

### 2016-08-07 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
changed mrl revisions

--- 2016-07-21 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
@@
 Here are the changes we have made in response to the referee's suggestions.
-\todo{make sure the theorem number here reflect the new numberings}
 \begin{enumerate}
-	\item \todo{Ask David how the new version sounds} We explained
+	\item We changed the name ``canonical ring'' to ``generalized canonical ring,'' as the referee suggested,
+		since the canonical ring is really a special case of the generalized canonical ring, in the case
+		$D = K$.
+	\item We explained
 		in more detail how our potential application
 		for Hilbert modular forms and the difficulty in producing
-		an explicit example.
+		an explicit example in the Modular Forms subsection of the introduction.
 	\item In all of the main theorems, it says that $\frac{c_i}{k_i}$ is in reduced form. 
@@
 Throughout our paper, the results hold for arbitrary fields, but we may assume the field is algebraically closed because the generator and relation degrees are preserved by base change to the algebraic closure.
-We have now included and clarified this in the ``Notations and Conventions'' subsection at the end of the Introduction.
+We have now included and clarified this in the ``Notations and Conventions'' subsection at the end of the introduction.
 	\item On page 2, line -9 of the previous version, $\deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$ and is now corrected.
-	\item Theorem 1.4 (now \autoref{thm:hirz-generators-relations}) has been rewritten into a simpler form by reducing some
+	\item Theorem 1.4 (now Theorem \ref{thm:hirz-generators-relations}) has been rewritten into a simpler form by reducing some
 		notation unnecessary to understanding the general idea.
-	\item Subsection 1.2 has now been moved to immediately precede Subsection 1.1 as a standalone paragraph.
+We then state it more precisely as Theorem \ref{thm:hirz-generators-relations-full}.
+The statement of Theorem \ref{thm:hirz-generators-relations-full} has also been simplified, since we noticed the previously defined quantity $\tau$ was unnecessary.
+	\item Subsection 1.2, which defined necessary notation for our main results, has now been moved to immediately precede the statement of our main results.
 	\item The reference to later items given on page 5, line 7 of the previous version
-		has been moved to Remark \autoref{rem:proj-grobner}.
+		has been moved to Remark \ref{rem:proj-grobner}.
 \item The use of best lower approximations has been replaced by the use of

### 2016-08-10 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
surfaces: refer to modular forms subsec by ref

@@
 		for Hilbert modular forms and the difficulty in producing
-		an explicit example in the Modular Forms subsection of the introduction.
+		an explicit example in Subsection \ref{subsection:modular-forms} of the introduction.
 	\item In all of the main theorems, it says that $\frac{c_i}{k_i}$ is in reduced form. 
@@
 	\item On page 2, line -9 of the previous version, $\deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$ and is now corrected.
-	\item Theorem 1.4 (now Theorem \ref{thm:hirz-generators-relations}) has been rewritten into a simpler form by reducing some
+	\item Theorem \ref{thm:hirz-generators-relations} (previously Theorem 1.4) has been rewritten into a simpler form by reducing some
 		notation unnecessary to understanding the general idea.

### 2016-08-10 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
surfaces: create copy of revision, responses clarity

@@
 \item The conditions of Proposition~\autoref{prop:pm-span-and-basis} have been reorganized for clarity.
-\item Remark 1.3 has been split into what is now Remark~\autoref{rem:proj-tight-bounds-eff} and Remark~\autoref{rem:proj-tight-bounds} (with
+\item What was previously Remark 1.3 has been split into what is now Remark~\autoref{rem:proj-tight-bounds-eff} and Remark~\autoref{rem:proj-tight-bounds} (with
 some material moved to Remark~\autoref{rem:exact-noneff-bounds}).

### 2016-08-10 surfaces-write-up/MRL/Landesman-Ruhm-Zhang-Rational-Surfaces-MRL-rev.tex
surfaces: create copy of revision, responses clarity

--- 2016-08-07 surfaces-write-up/surface-paper.tex
@@
 \subsection{Modular Forms}
+\label{subsection:modular-forms}
 The work in this paper was motivated by 

### 2017-03-24 surfaces-write-up/surface-paper.tex
edits in response to referee's second report

@@
 \author{Aaron Landesman}
-\address[Aaron Landesman]{Department of Mathematics, Harvard University}
-\email{aaronlandesman@college.harvard.edu}
+\address[Aaron Landesman]{Department of Mathematics, Stanford University}
+\email{aaronlandesman@stanford.edu}
 
@@
 appear when considering the canonical ring of surfaces of Kodaira dimension 1.
-A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
+In characteristic 0, every surface of Kodaira dimension 1 is an elliptic surface \cite[p. 244]{
 barthHPV:compactComplexSurfaces}, and
@@
 the denominators. This issue can easily be circumvented by adding in ``ghost
-points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
+divisors.'' That is, we may add divisors of the form $0 \cdot H_i$ to
 $D$, and reorder so that if $D = \sum_{i=0}^{n}\alpha_i V(f_i)$,
@@
 In Example ~\ref{eg:radical}, we show that it is still, in general,
-necessary to add ghost points, even when the irreducible components
+necessary to add ghost divisors, even when the irreducible components
 of a divisor are not all
@@
 $6$.
-However,  approach, as all lower degrees only have
+However, all lower degrees only have
 dimension at most 1. Therefore, we cannot hope to bound the degree
@@
 in analogy to \cite[Theorem 8]{dorney:canonical}
-unless we require that $D$ includes ghost points. That is, unless
+unless we require that $D$ includes ghost divisors. That is, unless
 $D_0,\ldots D_m$ are taken to be linearly independent hyperplanes.
@@
 
-Having justified the necessity of adding ghost points, we proceed to bound the
+Having justified the necessity of adding ghost divisors, we proceed to bound the
 number of generators and relations of arbitrary $\bq$-divisors in 

### 2017-03-24 surfaces-write-up/surface-paper.tex
added edits for second responses file

@@
 We now define some notation used throughout the paper.
-Use $m \in \bz$ to index the dimension of a given projective
+We use $m \in \bz$ to index the dimension of a given projective
 space $\bp^m$ and the type of the Hirzebruch surface $\hirz_m$.
@@
 denote the generalized canonical ring associated to the $\bq$-divisor $D$. 
-So, $R_D$ is notation for $R(X,D)$ when $X$ is understood from context.
+We use $R_D$ as notation for $R(X,D)$ when $X$ is understood from context.
 If $R$
@@
 \label{eg:radical}
-Consider $\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 +
+Consider $D :=\frac{-1}{5}V(x_0^2 + x_1^2 + x_2^2) + \frac{1}{7}V(x_0^2 + x_1^2 +
 x_3^2) + \frac{1}{17}V(x_0^2 + x_2^2 + x_3^2) - \frac{1}{596}V(x_1^2 + x_2^2 +
-x_3^2)$. In degree $355216 = 5 \cdot 7 \cdot 17 \cdot 596$, this has dimension
+x_3^2)$. In degree $355216 = 5 \cdot 7 \cdot 17 \cdot 596$, $R_D$ has dimension
 $6$.
-However, all lower degrees only have
-dimension at most 1. Therefore, we cannot hope to bound the degree
+However, for all $d \leq 355216,$ $h^0(\bp^3, dD) \leq 1$
+and 
+$h^0(\bp^3, dD)  = 1$ precisely when $\lfloor d D \rfloor = 0$ 
+(so in this case, $H^0(\bp^3, d D)$ corresponds to the constant functions).
+Therefore $R_D$ has a generator in degree $355216$.
+Hence, we cannot hope to bound the degree
 of generation of $R_D$ as a linear combination of $\ell_i$,
@@
 $(a + b + mc, c + d)$. Rational sections of $\hirz_m$ can be written as
-rational functions with numerators and denominators with the same bi-degrees. To see this, 
+rational functions with numerators and denominators of the same bi-degrees. To see this, 
 observe

### 2017-08-27 surfaces-write-up/surface-paper.tex
first round of edits to mrl revision 3

@@
 \theoremstyle{plain}
-  \newtheorem{thm}{Theorem}[section]
+  \newtheorem{thm}{Theorem}[subsection]
   \newtheorem{prop}[thm]{Proposition}
@@
 
-\numberwithin{equation}{section}
+\numberwithin{equation}{subsection}
 
@@
 \newcommand\pdeg{\delta}
-\newcommand\hirz{\mathbb{F}}
+\newcommand\hirz{F}
 \newcommand\mss{\mathscr{S}}
@@
 
-\title{Generalized canonical rings of $\bq$-divisors on minimal rational surfaces}
+\title[Section Rings of $\bq$-divisors]{Section Rings of $\bq$-divisors on minimal rational surfaces}
 
@@
 \begin{abstract}
- 	We give bounds on the degree of generation and relations of
-	generalized 
-	canonical rings of arbitrary $\bq$-divisors on projective spaces of 
-	all dimensions and Hirzebruch surfaces. We also give exact bounds 
-	on the degree of generators and relations of the generalized
-	canonical ring of 
-	any effective $\bq$-divisor on projective space.
+ 	We bound the degrees of generators and relations of
+	section rings associated to arbitrary $\bq$-divisors on projective spaces of 
+	all dimensions and Hirzebruch surfaces.
 \end{abstract}
@@
 For any Weil $\bq$-divisor $D$ on a rational surface $X$, the graded
-\textbf{generalized canonical ring} is $R(X, D) := \bigoplus_{d \geq 0} u^d
-H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy variable to keep
+\textbf{section ring} is $R(X, D) := \bigoplus_{d \geq 0}
+H^0(X, \lfloor dD \rfloor)$.
+%, where $u$ is a dummy variable to keep
 track of degree.
-We study the generators and relations of generalized canonical
+We study the generators and relations of section 
 rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
@@
 $\hirz_m$, we give bounds on the generators and relations of
-$R(X, D)$. In particular, we give a minimal presentation of the
-generalized canonical ring when $X = \bp^m$ and $D$ is any effective
+$R(X, D)$. In particular, we give a presentation of the
+section ring when $X = \bp^m$ and $D$ is any effective
 $\bq$-divisor.
@@
 O'Dorney \cite{dorney:canonical}, which gives similar descriptions
-of generalized canonical rings for general $\bq$-divisors on $\bp^1$. This
+of section rings for general $\bq$-divisors on $\bp^1$. This
 study also has connections to the papers by Voight--Zureick-Brown 
@@
 \begin{align*}
-	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
+	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} H^0 \left(
 	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
@@
 $\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
-
-\subsection{Modular Forms}
-\label{subsection:modular-forms}
-The work in this paper was motivated by 
-potential applications to
-calculating a presentation of certain rings of
-Hilbert 
-modular forms and Siegel modular forms. 
-Recall that Hilbert and Siegel 
-modular forms are two generalizations of modular forms to higher dimensions,
-as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
-Voight and Zureick-Brown show that 
-one can translate the analytic category of 1-dimensional complex orbifolds to
-the algebraic category of stacky curves \cite[Proposition 6.1.5]{vzb:stacky}. 
-If one could generalize this result to yield an equivalence of
-categories between an appropriate subcategory of $m$-dimensional orbifolds and
-a subcategory of $m$-dimensional algebraic spaces,
-this would allow us to translate rings of Hilbert modular forms
-and Siegel modular forms whose coarse space is a projective space or a
-Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
-Thereby, if our results could be extended to all rational surfaces,
-they would give a bound on generators and relations for such
-rings of Hilbert and Siegel modular forms parameterized by rational
-Hilbert and Siegel modular surfaces.
-This would be interesting because such modular surfaces tend to be
-immensely complicated: ``Already for $g = 2$, the boundary of this fundamental domain is complicated; Gottschling found that it possesses $28$ boundary pieces'' \cite[p.\ 7]{geer:siegel-modular}.
-Since our results only apply to minimal rational surfaces, and because the rings of Hilbert and Siegel modular forms are so complex, we were unable
-to use our work to compute the canonical ring of an explicit modular surface.
-Although we did not obtain a bound on the degree of generators and relations
-for general rational surfaces, the restricted class of rational varieties we consider still required significant work.
 
@@
 \lfloor \alpha_i \rfloor D_i$. Let 
-$R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$
-denote the generalized canonical ring associated to the $\bq$-divisor $D$. 
+$R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)$
+denote the section ring associated to the $\bq$-divisor $D$. 
+We often alternatively write
+$R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$, where $u$ is a dummy
+variable to keep track of the degree.
 We use $R_D$ as notation for $R(X,D)$ when $X$ is understood from context.
@@
 Throughout, we work over a fixed algebraically closed field $\bk$.
-Since generator and relation degrees are preserved under base change to the algebraic closure, assuming that $\bk$ is algebraically closed is no restriction
+Since generator and relation degrees are preserved under base change to the algebraic closure, 
+as cohomology commutes with flat base change,
+assuming that $\bk$ is algebraically closed is no restriction
 on generality and the results hold equally well over an arbitrary field.
@@
 the degree of generators and relations of
-generalized canonical rings on $\bp^m$. The first applies
+section rings on $\bp^m$. The first applies
 to effective $\bq$-divisors and the second applies to arbitrary
@@
 
-Then the generalized canonical ring $R_D$
+Then the section ring $R_D$
 is generated in degrees at most $\max_{0 \leq i \leq n}{k_i}$ with
@@
 \end{restatable}
-
-\begin{rem}
-\label{rem:proj-tight-bounds-eff}
-Note that the bounds
-given in Theorem ~\ref{thm:proj-effective-intro}
-are tight and are typically attained, as explained in
-Remark ~\ref{rem:exact-effective-bounds}.
-\end{rem}
 
@@
 \label{rem:proj-tight-bounds}
-Note that the bounds given in Theorem 
+The bounds
+given in Theorem ~\ref{thm:proj-effective-intro}
+are tight and are typically attained, as explained in
+Remark ~\ref{rem:exact-effective-bounds}.
+Simlarly, the bounds given in Theorem 
 ~\ref{thm:proj-generators-relations} are asymptotically
@@
 
-In Section \ref{sec:hirz}, we shift our attention to Hirzebruch surfaces. Recall that for each $m \geq 0$ we can define the
-Hirzebruch surface $F_m := \proj(\sym^\bullet \sco_{\bp^1} \oplus
-\sco_{\bp^1}(m))$ as a projective bundle over $\bp^1$.
+In Section \ref{sec:hirz}, we shift our attention to Hirzebruch surfaces. Recall that for each $m \geq 0$ we define the
+Hirzebruch surface $F_m := \proj \sym (\sco_{\bp^1} \oplus
+\sco_{\bp^1}(m))$, viewed as a projective bundle over $\bp^1$.
 Let $u,v$ the projective coordinates on the base $\bp^1$ and let $z,w$ be the projective coordinates
@@
 \ref{sec:hirz}.
-Since Hirzebruch surfaces are smooth, the natural map from Cartier
-divisors to Weil divisors is an isomorphism.
-In other words, all Cartier divisors arise as the zero locus
-of a section of some line bundle. We implicitly use this in the
-statement of the following theorem. The analogous fact for
-projective space was also implicitly used in Theorems
-~\ref{thm:proj-effective-intro} and ~\ref{thm:proj-generators-relations}.
+%Since Hirzebruch surfaces are smooth, the natural map from Cartier
+%divisors to Weil divisors is an isomorphism.
+%In other words, all Cartier divisors arise as the zero locus
+%of a section of some line bundle. We implicitly use this in the
+%statement of the following theorem. The analogous fact for
+%projective space was also implicitly used in Theorems
+%~\ref{thm:proj-effective-intro} and ~\ref{thm:proj-generators-relations}.
 
@@
 \ref{thm:hirz-generators-relations} provide bounds on generators
-and relations for the generalized canonical ring of any $\bq$-divisor on any
+and relations for the section ring of any $\bq$-divisor on any
 minimal rational surface. Section \ref{sec:conc} discusses further questions.
+
+\subsection{Modular Forms}
+\label{subsection:modular-forms}
+The work in this paper was motivated by 
+potential applications to
+calculating a presentation of certain rings of
+Hilbert 
+modular forms and Siegel modular forms. 
+Recall that Hilbert and Siegel 
+modular forms are two generalizations of modular forms to higher dimensions,
+as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
+%Voight and Zureick-Brown show that 
+%one can translate the analytic category of 1-dimensional complex orbifolds to
+%the algebraic category of stacky curves \cite[Proposition 6.1.5]{vzb:stacky}. 
+%If one could generalize this result to yield an equivalence of
+%categories between an appropriate subcategory of $m$-dimensional orbifolds and
+%a subcategory of $m$-dimensional algebraic spaces,
+%this would allow us to translate 
+%rings of Hilbert modular forms
+%and Siegel modular forms whose coarse space is a projective space or a
+%Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
+If the bounds given in 
+Theorem~\ref{thm:proj-generators-relations} and Theorem~\ref{thm:hirz-generators-relations}
+could be extended to all rational surfaces, instead of just minimal ones,
+they would give a bound on generators and relations for 
+rings of Hilbert and Siegel modular forms parameterized by rational
+Hilbert and Siegel modular surfaces.
+See Theorem~\ref{sec:conc} for a potential approach for generalizing our results to arbitrary rational surfaces.
+This would be interesting because such modular surfaces tend to be
+immensely complicated. 
+%``Already for $g = 2$, the boundary of this fundamental domain is complicated; Gottschling found that it possesses $28$ boundary pieces'' \cite[p.\ 7]{geer:siegel-modular}.
+
+Since our results only apply to minimal rational surfaces, and because the rings of Hilbert and Siegel modular forms are so complex, we were unable
+to use our work to compute the canonical ring of an explicit modular surface.
+Although we did not obtain a bound on the degree of generators and relations
+for general rational surfaces, the restricted class of rational varieties we consider still required significant work.
 
@@
 ~\ref{thm:proj-effective-intro}.
-Note that if $\deg D < 0$ the
-generalized canonical ring is concentrated in degree 0, and if
-$\deg D = 0$, then the generalized canonical ring has a single
+If $\deg D < 0$, the
+section ring is concentrated in degree 0, and if
+$\deg D = 0$, then the section ring has a single
 generator. Therefore, for the remainder of this section,
@@
 \cite{dorney:canonical}. We also give an explicit description of the
-generators of the generalized canonical ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}
+generators of the section ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}.
 
@@
 choose an
-isomorphism $\bp^m \cong \proj V$ for some vector space $V$ with
-basis $x_0,\ldots, x_m$.
+isomorphism $\bp^m \cong \proj \bk[x_0, \ldots, x_m]$.
 
@@
 Before bounding the degree of generation and relations of
-generalized canonical rings on projective space, we first
+section rings on projective space, we first
 describe a particular choice of basis for $R_D$ as a $\bk$ vector
@@
 \label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ satisfying
+The functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ \rm{(}recall $u$ is a dummy variable keeping
+track of the degree\rm{)}
+satisfying
 both of the following conditions
@@
 \noindent
+for $c_0, \ldots, c_n \in \bz$
 span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, such functions 
@@
 \begin{enumerate}[resume]
-	\item $c_i = -\lfloor d\alpha_i \rfloor \text{ for } i > m$
+	\item $c_i = -\lfloor d\alpha_i \rfloor \text{ for all } i > m$
 \end{enumerate}
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$.
+(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$, and are also necessary to lie in
+$H^0(\mathbb{P}^m,dD)$.
 To complete the proof, it
-suffices to check functions satisfying conditions (1-3) form
-a basis of $H^0(\bp^m,dD)$. Note that there are $\binom{m+ \deg \lfloor dD \rfloor }{m}$
-functions satisfying conditions (1-3). However we know
+suffices to check functions satisfying conditions (1)-(3) form
+a basis of $H^0(\bp^m,dD)$. There are $\binom{m+ \deg \lfloor dD \rfloor }{m}$
+functions satisfying conditions (1)-(3). However we know
 $h^0(\bp^m,dD) = \binom{m+ \deg \lfloor dD \rfloor }{m},$ so it suffices to show
-that those functions satisfying conditions (1-3) are
-independent. This follows from the assumption that $f_0,\ldots f_m$ form a
-basis of linear forms, and so all monomials in $f_0,\ldots, f_m$
-of degree $\deg \lfloor d (\deg D) \rfloor $
-form a basis of degree $\deg \lfloor d  D \rfloor$ rational functions.
+that those monomials satisfying conditions (1)-(3) are
+independent. 
+To see why these are independent, observe that monomials satisfying (1)-(3) are all of the form
+$f_0^{c_0} \cdots f_m^{c_m} \cdot g$ for the fixed monomial
+$g = f_{m+1}^{-\lfloor d\alpha_{m+1} \rfloor} \cdots f_n^{-\lfloor d\alpha_{m+1} \rfloor}$.
+For any fixed $N \in \bz$, the set 
+\begin{align*}
+ \left\{ f_0^{c_0} \cdots f_m^{c_m} : (c_0, \ldots, c_m) \in \bz^{m+1}, \sum_{i=0}^m c_i = N \right\}	
+\end{align*}
+forms an independent set over $\bk$.
+Therefore, multiplying the monomials in the above set with the $g$ also forms an independent set, and these are precisely the monomials satisfying (1)-(3) 
+with $N = -\deg g$.
 \end{proof}
@@
 In this subsection, we restrict attention to the case of effective
-fractional divisors $D \in \bq \otimes_\bz \di \bp^m$. We give an explicit presentation of the generalized canonical ring when $D$ is an effective
+fractional divisors $D \in \bq \otimes_\bz \di \bp^m$. We give an explicit presentation of the section ring when $D$ is an effective
 divisor.
@@
 and $j \in \{0,\ldots, m\}$ be the smallest index such that $w_j$ is
-nonzero. Define a relation on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
+nonzero. Define a partial ordering
+on $\bz^{m+1}$ by $\vec{v} \prec \vec{w}$ if $i \leq j$.
 \end{defn}
@@
 \otimes_\bz \di \bp^m$ and $D = D' + \alpha H$, with $\alpha =
-\frac{p}{q} \in \bq_{>0}$ and $H := V(x_k)$ a hyperplane of $\bp^m$.
+\frac{p}{q} \in \bq_{>0}$, $H := V(x_k)$ a hyperplane of $\bp^m$,
+and $H \notin \supp(D').$
 Let
@@
 be the convergents of the Hirzebruch-Jung continued fraction of
-$\alpha$. Then, the generalized canonical ring
+$\alpha$. Then, the section ring
 \[
@@
 \noindent
-has a minimal presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
-{{m + c_i - 1} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
+has a presentation over $R_{D'}$ consisting of the $\sum_{i = 0}^{r}
+{{m + c_i} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
 x^{\vec{v}}}{x_k^{c_i}}$ where $0 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
@@
 \noindent
+\todo{should we rule out other stupid relations, like those given when w< v?}
 where $\vec{y}$ and $\vec{z}$ are the unique
@@
 \sssec*{Idea of Proof:}
-The proof follows in four steps. First, we demonstrate that
-the $F_{i}^{\vec{v}}$'s form a set of minimal generators of $R_D$
-over $R_{D'}$ using their construction in terms of convergents of the
-Hirzebruch-Jung continued fraction of $\alpha$. Then, since the
+The proof follows in three steps. 
+%First, we demonstrate that
+%the $F_{i}^{\vec{v}}$'s form a set of minimal generators of $R_D$
+%over $R_{D'}$ using their construction in terms of convergents of the
+%Hirzebruch-Jung continued fraction of $\alpha$. 
+First, since the
 $F_{i}^{\vec{v}}$ generate
@@
 $G_{i,j}^{\vec v, \vec w}$ lies in $R_{D'}$, we obtain the
-relations $G_{i, j}^{\vec{v}, \vec{w}}$. We derive the relations
+relations $G_{i, j}^{\vec{v}, \vec{w}}$. 
+Then, we derive the relations
 $L_{i, j}^{\vec{v}, \vec{w}}$ by considering when products of
@@
 \begin{proof}
-For simplicity, we give a proof for when $D' = 0$, but the general
-can be analogously proved by replacing the orders of zeros and poles
-by the order of zeros and poles relative to $D'$. That is,
-one can work with rational sections of $\mathscr O_{\bp^m}(D')$
-instead of rational sections of $\mathscr O_{\bp^m}$,
-and the following proof goes through otherwise unchanged.
-
-We will first check that $F^{\vec v}_i$ determine a system of minimal
-generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} \colon \deg \vec{v} =
-\left\lfloor
-\frac{p}{q} \right\rfloor \right\}$ are minimal generators in
-degree $1$. Now let $i > 1$. Suppose $F_i^{\vec{v}}$ were not
-minimal for some $\vec{v} \in \mss_i$. Then $F_i^{\vec{v}} =
-F_{s}^{\vec{y}} F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and
-$\vec{y}, \vec{z} \in \bz_{ \geq 0}^{m + 1}$. In particular, we see
-that 
-\begin{align*}
-	&d_i = s + t \\
-	&c_i = \deg \vec{v} = \deg \vec{y} + \deg \vec{z}
-\end{align*}
-
-\noindent
-so $\frac{c_i}{d_i}$ is the mediant of the rational numbers
-$\frac{\deg \vec{y}}{s}, \frac{\deg \vec{z}}{t}$ which both
-do not exceed $\alpha$. One of $\frac{\deg \vec{y}}{s},
-\frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
-and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that
-$\frac{c_i}{d_i}$ is a convergent of the Hirzebruch-Jung continued
-fraction of $\alpha$. Therefore, none of the $F_i^{\vec v}$ are redundant.
-
+As a first step, we reduce to the case $D' = 0$.
+Using that $D$ is effective, we can write
+$R_D = R_{D'} + R_{\alpha H}$ (where the sum is nearly a direct sum, except 
+the $(R_{D'})_d \cap (R_{\alpha H})_d$ is the one dimensional subspace generated by $u^d$).
+Then, to give a presentation of $R_D$ over $R_D'$,
+it suffices to give a presentation of $R_{\alpha H}$:
+generators of $R_{\alpha H}$ map to generators of $R_D$ over $R_{D'}$ under the inclusion $\iota: R_{\alpha H} \rightarrow R_D$
+and relations map to a full set of relations for $R_D$ over $R_{D'}$.
+%is equivalent to giving a presentation
+%For simplicity, we give a proof for when $D' = 0$, but the general case
+%can be analogously proved by replacing the orders of zeros and poles
+%by the order of zeros and poles relative to $D'$. That is,
+%one can work with rational sections of $\mathscr O_{\bp^m}(D')$
+%instead of rational sections of $\mathscr O_{\bp^m}$,
+%and the following proof goes through otherwise unchanged.
+
+Hence, for the remainder of the proof, we assume $D' = 0$.
+%We will first check that $F^{\vec v}_i$ determine a system of minimal
+%generators of $R_D$. We know $\left\{F_{1}^{\vec{v}} \colon \deg \vec{v} =
+%\left\lfloor
+%\frac{p}{q} \right\rfloor \right\}$ are minimal generators in
+%degree $1$. Now let $i > 1$. Suppose $F_i^{\vec{v}}$ were not
+%minimal for some $\vec{v} \in \mss_i$. Then $F_i^{\vec{v}} =
+%F_{s}^{\vec{y}} F_{t}^{\vec{z}}$ for some $s, t \in \bn$ and
+%$\vec{y}, \vec{z} \in \bz_{ \geq 0}^{m + 1}$. In particular, we see
+%that 
+%\begin{align*}
+%	&d_i = s + t \\
+%	&c_i = \deg \vec{v} = \deg \vec{y} + \deg \vec{z}
+%\end{align*}
+%
+%\noindent
+%so $\frac{c_i}{d_i}$ is the mediant of the rational numbers
+%$\frac{\deg \vec{y}}{s}, \frac{\deg \vec{z}}{t}$ which both
+%do not exceed $\alpha$. One of $\frac{\deg \vec{y}}{s},
+%\frac{\deg \vec{z}}{t}$ must be at least $\frac{c_i}{d_i}$
+%and $s$ and $t$ are both less than $d_i$, which contradicts the assumption that
+%$\frac{c_i}{d_i}$ is a convergent of the Hirzebruch-Jung continued
+%fraction of $\alpha$. Therefore, none of the $F_i^{\vec v}$ are redundant.
+%
 Next we show that $F^{\vec v}_i$ generate all of $R_D$. In the case $m = 1$, O'Dorney \cite[Theorem 6]
@@
 $\frac{u^{\beta} x^{\vec{v}}}{x_k^\gamma} \in R_D$ as a product of generators,
-this shows that $F_i^{\vec v}$ minimally generate $R_D$.
+this shows that $F_i^{\vec v}$ generate $R_D$.
 
@@
 \label{rem:proj-two-points}
-Note that we cannot extend this result to the case when
+We cannot extend this result to the case when
 $D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
@@
 in Example ~\ref{eg:hyperplane}, the degrees of generation of the
-generalized canonical ring of a general $\bq$-divisor supported on two
+section ring of a general $\bq$-divisor supported on two
 hyperplanes cannot be bounded so tightly. The two-point
@@
 hyperplanes. However, for $m \geq 2$, there are hypersurfaces which
-are not unions of hyperplanes.
-We now address this general case, giving an inductive presentation of generalized canonical rings of effective divisors, and a tight bound on the degrees of their generators and
+are not unions of hyperplanes. We now address this general case, giving an inductive presentation of section rings of effective divisors, and a tight bound on the degrees of their generators and
 relations.
 
-\restateeffective*
-
-\begin{proof}
+%\restateeffective*
+\begin{proof}[Proof of Theorem~\ref{thm:proj-effective-intro}]
 We proceed by induction on $n$.
@@
 a hyperplane in $\bp^{\binom{{m + \pdeg}}{\pdeg} - 1}$ with $\nu_\pdeg^m(\bp^m)$.
-Now, note that the ring $R_{\alpha C}$ is isomorphic to the
-$\pdeg$ Veronese subring of $R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0))$ and so
-the generalized canonical ring $R_H$ of the hyperplane $H \subset \bp^{\binom{m+\pdeg}{\pdeg}-1}$
-restricted to $\nu_\pdeg^m(C)$ is isomorphic to $R_C$.
+Now, the ring $R_{\alpha C}$ is isomorphic to the
+$\pdeg$ Veronese subring of 
+\[R_{\alpha V(x_0)} = \bigoplus_{d \geq 0} u^d H^0(\bp^m, d \alpha V(x_0)).\]
 Therefore, we can bound the degree of generators and relations of
@@
 \label{rem:exact-effective-bounds}
-Note that the proof of Theorem ~\ref{thm:proj-effective-intro} not only gives bounds on the degrees of the generators and relations, but actually gives an explicit method for computing the presentation.
-In particular, these bounds are tight.
-The generator bound is always achieved and the bound on the relations is achieved if $m \geq 2$.
+The proof of Theorem ~\ref{thm:proj-effective-intro} not only gives bounds on the degrees of the generators and relations, but actually gives an explicit method for computing the presentation. 
+Also, a minimal generating set of $R_D$ over $R_{D'}$ in 
+Theorem~\ref{thm:proj-one-point}
+can be given as a subset of the generating set given in 
+Theorem~\ref{thm:proj-one-point}. Further,
+one can verify a minimal generating
+set necessarily contains generators in each of the degrees $d_0, \ldots, d_r$
+using the definition of 
+Hirzebruch-Jung continued fractions.
+In particular,
+the bounds of
+Theorem ~\ref{thm:proj-effective-intro}
+are tight. The generator bound is always achieved and the bound on the relations is achieved if $m \geq 2$.
 \end{rem}
 
+Before giving bounds for arbitrary divisors on projective space in Subsection~\ref{ssec:arbitrary-projective},
+we give a detailed example of the generators and relations for a
+section ring associated to an effective divisor on projective space.
+\begin{example}
+	\label{example:}
+	In this example, we work out generators and relations 
+	for the section ring $R(\bp^2, D)$ with
+	\begin{align*}
+		D := \frac{1}{6}V(x^2 + y^2 + z^2) + \frac{2}{5}V(x).
+	\end{align*}
+	We loosely follow the
+	algorithm
+	described in the course of the 
+	proof of Theorem~\ref{thm:proj-effective-intro} and use notation from the statement of Theorem~\ref{thm:proj-effective-intro}.
+
+	For ease of notation, let $h := x^2 + y^2 + z^2$
+	and let $D' := \frac{1}{6}V(h)$.
+	We first compute generators and relations for $R_{D'}$,
+	then compute generators and relations for $R_D$ over $R_{D'}$,
+	and finally put them together to obtain generators and relations
+	for $R_D$.
+
+	To start, we compute generators and relations for $R_{D'}$.
+	Indeed, applying \ref{thm:proj-one-point} and scaling
+	the degrees by 2, we see that $\frac{1}{6}$ has convergents
+	given by
+	\begin{align*}
+		0 = \frac{0}{1} < \frac{1}{6},
+	\end{align*}
+	and so the generators are given by 
+	\begin{align}
+	\begin{aligned}
+	\label{equation:d'-generators}
+		F_0^{'(0,0,0)} &= u^1 \\
+		F_1^{'(2,0,0)} &= \frac{u^6 x^2}{h}, \\
+		F_1^{'(1,1,0)} &= \frac{u^6 xy}{h}, \\ 
+		F_1^{'(1,0,1)} &= \frac{u^6 xz}{h}, \\
+		F_1^{'(0,2,0)} &= \frac{u^6 y^2}{h}, \\
+		F_1^{'(0,1,1)} &= \frac{u^6 yz}{h},  \\
+		F_1^{'(0,0,2)} &= \frac{u^6 z^2}{h}.
+	\end{aligned}
+	\end{align}
+Further, the relations in $R_{D'}$ are given by 	
+\begin{align}	
+			\begin{aligned}
+	\label{equation:d'-relations}
+		L_{1,1}^{'(1,1,0), (1,0,1)} &= \frac{u^6 xy}{h}\frac{u^6 xz}{h} - \frac{u^6x^2}{h}\frac{u^6yz}{h},\\
+		L_{1,1}^{'(1,0,1), (0,1,1)} &= \frac{u^6 xz}{h}\frac{u^6 yz}{h} - \frac{u^6xy}{h}\frac{u^6z^2}{h},\\
+		L_{1,1}^{'(1,0,1), (0,2,0)} &= \frac{u^6 xz}{h}\frac{u^6 y^2}{h} - \frac{u^6xy}{h}\frac{u^6yz}{h}, \\
+		L_{1,1}^{'(1,1,0), (1,1,0)} &= \frac{u^6 xy}{h}\frac{u^6 xy}{h} - \frac{u^6x^2}{h}\frac{u^6y^2}{h}, \\
+		L_{1,1}^{'(1,0,1), (1,0,1)} &= \frac{u^6 xz}{h}\frac{u^6 xz}{h} - \frac{u^6x^2}{h}\frac{u^6z^2}{h}, \\
+		L_{1,1}^{'(0,1,1), (0,1,1)} &= \frac{u^6 yz}{h}\frac{u^6 yz}{h} - \frac{u^6y^2}{h}\frac{u^6z^2}{h}.
+\end{aligned}
+\end{align}
+
+	Next, we describe generators and relations for $R_D$ over $R_{D'}$.
+	Indeed, in this case, $\frac{2}{5}$ has convergents given by
+	\begin{align*}
+		0 = \frac{0}{1} < \frac{1}{3} < \frac{2}{5}.
+	\end{align*}
+	Therefore, the generators of $R_D$ over $R_{D'}$ are given by
+	\begin{align}
+		\begin{aligned}
+		\label{equation:d-generators}
+		F_0^{(0,0,0)} &= u^1, \\
+		F_1^{(0,1,0)} &= \frac{u^3y}{x}, &F_1^{(0,0,1)} &= \frac{u^3z}{x}, \\
+		F_2^{(0,2,0)} &= \frac{u^5y^2}{x^2}, &F_2^{(0,1,1)} &= \frac{u^5yz}{x^2}, &F_2^{(0,0,2)} &= \frac{u^5z^2}{x^2}.
+	\end{aligned}
+	\end{align}
+Note that the generator $F_3^{(1,0,0)} = \frac{u^3x}{x}$ could be included, but it is redundant as it is equal to $(u^1)^3$.
+	Similarly, the generators $\frac{u^5x^2}{x^2}, \frac{u^5xy}{x^2}, \frac{u^5xz}{x^2}$ are redundant.
+	Furthermore, we have relations given by
+	\begin{align}
+		\begin{aligned}
+		\label{equation:d-relations}
+		G_{0,2}^{(0,0,0),(0,2,0)} &= u \cdot \frac{u^5 y^2}{x^2} - \left( \frac{u^3y}{x} \right)^2 \\
+		G_{0,2}^{(0,0,0),(0,1,1)} &= u \cdot \frac{u^5 yz}{x^2} -  \frac{u^3y}{x} \frac{u^3z}{x} \\
+		G_{0,2}^{(0,0,0),(0,0,2)} &= u \cdot \frac{u^5 z^2}{x^2} - \left( \frac{u^3z}{x} \right)^2 \\
+		L_{1,2}^{(0,0,1), (0,2,0)} &= \frac{u^3z}{x}\cdot \frac{u^5y^2}{x^2} - \frac{u^3y}{x}\frac{u^5yz}{x^2} \\
+		L_{1,2}^{(0,0,1), (0,1,1)} &= \frac{u^3z}{x}\cdot \frac{u^5yz}{x^2} - \frac{u^3y}{x}\frac{u^5z^2}{x^2} \\
+		L_{2,2}^{(0,1,1),(0,1,1)} &= \frac{u^5yz}{x^2}\cdot \frac{u^5 yz}{x^2} - \frac{u^5y^2}{x^2}\frac{u^5z^2}{x^2}.
+\end{aligned}
+\end{align}
+
+	Then, combining the above, generators for the ring $R_D$ are given by	
+	\eqref{equation:d'-generators} together with
+	Generators and \eqref{equation:d-generators}
+	and relations are given
+	\eqref{equation:d'-relations} together with \eqref{equation:d-relations}.
+\end{example}
+
 \ssec{Bounds for Arbitrary Divisors on Projective Space}
+\label{ssec:arbitrary-projective}
 
@@
 Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ and let $f_i$ be
-homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$
+homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ and
 $\deg(f_i) = a_i$ for all $i$.
@@
 projective space. We bound the generators in Lemma ~\ref{lem:proj-generators}, and we use Lemmas ~\ref{lem:composite-map}, ~\ref{lem:bound-ker-chi}, and ~\ref{lem:proj-relations-psi} to bound the 
-degree of relations in the proof of Theorem ~\ref{thm:proj-generators-relations}.
-Note that Proposition ~\ref{prop:cone-generation}, Lemma ~\ref{lem:composite-map}, and Lemma ~\ref{lem:bound-ker-chi} are quite
+degree of relations in the proof of Theorem ~\ref{thm:proj-generators-relations}. Proposition ~\ref{prop:cone-generation}, Lemma ~\ref{lem:composite-map}, and Lemma ~\ref{lem:bound-ker-chi} are quite 
 general and will also be used in Section ~\ref{sec:hirz} to bound the 
 degree of generators and relations on Hirzebruch surfaces.
+
+Recall that for a semigroup $\Sigma \subset \bz^m$ we say $e_0, \ldots, e_n \in \Sigma$ are a set of {\bf extremal rays}
+for $\Sigma$ if 
+$\Sigma$ is contained in the $\bq_{\geq 0}$ span of
+$e_0, \ldots, e_n$.
 
@@
 Suppose $e_0, \ldots, e_t \in \Sigma$ with $e_i = (\pdeg_i, c_0^i,
-\ldots, c_n^i)$ are a set of {\bf extremal rays} of $\Sigma$,
-i.e.~ $\Sigma$ is contained in the $\bq_{\geq 0}$ span of
-$e_0, \ldots, e_n$.
+\ldots, c_n^i)$ are a set of extremal rays of $\Sigma$.
 
@@
 $\ell_i = \lcm_{j \neq i} (k_j)$. Then, $R_D$ is generated in degrees at most $\sum_{i=0}^n \ell_i \bida_i.$
-
 \end{lem}
@@
 	\sum_{i=0}^n \ell_i \bida_i.
-\]
-\end{proof}
+\qedhere
+\]\end{proof}
 
@@
 \label{lem:composite-map}
-Let $X$ be an arbitrary scheme and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
+Let $X$ be a $\bk$ variety and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
 surjection $\phi\colon \bk[w_1,\ldots, w_r] \rightarrow R_D$ given by $w_i
@@
 \begin{proof}
-First, note that surjectivity of $\chi$ implies we have an exact sequence
+First, surjectivity of $\chi$ implies we have an exact sequence
 \[
@@
 By combining the above results, we get our main theorem bounding
-the generator and relation degrees of the generalized canonical ring of any
+the generator and relation degrees of the section ring of any
 $\bq$-divisor on projective space.
 
-\restateproj*
-
-\begin{proof}
+%\restateproj*
+
+\begin{proof}[Proof of Theorem~\ref{thm:proj-generators-relations}]
 The bound on degree of generation is precisely the content of Lemma 
@@
 	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
+	\qedhere
 \]
@@
 $\pi$, we may need to assume that the base field is infinite.
-Note that by the Remark immediately following Theorem 8 in 
-\cite{dorney:canonical},
+By
+\cite[Remark, p. 9]{dorney:canonical},
 the given bounds on the generators and relations of
@@
 \label{sec:hirz}
+\subsection{}
 The aim of this section is to prove Theorem
 ~\ref{thm:hirz-generators-relations}, bounding the degree of
-generators and relations of the generalized canonical ring of a $\bq$-divisor
+generators and relations of the section ring of a $\bq$-divisor
 on any Hirzebruch surface.
@@
 restriction. If either of the bi-degrees of $D$ are negative,
-then the generalized canonical ring is concentrated in degree 0. If one of the
+then the section ring is concentrated in degree 0. If one of the
 bi-degrees is 0, say the first one is 0, then $R_D$ is isomorphic
@@
 divisors with of the desired form with a coefficient $0$).
-Also, note that, $f_1$ and $f_2$ are independent linear
+Also, $f_1$ and $f_2$ are independent linear
 polynomials in $u$ and $v$ and $f_3$ and $f_4$ are independent
@@
 \label{lem:hirz-generators}
-For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \bq \otimes_\bz \hirz_m$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the generalized canonical ring $R_D$ is generated in degrees at most
+For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \bq \otimes_\bz \hirz_m$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the section ring $R_D$ is generated in degrees at most
 \begin{equation}\label{eqn:def-sigma}
@@
 can be expressed as $H \cap \overline{e_i e_j},$ where $i \neq j$ and $e_i,
-e_j \notin H$. Note that $e_{i,j}$ is only defined in the case
+e_j \notin H$. In this case, $e_{i,j}$ is only defined when
 $\# \{H \cap \overline{e_i, e_j}\} = 1$.
@@
 	i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
-\]
-\end{proof}
+\qedhere
+\]\end{proof}
 
@@
 
-\textbf{For the remainder of this proof:} we fix $i \in \{1, \ldots,
+For the remainder of this proof: we fix $i \in \{1, \ldots,
 n\}$ and fix a relation of the form $u^d (z_i - \beta_i) \prod_{j =
 1}^n z_j^{c_j}$ as we seek to bound the degree of generation of the
-ideal $(\beta_i - z_i) \cap \ker(\psi)$. Note that there are no
+ideal $(\beta_i - z_i) \cap \ker(\psi)$. There are no
 relations for $i\in \{1, 2, 3, 4\}$ as then $\beta_i - z_i = 0 \in
@@
 
-Note that
+Then,
 \begin{align}
@@
 	\bidb_i) \bigr) \right)\le 2\rho.
+	\qedhere
 \]
@@
 \label{sec:conc}
+\subsection{}
 Recall that every minimal rational surface is either isomorphic to
@@
 ~\ref{thm:proj-generators-relations} and ~\ref{thm:hirz-generators-relations}, we have given bounds for the generators and relations
-of arbitrary generalized canonical rings on any minimal rational surface. A
+of arbitrary section rings on any minimal rational surface. A
 natural extension of our results is the following.
@@
 to bound the degree of generators and relations of the 
-generalized canonical ring of a divisor on a blow-up of a given surface
-in terms of the generalized canonical
+section ring of a divisor on a blow-up of a given surface
+in terms of the section 
 rings of some associated divisors that given surface.
@@
 Another direction to generalize the work in this paper
-would be to try to express generalized canonical rings of $\bq$-divisors on
+would be to try to express section rings of $\bq$-divisors on
 $X \times Y$ in terms of those on $X$ and $Y$. In this paper,
-we bounded the degrees of presentations on generalized canonical rings on $\bp^1 \times \bp^1 \cong \hirz_0$.
+we bounded the degrees of presentations on section rings on $\bp^1 \times \bp^1 \cong \hirz_0$.
 Perhaps similar techniques can be used to bound
-degrees of presentations on generalized canonical rings on $(\bp^1)^k$ or
+degrees of presentations on section rings on $(\bp^1)^k$ or
 more generally on $(\bp^1)^{i_1} \times \cdots (\bp^k)^{i_k}.$

### 2017-09-15 surfaces-write-up/surface-paper.tex
second round of edits to mrl revision 3

@@
 	section rings associated to arbitrary $\bq$-divisors on projective spaces of 
-	all dimensions and Hirzebruch surfaces.
+	all dimensions and Hirzebruch surfaces. For section rings of
+	effective $\bq$-divisors on projective spaces, we find 
+	the best possible bound on
+	the degrees of generators and relations.
 \end{abstract}
@@
 Let $D = \sum_{i = 0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
-with $\alpha_i = \frac{c_i}{k_i}\in \bq$ in reduced form. Write $\ell_i := \lcm
-_{j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m \cong \proj
-\bk[x_0, \ldots, x_m]$ and define $D_i := V(f_i)$, for some $f_i \in \bk[x_0, \ldots, 
-x_m]$. Now suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
+with $\alpha_i = \frac{c_i}{k_i}\in \bq$ in reduced form. Write
+$\ell_i := \lcm_{0\le j \le n, j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m
+\cong \proj \bk[x_0, \ldots, x_m]$ and let
+$f_i \in \bk[x_0, \ldots, x_m]$ such that $D_i = V(f_i)$. Now
+suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
 linear polynomials in $x_0, \ldots, x_m$ {\rm(}where we allow for 
@@
 \[
-	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
+	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0 \le i \le n}
 	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
@@
 Since our results only apply to minimal rational surfaces, and because the rings of Hilbert and Siegel modular forms are so complex, we were unable
-to use our work to compute the canonical ring of an explicit modular surface.
+to use our work to compute the section ring of an explicit modular surface.
 Although we did not obtain a bound on the degree of generators and relations
@@
 
-\section{Canonical Rings of Projective Space}
+\section{Section Rings of Projective Space}
 \label{sec:proj}
@@
 \end{align*}
+%% TODO: replace \kappa_1 and \kappa_2 with two letters or use prod notation
 
@@
 	\eqref{equation:d'-generators} together with
-	Generators and \eqref{equation:d-generators}
-	and relations are given
+	\eqref{equation:d-generators}
+	and relations are given by
 	\eqref{equation:d'-relations} together with \eqref{equation:d-relations}.
@@
 \label{eqn:factor-through-semigroup-ring}
-\begin{tikzcd}[baseline=(current  bounding  box.center)]
+\begin{tikzcd}[baseline=(current  bounding  box.center), row sep = tiny]
 \bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
@@
 \[
-\begin{tikzcd}
+\begin{tikzcd}[row sep = tiny]
 \bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
@@
 \label{eqn:proj-relation-degree}
-	\frac{\max_{0\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=0}^n \ell_i a_i.
+	\frac{\max_{0 \le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=0}^n \ell_i a_i.
 \end{align}
@@
 \[
-	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0\le i \le n}
+	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0 \le i \le n}
 	(\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
@@
 
-\section{Canonical Rings of Hirzebruch surfaces}
+\section{Section Rings of Hirzebruch surfaces}
 \label{sec:hirz}
@@
 \[
-\begin{tikzcd}
+\begin{tikzcd}[row sep = tiny]
 	\bk[w_1,\ldots, w_r] \ar {r}{\chi} & \bk[\Sigma] \ar {r}{\psi} & R_D \\
@@
 By combining the above results, we get our main theorem bounding
-the generator and relation degrees of the canonical ring of
+the generator and relation degrees of the section ring of
 $\bq$-divisors on Hirzebruch surfaces.

### 2017-10-30 surfaces-write-up/surface-paper.tex
rewrote first section of intro

@@
 H^0(X, \lfloor dD \rfloor)$.
-%, where $u$ is a dummy variable to keep
-track of degree.
-We study the generators and relations of section 
-rings for projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
-When $D$ is a general $\bq$-divisor on $\bp^m$ or
-$\hirz_m$, we give bounds on the generators and relations of
-$R(X, D)$. In particular, we give a presentation of the
-section ring when $X = \bp^m$ and $D$ is any effective
-$\bq$-divisor.
-
-In part, this work is motivated by a recent paper by
-O'Dorney \cite{dorney:canonical}, which gives similar descriptions
-of section rings for general $\bq$-divisors on $\bp^1$. This
-study also has connections to the papers by Voight--Zureick-Brown 
+%, where $u$ is a dummy variable to keep track of degree.
+In the case that $D = K_X$, the canonical divisor, the graded section ring is referred to as
+``the canonical ring'' and is a classical object of study.
+For example, if $C$ is a curve of genus $g \geq 4$, Petri's theorem
+relates the geometry of the curve $C$ to the canonical ring:
+$R(C, K_C)$ is generated in degree 1 with relations in degree 2 
+unless $C$ is hyperelliptic, trigonal, or a plane quintic
+(see
+\cite[p. 157]{saint-donat:proj} and \cite[Section 3.3]{acgh:algebraic-curves}).
+In this way, explicit descriptions of generators and relations of section rings yield
+geometric information about the underlying variety.
+
+One natural way to generalize of the classical result of Petri mentioned above
+is to examine the section rings of stacky curves (i.e., smooth proper
+geometrically connected 1-dimensional Deligne-Mumford
+stacks over a field with a dense open subscheme).
+Indeed,
+these were studied by Voight--Zureick-Brown 
 \cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring},
@@
 stacky curves.
-
-Another closely related topic is the Hassett-Keel program \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form 
+All rings of modular forms associated to Fuchsian groups can be realized as canonical rings of
+such curves, and so the above work also yields insight into such rings
+of modular forms.
+Further, 
+O'Dorney \cite{dorney:canonical} gives similar descriptions
+of section rings for arbitrary $\bq$-divisors on $\bp^1$
+(as opposed to just log canonical $\bq$-divisors and log spin canonical $\bq$-divisors).
+
+In addition to section rings of curves, section rings of certain higher dimensional
+stacks have also been studied.
+For example, the Hassett-Keel program \cite{hassett:classical-and-minimal-models}
+studies log canonical rings on ${\mathscr M}_g$ of the form 
 \begin{align*}
@@
 moduli space of stable genus $g$ curves.
-Moreover, $\bq$-divisors on surfaces also naturally
+
+Moreover, $\bq$-divisors on surfaces not only appear in the context of stacks,
+but also naturally
 appear when considering the canonical ring of surfaces of Kodaira dimension 1.
@@
 $\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
+
+In this paper, we continue the study of section rings of
+surfaces and higher dimensional varieties, examining section rings of
+projective spaces $\bp^m$ and Hirzebruch surfaces $\hirz_m$.
+When $D$ is a general $\bq$-divisor on $\bp^m$ or
+$\hirz_m$, we give bounds on the generators and relations of
+$R(X, D)$. In particular, we give a presentation of the
+section ring when $X = \bp^m$ and $D$ is any effective
+$\bq$-divisor.
 
@@
 Remark ~\ref{rem:exact-effective-bounds}.
-Simlarly, the bounds given in Theorem 
+Similarly, the bounds given in Theorem 
 ~\ref{thm:proj-generators-relations} are asymptotically

### 2017-10-30 surfaces-write-up/surface-paper.tex
surfaces: address 29 & 31

@@
 %
+
 Next we show that $F^{\vec v}_i$ generate all of $R_D$. In the case $m = 1$, O'Dorney \cite[Theorem 6]
@@
 of $(d_h, c_h)$ and $(d_{h + 1}, c_{h + 1})$ for
-some $h \in \{0, \ldots, r\}$. A similar strategy works in the case $m > 1$. Let $(\beta, \gamma) = \kappa_1
-(d_h, c_h) + \kappa_2 (d_{h + 1}, c_{h + 1})$ for $\kappa_1, \kappa_2 \in
+some $h \in \{0, \ldots, r\}$. A similar strategy works in the case $m > 1$. Let $(\beta, \gamma) = \lambda
+(d_h, c_h) + \kappa (d_{h + 1}, c_{h + 1})$ for $\lambda, \kappa \in
 \bz_{\geq 0}$. Any element $\frac{u^{\beta}
@@
 	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}} = \left(\frac{u^{d_h}}
-	{x_k^{c_h}}\right)^{\kappa_1} \left(\frac{u^{d_{h + 1}}}
-	{x_k^{c_{h + 1}}}\right)^{\kappa_2} x^{\vec{v}}.
+	{x_k^{c_h}}\right)^{\lambda} \left(\frac{u^{d_{h + 1}}}
+	{x_k^{c_{h + 1}}}\right)^{\kappa} x^{\vec{v}}.
 \end{align*}
@@
 \noindent
-We can then write $\vec{v}  = \sum_{\lambda=1}^{\kappa_1}\vec{w}_{(\lambda)} +
-\sum_{\eta=1}^{\kappa_2} \vec z_{(\eta)}$ with $w_{(\lambda)} \in \mss_h$ and
-$z_{(\eta)} \in \mss_{h+1}$ to give a decomposition
+We can then write $\vec{v}  = \sum_{\tau=1}^{\lambda}\vec{w}_{(\tau)} +
+\sum_{\eta=1}^{\kappa} \vec z_{(\eta)}$ with $\vec w_{(\tau)} \in \mss_h$ and
+$\vec z_{(\eta)} \in \mss_{h+1}$ to give a decomposition
 \begin{align}
 \label{eqn:one-point-canonical-form}
-	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{\lambda = 1}
-	^{\kappa_1} \frac{u^{d_h} x^{\vec{w}_{(\lambda)}}} {x_k^{c_h}}
-	\prod_{\eta = 1}^{\kappa_2} \frac{u^{d_{h + 1}} x^{\vec{z}_{(\eta)}}}
+	\frac{u^{\beta} x^{\vec{v}}} {x_k^{\gamma}}	= \prod_{\tau = 1}
+	^{\lambda} \frac{u^{d_h} x^{\vec{w}_{(\tau)}}} {x_k^{c_h}}
+	\prod_{\eta = 1}^{\kappa} \frac{u^{d_{h + 1}} x^{\vec{z}_{(\eta)}}}
 	{x_k^{c_{h + 1}}}
@@
 $\frac{u^{\beta} x^{\vec{v}}}{x_k^\gamma} \in R_D$ as a product of generators,
-this shows that $F_i^{\vec v}$ generate $R_D$.
+this shows that the $F_i^{\vec v}$ generate $R_D$.
 
@@
 \begin{align*}
-	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(1)}}} \cdots
-	(F_i^{\vec{v}_{(\kappa_1)}})^{g_{\vec{v}_{(\kappa_1)}}}
-	(F_{i + 1}^{\vec{w}_{(1)}})^{g_{\vec{w}_{(1)}}} \cdots
-	(F_{i + 1}^{\vec{w}_{(\kappa_2)}})^{g_{\vec{w}_{(\kappa_2)}}}
+	\prod_{\tau=1}^\lambda (F_i^{\vec{v}_{(\tau)}})^{g_{\vec{v}_{(\tau)}}}
+	\prod_{\eta=1}^\kappa (F_{i+1}^{\vec{v}_{(\eta)}})^{g_{\vec{v}_{(\eta)}}}
+	%=	(F_i^{\vec{v}_{(1)}})^{g_{\vec{v}_{(1)}}} \cdots
+	%(F_i^{\vec{v}_{(\lambda)}})^{g_{\vec{v}_{(\lambda)}}}
+	%(F_{i + 1}^{\vec{w}_{(1)}})^{g_{\vec{w}_{(1)}}} \cdots
+	%(F_{i + 1}^{\vec{w}_{(\kappa)}})^{g_{\vec{w}_{(\kappa)}}}
 \end{align*}
-%% TODO: replace \kappa_1 and \kappa_2 with two letters or use prod notation
 
@@
 where $\vec{v}_{(1)} \prec \vec{v}_{(2)} \prec \ldots \prec
-\vec{v}_{(\kappa_1)} \prec \vec{w}_{(1)} \prec \ldots \prec
-\vec{w}_{(\kappa_2)}$. Consequently, the relations of form
-$G_{i, j}^{\vec{v}, \vec{w}}$ and of form $L_{i, j}^{\vec{v},
-\vec{w}}$ generate all the relations among the $F_{i}^{\vec{v},
-\vec{w}}$.
+\vec{v}_{(\lambda)} \prec \vec{w}_{(1)} \prec \ldots \prec
+\vec{w}_{(\kappa)}$. Consequently, the relations of form
+$G_{i, j}^{\vec{v}, \vec{w}}$ and the relations of form
+$L_{i, j}^{\vec{v}, \vec{w}}$ generate all the relations among the
+$F_{i}^{\vec{v}, \vec{w}}$.
 \end{proof}
@@
 	given in Definition~\ref{defn:vec-order}.
-\end{rem}
-
-\begin{rem}
-\label{rem:proj-two-points}
-We cannot extend this result to the case when
-$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
-coefficients in the same manner that O'Dorney does for the
-$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
-in Example ~\ref{eg:hyperplane}, the degrees of generation of the
-section ring of a general $\bq$-divisor supported on two
-hyperplanes cannot be bounded so tightly. The two-point
-$\bp^1$ result leverages the fact that $\bp^1$ has precisely two
-independent coordinates, so that two distinct integral subschemes
-cannot represent equations of only $m$ of the $m+1$ coordinates.
 \end{rem}
@@
 $x_0,\ldots, x_m$.
+
+\begin{rem}
+\label{rem:proj-two-points}
+We cannot extend Theorem~\ref{thm:proj-one-point} to the case when
+$D$ is supported at two hypersurfaces with arbitrary rational (non-effective)
+coefficients in the same manner that O'Dorney does for the
+$\bp^1$ case \cite[Section 4]{dorney:canonical}. As shown
+in Example ~\ref{eg:hyperplane}, the degrees of generation of the
+section ring of a general $\bq$-divisor supported on two
+hyperplanes cannot be bounded so tightly. The two-point
+$\bp^1$ result leverages the fact that $\bp^1$ has precisely two
+independent coordinates, so that two distinct integral subschemes
+cannot represent equations of only $m$ of the $m+1$ coordinates.
+\end{rem}
 

### 2017-11-11 surfaces-write-up/surface-paper.tex
removed and reorganized 2.1

@@
 
-\numberwithin{equation}{subsection}
+\numberwithin{equation}{section}
 
@@
 
-\ssec{Preliminaries on Projective Space}
-Before bounding the degree of generation and relations of
-section rings on projective space, we first
-describe a particular choice of basis for $R_D$ as a $\bk$ vector
-space.
-
-Write \begin{align*}
-	D = \sum_{i=0}^{n}\alpha_i D_i.
-\end{align*}
-where $n \in \bz$, $\alpha_i \in \bq$, and $\deg D_i = \bida_i$. 
-Choose $f_i$ so that $D_i = V(f_i)$.
-We shall further assume for this subsection that (possibly after
-reordering) $f_0,\ldots, f_{m}$ are $m$ independent linear forms
-on $\bp^m$.  This may necessitate the inclusion of ``ghost divisors'' $D_i$ with coefficients $\alpha_i = 0$.
-
-\begin{prop}
-\label{prop:pm-span-and-basis}
-The functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ \rm{(}recall $u$ is a dummy variable keeping
-track of the degree\rm{)}
-satisfying
-both of the following conditions
-
-\begin{enumerate}
-	\item $\sum_{i=0}^{n} c_i \cdot \bida_i = 0$
-	\item $c_i \geq - \lfloor d \alpha_i \rfloor$
-\end{enumerate}
-
-\noindent
-for $c_0, \ldots, c_n \in \bz$
-span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, such functions 
-that also satisfy
-\begin{enumerate}[resume]
-	\item $c_i = -\lfloor d\alpha_i \rfloor \text{ for all } i > m$
-\end{enumerate}
-
-\noindent
-form a basis for $H^0(\bp^m, dD)$ over $\bk$.
-\end{prop}
-
-\begin{proof}
-By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$, and are also necessary to lie in
-$H^0(\mathbb{P}^m,dD)$.
-To complete the proof, it
-suffices to check functions satisfying conditions (1)-(3) form
-a basis of $H^0(\bp^m,dD)$. There are $\binom{m+ \deg \lfloor dD \rfloor }{m}$
-functions satisfying conditions (1)-(3). However we know
-$h^0(\bp^m,dD) = \binom{m+ \deg \lfloor dD \rfloor }{m},$ so it suffices to show
-that those monomials satisfying conditions (1)-(3) are
-independent. 
-To see why these are independent, observe that monomials satisfying (1)-(3) are all of the form
-$f_0^{c_0} \cdots f_m^{c_m} \cdot g$ for the fixed monomial
-$g = f_{m+1}^{-\lfloor d\alpha_{m+1} \rfloor} \cdots f_n^{-\lfloor d\alpha_{m+1} \rfloor}$.
-For any fixed $N \in \bz$, the set 
-\begin{align*}
- \left\{ f_0^{c_0} \cdots f_m^{c_m} : (c_0, \ldots, c_m) \in \bz^{m+1}, \sum_{i=0}^m c_i = N \right\}	
-\end{align*}
-forms an independent set over $\bk$.
-Therefore, multiplying the monomials in the above set with the $g$ also forms an independent set, and these are precisely the monomials satisfying (1)-(3) 
-with $N = -\deg g$.
-\end{proof}
-
 \ssec{Effective Divisors on Projective Space}
@@
 \label{ssec:arbitrary-projective}
-
 We now offer bounds on generators and relations of $R_D$ for a general $\bq$-divisor $D \in \bq \otimes_\bz \di \bp^m$.
-
-Let $D = \sum_{i=0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$ and let $f_i$ be
-homogeneous polynomials in $x_0, \ldots, x_m$ such that $D_i = V(f_i)$ and
-$\deg(f_i) = a_i$ for all $i$.
-
+Write \begin{align*}
+	D = \sum_{i=0}^{n}\alpha_i D_i \in \bq \otimes_\bz \di \bp^m
+\end{align*}
 For the remainder of this section, we shall make the additional assumption that 
@@
 	\text{ are independent linear forms.} \end{align}
-
-The first aim of this section is to prove Theorem
+This may necessitate the inclusion of ``ghost divisors'' $D_i$ with coefficients $\alpha_i = 0$.
+
+The main aim of this section is to prove Theorem
 ~\ref{thm:proj-generators-relations} bounding the number of generators and
-relations of $R_D$. Before doing so, we justify the importance of assumption
+relations of $R_D$. 
+Having justified the necessity of adding ghost divisors, we proceed to bound the
+number of generators and relations of arbitrary $\bq$-divisors in 
+projective space. 
+In \autoref{prop:pm-span-and-basis}, we record a general proposition describing
+a basis for $H^0(\bp^m, dD)$.
+We bound the generators in Lemma ~\ref{lem:proj-generators}, and we use Lemmas ~\ref{lem:composite-map}, ~\ref{lem:bound-ker-chi}, and ~\ref{lem:proj-relations-psi} to bound the 
+degree of relations in the proof of Theorem ~\ref{thm:proj-generators-relations}. Proposition ~\ref{prop:cone-generation}, Lemma ~\ref{lem:composite-map}, and Lemma ~\ref{lem:bound-ker-chi} are quite 
+general and will also be used in Section ~\ref{sec:hirz} to bound the 
+degree of generators and relations on Hirzebruch surfaces.
+However, before moving on to the proof of ~\ref{thm:proj-generators-relations}, we justify the importance of assumption
 ~\eqref{eqn:pm-basis-assumption} with several illustrative examples.
+%riga
+\sssec*{The importance of ghost divisors}
+\label{sssec:ghost-divisors}
 
@@
 \label{eg:hyperplane}
-In this example,we show that the naive generalization of
+In this example, we show that the naive generalization of
 ~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
@@
 
-Having justified the necessity of adding ghost divisors, we proceed to bound the
-number of generators and relations of arbitrary $\bq$-divisors in 
-projective space. We bound the generators in Lemma ~\ref{lem:proj-generators}, and we use Lemmas ~\ref{lem:composite-map}, ~\ref{lem:bound-ker-chi}, and ~\ref{lem:proj-relations-psi} to bound the 
-degree of relations in the proof of Theorem ~\ref{thm:proj-generators-relations}. Proposition ~\ref{prop:cone-generation}, Lemma ~\ref{lem:composite-map}, and Lemma ~\ref{lem:bound-ker-chi} are quite 
-general and will also be used in Section ~\ref{sec:hirz} to bound the 
-degree of generators and relations on Hirzebruch surfaces.
+\sssec*{A basis for sections on projective space}
+\label{sssec:basis-projective}
+
+In order to prepare ourselves to prove \autoref{thm:proj-generators-relations},
+we will need the following simple description of
+a basis for $H^0(\bp^m, dD)$.
+
+\begin{prop}
+\label{prop:pm-span-and-basis}
+Assuming \autoref{eqn:pm-basis-assumption},
+the functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ \rm{(}recall $u$ is a dummy variable keeping
+track of the degree\rm{)}
+satisfying
+both of the following conditions
+
+\begin{enumerate}
+	\item $\sum_{i=0}^{n} c_i \cdot \bida_i = 0$
+	\item $c_i \geq - \lfloor d \alpha_i \rfloor$
+\end{enumerate}
+
+\noindent
+for $c_0, \ldots, c_n \in \bz$
+span $H^0(\bp^m, dD)$ over $\bk$. Furthermore, such functions 
+that also satisfy
+\begin{enumerate}[resume]
+	\item $c_i = -\lfloor d\alpha_i \rfloor \text{ for all } i > m$
+\end{enumerate}
+
+\noindent
+form a basis for $H^0(\bp^m, dD)$ over $\bk$.
+\end{prop}
+
+\begin{proof}
+By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
+(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$, and are also necessary to lie in
+$H^0(\mathbb{P}^m,dD)$.
+To complete the proof, it
+suffices to check functions satisfying conditions (1)-(3) form
+a basis of $H^0(\bp^m,dD)$. There are $\binom{m+ \deg \lfloor dD \rfloor }{m}$
+functions satisfying conditions (1)-(3). However we know
+$h^0(\bp^m,dD) = \binom{m+ \deg \lfloor dD \rfloor }{m},$ so it suffices to show
+that those monomials satisfying conditions (1)-(3) are
+independent. 
+To see why these are independent, observe that monomials satisfying (1)-(3) are all of the form
+$f_0^{c_0} \cdots f_m^{c_m} \cdot g$ for the fixed monomial
+$g = f_{m+1}^{-\lfloor d\alpha_{m+1} \rfloor} \cdots f_n^{-\lfloor d\alpha_{m+1} \rfloor}$.
+For any fixed $N \in \bz$, the set 
+\begin{align*}
+ \left\{ f_0^{c_0} \cdots f_m^{c_m} : (c_0, \ldots, c_m) \in \bz^{m+1}, \sum_{i=0}^m c_i = N \right\}	
+\end{align*}
+forms an independent set over $\bk$.
+Therefore, multiplying the monomials in the above set with the $g$ also forms an independent set, and these are precisely the monomials satisfying (1)-(3) 
+with $N = -\deg g$.
+\end{proof}
+
+\sssec*{Bounding the generators}
+\label{sssec:bounding-generators}
+
+We now develop the tools to bound the degrees of generators for $R_D$ with $D$ a divisor on $\bp^m$.
 
@@
 
+\sssec*{Bounding the relations}
+\label{sssec:relations-projective}
+
+We now move on to bounding the relations of a section ring $R_D$ for $D$ a divisor on $\bp^m$.
 In Lemma ~\ref{lem:composite-map} we show that the degree of the
@@
 
+\sssec*{Proving Theorem ~\ref{thm:proj-generators-relations}}
+\label{sssec:proving-theorem-proj}
 By combining the above results, we get our main theorem bounding

### 2017-11-13 surfaces-write-up/surface-paper.tex
fixed 26

@@
 	In the case that $D = \alpha_0 D_0$ is supported on a single
-	hypersurface, the relations in Theorem ~\ref{thm:proj-one-point}
+	hypersurface and $D' = 0$, the relations in Theorem ~\ref{thm:proj-one-point}
 	form a reduced Gr\"{o}bner basis with respect to the ordering

### 2017-11-14 surfaces-write-up/surface-paper.tex
surfaces: minor intro edits

@@
 %, where $u$ is a dummy variable to keep track of degree.
-In the case that $D = K_X$, the canonical divisor, the graded section ring is referred to as
+In the case that $D = K_X$, where $K_X$ is the canonical divisor,
+the graded section ring is referred to as
 ``the canonical ring'' and is a classical object of study.
@@
 
-One natural way to generalize of the classical result of Petri mentioned above
-is to examine the section rings of stacky curves (i.e., smooth proper
-geometrically connected 1-dimensional Deligne-Mumford
-stacks over a field with a dense open subscheme).
-Indeed,
-these were studied by Voight--Zureick-Brown 
+One natural way to generalize of the classical result of Petri
+mentioned above is to examine the section rings of stacky curves
+(i.e., smooth proper geometrically connected 1-dimensional
+Deligne-Mumford stacks over a field with a dense open subscheme).
+These were studied by Voight--Zureick-Brown 
 \cite{vzb:stacky} and Landesman--Ruhm--Zhang \cite{lrz:spin-cring},
@@
 of log canonical rings and log spin canonical rings on arbitrary
-stacky curves.
-All rings of modular forms associated to Fuchsian groups can be realized as canonical rings of
-such curves, and so the above work also yields insight into such rings
+stacky curves. All rings of modular forms associated to Fuchsian
+groups can be realized as canonical rings of
+such curves, so the above work also yields insight into such rings
 of modular forms.
@@
 
-In addition to section rings of curves, section rings of certain higher dimensional
+Beyond section rings of curves, section rings of certain higher dimensional
 stacks have also been studied.
@@
 $R(X, D)$. In particular, we give a presentation of the
-section ring when $X = \bp^m$ and $D$ is any effective
-$\bq$-divisor.
+section ring when $D$ is any effective
+$\bq$-divisor on $\bp^m$.
 

### 2017-11-14 surfaces-write-up/surface-paper.tex
surfaces: notation subsec & invisible subsecs

@@
 }
+\newcommand\invisiblesubsection{%
+  \refstepcounter{subsection}%
+}
 \makeatother
@@
 \subsection{Notation}
+Throughout, we work over a fixed algebraically closed field $\bk$.
+Since generator and relation degrees are preserved under base change to the algebraic closure, 
+as cohomology commutes with flat base change,
+assuming that $\bk$ is algebraically closed is no restriction
+on generality and the results hold equally well over an arbitrary field.
+
 We now define some notation used throughout the paper.
-We use $m \in \bz$ to index the dimension of a given projective
+We use $m \in \bz_{\geq 0}$ to index the dimension of a given projective
 space $\bp^m$ and the type of the Hirzebruch surface $\hirz_m$.
@@
 \begin{align*}
-	D = \sum_{i=1}^{n}\alpha_i D_i \in \bq \otimes_\bz \di X.
+	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes_\bz \bq.
 \end{align*}\noindent
-where $n \in \bz$ indexes the number of irreducible divisors in 
+where $n \in \bz_{\geq 0}$ indexes the number of irreducible divisors in 
 the above expansion of $D$, $\alpha_i \in \bq$, and $D_i \in \di X$ is an integral
@@
 from $0$ to $n$. In the case $X = \bp^m$, define the degree of $D$ by $\deg D :=
-\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is a divisor $\lfloor D
-\rfloor \in \di X$ is defined to be $\lfloor D \rfloor := \sum_{i = 1}^{n}
+\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is the divisor
+$\lfloor D \rfloor := \sum_{i = 1}^{n}
 \lfloor \alpha_i \rfloor D_i$. Let 
@@
 \rfloor$ denote the fractional part of $r$. 
-Throughout, we work over a fixed algebraically closed field $\bk$.
-Since generator and relation degrees are preserved under base change to the algebraic closure, 
-as cohomology commutes with flat base change,
-assuming that $\bk$ is algebraically closed is no restriction
-on generality and the results hold equally well over an arbitrary field.
-If $D \in \bq \otimes_\bz
-\di X$ is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
+If $D \in \di X \otimes_\bz \bq$
+is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
 
@@
 $\bq$-divisors.
+
 \begin{restatable}{thm}{restateeffective}
 \label{thm:proj-effective-intro}
-Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, with $\alpha_i =
+Let $D = \sum_{i = 0}^{n} \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$, with $\alpha_i =
 \frac{c_i}{k_i} \in \bq_{> 0}$ in reduced form and each $D_i \in \di \bp^m$ an integral divisor.
@@
 \label{thm:proj-generators-relations}
-Let $D = \sum_{i = 0}^n \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$
+Let $D = \sum_{i = 0}^n \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$
 with $\alpha_i = \frac{c_i}{k_i}\in \bq$ in reduced form. Write
@@
 \label{thm:hirz-generators-relations}
-Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
-\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.  
+Let $D = \sum_{i = 1}^n \alpha_i D_i \in \di \hirz_m \otimes_\bz \bq$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.  
 Let each $D_i = V(f_i)$, where $f_i \in \sco(a_i, b_i)$.
@@
 In this subsection, we restrict attention to the case of effective
-fractional divisors $D \in \bq \otimes_\bz \di \bp^m$. We give an explicit presentation of the section ring when $D$ is an effective
+fractional divisors $D \in \di \bp^m \otimes_\bz \bq$. We give an explicit presentation of the section ring when $D$ is an effective
 divisor.
@@
 \label{thm:proj-one-point}
-Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D' \in \bq
-\otimes_\bz \di \bp^m$ and $D = D' + \alpha H$, with $\alpha =
+Let $\bp^m \cong \proj \bk [x_0, \ldots, x_m].$ Let $D' \in \di \bp^m \otimes_\bz \bq$ and $D = D' + \alpha H$, with $\alpha =
 \frac{p}{q} \in \bq_{>0}$, $H := V(x_k)$ a hyperplane of $\bp^m$,
@@
 Now, we inductively add hypersurfaces.
-Let $D' = \sum_{i = 0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, 
+Let $D' = \sum_{i = 0}^{n} \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$, 
 and assume the theorem holds for $D'$. It suffices to show
-the theorem holds for $D \in \di \bq \otimes_\bz \bp^m$, where $D = D' + \alpha C$ for some
+the theorem holds for $D \in \di \bp^m \otimes_\bz \bq$, where $D = D' + \alpha C$ for some
 degree $\pdeg$ hypersurface $C$.
@@
 \label{ssec:arbitrary-projective}
-We now offer bounds on generators and relations of $R_D$ for a general $\bq$-divisor $D \in \bq \otimes_\bz \di \bp^m$.
+We now offer bounds on generators and relations of $R_D$ for a general $\bq$-divisor $D \in \di \bp^m \otimes_\bz \bq$.
 Write \begin{align*}
-	D = \sum_{i=0}^{n}\alpha_i D_i \in \bq \otimes_\bz \di \bp^m
+	D = \sum_{i=0}^{n}\alpha_i D_i \in \di \bp^m \otimes_\bz \bq
 \end{align*}
@@
 This example generalizes slightly to any divisor of the form $D =
-\frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \bq \otimes_\bz \di \bp^2,$ with
+\frac{1}{k}H_0 - \frac{1}{k+1}H_1 \in \di \bp^2 \otimes_\bz \bq,$ with
 $k \in \bn$, showing that there will always exist a generator in
@@
 \[
-	D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \bq
-	\otimes_\bz \bq \di \bp^m,
+	D = \sum_{i=0}^{n} \frac{\num_i}{\den_i}D_i \in \di \bp^m \otimes_\bz \bq,
 \]
@@
 \begin{lem} \label{lem:proj-generators}
-Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m,$ where
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \di \bp^m \otimes_\bz \bq,$ where
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
@@
 \label{lem:composite-map}
-Let $X$ be a $\bk$ variety and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \bq \otimes_\bz \di X$ where $D_i = V(f_i)$. Suppose we have a
+Let $X$ be a $\bk$ variety and let $D = \sum_{i=0}^{n}\alpha_i D_i\in \di X \otimes_\bz \bq$ where $D_i = V(f_i)$. Suppose we have a
 surjection $\phi\colon \bk[w_1,\ldots, w_r] \rightarrow R_D$ given by $w_i
@@
 \label{lem:proj-relations-psi}
-Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \bq \otimes_\bz \di \bp^m$, where
+Let $D = \sum_{i=0}^{n} \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$, where
 $\deg D_i = \bida_i$, $\alpha_i = \frac{c_i}{k_i}\in \bq$, and
@@
 a divisor 
-$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \bq \otimes_\bz \di \bp^m$
+$ D = \sum_{i=0}^n\frac{p_i}{2q_i}H_i \in \di \bp^m \otimes_\bz \bq$
 such that $H_i$ are hyperplanes,  
@@
 \label{sec:hirz}
-\subsection{}
+\invisiblesubsection
 The aim of this section is to prove Theorem
@@
 bi-degrees is 0, say the first one is 0, then $R_D$ is isomorphic
-to $R_{D'}$, where $D' \in \bq \otimes_\bz \di \bp^1$, 
+to $R_{D'}$, where $D' \in \di \bp^1 \otimes_\bz \bq$, 
 where $D'$ can be written as a sum of divisors whose degrees
@@
 \label{lem:hirz-generators}
-For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \bq \otimes_\bz \hirz_m$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the section ring $R_D$ is generated in degrees at most
+For $D = \sum_{i=1}^{n} \frac{c_i}{k_i}D_i \in \di \hirz_m \otimes_\bz \bq$, with $\deg D_i = (\bida_i, \bidb_i), \ell_i = \lcm_{j\neq i} (k_j), \ell_{i,j} = \lcm_{h \neq i,j} (k_h).$ Then, the section ring $R_D$ is generated in degrees at most
 \begin{equation}\label{eqn:def-sigma}
@@
 \label{thm:hirz-generators-relations-full}
-Let $D = \sum_{i = 1}^n \alpha_i D_i \in \bq
-\otimes_\bz \di \hirz_m$ where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.
+Let $D = \sum_{i = 1}^n \alpha_i D_i \in \di \hirz_m \otimes_\bz \bq$
+where $\alpha_i = \frac{c_i}{k_i} \in \bq$ is written in reduced form.
 Write $\ell_{i,j} := \lcm_{h\ne i,j}(k_h)$.
@@
 \label{sec:conc}
-\subsection{}
+\invisiblesubsection
 Recall that every minimal rational surface is either isomorphic to

### 2017-11-15 surfaces-write-up/surface-paper.tex
surfaces: add HJ CF ref, most of (26)

@@
 \usepackage{enumitem}
+\usepackage{url}
 
@@
 be the convergents of the Hirzebruch-Jung continued fraction of
-$\alpha$. Then, the section ring
+$\alpha$ (q.v. \cite[Section 2]{voight:cf} and \cite[Section 3]{hirzebruch:cf}). Then, the section ring
 \[
@@
 {{m + c_i} \choose {c_i}}$ generators $F_i^{\vec{v}} := \frac{u^{d_i}
-x^{\vec{v}}}{x_k^{c_i}}$ where $0 \leq i \leq r$, $\vec{v} \in \bz_{\geq 0}^{m + 1}$
-with $\deg \vec v = c_i$. Furthermore, it has
-relations generated by the following two classes of elements.
+x^{\vec{v}}}{x_k^{c_i}}$ where $0 \leq i \leq r$ and $\vec{v} \in \bz_{\geq 0}^{m + 1}$
+with $\deg \vec v = c_i$. Furthermore, the ideal of
+relations $I$ is generated by the following two classes of elements.
 \begin{enumerate}
 	\item For each $(i, j)$ with $j \geq i + 2$ and each $\vec{v} \in \mss_i,
-\vec{w} \in \mss_j$, there is a relation of the form either
-\begin{flalign*}
-	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+		\vec{w} \in \mss_j$, there is either a relation of the form
+		\begin{align*}
+			G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
 			- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})
-	^{g_{\vec{y}}} &(i < h_{i, j} < j) \\
-	\text{or} \\
-	&G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}}
-	\cdot \prod_{ \vec{z} \in
-	\mss_{h_{i, j} + 1}} (F_{k_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}}
-	&(i < h_{i, j} < h_{i, j} + 1 < j).
-\end{flalign*}
+			^{g_{\vec{y}}} \in I,
+		\end{align*}
+		with $i < h_{i, j} < j$, or there is a relation of the form
+		\begin{align*}
+			G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+			- \left( \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}}
+			\right) \left( \prod_{ \vec{z} \in
+			\mss_{h_{i, j} + 1}} (F_{h_{i, j} + 1}^{\vec{z}})^{g'_{\vec{z}}} \right) \in I,
+		\end{align*}
+		with $i < h_{i, j} < h_{i, j} + 1 < j$.
 	\item For each $(i, j)$ with
@@
 			&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
-	- F_i^{\vec{y}} F_j^{\vec{z}} \\
+			- F_i^{\vec{y}} F_j^{\vec{z}} \in I
 		\end{align*}
@@
 \noindent
-\todo{should we rule out other stupid relations, like those given when w< v?}
+\todo{should we rule out other stupid relations, like those given when $w < v$?}
 where $\vec{y}$ and $\vec{z}$ are the unique
@@
 \noindent
-consisting of products of generators $F_h^{\vec{y}_{(\lambda)}}$
+consisting of products of generators $F_h^{\vec{w}_{(\lambda)}}$
 and $F_{h + 1}^{\vec{z}_{(\eta)}}$ which are in the form
@@
 products of generators in adjacent degrees where $h$
-depends on $i$ and $ j$, so we notate $h_{i, j} := h \in \{1, \ldots, r\}$. We 
+depends on $i$ and $ j$, so we denote $h_{i, j} := h \in \{1, \ldots, r\}$. We 
 also have that $i \leq h_{i, j} < j$ since $(d_i + d_j, c_i + c_j)$ is in the

### 2017-11-15 surfaces-write-up/surface-paper.tex
removed of

@@
 
-One natural way to generalize of the classical result of Petri
+One natural way to generalize the classical result of Petri
 mentioned above is to examine the section rings of stacky curves

### 2017-11-23 surfaces-write-up/surface-paper.tex
surfaces: restore referee comments, changed my email
addressed 14 and 18

@@
 \author{Robin Zhang}
-\address[Robin Zhang]{Department of Mathematics, Stanford University}
-\email{robinz16@stanford.edu}
+\address[Robin Zhang]{Department of Mathematics, Columbia University}
+\email{rzhang@math.columbia.edu}
 
@@
 \cong \proj \bk[x_0, \ldots, x_m]$ and let
-$f_i \in \bk[x_0, \ldots, x_m]$ such that $D_i = V(f_i)$. Now
-suppose that $\{f_0, \ldots, f_n\}$ contains $m + 1$ independent 
-linear polynomials in $x_0, \ldots, x_m$ {\rm(}where we allow for 
+$f_i \in \bk[x_0, \ldots, x_m]$ such that $D_i = V(f_i)$. 
+Suppose that $\{f_0, \ldots, f_n\}$ contains as a subset forming a basis
+for $H^0(\bp^m, \sco_{\bp^m}(1))$, i.e., $m+1$ independent polynomials with corresponding $a_i = 1$,
+{\rm(}where we allow for 
 $\alpha_j = 0$ in the expansion of $D${\rm)}.
@@
 \end{rem}
+
+Note that the assumption given in Theorem~\ref{thm:proj-generators-relations}
+that $\left\{ f_0, \ldots, f_n \right\}$ contains a basis for $H^0(\bp^m, \sco_{\bp^m}(1))$ is not a serious assumption:
+If $D$ is an arbitrary divisor, then $D + 0 \cdot V(x_0) + \cdots + 0 \cdot V(x_m)$ is a divisor satisfying this assumption. Plugging this divisor into the statement
+of Theorem~\ref{thm:proj-generators-relations}, we obtain the following bounds for an arbitrary divisor:
+\begin{cor}
+	\label{cor:proj-generators-relations}
+	Let $D = \sum_{i = 0}^n \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$ be a divisor of positive degree
+with $\alpha_i = \frac{c_i}{k_i}\in \bq$ in reduced form. Write
+$\ell := \lcm_{0 \leq j \leq n}(k_j)$, $\ell_i := \lcm_{0\le j \le n, j \ne i}(k_j)$ and $a_i := \deg D_i$. Let $\bp^m
+\cong \proj \bk[x_0, \ldots, x_m]$ and let
+$f_i \in \bk[x_0, \ldots, x_m]$ such that $D_i = V(f_i)$.
+
+Then $R_D$ is generated in degrees at most 
+$\ell(m+1) + \sum_{i = 0}^n \ell_i a_i$
+with relations generated in degrees at most
+\[
+	\max \left(2 \left(\ell(m+1)+\sum_{i=0}^n \ell_i a_i \right), \frac{\max_{0 \le i \le n}
+	(	\bida_i)}{\deg(D)} + \ell(m+1) + \sum_{i=0}^n \ell_i a_i \right).
+\]
+\end{cor}
 
@@
 $\hirz_m$, and suppose that $\{f_1, \ldots, f_n\}$
-contains two independent 
-linear polynomials in $u, v$ and two independent linear polynomials in
+contains 
+bases for $\sco_{F_m}(1,0)$ and $\sco_{F_m}(0,1)$,
+i.e., two independent linear polynomials in $u, v$ and two independent linear polynomials in
 $w, x$ {\rm(}where we allow for $\alpha_j = 0$ in the expansion of $D${\rm)}.
@@
 bound in Theorem~\ref{thm:hirz-generators-relations-full}.
+\end{rem}
+\begin{rem}
+	As in Theorem~\ref{thm:proj-generators-relations}, the condition that $D$ contain independent polynomials
+	in $u,v$ and $w,z$ is easily removed by replacing $D$ with $D' :=D +0 \cdot u + 0 \cdot v + 0 \cdot w + 0 \cdot z$,
+	and computing the resulting bound for $D'$.
+	One can either take the simpler bound (but slightly weaker) bound from Theorem~\ref{thm:hirz-generators-relations}
+	or the more precise bound given in Theorem~\ref{thm:hirz-generators-relations-full}.
 \end{rem}
@@
 projective space. 
-In \autoref{prop:pm-span-and-basis}, we record a general proposition describing
+In PRoposition~\ref{prop:pm-span-and-basis}, we record a general proposition describing
 a basis for $H^0(\bp^m, dD)$.
@@
 
-In order to prepare ourselves to prove \autoref{thm:proj-generators-relations},
+In order to prepare ourselves to prove Theorem~\ref{thm:proj-generators-relations},
 we will need the following simple description of
@@
 \label{prop:pm-span-and-basis}
-Assuming \autoref{eqn:pm-basis-assumption},
+Assuming Equation~\ref{eqn:pm-basis-assumption},
 the functions $u^d \cdot \prod_{i=0}^n f_i^{c_i} \in (R_D)_d$ \rm{(}recall $u$ is a dummy variable keeping

### 2017-11-23 surfaces-write-up/surface-paper.tex
added in base change remark

@@
 \subsection{Notation}
+\todo{move this notation subsection to its own section, after the introduction}
 Throughout, we work over a fixed algebraically closed field $\bk$.
-Since generator and relation degrees are preserved under base change to the algebraic closure, 
-as cohomology commutes with flat base change,
-assuming that $\bk$ is algebraically closed is no restriction
-on generality and the results hold equally well over an arbitrary field.
+%Since generator and relation degrees are preserved under base change to the algebraic closure, 
+%as cohomology commutes with flat base change,
+%assuming that $\bk$ is algebraically closed is no restriction
+%on generality and the results hold equally well over an arbitrary field.
+\begin{rem}
+	Because cohomology commutes with flat base change, in particular with field extensions,
+the dimensions of the graded pieces of the section ring will be preserved under base change from $\bk$ to $\overline \bk$. Therefore generators
+and relations are preserved under arbitrary base field extension, and hence their minimal degrees are preserve.
+Because of this, there is not harm in assuming $\bk =\overline \bk$. The bounds we give below hold equally well
+over arbitrary fields, but for simplicity we state and prove them over algebraically closed fields.
+
+We note that canonical divisors of root stacks may not behave well with respect to base change of purely inseparable extensions,
+so base change along purely inseparable extensions may cause problems if one considers 
+some section ring associated to the canonical divisor.
+But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
+ring is unchanged upon base change to the algebraic closure.
+\end{rem}
 

### 2017-11-24 surfaces-write-up/surface-paper.tex
finished going through comments and added response to referee

@@
 
-\subsection{Notation}
-\todo{move this notation subsection to its own section, after the introduction}
-Throughout, we work over a fixed algebraically closed field $\bk$.
-%Since generator and relation degrees are preserved under base change to the algebraic closure, 
-%as cohomology commutes with flat base change,
-%assuming that $\bk$ is algebraically closed is no restriction
-%on generality and the results hold equally well over an arbitrary field.
-\begin{rem}
-	Because cohomology commutes with flat base change, in particular with field extensions,
-the dimensions of the graded pieces of the section ring will be preserved under base change from $\bk$ to $\overline \bk$. Therefore generators
-and relations are preserved under arbitrary base field extension, and hence their minimal degrees are preserve.
-Because of this, there is not harm in assuming $\bk =\overline \bk$. The bounds we give below hold equally well
-over arbitrary fields, but for simplicity we state and prove them over algebraically closed fields.
-
-We note that canonical divisors of root stacks may not behave well with respect to base change of purely inseparable extensions,
-so base change along purely inseparable extensions may cause problems if one considers 
-some section ring associated to the canonical divisor.
-But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
-ring is unchanged upon base change to the algebraic closure.
-\end{rem}
-
-We now define some notation used throughout the paper.
-We use $m \in \bz_{\geq 0}$ to index the dimension of a given projective
-space $\bp^m$ and the type of the Hirzebruch surface $\hirz_m$.
-Let $D$ be a (Weil) $\bq$-divisor of the form
-\begin{align*}
-	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes_\bz \bq.
-\end{align*}\noindent
-where $n \in \bz_{\geq 0}$ indexes the number of irreducible divisors in 
-the above expansion of $D$, $\alpha_i \in \bq$, and $D_i \in \di X$ is an integral
-codimension 1 closed subscheme of $X$. When it is convenient to do
-so, we shall sometimes start the indexing at $0$, so that $i$ runs
-from $0$ to $n$. In the case $X = \bp^m$, define the degree of $D$ by $\deg D :=
-\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is the divisor
-$\lfloor D \rfloor := \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor D_i$. Let 
-$R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)$
-denote the section ring associated to the $\bq$-divisor $D$. 
-We often alternatively write
-$R_D := \bigoplus_{d \geq 0} u^d H^0(\bp^m, \lfloor dD \rfloor)$, where $u$ is a dummy
-variable to keep track of the degree.
-We use $R_D$ as notation for $R(X,D)$ when $X$ is understood from context.
-If $R$
-is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
-$\fr(r) := r - \lfloor r
-\rfloor$ denote the fractional part of $r$. 
-If $D \in \di X \otimes_\bz \bq$
-is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
+Throughout, for ease of notation,
+we work over a fixed algebraically closed field $\bk$.
+This is nonessential, see \autoref{rem:algebraically-closed}
 
@@
 
-In Section \ref{sec:proj} we prove the following two results bounding
+After briefly stating our notation in Section~\ref{section:notation},
+in Section~\ref{sec:proj}, we prove the following two results bounding
 the degree of generators and relations of
@@
 Then $R_D$ is generated in degrees at most 
-$\sum_{i = 0}^n \ell_i a_i$
+$\omega := \sum_{i = 0}^n \ell_i a_i$
 with relations generated in degrees at most
 \[
-	\max \left(2 \sum_{i=0}^n \ell_i a_i, \frac{\max_{0 \le i \le n}
-	(	\bida_i)}{\deg(D)} + \sum_{i=0}^n \ell_i a_i \right).
+	\max \left(2 \omega, \frac{\max_{0 \le i \le n}
+	(	\bida_i)}{\deg(D)} + \omega \right).
 \]
@@
 	\label{cor:proj-generators-relations}
-	Let $D = \sum_{i = 0}^n \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$ be a divisor of positive degree
+	Let $D = \sum_{i = 0}^n \alpha_i D_i \in \di \bp^m \otimes_\bz \bq$ 
 with $\alpha_i = \frac{c_i}{k_i}\in \bq$ in reduced form. Write
@@
 Then $R_D$ is generated in degrees at most 
-$\ell(m+1) + \sum_{i = 0}^n \ell_i a_i$
+$\omega' := \ell(m+1) + \sum_{i = 0}^n \ell_i a_i$
 with relations generated in degrees at most
 \[
-	\max \left(2 \left(\ell(m+1)+\sum_{i=0}^n \ell_i a_i \right), \frac{\max_{0 \le i \le n}
-	(	\bida_i)}{\deg(D)} + \ell(m+1) + \sum_{i=0}^n \ell_i a_i \right).
+	\max \left(2 \omega', \frac{\max_{0 \le i \le n}
+	(	\bida_i)}{\deg(D)} + \omega' \right).
 \]
@@
 \[
-	\lcm_{1\le i\le n}(k_i)\cdot \left(\sum_{1\le i\le j\le n} \bida_i \bidb_i\right) 
+	\rho' := \lcm_{1\le i\le n}(k_i)\cdot \left(\sum_{1\le i\le j\le n} \bida_i \bidb_i\right) 
 \]
@@
 with relations generated in degrees at most 
-\[
-	2 \cdot \lcm_{1\le i\le n}(k_i) \cdot \left( \sum_{1\le i\le j\le n} \bida_i \bidb_i\right) 
-\]
+$2 \rho'$.
+%\[
+%	2 \cdot \lcm_{1\le i\le n}(k_i) \cdot \left( \sum_{1\le i\le j\le n} \bida_i \bidb_i\right) 
+%\]
 \end{thm}
@@
 \begin{rem}
+	\label{rem:hirz-generators-relations-hypothesis}
 	As in Theorem~\ref{thm:proj-generators-relations}, the condition that $D$ contain independent polynomials
@@
 
+\section{Notation}
+\label{section:notation}
+\invisiblesubsection
+%Since generator and relation degrees are preserved under base change to the algebraic closure, 
+%as cohomology commutes with flat base change,
+%assuming that $\bk$ is algebraically closed is no restriction
+%on generality and the results hold equally well over an arbitrary field.
+
+In this section, we now collect various notation, used throughout the paper.
+Throughout, for ease of notation,
+we work over a fixed algebraically closed field $\bk$.
+Our results hold equally well over arbitrary fields, as we now explain.
+
+\begin{rem}
+	\label{rem:algebraically-closed}
+	Because cohomology commutes with flat base change, in particular with field extensions,
+the dimensions of the graded pieces of the section ring will be preserved under base change from $\bk$ to $\overline \bk$. Therefore generators
+and relations are preserved under arbitrary base field extension, and hence their minimal degrees are preserve.
+Because of this, there is not harm in assuming $\bk =\overline \bk$. The bounds we give below hold equally well
+over arbitrary fields, but for simplicity we state and prove them over algebraically closed fields.
+
+We note that if $L/\bk$ is an inseparable extension,
+and $X$ is a scheme over $\bk$ than the base change of the canonical divisor
+$(K_X)_L$ may be different then the canonical divisor of the base change
+$K_{X_L}$.
+Therefore, the canonical ring may not be preserved under base change
+along inseparable extensions.
+But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
+ring is unchanged upon base change to the algebraic closure.
+\end{rem}
+
+We next define some notation used throughout the paper.
+We use $m \in \bz_{\geq 0}$ to index the dimension of a given projective
+space $\bp^m$ and the type of the Hirzebruch surface $\hirz_m$.
+Let $D$ be a (Weil) $\bq$-divisor of the form
+\begin{align*}
+	D = \sum_{i=1}^{n}\alpha_i D_i \in \di X \otimes_\bz \bq.
+\end{align*}\noindent
+where $n \in \bz_{\geq 0}$ indexes the number of irreducible divisors in 
+the above expansion of $D$, $\alpha_i \in \bq$, and $D_i \in \di X$ is an integral
+codimension 1 closed subscheme of $X$. When it is convenient to do
+so, we shall sometimes start the indexing at $0$, so that $i$ runs
+from $0$ to $n$. In the case $X = \bp^m$, define the degree of $D$ by $\deg D :=
+\sum_{i=1}^{n}\alpha_i \cdot \deg D_i$. The floor of a $\bq$-divisor $D$ is the divisor
+$\lfloor D \rfloor := \sum_{i = 1}^{n}
+\lfloor \alpha_i \rfloor D_i$. Let 
+$R_D := \bigoplus_{d \geq 0} H^0(X, \lfloor dD \rfloor)$
+denote the section ring associated to the $\bq$-divisor $D$. 
+We often alternatively write
+$R_D := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy
+variable to keep track of the degree.
+We use $R_D$ as notation for $R(X,D)$ when $X$ is understood from context.
+If $R$
+is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
+$\fr(r) := r - \lfloor r
+\rfloor$ denote the fractional part of $r$. 
+If $D \in \di X \otimes_\bz \bq$
+is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
+
 \section{Section Rings of Projective Space}
@@
 		\begin{align*}
-			G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+			G_{i, j}^{\vec{v}, \vec{w}} := F_i^{\vec{v}} F_j^{\vec{w}}
 			- \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})
@@
 		\begin{align*}
-			G_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+			G_{i, j}^{\vec{v}, \vec{w}} := F_i^{\vec{v}} F_j^{\vec{w}}
 			- \left( \prod_{\vec{y} \in \mss_{h_{i, j}}} (F_{h_{i, j}}^{\vec{y}})^{g_{\vec{y}}}
@@
 		\begin{align*}
-			&L_{i, j}^{\vec{v}, \vec{w}} = F_i^{\vec{v}} F_j^{\vec{w}}
+			&L_{i, j}^{\vec{v}, \vec{w}} := F_i^{\vec{v}} F_j^{\vec{w}}
 			- F_i^{\vec{y}} F_j^{\vec{z}} \in I
@@
 \noindent
-\todo{should we rule out other stupid relations, like those given when $w < v$?}
 where $\vec{y}$ and $\vec{z}$ are the unique
@@
 \begin{example}
-	\label{example:}
+	\label{example:effective-example}
 	In this example, we work out generators and relations 
@@
 ~\eqref{eqn:pm-basis-assumption} with several illustrative examples.
-%riga
+
 \sssec*{The importance of ghost divisors}
@@
 By definition of $H^0(\bp^m,dD)$, functions satisfying conditions 
-(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$, and are also necessary to lie in
+(1) and (2) lie in $H^0(\mathbb{P}^m,dD)$.
+Conditions (1) and (2) are also necessary for some monomial in the $f_i$ to lie in
 $H^0(\mathbb{P}^m,dD)$.
+Since the monomials in the $f_i$ span $R_D$, it follows the monomials satisfying
+$(1)$ and $(2)$ span $(R_D)_d = H^0(\bp^m, dD)$.
 To complete the proof, it

### 2017-11-24 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee-3.tex
actually added referee response

--- 2016-08-07 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee.tex
@@
 \section{Changes Made}
-Here are the changes we have made in response to the referee's suggestions.
+Here are some responses to the referee's suggestions.
+Item's below are numbered to match the referee report.
+We applied nearly all changes suggested by the referee, though most need no
+comment. Here, we make some brief comments on how we applied certain suggested
+changes.
 \begin{enumerate}
-	\item We changed the name ``canonical ring'' to ``generalized canonical ring,'' as the referee suggested,
-		since the canonical ring is really a special case of the generalized canonical ring, in the case
-		$D = K$.
-	\item We explained
-		in more detail how our potential application
-		for Hilbert modular forms and the difficulty in producing
-		an explicit example in the Modular Forms subsection of the introduction.
-	\item In all of the main theorems, it says that $\frac{c_i}{k_i}$ is in reduced form. 
-	\item In Theorem \autoref{thm:proj-generators-relations}, $k$ is a field.
-Throughout our paper, the results hold for arbitrary fields, but we may assume the field is algebraically closed because the generator and relation degrees are preserved by base change to the algebraic closure.
-We have now included and clarified this in the ``Notations and Conventions'' subsection at the end of the introduction.
-	\item On page 2, line -9 of the previous version, $\deg(D)$ should have been $\frac{1}{2 \prod_{i=0}^n q_i}$ and is now corrected.
-	\item Theorem 1.4 (now Theorem \ref{thm:hirz-generators-relations}) has been rewritten into a simpler form by reducing some
-		notation unnecessary to understanding the general idea.
-We then state it more precisely as Theorem \ref{thm:hirz-generators-relations-full}.
-The statement of Theorem \ref{thm:hirz-generators-relations-full} has also been simplified, since we noticed the previously defined quantity $\tau$ was unnecessary.
-	\item Subsection 1.2, which defined necessary notation for our main results, has now been moved to immediately precede the statement of our main results.
-	\item The reference to later items given on page 5, line 7 of the previous version
-		has been moved to Remark \ref{rem:proj-grobner}.
-\item The use of best lower approximations has been replaced by the use of
-convergents of Hirzebruch-Jung continued fractions which are equivalent and
-well-known.
-\item The references for the O'Dorney and Landesman--Ruhm--Zhang papers have been updated. The citation for arxiv articles now includes the arxiv reference numbers.
-\item The conditions of Proposition~\autoref{prop:pm-span-and-basis} have been reorganized for clarity.
-\item Remark 1.3 has been split into what is now Remark~\autoref{rem:proj-tight-bounds-eff} and Remark~\autoref{rem:proj-tight-bounds} (with
-some material moved to Remark~\autoref{rem:exact-noneff-bounds}).
+	\item[(2)] 
+We have now added in a detailed example 
+\autoref{example:effective-example}
+explaining how to apply our method of proof to actually work out
+the generators and relations for a section ring
+associated to an effective divisor on $\bp^m$.
+\item[(10)]
+Response to the concern about base change along inseparable extensions:
+We added Remark \autoref{rem:algebraically-closed}
+explaining why purely inseparable extensions pose
+no addition issue. The point is that cohomology commutes with flat base change, and extensions of fields
+are always flat, so the dimensions of the graded pieces of the ring will be preserved. Therefore generators
+and relations are preserved under arbitrary base field extension. Of course,
+canonical divisors of root stacks may not behave well with respect to base change (as we learned from a version of Voight--Zureick-Brown's forthcoming book available on Voight's website)
+which is why inseparable extensions
+may cause problems for canonical rings.
+But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
+ring is unchanged upon base change to the algebraic closure.
 
+\item[(14) and (18)]
+We explained in both the projective space case and Hirzebruch case that this assumption was nonessential, adding
+\autoref{cor:proj-generators-relations} for the projective case
+and \autoref{rem:hirz-generators-relations-hypothesis} for the Hirzebruch case.
+You are correct that we could have easily changed coordinates and reordered the $f_i$ so that the first $m+1$ $f_i$ were $x_0, \ldots, x_m$, but
+it seems we may as well state it with arbitrary independent polynomials, so as not to require such a change of basis.
+\item[(22)]
+	We moved the notation to its own section after the introduction,
+	as most of the notation was not necessary to state
+	our main theorems.
+\item[(24)]
+	You're right that the proof of \autoref{prop:pm-span-and-basis}
+		was poorly phrased, and we have tried to clarify this now.
+The point is that we are only varying $f_0, \ldots, f_m,$ so
+the resulting monomials in the $f_i$ will be independent because products of the $f_i$ are. See the updated proof in the paper for the details.
+\item[(25)]
+It is not an ordering, only a partial ordering (which we have now stated).
+\item[(27)]
+Good point, we should have done a reduction instead of claiming it was analogous.
+\item[(28)]
+Wouldn't there be something like $\binom{m + c_1- 1}{c_1}$ elements? For example, if
+we take $\alpha = 1$, and $H = V(x_0)$ we will have generators $x_1/x_0, \ldots, x_m/x_0$.
+In any case, we decided to remove the paragraph this comment
+was referring to and the claim about minimality
+of the presentation from the theorem.
 \end{enumerate}

### 2017-11-25 surfaces-write-up/MRL/MRL-surfaces-responses-to-referee-3.tex
surfaces: revisions on Aaron's edits + finishing touches

@@
 \section{Changes Made}
-Here are some responses to the referee's suggestions.
-Item's below are numbered to match the referee report.
-We applied nearly all changes suggested by the referee, though most need no
-comment. Here, we make some brief comments on how we applied certain suggested
+The authors would like to express their gratitude for
+the numerous helpful suggestions given by the referee.
+We applied nearly all such suggestions and give here
+some brief comments on how we applied certain suggested
 changes.
@@
 	\item[(2)] 
-We have now added in a detailed example 
-\autoref{example:effective-example}
+		We have added in a detailed example 
+		(Example~\autoref{example:effective-example})
 		explaining how to apply our method of proof to actually work out
@@
 		associated to an effective divisor on $\bp^m$.
+
 	\item[(10)]
-Response to the concern about base change along inseparable extensions:
-We added Remark \autoref{rem:algebraically-closed}
+		Response to the concern about base change along inseparable
+		extensions:
+		We added Remark~\autoref{rem:algebraically-closed}
 		explaining why purely inseparable extensions pose
-no addition issue. The point is that cohomology commutes with flat base change, and extensions of fields
-are always flat, so the dimensions of the graded pieces of the ring will be preserved. Therefore generators
-and relations are preserved under arbitrary base field extension. Of course,
-canonical divisors of root stacks may not behave well with respect to base change (as we learned from a version of Voight--Zureick-Brown's forthcoming book available on Voight's website)
+		no additional issue. The point is that cohomology commutes with
+		flat base change, and extensions of fields
+		are always flat, so the dimensions of the graded pieces of the
+		ring will be preserved. Therefore generators
+		and relations are preserved under arbitrary base field
+		extension. Of course, canonical divisors of root stacks may not
+		behave well with respect to base change (as we learned from a
+		version of Voight--Zureick-Brown's forthcoming book available
+		on Voight's website)
 		which is why inseparable extensions
 		may cause problems for canonical rings.
-But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
+		But, for the purposes of this article, we fix a divisor on a
+		scheme over some base field, and the structure of that particular section
 		ring is unchanged upon base change to the algebraic closure.
 
-\item[(14) and (18)]
-We explained in both the projective space case and Hirzebruch case that this assumption was nonessential, adding
-\autoref{cor:proj-generators-relations} for the projective case
-and \autoref{rem:hirz-generators-relations-hypothesis} for the Hirzebruch case.
-You are correct that we could have easily changed coordinates and reordered the $f_i$ so that the first $m+1$ $f_i$ were $x_0, \ldots, x_m$, but
-it seems we may as well state it with arbitrary independent polynomials, so as not to require such a change of basis.
+	\item[(14) \& (18)]
+		We explained in both the projective space case and Hirzebruch case
+		that this assumption was nonessential, adding
+		Corollary~\autoref{cor:proj-generators-relations} for the projective case
+		and Remark~\autoref{rem:hirz-generators-relations-hypothesis} for the
+		Hirzebruch case. You are correct that we could have easily changed
+		coordinates and reordered the $f_i$ so that the first $m+1$
+		many $f_i$'s were $x_0, \ldots, x_m$, but
+		we may as well state it with arbitrary independent polynomials so
+		as not to require such a change of basis.
+
 	\item[(22)]
@@
 		our main theorems.
+
 	\item[(24)]
-	You're right that the proof of \autoref{prop:pm-span-and-basis}
-		was poorly phrased, and we have tried to clarify this now.
+		Indeed, the proof of \autoref{prop:pm-span-and-basis}	was poorly
+		phrased, and we have tried to clarify this now.
 		The point is that we are only varying $f_0, \ldots, f_m,$ so
-the resulting monomials in the $f_i$ will be independent because products of the $f_i$ are. See the updated proof in the paper for the details.
+		the resulting monomials in the $f_i$ will be independent because
+		products of the $f_i$ are. See the updated proof in the paper for the details.
+
 	\item[(25)]
 		It is not an ordering, only a partial ordering (which we have now stated).
+
 	\item[(27)]
 		Good point, we should have done a reduction instead of claiming it was analogous.
+		This is now included at the beginning of the proof of the theorem
+		(now numbered \autoref{thm:proj-one-point}).
+
 	\item[(28)]
-Wouldn't there be something like $\binom{m + c_1- 1}{c_1}$ elements? For example, if
-we take $\alpha = 1$, and $H = V(x_0)$ we will have generators $x_1/x_0, \ldots, x_m/x_0$.
-In any case, we decided to remove the paragraph this comment
-was referring to and the claim about minimality
-of the presentation from the theorem.
+		Wouldn't there be something like $\binom{m + c_1- 1}{c_1}$ many
+		elements? For example, if	we take $\alpha = 1$, and $H = V(x_0)$
+		we will have generators $x_1/x_0, \ldots, x_m/x_0$.
+		In any case, we decided to remove the paragraph mentioned by
+		this comment as well as the claim about minimality of the
+		presentation given in the theorem.
 \end{enumerate}

### 2017-11-25 surfaces-write-up/surface-paper.tex
surfaces: revisions on Aaron's edits + finishing touches

@@
 
-Then the section ring $R_D$
+Then the section ring $R(\bp^m, D)$
 is generated in degrees at most $\max_{0 \leq i \leq n}{k_i}$ with
@@
 $f_i \in \bk[x_0, \ldots, x_m]$ such that $D_i = V(f_i)$. 
-Suppose that $\{f_0, \ldots, f_n\}$ contains as a subset forming a basis
-for $H^0(\bp^m, \sco_{\bp^m}(1))$, i.e., $m+1$ independent polynomials with corresponding $a_i = 1$,
-{\rm(}where we allow for 
-$\alpha_j = 0$ in the expansion of $D${\rm)}.
-
-Then $R_D$ is generated in degrees at most 
+Suppose that $\{f_0, \ldots, f_n\}$ contains a basis
+for $H^0(\bp^m, \sco_{\bp^m}(1))$, {\rm(}i.e. $m+1$ independent polynomials with
+corresponding $a_i = 1${\rm)}.
+
+Then $R(\bp^m, D)$ is generated in degrees at most 
 $\omega := \sum_{i = 0}^n \ell_i a_i$
@@
 
-Then $R_D$ is generated in degrees at most 
-$\omega' := \ell(m+1) + \sum_{i = 0}^n \ell_i a_i$
+Then $R(\bp^m, D)$ is generated in degrees at most 
+$\omega' := (m+1)\ell + \sum_{i = 0}^n \ell_i a_i$
 with relations generated in degrees at most
@@
 $\hirz_m$, and suppose that $\{f_1, \ldots, f_n\}$
-contains 
-bases for $\sco_{F_m}(1,0)$ and $\sco_{F_m}(0,1)$,
-i.e., two independent linear polynomials in $u, v$ and two independent linear polynomials in
-$w, x$ {\rm(}where we allow for $\alpha_j = 0$ in the expansion of $D${\rm)}.
-
-Then $R_D$ is generated in degrees at most
+contains bases for $\sco_{F_m}(1,0)$ and $\sco_{F_m}(0,1)$
+{\rm(}i.e., two independent linear polynomials in $u, v$ and two independent linear polynomials in
+$w, z$ {\rm)}.
+
+Then $R(\hirz_m, D)$ is generated in degrees at most
 \[
@@
 \end{thm}
+
 \begin{rem}
-Theorem~\ref{thm:hirz-generators-relations} is restated with a more precise
-bound in Theorem~\ref{thm:hirz-generators-relations-full}.
+Theorem~\ref{thm:hirz-generators-relations} is restated with a more
+precise bound in Theorem~\ref{thm:hirz-generators-relations-full}.
 \end{rem}
+
 \begin{rem}
 	\label{rem:hirz-generators-relations-hypothesis}
-	As in Theorem~\ref{thm:proj-generators-relations}, the condition that $D$ contain independent polynomials
-	in $u,v$ and $w,z$ is easily removed by replacing $D$ with $D' :=D +0 \cdot u + 0 \cdot v + 0 \cdot w + 0 \cdot z$,
-	and computing the resulting bound for $D'$.
-	One can either take the simpler bound (but slightly weaker) bound from Theorem~\ref{thm:hirz-generators-relations}
-	or the more precise bound given in Theorem~\ref{thm:hirz-generators-relations-full}.
+	As in Theorem~\ref{thm:proj-generators-relations}, the condition
+	of Theorem~\ref{thm:hirz-generators-relations} that $D$ contain
+	independent polynomials in $u, v$ and $w, z$ is
+	easily removed by replacing $D$ with $D' :=D +0 \cdot u + 0 \cdot
+	v + 0 \cdot w + 0 \cdot z$,	and computing the resulting bound for
+	$D'$ using either the simpler (but slightly weaker) bound
+	from Theorem~\ref{thm:hirz-generators-relations} or the more
+	precise bound given in Theorem~\ref{thm:hirz-generators-relations-full}.
 \end{rem}
@@
 
-In this section, we now collect various notation, used throughout the paper.
-Throughout, for ease of notation,
-we work over a fixed algebraically closed field $\bk$.
-Our results hold equally well over arbitrary fields, as we now explain.
+In this section, we now collect various notation used throughout the paper.
+Throughout,
+we work over a fixed algebraically closed field $\bk$ for ease of notation,
+but our results hold equally well over arbitrary fields.
 
@@
 \label{rem:algebraically-closed}
-	Because cohomology commutes with flat base change, in particular with field extensions,
-the dimensions of the graded pieces of the section ring will be preserved under base change from $\bk$ to $\overline \bk$. Therefore generators
-and relations are preserved under arbitrary base field extension, and hence their minimal degrees are preserve.
-Because of this, there is not harm in assuming $\bk =\overline \bk$. The bounds we give below hold equally well
-over arbitrary fields, but for simplicity we state and prove them over algebraically closed fields.
-
-We note that if $L/\bk$ is an inseparable extension,
-and $X$ is a scheme over $\bk$ than the base change of the canonical divisor
-$(K_X)_L$ may be different then the canonical divisor of the base change
-$K_{X_L}$.
+Because cohomology commutes with flat base change (in particular
+with field extensions) the dimensions of the graded pieces of the
+section ring will be preserved under base change from $\bk$ to
+$\overline \bk$. Therefore generators and relations are preserved
+under arbitrary base field extension, and so their minimal
+degrees are preserved. Consequently, there is no harm in
+assuming $\bk = \overline \bk$ for our proofs. The bounds we give
+hold equally well over arbitrary fields.
+
+Note that if $L/\bk$ is an inseparable extension
+and $X$ is a scheme over $\bk$, then the base change of the
+canonical divisor $(K_X)_L$ may be different than the canonical
+divisor of the base change $K_{X_L}$.
 Therefore, the canonical ring may not be preserved under base change
-along inseparable extensions.
-But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
-ring is unchanged upon base change to the algebraic closure.
+along inseparable extensions. Nonetheless, the results we give are
+not affected because given a divisor on a scheme over some base field,
+the structure of that particular section ring is unchanged upon
+base change to the algebraic closure.
 \end{rem}
 
-We next define some notation used throughout the paper.
-We use $m \in \bz_{\geq 0}$ to index the dimension of a given projective
-space $\bp^m$ and the type of the Hirzebruch surface $\hirz_m$.
-Let $D$ be a (Weil) $\bq$-divisor of the form
+Let $D$ be a (Weil) $\bq$-divisor on a rational surface $X$ of the form
 \begin{align*}
@@
 $\lfloor D \rfloor := \sum_{i = 1}^{n}
-\lfloor \alpha_i \rfloor D_i$. Let 
-$R_D := \bigoplus_{d \geq 0} H^0(X, \lfloor dD \rfloor)$
+\lfloor \alpha_i \rfloor D_i$.
+
+Let $R(X, D) := \bigoplus_{d \geq 0} H^0(X, \lfloor dD \rfloor)$
 denote the section ring associated to the $\bq$-divisor $D$. 
 We often alternatively write
-$R_D := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy
+$R(X, D) := \bigoplus_{d \geq 0} u^d H^0(X, \lfloor dD \rfloor)$, where $u$ is a dummy
 variable to keep track of the degree.
-We use $R_D$ as notation for $R(X,D)$ when $X$ is understood from context.
-If $R$
-is a graded ring, we denote the $d$th graded component of $R$ by $R_d$. If $r$ is a rational number, we let
-$\fr(r) := r - \lfloor r
-\rfloor$ denote the fractional part of $r$. 
-If $D \in \di X \otimes_\bz \bq$
-is an arbitrary divisor, we denote $h^0(X, D) := \dim_\bk H^0(X,D)$.
+When $X$ is understood from context, we use $R_D$ as notation for $R(X, D)$.
+
+We use $m \in \bz_{\geq 0}$ to index the dimension of a given
+projective space $\bp^m$ and the type of the Hirzebruch surface
+$\hirz_m$. If $S$ is a graded ring, we denote the $d$th graded
+component of $S$ by $S_d$. If $r$ is a rational number, we let
+$\fr(r) := r - \lfloor r \rfloor$ denote the fractional part of $r$. 
+If $D \in \di X \otimes_\bz \bq$ is an arbitrary divisor, we denote
+$h^0(X, D) := \dim_\bk H^0(X,D)$.
 
@@
 Let $\bk$ be a field and let $\bp^m$ denote $m$-dimensional
-projective space over $\bk$. In this section, we bound the degrees
-of generators and relations for divisors
-on $\bp^m$, for all $m \geq 1$ in Theorem
-~\ref{thm:proj-effective-intro}.
+projective space over $\bk$. In this section, we prove
+Theorem~\ref{thm:proj-generators-relations}, which bounds the degrees
+of generators and relations of the section ring of any $\bq$-divisor
+on $X = \bp^m$ for all $m \geq 1$. We also prove
+Theorem ~\ref{thm:proj-effective-intro} to give an explicit
+description of the generators of the section ring $R_D$ when $D$ is
+an effective divisor.
+
 If $\deg D < 0$, the
@@
 we shall assume $\deg D > 0$.
-The $\bp^1$ case restricts to the results of
-\cite{dorney:canonical}. We also give an explicit description of the
-generators of the section ring $R_D$ when $D$ is an effective divisor in Theorem ~\ref{thm:proj-generators-relations}.
+Note that the $\bp^1$ case, in particular, restricts to the results
+of \cite{dorney:canonical}.
 
@@
 be the convergents of the Hirzebruch-Jung continued fraction of
-$\alpha$ (q.v. \cite[Section 2]{voight:cf} and \cite[Section 3]{hirzebruch:cf}). Then, the section ring
+$\alpha$ {\rm(}q.v. \cite[Section 2]{voight:cf} and
+\cite[Section 3]{hirzebruch:cf}{\rm)}. Then, the section ring
 \[
@@
 and relations map to a full set of relations for $R_D$ over $R_{D'}$.
+Hence, for the remainder of the proof, we can assume $D' = 0$.
 %is equivalent to giving a presentation
@@
 
-Hence, for the remainder of the proof, we assume $D' = 0$.
 %We will first check that $F^{\vec v}_i$ determine a system of minimal
@@
 The main aim of this section is to prove Theorem
-~\ref{thm:proj-generators-relations} bounding the number of generators and
-relations of $R_D$. 
+~\ref{thm:proj-generators-relations}.
 Having justified the necessity of adding ghost divisors, we proceed to bound the
@@
 projective space. 
-In PRoposition~\ref{prop:pm-span-and-basis}, we record a general proposition describing
+In Proposition~\ref{prop:pm-span-and-basis}, we record a general proposition describing
 a basis for $H^0(\bp^m, dD)$.
@@
 
-We now develop the tools to bound the degrees of generators for $R_D$ with $D$ a divisor on $\bp^m$.
+We now develop the tools to bound the degrees of generators for $R_D$
+for $D$ an arbitrary divisor on $\bp^m$.
 
@@
 
-We now move on to bounding the relations of a section ring $R_D$ for $D$ a divisor on $\bp^m$.
+We now move on to bounding the degree of relations of a section ring $R_D$ for $D$ a divisor on $\bp^m$.
 In Lemma ~\ref{lem:composite-map} we show that the degree of the
@@
 
-\section{Section Rings of Hirzebruch surfaces}
+\section{Section Rings of Hirzebruch Surfaces}
 \label{sec:hirz}
 \invisiblesubsection
+Let $\hirz_m$ denote the $m$-th Hirzebruch surface.
 The aim of this section is to prove Theorem
-~\ref{thm:hirz-generators-relations}, bounding the degree of
-generators and relations of the section ring of a $\bq$-divisor
-on any Hirzebruch surface.
+~\ref{thm:hirz-generators-relations}, which bounds the degree of
+generators and relations of the section ring of any $\bq$-divisor
+on $X = \hirz_m$, for all $m \geq 0$.
 
@@
 
-Furthermore, similarly to the case of projective space, 
-we will restrict to the case that $D$ is a divisor
+Furthermore, we will restrict to the case that $D$ is a divisor
 for which both of its bi-degrees are positive. We now justify this

### 2017-12-18 surfaces-write-up/surface-paper.tex
consistent title spelling

@@
 
-\title[Section Rings of $\bq$-divisors]{Section Rings of $\bq$-divisors on minimal rational surfaces}
+\title[Section rings of $\bq$-divisors]{Section rings of $\bq$-divisors on minimal rational surfaces}
 
@@
 to effective $\bq$-divisors and the second applies to arbitrary
-$\bq$-divisors.
+$\bq$-divisors. Note that here we allow coefficients of divisors to be 0,
+see Section~\ref{ssec:arbitrary-projective}.
 

### 2017-12-19 surfaces-write-up/Landesman-Ruhm-Zhang-Rational-Surfaces-MRL.tex
MRL style update

--- 2017-12-18 surfaces-write-up/surface-paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%
-\documentclass{amsart}
+\documentclass{mrlart7}
 
@@
 \usetikzlibrary{matrix,arrows,decorations.pathmorphing}
+
+%% MRL requirements
+	\def\volno{18}
+	\def\yrno{2011}
+	\def\issueno{00}
+	\setcounter{page}{10001}
+	\def\lpageno{100NN} %temporary numbers
+  %%replace NN with the pagelength of the paper%%
+	\overfullrule=5pt
 
@@
 \author{Aaron Landesman}
-\address[Aaron Landesman]{Department of Mathematics, Stanford University}
+\address[Aaron Landesman]{Department of Mathematics \\ Stanford University}
+\urladdr{http://web.stanford.edu/$\sim$aaronlan/}
 \email{aaronlandesman@stanford.edu}
@@
 \author{Peter Ruhm}
-\address[Peter Ruhm]{Department of Mathematics, Stanford University}
+\address[Peter Ruhm]{Department of Mathematics \\ Stanford University}
 \email{pruhm@stanford.edu}
@@
 \author{Robin Zhang}
-\address[Robin Zhang]{Department of Mathematics, Columbia University}
+\address[Robin Zhang]{Department of Mathematics \\ Columbia University}
+\urladdr{http://math.columbia.edu/$\sim$rzhang/}
 \email{rzhang@math.columbia.edu}
@@
 
-\section{Acknowledgments}
+\section*{Acknowledgments}
 \label{sec:ack}
@@
 \bibliography{bibliography-stacky-surface}
-\bibliographystyle{alpha}
+\bibliographystyle{mrl}
 

### 2017-12-19 surfaces-write-up/MRL/Landesman-Ruhm-Zhang-Rational-Surfaces-MRL-08-23-15.tex
MRL style update

--- 2015-08-23 surfaces-write-up/arXiv-versions/surface-write-up-arXiv-v1.tex
@@
 \begin{figure}
-\includegraphics{spin-lower-approximations-pic-pics.pdf}
+\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
 \caption{This figure shows each non-negative best lower

### 2018-01-09 surfaces-write-up/surface-paper.tex
fix section ref typo, delete comments
more typos found

@@
 they would give a bound on generators and relations for 
-rings of Hilbert and Siegel modular forms parameterized by rational
+rings of Hilbert and Siegel modular forms parametrized by rational
 Hilbert and Siegel modular surfaces.
-See Theorem~\ref{sec:conc} for a potential approach for generalizing our results to arbitrary rational surfaces.
+See Section~\ref{sec:conc} for a potential approach for generalizing our results to arbitrary rational surfaces.
 This would be interesting because such modular surfaces tend to be
@@
 in terms of the section 
-rings of some associated divisors that given surface.
+rings of some associated divisors on that given surface.
 
